### 2013-02-15 trunk/CompFuzzExt.tex
Initial commit

\documentclass[11pt]{article}
\def\shownotes{1}

\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsthm, amsfonts}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{algpseudocode}

\newcommand{\secref}[1]{\mbox{Section~\ref{#1}}}
\newcommand{\subsecref}[1]{\mbox{Subsection~\ref{#1}}}
\newcommand{\apref}[1]{\mbox{Appendix~\ref{#1}}}
\newcommand{\thref}[1]{\mbox{Theorem~\ref{#1}}}
\newcommand{\exref}[1]{\mbox{Example~\ref{#1}}}
\newcommand{\defref}[1]{\mbox{Definition~\ref{#1}}}
\newcommand{\corref}[1]{\mbox{Corollary~\ref{#1}}}
\newcommand{\lemref}[1]{\mbox{Lemma~\ref{#1}}}
\newcommand{\assref}[1]{\mbox{Assumption~\ref{#1}}}
\newcommand{\probref}[1]{\mbox{Problem~\ref{#1}}}
\newcommand{\clref}[1]{\mbox{Claim~\ref{#1}}}
\newcommand{\propref}[1]{\mbox{Proposition~\ref{#1}}}
\newcommand{\remref}[1]{\mbox{Remark~\ref{#1}}}
\newcommand{\consref}[1]{\mbox{Construction~\ref{#1}}}
\newcommand{\figref}[1]{\mbox{Figure~\ref{#1}}}
\DeclareMathOperator*{\expe}{\mathbb{E}}

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}

\newcommand{\A}{\mathcal{A}}
\newcommand{\D}{\mathcal{D}}

\newcommand{\metric}{\ensuremath{\mathtt{Metric}}\xspace}
\newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
\newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
\newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
\newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
\newcommand{\metricd}{\ensuremath{\mathtt{Metric}^*\mathtt{-d}}\xspace}
\newcommand{\hillstar}{\ensuremath{\mathtt{HILL}^*}\xspace}
\newcommand{\hillprime}{\ensuremath{\mathtt{HILL'}}\xspace}
\newcommand{\metricprime}{\ensuremath{\mathtt{Metric'}}\xspace}
\newcommand{\metricprimestar}{\ensuremath{\mathtt{Metric'}^*}\xspace}
\newcommand{\hillprimestar}{\ensuremath{\mathtt{HILL'}^*}\xspace}
\newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
\newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
\newcommand{\Hoo}{\mathrm{H}_\infty}
\newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
\newcommand{\Dom}{\mathsl{Dom}}
\newcommand{\Range}{\mathsl{Rng}}
\newcommand{\Keys}{\mathsl{Keys}}
\def\col{\mathrm{Col}}

\newcommand{\ddetbin}{\ensuremath{\mathcal{D}^{det,\{0,1\}}}}
\newcommand{\drandbin}{\ensuremath{\mathcal{D}^{rand,\{0,1\}}}}
\newcommand{\ddetrange}{\ensuremath{\mathcal{D}^{det,[0,1]}}}
\newcommand{\drandrange}{\ensuremath{\mathcal{D}^{rand,[0,1]}}}

\newcommand{\expinfo}{\ensuremath{\mathcal{E}}}
\newcommand{\ext}{\ensuremath{\mathtt{ext}}}
\newcommand{\rext}{\ensuremath{\mathtt{rext}}}
\newcommand{\cons}{\ensuremath{\mathtt{cons}}}
\newcommand{\decons}{\ensuremath{\mathtt{decons}}}

\newcommand{\lwe}{\class{LWE}}
\newcommand{\LWE}{\class{LWE}}
\newcommand{\distLWE}{\ensuremath{\class{dist\mbox{-}LWE}}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{construction}[theorem]{Construction}

\newcounter{ctr}
\newcounter{savectr}
\newcounter{ectr}

\newenvironment{newitemize}{%
\begin{list}{\mbox{}\hspace{5pt}$\bullet$\hfill}{\labelwidth=15pt%
\labelsep=5pt \leftmargin=20pt \topsep=3pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{3pt} }}{\end{list}}

\newenvironment{newenum}{%
\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=17pt%
\labelsep=5pt \leftmargin=22pt \topsep=3pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt} }}{\end{list}}

\newenvironment{tiret}{%
\begin{list}{\hspace{2pt}\rule[0.5ex]{6pt}{1pt}\hfill}{\labelwidth=15pt%
\labelsep=3pt \leftmargin=22pt \topsep=3pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt}}}{\end{list}}

\newenvironment{blocklist}{\begin{list}{}{\labelwidth=0pt%
\labelsep=0pt \leftmargin=0pt \topsep=10pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{20pt}}}{\end{list}}

\newenvironment{blocklistindented}{\begin{list}{}{\labelwidth=0pt%
\labelsep=30pt \leftmargin=30pt\topsep=5pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{10pt}}}{\end{list}}

\newenvironment{onelist}{%
\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=18pt%
\labelsep=7pt \leftmargin=25pt \topsep=2pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt} }}{\end{list}}

\newenvironment{twolist}{%
\begin{list}{{\rm (\arabic{ctr}.\arabic{ectr})}%
\hfill}{\usecounter{ectr} \labelwidth=26pt%
\labelsep=7pt \leftmargin=33pt \topsep=2pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt} }}{\end{list}}

\newenvironment{centerlist}{%
\begin{list}{\mbox{}}{\labelwidth=0pt%
\labelsep=0pt \leftmargin=0pt \topsep=10pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{10pt} }}{\end{list}}

\newenvironment{newcenter}[1]{\begin{centerlist}\centering%
\item #1}{\end{centerlist}}

\newenvironment{codecenter}[1]{\begin{small}\begin{centerlist}\centering%
\item #1}{\end{centerlist}\end{small}}

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\xnote}[1]{{\authnote{Xianrui}{#1}}}

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\ignore}[1]{}

\title{\textbf{Computational Fuzzy Extractors}}
\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
 \and Xianrui Meng \and Leonid Reyzin}
\begin{document}
\maketitle

\begin{abstract} 
One-message information reconciliation protocols called secure sketches remove noise
from secrets without revealing too much about them.  They are a crucial ingredient in
fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.

Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  The minimal entropy loss is dictated by bounds on error-correcting codes.

We overcome these bounds by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors, and building them based on the Learning with Errors (LWE) problem.  We thus obtain the first secure sketch with no loss in entropy.   More specifically, our contributions are as follows:

\begin{itemize}
\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.  We do so by demonstrating that a secure sketch defined via HILL pseudoentropy is subject to the same coding-based  bounds as the information-theoretic secure sketch.  We then find a different relaxation, using unpredictability entropy, and show that it can be used to construct computational fuzzy extractors.

\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.  This construction requires us to show that the decision version of LWE is secure when a small number of dimensions have no error---a result that may be of independent interest.
\end{itemize}
\end{abstract}

\newcommand{\M}{\mathcal{M}}
\section{Introduction}\label{sec:introduction}

Authentication generally requires secrets.  Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).  Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.

We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.  This feature is needed because $s$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.

Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. For example, in the application of secure sketches to fuzzy extractors (whose goal is to reliably produce a uniformly random secret key from a noisy input), the resulting secret key may be too short to be useful if the entropy loss is too high. However, because secure sketches are defined as information-theoretic objects, some entropy loss is inherent in any secure sketch construction, because $s$ contains enough information to recover $w$ from any value $w'$ that is close to it.

The minimum necessary  entropy loss has been quantified in past work.  Even if we don't require perfect correctness (i.e., allow $\rec$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).

\paragraph {Our Contributions}
To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  The definition of  \cite{DBLP:journals/siamcomp/DodisORS08} uses min-entropy as the information-theoretic measure of secrecy. 
 Finding the right computational measure of secrecy requires us to consider different possible computational analogs of min-entropy.

The natural relaxation of this secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.

On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful. We prove in \corref{cor:rec yields sketch} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
%Furthermore, we have (asymptotic)~constructions that meet these bounds.

On the positive side, we show that a different relaxation of the security requirement can in fact lead to a \emph{lossless} construction of secure sketches, in which the knowledge of $s$ does not reduce entropy of $w$ (see Theorem~%s~%\ref{thm:lossless secure sketch} and
~\ref{thm:lossless secure sketch log})).  This relaxation requires that $w$ have high \emph{unpredictability} entropy conditioned on $s$ (unpredictability  entropy is a computational notion originally defined in \cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}).  We demonstrate how to build such lossless sketches based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.

We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
\lnote{it would be good to find another application}

Both our lossless secure sketch and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.  To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).  We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.  The LWE error vector, in our case, is the input $w$ itself.  To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution. We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed). This relaxation requires new results about the hardness of LWE when samples have a fixed error vector, which may be of independent interest~(\thref{thm:blockLWE}).

\section{Preliminaries}
\label{sec:preliminaries}
We begin by recalling a few basic entropy definitions.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized $\{0,1\}$ distinguishers of size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.

\subsection{Fuzzy Extractors and Secure Sketches}
\label{sec:fuzzy extractors}

We now recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1, 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.  can we change this $d$ to $\mathsf{dis}$?}

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that if $\dis(w,w')\leq t$ and $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
\end{definition}
A fuzzy extractor can be produced from a \emph{average-case randomness extractor} %(all randomness extractors are average-case extractors with a small loss, see~\cite[Chapter 6]{vadhan2012}) 
and a \emph{secure sketch}.  
An average-case extractor is simply a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
An extractor $\ext$ is a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), Y), U_m\times
U_d \times Y) \le \epsilon$.
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  They produces a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t, \epsilon)$-\emph{approximately correct secure sketch} is a pair of randomized procedures, ``sketch'' (\sketch) and ``recover'' (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',SS(w))=w]\geq 1-\epsilon$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|SS(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time.  If $\epsilon=0$ we omit $\epsilon$ and say that $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch}.
\end{definition}
For an approximately correct secure sketch we assume that errors are drawn independently of $\sketch(w)$.  If the error pattern between $w$ and $w'$ depends on $\sketch(w)$ there is no guarantee about the probability of correctness.
%In \secref{sec:defCompFuzzyExtractors} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}
A fuzzy extractor is usually formed by combining a randomness extractor with a secure sketch.
\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(for $(r, x)$ drawn from the uniform distribution):
\begin{itemize}
\item $\gen(w; r, x):$ set $P=(\sketch(w; r), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).  %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.  In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.   
%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.

%=============================================================
\section{Defining Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
We first recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.

\begin{definition}
Let $(X, Y)$ be a pair of random variables.  $X$ has 
\emph{conditional HILL entropy} at least $k$ conditioned on $Y$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Y)\geq k$ if there exists a collection of
distributions $Z_y$ for each $y\in Y$, giving rise to a joint distribution
$(Z, Y)$, such that $\tilde{H}_\infty(Z|Y)\geq k$ and for all (randomized, binary output) circuits $D$ of size $s_{sec}$, $\delta^D((X, Y),(Z,Y))\leq \epsilon$.
\end{definition}

Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches can't perform much better than the information-theoretic ones.

Instead, in \secref{sec:unp secure sketch}, we define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  In particular, in \secref{sec:comp fuzzy extractors}, we show a natural construction of computational fuzzy extractors from secure sketches defined using unpredictability.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
It seems natural to replace a sketch that retains information theoretic entropy with a sketch that retains HILL entropy.  Then the paradigm of secure sketch and average case randomness extractor could be used. However, we show that using this definition it is impossible to beat information theoretic bounds on secure sketches.  We omit formal definitions for the moment and recall the two informal properties we seek:
\begin{itemize}
\item \emph{Correctness}: if $\dis(w, w')\leq t$ then $\rec(w', \sketch(w)) = w$.
\item \emph{Security}: For all $W$ where $H_\infty(W)\geq m$, $H^\hill_{\epsilon, s}(W|\sketch(W))  = \tilde{m}$.
\end{itemize}
%We will concentrate on the case where $gap = m-\tilde{m}=0$ however, any setting where  $gap$ is better than the best information theoretic sketch is still a meaningful result. % As before, we desired $\rec$ to be efficiently computable.  We start with this stronger definition to show the difficulty of constructing such an object.

Unfortunately, we will show if $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$ this implies an error correcting code with approximately $2^{\tilde{m}}$ points.  We provide intuition for the argument below and then present the formal argument.  Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  This means in order for $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$, there must be a distribution $Y$ where $\Hoo(Y)\geq \tilde{m}$ such that $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.  This means the points in $Y$ form an error correcting code and $\rec$ is an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  This means lower bounds on the entropy loss of an information theoretic sketch must apply.  There are several technical conditions required to make this intuition formal, we present them below.
%any function that is able to recover correctly on a large space is an decoder for an error correcting code formed by that space.  If there is a distribution $Y$ with many points such that $\rec(y', \sketch(w)) =y\in Y$ when $\dis(y, y')\leq t$.  Then $\rec$ is a decoder for the error correcting code formed by $Y$.
% and make no assumption about the behavior of $\rec $ outside of this ball.  The intuition is quite simply, on a point $w\leftarrow W$, the \rec oracle will always return $w$ within the $B_t(w)$.  If $W|\sketch(W)$ is indistinguishable from $Y|\sketch(W)$ then the $\rec$ oracle must also correct for points in $Y$.  However, this implies a code~(the points in $Y$) with $\rec$ as an efficient decoding algorithm. 
%\subsubsection{The Uniform Distribution}
%and extend to an arbitrary high-entropy distribution.  
%We begin by showing that any given no distribution $W$ can be indistinguishable from the uniform distribution given a sketch.
%We need two technical requirements on our metric space: 1) there is an efficient algorithm to sample neighbors 2) each point is regular~(has the same number of neighbors).  These requirements hold for several natural metric spaces including Hamming and symmetric difference metrics.
%The only other requirement we make is for the distribution and its neighborhood to be efficiently samplable.
%\begin{definition}
%A distribution $W$ is $s-$\emph{efficiently-samplable} if there exists a randomized circuit of size at most $s$ that outputs samples according to $W$.
%Furthermore, we say $W$ is \emph{efficiently-samplable} if there exists a randomized circuit of polynomial size that outputs samples according to $W$.
%\end{definition}
%We will be working with a metric space $\mathcal{M}, d$.  We will need to efficiently sample nearby points in the metric space.
We assume that sampling a random neighbor of a point is efficient:
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit, $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
Furthermore, there is a procedure that outputs a random point of distance at most $t$.  For convenience we denote this procedure by $\sample(X)$.
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, this is not very interesting in the context of fuzzy extractors~(as \gen can always output the empty string for $P$).

%We will concentrate on metrics where the size of each ball is fixed.  We say a metric space that obeys this property is regular~(using terminology from graph theory).  This will allow us to show that the neighbor of a uniformly chosen point is also uniformly random.  
%\begin{definition}
%A metric space $(\mathcal{M},d)$ is \emph{$(t, c)-$distance regular} if for all $x\in \mathcal{M}, |B_t(x)| = c$. 
%\end{definition}
%For a distribution $X$ we define the distribution $N_t(X)$ as the process of sampling a random neighbor of a random point in $X$.  That is $\Pr[N_t(X) = z] = \sum_{x\in X}\Pr[X=x \wedge y \leftarrow B_t(x) \wedge z=y]$.
%\begin{lemma}\label{lem:uniformNeighbor}
%Let $(\mathcal{M}, d)$ be a $(t, c)-$distance regular and let $U$ be uniform over $\mathcal{M}$.  Then $U \overset{d}= N_t(U)$.
%
%\end{lemma}
%\begin{proof}
%Note that $\forall z, \Pr[U = z] =1/|\mathcal{M}|$.  Thus, it suffices to show that $\forall z , \Pr[N_t(U) =z] =1/|\mathcal{M}|$.
%
%Fix an arbitrary $z\in \mathcal{M}$.  Then, 
%\begin{align*}
%\sum_{x\in U} \Pr[U=x \wedge y\leftarrow B_t(x) \wedge y=z] &=
%\sum_{x\in U} \Pr[U = x \wedge x\in B_t(z)] \Pr[y\leftarrow B_t(x) \wedge y=z | x\in B_t(z)]\\
%&=\frac{c}{|\mathcal{M}|} \frac{1}{c} = \frac{1}{\mathcal{M}}.
%\end{align*}
%%The uniform distribution over $\mathcal{M}$ is a random bit string of length $n$.  Let $x\leftarrow \mathcal{M}$, then $\sample (x) = z = x\oplus y$ where $y$ has at weight at least $1$ and at most $t$.  Since $x$ was uniformly random $x\oplus y$ is uniformly random.
%\end{proof}

Finally, we will dealing with an arbitrary secure sketch that only needs to satisfy the correctness property of a secure sketch~(see \defref{def:secure sketch}).

\begin{definition}
A pair of functions $(\sketch, \rec) $ is a $(s_{rec}, t)$-\emph{recover functionality for a metric space $\mathcal{M}, d$} if $\sketch : \mathcal{M}\rightarrow \{0,1 \}^*$ is a randomized function and $\rec: \mathcal{M}\times \{0, 1\}^*\rightarrow \mathcal{M}$ is a function computable by a circuit of size at most $s_{rec}$, such that $\rec (w', \sketch (w)) = w$ if $\dis(w, w')\leq t$ for all $w, w' \in \mathcal{M}$.
\end{definition}

\ignore{For any recover functionality, there is an inherent tradeoff between the ability to keep points stationary and to perform error correction.

\begin{theorem}\label{thm:compSketchImpUniform}
Let $\mathcal{M}, d$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable and $(t, c)$-distance regular.
Furthermore, let $(\sketch, \rec)$ be any $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.  Then $H^\hill_{\epsilon, s}( U |\sketch(U))\not \geq \Hoo(U)$ for $s \approx (s_{neigh} + 2s_{rec})$ and $\epsilon=1/2$~(if $s_{neigh}, s_{rec}$ are polynomial so is $s$).
\end{theorem}
%\emph{Intuition:  }The goal that a recover functionality cannot be both stable~(maps points to themselves) and correcting~(maps nearby points back to themselves).  If a recovery functionality is correcting then we can check if the input point maps to itself.  If a recovery functionality is stable then we can see if recovery succeeds with nearby points.

\begin{proof}
Let $U_\mathcal{M}$ be the uniform distribution over $\mathcal{M}$ and let $d$ a  metric.  Furthermore assume $\mathcal{M}$ is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be a $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.  Let $X\overset{d}= Y\overset{d}= U_\mathcal{M}$ be i.i.d..  It suffices to construct a distinguisher $D$~(whose size is $s\approx s_{neigh}+2s_{rec}$) such that $\expe[D(X, SS(X))]- \expe[D(Y, SS(X))]\geq \epsilon = 1/2$.  
%Let $q$ be a polynomial.  
$D$ is defined as follows:
\begin{enumerate}
\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$. 
\item Sample $b\leftarrow \{0,1\}, z'\leftarrow \sample(z)$.
\item If $b=1$:
\subitem If $\rec(z', s) = z\wedge \rec(z, s) = z$ output $1$.
\item If $b=0$:
\subitem If $\rec(z, s) = z \wedge \rec(z', s)=z$ output $1$.
\item Output $0$.
\end{enumerate}
First note that $D$ is of size $O(s_{neigh}+2s_{rec})$ and thus in polynomial in $s_{sam}, s_{neigh}$.  It remains to show that $D$ separates $(X,\sketch(X))$ and $(Y,\sketch(X))$.  We being by noting that on input $(X, \sketch(X)), D$ outputs $1$.
By \lemref{lem:uniformNeighbor} we have:
\begin{align*}
0&=\delta([Y, \sample(Y), \sketch(X)],& &[\sample(Y), Y, \sketch(X)])\\
&=\delta([Y, \sketch(X), \sample(Y), \sketch(X)],& &[\sample(Y), \sketch(X), Y, \sketch(X)])\\
&=\delta([\rec(Y,\sketch(X)), \rec(\sample(Y),\sketch(X))],& &[\rec(\sample(Y), \sketch(X)), \rec(Y, \sketch(X))])
\end{align*}
Thus, the output of $\rec$ is the same when given $(\sample(Y), Y)$ or $(Y, \sample(Y))$\footnote{This is also true for a stronger class of recover functionalities that is able to keep state between queries.}.  This means it can properly recover $Y$ with probability at most $1/2$ over the ordering of inputs.  Thus we have, 
\begin{align*}
\Pr[D'(X, \sketch(X))=1] - \Pr[D'(Y, \sketch(X))=1] &=\\
1 - \frac{1}{2}(\Pr[\rec(Y, \sketch(X)) = Y \wedge \rec(\sample(Y),\sketch(X))=Y]&+\\\Pr[\rec(\sample(Y), \sketch(X)) = Y \wedge \rec(Y, \sketch(X)) = Y])&\geq 
1-\frac{1}{2}\left(1\right) =\frac{1}{2}
\end{align*}

%\begin{enumerate}
%\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$.
%\item Initialize $correct, stable = 0$.
%\item For $i=1...q$:
%\subitem $x_i \leftarrow U$, if $\rec(x_i, s) = x_i, stable +=1/q$.
%\subitem $x_i' \leftarrow \sample (x_i)$, if $\rec(x_i', s) = x_i, correct+=1/q$.
%\item If $\rec(z, s)\neq z$ output $0$.
%\item If $stable<1/2$ output $1$
%\item Else $z'\leftarrow \sample(z)$.
%\subitem If $\rec(z', s) = z$ output $1$.
%\subitem Else output $0$.
%\end{enumerate}
%
%We begin by noting that $D$ is of size $O(q(s_{sam}+s_{neigh}+2s_{rec})+2s_{rec}+s_{neigh})$ and thus is polynomial in $s_{sam}, s_{neigh}, s_{rec}$.  It remains to show that $D$ separates $(X, SS(X))$ and $(Y, SS(X))$ by a noticeable $\epsilon$.  Let $STABLE = \Pr[\rec(U, \sketch(X)) = U]$.  We begin by noting that $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).  That is, after step (3) $D$ has a good approximation
%of $STABLE$.  Similarly, let $CORRECT = \Pr[\rec(\sample(U), \sketch(X)) = U]$.  As before $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
%Thus, after step (3), $\Pr[|CORRECT-correct|>\ngl \wedge |STABLE-stable|>\ngl|]<\ngl$.  We proceed assuming, that $CORRECT$ and $STABLE$ are known exactly at step (4), and note the output of $D$ is negligibly close to the output of a distinguisher that knows $CORRECT$ and $STABLE$ exactly~(we label this distinguisher $D'$).
%\begin{claim}
%$CORRECT+STABLE\leq 1$.
%\end{claim}
%\begin{proof}
%\begin{align*}
%\Pr[\rec(U, \sketch(X) = U] + \Pr[\rec(\sample(U), \sketch(X)) = U]&\leq\\
%\Pr[\rec(U, \sketch(X) = U]  + \Pr[\rec(Y), \sketch(X)\neq Y] &=1
%\end{align*}
%Where the first inequality proceeds because of \lemref{lem:uniformNeighbor} and the fact that \sample never returns itself.  The equality proceeds as these events as these events are complementary events after renaming. 
%\end{proof}
%We now show that when $(\sketch, \rec)$ is stable or correcting the distinguisher has nonnegligible advantage:
%\begin{itemize}
%\item Case 1: $STABLE<1/2$.
%\begin{align*}
%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1] &=\\
%\Pr[\rec(X, \sketch(X) = X] - \Pr[\rec(Y, \sketch(X) = Y] &\geq
% 1- 1/2  = 1/2
%\end{align*} 
%\item Case 2: $STABLE\geq 1/2, CORRECT \leq 1/2$.
%\begin{align*}
%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1]&=\\
%\Pr[\rec(X, \sketch(X)) = X \wedge \rec(\sample(X), \sketch(X)) = X] &-\\\Pr[\rec(Y, \sketch(X) = Y) \wedge \rec(\sample(Y), \sketch(X)) = Y)]&\geq\\
%1 - \Pr[\rec(\sample(Y), \sketch(X)) = Y)]= 1-1/2 = 1/2
%\end{align*}
%\end{itemize}
%Thus, in both cases we have $\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1]\geq 1/2$.  As noted above, $CORRECT, STABLE$ are only known approximately and thus:
%\[
%\Pr[D(X, \sketch(X) )= 1] - \Pr[D(Y, \sketch(X) )= 1]\geq 
%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1] - \ngl \geq 1/2 -\ngl
%\]
This completes the proof.
\end{proof}

This proof relied on two crucial facts: 1) that the neighbor of a uniform point was uniformly distributed 2) for an point uncorrelated with the value of the secure sketch it was impossible to distinguish between a point and its neighbor.  We can extend this result to distributions other than the uniform distribution but by drawing on more general results from coding theory.

\subsection{Indistinguishable sketches imply information theoretic sketches}
In this section we show that the results of \thref{thm:compSketchImpUniform} can be extended to whenever $X$ is indistinguishable from a high min-entropy distribution.  }

We show that any recovery functionality that retains high HILL entropy implies a information theoretic secure sketch.  We begin by reviewing definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t)) \neq c]<\epsilon$.
\end{definition}
This is a slightly nonstandard formulation, we only require the code to correct exactly $t$ errors\footnote{In the standard formulation, the code must correct up to $t$ errors.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.  Shannon codes work for all codewords, we can also consider a formulation that works for an ``average'' codeword.
\begin{definition}
Let $W$ be a distribution over space $\mathcal{M}$.  We say that $W$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that 
$\Pr_{w\leftarrow W}[\rec(\sample(w, t)) \neq w]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a (maximal error)~Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements}~(we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $W'$ where $|W'|\ge2^{k-1}$ and $W'$~(drawing a codeword uniformly) is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

With this conversion we can show a surprising result: recover functionalities that retain HILL entropy imply Shannon error correcting codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an $(s_{rec}, t)$-recover functionality over $\mathcal{M}$.  If $H^{\hill}_{\epsilon, s_{sec}}(X|SS(X))\geq k$ then there exists $x$ and a set $W'$ where $|W'|\geq 2^{k-1}$ such that for all $1\leq t'\leq t$, $W'$ is a $(t', 2\epsilon)$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$ for $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

We can use techniques from information reconciliation~\cite{smith2007scrambling} and privacy amplification~\cite{bennett1988privacy} to convert any  Shannon code into an information theoretic security sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}):
\begin{lemma}
\label{lem:shannon to sketch}
Let $t$ be a parameter.  Let $\mathcal{C}$ over $\{0,1\}^n$ be a set such that for all $1\leq t'\leq t$, $\mathcal{C}$ is a $(t', \epsilon)$ Shannon code with recovery procedure $\rec'$.  Let $W$ be a distribution with $\Hoo(W)\geq k$.  Define the following procedures
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item Input $w\leftarrow W$.
\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
\item Sample $c\leftarrow \mathcal{C}$.
\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
\item Output $p = x \oplus c, \pi$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item Input $(w', p, \pi)$
\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
\item Compute $c' = p \oplus x'$.
\item Compute $c = \rec'(c)$.
\item Output $p\oplus c$.
\\
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
Then $(\sketch, \rec)$ is a $(\{0,1\}^n, k, k-(n-\log |\mathcal{C}|), t, \epsilon)$ approximately correct secure sketch. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives our main negative result.  Any recover functionality that retains HILL entropy implies an information theoretic sketch:
\begin{corollary}
\label{cor:rec yields sketch}
Let $(\sketch', \rec')$ be a $(s_{rec}, t)$-recover functionality over $\{0,1\}^n$ such that $H^{\hill}_{\epsilon, s_{sec}}(X | \sketch'(X))\geq k$.  If $s_{sec}=\Omega(t(s_{rec} + n))$,  then for all $W$ with $\Hoo(W)\geq m$ there exists a $(\{0,1\}^n, m, m-(n-k+1), 2\epsilon)$ (information-theoretic) approximately correct secure sketch.
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the feasibility of constructing $(\sketch, \rec)$.  Several steps in \thref{thm:impSketchArbitraryW} are not constructive so there may not be an efficient procedure for $\sketch$.

\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.  Unfortunately, we have lower bounds for the entropy drop for information-theoretic sketches:

\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
\label{prop:lower bound entropy drop}
For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.  Here $h(\cdot)$ is the binary entropy function.
\end{proposition}

Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.  This entropy drop is tied to the Shannon capacity.  Furthermore, we have information theoretic constructions that meet these bounds.  Thus, defining a computational secure sketch using HILL entropy is unlikely to be useful.

%\begin{theorem}
%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable.  Furthermore, let $(\sketch, \rec)$ be any $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.  Let $U$ be the uniform distribution over $\mathcal{M}$.  If $s_{ball}, s_{rec}, s_{sam}$ are of polynomial size, then $H^\hill_{\epsilon, s}( U |\sketch(U))\not \geq \Hoo(U)$ for polynomial $s$ and noticeable $\epsilon$.
%\end{theorem}
%\emph{Intuition:  }We will show that a recover functionality cannot be both stable~(maps points to themselves) and correcting~(maps nearby points back to themselves).  If a recovery functionality is correcting then we can check if the input point maps to itself.  If a recovery functionality is stable then we can see if recovery succeeds with nearby points.  
%
%\begin{proof}
%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable~(by $\sample$).  Let $(\sketch, \rec)$ be a $s_{rec}, t$-recover functionality for $\mathcal{M}, d$.  Let $X, Y, U$ be i.i.d. and be the uniform distribution over $\mathcal{M}$.  By assumption $s_{ball}, s_{sam}, s_{rec}$ be of polynomial size.  It suffices to construct a polynomial size distinguisher $D$ such that $\expe[D(X, SS(X))]- \expe[D(Y, SS(X)]> \epsilon$ for noticeable $\epsilon$.  Let $q$ be a polynomial.  $D$ is defined as follows:
%
%\begin{enumerate}
%\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$.
%\item Initialize $correct, stable = 0$.
%\item For $i=1...q$:
%\subitem $x_i \leftarrow U$, if $\rec(x_i, s) = x_i, stable +=1/q$.
%\subitem $x_i' \leftarrow \sample (x_i)$, if $\rec(x_i', s) = x_i, correct+=1/q$.
%\item If $\rec(z, s)\neq z$ output $0$.
%\item If $stable<2/3$ output $1$
%\item Else $z'\leftarrow \sample(z)$.
%\subitem If $\rec(z', s) = z$ output $1$.
%\subitem Else output $0$.
%\end{enumerate}
%
%We begin by noting that $D$ is of size at most $q(s_{sam}+s_{ball}+2s_{rec})+2s_{rec}+s_{ball}$ and thus is polynomial assuming that $q, s_{sam}, s_{ball}, s_{rec}$ are of polynomial size.  It remains to show that $D$ separates $X, SS(X)$ and $Y, SS(X)$ by a noticeable $\epsilon$.  Let $STABLE = \Pr[\rec(U, \sketch(X)) = U]$.  We begin by noting that $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).  That is, after step (3) $D$ has a good approximation
%of $STABLE$.  Similarly, let $CORRECT = \Pr[\rec(\sample(U), \sketch(X)) = U]$.  As before $\Pr[|correct-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
%
%\begin{claim}
%$CORRECT+STABLE\leq 1$.
%\end{claim}
%\bnote{finish proof}
%
%\end{proof}

\subsection{Defining Secure Sketches using unpredictability entropy}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

\begin{definition}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\[
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We now provide a definition of a computational secure sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
An $(\mathcal{M},m, \tilde{m}, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\rec(w',SS(w))=w$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ is unpredictable given $\sketch(W)$.  That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say a construction is \emph{lossless} if $m=\tilde{m}$ and we omit the parameter $\tilde{m}$.
\end{definition}
We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational secure sketch that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.

\section{Lossless sketch based on \class{LWE}}
\label{sec:fuzzyCompExt}

In this section we describe our main construction.  The secure sketch is computed via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors~(not necessarily efficient).  We provide an informal description below.
%Please refer to \consref{cons:informal construction} for the description of the construction.

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\sketch, \rec$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Output $s = (\vA, \vA X+w)$.
\\
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', s)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Set $X' = \mathcal{I}_t(\vA, \vect{D}) $. 
\item Output $w = \vect{C}-\vA X'$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) \approx \Hoo(W)$.  Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.

The rest of this section is devoted to making these intuitive statements precise.
 We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
 %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
We describe conditions for efficient decoding in \secref{sec:time main construction}.  Finally, in \secref{sec:lossless sketch} we describe parameter settings where our construction yields a lossless secure sketch.\lnote{revise after going through the rest}.

\subsection{Security of \consref{cons:informal construction}}
\label{subsec:LWE}
The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For positive integers $n$ and $q \ge 2$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$. 
%The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
Let $m = m(n) = \poly(n)$ be an integer, $q = q(n) = \poly(n)$. The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-hard if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with the probability $\epsilon$.
\end{definition}

Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} shows that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is hard under the worst-case lattice problems.
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

\begin{proposition} 
\label{assume:entropy LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\alpha$ be the discretized Gaussian distribution with variance $(\alpha q)^2/2\pi$.  If GAPSVP and SIVP are hard to approximate within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}hard$ for all probabilistic distinguisher $D$, where $\epsilon = \ngl(n)$.

%H^{\unp}_{\epsilon, s_{sec}}(X | \vA, \vA X+E) =H^{\unp}_{\epsilon, s'_{sec}}(E| \vA, \vA X+E) \geq n\log q $ for $s'_{sec}\approx s_{sec}$.  
\end{proposition}

We cannot immediately adapt the construction in \consref{cons:informal construction} to the LWE problem.  Standard formulations of LWE require the error term to come from the discretized Gaussian distribution.  
%\subsection{LWE with uniform errors}
%\label{subsec:LWE uniform error}
Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of LWE with the uniform distribution over an interval reduces to the security of LWE where the noise comes from the discretized Gaussian.  This allows us to directly encode $w$ as the error term in an LWE problem by splitting it properly into $m$ blocks.
%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.  
We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
%\label{lem:uniform LWE}
%Let $n$ be a security parameter.  Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.  Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.  Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
%\end{lemma}

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume there exists a PPT-distinguisher $D$ such that $\delta^D((\vA, \vA X+E), (\vA, U))>\epsilon$ for non-negligible $\epsilon$ and $\vA\in \Fq^{m\times n}, X\in \Fq^{n}, U\in \Fq^m$ drawn uniformly and $E$ drawn uniformly from $[-\rho q, \rho q]$.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ in the worst case.
\end{lemma}

We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).  We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
\begin{lemma}
\label{lem:conversion to unpredictability}
Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon, s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
for $s_{sec}'\approx s_{sec}$.
\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.  We provide a formal description of our algorithm in the next section.
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

%\subsection{Computational Secure Sketch based on \class{LWE}}
%\label{subsec:fuzzyExtLWE}
%We now give a formal description of our sketch based on LWE.  We now consider a source $W$~(this fulfills the role of $E$ in standard LWE notation):
%
%\begin{construction}[Computation Secure Sketch based on LWE]
%\label{cons:LWESecureSketch} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers.  Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+3\gamma}m$.  Let $\mathcal{I}_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.  Let $W$ be a distribution over $\{0,1\}^{(\log \rho q)\times m}$\,.  Then the following is a computational secure sketch:%We present the construction in 
%%\begin{figure}
%%\label{fig:construction figure}
%%\caption{Computational Secure Sketch based on the Learning with Errors problem}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\vA\in\Fq^{m\times n}, x\in\Fq^n$ uniformly.
%\item Output $p = (\vA, \vA x+w)$.\\
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p)$
%\item Parse $p$ as $(\vA, \vect{C})$
%\item Set $x' = \mathcal{I}_t(\vA, \vect{C}-w') $. 
%\item Output $w = \vect{C}-\vA x'$.
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
%%\end{figure}
%%\textbf{\gen}
%%\begin{enumerate}
%%\item Input $w\leftarrow W$.
%%\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
%%\item Use $w$ as the randomness for the sampling algorithm, \\$\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
%%\item Output $p = (A, AX+E)$.
%%\end{enumerate}
%%
%%
%%\textbf{\rep}
%%\begin{enumerate}
%%\item Input $(w', p)$
%%\item Parse $p$ as $(A, C)$
%%\item Compute $E' \leftarrow \sample (w')$.
%%\item Set $X' = \mathcal{I}_t(A, C-E') $. 
%%\item Output $sam_w = C-AX'$.
%%\end{enumerate}
%\end{construction}

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\mathcal{I}_t$ can be efficiently implemented.  We now present a particular $\mathcal{I}_t$ and consider its efficiency:

\begin{construction}
\label{cons:decoding algorithm} Suppose that for a $(n, m, q, \chi)$ that the LWE errors problem is a unique witness relation except with negligible probability.  Let $R$ be the relation that decides whether $X$ is a witness for an instance $\vA, \vA X+W$.  We describe inverter $\mathcal{I}_t$:
\begin{enumerate}
\item Input $\vA , \vect{C} = \vA X + E - E'$
\item Randomly select rows without replacement $i_1,..., i_n\leftarrow [1,m]$.  
\item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this is $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
\item Compute $x = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $R(x, \vA, \vect{C}) \neq 1$.  Go to step (2).
\item Output $x$.
\end{enumerate}
\end{construction}

$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.  Our inverter will only succeed if it can verify it has the proper $X$. Consider a relation $R(X, (\vA, \vA X+W-W'))$ that verifies if $X$ is the point encoded in $\vA X+W-W'$.   If $n$ is large enough and if $|W-W'|_1$ is small enough, $R$ is a unique witness relation with high probability~(see \defref{def:unique witness relation}) and computable in time $O(n^3)$.
We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-1)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(m/n-1)$.  Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ for all but a negligible fraction of inputs over $\vA, \vA X+W - W'$.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-1$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-1)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.

%\textbf{Problems:} Construction~\ref{cons:LWESecureSketch} does not meet Definition~\ref{def:comp secure sketch}.  This is because the sampling algorithm may not be invertible.  Furthermore, in standard $\LWE$ the sampling algorithm is Gaussian and there is no fixed number of bits used to sample error in any dimension.  Approximating the Gaussian distribution using a fixed number of bits may be possible but there are still two error patterns which require a significantly different number of bits.  We will address both of these problems by sampling the error from a uniform distribution.

\subsection{Lossless Secure Sketch}
\label{sec:lossless sketch}
We now state a setting of parameters that yields a lossless sketch.  For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  There exist efficient lossless secure sketches based on \consref{cons:informal construction}:

%\begin{theorem}
%\label{thm:lossless secure sketch}
%Let $n$ be a security parameter and let $t$ be a constant.  Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.  Let $W$ be uniform over $\zo^{n(t+1)b}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors, there is a 
%\[
%(\zo^{n(t+1)b}, |W|,|W|, \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
%\]
% for $\epsilon = \ngl(n), s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
%\end{theorem}

\begin{theorem}
\label{thm:lossless secure sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:conversion to unpredictability}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

\thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.  A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

\section{\consref{cons:informal construction} with Symbol Fixing Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational secure sketch for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m- \alpha)b$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

We now study \consref{cons:informal construction} with a symbol fixing source.  Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations with no error and $W$ can be recovered with Gaussian elimination.  We show that security degrades exponentially as symbols are fixed.
\ignore{
\begin{assumption}[LWE w/ entropic errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-block fixing distribution over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
\end{assumption}
}
We now define the decisional $\LWE$ problem with symbol fixing errors is defined as follows: 
\begin{problem}[$\distLWE$ w/ symbol fixing errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$. For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$. The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
\end{problem}

The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m = \poly(n)$.  Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}

\thref{thm:blockLWE} allows us to construct a computational secure sketch from block-fixing sources:

%\begin{theorem}
%\label{thm:lossless block sketch}
%Let $n$ be a security parameter and let $t$ be a constant.  Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.  Let $W$ be an $\alpha$-symbol fixing source over $\zo^{((t+1)n+\alpha)b}$.  There is a \lnote{instead of ``there is'' can we actually point to the to construction?}
%\[
%(\zo^{((t+1)n+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
%\]
% for $s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
%\end{theorem}

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)n/d+\alpha)b}$.  Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.   \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$ for %the following parameters:
%\[
%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
%\]
$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}

\section{Computational Fuzzy Extractors}
In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using a paradigm similar to \lemref{lem:fuzzy ext construction}.  We begin with a formal definition of a computational fuzzy extractor:
\label{sec:comp fuzzy extractors}
\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, s_{rec}, s_{sec}, \epsilon)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\rep( w', P) = R$.  Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

\textbf{Note: }A computational fuzzy extractor can be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).  However, the entropy loss due to error correction may mean there is not be enough remaining bits to run a pseudorandom generator.  Depending on the application, it may be appropriate to make the sketch and/or extractor computational.

Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).  It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.  However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).  
\begin{definition}
An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.  Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
\end{definition}
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
\begin{lemma}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, s_{sec}, s_{sketch}, s_{rec}, t)$-computational secure sketch, and let $\rext:\mathcal{M}\times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
\begin{itemize}
\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
\end{itemize}
\end{lemma}
\begin{proof}
Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
\end{proof}

%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.

\ignore{
Additionally, it is simple to use a pseudorandom generator to produce a computational fuzzy extractor from a standard fuzzy extractor:
\begin{proposition}\label{prop:prg comp fuzzy extractor}
Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $(\epsilon_{prg}, s)$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.  Let \gen' and \rep' be defined as:
\begin{itemize}
\item \gen': $(R, P) \leftarrow \gen(w)$, output $(prg(R), P)$
\item \rep': Output  $prg(\rep (w', P))$.
\end{itemize}
Then $(\rep', \gen')$ is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.
\end{proposition}
Recall, our goal is to construct fuzzy extractors where the entropy drop due to an information theoretic construction were too high.  However, it seems difficult to definitionally exclude this type of construction.  For example, one could require that $R$ have information theoretic entropy in the absence of $P$.  This does not solve the problem:
\begin{proposition}\label{prop:xor comp fuzzy extractor}
Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $\epsilon_{prg}, s$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.  Let \gen' and \rep' be defined as:
\begin{itemize}
\item $\gen'(w)$
\subitem Sample $K\leftarrow \{0,1 \}^{\ell'}$
\subitem $(R, P) \leftarrow \gen(w)$
\subitem $H= prg(R)\oplus K$
\subitem Output $(K, (H, P))$
\item $\rep'(w', (H, P))$
\subitem Output $K' = H\oplus prg(\rep (w', P))$.
\end{itemize}
Then (\rep', \gen') is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.  Furthermore $H_\infty(K) = \ell'$.
\end{proposition}

Both of these constructions rely on a crucial property $\ell$ was long enough to provide a seed to a pseudorandom generator.  We are interested in the case where the remaining entropy is small and may not sufficient for pseudorandom generator.  We leave Definition~\ref{def:comp fuzzy extractor} as stated and note constructing a computational fuzzy extractor is desirable when a standard fuzzy extractor cannot be used.

In the information theoretic setting, Dodis et. al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.  A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
}
\bibliographystyle{alpha}
\bibliography{crypto}
\appendix
\section{Background}
\subsection{Notions of Computational Entropy}
\label{sec:notionsEntropy}
In this sections we provide some further definitions of computational entropy.  HILL entropy is defined in \secref{sec:defCompFuzzyExtractors}.  HILL entropy generalizes the notion of indistinguishability.  Yao entropy~\cite{DBLP:conf/focs/Yao82a, barak-computational} generalizes the notion of compressibility.  Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
\begin{definition}
\label{def:yao entropy}
For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
\[
\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
\]
\end{definition}
It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.  In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.  We also use a less common notion called unpredictability entropy.  This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
Unpredictability entropy is a notion between HILL and Yao entropy:
\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
\]
\end{lemma} 
\subsection{Unique Witness Relations}

We will need the ability to verify if we have a correct solution in~\consref{cons:informal construction}.

\begin{definition}
Let $R$ be a relation.  We say that $R$ is $s_{ver}$-\emph{unique witness verifiable} if $\forall y$ there exists a unique $x$ such that $R(x, y)=1$ and $R(x, y) =1$ is computable in time $s_{ver}$.
\end{definition}
We can relax this definition slightly to allow a relation that is unique witness verifiable with all but negligible probability~(when $x, y$ grow with the security parameter).

\begin{definition}
\label{def:unique witness relation}
Let $R:\mathcal{M}_1\times \mathcal{M}_2\rightarrow \zo$.  We say that $R$ is $(\epsilon, s_{ver})$-\emph{unique witness verifiable} if over $y\in \mathcal{M}_2$, drawn uniformly, the probability that $\exists x_1, x_2, x_1\neq x_2$ such that $R(x_1, y) =1 = R(x_2, y)$ is at most $\epsilon$ and $R$ is computable in time $s_{ver}$.
\end{definition}

\ignore{
\section{Possibility of Constructing Computational Fuzzy Extractors}\label{ssec:constructing comp fuzzy extractors}
In the \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best constructible codes.  Thus, some entropy drop seems necessary when considering $H^\hill_{\epsilon, s}(X | SS(X))$.  However, in \propref{prop:prg comp fuzzy extractor}, we showed that a computational fuzzy extractor exists using a pseudorandom generator.  A natural question is whether this is necessary.  Do there exist clever constructions of computational fuzzy extractors that rely on the hardness of some cryptographic primitive that is easy within some distance $t$.  We begin by recalling the important parameters of a computational fuzzy extractor:
\begin{itemize}
\item The input entropy $m$.
\item The length of the output string $\ell$.  This output string is required to be $(\epsilon, s_{sec})$-pseudorandom.
\item The accepting distance $t$.
\end{itemize}
We consider the possibility of constructing a computational fuzzy extractor based on the remaining entropy of $W$ conditioned on the string $P$~(generated by $(R, P)\leftarrow \gen(W)$).  We first define a parameter $k_{prg}$.  Let $k_{prg}$ be the smallest integer such that there exists a pseudorandom generator from $k_{prg}$ to at least $k_{prg}+1$ bits.  More precisely, let $k_{prg}$ be the smallest integer such that there exists a deterministic function $prg:\{0,1\}^{k_{prg}}\rightarrow \{0,1 \}^{k_{prg}+1}$ such that $\forall D\in \mathcal{D}_s$: $\delta^D(prg(U_{k_{prg}}), U_{k_{prg}+1})<\epsilon$ for some negligible $\epsilon$ and super polynomial $s$.  We now classify the existence of computational fuzzy extractors based on this parameter.  Let $CODE$ be some error-correcting code with parameters, $(n, k, 2t+1)$.  We define $|CODE| = n-k$.

\begin{tabular}{c | c}
Remaining Entropy & Constructible?\\\hline
$CODE$ is computationally computable. & Yes, use \propref{prop:prg comp fuzzy extractor} \\
$H_\infty (W) - |CODE|\geq k_{prg}$\\\hline
$CODE$ exists, not necessarily efficiently computable. & Seems impossible to disprove, efficient\\
$H_\infty(W) - |CODE|\geq k_{prg}$ & construction of $CODE$ admits \propref{prop:prg comp fuzzy extractor}.\\\hline
Let $CODE$ be the best code. & Unknown, main area of interest\\
$H_\infty(W) - |CODE|< k_{prg}\leq H_\infty(W)$\\\hline 
$H_\infty(W)< k_{prg}$ & Seems to imply existence \\
&of improved $prg$ by using $\gen$.
\end{tabular}

We begin by focusing on the last case where $H_\infty(W) < k_{prg}$.  We first introduce two concepts, efficiently-generatable sources and sources that are $prg$ qualified.

\begin{definition}
A distribution $W$ over $\mathcal{M}$ is \emph{$(s_{gen}, \ell)$-efficiently-generatable} if there exists a deterministic circuit $G$ of size at most $s_{gen}$ such that $W \overset{d}= G(U_{\ell})$.
\end{definition}
\begin{definition}
A distribution $W$ over $\mathcal{M}$ is \emph{$(\epsilon, s, s_{f})$ - prg-qualified} if there exists a deterministic function $f:\mathcal{M}\rightarrow \{0,1\}^d$~(computable in space $s_{f}$) such that for all $D\in\mathcal{D}_s$, $\delta^D(f(W), U)<\epsilon$ and $d\geq k_{prg}$\footnote{We can extend this definition to allow $f$ to have public-randomness.  The definition is not meaningful if $f$ has private randomness as $f$ can simply generate a fresh seed of length $d$.}.
\end{definition}
We use the term prg-qualified as the composition of $f$ and a $prg$ gives pseudorandom bits:
\begin{proposition}
Let $W$ over $\mathcal{M}$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution with function $f$ to $d$ bits.  Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator~(computable by a circuit of size $s_{prg}$) where $k\leq d$.  Then $\forall D\in\mathcal{D}_{\min\{s_W-s_{prg}, s_{sec}\}}$
\[
\delta^D(prg(f(W)_{1,..., k}), U_{k+1})< \epsilon_W + \epsilon_{prg}.
\]
\end{proposition}
\begin{proof}
Let $W$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution to $d$ bits.  Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator where $k\leq d$.  We proceed by contradiction.  Suppose that $\exists D$ of size at most $s= \min\{s_W -s_{prg}, s_{sec}\}$ such that $\delta^D(prg(f(W)), U_{k+1})\geq \epsilon_W+\epsilon_{prg}$.  By the triangle inequality, one has:
\begin{align*}
\epsilon_W+\epsilon_{prg}&\leq \delta^D(prg(f(W)_{1,...,k}), U_{k+1})\\
&\leq \delta^D(prg(f(W)_{1,...,k}, prg(U_k)) + \delta^D(prg(U_k), U_{k+1})
\end{align*}
Thus, either $\delta^D(prg(f(W)_{1,...,k}, prg(U_k))\geq \epsilon_{W}$ or $\delta^D(prg(U_k), U_{k+1})\geq \epsilon_{prg}$.

In the first case, we construct a distinguisher $D'$ that contradicts the $(\epsilon_W, s_W, s_{f})$-qualification of $W$.  $D'$ upon receiving input $x\in \{0,1\}^d$ computes $D(prg(x))$ and outputs $D$'s answer.  $D'$ is of size at most $s + s_{prg} \leq s_W-s_{prg}+s_{prg} = s_W$ and has advantage at least $\epsilon_W$.  This is a contradiction.

In the second case, $D$ immediately contradicts the $(\epsilon_{prg}, s_{sec})$ security of $prg$.  Thus, we have a contradiction in both cases.  This completes the proof.
\end{proof}

We now return to the question of whether we can build a computational fuzzy extractor when $H_\infty(W)<k_{prg}$.
\begin{theorem}

\end{theorem}
\begin{proof}
\bnote{Do the proof!}
\end{proof}
}
%We now provide a candidate construction of fuzzy extractor based directly on a computational problem~(the LWE problem introduced by Regev~\cite{regevLWEsurvey}).
%\begin{definition}
%An $(\mathcal{M}, m, \tilde{m}, t, s_{dist}, \epsilon)$-\emph{computational secure sketch} is a pair of randomized algorithms, ``sketch'' (\sketch) and ``recover'' (\rec) with the following properties:
%\begin{enumerate}
%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns two strings, $(x,s)\in\{0,1\}^*$ where $x$ is drawn from a distribution $X$ and $\Hoo(X)\geq m$.
%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of a computational secure sketches guarantees that if $d(w,w')\leq t$, then $Rec(w', SS(w)_2) = SS(w)_1$.  
%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, observing $SS(W)_2$ does not significantly help the adversary.  That is, $H^\hill_{\epsilon, s_{dist}}(X | SS(W)_2)\geq \tilde{m}$.
%\end{enumerate}
%A secure sketch is \emph{efficient} if \sketch runs in expected polynomial time and \rec runs in expected polynomial time if $d(w', w) < t$.
%\end{definition}
%This definition has two significant changes from the definition of a secure sketch.  First, we do not require that the distribution $X$ is equal to the input distribution $W$.  This is because constructions will utilize computationally hard problems that may be difficult to invert.  However, we can consider the special case where $X=W$.  None of the power of a secure sketch is lost when $X\neq W$.

%\textbf{Note: }  The entropy of $X$ is somehow limited by the entropy of $X$ we cannot completely hide some very high entropy string, using a low entropy string.  This would have to be reflected in the parameters of \hill entropy but I am not yet sure how to formalize this.
%
% Furthermore, note there are two conditions on the distribution $X$, $\Hoo(X)\geq m$ and $H^\hill_{\epsilon, s}(X|SS(W)_2)\geq \tilde{m}$.  This means that if an adversary does not see the helper value $s$ it has true entropy and its computational entropy is decrease by seeing $s$.

%Second, we now require that the value $X$ only has conditional \hill entropy.  Considering the special case where $m=\tilde{m}$ is interesting but constructions that improve on the $\tilde{m}$ achieved in secure sketch are interesting.  Furthermore, it seems natural to consider the case where $|\rec|<s$ however, \rec has a significantly more difficult task, \rec must recover all of $x$ while the distinguisher in the conditional \hill entropy definition only needs to distinguish $x$ from a high average min-entropy distribution.
%
%Thus, we can define a stronger definition where all of these desiderata are achieved.  
%
%\begin{definition}
%A $(\mathcal{M}, m, \tilde{m}, t, s, \epsilon)$-computational secure sketch is strong if the following properties hold:
%\begin{enumerate}
%\item Seeing $s$ does not decrease the conditional $\hill$ entropy of $X$.  That is, $m=\tilde{m}$.
%\item There exists a circuit of \rec' where the size of \rec' is polynomial, $|\rec'|<s_{dist}$ and \rec' satisfies the correctness property.
%\end{enumerate}
%\end{definition}
\ignore{
\subsection{Learning With Errors (\class{LWE})}
\label{subsec:LWE in detail}
The LWE problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise". For positive integers $n$ and $q \ge 2$, a vector $\vect{s} \in \Fq$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{s}, \chi}$ be the distribution obtained by choosing a vector $\vect{a} \overset{\$}\leftarrow \Fq^n$ uniformly at random and a noise term $e \overset{\$}\leftarrow \chi$, and outputting $(\vect{a}, \langle \vect{a}, \vect{s}\rangle + e) \in (\Fq^m, \Fq)$. A formal definition follows.

\label{sec:LWEoverview}
\begin{problem}[\class{LWE}]\label{prob:LWE}
Let $n$ be the security parameter. For a integer $q = q(n)$ and the error distribution $\chi = \chi(n)$ over $\Fq$, the Learning With Error problem $\class{LWE}_{n, m, q,\chi}$ is defined as follows: given access to an oracle that outputs $m$ samples from $A_{\vect{s}, \chi}$ for a uniformly random $\vect{s}$, output $\vect{s}$ with high probability.
\end{problem}

We will use the fixed form of the LWE assumption where a matrix is prepared ahead of time.  The matrix form is as follows: $\class{LWE}$ find $\vect{x}$ given $(\vect{A},\vect{Ax+e})$, where $\vect{A}\leftarrow \Fq^{m \times n}$ is chosen uniformly and the error vector $\vect{e} \leftarrow \chi$.
Results of Regev~\cite{regev2005LWE} and Peikert~\cite{peikert2009latticereduction} connect the hardness of the LWE problem to solving worst-case lattice problems.  The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_\alpha$~(following the notation of~\cite{regev2005LWE}).  We denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.  Here we present the theorem of~\cite{regev2005LWE}.

\begin{theorem}~\cite[Theorem 3.1]{regev2005LWE}
Let $n$ be a security parameter and $q = q(n) \in\Fq^+$, let $\alpha = \alpha(n)\in (0,1)$ be such that $\alpha q > 2\sqrt{n}$.  Let $\vA\in\Fq^{m\times n}, X\in \Fq^n$ be chosen uniformly at random and $E$ be chosen according to $\bar{\Psi}_\alpha$.  If there exists a PPT-algorithm $\mathcal{I}$ such that $\Pr_{\vA, X, E}[X\leftarrow  \mathcal{I}(\vA, \vA X+E) ]>\epsilon$ for some noticeable $\epsilon$, then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem~(GAPSVP) and the shortest independent vectors problem~(SIVP) to within $\Omega(n/\alpha)$ in the worst case.
\end{theorem}

We will consider a generalized assumption of \probref{prob:LWE}:
\begin{assumption}
\label{assume:general LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ and $q=q(n)\geq 2$ be integers and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, \vA\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{I}$ of size at most $s$
\[
\Pr_{\vA, X, E}[X\leftarrow \mathcal{I}(\vA, \vA X+E)]<\epsilon
\]
\end{assumption}
Furthermore, Regev shows a decision to search equivalence for $q=\poly(n)$, so we can consider an equivalent indistinguishability formulation:
\begin{assumption}
\label{assume:indist LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, A\in\Fq^{m\times n}, B\in\Fq^m$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{D}$ of size at most $s$:
\[
\Pr[D(\vA, \vA X+E)=1]-\Pr[D(\vA, B)=1]<\epsilon
\]
\end{assumption}
We can restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy~(see Definition~\ref{def:unp entropy}).  
}

\section{\lemref{lem:conversion to unpredictability}}
\label{sec:proof of unpred conversion}
In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.  %We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).  Thus, we have the following claim:
%\begin{claim}
%\label{lem:unp of x and e}
%Let $A, X, E$ be as above, then:
%\begin{itemize}
%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
%\end{itemize}
%\end{claim}
%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
%\begin{assumption}
%\label{assume:entropy LWE}
%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.  
%\end{assumption}
%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.  This says that if $\distLWE$ is hard then $X$ has many hardcore bits.  We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
\label{lem:many hardcore bits}
Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.  Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.  Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
\end{lemma}

\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard and that $m\geq n$.  Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.  Then according to \lemref{lem:many hardcore bits} we know that $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA , \vA X+E)\geq k\log q$.  By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.  To expand to $E$.

\begin{claim}
Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
\[
H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
\]
\end{claim}
%\begin{claim}
%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
%\end{claim}
%\begin{proof}
%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.  Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.  Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.  This completes the claim.
%\end{proof}

%\begin{claim}
%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
%\end{claim}
%\begin{proof}
%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.  Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.  Furthermore, let $C$ be a circuit of size at most $s_{sec}'$ where $\Pr[C(Z) = Y] > 2^{-k}$.  Define the circuit $C'$ that outputs the first $k$ bits of $C$'s output.  Thus, $\Pr[C'(Z) = Y_{1,..., k}] \geq \Pr[C(Z) = Y] > 2^{-k}$.  Note that $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,...,k}, Z), (Y_{1,..., k}, Z))<\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.  Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
%This completes the claim.
%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.  In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.  Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.  Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.  This completes the claim.
%\end{proof}

%\begin{claim}
%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
%\end{claim}
%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.  This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.  Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
%
%
%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.  By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.  This completes the proof of \lemref{lem:conversion to unpredictability}.
%\end{proof}
\begin{proof}
Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.  We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.  That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}'}}((E, \vA X+E), (Y, \vA+E))\leq \epsilon$, there exists $C$ of size $s_{sec}'$ such that $\Pr[C(\vA, \vA X+E) = Y]> 2^{-\ell}$.  Fix one such $Y$.  Let $\mathcal{E}$ be the event that $A_{1,..., n}^{-1}$ exists.  Note that $\mathcal{E}$ occurs with probability $1-\gamma$.

Define the distribution $Y' = A(%A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
\begin{align*}
\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))%&\leq %\delta^{\mathcal{D}_{s_{sec}'}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ (1-\gamma)\\
&\leq \delta^{\mathcal{D}_{s_{sec}'}}((\vA X+E - \vA Y', \vA, \vA X+E), (E, \vA, \vA X+E))\\
&\leq \delta^{\mathcal{D}_{s_{sec}'}}(( \vA (X-Y') +E, \vA, \vA X+E), (E, \vA, \vA X+E))
\end{align*}
\end{proof}

\begin{proof}[Proof of \clref{lem:unp of x and e}]
First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.  That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.  Define $I'$ by the following:
\begin{enumerate}
\item Input $(\vA, \vA X+E)$.
\item Run $y\leftarrow I(\vA, \vA X+E)$.
\item Output $z = \vA y - \vA X+E$.
\end{enumerate}
Note that $|I'|\approx |I|$.
It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
\begin{align*}
\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
\end{align*}
Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.  That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((E, \vA, \vA X+E), (Y, \vA, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.  Define $I'$ by the following:
\begin{enumerate}
\item Input $(A, \vA X+E)$.
\item Run $y\leftarrow I(\vA, \vA X+E)$.
\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
\item Output $z = \vA^{-1}(\vA X+E-y)$.
\end{enumerate}
Note that $|I'|\approx |I|$.  For sufficient parameter sizes the probability of $A^{-1}$ not existing is negligible.  Denote this probability by $\gamma$.  Then note that $\Pr[I'(\vA, \vA X+E) = Z] > 2^{-k}-\gamma = 2^{-k'}$.  Then one has the following~(conditioned on the event that $\vA^{-1}$ exists):
\begin{align*}
\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
\end{align*}
Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
\end{proof}

\end{proof}

\section{Proof of Theorem \ref{thm:blockLWE}}
\label{sec:proof of block theorem}

\begin{proof}
We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.  If the blocks are fixed to some other value the reduction is essentially the same.

%It should be clear to the reader where the reduction differs for another block fixing source.\lnote{I don't like the phrasing; maybe we should say that if the blocks are fixed to some non-0 value, the reduction is essentially the same}

Let $\D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.  That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx'$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.  We assume that, 
\[
|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
\]

We build a distinguish $\D'$ that distinguishes standard LWE instances from uniform.  Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.  Our goal is to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.

It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
\item If $\vb'$ is uniformly distributed then $\vb$ is uniformly distributed.
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists x$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve$ are $0$.
\end{enumerate}
\begin{figure}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.

\item Initialize $\vA^* = (\va^*_1, \ldots, \va^*_{m+\alpha})^T = \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)$.
\item \label{step:randomization}
For {$i=1\ldots m+\alpha$}:
\subitem Randomly generate $(\gamma_{i,1},\ldots, \gamma_{i,\alpha}) \leftarrow \Fq^\alpha$.
 \subitem For {$j = 1 \ldots n+\alpha$}:
\subsubitem Set $A_{ij} \leftarrow A^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}$
\subsubitem Set $b_i \leftarrow b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k}$
\item Run $\D$ on input $\vA, \vb$.
\item Output $\D$'s output.
\end{enumerate}
\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}

\begin{claim}
\label{cl:randomMatrixDist}
The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix.
\end{claim}
\begin{proof}
In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.  Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.  Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.  Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5. For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number. Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors. Therefore, the entire matrix $\vA$ is a truly random matrix.  This completes the claim.
\end{proof}
\begin{claim}
\label{cl:random ax+e}
If $\D'$ is provided with input distributed as $\vA', \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i} = b_{m+i}^*$ is uniformly generated otherwise and  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
\end{claim}
\begin{proof}
Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
Then define $\vx^*$ as:
\[
x^*_i = \begin{cases}
x_i', & \text{if }1\leq i\leq n \\
b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
\end{cases}
\]
Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).  Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).  Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.  The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
We have the following for all $i=1,..., m+\alpha$:
\begin{align*}
\va_i \vx^* + e_i^* &=\va^*_i\vx^*+\sum_{k=1}^\alpha \gamma_{i} \va^*_{m+k}\vx^*+e_i^*\\
&= \va_i^*\vx^* + e_i^* + \sum_{k=1}^\alpha \mathbf{\gamma}_{i} \va^*_{m+k}\vx^*\\
&= b_i^* + \sum_{k=1}^\alpha\gamma_i \va_{m+k}^* \vx^*\\
&= b_i^* + \sum_{k=1}^\alpha \gamma_i \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
&= b_i^* +\sum_{k=1}^\alpha\gamma_i b_{m+k}^*= b_i
\end{align*}
%\begin{align*}
%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
%& = b_i \label{reductionEq}
%\end{align*}
\end{proof}
\begin{claim} 
\label{clm:random b}
If $\D'$ is provided with input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random then $\vb$ is uniformly random.
\end{claim}
\begin{proof}
As before this is clearly satisfied before step~\ref{step:randomization}.  That is, each $b_i^*$ is uniformly and independently random.  After step~\ref{step:randomization} each $b_i$ is a fresh random linear combination of random values:
\[
b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
\]
Thus, each of these values is uniformly and independently random.
\end{proof}

%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$. 
%
%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$. Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
%\begin{align*}
%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
%\end{align*}
Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
\end{align*}
%==========
\ignore{
Before randomized:
$$\vA'\vx' + \ve = \vb'$$
For $i = 1\ldots m$,
$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
For $i = 1\ldots \alpha$,
$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
}
\end{proof}

\section{Additional Proofs}

\subsection{Proof of \lemref{lem:averageToMaximalError}}
\label{sec:proof of average to maximal error}
\begin{proof}
Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that 
\[
\sum_{w\in W} \Pr[W=w]\Pr[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]\leq \epsilon.
\]
For $w$ denote by $\epsilon_w = \Pr[w'\leftarrow \sample(w) \wedge \rec(w') \neq w]$.  Then by Markov inequality:
\[
\Pr_{w\in W}[ \epsilon_w \leq 2\expe_{w\leftarrow W} [\epsilon_w ] = 2\epsilon]\geq \frac{1}{2}
\]
Now suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]> 2\epsilon$.  This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.  Then note that $\Pr[W\in V]> 1/2$ as $W\setminus V$ contains at most $2^{k-1}-1$ points each of which has probability at most $1/2^k$ so $\Pr[W\in (W\setminus V)]\leq (2^{k-1}-1)/2^k < 1/2$.  Thus,
\begin{align*}
\Pr_{w\in W}[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]\\
&\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
\end{align*}
% where $\forall d\in D, \Pr[d'\leftarrow \sample(d) \wedge \rec(d') > 2\epsilon$.  In turn this implies that  
%\begin{align*}
%\Pr_{c\in C}[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]&=\frac{1}{|C|} \sum_{c\in C}  \Pr[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]\\
%&\geq \frac{1}{|C|} \sum_{d\in D}  \Pr[ d'\leftarrow \sample (d) \wedge \rec(d') \neq d]\\
%&\geq \frac{1}{|C|}\sum_{d\in D} 2\epsilon = \frac{1}{|C|}\left(\frac{|C|}{2}+1\right)2\epsilon = \epsilon + 2\epsilon/|C|> \epsilon
%\end{align*}
This is a contradiction.  The statement of~\lemref{lem:averageToMaximalError} follows directly.
\end{proof}

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
Let $\mathcal{M},d$ be a metric space that is $(s_{neigh},t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an $(s_{rec}, t)$-arbitrary recover functionality over $\mathcal{M}$.  Let $X$ be an arbitrary distribution.  Let $W$ be a distribution over $\mathcal{M}$ with $\Hoo(W)\geq k$ such that 
\[
\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.
\]  
For all $D$ of size at most $s = O(t(s_{neigh}+s_{rec}))$.  One such $W$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem Sample $z'\leftarrow \sample(z, t')$.
\subitem If $\rec(z', s) \neq  z$ output $0$.
\item Output $1$.
\end{enumerate}
  As before we know that $D(X, \sketch(X)) = 1$.  Since 
$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(W, SS(X))>1-\epsilon$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
%This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
Thus, for all $t', 1\leq t'\leq t$ on a random $w$
\[ \Pr_{w\leftarrow W}[w'\leftarrow \sample(w, t') \wedge \rec(w', \sketch(x')) = w]\geq 1-\epsilon.\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus, for all $1\leq t'\leq t$, $W$ is a $(t', \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

%\subsection{Proof of \lemref{lem:i t constant time}}
%\label{sec:proof lem i t constant time}
%\begin{proof} We consider the expected number of iterations in step 2 when $t+1\leq m/n$.  Steps 3 and 4 can be accomplished in time $n^3\log q +s_{ver}$.  An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.  The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
%\begin{align*}
%\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq  \prod_{i=0}^{n-1}\left( 1-\frac{m-n}{n(m-i)}\right)\\
%&\geq \prod_{i=0}^{n-1}\left( 1-\frac{1}{n}\right)\geq \left(1-\frac{1}{n}\right)^n \geq 1/4.
%\end{align*}
%Note in the last step we assume that $n\geq 2$.  The minimum of $(1-1/n)^n$ is achieved at $n=2$ and it quickly converges to $1/e$.  Thus, the expected number of iterations is at most $4$ giving the stated running time for $\mathcal{I}_t$.
%\end{proof}

\subsection{Proof of \lemref{lem:i t poly time}}
\label{sec:proof lem i t poly time}
\begin{proof}
We first note that $R(X, (\vA, \vA X+W))$ is computable in time $O(n^3\log q)$ by computing $AX+(W-W')- AX$ and checking if all dimensions have magnitude at most $|W|_\infty$ and at most $t$ dimensions have nonzero magnitude. We consider the expected number of iterations in step 2 when $t+1\leq m/n$.  Steps 3 and 4 can be accomplished in time $n^3\log q $.  An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.  The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
\begin{align*}
\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{n-1}\left( 1-\frac{\frac{dm\log n}{n}-1}{m-i}\right)\\
&\geq  \prod_{i=0}^{n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-n}{m-i}\right)\right)\geq \prod_{i=0}^{n-1}\left( 1-\frac{d\log n}{n}\right) \\
&= \left(1-\frac{d\log n}{n}\right)^n  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{d\log n}\geq \frac{1}{4^{d\log n}} = \frac{1}{n^{2d}}
\end{align*}
Thus, the expected number of iterations in step 2 is $n^{2d}$.  We assume all matrix operations can be completed in time $n^3\log q$, giving expected running approximately $n^{2d}(n^3 \log q)$.
\end{proof}

\section{Parameter Settings for \consref{cons:informal construction}}
\label{sec:parameter settings}
In this section, we explain the different parameters that go into our construction.  In \thref{thm:lossless secure sketch log} we give lossless sketches from a security parameter $n$ and an error $t$.  In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.  In this section, we will assume that the inverter runs in time proportional to the number of errors~(\lemref{lem:i t poly time}).  We begin by reviewing the parameters that make up our construction:

\begin{itemize}
\item $|W|$: The length of the source.  
\item $t$: Number of errors that can be supported.  
\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
\item $q$: The size of the field.  
\item $\rho$: The fraction of the field needed for error sampling.  
\item $m$: The size of each number of samples in the LWE instance.  
\end{itemize}
We will split the source $|W|$ into $m$ blocks each of size $\rho q$~(that is, $|W| = m\log \rho q$).  We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.  As stated above we have three constraints:
\begin{itemize}
\item Maintain security of LWE.  If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + 3\gamma} m = \poly(n)$.  The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.  We ignore this effect and assume that $\rho q = 2n^{1/2+3\gamma}m$.
\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-1)$.
\item Minimize entropy loss of the construction.  If we assume that $|X|\leq |W|$ then the entropy loss of the construction is $|W|-|X|$.  We want the entropy loss to be zero, that is, $|W| = |X|$.  Substituting, one has $m\log \rho q = n \log q$.
\end{itemize}
Collecting constraints we can support any setting where $t, n, q, \rho, m$ satisfy the following constraints~(for constants $d, f$):
\begin{align*}
n_0&< n\\
t&\leq d \log n\left(\frac{m}{n}-1\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+3\gamma}m\\
m\log \rho q &= n \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
\begin{align*}
n_0&< n\\
t&\leq d\log n\left(\frac{m}{n}-1\right)\\
m \log 2n^{1/2+3\gamma}m &= n \log n^f
\end{align*}
%\xnote{$ m \log 2n^{1/2+3\gamma}m = n \log n^f$}
This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n\\
t&\leq d\log n\left(\frac{ m }{n}\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{n}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$.  Finally we assume that $t = d \log n(m/n-1)$~(this means we have only as many dimensions as necessary for polynomial time recovery):
\begin{align*}
n_0&< n\\
m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
f &= \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}
\end{align*}

%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
Note that $f$ is at most a constant in $n$.

Assuming $n_0 < n$ and let $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+d)n^{3/2+3\gamma}}{d}
\end{align*}
Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.  This is the setting of parameters in \thref{thm:lossless secure sketch log}.

\ignore{
\subsection{Old parameter setting}
The question then becomes whether there is a setting 
Our construction has two goals: 1) maximizing correcting capability~(while retaining polynomial time decoding, and 2) maximizing the unpredictability entropy of $W$ conditioned on the construction~($\tilde{m}$ in \defref{def:comp secure sketch}).  Our parameters will differ significantly depending on what setting of $t$ is used.  We will consider both settings where $t\leq m/n-1$ and $t\leq c\log n (m/n-1)$.  Recall these corresponding to Construction~\ref{cons:decoding algorithm} running either in fixed polynomial time or time approximately $n^{2c}$.  We consider each of these settings:

$\mathbf{t \leq m/n-1}$

We first find the appropriate range of $n$.  First, we need $n>n_0$ for LWE security. Increasing $n$, up to the point when $H_\infty(X)=H_\infty(W)$, i.e., $n\log q = m\log\rho q$, increases the unpredictability entropy of the construction~(see \assref{assume:entropy LWE}). However, this decreases the number of errors $t$ we can correct. There is no advantage to increasing $n$ further\footnote{We primarily consider the construction with no entropy drop, if a drop is unpredictability entropy is acceptable, more errors can be corrected.  However, if the remaining unpredictability entropy is worse than a known information theoretic construction~(see~\cite{DBLP:journals/siamcomp/DodisORS08}), an information theoretic construction should be used.
}.

We first analyze the lossless construction, when  $H_\infty(X)=H_\infty(W)$ and thus $n\log q = m\log\rho q$.
Substituting $m \ge (t+1)n$ above one has:
\[
n \log q  = m \log \rho q \geq (t+1)n \log \rho q
\]
Thus, the lossless construction can support settings where $t+1\leq \frac{\log q}{\log \rho q}$.  In order to apply \lemref{lem:uniform LWE}, we need that $\rho q\geq 2n^2m \geq 2(t+1)n^3$.  We consider the setting $q = n^d$ for some constant $d$ (larger $q$ is unlikely to improve parameters unless 
%In Appendix~\ref{sec:parameters q expo}, we review parameters where $q=2^n$, these parameters are worse unless 
lattice problems are hard to approximate within exponential factors.)  
Dividing the above equations above we have:
\[
t+1\leq \frac{\log q}{\log \rho q}\leq \frac{\log q}{\log 2(t+1) n^3}\leq \frac{\log n^d}{\log 2t n^3} \approx d/3
\]
(the last step follows because the second-to-last step already implies $t\le d\log n$).
Thus, we can support a constant $d/3-1$ number of errors where $q = n^d$ is the size of our field.  Because we need $\rho q\geq 2n^2m \geq 2(t+1)n^3$ (to apply \lemref{lem:uniform LWE}), we require $\rho > n^{3-d}$.  Thus, our construction is secure if SIVP and GAPSVP are hard within approximation factors of 
\[
\tilde{O}(n^{5/2}m/\rho) = \tilde{O}\left(\frac{n^{5/2} m }{\rho}\right)
= \tilde{O}\left(\frac{n^{5/2}t}{n^{3-d}}\right)
= \tilde{O}\left(n^{d-1/2}m\right)
\]

%As an example if $\gamma = n^{c}$, this yields:
%\[
%t\leq \frac{n}{n + \log n + \log t - \log \gamma} = \frac{n}{n+\log n +\log t  -\log n} = \frac{n}{n + \log t}
%\]
%Alternatively, if $\gamma = n^{\log n}$, this yields:
%\[
%t\leq \frac{n}{n + \log n + \log t - \log \gamma} = \frac{n}{n+\log n +\log t  -\log^2 n} = \frac{n}{n+\log n - \log^2 n + \log t}
%\]
%Thus, as $q$ grows we can support a larger number of errors.  However, the growth of $q$ with a fixed size $\rho q$ leads to the approximation factor in \lemref{lem:uniform LWE} no longer being a harder problem.  Thus, $q$ can only be increased while the lattice problems in \lemref{lem:uniform LWE} is still believed to be hard.  Furthermore, in the decision formulation of \lemref{lem:uniform LWE decision} requires that $q(n) = poly(n)$.  This means that $t\leq O(\log n)$.

$\mathbf{t\leq c\log n(m/n -1)}$

We repeat the above analysis.  Recall we now consider the case where $m\geq (t+1)n/(c\log n)$.  We seek to satisfy:
\[
n\log q = m\log \rho q \geq (t+1)n \log \rho q /(c\log n)
\]
Again, we assume that $q = n^d$ for some constant $d$.  Then 
\[
t+1\leq \frac{c \log n \log q }{\log \rho q}\leq \frac{cd\log^2 n}{ \log \frac{2(t+1) n^3}{c\log n}}\leq \frac{cd \log^2 n}{3 \log n} \approx \frac{cd \log n}{3}.
\]
This gives $\rho > n^{3-d}/\log n$ and security if SVIP and GAPSVP are hard within approximation factors of $\tilde{O}(n^{d-1/2}m/\log n)$.

\textbf{Formulation from $W, t$:}

In a standard application, a source $W$ and number of errors $t$ will be given\footnote{Parameter settings will change the alphabet size and thus might change $t$, we ignore these effects and assume $t$ is given.}.  Thus, the goal is to maximize security subject to correcting $t$ errors.  This means the following parameters must be set:
\begin{itemize}
\item How large should $X$ be?  The size of $X$ is the limiting factor for the resulting unpredictability entropy.  Thus, $n$ should be as large as possible while allowing decoding.  We must also ensure that $n>n_0$ for security.
\item How large a field should we operate over?  This is the parameter $q$.  Increasing this parameter allows correcting more errors~(subject to the underlying lattice problems still being hard to approximate).
\item How length block should $W$ be split into?  This is the parameter $\rho q$.  Setting this parameter also sets $m = |W|/\log \rho q$.
\end{itemize}

Unfortunately, the parameters $m, n$ and depend on each other and cannot be set independently.  As before, we will consider the fixed poly time decoder and variable poly time decoder in turn.

$\mathbf{t\leq (m/n-1)}$

We set parameters in the following order:
\begin{itemize}
\item Let $m, n$ be integer solutions to the following equations that maximizes $n$~(if the maximum solution is less than $n_0$, we cannot support a secure construction):
\begin{align*}
|W| &= m\log 2n^2m\\
n&\leq m/(t+1)
\end{align*}
We assume that the solution for $m,n$ exists and is tight~(in the sense that $n = m/(t+1)$).  If not, there is an entropy loss in the construction due to size mismatches~(in the entropy analysis below) and padding~(to ensure that $|W|$ is an integer number of blocks).
\item Set $\rho q = 2n^2m $.
\item Set $q = n^{(t+1)\log( 2(t+1)n)/\log n}$.  Note that although $n$ appears in the exponent if $t$ is a fixed constant~(does not depend on $|W|$), this value is $q =\poly(n)$.  
\end{itemize}  Given these parameters, we can calculate the sizes of $X$ and $W$~(as we show in the \secref{sec:security of LWE cons} $\tilde{m} =|W|$):
\begin{align*}
H^{\unp}_{\epsilon, s} ( W | AX+W) &= \min\{ H_\infty(W), H_\infty(E)\}\\
H_\infty(X) = |X| &= n \log q= \frac{m}{t+1}\log n^{(t+1)\log 2(t+1)n/\log n} \\
&= \frac{m}{t+1} \frac{(t+1)\log 2(t+1)n}{\log n} \log n = m \log 2(t+1)n^3 \approx m\log 2n^2m\\
H_\infty(W) = |W| & = m \log \rho q = m \log 2n^2 m\,.
\end{align*}

$\mathbf{t \leq c\log n(m/n-1)}$
We set parameters in the following order:
\begin{itemize}
\item Let $m, n$ be integer solutions to the following equations that maximizes $n$~(if the maximum solution is less than $n_0$, we cannot support a secure construction):
\begin{align*}
|W| & = m\log 2n^2m\\
 \frac{nt}{c\log n} + n&\leq m
\end{align*}
We assume that the solution for $m,n$ exists and is tight~(in the sense that $ \frac{nt}{c\log n} + n=m$).  If not, there is an entropy loss in the construction due to size mismatches~(in the entropy analysis below) and padding~(to ensure that $|W|$ is an integer number of blocks).
\item Set $\rho q = 2n^2m $.
\item Set $q = (2n^2m)^{m/n}$.  Note if $t = O(\log n)$, then $m/n = \frac{t}{c\log n} +1 = O(1)$ and thus $q$ is polynomial in $n$.
\end{itemize}  Given these parameters, we can calculate the sizes of $X$ and $W$~(as we show in the \secref{sec:security of LWE cons} $\tilde{m} =|W|$):
\begin{align*}
H^{\unp}_{\epsilon, s} ( W | \vA X+W) &= \min\{ H_\infty(W), H_\infty(E)\}\\
H_\infty(X) = |X| &= n \log q= n \log (2n^2m)^{m/n} = m \log 2n^2m\\
H_\infty(W) = |W| & = m \log \rho q = m \log 2n^2 m\,.
\end{align*}

We'll now consider a formulation for a fixed length biometric and a number of block errors.  We assume that $n$ is given as a security parameter and thus we ask how many errors can be corrected for a noisy uniform distribution of length $w>>n$.  We denote the number of errors by $t$~(we'll be able to correct block errors over the alphabet $[-\rho q, \rho q]$).  
Let $n$ be a security parameter and let $W$ be the uniform distribution of length $w>>n$.  Let $m$ as the minimum integer such that $m\log 4m^2 n\geq w$.  Set $q = 2^{m/n}4m^2n$.  Then split $W=( W_1,..., W_m)$ where each $W_i$ is of length $\log 4m^2 n$ bits.  Then, for $W' =( W_1',.., W_m')$ if  $t = |\{i |  W_i \neq W_i'\}| \leq m/n$ block errors, Construction~\ref{cons:decoding algorithm} allows for decoding in expected polynomial time.  Furthermore, $H^{\unp}_{\epsilon, s}(W | \vA X+W)\geq |W|$~(stating \lemref{lem:uniform LWE decision} in the language of Assumption~\ref{assume:entropy LWE}).

\begin{theorem}
\label{thm:security of secure sketch}
Let $n_0$ be a security parameter and let $W$ be uniform over $\mathcal{M}$ and let $t$ be a constant.  Let $m,n $ be the solution to the following equations that maximizes $n$.
\begin{align*}
|W| &= m\log 2n^2m\\
n&\leq m/t
\end{align*}
If $n>n_0$ and $n = m/t$ and \assref{assume:entropy LWE} holds, then for 
\begin{align*}
q &= n^{3t\log( \sqrt[3]{2t}n)/\log n}\\
\rho q &= 2n^2m,
\end{align*}  Construction~\ref{cons:LWESecureSketch} with uniform error over the interval $[-2n^2m, 2n^2m]$ is a $(\mathcal{M}, |W|, |W|, \epsilon, s, s_{sketch}, s_{rec}, t)$-computational secure sketch for $s = \poly(n), s_{sketch} = O(m\times n )$ and $s_{rec}$ is expected polynomial time.
\end{theorem}

\bnote{Not sure what to do with this}
\begin{theorem}
\label{thm:security of block sketch}
Let $n_0$ be a security parameter and let $t$ be a constant.  Let $W\in \{0, 1\}^{(m+\alpha)\times \log 2n^2m}$ be an $\alpha$-symbol fixing source where $m,n $ are the solution to the following equations that maximizes $n$.
\begin{align*}
|W| &= (m+\alpha)\log 2n^2m\\
(n+\alpha)&\leq (m+\alpha)/t
\end{align*}
If $n>n_0$ and $n+\alpha = (m+\alpha)/t$ and \assref{assume:entropy LWE} holds, then for 
\begin{align*}
q &= n^{3t\log( \sqrt[3]{2t}n)/\log n}\\
\rho q &= 2n^2m,
\end{align*}  Construction~\ref{cons:LWESecureSketch} with uniform error over the interval $[-2n^2m, 2n^2m]$ is a $(\mathcal{M}, \Hoo(W), \Hoo(W), \epsilon, s, s_{sketch}, s_{rec}, t)$-computational secure sketch for $s= \poly(n)$,  $s_{sketch} = O(m\times n )$ and $s_{rec}$ is expected polynomial time under .
\end{theorem}

}

\ignore{
\section{Fuzzy Extractor Statement of Construction~\ref{cons:LWESecureSketch}}
\label{sec:fuzzy extractor phrasing}
In this section we restate Construction~\ref{cons:LWESecureSketch} as a computational fuzzy extractor instead of a computational secure sketch:
\begin{construction}[Computational Fuzzy Extractor based on LWE] 
\label{cons:LWEFuzzyExtractor} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers, furthermore let $\chi$ be a distribution $\Fq$ that can be sampled with a fixed number of bits $s_{err}$.
Let $\mathcal{I}_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.  Furthermore, let $\rext$ be a reconstructive extractor.  Let $W$ be a distribution over $\{0,1\}^{s_{err}\times m}$.

\textbf{\gen}
\begin{enumerate}
\item Input $w\leftarrow W$.
\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
\item Use $w$ as the randomness for the sampling algorithm, $\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
\item Sample $seed\leftarrow U$ as required for \rext.  Compute $r\leftarrow \rext(E, seed)$
\item Set $p = (A, AX+E, seed)$.
\item Output $(r, p)$.
\end{enumerate}

\textbf{\rep}
\begin{enumerate}
\item Input $(w', p)$
\item Parse $p$ as $(A, C, seed)$
\item Compute $E' \leftarrow \sample (w')$.
\item Set $X' = \mathcal{I}_t(A, C-E') $. 
\item Compute $r\leftarrow \rext (C-AX', seed)$.
\item Output $r$.
\end{enumerate}
\end{construction}

\begin{theorem}[Security of Construction~\ref{cons:LWEFuzzyExtractor}]\label{thm:LWEFuzzyExtractor}
Fix $(n, m, q, \chi)$ such that Assumption~\ref{assume:general LWE} holds for $\mathcal{I}$ of size at most $s$ with success $\epsilon$.  Furthermore assume that a fixed number of bits $s_{err}$ are necessary to sample from $\chi$.  Let $\rext: \chi^m \times\{0,1\}^\ell\rightarrow \{0,1\}^{k_{len}}\times \{0,1\}^\ell$ be an extractor with $(\log 1/\epsilon - \log 1/\delta, \delta)$-reconstruction $(\cons,\decons)$.  Let $\mathcal{I}_t$ be an inverter as described in Construction~\ref{cons:LWEFuzzyExtractor} of size $s_{\mathcal{I}_t}$.  Then Construction~\ref{cons:LWEFuzzyExtractor} is a $(\{0,1\}^{m\times s_{err}}, m\times s_{err}, k_{len}, t, s_{rec}, s/(|\cons|+|\decons|), 5\delta)$ computational fuzzy extractor where $s_{rec, t} = s_{\mathcal{I}_t}+ |\sample| + O(m\times n\times \log q) + |\rext|$.
\end{theorem}
}

\ignore{
\section{Min-entropy error LWE}
Throughout this section we will assume that \sample uses $\ell$ bits of randomness to produce the required distribution in a single dimension.  Usually, this is the normal (Gaussian) distribution with some mean.  Note that for the uniform distribution sampling requires $\log q$ bits where $q$ is the size of the range.  By information theory we know that in expectation, the number of random bits is smaller for an distribution that is not uniform, but this provides us no guarantee about the worst case number of bits.  We will begin with noting a few cases that seem significantly easier to show.  Recall that the distribution $W$ is drawn from is specified and known by the adversary.
\begin{itemize}
\item Case 1: $\Hoo(W)\leq \ell (m- n)$.  This case is not secure.  Let $W\in\{0,1\}^{\ell m}$ and we further specify $W=W_1,...,W_m$ where each $W_i\in\{0,1\}^\ell$.  We then set $W_1,...,W_n$ equal to some fixed value, $0$ without loss of generality, and $W_{n+1},...,W_m$ to the uniform distribution.  Then it is clear for the first $n$ equations, the adversary is solving a system $Ax=b$ without any error and this can be done in $P$.
\item Case 2: Full or no entropy.  As before, let $W\in\{0,1\}^{\ell m}$ and we further specify $W=W_1,...,W_m$ where each $W_i\in\{0,1\}^\ell$.  We further restrict to the case where each $W_i$ either $W_i\overset{d}=U_\ell$ or $\Hoo(W_i) = 0$.  Thus, for each dimension either, one of the two occurs: the error is properly generated or the adversary knows the error exactly. So, for each dimension, given the $W_i\overset{d}=U_\ell$, the adversary can only guess the correct random variable not better than $2^{\ell}$. Similarly, if given the $\Hoo(W_i) = 0$, the adversary can always guess the correct variable.(\xnote{This is trivial, since if we give $\Hoo(W_i) = 0$, we are actually giving the a random variable has probably of 1.})

We are considering the case that the adversary will be given the ensemble $\{W_1,...,W_n\}$, where each $W_i$ has some entropy.

\item Case 3: General case.
\item \textbf{Hypothetical worry case}  Suppose for convenience we are working with the normal distribution that has variance $\frac{2}{\pi}$ (centered around 0).  That is 
\[
\Pr[X=x] = \frac{1}{\sqrt{\frac{2}{\pi}}\sqrt{2\pi}}e^{-\frac{1}{2}{\frac{2}{\pi}x^2}}=\frac{1}{2}e^{-\pi x^2}
\]
Thus, $\Pr[X=0] =1/2$.  One can easily design a procedure $\sample'$ that generates this distribution using a maximum of some number $\ell$ bits.  Let $w_1,...,w_\ell$ be the bits that $\sample'$ takes as input.  Then when $w_1=0$ the sampler outputs $0$.  The generation for other values does not matter (only that generating some value takes $\ell$ bits).  Thus, to generate $n$ samples we need at most $\ell n$ bits.  However, there is a distribution with min-entropy $\Hoo(W)=(\ell -1) m$, that produces always produces the all zero error.  This distribution has the first bit of each $W_i$ 0 and the remaining bits truly random.  Thus, it seems impossible for our scheme to be secure for an arbitrary procedure \sample, but we will need to specify a specific \sample.  Another possibility is to use a different distribution that looks like the normai distribution but requires a ``flatter'' number of coins to be used for each distribution.  Is there a definition of an algorithm that uses the same number of random bits for each invocation?  Would this be enough to get rid of this problem?
\end{itemize}
Questions: 
\begin{enumerate}
\item How we sample this error vector $\vect{e}$?  Can we do something other than Gaussian to remove some worries?
\item Given the two biometric data which have small distance between each other, will we get the small distance between the error vector after sampling?
\textbf{Solved, each dimension is sampled independently.  Thus, our distance blowup is only as large as the number of bits needed to sample each dimension.}
\item When is LWE easy and when is LWE hard?  Are we going to be able to create a sufficient gap between these two cases?
\item Does the parallel sampler of Peikert allow for the distance in two randomness being small, creating small output distance?
\textbf{Solved, was trying to do the wrong thing.  Just Gaussian in each dimension.}
\item Does the sampler of Peikert allow for nonuniform input distribution?
\textbf{Solved, was trying to do the wrong thing (was trying to sample from lattice points, instead of adding noise around a lattice point).}
\subitem If not how does applying an extractor change the distance of two distributions?
\item How if it all can this be used concurrently?  Seems very one time right now.
\item How efficient will our decoding procedure be?  Efficient enough for practical usage?
\end{enumerate}

\textbf{What security do we need: }
}

\ignore{
\section{Robustness of LWE to error with min-entropy}
\label{sec: lwe min-entropy}

In this section we explore the robustness of the LWE assumption when the errors are drawn from a deficient distribution.  We provide a short introduction to the Learning with Errors problem in \secref{sec:fuzzyCompLWE}.  For a more complete introduction see the survey by Regev~\cite{regevLWEsurvey}.  The tools presented in this section are used to show the security of the computational secure sketch presented \subsecref{subsec:fuzzyExtLWE}.  This work is also of independent interest and can be viewed in a similar way to the work of Goldwasser et. al.~\cite{goldwasserRobustLWE}.  In their work, they consider the robustness of an LWE instance $A, Ax+e$ where $x$ is sampled from a distribution that has min-entropy but is not uniform.  They then use this result to show LWE-based cryptosystems are leakage-resilient.  Our theorem statement will follow a similar structure to the theorem statement of Goldwasser et. al. so we first present their informal theorem:
\begin{theorem}~(\cite[Theorem 1 (Informal)]{goldwasserRobustLWE})
For any super-polynomial modulus $q=q(n)$, any $k\geq \log q$, and any distribution $\mathcal{D}=\{D\}_{n\in\mathbb{N}}$ over $\{0,1\}^n$ with min-entropy $k$ , the (non-standard) LWE assumption, where the secret is drawn from distribution $\mathcal{D},$ follows from the (standard) LWE assumption with secret size $\ell\overset{\Delta}=\frac{k-\omega(\log n)}{\log q}$ (where the ``error rate'' is super-polynomially small and the adversaries run in time $\poly(n)$).
\end{theorem}

Before considering high entropy error, we must be clear about what this means.  The $x$ in an LWE instance is sampled uniformly from $\{0,q\}^n$, thus the sampling procedure requires $\lceil \log q\rceil\times n$ bits.  However, $e$ is sampled from some error distribution $\chi$.  $\chi$ is normally the normal distribution centered around $0$ with some variance $\sigma^2$ and then rounded to the nearest integer between $[-q/2, q/2]$.  Sampling from a rounded normal distribution requires a variable number of random bits for each dimension.    Indeed, using the normal distribution there are events with nonzero but negligible probability.  These events necessarily take a large number of bits to sample.

\textbf{This is internal discussion and needs to be taken care of before presentation:}  There are two ways to provide these bits: 1) break the random string into chunks where each chunk is as long as the maximum number of random bits needed 2) provide the random bits needed to each dimensions.  One might hope that this problem is avoided by rounding to the nearest integer, but there is still some weight assigned to integers far from $0$.  We could consider a distribution whose statistical distance to the normal distance is exponentially small and gives weight 0 to all integers outside some radius.

For the moment we will ignore these problems and assume that a fixed number of bits is used to sample each dimension.  This would be the case if we substituted the uniform distribution on a significantly smaller domain.  \bnote{We need to be sure this produces a secure LWE instance}.

Thus, we assume that there exists a $\sample$ that uses $\ell$ bits of randomness to produce an error term in one dimension.  We are now ready to present the LWE assumption:
\begin{assumption}[Learning with Errors]
Let $k$ be a security parameter and define $q=\poly(k)$\bnote{Do we want the poly or exponential case?}and $n = \poly( k)$.
Let $x\overset{\$}\leftarrow \{0,q\}^n$.   An LWE sample is of the form $(a,b) = (a, a_1x_1+...+a_nx_n+\sample(e) \mod q)$ where $a_1,...,a_n\overset{\$}\leftarrow\{0,q\}^n$ and $e\overset{\$}\leftarrow\{0,1\}^\ell$.  The $(m,n,q,k)$-LWE assumption is that no algorithm given $m = \poly(k)$ LWE samples running in time $\poly(k)$ can recover $x$ with probability greater than negligible in $k$.
\end{assumption}

We then achieve our non-standard LWE assumption by sampling $e$ from a high-entropy distribution instead of the uniform distribution.

\subsection{Affine min-entropy distributions}
In the previous section, we investigated the security of the LWE assumption with deficient distributions.  Namely, we saw that the LWE assumption for block-fixing sources was implied by the LWE assumption with fewer dimensions and samples.  We now ask: what other types of min-entropy distributions can be shown to reduce to the LWE assumption?  Using a reduction to standard LWE seems to require that the errors be considered homomorphically.  This is because recovering the error terms would break LWE.  Furthermore, these errors are first put through the \sample procedure, so this needs homomorphic properties as well.  Thus, the class we can hope for in this reduction is a linear set of errors.

Recall, a function, $f:D^n \mapsto R$, over field $K$ is a \textbf{linear transformation} if $\forall x,y\in D$ and $\forall a, b\in K, f(ax+by) = af(x) + bf(y)$.

We will consider the \textbf{LWE assumption w/ linear sources}.  That is, we consider an error distribution $E = E_1||...||E_k$ where $\Hoo(E) = qn$ and $E = \mathbf{T}(U_1||...||U_n)$ for rank $n$ matrix $\mathbf{T}: \Fq^n\mapsto \Fq^k$.
\vspace{.1in}
\begin{theorem}\label{thm:linearLWE}
Let $k$ be a security parameter and define $q, n, m = \poly(k)$.  Let $E$ be a linear source over $\{0,1\}^{\ell(m+\alpha)}$ where $\Hoo(E) \geq m\ell$.  Then the $(m,n,q,k)$-LWE assumption where \sample is a linear transformation implies the $(m+\alpha, n+\alpha, q, k)$-LWE w/ linear sources assumption.
\end{theorem}
\begin{proof}
The main difference between \thref{thm:blockLWE} and \thref{thm:linearLWE} is how we produce the errors terms.  We will use the same basic strategy of introducing equations and randomizing, however, the equations will errors will now be involved in the randomization.  As before, let $\mathcal{A}$ be an algorithm that accepts $m+\alpha$ LWE samples each of length $n+\alpha$ where the errors are generated $(E_1,..., E_{m+\alpha})^T = \mathbf{T} (U_1,..., U_m)^T$ for some matrix $\mathbf{T}$.  Further, assume that $\mathcal{A}$ returns $x$ with noticeable probability.  Our algorithm $\mathcal{A'}$ will make a single call to $\mathcal{A}$ and we will focus on properly preparing the LWE w/ linear sources instance.  We use $A',A,C,D,F,G,b,b'$ with the same meaning as before.
\end{proof}
}

\ignore{
\subsection{LWE search reduction}
\begin{proof}
Let $\mathcal{A}$ be an algorithm that accepts $m+\alpha$ LWE samples each of length $n+\alpha$ where $\alpha$ of the equations have a known error (and the remainder of the errors are uniformly generated) and returns $x$ with noticeable probability.  Denote this probability as $\epsilon$.  We will show how to convert $\mathcal{A}$ into an algorithm $\mathcal{A'}$ that accepts $m$ LWE samples of length $n$ and returns $x'$ with noticeable probability.  We begin by making the following assumptions for clarity:
\begin{itemize}
\item $\mathcal{A}$ asks for all $m+\alpha$ samples and asks for them simultaneously.  Since $\mathcal{A}$ has no effect on the samples, this does not limit $\mathcal{A}$'s power.
\item For the known error samples, the added error is $0$.  It is clear in our reduction where the added error would be added, but exposition is clearer without these errors.
\item The last $\alpha$ samples are the known error samples.  For other positioning of the known error samples, we can provide a permutation from our input, but this form is clearer.
\end{itemize}
The algorithm $\mathcal{A'}$ will make a single call to the algorithm $\mathcal{A}$ and thus the entire analysis will be showing that $\mathcal{A'}$ is able to properly prepare the instance that $\mathcal{A}$ is expecting and convert the result of $\mathcal{A}$ into a solution for the input of $\mathcal{A'}$.  We will use the matrix notation for the remainder of the proof.  Thus, the job of $\mathcal{A'}$ is to perform the following transformation:
\begin{align*}
\begin{array}{c | c}
\mathcal{A'}\text{ receives:        } & \mathcal{A}\text{ expects: }\\\hline
\left(A'\right) , b' = A' x' + e' & A = \left( \begin{array}{c | c}C & D \\ \hline F & G\end{array} \right), b=Ax+e
\end{array}
\end{align*}
Where the matrices have the dimensions as shown in \figref{fig:matrixDimension}: 
\begin{figure}[b]
\[
\begin{array}{c | c | c | c | c | c}
A & A' & C & D & F & G\\\hline
m\times n & (m+\alpha)\times( n+\alpha) & m\times n & m \times \alpha & \alpha \times n & \alpha \times \alpha
\end{array}
\]
\caption{Dimensions of matrices in reduction.}
\label{fig:matrixDimension}
\end{figure}
Thus, we have two major jobs, produce an augmented matrix $A$ that is a truly random matrix and to produce an augmented $b$ that given a solution for $x$ will yield a solution for $x'$.  The code of $\mathcal{A'}$ is presented in \figref{fig:imperfectLWEreduction}.  The main idea is to generate $\alpha$ new LWE samples and use $\alpha$ new variables to exactly solve these equations.  These last $\alpha$ equations then have no errors and can be used to randomize the instance to produce a random matrix without augmenting the error in the $b$ vector.
\begin{figure}
\begin{enumerate}
\item Input $A', b' = A'x' +e'$.
\item Randomly generate $F$.
\item Set $b = (b'_1,..., b'_n, \$, ..., \$)$ that is set the first $n$ values of $b$ equal to $b'$ and randomly generate the remainder.
\item Initialize $A = \left(\begin{array}{c | c}C = A' & D = \mathbf{0}\\\hline F & G = I\end{array}\right)$.
\item For $i=1...m+\alpha$, perform the following randomization:\label{step:randomizationSearch}
\subitem Randomly generate $\gamma_{i,1},.., \gamma_{i,\alpha}$.
\subitem Set $A_{i, \cdot} = A_{i, \cdot} +\sum_{j=1}^\alpha \gamma_{i,j}A_{m+j, \cdot}$.
\subitem Set $b_i = b_i +\sum_{j=1}^\alpha \gamma_{i,j} b_j$.
\item Run $\mathcal{A}$ on input $A, b$.
\item Receive output $x$ from $\mathcal{A'}$
\item Output $x' = x_1,..., x_n$.
\end{enumerate}
\caption{Code for $\mathcal{A'}$ to generate LWE w/ symbol fixing source from standard LWE instance}
\label{fig:imperfectLWEreduction}
\end{figure}
\begin{claim}\label{cl:randomMatrix}
The matrix $A$ generated after Step \ref{step:randomizationSearch} is a random matrix.
\end{claim}
\begin{proof}
First, the submatrices $D, G$ are clearly truly random after step \ref{step:randomizationSearch}.  For the matrix $D, D_{i, j}$ is assigned the value $\gamma_{(i,j-n)}$.  Similarly, for the matrix $G$, each entry is assigned as $\gamma_{(i-n, j-n)}$.  This is due to the original construction of the matrix $G$.  Then before step \ref{step:randomizationSearch} the matrices $C, F$ are random submatrices ($C=A'$ by assumption and $F$ by construction).  Thus, it remains to show that $C, F$ remain random after step 5.  We consider a single row vector of $C$.  The new row vector $C_{(i,\cdot)} = C_{(i,\cdot)} +\sum_{j=1}^\alpha \gamma_{i,j}F_{(j, \cdot)}$.  That is, $C_{(i,\cdot)}$ is the sum of a random vector and a random linear combination independent vectors.  That is, $C_{(i,\cdot)}$ is a random vector.

Similarly, consider a single row vector $F$. The new row vector $F_{(i,\cdot)} = \sum_{j=1}^\alpha \gamma_{i+n,j}F_{(i,\cdot)}$ is a random linear combination of independent vectors and thus truly random (since all $\gamma$ are chosen independently and randomly).  \bnote{I feel these claims are obvious but I would like to have a citation.}

Thus, the entire matrix $A=\left(\begin{array}{c | c}C & D \\\hline F & G\end{array}\right)$ is a truly random matrix.  This completes the claim.
\end{proof}
\begin{claim}\label{cl:goodLWEinstance}
The inputs $A, b$ provided to $\mathcal{A}$ is a random LWE w/ symbol fixing sources instance (provided that $A', b'$ was a random instance).
\end{claim}
\begin{proof}
By \clref{cl:randomMatrix} $A$ provided to $\mathcal{A}$ is a truly random matrix.  Thus, we must show that $b$ is of the proper form.  That is, we must show there exists an $x$ such that $b_i = A_{(i , \cdot)} x + e_i$ for $i=1,...,m$ and $b_i = A_{(i, \cdot)} x$ for $i=m+1,...,m+\alpha$.

By assumption there exists an $x'$ such that $A'x'+e' = b'$.  Before step \ref{step:randomizationSearch}, we have added $\alpha$ equations as well as $\alpha$ unknowns.  This means there no solutions have been eliminated.  Namely, $x^*_i = x'_i$ for $i=1,...,n$ and $x^*_i = b_i - \sum_{j=1}^m F_{i, j} x_j'$ for $i=n+1,..., n+\alpha$.  The case where $F$ does not have full row rank is also handled because the $G$ is the identity matrix and thus $F|G$ always has full row rank.  Furthermore, note that the last $\alpha$ equations have no error.  Thus, before step \ref{step:randomizationSearch} there exists a solution $x^*$ of the proper form.  It remains to show that the randomization in step \ref{step:randomizationSearch} retains the solution $x^*$.

The newly randomized system $A,b$ retains the same solution $x^*$  because we are not adding rows that have any error terms.  More precisely, let $A^*, b^*$ be the system before randomization (where $A^*x^*+e^* = b^*$).  Then for each row vector 
\begin{align*}
A_{(i, \cdot)} &= A^*_{(i, \cdot)}+\sum_{j=1}^\alpha \gamma_{i, j} A^*_{(m+j, \cdot)}, \\b_i &= b^*_i + \sum_{j=1}^\alpha \gamma_{i,j}b_j^*.
\end{align*}
Thus, we have the following for all $i=1,..., m$:
\begin{align*}
A_{(i, \cdot)} x^* +e_i^*&= (A^*_{(i, \cdot)}+\sum_{j=1}^\alpha \gamma_{i, j} A^*_{(m+j, \cdot)})x^*+e_i^*\\
&= A^*_{(i, \cdot)}x^* + \sum_{j=1}^\alpha \gamma_{i,j} A^*_{(m+j, \cdot)}x^*+e_i^*\\
&=\left( A^*_{(i, \cdot)}x^* + e_i^*\right)+ \sum_{j=1}^\alpha \gamma_{i,j} A^*_{(m+j, \cdot)}x^* \\
&= b^*_i + \sum_{j=1}^\alpha \gamma_{i,j}b_j^* = b_i
\end{align*}

The same equations follow without the term $e_i^*$ for $i=m+1,..., m+\alpha$.  
Thus, $x^*$ is a solution to the randomized LWE instance as well.  It remains to show that $x^*$ is a random vector.  This is clear for $x^*_i, i=1,...,n$.  For the remaining $x^*_i, i=m+1, ..., m+\alpha$ this follows since $x^*_i = b_i - \sum_{j=1}^m F_{i, j} x_j'$ where $b_i, F_{i, j}$ are randomly and independently chosen.  This completes the claim.
\end{proof}
\begin{claim}
If $x$ is a ``good'' solution output by $\mathcal{A}$ then $x'_i = x_i$ for $i=1,...,n$.  
\end{claim}
This claim follows by the analysis in \clref{cl:goodLWEinstance}.  The added equations and randomization do not affect the solution to the original $A', A'x'+e'$ instance provided.
\begin{claim}
$\mathcal{A'}$ outputs a ``good'' solution with probability only negligibly different  than the probability $\mathcal{A}$ outputs a good solution.
\end{claim}
The only time that $\mathcal{A'}$ does not produce the correct distribution is when the rows of $F$ are not linearly independent.  However, this occurs with negligible probability~\cite{something}.

Thus, we have constructed an algorithm $\mathcal{A'}$ that is able to recover a secret $x'$ of a standard LWE instance by adding samples  and equations that have no error.  Notice it was critical to add a variable for each new sample being provided to $\mathcal{A}$.  Furthermore, adding a degree of freedom for each new sample also allowed for construction of an equation with no error.  This completes the proof.

\end{proof}

\ignore{
\section{Parameters for Construction~\ref{cons:LWESecureSketch} when $q=2^n$}
\label{sec:parameters q expo}
The results of~\lemref{lem:uniform LWE decision} only support $q = \poly(n)$.  However, the reductions of Peikert may extend~\lemref{lem:uniform LWE decision} to exponential $q$.

$q = O(2^n)$. In this setting, we are no longer constrained by field size.  We need $\rho$ be large enough that the underlying lattice problems are still hard to approximate within a $\tilde{O}(n^{5/2}m/\rho)$ factor.  Unfortunately, even correcting a constant $c$ number of errors is difficult in this domain.  Let $\gamma$ be the maximum approximation factor where the underlying lattices problems are still hard.  Then, $\rho \leq \frac{n^{5/2}m}{\gamma}$.  To correct $c$ errors we need that $\log q/\log \rho q \geq c$.  That is,
\begin{align*}
c&\leq \frac{\log q}{\log \rho q}\\
&\leq \frac{n}{\log \frac{n^{5/2}mq}{\gamma}}\\
&\leq \frac{n}{\log \frac{n^{5/2}m2^n}{\gamma}}\\
&\leq \frac{n}{n + \log n + \log m - \log \gamma}
\end{align*}
Ignoring the $\log n$ and $\log m$ terms this yields that:
\begin{align*}
c&\leq \frac{n}{n-\log \gamma}\\
\frac{n(c-1)}{c}&\leq \log \gamma\\
2^{n(c-1)/c} &\leq \gamma
\end{align*}
Thus, supporting even a constant number of errors for $q=2^n$ requires lattice problems are exponentially hard to approximate, which would be quite surprising.  
}
}
\end{document}

### 2013-02-15 trunk/CompFuzzExt.tex
Initial commit

@@
 By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.
-To expand to $E$.
+To expand to $E$ we use the following claim:
 
@@
 
-Define the distribution $Y' = A(%A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
-\begin{align*}
-\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))%&\leq %\delta^{\mathcal{D}_{s_{sec}'}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ (1-\gamma)\\
-&\leq \delta^{\mathcal{D}_{s_{sec}'}}((\vA X+E - \vA Y', \vA, \vA X+E), (E, \vA, \vA X+E))\\
-&\leq \delta^{\mathcal{D}_{s_{sec}'}}(( \vA (X-Y') +E, \vA, \vA X+E), (E, \vA, \vA X+E))
+Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
+\begin{align*}
+\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
+&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
+&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
 \end{align*}
+Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
+Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$.
+Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.
+
+We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
+\begin{enumerate}
+\item Input $(\vA, \vA X+E)$.
+\item Run $y\leftarrow C(\vA, \vA X+E)$.
+\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
+\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
+\end{enumerate}
+Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
+Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.
+Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
 \end{proof}
 
-\begin{proof}[Proof of \clref{lem:unp of x and e}]
-First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
+The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
+%\begin{proof}[Proof of \clref{lem:unp of x and e}]
+%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
 That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
 Define $I'$ by the following:
-\begin{enumerate}
-\item Input $(\vA, \vA X+E)$.
-\item Run $y\leftarrow I(\vA, \vA X+E)$.
-\item Output $z = \vA y - \vA X+E$.
-\end{enumerate}
-Note that $|I'|\approx |I|$.
-It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
-\begin{align*}
-\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
-&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
-&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
-\end{align*}
-Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
+%\begin{enumerate}
+%\item Input $(\vA, \vA X+E)$.
+%\item Run $y\leftarrow I(\vA, \vA X+E)$.
+%\item Output $z = \vA y - \vA X+E$.
+%\end{enumerate}
+%Note that $|I'|\approx |I|$.
+%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
+%\begin{align*}
+%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
+%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
+%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
+%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
+%\end{align*}
+%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
 That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((E, \vA, \vA X+E), (Y, \vA, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
 Define $I'$ by the following:
-\begin{enumerate}
-\item Input $(A, \vA X+E)$.
-\item Run $y\leftarrow I(\vA, \vA X+E)$.
-\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
-\item Output $z = \vA^{-1}(\vA X+E-y)$.
-\end{enumerate}
-Note that $|I'|\approx |I|$.
+%\begin{enumerate}
+%\item Input $(A, \vA X+E)$.
+%\item Run $y\leftarrow I(\vA, \vA X+E)$.
+%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
+%\item Output $z = \vA^{-1}(\vA X+E-y)$.
+%\end{enumerate}
+%Note that $|I'|\approx |I|$.
 For sufficient parameter sizes the probability of $A^{-1}$ not existing is negligible.
@@
 Then one has the following~(conditioned on the event that $\vA^{-1}$ exists):
-\begin{align*}
-\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
-&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
-&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
-\end{align*}
-Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
-\end{proof}
+%\begin{align*}
+%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
+%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
+%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
+%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
+%\end{align*}
+%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
+%\end{proof}
 

### 2013-02-15 trunk/CompFuzzExt.tex
Initial commit

@@
 \label{lem:conversion to unpredictability}
-Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon, s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
-for $s_{sec}'\approx s_{sec}$.
+Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon', s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
+for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
 \end{lemma}

### 2013-02-15 trunk/CompFuzzExt.tex
clean up

@@
 \begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
-Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard and that $m\geq n$.
+Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
 Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.

### 2013-02-15 trunk/CompFuzzExt.tex
Update to parameter settings

@@
 \item $m$: The size of each number of samples in the LWE instance.  
+\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:conversion to unpredictability}).
 \end{itemize}
@@
 \item Minimize entropy loss of the construction.
-If we assume that $|X|\leq |W|$ then the entropy loss of the construction is $|W|-|X|$.
-We want the entropy loss to be zero, that is, $|W| = |X|$.
-Substituting, one has $m\log \rho q = n \log q$.
+We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.
+We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.
+Substituting, one has $m\log \rho q = k \log q$.
 \end{itemize}
-Collecting constraints we can support any setting where $t, n, q, \rho, m$ satisfy the following constraints~(for constants $d, f$):
-\begin{align*}
-n_0&< n\\
+Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
+\begin{align*}
+n_0&< n -k \\
 t&\leq d \log n\left(\frac{m}{n}-1\right)\\
@@
 \rho q  &= 2n^{1/2+3\gamma}m\\
-m\log \rho q &= n \log q
+m\log \rho q &= k \log q
 \end{align*}
@@
 \begin{align*}
-n_0&< n\\
+n_0&< n - k\\
 t&\leq d\log n\left(\frac{m}{n}-1\right)\\
-m \log 2n^{1/2+3\gamma}m &= n \log n^f
+m \log 2n^{1/2+3\gamma}m &= k \log n^f
 \end{align*}
@@
 n_0&< n\\
-t&\leq d\log n\left(\frac{ m }{n}\right)\\
+t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
 %f \log n &= \frac{m}{n}\log 2n^2m\\
@@
 \end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$.
+To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g$.
 Finally we assume that $t = d \log n(m/n-1)$~(this means we have only as many dimensions as necessary for polynomial time recovery):
@@
 m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
-f &= \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}
+f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+d)}{d}\frac{\log \frac{2(c+d)}{d} n^{3/2+3\gamma}}{\log n}
 \end{align*}
@@
 \end{align*}
-Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.  This is the setting of parameters in \thref{thm:lossless secure sketch log}.
+Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.
+We will set $g = 2$, that is the first half of $X$ our sketch will output the first half of $X$.
+This is the setting of parameters in \thref{thm:lossless secure sketch log}.
 

### 2013-02-15 CompFuzzExt.tex
Updates to theorems with HILL entropy

--- 2013-02-15 trunk/CompFuzzExt.tex
@@
 \label{lem:conversion to unpredictability}
-Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon', s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
+Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
 for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
@@
 We now state a setting of parameters that yields a lossless sketch.
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
-There exist efficient lossless secure sketches based on \consref{cons:informal construction}:
 
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
+Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
 Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then \consref{cons:informal construction} is a lossless secure sketch.
-That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$
+If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
 % for following parameters:
@@
 
+For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe setting $q = poly(n)$.  
 \thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.
@@
 Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.
-\consref{cons:informal construction} is a lossless secure sketch.
-That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$ for %the following parameters:
+There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
 %\[

### 2013-02-15 CompFuzzExt.tex
Updates to theorems with HILL entropy

@@
 
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe setting $q = poly(n)$.  
+For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
 \thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.
@@
 \end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g$.
+To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
 Finally we assume that $t = d \log n(m/n-1)$~(this means we have only as many dimensions as necessary for polynomial time recovery):
@@
 Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.
-We will set $g = 2$, that is the first half of $X$ our sketch will output the first half of $X$.
+We will set $g = 2$, that is our sketch will output the first half of $X$.
 This is the setting of parameters in \thref{thm:lossless secure sketch log}.

### 2013-02-15 trunk/CompFuzzExt.tex
section 4

@@
 
-We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-hard if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with the probability $\epsilon$.
+We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-hard if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
 \end{definition}
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume there exists a PPT-distinguisher $D$ such that $\delta^D((\vA, \vA X+E), (\vA, U))>\epsilon$ for non-negligible $\epsilon$ and $\vA\in \Fq^{m\times n}, X\in \Fq^{n}, U\in \Fq^m$ drawn uniformly and $E$ drawn uniformly from $[-\rho q, \rho q]$.
-Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ in the worst case.
+Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$hard, where $\epsilon = \ngl(n)$.
 \end{lemma}
@@
 
+For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
 \thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.
@@
 \begin{definition}
-Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m- \alpha)b$ and for all $W_i$ one of the following conditions is met:
+Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m - \alpha)b$ and for all $W_i$ one of the following conditions is met:
 \begin{itemize}

### 2013-02-15 CompFuzzExt.tex
Updates to theorems with HILL entropy

@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume there exists a PPT-distinguisher $D$ such that $\delta^D((\vA, \vA X+E), (\vA, U))>\epsilon$ for non-negligible $\epsilon$ and $\vA\in \Fq^{m\times n}, X\in \Fq^{n}, U\in \Fq^m$ drawn uniformly and $E$ drawn uniformly from $[-\rho q, \rho q]$.
-Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ in the worst case.
+Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$hard, where $\epsilon = \ngl(n)$.
 \end{lemma}
 
-We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).
-We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
-\begin{lemma}
-\label{lem:conversion to unpredictability}
-Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
-for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
+We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show there are many bits of $X$ that are unpredictable.
+This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
+We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
+\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
+\label{lem:many hardcore bits}
+Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
+Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
+Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
 \end{lemma}
+
+%\begin{lemma}
+%\label{lem:conversion to unpredictability}
+%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
+%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
+%\end{lemma}
 %\begin{lemma}
@@
 %\end{lemma}
-With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.
-We provide a formal description of our algorithm in the next section.
+With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} we can use the code-offset construction in \consref{cons:informal construction} and retain HILL entropy $k\log q$.  
 %\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}.
@@
 \begin{proof}
-Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:conversion to unpredictability}, efficiency follows by \lemref{lem:i t poly time}.
+Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
 \end{proof}
@@
 The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
-\vspace{.1in}
+%\vspace{.1in}
 \begin{theorem}
@@
 
-\section{\lemref{lem:conversion to unpredictability}}
-\label{sec:proof of unpred conversion}
-In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.
+%\section{\lemref{lem:conversion to unpredictability}}
+%\label{sec:proof of unpred conversion}
+%In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.
 %We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).
 Thus, we have the following claim:
-%\begin{claim}
-%\label{lem:unp of x and e}
-%Let $A, X, E$ be as above, then:
-%\begin{itemize}
-%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
-%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
-%\end{itemize}
-%\end{claim}
-%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
-%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
-%\begin{assumption}
-%\label{assume:entropy LWE}
-%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
+%%\begin{claim}
+%%\label{lem:unp of x and e}
+%%Let $A, X, E$ be as above, then:
+%%\begin{itemize}
+%%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
+%%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
+%%\end{itemize}
+%%\end{claim}
+%%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
+%%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
+%%\begin{assumption}
+%%\label{assume:entropy LWE}
+%%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
 If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.
-%\end{assumption}
-%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
-We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.
+%%\end{assumption}
+%%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
+%We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.
 This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
 We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
-\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-\label{lem:many hardcore bits}
-Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
+%\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
+%\label{lem:many hardcore bits}
+%Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
 Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
 Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
-\end{lemma}
-
-\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
-Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
+%\end{lemma}
+%
+%\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
+%Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
 Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.
@@
 To expand to $E$ we use the following claim:
-
-\begin{claim}
-Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
-\[
-H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
-\]
-\end{claim}
+%
 %\begin{claim}
-%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
+%Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
+%\[
+%H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
+%\]
 %\end{claim}
-%\begin{proof}
-%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
+%%\begin{claim}
+%%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
+%%\end{claim}
+%%\begin{proof}
+%%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
 Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
@@
 This completes the claim.
-%\end{proof}
-
-%\begin{claim}
-%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
-%\end{claim}
-%\begin{proof}
-%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
-%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.
+%%\end{proof}
+%
+%%\begin{claim}
+%%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
+%%\end{claim}
+%%\begin{proof}
+%%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
+%%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.
 Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
@@
 Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
-%This completes the claim.
-%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.
+%%This completes the claim.
+%%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.
 In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
-% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
+%% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
 Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
@@
 This completes the claim.
-%\end{proof}
-
-%\begin{claim}
-%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
-%\end{claim}
-%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.
+%%\end{proof}
+%
+%%\begin{claim}
+%%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
+%%\end{claim}
+%%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.
 This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.
 Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
-%
-%
-%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.
+%%
+%%
+%%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.
 By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.
 This completes the proof of \lemref{lem:conversion to unpredictability}.
-%\end{proof}
-\begin{proof}
-Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.
+%%\end{proof}
+%\begin{proof}
+%Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.
 We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.
@@
 Note that $\mathcal{E}$ occurs with probability $1-\gamma$.
-
-Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
-\begin{align*}
-\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
-&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
-&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
-\end{align*}
-Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
+%
+%Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
+%\begin{align*}
+%\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
+%&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
+%&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
+%\end{align*}
+%Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
 Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$.
 Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.
-
-We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
-\begin{enumerate}
-\item Input $(\vA, \vA X+E)$.
-\item Run $y\leftarrow C(\vA, \vA X+E)$.
-\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
-\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
-\end{enumerate}
-Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
+%
+%We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
+%\begin{enumerate}
+%\item Input $(\vA, \vA X+E)$.
+%\item Run $y\leftarrow C(\vA, \vA X+E)$.
+%\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
+%\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
+%\end{enumerate}
+%Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
 Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.
 Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
-\end{proof}
-
-The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
-%\begin{proof}[Proof of \clref{lem:unp of x and e}]
-%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
+%\end{proof}
+%
+%The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
+%%\begin{proof}[Proof of \clref{lem:unp of x and e}]
+%%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
 That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
 Define $I'$ by the following:
-%\begin{enumerate}
-%\item Input $(\vA, \vA X+E)$.
-%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%\item Output $z = \vA y - \vA X+E$.
-%\end{enumerate}
-%Note that $|I'|\approx |I|$.
-%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
-%\begin{align*}
-%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
-%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
-%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
-%\end{align*}
-%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
+%%\begin{enumerate}
+%%\item Input $(\vA, \vA X+E)$.
+%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
+%%\item Output $z = \vA y - \vA X+E$.
+%%\end{enumerate}
+%%Note that $|I'|\approx |I|$.
+%%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
+%%\begin{align*}
+%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
+%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
+%%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
+%%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
+%%\end{align*}
+%%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
 That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((E, \vA, \vA X+E), (Y, \vA, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
 Define $I'$ by the following:
-%\begin{enumerate}
-%\item Input $(A, \vA X+E)$.
-%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
-%\item Output $z = \vA^{-1}(\vA X+E-y)$.
-%\end{enumerate}
-%Note that $|I'|\approx |I|$.
+%%\begin{enumerate}
+%%\item Input $(A, \vA X+E)$.
+%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
+%%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
+%%\item Output $z = \vA^{-1}(\vA X+E-y)$.
+%%\end{enumerate}
+%%Note that $|I'|\approx |I|$.
 For sufficient parameter sizes the probability of $A^{-1}$ not existing is negligible.
@@
 Then one has the following~(conditioned on the event that $\vA^{-1}$ exists):
-%\begin{align*}
-%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
-%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
-%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
-%\end{align*}
-%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
+%%\begin{align*}
+%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
+%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
+%%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
+%%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
+%%\end{align*}
+%%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
+%%\end{proof}
+%
 %\end{proof}
-
-\end{proof}
 

### 2013-02-15 CompFuzzExt.tex
defining computational conductor

@@
 
-\subsection{Defining Secure Sketches using unpredictability entropy}
+\subsection{Defining Robust Computational Conductors}
 \label{sec:unp secure sketch}
@@
 The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
-However, if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
+However, our sketch outputs a new random variable, this problem does not occur.
+Instead of building a computational sketch, we will build a computational conductor.
+We review the definition of a computational conductor from~\cite{KanukurthiR09}:
+\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
+The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
+\begin{enumerate}
+\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
+\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+\end{definition}
+%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
 We begin by defining unpredictability entropy:
 
-\begin{definition}
-\label{def:unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
-\[
-\Pr[C(Z) = Y ] \leq 2^{-k}
-.\]
-\end{definition}
-We now provide a definition of a computational secure sketch using unpredictability entropy:
+%\begin{definition}
+%\label{def:unp entropy}
+%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+%\[
+%\Pr[C(Z) = Y ] \leq 2^{-k}
+%.\]
+%\end{definition}
+We now provide a definition of a robust computational sketch using unpredictability entropy:
 \begin{definition}\label{def:comp secure sketch}
-An $(\mathcal{M},m, \tilde{m}, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
+An $(\mathcal{M},m, \tilde{m}, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t, \epsilon)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
 \begin{enumerate}
@@
 \item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\rec(w',SS(w))=w$ and \rec runs in expected time $s_{rec}$.
+The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \epsilon$ and \rec runs in expected time $s_{rec}$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ is unpredictable given $\sketch(W)$.
-That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
+\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
+That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
@@
 We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational secure sketch that meets \defref{def:comp secure sketch}.
+In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a robust computational conductor that meets \defref{def:comp secure sketch}.
 We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.

### 2013-02-15 CompFuzzExt.tex
defining computational conductor

@@
 
-\subsection{Defining Robust Computational Conductors}
+\subsection{Defining Noisy Computational Conductors}
 \label{sec:unp secure sketch}
@@
 Instead of building a computational sketch, we will build a computational conductor.
-We review the definition of a computational conductor from~\cite{KanukurthiR09}:
-\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
-The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
-\begin{enumerate}
-\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
-\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-\end{definition}
+We adapt the definition of a noisy conductor from~\cite{KanukurthiR09} to the computational setting:
+%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
+%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
+%\begin{enumerate}
+%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
+%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
+%\end{enumerate}
+%\end{definition}
 %We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
@@
 %\end{definition}
-We now provide a definition of a robust computational sketch using unpredictability entropy:
+%We now provide a definition of a robust computational sketch using unpredictability entropy:
 \begin{definition}\label{def:comp secure sketch}
-An $(\mathcal{M},m, \tilde{m}, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t, \epsilon)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
+A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
 \begin{enumerate}
@@
 \item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \epsilon$ and \rec runs in expected time $s_{rec}$.
+The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
@@
 \end{enumerate}
-We say a construction is \emph{lossless} if $m=\tilde{m}$ and we omit the parameter $\tilde{m}$.
+We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
+If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
 \end{definition}
-We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a robust computational conductor that meets \defref{def:comp secure sketch}.
+%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
+In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.
 We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.
@@
 with 
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
 \end{theorem}
@@
 %\]
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{2d+3} \log n)$.
 \end{theorem}

### 2013-02-15 trunk/CompFuzzExt.tex
sketches -> conductor

@@
 On the positive side, we show that a different relaxation of the security requirement can in fact lead to a \emph{lossless} construction of secure sketches, in which the knowledge of $s$ does not reduce entropy of $w$ (see Theorem~%s~%\ref{thm:lossless secure sketch} and
-~\ref{thm:lossless secure sketch log})).
+~\ref{thm:lossless secure conductor log})).
 This relaxation requires that $w$ have high \emph{unpredictability} entropy conditioned on $s$ (unpredictability  entropy is a computational notion originally defined in \cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
@@
 
-\subsection{Defining Secure Sketches using unpredictability entropy}
+\subsection{Defining Noisy Computational Conductors}
 \label{sec:unp secure sketch}
@@
 The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
-However, if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
+However, our sketch outputs a new random variable, this problem does not occur.
+Instead of building a computational sketch, we will build a computational conductor.
+We adapt the definition of a noisy conductor from~\cite{KanukurthiR09} to the computational setting:
+%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
+%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
+%\begin{enumerate}
+%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
+%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
+%\end{enumerate}
+%\end{definition}
+%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
 We begin by defining unpredictability entropy:
 
-\begin{definition}
-\label{def:unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
-\[
-\Pr[C(Z) = Y ] \leq 2^{-k}
-.\]
-\end{definition}
-We now provide a definition of a computational secure sketch using unpredictability entropy:
+%\begin{definition}
+%\label{def:unp entropy}
+%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+%\[
+%\Pr[C(Z) = Y ] \leq 2^{-k}
+%.\]
+%\end{definition}
+%We now provide a definition of a robust computational sketch using unpredictability entropy:
 \begin{definition}\label{def:comp secure sketch}
-An $(\mathcal{M},m, \tilde{m}, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
+A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
 \begin{enumerate}
@@
 \item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\rec(w',SS(w))=w$ and \rec runs in expected time $s_{rec}$.
+The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ is unpredictable given $\sketch(W)$.
-That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
+\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
+That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
-We say a construction is \emph{lossless} if $m=\tilde{m}$ and we omit the parameter $\tilde{m}$.
+We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
+If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
 \end{definition}
-We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational secure sketch that meets \defref{def:comp secure sketch}.
+%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
+In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.
 We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.
 
-\section{Lossless sketch based on \class{LWE}}
+\section{Lossless conductor based on \class{LWE}}
 \label{sec:fuzzyCompExt}
@@
 \item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
-\item Set $X' = \mathcal{I}_t(\vA, \vect{D}) $. 
-\item Output $w = \vect{C}-\vA X'$.
+\item Let $X' = \mathcal{I}_t(\vA, \vect{D})$\\
+Set $X'_{n/2}$ be the first half bits of $X'$.		 
+\item Output $w = X'_{n/2}$.
 \end{enumerate}
@@
 We describe conditions for efficient decoding in \secref{sec:time main construction}.
-Finally, in \secref{sec:lossless sketch} we describe parameter settings where our construction yields a lossless secure sketch.\lnote{revise after going through the rest}.
+Finally, in \secref{sec:lossless conductor} we describe parameter settings where our construction yields a lossless secure sketch.\lnote{revise after going through the rest}.
 
@@
 
-We cannot immediately adapt the construction in \consref{cons:informal construction} to the LWE problem.
-Standard formulations of LWE require the error term to come from the discretized Gaussian distribution.
+We cannot immediately adapt the construction in \consref{cons:informal construction} to the $\LWE$ problem.
+Standard formulations of $\LWE$ require the error term to come from the discretized Gaussian distribution.
 %\subsection{LWE with uniform errors}
 %\label{subsec:LWE uniform error}
-Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of LWE with the uniform distribution over an interval reduces to the security of LWE where the noise comes from the discretized Gaussian.
-This allows us to directly encode $w$ as the error term in an LWE problem by splitting it properly into $m$ blocks.
+Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over an interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian.
+This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it properly into $m$ blocks.
 %As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.
@@
 
-We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).
-We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
-\begin{lemma}
-\label{lem:conversion to unpredictability}
-Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
-for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
+We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show there are many bits of $X$ that are unpredictable.
+This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
+We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
+\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
+\label{lem:many hardcore bits}
+Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
+Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
+Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
 \end{lemma}
+
+%\begin{lemma}
+%\label{lem:conversion to unpredictability}
+%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
+%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
+%\end{lemma}
 %\begin{lemma}
@@
 
-\subsection{Lossless Secure Sketch}
-\label{sec:lossless sketch}
-We now state a setting of parameters that yields a lossless sketch.
+\subsection{Lossless Conductor}
+\label{sec:lossless conductor}
+We now state a setting of parameters that yields a lossless conductor.
 
@@
 \begin{theorem}
-\label{thm:lossless secure sketch log}
+\label{thm:lossless secure conductor log}
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
@@
 Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.
+If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
@@
 with 
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
 \end{theorem}
 \begin{proof}
-Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:conversion to unpredictability}, efficiency follows by \lemref{lem:i t poly time}.
+Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
 \end{proof}
@@
 For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
-\thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.
+\thref{thm:lossless secure conductor log} shows that a noisy computational conductor can be built without incurring any entropy loss.
 This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.
@@
 In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.
-Showing security of a computational secure sketch for arbitrary high min-entropy distributions is an open problem.
+Showing security of a noisy computational conductor for arbitrary high min-entropy distributions is an open problem.
 First we recall the notion of a symbol fixing source~(from~\cite{KZ07}):
@@
 
-\thref{thm:blockLWE} allows us to construct a computational secure sketch from block-fixing sources:
+\thref{thm:blockLWE} allows us to construct a noisy computational conductor from block-fixing sources:
 
@@
 Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.
-There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.
+There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
@@
 
-Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
+Recall, we defined noisy computational conductor using unpredictability entropy~(\defref{def:comp secure sketch}).
 It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
@@
 \begin{lemma}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, s_{sec}, s_{sketch}, s_{rec}, t)$-computational secure sketch, and let $\rext:\mathcal{M}\times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, s_{sec}, s_{sketch}, s_{rec}, t)$-noisy computational conductor, and let $\rext:\mathcal{M}\times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
@@
 In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure sketch log} we give lossless sketches from a security parameter $n$ and an error $t$.
+In \thref{thm:lossless secure conductor log} we give lossless sketches from a security parameter $n$ and an error $t$.
 In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
@@
 We will set $g = 2$, that is our sketch will output the first half of $X$.
-This is the setting of parameters in \thref{thm:lossless secure sketch log}.
+This is the setting of parameters in \thref{thm:lossless secure conductor log}.
 

### 2013-02-15 CompFuzzExt.tex
New section 6

@@
 \begin{definition}\label{def:comp secure sketch}
-A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
+A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
 \begin{enumerate}
@@
 
-\section{Lossless sketch based on \class{LWE}}
+\section{Lossless conductor based on \class{LWE}}
 \label{sec:fuzzyCompExt}
@@
 \section{Computational Fuzzy Extractors}
-In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using a paradigm similar to \lemref{lem:fuzzy ext construction}.
+In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.
 We begin with a formal definition of a computational fuzzy extractor:
@@
 \begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-An $(\mathcal{M}, m, \ell, t, s_{rec}, s_{sec}, \epsilon)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
+An $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
 \begin{itemize}
@@
 The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\rep( w', P) = R$.
-Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
+%%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
 If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
@@
 \end{itemize}
+We say that $\gen, \rep$ is $(\epsilon, s_{sec})$ hard with error $\delta$.
 \end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
+Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
 
@@
 However, the entropy loss due to error correction may mean there is not be enough remaining bits to run a pseudorandom generator.
-Depending on the application, it may be appropriate to make the sketch and/or extractor computational.
-
-Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
+Depending on the application, it may be appropriate to make the noise correction procedure and/or extractor computational.
+
+Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
+\begin{lemma}
+Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
+Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.
+Let, $s' = s_{sec}-s_{ext}$, then
+$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
+\end{lemma}
+%  the same paradigm from 
+%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
 It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
 However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).
-\begin{definition}
-An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
+%\begin{definition}
+%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
 Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
-\end{definition}
-\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-\label{lem:unp extraction} 
-Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+%\end{definition}
+%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+%\label{lem:unp extraction} 
+%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
 Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-\end{lemma}
+%\end{lemma}
 We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
 \begin{lemma}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, s_{sec}, s_{sketch}, s_{rec}, t)$-computational secure sketch, and let $\rext:\mathcal{M}\times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-noisy computational conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
+Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
+Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
+\end{lemma}
+%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
-\begin{itemize}
-\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
-\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
-\end{itemize}
-\end{lemma}
-\begin{proof}
-Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
-\end{proof}
-
+%\begin{itemize}
+%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
+%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
+%\end{itemize}
+%\end{lemma}
+%\begin{proof}
+%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
+%\end{proof}
+%
 %For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.

### 2013-02-15 trunk/CompFuzzExt.tex
Small typo changes

@@
 Set $X'_{n/2}$ be the first half bits of $X'$.		 
-\item Output $w = X'_{n/2}$.
+\item Output $X'_{n/2}$.
 \end{enumerate}
@@
 However, the entropy loss due to error correction may mean there is not be enough remaining bits to run a pseudorandom generator.
-Depending on the application, it may be appropriate to make the sketch and/or extractor computational.
-
-Recall, we defined noisy computational conductor using unpredictability entropy~(\defref{def:comp secure sketch}).
+Depending on the application, it may be appropriate to make the noise correction procedure and/or extractor computational.
+
+Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
+\begin{lemma}
+Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
+Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.
+Let, $s' = s_{sec}-s_{ext}$, then
+$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
+\end{lemma}
+%  the same paradigm from 
+%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
 It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
 However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).
-\begin{definition}
-An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
+%\begin{definition}
+%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
 Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
-\end{definition}
-\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-\label{lem:unp extraction} 
-Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+%\end{definition}
+%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+%\label{lem:unp extraction} 
+%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
 Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-\end{lemma}
+%\end{lemma}
 We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
 \begin{lemma}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, s_{sec}, s_{sketch}, s_{rec}, t)$-noisy computational conductor, and let $\rext:\mathcal{M}\times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-noisy computational conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
+Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
+Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
+\end{lemma}
+%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
-\begin{itemize}
-\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
-\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
-\end{itemize}
-\end{lemma}
-\begin{proof}
-Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
-\end{proof}
-
+%\begin{itemize}
+%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
+%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
+%\end{itemize}
+%\end{lemma}
+%\begin{proof}
+%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
+%\end{proof}
+%
 %For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
@@
 In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure conductor log} we give lossless sketches from a security parameter $n$ and an error $t$.
+In \thref{thm:lossless secure conductor log} we give lossless conductors from a security parameter $n$ and an error $t$.
 In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.

### 2013-02-15 CompFuzzExt.tex
sketches -> conductor

@@
 \label{sec:unp secure sketch}
-In \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best information-theoretic sketches.
+In \secref{sec:imp HILL sketch}, we showed that defining a noisy computational conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
 The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
@@
 In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.
-We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.
+We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
 
@@
 \label{lem:i t poly time}
-Let $\vA, \vA X+W$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).
+Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance that is a unique witness relation~(except with negligible probability).
 Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
@@
 For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$.
-The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
+The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
 \end{problem}

### 2013-02-15 trunk/CompFuzzExt.tex
Adding error to def of comp fuzz ext

@@
 \label{sec:preliminaries}
-We begin by recalling a few basic entropy definitions.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
+We begin by recalling a few basic definitions.
+For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.
+The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
 %the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
@@
 \item Let $X' = \mathcal{I}_t(\vA, \vect{D})$\\
-Set $X'_{n/2}$ be the first half bits of $X'$.		 
-\item Output $X'_{n/2}$.
+Set $X'_{1,..., n}$ be the first half bits of $X'$.		 
+\item Output $X'_{1,...,n}$.
 \end{enumerate}
@@
 \item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\rep( w', P) = R$.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
 %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
@@
 \end{itemize}
-We say that $\gen, \rep$ is $(\epsilon, s_{sec})$ hard with error $\delta$.
+We say that $\gen, \rep$ is $(\epsilon, s_{sec})$-hard with error $\delta$.
 \end{definition}

### 2013-02-15 CompFuzzExt.tex
sketches -> conductor
Removing yao and unpredictability entropy

@@
 Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) \approx \Hoo(W)$.
+In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) \approx \Hoo(W)$.
 Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.
@@
 
-We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show there are many bits of $X$ that are unpredictable.
+We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
 This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
@@
 \section{Background}
-\subsection{Notions of Computational Entropy}
-\label{sec:notionsEntropy}
-In this sections we provide some further definitions of computational entropy.
+%\subsection{Notions of Computational Entropy}
+%\label{sec:notionsEntropy}
+%In this sections we provide some further definitions of computational entropy.
 HILL entropy is defined in \secref{sec:defCompFuzzyExtractors}.
@@
 Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
-\begin{definition}
-\label{def:yao entropy}
-For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
-\[
-\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
-\]
-\end{definition}
-It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.
+%\begin{definition}
+%\label{def:yao entropy}
+%For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
+%\[
+%\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
+%\]
+%\end{definition}
+%It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.
 In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
@@
 This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
-Unpredictability entropy is a notion between HILL and Yao entropy:
-\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
-\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
-\]
-\end{lemma} 
-\subsection{Unique Witness Relations}
+%Unpredictability entropy is a notion between HILL and Yao entropy:
+%\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
+%\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
+%\]
+%\end{lemma} 
+%\subsection{Unique Witness Relations}
 
@@
 \item $m$: The size of each number of samples in the LWE instance.  
-\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:conversion to unpredictability}).
+\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
 \end{itemize}

### 2013-02-15 trunk/CompFuzzExt.tex
working on 3.1

@@
 \label{sec:preliminaries}
-We begin by recalling a few basic definitions.
-For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.
-The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
+For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
 %the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
-and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite{DBLP:journals/siamcomp/DodisORS08}.  
+and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
 %The {\em collision probability} of  $X$ is 
@@
 For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
-We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized $\{0,1\}$ distinguishers of size at most $s_{sec}$.
+We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
 For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
+$U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
 
@@
 We now recall definitions and lemmas from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1, 8]{DBLP:journals/siamcomp/DodisORS08}.
+al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.
@@
 \begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
-An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
+An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
 \begin{enumerate}
@@
 \item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that if $\dis(w,w')\leq t$ and $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
@@
 \end{definition}
-A fuzzy extractor can be produced from a \emph{average-case randomness extractor} %(all randomness extractors are average-case extractors with a small loss, see~\cite[Chapter 6]{vadhan2012}) 
-and a \emph{secure sketch}.  
-An average-case extractor is simply a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):
-
-\begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-An extractor $\ext$ is a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), Y), U_m\times
-U_d \times Y) \le \epsilon$.
-\end{definition}
 
@@
 \label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t, \epsilon)$-\emph{approximately correct secure sketch} is a pair of randomized procedures, ``sketch'' (\sketch) and ``recover'' (\rec), with the following properties:
+An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' (\sketch) and ``recover'' (\rec), with the following properties:
 \begin{enumerate}
@@
 \item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',SS(w))=w]\geq 1-\epsilon$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
 \item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
-That is, $\Hav(W|SS(W))\geq \tilde{m}$.
+That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
 A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
-If $\epsilon=0$ we omit $\epsilon$ and say that $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch}.
 \end{definition}
-For an approximately correct secure sketch we assume that errors are drawn independently of $\sketch(w)$.
-If the error pattern between $w$ and $w'$ depends on $\sketch(w)$ there is no guarantee about the probability of correctness.
+
+Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
+
+A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
+An average-case extractor is simply a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):
+
+\begin{definition}
+Let $\chi_1$, $\chi_2$ be finite sets.
+A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^m$ a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
+of random variables $X, Y$ over $\chi_1, \chi_2$ such that
+$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), U_d, Y), U_m\times
+U_d \times Y) \le \epsilon$.
+\end{definition}
+
 %In \secref{sec:defCompFuzzyExtractors} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch?
@@
 %\end{definition}
-A fuzzy extractor is usually formed by combining a randomness extractor with a secure sketch.
+
 \begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
 \label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(for $(r, x)$ drawn from the uniform distribution):
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.
+Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
 \begin{itemize}
-\item $\gen(w; r, x):$ set $P=(\sketch(w; r), x), R=\ext(w;x)$, and output $(R,P)$.
+\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
 \item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
@@
 \begin{definition}
-Let $(X, Y)$ be a pair of random variables.  $X$ has 
-\emph{conditional HILL entropy} at least $k$ conditioned on $Y$,
-denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Y)\geq k$ if there exists a collection of
-distributions $Z_y$ for each $y\in Y$, giving rise to a joint distribution
-$(Z, Y)$, such that $\tilde{H}_\infty(Z|Y)\geq k$ and for all (randomized, binary output) circuits $D$ of size $s_{sec}$, $\delta^D((X, Y),(Z,Y))\leq \epsilon$.
+Let $(X, Z)$ be a pair of random variables.  $X$ has 
+\emph{conditional HILL entropy} at least $k$ conditioned on $Z$,
+denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Z)\geq k$ if there exists a collection of
+distributions $Y_z$ for each $z\in Z$, giving rise to a joint distribution
+$(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((X, Z),(Y,Z))\leq \epsilon$.
 \end{definition}
@@
 Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
-However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches can't perform much better than the information-theoretic ones.
+However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones.
 
@@
 \label{sec:imp HILL sketch}
-It seems natural to replace a sketch that retains information theoretic entropy with a sketch that retains HILL entropy.
-Then the paradigm of secure sketch and average case randomness extractor could be used.
-However, we show that using this definition it is impossible to beat information theoretic bounds on secure sketches.
-We omit formal definitions for the moment and recall the two informal properties we seek:
-\begin{itemize}
-\item \emph{Correctness}: if $\dis(w, w')\leq t$ then $\rec(w', \sketch(w)) = w$.
-\item \emph{Security}: For all $W$ where $H_\infty(W)\geq m$, $H^\hill_{\epsilon, s}(W|\sketch(W))  = \tilde{m}$.
-\end{itemize}
-%We will concentrate on the case where $gap = m-\tilde{m}=0$ however, any setting where  $gap$ is better than the best information theoretic sketch is still a meaningful result.
-% As before, we desired $\rec$ to be efficiently computable.
-We start with this stronger definition to show the difficulty of constructing such an object.
-
-Unfortunately, we will show if $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$ this implies an error correcting code with approximately $2^{\tilde{m}}$ points.
-We provide intuition for the argument below and then present the formal argument.
+Suppose we redefine secure sketches using HILL entropy: that is, an \emph{$(\epsilon,s_{sec})$-HILL-entropy secure sketch} is the same object as in Definition~\ref{def:secure sketch}, but the security requirement is replaced with  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
+Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches).
+For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
+In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.
+
+The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
 Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.
-This means in order for $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$, there must be a distribution $Y$ where $\Hoo(Y)\geq \tilde{m}$ such that $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.
+In order to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hoo(Y)\geq \tilde{m}$ \lnote{uncondtional?}; this distribution must be indistinguishable from \lnote{which one}, and, in particular, such that $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$ \lnote{explain why}.
 This means the points in $Y$ form an error correcting code and $\rec$ is an efficient decoder.
 We can then use standard arguments to turn this code into an information theoretic sketch.
-This means lower bounds on the entropy loss of an information theoretic sketch must apply.
-There are several technical conditions required to make this intuition formal, we present them below.
-%any function that is able to recover correctly on a large space is an decoder for an error correcting code formed by that space.
-If there is a distribution $Y$ with many points such that $\rec(y', \sketch(w)) =y\in Y$ when $\dis(y, y')\leq t$.
-Then $\rec$ is a decoder for the error correcting code formed by $Y$.
-% and make no assumption about the behavior of $\rec $ outside of this ball.
-The intuition is quite simply, on a point $w\leftarrow W$, the \rec oracle will always return $w$ within the $B_t(w)$.
-If $W|\sketch(W)$ is indistinguishable from $Y|\sketch(W)$ then the $\rec$ oracle must also correct for points in $Y$.
-However, this implies a code~(the points in $Y$) with $\rec$ as an efficient decoding algorithm.
-%\subsubsection{The Uniform Distribution}
-%and extend to an arbitrary high-entropy distribution.  
-%We begin by showing that any given no distribution $W$ can be indistinguishable from the uniform distribution given a sketch.
-%We need two technical requirements on our metric space: 1) there is an efficient algorithm to sample neighbors 2) each point is regular~(has the same number of neighbors).
-These requirements hold for several natural metric spaces including Hamming and symmetric difference metrics.
-%The only other requirement we make is for the distribution and its neighborhood to be efficiently samplable.
-%\begin{definition}
-%A distribution $W$ is $s-$\emph{efficiently-samplable} if there exists a randomized circuit of size at most $s$ that outputs samples according to $W$.
-%Furthermore, we say $W$ is \emph{efficiently-samplable} if there exists a randomized circuit of polynomial size that outputs samples according to $W$.
-%\end{definition}
-%We will be working with a metric space $\mathcal{M}, d$.  We will need to efficiently sample nearby points in the metric space.
-We assume that sampling a random neighbor of a point is efficient:
+\lnote{this intuition is confusing, esp.
+given notational inconsistencies of all the capital letters with what comes above and below}
+
+We need the following technical condition to make this intuition precise: 
+we assume that sampling a random neighbor of a point is efficient.
 \begin{definition}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit, $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.
+We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.
 %That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
@@
 %\]
-Furthermore, there is a procedure that outputs a random point of distance at most $t$.  For convenience we denote this procedure by $\sample(X)$.
 \end{definition}
 We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.
-While we could consider metric spaces where balls only contain their center, this is not very interesting in the context of fuzzy extractors~(as \gen can always output the empty string for $P$).
+While we could consider metric spaces where balls only contain their center, secure sketches are trivial in this context.
 
@@
 
-Finally, we will dealing with an arbitrary secure sketch that only needs to satisfy the correctness property of a secure sketch~(see \defref{def:secure sketch}).
+\ignore{
+Finally, we will 
+dealing with an arbitrary secure sketch that only needs to satisfy the correctness property of a secure sketch~(see \defref{def:secure sketch}).  \lnote{why do we need this definition?}
 
@@
 \end{definition}
+}
 
@@
 
-We show that any recovery functionality that retains high HILL entropy implies a information theoretic secure sketch.
-We begin by reviewing definitions of Shannon codes~\cite{shannon1949mathematical}:
+We review definitions of Shannon codes~\cite{shannon1949mathematical}:
 \begin{definition}
 Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t)) \neq c]<\epsilon$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$.
+To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
 \end{definition}
-This is a slightly nonstandard formulation, we only require the code to correct exactly $t$ errors\footnote{In the standard formulation, the code must correct up to $t$ errors.
+This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$.
+\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.
 For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
 However, we work with an arbitrary recover functionality that is not necessarily monotone.}.
-Shannon codes work for all codewords, we can also consider a formulation that works for an ``average'' codeword.
+
+Shannon codes work for all codewords.
+We can also consider a formulation that works for an ``average'' codeword.
+\lnote{notation here is messed up: why are we using $W$ for the code and $X$ for the input distribution in theorem 3.6?}
 \begin{definition}
-Let $W$ be a distribution over space $\mathcal{M}$.  We say that $W$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that 
-$\Pr_{w\leftarrow W}[\rec(\sample(w, t)) \neq w]<\epsilon$.
+Let $W$ be a distribution over space $\mathcal{M}$.  We say that $W$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
+$\Pr_{w\leftarrow W}[\rec(\sample(w, t')) \neq w]<\epsilon$.
 \end{definition}
-An average error Shannon code is convertible to a (maximal error)~Shannon code with a small loss.
-We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements}~(we provide a proof in \secref{sec:proof of average to maximal error}):
+An average error Shannon code is convertible to a maximal error Shannon code with a small loss.
+We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
 \begin{lemma}
@@
 Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
-There is a set $W'$ where $|W'|\ge2^{k-1}$ and $W'$~(drawing a codeword uniformly) is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
+There is a set $W'$ with $|W'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
 \end{lemma}
 
-With this conversion we can show a surprising result: recover functionalities that retain HILL entropy imply Shannon error correcting codes~(proof in \secref{sec:proof of thm sketch implies code}).
+We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
 Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an $(s_{rec}, t)$-recover functionality over $\mathcal{M}$.
-If $H^{\hill}_{\epsilon, s_{sec}}(X|SS(X))\geq k$ then there exists $x$ and a set $W'$ where $|W'|\geq 2^{k-1}$ such that for all $1\leq t'\leq t$, $W'$ is a $(t', 2\epsilon)$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$ for $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$.
+Let $(\sketch, \rec)$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{M}, m, k, t)$-secure sketch \lnote{why did we switch from $\tilde{m}$ to $k$?} with error $\delta$.
+Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
+Then there exists $x$ and a set $W'$ with $|W'|\geq 2^{k-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 
-We can use techniques from information reconciliation~\cite{smith2007scrambling} and privacy amplification~\cite{bennett1988privacy} to convert any  Shannon code into an information theoretic security sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}):
+It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.
+The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
+The formal statement is in the following Lemma.
 \begin{lemma}
 \label{lem:shannon to sketch}
-Let $t$ be a parameter.
-Let $\mathcal{C}$ over $\{0,1\}^n$ be a set such that for all $1\leq t'\leq t$, $\mathcal{C}$ is a $(t', \epsilon)$ Shannon code with recovery procedure $\rec'$.
-Let $W$ be a distribution with $\Hoo(W)\geq k$.
-Define the following procedures
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\sketch}
-\begin{enumerate}
-\item Input $w\leftarrow W$.
-\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
-\item Sample $c\leftarrow \mathcal{C}$.
-\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
-\item Output $p = x \oplus c, \pi$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rec}
-\begin{enumerate}
-\item Input $(w', p, \pi)$
-\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
-\item Compute $c' = p \oplus x'$.
-\item Compute $c = \rec'(c)$.
-\item Output $p\oplus c$.
-\\
-\end{enumerate}
-\end{minipage} 
-\end{tabular}
-\end{center}
-Then $(\sketch, \rec)$ is a $(\{0,1\}^n, k, k-(n-\log |\mathcal{C}|), t, \epsilon)$ approximately correct secure sketch. 
+For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.% with recovery procedure $\rec'$.
+%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
+%
+% Define the following procedures
+%\lnote{I think this description is buggy}
+%\begin{center}
+%\begin{tabular}{c|c}
+%\begin{minipage}{3in}
+%\textbf{\sketch}
+%\begin{enumerate}
+%\item Input $w\leftarrow W$.
+%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
+%\item Sample $c\leftarrow \mathcal{C}$.
+%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
+%\item Output $p = x \oplus c, \pi$.
+%\end{enumerate}
+% \end{minipage} &
+%\begin{minipage}{3in}
+%\textbf{\rec}
+%\begin{enumerate}
+%\item Input $(w', p, \pi)$
+%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
+%\item Compute $c' = p \oplus x'$.
+%\item Compute $c = \rec'(c)$.
+%\item Output $p\oplus c$.
+%\\
+%\end{enumerate}
+%\end{minipage} 
+%\end{tabular}
+%\end{center}
+Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
 %satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
@@
 %\end{construction}
-Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives our main negative result.
-Any recover functionality that retains HILL entropy implies an information theoretic sketch:
+Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
 \begin{corollary}
 \label{cor:rec yields sketch}
-Let $(\sketch', \rec')$ be a $(s_{rec}, t)$-recover functionality over $\{0,1\}^n$ such that $H^{\hill}_{\epsilon, s_{sec}}(X | \sketch'(X))\geq k$.
-If $s_{sec}=\Omega(t(s_{rec} + n))$,  then for all $W$ with $\Hoo(W)\geq m$ there exists a $(\{0,1\}^n, m, m-(n-k+1), 2\epsilon)$ (information-theoretic) approximately correct secure sketch.
+Let $Z$ be an alphabet.
+Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
+If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-1,t)$ (information-theoretic) secure sketch with error
+$2(\epsilon+\delta)$. 
 %Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
@@
 \end{corollary}
-\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the feasibility of constructing $(\sketch, \rec)$.
-Several steps in \thref{thm:impSketchArbitraryW} are not constructive so there may not be an efficient procedure for $\sketch$.
-
-\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.
+\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
+
+%\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.
 Unfortunately, we have lower bounds for the entropy drop for information-theoretic sketches:
 
-\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
-\label{prop:lower bound entropy drop}
-For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.
+%\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
+%\label{prop:lower bound entropy drop}
+%For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.
 Here $h(\cdot)$ is the binary entropy function.
-\end{proposition}
-
-Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.
+%\end{proposition}
+
+%Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.
 This entropy drop is tied to the Shannon capacity.
@@
 \begin{proof}
-Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that 
+Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that for all $t'\le t$
 \[
-\sum_{w\in W} \Pr[W=w]\Pr[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]\leq \epsilon.
+\sum_{w\in W} \Pr[W=w]\Pr[ w'\leftarrow \sample (w, t') \wedge \rec(w') \neq w]\leq \epsilon.
 \]
-For $w$ denote by $\epsilon_w = \Pr[w'\leftarrow \sample(w) \wedge \rec(w') \neq w]$.  Then by Markov inequality:
+For $w$ denote by $\epsilon_w = \Pr[w'\leftarrow \sample(w, t') \wedge \rec(w') \neq w]$.  Then by Markov inequality:
 \[
@@
 \]
-Now suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]> 2\epsilon$.
+Now suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]> 2\epsilon$.
 This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.
@@
 \begin{align*}
-\Pr_{w\in W}[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w) \wedge \rec(w') \neq w]\\
+\Pr_{w\in W}[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]\\
 &\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
@@
 \begin{proof}
-Let $\mathcal{M},d$ be a metric space that is $(s_{neigh},t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an $(s_{rec}, t)$-arbitrary recover functionality over $\mathcal{M}$.
-Let $X$ be an arbitrary distribution.
-Let $W$ be a distribution over $\mathcal{M}$ with $\Hoo(W)\geq k$ such that
+  Let $X$ be an arbitrary distribution of minentropy $m$.  Let $W$ be a distribution over $\mathcal{M}$ with $\Hoo(W)\geq k$ such that 
 \[ 
-\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.
+\delta^{\mathcal{D}_s}((X, \sketch(X)), (W, \sketch(X)))<\epsilon.
 \]  
-For all $D$ of size at most $s = O(t(s_{neigh}+s_{rec}))$.  One such $W$ must exist by the definition of conditional HILL entropy.
+where  $s = O(t(s_{neigh}+s_{rec}))$.  One such $W$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \item For all $1\leq t'\leq t$: 
-\subitem Sample $z'\leftarrow \sample(z, t')$.
+\subitem  $z'\leftarrow \sample(z, t')$.
 \subitem If $\rec(z', s) \neq  z$ output $0$.
@@
 \end{enumerate}
-  As before we know that $D(X, \sketch(X)) = 1$.  Since 
-$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(W, SS(X))>1-\epsilon$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
+  By correctness of the sketch $ \expe D(X, \sketch(X)) \ge 1-\delta$.  Since 
+$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(W, SS(X))>1-\epsilon-\delta$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
 %This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
 Thus, for all $t', 1\leq t'\leq t$ on a random $w$
-\[ \Pr_{w\leftarrow W}[w'\leftarrow \sample(w, t') \wedge \rec(w', \sketch(x')) = w]\geq 1-\epsilon.\]  
+\[ \Pr_{w\leftarrow W}[w'\leftarrow \sample(w, t') \wedge \rec(w', \sketch(x')) = w]\geq 1-\epsilon-\delta.\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus, for all $1\leq t'\leq t$, $W$ is a $(t', \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.
-The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
+Thus,  $W$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
 \end{proof}

### 2013-02-15 CompFuzzExt.tex
Updates to section 3 and associated proofs

@@
 Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
-However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches can't perform much better than the information-theoretic ones.
-
-Instead, in \secref{sec:unp secure sketch}, we define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
-In particular, in \secref{sec:comp fuzzy extractors}, we show a natural construction of computational fuzzy extractors from secure sketches defined using unpredictability.
+However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones.
+
+Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
+This object is the computational analogue of a noisy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
+  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from noisy computational conductors.
 %The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.
@@
 \label{sec:imp HILL sketch}
-It seems natural to replace a sketch that retains information theoretic entropy with a sketch that retains HILL entropy.
-Then the paradigm of secure sketch and average case randomness extractor could be used.
-However, we show that using this definition it is impossible to beat information theoretic bounds on secure sketches.
-We omit formal definitions for the moment and recall the two informal properties we seek:
-\begin{itemize}
-\item \emph{Correctness}: if $\dis(w, w')\leq t$ then $\rec(w', \sketch(w)) = w$.
-\item \emph{Security}: For all $W$ where $H_\infty(W)\geq m$, $H^\hill_{\epsilon, s}(W|\sketch(W))  = \tilde{m}$.
-\end{itemize}
-%We will concentrate on the case where $gap = m-\tilde{m}=0$ however, any setting where  $gap$ is better than the best information theoretic sketch is still a meaningful result.
-% As before, we desired $\rec$ to be efficiently computable.
-We start with this stronger definition to show the difficulty of constructing such an object.
-
-Unfortunately, we will show if $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$ this implies an error correcting code with approximately $2^{\tilde{m}}$ points.
-We provide intuition for the argument below and then present the formal argument.
+Suppose we redefine secure sketches using HILL entropy: that is, an \emph{$(\epsilon,s_{sec})$-HILL-entropy secure sketch} is the same object as in Definition~\ref{def:secure sketch}, but the security requirement is replaced with  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
+Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches).
+For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
+In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.
+
+The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
 Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.
-This means in order for $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$, there must be a distribution $Y$ where $\Hoo(Y)\geq \tilde{m}$ such that $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.
-This means the points in $Y$ form an error correcting code and $\rec$ is an efficient decoder.
+When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.
+Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y$ with high probability.
+In particular, $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.
+This means we can construct a set $C$ out of the points in the support of $Y$.
+Then $C$ will be an error correcting code and $\rec$ an efficient decoder.
 We can then use standard arguments to turn this code into an information theoretic sketch.
-This means lower bounds on the entropy loss of an information theoretic sketch must apply.
-There are several technical conditions required to make this intuition formal, we present them below.
-%any function that is able to recover correctly on a large space is an decoder for an error correcting code formed by that space.
-If there is a distribution $Y$ with many points such that $\rec(y', \sketch(w)) =y\in Y$ when $\dis(y, y')\leq t$.
-Then $\rec$ is a decoder for the error correcting code formed by $Y$.
-% and make no assumption about the behavior of $\rec $ outside of this ball.
-The intuition is quite simply, on a point $w\leftarrow W$, the \rec oracle will always return $w$ within the $B_t(w)$.
-If $W|\sketch(W)$ is indistinguishable from $Y|\sketch(W)$ then the $\rec$ oracle must also correct for points in $Y$.
-However, this implies a code~(the points in $Y$) with $\rec$ as an efficient decoding algorithm.
-%\subsubsection{The Uniform Distribution}
-%and extend to an arbitrary high-entropy distribution.  
-%We begin by showing that any given no distribution $W$ can be indistinguishable from the uniform distribution given a sketch.
-%We need two technical requirements on our metric space: 1) there is an efficient algorithm to sample neighbors 2) each point is regular~(has the same number of neighbors).
-These requirements hold for several natural metric spaces including Hamming and symmetric difference metrics.
-%The only other requirement we make is for the distribution and its neighborhood to be efficiently samplable.
-%\begin{definition}
-%A distribution $W$ is $s-$\emph{efficiently-samplable} if there exists a randomized circuit of size at most $s$ that outputs samples according to $W$.
-%Furthermore, we say $W$ is \emph{efficiently-samplable} if there exists a randomized circuit of polynomial size that outputs samples according to $W$.
-%\end{definition}
-%We will be working with a metric space $\mathcal{M}, d$.  We will need to efficiently sample nearby points in the metric space.
-We assume that sampling a random neighbor of a point is efficient:
+%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
+To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
 \begin{definition}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit, $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.
+We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.
 %That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
@@
 %\]
-Furthermore, there is a procedure that outputs a random point of distance at most $t$.  For convenience we denote this procedure by $\sample(X)$.
 \end{definition}
 We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.
-While we could consider metric spaces where balls only contain their center, this is not very interesting in the context of fuzzy extractors~(as \gen can always output the empty string for $P$).
+While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.
 
@@
 
-We show that any recovery functionality that retains high HILL entropy implies a information theoretic secure sketch.
-We begin by reviewing definitions of Shannon codes~\cite{shannon1949mathematical}:
+We review definitions of Shannon codes~\cite{shannon1949mathematical}:
 \begin{definition}
 Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t)) \neq c]<\epsilon$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$.
+To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
 \end{definition}
-This is a slightly nonstandard formulation, we only require the code to correct exactly $t$ errors\footnote{In the standard formulation, the code must correct up to $t$ errors.
+This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$.
+\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.
 For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
 However, we work with an arbitrary recover functionality that is not necessarily monotone.}.
-Shannon codes work for all codewords, we can also consider a formulation that works for an ``average'' codeword.
-\begin{definition}
-Let $W$ be a distribution over space $\mathcal{M}$.  We say that $W$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that 
-$\Pr_{w\leftarrow W}[\rec(\sample(w, t)) \neq w]<\epsilon$.
+
+Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
+Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
+$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
 \end{definition}
-An average error Shannon code is convertible to a (maximal error)~Shannon code with a small loss.
-We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements}~(we provide a proof in \secref{sec:proof of average to maximal error}):
+An average error Shannon code is convertible to a maximal error Shannon code with a small loss.
+We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
 \begin{lemma}
 \label{lem:averageToMaximalError}
-Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
-There is a set $W'$ where $|W'|\ge2^{k-1}$ and $W'$~(drawing a codeword uniformly) is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
+Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
+There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
 \end{lemma}
 
-With this conversion we can show a surprising result: recover functionalities that retain HILL entropy imply Shannon error correcting codes~(proof in \secref{sec:proof of thm sketch implies code}).
+We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
 Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an $(s_{rec}, t)$-recover functionality over $\mathcal{M}$.
-If $H^{\hill}_{\epsilon, s_{sec}}(X|SS(X))\geq k$ then there exists $x$ and a set $W'$ where $|W'|\geq 2^{k-1}$ such that for all $1\leq t'\leq t$, $W'$ is a $(t', 2\epsilon)$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$ for $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$.
+Let $(\sketch, \rec)$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$.
+Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
+Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \\
+\\
 \end{enumerate}
@@
 \item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
-\item Let $X' = \mathcal{I}_t(\vA, \vect{D})$\\
-Set $X'_{1,..., n}$ be the first half bits of $X'$.		 
-\item Output $X'_{1,...,n}$.
+\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
+Set $X_{1,..., n/2}$ be the first of $X$.		 
+\item Output $X_{1,...,n/2}$.
 \end{enumerate}
@@
 \begin{proof}
-Let $\mathcal{M},d$ be a metric space that is $(s_{neigh},t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an $(s_{rec}, t)$-arbitrary recover functionality over $\mathcal{M}$.
-Let $X$ be an arbitrary distribution.
-Let $W$ be a distribution over $\mathcal{M}$ with $\Hoo(W)\geq k$ such that
+  Let $X$ be an arbitrary distribution of min-entropy $m$.  Let $Y$ be a distribution over $\mathcal{M}$ with $\Hoo(Y)\geq k$ such that 
 \[ 
-\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.
+\delta^{\mathcal{D}_s}((X, \sketch(X)), (Y, \sketch(X)))<\epsilon.
 \]  
-For all $D$ of size at most $s = O(t(s_{neigh}+s_{rec}))$.  One such $W$ must exist by the definition of conditional HILL entropy.
+where  $s = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \end{enumerate}
-  As before we know that $D(X, \sketch(X)) = 1$.  Since 
-$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(W, SS(X))>1-\epsilon$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
+  By correctness of the sketch $ \expe D(X, \sketch(X)) \ge 1-\delta$.  Since 
+$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(Y, SS(X))>1-\epsilon-\delta$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
 %This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
-Thus, for all $t', 1\leq t'\leq t$ on a random $w$
-\[ \Pr_{w\leftarrow W}[w'\leftarrow \sample(w, t') \wedge \rec(w', \sketch(x')) = w]\geq 1-\epsilon.\]  
+Thus, for all $t', 1\leq t'\leq t$ on a random $y$
+\[ \Pr_{y\leftarrow Y}[y'\leftarrow \sample(y, t') \wedge \rec(y', \sketch(x')) = y]\geq 1-\epsilon-\delta.\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus, for all $1\leq t'\leq t$, $W$ is a $(t', \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.
-The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
+Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
 \end{proof}

### 2013-02-15 CompFuzzExt.tex
Updates to section 3 and associated proofs

@@
 Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$.
+Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
@@
 \begin{definition}\label{def:comp secure sketch}
-A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
+A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} if the following properties hold:
 \begin{enumerate}
@@
 \end{enumerate}
-We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
+We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
 If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
@@
 
-We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-hard if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
+We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-secure if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
 \end{definition}
 
-Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} shows that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is hard under the worst-case lattice problems.
+Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} shows that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard.
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
@@
 Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\alpha$ be the discretized Gaussian distribution with variance $(\alpha q)^2/2\pi$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}hard$ for all probabilistic distinguisher $D$, where $\epsilon = \ngl(n)$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))$-secure for all probabilistic distinguisher $D$, where $\epsilon = \ngl(n)$.
 
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$hard, where $\epsilon = \ngl(n)$.
+Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$secure, where $\epsilon = \ngl(n)$.
 \end{lemma}
@@
 We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
-This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
+This says that if $\distLWE$ is secure then $X$ has many hardcore bits.
 We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
@@
 \end{itemize}
-We say that $\gen, \rep$ is $(\epsilon, s_{sec})$-hard with error $\delta$.
+We say that $\gen, \rep$ is $(\epsilon, s_{sec})$-secure with error $\delta$.
 \end{definition}

### 2013-02-15 trunk/CompFuzzExt.tex
working on the intro

@@
 \newcommand{\vF}{\vect{F}}
+\newcommand{\recout}{x}
 \newcommand{\ignore}[1]{}
@@
 \begin{abstract} 
+\lnote{This is an old abstract, no longer correct}
 One-message information reconciliation protocols called secure sketches remove noise
@@
 To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
-The definition of  \cite{DBLP:journals/siamcomp/DodisORS08} uses min-entropy as the information-theoretic measure of secrecy.
- Finding the right computational measure of secrecy requires us to consider different possible computational analogs of min-entropy.
-
-The natural relaxation of this secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
+The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
 Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
@@
 On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful.
-We prove in \corref{cor:rec yields sketch} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
+We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
 %Furthermore, we have (asymptotic)~constructions that meet these bounds.
 
-On the positive side, we show that a different relaxation of the security requirement can in fact lead to a \emph{lossless} construction of secure sketches, in which the knowledge of $s$ does not reduce entropy of $w$ (see Theorem~%s~%\ref{thm:lossless secure sketch} and
+On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction.
+The idea is to give up on reconstructing $w$ and, instead, to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
+This string $\recout$ is  required to have high HILL entropy even conditioned on $s$.
+Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
+
+Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
 ~\ref{thm:lossless secure conductor log})).
-This relaxation requires that $w$ have high \emph{unpredictability} entropy conditioned on $s$ (unpredictability  entropy is a computational notion originally defined in \cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
-We demonstrate how to build such lossless sketches based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
+We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
 
@@
 
-Both our lossless secure sketch and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
+Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
 To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).
@@
 
-Instead, in \secref{sec:unp secure sketch}, we define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
-In particular, in \secref{sec:comp fuzzy extractors}, we show a natural construction of computational fuzzy extractors from secure sketches defined using unpredictability.
+Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
+This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
+  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
 %The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.
@@
 Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.
-In order to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hoo(Y)\geq \tilde{m}$ \lnote{uncondtional?}; this distribution must be indistinguishable from \lnote{which one}, and, in particular, such that $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$ \lnote{explain why}.
-This means the points in $Y$ form an error correcting code and $\rec$ is an efficient decoder.
+When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.
+Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y$ with high probability.
+In particular, $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.
+This means we can construct a set $C$ out of the points in the support of $Y$.
+Then $C$ will be an error correcting code and $\rec$ an efficient decoder.
 We can then use standard arguments to turn this code into an information theoretic sketch.
-\lnote{this intuition is confusing, esp.
-given notational inconsistencies of all the capital letters with what comes above and below}
-
-We need the following technical condition to make this intuition precise: 
-we assume that sampling a random neighbor of a point is efficient.
+%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
+To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
 \begin{definition}
@@
 We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.
-While we could consider metric spaces where balls only contain their center, secure sketches are trivial in this context.
+While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.
 
@@
 
-Shannon codes work for all codewords.
-We can also consider a formulation that works for an ``average'' codeword.
-\lnote{notation here is messed up: why are we using $W$ for the code and $X$ for the input distribution in theorem 3.6?}
-\begin{definition}
-Let $W$ be a distribution over space $\mathcal{M}$.  We say that $W$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{w\leftarrow W}[\rec(\sample(w, t')) \neq w]<\epsilon$.
+Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
+Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
+$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
 \end{definition}
@@
 \label{lem:averageToMaximalError}
-Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
-There is a set $W'$ with $|W'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
+Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
+There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
 \end{lemma}
@@
 Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{M}, m, k, t)$-secure sketch \lnote{why did we switch from $\tilde{m}$ to $k$?} with error $\delta$.
+Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
-Then there exists $x$ and a set $W'$ with $|W'|\geq 2^{k-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
+Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 
-\subsection{Defining Noisy Computational Conductors}
+\subsection{Defining  Computational Fuzzy Conductors}
 \label{sec:unp secure sketch}
-In \secref{sec:imp HILL sketch}, we showed that defining a noisy computational conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
+In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
 The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
@@
 Instead of building a computational sketch, we will build a computational conductor.
-We adapt the definition of a noisy conductor from~\cite{KanukurthiR09} to the computational setting:
+We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
 %\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
@@
 \begin{definition}\label{def:comp secure sketch}
-A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
+A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
 \begin{enumerate}
@@
 %We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.
+In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.
 We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
@@
 For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
-\thref{thm:lossless secure conductor log} shows that a noisy computational conductor can be built without incurring any entropy loss.
+\thref{thm:lossless secure conductor log} shows that a computational fuzzy conductor can be built without incurring any entropy loss.
 This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.
@@
 In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.
-Showing security of a noisy computational conductor for arbitrary high min-entropy distributions is an open problem.
+Showing security of a computational fuzzy conductor for arbitrary high min-entropy distributions is an open problem.
 First we recall the notion of a symbol fixing source~(from~\cite{KZ07}):
@@
 
-\thref{thm:blockLWE} allows us to construct a noisy computational conductor from block-fixing sources:
+\thref{thm:blockLWE} allows us to construct a computational fuzzy conductor from block-fixing sources:
 
@@
 \begin{lemma}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-noisy computational conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
 Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
@@
 \begin{proof}
-  Let $X$ be an arbitrary distribution of minentropy $m$.  Let $W$ be a distribution over $\mathcal{M}$ with $\Hoo(W)\geq k$ such that 
+  Let $X$ be an arbitrary distribution of min-entropy $m$.  Let $Y$ be a distribution over $\mathcal{M}$ with $\Hoo(Y)\geq k$ such that 
 \[ 
-\delta^{\mathcal{D}_s}((X, \sketch(X)), (W, \sketch(X)))<\epsilon.
+\delta^{\mathcal{D}_s}((X, \sketch(X)), (Y, \sketch(X)))<\epsilon.
 \]  
-where  $s = O(t(s_{neigh}+s_{rec}))$.  One such $W$ must exist by the definition of conditional HILL entropy.
+where  $s = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
   By correctness of the sketch $ \expe D(X, \sketch(X)) \ge 1-\delta$.  Since 
-$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(W, SS(X))>1-\epsilon-\delta$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
+$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(Y, SS(X))>1-\epsilon-\delta$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
 %This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
-Thus, for all $t', 1\leq t'\leq t$ on a random $w$
-\[ \Pr_{w\leftarrow W}[w'\leftarrow \sample(w, t') \wedge \rec(w', \sketch(x')) = w]\geq 1-\epsilon-\delta.\]  
+Thus, for all $t', 1\leq t'\leq t$ on a random $y$
+\[ \Pr_{y\leftarrow Y}[y'\leftarrow \sample(y, t') \wedge \rec(y', \sketch(x')) = y]\geq 1-\epsilon-\delta.\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $W$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
+Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
 \end{proof}

### 2013-02-15 trunk/CompFuzzExtUnp.tex
starting results on why unpred secure sketches are hard

--- 2013-02-15 CompFuzzExt.tex
@@
 On the positive side, we show that a different relaxation of the security requirement can in fact lead to a \emph{lossless} construction of secure sketches, in which the knowledge of $s$ does not reduce entropy of $w$ (see Theorem~%s~%\ref{thm:lossless secure sketch} and
-~\ref{thm:lossless secure conductor log})).
+~\ref{thm:lossless secure sketch log})).
 This relaxation requires that $w$ have high \emph{unpredictability} entropy conditioned on $s$ (unpredictability  entropy is a computational notion originally defined in \cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
@@
 \label{sec:preliminaries}
-We begin by recalling a few basic definitions.
-For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.
-The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
+We begin by recalling a few basic entropy definitions.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
 %the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
@@
 
-\subsection{Defining Noisy Computational Conductors}
+\subsection{Defining Secure Sketches using unpredictability entropy}
 \label{sec:unp secure sketch}
-In \secref{sec:imp HILL sketch}, we showed that defining a noisy computational conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
+In \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best information-theoretic sketches.
 The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
-However, our sketch outputs a new random variable, this problem does not occur.
-Instead of building a computational sketch, we will build a computational conductor.
-We adapt the definition of a noisy conductor from~\cite{KanukurthiR09} to the computational setting:
-%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
-%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
-%\begin{enumerate}
-%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
-%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%\end{definition}
-%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
+However, if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
 We begin by defining unpredictability entropy:
 
-%\begin{definition}
-%\label{def:unp entropy}
-%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
-%\[
-%\Pr[C(Z) = Y ] \leq 2^{-k}
-%.\]
-%\end{definition}
-%We now provide a definition of a robust computational sketch using unpredictability entropy:
+\begin{definition}
+\label{def:unp entropy}
+For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+\[
+\Pr[C(Z) = Y ] \leq 2^{-k}
+.\]
+\end{definition}
+We now provide a definition of a computational secure sketch using unpredictability entropy:
 \begin{definition}\label{def:comp secure sketch}
-A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
+An $(\mathcal{M},m, \tilde{m}, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
 \begin{enumerate}
@@
 \item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.
+The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\rec(w',SS(w))=w$ and \rec runs in expected time $s_{rec}$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
+\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ is unpredictable given $\sketch(W)$.
+That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
-We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
-If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
+We say a construction is \emph{lossless} if $m=\tilde{m}$ and we omit the parameter $\tilde{m}$.
 \end{definition}
-%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.
-We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
-
-\section{Lossless conductor based on \class{LWE}}
+We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
+In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational secure sketch that meets \defref{def:comp secure sketch}.
+We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.
+
+\section{Lossless sketch based on \class{LWE}}
 \label{sec:fuzzyCompExt}
@@
 \item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
-\item Let $X' = \mathcal{I}_t(\vA, \vect{D})$\\
-Set $X'_{1,..., n}$ be the first half bits of $X'$.		 
-\item Output $X'_{1,...,n}$.
+\item Set $X' = \mathcal{I}_t(\vA, \vect{D}) $. 
+\item Output $w = \vect{C}-\vA X'$.
 \end{enumerate}
@@
 Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) \approx \Hoo(W)$.
+In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) \approx \Hoo(W)$.
 Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.
@@
 We describe conditions for efficient decoding in \secref{sec:time main construction}.
-Finally, in \secref{sec:lossless conductor} we describe parameter settings where our construction yields a lossless secure sketch.\lnote{revise after going through the rest}.
+Finally, in \secref{sec:lossless sketch} we describe parameter settings where our construction yields a lossless secure sketch.\lnote{revise after going through the rest}.
 
@@
 
-We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-hard if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
+We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-hard if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with the probability $\epsilon$.
 \end{definition}
@@
 
-We cannot immediately adapt the construction in \consref{cons:informal construction} to the $\LWE$ problem.
-Standard formulations of $\LWE$ require the error term to come from the discretized Gaussian distribution.
+We cannot immediately adapt the construction in \consref{cons:informal construction} to the LWE problem.
+Standard formulations of LWE require the error term to come from the discretized Gaussian distribution.
 %\subsection{LWE with uniform errors}
 %\label{subsec:LWE uniform error}
-Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over an interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian.
-This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it properly into $m$ blocks.
+Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of LWE with the uniform distribution over an interval reduces to the security of LWE where the noise comes from the discretized Gaussian.
+This allows us to directly encode $w$ as the error term in an LWE problem by splitting it properly into $m$ blocks.
 %As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$hard, where $\epsilon = \ngl(n)$.
+Assume there exists a PPT-distinguisher $D$ such that $\delta^D((\vA, \vA X+E), (\vA, U))>\epsilon$ for non-negligible $\epsilon$ and $\vA\in \Fq^{m\times n}, X\in \Fq^{n}, U\in \Fq^m$ drawn uniformly and $E$ drawn uniformly from $[-\rho q, \rho q]$.
+Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ in the worst case.
 \end{lemma}
 
-We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
-This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
-We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
-\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-\label{lem:many hardcore bits}
-Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
-Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
+We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).
+We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
+\begin{lemma}
+\label{lem:conversion to unpredictability}
+Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon', s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
+for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
 \end{lemma}
-
-%\begin{lemma}
-%\label{lem:conversion to unpredictability}
-%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
-%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
-%\end{lemma}
 %\begin{lemma}
@@
 %\end{lemma}
-With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} we can use the code-offset construction in \consref{cons:informal construction} and retain HILL entropy $k\log q$.  
+With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.
+We provide a formal description of our algorithm in the next section.
 %\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}.
@@
 \label{lem:i t poly time}
-Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance that is a unique witness relation~(except with negligible probability).
+Let $\vA, \vA X+W$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).
 Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
@@
 
-\subsection{Lossless Conductor}
-\label{sec:lossless conductor}
-We now state a setting of parameters that yields a lossless conductor.
+\subsection{Lossless Secure Sketch}
+\label{sec:lossless sketch}
+We now state a setting of parameters that yields a lossless sketch.
+For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
+There exist efficient lossless secure sketches based on \consref{cons:informal construction}:
 
@@
 \begin{theorem}
-\label{thm:lossless secure conductor log}
+\label{thm:lossless secure sketch log}
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
+Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
 Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
+If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then \consref{cons:informal construction} is a lossless secure sketch.
+That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$
 % for following parameters:
@@
 with 
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
 \end{theorem}
 \begin{proof}
-Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
+Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:conversion to unpredictability}, efficiency follows by \lemref{lem:i t poly time}.
 \end{proof}
 
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
-\thref{thm:lossless secure conductor log} shows that a noisy computational conductor can be built without incurring any entropy loss.
+\thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.
 This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.
@@
 In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.
-Showing security of a noisy computational conductor for arbitrary high min-entropy distributions is an open problem.
+Showing security of a computational secure sketch for arbitrary high min-entropy distributions is an open problem.
 First we recall the notion of a symbol fixing source~(from~\cite{KZ07}):
 \begin{definition}
-Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m - \alpha)b$ and for all $W_i$ one of the following conditions is met:
+Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m- \alpha)b$ and for all $W_i$ one of the following conditions is met:
 \begin{itemize}
@@
 For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$.
-The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
+The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
 \end{problem}
@@
 The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
-%\vspace{.1in}
+\vspace{.1in}
 \begin{theorem}
@@
 
-\thref{thm:blockLWE} allows us to construct a noisy computational conductor from block-fixing sources:
+\thref{thm:blockLWE} allows us to construct a computational secure sketch from block-fixing sources:
 
@@
 Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.
-There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
+\consref{cons:informal construction} is a lossless secure sketch.
+That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$ for %the following parameters:
 %\[
@@
 %\]
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{2d+3} \log n)$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
 \end{theorem}
@@
 \section{Computational Fuzzy Extractors}
-In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.
+In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using a paradigm similar to \lemref{lem:fuzzy ext construction}.
 We begin with a formal definition of a computational fuzzy extractor:
@@
 \begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-An $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
+An $(\mathcal{M}, m, \ell, t, s_{rec}, s_{sec}, \epsilon)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
 \begin{itemize}
@@
 \item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-%%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\rep( w', P) = R$.
+Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
 If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
@@
 \end{itemize}
-We say that $\gen, \rep$ is $(\epsilon, s_{sec})$-hard with error $\delta$.
 \end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
+Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
 
@@
 However, the entropy loss due to error correction may mean there is not be enough remaining bits to run a pseudorandom generator.
-Depending on the application, it may be appropriate to make the noise correction procedure and/or extractor computational.
-
-Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
-\begin{lemma}
-Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
-Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.
-Let, $s' = s_{sec}-s_{ext}$, then
-$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
-\end{lemma}
-%  the same paradigm from 
-%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
+Depending on the application, it may be appropriate to make the sketch and/or extractor computational.
+
+Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
 It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
 However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).
-%\begin{definition}
-%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
+\begin{definition}
+An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
 Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
-%\end{definition}
-%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-%\label{lem:unp extraction} 
-%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+\end{definition}
+\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+\label{lem:unp extraction} 
+Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
 Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-%\end{lemma}
+\end{lemma}
 We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
 \begin{lemma}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-noisy computational conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
-Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
-Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, s_{sec}, s_{sketch}, s_{rec}, t)$-computational secure sketch, and let $\rext:\mathcal{M}\times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
+Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
+\begin{itemize}
+\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
+\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
+\end{itemize}
 \end{lemma}
-%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
-%\begin{itemize}
-%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
-%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
-%\end{itemize}
-%\end{lemma}
-%\begin{proof}
-%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
-%\end{proof}
-%
+\begin{proof}
+Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
+\end{proof}
+
 %For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
@@
 \section{Background}
-%\subsection{Notions of Computational Entropy}
-%\label{sec:notionsEntropy}
-%In this sections we provide some further definitions of computational entropy.
+\subsection{Notions of Computational Entropy}
+\label{sec:notionsEntropy}
+In this sections we provide some further definitions of computational entropy.
 HILL entropy is defined in \secref{sec:defCompFuzzyExtractors}.
@@
 Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
-%\begin{definition}
-%\label{def:yao entropy}
-%For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
-%\[
-%\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
-%\]
-%\end{definition}
-%It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.
+\begin{definition}
+\label{def:yao entropy}
+For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
+\[
+\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
+\]
+\end{definition}
+It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.
 In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
@@
 This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
-%Unpredictability entropy is a notion between HILL and Yao entropy:
-%\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
-%\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
-%\]
-%\end{lemma} 
-%\subsection{Unique Witness Relations}
+Unpredictability entropy is a notion between HILL and Yao entropy:
+\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
+\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
+\]
+\end{lemma} 
+\subsection{Unique Witness Relations}
 
@@
 
-%\section{\lemref{lem:conversion to unpredictability}}
-%\label{sec:proof of unpred conversion}
-%In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.
+\section{\lemref{lem:conversion to unpredictability}}
+\label{sec:proof of unpred conversion}
+In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.
 %We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).
 Thus, we have the following claim:
-%%\begin{claim}
-%%\label{lem:unp of x and e}
-%%Let $A, X, E$ be as above, then:
-%%\begin{itemize}
-%%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
-%%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
-%%\end{itemize}
-%%\end{claim}
-%%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
-%%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
-%%\begin{assumption}
-%%\label{assume:entropy LWE}
-%%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
+%\begin{claim}
+%\label{lem:unp of x and e}
+%Let $A, X, E$ be as above, then:
+%\begin{itemize}
+%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
+%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
+%\end{itemize}
+%\end{claim}
+%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
+%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
+%\begin{assumption}
+%\label{assume:entropy LWE}
+%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
 If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.
-%%\end{assumption}
-%%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
-%We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.
+%\end{assumption}
+%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
+We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.
 This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
 We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
-%\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-%\label{lem:many hardcore bits}
-%Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
+\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
+\label{lem:many hardcore bits}
+Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
 Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
 Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
-%\end{lemma}
-%
-%\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
-%Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
+\end{lemma}
+
+\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
+Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
 Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.
@@
 To expand to $E$ we use the following claim:
-%
+
+\begin{claim}
+Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
+\[
+H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
+\]
+\end{claim}
 %\begin{claim}
-%Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
-%\[
-%H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
-%\]
+%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
 %\end{claim}
-%%\begin{claim}
-%%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
-%%\end{claim}
-%%\begin{proof}
-%%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
+%\begin{proof}
+%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
 Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
@@
 This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
-%%\end{claim}
-%%\begin{proof}
-%%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
-%%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.
+%\end{proof}
+
+%\begin{claim}
+%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
+%\end{claim}
+%\begin{proof}
+%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
+%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.
 Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
@@
 Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
-%%This completes the claim.
-%%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.
+%This completes the claim.
+%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.
 In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
-%% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
+% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
 Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
@@
 This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
-%%\end{claim}
-%%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.
+%\end{proof}
+
+%\begin{claim}
+%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
+%\end{claim}
+%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.
 This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.
 Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
-%%
-%%
-%%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.
+%
+%
+%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.
 By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.
 This completes the proof of \lemref{lem:conversion to unpredictability}.
-%%\end{proof}
-%\begin{proof}
-%Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.
+%\end{proof}
+\begin{proof}
+Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.
 We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.
@@
 Note that $\mathcal{E}$ occurs with probability $1-\gamma$.
-%
-%Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
-%\begin{align*}
-%\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
-%\end{align*}
-%Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
+
+Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
+\begin{align*}
+\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
+&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
+&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
+\end{align*}
+Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
 Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$.
 Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.
-%
-%We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
+
+We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
+\begin{enumerate}
+\item Input $(\vA, \vA X+E)$.
+\item Run $y\leftarrow C(\vA, \vA X+E)$.
+\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
+\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
+\end{enumerate}
+Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
+Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.
+Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
+\end{proof}
+
+The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
+%\begin{proof}[Proof of \clref{lem:unp of x and e}]
+%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
+That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
+Define $I'$ by the following:
 %\begin{enumerate}
 %\item Input $(\vA, \vA X+E)$.
-%\item Run $y\leftarrow C(\vA, \vA X+E)$.
-%\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
-%\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
+%\item Run $y\leftarrow I(\vA, \vA X+E)$.
+%\item Output $z = \vA y - \vA X+E$.
 %\end{enumerate}
-%Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
-Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.
-Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
-%\end{proof}
-%
-%The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
-%%\begin{proof}[Proof of \clref{lem:unp of x and e}]
-%%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
-That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
-Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(\vA, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Output $z = \vA y - \vA X+E$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
-%%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
-%%\end{align*}
-%%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
+%Note that $|I'|\approx |I|$.
+%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
+%\begin{align*}
+%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
+%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
+%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
+%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
+%\end{align*}
+%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
 That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((E, \vA, \vA X+E), (Y, \vA, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
 Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(A, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
-%%\item Output $z = \vA^{-1}(\vA X+E-y)$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
+%\begin{enumerate}
+%\item Input $(A, \vA X+E)$.
+%\item Run $y\leftarrow I(\vA, \vA X+E)$.
+%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
+%\item Output $z = \vA^{-1}(\vA X+E-y)$.
+%\end{enumerate}
+%Note that $|I'|\approx |I|$.
 For sufficient parameter sizes the probability of $A^{-1}$ not existing is negligible.
@@
 Then one has the following~(conditioned on the event that $\vA^{-1}$ exists):
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
-%%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
-%%\end{align*}
-%%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
-%%\end{proof}
-%
+%\begin{align*}
+%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
+%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
+%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
+%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
+%\end{align*}
+%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
 %\end{proof}
+
+\end{proof}
 
@@
 In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure conductor log} we give lossless conductors from a security parameter $n$ and an error $t$.
+In \thref{thm:lossless secure sketch log} we give lossless sketches from a security parameter $n$ and an error $t$.
 In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
@@
 \item $m$: The size of each number of samples in the LWE instance.  
-\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
 \end{itemize}
@@
 \item Minimize entropy loss of the construction.
-We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.
-We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.
-Substituting, one has $m\log \rho q = k \log q$.
+If we assume that $|X|\leq |W|$ then the entropy loss of the construction is $|W|-|X|$.
+We want the entropy loss to be zero, that is, $|W| = |X|$.
+Substituting, one has $m\log \rho q = n \log q$.
 \end{itemize}
-Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
-\begin{align*}
-n_0&< n -k \\
+Collecting constraints we can support any setting where $t, n, q, \rho, m$ satisfy the following constraints~(for constants $d, f$):
+\begin{align*}
+n_0&< n\\
 t&\leq d \log n\left(\frac{m}{n}-1\right)\\
@@
 \rho q  &= 2n^{1/2+3\gamma}m\\
-m\log \rho q &= k \log q
+m\log \rho q &= n \log q
 \end{align*}
@@
 \begin{align*}
-n_0&< n - k\\
+n_0&< n\\
 t&\leq d\log n\left(\frac{m}{n}-1\right)\\
-m \log 2n^{1/2+3\gamma}m &= k \log n^f
+m \log 2n^{1/2+3\gamma}m &= n \log n^f
 \end{align*}
@@
 n_0&< n\\
-t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
+t&\leq d\log n\left(\frac{ m }{n}\right)\\
 %f \log n &= \frac{m}{n}\log 2n^2m\\
@@
 \end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
+To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$.
 Finally we assume that $t = d \log n(m/n-1)$~(this means we have only as many dimensions as necessary for polynomial time recovery):
@@
 m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+d)}{d}\frac{\log \frac{2(c+d)}{d} n^{3/2+3\gamma}}{\log n}
+f &= \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}
 \end{align*}
@@
 \end{align*}
-Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.
-We will set $g = 2$, that is our sketch will output the first half of $X$.
-This is the setting of parameters in \thref{thm:lossless secure conductor log}.
+Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.  This is the setting of parameters in \thref{thm:lossless secure sketch log}.
 
@@
 }
+
+\section{Impossibility of Unpredictable Secure Sketches}
+In this section we argue why constructing computational secure sketches with minimal loss is difficult.
+
+\begin{lemma}
+Let $X$ be the uniform distribution over $\zo^b$.
+Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch for $\epsilon = 0, s_{sec} = \Omega(|\rec|)$ with error $\delta$.
+Then $r < b - t + \log (1-\delta)$.
+\end{lemma}
+\begin{proof}
+It suffices to show that $H^{\unp}( X | \sketch(X)) < b-t + \log (1-\delta)$.  That is, it suffices to construct $D$ such that $\Pr[D(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.  We describe $D$:
+\begin{enumerate}
+\item Input $s = \sketch(x)$.
+\item Sample $z \leftarrow \zo^b$.
+\item Output $\rec(s, z)$.
+\end{enumerate}
+Now 
+\[
+\Pr[D(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{b-t}(1-\delta)
+\]
+That is $r < b-t+\log (1-\delta)$.
+\end{proof}
 \end{document}

### 2013-02-15 CompFuzzExtUnp.tex
starting results on why unpred secure sketches are hard

--- 2013-02-15 trunk/CompFuzzExtUnp.tex
@@
 Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch for $\epsilon = 0, s_{sec} = \Omega(|\rec|)$ with error $\delta$.
-Then $r < b - t + \log (1-\delta)$.
+Then $r < b - t -\log (1-\delta)$.
 \end{lemma}
 \begin{proof}
-It suffices to show that $H^{\unp}( X | \sketch(X)) < b-t + \log (1-\delta)$.  That is, it suffices to construct $D$ such that $\Pr[D(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.  We describe $D$:
+It suffices to show that $H^{\unp}_{0, s_{sec}}( X | \sketch(X)) < b-t + \log (1-\delta)$.
+That is, it suffices to construct $D$ such that $\Pr[D(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.
+We describe $D$:
 \begin{enumerate}
@@
 \item Sample $z \leftarrow \zo^b$.
-\item Output $\rec(s, z)$.
+\item Output $\rec(z, s)$.
 \end{enumerate}
@@
 \[
-\Pr[D(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{b-t}(1-\delta)
+\Pr[D(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{-b+t}(1-\delta)
 \]
-That is $r < b-t+\log (1-\delta)$.
+That is $r < b-t-\log (1-\delta)$.
 \end{proof}
+\bnote{Note we are underestimating the probability that $z\in B_t(x)$.  Just don't want to find the right probability right now.}
 \end{document}

### 2013-02-19 CompFuzzExtUnp.tex
Working on impossibility of verifiable and unpredictable sketches

@@
 \newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
+\newcommand{\ver}{\ensuremath{\class{Ver}}\xspace}
 \newcommand{\zo}{\ensuremath{\{0, 1\}}}
@@
 \begin{lemma}
+\label{lem:impossibility of sketch with eps = 0}
 Let $X$ be the uniform distribution over $\zo^b$.
@@
 It suffices to show that $H^{\unp}_{0, s_{sec}}( X | \sketch(X)) < b-t + \log (1-\delta)$.
-That is, it suffices to construct $D$ such that $\Pr[D(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.
-We describe $D$:
+That is, it suffices to construct $P$ such that $\Pr[P(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.
+We describe $P$:
 \begin{enumerate}
@@
 \[
-\Pr[D(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{-b+t}(1-\delta)
+\Pr[P(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{-b+t}(1-\delta)
 \]
@@
 \bnote{Note we are underestimating the probability that $z\in B_t(x)$.  Just don't want to find the right probability right now.}
+
+We will now consider the impossibility result where $\epsilon \neq 0$.
+We will focus on the case where $\rec$ is verifiable, that is, given an $x, s = \sketch(y)$ it is possible to tell whether $x$ is the value encoded in $s$.
+
+\begin{definition}
+We say a sketch $(\sketch, \rec)$ is $\delta$-verifiable if there exists an efficient randomized function $\ver$ such that with probability $1-\delta$ over the coins of $\sketch, \ver$ for all $y$ in the domain of $\sketch$, $\ver(y', \sketch(y)) = 1$ implies that $y=y'$.
+That is,
+\[
+\forall y\in \mathcal{M}, \Pr[\exists y'\neq y \wedge \ver(y', \sketch(y)) = 1]\leq \delta
+\]
+Furthermore, $\forall y\in\mathcal{M}, \Pr[\ver(y, \sketch(y)) = 1] =1$.
+\end{definition}
+
+We now show that if a sketch is unpredictable then either the quality or quantity of the unpredictability entropy must depend on $t$.
+\begin{theorem}
+Let $W$ be the uniform distribution over $\zo^b$.
+Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch that is $\delta$-verifiable with verifier $\ver$.
+Furthermore assume that $(\sketch, \rec)$ is  $\epsilon, \Omega(|\rec|+|\ver|)$-secure.
+Then $r<b-t -\log (1-\epsilon - \delta)$.
+That is, either $r$ or $\epsilon$ depends on $t$.
+\end{theorem}
+\begin{proof}
+Let $(\sketch, \rec)$ be a $\delta$-verifiable secure sketch with verification function $\ver$.  Let $W$ be the source, then we have the following claim:
+\begin{claim}
+If $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W))) \leq \epsilon$ for $s_{sec} = \Omega(|\ver|)$ then $\Pr[W = Y]\geq 1-\epsilon - \delta$.
+\end{claim}
+\begin{proof}
+We define a distinguisher $D(x, s) = \ver (x, s)$.  Then note that, 
+\begin{align*}
+1-\epsilon &\leq \Pr[D(Y, \sketch(W)) =1] = \Pr[\ver(Y, \sketch(W)) = 1] \\
+&\leq \Pr[\ver(Y, \sketch(W)) = 1 | \ver\text{ is unique}]\Pr[\ver\text{ is unique}] \\&+ \Pr[\ver(Y, \sketch(W)) = 1 | \ver\text{ is not unique}]\Pr[\ver\text{ is not unique}]\\
+&\leq \Pr[Y = W | \sketch(W)]\Pr[\ver \text{ is unique}] +\Pr[\ver\text{ is not unique}]\\
+&\leq \Pr[Y= W | \sketch(W)](1-\delta) + \delta
+\end{align*}
+This means that $\Pr[Y | \sketch(W)=W | \sketch(W)]\geq \frac{(1-\epsilon -\delta)}{(1-\delta)}\geq 1-\epsilon -\delta$.
+\end{proof}
+Thus, since $W = Y$ with high probability, any predictor for $W$ is also a predictor for $Y$.
+We reuse the predictor from \lemref{lem:impossibility of sketch with eps = 0}.
+Define $P$ as above.
+Then
+\[
+\Pr[P(\sketch(W) )= Y] \geq \Pr[P(\sketch(W) )= W]\Pr[W = Y | \sketch(W)]\geq 2^{-b+t}(1-\epsilon-\delta)
+\]
+If $\epsilon$ does not depend on $t$ then the remaining entropy must depend on $t$.  The statement of theorem follows.
+\end{proof}
 \end{document}

### 2013-02-26 trunk/CompFuzzExt.tex
Impossibility of unpredictability sketches

@@
 
+\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
+In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
+A reasonable question to ask is whether a sketch could retain unpredictability of the source.
+We begin by defining conditional unpredictability entropy:
+
+\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
+\label{def:unp entropy}
+For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+\[
+\Pr[C(Z) = Y ] \leq 2^{-k}
+.\]
+\end{definition}
+We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
+\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+\label{lem:unp extraction} 
+Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
+\end{lemma}
+Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).
+Unfortunately, we show that the unpredictability entropy must decrease with the $O(\log B_t(\cdot))$.
+\begin{theorem}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+\end{theorem}
+\begin{proof}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+We begin by showing that $Y$ must correctly recover most of the time.
+\begin{claim}
+\label{clm:y is recoverable}
+\begin{align*}
+\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
+\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
+\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
+\end{align*}
+\end{claim}
+\begin{proof}
+Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+\begin{itemize}
+\item Input $x\in \zo^b, s\in\zo^*$.
+\item Sample $x'\leftarrow B_t(x)$.
+\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
+\end{itemize}
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(W, \sketch(W))  ]\geq 1-\delta$.
+The statement of the claim follows as
+\begin{align*}
+\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
+\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
+\end{align*}
+\end{proof}
+We now consider a fixed $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
+\clref{clm:y is recoverable} says that
+\[
+ \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
+\]
+We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
+We restate this as $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
+We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+\begin{itemize}
+\item Input $s\in\zo^*$.
+\item Sample $x'\leftarrow \zo^b$.
+\item Output $\rec(x', s)$.
+\end{itemize}
+We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
+We now show that $\mathcal{I}$ predicts $Y$, defining :
+\begin{align*}
+2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
+&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{|B_t(\cdot)|}{2^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
+\end{align*}
+Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
+\end{proof}
+This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The two statements are incomparable.
 \subsection{Defining  Computational Fuzzy Conductors}
@@
 
-%\begin{definition}
-%\label{def:unp entropy}
-%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
-%\[
-%\Pr[C(Z) = Y ] \leq 2^{-k}
-%.\]
-%\end{definition}
 %We now provide a definition of a robust computational sketch using unpredictability entropy:

### 2013-02-26 CompFuzzExt.tex
Added Markov inequality to HILL impossibility

@@
 Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
-This object is the computational analogue of a noisy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
-  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from noisy computational conductors.
+This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
+  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
 %The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.
@@
 Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
-Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
+Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \label{lem:shannon to sketch}
-For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.% with recovery procedure $\rec'$.
+For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
 %  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
@@
 Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-1,t)$ (information-theoretic) secure sketch with error
-$2(\epsilon+\delta)$. 
+If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+$4(\epsilon+\delta)$. 
 %Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
@@
 
-\subsection{Defining Noisy Computational Conductors}
+\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
+In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
+A reasonable question to ask is whether a sketch could retain unpredictability of the source.
+We begin by defining conditional unpredictability entropy:
+
+\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
+\label{def:unp entropy}
+For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+\[
+\Pr[C(Z) = Y ] \leq 2^{-k}
+.\]
+\end{definition}
+We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
+\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+\label{lem:unp extraction} 
+Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
+\end{lemma}
+Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).
+Unfortunately, we show that the unpredictability entropy must decrease with the $O(\log B_t(\cdot))$.
+\begin{theorem}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+\end{theorem}
+\begin{proof}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+We begin by showing that $Y$ must correctly recover most of the time.
+\begin{claim}
+\label{clm:y is recoverable}
+\begin{align*}
+\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
+\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
+\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
+\end{align*}
+\end{claim}
+\begin{proof}
+Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+\begin{itemize}
+\item Input $x\in \zo^b, s\in\zo^*$.
+\item Sample $x'\leftarrow B_t(x)$.
+\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
+\end{itemize}
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(W, \sketch(W))  ]\geq 1-\delta$.
+The statement of the claim follows as
+\begin{align*}
+\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
+\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
+\end{align*}
+\end{proof}
+We now consider a fixed $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
+\clref{clm:y is recoverable} says that
+\[
+ \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
+\]
+We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
+We restate this as $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
+We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+\begin{itemize}
+\item Input $s\in\zo^*$.
+\item Sample $x'\leftarrow \zo^b$.
+\item Output $\rec(x', s)$.
+\end{itemize}
+We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
+We now show that $\mathcal{I}$ predicts $Y$, defining :
+\begin{align*}
+2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
+&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{|B_t(\cdot)|}{2^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
+\end{align*}
+Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
+\end{proof}
+This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The two statements are incomparable.
+\subsection{Defining  Computational Fuzzy Conductors}
 \label{sec:unp secure sketch}
-In \secref{sec:imp HILL sketch}, we showed that defining a noisy computational conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
+In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
 The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
@@
 
-%\begin{definition}
-%\label{def:unp entropy}
-%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
-%\[
-%\Pr[C(Z) = Y ] \leq 2^{-k}
-%.\]
-%\end{definition}
 %We now provide a definition of a robust computational sketch using unpredictability entropy:
 \begin{definition}\label{def:comp secure sketch}
-A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} if the following properties hold:
+A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
 \begin{enumerate}
@@
 \begin{proof}
-  Let $X$ be an arbitrary distribution of min-entropy $m$.  Let $Y$ be a distribution over $\mathcal{M}$ with $\Hoo(Y)\geq k$ such that 
+  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ such that 
 \[ 
-\delta^{\mathcal{D}_s}((X, \sketch(X)), (Y, \sketch(X)))<\epsilon.
+\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))<\epsilon.
 \]  
-where  $s = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
+where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \end{enumerate}
-  By correctness of the sketch $ \expe D(X, \sketch(X)) \ge 1-\delta$.  Since 
-$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(Y, SS(X))>1-\epsilon-\delta$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
+  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-\delta$.  Since 
+$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon.$ then $\Pr[D(Y, SS(W)) = 1]>1-\epsilon-\delta$.
+By Markov inequality there exists a set $S_W$ such that $\Pr[S_W]\geq 1/2$ and $\Pr[ D(Y, s) =1 | \sketch(W) = s \wedge s\in S_W]> 1- 2(\epsilon + \delta)$.
+Consider the random variable $1_{S_W}$ that is $1$ when $s\in S_X$ and otherwise.
+Then
+\[
+\Hav(Y  | W) = -\log \left( \Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} + \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})} \right)
+\] 
+Rearranging terms:
+\begin{align*}
+\Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} &= 2^{-\Hav(Y  | W) } - \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})}\\
+&=2^{-\Hav(Y  | W) } = 2^{-k}
+\end{align*}
+This means that $2^{-\Hav(Y | W\in 1_{S_W})} \geq 2^{-k}/\Pr[W\in 1_{S_W}] = 2^{-k+1}$.  That is, $\Hav(Y|W\in 1_{S_W})\geq k-1$.  Fix one value $s \in 1_{S_W}$ such that $\Hav(Y | s)\geq k-1$.
+%This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
 %This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
 Thus, for all $t', 1\leq t'\leq t$ on a random $y$
-\[ \Pr_{y\leftarrow Y}[y'\leftarrow \sample(y, t') \wedge \rec(y', \sketch(x')) = y]\geq 1-\epsilon-\delta.\]  
+\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]\geq 1-2(\epsilon+\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
+Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
 \end{proof}

### 2013-02-26 CompFuzzExt.tex
Added note after HILL impossibility for general distributions

@@
 \end{corollary}
-\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
+\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
+
+\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |Z|-\tilde{m})-2$ bits of entropy.
 

### 2013-02-26 trunk/CompFuzzExt.tex
Notes in Unp impossibility section

--- 2013-02-15 trunk/CompFuzzExt.tex
@@
 
+\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
+In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
+A reasonable question to ask is whether a sketch could retain unpredictability of the source.
+We begin by defining conditional unpredictability entropy:
+
+\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
+\label{def:unp entropy}
+For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+\[
+\Pr[C(Z) = Y ] \leq 2^{-k}
+.\]
+\end{definition}
+We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
+\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+\label{lem:unp extraction} 
+Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
+\end{lemma}
+Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).
+
+Unfortunately, unpredictability entropy must also decrease with $t$.
+That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
+The formal statement is below~(proof in \secref{sec:proof of imp unp entropy})
+\begin{theorem}
+\label{thm:imp of unp entropy}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+\end{theorem}
+This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
+The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution $Y$ actually contains many points.
+This means we cannot construct a good code out of the points of $Y$.
+Our bound is a result of the Hamming bound for the space.
 \subsection{Defining  Computational Fuzzy Conductors}
@@
 \end{enumerate}
-  By correctness of the sketch $ \expe D(X, \sketch(X)) \ge 1-\delta$.  Since 
-$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(Y, SS(X))>1-\epsilon-\delta$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
+  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-\delta$.  Since 
+$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon.$ then $\Pr[D(Y, SS(W)) = 1]>1-\epsilon-\delta$.
+By Markov inequality there exists a set $S_W$ such that $\Pr[S_W]\geq 1/2$ and $\Pr[ D(Y, s) =1 | \sketch(W) = s \wedge s\in S_W]> 1- 2(\epsilon + \delta)$.
+Consider the random variable $1_{S_W}$ that is $1$ when $s\in S_X$ and otherwise.
+Then
+\[
+\Hav(Y  | W) = -\log \left( \Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} + \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})} \right)
+\] 
+Rearranging terms:
+\begin{align*}
+\Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} &= 2^{-\Hav(Y  | W) } - \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})}\\
+&=2^{-\Hav(Y  | W) } = 2^{-k}
+\end{align*}
+This means that $2^{-\Hav(Y | W\in 1_{S_W})} \geq 2^{-k}/\Pr[W\in 1_{S_W}] = 2^{-k+1}$.  That is, $\Hav(Y|W\in 1_{S_W})\geq k-1$.  Fix one value $s \in 1_{S_W}$ such that $\Hav(Y | s)\geq k-1$.
+%This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
 %This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
 Thus, for all $t', 1\leq t'\leq t$ on a random $y$
-\[ \Pr_{y\leftarrow Y}[y'\leftarrow \sample(y, t') \wedge \rec(y', \sketch(x')) = y]\geq 1-\epsilon-\delta.\]  
+\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]\geq 1-2(\epsilon+\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
+Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
+\end{proof}
+
+\subsection{Proof of \thref{thm:imp of unp entropy}}
+\label{sec:proof of imp unp entropy}
+\begin{proof}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+We begin by showing that $Y$ must correctly recover most of the time.
+\begin{claim}
+\label{clm:y is recoverable}
+\begin{align*}
+\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
+\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
+\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
+\end{align*}
+\end{claim}
+\begin{proof}
+Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+\begin{itemize}
+\item Input $x\in \zo^b, s\in\zo^*$.
+\item Sample $x'\leftarrow B_t(x)$.
+\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
+\end{itemize}
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(W, \sketch(W))  ]\geq 1-\delta$.
+The statement of the claim follows as
+\begin{align*}
+\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
+\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
+\end{align*}
+\end{proof}
+We now consider a fixed $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
+\clref{clm:y is recoverable} says that
+\[
+ \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
+\]
+We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
+We restate this as $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
+We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+\begin{itemize}
+\item Input $s\in\zo^*$.
+\item Sample $x'\leftarrow \zo^b$.
+\item Output $\rec(x', s)$.
+\end{itemize}
+We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
+We now show that $\mathcal{I}$ predicts $Y$, defining :
+\begin{align*}
+2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
+&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
+&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{|B_t(\cdot)|}{2^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
+\end{align*}
+Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
 \end{proof}

### 2013-02-28 trunk/CompFuzzExt.tex
Notes in Unp impossibility section
Working on Section 3, impossibility of unpredictability

@@
 %=============================================================
-\section{Defining Computational Secure Sketches}
+\section{Impossibility of Computational Secure Sketches}
 \label{sec:defCompFuzzyExtractors}
-We first recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.
+%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp.
+unpredictability) entropy when given a source with $m$ bits of entropy.
+In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
+In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the number of neighbors of a point in the metric space.
+These results are strongest for high entropy sources.
+The results get weaker as we consider sources with lower starter entropy.
+This is necessary, if a source contains only codewords of an error correcting code  no sketch is necessary.
+
+\subsection{Bounds on Secure Sketches using HILL entropy}
+\label{sec:imp HILL sketch}
+We recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
 
@@
 
-\subsection{Bounds on Secure Sketches using HILL entropy}
-\label{sec:imp HILL sketch}
-Suppose we redefine secure sketches using HILL entropy: that is, an \emph{$(\epsilon,s_{sec})$-HILL-entropy secure sketch} is the same object as in Definition~\ref{def:secure sketch}, but the security requirement is replaced with  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
+Suppose we redefine secure sketches using HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
 Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches).
@@
 \subsection{Bounds on Secure Sketches using Unpredictability Entropy}
+\label{sec:imp unp sketch}
 In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
@@
 \label{def:unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+For a distribution $(X, Z)$, we say that $X$ has \emph{unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
 \[
@@
 \end{definition}
+We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy}$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfied \defref{def:secure sketch} with the security requirement replaces with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
 We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
@@
 
-Unfortunately, unpredictability entropy must also decrease with $t$.
-That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
-The formal statement is below~(proof in \secref{sec:proof of imp unp entropy})
+Unfortunately, unpredictability entropy must also depend on $t$.
+An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
+%That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
+The formal statement is below:
 \begin{theorem}
@@
 This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
-The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution $Y$ actually contains many points.
+The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.
 This means we cannot construct a good code out of the points of $Y$.
-Our bound is a result of the Hamming bound for the space.
+In \secref{sec:proof of imp unp entropy}, we prove a stronger version of \thref{thm:imp of unp entropy}, based on a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.
+
+\textbf{Avoiding lower bounds from \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy}:}
+
+The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.
+The results get weaker as we consider sources with lower starter entropy.
+This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.
+This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.
+
+Both of the lower bound results rely on the ability to ensure that \rec serves as an error-correcting codes for most points of the output distribution.
+It may be possible to avoid this problem if \rec outputs
 \subsection{Defining  Computational Fuzzy Conductors}
 \label{sec:unp secure sketch}
-In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
-The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
-However, our sketch outputs a new random variable, this problem does not occur.
+In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.
+If, the error correcting algorithm outputs a new random variable, bounds do not apply.
 Instead of building a computational sketch, we will build a computational conductor.
@@
 \end{definition}
+\textbf{Note:} If some efficient algorithm can take the output of $\rec$ and transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
+This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).
+
 %We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
@@
 \label{sec:proof of imp unp entropy}
+Instead of proving \thref{thm:imp of unp entropy}, we will prove a stronger result based on a weaker form of entropy.
+This relaxed definition allows both the variable and the condition to be replaced.
+Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}.
+
+\begin{definition}
+\label{def:relaxed unp entropy}
+For a distribution $(X, Z)$, we say that $X$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a joint distribution $Y, Z'$ such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z'))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+\[
+\Pr[C(Z) = Y ] \leq 2^{-k}
+.\]
+\end{definition}
+
+\begin{theorem}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+
+\end{theorem}
 \begin{proof}
-Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
-Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
-We begin by showing that $Y$ must correctly recover most of the time.
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $Y, Z'$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z'))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+We begin by showing that \rec must recover points of $Y$.
 \begin{claim}
@@
 \begin{align*}
-\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
-\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
-\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
+\Pr[\rec(B_t(Y), Z') = Y]&=\\
+\Pr[(y, z)\leftarrow (Y, Z) \wedge y'\leftarrow B_t(y) \wedge \rec(y', z) = y] &\geq 1-\epsilon -\delta.
 \end{align*}
@@
 \begin{proof}
-Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+Suppose that $\Pr[\rec(B_t(Y), Z') = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
 \begin{itemize}
@@
 \end{itemize}
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(W, \sketch(W))  ]\geq 1-\delta$.
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
 The statement of the claim follows as
 \begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
-\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
+\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, Z')] &=\\
+\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), Z') = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
 \end{align*}
 \end{proof}
-We now consider a fixed $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
-\clref{clm:y is recoverable} says that
+We now consider the experiment $(y, z)\leftarrow (Y, Z'), y'\leftarrow B_t(y)$ and define the quantity $P_{y' , z, y} = \Pr[\rec(y', z) =y]$.  \clref{clm:y is recoverable} says that 
 \[
- \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
+ \Pr[(y, z\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
 \]
-We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
-We restate this as $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
+We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, \Pr[B_t(y) = y' | Y=y] = 0$.
+Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
 We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
 \begin{itemize}
-\item Input $s\in\zo^*$.
-\item Sample $x'\leftarrow \zo^b$.
-\item Output $\rec(x', s)$.
+\item Input $z\in\zo^*$.
+\item Sample $x\leftarrow \zo^b$.
+\item Output $\rec(x, z)$.
 \end{itemize}
-We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
-We now show that $\mathcal{I}$ predicts $Y$, defining :
-\begin{align*}
-2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
-&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
-&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
-&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
-&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{|B_t(\cdot)|}{2^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+Let $X$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
+We now show that $\mathcal{I}$ predicts $Y$:
+\begin{align*}
+2^{\tilde{m}}& = \Pr[\mathcal{I}(Z') = Y] \\
+&= \Pr[(y, z)\leftarrow (Y, Z')] \Pr[\mathcal{I}(z) = y]\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', z, y}\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
 &\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
@@
 \end{proof}
+
+%\bnote{This is the proof for not relaxed unpredictability entropy}
+%\begin{proof}
+%Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+We begin by showing that $Y$ must correctly recover most of the time.
+%\begin{claim}
+%\label{clm:y is recoverable}
+%\begin{align*}
+%\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
+%\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
+%\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
+%\end{align*}
+%\end{claim}
+%\begin{proof}
+%Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+%\begin{itemize}
+%\item Input $x\in \zo^b, s\in\zo^*$.
+%\item Sample $x'\leftarrow B_t(x)$.
+%\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
+%\end{itemize}
+%Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
+The statement of the claim follows as
+%\begin{align*}
+%\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
+%\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
+%\end{align*}
+%\end{proof}
+%We now consider the experiment $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
+\clref{clm:y is recoverable} says that
+%\[
+% \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
+%\]
+%We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
+Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
+%We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+%\begin{itemize}
+%\item Input $s\in\zo^*$.
+%\item Sample $x'\leftarrow \zo^b$.
+%\item Output $\rec(x', s)$.
+%\end{itemize}
+%We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
+%We now show that $\mathcal{I}$ predicts $Y$:
+%\begin{align*}
+%2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
+%&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
+%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
+%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
+%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+%&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+%&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+%&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
+%\end{align*}
+%Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
+%\end{proof}
 

### 2013-03-01 CompFuzzExt.tex
Added discussion of LWE based PRG removed conductor language

@@
 \newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
+\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
 \newcommand{\zo}{\ensuremath{\{0, 1\}}}
@@
 \begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
-An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
+\label{def:fuzzy extractor}
+An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
 \begin{enumerate}
@@
 \label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' (\sketch) and ``recover'' (\rec), with the following properties:
+An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
 \begin{enumerate}
@@
 \end{lemma}
-The main parameter we will be concerned with is the entropy loss of the construction, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).
+The main parameter we will be concerned with is the entropy loss of the construction.
+We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
+
+\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
+A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
+\begin{itemize}
+\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
+\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
+%%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
+If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
+\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
+\end{itemize}
+\end{definition}
+Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
+
+It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then a randomness extractor.
+In the next section, we show this paradigm is difficult to realize.
+
+%\textbf{Note: }A computational fuzzy extractor could also be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).
+We compare the two approaches in \secref{sec:prg based comparison} after presenting our construction.
+%, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).
 %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.
@@
 %=============================================================
-\section{Defining Computational Secure Sketches}
+\section{Impossibility of Computational Secure Sketches}
 \label{sec:defCompFuzzyExtractors}
-We first recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.
+%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp.
+unpredictability) entropy when given a source with $m$ bits of entropy.
+In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
+In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the number of neighbors of a point in the metric space.
+These results are strongest for high entropy sources.
+The results get weaker as we consider sources with lower starting entropy.
+If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.
+
+\subsection{Bounds on Secure Sketches using HILL entropy}
+\label{sec:imp HILL sketch}
+We recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
 
@@
 Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).
-Unfortunately, we show that the unpredictability entropy must decrease with the $O(\log B_t(\cdot))$.
+
+Unfortunately, unpredictability entropy must also depend on $t$.
+An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
+%That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
+The formal statement is below:
 \begin{theorem}
+\label{thm:imp of unp entropy}
 Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
@@
 \end{theorem}
-\begin{proof}
-Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
-Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
-We begin by showing that $Y$ must correctly recover most of the time.
-\begin{claim}
-\label{clm:y is recoverable}
-\begin{align*}
-\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
-\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
-\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
-\end{align*}
-\end{claim}
-\begin{proof}
-Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
-\begin{itemize}
-\item Input $x\in \zo^b, s\in\zo^*$.
-\item Sample $x'\leftarrow B_t(x)$.
-\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
-\end{itemize}
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(W, \sketch(W))  ]\geq 1-\delta$.
-The statement of the claim follows as
-\begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
-\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
-\end{align*}
-\end{proof}
-We now consider a fixed $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
-\clref{clm:y is recoverable} says that
-\[
- \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
-\]
-We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
-We restate this as $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
-We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
-\begin{itemize}
-\item Input $s\in\zo^*$.
-\item Sample $x'\leftarrow \zo^b$.
-\item Output $\rec(x', s)$.
-\end{itemize}
-We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
-We now show that $\mathcal{I}$ predicts $Y$, defining :
-\begin{align*}
-2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
-&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
-&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
-&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
-&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{|B_t(\cdot)|}{2^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
-\end{align*}
-Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
-\end{proof}
-This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The two statements are incomparable.
-\subsection{Defining  Computational Fuzzy Conductors}
-\label{sec:unp secure sketch}
-In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.
-The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.
-However, our sketch outputs a new random variable, this problem does not occur.
+This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
+The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.
+This means we cannot construct a good code out of the points of $Y$.
+In \secref{sec:proof of imp unp entropy}, we prove a stronger version of \thref{thm:imp of unp entropy}, based on a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.
+
+\textbf{Avoiding lower bounds from \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy}:}
+
+The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.
+The results get weaker as we consider sources with lower starter entropy.
+This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.
+This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.
+
+Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the output distribution.
+It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
+This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.
+An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).
+Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).
+It is unknown if a more efficient construction could be achieved using a computational fuzzy conductor that is not also a computational fuzzy extractor.
+\bnote{Not happy with this wording, revise}
+
+%\subsection{Defining  Computational Fuzzy Conductors}
+%\label{sec:unp secure sketch}
+%In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.
+If, the error correcting algorithm outputs a new random variable, bounds do not apply.
 Instead of building a computational sketch, we will build a computational conductor.
 We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
-%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
-%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
+%%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
+%%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
+%%\begin{enumerate}
+%%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
+%%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
+%%\end{enumerate}
+%%\end{definition}
+%%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
+We begin by defining unpredictability entropy:
+%
+%
+%%We now provide a definition of a robust computational sketch using unpredictability entropy:
+%\begin{definition}\label{def:comp secure sketch}
+%A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
 %\begin{enumerate}
-%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
-%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%\end{definition}
-%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
-We begin by defining unpredictability entropy:
-
-%We now provide a definition of a robust computational sketch using unpredictability entropy:
-\begin{definition}\label{def:comp secure sketch}
-A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
-\begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
+%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
+%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
 The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
+%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
-If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
-\end{definition}
-%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.
+%\end{enumerate}
+%We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
+%If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
+%\end{definition}
+%
+%%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
+%In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.
 We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
 
-\section{Lossless conductor based on \class{LWE}}
+\section{Computational Fuzzy Extractor based on \class{LWE}}
 \label{sec:fuzzyCompExt}
@@
 In this section we describe our main construction.
-The secure sketch is computed via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
+Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
 Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors~(not necessarily efficient).
@@
 Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
-Define $\sketch, \rec$ as follows:%The following construction is a computational secure sketch:
+Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
 %Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$.
@@
 \begin{minipage}{3in}
-\textbf{\sketch}
+\textbf{\gen}
 \begin{enumerate}
@@
 \item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
-\item Output $s = (\vA, \vA X+w)$.
-\\
-\\
+\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
+\item Output $(r, p)$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', s)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
-\item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
+\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
+\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
 \item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
-Set $X_{1,..., n/2}$ be the first of $X$.		 
 \item Output $X_{1,...,n/2}$.
@@
 Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) \approx \Hoo(W)$.
+In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|P) \approx \Hoo(W)$.
 Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.
@@
 We describe conditions for efficient decoding in \secref{sec:time main construction}.
-Finally, in \secref{sec:lossless conductor} we describe parameter settings where our construction yields a lossless secure sketch.\lnote{revise after going through the rest}.
+In \secref{sec:lossless extractor} we describe parameter settings where our construction yields a lossless secure sketch.
+In \secref{sec:prg based comparison} we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.\lnote{revise after going through the rest}.
 
@@
 %\end{lemma}
-With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} we can use the code-offset construction in \consref{cons:informal construction} and retain HILL entropy $k\log q$.  
+With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, \consref{cons:informal construction} has many hardcore bits and we use these bits as our key.  
 %\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}.
@@
 If $n$ is large enough and if $|W-W'|_1$ is small enough, $R$ is a unique witness relation with high probability~(see \defref{def:unique witness relation}) and computable in time $O(n^3)$.
+\bnote{Need to get rid of this unique witness stuff, talk about high distance with high probability.}
 We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
@@
 
-\subsection{Lossless Conductor}
-\label{sec:lossless conductor}
-We now state a setting of parameters that yields a lossless conductor.
+\subsection{Lossless Computational Fuzzy Extractor}
+\label{sec:lossless extractor}
+We now state a setting of parameters that yields a lossless construction.
 
@@
 Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
+If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
@@
 
+\subsection{Comparison with \prg based construction}
+\label{sec:prg based comparison}
+In this section we showed how to construct a computational fuzzy extractor by making the whole process ``computational''.
+Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
+In particular, using the same hardness of approximating GAPSVP and SIVP, Applebaum et.
+al.
+use LWE to achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.
+Namely, consider $\vA$ as a public value, they show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.
+Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).
+Both techniques are able to produce a linear stretch on the entropy of the source.
+The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log t)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
+In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
+The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and the uniform distribution.
+We begin to address this second problem in the next section.
+
 \section{\consref{cons:informal construction} with Symbol Fixing Sources}
@@
 In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.
-Showing security of a computational fuzzy conductor for arbitrary high min-entropy distributions is an open problem.
+Showing security of a computational fuzzy extractor for arbitrary high min-entropy distributions is an open problem.
 First we recall the notion of a symbol fixing source~(from~\cite{KZ07}):
@@
 
-\thref{thm:blockLWE} allows us to construct a computational fuzzy conductor from block-fixing sources:
+\thref{thm:blockLWE} allows us to construct a computational fuzzy extractor from block-fixing sources:
 
@@
 
-\section{Computational Fuzzy Extractors}
-In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.
+%\section{Computational Fuzzy Extractors}
+%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.
 We begin with a formal definition of a computational fuzzy extractor:
-\label{sec:comp fuzzy extractors}
-\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-An $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
-\begin{itemize}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-%%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
-If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
-\end{itemize}
-We say that $\gen, \rep$ is $(\epsilon, s_{sec})$-secure with error $\delta$.
-\end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
-
-\textbf{Note: }A computational fuzzy extractor can be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).
-However, the entropy loss due to error correction may mean there is not be enough remaining bits to run a pseudorandom generator.
-Depending on the application, it may be appropriate to make the noise correction procedure and/or extractor computational.
-
-Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
-\begin{lemma}
-Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
+%\label{sec:comp fuzzy extractors}
+%
+%
+%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
+%\begin{lemma}
+%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
 Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.
 Let, $s' = s_{sec}-s_{ext}$, then
-$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
-\end{lemma}
-%  the same paradigm from 
-%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
+%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
+%\end{lemma}
+%%  the same paradigm from 
+%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
 It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
 However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).
-%\begin{definition}
-%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
+%%\begin{definition}
+%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
 Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
-%\end{definition}
-%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-%\label{lem:unp extraction} 
-%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+%%\end{definition}
+%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+%%\label{lem:unp extraction} 
+%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
 Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-%\end{lemma}
-We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
-\begin{lemma}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
+%%\end{lemma}
+%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
+%\begin{lemma}
+%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
 Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
 Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
-\end{lemma}
-%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
+%\end{lemma}
+%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
-%\begin{itemize}
-%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
-%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
-%\end{itemize}
-%\end{lemma}
-%\begin{proof}
-%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
-%\end{proof}
-%
-%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
+%%\begin{itemize}
+%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
+%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
+%%\end{itemize}
+%%\end{lemma}
+%%\begin{proof}
+%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
+%%\end{proof}
+%%
+%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
 
@@
 
+\subsection{Proof of \thref{thm:imp of unp entropy}}
+\label{sec:proof of imp unp entropy}
+Instead of proving \thref{thm:imp of unp entropy}, we will prove a stronger result based on a weaker form of entropy.
+This relaxed definition allows both the variable and the condition to be replaced.
+Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}.
+
+\begin{definition}
+\label{def:relaxed unp entropy}
+For a distribution $(X, Z)$, we say that $X$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a joint distribution $Y, Z'$ such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z'))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+\[
+\Pr[C(Z) = Y ] \leq 2^{-k}
+.\]
+\end{definition}
+
+\begin{theorem}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+
+\end{theorem}
+\begin{proof}
+Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $Y, Z'$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z'))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+We begin by showing that \rec must recover points of $Y$.
+\begin{claim}
+\label{clm:y is recoverable}
+\begin{align*}
+\Pr[\rec(B_t(Y), Z') = Y]&=\\
+\Pr[(y, z)\leftarrow (Y, Z) \wedge y'\leftarrow B_t(y) \wedge \rec(y', z) = y] &\geq 1-\epsilon -\delta.
+\end{align*}
+\end{claim}
+\begin{proof}
+Suppose that $\Pr[\rec(B_t(Y), Z') = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+\begin{itemize}
+\item Input $x\in \zo^b, s\in\zo^*$.
+\item Sample $x'\leftarrow B_t(x)$.
+\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
+\end{itemize}
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
+The statement of the claim follows as
+\begin{align*}
+\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, Z')] &=\\
+\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), Z') = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
+\end{align*}
+\end{proof}
+We now consider the experiment $(y, z)\leftarrow (Y, Z'), y'\leftarrow B_t(y)$ and define the quantity $P_{y' , z, y} = \Pr[\rec(y', z) =y]$.  \clref{clm:y is recoverable} says that 
+\[
+ \Pr[(y, z\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
+\]
+We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, \Pr[B_t(y) = y' | Y=y] = 0$.
+Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
+We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+\begin{itemize}
+\item Input $z\in\zo^*$.
+\item Sample $x\leftarrow \zo^b$.
+\item Output $\rec(x, z)$.
+\end{itemize}
+Let $X$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
+We now show that $\mathcal{I}$ predicts $Y$:
+\begin{align*}
+2^{\tilde{m}}& = \Pr[\mathcal{I}(Z') = Y] \\
+&= \Pr[(y, z)\leftarrow (Y, Z')] \Pr[\mathcal{I}(z) = y]\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', z, y}\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
+\end{align*}
+Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
+\end{proof}
+
+%\bnote{This is the proof for not relaxed unpredictability entropy}
+%\begin{proof}
+%Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+We begin by showing that $Y$ must correctly recover most of the time.
+%\begin{claim}
+%\label{clm:y is recoverable}
+%\begin{align*}
+%\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
+%\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
+%\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
+%\end{align*}
+%\end{claim}
+%\begin{proof}
+%Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+%\begin{itemize}
+%\item Input $x\in \zo^b, s\in\zo^*$.
+%\item Sample $x'\leftarrow B_t(x)$.
+%\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
+%\end{itemize}
+%Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
+The statement of the claim follows as
+%\begin{align*}
+%\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
+%\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
+%\end{align*}
+%\end{proof}
+%We now consider the experiment $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
+\clref{clm:y is recoverable} says that
+%\[
+% \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
+%\]
+%We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
+Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
+%We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+%\begin{itemize}
+%\item Input $s\in\zo^*$.
+%\item Sample $x'\leftarrow \zo^b$.
+%\item Output $\rec(x', s)$.
+%\end{itemize}
+%We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
+%We now show that $\mathcal{I}$ predicts $Y$:
+%\begin{align*}
+%2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
+%&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
+%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
+%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
+%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+%&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+%&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
+%&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
+%\end{align*}
+%Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
+%\end{proof}
+
 %\subsection{Proof of \lemref{lem:i t constant time}}
@@
 Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.
-We will set $g = 2$, that is our sketch will output the first half of $X$.
-This is the setting of parameters in \thref{thm:lossless secure conductor log}.
+We can output a $(g-1)/g$ fraction of $X$ and the bits will be pseudorandom.
+In \thref{thm:lossless secure conductor log}, we set $g=2$ and output the first half of $X$.
+By setting $g>2$, \consref{cons:informal construction} achieves a linear stretch in output size.
 

### 2013-03-01 trunk/CompFuzzExt.tex
Added discussion of LWE based PRG removed conductor language

@@
 These results are strongest for high entropy sources.
-The results get weaker as we consider sources with lower starter entropy.
-This is necessary, if a source contains only codewords of an error correcting code  no sketch is necessary.
+The results get weaker as we consider sources with lower starting entropy.
+If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.
 
@@
 
-Both of the lower bound results rely on the ability to ensure that \rec serves as an error-correcting codes for most points of the output distribution.
-It may be possible to avoid this problem if \rec outputs
-\subsection{Defining  Computational Fuzzy Conductors}
-\label{sec:unp secure sketch}
-In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.
+Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the output distribution.
+It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
+This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.
+An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).
+Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).
+It is unknown if a more efficient construction could be achieved using a computational fuzzy conductor that is not also a computational fuzzy extractor.
+\bnote{Not happy with this wording, revise}
+
+%\subsection{Defining  Computational Fuzzy Conductors}
+%\label{sec:unp secure sketch}
+%In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.
 If, the error correcting algorithm outputs a new random variable, bounds do not apply.
@@
 We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
-%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
-%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
+%%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
+%%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
+%%\begin{enumerate}
+%%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
+%%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
+%%\end{enumerate}
+%%\end{definition}
+%%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
+We begin by defining unpredictability entropy:
+%
+%
+%%We now provide a definition of a robust computational sketch using unpredictability entropy:
+%\begin{definition}\label{def:comp secure sketch}
+%A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
 %\begin{enumerate}
-%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
-%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%\end{definition}
-%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
-We begin by defining unpredictability entropy:
-
-%We now provide a definition of a robust computational sketch using unpredictability entropy:
-\begin{definition}\label{def:comp secure sketch}
-A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
-\begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
+%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
+%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
 The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
+%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
-If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
-\end{definition}
-\textbf{Note:} If some efficient algorithm can take the output of $\rec$ and transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
-This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).
-
-%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.
+%\end{enumerate}
+%We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
+%If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
+%\end{definition}
+%
+%%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
+%In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.
 We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
 
-\section{Lossless conductor based on \class{LWE}}
+\section{Computational Fuzzy Extractor based on \class{LWE}}
 \label{sec:fuzzyCompExt}
@@
 
+\subsection{Comparison with \prg based construction}
+\label{sec:prg based comparison}
+In this section we showed how to construct a computational fuzzy extractor by making the whole process ``computational''.
+Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
+In particular, using the same hardness of approximating GAPSVP and SIVP, Applebaum et.
+al.
+use LWE to achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.
+Namely, consider $\vA$ as a public value, they show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.
+Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).
+Both techniques are able to produce a linear stretch on the entropy of the source.
+The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log t)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
+In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
+The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.
+We begin to address this second problem in the next section.
+
 \section{\consref{cons:informal construction} with Symbol Fixing Sources}

### 2013-03-04 trunk/CompFuzzExt.tex
Run through of paper fixes, not done proofs

@@
 \label{sec:preliminaries}
-For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
+For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
+The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
 %the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
@@
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.
+%We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.
 For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
 We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
-For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
+For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 Secure sketches are the main technical tool in the construction of fuzzy extractors.
-They produces a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
+Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
 \begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
@@
 The main parameter we will be concerned with is the entropy loss of the construction.
+In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
 We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
@@
 If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
+\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
 \end{itemize}
@@
 
-It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then a randomness extractor.
+It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).
 In the next section, we show this paradigm is difficult to realize.
@@
 In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the number of neighbors of a point in the metric space.
-These results are strongest for high entropy sources.
+In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space.
+%These results are strongest for high entropy sources.
 The results get weaker as we consider sources with lower starting entropy.
@@
 
-Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
+%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
 This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
-  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
+%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
 %The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.
@@
 When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.
-Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y$ with high probability.
-In particular, $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.
-This means we can construct a set $C$ out of the points in the support of $Y$.
-Then $C$ will be an error correcting code and $\rec$ an efficient decoder.
+Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y, \sketch(W)$ with high probability.
+In particular, $\Pr [s\leftarrow \sketch(W) \wedge y\leftarrow Y_s\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y ]\geq 1-\epsilon$.
+This means we can construct a large set $C$ from the support of $Y$.
+$C$ will be an error correcting code and $\rec$ an efficient decoder.
 We can then use standard arguments to turn this code into an information theoretic sketch.
@@
 \end{definition}
-This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$.
-\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.
+This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.
 For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
@@
 \label{lem:averageToMaximalError}
-Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
+Let $C$ be a distribution over space $\mathcal{M}$ with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
 There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
@@
 Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
-Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
+Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 
-It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.
+%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
+For the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
 The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
@@
 Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
 $4(\epsilon+\delta)$. 
@@
 \end{definition}
-We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy}$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfied \defref{def:secure sketch} with the security requirement replaces with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
+We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
 We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
@@
 \end{lemma}
-Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).
-
-Unfortunately, unpredictability entropy must also depend on $t$.
-An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
+Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
+Unfortunately, the unpredictability entropy conditioned on the sketch must recreate with $t$.  
+%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
 %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
@@
 \label{thm:imp of unp entropy}
-Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
 \end{theorem}
@@
 This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.
-
-Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the output distribution.
+This same situation occurs when considering lower bounds for information-theoretic sketches.
+
+Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the indistinguishable distribution.
 It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
@@
 Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).
-It is unknown if a more efficient construction could be achieved using a computational fuzzy conductor that is not also a computational fuzzy extractor.
-\bnote{Not happy with this wording, revise}
+It may be possible to achieve significantly better parameters with a construction that is a computational fuzzy conductor~(but not a computational fuzzy extractor) and then applying an extractor.
+We leave this as an open problem.
 
@@
 In this section we describe our main construction.
+In this section, we consider only a uniform source $W$, we consider other distributions in \secref{sec:LWE block fixing sources}.
 Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors~(not necessarily efficient).
+Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors.
 We provide an informal description below.
@@
 \begin{construction}
-Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
+Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
 Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
@@
 \item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
-\item Output $X_{1,...,n/2}$.
+\item Output $r = X_{1,...,n/2}$.
 \end{enumerate}
@@
 Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|P) \approx \Hoo(W)$.
-Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.
+In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.
+Furthermore, this construction is only useful if $\mathcal{I}_t$ can be efficiently implemented.
+We demonstrate an efficient $\mathcal{I}_t$ that corrects a super-polynomial number of error patterns in polynomial time.
 
@@
 We describe conditions for efficient decoding in \secref{sec:time main construction}.
-In \secref{sec:lossless extractor} we describe parameter settings where our construction yields a lossless secure sketch.
-In \secref{sec:prg based comparison} we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.\lnote{revise after going through the rest}.
+In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.
+In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.
 
@@
 
-Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} shows that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard.
+Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
@@
 Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\alpha$ be the discretized Gaussian distribution with variance $(\alpha q)^2/2\pi$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))$-secure for all probabilistic distinguisher $D$, where $\epsilon = \ngl(n)$.
+If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.
+That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_q^m))\leq \epsilon$.
 
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$secure, where $\epsilon = \ngl(n)$.
+Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
 \end{lemma}
 
-We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
-This says that if $\distLWE$ is secure then $X$ has many hardcore bits.
+To extract pseudoranom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
+The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
 We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
@@
 Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
+If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$.
 \end{lemma}
+\bnote{Need to check on gap in the reduction, the claim here is that there is no loss.}
 
@@
 %\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
-\consref{cons:informal construction} is only useful if $\mathcal{I}_t$ can be efficiently implemented.  We now present a particular $\mathcal{I}_t$ and consider its efficiency:
+\consref{cons:informal construction} is only useful if $\mathcal{I}_t$ can be efficiently implemented.
+We now present a particular $\mathcal{I}_t$ and consider its efficiency:\bnote{Unique witness.
+BAD!!!}
 
@@
 \item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this is $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
-\item Compute $x = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $R(x, \vA, \vect{C}) \neq 1$.  Go to step (2).
-\item Output $x$.
+\item Compute $X = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $R(X, \vA, \vect{C}) \neq 1$.  Go to step (2).
+\item Output $X$.
 \end{enumerate}
@@
 Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
+Let $W$ be uniform over $\zo^{(c+d)nb/d}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
@@
 \thref{thm:lossless secure conductor log} shows that a computational fuzzy conductor can be built without incurring any entropy loss.
-This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.
-A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.
-We begin to provide an answer in \secref{sec:LWE block fixing sources}.
+This is essentially due to $\vA X+W$ looking like a uniformly random point and thus providing no information about either $X$ or $W$.
+%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.
 
@@
 \label{sec:prg based comparison}
-In this section we showed how to construct a computational fuzzy extractor by making the whole process ``computational''.
-Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
+In this section we to constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
 In particular, using the same hardness of approximating GAPSVP and SIVP, Applebaum et.
@@
 \begin{definition}
-Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m - \alpha)b$ and for all $W_i$ one of the following conditions is met:
+Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $m$-\emph{symbol fixing source} if $H_\infty(W)\geq mb$ and for all $W_i$ one of the following conditions is met:
 \begin{itemize}
@@
 For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$.
-The decisional learning with error problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
+The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
 \end{problem}
@@
 \end{theorem}
+\bnote{We should add some exposition here.  Some intuition about the proof.}
 
@@
 Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)n/d+\alpha)b}$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.
-There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
+Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)nb/d+\alpha b}$.
+Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms.
+There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
@@
 \begin{theorem}
-Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
 
@@
 \begin{proof}
-Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
 Let $Y, Z'$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z'))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
 We begin by showing that \rec must recover points of $Y$.
@@
 \begin{itemize}
-\item Input $x\in \zo^b, s\in\zo^*$.
+\item Input $x\in Z^n, s\in\zo^*$.
 \item Sample $x'\leftarrow B_t(x)$.
@@
 \end{itemize}
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in Z^n$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
 The statement of the claim follows as
@@
 \[
- \Pr[(y, z\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
+ \Pr[(y, z\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
 \]
@@
 \item Input $z\in\zo^*$.
-\item Sample $x\leftarrow \zo^b$.
+\item Sample $x\leftarrow Z^n$.
 \item Output $\rec(x, z)$.
@@
 &= \Pr[(y, z)\leftarrow (Y, Z')] \Pr[\mathcal{I}(z) = y]\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', z, y}\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[X = y' ] P_{y', z, y}\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \frac{|Z|^{-n}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq \frac{|B_t(\cdot)|}{|Z|^n} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq \frac{|B_t(\cdot)|}{|Z|^n}(1-\epsilon - \delta)
 \end{align*}
-Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
+Finally converting to entropy, one has $\tilde{m}\leq n\log |Z|-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
 \end{proof}

### 2013-03-05 trunk/CompFuzzExt.tex
Marked up paper with some current problems

@@
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
+If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
+For the Hamming metric over $Z^n$ the size of $B_t(\cdot) = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $, for clarity we express this value as $B_t(\cdot)$.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 
-We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
+We can now formalize the intuition above.
+A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
@@
 Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
-Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
+Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-$4(\epsilon+\delta)$. 
+$4(\epsilon+t\delta)$. 
 %Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
@@
 \end{lemma}
-\bnote{Need to check on gap in the reduction, the claim here is that there is no loss.}
+\bnote{Need to check on gap in the reduction, the claim here is that there is no loss.  I think it will go from $\ngl, \poly$ to $\ngl', \poly'$}
 
@@
 \begin{enumerate}
-\item Input $\vA , \vect{C} = \vA X + E - E'$
+\item Input $\vA , \vect{C} = \vA X + W - W'$
 \item Randomly select rows without replacement $i_1,..., i_n\leftarrow [1,m]$.  
@@
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = H_\infty(W)$
 % for following parameters:
@@
 Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms.
-There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
+There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\vA, \vA X+W) = H_\infty(W)$ for %the following parameters:
 %\[
@@
 
+\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
 \begin{proof}
@@
 Let $\D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.
-That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx'$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
+That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
 Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.
@@
 \item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
-\item If $\vb'$ is uniformly distributed then $\vb$ is uniformly distributed.
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists x$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve$ are $0$.
+\item If $\vb'$ is uniformly distributed then $\vb$ is uniformly distributed.\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
+\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
 \end{enumerate}
@@
 
-\item Initialize $\vA^* = (\va^*_1, \ldots, \va^*_{m+\alpha})^T = \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)$.
+\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)$.
 \item \label{step:randomization}
@@
 The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
+\bnote{We need to justify these steps better.}
+\bnote{Is it really standard to go to lower case for the rows?}
 We have the following for all $i=1,..., m+\alpha$:
@@
 That is, each $b_i^*$ is uniformly and independently random.
-After step~\ref{step:randomization} each $b_i$ is a fresh random linear combination of random values:
+After step~\ref{step:randomization} each $b_i$ is a fresh random linear combination of random values:\bnote{We need to better argue this property.}
 \[
@@
 \begin{proof}
-Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that for all $t'\le t$
+Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that for all $t'\le t$
 \[
@@
 \]
-For $w$ denote by $\epsilon_w = \Pr[w'\leftarrow \sample(w, t') \wedge \rec(w') \neq w]$.  Then by Markov inequality:
+For $w$ denote by $\epsilon_w = \Pr[w'\leftarrow \sample(w, t') \wedge \rec(w') \neq w]$.
+\bnote{There is something weird going on here.
+The Markov inequality doesn't connect to what is below it.}Then by Markov inequality:
 \[
-\Pr_{w\in W}[ \epsilon_w \leq 2\expe_{w\leftarrow W} [\epsilon_w ] = 2\epsilon]\geq \frac{1}{2}
+\Pr_{w\in W}[ \epsilon_w \leq 2\expe_{w\leftarrow W} [\epsilon_w ] ] = \Pr_{w\in W} [\epsilon_w \le 2\epsilon ] \geq \frac{1}{2}
 \]
@@
 \end{enumerate}
-  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-\delta$.  Since 
-$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon.$ then $\Pr[D(Y, SS(W)) = 1]>1-\epsilon-\delta$.
-By Markov inequality there exists a set $S_W$ such that $\Pr[S_W]\geq 1/2$ and $\Pr[ D(Y, s) =1 | \sketch(W) = s \wedge s\in S_W]> 1- 2(\epsilon + \delta)$.
+  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
+$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon.$ then $\Pr[D(Y, SS(W)) = 1]>1-\epsilon-t\delta$.
+By Markov inequality there exists a set $S_W$ such that $\Pr[S_W]\geq 1/2$ and $\Pr[ D(Y, s) =1 | \sketch(W) = s \wedge s\in S_W]> 1- 2(\epsilon + t\delta)$.
 Consider the random variable $1_{S_W}$ that is $1$ when $s\in S_X$ and otherwise.
-Then
+Then \bnote{I am splitting average min-entropy based on an indicator variable, everyone is okay with this?}
 \[
@@
 Thus, for all $t', 1\leq t'\leq t$ on a random $y$
-\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]\geq 1-2(\epsilon+\delta).\]  
+\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]\geq 1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
+Thus,  $Y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
 \end{proof}
@@
 \label{def:relaxed unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a joint distribution $Y, Z'$ such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z'))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+For a distribution $(X, Z)$, we say that $X$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a joint distribution $Y, Z'$ such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z'))\leq \epsilon$, and for all circuits $C$ of size at most $s_{sec}$,
 \[
@@
 \begin{theorem}
-Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 If $s_{sec} = \Omega(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
@@
 \end{itemize}
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in Z^n$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in Z^n$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) )= W)  ]\geq 1-\delta$.
 The statement of the claim follows as
@@
 \[
- \Pr[(y, z\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
+ \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
 \]
@@
 We first note that $R(X, (\vA, \vA X+W))$ is computable in time $O(n^3\log q)$ by computing $AX+(W-W')- AX$ and checking if all dimensions have magnitude at most $|W|_\infty$ and at most $t$ dimensions have nonzero magnitude.
-We consider the expected number of iterations in step 2 when $t+1\leq m/n$.
+We consider the expected number of iterations in step 2 when $t\leq d\log n\left(\frac{m}{n}-1\right)$.
 Steps 3 and 4 can be accomplished in time $n^3\log q $.
@@
 \begin{align*}
-\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{n-1}\left( 1-\frac{\frac{dm\log n}{n}-1}{m-i}\right)\\
+\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{n-1}\left( 1-\frac{d\log n\left(\frac{m}{n}-1\right)}{m-i}\right)\\
 &\geq  \prod_{i=0}^{n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-n}{m-i}\right)\right)\geq \prod_{i=0}^{n-1}\left( 1-\frac{d\log n}{n}\right) \\
@@
 In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
-In this section, we will assume that the inverter runs in time proportional to the number of errors~(\lemref{lem:i t poly time}).
 We begin by reviewing the parameters that make up our construction:
@@
 \begin{align*}
-n_0&< n\\
+n_0&< n -k \\
 t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
@@
 To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
-Finally we assume that $t = d \log n(m/n-1)$~(this means we have only as many dimensions as necessary for polynomial time recovery):
-\begin{align*}
-n_0&< n\\
+Finally we assume that $t = d \log n(m/n-1)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
+\begin{align*}
+n_0&< n -k \\
 m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
@@
 
-Assuming $n_0 < n$ and let $t= c\log n$ we get the following setting:
+Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
 \begin{align*}
@@
 \end{align*}
-Furthermore, we get decoding in time $O(n^{2d}(n^3\log n+s_{ver}))$.
-We can output a $(g-1)/g$ fraction of $X$ and the bits will be pseudorandom.
+Furthermore, we get decoding in time $O(n^{2d}(n^3\log n))$.
+We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).
+The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.
 In \thref{thm:lossless secure conductor log}, we set $g=2$ and output the first half of $X$.
-By setting $g>2$, \consref{cons:informal construction} achieves a linear stretch in output size.
+This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.
+Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
 

### 2013-03-05 trunk/CompFuzzExt.tex
Thm 5.3 and adding the notation to Prem.

@@
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
+During the presentation, we denote bold letters to be vectors or matrix, capitalized letters to be random variables, and lower case letter to be the elements in the vector.
 
@@
 
-\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
+%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
 \begin{proof}
@@
 \item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
-\item If $\vb'$ is uniformly distributed then $\vb$ is uniformly distributed.\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
+\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
+%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
 \item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
@@
 \bnote{Is it really standard to go to lower case for the rows?}
+\xnote{lower case for vectors, which is row vector in the matrix}
+
+\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
 We have the following for all $i=1,..., m+\alpha$:
@@
 \label{clm:random b}
-If $\D'$ is provided with input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random then $\vb$ is uniformly random.
+If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
 \end{claim}
 \begin{proof}
-As before this is clearly satisfied before step~\ref{step:randomization}.
-That is, each $b_i^*$ is uniformly and independently random.
-After step~\ref{step:randomization} each $b_i$ is a fresh random linear combination of random values:\bnote{We need to better argue this property.}
+Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.
+After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
 \[
@@
 \]
+%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each
+
+$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{I need show more work on this, maybe?}
 Thus, each of these values is uniformly and independently random.

### 2013-03-07 CompFuzzExt.tex
Adding statement of theorem from micciancio and peikert

@@
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.
+%We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.
 For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
 We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
-For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
+For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
+If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
+For the Hamming metric over $Z^n$ the size of $B_t(\cdot) = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $, for clarity we express this value as $B_t(\cdot)$.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
+During the presentation, we denote bold letters to be vectors or matrix, capitalized letters to be random variables, and lower case letter to be the elements in the vector.
 
@@
 Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
-Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
+Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-$4(\epsilon+\delta)$. 
+If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+$4(\epsilon+t\delta)$. 
 %Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$secure, where $\epsilon = \ngl(n)$.
+Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n/2$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
 \end{lemma}
 
-We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
-This says that if $\distLWE$ is secure then $X$ has many hardcore bits.
+To extract pseudoranom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
+The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
 We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
@@
 Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
+If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}'}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ where $s_{sec}' \approx s_{sec} - n^3$.
 \end{lemma}
@@
 \begin{enumerate}
-\item Input $\vA , \vect{C} = \vA X + E - E'$
+\item Input $\vA , \vect{C} = \vA X + W - W'$
 \item Randomly select rows without replacement $i_1,..., i_n\leftarrow [1,m]$.  
 \item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this is $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
-\item Compute $x = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $R(x, \vA, \vect{C}) \neq 1$.  Go to step (2).
-\item Output $x$.
+\item Compute $X = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $R(X, \vA, \vect{C}) \neq 1$.  Go to step (2).
+\item Output $X$.
 \end{enumerate}
@@
 Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
+Let $W$ be uniform over $\zo^{(c+d)nb/d}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = H_\infty(W)$
 % for following parameters:
@@
 In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
-The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and the uniform distribution.
+The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.
 We begin to address this second problem in the next section.
 
-\section{\consref{cons:informal construction} with Symbol Fixing Sources}
+\section{\consref{cons:informal construction} with Nonuniform Sources}
+\subsection{\consref{cons:informal construction} with Symbol Fixing Sources}
 \label{sec:LWE block fixing sources}
@@
 Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)n/d+\alpha)b}$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.
-There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
+Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)nb/d+\alpha b}$.
+Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/2$) using quantum algorithms.
+There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\vA, \vA X+W) = H_\infty(W)$ for %the following parameters:
 %\[
@@
 \end{theorem}
+
+\subsection{\consref{cons:informal construction} with slightly deficient sources}
+\label{sec:DP general error LWE}
+In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.
+We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.
+This result allows us to argue security for an arbitrary distribution that is nearly high entropy.
+This result should be seen as a complement to the proceeding sections.
+It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure conductor log}.
+Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
+\begin{theorem}
+Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.
+Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.
+Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.
+If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
+\end{theorem}
+\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.
+In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.
+The only requirement in the proof is that $|\chi|\geq m\log \rho$.
+Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.
+This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.
+This means we support all distributions whose entropy gap is no more than $m$ bits.
+
+\bnote{Need to continue and go through their Lemma 2.1 and 2.4 to be sure I believe this.  Everything else should go through fine.}
+
+\bnote{We need to turn this hardness result into a statement about computational fuzzy extractors.  Use the Akavia result.  Then we need to suggest parameters.  How much detail should we go into?}
 
@@
 
+%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
 \begin{proof}
@@
 \item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
-\item If $\vb'$ is uniformly distributed then $\vb$ is uniformly distributed.
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists x$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve$ are $0$.
+\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
+%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
+\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
 \end{enumerate}
@@
 The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
+\bnote{We need to justify these steps better.}
+\bnote{Is it really standard to go to lower case for the rows?}
+\xnote{lower case for vectors, which is row vector in the matrix}
+
+\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
 We have the following for all $i=1,..., m+\alpha$:
@@
 \label{clm:random b}
-If $\D'$ is provided with input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random then $\vb$ is uniformly random.
+If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
 \end{claim}
 \begin{proof}
-As before this is clearly satisfied before step~\ref{step:randomization}.
-That is, each $b_i^*$ is uniformly and independently random.
-After step~\ref{step:randomization} each $b_i$ is a fresh random linear combination of random values:
+Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.
+After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
 \[
@@
 \begin{theorem}
-Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} = \Omega(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
 
@@
 \end{itemize}
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in Z^n$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) )= W)  ]\geq 1-\delta$.
 The statement of the claim follows as
@@
 \[
- \Pr[(y, z\leftarrow (Y, Z')] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
+ \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
 \]

### 2013-03-07 trunk/CompFuzzExt.tex
Adding statement of theorem from micciancio and peikert

@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
+Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n/2$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
 \end{lemma}
@@
 Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$.
+If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}'}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ where $s_{sec}' \approx s_{sec} - n^3$.
 \end{lemma}
-\bnote{Need to check on gap in the reduction, the claim here is that there is no loss.  I think it will go from $\ngl, \poly$ to $\ngl', \poly'$}
 
@@
 
-\section{\consref{cons:informal construction} with Symbol Fixing Sources}
+\section{\consref{cons:informal construction} with Nonuniform Sources}
+\subsection{\consref{cons:informal construction} with Symbol Fixing Sources}
 \label{sec:LWE block fixing sources}
@@
 Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)nb/d+\alpha b}$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms.
+Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/2$) using quantum algorithms.
 There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
@@
 \end{theorem}
+
+\subsection{\consref{cons:informal construction} with slightly deficient sources}
+\label{sec:DP general error LWE}
+In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.
+We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.
+This result allows us to argue security for an arbitrary distribution that is nearly high entropy.
+This result should be seen as a complement to the proceeding sections.
+It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure conductor log}.
+Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
+\begin{theorem}
+Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.
+Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.
+Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.
+If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
+\end{theorem}
+\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.
+In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.
+The only requirement in the proof is that $|\chi|\geq m\log \rho$.
+Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.
+This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.
+This means we support all distributions whose entropy gap is no more than $m$ bits.
+
+\bnote{Need to continue and go through their Lemma 4.1 and 4.4 to be sure I believe this.  Everything else should go through fine.}
+
+\bnote{We need to turn this hardness result into a statement about computational fuzzy extractors.  Use the Akavia result.  Then we need to suggest parameters.  How much detail should we go into?}
 

### 2013-03-07 CompFuzzExt.tex
thm 5.3 cleaned...

@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n/2$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
+Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
 \end{lemma}
@@
 Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}'}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ where $s_{sec}' \approx s_{sec} - n^3$.
+If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$.
 \end{lemma}
+\bnote{Need to check on gap in the reduction, the claim here is that there is no loss.  I think it will go from $\ngl, \poly$ to $\ngl', \poly'$}
 
@@
 
-\section{\consref{cons:informal construction} with Nonuniform Sources}
-\subsection{\consref{cons:informal construction} with Symbol Fixing Sources}
+\section{\consref{cons:informal construction} with Symbol Fixing Sources}
 \label{sec:LWE block fixing sources}
@@
 Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)nb/d+\alpha b}$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/2$) using quantum algorithms.
+Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms.
 There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
@@
 \end{theorem}
-
-\subsection{\consref{cons:informal construction} with slightly deficient sources}
-\label{sec:DP general error LWE}
-In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.
-We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.
-This result allows us to argue security for an arbitrary distribution that is nearly high entropy.
-This result should be seen as a complement to the proceeding sections.
-It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure conductor log}.
-Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
-\begin{theorem}
-Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.
-Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.
-Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.
-If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
-\end{theorem}
-\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.
-In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.
-The only requirement in the proof is that $|\chi|\geq m\log \rho$.
-Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.
-This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.
-This means we support all distributions whose entropy gap is no more than $m$ bits.
-
-\bnote{Need to continue and go through their Lemma 2.1 and 2.4 to be sure I believe this.  Everything else should go through fine.}
-
-\bnote{We need to turn this hardness result into a statement about computational fuzzy extractors.  Use the Akavia result.  Then we need to suggest parameters.  How much detail should we go into?}
 
@@
 \bnote{We need to justify these steps better.}
-\bnote{Is it really standard to go to lower case for the rows?}
 \xnote{lower case for vectors, which is row vector in the matrix}
 
-\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
 We have the following for all $i=1,..., m+\alpha$:
 \begin{align*}
-\va_i \vx^* + e_i^* &=\va^*_i\vx^*+\sum_{k=1}^\alpha \gamma_{i} \va^*_{m+k}\vx^*+e_i^*\\
-&= \va_i^*\vx^* + e_i^* + \sum_{k=1}^\alpha \mathbf{\gamma}_{i} \va^*_{m+k}\vx^*\\
-&= b_i^* + \sum_{k=1}^\alpha\gamma_i \va_{m+k}^* \vx^*\\
-&= b_i^* + \sum_{k=1}^\alpha \gamma_i \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
+\va_i \vx^* + e_i^* &= \sum_{j=1}^{n+\alpha} \vA_{ij} x^*_j + e_i^*\\
+& = \sum_{j=1}^{n+\alpha}\left((\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j})x^*_j\right) + e_i^*\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x^*_j \\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x^*_j\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
 &= b_i^* +\sum_{k=1}^\alpha\gamma_i b_{m+k}^*= b_i
@@
 
-$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{I need show more work on this, maybe?}
+$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{It need show more work on this, maybe?}
 Thus, each of these values is uniformly and independently random.

### 2013-03-08 CompFuzzExt.tex
Cleaning up Theorem 5.3

@@
 \begin{proof}
-Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then define $\vx^*$ as:
+Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
+Then define $\vx$ as:
 \[
-x^*_i = \begin{cases}
+x_i = \begin{cases}
 x_i', & \text{if }1\leq i\leq n \\
-b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
+b_{m+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
 \end{cases}
 \]
-Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).
+We denote by $\vA^*$ the matrix before step~\ref{step:randomization}.
+The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$~(where $\ve$ is $\ve'$ with $\alpha$ 0s appended).
 Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
 %For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).
-Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
+For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  We now show that for all rows $i$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
 %, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
 The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-\bnote{We need to justify these steps better.}
-\xnote{lower case for vectors, which is row vector in the matrix}
-
-We have the following for all $i=1,..., m+\alpha$:
-\begin{align*}
-\va_i \vx^* + e_i^* &= \sum_{j=1}^{n+\alpha} \vA_{ij} x^*_j + e_i^*\\
-& = \sum_{j=1}^{n+\alpha}\left((\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j})x^*_j\right) + e_i^*\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x^*_j \\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x^*_j\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x^*_j + e_i^* + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
-&= b_i^* +\sum_{k=1}^\alpha\gamma_i b_{m+k}^*= b_i
+We have the following for all rows $i$:
+\begin{align*}
+\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
+& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
+&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
 \end{align*}

### 2013-03-08 trunk/CompFuzzExt.tex
Working on the stronger version of b random claim

--- 2013-03-05 trunk/CompFuzzExt.tex
@@
 \newcommand{\vb}{\vect{b}}
+\newcommand{\vgamma}{\mathbf{\Gamma}}
 \newcommand{\vt}{\vect{t}}
@@
 \item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
 
@@
 \begin{proof}
-Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then define $\vx^*$ as:
+Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
+Then define $\vx$ as:
 \[
-x^*_i = \begin{cases}
+x_i = \begin{cases}
 x_i', & \text{if }1\leq i\leq n \\
-b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
+b_{m+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
 \end{cases}
 \]
-Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).
+We denote by $\vA^*$ the matrix before step~\ref{step:randomization}.
+The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$~(where $\ve$ is $\ve'$ with $\alpha$ 0s appended).
 Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
 %For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).
-Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
+For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  We now show that for all rows $i$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
 %, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
 The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-\bnote{We need to justify these steps better.}
-\bnote{Is it really standard to go to lower case for the rows?}
-We have the following for all $i=1,..., m+\alpha$:
-\begin{align*}
-\va_i \vx^* + e_i^* &=\va^*_i\vx^*+\sum_{k=1}^\alpha \gamma_{i} \va^*_{m+k}\vx^*+e_i^*\\
-&= \va_i^*\vx^* + e_i^* + \sum_{k=1}^\alpha \mathbf{\gamma}_{i} \va^*_{m+k}\vx^*\\
-&= b_i^* + \sum_{k=1}^\alpha\gamma_i \va_{m+k}^* \vx^*\\
-&= b_i^* + \sum_{k=1}^\alpha \gamma_i \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
-&= b_i^* +\sum_{k=1}^\alpha\gamma_i b_{m+k}^*= b_i
+We have the following for all rows $i$:
+\begin{align*}
+\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
+& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
+&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
 \end{align*}
@@
 \]
+%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each
+
+$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{It need show more work on this, maybe?}
 Thus, each of these values is uniformly and independently random.
@@
 %\end{align*}
+
+\begin{claim}
+If the pair $(\vA', \vb')$ is uniformly distributed, then the pair $(\vA, \vb)$ is uniformly distributed.
+\end{claim}
+\begin{proof}
+Assume that $(\vA', \vb')$ is uniformly distributed.
+By \clref{cl:randomMatrixDist}, $\vA$ is uniformly distributed.
+Thus, it suffices to show that $\vb | \vA$ is uniformly distributed.
+Let $\vb^*$ be the vector generated in step~\ref{step:b generation} and note that $\vb^*$ is uniformly random.
+We show  a stronger claim that $\vb |( \vA, \vA', \vR)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i,j}$.
+
+ The matrix $\vgamma$ is a deterministic function of $(\vA, \vA', \vR)$.
+Thus, $\vb | (\vA, \vA', \vR) \overset{d}= \vb | (\vA, \vA', \vR, \vgamma)$.
+The only dependence of $\vb$ on $(\vA, \vA', \vR, \vgamma)$ is in the matrix $\vgamma$.
+Thus, $ \vb | (\vA, \vA', \vR, \vgamma) \overset{d}= \vb | \vgamma$.
+Recall that $\vb = \vb^* +  \left(\begin{array}{c | c}\mathbf{0} &\vgamma\end{array}\right)\vb^*$.
+Let $\vT = \vect{I}+  \left(\begin{array}{c | c}\mathbf{0} & \vgamma \end{array}\right)$.
+Since $\vT$ is a deterministic function of $\vgamma$, $\vb | \vgamma \overset{d} = \vb | \vT$.
+
+ \bnote{Now we want to say that $\vb$ is uniformly distributed since $\vb'$ is.
+If $\vT$ exists we can just that $\vb | \vT = (\vT^{-1} \vb )| \vT = \vb' | \vT = U | \vT$.
+It does with very high probability, but I don't want to add this restriction.
+Is there a way to get around this problem?}
+%\[
+%\vA=  \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)
+%\]
+%\begin{align*}
+%(\vA, \vb) =  \left(\left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) \right) , \left(\vb' + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \vb'\right)
+%\end{align*}
+\end{proof}
+\bnote{Remember this isn't good enough.  We need the enhanced claim above.}
 Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 

### 2013-03-14 trunk/CompFuzzExt.tex
Revised proof for theorem 5.3

@@
 \usepackage{color}
+\usepackage{framed}
 \usepackage{algpseudocode}
@@
 \newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
+\newcommand{\rank}{\ensuremath{\mathtt{rank}}\xspace}
 \newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
@@
 \newcommand{\vA}{\vect{A}}
+\newcommand{\vW}{\vect{W}}
 \newcommand{\vR}{\vect{R}}
@@
 \label{thm:blockLWE}
-Let $n$ be a security parameter and define $q, m = \poly(n)$.
+Let $n$ be a security parameter and define $q, m = \poly(n)$, let $\alpha < q$ and $\beta = \omega(1)$.
 Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
-Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha, m+\alpha, q, W}$ w/ symbol fixing sources problem.
+Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha + \beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
 \end{theorem}
@@
 
+\section{Proof of Theorem \ref{thm:blockLWE} Revised}
+\label{sec:proof of block theorem}
+
+%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
+\begin{proof}
+We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.
+If the blocks are fixed to some other value the reduction is essentially the same.
+For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
+
+%It should be clear to the reader where the reduction differs for another block fixing source.\lnote{I don't like the phrasing; maybe we should say that if the blocks are fixed to some non-0 value, the reduction is essentially the same}
+
+Let $n$ be a security parameter, $m = \poly(n), q = \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $\mod q$ and this notation is omitted.  
+Let $\D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where $\alpha$ of the equations have no error added.
+That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
+Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.
+We assume that,
+\[
+|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
+\]
+
+We build a distinguish $\D'$ that given $m$ samples over $n$ variables distinguisher LWE instances from uniform.
+Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
+Our goal is to prepare a random block fixing instance from the random instance we are given.
+The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
+
+We first note that $\mathcal{D'}$ has an advantage only when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
+\begin{claim}
+Let $S \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(S)<\alpha]<1 - e^{-1/\beta} = \ngl(n)$
+\end{claim}
+\begin{proof}
+\bnote{Note happy with this writeup.  Draws on On the Rank of Random Matrices by C. Cooper}
+The probability that all $\alpha$ rows is linearly independent is the successive probability that each row lies in the span of the previous rows, this probability is:
+\begin{align*}
+\Pr[\rank(\vS) = \alpha] &= \prod_{i=1}^\alpha\left( 1-q^i/q^{\alpha+\beta}\right)
+=\prod_{i=1}^\alpha\left( 1-q^{i-\alpha- \beta}\right)\\
+&\geq\prod_{i=1}^\alpha\left( 1- q^{-\beta}\right) = \left(1-\frac{1}{q^{\beta}}\right)^\alpha
+\end{align*}
+\end{proof}
+Recall that $\alpha < q$, thus,
+\begin{align*}
+\left(1-\frac{1}{q^{-\beta}}\right)^\alpha &\geq \left(1-\frac{1}{q^{\beta}}\right)^q\\
+&=\left(\left(1-\frac{1}{q^{\beta}}\right)^{q^{\beta}}\right)^{1/\beta}\approx e^{-1/\beta}
+\end{align*}
+\begin{corollary}
+$
+|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
+$
+\end{corollary}
+
+Thus, we only consider the case where $\rank(\vS) = \alpha$.  
+It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
+\begin{enumerate}
+\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
+%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
+\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
+\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
+\end{enumerate}
+
+\begin{figure}[t]
+\begin{framed}
+\begin{enumerate}
+\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
+\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
+\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$.
+\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
+\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
+\item Initialize $\vW \in \Fq^{n\times \alpha+\beta}$ to be the zero matrix.
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
+\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
+\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
+\subitem For $j=1,..., n$:
+\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
+\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
+\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
+\item \label{step:randomization}
+For {$i=1,..., n$}:
+\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
+\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
+\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
+\item Run $\D$ on input $\vA, \vb$.
+\item Output $\D$'s output.
+\end{enumerate}
+\end{framed}
+\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
+\label{fig:perfectLWEreduction}
+\end{figure}
+
+\begin{claim}
+\label{cl:randomMatrixDist}
+The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix with $\rank(\vS) = \alpha$.
+\end{claim}
+\begin{proof}
+It should be clear that $\vR, \vS$ are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
+The quadrant represented by $\vA'$ remains random after step~\ref{step:randomization} as we are adding uncorrelated random values.
+For the matrix $\vW$, the columns whose indices are not included in $T$ are random.  They are the addition of a randomly generated value and uncorrelated random values.
+
+Thus, we restrict attention to the columns of $\vW$ whose indices are in $T$.
+We denote this restricted matrix by $\vW_T$.
+Fix a particular row $i$.
+Then $\vW_{i, T} = \gamma_i \vS_{T}$.
+Since $\vS_T$ is full rank and $\gamma_i$ is uniformly generated, $\vW_{i, T}$ is uniformly generated.
+
+Thus, the entire matrix $\vA$ after step~\ref{step:randomization} is uniformly generated conditioned on $\rank(S) = \alpha$.
+% In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
+Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.
+Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.
+Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5.
+For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number.
+Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors.
+Therefore, the entire matrix $\vA$ is a truly random matrix.
+This completes the claim.
+\end{proof}
+\begin{claim}
+\label{cl:random ax+e}
+If $\D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
+\end{claim}
+\begin{proof}
+Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
+Then define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ is uniformly generated if $i\not\in T$.
+Denote by $\vS_{T^c}$ the restriction of $\vS$ to the columns whose indices are not $T$~(similarly for the vector $\vx$).
+
+Denote by $\vx_T$ the restriction of $\vx$ to the indices in $T$.  Then, define $\vx$ as the solution to the following system of equations~(a solution exists as $\vS_T$ is full rank).
+\[
+\vS_T  \vx_T = \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
+\]
+Denote by $\vA^*$ the matrix before step~\ref{step:randomization}.
+The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$~(where $\ve$ is $\ve'$ with $\alpha$ 0s appended).
+Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
+%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
+We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
+%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
+The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
+We have the following for $1\leq i\leq m$:
+\begin{align*}
+\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
+&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx= b_i^* + \gamma_i (\vR||\vS)\vx
+\end{align*}
+We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha+\beta}^*)$,
+\[
+(\vR|| \vS) \vx = \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T =  \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}
+\]
+This completes the proof of the claim.
+\end{proof}
+\begin{claim}
+If the pair $(\vA', \vb')$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
+\end{claim}
+\begin{proof}
+\bnote{This needs to be checked.}
+Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
+The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$.
+That is, for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.
+Thus $b^* | \vA^*$ is uniformly distributed.
+Instead of showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}, we show that $\vb |( \vA, \vA^*)$ is uniformly distributed.
+Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
+
+ The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.
+Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.
+The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.
+Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$.
+Recall that
+ \[
+ \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
+\]
+Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
+\end{proof}
+Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus, 
+\begin{align*}
+&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
+& =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right|\geq \epsilon - \ngl(n)
+\end{align*}
+\end{proof}
 \section{Additional Proofs}

### 2013-03-18 trunk/CompFuzzExt.tex
Revising new proof of 5.3

@@
 For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
+For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.
+Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.
+We use similar notation for the complement of $T$, denoted $T^c$.
 
@@
 
-Let $n$ be a security parameter, $m = \poly(n), q = \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $\mod q$ and this notation is omitted.  
-Let $\D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where $\alpha$ of the equations have no error added.
-That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
-Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.
-We assume that,
+Let $n$ be a security parameter, $m = \poly(n), q = \poly(n)$.  Let $\alpha < q$ and $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
+Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
+That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
+We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
+Let $\epsilon \geq 1/\poly(n)$, then,
 \[
@@
 \]
-
-We build a distinguish $\D'$ that given $m$ samples over $n$ variables distinguisher LWE instances from uniform.
+We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
 Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-Our goal is to prepare a random block fixing instance from the random instance we are given.
-The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
-
-We first note that $\mathcal{D'}$ has an advantage only when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
-\begin{claim}
-Let $S \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(S)<\alpha]<1 - e^{-1/\beta} = \ngl(n)$
-\end{claim}
-\begin{proof}
-\bnote{Note happy with this writeup.  Draws on On the Rank of Random Matrices by C. Cooper}
-The probability that all $\alpha$ rows is linearly independent is the successive probability that each row lies in the span of the previous rows, this probability is:
-\begin{align*}
-\Pr[\rank(\vS) = \alpha] &= \prod_{i=1}^\alpha\left( 1-q^i/q^{\alpha+\beta}\right)
-=\prod_{i=1}^\alpha\left( 1-q^{i-\alpha- \beta}\right)\\
-&\geq\prod_{i=1}^\alpha\left( 1- q^{-\beta}\right) = \left(1-\frac{1}{q^{\beta}}\right)^\alpha
-\end{align*}
-\end{proof}
-Recall that $\alpha < q$, thus,
-\begin{align*}
-\left(1-\frac{1}{q^{-\beta}}\right)^\alpha &\geq \left(1-\frac{1}{q^{\beta}}\right)^q\\
-&=\left(\left(1-\frac{1}{q^{\beta}}\right)^{q^{\beta}}\right)^{1/\beta}\approx e^{-1/\beta}
-\end{align*}
-\begin{corollary}
-$
-|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
-$
-\end{corollary}
-
-Thus, we only consider the case where $\rank(\vS) = \alpha$.  
-It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
-%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
-\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
-\end{enumerate}
+It suffices to build a distinguisher $\D'$ whose size at most \bnote{fill in} bigger than $\D$ where
+\begin{align}
+\label{eq:block LWE dist}
+|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
+\end{align}
+We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
 
@@
 \item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
-\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$.
+\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
 \item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
 \item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
-\item Initialize $\vW \in \Fq^{n\times \alpha+\beta}$ to be the zero matrix.
+\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
 \item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
@@
 \end{figure}
+The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(we use techniques from Cooper~\cite{cooper2000rank}):
+\begin{claim}
+Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)<\alpha]<1 - e^{-1/\beta} = \ngl(n)$.
+\end{claim}
+\begin{proof}
+\bnote{Note happy with this writeup.  Draws on On the Rank of Random Matrices by C. Cooper}
+The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, this probability is:
+\begin{align*}
+\Pr[\rank(\vS) = \alpha] &= \prod_{i=1}^\alpha\left( 1-q^{i-1}/q^{\alpha+\beta}\right)
+=\prod_{i=1}^\alpha\left( 1-q^{i-\alpha- \beta-1}\right)\\
+&\geq\prod_{i=1}^\alpha\left( 1- q^{-\beta}\right) = \left(1-\frac{1}{q^{\beta}}\right)^\alpha
+\end{align*}
+\end{proof}
+Recall that $\alpha < q$, thus,
+\begin{align*}
+\left(1-\frac{1}{q^{-\beta}}\right)^\alpha &\geq \left(1-\frac{1}{q^{\beta}}\right)^q
+=\left(\left(1-\frac{1}{q^{\beta}}\right)^{q^{\beta}}\right)^{1/\beta}\approx e^{-1/\beta}
+\end{align*}
+\begin{corollary}
+$
+|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
+$
+\end{corollary}
+
+We restrict analysis to the case where $\rank(\vS) = \alpha$.  
+It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
+\begin{enumerate}
+\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
+%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
+\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
+\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
+\end{enumerate}
 
@@
 The quadrant represented by $\vA'$ remains random after step~\ref{step:randomization} as we are adding uncorrelated random values.
-For the matrix $\vW$, the columns whose indices are not included in $T$ are random.  They are the addition of a randomly generated value and uncorrelated random values.
-
-Thus, we restrict attention to the columns of $\vW$ whose indices are in $T$.
-We denote this restricted matrix by $\vW_T$.
+The matrix $\vW_{T^c}$~(recall this is the restriction of $\vW$ to the columns not in $T$) is random as it is initialized with random values and only uncorrelated random values are added.
+
+Thus, we restrict attention to $\vW_T$~(the columns of $W$ included in $T$).
 Fix a particular row $i$.
@@
 
-Thus, the entire matrix $\vA$ after step~\ref{step:randomization} is uniformly generated conditioned on $\rank(S) = \alpha$.
+Thus, the entire matrix $\vA$ after step~\ref{step:randomization} is uniformly generated conditioned on $\rank(\vS) = \alpha$.
 % In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
@@
 Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ is uniformly generated if $i\not\in T$.
-Denote by $\vS_{T^c}$ the restriction of $\vS$ to the columns whose indices are not $T$~(similarly for the vector $\vx$).
-
-Denote by $\vx_T$ the restriction of $\vx$ to the indices in $T$.  Then, define $\vx$ as the solution to the following system of equations~(a solution exists as $\vS_T$ is full rank).
+Then partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
+We define the remaining variables $\vx_T$ as the solution to the following system of equations.
 \[
@@
 \]
-Denote by $\vA^*$ the matrix before step~\ref{step:randomization}.
-The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$~(where $\ve$ is $\ve'$ with $\alpha$ 0s appended).
-Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
+A solution $\vx_T$ exists as $\vS_T$ is full rank and $\vx_T$ is uniformly distributed.
+Denote by $\vA^*$ the matrix before step~\ref{step:randomization} and denote by $\ve$ the vector $\ve'$ with $\alpha$ 0s appended.
+The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$.
+Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
 %For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
@@
 \va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
-&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx= b_i^* + \gamma_i (\vR||\vS)\vx
-\end{align*}
-We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha+\beta}^*)$,
-\[
-(\vR|| \vS) \vx = \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T =  \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}
-\]
+&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
+\end{align*}
+We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
+\begin{align*}
+(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
+&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
+\\&=  \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}
+\end{align*}
 This completes the proof of the claim.
@@
 \begin{claim}
-If the pair $(\vA', \vb')$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
+If the pair $\vb' | \vA'$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
 \end{claim}
@@
 &\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
-& =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right|\geq \epsilon - \ngl(n)
-\end{align*}
+&\left|\Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right] \Pr[\rank(\vS) = \alpha] \right|\\
+&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
+&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
+\end{align*}
+Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
 \end{proof}

### 2013-03-18 trunk/CompFuzzExt.tex
Revising theorem 5.3

@@
 
-The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
+The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$~(proof in \secref{sec:proof of block theorem}).
 %\vspace{.1in}
@@
 \label{thm:blockLWE}
-Let $n$ be a security parameter and define $q, m = \poly(n)$, let $\alpha < q$ and $\beta = \omega(1)$.
-Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
-Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha + \beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
+Let $n$ be a security parameter and define $q, m = \poly(n)$.
+Let $\alpha< q$, $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
+Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
 \end{theorem}
@@
 \item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.
 
@@
 \begin{proof}
-Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then define $\vx$ as:
+Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
+Then define $\vx^*$ as:
 \[
-x_i = \begin{cases}
+x^*_i = \begin{cases}
 x_i', & \text{if }1\leq i\leq n \\
-b_{m+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
+b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
 \end{cases}
 \]
-We denote by $\vA^*$ the matrix before step~\ref{step:randomization}.
-The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$~(where $\ve$ is $\ve'$ with $\alpha$ 0s appended).
+Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).
 Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
 %For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  We now show that for all rows $i$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
+For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).
+Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
 %, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
 The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-We have the following for all rows $i$:
+\bnote{We need to justify these steps better.}
+\bnote{Is it really standard to go to lower case for the rows?}
+\xnote{lower case for vectors, which is row vector in the matrix}
+
+\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
+We have the following for all $i=1,..., m+\alpha$:
 \begin{align*}

### 2013-03-18 trunk/CompFuzzExt.tex
Integrating Micciancio and Peikert result

@@
 
+The main item I think needs to change is their Lemma 2.4
+\begin{lemma}~\cite[Min-Entropy Version of Lemma 2.4]{micciancio2013hardness}
+Let $\mathcal{L}$ be a family of functions on a common domain $X$ and let $Z$ be a distribution over $X$.
+Then $(\mathcal{L}, Z)$ is $\epsilon$-uninvertible~(even statistically, with respect to computationally unbounded adversaries) for $\epsilon = \expe_{f\leftarrow \mathcal{L}} [|f(X)|]/ 2^{-H_\infty(Z)}$.
+\end{lemma}
+\begin{proof}
+Fix a function $f$.
+The best way to predict $Z$ given $f(Z)$ is the average predictability of $Z | f(Z)$.
+This predictability is $2^{-\Hav(Z | f(Z))}$.
+By Lemma 2.2 of Dodis et.al.~\cite{DBLP:journals/siamcomp/DodisORS08},
+\[
+\tilde{H}_\infty(Z | f(Z))\geq H_\infty(Z) - \log |f(Z)| \geq \Hoo(Z) - \log |f(X)|.
+\]
+  The statement of the lemma follows by converting to predictability.
+\end{proof}
 %\section{Computational Fuzzy Extractors}

### 2013-03-19 CompFuzzExt.tex
Cleanup up full rank notation in Theorem 5.3

--- 2013-03-07 CompFuzzExt.tex
@@
 \label{thm:blockLWE}
-Let $n$ be a security parameter and define $q, m = \poly(n)$.
-Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
-Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha, m+\alpha, q, W}$ w/ symbol fixing sources problem.
+Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
+Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
+Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
 \end{theorem}
@@
 
-\bnote{Need to continue and go through their Lemma 2.1 and 2.4 to be sure I believe this.  Everything else should go through fine.}
+\bnote{Need to continue and go through their Lemma 4.1 and 4.4 to be sure I believe this.  Everything else should go through fine.}
 
@@
 \begin{align*}
-\va_i \vx^* + e_i^* &=\va^*_i\vx^*+\sum_{k=1}^\alpha \gamma_{i} \va^*_{m+k}\vx^*+e_i^*\\
-&= \va_i^*\vx^* + e_i^* + \sum_{k=1}^\alpha \mathbf{\gamma}_{i} \va^*_{m+k}\vx^*\\
-&= b_i^* + \sum_{k=1}^\alpha\gamma_i \va_{m+k}^* \vx^*\\
-&= b_i^* + \sum_{k=1}^\alpha \gamma_i \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
-&= b_i^* +\sum_{k=1}^\alpha\gamma_i b_{m+k}^*= b_i
+\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
+& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
+& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
+&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
 \end{align*}
@@
 
+\section{Proof of Theorem \ref{thm:blockLWE} Revised}
+\label{sec:proof of block theorem}
+
+%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
+\begin{proof}
+We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.
+If the blocks are fixed to some other value the reduction is essentially the same.
+For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
+For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.
+Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.
+We use similar notation for the complement of $T$, denoted $T^c$.
+
+%It should be clear to the reader where the reduction differs for another block fixing source.\lnote{I don't like the phrasing; maybe we should say that if the blocks are fixed to some non-0 value, the reduction is essentially the same}
+
+Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
+Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
+That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
+We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
+Let $\epsilon \geq 1/\poly(n)$, then,
+\[
+|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
+\]
+We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
+Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
+It suffices to build a distinguisher $\D'$ whose size at most \bnote{fill in} bigger than $\D$ where
+\begin{align}
+\label{eq:block LWE dist}
+|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
+\end{align}
+We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
+
+\begin{figure}[t]
+\begin{framed}
+\begin{enumerate}
+\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
+\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
+\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
+\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
+\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
+\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
+\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
+\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
+\subitem For $j=1,..., n$:
+\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
+\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
+\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
+\item \label{step:randomization}
+For {$i=1,..., n$}:
+\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
+\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
+\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
+\item Run $\D$ on input $\vA, \vb$.
+\item Output $\D$'s output.
+\end{enumerate}
+\end{framed}
+\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
+\label{fig:perfectLWEreduction}
+\end{figure}
+The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(we use techniques from Cooper~\cite{cooper2000rank}):
+\begin{claim}
+Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
+\end{claim}
+\begin{proof}
+The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$, thus by union bound this probability is:
+\begin{align*}
+\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
+\leq \alpha \frac{q^{\alpha}}{q^{\beta+\alpha} }= \frac{\alpha}{q^{\beta}} = \ngl(n)\\
+\end{align*}
+Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
+\end{proof}
+\begin{corollary}
+$
+|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
+$
+\end{corollary}
+
+We restrict analysis to the case where $\rank(\vS) = \alpha$.  
+It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
+\begin{enumerate}
+\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
+%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
+\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
+\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
+\end{enumerate}
+
+\begin{claim}
+\label{cl:randomMatrixDist}
+The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix with $\rank(\vS) = \alpha$.
+\end{claim}
+\begin{proof}
+It should be clear that $\vR, \vS$ are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
+The quadrant represented by $\vA'$ remains random after step~\ref{step:randomization} as we are adding uncorrelated random values.
+The matrix $\vW_{T^c}$~(recall this is the restriction of $\vW$ to the columns not in $T$) is random as it is initialized with random values and only uncorrelated random values are added.
+
+Thus, we restrict attention to $\vW_T$~(the columns of $W$ included in $T$).
+Fix a particular row $i$.
+Then $\vW_{i, T} = \gamma_i \vS_{T}$.
+Since $\vS_T$ is full rank and $\gamma_i$ is uniformly generated, $\vW_{i, T}$ is uniformly generated.
+
+Thus, the entire matrix $\vA$ after step~\ref{step:randomization} is uniformly generated conditioned on $\rank(\vS) = \alpha$.
+% In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
+Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.
+Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.
+Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5.
+For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number.
+Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors.
+Therefore, the entire matrix $\vA$ is a truly random matrix.
+This completes the claim.
+\end{proof}
+\begin{claim}
+\label{cl:random ax+e}
+If $\D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
+\end{claim}
+\begin{proof}
+Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
+Then partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
+We define the remaining variables $\vx_T$ as the solution to the following system of equations.
+\[
+\vS_T  \vx_T = \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
+\]
+A solution $\vx_T$ exists as $\vS_T$ is full rank and $\vx_T$ is uniformly distributed.
+Denote by $\vA^*$ the matrix before step~\ref{step:randomization} and denote by $\ve$ the vector $\ve'$ with $\alpha$ 0s appended.
+The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$.
+Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
+%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
+We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
+%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
+The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
+We have the following for $1\leq i\leq m$:
+\begin{align*}
+\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
+&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
+\end{align*}
+We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
+\begin{align*}
+(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
+&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
+\\&=  \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}
+\end{align*}
+This completes the proof of the claim.
+\end{proof}
+\begin{claim}
+If the pair $\vb' | \vA'$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
+\end{claim}
+\begin{proof}
+\bnote{This needs to be checked.}
+Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
+The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$.
+That is, for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.
+Thus $b^* | \vA^*$ is uniformly distributed.
+Instead of showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}, we show that $\vb |( \vA, \vA^*)$ is uniformly distributed.
+Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
+
+ The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.
+Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.
+The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.
+Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$.
+Recall that
+ \[
+ \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
+\]
+Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
+\end{proof}
+Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus, 
+\begin{align*}
+&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
+&\left|\Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right] \Pr[\rank(\vS) = \alpha] \right|\\
+&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
+&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
+\end{align*}
+Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
+\end{proof}
 \section{Additional Proofs}

### 2013-03-19 CompFuzzExt.tex
Cleanup up full rank notation in Theorem 5.3

@@
 \end{figure}
-The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(we use techniques from Cooper~\cite{cooper2000rank}):
+The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
 \begin{claim}
@@
 \begin{proof}
-The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$, thus by union bound this probability is:
+The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
+By union bound, the probability that $\vS$ is not full rank is:
 \begin{align*}

### 2013-03-22 trunk/CompFuzzExt.tex
Minimum distance in place of unique witness

@@
 %\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
-\consref{cons:informal construction} is only useful if $\mathcal{I}_t$ can be efficiently implemented.
-We now present a particular $\mathcal{I}_t$ and consider its efficiency:\bnote{Unique witness.
-BAD!!!}
+\consref{cons:informal construction} is only useful if $\mathcal{I}_t$ can be efficiently implemented.  We now present a particular $\mathcal{I}_t$ and consider its efficiency:
 
 \begin{construction}
-\label{cons:decoding algorithm} Suppose that for a $(n, m, q, \chi)$ that the LWE errors problem is a unique witness relation except with negligible probability.
-Let $R$ be the relation that decides whether $X$ is a witness for an instance $\vA, \vA X+W$.
-We describe inverter $\mathcal{I}_t$:
+\label{cons:decoding algorithm} Suppose that for a $(n, m, q, \chi)$ where $m\geq 2n$.  We describe inverter $\mathcal{I}_t$:
 \begin{enumerate}
@@
 \item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this is $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
-\item Compute $X = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $R(X, \vA, \vect{C}) \neq 1$.  Go to step (2).
-\item Output $X$.
+\item Compute $X' = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
+\item Output $X'$.
 \end{enumerate}
@@
 $\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.
-Our inverter will only succeed if it can verify it has the proper $X$.
-Consider a relation $R(X, (\vA, \vA X+W-W'))$ that verifies if $X$ is the point encoded in $\vA X+W-W'$.
-If $n$ is large enough and if $|W-W'|_1$ is small enough, $R$ is a unique witness relation with high probability~(see \defref{def:unique witness relation}) and computable in time $O(n^3)$.
-\bnote{Need to get rid of this unique witness stuff, talk about high distance with high probability.}
-We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
+We need $t$ to be small enough for step (4) to succeed with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
+The second condition is to ensure that there are few false positives in step (4).
+This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.
+The exact statement is in \corref{cor:code high distance}.
+Furthermore step (4) is computable in time $O(n^3)$.
+This is also a sufficient condition for step (4) to succeed with probability at least $1/\poly(n)$.  We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
 %  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).
@@
 \label{lem:i t poly time}
-Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance that is a unique witness relation~(except with negligible probability).
+Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 2n$.
 Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
-Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(m/n-1)$.
-Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ for all but a negligible fraction of inputs over $\vA, \vA X+W - W'$.
+Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-1)\log n$.
+Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
 \end{lemma}
@@
 with 
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
 \end{theorem}
@@
 \label{thm:blockLWE}
-Let $n$ be a security parameter and define $q, m = \poly(n)$.
-Let $\alpha< q$, $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
+Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
+Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
 Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
 \end{theorem}
-\bnote{We should add some exposition here.  Some intuition about the proof.}
+\bnote{Work on this writeup.}
+We believe this statement is of independent interest.
+It says that as long as there are security parameter more variables than equations no error we still get a secure $\LWE$ instance.
+Intuitively, providing a single sample with no error should provide information should fix at most a single variable.
+Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.
+We are able to show that $\distLWE$ is still hard.
+In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to prepare a random block fixing instance even without knowing the values for the first $n$ variables.
+The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
 
@@
 
+\bnote{Need to rework this statement based on addition of $\beta$ above.}
 \begin{theorem}
@@
 Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)nb/d+\alpha b}$.
+Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)nb/d+\alpha b})$.
 Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/2$) using quantum algorithms.
@@
 %\]
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{2d+3} \log n)$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{2d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
 \end{theorem}
@@
 \appendix
-\section{Background}
+\section{Random Linear Codes Have High Distance}
 %\subsection{Notions of Computational Entropy}
@@
 
-We will need the ability to verify if we have a correct solution in~\consref{cons:informal construction}.
-
-\begin{definition}
-Let $R$ be a relation.  We say that $R$ is $s_{ver}$-\emph{unique witness verifiable} if $\forall y$ there exists a unique $x$ such that $R(x, y)=1$ and $R(x, y) =1$ is computable in time $s_{ver}$.
-\end{definition}
-We can relax this definition slightly to allow a relation that is unique witness verifiable with all but negligible probability~(when $x, y$ grow with the security parameter).
-
-\begin{definition}
-\label{def:unique witness relation}
-Let $R:\mathcal{M}_1\times \mathcal{M}_2\rightarrow \zo$.
+%We will need the ability to verify if we have a correct solution in~\consref{cons:informal construction}.  
+%
+%\begin{definition}
+%Let $R$ be a relation.  We say that $R$ is $s_{ver}$-\emph{unique witness verifiable} if $\forall y$ there exists a unique $x$ such that $R(x, y)=1$ and $R(x, y) =1$ is computable in time $s_{ver}$.
+%\end{definition}
+%We can relax this definition slightly to allow a relation that is unique witness verifiable with all but negligible probability~(when $x, y$ grow with the security parameter).
+%
+%\begin{definition}
+%\label{def:unique witness relation}
+%Let $R:\mathcal{M}_1\times \mathcal{M}_2\rightarrow \zo$.
 We say that $R$ is $(\epsilon, s_{ver})$-\emph{unique witness verifiable} if over $y\in \mathcal{M}_2$, drawn uniformly, the probability that $\exists x_1, x_2, x_1\neq x_2$ such that $R(x_1, y) =1 = R(x_2, y)$ is at most $\epsilon$ and $R$ is computable in time $s_{ver}$.
-\end{definition}
+%\end{definition}
+%
+For efficient decoding of \consref{cons:informal construction}, we need the $\LWE$ instance to have high distance with overwhelming probability.
+We will use the $q$-ary entropy function, denoted $H_q(x)$ and defined as $H_q(x) = x\log _q(q-1) - x\log_q x - (1-x)\log_q (1-x)$.
+Note that $H_2(x) = -x\log x - (1-x)\log (1-x)$.
+In the region $[0, \frac{1}{2}]$ for any value $q'\geq q$, $H_{q'}(x)\leq H_{q}(x)$.
+The following theorem is standard in coding theory:
+
+\begin{theorem}~\cite[Theorem 8]{venkatLecture}
+\label{thm:random code good distance}
+For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .
+If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
+\end{theorem}
+Of particular, concern will be the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
+\begin{corollary}
+\label{cor:code high distance}
+Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
+Let $q$ be a prime and $t = O(\frac{m}{n}\log n )$.
+For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $t$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
+\end{corollary}
+\begin{proof}
+Let $c$ be some constant.
+Let $\delta = t/m = \frac{c\log n}{n}$.
+We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).
+It suffices to show that for sufficiently large $n$, $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.
+For sufficiently large $n$:
+\begin{itemize}
+\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
+\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
+\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.
+
+% and note that there $\exists \epsilon$ where $0<\epsilon< 1-H_q(\frac{c\log n}{2n})< 1-H_q(\frac{c\log n}{m})$ and $1-H_q(c\log n/n) -\epsilon =1/2$ or equivalently $H_q(c\log n/n)+\epsilon = 1/2$.
+Let $d$ be some constant such that $q< n^d$.
+Consider the value of $H_q(\frac{c\log n}{n})$:
+%\begin{align*}
+%H_q(\frac{c\log n}{n})&\leq  H_{n^d}(\frac{c\log n}{n})\\
+%&=\frac{c\log n}{n} \log_{n^d}(n^d-1) - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} (1-\frac{c\log n}{n})\\
+%&\leq \frac{c\log n}{n}  - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
+%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n})-\log_{n^d} (\frac{n-c\log n}{n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
+%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n-c\log n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
+%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} (\frac{n}{c\log n}-1) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
+%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} n \right)- \log_{n^d} \left(\frac{1}{n}\right)\\
+%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} - \log_{n^d} \left(\frac{1}{n}\right)\\
+%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} + \frac{1}{d}
+%\end{align*}
+%Thus for large enough values of $n$, $H_{n^d}(\frac{c\log n}{n})\leq 1/2 + O(\frac{c\log n}{dn}) \leq 2/3$, thus $1 - H_q(\frac{c\log n}{n})> 1-H_{n^d}(\frac{c\log n}{n} )> 1/3$.
+Taking $\epsilon  = 1/21/6$ the conditions of the corollary are satisfied.
+\end{proof}
 
@@
 
-Let $n$ be a security parameter, $m = \poly(n), q = \poly(n)$.  Let $\alpha < q$ and $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
+Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
 Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
@@
 \subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
-\subitem For $j=1,..., n$:
+\subitem For $j=1,..., m$:
 \subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
@@
 \item \label{step:randomization}
-For {$i=1,..., n$}:
+For {$i=1,..., m$}:
 \subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
@@
 \end{figure}
-The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(we use techniques from Cooper~\cite{cooper2000rank}):
+The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
 \begin{claim}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)<\alpha]<1 - e^{-1/\beta} = \ngl(n)$.
+Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
 \end{claim}
 \begin{proof}
-\bnote{Note happy with this writeup.  Draws on On the Rank of Random Matrices by C. Cooper}
-The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, this probability is:
-\begin{align*}
-\Pr[\rank(\vS) = \alpha] &= \prod_{i=1}^\alpha\left( 1-q^{i-1}/q^{\alpha+\beta}\right)
-=\prod_{i=1}^\alpha\left( 1-q^{i-\alpha- \beta-1}\right)\\
-&\geq\prod_{i=1}^\alpha\left( 1- q^{-\beta}\right) = \left(1-\frac{1}{q^{\beta}}\right)^\alpha
-\end{align*}
+The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
+By union bound, the probability that $\vS$ is not full rank is:
+\begin{align*}
+\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
+\leq \alpha \frac{q^{\alpha}}{q^{\beta+\alpha} }= \frac{\alpha}{q^{\beta}} = \ngl(n)\\
+\end{align*}
+Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
 \end{proof}
-Recall that $\alpha < q$, thus,
-\begin{align*}
-\left(1-\frac{1}{q^{-\beta}}\right)^\alpha &\geq \left(1-\frac{1}{q^{\beta}}\right)^q
-=\left(\left(1-\frac{1}{q^{\beta}}\right)^{q^{\beta}}\right)^{1/\beta}\approx e^{-1/\beta}
-\end{align*}
 \begin{corollary}

### 2013-03-24 CompFuzzExt.tex
Two seconds, two bugs
Thm 5.3 fixed and cleaned..

@@
 \end{theorem}
-\bnote{We should add some exposition here.  Some intuition about the proof.}
+\bnote{Work on this writeup.}
+We believe this statement is of independent interest.
+It says that as long as there are security parameter more variables than equations no error we still get a secure $\LWE$ instance.
+Intuitively, providing a single sample with no error should provide information should fix at most a single variable.
+Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.
+We are able to show that $\distLWE$ is still hard.
+In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to prepare a random block fixing instance even without knowing the values for the first $n$ variables.
+The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
 
@@
 
+\ignore{
 \section{Proof of Theorem \ref{thm:blockLWE}}
@@
 \end{proof}
-
-\section{Proof of Theorem \ref{thm:blockLWE} Revised}
+}
+
+\section{Proof of Theorem \ref{thm:blockLWE}}
 \label{sec:proof of block theorem}
@@
 Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-It suffices to build a distinguisher $\D'$ whose size at most \bnote{fill in} bigger than $\D$ where
+It suffices to build a ppt distinguisher $\D'$  where
 \begin{align}
@@
 \item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
+\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
 \item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
-\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
-\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
+		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
+\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
 \item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
 \subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
-\subitem For $j=1,..., n$:
+\subitem For $j=1,..., m$:
 \subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
@@
 \item \label{step:randomization}
-For {$i=1,..., n$}:
-\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
+For {$i=1,..., m$}:
+\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
 \subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
@@
 \begin{claim}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
+Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
 \end{claim}
@@
 The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
-By union bound, the probability that $\vS$ is not full rank is:
+By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
 \begin{align*}
 \Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-\leq \alpha \frac{q^{\alpha}}{q^{\beta+\alpha} }= \frac{\alpha}{q^{\beta}} = \ngl(n)\\
+\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
 \end{align*}
@@
 
-We restrict analysis to the case where $\rank(\vS) = \alpha$.  
-It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
+We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ can properly prepares a random instance in this case. We show this in the following three claims: 
 \begin{enumerate}
@@
 \end{proof}
-\begin{claim}
+\begin{claim}\label{clm:random b}
 If the pair $\vb' | \vA'$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
@@
 \begin{proof}
-\bnote{This needs to be checked.}
 Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$.
-That is, for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.
-Thus $b^* | \vA^*$ is uniformly distributed.
-Instead of showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}, we show that $\vb |( \vA, \vA^*)$ is uniformly distributed.
+The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$, i.e.
+for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.
+Thus $\vb^* | \vA^*$ is uniformly distributed.
+We show that $\vb |( \vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}.
 Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
@@
 \end{proof}
-Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus, 
+
+Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus,
 \begin{align*}
 &\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
-&\left|\Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right] \Pr[\rank(\vS) = \alpha] \right|\\
+&\, = \left| \Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
 &\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\

### 2013-03-25 trunk/CompFuzzExt.tex
Cleaning up proof of 3.5 and explanation of 5.3

@@
 We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-secure if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
+If $\distLWE_{n, m, q, \chi}$ is secure for all $t = \poly(n), \epsilon  = 1/\poly(n)$ we say it is \emph{secure}.
 \end{definition}
@@
 
-The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$~(proof in \secref{sec:proof of block theorem}).
+The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$.
 %\vspace{.1in}
@@
 Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
-Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
+The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
 \end{theorem}
-\bnote{Work on this writeup.}
-We believe this statement is of independent interest.
-It says that as long as there are security parameter more variables than equations no error we still get a secure $\LWE$ instance.
-Intuitively, providing a single sample with no error should provide information should fix at most a single variable.
+We believe this statement is of interest outside our setting.
+\thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known error.
+Roughly, we need the number of variables to be security parameter larger than the number of equations with known error.
+Providing a single sample with no error ``fixes'' at most a single variable.
 Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.
-We are able to show that $\distLWE$ is still hard.
-In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to prepare a random block fixing instance even without knowing the values for the first $n$ variables.
+We are able to show~(a stronger result) that $\distLWE$ is still hard.
+In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to explain a random value for the last $\alpha$ samples without knowledge of the other variables.
 The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
+A formal proof is in \secref{sec:proof of block theorem}.
 
@@
 \item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
+\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
 \item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
-\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
-\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
+		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
+\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
 \item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
@@
 For {$i=1,..., m$}:
-\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
+\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
 \subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
@@
 
-We restrict analysis to the case where $\rank(\vS) = \alpha$.  
-It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
+We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ prepares a random instance in this case. We show this in the following three claims: 
 \begin{enumerate}
@@
 \]
-A solution $\vx_T$ exists as $\vS_T$ is full rank and $\vx_T$ is uniformly distributed.
+A solution $\vx_T$ exists as $\vS_T$ is full rank and furthermore, $\vx_T$ is uniformly distributed.
 Denote by $\vA^*$ the matrix before step~\ref{step:randomization} and denote by $\ve$ the vector $\ve'$ with $\alpha$ 0s appended.
@@
 \end{align*}
-We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
+Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
 \begin{align*}
@@
 \[
-\sum_{w\in W} \Pr[W=w]\Pr[ w'\leftarrow \sample (w, t') \wedge \rec(w') \neq w]\leq \epsilon.
+\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \sample (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
 \]
-For $w$ denote by $\epsilon_w = \Pr[w'\leftarrow \sample(w, t') \wedge \rec(w') \neq w]$.
-\bnote{There is something weird going on here.
-The Markov inequality doesn't connect to what is below it.}Then by Markov inequality:
+For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \sample(c, t') \wedge \rec(c') \neq c]$.  
+Then by Markov inequality:
 \[
-\Pr_{w\in W}[ \epsilon_w \leq 2\expe_{w\leftarrow W} [\epsilon_w ] ] = \Pr_{w\in W} [\epsilon_w \le 2\epsilon ] \geq \frac{1}{2}
+\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
 \]
-Now suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]> 2\epsilon$.
-This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.
+Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.
+Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.
+Since $H_\infty(C)\geq k, |C'|\geq 2^{k-1}$~(otherwise $C'$ would contain total weight less that $2^{k-1}\frac{1}{2^k} = 1/2$).
+This completes the proof of the~\lemref{lem:averageToMaximalError}.
+
+%Suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]> 2\epsilon$.  
+%This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.
 Then note that $\Pr[W\in V]> 1/2$ as $W\setminus V$ contains at most $2^{k-1}-1$ points each of which has probability at most $1/2^k$ so $\Pr[W\in (W\setminus V)]\leq (2^{k-1}-1)/2^k < 1/2$.
 Thus,
-\begin{align*}
-\Pr_{w\in W}[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]\\
-&\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
-\end{align*}
-% where $\forall d\in D, \Pr[d'\leftarrow \sample(d) \wedge \rec(d') > 2\epsilon$.  In turn this implies that  
 %\begin{align*}
-%\Pr_{c\in C}[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]&=\frac{1}{|C|} \sum_{c\in C}  \Pr[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]\\
-%&\geq \frac{1}{|C|} \sum_{d\in D}  \Pr[ d'\leftarrow \sample (d) \wedge \rec(d') \neq d]\\
-%&\geq \frac{1}{|C|}\sum_{d\in D} 2\epsilon = \frac{1}{|C|}\left(\frac{|C|}{2}+1\right)2\epsilon = \epsilon + 2\epsilon/|C|> \epsilon
+%\Pr_{w\in W}[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]\\
+%&\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
 %\end{align*}
-This is a contradiction.  The statement of~\lemref{lem:averageToMaximalError} follows directly.
+%% where $\forall d\in D, \Pr[d'\leftarrow \sample(d) \wedge \rec(d') > 2\epsilon$.  In turn this implies that  
+%%\begin{align*}
+%%\Pr_{c\in C}[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]&=\frac{1}{|C|} \sum_{c\in C}  \Pr[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]\\
+%%&\geq \frac{1}{|C|} \sum_{d\in D}  \Pr[ d'\leftarrow \sample (d) \wedge \rec(d') \neq d]\\
+%%&\geq \frac{1}{|C|}\sum_{d\in D} 2\epsilon = \frac{1}{|C|}\left(\frac{|C|}{2}+1\right)2\epsilon = \epsilon + 2\epsilon/|C|> \epsilon
+%%\end{align*}
+%This is a contradiction.  The statement of~\lemref{lem:averageToMaximalError} follows directly.
 \end{proof}

### 2013-03-25 trunk/CompFuzzExt.tex
Revised introduction

@@
 
-We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
-a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
-It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
-the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
-Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.
+One of the primary building blocks for authentications is reliable key derivation.
+Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources.
+(\bnote{Are these references for fuzzy extractors or secure sketches?} as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
+The setting
+%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
+%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
+consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).
+The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.
+This information allows
+the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
+Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.
+This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
+
+As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a fuzzy extractor is the difference in the entropy of $w$ and the length of the key $r$.
+A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
+The resulting secret key may be too short to be useful if the entropy loss is too high.
+Traditionally, fuzzy extractors are defined as information-theoretic objects.
+In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
+
+The main novel tool in constructing fuzzy extractors is the secure sketch.
+The secure sketch produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
+The security requirement is that $w$ has high min-entropy conditioned on $s$.
+The key $r$ is formed by applying a randomness extractor~\cite{nisan1993randomness} to $w$.
+%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
+When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high.
+The minimum entropy loss for secure sketches has been quantified in past work.
+Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
+the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
+Known constructions of fuzzy extractors use a secure sketch suffer from this bound.
+%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
+
+\paragraph {Our Contributions}
+To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.
+Our overall goal is to produce a fuzzy extractor~(with small entropy loss), where the key $r$ is pseudorandom even conditioned on $p$.
+
+On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.
+We show that some entropy loss is necessary for secure sketches.
+The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
+Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
+We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
+%Furthermore, we have (asymptotic)~constructions that meet these bounds.
+
+Another possible relaxation is to require that the value $w$ is still unpredictable conditioned on $s$.
+Using an extractor with a reconstruction would still yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
+We consider sketches that preserve the weaker notion of unpredictability for the Hamming metric.
+In \thref{thm:imp of unp entropy}, we show  a significant loss in unpredictability is necessary for a secure sketch.
+The entropy loss is proportional to the volume of the ball of radius $t$.
+
+Both of these impossibility results arise because a sketch must function like an error-correcting code.
+To avoid these impossibility results, we give up on reconstructing $w$ and focus directly on the entropy loss in fuzzy extractors.
+%to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
+This string $\recout$ is  required to have high HILL entropy even conditioned on $s$.
+Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
+We build \emph{lossless} computational fuzzy extractors, in which $r$ is pseudorandom conditioned on $p$ and $r$ is as long as the entropy of $w$.
+% without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
+We demonstrate how to build such lossless fuzzy extractors~(\consref{cons:informal construction}) based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
+
+%We show that this relaxation of the security requirement is  useful.
+Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
+%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
+The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
+%\lnote{it would be good to find another application}
+
+Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
+To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).
+We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
+The LWE error vector, in our case, is the input $w$ itself.
+To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
+We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed).
+This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
+
+%Authentication generally requires secrets.
+Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
+Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
+%
+%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
+%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
+%It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
+%the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
+%Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.
 This feature is needed because $s$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
-As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.
-
-Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
+%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.  
+%
+%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
 For example, in the application of secure sketches to fuzzy extractors (whose goal is to reliably produce a uniformly random secret key from a noisy input), the resulting secret key may be too short to be useful if the entropy loss is too high.
 However, because secure sketches are defined as information-theoretic objects, some entropy loss is inherent in any secure sketch construction, because $s$ contains enough information to recover $w$ from any value $w'$ that is close to it.
-
-The minimum necessary  entropy loss has been quantified in past work.
+%
+%The minimum necessary  entropy loss has been quantified in past work.
 Even if we don't require perfect correctness (i.e., allow $\rec$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
-the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
-%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-
-\paragraph {Our Contributions}
-To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
-The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
+%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
+%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
+%
+%\paragraph {Our Contributions}
+%To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
+%The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
 Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-
-On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful.
+%
+%On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful.
 We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%Furthermore, we have (asymptotic)~constructions that meet these bounds.
-
-On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction.
+%%Furthermore, we have (asymptotic)~constructions that meet these bounds.
+%
+%On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction.
 The idea is to give up on reconstructing $w$ and, instead, to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
@@
 Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-
-Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
-~\ref{thm:lossless secure conductor log})).
+%
+%Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
+%~\ref{thm:lossless secure conductor log})).
 We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
-
-We show that this relaxation of the security requirement is  useful.
+%
+%We show that this relaxation of the security requirement is  useful.
 Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
-We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
+%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
 The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
-\lnote{it would be good to find another application}
-
-Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
+%\lnote{it would be good to find another application} 
+%
+%Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
 To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).
@@
 This relaxation requires new results about the hardness of LWE when samples have a fixed error vector, which may be of independent interest~(\thref{thm:blockLWE}).
-
 \section{Preliminaries}

### 2013-03-25 CompFuzzExt.tex
Restated 5.4 with the revised 5.3

@@
 
-\bnote{Need to rework this statement based on addition of $\beta$ above.}
 \begin{theorem}
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)nb/d+\alpha b})$.
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
+Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+d)n/d+\alpha \right)b})$.
 Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/2$) using quantum algorithms.
 There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\vA, \vA X+W) = H_\infty(W)$ for %the following parameters:
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/3} |\vA, \vA X+W) = H_\infty(W)$ for %the following parameters:
 %\[
@@
 \end{theorem}
+
+\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).
+The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
+We could set $\alpha$ larger than $n/3$ and extract fewer hardcore dimensions.
+To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant in $n$.
+The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for smal values of $n$.
 
@@
 
-We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ can properly prepares a random instance in this case. We show this in the following three claims: 
+We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ prepares a random instance in this case. We show this in the following three claims: 
 \begin{enumerate}
@@
 Consider the random variable $1_{S_W}$ that is $1$ when $s\in S_X$ and otherwise.
-Then \bnote{I am splitting average min-entropy based on an indicator variable, everyone is okay with this?}
+Then,
 \[
@@
 %f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{n}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
+f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
 \end{align*}
 To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
-Finally we assume that $t = d \log n(m/n-1)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
+Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-1)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
 \begin{align*}
@@
 Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
+
+\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
+\label{ssec:block params}
+We repeat parameter settings for block fixing sources.
+We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.
+We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
+\begin{align*}
+n_0&< n -k  -\alpha -\beta\\
+t&\leq d \log n\left(\frac{m}{n}-1\right)\\
+q &= n^f\\
+\rho q  &= 2n^{1/2+3\gamma}m\\
+m\log \rho q &= k \log q
+\end{align*}
+Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
+\begin{align*}
+n_0&< n - k - \alpha -\beta\\
+t&\leq d\log n\left(\frac{m}{n}-1\right)\\
+m \log 2n^{1/2+3\gamma}m &= k \log n^f
+\end{align*}
+As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.
+However, the last equation may have no solution for $f$ constant.
+Putting the last equation in terms of $f$ one has:
+\begin{align*}
+n_0&< n -k  - \alpha - \omega(1) \\
+t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
+%f \log n &= \frac{m}{n}\log 2n^2m\\
+f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
+\end{align*}
+To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.
+Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-1)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
+\begin{align*}
+n_0&< n/3 -  \log n\\
+m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
+f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+d)}{d}\right)\frac{\log \frac{2(c+d)}{d} n^{3/2+3\gamma}}{\log n}
+\end{align*}
+
+Assuming $n/3-\log(n)> n_0$ and letting $t= c\log n$ we get the following setting:
+\begin{align*}
+m &= \frac{(c+d)n}{d}\\
+q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
+\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+d)n^{3/2+3\gamma}}{d}
+\end{align*}
 

### 2013-03-26 trunk/CompFuzzExt.tex
Working on wording of introduction

@@
 
-Authentication generally requires secrets.
-Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
-Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
-
-One of the primary building blocks for authentications is reliable key derivation.
+Authentication generally require a secret drawn from some high-entropy source.
+One of the primary building blocks for authentication is reliable key derivation.
+Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
+%Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
+
 Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources.
@@
 This information allows
-the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
+the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
 Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.
-This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
-
-As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a fuzzy extractor is the difference in the entropy of $w$ and the length of the key $r$.
+This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
+
+%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
+The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.
 A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
@@
 The minimum entropy loss for secure sketches has been quantified in past work.
-Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
+Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08},
+%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
+the entropy loss of a secure sketch that can reconcile $t$ errors
+ %with high probability 
+ is bounded by the redundancy of
 the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
-Known constructions of fuzzy extractors use a secure sketch suffer from this bound.
+Constructions of fuzzy extractors that use a secure sketch inherit this bound.
 %(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
@@
 \paragraph {Our Contributions}
-To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.
-Our overall goal is to produce a fuzzy extractor~(with small entropy loss), where the key $r$ is pseudorandom even conditioned on $p$.
+To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.
+Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.
 
@@
 
-Another possible relaxation is to require that the value $w$ is still unpredictable conditioned on $s$.
-Using an extractor with a reconstruction would still yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
-We consider sketches that preserve the weaker notion of unpredictability for the Hamming metric.
-In \thref{thm:imp of unp entropy}, we show  a significant loss in unpredictability is necessary for a secure sketch.
-The entropy loss is proportional to the volume of the ball of radius $t$.
-
-Both of these impossibility results arise because a sketch must function like an error-correcting code.
-To avoid these impossibility results, we give up on reconstructing $w$ and focus directly on the entropy loss in fuzzy extractors.
+Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
+Using an extractor with a reconstruction would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
+We show lower bounds on the unpredictability loss of sketches in the Hamming metric.
+We prove in \thref{thm:imp of unp entropy} that the unpredictability loss must be at least the volume of the ball of radius $t$.
+
+Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.
+To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.
+
 %to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
@@
 Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-We build \emph{lossless} computational fuzzy extractors, in which $r$ is pseudorandom conditioned on $p$ and $r$ is as long as the entropy of $w$.
+We build \emph{lossless} computational fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{If a source has enough entropy, the entropy losses of a information-theoretic fuzzy extractor can be overcome by running a pseudorandom generator on the derived key $r$.
+However, when the source is low entropy, these entropy losses may not leave sufficient entropy to run a pseudorandom generator.}.
 % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
-We demonstrate how to build such lossless fuzzy extractors~(\consref{cons:informal construction}) based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
-
+Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
 %We show that this relaxation of the security requirement is  useful.
@@
 %\lnote{it would be good to find another application} 
-
-Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
-To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).
-We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-The LWE error vector, in our case, is the input $w$ itself.
+Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.
+To apply the LWE assumption, we correct errors of a random linear code which limits our decoding algorithm to reconciling a logarithmic number of differences.
+
+The recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the hardness of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
+This allows us to directly use our source $w$ as the LWE error vector.
 To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
-We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed).
+We are able to relax this limitation and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
 This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).

### 2013-03-29 trunk/CompFuzzExt.tex
went through 3.1 and C.1 C.2

@@
 In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space.
+In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space \lnote{not the most clear sentence}.
 %These results are strongest for high entropy sources.
@@
 
-Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.
+\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.
 Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
 However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones.
+\lnote{this paragraph needs rephrasing and better gluing with the next one}
 
@@
 The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
-Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.
-When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.
-Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y, \sketch(W)$ with high probability.
-In particular, $\Pr [s\leftarrow \sketch(W) \wedge y\leftarrow Y_s\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y ]\geq 1-\epsilon$.
-This means we can construct a large set $C$ from the support of $Y$.
+In order to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ such that $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $(Y, \sketch(W))$ is computationally indistinguishable from $(W, \sketch(W))$.
+Sample a sketch $s\leftarrow \sketch(W)$.
+We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).
+So, by indistinguishability, it must also succeed on $Y$: specifically, $\rec (y',s) = y$ with high probability, for $y\leftarrow Y|s$ and $y'\leftarrow B_t(y)$).
+ This means we can construct a large set $C$ from the support of $Y|s$.
 $C$ will be an error correcting code and $\rec$ an efficient decoder.
 We can then use standard arguments to turn this code into an information theoretic sketch.
-%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
+
 To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
@@
 While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.
+\lnote{ do we need this?
+if distance is exactly $t'$, then the point is different as long as $t'>0$.
+So why not just say "exactly $t'$ in the definition?}
 
@@
 \begin{definition}
+\label{def:shannon-code}
 Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
@@
 
-Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
+Shannon codes work for all codewords.
+We can also consider a formulation that works for an ``average'' codeword.
+\lnote{is there a source we can reference for the terms average-error and maximal-error?}
+
+ \begin{definition}
 Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
@@
 \end{definition}
-An average error Shannon code is convertible to a maximal error Shannon code with a small loss.
+An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
 We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
@@
 \label{lem:averageToMaximalError}
-Let $C$ be a distribution over space $\mathcal{M}$ with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.
+Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
 There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
@@
 \begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
+Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood \lnote{why $s_{neigh}$ and not $s_{sam}$ as above?} samplable.
 Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.
-Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
+Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$ \lnote{I don't think the asymptotics work here -- we are using concrete parameters, nothing is going to $\infty$, so what does $\Omega$ mean?} .
+Then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 %It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
-For the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
-The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
+For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
+The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
 The formal statement is in the following Lemma.
@@
 Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$ \lnote{same comment about $\Omega$}, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
 $4(\epsilon+t\delta)$. 
@@
 \begin{proof}
-Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that for all $t'\le t$
+Let $C$ be the  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$ such that  $\Hoo(C)\geq k$.  Then for all $t'\le t$
 \[
@@
 For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \sample(c, t') \wedge \rec(c') \neq c]$.  
-Then by Markov inequality:
+Then by Markov's inequality:
 \[
@@
 Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.
-Since $H_\infty(C)\geq k, |C'|\geq 2^{k-1}$~(otherwise $C'$ would contain total weight less that $2^{k-1}\frac{1}{2^k} = 1/2$).
+Since $H_\infty(C)\geq k$, we know $|C'|\geq 2^{k-1}$~(otherwise $\Pr_{c\leftarrow C}[c\in C']=\sum_{c\in C'}\Pr[C=c]$ would be less than $2^{k-1}\frac{1}{2^k} = 1/2$).
 This completes the proof of the~\lemref{lem:averageToMaximalError}.
@@
 \begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ such that 
+  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ and
 \[ 
@@
 \]  
-where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
+where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$\lnote{again, why asysmptotics?}.  One such $Y$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon.$ then $\Pr[D(Y, SS(W)) = 1]>1-\epsilon-t\delta$.
-By Markov inequality there exists a set $S_W$ such that $\Pr[S_W]\geq 1/2$ and $\Pr[ D(Y, s) =1 | \sketch(W) = s \wedge s\in S_W]> 1- 2(\epsilon + t\delta)$.
-Consider the random variable $1_{S_W}$ that is $1$ when $s\in S_X$ and otherwise.
-Then,
-\[
-\Hav(Y  | W) = -\log \left( \Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} + \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})} \right)
-\] 
-Rearranging terms:
-\begin{align*}
-\Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} &= 2^{-\Hav(Y  | W) } - \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})}\\
-&=2^{-\Hav(Y  | W) } = 2^{-k}
-\end{align*}
-This means that $2^{-\Hav(Y | W\in 1_{S_W})} \geq 2^{-k}/\Pr[W\in 1_{S_W}] = 2^{-k+1}$.  That is, $\Hav(Y|W\in 1_{S_W})\geq k-1$.  Fix one value $s \in 1_{S_W}$ such that $\Hav(Y | s)\geq k-1$.
-%This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
-%This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
-Thus, for all $t', 1\leq t'\leq t$ on a random $y$
-\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]\geq 1-2(\epsilon+t\delta).\]  
+$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon$, we know $\Pr[D(Y, \sketch(W)) = 1]>1-\epsilon-t\delta$.
+By Markov's inequality,  there exists a set $S_W$ such that $\Pr[\sketch(W)\in S_W]\ge 1/2$ and for all $s\in \sketch(W)$, $\Pr[ D(Y_s, s) =1]> 1- 2(\epsilon + t\delta)$.
+Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_W$ such that $\Pr[\sketch(W)\in S'_W]> 1/2$ and for all $s\in \sketch(W)$, $\Hoo(Y_s)\ge k-1$.
+\lnote{simplified this derivation}  Fix one value $s \in S_W\cap S'_W$ (which exists because the sum of probabilities of $S_W$ and $S'_W$ is greater than 1).
+Thus, for all such that $t', 1\leq t'\leq t$, 
+\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  

### 2013-03-29 trunk/CompFuzzExt.tex
Working on presentation

@@
 Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-We build \emph{lossless} computational fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{If a source has enough entropy, the entropy losses of a information-theoretic fuzzy extractor can be overcome by running a pseudorandom generator on the derived key $r$.
-However, when the source is low entropy, these entropy losses may not leave sufficient entropy to run a pseudorandom generator.}.
+By considering a computational secrecy requirement, we are able to construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{A trivial construction is possible for very high entropy sources.
+An information-theoretic fuzzy extractor can be used to derive a key $r$ and $r$ can be expanded using a pseudorandom generator.
+However, when the source is low entropy, the entropy loss due to the information theoretic fuzzy extractor may make it impossible to securely run a pseudorandom generator.
+We present a comparison between the two methods in \secref{sec:prg based comparison}}.
 % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).

### 2013-04-01 CompFuzzExt.tex
First draft of presentation

@@
 Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-We build \emph{lossless} computational fuzzy extractors, in which $r$ is pseudorandom conditioned on $p$ and $r$ is as long as the entropy of $w$.
+By considering a computational secrecy requirement, we are able to construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{A trivial construction is possible for very high entropy sources.
+An information-theoretic fuzzy extractor can be used to derive a key $r$ and $r$ can be expanded using a pseudorandom generator.
+However, when the source is low entropy, the entropy loss due to the information theoretic fuzzy extractor may make it impossible to securely run a pseudorandom generator.
+We present a comparison between the two methods in \secref{sec:prg based comparison}}.
 % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
-We demonstrate how to build such lossless fuzzy extractors~(\consref{cons:informal construction}) based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
-
+Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
 %We show that this relaxation of the security requirement is  useful.
@@
 \item Randomly select rows without replacement $i_1,..., i_n\leftarrow [1,m]$.  
-\item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this is $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
+\item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this as $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
 \item Compute $X' = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).

### 2013-04-02 trunk/CompFuzzExt.tex
Fixing inversion algorithm not taking enough samples

@@
 \newcommand{\vA}{\vect{A}}
+\newcommand{\vc}{\vect{c}}
 \newcommand{\vW}{\vect{W}}
@@
 \newcommand{\vs}{\vect{s}}
-\newcommand{\vc}{\vect{c}}
 \newcommand{\vx}{\vect{x}}
@@
 In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space \lnote{not the most clear sentence}.
+In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch is at most $n - |B_t(\cdot)|$.
+For comparison, random linear codes achieve unpredictability $n(1-o(1)) - B_t(\cdot) $.
+
 %These results are strongest for high entropy sources.
@@
 \end{definition}
-We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.
+%We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.
 While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.
@@
 We can also consider a formulation that works for an ``average'' codeword.
-\lnote{is there a source we can reference for the terms average-error and maximal-error?}
+\lnote{is there a source we can reference for the terms average-error and maximal-error?}\bnote{I think the right thing to reference is Cover-Thomas, but I don't have a copy to check right now}
 
@@
 \begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood \lnote{why $s_{neigh}$ and not $s_{sam}$ as above?} samplable.
+Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.
 Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$ \lnote{I don't think the asymptotics work here -- we are using concrete parameters, nothing is going to $\infty$, so what does $\Omega$ mean?} .
-Then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
+Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
+If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$ \lnote{same comment about $\Omega$}, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
 $4(\epsilon+t\delta)$. 
@@
 
-To extract pseudoranom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
+To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
 The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
@@
 \begin{construction}
-\label{cons:decoding algorithm} Suppose that for a $(n, m, q, \chi)$ where $m\geq 2n$.  We describe inverter $\mathcal{I}_t$:
+\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe inverter $\mathcal{I}_t$:
 \begin{enumerate}
-\item Input $\vA , \vect{C} = \vA X + W - W'$
-\item Randomly select rows without replacement $i_1,..., i_n\leftarrow [1,m]$.  
-\item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this is $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
-\item Compute $X' = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
+\item Input $\vA , \vc = \vA X + W - W'$
+\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
+\item Restrict $\vA, \vc$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, \vc_{i_1,...,i_{2n}}$.
+\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
+Denote by $\vA', \vc'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
+\item Compute $X' = \vA'\vc'$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
 \item Output $X'$.
@@
 We need $t$ to be small enough for step (4) to succeed with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
-The second condition is to ensure that there are few false positives in step (4).
+The second condition is to ensure that there are few false positives in step (5).
 This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.
 The exact statement is in \corref{cor:code high distance}.
-Furthermore step (4) is computable in time $O(n^3)$.
-This is also a sufficient condition for step (4) to succeed with probability at least $1/\poly(n)$.  We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
+Furthermore, steps (3-5) are computable in time $O(n^3)$.
+This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.
+We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
+$\mathcal{I}_t$ is efficient as long as $t$ is small enough.
+The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
 %  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).
@@
 %\end{lemma}
-\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-1)$]
+\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-2)$]
 \label{lem:i t poly time}
-Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 2n$.
+Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.
 Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
 Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-1)\log n$.
-Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
+Then $\mathcal{I}_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
 \end{lemma}
-\textbf{Note:} If we consider the setting where $t\leq m/n-1$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.
-Our main theorems apply when $t\leq m/n$ with slightly better parameters.
-We concentrate on the setting $t\leq d\log n(m/n-1)$.
+\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.
+Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.
+We concentrate on the setting $t\leq d\log n(m/n-2)$.
 Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $W$ be uniform over $\zo^{(c+d)nb/d}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
+Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
+Let $W$ be uniform over $\zo^{(c+2d)nb/d}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
 That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = H_\infty(W)$
@@
 with 
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
 \end{theorem}
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.
-Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+d)n/d+\alpha \right)b})$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/2$) using quantum algorithms.
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
+Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+2d)n/d+\alpha \right)b})$.
+Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms.
 There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
@@
 %\]
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{2d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
+$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
 \end{theorem}
@@
 \begin{claim}
+\label{cl:full rank matrix}
 Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
@@
 \]  
-where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$\lnote{again, why asysmptotics?}.  One such $Y$ must exist by the definition of conditional HILL entropy.
+where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $Y$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_W$ such that $\Pr[\sketch(W)\in S'_W]> 1/2$ and for all $s\in \sketch(W)$, $\Hoo(Y_s)\ge k-1$.
-\lnote{simplified this derivation}  Fix one value $s \in S_W\cap S'_W$ (which exists because the sum of probabilities of $S_W$ and $S'_W$ is greater than 1).
+\lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $s \in S_W\cap S'_W$ (which exists because the sum of probabilities of $S_W$ and $S'_W$ is greater than 1).
 Thus, for all such that $t', 1\leq t'\leq t$, 
@@
 \begin{proof}
-We first note that $R(X, (\vA, \vA X+W))$ is computable in time $O(n^3\log q)$ by computing $AX+(W-W')- AX$ and checking if all dimensions have magnitude at most $|W|_\infty$ and at most $t$ dimensions have nonzero magnitude.
-We consider the expected number of iterations in step 2 when $t\leq d\log n\left(\frac{m}{n}-1\right)$.
-Steps 3 and 4 can be accomplished in time $n^3\log q $.
-An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.
+Let $d$ be a constant and $t = d\log n\left( \frac{m}{n}-2\right)$.  
+By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $t$ with probability $1-e^{-\Omega(n)}$.
+Thus, a false matches occurs in step (5) with probability $e^{-\Omega(n)}$.
+This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\mathcal{I}_t$.
+We consider the expected number of times step 2 is executed when $t\leq d\log n\left(\frac{m}{n}-1\right)$.
+Steps (3-5) can be accomplished in time $n^3\log q $.
+An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.
+The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $\vc_{i_1,...,i_{2n}}$ has no errors.
 The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
@@
 \begin{align*}
-\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{n-1}\left( 1-\frac{d\log n\left(\frac{m}{n}-1\right)}{m-i}\right)\\
-&\geq  \prod_{i=0}^{n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-n}{m-i}\right)\right)\geq \prod_{i=0}^{n-1}\left( 1-\frac{d\log n}{n}\right) \\
-&= \left(1-\frac{d\log n}{n}\right)^n  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{d\log n}\geq \frac{1}{4^{d\log n}} = \frac{1}{n^{2d}}
-\end{align*}
-Thus, the expected number of iterations in step 2 is $n^{2d}$.  We assume all matrix operations can be completed in time $n^3\log q$, giving expected running approximately $n^{2d}(n^3 \log q)$.
+\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n\left(\frac{m}{n}-2\right)}{m-i}\right)\\
+&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
+&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}
+\end{align*}
+Now, we consider the probability that no sub matrix of $\vA_{i_1,..., i_{2n}}$ has full rank.
+This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).
+Thus, the probability that a given iteration succeeds $\frac{1}{n^{4d}} - e^{-\Omega(n)}$.
+Thus, the expected number of iterations in step 2 at most  $2n^{4d}$.
+We assume all matrix operations can be completed in time $n^3\log q$, giving expected running approximately $O(n^{4d}(n^3 \log q))$.
 \end{proof}
@@
 We ignore this effect and assume that $\rho q = 2n^{1/2+3\gamma}m$.
-\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-1)$.
+\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
 \item Minimize entropy loss of the construction.
@@
 n_0&< n -k \\
-t&\leq d \log n\left(\frac{m}{n}-1\right)\\
+t&\leq d \log n\left(\frac{m}{n}-2\right)\\
 q &= n^f\\
@@
 n_0&< n - k\\
-t&\leq d\log n\left(\frac{m}{n}-1\right)\\
+t&\leq d\log n\left(\frac{m}{n}-2\right)\\
 m \log 2n^{1/2+3\gamma}m &= k \log n^f
@@
 n_0&< n -k \\
-t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
+t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
 %f \log n &= \frac{m}{n}\log 2n^2m\\
@@
 To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
-Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-1)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
+Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
 \begin{align*}
 n_0&< n -k \\
-m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+d)}{d}\frac{\log \frac{2(c+d)}{d} n^{3/2+3\gamma}}{\log n}
+m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
+f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
 \end{align*}
@@
 \begin{align*}
-m &= \frac{(c+d)n}{d}\\
+m &= \frac{(c+2d)n}{d}\\
 q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+d)n^{3/2+3\gamma}}{d}
-\end{align*}
-Furthermore, we get decoding in time $O(n^{2d}(n^3\log n))$.
+\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
+\end{align*}
+Furthermore, we get decoding in time $O(n^{4d}(n^3\log n))$.
 We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).
@@
 n_0&< n -k  -\alpha -\beta\\
-t&\leq d \log n\left(\frac{m}{n}-1\right)\\
+t&\leq d \log n\left(\frac{m}{n}-2\right)\\
 q &= n^f\\
@@
 n_0&< n - k - \alpha -\beta\\
-t&\leq d\log n\left(\frac{m}{n}-1\right)\\
+t&\leq d\log n\left(\frac{m}{n}-2\right)\\
 m \log 2n^{1/2+3\gamma}m &= k \log n^f
@@
 n_0&< n -k  - \alpha - \omega(1) \\
-t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
+t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
 %f \log n &= \frac{m}{n}\log 2n^2m\\
@@
 To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.
-Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-1)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
+Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
 \begin{align*}
 n_0&< n/3 -  \log n\\
-m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+d)}{d}\right)\frac{\log \frac{2(c+d)}{d} n^{3/2+3\gamma}}{\log n}
+m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
+f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
 \end{align*}
@@
 \begin{align*}
-m &= \frac{(c+d)n}{d}\\
+m &= \frac{(c+2d)n}{d}\\
 q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+d)n^{3/2+3\gamma}}{d}
+\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
 \end{align*}

### 2013-04-03 trunk/CompFuzzExt.tex
Switched HILL imp to relaxed HILL

@@
 \newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
+\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL-rlx}}\xspace}
 \newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
@@
 \label{sec:imp HILL sketch}
-We recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
+It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}, here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}).
 
 \begin{definition}
-Let $(X, Z)$ be a pair of random variables.  $X$ has 
-\emph{conditional HILL entropy} at least $k$ conditioned on $Z$,
-denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Z)\geq k$ if there exists a collection of
-distributions $Y_z$ for each $z\in Z$, giving rise to a joint distribution
-$(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((X, Z),(Y,Z))\leq \epsilon$.
+Let $(W, X)$ be a pair of random variables.  $W$ has 
+\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
+denoted $H^{\hill-rlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
 \end{definition}
 
-\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.
+%\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}
+
+Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.
 Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
-However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones.
-\lnote{this paragraph needs rephrasing and better gluing with the next one}
-
 %Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
@@
 We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.
-
-Suppose we redefine secure sketches using HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
+We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
+
 Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches).
@@
 The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
-In order to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ such that $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $(Y, \sketch(W))$ is computationally indistinguishable from $(W, \sketch(W))$.
+In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y, Z$ such that $\Hav(Y | Z)\geq \tilde{m}$ and $(Y, Z)$ is computationally indistinguishable from $(W, \sketch(W))$.
 Sample a sketch $s\leftarrow \sketch(W)$.
 We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).
-So, by indistinguishability, it must also succeed on $Y$: specifically, $\rec (y',s) = y$ with high probability, for $y\leftarrow Y|s$ and $y'\leftarrow B_t(y)$).
- This means we can construct a large set $C$ from the support of $Y|s$.
+%So, by indistinguishability, it must also succeed on $Y$.
+ Consider the following experiment: 1) sample $z\leftarrow Z$, 2) draw $y\leftarrow Y|z$ and 3) $y'\leftarrow B_t(y)$. By indistinguishability $\rec (y',z) = y$ with high probability.
+ This means we can construct a large set $C$ from the support of $Y|z$.
 $C$ will be an error correcting code and $\rec$ an efficient decoder.
@@
 
-Shannon codes work for all codewords.
-We can also consider a formulation that works for an ``average'' codeword.
-\lnote{is there a source we can reference for the terms average-error and maximal-error?}\bnote{I think the right thing to reference is Cover-Thomas, but I don't have a copy to check right now}
+Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.
 
@@
 \end{definition}
+An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
+See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.
 An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
-We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
+We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
 \begin{lemma}
@@
 We can now formalize the intuition above.
-A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
+A sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
@@
 \begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ and
+  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(Y, Z)$ be a joint distribution such that $\Hav(Y | Z)\geq k$ and
 \[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))<\epsilon.
+\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z))<\epsilon.
 \]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $Y$ must exist by the definition of conditional HILL entropy.
+where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \begin{enumerate}
-\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*, t$.
+\item Input $y\in\mathcal{M}, z \in\{0, 1\}^*, t$.
 \item For all $1\leq t'\leq t$: 
-\subitem  $z'\leftarrow \sample(z, t')$.
-\subitem If $\rec(z', s) \neq  z$ output $0$.
+\subitem  $y'\leftarrow \sample(y, t')$.
+\subitem If $\rec(y', z) \neq  y$ output $0$.
 \item Output $1$.
@@
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon$, we know $\Pr[D(Y, \sketch(W)) = 1]>1-\epsilon-t\delta$.
-By Markov's inequality,  there exists a set $S_W$ such that $\Pr[\sketch(W)\in S_W]\ge 1/2$ and for all $s\in \sketch(W)$, $\Pr[ D(Y_s, s) =1]> 1- 2(\epsilon + t\delta)$.
-Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_W$ such that $\Pr[\sketch(W)\in S'_W]> 1/2$ and for all $s\in \sketch(W)$, $\Hoo(Y_s)\ge k-1$.
-\lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $s \in S_W\cap S'_W$ (which exists because the sum of probabilities of $S_W$ and $S'_W$ is greater than 1).
+$\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.
+By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y|z, z) =1]> 1- 2(\epsilon + t\delta)$.
+Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$ and for all $z\in S'_Z$, $\Hoo(Y | z)\ge k-1$.
+\lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).
 Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
+\[ \Pr_{y\leftarrow Y|z}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
+Thus,  $Y|z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$ and $2^{k-1}$ points.
+The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
 \end{proof}
@@
 Our parameters will differ significantly depending on what setting of $t$ is used.
-We will consider both settings where $t\leq m/n-1$ and $t\leq c\log n (m/n-1)$.
+We will consider both settings where $t\leq m/n-2$ and $t\leq c\log n (m/n-2)$.
 Recall these corresponding to Construction~\ref{cons:decoding algorithm} running either in fixed polynomial time or time approximately $n^{2c}$.

### 2013-04-05 CompFuzzExt.tex
Switched HILL imp to relaxed HILL

@@
 
-Shannon codes work for all codewords.
-We can also consider a formulation that works for an ``average'' codeword.
-\lnote{is there a source we can reference for the terms average-error and maximal-error?}
+Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.
 
@@
 We can now formalize the intuition above.
-A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
+A sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood \lnote{why $s_{neigh}$ and not $s_{sam}$ as above?} samplable.
+Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.
 Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$ \lnote{I don't think the asymptotics work here -- we are using concrete parameters, nothing is going to $\infty$, so what does $\Omega$ mean?} .
-Then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
+Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
+If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \begin{construction}
-\label{cons:decoding algorithm} Suppose that for a $(n, m, q, \chi)$ where $m\geq 2n$.  We describe inverter $\mathcal{I}_t$:
+\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe inverter $\mathcal{I}_t$:
 \begin{enumerate}
-\item Input $\vA , \vect{C} = \vA X + W - W'$
-\item Randomly select rows without replacement $i_1,..., i_n\leftarrow [1,m]$.  
-\item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this as $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
-\item Compute $X' = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
+\item Input $\vA , \vc = \vA X + W - W'$
+\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
+\item Restrict $\vA, \vc$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, \vc_{i_1,...,i_{2n}}$.
+\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
+Denote by $\vA', \vc'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
+\item Compute $X' = \vA'\vc'$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
 \item Output $X'$.
@@
 \begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ and
+  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(Y, Z)$ be a joint distribution such that $\Hav(Y | Z)\geq k$ and
 \[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))<\epsilon.
+\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z))<\epsilon.
 \]  
-where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$\lnote{again, why asysmptotics?}.  One such $Y$ must exist by the definition of conditional HILL entropy.
+where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon$, we know $\Pr[D(Y, \sketch(W)) = 1]>1-\epsilon-t\delta$.
-By Markov's inequality,  there exists a set $S_W$ such that $\Pr[\sketch(W)\in S_W]\ge 1/2$ and for all $s\in \sketch(W)$, $\Pr[ D(Y_s, s) =1]> 1- 2(\epsilon + t\delta)$.
-Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_W$ such that $\Pr[\sketch(W)\in S'_W]> 1/2$ and for all $s\in \sketch(W)$, $\Hoo(Y_s)\ge k-1$.
-\lnote{simplified this derivation}  Fix one value $s \in S_W\cap S'_W$ (which exists because the sum of probabilities of $S_W$ and $S'_W$ is greater than 1).
+$\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.
+By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y|z, z) =1]> 1- 2(\epsilon + t\delta)$.
+Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$ and for all $z\in S'_Z$, $\Hoo(Y | z)\ge k-1$.
+\lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).
 Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
+\[ \Pr_{y\leftarrow Y|z}[y'\leftarrow \sample(y, t') \wedge \rec(y',z) = y]> 1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
+Thus,  $Y|z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,z)$ and $2^{k-1}$ points.
+The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
 \end{proof}

### 2013-04-05 CompFuzzExt.tex
Adding references to computational extractors

@@
 Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-By considering a computational secrecy requirement, we are able to construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{A trivial construction is possible for very high entropy sources.
+Computational extractors~\cite{krawczyk2010cryptographic, dachman2012computational} have the same goal in the setting without errors.
+One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.
+In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.
+This construction is only possible if the entropy losses due to a secure sketch and information-theoretic extraction leave enough truly random bits.
+We ask if a better solution is possible by making the entire process ``computational''.
+
+By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{A trivial construction is possible for very high entropy sources.
 An information-theoretic fuzzy extractor can be used to derive a key $r$ and $r$ can be expanded using a pseudorandom generator.

### 2013-04-09 CompFuzzExt.tex
Second draft of presentation

@@
 \begin{abstract} 
-\lnote{This is an old abstract, no longer correct}
-One-message information reconciliation protocols called secure sketches remove noise
-from secrets without revealing too much about them.  They are a crucial ingredient in
-fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.
+%\lnote{This is an old abstract, no longer correct}
+Fuzzy extractors derive cryptographically strong keys from noisy sources.
+They are traditionally built by combining a secure sketch and a randomness extractor.
+Secure sketches remove noise from correct errors in the source while revealing little about the source.
+Randomness extractors convert high entropy sources to the uniform distribution.
+%Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.
+The minimal entropy loss
+%One-message information reconciliation protocols called secure sketches remove noise
+%from secrets without revealing too much about them.  They are a crucial ingredient in
+%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.
 
 Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  
-The minimal entropy loss is dictated by bounds on error-correcting codes.
-
-We overcome these bounds by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors, and building them based on the Learning with Errors (LWE) problem.
-We thus obtain the first secure sketch with no loss in entropy.
-More specifically, our contributions are as follows:
-
+The minimal entropy loss is dictated by bounds on error-correcting codes.  Fuzzy extractors suffer from similar bounds imposed by coding theory.
+
+We ask whether these bounds can be overcome by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors.
+%The answer we provide an answer for both secure sketches and fuzzy extractors.
+The answer to this question is mixed, For secure sketches the answer is no, and for fuzzy extractors the answer is yes.
 \begin{itemize}
-\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.
+\item \textbf{Secure Sketches:} We show that a secure sketch that retains a large amount of HILL pseudo entropy implies a secure sketch which retains a similar amount of information-theoretic entropy.
+We also consider a weaker computational notion of security, the unpredictability of a source conditioned on output of the secure sketch.
+We show that in order to correct $t$ errors, the unpredictability of a source must decrease with the volume of a ball of radius $t$.
+\item \textbf{Fuzzy Extractors:}  We show these impossibility results can be overcome by analyzing fuzzy extractors directly.
+Namely, we show how to build a \emph{lossless} computational fuzzy extractor for uniform sources and certain other sources of high entropy~(namely, symbol-fixing sources, where each dimension is either uniform or fixed), based on the hardness of the Learning with Errors~(LWE) problem.
+This construction requires us to show that the decision version of LWE is secure when a small number of dimension has no error---a result that may be of independent interest.
+\end{itemize}
+%mixed, and building them based on the Learning with Errors (LWE) problem.  We thus obtain the first secure sketch with no loss in entropy.   More specifically, our contributions are as follows:
+%
+%\begin{itemize}
+%\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.
 We do so by demonstrating that a secure sketch defined via HILL pseudoentropy is subject to the same coding-based  bounds as the information-theoretic secure sketch.
 We then find a different relaxation, using unpredictability entropy, and show that it can be used to construct computational fuzzy extractors.
-
-\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.
+%
+%
+%\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.
 This construction requires us to show that the decision version of LWE is secure when a small number of dimensions have no error---a result that may be of independent interest.
-\end{itemize}
+%\end{itemize}
 \end{abstract}

### 2013-04-11 trunk/CompFuzzExt.tex
minor edits to 3, 3.1, and clarifiying the proof in appendix C.2

@@
 \usepackage{algpseudocode}
+
+\mathchardef\mhyphen="2D
 
@@
 \newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
-\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL-rlx}}\xspace}
+\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL\mhyphen rlx}}\xspace}
 \newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
@@
 \label{sec:defCompFuzzyExtractors}
-In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.
+In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.
+We consider two different notions for computational entropy, and for both of them show that we can do essentially as well information-theoretically as computationally.
+
 %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp.
@@
 In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch is at most $n - |B_t(\cdot)|$.
-For comparison, random linear codes achieve unpredictability $n(1-o(1)) - B_t(\cdot) $.
+In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $n - |B_t(\cdot)|$.
+Since random linear codes already achieve min-entropy $n(1-o(1)) - B_t(\cdot)$ on uniform inputs, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.
+\lnote{$B_t$ notation is not correct here -- it denotes the ball, not the logarithm of its volume} \lnote{Should we say something about efficiency of decoding?
+Also, should we be clearer that these bounds are tight for uniform inputs and Hamming metric, but not necessarily otherwise?
+Perhaps just a pointer to the last part of this section (which could be called 3.3?}
 
@@
 HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
-It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}, here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}).
+It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+Here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}); since we show impossibility even for this weaker definition, impossibility for the stronger definition follows immediately.
 
@@
 \emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
-denoted $H^{\hill-rlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
+denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
 \end{definition}
@@
 
-We can now formalize the intuition above.
-A sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
+We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
@@
 \]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy.
+where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy. Let $Y_z$ denote the random variable $Y|Z=z$.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 $\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.
-By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y|z, z) =1]> 1- 2(\epsilon + t\delta)$.
-Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$ and for all $z\in S'_Z$, $\Hoo(Y | z)\ge k-1$.
-\lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).
+By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y_z, z) =1]> 1- 2(\epsilon + t\delta)$.
+
+Because $\Hav(Y | Z)\geq k$, we know that $\expe_{z\leftarrow Z} \max_y \Pr[Y_z=y]\geq 2^k$.
+Applying Markov's inequality to the random variable $\max_y \Pr[Y_z=y]$, there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$, and for all $z\in S'_Z$, $\Hoo(Y_z)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_y \Pr[Y_z=y]$ is positive).
+Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).
 Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{y\leftarrow Y|z}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
+\[ \Pr_{y\leftarrow Y_z}[y'\leftarrow \sample(y, t') \wedge \rec(y',z) = y]> 1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y|z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$ and $2^{k-1}$ points.
+Thus,  $Y_z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,z)$ and $2^{k-1}$ points.
 The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.

### 2013-05-06 trunk/CompFuzzExt.tex
Removing Hamming metric from unpredictability bound

@@
 \newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
+\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
 \newcommand{\dis}{\ensuremath{\mathsf{dis}}}
@@
 In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $n - |B_t(\cdot)|$.
-Since random linear codes already achieve min-entropy $n(1-o(1)) - B_t(\cdot)$ on uniform inputs, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.
-\lnote{$B_t$ notation is not correct here -- it denotes the ball, not the logarithm of its volume} \lnote{Should we say something about efficiency of decoding?
-Also, should we be clearer that these bounds are tight for uniform inputs and Hamming metric, but not necessarily otherwise?
-Perhaps just a pointer to the last part of this section (which could be called 3.3?}
+In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $n - \log |B_t(\cdot)|$.
+Since random linear codes already achieve min-entropy $n(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.
+In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
 
@@
 \begin{definition}
+\label{def:relaxed hill}
 Let $(W, X)$ be a pair of random variables.  $W$ has 
@@
 \begin{definition}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.
+\label{def:neighborhood samplable}
+We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (x, t')$ outputs a random point at distance $t'$ of $x$.
 %That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
@@
 Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$.
 To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
@@
 Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
+$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]<\epsilon$.
 \end{definition}
@@
 \begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.
+Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
 Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
@@
 Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
-Unfortunately, the unpredictability entropy conditioned on the sketch must recreate with $t$.  
+Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
 %An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
@@
 \label{thm:imp of unp entropy}
-Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} = \Omega(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
@@
 This means we cannot construct a good code out of the points of $Y$.
-In \secref{sec:proof of imp unp entropy}, we prove a stronger version of \thref{thm:imp of unp entropy}, based on a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.
-
-\textbf{Avoiding lower bounds from \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy}:}
+In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.
+
+\subsection{Avoiding sketch entropy upper bounds}
+\label{ssec:avoiding bounds}
 
@@
 \[
-\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \sample (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
+\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \neigh (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
 \]
-For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \sample(c, t') \wedge \rec(c') \neq c]$.  
+For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \neigh(c, t') \wedge \rec(c') \neq c]$.  
 Then by Markov's inequality:
@@
 \begin{enumerate}
-\item Input $y\in\mathcal{M}, z \in\{0, 1\}^*, t$.
+\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
 \item For all $1\leq t'\leq t$: 
-\subitem  $y'\leftarrow \sample(y, t')$.
-\subitem If $\rec(y', z) \neq  y$ output $0$.
+\subitem  $w'\leftarrow \neigh(w, t')$.
+\subitem If $\rec(w', z) \neq  w$ output $0$.
 \item Output $1$.
@@
 
+\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
 \subsection{Proof of \thref{thm:imp of unp entropy}}
@@
 This relaxed definition allows both the variable and the condition to be replaced.
-Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}.
+This is analogous to the relaxed HILL entropy~(see \defref{def:relaxed hill}).%Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}~(we provide a formulation of this notion in \defref{def:relaxed hill}).
 
@@
 
+We will prove the result for a metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
+We now define this second condition:
+\begin{definition}
+A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
+\end{definition}
+
 \begin{theorem}
-Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} = \Omega(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
-
+Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
+Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is fixed~(this quantity is denoted by $B_t(\cdot)$).
+Let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
 \end{theorem}
 \begin{proof}
-Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
+Let $\mathcal{M}, \dis$ be a $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable metric space~(by procedures $\sample$ and $\neigh$ respectively).  
+Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.
 Let $Y, Z'$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z'))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n\log |Z| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
+
+Let $B_t(y)$ denote the random variable of a random neighbor of distance at most $t$ from $y$.
+Recall, the algorithm $\neigh$ outputs neighbors at a fixed distance, the random variable $B_t(y)$ may not be efficiently computable, we only use it as a random variable.
 We begin by showing that \rec must recover points of $Y$.  
@@
 \Pr[\rec(B_t(Y), Z') = Y]&=\\
-\Pr[(y, z)\leftarrow (Y, Z) \wedge y'\leftarrow B_t(y) \wedge \rec(y', z) = y] &\geq 1-\epsilon -\delta.
+\Pr[(y, z)\leftarrow (Y, Z) \wedge y'\leftarrow B_t(y) \wedge \rec(y', z) = y] &\geq 1-\epsilon -t\delta.
 \end{align*}
@@
 \begin{proof}
-Suppose that $\Pr[\rec(B_t(Y), Z') = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+Suppose that $\Pr[\rec(B_t(Y), Z') = Y]<1-\epsilon -t\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
 \begin{itemize}
-\item Input $x\in Z^n, s\in\zo^*$.
-\item Sample $x'\leftarrow B_t(x)$.
-\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
+\item Input $w\in \mathcal{M}, s\in\zo^*$.
+\item For all $1\leq t'\leq t$: 
+\subitem  $w'\leftarrow \neigh(w, t')$.
+\subitem If $\rec(w', z) \neq  w$ output $0$.
+\item Output $1$.
 \end{itemize}
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in Z^n$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) )= W)  ]\geq 1-\delta$.
-The statement of the claim follows as
-\begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, Z')] &=\\
-\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), Z') = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
-\end{align*}
+First note that $|D| = t( |\rec|+ s_{neigh} )$.
+Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
+If $\Pr[\rec(B_t(Y), Z') = Y] < 1-\epsilon -t\delta$ there must exist some $1\leq t'\leq t$ where this is true.
+Then
+\begin{align*}
+\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, Z')=1] &\geq\\
+(1-t\delta) - \Pr[\rec(\neigh(Y, t'), Z') = Y] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
+\end{align*}
+This is a contradiction and the statement of the claim follows.
 \end{proof}
@@
 \[
- \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\delta -\epsilon.
+ \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \mathcal{M}} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\epsilon - t\delta.
 \]
 We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, \Pr[B_t(y) = y' | Y=y] = 0$.
-Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
-We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$.
+Now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
 \begin{itemize}
 \item Input $z\in\zo^*$.
-\item Sample $x\leftarrow Z^n$.
-\item Output $\rec(x, z)$.
+\item Sample $x\leftarrow \sample(\cdot)$.
+\item Output $\rec(x, s)$.
 \end{itemize}
-Let $X$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
+Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
 We now show that $\mathcal{I}$ predicts $Y$:
@@
 &= \Pr[(y, z)\leftarrow (Y, Z')] \Pr[\mathcal{I}(z) = y]\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[X = y' ] P_{y', z, y}\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \frac{|Z|^{-n}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq \frac{|B_t(\cdot)|}{|Z|^n} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in Z^n} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq \frac{|B_t(\cdot)|}{|Z|^n}(1-\epsilon - \delta)
-\end{align*}
-Finally converting to entropy, one has $\tilde{m}\leq n\log |Z|-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[X = y' ] P_{y', z, y}\\
+&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \frac{1/|\mathcal{M}|}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
+\end{align*}
+Finally converting to entropy, one has $\tilde{m}\leq \log |\mathcal{M}|-\log |B_t(\cdot)| - \log (1-\epsilon -t \delta)$.
 \end{proof}

### 2013-05-09 trunk/CompFuzzExt.tex
Cleaning up references in introduction

@@
 \documentclass[11pt]{article}
-\def\shownotes{1}
+\def\shownotes{0}
 
@@
 
-Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  
-The minimal entropy loss is dictated by bounds on error-correcting codes.  Fuzzy extractors suffer from similar bounds imposed by coding theory.
+Secure sketches necessarily reveal some information about the noisy secret.
+% and thus the key derived by fuzzy extractors has lower entropy than the source.  
+The minimal entropy loss is dictated by bounds on error-correcting codes.  
+Fuzzy extractors constructed using secure sketches suffer a similar entropy loss.  This entropy loss decreases the length of the derived key.  
+%suffer from similar bounds imposed by coding theory.
 
@@
 
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources.
-(\bnote{Are these references for fuzzy extractors or secure sketches?} as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
+Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).
 The setting
@@
 \end{proof}
+
 %\section{Computational Fuzzy Extractors}

### 2013-05-14 CompFuzzExt.tex
Working on notation, notes added through section 3, need to work through unpredictability proof

@@
 They are traditionally built by combining a secure sketch and a randomness extractor.
-Secure sketches remove noise from correct errors in the source while revealing little about the source.
+Secure sketches remove noise from the source while revealing little information about the source.
 Randomness extractors convert high entropy sources to the uniform distribution.
@@
 
-Authentication generally require a secret drawn from some high-entropy source.
+Authentication generally requires a secret drawn from some high-entropy source.
 One of the primary building blocks for authentication is reliable key derivation.
@@
 
+\bnote{This language is pretty clunky. Revise.}
 The main novel tool in constructing fuzzy extractors is the secure sketch.
@@
 Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
-Using an extractor with a reconstruction would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
-We show lower bounds on the unpredictability loss of sketches in the Hamming metric.
-We prove in \thref{thm:imp of unp entropy} that the unpredictability loss must be at least the volume of the ball of radius $t$.
+Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
+We show lower bounds on the unpredictability loss of sketches.
+We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
 
@@
 This construction is only possible if the entropy losses due to a secure sketch and information-theoretic extraction leave enough truly random bits.
-We ask if a better solution is possible by making the entire process ``computational''.
-
-By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{A trivial construction is possible for very high entropy sources.
-An information-theoretic fuzzy extractor can be used to derive a key $r$ and $r$ can be expanded using a pseudorandom generator.
-However, when the source is low entropy, the entropy loss due to the information theoretic fuzzy extractor may make it impossible to securely run a pseudorandom generator.
-We present a comparison between the two methods in \secref{sec:prg based comparison}}.
+We ask if a better solution is possible by making the entire process ``computational.''\bnote{Should add something about the Dana's result implying PRGs}
+
+By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{As noted above, using a computational extractor, in place of a information-theoretic extractor, allows a lossless construction.
+However, this approach requires the computational extractor to work on the remaining entropy after the secure sketch.
+We compare the two approaches in \secref{sec:prg based comparison}}.
 % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
@@
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-During the presentation, we denote bold letters to be vectors or matrix, capitalized letters to be random variables, and lower case letter to be the elements in the vector.
+We use bold letters for vectors or matrices, capitalized letters to be random variables, and lower case letters for the elements in the vector or samples from a random variable.
 
@@
 A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
-An average-case extractor is simply a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):
+An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):
 
@@
 
+\bnote{The definition of extractor above does not match this lemma.}
 \begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
@@
 
+\bnote{There needs to be more linking language here.}
 It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).
@@
 In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch is at most $n - |B_t(\cdot)|$.
-For comparison, random linear codes achieve unpredictability $n(1-o(1)) - B_t(\cdot) $.
+In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
+Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
+Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
 
@@
 HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
-It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}, here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}).
+It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+Here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}); since we show impossibility even for this weaker definition, impossibility for the stronger definition follows immediately.
 
 \begin{definition}
-Let $(W, X)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
-denoted $H^{\hill-rlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
+\label{def:relaxed hill}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon$.
 \end{definition}
@@
 The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
-In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y, Z$ such that $\Hav(Y | Z)\geq \tilde{m}$ and $(Y, Z)$ is computationally indistinguishable from $(W, \sketch(W))$.
+In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $X, Y$ such that $\Hav(X | Y)\geq \tilde{m}$ and $(X, Y)$ is computationally indistinguishable from $(W, \sketch(W))$.
 Sample a sketch $s\leftarrow \sketch(W)$.
@@
 %So, by indistinguishability, it must also succeed on $Y$.
- Consider the following experiment: 1) sample $z\leftarrow Z$, 2) draw $y\leftarrow Y|z$ and 3) $y'\leftarrow B_t(y)$. By indistinguishability $\rec (y',z) = y$ with high probability.
- This means we can construct a large set $C$ from the support of $Y|z$.
-$C$ will be an error correcting code and $\rec$ an efficient decoder.
+ Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability $\rec (x',z) = x$ with high probability.
+ This means we can construct a large set $\mathcal{C}$ from the support of $X|y$.
+$\mathcal{C}$ will be an error correcting code and $\rec$ an efficient decoder.
 We can then use standard arguments to turn this code into an information theoretic sketch.
@@
 \begin{definition}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.
+\label{def:neighborhood samplable}
+We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.
 %That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
@@
 Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$.
 To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
 \end{definition}
-This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.
+This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
 For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
@@
 Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
-There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
+There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
 \end{lemma}
 
-We can now formalize the intuition above.
-A sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
+We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.
+Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
 Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
-If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
+If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
-The formal statement is in the following Lemma.
+The formal statement is in the following Lemma.\bnote{I feel we should cite this.}
 \begin{lemma}
@@
 \label{def:unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has \emph{unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $I$ of size $s_{sec}$,
 \[
-\Pr[C(Z) = Y ] \leq 2^{-k}
+\Pr[I(Z) = Y ] \leq 2^{-k}
 .\]
@@
 \label{lem:unp extraction} 
-Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
+\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
+Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
 \end{lemma}
 Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
-Unfortunately, the unpredictability entropy conditioned on the sketch must recreate with $t$.  
+Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
 %An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
@@
 This means we cannot construct a good code out of the points of $Y$.
-In \secref{sec:proof of imp unp entropy}, we prove a stronger version of \thref{thm:imp of unp entropy}, based on a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.
-
-\textbf{Avoiding lower bounds from \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy}:}
+In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy~(similar to the relaxed notion of HILL entropy in \defref{def:relaxed hill}).%Our bound is a result of the Hamming bound for the space.
+
+\subsection{Avoiding sketch entropy upper bounds}
+\label{ssec:avoiding bounds}
 
@@
 
+\ignore{
 \subsection{\consref{cons:informal construction} with slightly deficient sources}
@@
 \end{proof}
+
+}
+
 %\section{Computational Fuzzy Extractors}
@@
 \begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(Y, Z)$ be a joint distribution such that $\Hav(Y | Z)\geq k$ and
+  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
 \[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z))<\epsilon.
+\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))<\epsilon.
 \]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy.
+where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. Let $X_y$ denote the random variable $X|Y=y$.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.
-By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y|z, z) =1]> 1- 2(\epsilon + t\delta)$.
-Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$ and for all $z\in S'_Z$, $\Hoo(Y | z)\ge k-1$.
-\lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).
+$\delta^D((W, \sketch(W)), (X, Y))<\epsilon$, we know $\Pr[D(X, Y) = 1]>1-\epsilon-t\delta$.
+By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]> 1- 2(\epsilon + t\delta)$.
+
+Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.
+Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).
+Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).
 Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{y\leftarrow Y|z}[y'\leftarrow \sample(y, t') \wedge \rec(y',z) = y]> 1-2(\epsilon+t\delta).\]  
+\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]> 1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y|z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,z)$ and $2^{k-1}$ points.
+Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.
 The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
@@
 This relaxed definition allows both the variable and the condition to be replaced.
-Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}.
-
+This is analogous to the relaxed HILL entropy~(see \defref{def:relaxed hill}).%Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}~(we provide a formulation of this notion in \defref{def:relaxed hill}).
+
+\bnote{This needs to be consistent with the notation above.  Should be $W, S$ for original and $X, Y$ for indistinguishable distribution.}
 \begin{definition}

### 2013-05-14 CompFuzzExt.tex
Notational consistency for entropy definitions

@@
 \newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
+\newcommand{\unprlx}{\ensuremath{\mathtt{unp\mhyphen rlx}}\xspace}
 \newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
@@
 \label{def:unp entropy}
-For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $I$ of size $s_{sec}$,
+For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
 \[
-\Pr[I(Z) = Y ] \leq 2^{-k}
+\Pr[\mathcal{I}(Z) = Y ] \leq 2^{-k}
 .\]
@@
 The formal statement is below:
+\bnote{Should we list the stronger statement in the appendix or keep this for clarity?}
 \begin{theorem}
@@
 We provide an informal description below.
+\bnote{$\mathcal{I}$ is overloaded as the inverter in unpredictability entropy.  We okay?}
 %Please refer to \consref{cons:informal construction} for the description of the construction.
@@
 In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.
-In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.
+In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output~(this is replacing the randomness extractor with a computational extractor).
 
@@
 
-\bnote{This needs to be consistent with the notation above.  Should be $W, S$ for original and $X, Y$ for indistinguishable distribution.}
 \begin{definition}
 \label{def:relaxed unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a joint distribution $Y, Z'$ such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z'))\leq \epsilon$, and for all circuits $C$ of size at most $s_{sec}$,
+For a distribution $(W, S)$, we say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a joint distribution $X, Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size at most $s_{sec}$,
 \[
-\Pr[C(Z) = Y ] \leq 2^{-k}
+\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
 .\]
@@
 Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.
-Let $Y, Z'$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z'))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n\log |Z| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
-
-Let $B_t(y)$ denote the random variable of a random neighbor of distance at most $t$ from $y$.
-Recall, the algorithm $\neigh$ outputs neighbors at a fixed distance, the random variable $B_t(y)$ may not be efficiently computable, we only use it as a random variable.
-We begin by showing that \rec must recover points of $Y$.  
+Let $X, Y$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
+
+Let $B_t(x)$ denote the random variable of a random neighbor of distance at most $t$ from $x$.
+Recall, the algorithm $\neigh$ outputs neighbors at a fixed distance, the random variable $B_t(x)$ may not be efficiently computable, we use it as a random variable.
+We begin by showing that \rec must recover points of $X$.  
 \begin{claim}
@@
 \begin{align*}
-\Pr[\rec(B_t(Y), Z') = Y]&=\\
-\Pr[(y, z)\leftarrow (Y, Z) \wedge y'\leftarrow B_t(y) \wedge \rec(y', z) = y] &\geq 1-\epsilon -t\delta.
+\Pr[\rec(B_t(X), Y) = X]&=\\
+\Pr[(x, y)\leftarrow (X, Y) \wedge x'\leftarrow B_t(x) \wedge \rec(x', y) = x] &\geq 1-\epsilon -t\delta.
 \end{align*}
@@
 \begin{proof}
-Suppose that $\Pr[\rec(B_t(Y), Z') = Y]<1-\epsilon -t\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
 \begin{itemize}
@@
 Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
-If $\Pr[\rec(B_t(Y), Z') = Y] < 1-\epsilon -t\delta$ there must exist some $1\leq t'\leq t$ where this is true.
+If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist some $1\leq t'\leq t$ where this is true.
 Then
 \begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, Z')=1] &\geq\\
-(1-t\delta) - \Pr[\rec(\neigh(Y, t'), Z') = Y] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
+\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(X, Y)=1] &\geq\\
+(1-t\delta) - \Pr[\rec(\neigh(X, t'), Y) = X] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
 \end{align*}
@@
 \end{proof}
-We now consider the experiment $(y, z)\leftarrow (Y, Z'), y'\leftarrow B_t(y)$ and define the quantity $P_{y' , z, y} = \Pr[\rec(y', z) =y]$.  \clref{clm:y is recoverable} says that 
+We now consider the experiment $(x, y)\leftarrow (X, Y), x'\leftarrow B_t(x)$ and define the quantity $P_{x' , y,x} = \Pr[\rec(x', y) =x]$.  \clref{clm:y is recoverable} says that 
 \[
- \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \mathcal{M}} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\epsilon - t\delta.
+ \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in \mathcal{M}} \Pr[B_t(x) =x' | X = x] P_{x',  y,x} \geq 1-\epsilon - t\delta.
 \]
-We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, \Pr[B_t(y) = y' | Y=y] = 0$.
-Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$.
+We note that for any particular $x, x'$ such that $\dis(x, x')\leq t, \Pr[B_t(x) = x' | X=x] = 1/|B_t(\cdot)|$ and if $\dis(x, x')>t, \Pr[B_t(x) = x' | X=x] = 0$.
+Thus, for all $x, x', \Pr[B_t(x) = x' | X=x] \leq 1/|B_t(\cdot)|$.
 Now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
 \begin{itemize}
-\item Input $z\in\zo^*$.
+\item Input $y\in\zo^*$.
 \item Sample $x\leftarrow \sample(\cdot)$.
@@
 \end{itemize}
-Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
-We now show that $\mathcal{I}$ predicts $Y$:
-\begin{align*}
-2^{\tilde{m}}& = \Pr[\mathcal{I}(Z') = Y] \\
-&= \Pr[(y, z)\leftarrow (Y, Z')] \Pr[\mathcal{I}(z) = y]\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[X = y' ] P_{y', z, y}\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \frac{1/|\mathcal{M}|}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
+Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X'$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
+We now show that $\mathcal{I}$ predicts $X$:
+\begin{align*}
+2^{\tilde{m}}& = \Pr[\mathcal{I}(Y) = x] \\
+&= \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
+&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[X' = x' ]\Pr[\mathcal{I}(y) = x | X = x']\\
+&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[X' = x' ] P_{x', y, x}\\
+&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \frac{\Pr[X' = x']}{\Pr[B_t(x) = x' | X = x]}\Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
+&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \frac{1/|\mathcal{M}|}{1/|B_t(\cdot)|} \Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
+&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
 &\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)

### 2013-05-14 trunk/CompFuzzExt.tex
Notes for sections 4 and 5

@@
 \documentclass[11pt]{article}
-\def\shownotes{0}
+\def\shownotes{1}
 
@@
 In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $n - \log |B_t(\cdot)|$.
-Since random linear codes already achieve min-entropy $n(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.
-In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
+In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
+Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
+Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
 
@@
 \label{def:relaxed hill}
-Let $(W, X)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
-denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon$.
 \end{definition}
@@
 \label{def:neighborhood samplable}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (x, t')$ outputs a random point at distance $t'$ of $x$.
+We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.
 %That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
@@
 \end{definition}
-This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.
+This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
 For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
@@
 Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
-There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
+There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
 \end{lemma}
@@
 Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
-If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
+If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
 %Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 \label{def:unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has \emph{unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
+For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
 \[
-\Pr[C(Z) = Y ] \leq 2^{-k}
+\Pr[\mathcal{I}(Z) = Y ] \leq 2^{-k}
 .\]
@@
 \label{lem:unp extraction} 
-Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
+\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
+Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
 \end{lemma}
@@
 This means we cannot construct a good code out of the points of $Y$.
-In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.
+In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy~(similar to the relaxed notion of HILL entropy in \defref{def:relaxed hill}).%Our bound is a result of the Hamming bound for the space.
 
@@
 
-\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
-Let $m = m(n) = \poly(n)$ be an integer, $q = q(n) = \poly(n)$.
+\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
+Let $m = m(n) = \poly(n)$ and $q = q(n) = \poly(n)$ be integers.
 The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
 
-We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-secure if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If $\distLWE_{n, m, q, \chi}$ is secure for all $t = \poly(n), \epsilon  = 1/\poly(n)$ we say it is \emph{secure}.
+We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
+If $\distLWE_{n, m, q, \chi}$ is secure for all $s_{sec} = \poly(n), \epsilon  = 1/\poly(n)$ we say it is \emph{secure}.
 \end{definition}
@@
 Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
+\bnote{Should we mention the recent classical reduction here?}
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
@@
 If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.
-That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_q^m))\leq \epsilon$.
+That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_{m\log q}))\leq \epsilon$.
 
@@
 %\label{subsec:LWE uniform error}
-Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over an interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian.
-This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it properly into $m$ blocks.
+Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over an interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
+The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
+This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.
+The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
 %As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.
-We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
+%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
 %\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
@@
 \label{lem:uniform LWE decision}
+\bnote{I'm confused, how can the decision version of lattice problems be hard to approximate?  Should it just be if GAPSVP and SIVP are hard to approximate?}
 Let $n$ be a security parameter.
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n/2$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
+If the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
 \end{lemma}
@@
 \label{lem:many hardcore bits}
-Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
+Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\Fq$ and $k\leq n$ be an integer.
 Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}'}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ where $s_{sec}' \approx s_{sec} - n^3$.
+If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard then $H^{\hill}_{\epsilon, s_{sec}'}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ where $s_{sec}' \approx s_{sec} - n^3$.
 \end{lemma}
@@
 \begin{enumerate}
-\item Input $\vA , \vc = \vA X + W - W'$
+\item Input $\vA , B = \vA X + W - W'$
 \item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, \vc$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, \vc_{i_1,...,i_{2n}}$.
+\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
 \item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
-Denote by $\vA', \vc'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
-\item Compute $X' = \vA'\vc'$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
+Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
+\item Compute $X' = (\vA')^{-1}B'$.  If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
 \item Output $X'$.
@@
 $\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.
-We need $t$ to be small enough for step (4) to succeed with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
+We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
 The second condition is to ensure that there are few false positives in step (5).
@@
 Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
-Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-1)\log n$.
+Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.
 Then $\mathcal{I}_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
@@
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = H_\infty(W)$
+That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = n/2\log q = H_\infty(W)$
 % for following parameters:
@@
 \thref{thm:lossless secure conductor log} shows that a computational fuzzy conductor can be built without incurring any entropy loss.
-This is essentially due to $\vA X+W$ looking like a uniformly random point and thus providing no information about either $X$ or $W$.
+This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.
 %A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.
@@
 In this section we to constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
+This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.
 In particular, using the same hardness of approximating GAPSVP and SIVP, Applebaum et.
@@
 We now study \consref{cons:informal construction} with a symbol fixing source.
-Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations with no error and $W$ can be recovered with Gaussian elimination.
+Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations and their error and $W$ can be recovered with Gaussian elimination.
 We show that security degrades exponentially as symbols are fixed.
@@
 Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$.
-For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$.
+For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$.
 The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
@@
 To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant in $n$.
-The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for smal values of $n$.
-
+The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
+
+\ignore{
 \subsection{\consref{cons:informal construction} with slightly deficient sources}
@@
 \end{proof}
+
+}
 
@@
 \begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(Y, Z)$ be a joint distribution such that $\Hav(Y | Z)\geq k$ and
+  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
 \[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z))<\epsilon.
+\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))<\epsilon.
 \]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy. Let $Y_z$ denote the random variable $Y|Z=z$.
+where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. Let $X_y$ denote the random variable $X|Y=y$.
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.
-By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y_z, z) =1]> 1- 2(\epsilon + t\delta)$.
-
-Because $\Hav(Y | Z)\geq k$, we know that $\expe_{z\leftarrow Z} \max_y \Pr[Y_z=y]\geq 2^k$.
-Applying Markov's inequality to the random variable $\max_y \Pr[Y_z=y]$, there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$, and for all $z\in S'_Z$, $\Hoo(Y_z)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_y \Pr[Y_z=y]$ is positive).
-Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).
+$\delta^D((W, \sketch(W)), (X, Y))<\epsilon$, we know $\Pr[D(X, Y) = 1]>1-\epsilon-t\delta$.
+By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]> 1- 2(\epsilon + t\delta)$.
+
+Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.
+Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).
+Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).
 Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{y\leftarrow Y_z}[y'\leftarrow \sample(y, t') \wedge \rec(y',z) = y]> 1-2(\epsilon+t\delta).\]  
+\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]> 1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $Y_z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,z)$ and $2^{k-1}$ points.
+Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.
 The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
@@
 \label{def:relaxed unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a joint distribution $Y, Z'$ such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z'))\leq \epsilon$, and for all circuits $C$ of size at most $s_{sec}$,
+For a distribution $(W, S)$, we say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a joint distribution $X, Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size at most $s_{sec}$,
 \[
-\Pr[C(Z) = Y ] \leq 2^{-k}
+\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
 .\]

### 2013-05-14 CompFuzzExt.tex
Adding notes to appendices

@@
 To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant in $n$.
-The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for smal values of $n$.
+The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
 
@@
 \end{theorem}
-Of particular, concern will be the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
+Our setting is the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
 \begin{corollary}
@@
 We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).
-It suffices to show that for sufficiently large $n$, $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.
+It suffices to show that for sufficiently large $n$, there exists $\epsilon>0$ where $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.
 For sufficiently large $n$:
@@
 
+\bnote{Why are our distinguishers in mathcal here?  There aren't in the body.}
 Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
@@
 Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-It suffices to build a ppt distinguisher $\D'$  where
+It suffices to build a distinguisher~(of polynomial size) $\D'$  where
 \begin{align}
@@
 \begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
+\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
 \item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
@@
 %\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
+\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve$ and where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
 \item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
@@
 Thus, we restrict attention to $\vW_T$~(the columns of $W$ included in $T$).
-Fix a particular row $i$.
+Consider a particular row $i$.
 Then $\vW_{i, T} = \gamma_i \vS_{T}$.
@@
 \begin{proof}
-Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
+Denote by $\vx'$ the value such that $\vA'\vx'+\ve' = \vb'$.  
 Then partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
@@
 \[
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
+\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
 \]
@@
 (\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
-&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
-\\&=  \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}
+&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
+\\&=  \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
 \end{align*}
@@
 Steps (3-5) can be accomplished in time $n^3\log q $.
-An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.
-The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $\vc_{i_1,...,i_{2n}}$ has no errors.
+An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.
+The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $B_{i_1,...,i_{2n}}$ has no errors.
 The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
@@
 \end{align*}
-Now, we consider the probability that no sub matrix of $\vA_{i_1,..., i_{2n}}$ has full rank.
+Now, we consider the probability that some sub matrix of $\vA_{i_1,..., i_{2n}}$ has full rank.
 This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).
@@
 %\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
-Note that $f$ is at most a constant in $n$.
+Note that $f$ is at a constant in $n$.
 
@@
 This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.
-Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
+%Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
 
@@
 \begin{align*}
-n_0&< n -k  - \alpha - \omega(1) \\
+n_0&< n -k  - \alpha - \beta \\
 t&\leq d\log n\left(\frac{ m }{n} -2\right)\\

### 2013-05-14 trunk/notation.tex
adding notation file for lookup consistency

--- 2013-05-14 CompFuzzExt.tex
@@
 \documentclass[11pt]{article}
-\def\shownotes{1}
 
@@
 \usepackage{algpseudocode}
-
-\mathchardef\mhyphen="2D
-
-\newcommand{\secref}[1]{\mbox{Section~\ref{#1}}}
-\newcommand{\subsecref}[1]{\mbox{Subsection~\ref{#1}}}
-\newcommand{\apref}[1]{\mbox{Appendix~\ref{#1}}}
-\newcommand{\thref}[1]{\mbox{Theorem~\ref{#1}}}
-\newcommand{\exref}[1]{\mbox{Example~\ref{#1}}}
-\newcommand{\defref}[1]{\mbox{Definition~\ref{#1}}}
-\newcommand{\corref}[1]{\mbox{Corollary~\ref{#1}}}
-\newcommand{\lemref}[1]{\mbox{Lemma~\ref{#1}}}
-\newcommand{\assref}[1]{\mbox{Assumption~\ref{#1}}}
-\newcommand{\probref}[1]{\mbox{Problem~\ref{#1}}}
-\newcommand{\clref}[1]{\mbox{Claim~\ref{#1}}}
-\newcommand{\propref}[1]{\mbox{Proposition~\ref{#1}}}
-\newcommand{\remref}[1]{\mbox{Remark~\ref{#1}}}
-\newcommand{\consref}[1]{\mbox{Construction~\ref{#1}}}
-\newcommand{\figref}[1]{\mbox{Figure~\ref{#1}}}
-\DeclareMathOperator*{\expe}{\mathbb{E}}
 
@@
 
-\newcommand{\lwe}{\class{LWE}}
-\newcommand{\LWE}{\class{LWE}}
-\newcommand{\distLWE}{\ensuremath{\class{dist\mbox{-}LWE}}}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
-
-\newcounter{ctr}
-\newcounter{savectr}
-\newcounter{ectr}
-
-\newenvironment{newitemize}{%
-\begin{list}{\mbox{}\hspace{5pt}$\bullet$\hfill}{\labelwidth=15pt%
-\labelsep=5pt \leftmargin=20pt \topsep=3pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{3pt} }}{\end{list}}
-
-\newenvironment{newenum}{%
-\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=17pt%
-\labelsep=5pt \leftmargin=22pt \topsep=3pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt} }}{\end{list}}
-
-\newenvironment{tiret}{%
-\begin{list}{\hspace{2pt}\rule[0.5ex]{6pt}{1pt}\hfill}{\labelwidth=15pt%
-\labelsep=3pt \leftmargin=22pt \topsep=3pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt}}}{\end{list}}
-
-\newenvironment{blocklist}{\begin{list}{}{\labelwidth=0pt%
-\labelsep=0pt \leftmargin=0pt \topsep=10pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{20pt}}}{\end{list}}
-
-\newenvironment{blocklistindented}{\begin{list}{}{\labelwidth=0pt%
-\labelsep=30pt \leftmargin=30pt\topsep=5pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{10pt}}}{\end{list}}
-
-\newenvironment{onelist}{%
-\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=18pt%
-\labelsep=7pt \leftmargin=25pt \topsep=2pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt} }}{\end{list}}
-
-\newenvironment{twolist}{%
-\begin{list}{{\rm (\arabic{ctr}.\arabic{ectr})}%
-\hfill}{\usecounter{ectr} \labelwidth=26pt%
-\labelsep=7pt \leftmargin=33pt \topsep=2pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt} }}{\end{list}}
-
-\newenvironment{centerlist}{%
-\begin{list}{\mbox{}}{\labelwidth=0pt%
-\labelsep=0pt \leftmargin=0pt \topsep=10pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{10pt} }}{\end{list}}
-
-\newenvironment{newcenter}[1]{\begin{centerlist}\centering%
-\item #1}{\end{centerlist}}
-
-\newenvironment{codecenter}[1]{\begin{small}\begin{centerlist}\centering%
-\item #1}{\end{centerlist}\end{small}}
-
-\ifnum\shownotes=1
-\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
-\else
-\newcommand{\authnote}[2]{}
-\fi
-\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
-\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
-\newcommand{\xnote}[1]{{\authnote{Xianrui}{#1}}}
-
-\newcommand{\ve}{\vect{e}}
-\newcommand{\vm}{\vect{m}}
-\newcommand{\vy}{\vect{y}}
-\newcommand{\vE}{\vect{E}}
-\newcommand{\vS}{\vect{S}}
-\newcommand{\vA}{\vect{A}}
-\newcommand{\vc}{\vect{c}}
-\newcommand{\vW}{\vect{W}}
-\newcommand{\vR}{\vect{R}}
-\newcommand{\vU}{\vect{U}}
-\newcommand{\vT}{\vect{T}}
-\newcommand{\vX}{\vect{X}}
-\newcommand{\vB}{\vect{B}}
-\newcommand{\vz}{\vect{z}}
-\newcommand{\vd}{\vect{d}}
-\newcommand{\vs}{\vect{s}}
-\newcommand{\vx}{\vect{x}}
-\newcommand{\va}{\vect{a}}
-\newcommand{\vb}{\vect{b}}
-\newcommand{\vgamma}{\mathbf{\Gamma}}
-\newcommand{\vt}{\vect{t}}
-\newcommand{\vu}{\vect{u}}
-\newcommand{\vF}{\vect{F}}
-\newcommand{\recout}{x}
-\newcommand{\ignore}[1]{}
-
-\title{\textbf{Computational Fuzzy Extractors}}
-\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
- \and Xianrui Meng \and Leonid Reyzin}
 \begin{document}
-\maketitle
-
-\begin{abstract} 
-%\lnote{This is an old abstract, no longer correct}
-Fuzzy extractors derive cryptographically strong keys from noisy sources.
-They are traditionally built by combining a secure sketch and a randomness extractor.
-Secure sketches remove noise from the source while revealing little information about the source.
-Randomness extractors convert high entropy sources to the uniform distribution.
-%Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.
-The minimal entropy loss
-%One-message information reconciliation protocols called secure sketches remove noise
-%from secrets without revealing too much about them.  They are a crucial ingredient in
-%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.
-
-Secure sketches necessarily reveal some information about the noisy secret.
-% and thus the key derived by fuzzy extractors has lower entropy than the source.  
-The minimal entropy loss is dictated by bounds on error-correcting codes.  
-Fuzzy extractors constructed using secure sketches suffer a similar entropy loss.  This entropy loss decreases the length of the derived key.  
-%suffer from similar bounds imposed by coding theory.
-
-We ask whether these bounds can be overcome by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors.
-%The answer we provide an answer for both secure sketches and fuzzy extractors.
-The answer to this question is mixed, For secure sketches the answer is no, and for fuzzy extractors the answer is yes.
+Notation:
 \begin{itemize}
-\item \textbf{Secure Sketches:} We show that a secure sketch that retains a large amount of HILL pseudo entropy implies a secure sketch which retains a similar amount of information-theoretic entropy.
-We also consider a weaker computational notion of security, the unpredictability of a source conditioned on output of the secure sketch.
-We show that in order to correct $t$ errors, the unpredictability of a source must decrease with the volume of a ball of radius $t$.
-\item \textbf{Fuzzy Extractors:}  We show these impossibility results can be overcome by analyzing fuzzy extractors directly.
-Namely, we show how to build a \emph{lossless} computational fuzzy extractor for uniform sources and certain other sources of high entropy~(namely, symbol-fixing sources, where each dimension is either uniform or fixed), based on the hardness of the Learning with Errors~(LWE) problem.
-This construction requires us to show that the decision version of LWE is secure when a small number of dimension has no error---a result that may be of independent interest.
-\end{itemize}
-%mixed, and building them based on the Learning with Errors (LWE) problem.  We thus obtain the first secure sketch with no loss in entropy.   More specifically, our contributions are as follows:
-%
-%\begin{itemize}
-%\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.
-We do so by demonstrating that a secure sketch defined via HILL pseudoentropy is subject to the same coding-based  bounds as the information-theoretic secure sketch.
-We then find a different relaxation, using unpredictability entropy, and show that it can be used to construct computational fuzzy extractors.
-%
-%
-%\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.
-This construction requires us to show that the decision version of LWE is secure when a small number of dimensions have no error---a result that may be of independent interest.
-%\end{itemize}
-\end{abstract}
-
-\newcommand{\M}{\mathcal{M}}
-\section{Introduction}\label{sec:introduction}
-
-Authentication generally requires a secret drawn from some high-entropy source.
-One of the primary building blocks for authentication is reliable key derivation.
-Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
-%Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
-
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).
-The setting
-%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
-%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
-consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).
-The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.
-This information allows
-the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
-Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.
-This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
-
-%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
-The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.
-A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
-The resulting secret key may be too short to be useful if the entropy loss is too high.
-Traditionally, fuzzy extractors are defined as information-theoretic objects.
-In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
-
-\bnote{This language is pretty clunky. Revise.}
-The main novel tool in constructing fuzzy extractors is the secure sketch.
-The secure sketch produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
-The security requirement is that $w$ has high min-entropy conditioned on $s$.
-The key $r$ is formed by applying a randomness extractor~\cite{nisan1993randomness} to $w$.
-%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
-When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high.
-The minimum entropy loss for secure sketches has been quantified in past work.
-Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08},
-%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
-the entropy loss of a secure sketch that can reconcile $t$ errors
- %with high probability 
- is bounded by the redundancy of
-the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
-Constructions of fuzzy extractors that use a secure sketch inherit this bound.
-%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-
-\paragraph {Our Contributions}
-To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.
-Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.
-
-On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.
-We show that some entropy loss is necessary for secure sketches.
-The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%Furthermore, we have (asymptotic)~constructions that meet these bounds.
-
-Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
-Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
-We show lower bounds on the unpredictability loss of sketches.
-We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
-
-Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.
-To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.
-
-%to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
-This string $\recout$ is  required to have high HILL entropy even conditioned on $s$.
-Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-Computational extractors~\cite{krawczyk2010cryptographic, dachman2012computational} have the same goal in the setting without errors.
-One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.
-In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.
-This construction is only possible if the entropy losses due to a secure sketch and information-theoretic extraction leave enough truly random bits.
-We ask if a better solution is possible by making the entire process ``computational.''\bnote{Should add something about the Dana's result implying PRGs}
-
-By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{As noted above, using a computational extractor, in place of a information-theoretic extractor, allows a lossless construction.
-However, this approach requires the computational extractor to work on the remaining entropy after the secure sketch.
-We compare the two approaches in \secref{sec:prg based comparison}}.
-% without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
-Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
-%We show that this relaxation of the security requirement is  useful.
-Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
-%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
-The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
-%\lnote{it would be good to find another application} 
-Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.
-To apply the LWE assumption, we correct errors of a random linear code which limits our decoding algorithm to reconciling a logarithmic number of differences.
-
-The recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the hardness of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-This allows us to directly use our source $w$ as the LWE error vector.
-To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
-We are able to relax this limitation and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
-This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
-
-%Authentication generally requires secrets.
-Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
-Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
-%
-%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
-%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
-%It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
-%the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
-%Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.
-This feature is needed because $s$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
-%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.  
-%
-%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
-For example, in the application of secure sketches to fuzzy extractors (whose goal is to reliably produce a uniformly random secret key from a noisy input), the resulting secret key may be too short to be useful if the entropy loss is too high.
-However, because secure sketches are defined as information-theoretic objects, some entropy loss is inherent in any secure sketch construction, because $s$ contains enough information to recover $w$ from any value $w'$ that is close to it.
-%
-%The minimum necessary  entropy loss has been quantified in past work.
-Even if we don't require perfect correctness (i.e., allow $\rec$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
-%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
-%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-%
-%\paragraph {Our Contributions}
-%To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
-%The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-%
-%On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful.
-We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%%Furthermore, we have (asymptotic)~constructions that meet these bounds.
-%
-%On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction.
-The idea is to give up on reconstructing $w$ and, instead, to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
-This string $\recout$ is  required to have high HILL entropy even conditioned on $s$.
-Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-%
-%Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
-%~\ref{thm:lossless secure conductor log})).
-We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
-%
-%We show that this relaxation of the security requirement is  useful.
-Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
-%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
-The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
-%\lnote{it would be good to find another application} 
-%
-%Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
-To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).
-We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-The LWE error vector, in our case, is the input $w$ itself.
-To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
-We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed).
-This relaxation requires new results about the hardness of LWE when samples have a fixed error vector, which may be of independent interest~(\thref{thm:blockLWE}).
-\section{Preliminaries}
-\label{sec:preliminaries}
-For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
-The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
-%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
-and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
-%The {\em collision probability} of  $X$ is 
-%$\col(X) = \sum_{x} \Pr[X=x]^2$.
-The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-%We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.
-For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
-We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
-For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
-If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-For the Hamming metric over $Z^n$ the size of $B_t(\cdot) = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $, for clarity we express this value as $B_t(\cdot)$.
-$U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-We use bold letters for vectors or matrices, capitalized letters to be random variables, and lower case letters for the elements in the vector or samples from a random variable.
-
-\subsection{Fuzzy Extractors and Secure Sketches}
-\label{sec:fuzzy extractors}
-
-We now recall definitions and lemmas from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
-Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.
-can we change this $d$ to $\mathsf{dis}$?}
-
-\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
-\label{def:fuzzy extractor}
-An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
-\begin{enumerate}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
-\end{enumerate}
-\end{definition}
-
-Secure sketches are the main technical tool in the construction of fuzzy extractors.
-Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
-\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
-\label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
-\begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
-That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
-\end{definition}
-
-Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
-
-A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
-An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):
-
-\begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^m$ a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), U_d, Y), U_m\times
-U_d \times Y) \le \epsilon$.
-\end{definition}
-
-%In \secref{sec:defCompFuzzyExtractors} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch?
-It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
-%\begin{definition}
-%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
-%\[
-%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
-%\] where the probability is taken over the coins of \sketch and \rec.
-%\end{definition}
-
-\bnote{The definition of extractor above does not match this lemma.}
-\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
-\label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
-\begin{itemize}
-\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
-\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
-\end{itemize}
-\end{lemma}
-The main parameter we will be concerned with is the entropy loss of the construction.
-In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
-We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
-
-\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
-\begin{itemize}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-%%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
-If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
-\end{itemize}
-\end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
-
-\bnote{There needs to be more linking language here.}
-It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).
-In the next section, we show this paradigm is difficult to realize.
-
-%\textbf{Note: }A computational fuzzy extractor could also be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).
-We compare the two approaches in \secref{sec:prg based comparison} after presenting our construction.
-%, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).
-%The cause for the entropy loss in the secure sketch is the additional bits added for error correction.
-In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.
-%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.
-
-%=============================================================
-\section{Impossibility of Computational Secure Sketches}
-\label{sec:defCompFuzzyExtractors}
-In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.
-We consider two different notions for computational entropy, and for both of them show that we can do essentially as well information-theoretically as computationally.
-
-%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp.
-unpredictability) entropy when given a source with $m$ bits of entropy.
-In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
-Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
-
-%These results are strongest for high entropy sources.
-The results get weaker as we consider sources with lower starting entropy.
-If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.
-
-\subsection{Bounds on Secure Sketches using HILL entropy}
-\label{sec:imp HILL sketch}
-HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
-It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
-Here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}); since we show impossibility even for this weaker definition, impossibility for the stronger definition follows immediately.
-
-\begin{definition}
-\label{def:relaxed hill}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon$.
-\end{definition}
-
-%\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}
-
-Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.
-Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
-%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
-This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
-%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
-%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.
-We simply include both of these parameters in the definition.
-We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.
-We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
-
-Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches).
-For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
-In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.
-
-The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
-In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $X, Y$ such that $\Hav(X | Y)\geq \tilde{m}$ and $(X, Y)$ is computationally indistinguishable from $(W, \sketch(W))$.
-Sample a sketch $s\leftarrow \sketch(W)$.
-We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).
-%So, by indistinguishability, it must also succeed on $Y$.
- Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability $\rec (x',z) = x$ with high probability.
- This means we can construct a large set $\mathcal{C}$ from the support of $X|y$.
-$\mathcal{C}$ will be an error correcting code and $\rec$ an efficient decoder.
-We can then use standard arguments to turn this code into an information theoretic sketch.
-
-To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
-\begin{definition}
-\label{def:neighborhood samplable}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.
-%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
-%\[
-%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
-%\]
-\end{definition}
-%We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.
-While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.
-\lnote{ do we need this?
-if distance is exactly $t'$, then the point is different as long as $t'>0$.
-So why not just say "exactly $t'$ in the definition?}
-
-%We will concentrate on metrics where the size of each ball is fixed.
-We say a metric space that obeys this property is regular~(using terminology from graph theory).
-This will allow us to show that the neighbor of a uniformly chosen point is also uniformly random.
-%\begin{definition}
-%A metric space $(\mathcal{M},d)$ is \emph{$(t, c)-$distance regular} if for all $x\in \mathcal{M}, |B_t(x)| = c$. 
-%\end{definition}
-%For a distribution $X$ we define the distribution $N_t(X)$ as the process of sampling a random neighbor of a random point in $X$.
-That is $\Pr[N_t(X) = z] = \sum_{x\in X}\Pr[X=x \wedge y \leftarrow B_t(x) \wedge z=y]$.
-%\begin{lemma}\label{lem:uniformNeighbor}
-%Let $(\mathcal{M}, d)$ be a $(t, c)-$distance regular and let $U$ be uniform over $\mathcal{M}$.  Then $U \overset{d}= N_t(U)$.
-%
-%\end{lemma}
-%\begin{proof}
-%Note that $\forall z, \Pr[U = z] =1/|\mathcal{M}|$.  Thus, it suffices to show that $\forall z , \Pr[N_t(U) =z] =1/|\mathcal{M}|$.
-%
-%Fix an arbitrary $z\in \mathcal{M}$.  Then, 
-%\begin{align*}
-%\sum_{x\in U} \Pr[U=x \wedge y\leftarrow B_t(x) \wedge y=z] &=
-%\sum_{x\in U} \Pr[U = x \wedge x\in B_t(z)] \Pr[y\leftarrow B_t(x) \wedge y=z | x\in B_t(z)]\\
-%&=\frac{c}{|\mathcal{M}|} \frac{1}{c} = \frac{1}{\mathcal{M}}.
-%\end{align*}
-%%The uniform distribution over $\mathcal{M}$ is a random bit string of length $n$.
-Let $x\leftarrow \mathcal{M}$, then $\sample (x) = z = x\oplus y$ where $y$ has at weight at least $1$ and at most $t$.
-Since $x$ was uniformly random $x\oplus y$ is uniformly random.
-%\end{proof}
-
-\ignore{
-Finally, we will 
-dealing with an arbitrary secure sketch that only needs to satisfy the correctness property of a secure sketch~(see \defref{def:secure sketch}).  \lnote{why do we need this definition?}
-
-\begin{definition}
-A pair of functions $(\sketch, \rec) $ is a $(s_{rec}, t)$-\emph{recover functionality for a metric space $\mathcal{M}, d$} if $\sketch : \mathcal{M}\rightarrow \{0,1 \}^*$ is a randomized function and $\rec: \mathcal{M}\times \{0, 1\}^*\rightarrow \mathcal{M}$ is a function computable by a circuit of size at most $s_{rec}$, such that $\rec (w', \sketch (w)) = w$ if $\dis(w, w')\leq t$ for all $w, w' \in \mathcal{M}$.
-\end{definition}
-}
-
-\ignore{For any recover functionality, there is an inherent tradeoff between the ability to keep points stationary and to perform error correction.
-
-\begin{theorem}\label{thm:compSketchImpUniform}
-Let $\mathcal{M}, d$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable and $(t, c)$-distance regular.
-Furthermore, let $(\sketch, \rec)$ be any $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.
-Then $H^\hill_{\epsilon, s}( U |\sketch(U))\not \geq \Hoo(U)$ for $s \approx (s_{neigh} + 2s_{rec})$ and $\epsilon=1/2$~(if $s_{neigh}, s_{rec}$ are polynomial so is $s$).
-\end{theorem}
-%\emph{Intuition:  }The goal that a recover functionality cannot be both stable~(maps points to themselves) and correcting~(maps nearby points back to themselves).
-If a recovery functionality is correcting then we can check if the input point maps to itself.
-If a recovery functionality is stable then we can see if recovery succeeds with nearby points.
-
-\begin{proof}
-Let $U_\mathcal{M}$ be the uniform distribution over $\mathcal{M}$ and let $d$ a  metric.
-Furthermore assume $\mathcal{M}$ is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be a $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.
-Let $X\overset{d}= Y\overset{d}= U_\mathcal{M}$ be i.i.d..
-It suffices to construct a distinguisher $D$~(whose size is $s\approx s_{neigh}+2s_{rec}$) such that $\expe[D(X, SS(X))]- \expe[D(Y, SS(X))]\geq \epsilon = 1/2$.
-%Let $q$ be a polynomial.  
-$D$ is defined as follows:
-\begin{enumerate}
-\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$. 
-\item Sample $b\leftarrow \{0,1\}, z'\leftarrow \sample(z)$.
-\item If $b=1$:
-\subitem If $\rec(z', s) = z\wedge \rec(z, s) = z$ output $1$.
-\item If $b=0$:
-\subitem If $\rec(z, s) = z \wedge \rec(z', s)=z$ output $1$.
-\item Output $0$.
-\end{enumerate}
-First note that $D$ is of size $O(s_{neigh}+2s_{rec})$ and thus in polynomial in $s_{sam}, s_{neigh}$.
-It remains to show that $D$ separates $(X,\sketch(X))$ and $(Y,\sketch(X))$.
-We being by noting that on input $(X, \sketch(X)), D$ outputs $1$.
-By \lemref{lem:uniformNeighbor} we have:
-\begin{align*}
-0&=\delta([Y, \sample(Y), \sketch(X)],& &[\sample(Y), Y, \sketch(X)])\\
-&=\delta([Y, \sketch(X), \sample(Y), \sketch(X)],& &[\sample(Y), \sketch(X), Y, \sketch(X)])\\
-&=\delta([\rec(Y,\sketch(X)), \rec(\sample(Y),\sketch(X))],& &[\rec(\sample(Y), \sketch(X)), \rec(Y, \sketch(X))])
-\end{align*}
-Thus, the output of $\rec$ is the same when given $(\sample(Y), Y)$ or $(Y, \sample(Y))$\footnote{This is also true for a stronger class of recover functionalities that is able to keep state between queries.}.
-This means it can properly recover $Y$ with probability at most $1/2$ over the ordering of inputs.
-Thus we have,
-\begin{align*}
-\Pr[D'(X, \sketch(X))=1] - \Pr[D'(Y, \sketch(X))=1] &=\\
-1 - \frac{1}{2}(\Pr[\rec(Y, \sketch(X)) = Y \wedge \rec(\sample(Y),\sketch(X))=Y]&+\\\Pr[\rec(\sample(Y), \sketch(X)) = Y \wedge \rec(Y, \sketch(X)) = Y])&\geq 
-1-\frac{1}{2}\left(1\right) =\frac{1}{2}
-\end{align*}
-
-%\begin{enumerate}
-%\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$.
-%\item Initialize $correct, stable = 0$.
-%\item For $i=1...q$:
-%\subitem $x_i \leftarrow U$, if $\rec(x_i, s) = x_i, stable +=1/q$.
-%\subitem $x_i' \leftarrow \sample (x_i)$, if $\rec(x_i', s) = x_i, correct+=1/q$.
-%\item If $\rec(z, s)\neq z$ output $0$.
-%\item If $stable<1/2$ output $1$
-%\item Else $z'\leftarrow \sample(z)$.
-%\subitem If $\rec(z', s) = z$ output $1$.
-%\subitem Else output $0$.
-%\end{enumerate}
-%
-%We begin by noting that $D$ is of size $O(q(s_{sam}+s_{neigh}+2s_{rec})+2s_{rec}+s_{neigh})$ and thus is polynomial in $s_{sam}, s_{neigh}, s_{rec}$.
-It remains to show that $D$ separates $(X, SS(X))$ and $(Y, SS(X))$ by a noticeable $\epsilon$.
-Let $STABLE = \Pr[\rec(U, \sketch(X)) = U]$.
-We begin by noting that $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-That is, after step (3) $D$ has a good approximation
-%of $STABLE$.  Similarly, let $CORRECT = \Pr[\rec(\sample(U), \sketch(X)) = U]$.  As before $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-%Thus, after step (3), $\Pr[|CORRECT-correct|>\ngl \wedge |STABLE-stable|>\ngl|]<\ngl$.
-We proceed assuming, that $CORRECT$ and $STABLE$ are known exactly at step (4), and note the output of $D$ is negligibly close to the output of a distinguisher that knows $CORRECT$ and $STABLE$ exactly~(we label this distinguisher $D'$).
-%\begin{claim}
-%$CORRECT+STABLE\leq 1$.
-%\end{claim}
-%\begin{proof}
-%\begin{align*}
-%\Pr[\rec(U, \sketch(X) = U] + \Pr[\rec(\sample(U), \sketch(X)) = U]&\leq\\
-%\Pr[\rec(U, \sketch(X) = U]  + \Pr[\rec(Y), \sketch(X)\neq Y] &=1
-%\end{align*}
-%Where the first inequality proceeds because of \lemref{lem:uniformNeighbor} and the fact that \sample never returns itself.
-The equality proceeds as these events as these events are complementary events after renaming.
-%\end{proof}
-%We now show that when $(\sketch, \rec)$ is stable or correcting the distinguisher has nonnegligible advantage:
-%\begin{itemize}
-%\item Case 1: $STABLE<1/2$.
-%\begin{align*}
-%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1] &=\\
-%\Pr[\rec(X, \sketch(X) = X] - \Pr[\rec(Y, \sketch(X) = Y] &\geq
-% 1- 1/2  = 1/2
-%\end{align*} 
-%\item Case 2: $STABLE\geq 1/2, CORRECT \leq 1/2$.
-%\begin{align*}
-%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1]&=\\
-%\Pr[\rec(X, \sketch(X)) = X \wedge \rec(\sample(X), \sketch(X)) = X] &-\\\Pr[\rec(Y, \sketch(X) = Y) \wedge \rec(\sample(Y), \sketch(X)) = Y)]&\geq\\
-%1 - \Pr[\rec(\sample(Y), \sketch(X)) = Y)]= 1-1/2 = 1/2
-%\end{align*}
-%\end{itemize}
-%Thus, in both cases we have $\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1]\geq 1/2$.  As noted above, $CORRECT, STABLE$ are only known approximately and thus:
-%\[
-%\Pr[D(X, \sketch(X) )= 1] - \Pr[D(Y, \sketch(X) )= 1]\geq 
-%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1] - \ngl \geq 1/2 -\ngl
-%\]
-This completes the proof.
-\end{proof}
-
-This proof relied on two crucial facts: 1) that the neighbor of a uniform point was uniformly distributed 2) for an point uncorrelated with the value of the secure sketch it was impossible to distinguish between a point and its neighbor.
-We can extend this result to distributions other than the uniform distribution but by drawing on more general results from coding theory.
-
-\subsection{Indistinguishable sketches imply information theoretic sketches}
-In this section we show that the results of \thref{thm:compSketchImpUniform} can be extended to whenever $X$ is indistinguishable from a high min-entropy distribution.  }
-
-We review definitions of Shannon codes~\cite{shannon1949mathematical}:
-\begin{definition}
-\label{def:shannon-code}
-Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$.
-To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
-\end{definition}
-This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
-For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
-However, we work with an arbitrary recover functionality that is not necessarily monotone.}.
-
-Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.
-
- \begin{definition}
-Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]<\epsilon$.
-\end{definition}
-An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
-See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.
-An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
-We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
-\begin{lemma}
-\label{lem:averageToMaximalError}
-Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
-There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
-\end{lemma}
-
-We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
-\begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
-If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
-%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
-If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
-\end{theorem}
-%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.
-In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.
-Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.
-Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g.
-where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).
-However, this is still a meaningful set of error correcting codes.
-A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.
-They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.
-
-%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
-For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
-The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
-The formal statement is in the following Lemma.\bnote{I feel we should cite this.}
-\begin{lemma}
-\label{lem:shannon to sketch}
-For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
-%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
-%
-% Define the following procedures
-%\lnote{I think this description is buggy}
-%\begin{center}
-%\begin{tabular}{c|c}
-%\begin{minipage}{3in}
-%\textbf{\sketch}
-%\begin{enumerate}
-%\item Input $w\leftarrow W$.
-%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
-%\item Sample $c\leftarrow \mathcal{C}$.
-%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
-%\item Output $p = x \oplus c, \pi$.
-%\end{enumerate}
-% \end{minipage} &
-%\begin{minipage}{3in}
-%\textbf{\rec}
-%\begin{enumerate}
-%\item Input $(w', p, \pi)$
-%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
-%\item Compute $c' = p \oplus x'$.
-%\item Compute $c = \rec'(c)$.
-%\item Output $p\oplus c$.
-%\\
-%\end{enumerate}
-%\end{minipage} 
-%\end{tabular}
-%\end{center}
-Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
-%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
-%\begin{itemize}
-%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
-%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
-%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
-%\end{itemize}
-\end{lemma}
-%\begin{construction}
-%Let $\delta >0$ be a parameter.
-%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.
-Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.
-Thefn for $\beta = 2^{-\ell}
-%\end{construction}
-Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
-\begin{corollary}
-\label{cor:rec yields sketch}
-Let $Z$ be an alphabet.
-Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-$4(\epsilon+t\delta)$. 
-%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
-\end{corollary}
-\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
-
-\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |Z|-\tilde{m})-2$ bits of entropy.
-
-%\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.
-Unfortunately, we have lower bounds for the entropy drop for information-theoretic sketches:
-
-%\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
-%\label{prop:lower bound entropy drop}
-%For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.
-Here $h(\cdot)$ is the binary entropy function.
-%\end{proposition}
-
-%Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.
-This entropy drop is tied to the Shannon capacity.
-Furthermore, we have information theoretic constructions that meet these bounds.
-Thus, defining a computational secure sketch using HILL entropy is unlikely to be useful.
-
-%\begin{theorem}
-%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable.
-Furthermore, let $(\sketch, \rec)$ be any $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.
-Let $U$ be the uniform distribution over $\mathcal{M}$.
-If $s_{ball}, s_{rec}, s_{sam}$ are of polynomial size, then $H^\hill_{\epsilon, s}( U |\sketch(U))\not \geq \Hoo(U)$ for polynomial $s$ and noticeable $\epsilon$.
-%\end{theorem}
-%\emph{Intuition:  }We will show that a recover functionality cannot be both stable~(maps points to themselves) and correcting~(maps nearby points back to themselves).
-If a recovery functionality is correcting then we can check if the input point maps to itself.
-If a recovery functionality is stable then we can see if recovery succeeds with nearby points.
-%
-%\begin{proof}
-%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable~(by $\sample$).
-Let $(\sketch, \rec)$ be a $s_{rec}, t$-recover functionality for $\mathcal{M}, d$.
-Let $X, Y, U$ be i.i.d.
-and be the uniform distribution over $\mathcal{M}$.
-By assumption $s_{ball}, s_{sam}, s_{rec}$ be of polynomial size.
-It suffices to construct a polynomial size distinguisher $D$ such that $\expe[D(X, SS(X))]- \expe[D(Y, SS(X)]> \epsilon$ for noticeable $\epsilon$.
-Let $q$ be a polynomial.
-$D$ is defined as follows:
-%
-%\begin{enumerate}
-%\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$.
-%\item Initialize $correct, stable = 0$.
-%\item For $i=1...q$:
-%\subitem $x_i \leftarrow U$, if $\rec(x_i, s) = x_i, stable +=1/q$.
-%\subitem $x_i' \leftarrow \sample (x_i)$, if $\rec(x_i', s) = x_i, correct+=1/q$.
-%\item If $\rec(z, s)\neq z$ output $0$.
-%\item If $stable<2/3$ output $1$
-%\item Else $z'\leftarrow \sample(z)$.
-%\subitem If $\rec(z', s) = z$ output $1$.
-%\subitem Else output $0$.
-%\end{enumerate}
-%
-%We begin by noting that $D$ is of size at most $q(s_{sam}+s_{ball}+2s_{rec})+2s_{rec}+s_{ball}$ and thus is polynomial assuming that $q, s_{sam}, s_{ball}, s_{rec}$ are of polynomial size.
-It remains to show that $D$ separates $X, SS(X)$ and $Y, SS(X)$ by a noticeable $\epsilon$.
-Let $STABLE = \Pr[\rec(U, \sketch(X)) = U]$.
-We begin by noting that $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-That is, after step (3) $D$ has a good approximation
-%of $STABLE$.  Similarly, let $CORRECT = \Pr[\rec(\sample(U), \sketch(X)) = U]$.  As before $\Pr[|correct-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-%
-%\begin{claim}
-%$CORRECT+STABLE\leq 1$.
-%\end{claim}
-%\bnote{finish proof}
-%
-%\end{proof}
-
-\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
-\label{sec:imp unp sketch}
-In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
-A reasonable question to ask is whether a sketch could retain unpredictability of the source.
-We begin by defining conditional unpredictability entropy:
-
-\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
-\label{def:unp entropy}
-For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $I$ of size $s_{sec}$,
-\[
-\Pr[I(Z) = Y ] \leq 2^{-k}
-.\]
-\end{definition}
-We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
-\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-\label{lem:unp extraction} 
-\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
-Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-\end{lemma}
-Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
-Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
-%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
-%That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
-The formal statement is below:
-\begin{theorem}
-\label{thm:imp of unp entropy}
-Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
-\end{theorem}
-This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
-The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.
-This means we cannot construct a good code out of the points of $Y$.
-In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy~(similar to the relaxed notion of HILL entropy in \defref{def:relaxed hill}).%Our bound is a result of the Hamming bound for the space.
-
-\subsection{Avoiding sketch entropy upper bounds}
-\label{ssec:avoiding bounds}
-
-The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.
-The results get weaker as we consider sources with lower starter entropy.
-This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.
-This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.
-This same situation occurs when considering lower bounds for information-theoretic sketches.
-
-Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the indistinguishable distribution.
-It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
-This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.
-An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).
-Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).
-It may be possible to achieve significantly better parameters with a construction that is a computational fuzzy conductor~(but not a computational fuzzy extractor) and then applying an extractor.
-We leave this as an open problem.
-
-%\subsection{Defining  Computational Fuzzy Conductors}
-%\label{sec:unp secure sketch}
-%In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.
-If, the error correcting algorithm outputs a new random variable, bounds do not apply.
-Instead of building a computational sketch, we will build a computational conductor.
-We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
-%%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
-%%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
-%%\begin{enumerate}
-%%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
-%%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
-%%\end{enumerate}
-%%\end{definition}
-%%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
-We begin by defining unpredictability entropy:
-%
-%
-%%We now provide a definition of a robust computational sketch using unpredictability entropy:
-%\begin{definition}\label{def:comp secure sketch}
-%A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
-%\begin{enumerate}
-%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
-%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
-%If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
-%\end{definition}
-%
-%%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-%In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.
-We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
-
-\section{Computational Fuzzy Extractor based on \class{LWE}}
-\label{sec:fuzzyCompExt}
-
-In this section we describe our main construction.
-In this section, we consider only a uniform source $W$, we consider other distributions in \secref{sec:LWE block fixing sources}.
-Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors.
-We provide an informal description below.
-%Please refer to \consref{cons:informal construction} for the description of the construction.
-
-\begin{construction}
-Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
-Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
-%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$.
-$\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$.
-$m > n$ are parameters to be figured out later.
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
-\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
-\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
-\item Output $(r, p)$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rec}
-\begin{enumerate}
-\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
-\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
-\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
-\item Output $r = X_{1,...,n/2}$.
-\end{enumerate}
-\end{minipage} 
-\end{tabular}
-\end{center}
-\label{cons:informal construction}
-\end{construction}
-
-Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.
-Furthermore, this construction is only useful if $\mathcal{I}_t$ can be efficiently implemented.
-We demonstrate an efficient $\mathcal{I}_t$ that corrects a super-polynomial number of error patterns in polynomial time.
-
-The rest of this section is devoted to making these intuitive statements precise.
- We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
- %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
-We describe conditions for efficient decoding in \secref{sec:time main construction}.
-In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.
-In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.
-
-\subsection{Security of \consref{cons:informal construction}}
-\label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For positive integers $n$ and $q \ge 2$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
-%The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.
-
-\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
-Let $m = m(n) = \poly(n)$ be an integer, $q = q(n) = \poly(n)$.
-The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
-
-We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-secure if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If $\distLWE_{n, m, q, \chi}$ is secure for all $t = \poly(n), \epsilon  = 1/\poly(n)$ we say it is \emph{secure}.
-\end{definition}
-
-Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
-%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
-Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
-%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):
-
-\begin{proposition} 
-\label{assume:entropy LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\alpha$ be the discretized Gaussian distribution with variance $(\alpha q)^2/2\pi$.
-If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.
-That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_q^m))\leq \epsilon$.
-
-%H^{\unp}_{\epsilon, s_{sec}}(X | \vA, \vA X+E) =H^{\unp}_{\epsilon, s'_{sec}}(E| \vA, \vA X+E) \geq n\log q $ for $s'_{sec}\approx s_{sec}$.  
-\end{proposition}
-
-We cannot immediately adapt the construction in \consref{cons:informal construction} to the $\LWE$ problem.
-Standard formulations of $\LWE$ require the error term to come from the discretized Gaussian distribution.
-%\subsection{LWE with uniform errors}
-%\label{subsec:LWE uniform error}
-Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over an interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian.
-This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it properly into $m$ blocks.
-%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.
-We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
-%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
-%\label{lem:uniform LWE}
-%Let $n$ be a security parameter.
-Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.
-Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.
-Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.
-Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
-%\end{lemma}
-
-%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
-\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
-\label{lem:uniform LWE decision}
-Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer.
-Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n/2$) with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
-\end{lemma}
-
-To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
-The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
-We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
-\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-\label{lem:many hardcore bits}
-Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
-Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-If $\distLWE_{(n-k, m, q, \chi)}$ is $\epsilon, s_{sec}$ hard then $H^{\hill}_{\epsilon, s_{sec}'}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ where $s_{sec}' \approx s_{sec} - n^3$.
-\end{lemma}
-
-%\begin{lemma}
-%\label{lem:conversion to unpredictability}
-%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
-%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
-%\end{lemma}
-%\begin{lemma}
-%\label{lem:dmq with unp entropy}
-%Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer.
-Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.
-Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.
-Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
-%\[
-%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
-%\]
-%\end{lemma}
-With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, \consref{cons:informal construction} has many hardcore bits and we use these bits as our key.  
-%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}.
-2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.
-
-%\subsection{Computational Secure Sketch based on \class{LWE}}
-%\label{subsec:fuzzyExtLWE}
-%We now give a formal description of our sketch based on LWE.  We now consider a source $W$~(this fulfills the role of $E$ in standard LWE notation):
-%
-%\begin{construction}[Computation Secure Sketch based on LWE]
-%\label{cons:LWESecureSketch} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers.
-Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+3\gamma}m$.
-Let $\mathcal{I}_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
-Let $W$ be a distribution over $\{0,1\}^{(\log \rho q)\times m}$\,.
-Then the following is a computational secure sketch:%We present the construction in
-%%\begin{figure}
-%%\label{fig:construction figure}
-%%\caption{Computational Secure Sketch based on the Learning with Errors problem}
-%\begin{center}
-%\begin{tabular}{c|c}
-%\begin{minipage}{3in}
-%\textbf{\sketch}
-%\begin{enumerate}
-%\item Input $w\leftarrow W$.
-%\item Sample $\vA\in\Fq^{m\times n}, x\in\Fq^n$ uniformly.
-%\item Output $p = (\vA, \vA x+w)$.\\
-%\end{enumerate}
-% \end{minipage} &
-%\begin{minipage}{3in}
-%\textbf{\rec}
-%\begin{enumerate}
-%\item Input $(w', p)$
-%\item Parse $p$ as $(\vA, \vect{C})$
-%\item Set $x' = \mathcal{I}_t(\vA, \vect{C}-w') $. 
-%\item Output $w = \vect{C}-\vA x'$.
-%\end{enumerate}
-%\end{minipage} 
-%\end{tabular}
-%\end{center}
-%%\end{figure}
-%%\textbf{\gen}
-%%\begin{enumerate}
-%%\item Input $w\leftarrow W$.
-%%\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
-%%\item Use $w$ as the randomness for the sampling algorithm, \\$\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
-%%\item Output $p = (A, AX+E)$.
-%%\end{enumerate}
-%%
-%%
-%%\textbf{\rep}
-%%\begin{enumerate}
-%%\item Input $(w', p)$
-%%\item Parse $p$ as $(A, C)$
-%%\item Compute $E' \leftarrow \sample (w')$.
-%%\item Set $X' = \mathcal{I}_t(A, C-E') $. 
-%%\item Output $sam_w = C-AX'$.
-%%\end{enumerate}
-%\end{construction}
-
-\subsection{Efficiency of \consref{cons:informal construction}}
-\label{sec:time main construction}
-%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
-\consref{cons:informal construction} is only useful if $\mathcal{I}_t$ can be efficiently implemented.  We now present a particular $\mathcal{I}_t$ and consider its efficiency:
-
-\begin{construction}
-\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe inverter $\mathcal{I}_t$:
-\begin{enumerate}
-\item Input $\vA , \vc = \vA X + W - W'$
-\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, \vc$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, \vc_{i_1,...,i_{2n}}$.
-\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
-Denote by $\vA', \vc'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
-\item Compute $X' = \vA'\vc'$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
-\item Output $X'$.
-\end{enumerate}
-\end{construction}
-
-$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.
-We need $t$ to be small enough for step (4) to succeed with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
-The second condition is to ensure that there are few false positives in step (5).
-This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.
-The exact statement is in \corref{cor:code high distance}.
-Furthermore, steps (3-5) are computable in time $O(n^3)$.
-This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.
-We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
-$\mathcal{I}_t$ is efficient as long as $t$ is small enough.
-The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
-%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).
-\lnote{can we combine these lemmas into one?
-It's hard for the reader to compare line-by-line to see where the differences are.
-More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
-%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
-%\label{lem:i t constant time}
-%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).
-Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.
-Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
-%\end{lemma}
-\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-2)$]
-\label{lem:i t poly time}
-Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.
-Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
-Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-1)\log n$.
-Then $\mathcal{I}_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
-\end{lemma}
-\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.
-Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.
-We concentrate on the setting $t\leq d\log n(m/n-2)$.
-Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.
-
-%\textbf{Problems:} Construction~\ref{cons:LWESecureSketch} does not meet Definition~\ref{def:comp secure sketch}.
-This is because the sampling algorithm may not be invertible.
-Furthermore, in standard $\LWE$ the sampling algorithm is Gaussian and there is no fixed number of bits used to sample error in any dimension.
-Approximating the Gaussian distribution using a fixed number of bits may be possible but there are still two error patterns which require a significantly different number of bits.
-We will address both of these problems by sampling the error from a uniform distribution.
-
-\subsection{Lossless Computational Fuzzy Extractor}
-\label{sec:lossless extractor}
-We now state a setting of parameters that yields a lossless construction.
-
-%\begin{theorem}
-%\label{thm:lossless secure sketch}
-%Let $n$ be a security parameter and let $t$ be a constant.
-Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.
-Let $W$ be uniform over $\zo^{n(t+1)b}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors, there is a
-%\[
-%(\zo^{n(t+1)b}, |W|,|W|, \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-% for $\epsilon = \ngl(n), s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
-%\end{theorem}
-
-\begin{theorem}
-\label{thm:lossless secure conductor log}
-Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
-Let $W$ be uniform over $\zo^{(c+2d)nb/d}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = H_\infty(W)$
-% for following parameters:
-%\[
-%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
-%\] 
-with 
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
-\end{theorem}
-\begin{proof}
-Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
-\end{proof}
-
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
-\thref{thm:lossless secure conductor log} shows that a computational fuzzy conductor can be built without incurring any entropy loss.
-This is essentially due to $\vA X+W$ looking like a uniformly random point and thus providing no information about either $X$ or $W$.
-%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.
-
-\subsection{Comparison with \prg based construction}
-\label{sec:prg based comparison}
-In this section we to constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
-In particular, using the same hardness of approximating GAPSVP and SIVP, Applebaum et.
-al.
-use LWE to achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.
-Namely, consider $\vA$ as a public value, they show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.
-Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).
-Both techniques are able to produce a linear stretch on the entropy of the source.
-The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log t)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
-In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
-The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.
-We begin to address this second problem in the next section.
-
-\section{\consref{cons:informal construction} with Nonuniform Sources}
-\subsection{\consref{cons:informal construction} with Symbol Fixing Sources}
-\label{sec:LWE block fixing sources}
-In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.
-Showing security of a computational fuzzy extractor for arbitrary high min-entropy distributions is an open problem.
-First we recall the notion of a symbol fixing source~(from~\cite{KZ07}):
-\begin{definition}
-Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $m$-\emph{symbol fixing source} if $H_\infty(W)\geq mb$ and for all $W_i$ one of the following conditions is met:
-\begin{itemize}
-\item $W_i \overset{d}= U_b$
-\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
-\end{itemize}
-\end{definition}
-%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.
-
-We now study \consref{cons:informal construction} with a symbol fixing source.
-Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations with no error and $W$ can be recovered with Gaussian elimination.
-We show that security degrades exponentially as symbols are fixed.
-\ignore{
-\begin{assumption}[LWE w/ entropic errors]
-Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-block fixing distribution over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
-Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
-\end{assumption}
-}
-We now define the decisional $\LWE$ problem with symbol fixing errors is defined as follows: 
-\begin{problem}[$\distLWE$ w/ symbol fixing errors]
-Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.
-Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$.
-For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and output $\vA X + W$.
-The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
-\end{problem}
-
-The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$.
-%\vspace{.1in}
-\begin{theorem}
-\label{thm:blockLWE}
-Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
-Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
-The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
-\end{theorem}
-We believe this statement is of interest outside our setting.
-\thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known error.
-Roughly, we need the number of variables to be security parameter larger than the number of equations with known error.
-Providing a single sample with no error ``fixes'' at most a single variable.
-Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.
-We are able to show~(a stronger result) that $\distLWE$ is still hard.
-In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to explain a random value for the last $\alpha$ samples without knowledge of the other variables.
-The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
-A formal proof is in \secref{sec:proof of block theorem}.
-
-\thref{thm:blockLWE} allows us to construct a computational fuzzy extractor from block-fixing sources:
-
-%\begin{theorem}
-%\label{thm:lossless block sketch}
-%Let $n$ be a security parameter and let $t$ be a constant.
-Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.
-Let $W$ be an $\alpha$-symbol fixing source over $\zo^{((t+1)n+\alpha)b}$.
-There is a \lnote{instead of ``there is'' can we actually point to the to construction?}
-%\[
-%(\zo^{((t+1)n+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-% for $s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
-%\end{theorem}
-
-\begin{theorem}
-\label{thm:lossless block sketch log}
-Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
-Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+2d)n/d+\alpha \right)b})$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms.
-There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/3} |\vA, \vA X+W) = H_\infty(W)$ for %the following parameters:
-%\[
-%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
-\end{theorem}
-
-\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).
-The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
-We could set $\alpha$ larger than $n/3$ and extract fewer hardcore dimensions.
-To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant in $n$.
-The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for smal values of $n$.
-
-\ignore{
-\subsection{\consref{cons:informal construction} with slightly deficient sources}
-\label{sec:DP general error LWE}
-In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.
-We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.
-This result allows us to argue security for an arbitrary distribution that is nearly high entropy.
-This result should be seen as a complement to the proceeding sections.
-It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure conductor log}.
-Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
-\begin{theorem}
-Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.
-Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.
-Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.
-If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
-\end{theorem}
-\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.
-In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.
-The only requirement in the proof is that $|\chi|\geq m\log \rho$.
-Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.
-This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.
-This means we support all distributions whose entropy gap is no more than $m$ bits.
-
-\bnote{Need to continue and go through their Lemma 4.1 and 4.4 to be sure I believe this.  Everything else should go through fine.}
-
-\bnote{We need to turn this hardness result into a statement about computational fuzzy extractors.  Use the Akavia result.  Then we need to suggest parameters.  How much detail should we go into?}
-
-The main item I think needs to change is their Lemma 2.4
-\begin{lemma}~\cite[Min-Entropy Version of Lemma 2.4]{micciancio2013hardness}
-Let $\mathcal{L}$ be a family of functions on a common domain $X$ and let $Z$ be a distribution over $X$.
-Then $(\mathcal{L}, Z)$ is $\epsilon$-uninvertible~(even statistically, with respect to computationally unbounded adversaries) for $\epsilon = \expe_{f\leftarrow \mathcal{L}} [|f(X)|]/ 2^{-H_\infty(Z)}$.
-\end{lemma}
-\begin{proof}
-Fix a function $f$.
-The best way to predict $Z$ given $f(Z)$ is the average predictability of $Z | f(Z)$.
-This predictability is $2^{-\Hav(Z | f(Z))}$.
-By Lemma 2.2 of Dodis et.al.~\cite{DBLP:journals/siamcomp/DodisORS08},
-\[
-\tilde{H}_\infty(Z | f(Z))\geq H_\infty(Z) - \log |f(Z)| \geq \Hoo(Z) - \log |f(X)|.
-\]
-  The statement of the lemma follows by converting to predictability.
-\end{proof}
-
-}
-
-%\section{Computational Fuzzy Extractors}
-%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.
-We begin with a formal definition of a computational fuzzy extractor:
-%\label{sec:comp fuzzy extractors}
-%
-%
-%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
-%\begin{lemma}
-%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
-Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.
-Let, $s' = s_{sec}-s_{ext}$, then
-%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
-%\end{lemma}
-%%  the same paradigm from 
-%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
-It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
-However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).
-%%\begin{definition}
-%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
-Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
-%%\end{definition}
-%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-%%\label{lem:unp extraction} 
-%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-%%\end{lemma}
-%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
-%\begin{lemma}
-%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
-Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
-Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
-%\end{lemma}
-%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
-%%\begin{itemize}
-%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
-%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
-%%\end{itemize}
-%%\end{lemma}
-%%\begin{proof}
-%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
-%%\end{proof}
-%%
-%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
-
-\ignore{
-Additionally, it is simple to use a pseudorandom generator to produce a computational fuzzy extractor from a standard fuzzy extractor:
-\begin{proposition}\label{prop:prg comp fuzzy extractor}
-Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $(\epsilon_{prg}, s)$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.
-Let \gen' and \rep' be defined as:
-\begin{itemize}
-\item \gen': $(R, P) \leftarrow \gen(w)$, output $(prg(R), P)$
-\item \rep': Output  $prg(\rep (w', P))$.
-\end{itemize}
-Then $(\rep', \gen')$ is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.
-\end{proposition}
-Recall, our goal is to construct fuzzy extractors where the entropy drop due to an information theoretic construction were too high.
-However, it seems difficult to definitionally exclude this type of construction.
-For example, one could require that $R$ have information theoretic entropy in the absence of $P$.
-This does not solve the problem:
-\begin{proposition}\label{prop:xor comp fuzzy extractor}
-Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $\epsilon_{prg}, s$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.
-Let \gen' and \rep' be defined as:
-\begin{itemize}
-\item $\gen'(w)$
-\subitem Sample $K\leftarrow \{0,1 \}^{\ell'}$
-\subitem $(R, P) \leftarrow \gen(w)$
-\subitem $H= prg(R)\oplus K$
-\subitem Output $(K, (H, P))$
-\item $\rep'(w', (H, P))$
-\subitem Output $K' = H\oplus prg(\rep (w', P))$.
-\end{itemize}
-Then (\rep', \gen') is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.  Furthermore $H_\infty(K) = \ell'$.
-\end{proposition}
-
-Both of these constructions rely on a crucial property $\ell$ was long enough to provide a seed to a pseudorandom generator.
-We are interested in the case where the remaining entropy is small and may not sufficient for pseudorandom generator.
-We leave Definition~\ref{def:comp fuzzy extractor} as stated and note constructing a computational fuzzy extractor is desirable when a standard fuzzy extractor cannot be used.
-
-In the information theoretic setting, Dodis et.
-al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.
-A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
-}
-\bibliographystyle{alpha}
-\bibliography{crypto}
-\appendix
-\section{Random Linear Codes Have High Distance}
-%\subsection{Notions of Computational Entropy}
-%\label{sec:notionsEntropy}
-%In this sections we provide some further definitions of computational entropy.
-HILL entropy is defined in \secref{sec:defCompFuzzyExtractors}.
-HILL entropy generalizes the notion of indistinguishability.
-Yao entropy~\cite{DBLP:conf/focs/Yao82a, barak-computational} generalizes the notion of compressibility.
-Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
-%\begin{definition}
-%\label{def:yao entropy}
-%For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
-%\[
-%\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
-%\]
-%\end{definition}
-%It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.
-In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
-We also use a less common notion called unpredictability entropy.
-This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
-%Unpredictability entropy is a notion between HILL and Yao entropy:
-%\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
-%\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
-%\]
-%\end{lemma} 
-%\subsection{Unique Witness Relations}
-
-%We will need the ability to verify if we have a correct solution in~\consref{cons:informal construction}.  
-%
-%\begin{definition}
-%Let $R$ be a relation.  We say that $R$ is $s_{ver}$-\emph{unique witness verifiable} if $\forall y$ there exists a unique $x$ such that $R(x, y)=1$ and $R(x, y) =1$ is computable in time $s_{ver}$.
-%\end{definition}
-%We can relax this definition slightly to allow a relation that is unique witness verifiable with all but negligible probability~(when $x, y$ grow with the security parameter).
-%
-%\begin{definition}
-%\label{def:unique witness relation}
-%Let $R:\mathcal{M}_1\times \mathcal{M}_2\rightarrow \zo$.
-We say that $R$ is $(\epsilon, s_{ver})$-\emph{unique witness verifiable} if over $y\in \mathcal{M}_2$, drawn uniformly, the probability that $\exists x_1, x_2, x_1\neq x_2$ such that $R(x_1, y) =1 = R(x_2, y)$ is at most $\epsilon$ and $R$ is computable in time $s_{ver}$.
-%\end{definition}
-%
-For efficient decoding of \consref{cons:informal construction}, we need the $\LWE$ instance to have high distance with overwhelming probability.
-We will use the $q$-ary entropy function, denoted $H_q(x)$ and defined as $H_q(x) = x\log _q(q-1) - x\log_q x - (1-x)\log_q (1-x)$.
-Note that $H_2(x) = -x\log x - (1-x)\log (1-x)$.
-In the region $[0, \frac{1}{2}]$ for any value $q'\geq q$, $H_{q'}(x)\leq H_{q}(x)$.
-The following theorem is standard in coding theory:
-
-\begin{theorem}~\cite[Theorem 8]{venkatLecture}
-\label{thm:random code good distance}
-For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .
-If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
-\end{theorem}
-Of particular, concern will be the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
-\begin{corollary}
-\label{cor:code high distance}
-Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
-Let $q$ be a prime and $t = O(\frac{m}{n}\log n )$.
-For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $t$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
-\end{corollary}
-\begin{proof}
-Let $c$ be some constant.
-Let $\delta = t/m = \frac{c\log n}{n}$.
-We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).
-It suffices to show that for sufficiently large $n$, $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.
-For sufficiently large $n$:
-\begin{itemize}
-\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
-\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
-\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.
-
-% and note that there $\exists \epsilon$ where $0<\epsilon< 1-H_q(\frac{c\log n}{2n})< 1-H_q(\frac{c\log n}{m})$ and $1-H_q(c\log n/n) -\epsilon =1/2$ or equivalently $H_q(c\log n/n)+\epsilon = 1/2$.
-Let $d$ be some constant such that $q< n^d$.
-Consider the value of $H_q(\frac{c\log n}{n})$:
-%\begin{align*}
-%H_q(\frac{c\log n}{n})&\leq  H_{n^d}(\frac{c\log n}{n})\\
-%&=\frac{c\log n}{n} \log_{n^d}(n^d-1) - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} (1-\frac{c\log n}{n})\\
-%&\leq \frac{c\log n}{n}  - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n})-\log_{n^d} (\frac{n-c\log n}{n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n-c\log n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} (\frac{n}{c\log n}-1) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} n \right)- \log_{n^d} \left(\frac{1}{n}\right)\\
-%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} - \log_{n^d} \left(\frac{1}{n}\right)\\
-%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} + \frac{1}{d}
-%\end{align*}
-%Thus for large enough values of $n$, $H_{n^d}(\frac{c\log n}{n})\leq 1/2 + O(\frac{c\log n}{dn}) \leq 2/3$, thus $1 - H_q(\frac{c\log n}{n})> 1-H_{n^d}(\frac{c\log n}{n} )> 1/3$.
-Taking $\epsilon  = 1/21/6$ the conditions of the corollary are satisfied.
-\end{proof}
-
-\ignore{
-\section{Possibility of Constructing Computational Fuzzy Extractors}\label{ssec:constructing comp fuzzy extractors}
-In the \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best constructible codes.
-Thus, some entropy drop seems necessary when considering $H^\hill_{\epsilon, s}(X | SS(X))$.
-However, in \propref{prop:prg comp fuzzy extractor}, we showed that a computational fuzzy extractor exists using a pseudorandom generator.
-A natural question is whether this is necessary.
-Do there exist clever constructions of computational fuzzy extractors that rely on the hardness of some cryptographic primitive that is easy within some distance $t$.
-We begin by recalling the important parameters of a computational fuzzy extractor:
-\begin{itemize}
-\item The input entropy $m$.
-\item The length of the output string $\ell$.  This output string is required to be $(\epsilon, s_{sec})$-pseudorandom.
-\item The accepting distance $t$.
-\end{itemize}
-We consider the possibility of constructing a computational fuzzy extractor based on the remaining entropy of $W$ conditioned on the string $P$~(generated by $(R, P)\leftarrow \gen(W)$).
-We first define a parameter $k_{prg}$.
-Let $k_{prg}$ be the smallest integer such that there exists a pseudorandom generator from $k_{prg}$ to at least $k_{prg}+1$ bits.
-More precisely, let $k_{prg}$ be the smallest integer such that there exists a deterministic function $prg:\{0,1\}^{k_{prg}}\rightarrow \{0,1 \}^{k_{prg}+1}$ such that $\forall D\in \mathcal{D}_s$: $\delta^D(prg(U_{k_{prg}}), U_{k_{prg}+1})<\epsilon$ for some negligible $\epsilon$ and super polynomial $s$.
-We now classify the existence of computational fuzzy extractors based on this parameter.
-Let $CODE$ be some error-correcting code with parameters, $(n, k, 2t+1)$.
-We define $|CODE| = n-k$.
-
-\begin{tabular}{c | c}
-Remaining Entropy & Constructible?\\\hline
-$CODE$ is computationally computable. & Yes, use \propref{prop:prg comp fuzzy extractor} \\
-$H_\infty (W) - |CODE|\geq k_{prg}$\\\hline
-$CODE$ exists, not necessarily efficiently computable. & Seems impossible to disprove, efficient\\
-$H_\infty(W) - |CODE|\geq k_{prg}$ & construction of $CODE$ admits \propref{prop:prg comp fuzzy extractor}.\\\hline
-Let $CODE$ be the best code. & Unknown, main area of interest\\
-$H_\infty(W) - |CODE|< k_{prg}\leq H_\infty(W)$\\\hline 
-$H_\infty(W)< k_{prg}$ & Seems to imply existence \\
-&of improved $prg$ by using $\gen$.
-\end{tabular}
-
-We begin by focusing on the last case where $H_\infty(W) < k_{prg}$.  We first introduce two concepts, efficiently-generatable sources and sources that are $prg$ qualified.
-
-\begin{definition}
-A distribution $W$ over $\mathcal{M}$ is \emph{$(s_{gen}, \ell)$-efficiently-generatable} if there exists a deterministic circuit $G$ of size at most $s_{gen}$ such that $W \overset{d}= G(U_{\ell})$.
-\end{definition}
-\begin{definition}
-A distribution $W$ over $\mathcal{M}$ is \emph{$(\epsilon, s, s_{f})$ - prg-qualified} if there exists a deterministic function $f:\mathcal{M}\rightarrow \{0,1\}^d$~(computable in space $s_{f}$) such that for all $D\in\mathcal{D}_s$, $\delta^D(f(W), U)<\epsilon$ and $d\geq k_{prg}$\footnote{We can extend this definition to allow $f$ to have public-randomness.
-The definition is not meaningful if $f$ has private randomness as $f$ can simply generate a fresh seed of length $d$.}.
-\end{definition}
-We use the term prg-qualified as the composition of $f$ and a $prg$ gives pseudorandom bits:
-\begin{proposition}
-Let $W$ over $\mathcal{M}$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution with function $f$ to $d$ bits.
-Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator~(computable by a circuit of size $s_{prg}$) where $k\leq d$.
-Then $\forall D\in\mathcal{D}_{\min\{s_W-s_{prg}, s_{sec}\}}$
-\[
-\delta^D(prg(f(W)_{1,..., k}), U_{k+1})< \epsilon_W + \epsilon_{prg}.
-\]
-\end{proposition}
-\begin{proof}
-Let $W$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution to $d$ bits.
-Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator where $k\leq d$.
-We proceed by contradiction.
-Suppose that $\exists D$ of size at most $s= \min\{s_W -s_{prg}, s_{sec}\}$ such that $\delta^D(prg(f(W)), U_{k+1})\geq \epsilon_W+\epsilon_{prg}$.
-By the triangle inequality, one has:
-\begin{align*}
-\epsilon_W+\epsilon_{prg}&\leq \delta^D(prg(f(W)_{1,...,k}), U_{k+1})\\
-&\leq \delta^D(prg(f(W)_{1,...,k}, prg(U_k)) + \delta^D(prg(U_k), U_{k+1})
-\end{align*}
-Thus, either $\delta^D(prg(f(W)_{1,...,k}, prg(U_k))\geq \epsilon_{W}$ or $\delta^D(prg(U_k), U_{k+1})\geq \epsilon_{prg}$.
-
-In the first case, we construct a distinguisher $D'$ that contradicts the $(\epsilon_W, s_W, s_{f})$-qualification of $W$.
-$D'$ upon receiving input $x\in \{0,1\}^d$ computes $D(prg(x))$ and outputs $D$'s answer.
-$D'$ is of size at most $s + s_{prg} \leq s_W-s_{prg}+s_{prg} = s_W$ and has advantage at least $\epsilon_W$.
-This is a contradiction.
-
-In the second case, $D$ immediately contradicts the $(\epsilon_{prg}, s_{sec})$ security of $prg$.  Thus, we have a contradiction in both cases.  This completes the proof.
-\end{proof}
-
-We now return to the question of whether we can build a computational fuzzy extractor when $H_\infty(W)<k_{prg}$.
-\begin{theorem}
-
-\end{theorem}
-\begin{proof}
-\bnote{Do the proof!}
-\end{proof}
-}
-%We now provide a candidate construction of fuzzy extractor based directly on a computational problem~(the LWE problem introduced by Regev~\cite{regevLWEsurvey}).
-%\begin{definition}
-%An $(\mathcal{M}, m, \tilde{m}, t, s_{dist}, \epsilon)$-\emph{computational secure sketch} is a pair of randomized algorithms, ``sketch'' (\sketch) and ``recover'' (\rec) with the following properties:
-%\begin{enumerate}
-%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns two strings, $(x,s)\in\{0,1\}^*$ where $x$ is drawn from a distribution $X$ and $\Hoo(X)\geq m$.
-%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of a computational secure sketches guarantees that if $d(w,w')\leq t$, then $Rec(w', SS(w)_2) = SS(w)_1$.
-%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, observing $SS(W)_2$ does not significantly help the adversary.
-That is, $H^\hill_{\epsilon, s_{dist}}(X | SS(W)_2)\geq \tilde{m}$.
-%\end{enumerate}
-%A secure sketch is \emph{efficient} if \sketch runs in expected polynomial time and \rec runs in expected polynomial time if $d(w', w) < t$.
-%\end{definition}
-%This definition has two significant changes from the definition of a secure sketch.
-First, we do not require that the distribution $X$ is equal to the input distribution $W$.
-This is because constructions will utilize computationally hard problems that may be difficult to invert.
-However, we can consider the special case where $X=W$.
-None of the power of a secure sketch is lost when $X\neq W$.
-
-%\textbf{Note: }  The entropy of $X$ is somehow limited by the entropy of $X$ we cannot completely hide some very high entropy string, using a low entropy string.
-This would have to be reflected in the parameters of \hill entropy but I am not yet sure how to formalize this.
-%
-% Furthermore, note there are two conditions on the distribution $X$, $\Hoo(X)\geq m$ and $H^\hill_{\epsilon, s}(X|SS(W)_2)\geq \tilde{m}$.
-This means that if an adversary does not see the helper value $s$ it has true entropy and its computational entropy is decrease by seeing $s$.
-
-%Second, we now require that the value $X$ only has conditional \hill entropy.
-Considering the special case where $m=\tilde{m}$ is interesting but constructions that improve on the $\tilde{m}$ achieved in secure sketch are interesting.
-Furthermore, it seems natural to consider the case where $|\rec|<s$ however, \rec has a significantly more difficult task, \rec must recover all of $x$ while the distinguisher in the conditional \hill entropy definition only needs to distinguish $x$ from a high average min-entropy distribution.
-%
-%Thus, we can define a stronger definition where all of these desiderata are achieved.  
-%
-%\begin{definition}
-%A $(\mathcal{M}, m, \tilde{m}, t, s, \epsilon)$-computational secure sketch is strong if the following properties hold:
-%\begin{enumerate}
-%\item Seeing $s$ does not decrease the conditional $\hill$ entropy of $X$.  That is, $m=\tilde{m}$.
-%\item There exists a circuit of \rec' where the size of \rec' is polynomial, $|\rec'|<s_{dist}$ and \rec' satisfies the correctness property.
-%\end{enumerate}
-%\end{definition}
-\ignore{
-\subsection{Learning With Errors (\class{LWE})}
-\label{subsec:LWE in detail}
-The LWE problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise".
-For positive integers $n$ and $q \ge 2$, a vector $\vect{s} \in \Fq$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{s}, \chi}$ be the distribution obtained by choosing a vector $\vect{a} \overset{\$}\leftarrow \Fq^n$ uniformly at random and a noise term $e \overset{\$}\leftarrow \chi$, and outputting $(\vect{a}, \langle \vect{a}, \vect{s}\rangle + e) \in (\Fq^m, \Fq)$.
-A formal definition follows.
-
-\label{sec:LWEoverview}
-\begin{problem}[\class{LWE}]\label{prob:LWE}
-Let $n$ be the security parameter.
-For a integer $q = q(n)$ and the error distribution $\chi = \chi(n)$ over $\Fq$, the Learning With Error problem $\class{LWE}_{n, m, q,\chi}$ is defined as follows: given access to an oracle that outputs $m$ samples from $A_{\vect{s}, \chi}$ for a uniformly random $\vect{s}$, output $\vect{s}$ with high probability.
-\end{problem}
-
-We will use the fixed form of the LWE assumption where a matrix is prepared ahead of time.
-The matrix form is as follows: $\class{LWE}$ find $\vect{x}$ given $(\vect{A},\vect{Ax+e})$, where $\vect{A}\leftarrow \Fq^{m \times n}$ is chosen uniformly and the error vector $\vect{e} \leftarrow \chi$.
-Results of Regev~\cite{regev2005LWE} and Peikert~\cite{peikert2009latticereduction} connect the hardness of the LWE problem to solving worst-case lattice problems.
-The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_\alpha$~(following the notation of~\cite{regev2005LWE}).
-We denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.
-Here we present the theorem of~\cite{regev2005LWE}.
-
-\begin{theorem}~\cite[Theorem 3.1]{regev2005LWE}
-Let $n$ be a security parameter and $q = q(n) \in\Fq^+$, let $\alpha = \alpha(n)\in (0,1)$ be such that $\alpha q > 2\sqrt{n}$.
-Let $\vA\in\Fq^{m\times n}, X\in \Fq^n$ be chosen uniformly at random and $E$ be chosen according to $\bar{\Psi}_\alpha$.
-If there exists a PPT-algorithm $\mathcal{I}$ such that $\Pr_{\vA, X, E}[X\leftarrow  \mathcal{I}(\vA, \vA X+E) ]>\epsilon$ for some noticeable $\epsilon$, then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem~(GAPSVP) and the shortest independent vectors problem~(SIVP) to within $\Omega(n/\alpha)$ in the worst case.
-\end{theorem}
-
-We will consider a generalized assumption of \probref{prob:LWE}:
-\begin{assumption}
-\label{assume:general LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ and $q=q(n)\geq 2$ be integers and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, \vA\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{I}$ of size at most $s$
-\[
-\Pr_{\vA, X, E}[X\leftarrow \mathcal{I}(\vA, \vA X+E)]<\epsilon
-\]
-\end{assumption}
-Furthermore, Regev shows a decision to search equivalence for $q=\poly(n)$, so we can consider an equivalent indistinguishability formulation:
-\begin{assumption}
-\label{assume:indist LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, A\in\Fq^{m\times n}, B\in\Fq^m$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{D}$ of size at most $s$:
-\[
-\Pr[D(\vA, \vA X+E)=1]-\Pr[D(\vA, B)=1]<\epsilon
-\]
-\end{assumption}
-We can restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy~(see Definition~\ref{def:unp entropy}).  
-}
-
-%\section{\lemref{lem:conversion to unpredictability}}
-%\label{sec:proof of unpred conversion}
-%In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.
-%We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).
-Thus, we have the following claim:
-%%\begin{claim}
-%%\label{lem:unp of x and e}
-%%Let $A, X, E$ be as above, then:
-%%\begin{itemize}
-%%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
-%%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
-%%\end{itemize}
-%%\end{claim}
-%%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
-%%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
-%%\begin{assumption}
-%%\label{assume:entropy LWE}
-%%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.
-%%\end{assumption}
-%%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
-%We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.
-This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
-We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
-%\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-%\label{lem:many hardcore bits}
-%Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
-Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
-%\end{lemma}
-%
-%\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
-%Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
-Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.
-Then according to \lemref{lem:many hardcore bits} we know that $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA , \vA X+E)\geq k\log q$.
-By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.
-To expand to $E$ we use the following claim:
-%
-%\begin{claim}
-%Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
-%\[
-%H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
-%\]
-%\end{claim}
-%%\begin{claim}
-%%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
-%%\end{claim}
-%%\begin{proof}
-%%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
-Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
-Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.
-This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
-%%\end{claim}
-%%\begin{proof}
-%%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
-%%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.
-Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
-Furthermore, let $C$ be a circuit of size at most $s_{sec}'$ where $\Pr[C(Z) = Y] > 2^{-k}$.
-Define the circuit $C'$ that outputs the first $k$ bits of $C$'s output.
-Thus, $\Pr[C'(Z) = Y_{1,..., k}] \geq \Pr[C(Z) = Y] > 2^{-k}$.
-Note that $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,...,k}, Z), (Y_{1,..., k}, Z))<\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
-Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
-%%This completes the claim.
-%%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.
-In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
-%% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
-Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
-Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.
-This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
-%%\end{claim}
-%%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.
-This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.
-Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
-%%
-%%
-%%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.
-By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.
-This completes the proof of \lemref{lem:conversion to unpredictability}.
-%%\end{proof}
-%\begin{proof}
-%Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.
-We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.
-That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}'}}((E, \vA X+E), (Y, \vA+E))\leq \epsilon$, there exists $C$ of size $s_{sec}'$ such that $\Pr[C(\vA, \vA X+E) = Y]> 2^{-\ell}$.
-Fix one such $Y$.
-Let $\mathcal{E}$ be the event that $A_{1,..., n}^{-1}$ exists.
-Note that $\mathcal{E}$ occurs with probability $1-\gamma$.
-%
-%Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
-%\begin{align*}
-%\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
-%\end{align*}
-%Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
-Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$.
-Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.
-%
-%We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
-%\begin{enumerate}
-%\item Input $(\vA, \vA X+E)$.
-%\item Run $y\leftarrow C(\vA, \vA X+E)$.
-%\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
-%\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
-%\end{enumerate}
-%Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
-Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.
-Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
-%\end{proof}
-%
-%The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
-%%\begin{proof}[Proof of \clref{lem:unp of x and e}]
-%%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
-That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
-Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(\vA, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Output $z = \vA y - \vA X+E$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
-%%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
-%%\end{align*}
-%%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
-That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((E, \vA, \vA X+E), (Y, \vA, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
-Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(A, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
-%%\item Output $z = \vA^{-1}(\vA X+E-y)$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
-For sufficient parameter sizes the probability of $A^{-1}$ not existing is negligible.
-Denote this probability by $\gamma$.
-Then note that $\Pr[I'(\vA, \vA X+E) = Z] > 2^{-k}-\gamma = 2^{-k'}$.
-Then one has the following~(conditioned on the event that $\vA^{-1}$ exists):
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
-%%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
-%%\end{align*}
-%%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
-%%\end{proof}
-%
-%\end{proof}
-
-\ignore{
-\section{Proof of Theorem \ref{thm:blockLWE}}
-\label{sec:proof of block theorem}
-
-%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
-\begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.
-If the blocks are fixed to some other value the reduction is essentially the same.
-
-%It should be clear to the reader where the reduction differs for another block fixing source.\lnote{I don't like the phrasing; maybe we should say that if the blocks are fixed to some non-0 value, the reduction is essentially the same}
-
-Let $\D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.
-That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
-Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.
-We assume that,
-\[
-|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
-\]
-
-We build a distinguish $\D'$ that distinguishes standard LWE instances from uniform.
-Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-Our goal is to prepare a random block fixing instance from the random instance we are given.
-The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
-
-It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
-\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
-%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
-\end{enumerate}
-\begin{figure}
-\begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.
-
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)$.
-\item \label{step:randomization}
-For {$i=1\ldots m+\alpha$}:
-\subitem Randomly generate $(\gamma_{i,1},\ldots, \gamma_{i,\alpha}) \leftarrow \Fq^\alpha$.
- \subitem For {$j = 1 \ldots n+\alpha$}:
-\subsubitem Set $A_{ij} \leftarrow A^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}$
-\subsubitem Set $b_i \leftarrow b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k}$
-\item Run $\D$ on input $\vA, \vb$.
-\item Output $\D$'s output.
-\end{enumerate}
-\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-
-\begin{claim}
-\label{cl:randomMatrixDist}
-The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix.
-\end{claim}
-\begin{proof}
-In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
-Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.
-Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.
-Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5.
-For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number.
-Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors.
-Therefore, the entire matrix $\vA$ is a truly random matrix.
-This completes the claim.
-\end{proof}
-\begin{claim}
-\label{cl:random ax+e}
-If $\D'$ is provided with input distributed as $\vA', \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i} = b_{m+i}^*$ is uniformly generated otherwise and  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
-\end{claim}
-\begin{proof}
-Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then define $\vx^*$ as:
-\[
-x^*_i = \begin{cases}
-x_i', & \text{if }1\leq i\leq n \\
-b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
-\end{cases}
-\]
-Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).
-Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
-%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).
-Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
-%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
-The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-\bnote{We need to justify these steps better.}
-\bnote{Is it really standard to go to lower case for the rows?}
-\xnote{lower case for vectors, which is row vector in the matrix}
-
-\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
-We have the following for all $i=1,..., m+\alpha$:
-\begin{align*}
-\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
-& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
-&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
-\end{align*}
-%\begin{align*}
-%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
-%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
-%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
-%& = b_i \label{reductionEq}
-%\end{align*}
-\end{proof}
-\begin{claim} 
-\label{clm:random b}
-If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
-\end{claim}
-\begin{proof}
-Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.
-After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
-\[
-b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
-\]
-%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each
-
-$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{It need show more work on this, maybe?}
-Thus, each of these values is uniformly and independently random.
-\end{proof}
-
-%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$.
-%
-%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$.
-Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
-%\begin{align*}
-%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
-%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
-%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
-%\end{align*}
-
-\begin{claim}
-If the pair $(\vA', \vb')$ is uniformly distributed, then the pair $(\vA, \vb)$ is uniformly distributed.
-\end{claim}
-\begin{proof}
-Assume that $(\vA', \vb')$ is uniformly distributed.
-By \clref{cl:randomMatrixDist}, $\vA$ is uniformly distributed.
-Thus, it suffices to show that $\vb | \vA$ is uniformly distributed.
-Let $\vb^*$ be the vector generated in step~\ref{step:b generation} and note that $\vb^*$ is uniformly random.
-We show  a stronger claim that $\vb |( \vA, \vA', \vR)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i,j}$.
-
- The matrix $\vgamma$ is a deterministic function of $(\vA, \vA', \vR)$.
-Thus, $\vb | (\vA, \vA', \vR) \overset{d}= \vb | (\vA, \vA', \vR, \vgamma)$.
-The only dependence of $\vb$ on $(\vA, \vA', \vR, \vgamma)$ is in the matrix $\vgamma$.
-Thus, $ \vb | (\vA, \vA', \vR, \vgamma) \overset{d}= \vb | \vgamma$.
-Recall that $\vb = \vb^* +  \left(\begin{array}{c | c}\mathbf{0} &\vgamma\end{array}\right)\vb^*$.
-Let $\vT = \vect{I}+  \left(\begin{array}{c | c}\mathbf{0} & \vgamma \end{array}\right)$.
-Since $\vT$ is a deterministic function of $\vgamma$, $\vb | \vgamma \overset{d} = \vb | \vT$.
-
- \bnote{Now we want to say that $\vb$ is uniformly distributed since $\vb'$ is.
-If $\vT$ exists we can just that $\vb | \vT = (\vT^{-1} \vb )| \vT = \vb' | \vT = U | \vT$.
-It does with very high probability, but I don't want to add this restriction.
-Is there a way to get around this problem?}
-%\[
-%\vA=  \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)
-%\]
-%\begin{align*}
-%(\vA, \vb) =  \left(\left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) \right) , \left(\vb' + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \vb'\right)
-%\end{align*}
-\end{proof}
-\bnote{Remember this isn't good enough.  We need the enhanced claim above.}
-Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
-\begin{align*}
-&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
-& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
-\end{align*}
-%==========
-\ignore{
-Before randomized:
-$$\vA'\vx' + \ve = \vb'$$
-For $i = 1\ldots m$,
-$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
-For $i = 1\ldots \alpha$,
-$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
-}
-\end{proof}
-}
-
-\section{Proof of Theorem \ref{thm:blockLWE}}
-\label{sec:proof of block theorem}
-
-%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
-\begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.
-If the blocks are fixed to some other value the reduction is essentially the same.
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
-For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.
-Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.
-We use similar notation for the complement of $T$, denoted $T^c$.
-
-%It should be clear to the reader where the reduction differs for another block fixing source.\lnote{I don't like the phrasing; maybe we should say that if the blocks are fixed to some non-0 value, the reduction is essentially the same}
-
-Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
-Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
-That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
-We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
-Let $\epsilon \geq 1/\poly(n)$, then,
-\[
-|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
-\]
-We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
-Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-It suffices to build a ppt distinguisher $\D'$  where
-\begin{align}
-\label{eq:block LWE dist}
-|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
-\end{align}
-We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
-
-\begin{figure}[t]
-\begin{framed}
-\begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
-\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
-		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
-\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
-\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
-\subitem For $j=1,..., m$:
-\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
-\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
-\item \label{step:randomization}
-For {$i=1,..., m$}:
-\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
-\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
-\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
-\item Run $\D$ on input $\vA, \vb$.
-\item Output $\D$'s output.
-\end{enumerate}
-\end{framed}
-\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
-\begin{claim}
-\label{cl:full rank matrix}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
-\end{claim}
-\begin{proof}
-The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
-By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
-\begin{align*}
-\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
-\end{align*}
-Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
-\end{proof}
-\begin{corollary}
-$
-|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
-$
-\end{corollary}
-
-We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ prepares a random instance in this case. We show this in the following three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
-%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
-\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
-\end{enumerate}
-
-\begin{claim}
-\label{cl:randomMatrixDist}
-The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix with $\rank(\vS) = \alpha$.
-\end{claim}
-\begin{proof}
-It should be clear that $\vR, \vS$ are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
-The quadrant represented by $\vA'$ remains random after step~\ref{step:randomization} as we are adding uncorrelated random values.
-The matrix $\vW_{T^c}$~(recall this is the restriction of $\vW$ to the columns not in $T$) is random as it is initialized with random values and only uncorrelated random values are added.
-
-Thus, we restrict attention to $\vW_T$~(the columns of $W$ included in $T$).
-Fix a particular row $i$.
-Then $\vW_{i, T} = \gamma_i \vS_{T}$.
-Since $\vS_T$ is full rank and $\gamma_i$ is uniformly generated, $\vW_{i, T}$ is uniformly generated.
-
-Thus, the entire matrix $\vA$ after step~\ref{step:randomization} is uniformly generated conditioned on $\rank(\vS) = \alpha$.
-% In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
-Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.
-Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.
-Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5.
-For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number.
-Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors.
-Therefore, the entire matrix $\vA$ is a truly random matrix.
-This completes the claim.
-\end{proof}
-\begin{claim}
-\label{cl:random ax+e}
-If $\D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
-\end{claim}
-\begin{proof}
-Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
-We define the remaining variables $\vx_T$ as the solution to the following system of equations.
-\[
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
-\]
-A solution $\vx_T$ exists as $\vS_T$ is full rank and furthermore, $\vx_T$ is uniformly distributed.
-Denote by $\vA^*$ the matrix before step~\ref{step:randomization} and denote by $\ve$ the vector $\ve'$ with $\alpha$ 0s appended.
-The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$.
-Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
-%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
-We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
-%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
-The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-We have the following for $1\leq i\leq m$:
-\begin{align*}
-\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
-&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
-\end{align*}
-Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
-\begin{align*}
-(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
-&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
-\\&=  \begin{pmatrix} b_{m+1}  \\ \vdots \\b_{m+\alpha} \end{pmatrix}
-\end{align*}
-This completes the proof of the claim.
-\end{proof}
-\begin{claim}\label{clm:random b}
-If the pair $\vb' | \vA'$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
-\end{claim}
-\begin{proof}
-Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$, i.e.
-for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.
-Thus $\vb^* | \vA^*$ is uniformly distributed.
-We show that $\vb |( \vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}.
-Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
-
- The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.
-Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.
-The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.
-Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$.
-Recall that
- \[
- \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
-\]
-Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
-\end{proof}
-
-Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus,
-\begin{align*}
-&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
-&\, = \left| \Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
-&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
-&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
-\end{align*}
-Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
-\end{proof}
-\section{Additional Proofs}
-
-\subsection{Proof of \lemref{lem:averageToMaximalError}}
-\label{sec:proof of average to maximal error}
-\begin{proof}
-Let $C$ be the  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$ such that  $\Hoo(C)\geq k$.  Then for all $t'\le t$
-\[
-\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \neigh (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
-\]
-For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \neigh(c, t') \wedge \rec(c') \neq c]$.  
-Then by Markov's inequality:
-\[
-\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
-\]
-Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.
-Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.
-Since $H_\infty(C)\geq k$, we know $|C'|\geq 2^{k-1}$~(otherwise $\Pr_{c\leftarrow C}[c\in C']=\sum_{c\in C'}\Pr[C=c]$ would be less than $2^{k-1}\frac{1}{2^k} = 1/2$).
-This completes the proof of the~\lemref{lem:averageToMaximalError}.
-
-%Suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]> 2\epsilon$.  
-%This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.
-Then note that $\Pr[W\in V]> 1/2$ as $W\setminus V$ contains at most $2^{k-1}-1$ points each of which has probability at most $1/2^k$ so $\Pr[W\in (W\setminus V)]\leq (2^{k-1}-1)/2^k < 1/2$.
-Thus,
-%\begin{align*}
-%\Pr_{w\in W}[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]\\
-%&\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
-%\end{align*}
-%% where $\forall d\in D, \Pr[d'\leftarrow \sample(d) \wedge \rec(d') > 2\epsilon$.  In turn this implies that  
-%%\begin{align*}
-%%\Pr_{c\in C}[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]&=\frac{1}{|C|} \sum_{c\in C}  \Pr[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]\\
-%%&\geq \frac{1}{|C|} \sum_{d\in D}  \Pr[ d'\leftarrow \sample (d) \wedge \rec(d') \neq d]\\
-%%&\geq \frac{1}{|C|}\sum_{d\in D} 2\epsilon = \frac{1}{|C|}\left(\frac{|C|}{2}+1\right)2\epsilon = \epsilon + 2\epsilon/|C|> \epsilon
-%%\end{align*}
-%This is a contradiction.  The statement of~\lemref{lem:averageToMaximalError} follows directly.
-\end{proof}
-
-\subsection{Proof of \thref{thm:impSketchArbitraryW}}
-\label{sec:proof of thm sketch implies code}
-\begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
-\[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))<\epsilon.
-\]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. Let $X_y$ denote the random variable $X|Y=y$.
-%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
-Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.
-This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.
-Define $D$ as:
-\begin{enumerate}
-\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{enumerate}
- By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((W, \sketch(W)), (X, Y))<\epsilon$, we know $\Pr[D(X, Y) = 1]>1-\epsilon-t\delta$.
-By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]> 1- 2(\epsilon + t\delta)$.
-
-Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.
-Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).
-Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).
-Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]> 1-2(\epsilon+t\delta).\]  
-%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
-Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.
-The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
-\end{proof}
-
-\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
-\subsection{Proof of \thref{thm:imp of unp entropy}}
-\label{sec:proof of imp unp entropy}
-Instead of proving \thref{thm:imp of unp entropy}, we will prove a stronger result based on a weaker form of entropy.
-This relaxed definition allows both the variable and the condition to be replaced.
-This is analogous to the relaxed HILL entropy~(see \defref{def:relaxed hill}).%Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}~(we provide a formulation of this notion in \defref{def:relaxed hill}).
-
-\bnote{This needs to be consistent with the notation above.  Should be $W, S$ for original and $X, Y$ for indistinguishable distribution.}
-\begin{definition}
-\label{def:relaxed unp entropy}
-For a distribution $(X, Z)$, we say that $X$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a joint distribution $Y, Z'$ such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z'))\leq \epsilon$, and for all circuits $C$ of size at most $s_{sec}$,
-\[
-\Pr[C(Z) = Y ] \leq 2^{-k}
-.\]
-\end{definition}
-
-We will prove the result for a metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
-We now define this second condition:
-\begin{definition}
-A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
-\end{definition}
-
-\begin{theorem}
-Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
-Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is fixed~(this quantity is denoted by $B_t(\cdot)$).
-Let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
-\end{theorem}
-\begin{proof}
-Let $\mathcal{M}, \dis$ be a $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable metric space~(by procedures $\sample$ and $\neigh$ respectively).  
-Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.
-Let $Y, Z'$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z'))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Z') = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n\log |Z| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
-
-Let $B_t(y)$ denote the random variable of a random neighbor of distance at most $t$ from $y$.
-Recall, the algorithm $\neigh$ outputs neighbors at a fixed distance, the random variable $B_t(y)$ may not be efficiently computable, we only use it as a random variable.
-We begin by showing that \rec must recover points of $Y$.  
-\begin{claim}
-\label{clm:y is recoverable}
-\begin{align*}
-\Pr[\rec(B_t(Y), Z') = Y]&=\\
-\Pr[(y, z)\leftarrow (Y, Z) \wedge y'\leftarrow B_t(y) \wedge \rec(y', z) = y] &\geq 1-\epsilon -t\delta.
-\end{align*}
-\end{claim}
-\begin{proof}
-Suppose that $\Pr[\rec(B_t(Y), Z') = Y]<1-\epsilon -t\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
-\begin{itemize}
-\item Input $w\in \mathcal{M}, s\in\zo^*$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{itemize}
-First note that $|D| = t( |\rec|+ s_{neigh} )$.
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
-If $\Pr[\rec(B_t(Y), Z') = Y] < 1-\epsilon -t\delta$ there must exist some $1\leq t'\leq t$ where this is true.
-Then
-\begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, Z')=1] &\geq\\
-(1-t\delta) - \Pr[\rec(\neigh(Y, t'), Z') = Y] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
-\end{align*}
-This is a contradiction and the statement of the claim follows.
-\end{proof}
-We now consider the experiment $(y, z)\leftarrow (Y, Z'), y'\leftarrow B_t(y)$ and define the quantity $P_{y' , z, y} = \Pr[\rec(y', z) =y]$.  \clref{clm:y is recoverable} says that 
-\[
- \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in \mathcal{M}} \Pr[B_t(y) =y' | Y = y] P_{y',  z, y} \geq 1-\epsilon - t\delta.
-\]
-We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, \Pr[B_t(y) = y' | Y=y] = 0$.
-Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$.
-Now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
-\begin{itemize}
-\item Input $z\in\zo^*$.
-\item Sample $x\leftarrow \sample(\cdot)$.
-\item Output $\rec(x, s)$.
-\end{itemize}
-Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
-We now show that $\mathcal{I}$ predicts $Y$:
-\begin{align*}
-2^{\tilde{m}}& = \Pr[\mathcal{I}(Z') = Y] \\
-&= \Pr[(y, z)\leftarrow (Y, Z')] \Pr[\mathcal{I}(z) = y]\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[X = y' ]\Pr[\mathcal{I}(z) = y | X = y']\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[X = y' ] P_{y', z, y}\\
-&\geq \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq  \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \frac{1/|\mathcal{M}|}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[(y, z)\leftarrow (Y, Z')] \sum_{y'\in\mathcal{M}} \Pr[B_t(y) = y' | Y=y ] P_{y', z, y}\\
-&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
-\end{align*}
-Finally converting to entropy, one has $\tilde{m}\leq \log |\mathcal{M}|-\log |B_t(\cdot)| - \log (1-\epsilon -t \delta)$.
-\end{proof}
-
-%\bnote{This is the proof for not relaxed unpredictability entropy}
-%\begin{proof}
-%Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
-Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
-We begin by showing that $Y$ must correctly recover most of the time.
-%\begin{claim}
-%\label{clm:y is recoverable}
-%\begin{align*}
-%\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
-%\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
-%\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
-%\end{align*}
-%\end{claim}
-%\begin{proof}
-%Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
-%\begin{itemize}
-%\item Input $x\in \zo^b, s\in\zo^*$.
-%\item Sample $x'\leftarrow B_t(x)$.
-%\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
-%\end{itemize}
-%Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
-The statement of the claim follows as
-%\begin{align*}
-%\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
-%\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
-%\end{align*}
-%\end{proof}
-%We now consider the experiment $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
-\clref{clm:y is recoverable} says that
-%\[
-% \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
-%\]
-%We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
-Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
-%We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
-%\begin{itemize}
-%\item Input $s\in\zo^*$.
-%\item Sample $x'\leftarrow \zo^b$.
-%\item Output $\rec(x', s)$.
-%\end{itemize}
-%We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
-%We now show that $\mathcal{I}$ predicts $Y$:
-%\begin{align*}
-%2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
-%&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
-%\end{align*}
-%Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
-%\end{proof}
-
-%\subsection{Proof of \lemref{lem:i t constant time}}
-%\label{sec:proof lem i t constant time}
-%\begin{proof} We consider the expected number of iterations in step 2 when $t+1\leq m/n$.
-Steps 3 and 4 can be accomplished in time $n^3\log q +s_{ver}$.
-An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
-That is,
-%\begin{align*}
-%\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq  \prod_{i=0}^{n-1}\left( 1-\frac{m-n}{n(m-i)}\right)\\
-%&\geq \prod_{i=0}^{n-1}\left( 1-\frac{1}{n}\right)\geq \left(1-\frac{1}{n}\right)^n \geq 1/4.
-%\end{align*}
-%Note in the last step we assume that $n\geq 2$.
-The minimum of $(1-1/n)^n$ is achieved at $n=2$ and it quickly converges to $1/e$.
-Thus, the expected number of iterations is at most $4$ giving the stated running time for $\mathcal{I}_t$.
-%\end{proof}
-
-\subsection{Proof of \lemref{lem:i t poly time}}
-\label{sec:proof lem i t poly time}
-\begin{proof}
-Let $d$ be a constant and $t = d\log n\left( \frac{m}{n}-2\right)$.  
-By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $t$ with probability $1-e^{-\Omega(n)}$.
-Thus, a false matches occurs in step (5) with probability $e^{-\Omega(n)}$.
-This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\mathcal{I}_t$.
-We consider the expected number of times step 2 is executed when $t\leq d\log n\left(\frac{m}{n}-1\right)$.
-Steps (3-5) can be accomplished in time $n^3\log q $.
-An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.
-The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $\vc_{i_1,...,i_{2n}}$ has no errors.
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
-That is,
-\begin{align*}
-\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n\left(\frac{m}{n}-2\right)}{m-i}\right)\\
-&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
-&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}
-\end{align*}
-Now, we consider the probability that no sub matrix of $\vA_{i_1,..., i_{2n}}$ has full rank.
-This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).
-Thus, the probability that a given iteration succeeds $\frac{1}{n^{4d}} - e^{-\Omega(n)}$.
-Thus, the expected number of iterations in step 2 at most  $2n^{4d}$.
-We assume all matrix operations can be completed in time $n^3\log q$, giving expected running approximately $O(n^{4d}(n^3 \log q))$.
-\end{proof}
-
-\section{Parameter Settings for \consref{cons:informal construction}}
-\label{sec:parameter settings}
-In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure conductor log} we give lossless conductors from a security parameter $n$ and an error $t$.
-In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
-We begin by reviewing the parameters that make up our construction:
-
-\begin{itemize}
-\item $|W|$: The length of the source.  
-\item $t$: Number of errors that can be supported.  
-\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
-\item $q$: The size of the field.  
-\item $\rho$: The fraction of the field needed for error sampling.  
-\item $m$: The size of each number of samples in the LWE instance.  
-\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
-\end{itemize}
-We will split the source $|W|$ into $m$ blocks each of size $\rho q$~(that is, $|W| = m\log \rho q$).
-We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.
-As stated above we have three constraints:
-\begin{itemize}
-\item Maintain security of LWE.
-If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + 3\gamma} m = \poly(n)$.
-The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.
-We ignore this effect and assume that $\rho q = 2n^{1/2+3\gamma}m$.
-\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
-\item Minimize entropy loss of the construction.
-We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.
-We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.
-Substituting, one has $m\log \rho q = k \log q$.
-\end{itemize}
-Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
-\begin{align*}
-n_0&< n -k \\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+3\gamma}m\\
-m\log \rho q &= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log 2n^{1/2+3\gamma}m &= k \log n^f
-\end{align*}
-%\xnote{$ m \log 2n^{1/2+3\gamma}m = n \log n^f$}
-This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-%f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
-Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n -k \\
-m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
-\end{align*}
-
-%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
-Note that $f$ is at most a constant in $n$.
-
-Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= \frac{(c+2d)n}{d}\\
-q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
-\end{align*}
-Furthermore, we get decoding in time $O(n^{4d}(n^3\log n))$.
-We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).
-The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.
-In \thref{thm:lossless secure conductor log}, we set $g=2$ and output the first half of $X$.
-This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.
-Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
-
-\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
-\label{ssec:block params}
-We repeat parameter settings for block fixing sources.
-We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.
-We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
-\begin{align*}
-n_0&< n -k  -\alpha -\beta\\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+3\gamma}m\\
-m\log \rho q &= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k - \alpha -\beta\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log 2n^{1/2+3\gamma}m &= k \log n^f
-\end{align*}
-As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k  - \alpha - \omega(1) \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-%f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.
-Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n/3 -  \log n\\
-m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
-\end{align*}
-
-Assuming $n/3-\log(n)> n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= \frac{(c+2d)n}{d}\\
-q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
-\end{align*}
-
-\ignore{
-\subsection{Old parameter setting}
-The question then becomes whether there is a setting 
-Our construction has two goals: 1) maximizing correcting capability~(while retaining polynomial time decoding, and 2) maximizing the unpredictability entropy of $W$ conditioned on the construction~($\tilde{m}$ in \defref{def:comp secure sketch}).
-Our parameters will differ significantly depending on what setting of $t$ is used.
-We will consider both settings where $t\leq m/n-2$ and $t\leq c\log n (m/n-2)$.
-Recall these corresponding to Construction~\ref{cons:decoding algorithm} running either in fixed polynomial time or time approximately $n^{2c}$.
-We consider each of these settings:
-
-$\mathbf{t \leq m/n-1}$
-
-We first find the appropriate range of $n$.
-First, we need $n>n_0$ for LWE security.
-Increasing $n$, up to the point when $H_\infty(X)=H_\infty(W)$, i.e., $n\log q = m\log\rho q$, increases the unpredictability entropy of the construction~(see \assref{assume:entropy LWE}).
-However, this decreases the number of errors $t$ we can correct.
-There is no advantage to increasing $n$ further\footnote{We primarily consider the construction with no entropy drop, if a drop is unpredictability entropy is acceptable, more errors can be corrected.
-However, if the remaining unpredictability entropy is worse than a known information theoretic construction~(see~\cite{DBLP:journals/siamcomp/DodisORS08}), an information theoretic construction should be used.
-}.
-
-We first analyze the lossless construction, when  $H_\infty(X)=H_\infty(W)$ and thus $n\log q = m\log\rho q$.
-Substituting $m \ge (t+1)n$ above one has:
-\[
-n \log q  = m \log \rho q \geq (t+1)n \log \rho q
-\]
-Thus, the lossless construction can support settings where $t+1\leq \frac{\log q}{\log \rho q}$.
-In order to apply \lemref{lem:uniform LWE}, we need that $\rho q\geq 2n^2m \geq 2(t+1)n^3$.
-We consider the setting $q = n^d$ for some constant $d$ (larger $q$ is unlikely to improve parameters unless
-%In Appendix~\ref{sec:parameters q expo}, we review parameters where $q=2^n$, these parameters are worse unless 
-lattice problems are hard to approximate within exponential factors.)  
-Dividing the above equations above we have:
-\[
-t+1\leq \frac{\log q}{\log \rho q}\leq \frac{\log q}{\log 2(t+1) n^3}\leq \frac{\log n^d}{\log 2t n^3} \approx d/3
-\]
-(the last step follows because the second-to-last step already implies $t\le d\log n$).
-Thus, we can support a constant $d/3-1$ number of errors where $q = n^d$ is the size of our field.
-Because we need $\rho q\geq 2n^2m \geq 2(t+1)n^3$ (to apply \lemref{lem:uniform LWE}), we require $\rho > n^{3-d}$.
-Thus, our construction is secure if SIVP and GAPSVP are hard within approximation factors of
-\[
-\tilde{O}(n^{5/2}m/\rho) = \tilde{O}\left(\frac{n^{5/2} m }{\rho}\right)
-= \tilde{O}\left(\frac{n^{5/2}t}{n^{3-d}}\right)
-= \tilde{O}\left(n^{d-1/2}m\right)
-\]
-
-%As an example if $\gamma = n^{c}$, this yields:
-%\[
-%t\leq \frac{n}{n + \log n + \log t - \log \gamma} = \frac{n}{n+\log n +\log t  -\log n} = \frac{n}{n + \log t}
-%\]
-%Alternatively, if $\gamma = n^{\log n}$, this yields:
-%\[
-%t\leq \frac{n}{n + \log n + \log t - \log \gamma} = \frac{n}{n+\log n +\log t  -\log^2 n} = \frac{n}{n+\log n - \log^2 n + \log t}
-%\]
-%Thus, as $q$ grows we can support a larger number of errors.
-However, the growth of $q$ with a fixed size $\rho q$ leads to the approximation factor in \lemref{lem:uniform LWE} no longer being a harder problem.
-Thus, $q$ can only be increased while the lattice problems in \lemref{lem:uniform LWE} is still believed to be hard.
-Furthermore, in the decision formulation of \lemref{lem:uniform LWE decision} requires that $q(n) = poly(n)$.
-This means that $t\leq O(\log n)$.
-
-$\mathbf{t\leq c\log n(m/n -1)}$
-
-We repeat the above analysis.  Recall we now consider the case where $m\geq (t+1)n/(c\log n)$.  We seek to satisfy:
-\[
-n\log q = m\log \rho q \geq (t+1)n \log \rho q /(c\log n)
-\]
-Again, we assume that $q = n^d$ for some constant $d$.  Then 
-\[
-t+1\leq \frac{c \log n \log q }{\log \rho q}\leq \frac{cd\log^2 n}{ \log \frac{2(t+1) n^3}{c\log n}}\leq \frac{cd \log^2 n}{3 \log n} \approx \frac{cd \log n}{3}.
-\]
-This gives $\rho > n^{3-d}/\log n$ and security if SVIP and GAPSVP are hard within approximation factors of $\tilde{O}(n^{d-1/2}m/\log n)$.
-
-\textbf{Formulation from $W, t$:}
-
-In a standard application, a source $W$ and number of errors $t$ will be given\footnote{Parameter settings will change the alphabet size and thus might change $t$, we ignore these effects and assume $t$ is given.}.
-Thus, the goal is to maximize security subject to correcting $t$ errors.
-This means the following parameters must be set:
-\begin{itemize}
-\item How large should $X$ be?
-The size of $X$ is the limiting factor for the resulting unpredictability entropy.
-Thus, $n$ should be as large as possible while allowing decoding.
-We must also ensure that $n>n_0$ for security.
-\item How large a field should we operate over?
-This is the parameter $q$.
-Increasing this parameter allows correcting more errors~(subject to the underlying lattice problems still being hard to approximate).
-\item How length block should $W$ be split into?  This is the parameter $\rho q$.  Setting this parameter also sets $m = |W|/\log \rho q$.
+\item $B_t(x)$ - the ball of radius $t$ around a point $x$
+\item $\sketch$ - secure sketch procedure
+\item $\rec$ - recover procedure for secure sketch
+\item $\gen$ - fuzzy extractor generate
+\item $\rep$ - fuzzy extractor reproduce
+\item $w/W$ - the noisy source we are drawing from
+\item $s$ - output of secure sketch
+\item $S$ - the distribution W is conditioned on, we also denote this by $\sketch(W)$
+\item $R$ - key from fuzzy extractor
+\item $P$ - helper value for fuzzy extractor
+\item $X, Y$ - these are used for the indistinguishable distributions, for the $\hill$ and $\unp$ entropy.
+\item $D, \mathcal{D}$ - distinguisher and distinguisher class
+\item $Z$ - the alphabet when we consider Hamming metric
+\item $\ell$ - derived key length
+\item $\epsilon$ - distance from uniform either for extractor or fuzzy extractor
+\item $\delta$ - error rate of a fuzzy extractor or secure sketch
+\item $\ext$ - extractor
+\item $\rext$ - reconstructive extractor
+\item $(\mathcal{M}, \dis)$ - metric space and associated distance
+\item $s_{sam}$ - size of $\sample$
+\item $s_{sec}$ - size of security circuit
+\item $s_{rec}$ - size of recover circuit
+\item $t$- bounded such that $\dis(w, w')\leq t$
+\item $k$- the number of hardcore dimensions in AKV09, this is the size of our resulting key
+\item $m$- starting min-entropy of source
+\item $\tilde{m}$ - resulting min-entropy of a construction
+\item $\vect{A}$ - random matrix in LWE
+\item $n$ - security parameter for LWE
+\item $q$ - size of field for LWE
+\item $m$ - number of samples in LWE
+\item $\vect{x} / X$ - secret vector in LWE
+\item $\chi$ - arbitrary error distribution for LWE
+\item $\bar{\Psi}_\alpha$ - discretized Gaussian distribution
+\item $\gamma$ - Parameter in DMQ error size and lattice hardness
+\item $d$ - running time of inverter, tied to number of errors that can be corrected and redundancy in m
+\item $c$ - constant log errors that can be corrected
+\item $\rho$ - $\rho q$ is the noise width
+\item $b$ - the number of bits in a block $b = \log \rho q$
+\item $\mathcal{C}$ - a set that forms a code
+\item $C$ - a distribution of points that we use to form a code
+\item $C, D$ - the reconstruction procedures for a reconstructive extractor
+   NOTE: both of these are used above, need to change
+\item $\neigh , s_{neigh}$- algorithm for sampling a neighbor
+\item $\sample, s_{sam} $- algorithm for picking a random point in the metric space
+\item $\vect{C}, \vect{D} $ used in the decoding algorithms of code-offset construction
+\item $f$ - the degree of the polynomial used to express the size of the field q
+\item $n_0$ - first point where LWE is considered secure
+\item $\alpha$ - the number of fixed dimensions for a block fixing source
+\item $\beta$ - the extra variables added in Theorem 5.3
+\item $\gamma$ - parameter in DMQ13, slightly changes their setting, we consider $\gamma = 1/2$
+\item $g$ - the fraction of n that we will output as hardcore bits
 \end{itemize}
 
-Unfortunately, the parameters $m, n$ and depend on each other and cannot be set independently.  As before, we will consider the fixed poly time decoder and variable poly time decoder in turn.
-
-$\mathbf{t\leq (m/n-1)}$
-
-We set parameters in the following order:
-\begin{itemize}
-\item Let $m, n$ be integer solutions to the following equations that maximizes $n$~(if the maximum solution is less than $n_0$, we cannot support a secure construction):
-\begin{align*}
-|W| &= m\log 2n^2m\\
-n&\leq m/(t+1)
-\end{align*}
-We assume that the solution for $m,n$ exists and is tight~(in the sense that $n = m/(t+1)$).
-If not, there is an entropy loss in the construction due to size mismatches~(in the entropy analysis below) and padding~(to ensure that $|W|$ is an integer number of blocks).
-\item Set $\rho q = 2n^2m $.
-\item Set $q = n^{(t+1)\log( 2(t+1)n)/\log n}$.  Note that although $n$ appears in the exponent if $t$ is a fixed constant~(does not depend on $|W|$), this value is $q =\poly(n)$.  
-\end{itemize}  Given these parameters, we can calculate the sizes of $X$ and $W$~(as we show in the \secref{sec:security of LWE cons} $\tilde{m} =|W|$):
-\begin{align*}
-H^{\unp}_{\epsilon, s} ( W | AX+W) &= \min\{ H_\infty(W), H_\infty(E)\}\\
-H_\infty(X) = |X| &= n \log q= \frac{m}{t+1}\log n^{(t+1)\log 2(t+1)n/\log n} \\
-&= \frac{m}{t+1} \frac{(t+1)\log 2(t+1)n}{\log n} \log n = m \log 2(t+1)n^3 \approx m\log 2n^2m\\
-H_\infty(W) = |W| & = m \log \rho q = m \log 2n^2 m\,.
-\end{align*}
-
-$\mathbf{t \leq c\log n(m/n-1)}$
-We set parameters in the following order:
-\begin{itemize}
-\item Let $m, n$ be integer solutions to the following equations that maximizes $n$~(if the maximum solution is less than $n_0$, we cannot support a secure construction):
-\begin{align*}
-|W| & = m\log 2n^2m\\
- \frac{nt}{c\log n} + n&\leq m
-\end{align*}
-We assume that the solution for $m,n$ exists and is tight~(in the sense that $ \frac{nt}{c\log n} + n=m$).
-If not, there is an entropy loss in the construction due to size mismatches~(in the entropy analysis below) and padding~(to ensure that $|W|$ is an integer number of blocks).
-\item Set $\rho q = 2n^2m $.
-\item Set $q = (2n^2m)^{m/n}$.  Note if $t = O(\log n)$, then $m/n = \frac{t}{c\log n} +1 = O(1)$ and thus $q$ is polynomial in $n$.
-\end{itemize}  Given these parameters, we can calculate the sizes of $X$ and $W$~(as we show in the \secref{sec:security of LWE cons} $\tilde{m} =|W|$):
-\begin{align*}
-H^{\unp}_{\epsilon, s} ( W | \vA X+W) &= \min\{ H_\infty(W), H_\infty(E)\}\\
-H_\infty(X) = |X| &= n \log q= n \log (2n^2m)^{m/n} = m \log 2n^2m\\
-H_\infty(W) = |W| & = m \log \rho q = m \log 2n^2 m\,.
-\end{align*}
-
-We'll now consider a formulation for a fixed length biometric and a number of block errors.
-We assume that $n$ is given as a security parameter and thus we ask how many errors can be corrected for a noisy uniform distribution of length $w>>n$.
-We denote the number of errors by $t$~(we'll be able to correct block errors over the alphabet $[-\rho q, \rho q]$).
-Let $n$ be a security parameter and let $W$ be the uniform distribution of length $w>>n$.
-Let $m$ as the minimum integer such that $m\log 4m^2 n\geq w$.
-Set $q = 2^{m/n}4m^2n$.
-Then split $W=( W_1,..., W_m)$ where each $W_i$ is of length $\log 4m^2 n$ bits.
-Then, for $W' =( W_1',.., W_m')$ if  $t = |\{i |  W_i \neq W_i'\}| \leq m/n$ block errors, Construction~\ref{cons:decoding algorithm} allows for decoding in expected polynomial time.
-Furthermore, $H^{\unp}_{\epsilon, s}(W | \vA X+W)\geq |W|$~(stating \lemref{lem:uniform LWE decision} in the language of Assumption~\ref{assume:entropy LWE}).
-
-\begin{theorem}
-\label{thm:security of secure sketch}
-Let $n_0$ be a security parameter and let $W$ be uniform over $\mathcal{M}$ and let $t$ be a constant.  Let $m,n $ be the solution to the following equations that maximizes $n$.
-\begin{align*}
-|W| &= m\log 2n^2m\\
-n&\leq m/t
-\end{align*}
-If $n>n_0$ and $n = m/t$ and \assref{assume:entropy LWE} holds, then for 
-\begin{align*}
-q &= n^{3t\log( \sqrt[3]{2t}n)/\log n}\\
-\rho q &= 2n^2m,
-\end{align*}  Construction~\ref{cons:LWESecureSketch} with uniform error over the interval $[-2n^2m, 2n^2m]$ is a $(\mathcal{M}, |W|, |W|, \epsilon, s, s_{sketch}, s_{rec}, t)$-computational secure sketch for $s = \poly(n), s_{sketch} = O(m\times n )$ and $s_{rec}$ is expected polynomial time.
-\end{theorem}
-
-\bnote{Not sure what to do with this}
-\begin{theorem}
-\label{thm:security of block sketch}
-Let $n_0$ be a security parameter and let $t$ be a constant.
-Let $W\in \{0, 1\}^{(m+\alpha)\times \log 2n^2m}$ be an $\alpha$-symbol fixing source where $m,n $ are the solution to the following equations that maximizes $n$.
-\begin{align*}
-|W| &= (m+\alpha)\log 2n^2m\\
-(n+\alpha)&\leq (m+\alpha)/t
-\end{align*}
-If $n>n_0$ and $n+\alpha = (m+\alpha)/t$ and \assref{assume:entropy LWE} holds, then for 
-\begin{align*}
-q &= n^{3t\log( \sqrt[3]{2t}n)/\log n}\\
-\rho q &= 2n^2m,
-\end{align*}  Construction~\ref{cons:LWESecureSketch} with uniform error over the interval $[-2n^2m, 2n^2m]$ is a $(\mathcal{M}, \Hoo(W), \Hoo(W), \epsilon, s, s_{sketch}, s_{rec}, t)$-computational secure sketch for $s= \poly(n)$,  $s_{sketch} = O(m\times n )$ and $s_{rec}$ is expected polynomial time under .
-\end{theorem}
-
-}
-
-\ignore{
-\section{Fuzzy Extractor Statement of Construction~\ref{cons:LWESecureSketch}}
-\label{sec:fuzzy extractor phrasing}
-In this section we restate Construction~\ref{cons:LWESecureSketch} as a computational fuzzy extractor instead of a computational secure sketch:
-\begin{construction}[Computational Fuzzy Extractor based on LWE] 
-\label{cons:LWEFuzzyExtractor} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers, furthermore let $\chi$ be a distribution $\Fq$ that can be sampled with a fixed number of bits $s_{err}$.
-Let $\mathcal{I}_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
-Furthermore, let $\rext$ be a reconstructive extractor.
-Let $W$ be a distribution over $\{0,1\}^{s_{err}\times m}$.
-
-\textbf{\gen}
-\begin{enumerate}
-\item Input $w\leftarrow W$.
-\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
-\item Use $w$ as the randomness for the sampling algorithm, $\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
-\item Sample $seed\leftarrow U$ as required for \rext.  Compute $r\leftarrow \rext(E, seed)$
-\item Set $p = (A, AX+E, seed)$.
-\item Output $(r, p)$.
-\end{enumerate}
-
-\textbf{\rep}
-\begin{enumerate}
-\item Input $(w', p)$
-\item Parse $p$ as $(A, C, seed)$
-\item Compute $E' \leftarrow \sample (w')$.
-\item Set $X' = \mathcal{I}_t(A, C-E') $. 
-\item Compute $r\leftarrow \rext (C-AX', seed)$.
-\item Output $r$.
-\end{enumerate}
-\end{construction}
-
-\begin{theorem}[Security of Construction~\ref{cons:LWEFuzzyExtractor}]\label{thm:LWEFuzzyExtractor}
-Fix $(n, m, q, \chi)$ such that Assumption~\ref{assume:general LWE} holds for $\mathcal{I}$ of size at most $s$ with success $\epsilon$.
-Furthermore assume that a fixed number of bits $s_{err}$ are necessary to sample from $\chi$.
-Let $\rext: \chi^m \times\{0,1\}^\ell\rightarrow \{0,1\}^{k_{len}}\times \{0,1\}^\ell$ be an extractor with $(\log 1/\epsilon - \log 1/\delta, \delta)$-reconstruction $(\cons,\decons)$.
-Let $\mathcal{I}_t$ be an inverter as described in Construction~\ref{cons:LWEFuzzyExtractor} of size $s_{\mathcal{I}_t}$.
-Then Construction~\ref{cons:LWEFuzzyExtractor} is a $(\{0,1\}^{m\times s_{err}}, m\times s_{err}, k_{len}, t, s_{rec}, s/(|\cons|+|\decons|), 5\delta)$ computational fuzzy extractor where $s_{rec, t} = s_{\mathcal{I}_t}+ |\sample| + O(m\times n\times \log q) + |\rext|$.
-\end{theorem}
-}
-
-\ignore{
-\section{Min-entropy error LWE}
-Throughout this section we will assume that \sample uses $\ell$ bits of randomness to produce the required distribution in a single dimension.
-Usually, this is the normal (Gaussian) distribution with some mean.
-Note that for the uniform distribution sampling requires $\log q$ bits where $q$ is the size of the range.
-By information theory we know that in expectation, the number of random bits is smaller for an distribution that is not uniform, but this provides us no guarantee about the worst case number of bits.
-We will begin with noting a few cases that seem significantly easier to show.
-Recall that the distribution $W$ is drawn from is specified and known by the adversary.
-\begin{itemize}
-\item Case 1: $\Hoo(W)\leq \ell (m- n)$.
-This case is not secure.
-Let $W\in\{0,1\}^{\ell m}$ and we further specify $W=W_1,...,W_m$ where each $W_i\in\{0,1\}^\ell$.
-We then set $W_1,...,W_n$ equal to some fixed value, $0$ without loss of generality, and $W_{n+1},...,W_m$ to the uniform distribution.
-Then it is clear for the first $n$ equations, the adversary is solving a system $Ax=b$ without any error and this can be done in $P$.
-\item Case 2: Full or no entropy.
-As before, let $W\in\{0,1\}^{\ell m}$ and we further specify $W=W_1,...,W_m$ where each $W_i\in\{0,1\}^\ell$.
-We further restrict to the case where each $W_i$ either $W_i\overset{d}=U_\ell$ or $\Hoo(W_i) = 0$.
-Thus, for each dimension either, one of the two occurs: the error is properly generated or the adversary knows the error exactly.
-So, for each dimension, given the $W_i\overset{d}=U_\ell$, the adversary can only guess the correct random variable not better than $2^{\ell}$.
-Similarly, if given the $\Hoo(W_i) = 0$, the adversary can always guess the correct variable.(\xnote{This is trivial, since if we give $\Hoo(W_i) = 0$, we are actually giving the a random variable has probably of 1.})
-
-We are considering the case that the adversary will be given the ensemble $\{W_1,...,W_n\}$, where each $W_i$ has some entropy.
-
-\item Case 3: General case.
-\item \textbf{Hypothetical worry case}  Suppose for convenience we are working with the normal distribution that has variance $\frac{2}{\pi}$ (centered around 0).  That is 
-\[
-\Pr[X=x] = \frac{1}{\sqrt{\frac{2}{\pi}}\sqrt{2\pi}}e^{-\frac{1}{2}{\frac{2}{\pi}x^2}}=\frac{1}{2}e^{-\pi x^2}
-\]
-Thus, $\Pr[X=0] =1/2$.
-One can easily design a procedure $\sample'$ that generates this distribution using a maximum of some number $\ell$ bits.
-Let $w_1,...,w_\ell$ be the bits that $\sample'$ takes as input.
-Then when $w_1=0$ the sampler outputs $0$.
-The generation for other values does not matter (only that generating some value takes $\ell$ bits).
-Thus, to generate $n$ samples we need at most $\ell n$ bits.
-However, there is a distribution with min-entropy $\Hoo(W)=(\ell -1) m$, that produces always produces the all zero error.
-This distribution has the first bit of each $W_i$ 0 and the remaining bits truly random.
-Thus, it seems impossible for our scheme to be secure for an arbitrary procedure \sample, but we will need to specify a specific \sample.
-Another possibility is to use a different distribution that looks like the normai distribution but requires a ``flatter'' number of coins to be used for each distribution.
-Is there a definition of an algorithm that uses the same number of random bits for each invocation?
-Would this be enough to get rid of this problem?
-\end{itemize}
-Questions: 
-\begin{enumerate}
-\item How we sample this error vector $\vect{e}$?  Can we do something other than Gaussian to remove some worries?
-\item Given the two biometric data which have small distance between each other, will we get the small distance between the error vector after sampling?
-\textbf{Solved, each dimension is sampled independently.  Thus, our distance blowup is only as large as the number of bits needed to sample each dimension.}
-\item When is LWE easy and when is LWE hard?  Are we going to be able to create a sufficient gap between these two cases?
-\item Does the parallel sampler of Peikert allow for the distance in two randomness being small, creating small output distance?
-\textbf{Solved, was trying to do the wrong thing.  Just Gaussian in each dimension.}
-\item Does the sampler of Peikert allow for nonuniform input distribution?
-\textbf{Solved, was trying to do the wrong thing (was trying to sample from lattice points, instead of adding noise around a lattice point).}
-\subitem If not how does applying an extractor change the distance of two distributions?
-\item How if it all can this be used concurrently?  Seems very one time right now.
-\item How efficient will our decoding procedure be?  Efficient enough for practical usage?
-\end{enumerate}
-
-\textbf{What security do we need: }
-}
-
-\ignore{
-\section{Robustness of LWE to error with min-entropy}
-\label{sec: lwe min-entropy}
-
-In this section we explore the robustness of the LWE assumption when the errors are drawn from a deficient distribution.
-We provide a short introduction to the Learning with Errors problem in \secref{sec:fuzzyCompLWE}.
-For a more complete introduction see the survey by Regev~\cite{regevLWEsurvey}.
-The tools presented in this section are used to show the security of the computational secure sketch presented \subsecref{subsec:fuzzyExtLWE}.
-This work is also of independent interest and can be viewed in a similar way to the work of Goldwasser et.
-al.~\cite{goldwasserRobustLWE}.
-In their work, they consider the robustness of an LWE instance $A, Ax+e$ where $x$ is sampled from a distribution that has min-entropy but is not uniform.
-They then use this result to show LWE-based cryptosystems are leakage-resilient.
-Our theorem statement will follow a similar structure to the theorem statement of Goldwasser et.
-al.
-so we first present their informal theorem:
-\begin{theorem}~(\cite[Theorem 1 (Informal)]{goldwasserRobustLWE})
-For any super-polynomial modulus $q=q(n)$, any $k\geq \log q$, and any distribution $\mathcal{D}=\{D\}_{n\in\mathbb{N}}$ over $\{0,1\}^n$ with min-entropy $k$ , the (non-standard) LWE assumption, where the secret is drawn from distribution $\mathcal{D},$ follows from the (standard) LWE assumption with secret size $\ell\overset{\Delta}=\frac{k-\omega(\log n)}{\log q}$ (where the ``error rate'' is super-polynomially small and the adversaries run in time $\poly(n)$).
-\end{theorem}
-
-Before considering high entropy error, we must be clear about what this means.
-The $x$ in an LWE instance is sampled uniformly from $\{0,q\}^n$, thus the sampling procedure requires $\lceil \log q\rceil\times n$ bits.
-However, $e$ is sampled from some error distribution $\chi$.
-$\chi$ is normally the normal distribution centered around $0$ with some variance $\sigma^2$ and then rounded to the nearest integer between $[-q/2, q/2]$.
-Sampling from a rounded normal distribution requires a variable number of random bits for each dimension.
-Indeed, using the normal distribution there are events with nonzero but negligible probability.
-These events necessarily take a large number of bits to sample.
-
-\textbf{This is internal discussion and needs to be taken care of before presentation:}  There are two ways to provide these bits: 1) break the random string into chunks where each chunk is as long as the maximum number of random bits needed 2) provide the random bits needed to each dimensions.
-One might hope that this problem is avoided by rounding to the nearest integer, but there is still some weight assigned to integers far from $0$.
-We could consider a distribution whose statistical distance to the normal distance is exponentially small and gives weight 0 to all integers outside some radius.
-
-For the moment we will ignore these problems and assume that a fixed number of bits is used to sample each dimension.
-This would be the case if we substituted the uniform distribution on a significantly smaller domain.
-\bnote{We need to be sure this produces a secure LWE instance}.
-
-Thus, we assume that there exists a $\sample$ that uses $\ell$ bits of randomness to produce an error term in one dimension.  We are now ready to present the LWE assumption:
-\begin{assumption}[Learning with Errors]
-Let $k$ be a security parameter and define $q=\poly(k)$\bnote{Do we want the poly or exponential case?}and $n = \poly( k)$.
-Let $x\overset{\$}\leftarrow \{0,q\}^n$.
-An LWE sample is of the form $(a,b) = (a, a_1x_1+...+a_nx_n+\sample(e) \mod q)$ where $a_1,...,a_n\overset{\$}\leftarrow\{0,q\}^n$ and $e\overset{\$}\leftarrow\{0,1\}^\ell$.
-The $(m,n,q,k)$-LWE assumption is that no algorithm given $m = \poly(k)$ LWE samples running in time $\poly(k)$ can recover $x$ with probability greater than negligible in $k$.
-\end{assumption}
-
-We then achieve our non-standard LWE assumption by sampling $e$ from a high-entropy distribution instead of the uniform distribution.
-
-\subsection{Affine min-entropy distributions}
-In the previous section, we investigated the security of the LWE assumption with deficient distributions.
-Namely, we saw that the LWE assumption for block-fixing sources was implied by the LWE assumption with fewer dimensions and samples.
-We now ask: what other types of min-entropy distributions can be shown to reduce to the LWE assumption?
-Using a reduction to standard LWE seems to require that the errors be considered homomorphically.
-This is because recovering the error terms would break LWE.
-Furthermore, these errors are first put through the \sample procedure, so this needs homomorphic properties as well.
-Thus, the class we can hope for in this reduction is a linear set of errors.
-
-Recall, a function, $f:D^n \mapsto R$, over field $K$ is a \textbf{linear transformation} if $\forall x,y\in D$ and $\forall a, b\in K, f(ax+by) = af(x) + bf(y)$.
-
-We will consider the \textbf{LWE assumption w/ linear sources}.
-That is, we consider an error distribution $E = E_1||...||E_k$ where $\Hoo(E) = qn$ and $E = \mathbf{T}(U_1||...||U_n)$ for rank $n$ matrix $\mathbf{T}: \Fq^n\mapsto \Fq^k$.
-\vspace{.1in}
-\begin{theorem}\label{thm:linearLWE}
-Let $k$ be a security parameter and define $q, n, m = \poly(k)$.
-Let $E$ be a linear source over $\{0,1\}^{\ell(m+\alpha)}$ where $\Hoo(E) \geq m\ell$.
-Then the $(m,n,q,k)$-LWE assumption where \sample is a linear transformation implies the $(m+\alpha, n+\alpha, q, k)$-LWE w/ linear sources assumption.
-\end{theorem}
-\begin{proof}
-The main difference between \thref{thm:blockLWE} and \thref{thm:linearLWE} is how we produce the errors terms.
-We will use the same basic strategy of introducing equations and randomizing, however, the equations will errors will now be involved in the randomization.
-As before, let $\mathcal{A}$ be an algorithm that accepts $m+\alpha$ LWE samples each of length $n+\alpha$ where the errors are generated $(E_1,..., E_{m+\alpha})^T = \mathbf{T} (U_1,..., U_m)^T$ for some matrix $\mathbf{T}$.
-Further, assume that $\mathcal{A}$ returns $x$ with noticeable probability.
-Our algorithm $\mathcal{A'}$ will make a single call to $\mathcal{A}$ and we will focus on properly preparing the LWE w/ linear sources instance.
-We use $A',A,C,D,F,G,b,b'$ with the same meaning as before.
-\end{proof}
-}
-
-\ignore{
-\subsection{LWE search reduction}
-\begin{proof}
-Let $\mathcal{A}$ be an algorithm that accepts $m+\alpha$ LWE samples each of length $n+\alpha$ where $\alpha$ of the equations have a known error (and the remainder of the errors are uniformly generated) and returns $x$ with noticeable probability.
-Denote this probability as $\epsilon$.
-We will show how to convert $\mathcal{A}$ into an algorithm $\mathcal{A'}$ that accepts $m$ LWE samples of length $n$ and returns $x'$ with noticeable probability.
-We begin by making the following assumptions for clarity:
-\begin{itemize}
-\item $\mathcal{A}$ asks for all $m+\alpha$ samples and asks for them simultaneously.  Since $\mathcal{A}$ has no effect on the samples, this does not limit $\mathcal{A}$'s power.
-\item For the known error samples, the added error is $0$.  It is clear in our reduction where the added error would be added, but exposition is clearer without these errors.
-\item The last $\alpha$ samples are the known error samples.  For other positioning of the known error samples, we can provide a permutation from our input, but this form is clearer.
-\end{itemize}
-The algorithm $\mathcal{A'}$ will make a single call to the algorithm $\mathcal{A}$ and thus the entire analysis will be showing that $\mathcal{A'}$ is able to properly prepare the instance that $\mathcal{A}$ is expecting and convert the result of $\mathcal{A}$ into a solution for the input of $\mathcal{A'}$.
-We will use the matrix notation for the remainder of the proof.
-Thus, the job of $\mathcal{A'}$ is to perform the following transformation:
-\begin{align*}
-\begin{array}{c | c}
-\mathcal{A'}\text{ receives:        } & \mathcal{A}\text{ expects: }\\\hline
-\left(A'\right) , b' = A' x' + e' & A = \left( \begin{array}{c | c}C & D \\ \hline F & G\end{array} \right), b=Ax+e
-\end{array}
-\end{align*}
-Where the matrices have the dimensions as shown in \figref{fig:matrixDimension}: 
-\begin{figure}[b]
-\[
-\begin{array}{c | c | c | c | c | c}
-A & A' & C & D & F & G\\\hline
-m\times n & (m+\alpha)\times( n+\alpha) & m\times n & m \times \alpha & \alpha \times n & \alpha \times \alpha
-\end{array}
-\]
-\caption{Dimensions of matrices in reduction.}
-\label{fig:matrixDimension}
-\end{figure}
-Thus, we have two major jobs, produce an augmented matrix $A$ that is a truly random matrix and to produce an augmented $b$ that given a solution for $x$ will yield a solution for $x'$.
-The code of $\mathcal{A'}$ is presented in \figref{fig:imperfectLWEreduction}.
-The main idea is to generate $\alpha$ new LWE samples and use $\alpha$ new variables to exactly solve these equations.
-These last $\alpha$ equations then have no errors and can be used to randomize the instance to produce a random matrix without augmenting the error in the $b$ vector.
-\begin{figure}
-\begin{enumerate}
-\item Input $A', b' = A'x' +e'$.
-\item Randomly generate $F$.
-\item Set $b = (b'_1,..., b'_n, \$, ..., \$)$ that is set the first $n$ values of $b$ equal to $b'$ and randomly generate the remainder.
-\item Initialize $A = \left(\begin{array}{c | c}C = A' & D = \mathbf{0}\\\hline F & G = I\end{array}\right)$.
-\item For $i=1...m+\alpha$, perform the following randomization:\label{step:randomizationSearch}
-\subitem Randomly generate $\gamma_{i,1},.., \gamma_{i,\alpha}$.
-\subitem Set $A_{i, \cdot} = A_{i, \cdot} +\sum_{j=1}^\alpha \gamma_{i,j}A_{m+j, \cdot}$.
-\subitem Set $b_i = b_i +\sum_{j=1}^\alpha \gamma_{i,j} b_j$.
-\item Run $\mathcal{A}$ on input $A, b$.
-\item Receive output $x$ from $\mathcal{A'}$
-\item Output $x' = x_1,..., x_n$.
-\end{enumerate}
-\caption{Code for $\mathcal{A'}$ to generate LWE w/ symbol fixing source from standard LWE instance}
-\label{fig:imperfectLWEreduction}
-\end{figure}
-\begin{claim}\label{cl:randomMatrix}
-The matrix $A$ generated after Step \ref{step:randomizationSearch} is a random matrix.
-\end{claim}
-\begin{proof}
-First, the submatrices $D, G$ are clearly truly random after step \ref{step:randomizationSearch}.
-For the matrix $D, D_{i, j}$ is assigned the value $\gamma_{(i,j-n)}$.
-Similarly, for the matrix $G$, each entry is assigned as $\gamma_{(i-n, j-n)}$.
-This is due to the original construction of the matrix $G$.
-Then before step \ref{step:randomizationSearch} the matrices $C, F$ are random submatrices ($C=A'$ by assumption and $F$ by construction).
-Thus, it remains to show that $C, F$ remain random after step 5.
-We consider a single row vector of $C$.
-The new row vector $C_{(i,\cdot)} = C_{(i,\cdot)} +\sum_{j=1}^\alpha \gamma_{i,j}F_{(j, \cdot)}$.
-That is, $C_{(i,\cdot)}$ is the sum of a random vector and a random linear combination independent vectors.
-That is, $C_{(i,\cdot)}$ is a random vector.
-
-Similarly, consider a single row vector $F$.
-The new row vector $F_{(i,\cdot)} = \sum_{j=1}^\alpha \gamma_{i+n,j}F_{(i,\cdot)}$ is a random linear combination of independent vectors and thus truly random (since all $\gamma$ are chosen independently and randomly).
-\bnote{I feel these claims are obvious but I would like to have a citation.}
-
-Thus, the entire matrix $A=\left(\begin{array}{c | c}C & D \\\hline F & G\end{array}\right)$ is a truly random matrix.  This completes the claim.
-\end{proof}
-\begin{claim}\label{cl:goodLWEinstance}
-The inputs $A, b$ provided to $\mathcal{A}$ is a random LWE w/ symbol fixing sources instance (provided that $A', b'$ was a random instance).
-\end{claim}
-\begin{proof}
-By \clref{cl:randomMatrix} $A$ provided to $\mathcal{A}$ is a truly random matrix.
-Thus, we must show that $b$ is of the proper form.
-That is, we must show there exists an $x$ such that $b_i = A_{(i , \cdot)} x + e_i$ for $i=1,...,m$ and $b_i = A_{(i, \cdot)} x$ for $i=m+1,...,m+\alpha$.
-
-By assumption there exists an $x'$ such that $A'x'+e' = b'$.
-Before step \ref{step:randomizationSearch}, we have added $\alpha$ equations as well as $\alpha$ unknowns.
-This means there no solutions have been eliminated.
-Namely, $x^*_i = x'_i$ for $i=1,...,n$ and $x^*_i = b_i - \sum_{j=1}^m F_{i, j} x_j'$ for $i=n+1,..., n+\alpha$.
-The case where $F$ does not have full row rank is also handled because the $G$ is the identity matrix and thus $F|G$ always has full row rank.
-Furthermore, note that the last $\alpha$ equations have no error.
-Thus, before step \ref{step:randomizationSearch} there exists a solution $x^*$ of the proper form.
-It remains to show that the randomization in step \ref{step:randomizationSearch} retains the solution $x^*$.
-
-The newly randomized system $A,b$ retains the same solution $x^*$  because we are not adding rows that have any error terms.
-More precisely, let $A^*, b^*$ be the system before randomization (where $A^*x^*+e^* = b^*$).
-Then for each row vector
-\begin{align*}
-A_{(i, \cdot)} &= A^*_{(i, \cdot)}+\sum_{j=1}^\alpha \gamma_{i, j} A^*_{(m+j, \cdot)}, \\b_i &= b^*_i + \sum_{j=1}^\alpha \gamma_{i,j}b_j^*.
-\end{align*}
-Thus, we have the following for all $i=1,..., m$:
-\begin{align*}
-A_{(i, \cdot)} x^* +e_i^*&= (A^*_{(i, \cdot)}+\sum_{j=1}^\alpha \gamma_{i, j} A^*_{(m+j, \cdot)})x^*+e_i^*\\
-&= A^*_{(i, \cdot)}x^* + \sum_{j=1}^\alpha \gamma_{i,j} A^*_{(m+j, \cdot)}x^*+e_i^*\\
-&=\left( A^*_{(i, \cdot)}x^* + e_i^*\right)+ \sum_{j=1}^\alpha \gamma_{i,j} A^*_{(m+j, \cdot)}x^* \\
-&= b^*_i + \sum_{j=1}^\alpha \gamma_{i,j}b_j^* = b_i
-\end{align*}
-
-The same equations follow without the term $e_i^*$ for $i=m+1,..., m+\alpha$.  
-Thus, $x^*$ is a solution to the randomized LWE instance as well.
-It remains to show that $x^*$ is a random vector.
-This is clear for $x^*_i, i=1,...,n$.
-For the remaining $x^*_i, i=m+1, ..., m+\alpha$ this follows since $x^*_i = b_i - \sum_{j=1}^m F_{i, j} x_j'$ where $b_i, F_{i, j}$ are randomly and independently chosen.
-This completes the claim.
-\end{proof}
-\begin{claim}
-If $x$ is a ``good'' solution output by $\mathcal{A}$ then $x'_i = x_i$ for $i=1,...,n$.  
-\end{claim}
-This claim follows by the analysis in \clref{cl:goodLWEinstance}.  The added equations and randomization do not affect the solution to the original $A', A'x'+e'$ instance provided.
-\begin{claim}
-$\mathcal{A'}$ outputs a ``good'' solution with probability only negligibly different  than the probability $\mathcal{A}$ outputs a good solution.
-\end{claim}
-The only time that $\mathcal{A'}$ does not produce the correct distribution is when the rows of $F$ are not linearly independent.  However, this occurs with negligible probability~\cite{something}.
-
-Thus, we have constructed an algorithm $\mathcal{A'}$ that is able to recover a secret $x'$ of a standard LWE instance by adding samples  and equations that have no error.
-Notice it was critical to add a variable for each new sample being provided to $\mathcal{A}$.
-Furthermore, adding a degree of freedom for each new sample also allowed for construction of an equation with no error.
-This completes the proof.
-
-\end{proof}
-
-\ignore{
-\section{Parameters for Construction~\ref{cons:LWESecureSketch} when $q=2^n$}
-\label{sec:parameters q expo}
-The results of~\lemref{lem:uniform LWE decision} only support $q = \poly(n)$.  However, the reductions of Peikert may extend~\lemref{lem:uniform LWE decision} to exponential $q$.
-
-$q = O(2^n)$.
-In this setting, we are no longer constrained by field size.
-We need $\rho$ be large enough that the underlying lattice problems are still hard to approximate within a $\tilde{O}(n^{5/2}m/\rho)$ factor.
-Unfortunately, even correcting a constant $c$ number of errors is difficult in this domain.
-Let $\gamma$ be the maximum approximation factor where the underlying lattices problems are still hard.
-Then, $\rho \leq \frac{n^{5/2}m}{\gamma}$.
-To correct $c$ errors we need that $\log q/\log \rho q \geq c$.
-That is,
-\begin{align*}
-c&\leq \frac{\log q}{\log \rho q}\\
-&\leq \frac{n}{\log \frac{n^{5/2}mq}{\gamma}}\\
-&\leq \frac{n}{\log \frac{n^{5/2}m2^n}{\gamma}}\\
-&\leq \frac{n}{n + \log n + \log m - \log \gamma}
-\end{align*}
-Ignoring the $\log n$ and $\log m$ terms this yields that:
-\begin{align*}
-c&\leq \frac{n}{n-\log \gamma}\\
-\frac{n(c-1)}{c}&\leq \log \gamma\\
-2^{n(c-1)/c} &\leq \gamma
-\end{align*}
-Thus, supporting even a constant number of errors for $q=2^n$ requires lattice problems are exponentially hard to approximate, which would be quite surprising.  
-}
-}
 \end{document}

### 2013-05-14 trunk/CompFuzzExt.tex
Took care some notes.

@@
 \newcommand{\A}{\mathcal{A}}
-\newcommand{\D}{\mathcal{D}}
 
@@
 
-Let $\D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.
+Let $D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.
 That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
@@
 Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
-Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
-That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
+Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
+That is, $D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
 We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
@@
 \[
-|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
+|\Pr[D(\vA, \vA\vx+\ve) = 1] - \Pr[D(\vA, \vu) =1]|> \epsilon.
 \]
@@
 Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-It suffices to build a ppt distinguisher $\D'$  where
+It suffices to build a distinguisher~(of polynomial size) $D'$  where
 \begin{align}
 \label{eq:block LWE dist}
-|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
+|\Pr[D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
 \end{align}
-We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
+We will make a single call to $D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
 
@@
 \subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
-\item Run $\D$ on input $\vA, \vb$.
-\item Output $\D$'s output.
+\item Run $D$ on input $\vA, \vb$.
+\item Output $D$'s output.
 \end{enumerate}
 \end{framed}
-\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
+\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
 \label{fig:perfectLWEreduction}
 \end{figure}
-The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
+The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
 \begin{claim}
@@
 $
-|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
+|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
 $
@@
 
-We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ prepares a random instance in this case. We show this in the following three claims: 
+We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a random instance in this case. We show this in the following three claims: 
 \begin{enumerate}
@@
 \label{cl:random ax+e}
-If $\D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
+If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
 \end{claim}
 \begin{proof}
-Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
+Denote by $\vx'$ the value such that $\vA'\vx'+\ve' = \vb'$.  
 Then partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
@@
 
-Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus,
-\begin{align*}
-&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
-&\, = \left| \Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
-&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
+Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $D'$ properly prepares the instance thus,
+\begin{align*}
+&\left|\Pr\left[D'(\vA', \vu') = 1\right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
+&\, = \left| \Pr\left[D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
+&\, =\left|\Pr\left[D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
 &\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon

### 2013-05-14 trunk/CompFuzzExt.tex
add some notes

@@
 \bnote{$\mathcal{I}$ is overloaded as the inverter in unpredictability entropy.  We okay?} 
+\xnote{change it to \class{Decode()}?}
 %Please refer to \consref{cons:informal construction} for the description of the construction.
@@
 %\label{subsec:LWE uniform error}
-Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over an interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
+Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over a small interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
 The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
@@
 \bnote{I'm confused, how can the decision version of lattice problems be hard to approximate?  Should it just be if GAPSVP and SIVP are hard to approximate?}
+\xnote{Approximating to decision version of GapSVP is to decision problem of SVP by creating the `gap'... don't think it's confusing...}
 Let $n$ be a security parameter.

### 2013-05-15 trunk/CompFuzzExt.tex
Cleaning up some notes

@@
 \newcommand{\dis}{\ensuremath{\mathsf{dis}}}
+\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
 
@@
 Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-Computational extractors~\cite{krawczyk2010cryptographic, dachman2012computational} have the same goal in the setting without errors.
+Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal in the setting without errors.
 One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.
@@
 Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^m$ a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
+A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
 of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), U_d, Y), U_m\times
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
 U_d \times Y) \le \epsilon$.
@@
 %\end{definition}
-
-\bnote{The definition of extractor above does not match this lemma.}
 \begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
 \label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
@@
 We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
-\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-\label{lem:unp extraction} 
-\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
-Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
+We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(as shown by \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
+%\footnote{See~\cite{barak-computational} for the definition of reconstruction extractor.}.   show that unpredictability entropy can be e.
+%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
+%\label{lem:unp extraction} 
+%\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
+%Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
 Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-\end{lemma}
-Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
+%\end{lemma}
+%Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
 Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
@@
 Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors.
+Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors.
 We provide an informal description below.
-\bnote{$\mathcal{I}$ is overloaded as the inverter in unpredictability entropy.  We okay?} 
-\xnote{change it to \class{Decode()}?}
 %Please refer to \consref{cons:informal construction} for the description of the construction.
@@
 %Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$.
-$\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$.
+$\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$.
 $m > n$ are parameters to be figured out later.
@@
 \item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
-\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
+\item Let $X = \decode_t(\vA, \vect{D})$\\
 \item Output $r = X_{1,...,n/2}$.
@@
 In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.
-Furthermore, this construction is only useful if $\mathcal{I}_t$ can be efficiently implemented.
-We demonstrate an efficient $\mathcal{I}_t$ that corrects a super-polynomial number of error patterns in polynomial time.
+Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.
+We demonstrate an efficient $\decode_t$ that corrects a super-polynomial number of error patterns in polynomial time.
 
@@
 \label{lem:uniform LWE decision}
-\bnote{I'm confused, how can the decision version of lattice problems be hard to approximate?  Should it just be if GAPSVP and SIVP are hard to approximate?}
-\xnote{Approximating to decision version of GapSVP is to decision problem of SVP by creating the `gap'... don't think it's confusing...}
 Let $n$ be a security parameter.
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-If the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
+If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
 \end{lemma}
@@
 Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+3\gamma}m$.
-Let $\mathcal{I}_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
+Let $\decode_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
 Let $W$ be a distribution over $\{0,1\}^{(\log \rho q)\times m}$\,.
@@
 %\item Parse $p$ as $(\vA, \vect{C})$
-%\item Set $x' = \mathcal{I}_t(\vA, \vect{C}-w') $. 
+%\item Set $x' = \decode_t(\vA, \vect{C}-w') $. 
 %\item Output $w = \vect{C}-\vA x'$.
@@
 %%\item Compute $E' \leftarrow \sample (w')$.
-%%\item Set $X' = \mathcal{I}_t(A, C-E') $. 
+%%\item Set $X' = \decode_t(A, C-E') $. 
 %%\item Output $sam_w = C-AX'$.
@@
 %\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
-\consref{cons:informal construction} is only useful if $\mathcal{I}_t$ can be efficiently implemented.  We now present a particular $\mathcal{I}_t$ and consider its efficiency:
+\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We now present a particular $\decode_t$ and consider its efficiency:
 
 \begin{construction}
-\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe inverter $\mathcal{I}_t$:
+\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
 \begin{enumerate}
@@
 
-$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.
+$\decode_t$ is an efficient decoding procedure when $t$ is small enough.
 We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
@@
 This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.
-We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
-$\mathcal{I}_t$ is efficient as long as $t$ is small enough.
+We consider the setting where the running time of $\decode_t$ grows with $t$.
+$\decode_t$ is efficient as long as $t$ is small enough.
 The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
@@
 More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
-%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
+%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
 %\label{lem:i t constant time}
@@
 Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.
-Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
+Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
 %\end{lemma}
-\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-2)$]
+\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d\log n (m/n-2)$]
 \label{lem:i t poly time}
@@
 Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.
-Then $\mathcal{I}_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
+Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
 \end{lemma}
-\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.
+\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3\log n)$.
 Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.
 We concentrate on the setting $t\leq d\log n(m/n-2)$.
-Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.
+Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
 
@@
 
-\subsection{Comparison with \prg based construction}
+\subsection{Comparison with computational extractor based construction}
 \label{sec:prg based comparison}
-In this section we to constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
+In this section, we constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using a computational extractor~\cite{krawczyk2010cryptographic} in place of the information-theoretic randomness extractor.
+One simple example is the extract-then-expand mechanism: a pseudorandom generator is applied to the output of a information-thereotic randomness extractor.
+%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
 This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.
@@
 Both techniques are able to produce a linear stretch on the entropy of the source.
-The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log t)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
+
+The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
 In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
+The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).
 The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.
@@
 \end{itemize}
-Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X'$ the random variable corresponding to the sample $x$ taken by $\mathcal{I}_t$.
+Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X'$ the random variable corresponding to the sample $x$ taken by $\decode_t$.
 We now show that $\mathcal{I}$ predicts $X$:
@@
 %\end{itemize}
-%We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
+%We define by $X$ the random variable corresponding to the sample $x'$ performed by $\decode_t$.
 %We now show that $\mathcal{I}$ predicts $Y$:
@@
 Steps 3 and 4 can be accomplished in time $n^3\log q +s_{ver}$.
-An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.
+An iteration of $\decode_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.
 The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
@@
 The minimum of $(1-1/n)^n$ is achieved at $n=2$ and it quickly converges to $1/e$.
-Thus, the expected number of iterations is at most $4$ giving the stated running time for $\mathcal{I}_t$.
+Thus, the expected number of iterations is at most $4$ giving the stated running time for $\decode_t$.
 %\end{proof}
@@
 Thus, a false matches occurs in step (5) with probability $e^{-\Omega(n)}$.
-This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\mathcal{I}_t$.
+This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\decode_t$.
 We consider the expected number of times step 2 is executed when $t\leq d\log n\left(\frac{m}{n}-1\right)$.
 Steps (3-5) can be accomplished in time $n^3\log q $.
-An iteration of $\mathcal{I}_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.
+An iteration of $\decode_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.
 The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $B_{i_1,...,i_{2n}}$ has no errors.
@@
 \label{cons:LWEFuzzyExtractor} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers, furthermore let $\chi$ be a distribution $\Fq$ that can be sampled with a fixed number of bits $s_{err}$.
-Let $\mathcal{I}_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
+Let $\decode_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
 Furthermore, let $\rext$ be a reconstructive extractor.
@@
 \item Compute $E' \leftarrow \sample (w')$.
-\item Set $X' = \mathcal{I}_t(A, C-E') $. 
+\item Set $X' = \decode_t(A, C-E') $. 
 \item Compute $r\leftarrow \rext (C-AX', seed)$.
@@
 Let $\rext: \chi^m \times\{0,1\}^\ell\rightarrow \{0,1\}^{k_{len}}\times \{0,1\}^\ell$ be an extractor with $(\log 1/\epsilon - \log 1/\delta, \delta)$-reconstruction $(\cons,\decons)$.
-Let $\mathcal{I}_t$ be an inverter as described in Construction~\ref{cons:LWEFuzzyExtractor} of size $s_{\mathcal{I}_t}$.
-Then Construction~\ref{cons:LWEFuzzyExtractor} is a $(\{0,1\}^{m\times s_{err}}, m\times s_{err}, k_{len}, t, s_{rec}, s/(|\cons|+|\decons|), 5\delta)$ computational fuzzy extractor where $s_{rec, t} = s_{\mathcal{I}_t}+ |\sample| + O(m\times n\times \log q) + |\rext|$.
+Let $\decode_t$ be an inverter as described in Construction~\ref{cons:LWEFuzzyExtractor} of size $s_{\decode_t}$.
+Then Construction~\ref{cons:LWEFuzzyExtractor} is a $(\{0,1\}^{m\times s_{err}}, m\times s_{err}, k_{len}, t, s_{rec}, s/(|\cons|+|\decons|), 5\delta)$ computational fuzzy extractor where $s_{rec, t} = s_{\decode_t}+ |\sample| + O(m\times n\times \log q) + |\rext|$.
 \end{theorem}

### 2013-05-15 CompFuzzExt.tex
write the talk abstract; edited Section 3

@@
 \newcommand{\dis}{\ensuremath{\mathsf{dis}}}
+\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
 
 \newcommand{\A}{\mathcal{A}}
-\newcommand{\D}{\mathcal{D}}
 
@@
 In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
-Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
+Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
+Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
 
@@
 \end{definition}
-This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
+This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
 For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
@@
 The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
-The formal statement is in the following Lemma.\bnote{I feel we should cite this.}
+The formal statement is in the following Lemma.\bnote{I feel we should cite this.}\lnote{You mean, say Lemma~\ref{lem:shannon to sketch} instead?
+No problem if you want to.}
 \begin{lemma}
@@
 In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
-A reasonable question to ask is whether a sketch could retain unpredictability of the source.
-We begin by defining conditional unpredictability entropy:
+However, HILL entropy is a strong notion.
+In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.
+We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax it similar to the way conditional HILL entropy was relaxed in the previous section).
 
@@
 \label{def:unp entropy}
-For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
+Let  $(W, S)$ be a pair of random variables.
+We say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
 \[
-\Pr[\mathcal{I}(Z) = Y ] \leq 2^{-k}
+\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
 .\]
 \end{definition}
-We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
-\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-\label{lem:unp extraction} 
-\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
-Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-\end{lemma}
-Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
-Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
-%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
-%That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
-The formal statement is below:
-\bnote{Should we list the stronger statement in the appendix or keep this for clarity?}
+
+We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
+hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
+Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a 
+\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
+
+Unfortunately, the conditional unpredictability entropy $\tilde{m}$ must decrease as $t$ increases, as the following theorem states.
+(The proof of the theorem, generalized to more metric spaces, is in \secref{sec:proof of imp unp entropy}.)
+
 \begin{theorem}
 \label{thm:imp of unp entropy}
-Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
+In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.
+Essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the code-offset construction\lnote{cite here, and is it the randomized construction or the deterministic one that we should use here?} applied to the best possible codes (e.g., random codes\lnote{cite performance of codes?}).
+Thus, unpredictability-entropy secure sketches cannot improve on the best possible information-theoretic entropy loss (at least for uniform inputs).
+However, because the best possible codes may not have efficient decoding, it is conceivable that unpredictability entropy secure sketch could achieve lower entropy loss than is possible with efficient information-theoretic sketches.
+
 This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
@@
 This means we cannot construct a good code out of the points of $Y$.
-In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy~(similar to the relaxed notion of HILL entropy in \defref{def:relaxed hill}).%Our bound is a result of the Hamming bound for the space.
+\lnote{I find the previous three sentences more confusing than helpful; do we really need them?
+should we reword or remove?} %Our bound is a result of the Hamming bound for the space.
 
@@
 The results get weaker as we consider sources with lower starter entropy.
-This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.
+This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed.
 This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.
-This same situation occurs when considering lower bounds for information-theoretic sketches.
+This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .
 
@@
 Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors.
+Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors.
 We provide an informal description below.
-\bnote{$\mathcal{I}$ is overloaded as the inverter in unpredictability entropy.  We okay?}
 %Please refer to \consref{cons:informal construction} for the description of the construction.
@@
 \label{lem:uniform LWE decision}
-\bnote{I'm confused, how can the decision version of lattice problems be hard to approximate?  Should it just be if GAPSVP and SIVP are hard to approximate?}
 Let $n$ be a security parameter.
@@
 
-\bnote{Why are our distinguishers in mathcal here?  There aren't in the body.}
 Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
-Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
-That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
+Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
+That is, $D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
 We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
@@
 Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-It suffices to build a distinguisher~(of polynomial size) $\D'$  where
+It suffices to build a distinguisher~(of polynomial size) $D'$  where
 \begin{align}
 \label{eq:block LWE dist}
-|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
+|\Pr[D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
 \end{align}
-We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
+We will make a single call to $D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
 
@@
 \label{cl:random ax+e}
-If $\D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
+If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
 \end{claim}

### 2013-05-16 CompFuzzExt.tex
Working on comparison with computational extractors

@@
 \documentclass[11pt]{article}
+%\documentclass{llncs}
 \def\shownotes{1}
@@
 \usepackage{graphicx}
-\usepackage{amssymb, amsmath, amsthm, amsfonts}
+\usepackage{amssymb, amsmath, amsfonts}
+\usepackage{amsthm}
 \usepackage{enumerate}
@@
 Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal in the setting without errors.
-One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.
-In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.
-This construction is only possible if the entropy losses due to a secure sketch and information-theoretic extraction leave enough truly random bits.
-We ask if a better solution is possible by making the entire process ``computational.''\bnote{Should add something about the Dana's result implying PRGs}
 
@@
 This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
+
+\textbf{Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal in the setting without errors.
+One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.
+In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.
+This construction is only possible if the entropy loss due to a secure sketch leaves enough truly random bits.
+%We ask whether it is possible to avoid this loss by making whole process ``computational.''
+We compare the two approaches in \secref{sec:prg based comparison}.
 
@@
 In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
+The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
 Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
@@
 %So, by indistinguishability, it must also succeed on $Y$.
- Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability $\rec (x',z) = x$ with high probability.
+ Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability, $\rec (x',y) = x$ with high probability.
  This means we can construct a large set $\mathcal{C}$ from the support of $X|y$.
@@
 hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
-Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a 
+Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
 \emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
@@
 In this section, we constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using a computational extractor~\cite{krawczyk2010cryptographic} in place of the information-theoretic randomness extractor.
-One simple example is the extract-then-expand mechanism: a pseudorandom generator is applied to the output of a information-thereotic randomness extractor.
+A simple example of a computational extractor is the \emph{extract-then-expand} mechanism: a pseudorandom generator is applied to the output of a information-thereotic randomness extractor.
 %using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
 This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.
-In particular, using the same hardness of approximating GAPSVP and SIVP, Applebaum et.
+Under the same hardness of approximating GAPSVP and SIVP, Applebaum et.
 al.
-use LWE to achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.
-Namely, consider $\vA$ as a public value, they show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.
+achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.
+They consider $\vA$ as a public value and show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.
 Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).
@@
 
-The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
+Thus, using the assumptions of \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.
+This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
+We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-then-cextract}.
+
+Any improvement in computational extractors yields an improvement to the \emph{sketch-then-cextract} construction of a computational fuzzy extractor.
+Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).
+Thus, improving computational fuzzy extractors may improvement computational extractors.
+
+The main advantage to analyzing the construction as a whole~(instead of \emph{sketch-then-cextract}) is that security need not depend on the decoding radius $t$.
+In \emph{sketch-then-cextract} paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
+As shown in \secref{sec:defCompFuzzyExtractors}, this value depends on bounds from error-correcting codes.
+In our construction, the decoding radius does not affect the security of the construction.
+The decoding radius only impacts the running time of the decoding algorithm.
+Conceivably, a computational fuzzy extractor could be built where only correctness depends on $t$~(not efficiency or security).
+%However, the construction of a computational fuzzy extractor by 
+%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
 In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
 The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).
+
+To summarize, the advantage of \consref{cons:informal construction} is that the security of our construction does not depend on the decoding radius $t$.  
 The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.

### 2013-05-16 trunk/CompFuzzExt.tex
minor fixing

@@
 In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
-Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
+The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
+Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
 
@@
 \label{def:unp entropy}
-For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
+Let  $(W, S)$ be a pair of random variables.
+We say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
 \[
-\Pr[\mathcal{I}(Z) = Y ] \leq 2^{-k}
+\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
 .\]
 \end{definition}
-We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(as shown by \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
-%\footnote{See~\cite{barak-computational} for the definition of reconstruction extractor.}.   show that unpredictability entropy can be e.
-%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-%\label{lem:unp extraction} 
-%\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
-%Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-%\end{lemma}
-%Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
-Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
-%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.
-%That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.
-The formal statement is below:
-\bnote{Should we list the stronger statement in the appendix or keep this for clarity?}
+
+We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
+hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
+Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
+\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
+
+Unfortunately, the conditional unpredictability entropy $\tilde{m}$ must decrease as $t$ increases, as the following theorem states.
+(The proof of the theorem, generalized to more metric spaces, is in \secref{sec:proof of imp unp entropy}.)
+
 \begin{theorem}
 \label{thm:imp of unp entropy}
-Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
+In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.
+Essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the code-offset construction\lnote{cite here, and is it the randomized construction or the deterministic one that we should use here?} applied to the best possible codes (e.g., random codes\lnote{cite performance of codes?}).
+Thus, unpredictability-entropy secure sketches cannot improve on the best possible information-theoretic entropy loss (at least for uniform inputs).
+However, because the best possible codes may not have efficient decoding, it is conceivable that unpredictability entropy secure sketch could achieve lower entropy loss than is possible with efficient information-theoretic sketches.
+
 This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
@@
 Let $X, Y$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
+It suffices to show that $\exists \ \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
 

### 2013-05-16 trunk/CompFuzzExt.tex
Working on Section 3.3

@@
 One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.
-In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.
+In particular, one technique is \emph{extract-then-expand}, where the output of a randomness extractor is stretched using a pseudorandom generator.
 This construction is only possible if the entropy loss due to a secure sketch leaves enough truly random bits.
@@
 In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
+Section 8.2The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
 Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
@@
 
-This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
+%This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
 The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.
@@
 The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  
-The results get weaker as we consider sources with lower starter entropy.
-This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed.
-This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.
+%The results get weaker as we consider sources with lower starter entropy.  
+This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed, and thus there is no (computational)~entropy loss.  
+%For example, we can not rule out a computational secure sketch with entropy loss for low entropy sources.
+%This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.  
 This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .
 
-Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the indistinguishable distribution.
-It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
+Both of lower bounds arise because \rec must function as an error-correcting code for many points of any indistinguishable distribution.
+It may be possible to avoid these bounds if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
 This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.
-An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).
+Such an algorithm is called a computational fuzzy conductor.
+See~\cite{KanukurthiR09} for the definition of a fuzzy conductor.
+To the best of our knowledge, a computational fuzzy conductor has not been defined in the literature, the natural definition is to replace the pseudorandomness condition in \defref{def:comp fuzzy extractor} with a HILL entropy requirement.
+
 Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).
@@
 Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
-\bnote{Should we mention the recent classical reduction here?}
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
@@
 
-Thus, using the assumptions of \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.
+Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.
 This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.

### 2013-05-16 trunk/CompFuzzExt.tex
almost done with section 3 and appendix C

@@
 We consider two different notions for computational entropy, and for both of them show that we can do essentially as well information-theoretically as computationally.
+\lnote{too strong?} Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on high-entropy sources.
 
@@
 unpredictability) entropy when given a source with $m$ bits of entropy.
+In particular, for the case of the Hamming metric and inputs that have full entropy, our results are as follows.
 In  \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
 In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-Section 8.2The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
-Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
+Dodis et al.
+\cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  construct sketches with essentially the same information-theoretic security\footnote{The security in  \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  is expressed in terms of entropy of the error rate; recall that $\log B_t(\cdot)\approx H_q(t/n)$, where $n$ is the number of symbols, $q$ is the alphabet size, and $H_q$ is the $q$-ary entropy function.} .
+
+In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
 
@@
 Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
 To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
@@
 Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]<\epsilon$.
+$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
 \end{definition}
@@
 The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
-The formal statement is in the following Lemma.\bnote{I feel we should cite this.}\lnote{You mean, say Lemma~\ref{lem:shannon to sketch} instead?
-No problem if you want to.}
+The formal statement of this result  can be expressed in the following Lemma (which is implicit in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}).
 \begin{lemma}
@@
 In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.
-Essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the code-offset construction\lnote{cite here, and is it the randomized construction or the deterministic one that we should use here?} applied to the best possible codes (e.g., random codes\lnote{cite performance of codes?}).
-Thus, unpredictability-entropy secure sketches cannot improve on the best possible information-theoretic entropy loss (at least for uniform inputs).
-However, because the best possible codes may not have efficient decoding, it is conceivable that unpredictability entropy secure sketch could achieve lower entropy loss than is possible with efficient information-theoretic sketches.
+As mentioned at the beginning of~\secref{sec:defCompFuzzyExtractors}, essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the randomized code-offset construction.
+However, it is conceivable that unpredictability entropy secure sketches could achieve lower entropy loss with greater efficiency for some parameter settings.
 
@@
 \[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))<\epsilon.
+\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\le \epsilon\, ,
 \]  
@@
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((W, \sketch(W)), (X, Y))<\epsilon$, we know $\Pr[D(X, Y) = 1]>1-\epsilon-t\delta$.
-By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]> 1- 2(\epsilon + t\delta)$.
+$\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.
+By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.
 
@@
 Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]> 1-2(\epsilon+t\delta).\]  
+\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
@@
 \label{sec:proof of imp unp entropy}
-Instead of proving \thref{thm:imp of unp entropy}, we will prove a stronger result based on a weaker form of entropy.
-This relaxed definition allows both the variable and the condition to be replaced.
-This is analogous to the relaxed HILL entropy~(see \defref{def:relaxed hill}).%Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}~(we provide a formulation of this notion in \defref{def:relaxed hill}).
-
-\begin{definition}
-\label{def:relaxed unp entropy}
-For a distribution $(W, S)$, we say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a joint distribution $X, Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size at most $s_{sec}$,
-\[
-\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
-.\]
-\end{definition}
-
-We will prove the result for a metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
+Instead of proving the result just for Hamming metric over $Z^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
 We now define this second condition:
@@
 Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
-Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is fixed~(this quantity is denoted by $B_t(\cdot)$).
-Let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
+Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least $B_t(\cdot)$.
+Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
 \begin{proof}
-Let $\mathcal{M}, \dis$ be a $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable metric space~(by procedures $\sample$ and $\neigh$ respectively).  
-Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.
-Let $X, Y$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
-It suffices to show that $\exists \ \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
-
-Let $B_t(x)$ denote the random variable of a random neighbor of distance at most $t$ from $x$.
-Recall, the algorithm $\neigh$ outputs neighbors at a fixed distance, the random variable $B_t(x)$ may not be efficiently computable, we use it as a random variable.
+Let $(X, Y)$ be two random variables such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq |\mathcal{M}| (1-\epsilon -t\delta) / |B_t(\cdot)|$.
+
+Let $B_t(x)$ denote the random variable representing a random neighbor of distance at most $t$ from $x$ (note that $B_t$ may not be efficiently samplable, because we are assuming only that a neighbor a fixed distance is efficiently samplable).
 We begin by showing that \rec must recover points of $X$.  
@@
 \begin{proof}
-Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
+Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.
+We construct the following distinguisher $D\in\mathcal{D}_{s_{sec}}$ (the distinguisher design is slightly complicated by the fact that we don't know at which particular distance $t'$ the recover procedure is most likely to fail, so we have to try all distances):
 \begin{itemize}
@@
 First note that $|D| = t( |\rec|+ s_{neigh} )$.
-Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
-If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist some $1\leq t'\leq t$ where this is true.
+Since $(\sketch, \rec)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
+If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist at least one $1\leq t'\leq t$ for which $\Pr[\rec(\neigh(X, t'), Y) = X] < 1-\epsilon -t\delta$.
 Then
@@
 \end{proof}
-We now consider the experiment $(x, y)\leftarrow (X, Y), x'\leftarrow B_t(x)$ and define the quantity $P_{x' , y,x} = \Pr[\rec(x', y) =x]$.  \clref{clm:y is recoverable} says that 
-\[
- \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in \mathcal{M}} \Pr[B_t(x) =x' | X = x] P_{x',  y,x} \geq 1-\epsilon - t\delta.
-\]
-We note that for any particular $x, x'$ such that $\dis(x, x')\leq t, \Pr[B_t(x) = x' | X=x] = 1/|B_t(\cdot)|$ and if $\dis(x, x')>t, \Pr[B_t(x) = x' | X=x] = 0$.
-Thus, for all $x, x', \Pr[B_t(x) = x' | X=x] \leq 1/|B_t(\cdot)|$.
-Now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
+
+Now define $\mathcal{I}$ as follows:
 \begin{itemize}
 \item Input $y\in\zo^*$.
-\item Sample $x\leftarrow \sample(\cdot)$.
-\item Output $\rec(x, s)$.
+\item Sample $x'\leftarrow \sample$.
+\item Output $\rec(x', y)$.
 \end{itemize}
-Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X'$ the random variable corresponding to the sample $x$ taken by $\decode_t$.
+Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$. 
 We now show that $\mathcal{I}$ predicts $X$:
 \begin{align*}
-2^{\tilde{m}}& = \Pr[\mathcal{I}(Y) = x] \\
-&= \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
-&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[X' = x' ]\Pr[\mathcal{I}(y) = x | X = x']\\
-&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[X' = x' ] P_{x', y, x}\\
-&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \frac{\Pr[X' = x']}{\Pr[B_t(x) = x' | X = x]}\Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
-&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \frac{1/|\mathcal{M}|}{1/|B_t(\cdot)|} \Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
-&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
+\Pr[\mathcal{I}(Y) = X] & = \\
+&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
+&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[\sample = x' ] \Pr[\rec(x', y) =x]\\
+&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x' \mathrm{ s. t. } \dis(x', x)\le t} \Pr[\sample = x']\Pr[\rec(x', y) =x]\\
+&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\mathrm{ s. t. } \dis(x', x)\le t} \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[B_t(x) = x'] \Pr[\rec(x', y) =x]\\
 &\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
 \end{align*}
-Finally converting to entropy, one has $\tilde{m}\leq \log |\mathcal{M}|-\log |B_t(\cdot)| - \log (1-\epsilon -t \delta)$.
+(the last step follows by  \clref{clm:y is recoverable}).
 \end{proof}

### 2013-05-16 CompFuzzExt.tex
working on the intro

@@
 A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
-The resulting secret key may be too short to be useful if the entropy loss is too high.
-Traditionally, fuzzy extractors are defined as information-theoretic objects.
+Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful Traditionally, fuzzy extractors are defined as information-theoretic objects.
 In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
 
-\bnote{This language is pretty clunky. Revise.}
-The main novel tool in constructing fuzzy extractors is the secure sketch.
-The secure sketch produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
-The security requirement is that $w$ has high min-entropy conditioned on $s$.
-The key $r$ is formed by applying a randomness extractor~\cite{nisan1993randomness} to $w$.
+We ask whether it is possible to obtain longer keys by considering
+computational, rather than information theoretic, security.
+
+\paragraph {Our Contributions}
+We first study whether improvements are possible by relaxing the definition of the main building block of fuzzy extractors, called \emph{secure sketch}.
+A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$ (The key $r$ is formed by the fuzzy extractor by applying a randomness extractor~\cite{nisan1993randomness} to $w$.)  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.
+
+The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
+Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
+We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
+%Furthermore, we have (asymptotic)~constructions that meet these bounds.
+
+Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
+Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
+We show lower bounds on the unpredictability loss of sketches.
+We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
+
+Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.
+To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.
+\lnote{stopped here}
+
 %Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
@@
 
-\paragraph {Our Contributions}
 To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.
@@
 We show that some entropy loss is necessary for secure sketches.
-The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%Furthermore, we have (asymptotic)~constructions that meet these bounds.
-
-Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
-Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
-We show lower bounds on the unpredictability loss of sketches.
-We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
-
-Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.
-To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.
 
@@
 unpredictability) entropy when given a source with $m$ bits of entropy.
+In particular, for the case of the Hamming metric and inputs that have full entropy, our results are as follows.
 In  \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
 In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.
-Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
+Dodis et al.
+\cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  construct sketches with essentially the same information-theoretic security\footnote{The security in  \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  is expressed in terms of entropy of the error rate; recall that $\log B_t(\cdot)\approx H_q(t/n)$, where $n$ is the number of symbols, $q$ is the alphabet size, and $H_q$ is the $q$-ary entropy function.} .
+
+In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
 
@@
 In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.
-Essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the code-offset construction\lnote{cite here, and is it the randomized construction or the deterministic one that we should use here?} applied to the best possible codes (e.g., random codes\lnote{cite performance of codes?}).
-Thus, unpredictability-entropy secure sketches cannot improve on the best possible information-theoretic entropy loss (at least for uniform inputs).
-However, because the best possible codes may not have efficient decoding, it is conceivable that unpredictability entropy secure sketch could achieve lower entropy loss than is possible with efficient information-theoretic sketches.
-
-This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
+As mentioned at the beginning of~\secref{sec:defCompFuzzyExtractors}, essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the randomized code-offset construction.
+However, it is conceivable that unpredictability entropy secure sketches could achieve lower entropy loss with greater efficiency for some parameter settings.
+
+%This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
 The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.
@@
 Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
-Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is fixed~(this quantity is denoted by $B_t(\cdot)$).
-Let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
+Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least $B_t(\cdot)$.
+Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
 \begin{proof}
-Let $\mathcal{M}, \dis$ be a $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable metric space~(by procedures $\sample$ and $\neigh$ respectively).  
-Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.
-Let $X, Y$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
-
-Let $B_t(x)$ denote the random variable of a random neighbor of distance at most $t$ from $x$.
-Recall, the algorithm $\neigh$ outputs neighbors at a fixed distance, the random variable $B_t(x)$ may not be efficiently computable, we use it as a random variable.
+Let $(X, Y)$ be two random variables such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
+It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq |\mathcal{M}| (1-\epsilon -t\delta) / |B_t(\cdot)|$.
+
+Let $B_t(x)$ denote the random variable representing a random neighbor of distance at most $t$ from $x$ (note that $B_t$ may not be efficiently samplable, because we are assuming only that a neighbor a fixed distance is efficiently samplable).
 We begin by showing that \rec must recover points of $X$.  

### 2013-05-17 CompFuzzExt.tex
finished working on intro

@@
 %\geometry{landscape}                % Activate for for rotated page geometry
-\usepackage[parfill]{parskip}    
+%\usepackage[parfill]{parskip}    
 \usepackage{graphicx}
@@
 
-\paragraph {Our Contributions}
-We first study whether improvements are possible by relaxing the definition of the main building block of fuzzy extractors, called \emph{secure sketch}.
-A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$ (The key $r$ is formed by the fuzzy extractor by applying a randomness extractor~\cite{nisan1993randomness} to $w$.)  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.
-
-The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
+\paragraph {Our Negative Results}
+We first study whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.
+A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
+The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.
+This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors get random strings from strings with conditional min-entropy.
+
+The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
+Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.
+Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
 %Furthermore, we have (asymptotic)~constructions that meet these bounds.
@@
 Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
-Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
-We show lower bounds on the unpredictability loss of sketches.
-We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
-
-Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.
-To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.
-\lnote{stopped here}
-
-%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
+This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
+Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$, which (for high-entropy sources of $w$ over the Hamming metric) matches the best information-theoretic security sketches.
+
+%%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
 When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high.
-The minimum entropy loss for secure sketches has been quantified in past work.
+%The minimum entropy loss for secure sketches has been quantified in past work.
 Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08},
-%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
-the entropy loss of a secure sketch that can reconcile $t$ errors
- %with high probability 
- is bounded by the redundancy of
-the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
+%%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
+%the entropy loss of a secure sketch that can reconcile $t$ errors
+% %with high probability 
+% is bounded by the redundancy of
+%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
 Constructions of fuzzy extractors that use a secure sketch inherit this bound.
-%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-
-To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.
-Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.
-
-On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.
-We show that some entropy loss is necessary for secure sketches.
+%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
 
@@
 
-By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{As noted above, using a computational extractor, in place of a information-theoretic extractor, allows a lossless construction.
-However, this approach requires the computational extractor to work on the remaining entropy after the secure sketch.
-We compare the two approaches in \secref{sec:prg based comparison}}.
+\paragraph {Our Postive Results}
+
+Both of the above negative results arise because a secure sketch functions like a decoder of an error-correcting code.
+To avoid them, we give up on building computational secure sketches and focus directly on the entropy loss in fuzzy extractors.
+Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.
+
+By considering this computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$.
 % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
@@
 Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.
-To apply the LWE assumption, we correct errors of a random linear code which limits our decoding algorithm to reconciling a logarithmic number of differences.
+To apply the LWE assumption, we correct errors of a random linear code, which limits our decoding algorithm to reconciling a logarithmic number of differences.
 
@@
 
-\textbf{Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal in the setting without errors.
-One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.
-In particular, one technique is \emph{extract-then-expand}, where the output of a randomness extractor is stretched using a pseudorandom generator.
-This construction is only possible if the entropy loss due to a secure sketch leaves enough truly random bits.
+\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.
+They can be constructed, for example, by applying to pseudorandom generator to the output of an information-theoretic extractor.
+One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.
+However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
 %We ask whether it is possible to avoid this loss by making whole process ``computational.''

### 2013-05-17 trunk/CompFuzzExt.tex
edited abstract

@@
 \begin{abstract} 
-%\lnote{This is an old abstract, no longer correct}
-Fuzzy extractors derive cryptographically strong keys from noisy sources.
-They are traditionally built by combining a secure sketch and a randomness extractor.
-Secure sketches remove noise from the source while revealing little information about the source.
-Randomness extractors convert high entropy sources to the uniform distribution.
-%Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.
-The minimal entropy loss
-%One-message information reconciliation protocols called secure sketches remove noise
-%from secrets without revealing too much about them.  They are a crucial ingredient in
-%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.
-
-Secure sketches necessarily reveal some information about the noisy secret.
-% and thus the key derived by fuzzy extractors has lower entropy than the source.  
-The minimal entropy loss is dictated by bounds on error-correcting codes.  
-Fuzzy extractors constructed using secure sketches suffer a similar entropy loss.  This entropy loss decreases the length of the derived key.  
-%suffer from similar bounds imposed by coding theory.
-
-We ask whether these bounds can be overcome by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors.
-%The answer we provide an answer for both secure sketches and fuzzy extractors.
-The answer to this question is mixed, For secure sketches the answer is no, and for fuzzy extractors the answer is yes.
+Fuzzy extractors derive strong keys from noisy sources.  Their
+security is defined information-theoretically, which limits the length
+of the derived key, sometimes making it too short to be useful. We ask
+whether it is possible to obtain longer keys by considering
+computational security, and show the following.
+
 \begin{itemize}
-\item \textbf{Secure Sketches:} We show that a secure sketch that retains a large amount of HILL pseudo entropy implies a secure sketch which retains a similar amount of information-theoretic entropy.
-We also consider a weaker computational notion of security, the unpredictability of a source conditioned on output of the secure sketch.
-We show that in order to correct $t$ errors, the unpredictability of a source must decrease with the volume of a ball of radius $t$.
-\item \textbf{Fuzzy Extractors:}  We show these impossibility results can be overcome by analyzing fuzzy extractors directly.
-Namely, we show how to build a \emph{lossless} computational fuzzy extractor for uniform sources and certain other sources of high entropy~(namely, symbol-fixing sources, where each dimension is either uniform or fixed), based on the hardness of the Learning with Errors~(LWE) problem.
-This construction requires us to show that the decision version of LWE is secure when a small number of dimension has no error---a result that may be of independent interest.
+\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
+achieved using an information reconciliation component called ``secure
+sketch.'' The security of this component, which directly affects the
+length of the resulting key, is subject to lower bounds from coding
+theory.  We show that, even when defined computationally, secure
+sketches are still subject to the same lower bounds. Specifically, we consider
+two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy.
+For both cases we show  that computational secure sketches cannot outperform information-theoretic ones in the case of high-entropy Hamming metric sources.
+
+\item\textbf{Positive Result:} We show that the negative result can be overcome by
+analyzing computational fuzzy extractors directly.  Namely, we show
+how to build a computational fuzzy extractor whose output key length
+equals the entropy of the source (this is impossible in the
+information-theoretic setting). Our construction is based on the
+hardness of the Learning with Errors (LWE) problem, and is secure when
+the noisy source is uniform or symbol-fixing (that is, each dimension
+is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
+that the decision version of LWE is secure even when a small number of
+dimensions has no error.
 \end{itemize}
-%mixed, and building them based on the Learning with Errors (LWE) problem.  We thus obtain the first secure sketch with no loss in entropy.   More specifically, our contributions are as follows:
-%
-%\begin{itemize}
-%\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.
-We do so by demonstrating that a secure sketch defined via HILL pseudoentropy is subject to the same coding-based  bounds as the information-theoretic secure sketch.
-We then find a different relaxation, using unpredictability entropy, and show that it can be used to construct computational fuzzy extractors.
-%
-%
-%\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.
-This construction requires us to show that the decision version of LWE is secure when a small number of dimensions have no error---a result that may be of independent interest.
-%\end{itemize}
 \end{abstract}
@@
 A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
-The resulting secret key may be too short to be useful if the entropy loss is too high.
-Traditionally, fuzzy extractors are defined as information-theoretic objects.
+Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful Traditionally, fuzzy extractors are defined as information-theoretic objects.
 In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
 
-\bnote{This language is pretty clunky. Revise.}
-The main novel tool in constructing fuzzy extractors is the secure sketch.
-The secure sketch produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
-The security requirement is that $w$ has high min-entropy conditioned on $s$.
-The key $r$ is formed by applying a randomness extractor~\cite{nisan1993randomness} to $w$.
-%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
+We ask whether it is possible to obtain longer keys by considering
+computational, rather than information theoretic, security.
+
+\paragraph {Our Negative Results}
+We first study whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.
+A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
+The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.
+This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors get random strings from strings with conditional min-entropy.
+
+The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
+Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.
+Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
+%Furthermore, we have (asymptotic)~constructions that meet these bounds.
+
+Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
+This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
+Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$, which (for high-entropy sources of $w$ over the Hamming metric) matches the best information-theoretic security sketches.
+
+%%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
 When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high.
-The minimum entropy loss for secure sketches has been quantified in past work.
+%The minimum entropy loss for secure sketches has been quantified in past work.
 Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08},
-%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
-the entropy loss of a secure sketch that can reconcile $t$ errors
- %with high probability 
- is bounded by the redundancy of
-the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
+%%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
+%the entropy loss of a secure sketch that can reconcile $t$ errors
+% %with high probability 
+% is bounded by the redundancy of
+%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
 Constructions of fuzzy extractors that use a secure sketch inherit this bound.
-%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-
-\paragraph {Our Contributions}
-To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.
-Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.
-
-On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.
-We show that some entropy loss is necessary for secure sketches.
-The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%Furthermore, we have (asymptotic)~constructions that meet these bounds.
-
-Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
-Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.
-We show lower bounds on the unpredictability loss of sketches.
-We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
-
-Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.
-To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.
+%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
 
@@
 In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.
-We consider two different notions for computational entropy, and for both of them show that we can do essentially as well information-theoretically as computationally.
-\lnote{too strong?} Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on high-entropy sources.
+We consider two different notions for computational entropy, and for both of them show that corresponding secure sketches are subject to the same upper bounds as those for information-theoretic secure sketches.
+Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help.
 
@@
 In this section we describe our main construction.
-In this section, we consider only a uniform source $W$, we consider other distributions in \secref{sec:LWE block fixing sources}.
+In this section, we consider only a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.
 Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors.
-We provide an informal description below.
-%Please refer to \consref{cons:informal construction} for the description of the construction.
+Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \label{sec:time main construction}).
 
@@
 \section{\consref{cons:informal construction} with Nonuniform Sources}
+\lnote{what's up with this section/subsection thing?}
 \subsection{\consref{cons:informal construction} with Symbol Fixing Sources}

### 2013-05-17 trunk/CompFuzzExt.tex
Small changes to abstract

@@
 \item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
-achieved using an information reconciliation component called ``secure
+achieved using an information reconciliation component called a ``secure
 sketch.'' The security of this component, which directly affects the
@@
 theory.  We show that, even when defined computationally, secure
-sketches are still subject to the same lower bounds. Specifically, we consider
+sketches are still subject to lower bounds from coding theory. Specifically, we consider
 two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy.
-For both cases we show  that computational secure sketches cannot outperform information-theoretic ones in the case of high-entropy Hamming metric sources.
+For both cases we show  that computational secure sketches cannot outperform the best information-theoretic secure sketches in the case of high-entropy Hamming metric sources.
 
@@
 
-\bnote{There needs to be more linking language here.}
-It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).
+%\bnote{There needs to be more linking language here.}
+%It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).
 In the next section, we show this paradigm is difficult to realize.

### 2013-05-17 CompFuzzExt.tex
clean up

@@
 \begin{abstract} 
-%\lnote{This is an old abstract, no longer correct}
-Fuzzy extractors derive cryptographically strong keys from noisy sources.
-They are traditionally built by combining a secure sketch and a randomness extractor.
-Secure sketches remove noise from the source while revealing little information about the source.
-Randomness extractors convert high entropy sources to the uniform distribution.
-%Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.
-The minimal entropy loss
-%One-message information reconciliation protocols called secure sketches remove noise
-%from secrets without revealing too much about them.  They are a crucial ingredient in
-%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.
-
-Secure sketches necessarily reveal some information about the noisy secret.
-% and thus the key derived by fuzzy extractors has lower entropy than the source.  
-The minimal entropy loss is dictated by bounds on error-correcting codes.  
-Fuzzy extractors constructed using secure sketches suffer a similar entropy loss.  This entropy loss decreases the length of the derived key.  
-%suffer from similar bounds imposed by coding theory.
-
-We ask whether these bounds can be overcome by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors.
-%The answer we provide an answer for both secure sketches and fuzzy extractors.
-The answer to this question is mixed, For secure sketches the answer is no, and for fuzzy extractors the answer is yes.
+Fuzzy extractors derive strong keys from noisy sources.  Their
+security is defined information-theoretically, which limits the length
+of the derived key, sometimes making it too short to be useful. We ask
+whether it is possible to obtain longer keys by considering
+computational security, and show the following.
+
 \begin{itemize}
-\item \textbf{Secure Sketches:} We show that a secure sketch that retains a large amount of HILL pseudo entropy implies a secure sketch which retains a similar amount of information-theoretic entropy.
-We also consider a weaker computational notion of security, the unpredictability of a source conditioned on output of the secure sketch.
-We show that in order to correct $t$ errors, the unpredictability of a source must decrease with the volume of a ball of radius $t$.
-\item \textbf{Fuzzy Extractors:}  We show these impossibility results can be overcome by analyzing fuzzy extractors directly.
-Namely, we show how to build a \emph{lossless} computational fuzzy extractor for uniform sources and certain other sources of high entropy~(namely, symbol-fixing sources, where each dimension is either uniform or fixed), based on the hardness of the Learning with Errors~(LWE) problem.
-This construction requires us to show that the decision version of LWE is secure when a small number of dimension has no error---a result that may be of independent interest.
+\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
+achieved using an information reconciliation component called a ``secure
+sketch.'' The security of this component, which directly affects the
+length of the resulting key, is subject to lower bounds from coding
+theory.  We show that, even when defined computationally, secure
+sketches are still subject to lower bounds from coding theory. Specifically, we consider
+two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy.
+For both cases we show  that computational secure sketches cannot outperform the best information-theoretic secure sketches in the case of high-entropy Hamming metric sources.
+
+\item\textbf{Positive Result:} We show that the negative result can be overcome by
+analyzing computational fuzzy extractors directly.  Namely, we show
+how to build a computational fuzzy extractor whose output key length
+equals the entropy of the source (this is impossible in the
+information-theoretic setting). Our construction is based on the
+hardness of the Learning with Errors (LWE) problem, and is secure when
+the noisy source is uniform or symbol-fixing (that is, each dimension
+is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
+that the decision version of LWE is secure even when a small number of
+dimensions has no error.
 \end{itemize}
-%mixed, and building them based on the Learning with Errors (LWE) problem.  We thus obtain the first secure sketch with no loss in entropy.   More specifically, our contributions are as follows:
-%
-%\begin{itemize}
-%\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.
-We do so by demonstrating that a secure sketch defined via HILL pseudoentropy is subject to the same coding-based  bounds as the information-theoretic secure sketch.
-We then find a different relaxation, using unpredictability entropy, and show that it can be used to construct computational fuzzy extractors.
-%
-%
-%\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.
-This construction requires us to show that the decision version of LWE is secure when a small number of dimensions have no error---a result that may be of independent interest.
-%\end{itemize}
 \end{abstract}
@@
 
-\section{\consref{cons:informal construction} with Nonuniform Sources}
-\subsection{\consref{cons:informal construction} with Symbol Fixing Sources}
+\section{Computational Fuzzy Exactor with Nonuniform Sources}
 \label{sec:LWE block fixing sources}
@@
 
-%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
 \begin{proof}
@@
 If the blocks are fixed to some other value the reduction is essentially the same.
-
-%It should be clear to the reader where the reduction differs for another block fixing source.\lnote{I don't like the phrasing; maybe we should say that if the blocks are fixed to some non-0 value, the reduction is essentially the same}
 
@@
 \item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
-%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
 \item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.

### 2013-05-17 CompFuzzExt.tex
working on intro and section 4

@@
 
-By considering this computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$.
-% without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
-Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
+By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$.
+It is uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.
+First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$.
+Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} to get a long $r$ out.
+
+Specifically,  we use the  recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012}, which shows the hardness of decoding random linear codes when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
+This allows us to use $w$ as the error vector, assuming it is uniform.
+We also use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009},  which says that LWE has many hardcore bits, to hide $r$.
+
+Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.
+Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor.
+
 %We show that this relaxation of the security requirement is  useful.
@@
 %\lnote{it would be good to find another application}
-Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.
-To apply the LWE assumption, we correct errors of a random linear code, which limits our decoding algorithm to reconciling a logarithmic number of differences.
-
-The recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the hardness of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-This allows us to directly use our source $w$ as the LWE error vector.
-To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
-We are able to relax this limitation and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
-This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
+
+We are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
+This relaxation follows from new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
+See Section~\ref{}.
 

### 2013-05-17 trunk/CompFuzzExt.tex
clean up 5
further edits to intro -- in light of the talk

@@
 \paragraph {Our Negative Results}
-We first study whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.
+We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.
 A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
@@
 This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors get random strings from strings with conditional min-entropy.
+We call this the ``sketch-and-extract'' construction.
 
@@
 
-By considering this computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$.
-% without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).
-Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
+By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$.
+It is uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.
+First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$.
+Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} to get a long $r$ out.
+
+Specifically,  we use the  recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012}, which shows the hardness of decoding random linear codes when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
+This allows us to use $w$ as the error vector, assuming it is uniform.
+We also use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009},  which says that LWE has many hardcore bits, to hide $r$.
+
+Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.
+Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor.
+If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.
+
 %We show that this relaxation of the security requirement is  useful.
@@
 %\lnote{it would be good to find another application}
-Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.
-To apply the LWE assumption, we correct errors of a random linear code, which limits our decoding algorithm to reconciling a logarithmic number of differences.
-
-The recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the hardness of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-This allows us to directly use our source $w$ as the LWE error vector.
-To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
-We are able to relax this limitation and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
-This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
+
+In \secref{sec:LWE block fixing sources}, we are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
+This relaxation follows from our results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
 
@@
 They can be constructed, for example, by applying to pseudorandom generator to the output of an information-theoretic extractor.
-One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.
+One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.
 However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
@@
 
-%In \secref{sec:defCompFuzzyExtractors} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch?
+%In \secref{sec:impossCompSecSketch} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch?
 It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
@@
 \section{Impossibility of Computational Secure Sketches}
-\label{sec:defCompFuzzyExtractors}
+\label{sec:impossCompSecSketch}
 In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.
@@
 In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.
-As mentioned at the beginning of~\secref{sec:defCompFuzzyExtractors}, essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the randomized code-offset construction.
+As mentioned at the beginning of~\secref{sec:impossCompSecSketch}, essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the randomized code-offset construction.
 However, it is conceivable that unpredictability entropy secure sketches could achieve lower entropy loss with greater efficiency for some parameter settings.
@@
 Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \label{sec:time main construction}).
+Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).
 
@@
 In \emph{sketch-then-cextract} paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
-As shown in \secref{sec:defCompFuzzyExtractors}, this value depends on bounds from error-correcting codes.
+As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.
 In our construction, the decoding radius does not affect the security of the construction.
@@
 
-\section{\consref{cons:informal construction} with Nonuniform Sources}
-\lnote{what's up with this section/subsection thing?}
-\subsection{\consref{cons:informal construction} with Symbol Fixing Sources}
+\section{Computational Fuzzy Exactor with Nonuniform Sources}
 \label{sec:LWE block fixing sources}
@@
 %In this sections we provide some further definitions of computational entropy.
-HILL entropy is defined in \secref{sec:defCompFuzzyExtractors}.
+HILL entropy is defined in \secref{sec:impossCompSecSketch}.
 HILL entropy generalizes the notion of indistinguishability.

### 2013-05-17 trunk/CompFuzzExt.tex
Changes to decoding talk

@@
 %\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
-\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We now present a particular $\decode_t$ and consider its efficiency:
+\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.
+We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.
+We present a simple $\decode_t$.
+Replacing our algorithm  with a state of the art algorithm will only increase our correcting capability and improve \consref{cons:informal construction}.
 

### 2013-05-17 trunk/CompFuzzExt.tex
4.6 Construction...

@@
 \item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
-Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
-\item Compute $X' = (\vA')^{-1}B'$.  If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
+If no such rows exist go to step (2).
+\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows.
+Compute $X' = (\vA')^{-1}B'$.
+If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
 \item Output $X'$.
@@
 We believe this statement is of interest outside our setting.
-\thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known error.
-Roughly, we need the number of variables to be security parameter larger than the number of equations with known error.
+\thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known errors.
+Roughly, we need the number of variables larger than the number of equations with known error by letting the number of variables be the security parameter.
 Providing a single sample with no error ``fixes'' at most a single variable.

### 2013-05-17 CompFuzzExt.tex
messed with 4-4.2

@@
 Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor.
+If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.
 
@@
 
-We are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
-This relaxation follows from new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
-See Section~\ref{}.
+In \secref{sec:LWE block fixing sources}, we are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
+This relaxation follows from our results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
 
@@
 Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.
-Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
+Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the sketch-and-extract construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
 %Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
@@
 hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
-Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
+Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
 \emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
@@
 Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \label{sec:time main construction}).
+Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).
 
 \begin{construction}
-Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
+Let $n$ be a security parameter and let $m> n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
 Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
@@
 Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.
-We demonstrate an efficient $\decode_t$ that corrects a super-polynomial number of error patterns in polynomial time.
 
@@
  %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
-We describe conditions for efficient decoding in \secref{sec:time main construction}.
+We describe one possible polynomial-time $\decode_t$ (which corrects more errors than is possible by exhaustive search) in \secref{sec:time main construction}.
 In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.
-In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output~(this is replacing the randomness extractor with a computational extractor).
+In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a sketch-and-extract approach (\lemref{lem:fuzzy ext construction}) instantiated with a computational extractor.
 
@@
 \label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For positive integers $n$ and $q \ge 2$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
+The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integers $n$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
 %The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.
@@
 \begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ and $q = q(n) = \poly(n)$ be integers.
+Let $m = m(n) = \poly(n)$ be an integer $q = q(n) = \poly(n)$ be a prime.
 The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
@@
 We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If $\distLWE_{n, m, q, \chi}$ is secure for all $s_{sec} = \poly(n), \epsilon  = 1/\poly(n)$ we say it is \emph{secure}.
+If $\distLWE_{n, m, q, \chi}$ is secure for all $s_{sec} = \poly(n), \epsilon  = 1/\poly(n)$, we say it is \emph{secure}.
 \end{definition}
 
-Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
+Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.
+Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
@@
 
-We cannot immediately adapt the construction in \consref{cons:informal construction} to the $\LWE$ problem.
-Standard formulations of $\LWE$ require the error term to come from the discretized Gaussian distribution.
+The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
 %\subsection{LWE with uniform errors}
 %\label{subsec:LWE uniform error}
-Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over a small interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
+Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
 The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
@@
 $\decode_t$ is an efficient decoding procedure when $t$ is small enough.
-We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
+We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$.
+Furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
 The second condition is to ensure that there are few false positives in step (5).
@@
 This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
-We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-then-cextract}.
-
-Any improvement in computational extractors yields an improvement to the \emph{sketch-then-cextract} construction of a computational fuzzy extractor.
+We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-and-comp-extract}.
+
+Any improvement in computational extractors yields an improvement to the sketch-and-comp-extract construction of a computational fuzzy extractor.
 Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).
@@
 
-The main advantage to analyzing the construction as a whole~(instead of \emph{sketch-then-cextract}) is that security need not depend on the decoding radius $t$.
-In \emph{sketch-then-cextract} paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
-As shown in \secref{sec:defCompFuzzyExtractors}, this value depends on bounds from error-correcting codes.
+The main advantage to analyzing the construction as a whole~(instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.
+In sketch-and-comp-extract paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
+As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.
 In our construction, the decoding radius does not affect the security of the construction.

### 2013-05-17 CompFuzzExt.tex
revising introduction

@@
 %As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
+Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and traditionally are defined as information-theoretic objects.
 The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.
+In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
 A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
-Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful Traditionally, fuzzy extractors are defined as information-theoretic objects.
-In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
+Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.
 
@@
 We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.
-A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
+A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
 The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.
-This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors get random strings from strings with conditional min-entropy.
-We call this the ``sketch-and-extract'' construction.
+This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors produce random strings from strings with conditional min-entropy.
+We call this the \emph{sketch-and-extract} construction.
 
@@
 This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
-Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$, which (for high-entropy sources of $w$ over the Hamming metric) matches the best information-theoretic security sketches.
+Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
+For high-entropy sources of $w$ over the Hamming metric, this bound matches the best information-theoretic security sketches.
 
@@
 By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$.
-It is uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.
+Our construction is for the Hamming metric and uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.
 First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$.
-Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} to get a long $r$ out.
+Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.
 
@@
 If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.
+Given the hardness of decoding random linear codes~\cite{berlekamp1978}, we do not expect significant improvement in error-tolerance of our construction.
 

### 2013-05-17 trunk/CompFuzzExt.tex
revising introduction

@@
 
-\paragraph {Our Postive Results}
+\paragraph {Our Positive Results}
 
@@
 \begin{construction}
-Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
+Let $n$ be a security parameter and let $m> n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
 Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
@@
 
-The main advantage to analyzing the construction as a whole~(instead of \emph{sketch-then-cextract}) is that security need not depend on the decoding radius $t$.
-In \emph{sketch-then-cextract} paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
+The main advantage to analyzing the construction as a whole~(instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.
+In sketch-and-comp-extract paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
 As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.

### 2013-05-17 CompFuzzExt.tex
working on 4.4

@@
 
-\subsection{Comparison with computational extractor based construction}
+\subsection{Comparison with computational-extractor-based constructions}
 \label{sec:prg based comparison}
-In this section, we constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using a computational extractor~\cite{krawczyk2010cryptographic} in place of the information-theoretic randomness extractor.
-A simple example of a computational extractor is the \emph{extract-then-expand} mechanism: a pseudorandom generator is applied to the output of a information-thereotic randomness extractor.
+As we already mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
+We will call this approach \emph{sketch-and-comp-extract}.
+(A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; but other approaches are also possible.)
 %using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
 This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.
+
+This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.
+However, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has just barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
+
+In contrast, in our approach, the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ is not relevant to security, because we do not extract from $w$.
+Instead, we require that $w$ is not recoverable computationally given $p$.
+Note that this requirement does not imply that $w$ can be extracted from, because computational extractors may require a longer minimum input length than the computational entropy of $w$.
+Our approach works in such a setting because instead of extracting from $w$, we hide secret randomness using $w$.
+
+The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.
+Our codes (namely, random linear codes) can tolerate very high $t$, in fact.
+In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.
+In our construction, the decoding radius depends only on the best available decoding algorithm for random linear codes.
+
+\lnote{use any of the below?}
+ utilize secret randomness to obtain the key $r$, and hide that randomness using $w$.
+
+The code defined by $\vA$ can correct very high
+
 Under the same hardness of approximating GAPSVP and SIVP, Applebaum et.
@@
 
-\begin{figure}[t]
+\begin{figure}[p]
 \begin{framed}

### 2013-05-17 CompFuzzExt.tex
worked on section 4.4

@@
 We will call this approach \emph{sketch-and-comp-extract}.
-(A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; but other approaches are also possible.)
+(A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; note that LWE-based pseudorandom generators exist~\cite{applebaum2006pseudorandom}.)
 %using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
@@
 This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.
-However, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has just barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
-
-In contrast, in our approach, the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ is not relevant to security, because we do not extract from $w$.
-Instead, we require that $w$ is not recoverable computationally given $p$.
-Note that this requirement does not imply that $w$ can be extracted from, because computational extractors may require a longer minimum input length than the computational entropy of $w$.
-Our approach works in such a setting because instead of extracting from $w$, we hide secret randomness using $w$.
-
-The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.
-Our codes (namely, random linear codes) can tolerate very high $t$, in fact.
+However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
+
+In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor.
+Instead, we require that $w$ is not computationally recoverable  given $p$.
+This requirement is weaker.
+The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$.
+Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.
+
+The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.
+Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.
 In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.
-In our construction, the decoding radius depends only on the best available decoding algorithm for random linear codes.
-
-\lnote{use any of the below?}
- utilize secret randomness to obtain the key $r$, and hide that randomness using $w$.
-
-The code defined by $\vA$ can correct very high
-
-Under the same hardness of approximating GAPSVP and SIVP, Applebaum et.
-al.
-achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.
-They consider $\vA$ as a public value and show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.
-Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).
-Both techniques are able to produce a linear stretch on the entropy of the source.
-
-Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.
-This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
-We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-and-comp-extract}.
-
-Any improvement in computational extractors yields an improvement to the sketch-and-comp-extract construction of a computational fuzzy extractor.
-Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).
-Thus, improving computational fuzzy extractors may improvement computational extractors.
-
-The main advantage to analyzing the construction as a whole~(instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.
-In sketch-and-comp-extract paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
-As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.
-In our construction, the decoding radius does not affect the security of the construction.
-The decoding radius only impacts the running time of the decoding algorithm.
-Conceivably, a computational fuzzy extractor could be built where only correctness depends on $t$~(not efficiency or security).
-%However, the construction of a computational fuzzy extractor by 
-%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
-In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
-The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).
+In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.
+
+Unfortunately, LWE parameter sizes require relatively long $w$.
+Therefore, in practice, sketch-then-comp-extract will beat our construction  if the computational extractor is instantiated efficiently based on assumptions other than LWE (for example, a cryptographic hash function for an extractor and a block cipher for a PRG).
+However, we believe that our conceptual framework can lead to better constructions.
+Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.
 

### 2013-05-17 CompFuzzExt.tex
fixing conductor badness

@@
 \newcommand{\ignore}[1]{}
+\newcommand{\M}{\mathcal{M}}
 
@@
 \end{itemize}
+\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, noise tolerance, error-correcting codes, computational entropy, randomness extractors.
 \end{abstract}
 
-\newcommand{\M}{\mathcal{M}}
 \section{Introduction}\label{sec:introduction}
@@
 %Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
-%~\ref{thm:lossless secure conductor log})).
+%~\ref{thm:lossless secure extractor log})).
 We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
@@
 \end{definition}
-This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
+This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
 For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
@@
 In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.
-We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax it similar to the way conditional HILL entropy was relaxed in the previous section).
+We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (our relaxation is analogous to relaxed HILL entropy described in the previous section).
 
@@
 \begin{theorem}
-\label{thm:lossless secure conductor log}
+\label{thm:lossless secure extractor log}
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
@@
 For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
-\thref{thm:lossless secure conductor log} shows that a computational fuzzy conductor can be built without incurring any entropy loss.
+\thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.
 This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.
@@
 Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.
+
+%However, the construction of a computational fuzzy extractor by 
+%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
+In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
+The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).
 
@@
 This result should be seen as a complement to the proceeding sections.
-It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure conductor log}.
+It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure extractor log}.
 Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
@@
 %\begin{lemma}
-%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
+%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
 Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
@@
 In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure conductor log} we give lossless conductors from a security parameter $n$ and an error $t$.
+In \thref{thm:lossless secure extractor log} we give a lossless fuzzy extractor from a security parameter $n$ and an error $t$.
 In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
@@
 The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.
-In \thref{thm:lossless secure conductor log}, we set $g=2$ and output the first half of $X$.
+In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.
 This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.

### 2013-05-17 trunk/CompFuzzExt.tex
finished section 5

@@
 \newcommand{\ignore}[1]{}
+\newcommand{\M}{\mathcal{M}}
 
 \title{\textbf{Computational Fuzzy Extractors}}
-\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+%\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
- \and Xianrui Meng \and Leonid Reyzin}
+% \and Xianrui Meng \and Leonid Reyzin}
+\author{}
 \begin{document}
@@
 \end{itemize}
+\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, error-correcting codes, computational entropy, randomness extractors.
 \end{abstract}
 
-\newcommand{\M}{\mathcal{M}}
 \section{Introduction}\label{sec:introduction}
@@
 
-\subsection{Comparison with computational extractor based construction}
+\subsection{Comparison with computational-extractor-based constructions}
 \label{sec:prg based comparison}
-In this section, we constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using a computational extractor~\cite{krawczyk2010cryptographic} in place of the information-theoretic randomness extractor.
-A simple example of a computational extractor is the \emph{extract-then-expand} mechanism: a pseudorandom generator is applied to the output of a information-thereotic randomness extractor.
+As we already mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
+We will call this approach \emph{sketch-and-comp-extract}.
+(A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; note that LWE-based pseudorandom generators exist~\cite{applebaum2006pseudorandom}.)
 %using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
 This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.
-Under the same hardness of approximating GAPSVP and SIVP, Applebaum et.
-al.
-achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.
-They consider $\vA$ as a public value and show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.
-Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).
-Both techniques are able to produce a linear stretch on the entropy of the source.
-
-Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.
-This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
-We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-and-comp-extract}.
-
-Any improvement in computational extractors yields an improvement to the sketch-and-comp-extract construction of a computational fuzzy extractor.
-Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).
-Thus, improving computational fuzzy extractors may improvement computational extractors.
-
-The main advantage to analyzing the construction as a whole~(instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.
-In sketch-and-comp-extract paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.
-As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.
-In our construction, the decoding radius does not affect the security of the construction.
-The decoding radius only impacts the running time of the decoding algorithm.
-Conceivably, a computational fuzzy extractor could be built where only correctness depends on $t$~(not efficiency or security).
+
+This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.
+However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
+
+In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor.
+Instead, we require that $w$ is not computationally recoverable  given $p$.
+This requirement is weaker.
+The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$.
+Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.
+
+The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.
+Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.
+In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.
+In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.
+
+Unfortunately, LWE parameter sizes require relatively long $w$.
+Therefore, in practice, sketch-then-comp-extract will beat our construction  if the computational extractor is instantiated efficiently based on assumptions other than LWE (for example, a cryptographic hash function for an extractor and a block cipher for a PRG).
+However, we believe that our conceptual framework can lead to better constructions.
+Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.
+
 %However, the construction of a computational fuzzy extractor by 
@@
 
-\section{Computational Fuzzy Exactor with Nonuniform Sources}
+\section{Computational Fuzzy Extractor for Nonuniform Sources}
 \label{sec:LWE block fixing sources}
-In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.
-Showing security of a computational fuzzy extractor for arbitrary high min-entropy distributions is an open problem.
+While showing the security of~\consref{cons:informal construction} for arbitrary high-min-entropy distributions is an open problem, in this section we show it for a particular class of distributions called symbol-fixing.
 First we recall the notion of a symbol fixing source~(from~\cite{KZ07}):
@@
 
+\ignore{
 We now study \consref{cons:informal construction} with a symbol fixing source.
-Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations and their error and $W$ can be recovered with Gaussian elimination.
-We show that security degrades exponentially as symbols are fixed.
-\ignore{
+
 \begin{assumption}[LWE w/ entropic errors]
@@
 }
-We now define the decisional $\LWE$ problem with symbol fixing errors is defined as follows: 
+We now define the decisional $\LWE$ problem with symbol fixing errors: 
 \begin{problem}[$\distLWE$ w/ symbol fixing errors]
@@
 
-The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$.
+The following theorem states the main technical result of this section, which is of potential interest outside our specific setting.
+The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$,  with security degrading exponentially as symbols are fixed (of course, once $n$ symbols are fixed, no security remains, because there are $n$ linear equations with known error and $n$ unknowns).
 %\vspace{.1in}
@@
 \end{theorem}
-We believe this statement is of interest outside our setting.
-\thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known errors.
-Roughly, we need the number of variables larger than the number of equations with known error by letting the number of variables be the security parameter.
+
+The intuition for this result is as follows.
 Providing a single sample with no error ``fixes'' at most a single variable.
-Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.
-We are able to show~(a stronger result) that $\distLWE$ is still hard.
-In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to explain a random value for the last $\alpha$ samples without knowledge of the other variables.
+Thus, if there are significantly more variables than samples with no error, intuitively search $\LWE$ should still be hard.
+We are able to show a stronger result that $\distLWE$ is still hard.
+The nontrivial part of the reduction is using the additional $\alpha+ \beta$ variables  to ``explain'' a random value for the last $\alpha$ samples, without knowing the other variables.
 The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
@@
 We could set $\alpha$ larger than $n/3$ and extract fewer hardcore dimensions.
-To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant in $n$.
+To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant fraction of $n$.
 The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.

### 2013-05-18 trunk/CompFuzzExt.tex
Minor revisions from proof reading

@@
 %As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
-Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and traditionally are defined as information-theoretic objects.
+Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.
 The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.
@@
 \paragraph {Our Negative Results}
-We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.
+We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called a \emph{secure sketch}.
 A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
@@
 \begin{enumerate}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.
+\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
+\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
@@
 \end{enumerate}
+A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
 \end{definition}
@@
 \begin{itemize}
-\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
-\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
+\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
+\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
 \end{itemize}
@@
 In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.
-We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (our relaxation is analogous to relaxed HILL entropy described in the previous section).
+We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax the definition slightly, similarly to the relaxation of HILL entropy described in the previous section).
 
@@
 Let  $(W, S)$ be a pair of random variables.
-We say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
+We say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
 \[
@@
 
-We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
+We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
 Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
@@
 In this section, we consider only a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.
-Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
+Our construction uses the code-offset construction~\cite{JW99}, \cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
 Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).
@@
 
-Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.
-Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
+Denote by $\bar{\Psi}_\rho$ the discretized Gaussian distribution over $\Fq$ with variance $(\rho q)^2/(2\pi)$.
+Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that for $\rho q >2\sqrt{n}$, when $\chi = \bar{\Psi}_{\rho}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
-Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
+%Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
 %We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):
@@
 \label{assume:entropy LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\alpha$ be the discretized Gaussian distribution with variance $(\alpha q)^2/2\pi$.
+Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$.
+Let $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
 If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.
@@
 We present a simple $\decode_t$.
-Replacing our algorithm  with a state of the art algorithm will only increase our correcting capability and improve \consref{cons:informal construction}.
-
+Replacing our algorithm  with a state of the art algorithm will increase our correcting capability and improve \consref{cons:informal construction}.
+
+\newpage
 \begin{construction}
@@
 The second condition is to ensure that there are few false positives in step (5).
-This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.
+
+We are concerned with the setting $t = O(\frac{m}{n}\log n)$.
+Random linear codes have distance at least $t = O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$.
 The exact statement is in \corref{cor:code high distance}.
+This, with overwhelming probability over the choice of $\vA$ the second condition is satisfied.
 Furthermore, steps (3-5) are computable in time $O(n^3)$.
-This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.
+Setting $t = O(\frac{m}{n}\log n)$ is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.
 We consider the setting where the running time of $\decode_t$ grows with $t$.
-$\decode_t$ is efficient as long as $t$ is small enough.
 The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
@@
 Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.
-Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
+Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $X$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
 \end{lemma}
@@
 \thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.
-This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.
+We can essentially think of $\vA X+W$ as an encryption of $X$ that where decryption works from any close $W'$.
 %A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.
@@
 Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
-Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
+Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$~(that is, $\Hoo(W) = mb$).
 The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
@@
 \]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. Let $X_y$ denote the random variable $X|Y=y$.
+where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. 
 %Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
@@
 $\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.
+Let $X_y$ denote the random variable $X|Y=y$.
 By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.
@@
 
-\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
 \subsection{Proof of \thref{thm:imp of unp entropy}}
@@
 Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
-Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least $B_t(\cdot)$.
+Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least some fixed value $B_t(\cdot)$.
 Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
@@
 (the last step follows by  \clref{clm:y is recoverable}).
+
+\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
 \end{proof}
@@
 \end{align*}
-
 %\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
 Note that $f$ is at a constant in $n$.
-
 Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:

### 2013-05-20 trunk/CompFuzzExt.tex
went over Section 4

@@
 A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
-An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):
+An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
 
@@
 We describe one possible polynomial-time $\decode_t$ (which corrects more errors than is possible by exhaustive search) in \secref{sec:time main construction}.
-In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.
+In \secref{sec:lossless extractor}, we describe parameter settings that allow us to extract as many bits as the input entropy, resulting in a lossless construction.
 In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a sketch-and-extract approach (\lemref{lem:fuzzy ext construction}) instantiated with a computational extractor.
@@
 \label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integers $n$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
+The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integer $n$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
 %The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.
@@
 \begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ be an integer $q = q(n) = \poly(n)$ be a prime.
+Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime.
 The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
@@
 We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If $\distLWE_{n, m, q, \chi}$ is secure for all $s_{sec} = \poly(n), \epsilon  = 1/\poly(n)$, we say it is \emph{secure}.
+If for any $s_{sec} = \poly(n)$, there exists   $\epsilon  = \ngl(n)$ such that  $\distLWE_{n, m, q, \chi}$ is$(\epsilon, s_{sec})$-secure, then we say  it is \emph{secure}.
 \end{definition}
 
-Denote by $\bar{\Psi}_\rho$ the discretized Gaussian distribution over $\Fq$ with variance $(\rho q)^2/(2\pi)$.
-Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that for $\rho q >2\sqrt{n}$, when $\chi = \bar{\Psi}_{\rho}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
+ Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as stated in the following proposition.
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
@@
 Let $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
-If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.
-That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_{m\log q}))\leq \epsilon$.
+If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho}$ is secure.
 
@@
 Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
-The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
+The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}).
 This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.
@@
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
+If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is secure.
 \end{lemma}
@@
 The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
-We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
+We state their result for a general error distribution~(noting that their proof does not depend on the error distribution):
 \begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
 \label{lem:many hardcore bits}
-Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\Fq$ and $k\leq n$ be an integer.
-Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard then $H^{\hill}_{\epsilon, s_{sec}'}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ where $s_{sec}' \approx s_{sec} - n^3$.
+ If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then
+\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,..., k}, \vA, \vA X+E) , (U, \vA, \vA X+E)) \le \epsilon\,,\]
+where $U$ denotes the uniform distribution over $\Fq^m$,  $s_{sec}' \approx s_{sec} - n^3$, and the remaining variables are as in \defref{def:dist-LWE}.
 \end{lemma}
@@
 %\end{lemma}
-With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, \consref{cons:informal construction} has many hardcore bits and we use these bits as our key.  
+The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} as long as all the parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.
 %\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}.
@@
 We present a simple $\decode_t$.
-Replacing our algorithm  with a state of the art algorithm will increase our correcting capability and improve \consref{cons:informal construction}.
+If better decoding algorithms become known, they can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
 
@@
 \item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
+\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
 \item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
 If no such rows exist go to step (2).
-\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows.
-Compute $X' = (\vA')^{-1}B'$.
-If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
+\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
+\item If $B- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
 \item Output $X'$.
@@
 
-$\decode_t$ is an efficient decoding procedure when $t$ is small enough.
-We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$.
-Furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
-The second condition is to ensure that there are few false positives in step (5).
-
-We are concerned with the setting $t = O(\frac{m}{n}\log n)$.
-Random linear codes have distance at least $t = O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$.
-The exact statement is in \corref{cor:code high distance}.
-This, with overwhelming probability over the choice of $\vA$ the second condition is satisfied.
-Furthermore, steps (3-5) are computable in time $O(n^3)$.
-Setting $t = O(\frac{m}{n}\log n)$ is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.
-We consider the setting where the running time of $\decode_t$ grows with $t$.
+Each step is computable in time $O(n^3)$. 
+For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows), and $\vA_{i_1,...,i_{2n}}$ has rank at least $n$.
+If this happens, then $X'=X$, and the algorithm terminates.
+However, we also need a second condition, to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.
+This detection will happen if $B-\vA X' = \vA (X-X')+(W-W')$ has more than $t$ nonzero coordinates.
+It suffices to ensure that $\vA (X-X')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $W-W'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
+
+Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.
+Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
 The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
@@
 %\end{lemma}
-\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d\log n (m/n-2)$]
+\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
 \label{lem:i t poly time}
-Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.
-Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
-Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.
-Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $X$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
+%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
+Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution $\vA, \vA X+W - W'$).
+It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$).
 \end{lemma}
-\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3\log n)$.
-Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.
-We concentrate on the setting $t\leq d\log n(m/n-2)$.
-Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
+\textbf{Note:}
+Even though we are correcting $O(\log n)$ errors, this corresponds to a super polynomial number of possible error patterns; the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
+Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).
+Thus, our main theorems get  better parameters when  $t\leq m/n-2$.
 
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
-Let $W$ be uniform over $\zo^{(c+2d)nb/d}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = n/2\log q = H_\infty(W)$
+Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet of $Z$ size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.
+Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds.
+\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$  hard with error $\delta = e^{-\Omega(n)}$.
+Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
 % for following parameters:
@@
 %\] 
-with 
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
 \end{theorem}
@@
 Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
+For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
+In particular, we describe how to set $q = \poly(n)$.
 \end{proof}
 
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
 \thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.
@@
 Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
-Let $q$ be a prime and $t = O(\frac{m}{n}\log n )$.
-For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $t$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
+Let $q$ be a prime and $\tau = O(\frac{m}{n}\log n )$.
+For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $\tau$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
 \end{corollary}
@@
 Let $c$ be some constant.
-Let $\delta = t/m = \frac{c\log n}{n}$.
+Let $\delta = \tau/m = \frac{c\log n}{n}$.
 We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).
@@
 \begin{proof}
-Let $d$ be a constant and $t = d\log n\left( \frac{m}{n}-2\right)$.  
-By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $t$ with probability $1-e^{-\Omega(n)}$.
-Thus, a false matches occurs in step (5) with probability $e^{-\Omega(n)}$.
+Let $d$ be a constant and $t = d\left( \frac{m}{n}-2\right)\log n$.  
+By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $2t+1$ with probability $1-e^{-\Omega(n)}$.
+Thus, if $X\neq X'$, step (6) will detect it with probability at least $1-e^{-\Omega(n)}$.
 This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\decode_t$.
-We consider the expected number of times step 2 is executed when $t\leq d\log n\left(\frac{m}{n}-1\right)$.
-Steps (3-5) can be accomplished in time $n^3\log q $.
-An iteration of $\decode_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when there is a sub matrix of $A_{i_1,..., i_{2n}}$ that has full rank.
-The probability that $A_{i_1,..., i_{2n}}$ is full rank depends only on the coins of $\gen$ and is independent of the probability that $B_{i_1,...,i_{2n}}$ has no errors.
+We consider the expected number of times step 2 is executed when $t\leq d\left(\frac{m}{n}-2\right)\log n$.
+An iteration of $\decode_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when  $\vA_{i_1,..., i_{2n}}$ has rank $n$.
+The event that $\vA_{i_1,..., i_{2n}}$ has rank $n$ is independent of event that the rows $i_1,...,i_{2n}$ have no errors.
 The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
@@
 \begin{align*}
-\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n\left(\frac{m}{n}-2\right)}{m-i}\right)\\
+\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\left(\frac{m}{n}-2\right)\log n}{m-i}\right)\\
 &\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
@@
 \end{align*}
-Now, we consider the probability that some sub matrix of $\vA_{i_1,..., i_{2n}}$ has full rank.
+Now, we consider the probability  $\vA_{i_1,..., i_{2n}}$  rank $n$.
 This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).
@@
 Thus, the expected number of iterations in step 2 at most  $2n^{4d}$.
-We assume all matrix operations can be completed in time $n^3\log q$, giving expected running approximately $O(n^{4d}(n^3 \log q))$.
+We assume all matrix operations can be completed in  $O(n^3)$ operations over $\Fq$, giving a total of expected $O(n^{4d+3})$ operations over $\Fq$.
 \end{proof}
@@
 \end{align*}
-Furthermore, we get decoding in time $O(n^{4d}(n^3\log n))$.
+Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.
 We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).

### 2013-05-20 CompFuzzExt.tex
typo fixed

@@
 \title{\textbf{Computational Fuzzy Extractors}}
-\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+%\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
- \and Xianrui Meng \and Leonid Reyzin}
+% \and Xianrui Meng \and Leonid Reyzin}
+\author{}
 \begin{document}
@@
 \end{itemize}
-\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, noise tolerance, error-correcting codes, computational entropy, randomness extractors.
+\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, error-correcting codes, computational entropy, randomness extractors.
 \end{abstract}
@@
 We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If $\distLWE_{n, m, q, \chi}$ is secure for all $s_{sec} = \poly(n), \epsilon  = 1/\poly(n)$, we say it is \emph{secure}.
+If for any $s_{sec} = \poly(n)$, there exists   $\epsilon  = \ngl(n)$ such that  $\distLWE_{n, m, q, \chi}$ is$(\epsilon, s_{sec})$-secure, then we say  it is \emph{secure}.
 \end{definition}
 
-Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.
-Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
+ Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as stated in the following proposition.
 %The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
-Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
+%Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
 %We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):
@@
 \label{assume:entropy LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\alpha$ be the discretized Gaussian distribution with variance $(\alpha q)^2/2\pi$.
-If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.
-That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_{m\log q}))\leq \epsilon$.
+Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$.
+Let $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
+If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho}$ is secure.
 
@@
 We present a simple $\decode_t$.
-Replacing our algorithm  with a state of the art algorithm will only increase our correcting capability and improve \consref{cons:informal construction}.
-
+If better decoding algorithms become known, they can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
+
+\newpage
 \begin{construction}
@@
 
-$\decode_t$ is an efficient decoding procedure when $t$ is small enough.
-We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$.
-Furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.
-The second condition is to ensure that there are few false positives in step (5).
-This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.
-The exact statement is in \corref{cor:code high distance}.
-Furthermore, steps (3-5) are computable in time $O(n^3)$.
-This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.
-We consider the setting where the running time of $\decode_t$ grows with $t$.
-$\decode_t$ is efficient as long as $t$ is small enough.
+Each step is computable in time $O(n^3)$. 
+For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows), and $\vA_{i_1,...,i_{2n}}$ has rank  $n$.
+If this happens, then $X'=X$, and the algorithm terminates.
+However, we also need a second condition, to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.
+This detection will happen if $B-\vA X' = \vA (X-X')+(W-W')$ has more than $t$ nonzero coordinates.
+It suffices to ensure that $\vA (X-X')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $W-W'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
+
+Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.
+Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
 The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
@@
 %\end{lemma}
-\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d\log n (m/n-2)$]
+\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
 \label{lem:i t poly time}
-Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.
-Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.
-Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.
-Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
+%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
+Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution $\vA, \vA X+W - W'$).
+It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$).
 \end{lemma}
-\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3\log n)$.
-Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.
-We concentrate on the setting $t\leq d\log n(m/n-2)$.
-Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
+\textbf{Note:}
+Even though we are correcting $O(\log n)$ errors, this corresponds to a super polynomial number of possible error patterns; the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
+Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).
+Thus, our main theorems get  better parameters when  $t\leq m/n-2$.
 
@@
 Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
+For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
+In particular, we describe how to set $q = \poly(n)$.
 \end{proof}
 
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
 \thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.
-This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.
+We can essentially think of $\vA X+W$ as an encryption of $X$ that where decryption works from any close $W'$.
 %A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.
@@
 Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
-Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.
+Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$~(that is, $\Hoo(W) = mb$).
 The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
 \end{theorem}
-We believe this statement is of interest outside our setting.
-\thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known errors.
-Roughly, we need the number of variables larger than the number of equations with known error by letting the number of variables be the security parameter.
+
+The intuition for this result is as follows.
 Providing a single sample with no error ``fixes'' at most a single variable.
-Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.
-We are able to show~(a stronger result) that $\distLWE$ is still hard.
-In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to explain a random value for the last $\alpha$ samples without knowledge of the other variables.
+Thus, if there are significantly more variables than samples with no error, intuitively search $\LWE$ should still be hard.
+We are able to show a stronger result that $\distLWE$ is still hard.
+The nontrivial part of the reduction is using the additional $\alpha+ \beta$ variables  to ``explain'' a random value for the last $\alpha$ samples, without knowing the other variables.
 The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.

### 2013-05-20 CompFuzzExt.tex
Thm 5.4 revised...

@@
 If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds.
-\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$  hard with error $\delta = e^{-\Omega(n)}$.
+\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 $\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
+\end{theorem}
+
+\begin{theorem}
+\label{thm:lossless block sketch log}
+Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
+Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+2d)n/d+\alpha \right)b})$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
+ there exists $\epsilon = \ngl(n)$ such that the following holds: 
+\consref{cons:informal construction} is a $(\M, mb, mb, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+Sketch takes $O(n^3\log n)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
 \end{theorem}

### 2013-05-20 trunk/CompFuzzExt.tex
Fixed Thm 5.4... and 4.8

@@
 Each step is computable in time $O(n^3)$. 
-For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows), and $\vA_{i_1,...,i_{2n}}$ has rank at least $n$.
+For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows), and $\vA_{i_1,...,i_{2n}}$ has rank  $n$.
 If this happens, then $X'=X$, and the algorithm terminates.
@@
 If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds.
-\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$  hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
+\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
 % for following parameters:
@@
 Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
-Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+2d)n/d+\alpha \right)b})$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms.
-There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/3} |\vA, \vA X+W) = H_\infty(W)$ for %the following parameters:
-%\[
-%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
+Let $\alpha \leq n/3$ and $m=(c+2d)n/d$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
+ there exists $\epsilon = \ngl(n)$ such that the following holds: 
+\consref{cons:informal construction} is a $(\M, mb, mb, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
 \end{theorem}

### 2013-05-20 CompFuzzExt.tex
Small changes to thm 5.4

@@
 \consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
+Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
 % for following parameters:
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
-Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+2d)n/d+\alpha \right)b})$.
-Assume GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms.
-There is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/3} |\vA, \vA X+W) = H_\infty(W)$ for %the following parameters:
-%\[
-%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
-\end{theorem}
-
-\begin{theorem}
-\label{thm:lossless block sketch log}
-Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
-Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+2d)n/d+\alpha \right)b})$.
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.
+Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
  there exists $\epsilon = \ngl(n)$ such that the following holds: 
-\consref{cons:informal construction} is a $(\M, mb, mb, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^3\log n)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
+\consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
 \end{theorem}
 
-\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).
+\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE}.
+Efficiency follows by \lemref{lem:i t poly time}.
+For a more detailed explanation of parameters see \secref{ssec:block params}.
+\end{proof}
+
+\textbf{Comparison with \thref{thm:lossless secure extractor log}}
+%\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  
 The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
-We could set $\alpha$ larger than $n/3$ and extract fewer hardcore dimensions.
+We could set $\alpha$ larger than $n/3$.
+This would yield fewer hardcore dimensions and force us to use a larger field.
 To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant fraction of $n$.
-The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
+We consider the setting where the number of fixed errors, hardcore dimensions, and dimensions used for randomness are all $n/3$.
+%The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
 

### 2013-05-21 CompFuzzExt.tex
Fixing of sketch time

@@
 \consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
+Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
 % for following parameters:
@@
 \consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
+Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
 \end{theorem}
@@
 
-\textbf{Comparison with \thref{thm:lossless secure extractor log}}
-%\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  
-The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
+%\textbf{Comparison with \thref{thm:lossless secure extractor log}}
+%%\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  
+%The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
 We could set $\alpha$ larger than $n/3$.

### 2013-05-21 CompFuzzExt.tex
thms fixing

@@
 \begin{minipage}{3in}
-\textbf{\rec}
+\textbf{\rep}
 \begin{enumerate}
@@
 We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If for any $s_{sec} = \poly(n)$, there exists   $\epsilon  = \ngl(n)$ such that  $\distLWE_{n, m, q, \chi}$ is$(\epsilon, s_{sec})$-secure, then we say  it is \emph{secure}.
+If for any $s_{sec} = \poly(n)$, there exists   $\epsilon  = \ngl(n)$ such that  $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure, then we say  it is \emph{secure}.
 \end{definition}
@@
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds.
-\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
 % for following parameters:
@@
 \consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
+The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
 \end{theorem}

### 2013-05-21 CompFuzzExt.tex
last thms

@@
 \begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
+A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
 \begin{itemize}
@@
  there exists $\epsilon = \ngl(n)$ such that the following holds: 
-\consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+\consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor for any symbol-fixing distribution symbol $W$ such that it is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.

### 2013-05-21 CompFuzzExt.tex
rewording theorem 5.4

@@
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
- there exists $\epsilon = \ngl(n)$ such that the following holds: 
-\consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor for any symbol-fixing distribution symbol $W$ such that it is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+ there exists $\epsilon = \ngl(n)$ such that \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.

### 2013-05-21 trunk/CompFuzzExt.tex
rewording theorem 5.4

@@
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds.
-\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
 % for following parameters:
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.
-Let $\alpha \leq n/3$ and $m=(c+2d)n/d$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.
+Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
- there exists $\epsilon = \ngl(n)$ such that the following holds: 
-\consref{cons:informal construction} is a $(\M, mb, mb, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-Sketch takes $O(n^3)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
+ there exists $\epsilon = \ngl(n)$ such that \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$, correcting $t$ errors) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
 \end{theorem}
 
-\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).
-The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
-We could set $\alpha$ larger than $n/3$ and extract fewer hardcore dimensions.
+\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE}.
+Efficiency follows by \lemref{lem:i t poly time}.
+For a more detailed explanation of parameters see \secref{ssec:block params}.
+\end{proof}
+
+%\textbf{Comparison with \thref{thm:lossless secure extractor log}}
+%%\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  
+%The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
+We could set $\alpha$ larger than $n/3$.
+This would yield fewer hardcore dimensions and force us to use a larger field.
 To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant fraction of $n$.
-The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
+We consider the setting where the number of fixed errors, hardcore dimensions, and dimensions used for randomness are all $n/3$.
+%The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
 

### 2013-05-21 CompFuzzExt.tex
rewording theorem 5.4

@@
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
- there exists $\epsilon = \ngl(n)$ such that \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+ there exists $\epsilon = \ngl(n)$ where \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$, correcting $t$ errors) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.

### 2013-05-23 trunk/CompFuzzExt.tex
going through section 5

@@
 In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
-We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
+We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.\footnote{In addition, we modify the notation so that we can specify a general class of sources for which the fuzzy extractor is designed to work (rather than limiting ourselves to the class of that consists of all sources of a given min-entropy $m$).}
 
 \begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
+Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
+A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
 \begin{itemize}
@@
 If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
 \end{itemize}
@@
 Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer.
+Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer.
 Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet of $Z$ size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.
+Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z$ of size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 While showing the security of~\consref{cons:informal construction} for arbitrary high-min-entropy distributions is an open problem, in this section we show it for a particular class of distributions called symbol-fixing.
-First we recall the notion of a symbol fixing source~(from~\cite{KZ07}):
+First we recall the notion of a symbol fixing source~(from~\cite[Definition 2.3]{KZ07}):
 \begin{definition}
-Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $m$-\emph{symbol fixing source} if $H_\infty(W)\geq mb$ and for all $W_i$ one of the following conditions is met:
-\begin{itemize}
-\item $W_i \overset{d}= U_b$
-\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
-\end{itemize}
+Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $Z$ of size  $2^b$.  We say that it is a $(m+
+\alpha, m, 2^b) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
+Note that $H_\infty(W)=mb$.
 \end{definition}
+\lnote{do we need exactly $\alpha$ fixed, or can we do up to $\alpha$ fixed?
+The KZ07 definition requires exactly.
+We shouldn't chagne the definition, but may restate the theorem to include all symbol fixing source of entropy $mb$ and up}
 %A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.
@@
 \begin{assumption}[LWE w/ entropic errors]
-Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-block fixing distribution over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
+Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be $(m+
+\alpha, m, 2^b)$ symbol-fixing source over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
 Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
@@
 \begin{problem}[$\distLWE$ w/ symbol fixing errors]
-Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.
-Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$.
+Let $n$ be a security parameter.  Let $q=q(n)=\poly(n)$ be a prime and  $m = m(n)=\poly(n)$ be an integer.  Let $W = W_1||...||W_{m+\alpha}$ be a$(m+
+\alpha, m, 2^b)$ symbol fixing source over an $Z^{m+\alpha}$ for an alphabet $Z$\lnote{what alphabet?
+it should be integers} of size $2^b$.
 For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$.
-The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
+The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ \lnote{why is $X$ a subscript in this notation by A is uniform?
+why not both?} for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
 \end{problem}
@@
 
-\thref{thm:blockLWE} allows us to construct a computational fuzzy extractor from block-fixing sources:
+\thref{thm:blockLWE} allows us to construct a lossless computational fuzzy extractor from block-fixing sources:
 
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.
-Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z$ of size $2^b$, where the block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.
+Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $\mathcal{W}$ be the class of all $m$-symbol fixing sources over $\zo^{(m+\alpha)b}$.
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
- there exists $\epsilon = \ngl(n)$ such that \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$, correcting $t$ errors) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+ there exists $\epsilon = \ngl(n)$ 
+such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
  The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.

### 2013-06-14 CompFuzzExt.tex
updated Lem 4.4 to match DMQ13 Cor. 1

--- 2013-05-21 CompFuzzExt.tex
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-For the Hamming metric over $Z^n$ the size of $B_t(\cdot) = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $, for clarity we express this value as $B_t(\cdot)$.
+For the Hamming metric over $Z^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
-We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
+We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
+Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
 
 \begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
+Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
+A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
 \begin{itemize}
@@
 \begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime.
+Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime (unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding).
 The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
@@
 %This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
-\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
+\begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
 \label{lem:uniform LWE decision}
 Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer.
-Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is secure.
+Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer with $m\ge 3n$.
+Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$.
+If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$,  $\distLWE_{n, m, q, \chi}$ is secure.
 \end{lemma}
@@
 Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer.
-Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.
+Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+\sigma}m$.
+Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+\sigma}m/\rho)$.
 Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.
@@
 %\label{cons:LWESecureSketch} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers.
-Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+3\gamma}m$.
+Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+\sigma}m$.
 Let $\decode_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
@@
 
-\newpage
 \begin{construction}
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet of $Z$ size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.
+Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1}+1,2^{b-1}]$ of size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.
-Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z$ of size $2^b$, where the block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.
+Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $\mathcal{W}$ be the class of all $m$-symbol fixing sources over $\zo^{(m+\alpha)b}$.
 If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
- there exists $\epsilon = \ngl(n)$ such that \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+ there exists $\epsilon = \ngl(n)$ 
+such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
  The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
@@
 \item Maintain security of LWE.
-If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + 3\gamma} m = \poly(n)$.
+If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + \sigma} m = \poly(n)$.
 The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.
-We ignore this effect and assume that $\rho q = 2n^{1/2+3\gamma}m$.
+We ignore this effect and assume that $\rho q = 2n^{1/2+\sigma}m$.
 \item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
@@
 q &= n^f\\
-\rho q  &= 2n^{1/2+3\gamma}m\\
+\rho q  &= 2n^{1/2+\sigma}m\\
 m\log \rho q &= k \log q
 \end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
+Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
 \begin{align*}
@@
 t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log 2n^{1/2+3\gamma}m &= k \log n^f
-\end{align*}
-%\xnote{$ m \log 2n^{1/2+3\gamma}m = n \log n^f$}
+m \log 2n^{1/2+\sigma}m &= k \log n^f
+\end{align*}
+%\xnote{$ m \log 2n^{1/2+\sigma}m = n \log n^f$}
 This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.
@@
 %f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
+f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma} m}{\log n}
 \end{align*}
@@
 m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
-\end{align*}
-%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
+f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+\sigma}}{\log n}
+\end{align*}
+%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+\sigma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+\sigma}}{\log n}$}
 Note that $f$ is at a constant in $n$.
@@
 m &= \frac{(c+2d)n}{d}\\
-q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
+q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+\sigma}m}{\log n}} = \poly(n)\\
+\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
 \end{align*}
@@
 t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log 2n^{1/2+3\gamma}m &= k \log n^f
+m \log 2n^{1/2+\sigma}m &= k \log n^f
 \end{align*}
@@
 m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
+f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+\sigma}}{\log n}
 \end{align*}

### 2013-06-14 CompFuzzExt.tex
Changing parameter settings to 2rhoq+1

@@
 \end{itemize}
-We will split the source $|W|$ into $m$ blocks each of size $\rho q$~(that is, $|W| = m\log \rho q$).
+We will split the source $|W|$ into $m$ blocks each of size $2\rho q+1$~(that is, $|W| = m\log (2\rho q+1)$).
 We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.
@@
 We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.
-Substituting, one has $m\log \rho q = k \log q$.
+Substituting, one has $m\log 2\rho q+1 = k \log q$.
 \end{itemize}
@@
 \rho q  &= 2n^{1/2+\sigma}m\\
-m\log \rho q &= k \log q
+m\log (2\rho q +1)&= k \log q
 \end{align*}
@@
 t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log 2n^{1/2+\sigma}m &= k \log n^f
+m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
 \end{align*}
@@
 %f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma} m}{\log n}
+f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma} m+1}{\log n}
 \end{align*}
@@
 m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+\sigma}}{\log n}
+f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma}m+1}{\log n} = \frac{g(c+2d)}{d}\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
 \end{align*}
@@
 m &= \frac{(c+2d)n}{d}\\
-q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+\sigma}m}{\log n}} = \poly(n)\\
+q & = n^f = n^{\frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
 \rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
 \end{align*}
+
+Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $c>d$~(the condition that $m\geq 3n$ is also required for \lemref{lem:i t poly time} to hold).
+Since $\rho q = 2n^{1/2+\rho }m = O(n^{5/2})$ in our setting $\rho = O(n^{-1/2})$.
+Thus, for large enough settings of parameters $\rho$ is less than $1/10$ as required by \lemref{lem:uniform LWE decision}.
+
 Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.
@@
 In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.
-This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.
+This analysis proceeds similarly when we desire a linear stretch instead of $m\log (2\rho q +1)= k\log q$.
 %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
@@
 \rho q  &= 2n^{1/2+\sigma}m\\
-m\log \rho q &= k \log q
+m\log (2\rho q+1)&= k \log q
 \end{align*}
@@
 %f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma} m}{\log n}
+f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma} m+1)}{\log n}
 \end{align*}
@@
 m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+\sigma}}{\log n}
+f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
 \end{align*}
@@
 m &= \frac{(c+2d)n}{d}\\
-q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+\sigma}m}{\log n}} = \poly(n)\\
+q & = n^f = n^{\frac{m}{n}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
 \rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
 \end{align*}
+
+\bnote{As before explain why $\rho<1/10$ condition is satisfied}
 

### 2013-06-14 CompFuzzExt.tex
working on section 4 and 5

@@
 \label{lem:many hardcore bits}
- If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then
+ If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then \lnote{notation doesn't exactly match def 4.2}
 \[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,..., k}, \vA, \vA X+E) , (U, \vA, \vA X+E)) \le \epsilon\,,\]
@@
 %Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
-Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
+Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
 Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution $\vA, \vA X+W - W'$).
@@
 \label{thm:lossless secure extractor log}
-Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1}+1,2^{b-1}]$ of size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.
+Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
+Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b \approx \log (2n^3 (c+2d)/d)=O(\log n)$ \lnote{this may need to be modified after App D calculation}.
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/4$)}  using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 \begin{proof}
-Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
+Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}; efficiency follows by \lemref{lem:i t poly time}.
 For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
@@
 \begin{definition}
-Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $Z$ of size  $2^b$.  We say that it is a $(m+
-\alpha, m, 2^b) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
-Note that $H_\infty(W)=mb$.
+Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $Z$.  We say that it is a $(m+
+\alpha, m, |Z|) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
+Note that $H_\infty(W)=m\log |Z|$.
 \end{definition}
-\lnote{do we need exactly $\alpha$ fixed, or can we do up to $\alpha$ fixed?
-The KZ07 definition requires exactly.
-We shouldn't chagne the definition, but may restate the theorem to include all symbol fixing source of entropy $mb$ and up}
-%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.
 
@@
 \begin{problem}[$\distLWE$ w/ symbol fixing errors]
-Let $n$ be a security parameter.  Let $q=q(n)=\poly(n)$ be a prime and  $m = m(n)=\poly(n)$ be an integer.  Let $W = W_1||...||W_{m+\alpha}$ be a$(m+
-\alpha, m, 2^b)$ symbol fixing source over an $Z^{m+\alpha}$ for an alphabet $Z$\lnote{what alphabet?
-it should be integers} of size $2^b$.
-For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$.
-The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ \lnote{why is $X$ a subscript in this notation by A is uniform?
-why not both?} for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
+Let $n$ be a security parameter.  Let $q=q(n)=\poly(n)$ be a prime and  $m = m(n)=\poly(n)$ be an integer.  Let $W = W_1||...||W_{m+\alpha}$ be an $(m+
+\alpha, m, |Z|)$ symbol fixing source over  $Z^{m+\alpha}$ for the alphabet $Z=[-2^{b-1},2^{b-1}]$.
+For a vector $X \leftarrow \Fq^n$, let $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$.
+The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ withAt symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ \lnote{why is $X$ a subscript in this notation by A is uniform?
+why not both?}   \lnote{notation doesn't exactly match def 4.2}
+for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
 \end{problem}
@@
 \label{thm:blockLWE}
+ \lnote{notation doesn't exactly match def 4.2}
 Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z$ of size $2^b$, where the block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.
-Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $\mathcal{W}$ be the class of all $m$-symbol fixing sources over $\zo^{(m+\alpha)b}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
+Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log (2n^3 (c+2d)/d) = O(\log n)$ \lnote{this may need to be modified after App D.1 calculation}.
+Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $\mathcal{W}$ be the class of all $m$-symbol fixing sources over $Z^{m+\alpha}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/6$)} using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
  there exists $\epsilon = \ngl(n)$ 

### 2013-06-14 CompFuzzExt.tex
revising thm 4.8 with \rho q parameters

@@
 Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b \approx \log (2n^3 (c+2d)/d)=O(\log n)$ \lnote{this may need to be modified after App D calculation}.
-Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
+Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
+Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
 If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/4$)}  using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
@@
 \begin{proof}
-Let $d$ be a constant and $t = d\left( \frac{m}{n}-2\right)\log n$.  
+Let $d$ be a positive constant and $t = d\left( \frac{m}{n}-2\right)\log n$.  
 By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $2t+1$ with probability $1-e^{-\Omega(n)}$.
@@
 n_0&< n -k \\
-m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
+m &= \frac{(c/d+2)n \log n}{\log n} = (\frac{c}{d}+2)n\\
 f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma}m+1}{\log n} = \frac{g(c+2d)}{d}\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
@@
 \begin{align*}
-m &= \frac{(c+2d)n}{d}\\
+m &= (\frac{c}{d}+2)n\\
 q & = n^f = n^{\frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
-\end{align*}
-
-Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $c>d$~(the condition that $m\geq 3n$ is also required for \lemref{lem:i t poly time} to hold).
+\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
+\end{align*}
+
+Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $d<c$~(this also ensures that $m\geq 3n$, as required for \lemref{lem:i t poly time} to hold).
 Since $\rho q = 2n^{1/2+\rho }m = O(n^{5/2})$ in our setting $\rho = O(n^{-1/2})$.
@@
 In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.
-This analysis proceeds similarly when we desire a linear stretch instead of $m\log (2\rho q +1)= k\log q$.
+Setting $1<g<2$ achieves an increase in output length~(over the input length of $W$).
+We also (arbitrarily) set $\sigma=1/2$ to simplify the statement of \thref{thm:lossless secure extractor log}, making $\rho q = 2(c/d+2) n^2$.
+
+%The output corresponds to stretch~(in computational entropy) of $1/g$.
+%, A linear stretch instead of $m\log (2\rho q +1)= k\log q$.
 %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
@@
 n_0&< n/3 -  \log n\\
-m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
+m &= \frac{(c/d+2)n \log n}{ \log n} = (\frac{c}{d}+2)n\\
+f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(3(\frac{c}{d}+2)\right)\frac{\log (4(\frac{c}{d}+2) n^{3/2+\sigma}+1)}{\log n} = O(1)
 \end{align*}
@@
 
-\bnote{As before explain why $\rho<1/10$ condition is satisfied}
+As before we arbitrarily set $\sigma = 1/2$.  Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
 

### 2013-06-14 trunk/CompFuzzExt.tex
edited section 5 and minor edits elsewhere

@@
 Our construction is for the Hamming metric and uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.
-First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$.
+First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$ (this idea is similar to the way the code-offset construction is presented in
+\cite{JW99} as  a ``fuzzy commitment'') .
 Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.
@@
 In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
-We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.\footnote{In addition, we modify the notation so that we can specify a general class of sources for which the fuzzy extractor is designed to work (rather than limiting ourselves to the class of that consists of all sources of a given min-entropy $m$).}
+We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
+Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
 
@@
 %This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
-\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
+\begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
 \label{lem:uniform LWE decision}
 Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer.
-Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.
-If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is secure.
+Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer with $m\ge 3n$.
+Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$.
+If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$,  $\distLWE_{n, m, q, \chi}$ is secure.
 \end{lemma}
@@
  If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then
-\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,..., k}, \vA, \vA X+E) , (U, \vA, \vA X+E)) \le \epsilon\,,\]
-where $U$ denotes the uniform distribution over $\Fq^m$,  $s_{sec}' \approx s_{sec} - n^3$, and the remaining variables are as in \defref{def:dist-LWE}.
+\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,\dots, k}, \vA, \vA X+\chi) , (U, \vA, \vA X+\chi)) \le \epsilon\,,\]
+where $U$ denotes the uniform distribution over $\Fq^k$,  $\vA$ denotes the uniform distribution over $\Fq^{m\times n}$, $X$ denotes the uniform distribution over $\Fq^n$, $X_{1,\dots, k}$ denote the first $k$ coordinates of $x$, and $s_{sec}' \approx s_{sec} - n^3$.
 \end{lemma}
@@
 \label{thm:lossless secure extractor log}
-Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z$ of size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.
-Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
+Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
+Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/4$)}  using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 \begin{definition}
-Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $Z$ of size  $2^b$.  We say that it is a $(m+
-\alpha, m, 2^b) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
-Note that $H_\infty(W)=mb$.
+Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $Z$.  We say that it is a $(m+
+\alpha, m, |Z|) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
+Note that $H_\infty(W)=m\log |Z|$.
 \end{definition}
-\lnote{do we need exactly $\alpha$ fixed, or can we do up to $\alpha$ fixed?
-The KZ07 definition requires exactly.
-We shouldn't chagne the definition, but may restate the theorem to include all symbol fixing source of entropy $mb$ and up}
-%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.
-
-\ignore{
-We now study \consref{cons:informal construction} with a symbol fixing source.
-
-\begin{assumption}[LWE w/ entropic errors]
-Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be $(m+
-\alpha, m, 2^b)$ symbol-fixing source over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
-Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
-\end{assumption}
-}
-We now define the decisional $\LWE$ problem with symbol fixing errors: 
-\begin{problem}[$\distLWE$ w/ symbol fixing errors]
-Let $n$ be a security parameter.  Let $q=q(n)=\poly(n)$ be a prime and  $m = m(n)=\poly(n)$ be an integer.  Let $W = W_1||...||W_{m+\alpha}$ be a$(m+
-\alpha, m, 2^b)$ symbol fixing source over an $Z^{m+\alpha}$ for an alphabet $Z$\lnote{what alphabet?
-it should be integers} of size $2^b$.
-For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$.
-The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ \lnote{why is $X$ a subscript in this notation by A is uniform?
-why not both?} for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
-\end{problem}
 
 The following theorem states the main technical result of this section, which is of potential interest outside our specific setting.
-The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$,  with security degrading exponentially as symbols are fixed (of course, once $n$ symbols are fixed, no security remains, because there are $n$ linear equations with known error and $n$ unknowns).
+The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$ (but for $n$ and $m$ reduced by the amount of fixed symbols).
 %\vspace{.1in}
@@
 \label{thm:blockLWE}
-Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
-Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$~(that is, $\Hoo(W) = mb$).
-The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
+Let $n$ be a security parameter, $\alpha$ be polynomial in $n$, and $\beta=\beta(n)=\omega(1)$.
+Let $U$ denote the uniform distribution over $Z^m$ for an alphabet $Z\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |Z|)$ symbol fixing source over $Z^{m+\alpha}$.
+If $\distLWE_{n, m,q, U}$ is secure, then $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ is also secure.
 \end{theorem}
@@
 q &= n^f\\
-\rho q  &= 2n^{1/2+3\gamma}m\\
-m\log \rho q &= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
+\rho q  &= 2n^{1/2+\sigma}m\\
+m\log (2\rho q +1)&= k \log q
+\end{align*}
+Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
 \begin{align*}
@@
 t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log 2n^{1/2+3\gamma}m &= k \log n^f
-\end{align*}
-%\xnote{$ m \log 2n^{1/2+3\gamma}m = n \log n^f$}
+m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
+\end{align*}
+%\xnote{$ m \log 2n^{1/2+\sigma}m = n \log n^f$}
 This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.
@@
 %f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
+f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma} m+1}{\log n}
 \end{align*}
@@
 n_0&< n -k \\
-m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
-\end{align*}
-%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}
+m &= \frac{(c/d+2)n \log n}{\log n} = (\frac{c}{d}+2)n\\
+f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma}m+1}{\log n} = \frac{g(c+2d)}{d}\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
+\end{align*}
+%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+\sigma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+\sigma}}{\log n}$}
 Note that $f$ is at a constant in $n$.
@@
 \begin{align*}
-m &= \frac{(c+2d)n}{d}\\
-q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
-\end{align*}
+m &= (\frac{c}{d}+2)n\\
+q & = n^f = n^{\frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
+\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
+\end{align*}
+
+Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $d<c$~(this also ensures that $m\geq 3n$, as required for \lemref{lem:i t poly time} to hold).
+Since $\rho q = 2n^{1/2+\rho }m = O(n^{5/2})$ in our setting $\rho = O(n^{-1/2})$.
+Thus, for large enough settings of parameters $\rho$ is less than $1/10$ as required by \lemref{lem:uniform LWE decision}.
+
 Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.
@@
 In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.
-This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.
+Setting $1<g<2$ achieves an increase in output length~(over the input length of $W$).
+We also (arbitrarily) set $\sigma=1/2$ to simplify the statement of \thref{thm:lossless secure extractor log}, making $\rho q = 2(c/d+2) n^2$.
+
+%The output corresponds to stretch~(in computational entropy) of $1/g$.
+%, A linear stretch instead of $m\log (2\rho q +1)= k\log q$.
 %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
@@
 q &= n^f\\
-\rho q  &= 2n^{1/2+3\gamma}m\\
-m\log \rho q &= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
+\rho q  &= 2n^{1/2+\sigma}m\\
+m\log (2\rho q+1)&= k \log q
+\end{align*}
+Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
 \begin{align*}
@@
 t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log 2n^{1/2+3\gamma}m &= k \log n^f
+m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
 \end{align*}
@@
 %f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
+f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma} m+1)}{\log n}
 \end{align*}
@@
 n_0&< n/3 -  \log n\\
-m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
-f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}
+m &= \frac{(c/d+2)n \log n}{ \log n} = (\frac{c}{d}+2)n\\
+f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(3(\frac{c}{d}+2)\right)\frac{\log (4(\frac{c}{d}+2) n^{3/2+\sigma}+1)}{\log n} = O(1)
 \end{align*}
@@
 m &= \frac{(c+2d)n}{d}\\
-q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
-\end{align*}
+q & = n^f = n^{\frac{m}{n}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
+\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
+\end{align*}
+
+As before we arbitrarily set $\sigma = 1/2$.  Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
 

### 2013-06-14 trunk/CompFuzzExt.tex
matching theorem 5.3 with new appendix D

@@
 \label{thm:lossless block sketch log}
-Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.
-Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log (2n^3 (c+2d)/d) = O(\log n)$ \lnote{this may need to be modified after App D.1 calculation}.
-Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $\mathcal{W}$ be the class of all $m$-symbol fixing sources over $Z^{m+\alpha}$.
+Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
+Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
+Let $\mathcal{M} = Z^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
+Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |Z|)$-symbol fixing sources.
 If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/6$)} using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
  there exists $\epsilon = \ngl(n)$ 
-such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
  The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
@@
 \begin{align*}
-m &= \frac{(c+2d)n}{d}\\
+m &= (\frac{c}{d}+2)n\\
 q & = n^f = n^{\frac{m}{n}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
-\end{align*}
-
-As before we arbitrarily set $\sigma = 1/2$.  Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
+\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
+\end{align*}
+
+As before we arbitrarily set $\sigma = 1/2$, giving $\rho q = 2(\frac{c}{d}+2)n^2$.
+Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
 

### 2013-06-14 trunk/CompFuzzExt.tex
added note about 5.3 working for arbitrary error distribution

@@
 \end{theorem}
+
+\thref{thm:blockLWE} holds for an arbitrary error distribution~(not just uniform error) in the following sense.
+Let $\chi$ be an arbitrary error distribution.
+Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.
+Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.
 

### 2013-06-14 CompFuzzExt.tex
Changing \vW to \vQ for consistency

@@
 \newcommand{\vW}{\vect{W}}
+\newcommand{\vQ}{\vect{Q}}
 \newcommand{\vR}{\vect{R}}
@@
 \label{lem:many hardcore bits}
- If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then \lnote{notation doesn't exactly match def 4.2}
-\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,..., k}, \vA, \vA X+E) , (U, \vA, \vA X+E)) \le \epsilon\,,\]
-where $U$ denotes the uniform distribution over $\Fq^m$,  $s_{sec}' \approx s_{sec} - n^3$, and the remaining variables are as in \defref{def:dist-LWE}.
+ If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then
+\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,\dots, k}, \vA, \vA X+\chi) , (U, \vA, \vA X+\chi)) \le \epsilon\,,\]
+where $U$ denotes the uniform distribution over $\Fq^k$,  $\vA$ denotes the uniform distribution over $\Fq^{m\times n}$, $X$ denotes the uniform distribution over $\Fq^n$, $X_{1,\dots, k}$ denote the first $k$ coordinates of $x$, and $s_{sec}' \approx s_{sec} - n^3$.
 \end{lemma}
@@
 
-\ignore{
-We now study \consref{cons:informal construction} with a symbol fixing source.
-
-\begin{assumption}[LWE w/ entropic errors]
-Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be $(m+
-\alpha, m, 2^b)$ symbol-fixing source over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
-Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
-\end{assumption}
-}
-We now define the decisional $\LWE$ problem with symbol fixing errors: 
-\begin{problem}[$\distLWE$ w/ symbol fixing errors]
-Let $n$ be a security parameter.  Let $q=q(n)=\poly(n)$ be a prime and  $m = m(n)=\poly(n)$ be an integer.  Let $W = W_1||...||W_{m+\alpha}$ be an $(m+
-\alpha, m, |Z|)$ symbol fixing source over  $Z^{m+\alpha}$ for the alphabet $Z=[-2^{b-1},2^{b-1}]$.
-For a vector $X \leftarrow \Fq^n$, let $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$.
-The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ withAt symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ \lnote{why is $X$ a subscript in this notation by A is uniform?
-why not both?}   \lnote{notation doesn't exactly match def 4.2}
-for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
-\end{problem}
-
 The following theorem states the main technical result of this section, which is of potential interest outside our specific setting.
-The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$,  with security degrading exponentially as symbols are fixed (of course, once $n$ symbols are fixed, no security remains, because there are $n$ linear equations with known error and $n$ unknowns).
+The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$ (but for $n$ and $m$ reduced by the amount of fixed symbols).
 %\vspace{.1in}
@@
 \label{thm:blockLWE}
- \lnote{notation doesn't exactly match def 4.2}
-Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.
-Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$~(that is, $\Hoo(W) = mb$).
-The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
+Let $n$ be a security parameter, $\alpha$ be polynomial in $n$, and $\beta=\beta(n)=\omega(1)$.
+Let $U$ denote the uniform distribution over $Z^m$ for an alphabet $Z\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |Z|)$ symbol fixing source over $Z^{m+\alpha}$.
+If $\distLWE_{n, m,q, U}$ is secure, then $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ is also secure.
 \end{theorem}
+
+\thref{thm:blockLWE} holds for an arbitrary error distribution~(not just uniform error) in the following sense.
+Let $\chi$ be an arbitrary error distribution.
+Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.
+Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.
 
@@
 \item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
+\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vQ \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
 \item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
@@
 \subitem For $j=1,..., m$:
-\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
-\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
+\subsubitem Generate $\vQ_{j, i}\overset{\$}\leftarrow \Fq$
+\subsubitem Set $b_j^* = b_j^* + \vQ_{j, i} x_i$.
+\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
 \item \label{step:randomization}
@@
 The quadrant represented by $\vA'$ remains random after step~\ref{step:randomization} as we are adding uncorrelated random values.
-The matrix $\vW_{T^c}$~(recall this is the restriction of $\vW$ to the columns not in $T$) is random as it is initialized with random values and only uncorrelated random values are added.
-
-Thus, we restrict attention to $\vW_T$~(the columns of $W$ included in $T$).
+The matrix $\vQ_{T^c}$~(recall this is the restriction of $\vQ$ to the columns not in $T$) is random as it is initialized with random values and only uncorrelated random values are added.
+
+Thus, we restrict attention to $\vQ_T$~(the columns of $W$ included in $T$).
 Consider a particular row $i$.
-Then $\vW_{i, T} = \gamma_i \vS_{T}$.
-Since $\vS_T$ is full rank and $\gamma_i$ is uniformly generated, $\vW_{i, T}$ is uniformly generated.
+Then $\vQ_{i, T} = \gamma_i \vS_{T}$.
+Since $\vS_T$ is full rank and $\gamma_i$ is uniformly generated, $\vQ_{i, T}$ is uniformly generated.
 
@@
 Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$, i.e.
-for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.
+The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vQ$, i.e.
+for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vQ_{i, j} x_j$, thus conditioning on $\vQ$, $b_i^*$ is uniform assuming $b_i$ is uniform.
 Thus $\vb^* | \vA^*$ is uniformly distributed.

### 2013-06-17 CompFuzzExt.tex
Adding notes to sections 4, 5

@@
 In this section we describe our main construction.
-In this section, we consider only a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.
+Security of our construction depends on the source $W$.
+We first consider  a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.
 Our construction uses the code-offset construction~\cite{JW99}, \cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
@@
 \begin{construction}
-Let $n$ be a security parameter and let $m> n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
+Let $n$ be a security parameter and let $m> n$\bnote{should we just switch to $m\ge 3n$ here?}.
+Let $q$ be a prime.
+%Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.
 Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
@@
 \item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
-\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
-\item Let $X = \decode_t(\vA, \vect{D})$\\
+\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{B}=\vect{C}-w'$.
+\item Let $X = \decode_t(\vA, \vect{B})$\\
 \item Output $r = X_{1,...,n/2}$.
@@
 
-Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
+Intuitively, security comes from the computational hardness of decoding random linear codes with a high number of errors (introduced by $w$).  
 In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.
@@
 \label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integer $n$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
+The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integers $n, m$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ \bnote{only two places we use this notation.}be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
 %The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.
@@
 \begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime (unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding).
-The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
+Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime (unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding)\bnote{does this belong in a definition?}.
+The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ \bnote{only two places we use this notation.} for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
 
@@
 \begin{proposition} 
+\bnote{Why is this not a theorem?  For example Theorem 1 from Reg05?}
 \label{assume:entropy LWE}
@@
 %\label{subsec:LWE uniform error}
-Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
+Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\bnote{Their reduction is ultimately to the same problems not to Gaussian LWE}\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
 The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}).
@@
 
-To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
+To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits\bnote{Do we need to cite anything about hardcore?}.
 The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
@@
 We present a simple $\decode_t$.
-If better decoding algorithms become known, they can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
+An improved decoding algorithm can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
 
@@
 \begin{enumerate}
-\item Input $\vA , B = \vA X + W - W'$
+\item Input $\vA , \vB = \vA X + W - W'$
 \item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
+\item Restrict $\vA, \vB$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vB_{i_1,...,i_{2n}}$.
 \item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
 If no such rows exist go to step (2).
-\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
-\item If $B- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
+\item Denote by $\vA', \vB'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vB_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
+\item If $\vB- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
 \item Output $X'$.
@@
 If this happens, then $X'=X$, and the algorithm terminates.
-However, we also need a second condition, to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.
+However, we also need to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.
 This detection will happen if $B-\vA X' = \vA (X-X')+(W-W')$ has more than $t$ nonzero coordinates.
@@
 Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution $\vA, \vA X+W - W'$).
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution\bnote{this needs to be more precise} $\vA, \vA X+W - W'$).
 It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$).
@@
 Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).
-Thus, our main theorems get  better parameters when  $t\leq m/n-2$.
+Our main theorems get  better parameters when  $t\leq m/n-2$.
 
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
+Let $d<c$ be a positive constant \bnote{need to describe $d$} and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/4$)}  using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors% \lnote{removed (on lattices of dimension $n/4$)}
+using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
-In particular, we describe how to set $q = \poly(n)$.
+%In particular, we describe how to set $q = \poly(n)$.
 \end{proof}
@@
 Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.
-In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.
+In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$\bnote{this sentence worries me a little}.
 In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.
@@
 Providing a single sample with no error ``fixes'' at most a single variable.
-Thus, if there are significantly more variables than samples with no error, intuitively search $\LWE$ should still be hard.
+Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.
 We are able to show a stronger result that $\distLWE$ is still hard.
@@
 Let $\mathcal{M} = Z^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
-Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |Z|)$-symbol fixing sources.
-If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/6$)} using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
+Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |Z|)$-symbol fixing sources.  If GAPSVP and SIVP are hard to approximate within polynomial factors 
+%\lnote{removed (on lattices of dimension $n/6$)} 
+using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
  there exists $\epsilon = \ngl(n)$ 

### 2013-06-17 trunk/CompFuzzExt.tex
went through notes in section 4

@@
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-We use bold letters for vectors or matrices, capitalized letters to be random variables, and lower case letters for the elements in the vector or samples from a random variable.
+Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.
 
@@
 \begin{construction}
-Let $n$ be a security parameter and let $m> n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
+Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
 Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
@@
 \label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integer $n$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
-%The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.
-
-\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime (unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding).
-The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
+The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." We now recall the definition of the decisional version of the problem.
+
+\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
+Let $n$ be a security parameter.  
+Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime\footnote{%
+Unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding.}.
+%
+Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $\vx$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
+ The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
+$(\vA, \vA\vx+\chi)$ from
+ the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
 
@@
 
- Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as stated in the following proposition.
-%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
-%Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
-%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):
-
-\begin{proposition} 
-\label{assume:entropy LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$.
-Let $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
-If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho}$ is secure.
-
-%H^{\unp}_{\epsilon, s_{sec}}(X | \vA, \vA X+E) =H^{\unp}_{\epsilon, s'_{sec}}(E| \vA, \vA X+E) \geq n\log q $ for $s'_{sec}\approx s_{sec}$.  
-\end{proposition}
+ Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
+Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
+If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.
 
@@
 %\label{subsec:LWE uniform error}
-Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
-The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}).
+Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
+The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
 This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.
@@
 Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$.
-If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$,  $\distLWE_{n, m, q, \chi}$ is secure.
+If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]^m$,  $\distLWE_{n, m, q, \chi}$ is secure.
 \end{lemma}
 
-To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.
+To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has simultaneously many hardcore bits.
 The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
@@
 Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution $\vA, \vA X+W - W'$).
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution\bnote{this is probably wrong, because we have a nonzero probability of an infinite running time when $A$ has rank $<n$} $\vA, \vA X+W - W'$).
 It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$).
@@
 Even though we are correcting $O(\log n)$ errors, this corresponds to a super polynomial number of possible error patterns; the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
-Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).
-Thus, our main theorems get  better parameters when  $t\leq m/n-2$.
+\lnote{Should we clarify this --- this is about constant errors rather than logarithmic: Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).
+Our main theorems get  better parameters when  $t\leq m/n-2$.
+}
 
@@
 \label{thm:lossless secure extractor log}
-Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
+Let $n$ be a security parameter and let the number of errors $t = c\log n$ for some positive constant $c$.
+Let $d$ be a positive constant (giving us a tradeoff between running time of $\rep$ and $|w|$).
+Consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/4$)}  using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors% \lnote{removed (on lattices of dimension $n/4$)}
+using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 Instead, we require that $w$ is not computationally recoverable  given $p$.
-This requirement is weaker.
+This requirement is weaker---in particular, in our construction, $w$ may have no information-theoretic entropy conditioned on $p$.
 The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$.
@@
 The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.
-Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.
-In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.
-In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.
+In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes, because decoding algorithms will not reach the information-theoretic decoding radius.
 
@@
 
-\thref{thm:blockLWE} holds for an arbitrary error distribution~(not just uniform error) in the following sense.
+\thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.
 Let $\chi$ be an arbitrary error distribution.
@@
 Providing a single sample with no error ``fixes'' at most a single variable.
-Thus, if there are significantly more variables than samples with no error, intuitively search $\LWE$ should still be hard.
+Thus, if there are significantly more variables than samples with no error,  search $\LWE$ should still be hard.
 We are able to show a stronger result that $\distLWE$ is still hard.
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
+Let $d\le c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
 Let $\mathcal{M} = Z^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
-Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |Z|)$-symbol fixing sources.
-If GAPSVP and SIVP are hard to approximate within polynomial factors \lnote{removed (on lattices of dimension $n/6$)} using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
+Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |Z|)$-symbol fixing sources.  If GAPSVP and SIVP are hard to approximate within polynomial factors 
+using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
  there exists $\epsilon = \ngl(n)$ 
@@
 We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
-Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
+Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi$.
 It suffices to build a distinguisher~(of polynomial size) $D'$  where
@@
 \end{align*}
-Now, we consider the probability  $\vA_{i_1,..., i_{2n}}$  rank $n$.
+Now, we consider the probability  $\vA_{i_1,..., i_{2n}}$  has rank at least $n$.
 This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).

### 2013-06-18 trunk/CompFuzzExt.tex
edited decode and its efficiency analysis

@@
 %\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
-\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.
+\consref{cons:informal construction} is useful only if $\decode_t$ can be efficiently implemented.
 We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.
-We present a simple $\decode_t$.
+We present a simple $\decode_t$ that runs in polynomial time and can correct
+correcting $O(\log n)$ errors (note that this corresponds to a superpolynomial number of possible error patterns).
+This algorithm is only a proof of concept, and neither the algorithm nor its analysis have been optimized for constants.
 An improved decoding algorithm can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
@@
 \item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
-If no such rows exist go to step (2).
+If no such rows exist, output $\perp$ and stop.
 \item Denote by $\vA', \vB'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vB_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
@@
 Each step is computable in time $O(n^3)$. 
-For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows), and $\vA_{i_1,...,i_{2n}}$ has rank  $n$.
-If this happens, then $X'=X$, and the algorithm terminates.
+For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows).
+If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $X'=X$, and the algorithm terminates.
 However, we also need to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.
@@
 Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution\bnote{this is probably wrong, because we have a nonzero probability of an infinite running time when $A$ has rank $<n$} $\vA, \vA X+W - W'$).
-It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$).
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$.
+It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
 \end{lemma}
-\textbf{Note:}
-Even though we are correcting $O(\log n)$ errors, this corresponds to a super polynomial number of possible error patterns; the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
-\lnote{Should we clarify this --- this is about constant errors rather than logarithmic: Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).
-Our main theorems get  better parameters when  $t\leq m/n-2$.
-}
 
@@
 \label{cl:full rank matrix}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
+Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.\lnote{what is $n$?}
 \end{claim}
@@
 \begin{proof}
-Let $d$ be a positive constant and $t = d\left( \frac{m}{n}-2\right)\log n$.  
-By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $2t+1$ with probability $1-e^{-\Omega(n)}$.
-Thus, if $X\neq X'$, step (6) will detect it with probability at least $1-e^{-\Omega(n)}$.
-This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\decode_t$.
-We consider the expected number of times step 2 is executed when $t\leq d\left(\frac{m}{n}-2\right)\log n$.
-An iteration of $\decode_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when  $\vA_{i_1,..., i_{2n}}$ has rank $n$.
-The event that $\vA_{i_1,..., i_{2n}}$ has rank $n$ is independent of event that the rows $i_1,...,i_{2n}$ have no errors.
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
-That is,
+Note that $\decode_t$ will stop if $W$ and $W'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
+The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
 \begin{align*}
@@
 &\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
-&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}
-\end{align*}
-Now, we consider the probability  $\vA_{i_1,..., i_{2n}}$  has rank at least $n$.
-This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).
-Thus, the probability that a given iteration succeeds $\frac{1}{n^{4d}} - e^{-\Omega(n)}$.
-Thus, the expected number of iterations in step 2 at most  $2n^{4d}$.
-We assume all matrix operations can be completed in  $O(n^3)$ operations over $\Fq$, giving a total of expected $O(n^{4d+3})$ operations over $\Fq$.
+&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}\,.
+\end{align*}
+(The second-to-last step holds as long as $n\ge 2d\log n$.) Because at each iteration, we select $2n$ rows independently at random, the expected number of iterations is at most $n^{4d}$; each iteration takes $O(n^3)$ operations in $\Fq$, which gives us the expected running time bound.
+
+The probability that $\decode_t$ outputs $\perp$ is bounded by 
+\begin{eqnarray*}
+\Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
+&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1},\dots, \vA_{i_{2n}})<n]\\
+&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1},\dots, \vA_{i_{2n}})<n]\\
+&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot e^{-\Omega(n)}\\
+& = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
+\end{eqnarray*}
+(the second to last line follows from \clref{cl:full rank matrix} \lnote{actually, it doesn't -- \clref{cl:full rank matrix} doesn't have an exponential bound}).
+
+We claim that if the code generated by $\vA$ 
+has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $X'=X$.
+Indeed, suppose $X'\neq X$.
+Since $\vA (X-X')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $W-W'$, such an $X'$ will not pass Step 6.
+
+The probability that the code generated by $\vA$ has distance lower than $2t+1$ is at most $e^{-\Omega(n)}$ (see \corref{cor:code high distance}), and so is the probability of ouptutting $\perp$, computed above.
+This gives the correctness bound for $\decode_t$.
 \end{proof}

### 2013-06-20 trunk/CompFuzzExt.tex
revisions to proof of 4.6

@@
 Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$.
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this probability is over the choice of random coins of \rep).
 It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
@@
 \appendix
-\section{Random Linear Codes Have High Distance}
-%\subsection{Notions of Computational Entropy}
-%\label{sec:notionsEntropy}
-%In this sections we provide some further definitions of computational entropy.
-HILL entropy is defined in \secref{sec:impossCompSecSketch}.
-HILL entropy generalizes the notion of indistinguishability.
-Yao entropy~\cite{DBLP:conf/focs/Yao82a, barak-computational} generalizes the notion of compressibility.
-Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
-%\begin{definition}
-%\label{def:yao entropy}
-%For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
-%\[
-%\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
-%\]
-%\end{definition}
-%It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.
-In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
-We also use a less common notion called unpredictability entropy.
-This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
-%Unpredictability entropy is a notion between HILL and Yao entropy:
-%\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
-%\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
-%\]
-%\end{lemma} 
-%\subsection{Unique Witness Relations}
-
-%We will need the ability to verify if we have a correct solution in~\consref{cons:informal construction}.  
-%
-%\begin{definition}
-%Let $R$ be a relation.  We say that $R$ is $s_{ver}$-\emph{unique witness verifiable} if $\forall y$ there exists a unique $x$ such that $R(x, y)=1$ and $R(x, y) =1$ is computable in time $s_{ver}$.
-%\end{definition}
-%We can relax this definition slightly to allow a relation that is unique witness verifiable with all but negligible probability~(when $x, y$ grow with the security parameter).
-%
-%\begin{definition}
-%\label{def:unique witness relation}
-%Let $R:\mathcal{M}_1\times \mathcal{M}_2\rightarrow \zo$.
-We say that $R$ is $(\epsilon, s_{ver})$-\emph{unique witness verifiable} if over $y\in \mathcal{M}_2$, drawn uniformly, the probability that $\exists x_1, x_2, x_1\neq x_2$ such that $R(x_1, y) =1 = R(x_2, y)$ is at most $\epsilon$ and $R$ is computable in time $s_{ver}$.
-%\end{definition}
-%
+\section{Properties of Random Linear Codes}
 For efficient decoding of \consref{cons:informal construction}, we need the $\LWE$ instance to have high distance with overwhelming probability.
@@
 \end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.
-
-% and note that there $\exists \epsilon$ where $0<\epsilon< 1-H_q(\frac{c\log n}{2n})< 1-H_q(\frac{c\log n}{m})$ and $1-H_q(c\log n/n) -\epsilon =1/2$ or equivalently $H_q(c\log n/n)+\epsilon = 1/2$.
-Let $d$ be some constant such that $q< n^d$.
-Consider the value of $H_q(\frac{c\log n}{n})$:
-%\begin{align*}
-%H_q(\frac{c\log n}{n})&\leq  H_{n^d}(\frac{c\log n}{n})\\
-%&=\frac{c\log n}{n} \log_{n^d}(n^d-1) - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} (1-\frac{c\log n}{n})\\
-%&\leq \frac{c\log n}{n}  - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n})-\log_{n^d} (\frac{n-c\log n}{n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n-c\log n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} (\frac{n}{c\log n}-1) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} n \right)- \log_{n^d} \left(\frac{1}{n}\right)\\
-%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} - \log_{n^d} \left(\frac{1}{n}\right)\\
-%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} + \frac{1}{d}
-%\end{align*}
-%Thus for large enough values of $n$, $H_{n^d}(\frac{c\log n}{n})\leq 1/2 + O(\frac{c\log n}{dn}) \leq 2/3$, thus $1 - H_q(\frac{c\log n}{n})> 1-H_{n^d}(\frac{c\log n}{n} )> 1/3$.
-Taking $\epsilon  = 1/21/6$ the conditions of the corollary are satisfied.
 \end{proof}
 
-\ignore{
-\section{Possibility of Constructing Computational Fuzzy Extractors}\label{ssec:constructing comp fuzzy extractors}
-In the \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best constructible codes.
-Thus, some entropy drop seems necessary when considering $H^\hill_{\epsilon, s}(X | SS(X))$.
-However, in \propref{prop:prg comp fuzzy extractor}, we showed that a computational fuzzy extractor exists using a pseudorandom generator.
-A natural question is whether this is necessary.
-Do there exist clever constructions of computational fuzzy extractors that rely on the hardness of some cryptographic primitive that is easy within some distance $t$.
-We begin by recalling the important parameters of a computational fuzzy extractor:
-\begin{itemize}
-\item The input entropy $m$.
-\item The length of the output string $\ell$.  This output string is required to be $(\epsilon, s_{sec})$-pseudorandom.
-\item The accepting distance $t$.
-\end{itemize}
-We consider the possibility of constructing a computational fuzzy extractor based on the remaining entropy of $W$ conditioned on the string $P$~(generated by $(R, P)\leftarrow \gen(W)$).
-We first define a parameter $k_{prg}$.
-Let $k_{prg}$ be the smallest integer such that there exists a pseudorandom generator from $k_{prg}$ to at least $k_{prg}+1$ bits.
-More precisely, let $k_{prg}$ be the smallest integer such that there exists a deterministic function $prg:\{0,1\}^{k_{prg}}\rightarrow \{0,1 \}^{k_{prg}+1}$ such that $\forall D\in \mathcal{D}_s$: $\delta^D(prg(U_{k_{prg}}), U_{k_{prg}+1})<\epsilon$ for some negligible $\epsilon$ and super polynomial $s$.
-We now classify the existence of computational fuzzy extractors based on this parameter.
-Let $CODE$ be some error-correcting code with parameters, $(n, k, 2t+1)$.
-We define $|CODE| = n-k$.
-
-\begin{tabular}{c | c}
-Remaining Entropy & Constructible?\\\hline
-$CODE$ is computationally computable. & Yes, use \propref{prop:prg comp fuzzy extractor} \\
-$H_\infty (W) - |CODE|\geq k_{prg}$\\\hline
-$CODE$ exists, not necessarily efficiently computable. & Seems impossible to disprove, efficient\\
-$H_\infty(W) - |CODE|\geq k_{prg}$ & construction of $CODE$ admits \propref{prop:prg comp fuzzy extractor}.\\\hline
-Let $CODE$ be the best code. & Unknown, main area of interest\\
-$H_\infty(W) - |CODE|< k_{prg}\leq H_\infty(W)$\\\hline 
-$H_\infty(W)< k_{prg}$ & Seems to imply existence \\
-&of improved $prg$ by using $\gen$.
-\end{tabular}
-
-We begin by focusing on the last case where $H_\infty(W) < k_{prg}$.  We first introduce two concepts, efficiently-generatable sources and sources that are $prg$ qualified.
-
-\begin{definition}
-A distribution $W$ over $\mathcal{M}$ is \emph{$(s_{gen}, \ell)$-efficiently-generatable} if there exists a deterministic circuit $G$ of size at most $s_{gen}$ such that $W \overset{d}= G(U_{\ell})$.
-\end{definition}
-\begin{definition}
-A distribution $W$ over $\mathcal{M}$ is \emph{$(\epsilon, s, s_{f})$ - prg-qualified} if there exists a deterministic function $f:\mathcal{M}\rightarrow \{0,1\}^d$~(computable in space $s_{f}$) such that for all $D\in\mathcal{D}_s$, $\delta^D(f(W), U)<\epsilon$ and $d\geq k_{prg}$\footnote{We can extend this definition to allow $f$ to have public-randomness.
-The definition is not meaningful if $f$ has private randomness as $f$ can simply generate a fresh seed of length $d$.}.
-\end{definition}
-We use the term prg-qualified as the composition of $f$ and a $prg$ gives pseudorandom bits:
-\begin{proposition}
-Let $W$ over $\mathcal{M}$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution with function $f$ to $d$ bits.
-Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator~(computable by a circuit of size $s_{prg}$) where $k\leq d$.
-Then $\forall D\in\mathcal{D}_{\min\{s_W-s_{prg}, s_{sec}\}}$
-\[
-\delta^D(prg(f(W)_{1,..., k}), U_{k+1})< \epsilon_W + \epsilon_{prg}.
-\]
-\end{proposition}
-\begin{proof}
-Let $W$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution to $d$ bits.
-Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator where $k\leq d$.
-We proceed by contradiction.
-Suppose that $\exists D$ of size at most $s= \min\{s_W -s_{prg}, s_{sec}\}$ such that $\delta^D(prg(f(W)), U_{k+1})\geq \epsilon_W+\epsilon_{prg}$.
-By the triangle inequality, one has:
-\begin{align*}
-\epsilon_W+\epsilon_{prg}&\leq \delta^D(prg(f(W)_{1,...,k}), U_{k+1})\\
-&\leq \delta^D(prg(f(W)_{1,...,k}, prg(U_k)) + \delta^D(prg(U_k), U_{k+1})
-\end{align*}
-Thus, either $\delta^D(prg(f(W)_{1,...,k}, prg(U_k))\geq \epsilon_{W}$ or $\delta^D(prg(U_k), U_{k+1})\geq \epsilon_{prg}$.
-
-In the first case, we construct a distinguisher $D'$ that contradicts the $(\epsilon_W, s_W, s_{f})$-qualification of $W$.
-$D'$ upon receiving input $x\in \{0,1\}^d$ computes $D(prg(x))$ and outputs $D$'s answer.
-$D'$ is of size at most $s + s_{prg} \leq s_W-s_{prg}+s_{prg} = s_W$ and has advantage at least $\epsilon_W$.
-This is a contradiction.
-
-In the second case, $D$ immediately contradicts the $(\epsilon_{prg}, s_{sec})$ security of $prg$.  Thus, we have a contradiction in both cases.  This completes the proof.
-\end{proof}
-
-We now return to the question of whether we can build a computational fuzzy extractor when $H_\infty(W)<k_{prg}$.
-\begin{theorem}
-
-\end{theorem}
-\begin{proof}
-\bnote{Do the proof!}
-\end{proof}
-}
-%We now provide a candidate construction of fuzzy extractor based directly on a computational problem~(the LWE problem introduced by Regev~\cite{regevLWEsurvey}).
-%\begin{definition}
-%An $(\mathcal{M}, m, \tilde{m}, t, s_{dist}, \epsilon)$-\emph{computational secure sketch} is a pair of randomized algorithms, ``sketch'' (\sketch) and ``recover'' (\rec) with the following properties:
-%\begin{enumerate}
-%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns two strings, $(x,s)\in\{0,1\}^*$ where $x$ is drawn from a distribution $X$ and $\Hoo(X)\geq m$.
-%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of a computational secure sketches guarantees that if $d(w,w')\leq t$, then $Rec(w', SS(w)_2) = SS(w)_1$.
-%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, observing $SS(W)_2$ does not significantly help the adversary.
-That is, $H^\hill_{\epsilon, s_{dist}}(X | SS(W)_2)\geq \tilde{m}$.
-%\end{enumerate}
-%A secure sketch is \emph{efficient} if \sketch runs in expected polynomial time and \rec runs in expected polynomial time if $d(w', w) < t$.
-%\end{definition}
-%This definition has two significant changes from the definition of a secure sketch.
-First, we do not require that the distribution $X$ is equal to the input distribution $W$.
-This is because constructions will utilize computationally hard problems that may be difficult to invert.
-However, we can consider the special case where $X=W$.
-None of the power of a secure sketch is lost when $X\neq W$.
-
-%\textbf{Note: }  The entropy of $X$ is somehow limited by the entropy of $X$ we cannot completely hide some very high entropy string, using a low entropy string.
-This would have to be reflected in the parameters of \hill entropy but I am not yet sure how to formalize this.
-%
-% Furthermore, note there are two conditions on the distribution $X$, $\Hoo(X)\geq m$ and $H^\hill_{\epsilon, s}(X|SS(W)_2)\geq \tilde{m}$.
-This means that if an adversary does not see the helper value $s$ it has true entropy and its computational entropy is decrease by seeing $s$.
-
-%Second, we now require that the value $X$ only has conditional \hill entropy.
-Considering the special case where $m=\tilde{m}$ is interesting but constructions that improve on the $\tilde{m}$ achieved in secure sketch are interesting.
-Furthermore, it seems natural to consider the case where $|\rec|<s$ however, \rec has a significantly more difficult task, \rec must recover all of $x$ while the distinguisher in the conditional \hill entropy definition only needs to distinguish $x$ from a high average min-entropy distribution.
-%
-%Thus, we can define a stronger definition where all of these desiderata are achieved.  
-%
-%\begin{definition}
-%A $(\mathcal{M}, m, \tilde{m}, t, s, \epsilon)$-computational secure sketch is strong if the following properties hold:
-%\begin{enumerate}
-%\item Seeing $s$ does not decrease the conditional $\hill$ entropy of $X$.  That is, $m=\tilde{m}$.
-%\item There exists a circuit of \rec' where the size of \rec' is polynomial, $|\rec'|<s_{dist}$ and \rec' satisfies the correctness property.
-%\end{enumerate}
-%\end{definition}
-\ignore{
-\subsection{Learning With Errors (\class{LWE})}
-\label{subsec:LWE in detail}
-The LWE problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise".
-For positive integers $n$ and $q \ge 2$, a vector $\vect{s} \in \Fq$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{s}, \chi}$ be the distribution obtained by choosing a vector $\vect{a} \overset{\$}\leftarrow \Fq^n$ uniformly at random and a noise term $e \overset{\$}\leftarrow \chi$, and outputting $(\vect{a}, \langle \vect{a}, \vect{s}\rangle + e) \in (\Fq^m, \Fq)$.
-A formal definition follows.
-
-\label{sec:LWEoverview}
-\begin{problem}[\class{LWE}]\label{prob:LWE}
-Let $n$ be the security parameter.
-For a integer $q = q(n)$ and the error distribution $\chi = \chi(n)$ over $\Fq$, the Learning With Error problem $\class{LWE}_{n, m, q,\chi}$ is defined as follows: given access to an oracle that outputs $m$ samples from $A_{\vect{s}, \chi}$ for a uniformly random $\vect{s}$, output $\vect{s}$ with high probability.
-\end{problem}
-
-We will use the fixed form of the LWE assumption where a matrix is prepared ahead of time.
-The matrix form is as follows: $\class{LWE}$ find $\vect{x}$ given $(\vect{A},\vect{Ax+e})$, where $\vect{A}\leftarrow \Fq^{m \times n}$ is chosen uniformly and the error vector $\vect{e} \leftarrow \chi$.
-Results of Regev~\cite{regev2005LWE} and Peikert~\cite{peikert2009latticereduction} connect the hardness of the LWE problem to solving worst-case lattice problems.
-The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_\alpha$~(following the notation of~\cite{regev2005LWE}).
-We denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.
-Here we present the theorem of~\cite{regev2005LWE}.
-
-\begin{theorem}~\cite[Theorem 3.1]{regev2005LWE}
-Let $n$ be a security parameter and $q = q(n) \in\Fq^+$, let $\alpha = \alpha(n)\in (0,1)$ be such that $\alpha q > 2\sqrt{n}$.
-Let $\vA\in\Fq^{m\times n}, X\in \Fq^n$ be chosen uniformly at random and $E$ be chosen according to $\bar{\Psi}_\alpha$.
-If there exists a PPT-algorithm $\mathcal{I}$ such that $\Pr_{\vA, X, E}[X\leftarrow  \mathcal{I}(\vA, \vA X+E) ]>\epsilon$ for some noticeable $\epsilon$, then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem~(GAPSVP) and the shortest independent vectors problem~(SIVP) to within $\Omega(n/\alpha)$ in the worst case.
-\end{theorem}
-
-We will consider a generalized assumption of \probref{prob:LWE}:
-\begin{assumption}
-\label{assume:general LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ and $q=q(n)\geq 2$ be integers and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, \vA\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{I}$ of size at most $s$
-\[
-\Pr_{\vA, X, E}[X\leftarrow \mathcal{I}(\vA, \vA X+E)]<\epsilon
-\]
-\end{assumption}
-Furthermore, Regev shows a decision to search equivalence for $q=\poly(n)$, so we can consider an equivalent indistinguishability formulation:
-\begin{assumption}
-\label{assume:indist LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, A\in\Fq^{m\times n}, B\in\Fq^m$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{D}$ of size at most $s$:
-\[
-\Pr[D(\vA, \vA X+E)=1]-\Pr[D(\vA, B)=1]<\epsilon
-\]
-\end{assumption}
-We can restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy~(see Definition~\ref{def:unp entropy}).  
-}
-
-%\section{\lemref{lem:conversion to unpredictability}}
-%\label{sec:proof of unpred conversion}
-%In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.
-%We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).
-Thus, we have the following claim:
-%%\begin{claim}
-%%\label{lem:unp of x and e}
-%%Let $A, X, E$ be as above, then:
-%%\begin{itemize}
-%%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
-%%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
-%%\end{itemize}
-%%\end{claim}
-%%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
-%%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
-%%\begin{assumption}
-%%\label{assume:entropy LWE}
-%%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.
-%%\end{assumption}
-%%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
-%We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.
-This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
-We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
-%\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-%\label{lem:many hardcore bits}
-%Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
-Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
-%\end{lemma}
-%
-%\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
-%Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
-Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.
-Then according to \lemref{lem:many hardcore bits} we know that $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA , \vA X+E)\geq k\log q$.
-By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.
-To expand to $E$ we use the following claim:
-%
-%\begin{claim}
-%Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
-%\[
-%H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
-%\]
-%\end{claim}
-%%\begin{claim}
-%%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
-%%\end{claim}
-%%\begin{proof}
-%%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
-Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
-Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.
-This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
-%%\end{claim}
-%%\begin{proof}
-%%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
-%%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.
-Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
-Furthermore, let $C$ be a circuit of size at most $s_{sec}'$ where $\Pr[C(Z) = Y] > 2^{-k}$.
-Define the circuit $C'$ that outputs the first $k$ bits of $C$'s output.
-Thus, $\Pr[C'(Z) = Y_{1,..., k}] \geq \Pr[C(Z) = Y] > 2^{-k}$.
-Note that $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,...,k}, Z), (Y_{1,..., k}, Z))<\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
-Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
-%%This completes the claim.
-%%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.
-In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
-%% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
-Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
-Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.
-This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
-%%\end{claim}
-%%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.
-This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.
-Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
-%%
-%%
-%%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.
-By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.
-This completes the proof of \lemref{lem:conversion to unpredictability}.
-%%\end{proof}
-%\begin{proof}
-%Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.
-We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.
-That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}'}}((E, \vA X+E), (Y, \vA+E))\leq \epsilon$, there exists $C$ of size $s_{sec}'$ such that $\Pr[C(\vA, \vA X+E) = Y]> 2^{-\ell}$.
-Fix one such $Y$.
-Let $\mathcal{E}$ be the event that $A_{1,..., n}^{-1}$ exists.
-Note that $\mathcal{E}$ occurs with probability $1-\gamma$.
-%
-%Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
-%\begin{align*}
-%\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
-%\end{align*}
-%Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
-Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$.
-Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.
-%
-%We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
-%\begin{enumerate}
-%\item Input $(\vA, \vA X+E)$.
-%\item Run $y\leftarrow C(\vA, \vA X+E)$.
-%\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
-%\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
-%\end{enumerate}
-%Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
-Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.
-Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
-%\end{proof}
-%
-%The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
-%%\begin{proof}[Proof of \clref{lem:unp of x and e}]
-%%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
-That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
-Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(\vA, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Output $z = \vA y - \vA X+E$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
-%%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
-%%\end{align*}
-%%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
-That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((E, \vA, \vA X+E), (Y, \vA, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
-Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(A, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
-%%\item Output $z = \vA^{-1}(\vA X+E-y)$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
-For sufficient parameter sizes the probability of $A^{-1}$ not existing is negligible.
-Denote this probability by $\gamma$.
-Then note that $\Pr[I'(\vA, \vA X+E) = Z] > 2^{-k}-\gamma = 2^{-k'}$.
-Then one has the following~(conditioned on the event that $\vA^{-1}$ exists):
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
-%%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
-%%\end{align*}
-%%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
-%%\end{proof}
-%
-%\end{proof}
-
-\ignore{
-\section{Proof of Theorem \ref{thm:blockLWE}}
-\label{sec:proof of block theorem}
-
-\begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.
-If the blocks are fixed to some other value the reduction is essentially the same.
-
-Let $D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.
-That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
-Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.
-We assume that,
-\[
-|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
-\]
-
-We build a distinguish $\D'$ that distinguishes standard LWE instances from uniform.
-Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-Our goal is to prepare a random block fixing instance from the random instance we are given.
-The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
-
-It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
-\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
-\end{enumerate}
-\begin{figure}
-\begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.
-
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)$.
-\item \label{step:randomization}
-For {$i=1\ldots m+\alpha$}:
-\subitem Randomly generate $(\gamma_{i,1},\ldots, \gamma_{i,\alpha}) \leftarrow \Fq^\alpha$.
- \subitem For {$j = 1 \ldots n+\alpha$}:
-\subsubitem Set $A_{ij} \leftarrow A^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}$
-\subsubitem Set $b_i \leftarrow b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k}$
-\item Run $\D$ on input $\vA, \vb$.
-\item Output $\D$'s output.
-\end{enumerate}
-\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-
+We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
 \begin{claim}
-\label{cl:randomMatrixDist}
-The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix.
+\label{cl:full rank matrix}
+Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
+let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \alpha q^{\beta}$.
 \end{claim}
 \begin{proof}
-In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
-Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.
-Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.
-Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5.
-For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number.
-Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors.
-Therefore, the entire matrix $\vA$ is a truly random matrix.
-This completes the claim.
+The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
+By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
+\begin{align*}
+\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
+\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }= \alpha q^{-\beta}.
+\end{align*}
 \end{proof}
-\begin{claim}
-\label{cl:random ax+e}
-If $\D'$ is provided with input distributed as $\vA', \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i} = b_{m+i}^*$ is uniformly generated otherwise and  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
-\end{claim}
-\begin{proof}
-Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then define $\vx^*$ as:
-\[
-x^*_i = \begin{cases}
-x_i', & \text{if }1\leq i\leq n \\
-b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
-\end{cases}
-\]
-Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).
-Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
-%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).
-Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
-%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
-The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-\bnote{We need to justify these steps better.}
-\bnote{Is it really standard to go to lower case for the rows?}
-\xnote{lower case for vectors, which is row vector in the matrix}
-
-\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
-We have the following for all $i=1,..., m+\alpha$:
-\begin{align*}
-\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
-& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
-&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
-\end{align*}
-%\begin{align*}
-%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
-%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
-%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
-%& = b_i \label{reductionEq}
-%\end{align*}
-\end{proof}
-\begin{claim} 
-\label{clm:random b}
-If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
-\end{claim}
-\begin{proof}
-Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.
-After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
-\[
-b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
-\]
-%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each
-
-$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{It need show more work on this, maybe?}
-Thus, each of these values is uniformly and independently random.
-\end{proof}
-
-%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$.
-%
-%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$.
-Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
-%\begin{align*}
-%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
-%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
-%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
-%\end{align*}
-
-\begin{claim}
-If the pair $(\vA', \vb')$ is uniformly distributed, then the pair $(\vA, \vb)$ is uniformly distributed.
-\end{claim}
-\begin{proof}
-Assume that $(\vA', \vb')$ is uniformly distributed.
-By \clref{cl:randomMatrixDist}, $\vA$ is uniformly distributed.
-Thus, it suffices to show that $\vb | \vA$ is uniformly distributed.
-Let $\vb^*$ be the vector generated in step~\ref{step:b generation} and note that $\vb^*$ is uniformly random.
-We show  a stronger claim that $\vb |( \vA, \vA', \vR)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i,j}$.
-
- The matrix $\vgamma$ is a deterministic function of $(\vA, \vA', \vR)$.
-Thus, $\vb | (\vA, \vA', \vR) \overset{d}= \vb | (\vA, \vA', \vR, \vgamma)$.
-The only dependence of $\vb$ on $(\vA, \vA', \vR, \vgamma)$ is in the matrix $\vgamma$.
-Thus, $ \vb | (\vA, \vA', \vR, \vgamma) \overset{d}= \vb | \vgamma$.
-Recall that $\vb = \vb^* +  \left(\begin{array}{c | c}\mathbf{0} &\vgamma\end{array}\right)\vb^*$.
-Let $\vT = \vect{I}+  \left(\begin{array}{c | c}\mathbf{0} & \vgamma \end{array}\right)$.
-Since $\vT$ is a deterministic function of $\vgamma$, $\vb | \vgamma \overset{d} = \vb | \vT$.
-
- \bnote{Now we want to say that $\vb$ is uniformly distributed since $\vb'$ is.
-If $\vT$ exists we can just that $\vb | \vT = (\vT^{-1} \vb )| \vT = \vb' | \vT = U | \vT$.
-It does with very high probability, but I don't want to add this restriction.
-Is there a way to get around this problem?}
-%\[
-%\vA=  \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)
-%\]
-%\begin{align*}
-%(\vA, \vb) =  \left(\left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) \right) , \left(\vb' + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \vb'\right)
-%\end{align*}
-\end{proof}
-\bnote{Remember this isn't good enough.  We need the enhanced claim above.}
-Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
-\begin{align*}
-&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
-& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
-\end{align*}
-%==========
-\ignore{
-Before randomized:
-$$\vA'\vx' + \ve = \vb'$$
-For $i = 1\ldots m$,
-$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
-For $i = 1\ldots \alpha$,
-$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
-}
-\end{proof}
-}
 
@@
 \end{figure}
-The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
+The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
 \begin{claim}
-\label{cl:full rank matrix}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.\lnote{what is $n$?}
+\label{cl:full rank matrix 5.2}
+Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
 \end{claim}
 \begin{proof}
-The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
-By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
-\begin{align*}
-\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
-\end{align*}
-Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
+Direct application of \clref{cl:full rank matrix} when $\alpha = \poly(n)$ and $\beta = \omega(1)$ in $n$.
 \end{proof}
@@
 \end{eqnarray*}
-(the second to last line follows from \clref{cl:full rank matrix} \lnote{actually, it doesn't -- \clref{cl:full rank matrix} doesn't have an exponential bound}).
+(the second to last line follows from \clref{cl:full rank matrix} when $\alpha, \beta = O(n)$ \bnote{need to say this is a randomly generated matrix, but there are previous iterations.
+I know we abort if we find a non full rank matrix but this still bothers me.}).
 
@@
 
-The probability that the code generated by $\vA$ has distance lower than $2t+1$ is at most $e^{-\Omega(n)}$ (see \corref{cor:code high distance}), and so is the probability of ouptutting $\perp$, computed above.
+The probability that the code generated by $\vA$ has distance lower than $2t+1$ is at most $e^{-\Omega(n)}$ (see \corref{cor:code high distance}), the probability of outputting $\perp$ is also $e^{-\Omega(n)}$~(computed above).
 This gives the correctness bound for $\decode_t$.

### 2013-06-20 CompFuzzExt.tex
notation and explanations changed in 4.1, 4.2 and C.4

@@
 \newcommand{\zo}{\ensuremath{\{0, 1\}}}
-\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
+\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
 \newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
@@
 \begin{construction}
-Let $n$ be a security parameter and let $m> n$\bnote{should we just switch to $m\ge 3n$ here?}.
-Let $q$ be a prime.
-%Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.
+Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
 Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
@@
 \item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
-\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
-\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
+\item Sample $\vA\in\Fq^{m\times n}, \vx\in\Fq^n$ uniformly.
+\item Compute $p = (\vA, \vA \vx+w)$, \\\ $r = \vx_{1,...,n/2}$.
 \item Output $(r, p)$.
@@
 \item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
-\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{B}=\vect{C}-w'$.
-\item Let $X = \decode_t(\vA, \vect{B})$\\
-\item Output $r = X_{1,...,n/2}$.
+\item Parse $p$ as $(\vA, \vect{c})$; let $\vb=\vect{c}-w'$.
+\item Let $x = \decode_t(\vA, \vb)$\\
+\item Output $r = x_{1,...,n/2}$.
 \end{enumerate}
@@
 \label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integers $n, m$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ \bnote{only two places we use this notation.}be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$.
-%The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.
-
-\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime (unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding)\bnote{does this belong in a definition?}.
-The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ \bnote{only two places we use this notation.} for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
+The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." We now recall the definition of the decisional version of the problem.
+
+\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
+Let $n$ be a security parameter.  
+Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime\footnote{%
+Unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding.}.
+%
+Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $X$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
+ The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
+$(\vA, \vA X+\chi)$ from
+ the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
 
@@
 
- Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as stated in the following proposition.
-%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
-%Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
-%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):
-
-\begin{proposition} 
-\bnote{Why is this not a theorem?  For example Theorem 1 from Reg05?}
-\label{assume:entropy LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$.
-Let $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
-If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho}$ is secure.
-
-%H^{\unp}_{\epsilon, s_{sec}}(X | \vA, \vA X+E) =H^{\unp}_{\epsilon, s'_{sec}}(E| \vA, \vA X+E) \geq n\log q $ for $s'_{sec}\approx s_{sec}$.  
-\end{proposition}
+ Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
+Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
+If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.
 
@@
 %\label{subsec:LWE uniform error}
-Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\bnote{Their reduction is ultimately to the same problems not to Gaussian LWE}\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
-The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}).
+Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
+The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
 This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.
@@
 Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$.
-If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$,  $\distLWE_{n, m, q, \chi}$ is secure.
+If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]^m$,  $\distLWE_{n, m, q, \chi}$ is secure.
 \end{lemma}
 
-To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits\bnote{Do we need to cite anything about hardcore?}.
+To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has simultaneously many hardcore bits.
 The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
@@
 \begin{enumerate}
-\item Input $\vA , \vB = \vA X + W - W'$
+\item Input $\vA , \vb = \vA \vx + w - w'$
 \item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, \vB$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vB_{i_1,...,i_{2n}}$.
+\item Restrict $\vA, \vb$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vb_{i_1,...,i_{2n}}$.
 \item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
-If no such rows exist go to step (2).
-\item Denote by $\vA', \vB'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vB_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
-\item If $\vB- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
-\item Output $X'$.
+If no such rows exist, output $\perp$ and stop.
+\item Denote by $\vA', \vb'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vb_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $\vx' = (\vA')^{-1}\vb'$.  
+\item If $\vb- \vA \vx'$ has more than $t$ nonzero coordinates, go to step (2).
+\item Output $\vx'$.
 \end{enumerate}
@@
 Each step is computable in time $O(n^3)$. 
-For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows), and $\vA_{i_1,...,i_{2n}}$ has rank  $n$.
-If this happens, then $X'=X$, and the algorithm terminates.
-However, we also need to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.
-This detection will happen if $B-\vA X' = \vA (X-X')+(W-W')$ has more than $t$ nonzero coordinates.
-It suffices to ensure that $\vA (X-X')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $W-W'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
+For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $w$ and $w'$ agree on those rows).
+If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $\vx'=\vx$, and the algorithm terminates.
+However, we also need to ensure correctness: we need to make sure that if $\vx'\neq \vx$, we detect it in step 6.
+This detection will happen if $\vb-\vA \vx' = \vA (\vx-\vx')+(w-w')$ has more than $t$ nonzero coordinates.
+It suffices to ensure that $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $w-w'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
 
@@
 Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$ (the expectation is taken over the input distribution\bnote{this needs to be more precise} $\vA, \vA X+W - W'$).
-It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$).
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this expectation is over the choice of random coins of $\decode_t$, regardless of the input, as long as $\dis(w, w')\le t$).
+It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
 \end{lemma}
-\textbf{Note:}
-Even though we are correcting $O(\log n)$ errors, this corresponds to a super polynomial number of possible error patterns; the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.
-Furthermore, if we consider the setting of $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3)$ field operations (this does not immediately follow from \lemref{lem:i t poly time}, but requires a simple reanalysis).
-Our main theorems get  better parameters when  $t\leq m/n-2$.
 
@@
 \label{thm:lossless secure extractor log}
-Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d<c$ be a positive constant \bnote{need to describe $d$} and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
+Let $n$ be a security parameter and let the number of errors $t = c\log n$ for some positive constant $c$.
+Let $d$ be a positive constant (giving us a tradeoff between running time of $\rep$ and $|w|$).
+Consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
@@
 The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.
-Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.
-In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$\bnote{this sentence worries me a little}.
-In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.
+In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes, because decoding algorithms will not reach the information-theoretic decoding radius.
 
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d<c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
+Let $d\le c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
 Let $\mathcal{M} = Z^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
 Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |Z|)$-symbol fixing sources.  If GAPSVP and SIVP are hard to approximate within polynomial factors 
-%\lnote{removed (on lattices of dimension $n/6$)} 
 using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
@@
 \end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.
-
-% and note that there $\exists \epsilon$ where $0<\epsilon< 1-H_q(\frac{c\log n}{2n})< 1-H_q(\frac{c\log n}{m})$ and $1-H_q(c\log n/n) -\epsilon =1/2$ or equivalently $H_q(c\log n/n)+\epsilon = 1/2$.
-Let $d$ be some constant such that $q< n^d$.
-Consider the value of $H_q(\frac{c\log n}{n})$:
-%\begin{align*}
-%H_q(\frac{c\log n}{n})&\leq  H_{n^d}(\frac{c\log n}{n})\\
-%&=\frac{c\log n}{n} \log_{n^d}(n^d-1) - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} (1-\frac{c\log n}{n})\\
-%&\leq \frac{c\log n}{n}  - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n})-\log_{n^d} (\frac{n-c\log n}{n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n-c\log n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} (\frac{n}{c\log n}-1) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
-%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} n \right)- \log_{n^d} \left(\frac{1}{n}\right)\\
-%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} - \log_{n^d} \left(\frac{1}{n}\right)\\
-%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} + \frac{1}{d}
-%\end{align*}
-%Thus for large enough values of $n$, $H_{n^d}(\frac{c\log n}{n})\leq 1/2 + O(\frac{c\log n}{dn}) \leq 2/3$, thus $1 - H_q(\frac{c\log n}{n})> 1-H_{n^d}(\frac{c\log n}{n} )> 1/3$.
-Taking $\epsilon  = 1/21/6$ the conditions of the corollary are satisfied.
 \end{proof}
 
-\ignore{
-\section{Possibility of Constructing Computational Fuzzy Extractors}\label{ssec:constructing comp fuzzy extractors}
-In the \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best constructible codes.
-Thus, some entropy drop seems necessary when considering $H^\hill_{\epsilon, s}(X | SS(X))$.
-However, in \propref{prop:prg comp fuzzy extractor}, we showed that a computational fuzzy extractor exists using a pseudorandom generator.
-A natural question is whether this is necessary.
-Do there exist clever constructions of computational fuzzy extractors that rely on the hardness of some cryptographic primitive that is easy within some distance $t$.
-We begin by recalling the important parameters of a computational fuzzy extractor:
-\begin{itemize}
-\item The input entropy $m$.
-\item The length of the output string $\ell$.  This output string is required to be $(\epsilon, s_{sec})$-pseudorandom.
-\item The accepting distance $t$.
-\end{itemize}
-We consider the possibility of constructing a computational fuzzy extractor based on the remaining entropy of $W$ conditioned on the string $P$~(generated by $(R, P)\leftarrow \gen(W)$).
-We first define a parameter $k_{prg}$.
-Let $k_{prg}$ be the smallest integer such that there exists a pseudorandom generator from $k_{prg}$ to at least $k_{prg}+1$ bits.
-More precisely, let $k_{prg}$ be the smallest integer such that there exists a deterministic function $prg:\{0,1\}^{k_{prg}}\rightarrow \{0,1 \}^{k_{prg}+1}$ such that $\forall D\in \mathcal{D}_s$: $\delta^D(prg(U_{k_{prg}}), U_{k_{prg}+1})<\epsilon$ for some negligible $\epsilon$ and super polynomial $s$.
-We now classify the existence of computational fuzzy extractors based on this parameter.
-Let $CODE$ be some error-correcting code with parameters, $(n, k, 2t+1)$.
-We define $|CODE| = n-k$.
-
-\begin{tabular}{c | c}
-Remaining Entropy & Constructible?\\\hline
-$CODE$ is computationally computable. & Yes, use \propref{prop:prg comp fuzzy extractor} \\
-$H_\infty (W) - |CODE|\geq k_{prg}$\\\hline
-$CODE$ exists, not necessarily efficiently computable. & Seems impossible to disprove, efficient\\
-$H_\infty(W) - |CODE|\geq k_{prg}$ & construction of $CODE$ admits \propref{prop:prg comp fuzzy extractor}.\\\hline
-Let $CODE$ be the best code. & Unknown, main area of interest\\
-$H_\infty(W) - |CODE|< k_{prg}\leq H_\infty(W)$\\\hline 
-$H_\infty(W)< k_{prg}$ & Seems to imply existence \\
-&of improved $prg$ by using $\gen$.
-\end{tabular}
-
-We begin by focusing on the last case where $H_\infty(W) < k_{prg}$.  We first introduce two concepts, efficiently-generatable sources and sources that are $prg$ qualified.
-
-\begin{definition}
-A distribution $W$ over $\mathcal{M}$ is \emph{$(s_{gen}, \ell)$-efficiently-generatable} if there exists a deterministic circuit $G$ of size at most $s_{gen}$ such that $W \overset{d}= G(U_{\ell})$.
-\end{definition}
-\begin{definition}
-A distribution $W$ over $\mathcal{M}$ is \emph{$(\epsilon, s, s_{f})$ - prg-qualified} if there exists a deterministic function $f:\mathcal{M}\rightarrow \{0,1\}^d$~(computable in space $s_{f}$) such that for all $D\in\mathcal{D}_s$, $\delta^D(f(W), U)<\epsilon$ and $d\geq k_{prg}$\footnote{We can extend this definition to allow $f$ to have public-randomness.
-The definition is not meaningful if $f$ has private randomness as $f$ can simply generate a fresh seed of length $d$.}.
-\end{definition}
-We use the term prg-qualified as the composition of $f$ and a $prg$ gives pseudorandom bits:
-\begin{proposition}
-Let $W$ over $\mathcal{M}$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution with function $f$ to $d$ bits.
-Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator~(computable by a circuit of size $s_{prg}$) where $k\leq d$.
-Then $\forall D\in\mathcal{D}_{\min\{s_W-s_{prg}, s_{sec}\}}$
-\[
-\delta^D(prg(f(W)_{1,..., k}), U_{k+1})< \epsilon_W + \epsilon_{prg}.
-\]
-\end{proposition}
-\begin{proof}
-Let $W$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution to $d$ bits.
-Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator where $k\leq d$.
-We proceed by contradiction.
-Suppose that $\exists D$ of size at most $s= \min\{s_W -s_{prg}, s_{sec}\}$ such that $\delta^D(prg(f(W)), U_{k+1})\geq \epsilon_W+\epsilon_{prg}$.
-By the triangle inequality, one has:
-\begin{align*}
-\epsilon_W+\epsilon_{prg}&\leq \delta^D(prg(f(W)_{1,...,k}), U_{k+1})\\
-&\leq \delta^D(prg(f(W)_{1,...,k}, prg(U_k)) + \delta^D(prg(U_k), U_{k+1})
-\end{align*}
-Thus, either $\delta^D(prg(f(W)_{1,...,k}, prg(U_k))\geq \epsilon_{W}$ or $\delta^D(prg(U_k), U_{k+1})\geq \epsilon_{prg}$.
-
-In the first case, we construct a distinguisher $D'$ that contradicts the $(\epsilon_W, s_W, s_{f})$-qualification of $W$.
-$D'$ upon receiving input $x\in \{0,1\}^d$ computes $D(prg(x))$ and outputs $D$'s answer.
-$D'$ is of size at most $s + s_{prg} \leq s_W-s_{prg}+s_{prg} = s_W$ and has advantage at least $\epsilon_W$.
-This is a contradiction.
-
-In the second case, $D$ immediately contradicts the $(\epsilon_{prg}, s_{sec})$ security of $prg$.  Thus, we have a contradiction in both cases.  This completes the proof.
-\end{proof}
-
-We now return to the question of whether we can build a computational fuzzy extractor when $H_\infty(W)<k_{prg}$.
-\begin{theorem}
-
-\end{theorem}
-\begin{proof}
-\bnote{Do the proof!}
-\end{proof}
-}
-%We now provide a candidate construction of fuzzy extractor based directly on a computational problem~(the LWE problem introduced by Regev~\cite{regevLWEsurvey}).
-%\begin{definition}
-%An $(\mathcal{M}, m, \tilde{m}, t, s_{dist}, \epsilon)$-\emph{computational secure sketch} is a pair of randomized algorithms, ``sketch'' (\sketch) and ``recover'' (\rec) with the following properties:
-%\begin{enumerate}
-%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns two strings, $(x,s)\in\{0,1\}^*$ where $x$ is drawn from a distribution $X$ and $\Hoo(X)\geq m$.
-%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of a computational secure sketches guarantees that if $d(w,w')\leq t$, then $Rec(w', SS(w)_2) = SS(w)_1$.
-%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, observing $SS(W)_2$ does not significantly help the adversary.
-That is, $H^\hill_{\epsilon, s_{dist}}(X | SS(W)_2)\geq \tilde{m}$.
-%\end{enumerate}
-%A secure sketch is \emph{efficient} if \sketch runs in expected polynomial time and \rec runs in expected polynomial time if $d(w', w) < t$.
-%\end{definition}
-%This definition has two significant changes from the definition of a secure sketch.
-First, we do not require that the distribution $X$ is equal to the input distribution $W$.
-This is because constructions will utilize computationally hard problems that may be difficult to invert.
-However, we can consider the special case where $X=W$.
-None of the power of a secure sketch is lost when $X\neq W$.
-
-%\textbf{Note: }  The entropy of $X$ is somehow limited by the entropy of $X$ we cannot completely hide some very high entropy string, using a low entropy string.
-This would have to be reflected in the parameters of \hill entropy but I am not yet sure how to formalize this.
-%
-% Furthermore, note there are two conditions on the distribution $X$, $\Hoo(X)\geq m$ and $H^\hill_{\epsilon, s}(X|SS(W)_2)\geq \tilde{m}$.
-This means that if an adversary does not see the helper value $s$ it has true entropy and its computational entropy is decrease by seeing $s$.
-
-%Second, we now require that the value $X$ only has conditional \hill entropy.
-Considering the special case where $m=\tilde{m}$ is interesting but constructions that improve on the $\tilde{m}$ achieved in secure sketch are interesting.
-Furthermore, it seems natural to consider the case where $|\rec|<s$ however, \rec has a significantly more difficult task, \rec must recover all of $x$ while the distinguisher in the conditional \hill entropy definition only needs to distinguish $x$ from a high average min-entropy distribution.
-%
-%Thus, we can define a stronger definition where all of these desiderata are achieved.  
-%
-%\begin{definition}
-%A $(\mathcal{M}, m, \tilde{m}, t, s, \epsilon)$-computational secure sketch is strong if the following properties hold:
-%\begin{enumerate}
-%\item Seeing $s$ does not decrease the conditional $\hill$ entropy of $X$.  That is, $m=\tilde{m}$.
-%\item There exists a circuit of \rec' where the size of \rec' is polynomial, $|\rec'|<s_{dist}$ and \rec' satisfies the correctness property.
-%\end{enumerate}
-%\end{definition}
-\ignore{
-\subsection{Learning With Errors (\class{LWE})}
-\label{subsec:LWE in detail}
-The LWE problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise".
-For positive integers $n$ and $q \ge 2$, a vector $\vect{s} \in \Fq$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{s}, \chi}$ be the distribution obtained by choosing a vector $\vect{a} \overset{\$}\leftarrow \Fq^n$ uniformly at random and a noise term $e \overset{\$}\leftarrow \chi$, and outputting $(\vect{a}, \langle \vect{a}, \vect{s}\rangle + e) \in (\Fq^m, \Fq)$.
-A formal definition follows.
-
-\label{sec:LWEoverview}
-\begin{problem}[\class{LWE}]\label{prob:LWE}
-Let $n$ be the security parameter.
-For a integer $q = q(n)$ and the error distribution $\chi = \chi(n)$ over $\Fq$, the Learning With Error problem $\class{LWE}_{n, m, q,\chi}$ is defined as follows: given access to an oracle that outputs $m$ samples from $A_{\vect{s}, \chi}$ for a uniformly random $\vect{s}$, output $\vect{s}$ with high probability.
-\end{problem}
-
-We will use the fixed form of the LWE assumption where a matrix is prepared ahead of time.
-The matrix form is as follows: $\class{LWE}$ find $\vect{x}$ given $(\vect{A},\vect{Ax+e})$, where $\vect{A}\leftarrow \Fq^{m \times n}$ is chosen uniformly and the error vector $\vect{e} \leftarrow \chi$.
-Results of Regev~\cite{regev2005LWE} and Peikert~\cite{peikert2009latticereduction} connect the hardness of the LWE problem to solving worst-case lattice problems.
-The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_\alpha$~(following the notation of~\cite{regev2005LWE}).
-We denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.
-Here we present the theorem of~\cite{regev2005LWE}.
-
-\begin{theorem}~\cite[Theorem 3.1]{regev2005LWE}
-Let $n$ be a security parameter and $q = q(n) \in\Fq^+$, let $\alpha = \alpha(n)\in (0,1)$ be such that $\alpha q > 2\sqrt{n}$.
-Let $\vA\in\Fq^{m\times n}, X\in \Fq^n$ be chosen uniformly at random and $E$ be chosen according to $\bar{\Psi}_\alpha$.
-If there exists a PPT-algorithm $\mathcal{I}$ such that $\Pr_{\vA, X, E}[X\leftarrow  \mathcal{I}(\vA, \vA X+E) ]>\epsilon$ for some noticeable $\epsilon$, then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem~(GAPSVP) and the shortest independent vectors problem~(SIVP) to within $\Omega(n/\alpha)$ in the worst case.
-\end{theorem}
-
-We will consider a generalized assumption of \probref{prob:LWE}:
-\begin{assumption}
-\label{assume:general LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ and $q=q(n)\geq 2$ be integers and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, \vA\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{I}$ of size at most $s$
-\[
-\Pr_{\vA, X, E}[X\leftarrow \mathcal{I}(\vA, \vA X+E)]<\epsilon
-\]
-\end{assumption}
-Furthermore, Regev shows a decision to search equivalence for $q=\poly(n)$, so we can consider an equivalent indistinguishability formulation:
-\begin{assumption}
-\label{assume:indist LWE}
-Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, A\in\Fq^{m\times n}, B\in\Fq^m$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{D}$ of size at most $s$:
-\[
-\Pr[D(\vA, \vA X+E)=1]-\Pr[D(\vA, B)=1]<\epsilon
-\]
-\end{assumption}
-We can restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy~(see Definition~\ref{def:unp entropy}).  
-}
-
-%\section{\lemref{lem:conversion to unpredictability}}
-%\label{sec:proof of unpred conversion}
-%In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.
-%We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).
-Thus, we have the following claim:
-%%\begin{claim}
-%%\label{lem:unp of x and e}
-%%Let $A, X, E$ be as above, then:
-%%\begin{itemize}
-%%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
-%%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
-%%\end{itemize}
-%%\end{claim}
-%%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
-%%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
-%%\begin{assumption}
-%%\label{assume:entropy LWE}
-%%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.
-If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.
-%%\end{assumption}
-%%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
-%We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.
-This says that if $\distLWE$ is hard then $X$ has many hardcore bits.
-We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
-%\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-%\label{lem:many hardcore bits}
-%Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.
-Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.
-Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
-%\end{lemma}
-%
-%\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
-%Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.
-Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.
-Then according to \lemref{lem:many hardcore bits} we know that $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA , \vA X+E)\geq k\log q$.
-By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.
-To expand to $E$ we use the following claim:
-%
-%\begin{claim}
-%Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
-%\[
-%H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
-%\]
-%\end{claim}
-%%\begin{claim}
-%%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
-%%\end{claim}
-%%\begin{proof}
-%%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
-Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
-Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.
-This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
-%%\end{claim}
-%%\begin{proof}
-%%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
-%%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.
-Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
-Furthermore, let $C$ be a circuit of size at most $s_{sec}'$ where $\Pr[C(Z) = Y] > 2^{-k}$.
-Define the circuit $C'$ that outputs the first $k$ bits of $C$'s output.
-Thus, $\Pr[C'(Z) = Y_{1,..., k}] \geq \Pr[C(Z) = Y] > 2^{-k}$.
-Note that $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,...,k}, Z), (Y_{1,..., k}, Z))<\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.
-Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
-%%This completes the claim.
-%%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.
-In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
-%% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.
-Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.
-Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.
-This completes the claim.
-%%\end{proof}
-%
-%%\begin{claim}
-%%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
-%%\end{claim}
-%%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.
-This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.
-Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
-%%
-%%
-%%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.
-By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.
-This completes the proof of \lemref{lem:conversion to unpredictability}.
-%%\end{proof}
-%\begin{proof}
-%Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.
-We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.
-That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}'}}((E, \vA X+E), (Y, \vA+E))\leq \epsilon$, there exists $C$ of size $s_{sec}'$ such that $\Pr[C(\vA, \vA X+E) = Y]> 2^{-\ell}$.
-Fix one such $Y$.
-Let $\mathcal{E}$ be the event that $A_{1,..., n}^{-1}$ exists.
-Note that $\mathcal{E}$ occurs with probability $1-\gamma$.
-%
-%Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
-%\begin{align*}
-%\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
-%&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
-%\end{align*}
-%Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.
-Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$.
-Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.
-%
-%We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
-%\begin{enumerate}
-%\item Input $(\vA, \vA X+E)$.
-%\item Run $y\leftarrow C(\vA, \vA X+E)$.
-%\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
-%\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
-%\end{enumerate}
-%Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.
-Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.
-Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
-%\end{proof}
-%
-%The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
-%%\begin{proof}[Proof of \clref{lem:unp of x and e}]
-%%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.
-That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
-Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(\vA, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Output $z = \vA y - \vA X+E$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
-%%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((\vA X, \vA, \vA X+E), (\vA Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'}((X, \vA, \vA X+E), (Y, \vA, \vA X+E)) \leq \epsilon.
-%%\end{align*}
-%%Now suppose that $H^\unp_{\epsilon, s}(E | A, \vA X+E)<k$.
-That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((E, \vA, \vA X+E), (Y, \vA, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.
-Define $I'$ by the following:
-%%\begin{enumerate}
-%%\item Input $(A, \vA X+E)$.
-%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
-%%\item Try to compute $\vA^{-1}$, if $\vA^{-1}$ does not exist output $\perp$.
-%%\item Output $z = \vA^{-1}(\vA X+E-y)$.
-%%\end{enumerate}
-%%Note that $|I'|\approx |I|$.
-For sufficient parameter sizes the probability of $A^{-1}$ not existing is negligible.
-Denote this probability by $\gamma$.
-Then note that $\Pr[I'(\vA, \vA X+E) = Z] > 2^{-k}-\gamma = 2^{-k'}$.
-Then one has the following~(conditioned on the event that $\vA^{-1}$ exists):
-%%\begin{align*}
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
-%%\delta^{\mathcal{D}_s'} ((X, \vA, \vA X+E), (\vA^{-1}(\vA X+E-Y), \vA, \vA X+E)) \\
-%%&\leq \delta^{\mathcal{D}_s'} ((\vA^{-1}E, \vA, \vA X+E), (\vA^{-1}Y, \vA, \vA X+E))\\
-%%&\leq \delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Y, \vA, \vA X+E))\leq \epsilon
-%%\end{align*}
-%%Since $A^{-1}$ exists with probability $1-\gamma$ we obtain total distance at most $\epsilon(1-\gamma)=\epsilon'$.
-%%\end{proof}
-%
-%\end{proof}
-
-\ignore{
-\section{Proof of Theorem \ref{thm:blockLWE}}
-\label{sec:proof of block theorem}
-
-\begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.
-If the blocks are fixed to some other value the reduction is essentially the same.
-
-Let $D$ be a distinguisher that can distinguish $(m+\alpha)$ $\LWE$ instances from uniform where $\alpha$ of the equations have no error added.
-That is, let $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha)}$, let $\vx$ be uniform over $\Fq^{(n+\alpha)}$, $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
-Furthermore, let $\vu$ be the uniform distribution over $\Fq^{m+\alpha}$.
-We assume that,
-\[
-|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
-\]
-
-We build a distinguish $\D'$ that distinguishes standard LWE instances from uniform.
-Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.
-Our goal is to prepare a random block fixing instance from the random instance we are given.
-The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.
-
-It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
-\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
-\end{enumerate}
-\begin{figure}
-\begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.
-
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)$.
-\item \label{step:randomization}
-For {$i=1\ldots m+\alpha$}:
-\subitem Randomly generate $(\gamma_{i,1},\ldots, \gamma_{i,\alpha}) \leftarrow \Fq^\alpha$.
- \subitem For {$j = 1 \ldots n+\alpha$}:
-\subsubitem Set $A_{ij} \leftarrow A^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}$
-\subsubitem Set $b_i \leftarrow b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k}$
-\item Run $\D$ on input $\vA, \vb$.
-\item Output $\D$'s output.
-\end{enumerate}
-\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-
+We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
 \begin{claim}
-\label{cl:randomMatrixDist}
-The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix.
+\label{cl:full rank matrix}
+Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
+let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha] >  1- q^{-\beta}$.
 \end{claim}
 \begin{proof}
-In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
-Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.
-Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.
-Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5.
-For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number.
-Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors.
-Therefore, the entire matrix $\vA$ is a truly random matrix.
-This completes the claim.
+Let $p_i$ be the probability that the $i$th
+row is linearly dependent on the previous $i-1$ rows. 
+By the union bound, the probability that $\alpha$ rows are linearly dependent is bounded by 
+$\sum_{i=1}^\alpha p_i$.
+Since $i-1$ rows can span a space of size at most $q^{i-1}$, the probability $p_i$ that a randomly chosen $i$th row is in that space is at most $q^{i-1}/q^{\alpha+\beta}$. So
+\begin{align*}
+\Pr[\rank(\vS) < \alpha] &=\sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
+= \frac{q^{\alpha}-1}{q-1}\frac{1}{q^{\alpha+\beta} }< q^{-\beta}.
+\end{align*}
 \end{proof}
-\begin{claim}
-\label{cl:random ax+e}
-If $\D'$ is provided with input distributed as $\vA', \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i} = b_{m+i}^*$ is uniformly generated otherwise and  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
-\end{claim}
-\begin{proof}
-Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
-Then define $\vx^*$ as:
-\[
-x^*_i = \begin{cases}
-x_i', & \text{if }1\leq i\leq n \\
-b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
-\end{cases}
-\]
-Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).
-Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
-%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).
-Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
-%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
-The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-\bnote{We need to justify these steps better.}
-\bnote{Is it really standard to go to lower case for the rows?}
-\xnote{lower case for vectors, which is row vector in the matrix}
-
-\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
-We have the following for all $i=1,..., m+\alpha$:
-\begin{align*}
-\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
-& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
-& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
-&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
-\end{align*}
-%\begin{align*}
-%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
-%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
-%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
-%& = b_i \label{reductionEq}
-%\end{align*}
-\end{proof}
-\begin{claim} 
-\label{clm:random b}
-If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
-\end{claim}
-\begin{proof}
-Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.
-After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
-\[
-b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
-\]
-%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each
-
-$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{It need show more work on this, maybe?}
-Thus, each of these values is uniformly and independently random.
-\end{proof}
-
-%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$.
-%
-%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$.
-Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
-%\begin{align*}
-%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
-%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
-%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
-%\end{align*}
-
-\begin{claim}
-If the pair $(\vA', \vb')$ is uniformly distributed, then the pair $(\vA, \vb)$ is uniformly distributed.
-\end{claim}
-\begin{proof}
-Assume that $(\vA', \vb')$ is uniformly distributed.
-By \clref{cl:randomMatrixDist}, $\vA$ is uniformly distributed.
-Thus, it suffices to show that $\vb | \vA$ is uniformly distributed.
-Let $\vb^*$ be the vector generated in step~\ref{step:b generation} and note that $\vb^*$ is uniformly random.
-We show  a stronger claim that $\vb |( \vA, \vA', \vR)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i,j}$.
-
- The matrix $\vgamma$ is a deterministic function of $(\vA, \vA', \vR)$.
-Thus, $\vb | (\vA, \vA', \vR) \overset{d}= \vb | (\vA, \vA', \vR, \vgamma)$.
-The only dependence of $\vb$ on $(\vA, \vA', \vR, \vgamma)$ is in the matrix $\vgamma$.
-Thus, $ \vb | (\vA, \vA', \vR, \vgamma) \overset{d}= \vb | \vgamma$.
-Recall that $\vb = \vb^* +  \left(\begin{array}{c | c}\mathbf{0} &\vgamma\end{array}\right)\vb^*$.
-Let $\vT = \vect{I}+  \left(\begin{array}{c | c}\mathbf{0} & \vgamma \end{array}\right)$.
-Since $\vT$ is a deterministic function of $\vgamma$, $\vb | \vgamma \overset{d} = \vb | \vT$.
-
- \bnote{Now we want to say that $\vb$ is uniformly distributed since $\vb'$ is.
-If $\vT$ exists we can just that $\vb | \vT = (\vT^{-1} \vb )| \vT = \vb' | \vT = U | \vT$.
-It does with very high probability, but I don't want to add this restriction.
-Is there a way to get around this problem?}
-%\[
-%\vA=  \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right)
-%\]
-%\begin{align*}
-%(\vA, \vb) =  \left(\left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) \right) , \left(\vb' + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \vb'\right)
-%\end{align*}
-\end{proof}
-\bnote{Remember this isn't good enough.  We need the enhanced claim above.}
-Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
-\begin{align*}
-&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
-& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
-\end{align*}
-%==========
-\ignore{
-Before randomized:
-$$\vA'\vx' + \ve = \vb'$$
-For $i = 1\ldots m$,
-$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
-For $i = 1\ldots \alpha$,
-$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
-}
-\end{proof}
-}
 
@@
 \end{figure}
-The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
+The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
 \begin{claim}
-\label{cl:full rank matrix}
+\label{cl:full rank matrix 5.2}
 Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
@@
 \begin{proof}
-The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
-By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
-\begin{align*}
-\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
-\end{align*}
-Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
+Direct application of \clref{cl:full rank matrix} when $\alpha = \poly(n)$ and $\beta = \omega(1)$ in $n$.
 \end{proof}
@@
 \begin{proof}
-Let $d$ be a positive constant and $t = d\left( \frac{m}{n}-2\right)\log n$.  
-By \corref{cor:code high distance}, the code generated by $\vA$ has distance at least $2t+1$ with probability $1-e^{-\Omega(n)}$.
-Thus, if $X\neq X'$, step (6) will detect it with probability at least $1-e^{-\Omega(n)}$.
-This probability is over the coins of $\gen$ and thus does not grow with the number of iterations in $\decode_t$.
-We consider the expected number of times step 2 is executed when $t\leq d\left(\frac{m}{n}-2\right)\log n$.
-An iteration of $\decode_t$ succeeds when all selected rows of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ have no error and when  $\vA_{i_1,..., i_{2n}}$ has rank $n$.
-The event that $\vA_{i_1,..., i_{2n}}$ has rank $n$ is independent of event that the rows $i_1,...,i_{2n}$ have no errors.
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
-That is,
+Note that $\decode_t$ will stop if $w$ and $w'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
+The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
 \begin{align*}
@@
 &\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
-&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}
-\end{align*}
-Now, we consider the probability  $\vA_{i_1,..., i_{2n}}$  rank $n$.
-This probability is at least $1-e^{-\Omega(n)}$~(see \clref{cl:full rank matrix}).
-Thus, the probability that a given iteration succeeds $\frac{1}{n^{4d}} - e^{-\Omega(n)}$.
-Thus, the expected number of iterations in step 2 at most  $2n^{4d}$.
-We assume all matrix operations can be completed in  $O(n^3)$ operations over $\Fq$, giving a total of expected $O(n^{4d+3})$ operations over $\Fq$.
+&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}\,.
+\end{align*}
+(The second-to-last step holds as long as $n\ge 2d\log n$.) Because at each iteration, we select $2n$ rows independently at random, the expected number of iterations is at most $n^{4d}$; each iteration takes $O(n^3)$ operations in $\Fq$, which gives us the expected running time bound.
+
+The probability that $\decode_t$ outputs $\perp$ is bounded by 
+\begin{eqnarray*}
+\Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
+&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
+&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
+&= &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times}]\cdot \Pr[\rank(\vA_{i_1,\dots, i_{2n}})<n]\\
+&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot q^{-n}\\
+& = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
+\end{eqnarray*}
+The third line from the bottom follows from the fact that the locations of the errors are assumed to be independent of the sketch, and therefore independent of the matrix $\vA$.
+The second line from the bottom follows from \clref{cl:full rank matrix} when $\beta = n$; note that, because we use the union bound and evaluate the probability separately for each value of $j$,  we can treat $\vA_{i_1,\dots, i_{2n}}$ as a randomly chosen $2n\times n$ matrix, ignoring the fact that these matrices are correlated.
+
+We claim that if the code generated by $\vA$ 
+has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $\vx'=\vx$.
+Indeed, suppose $\vx'\neq \vx$.
+Since $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $w-w'$, such an $\vx'$ will not pass Step 6.
+
+The probability that the code generated by $\vA$ has distance lower than $2t+1$ is at most $e^{-\Omega(n)}$ (see \corref{cor:code high distance}), the probability of outputting $\perp$ is also $e^{-\Omega(n)}$~(computed above).
+This gives the correctness bound for $\decode_t$.
 \end{proof}

### 2013-06-20 trunk/CompFuzzExt.tex
Changing claim B.1 to match A.3

@@
 %
-Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $\vx$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
+Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $X$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
  The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
-$(\vA, \vA\vx+\chi)$ from
+$(\vA, \vA X+\chi)$ from
  the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
@@
 \begin{enumerate}
-\item Input $\vA , \vB = \vA X + W - W'$
+\item Input $\vA , \vb = \vA \vx + w - w'$
 \item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, \vB$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vB_{i_1,...,i_{2n}}$.
+\item Restrict $\vA, \vb$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vb_{i_1,...,i_{2n}}$.
 \item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
 If no such rows exist, output $\perp$ and stop.
-\item Denote by $\vA', \vB'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vB_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
-\item If $\vB- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
-\item Output $X'$.
+\item Denote by $\vA', \vb'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vb_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $\vx' = (\vA')^{-1}\vb'$.  
+\item If $\vb- \vA \vx'$ has more than $t$ nonzero coordinates, go to step (2).
+\item Output $\vx'$.
 \end{enumerate}
@@
 Each step is computable in time $O(n^3)$. 
-For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows).
-If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $X'=X$, and the algorithm terminates.
-However, we also need to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.
-This detection will happen if $B-\vA X' = \vA (X-X')+(W-W')$ has more than $t$ nonzero coordinates.
-It suffices to ensure that $\vA (X-X')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $W-W'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
+For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $w$ and $w'$ agree on those rows).
+If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $\vx'=\vx$, and the algorithm terminates.
+However, we also need to ensure correctness: we need to make sure that if $\vx'\neq \vx$, we detect it in step 6.
+This detection will happen if $\vb-\vA \vx' = \vA (\vx-\vx')+(w-w')$ has more than $t$ nonzero coordinates.
+It suffices to ensure that $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $w-w'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
 
@@
 Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this probability is over the choice of random coins of \rep).
+Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this expectation is over the choice of random coins of $\decode_t$, regardless of the input, as long as $\dis(w, w')\le t$).
 It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
@@
 Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
-let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \alpha q^{\beta}$.
+let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha] >  1- q^{-\beta}$.
 \end{claim}
 \begin{proof}
-The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.
-By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
-\begin{align*}
-\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }= \alpha q^{-\beta}.
+Let $p_i$ be the probability that the $i$th
+row is linearly dependent on the previous $i-1$ rows. 
+By the union bound, the probability that $\alpha$ rows are linearly dependent is bounded by 
+$\sum_{i=1}^\alpha p_i$.
+Since $i-1$ rows can span a space of size at most $q^{i-1}$, the probability $p_i$ that a randomly chosen $i$th row is in that space is at most $q^{i-1}/q^{\alpha+\beta}$. So
+\begin{align*}
+\Pr[\rank(\vS) < \alpha] &=\sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
+= \frac{q^{\alpha}-1}{q-1}\frac{1}{q^{\alpha+\beta} }< q^{-\beta}.
 \end{align*}
@@
 \begin{proof}
-Direct application of \clref{cl:full rank matrix} when $\alpha = \poly(n)$ and $\beta = \omega(1)$ in $n$.
+Direct result of \clref{cl:full rank matrix} when $\beta = \omega(1)$ in $n$.
 \end{proof}
@@
 \begin{proof}
-Note that $\decode_t$ will stop if $W$ and $W'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
+Note that $\decode_t$ will stop if $w$ and $w'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
 The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
@@
 \Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
-&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1},\dots, \vA_{i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1},\dots, \vA_{i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot e^{-\Omega(n)}\\
+&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
+&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
+&= &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times}]\cdot \Pr[\rank(\vA_{i_1,\dots, i_{2n}})<n]\\
+&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot q^{-n}\\
 & = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
 \end{eqnarray*}
-(the second to last line follows from \clref{cl:full rank matrix} when $\alpha, \beta = O(n)$ \bnote{need to say this is a randomly generated matrix, but there are previous iterations.
-I know we abort if we find a non full rank matrix but this still bothers me.}).
+The third line from the bottom follows from the fact that the locations of the errors are assumed to be independent of the sketch, and therefore independent of the matrix $\vA$.
+The second line from the bottom follows from \clref{cl:full rank matrix} when $\beta = n$; note that, because we use the union bound and evaluate the probability separately for each value of $j$,  we can treat $\vA_{i_1,\dots, i_{2n}}$ as a randomly chosen $2n\times n$ matrix, ignoring the fact that these matrices are correlated.
 
 We claim that if the code generated by $\vA$ 
-has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $X'=X$.
-Indeed, suppose $X'\neq X$.
-Since $\vA (X-X')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $W-W'$, such an $X'$ will not pass Step 6.
+has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $\vx'=\vx$.
+Indeed, suppose $\vx'\neq \vx$.
+Since $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $w-w'$, such an $\vx'$ will not pass Step 6.
 

### 2013-06-20 trunk/CompFuzzExt.tex
went through all of appendix B except claim B.5

@@
 \label{thm:blockLWE}
-Let $n$ be a security parameter, $\alpha$ be polynomial in $n$, and $\beta=\beta(n)=\omega(1)$.
+Let $n$ be a security parameter, $\alpha$ be polynomial in $n$, and $\beta=\beta(n)=\omega(1)$. \lnote{rephrase so that $q=q(n)$ and$q^{-\beta}$ is negl in $n$}
 Let $U$ denote the uniform distribution over $Z^m$ for an alphabet $Z\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |Z|)$ symbol fixing source over $Z^{m+\alpha}$.
@@
 For a more detailed explanation of parameters see \secref{ssec:block params}.
+\lnote{to satsify \thref{thm:blockLWE} condition on $\beta$ is easy here, because $q$ is at least $n^2$, so superconstant $\beta$ is enough}
 \end{proof}
@@
 \begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.
-If the blocks are fixed to some other value the reduction is essentially the same.
+We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$ \lnote{are we using $W$ or $\chi$ notation?}.
+If the blocks are fixed to some other value, the reduction is essentially the same\lnote{isn't the point of a block fixing source that we don't know which values are fixed and to what?
+At least in the extractor literature, that would seem to be crucial---else, extraction is trivial}.
 For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
@@
 
-Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
-Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
-That is, $D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
-We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
-Let $\epsilon \geq 1/\poly(n)$, then,
+Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
+Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ with advantage $\epsilon>1/\poly(n)$m
+where $\chi'_i = \chi_i$ for $i\leq m$ \lnote{what's $\chi_i$?} and $\chi_i \overset{d}= 0$ otherwise.
+\lnote{we should probably swap $\chi$ and $\chi'$ to be consistent about the use of primes} Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ .
+Then
 \[
-|\Pr[D(\vA, \vA\vx+\ve) = 1] - \Pr[D(\vA, \vu) =1]|> \epsilon.
+|\Pr[D(\vA, \vA X+\chi') = 1] - \Pr[D(\vA, U =1]|> \epsilon.
 \]
 We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
-Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi$.
-It suffices to build a distinguisher~(of polynomial size) $D'$  where
+Let $\vA'$ denote the uniform distribution over $\Fq^{m\times n}$, $X'$ denote the uniform distribution over $\Fq^n$, and $U'$ denote the uniform distribution over $\Fq^{m}$ .
+We will build a distinguisher $D'$ of polynomial size for which
 \begin{align}
 \label{eq:block LWE dist}
-|\Pr[D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
+|\Pr[D'(\vA', \vA'X'+\chi) = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
 \end{align}
-We will make a single call to $D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
-
-\begin{figure}[p]
-\begin{framed}
+$D'$  will make a single call to $D$, so we focus on how to prepare a random block-fixing instance for $D$ from the random instance that $D'$ is given.
+The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
+
+%\begin{figure}[p]
+%\begin{framed}
 \begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vQ \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
-\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
+\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
+\item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, for uniformly chosen $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
+\item Choose $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ uniformly at random.
 		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
-\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
-\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
-\subitem For $j=1,..., m$:
-\subsubitem Generate $\vQ_{j, i}\overset{\$}\leftarrow \Fq$
-\subsubitem Set $b_j^* = b_j^* + \vQ_{j, i} x_i$.
+\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.
+\item For all $j\notin T$, $1\le j \le \alpha+\beta$:\lnote{swapped $i$, $j$ and shifted}\label{step:fill in matrix}
+\subitem Choose $x_{j+n}\overset{\$}\leftarrow \Fq$ uniformly at random.  
+\subitem For $i=1,..., m$:
+\subsubitem Choose $\vQ_{i,j}\overset{\$}\leftarrow \Fq$ uniformly at random.
+\subsubitem Set $b_i^* = b_i^* + \vQ_{i,j} x_{n+j}$.
 \item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
@@
 For {$i=1,..., m$}:
-\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
+\subitem Choose a row vector $\gamma_i \leftarrow \Fq^{1 \times \alpha}$ uniformly at random.
 \subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
-\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
-\item Run $D$ on input $\vA, \vb$.
-\item Output $D$'s output.
+\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})^{\mathsf{T}}$
+\item For $i=m+1,\dots, m+\alpha$:
+\subitem Set $\va_i \leftarrow \va^*_i$
+\subitem Set $b_i = b_i^*$.
+\item Output $D(\vA, \vb)$. 
 \end{enumerate}
-\end{framed}
-\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
+%\end{framed}
+%\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
+%\label{fig:perfectLWEreduction}
+%\end{figure}
+The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
 \begin{claim}
@@
 \begin{proof}
-Direct result of \clref{cl:full rank matrix} when $\beta = \omega(1)$ in $n$.
+Direct result of \clref{cl:full rank matrix} when $\beta = \omega(1)$ in $n$. \lnote{rephrase to say that it follows from the assumption that $q^{-\beta}$ is negligible.}
 \end{proof}
@@
 $
-|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
+|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
 $
 \end{corollary}
-
-We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a random instance in this case. We show this in the following three claims: 
+\lnote{why is this a corollary?  A corollary should follow from something above it, usually}
+
+We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a good instance for $D$ in this case. We show this in the following three claims: 
 \begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
+\item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
 %\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve$ and where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
-\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
+\item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
+\item If $(\vb' , \vA')$ is uniformly distributed then $(\vb, \vA)$ is uniformly distributed.
 \end{enumerate}
@@
 \label{cl:randomMatrixDist}
-The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix with $\rank(\vS) = \alpha$.
+The matrix $\vA$ is distributed as a uniformly random choice from the set of all matrices whose bottom-right $\alpha\times (\alpha+\beta)$ submatrix $\vS$ satisfies $\rank(\vS) = \alpha$.
 \end{claim}
 \begin{proof}
-It should be clear that $\vR, \vS$ are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
-The quadrant represented by $\vA'$ remains random after step~\ref{step:randomization} as we are adding uncorrelated random values.
-The matrix $\vQ_{T^c}$~(recall this is the restriction of $\vQ$ to the columns not in $T$) is random as it is initialized with random values and only uncorrelated random values are added.
-
-Thus, we restrict attention to $\vQ_T$~(the columns of $W$ included in $T$).
+The bottom $\alpha$ rows of $\vA$ (namely, $\vR|\vS$) are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
+The top left $m\times n$ quadrant of $\vA$ is also random, because it is produced as a sum of a uniformly random $\vA'$ with some values that are uncorrelated with $\vA'$.
+The submatrix of the top-right $m\times (\alpha+\beta)$ quadrant corresponding to $\vQ_{T^c}$~(recall this is the restriction of $\vQ$ to the columns not in $T$) is also random, because it is initialized with random values to which some uncorrelated values are then added.
+It is important to note that all these values are independent of $\gamma_i$ values.
+
+Thus, we restrict attention to the $m\times \alpha$ submatrix of $\vA$ that corresponds to $\vQ_T$ in $\vA^*$ (note that these values are $0$ in $\vA^*$).
 Consider a particular row $i$.
-Then $\vQ_{i, T} = \gamma_i \vS_{T}$.
-Since $\vS_T$ is full rank and $\gamma_i$ is uniformly generated, $\vQ_{i, T}$ is uniformly generated.
-
-Thus, the entire matrix $\vA$ after step~\ref{step:randomization} is uniformly generated conditioned on $\rank(\vS) = \alpha$.
+That row is computed as $\gamma_i \vS_{T}$.
+Since $\vS_T$ is a full rank square matrix and $\gamma_i$ is uniformly and independently generated, that row is also uniform and independent of other entries in $\vA$.
 % In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
@@
 \label{cl:random ax+e}
-If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i}$ are uniformly generated otherwise,  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
+If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$, where
+\begin{itemize}
+\item $e_i = e_i'$ for $1\leq i\leq m$,
+\item $e_i = 0$ for $m<i\leq m+\alpha$,
+\item $x_i = x_i'$ for $1\leq i \leq n$,
+\item and $x_i$ is uniform and independent of $\vA$ and $\ve'$ for $n<i\le n+\alpha+\beta$,
+\end{itemize}
 \end{claim}
 \begin{proof}
-Denote by $\vx'$ the value such that $\vA'\vx'+\ve' = \vb'$.  
-Then partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
-We define the remaining variables $\vx_T$ as the solution to the following system of equations.
+Partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
+Define the remaining variables $\vx_T$ as the solution to the following system of equations.
 \[
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}  
+\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  
 \]
-A solution $\vx_T$ exists as $\vS_T$ is full rank and furthermore, $\vx_T$ is uniformly distributed.
-Denote by $\vA^*$ the matrix before step~\ref{step:randomization} and denote by $\ve$ the vector $\ve'$ with $\alpha$ 0s appended.
-The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$.
+A solution $\vx_T$ exists as $\vS_T$ is full rank.
+Moreover, it is uniform and independent of $\vA$ and $\ve'$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve'$.
+Note that $\vb^*=\vA^*\vx+\ve$ before step~\ref{step:randomization} \lnote{this requires careful attention to the algorithm and the definition of $\vx$, not much different from the steps below.
+Why do the steps below get the attention and this one doesn't?
+Perhaps for the above stuff say "by inspection, particularly Step 6, and for below part say "by inspection, we show it formally below"}.
 Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
@@
 \begin{claim}\label{clm:random b}
-If the pair $\vb' | \vA'$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
+If the pair $(\vb', \vA')$ is uniformly distributed, then $(\vb, \vA)$ is uniformly distributed \lnote{this can't possibly be true because $\vA$ is not uniform, because $S$ is full-rank}.
 \end{claim}
@@
 \end{align*}
-Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
+\lnote{change notation above to match notation at the beginning of this section; also, note that the first line follows from teh coinflip if rank is not right} Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
 \end{proof}

### 2013-06-21 CompFuzzExt.tex
changed proof of claim B.5

@@
 
-Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
-Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.
-That is, $D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.
-We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$.
-Let $\epsilon \geq 1/\poly(n)$, then,
+Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
+Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ with advantage $\epsilon>1/\poly(n)$m
+where $\chi'_i = \chi_i$ for $i\leq m$ \lnote{what's $\chi_i$?} and $\chi_i \overset{d}= 0$ otherwise.
+\lnote{we should probably swap $\chi$ and $\chi'$ to be consistent about the use of primes} Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ .
+Then
 \[
-|\Pr[D(\vA, \vA\vx+\ve) = 1] - \Pr[D(\vA, \vu) =1]|> \epsilon.
+|\Pr[D(\vA, \vA X+\chi') = 1] - \Pr[D(\vA, U =1]|> \epsilon.
 \]
 We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
-Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi$.
-It suffices to build a distinguisher~(of polynomial size) $D'$  where
+Let $\vA'$ denote the uniform distribution over $\Fq^{m\times n}$, $X'$ denote the uniform distribution over $\Fq^n$, and $U'$ denote the uniform distribution over $\Fq^{m}$ .
+We will build a distinguisher $D'$ of polynomial size for which
 \begin{align}
 \label{eq:block LWE dist}
-|\Pr[D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
+|\Pr[D'(\vA', \vA'X'+\chi) = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
 \end{align}
-We will make a single call to $D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
-
-\begin{figure}[p]
-\begin{framed}
+$D'$  will make a single call to $D$, so we focus on how to prepare a random block-fixing instance for $D$ from the random instance that $D'$ is given.
+The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
+
+%\begin{figure}[p]
+%\begin{framed}
 \begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
-\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vQ \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
-\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
+\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
+\item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
+\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, for uniformly chosen $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
+\item Choose $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ uniformly at random.
 		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
-\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
-\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
-\subitem For $j=1,..., m$:
-\subsubitem Generate $\vQ_{j, i}\overset{\$}\leftarrow \Fq$
-\subsubitem Set $b_j^* = b_j^* + \vQ_{j, i} x_i$.
+\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
+\item For all $j\notin T$, $1\le j \le \alpha+\beta$:\lnote{swapped $i$, $j$ and shifted}\label{step:fill in matrix}
+\subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
+\subitem For $i=1,..., m$:
+\subsubitem Choose $\vQ_{i,j}\overset{\$}\leftarrow \Fq$ uniformly at random.
+\subsubitem Set $b_i^* = b_i^* + \vQ_{i,j} x_{n+j}$.
 \item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
@@
 For {$i=1,..., m$}:
-\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
+\subitem Choose a row vector $\gamma_i \leftarrow \Fq^{1 \times \alpha}$ uniformly at random.
 \subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
-\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
-\item Run $D$ on input $\vA, \vb$.
-\item Output $D$'s output.
+\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+\alpha})^{\mathsf{T}}$
+\item For $i=m+1,\dots, m+\alpha$:
+\subitem Set $\va_i \leftarrow \va^*_i$
+\subitem Set $b_i = b_i^*$.
+\item Output $D(\vA, \vb)$. 
 \end{enumerate}
-\end{framed}
-\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
+%\end{framed}
+%\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
+%\label{fig:perfectLWEreduction}
+%\end{figure}
+The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
 \begin{claim}
@@
 \begin{proof}
-Direct application of \clref{cl:full rank matrix} when $\alpha = \poly(n)$ and $\beta = \omega(1)$ in $n$.
+Direct result of \clref{cl:full rank matrix} when $\beta = \omega(1)$ in $n$. \lnote{rephrase to say that it follows from the assumption that $q^{-\beta}$ is negligible.}
 \end{proof}
@@
 $
-|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
+|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
 $
 \end{corollary}
-
-We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a random instance in this case. We show this in the following three claims: 
+\lnote{why is this a corollary?  A corollary should follow from something above it, usually}
+
+We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a good instance for $D$ in this case. We show this in the following three claims: 
 \begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
+\item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
 %\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
-\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve$ and where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
-\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
+\item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
+\item If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then the conditional distribution $\vb\,|\,\vA$ is also uniform.
 \end{enumerate}
@@
 \begin{claim}\label{clm:random b}
-If the pair $\vb' | \vA'$ is uniformly distributed, then $\vb |\vA$ is uniformly distributed.
+If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then $\vb\,|\,\vA$ is also uniform.
 \end{claim}
 \begin{proof}
+Since $\vR, \vS$, and $\vQ$ are chosen independently of $\vb'$, the distribution $\vb'\,|\,\vA^*$ is uniform.
 Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vQ$, i.e.
-for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vQ_{i, j} x_j$, thus conditioning on $\vQ$, $b_i^*$ is uniform assuming $b_i$ is uniform.
-Thus $\vb^* | \vA^*$ is uniformly distributed.
-We show that $\vb |( \vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}.
-Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
-
- The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.
-Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.
-The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.
+Its first $m$ coordinates are  computed by adding the uniform vector $\vb'$ to values that are independent of $\vb^*$, and its remaining $\alpha$ coordinates $b^*_{m+1},\dots,b^*_{m+\alpha}$ are   chosen uniformly.
+Thus $\vb^*\,|\,\vA^*$ is uniform.
+
+\lnote{I would delete this paragraph and the next one, and replace with the one below} We will now show that $\vb\,|\,(\vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb\,|\,\vA$ is uniform.
+Indeed, let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
+
+ The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$ \lnote{why?
+And does it depend on the choice of the set $T$ in step 5 being deterministic?
+and do you need this?
+Can't you just write $\vb\,|\,\vA=\vb\,|\,(\vA^*,\Gamma)$, because $\vA$ is a function of $\vA^*, \Gamma$?}.
+Thus, $\vb\,|\,(\vA, \vA^*)$ has the same distribution as $\vb\, |\,(\vA, \vA^*, \vgamma)$.
+The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$\lnote{not sure what the previous sentence means}.
 Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$.
@@
 Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
+
+\lnote{I got confused by the two paragraphs above --- see comments --- so I wrote it differently.  If you agree, delete the two paragraphs above.}
+
+Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
+It is independent of $\vb^*$ and $\vA^*$, so $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform.
+Let $\vgamma'=\left(\begin{array}{c | c}\vect{I_m} & \vgamma \\\hline \vect{0} & \vect{I_\alpha}\end{array}\right)$.
+Note that $\vb=\vgamma' \vb^*$.  Since $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform, and $\vgamma'$ is invertible, $\vb\,|\,(\vA^*, \vgamma)$ must also be uniform.
+Since $\vA$ is a deterministic function of $\vA^*$ and $\vgamma$ (assuming Step~\ref{step:find columns} is deterministic---if not, we can fix the coins used), the distribution $\vb\,|\,\vA$ is the same  as $\vb\,|\,(\vA^*, \vgamma)$ and is thus also uniform.
 \end{proof}

### 2013-06-23 CompFuzzExt.tex
Cleaning up notes in Section B

@@
 \title{\textbf{Computational Fuzzy Extractors}}
-%\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+\author{Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
+Work done in part while the author was at MIT Lincoln Laboratory.
+The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
-% \and Xianrui Meng \and Leonid Reyzin}
-\author{}
+~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
+%\author{}
 \begin{document}
@@
 \label{thm:blockLWE}
-Let $n$ be a security parameter, $\alpha$ be polynomial in $n$, and $\beta=\beta(n)=\omega(1)$. \lnote{rephrase so that $q=q(n)$ and$q^{-\beta}$ is negl in $n$}
+Let $n$ be a security parameter, $m, \alpha$ be polynomial in $n$, and $q=\poly(n)$ be a prime and $\beta\in\mathbb{Z^+}$ be such that $q^{-\beta} = \ngl(n)$. 
 Let $U$ denote the uniform distribution over $Z^m$ for an alphabet $Z\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |Z|)$ symbol fixing source over $Z^{m+\alpha}$.
@@
 \thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.
-Let $\chi$ be an arbitrary error distribution.
-Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.
+Let $\chi'$ be an arbitrary error distribution.
+Define $\chi$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.
 Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.
+We show this stronger version of the theorem in \apref{sec:proof of block theorem}.
 
@@
 The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
-A formal proof is in \secref{sec:proof of block theorem}.
 
@@
 
-\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE}.
+\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .
+Since \lemref{lem:uniform LWE decision} requires that $q = O(n^{3/2})$, setting  $\beta = \omega(1)$ is sufficient for $q^{-\beta} = \ngl(n)$ as required in \thref{thm:blockLWE}.
 Efficiency follows by \lemref{lem:i t poly time}.
 For a more detailed explanation of parameters see \secref{ssec:block params}.
-\lnote{to satsify \thref{thm:blockLWE} condition on $\beta$ is easy here, because $q$ is at least $n^2$, so superconstant $\beta$ is enough}
 \end{proof}
@@
 \begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$ \lnote{are we using $W$ or $\chi$ notation?}.
-If the blocks are fixed to some other value, the reduction is essentially the same\lnote{isn't the point of a block fixing source that we don't know which values are fixed and to what?
-At least in the extractor literature, that would seem to be crucial---else, extraction is trivial}.
+We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same
+ In the reduction, the distinguisher is allowed to depend on the source and can know the positions of the fixed blocks and their values.
 For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
@@
 We use similar notation for the complement of $T$, denoted $T^c$.
+For a matrix or vector we use $\mathsf{T}$ to denote the transpose.
+We use $i$ as a index into matrix rows and the error vector and $j$ as an  index into columns and the solution vector.
 
@@
 
-Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
-Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ with advantage $\epsilon>1/\poly(n)$m
-where $\chi'_i = \chi_i$ for $i\leq m$ \lnote{what's $\chi_i$?} and $\chi_i \overset{d}= 0$ otherwise.
-\lnote{we should probably swap $\chi$ and $\chi'$ to be consistent about the use of primes} Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ .
+Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.
+Let $\beta$ be such that $q^{-\beta} = \ngl(n)$.
+All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
+Let $\chi'$ be some error distribution over $\Fq^m$ and let $\chi$ over $\Fq^{m+n}$ be defined by sampling $\chi'$ to obtain values on dimensions $1,..., m$ and then appending $\alpha$ 0s.
+
+Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi}$ with advantage $\epsilon>1/\poly(n)$.
+Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ .
 Then
 \[
-|\Pr[D(\vA, \vA X+\chi') = 1] - \Pr[D(\vA, U =1]|> \epsilon.
+|\Pr[D(\vA, \vA X+\chi) = 1] - \Pr[D(\vA, U )=1]|> \epsilon.
 \]
+
 We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
@@
 \label{eq:block LWE dist}
-|\Pr[D'(\vA', \vA'X'+\chi) = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
+|\Pr[D'(\vA', \vA'X'+\chi') = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
 \end{align}
@@
 
-%\begin{figure}[p]
-%\begin{framed}
+\begin{figure}[p]
+\begin{framed}
 \begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
+\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi'$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
 \item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
@@
 \item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
-\item For all $j\notin T$, $1\le j \le \alpha+\beta$:\lnote{swapped $i$, $j$ and shifted}\label{step:fill in matrix}
+\item For all $1\le j \le \alpha+\beta$, $j\notin T$:
+\label{step:fill in matrix}
 \subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
@@
 \end{enumerate}
-%\end{framed}
-%\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-%\label{fig:perfectLWEreduction}
-%\end{figure}
+\end{framed}
+\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
+\label{fig:perfectLWEreduction}
+\end{figure}
+
 The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
@@
 \begin{proof}
-Direct result of \clref{cl:full rank matrix} when $\beta = \omega(1)$ in $n$. \lnote{rephrase to say that it follows from the assumption that $q^{-\beta}$ is negligible.}
+Direct result of \clref{cl:full rank matrix} because $q^{-\beta} = \ngl(n)$.
 \end{proof}
-\begin{corollary}
-$
+The probability that a random $\vS$ is not full rank is $\ngl(n)$ so the distinguisher $D$ must still have an advantage when the matrix $\vS$ is full rank.  That is,
+\[
 |\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
-$
-\end{corollary}
-\lnote{why is this a corollary?  A corollary should follow from something above it, usually}
-
-We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $D'$ prepares a good instance for $D$ in this case. We show this in the following three claims: 
+\]
+
+It suffices to show that $D'$ prepares a good instance for $D$ conditioned on $\vS$ being full rank. We show this in the following three claims: 
 \begin{enumerate}
@@
 \item $e_i = 0$ for $m<i\leq m+\alpha$,
-\item $x_i = x_i'$ for $1\leq i \leq n$,
-\item and $x_i$ is uniform and independent of $\vA$ and $\ve'$ for $n<i\le n+\alpha+\beta$,
+\item $x_j = x_j'$ for $1\leq j \leq n$,
+\item and $x_j$ is uniform and independent of $\vA$ and $\ve'$ for $n<j\le n+\alpha+\beta$,
 \end{itemize}
@@
 \begin{proof}
-Partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
+Partially define $\vx$ as $x_j = x_j'$ if $1\leq j \leq n$ and $x_j$ as the value generated in step~\ref{step:fill in matrix} for $j>n $ and $j\not\in T$.
 Define the remaining variables $\vx_T$ as the solution to the following system of equations.
-\[
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  
-\]
+\begin{eqnarray}
+\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  \label{eq:x t solution}
+\end{eqnarray}
 A solution $\vx_T$ exists as $\vS_T$ is full rank.
-Moreover, it is uniform and independent of $\vA$ and $\ve'$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve'$.
-Note that $\vb^*=\vA^*\vx+\ve$ before step~\ref{step:randomization} \lnote{this requires careful attention to the algorithm and the definition of $\vx$, not much different from the steps below.
-Why do the steps below get the attention and this one doesn't?
-Perhaps for the above stuff say "by inspection, particularly Step 6, and for below part say "by inspection, we show it formally below"}.
+Moreover, it is uniform and independent of $\vA$ and $\ve$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve$.
+
+We now show that $\vb^* = \vA^* \vx+\ve$.
+All entries in matrix $\vQ$ corresponding to variables in $T$ are set to zero.
+Thus, the values of $\vx^T$ do not affect $b_i$ for $1\le i \le m$.
+The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $\vb_i$.
+Thus, for $1 \leq i \le m$, we have $\vb^* = \vA^*\vx+\ve$.
+For $m< i$, this constraint is also satisfied by the values of $\vx_T$ set in Equation~\ref{eq:x t solution}.
+
 Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
@@
 The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
-We have the following for $1\leq i\leq m$:
+Recall the other rows are not modified.  We have the following for $1\leq i\leq m$:
 \begin{align*}
@@
 
-\lnote{I would delete this paragraph and the next one, and replace with the one below} We will now show that $\vb\,|\,(\vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb\,|\,\vA$ is uniform.
-Indeed, let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
-
- The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$ \lnote{why?
-And does it depend on the choice of the set $T$ in step 5 being deterministic?
-and do you need this?
-Can't you just write $\vb\,|\,\vA=\vb\,|\,(\vA^*,\Gamma)$, because $\vA$ is a function of $\vA^*, \Gamma$?}.
-Thus, $\vb\,|\,(\vA, \vA^*)$ has the same distribution as $\vb\, |\,(\vA, \vA^*, \vgamma)$.
-The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$\lnote{not sure what the previous sentence means}.
-Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$.
-Recall that
- \[
- \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
-\]
-Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
-
-\lnote{I got confused by the two paragraphs above --- see comments --- so I wrote it differently.  If you agree, delete the two paragraphs above.}
-
 Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
@@
 \begin{align*}
-&\left|\Pr\left[D'(\vA', \vu') = 1\right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
+&\left|\Pr[D'(\vA, \vA X+\chi) = 1] - \Pr[D'(\vA, U) =1] \right|\\
 &\, = \left| \Pr\left[D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
-&\, =\left|\Pr\left[D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
+&\, =\left|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]  \right| \Pr[\rank(\vS) = \alpha] \\
 &\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
 \end{align*}
-\lnote{change notation above to match notation at the beginning of this section; also, note that the first line follows from teh coinflip if rank is not right} Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
+Where the second line follows because we can detect when $\rank(\vS)<\alpha$ and output a random bit in this case.
+Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
 \end{proof}

### 2013-06-24 CompFuzzExt.tex
Added acknowledgements section

@@
 \title{\textbf{Computational Fuzzy Extractors}}
-\author{Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
-Work done in part while the author was at MIT Lincoln Laboratory.
-The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
+\author{Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
 ~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
@@
 
-%\textbf{Comparison with \thref{thm:lossless secure extractor log}}
-%%\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  
-%The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
-We could set $\alpha$ larger than $n/3$.
-This would yield fewer hardcore dimensions and force us to use a larger field.
-To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant fraction of $n$.
-We consider the setting where the number of fixed errors, hardcore dimensions, and dimensions used for randomness are all $n/3$.
-%The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
+\section*{Acknowledgements}
+The authors are grateful to Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
+In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.
+The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
 

### 2013-06-24 CompFuzzExt.tex
Finalish edits

@@
 Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors% \lnote{removed (on lattices of dimension $n/4$)}
-using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 Let $\chi'$ be an arbitrary error distribution.
-Define $\chi$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.
-Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.
+Define $\chi$ as the distribution where $m$ dimensions are sampled according to $\chi'$ and the remaining dimensions have some fixed error.
+Then, security of $\distLWE_{n, m, q, \chi'}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi}$.
 We show this stronger version of the theorem in \apref{sec:proof of block theorem}.
@@
 \begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same
+We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same.
  In the reduction, the distinguisher is allowed to depend on the source and can know the positions of the fixed blocks and their values.
@@
 All entries in matrix $\vQ$ corresponding to variables in $T$ are set to zero.
-Thus, the values of $\vx^T$ do not affect $b_i$ for $1\le i \le m$.
-The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $\vb_i$.
+Thus, the values of $\vx^T$ do not affect $b_i^*$ for $1\le i \le m$.
+The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $b_i^*$.
 Thus, for $1 \leq i \le m$, we have $\vb^* = \vA^*\vx+\ve$.

### 2013-09-03 trunk/CompFuzzExt.tex
Dealing with Asiacrypt reviewer comments

@@
 \title{\textbf{Computational Fuzzy Extractors}}
-%\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
-% \and Xianrui Meng \and Leonid Reyzin}
-\author{}
+\author{Benjamin Fuller 
+\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
+~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
+%\author{}
 \begin{document}
@@
 First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$ (this idea is similar to the way the code-offset construction is presented in
-\cite{JW99} as  a ``fuzzy commitment'') .
+\cite{JW99} as  a ``fuzzy commitment'').
+Our construction uses private randomness, which is allowed in the fuzzy extractor setting but not in noiseless randomness extraction.
 Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.
@@
 However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
+Furthermore, a computational extractor cannot use private randomness; private randomness is a crucial ingredient in our main construction.
 %We ask whether it is possible to avoid this loss by making whole process ``computational.''
@@
 We now state a setting of parameters that yields a lossless construction.
+The intuition is that our key is $X_{1,\dots, k}$ which is of size $k \log q$ while our input $w$ is of length $m\log \rho q$.
+Though we need $m>n>k$ for decoding, dimensions of $w$ are sampled using fewer bits than dimensions of $X$.
+That is, $\log \rho q < \log q$.
+Thus by increasing the size of $q$ we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
 
@@
 \label{sec:prg based comparison}
-As we already mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
+As mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
 We will call this approach \emph{sketch-and-comp-extract}.
@@
 
+Symbol-fixing sources are a very structured class of distributions.
+However, extending \consref{cons:informal construction} to such a class is not obvious.
+Although symbol-fixing sources are deterministically extractor, we cannot first run a deterministic extractor before using \consref{cons:informal construction}.
+This is because we need to preserve distance between $w_0$ and $w_1$ and an extractor must not preserve distance between input points.
+We present an alternative approach, showing security of \LWE directly with symbol-fixing sources.
+
 The following theorem states the main technical result of this section, which is of potential interest outside our specific setting.
@@
 \thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.
-Let $\chi$ be an arbitrary error distribution.
-Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.
-Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.
+Let $\chi'$ be an arbitrary error distribution.
+Define $\chi$ as the distribution where $m$ dimensions are sampled according to $\chi'$ and the remaining dimensions have some fixed error.
+Then, security of $\distLWE_{n, m, q, \chi'}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi}$.
+We show this stronger version of the theorem in \apref{sec:proof of block theorem}.
 
@@
 The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
-A formal proof is in \secref{sec:proof of block theorem}.
+A similar theorem for the case of a single fixed dimension was shown in concurrent work by Brakerski et al.~\cite[Lemma 4.3]{brakerski2013classical}.
+The proof techniques of Brakerski et al.
+allow removal of $\beta$, improving the parameters of \thref{thm:blockLWE}.
 
@@
 
-\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE}.
+\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .
+Since \lemref{lem:uniform LWE decision} requires that $q = O(n^{3/2})$, setting  $\beta = \omega(1)$ is sufficient for $q^{-\beta} = \ngl(n)$ as required in \thref{thm:blockLWE}.
 Efficiency follows by \lemref{lem:i t poly time}.
 For a more detailed explanation of parameters see \secref{ssec:block params}.
-\lnote{to satsify \thref{thm:blockLWE} condition on $\beta$ is easy here, because $q$ is at least $n^2$, so superconstant $\beta$ is enough}
 \end{proof}
 
-%\textbf{Comparison with \thref{thm:lossless secure extractor log}}
-%%\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  
-%The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.
-We could set $\alpha$ larger than $n/3$.
-This would yield fewer hardcore dimensions and force us to use a larger field.
-To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant fraction of $n$.
-We consider the setting where the number of fixed errors, hardcore dimensions, and dimensions used for randomness are all $n/3$.
-%The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.
-
-\ignore{
-\subsection{\consref{cons:informal construction} with slightly deficient sources}
-\label{sec:DP general error LWE}
-In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.
-We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.
-This result allows us to argue security for an arbitrary distribution that is nearly high entropy.
-This result should be seen as a complement to the proceeding sections.
-It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure extractor log}.
-Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
-\begin{theorem}
-Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.
-Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.
-Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.
-If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
-\end{theorem}
-\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.
-In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.
-The only requirement in the proof is that $|\chi|\geq m\log \rho$.
-Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.
-This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.
-This means we support all distributions whose entropy gap is no more than $m$ bits.
-
-\bnote{Need to continue and go through their Lemma 4.1 and 4.4 to be sure I believe this.  Everything else should go through fine.}
-
-\bnote{We need to turn this hardness result into a statement about computational fuzzy extractors.  Use the Akavia result.  Then we need to suggest parameters.  How much detail should we go into?}
-
-The main item I think needs to change is their Lemma 2.4
-\begin{lemma}~\cite[Min-Entropy Version of Lemma 2.4]{micciancio2013hardness}
-Let $\mathcal{L}$ be a family of functions on a common domain $X$ and let $Z$ be a distribution over $X$.
-Then $(\mathcal{L}, Z)$ is $\epsilon$-uninvertible~(even statistically, with respect to computationally unbounded adversaries) for $\epsilon = \expe_{f\leftarrow \mathcal{L}} [|f(X)|]/ 2^{-H_\infty(Z)}$.
-\end{lemma}
-\begin{proof}
-Fix a function $f$.
-The best way to predict $Z$ given $f(Z)$ is the average predictability of $Z | f(Z)$.
-This predictability is $2^{-\Hav(Z | f(Z))}$.
-By Lemma 2.2 of Dodis et.al.~\cite{DBLP:journals/siamcomp/DodisORS08},
-\[
-\tilde{H}_\infty(Z | f(Z))\geq H_\infty(Z) - \log |f(Z)| \geq \Hoo(Z) - \log |f(X)|.
-\]
-  The statement of the lemma follows by converting to predictability.
-\end{proof}
-
-}
-
-%\section{Computational Fuzzy Extractors}
-%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.
-We begin with a formal definition of a computational fuzzy extractor:
-%\label{sec:comp fuzzy extractors}
-%
-%
-%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
-%\begin{lemma}
-%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
-Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.
-Let, $s' = s_{sec}-s_{ext}$, then
-%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
-%\end{lemma}
-%%  the same paradigm from 
-%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
-It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
-However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).
-%%\begin{definition}
-%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
-Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
-%%\end{definition}
-%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-%%\label{lem:unp extraction} 
-%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-%%\end{lemma}
-%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
-%\begin{lemma}
-%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
-Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
-Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
-%\end{lemma}
-%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
-%%\begin{itemize}
-%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
-%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
-%%\end{itemize}
-%%\end{lemma}
-%%\begin{proof}
-%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
-%%\end{proof}
-%%
-%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
-
-\ignore{
-Additionally, it is simple to use a pseudorandom generator to produce a computational fuzzy extractor from a standard fuzzy extractor:
-\begin{proposition}\label{prop:prg comp fuzzy extractor}
-Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $(\epsilon_{prg}, s)$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.
-Let \gen' and \rep' be defined as:
-\begin{itemize}
-\item \gen': $(R, P) \leftarrow \gen(w)$, output $(prg(R), P)$
-\item \rep': Output  $prg(\rep (w', P))$.
-\end{itemize}
-Then $(\rep', \gen')$ is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.
-\end{proposition}
-Recall, our goal is to construct fuzzy extractors where the entropy drop due to an information theoretic construction were too high.
-However, it seems difficult to definitionally exclude this type of construction.
-For example, one could require that $R$ have information theoretic entropy in the absence of $P$.
-This does not solve the problem:
-\begin{proposition}\label{prop:xor comp fuzzy extractor}
-Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $\epsilon_{prg}, s$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.
-Let \gen' and \rep' be defined as:
-\begin{itemize}
-\item $\gen'(w)$
-\subitem Sample $K\leftarrow \{0,1 \}^{\ell'}$
-\subitem $(R, P) \leftarrow \gen(w)$
-\subitem $H= prg(R)\oplus K$
-\subitem Output $(K, (H, P))$
-\item $\rep'(w', (H, P))$
-\subitem Output $K' = H\oplus prg(\rep (w', P))$.
-\end{itemize}
-Then (\rep', \gen') is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.  Furthermore $H_\infty(K) = \ell'$.
-\end{proposition}
-
-Both of these constructions rely on a crucial property $\ell$ was long enough to provide a seed to a pseudorandom generator.
-We are interested in the case where the remaining entropy is small and may not sufficient for pseudorandom generator.
-We leave Definition~\ref{def:comp fuzzy extractor} as stated and note constructing a computational fuzzy extractor is desirable when a standard fuzzy extractor cannot be used.
-
-In the information theoretic setting, Dodis et.
-al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.
-A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
-}
+\section*{Acknowledgements}
+The authors are grateful to Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
+In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.
+We thank Jacob Alperin-Sheriff for pointing out the connection with the work of Brakerski et al.
+The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
+
 \bibliographystyle{alpha}
@@
 \begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$ \lnote{are we using $W$ or $\chi$ notation?}.
-If the blocks are fixed to some other value, the reduction is essentially the same\lnote{isn't the point of a block fixing source that we don't know which values are fixed and to what?
-At least in the extractor literature, that would seem to be crucial---else, extraction is trivial}.
+We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same.
+ In the reduction, the distinguisher is allowed to depend on the source and can know the positions of the fixed blocks and their values.
 For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
@@
 		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.
-\item For all $j\notin T$, $1\le j \le \alpha+\beta$:\lnote{swapped $i$, $j$ and shifted}\label{step:fill in matrix}
-\subitem Choose $x_{j+n}\overset{\$}\leftarrow \Fq$ uniformly at random.  
+\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
+\item For all $1\le j \le \alpha+\beta$, $j\notin T$:
+\label{step:fill in matrix}
+\subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
 \subitem For $i=1,..., m$:
@@
 \subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
-\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})^{\mathsf{T}}$
+\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+\alpha})^{\mathsf{T}}$
 \item For $i=m+1,\dots, m+\alpha$:
@@
 \item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
-\item If $(\vb' , \vA')$ is uniformly distributed then $(\vb, \vA)$ is uniformly distributed.
+\item If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then the conditional distribution $\vb\,|\,\vA$ is also uniform.
 \end{enumerate}
@@
 \begin{proof}
-Partially define $\vx$ as $x_i = x_i'$ if $1\leq i \leq n$ and $x_i$ as the value generated in step~\ref{step:fill in matrix} for $i>n $ and $i\not\in T$.
+Partially define $\vx$ as $x_j = x_j'$ if $1\leq j \leq n$ and $x_j$ as the value generated in step~\ref{step:fill in matrix} for $j>n $ and $j\not\in T$.
 Define the remaining variables $\vx_T$ as the solution to the following system of equations.
-\[
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  
-\]
+\begin{eqnarray}
+\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  \label{eq:x t solution}
+\end{eqnarray}
 A solution $\vx_T$ exists as $\vS_T$ is full rank.
-Moreover, it is uniform and independent of $\vA$ and $\ve'$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve'$.
-Note that $\vb^*=\vA^*\vx+\ve$ before step~\ref{step:randomization} \lnote{this requires careful attention to the algorithm and the definition of $\vx$, not much different from the steps below.
-Why do the steps below get the attention and this one doesn't?
-Perhaps for the above stuff say "by inspection, particularly Step 6, and for below part say "by inspection, we show it formally below"}.
+Moreover, it is uniform and independent of $\vA$ and $\ve$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve$.
+
+We now show that $\vb^* = \vA^* \vx+\ve$.
+All entries in matrix $\vQ$ corresponding to variables in $T$ are set to zero.
+Thus, the values of $\vx^T$ do not affect $b_i^*$ for $1\le i \le m$.
+The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $b_i^*$.
+Thus, for $1 \leq i \le m$, we have $\vb^* = \vA^*\vx+\ve$.
+For $m< i$, this constraint is also satisfied by the values of $\vx_T$ set in Equation~\ref{eq:x t solution}.
+
 Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
@@
 \begin{claim}\label{clm:random b}
-If the pair $(\vb', \vA')$ is uniformly distributed, then $(\vb, \vA)$ is uniformly distributed \lnote{this can't possibly be true because $\vA$ is not uniform, because $S$ is full-rank}.
+If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then $\vb\,|\,\vA$ is also uniform.
 \end{claim}
 \begin{proof}
+Since $\vR, \vS$, and $\vQ$ are chosen independently of $\vb'$, the distribution $\vb'\,|\,\vA^*$ is uniform.
 Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vQ$, i.e.
-for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vQ_{i, j} x_j$, thus conditioning on $\vQ$, $b_i^*$ is uniform assuming $b_i$ is uniform.
-Thus $\vb^* | \vA^*$ is uniformly distributed.
-We show that $\vb |( \vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}.
+Its first $m$ coordinates are  computed by adding the uniform vector $\vb'$ to values that are independent of $\vb^*$, and its remaining $\alpha$ coordinates $b^*_{m+1},\dots,b^*_{m+\alpha}$ are   chosen uniformly.
+Thus $\vb^*\,|\,\vA^*$ is uniform.
+
 Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
-
- The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.
-Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.
-The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.
-Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$.
-Recall that
- \[
- \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
-\]
-Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
+It is independent of $\vb^*$ and $\vA^*$, so $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform.
+Let $\vgamma'=\left(\begin{array}{c | c}\vect{I_m} & \vgamma \\\hline \vect{0} & \vect{I_\alpha}\end{array}\right)$.
+Note that $\vb=\vgamma' \vb^*$.  Since $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform, and $\vgamma'$ is invertible, $\vb\,|\,(\vA^*, \vgamma)$ must also be uniform.
+Since $\vA$ is a deterministic function of $\vA^*$ and $\vgamma$ (assuming Step~\ref{step:find columns} is deterministic---if not, we can fix the coins used), the distribution $\vb\,|\,\vA$ is the same  as $\vb\,|\,(\vA^*, \vgamma)$ and is thus also uniform.
 \end{proof}

### 2013-09-03 trunk/CompFuzzExt.tex
update

@@
 \paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.
-They can be constructed, for example, by applying to pseudorandom generator to the output of an information-theoretic extractor.
+They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.
 One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.
 However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
-Furthermore, a computational extractor cannot use private randomness; private randomness is a crucial ingredient in our main construction.
 %We ask whether it is possible to avoid this loss by making whole process ``computational.''
@@
 
-Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
+Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
 
@@
 \label{lem:many hardcore bits}
- If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure then
+ If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure, then
 \[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,\dots, k}, \vA, \vA X+\chi) , (U, \vA, \vA X+\chi)) \le \epsilon\,,\]

### 2013-09-03 CompFuzzExt.tex
Revisions with reviewer comments

@@
 \title{\textbf{Computational Fuzzy Extractors}}
-\author{Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
+\author{Benjamin Fuller 
+\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
 ~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
@@
 \paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.
-They can be constructed, for example, by applying to pseudorandom generator to the output of an information-theoretic extractor.
+They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.
 One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.
@@
 We now state a setting of parameters that yields a lossless construction.
+The intuition is as follows.
+We are splitting our source into $m$ blocks each of size $\log \rho q$~(from \lemref{lem:uniform LWE decision}) for a total input entropy of $m\log \rho q$.
+Our key is derived from hardcore bits of $X$: $X_{1,\dots, k}$ and is of size $k \log q$~(from \lemref{lem:many hardcore bits}).
+Thus, to achieve a lossless construction we need $k \log q = m\log \rho q$.
+In order to decode a meaningful number of errors we need $m>n>k$.
+However, dimensions of $w$ are sampled with fewer bits than dimensions of $X$.
+That is, $\log \rho q < \log q$.
+Thus, by increasing the size of $q$ we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
+The formal statement is below.
 
@@
 
+Symbol-fixing sources are a very structured class of distributions.
+However, extending \consref{cons:informal construction} to such a class is not obvious.
+Although symbol-fixing sources are deterministically extractible~\cite{KZ07}, we cannot first run a deterministic extractor before using \consref{cons:informal construction}.
+This is because we need to preserve distance between $w$ and $w'$ and an extractor must not preserve distance between input points.
+We present an alternative approach, showing security of $\LWE$ directly with symbol-fixing sources.
+
 The following theorem states the main technical result of this section, which is of potential interest outside our specific setting.
@@
 The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
+A similar theorem for the case of a single fixed dimension was shown in concurrent work by Brakerski et al.~\cite[Lemma 4.3]{brakerski2013classical}.
+The proof techniques of Brakerski et al.
+allow removal of $\beta$, improving the parameters of \thref{thm:blockLWE}.
 
@@
 In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.
+We thank Jacob Alperin-Sheriff for pointing out the connection with the work of Brakerski et al.
 The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
@@
 
-\ignore{
-\subsection{\consref{cons:informal construction} with slightly deficient sources}
-\label{sec:DP general error LWE}
-In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.
-We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.
-This result allows us to argue security for an arbitrary distribution that is nearly high entropy.
-This result should be seen as a complement to the proceeding sections.
-It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure extractor log}.
-Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
-\begin{theorem}
-Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.
-Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.
-Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.
-If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
-\end{theorem}
-\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.
-In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.
-The only requirement in the proof is that $|\chi|\geq m\log \rho$.
-Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.
-This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.
-This means we support all distributions whose entropy gap is no more than $m$ bits.
-
-\bnote{Need to continue and go through their Lemma 4.1 and 4.4 to be sure I believe this.  Everything else should go through fine.}
-
-\bnote{We need to turn this hardness result into a statement about computational fuzzy extractors.  Use the Akavia result.  Then we need to suggest parameters.  How much detail should we go into?}
-
-The main item I think needs to change is their Lemma 2.4
-\begin{lemma}~\cite[Min-Entropy Version of Lemma 2.4]{micciancio2013hardness}
-Let $\mathcal{L}$ be a family of functions on a common domain $X$ and let $Z$ be a distribution over $X$.
-Then $(\mathcal{L}, Z)$ is $\epsilon$-uninvertible~(even statistically, with respect to computationally unbounded adversaries) for $\epsilon = \expe_{f\leftarrow \mathcal{L}} [|f(X)|]/ 2^{-H_\infty(Z)}$.
-\end{lemma}
-\begin{proof}
-Fix a function $f$.
-The best way to predict $Z$ given $f(Z)$ is the average predictability of $Z | f(Z)$.
-This predictability is $2^{-\Hav(Z | f(Z))}$.
-By Lemma 2.2 of Dodis et.al.~\cite{DBLP:journals/siamcomp/DodisORS08},
-\[
-\tilde{H}_\infty(Z | f(Z))\geq H_\infty(Z) - \log |f(Z)| \geq \Hoo(Z) - \log |f(X)|.
-\]
-  The statement of the lemma follows by converting to predictability.
-\end{proof}
-
-}
-
-%\section{Computational Fuzzy Extractors}
-%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.
-We begin with a formal definition of a computational fuzzy extractor:
-%\label{sec:comp fuzzy extractors}
-%
-%
-%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
-%\begin{lemma}
-%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.
-Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.
-Let, $s' = s_{sec}-s_{ext}$, then
-%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
-%\end{lemma}
-%%  the same paradigm from 
-%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).
-It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.
-However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).
-%%\begin{definition}
-%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.
-Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
-%%\end{definition}
-%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
-%%\label{lem:unp extraction} 
-%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.
-Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
-%%\end{lemma}
-%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
-%\begin{lemma}
-%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.
-Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.
-Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
-%\end{lemma}
-%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
-%%\begin{itemize}
-%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
-%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
-%%\end{itemize}
-%%\end{lemma}
-%%\begin{proof}
-%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
-%%\end{proof}
-%%
-%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
-
-\ignore{
-Additionally, it is simple to use a pseudorandom generator to produce a computational fuzzy extractor from a standard fuzzy extractor:
-\begin{proposition}\label{prop:prg comp fuzzy extractor}
-Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $(\epsilon_{prg}, s)$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.
-Let \gen' and \rep' be defined as:
-\begin{itemize}
-\item \gen': $(R, P) \leftarrow \gen(w)$, output $(prg(R), P)$
-\item \rep': Output  $prg(\rep (w', P))$.
-\end{itemize}
-Then $(\rep', \gen')$ is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.
-\end{proposition}
-Recall, our goal is to construct fuzzy extractors where the entropy drop due to an information theoretic construction were too high.
-However, it seems difficult to definitionally exclude this type of construction.
-For example, one could require that $R$ have information theoretic entropy in the absence of $P$.
-This does not solve the problem:
-\begin{proposition}\label{prop:xor comp fuzzy extractor}
-Let \gen, \rep be a $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(where \rep is computable by a  $s_{rec}$ size circuit) and let $prg: \{0,1\}^\ell\rightarrow \{0, 1\}^{\ell'}$ be a $\epsilon_{prg}, s$ pseudorandom generator (computable by a circuit of size $s_{peg}$) from $\ell$ bits to $\ell'$ bits.
-Let \gen' and \rep' be defined as:
-\begin{itemize}
-\item $\gen'(w)$
-\subitem Sample $K\leftarrow \{0,1 \}^{\ell'}$
-\subitem $(R, P) \leftarrow \gen(w)$
-\subitem $H= prg(R)\oplus K$
-\subitem Output $(K, (H, P))$
-\item $\rep'(w', (H, P))$
-\subitem Output $K' = H\oplus prg(\rep (w', P))$.
-\end{itemize}
-Then (\rep', \gen') is a $(\mathcal{M}, m, \ell', t, s_{rec}+s_{prg}, s, \epsilon+\epsilon_{prg})$-computational fuzzy extractor.  Furthermore $H_\infty(K) = \ell'$.
-\end{proposition}
-
-Both of these constructions rely on a crucial property $\ell$ was long enough to provide a seed to a pseudorandom generator.
-We are interested in the case where the remaining entropy is small and may not sufficient for pseudorandom generator.
-We leave Definition~\ref{def:comp fuzzy extractor} as stated and note constructing a computational fuzzy extractor is desirable when a standard fuzzy extractor cannot be used.
-
-In the information theoretic setting, Dodis et.
-al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.
-A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
-}
 \bibliographystyle{alpha}

### 2013-09-03 trunk/CompFuzzExt.tex
take care of the bad writing comments from the reviewers.

@@
 Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+We say that $\mathcal{C}$ is a $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
 To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
@@
  \begin{definition}
-Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
+Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is a $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
 $\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
@@
 
-We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
+We will say that a pair of procedures $(\sketch, \rec)$ is an \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
+Note that this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor
 \emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
@@
 \label{thm:imp of unp entropy}
-Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+Let $Z$ be an alphabet and $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
@@
 %\label{subsec:LWE uniform error}
-Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
+Fortunately, recent work of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
 The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
@@
 This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.
-However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
+However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
 
@@
 Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
+\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \neigh(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
 %Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  

### 2013-09-03 trunk/CompFuzzExt.tex
Reviewer comments

--- 2013-09-03 trunk/CompFuzzExt.tex
@@
 \label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." We now recall the definition of the decisional version of the problem.
+The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a complete description of the $\LWE$ problem and related lattices problems~(which we do not define here) see~\cite{regev2005LWE}.
+We now recall the definition of the decisional version of the problem.
 
@@
 We now state a setting of parameters that yields a lossless construction.
-The intuition is that our key is $X_{1,\dots, k}$ which is of size $k \log q$ while our input $w$ is of length $m\log \rho q$.
-Though we need $m>n>k$ for decoding, dimensions of $w$ are sampled using fewer bits than dimensions of $X$.
+The intuition is as follows.
+We are splitting our source into $m$ blocks each of size $\log \rho q$~(from \lemref{lem:uniform LWE decision}) for a total input entropy of $m\log \rho q$.
+Our key is derived from hardcore bits of $X$: $X_{1,\dots, k}$ and is of size $k \log q$~(from \lemref{lem:many hardcore bits}).
+Thus, to achieve a lossless construction we need $k \log q = m\log \rho q$.
+In order to decode a meaningful number of errors we need $m>n>k$.
+However, dimensions of $w$ are sampled with fewer bits than dimensions of $X$.
 That is, $\log \rho q < \log q$.
-Thus by increasing the size of $q$ we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
+Thus, by increasing the size of $q$ we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
+The formal statement is below.
 
@@
 However, extending \consref{cons:informal construction} to such a class is not obvious.
-Although symbol-fixing sources are deterministically extractor, we cannot first run a deterministic extractor before using \consref{cons:informal construction}.
-This is because we need to preserve distance between $w_0$ and $w_1$ and an extractor must not preserve distance between input points.
-We present an alternative approach, showing security of \LWE directly with symbol-fixing sources.
+Although symbol-fixing sources are deterministically extractible~\cite{KZ07}, we cannot first run a deterministic extractor before using \consref{cons:informal construction}.
+This is because we need to preserve distance between $w$ and $w'$ and an extractor must not preserve distance between input points.
+We present an alternative approach, showing security of $\LWE$ directly with symbol-fixing sources.
 
@@
 \begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .
-Since \lemref{lem:uniform LWE decision} requires that $q = O(n^{3/2})$, setting  $\beta = \omega(1)$ is sufficient for $q^{-\beta} = \ngl(n)$ as required in \thref{thm:blockLWE}.
-Efficiency follows by \lemref{lem:i t poly time}.
-For a more detailed explanation of parameters see \secref{ssec:block params}.
+%Recall that \thref{thm:blockLWE} requires that $q^{-\beta} = \ngl(n)$.
+Since, \lemref{lem:uniform LWE decision} requires that $q = O(n^{3/2})$, the condition of \thref{thm:blockLWE} are satisfied by any  $\beta = \omega(1)$.
+Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see \secref{ssec:block params}. 
 \end{proof}
@@
 
+\bnote{Need grants for Leo and Xianrui}
 \bibliographystyle{alpha}

### 2013-09-03 CompFuzzExt.tex
Discussion of behavior when distance is large

@@
 However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
+Furthermore, this approach does not allow the use of private randomness; private randomness is a crucial ingredient in our construction.
 %We ask whether it is possible to avoid this loss by making whole process ``computational.''
@@
 \label{sec:preliminaries}
-For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
+For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-For the Hamming metric over $Z^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $.
+For the Hamming metric over $\mathcal{Z}^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose t} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
-If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
+If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
 \item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
@@
 \end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
+Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.
+
+\paragraph{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.
+In the information-theoretic setting this seemed inherent as the ``correct'' $R$ should be information-theoretically unknown conditioned on $P$.
+However, in the computationally setting this is not true.
+Looking ahead, in our construction $R$ is information-theoretically determined conditioned on $P$~(with high probability over the coins of \gen).
+Our $\rep$ algorithm will never output an incorrect key but may run for an unbounded time~(with high probability over the coins of \gen).
+However, it is not clear this is the desired behavior.
+For this reason, we leave the behavior of \rep ambiguous when $\dis(w, w')>t$.
+% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
 
@@
 \label{lem:shannon to sketch}
-For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
+For an alphabet $\mathcal{Z}$, let $\mathcal{C}$ over $\mathcal{Z}^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
 %  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
@@
 %\end{center}
-Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
+Then there exists a $(\mathcal{Z}^n, m, m-(n\log|\mathcal{Z}|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$. 
 %satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
@@
 \label{cor:rec yields sketch}
-Let $Z$ be an alphabet.
-Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+Let $\mathcal{Z}$ be an alphabet.
+Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
+If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
 $4(\epsilon+t\delta)$. 
@@
 
-\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |Z|-\tilde{m})-2$ bits of entropy.
+\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |\mathcal{Z}|-\tilde{m})-2$ bits of entropy.
 
@@
 \label{thm:imp of unp entropy}
-Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
+Let $\mathcal{Z}$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{Z}^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+If $s_{sec} \geq t(|\rec|+n\log |\mathcal{Z}|)$, then $\tilde{m}\leq n\log |\mathcal{Z}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
@@
 If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.
+(A recent result of Brakerski et al.~\cite{brakerski2013classical} shows security of $\LWE$ based on hardness of approximating lattices problems for classical algorithms.
+We have not considered how this result can be integrated into our analysis.)
 
@@
 Thus, to achieve a lossless construction we need $k \log q = m\log \rho q$.
-In order to decode a meaningful number of errors we need $m>n>k$.
-However, dimensions of $w$ are sampled with fewer bits than dimensions of $X$.
-That is, $\log \rho q < \log q$.
+In other words, in order to decode a meaningful number of errors, the vector $w$ is of higher dimension than the vector $X$, but each coordinate of $w$ is sampled using fewer bits than each coordinate of $X$.
 Thus, by increasing the size of $q$ we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
@@
 Let $d$ be a positive constant (giving us a tradeoff between running time of $\rep$ and $|w|$).
-Consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
-Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+Consider the Hamming metric over the alphabet $\mathcal{Z}=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
+Let $W$ be uniform over $\mathcal{M}=\mathcal{Z}^m$, where $m={(c/d+2)n}=O(n)$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |\mathcal{Z}|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
@@
 \begin{definition}
-Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $Z$.  We say that it is a $(m+
-\alpha, m, |Z|) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
-Note that $H_\infty(W)=m\log |Z|$.
+Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $\mathcal{Z}$.  We say that it is a $(m+
+\alpha, m, |\mathcal{Z}|) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
+Note that $H_\infty(W)=m\log |\mathcal{Z}|$.
 \end{definition}
@@
 Let $n$ be a security parameter, $m, \alpha$ be polynomial in $n$, and $q=\poly(n)$ be a prime and $\beta\in\mathbb{Z^+}$ be such that $q^{-\beta} = \ngl(n)$. 
-Let $U$ denote the uniform distribution over $Z^m$ for an alphabet $Z\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |Z|)$ symbol fixing source over $Z^{m+\alpha}$.
+Let $U$ denote the uniform distribution over $\mathcal{Z}^m$ for an alphabet $\mathcal{Z}\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |\mathcal{Z}|)$ symbol fixing source over $\mathcal{Z}^{m+\alpha}$.
 If $\distLWE_{n, m,q, U}$ is secure, then $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ is also secure.
@@
 The proof techniques of Brakerski et al.
-allow removal of $\beta$, improving the parameters of \thref{thm:blockLWE}.
+can be extended to our setting with multiple fixed dimensions, improving the parameters of \thref{thm:blockLWE}~(specifically, removing the need for $\beta$).
 
@@
 Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d\le c$ be a positive constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
-Let $\mathcal{M} = Z^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
-Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |Z|)$-symbol fixing sources.  If GAPSVP and SIVP are hard to approximate within polynomial factors 
+Let $d\le c$ be a positive constant and consider the Hamming metric over the alphabet $\mathcal{Z}=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
+Let $\mathcal{M} = \mathcal{Z}^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
+Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |\mathcal{Z}|)$-symbol fixing sources.  If GAPSVP and SIVP are hard to approximate within polynomial factors 
 using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
  there exists $\epsilon = \ngl(n)$ 
-such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, m\log |\mathcal{Z}|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
  The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
@@
 \label{sec:proof of imp unp entropy}
-Instead of proving the result just for Hamming metric over $Z^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
+Instead of proving the result just for Hamming metric over $\mathcal{Z}^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
 We now define this second condition:
@@
 
-\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
+\thref{thm:imp of unp entropy} follows by noting that $\mathcal{Z}^n$ can be sampled in time $n\log |\mathcal{Z}|$ and neighborhood sampled in time $n\log |\mathcal{Z}|$.
 \end{proof}

### 2013-09-04 trunk/CompFuzzExt.tex
Removing dead text from tex file

@@
 Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
-%Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
 
@@
 The setting
-%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
-%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
 consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).
@@
 
-%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
 Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.
@@
 Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%Furthermore, we have (asymptotic)~constructions that meet these bounds.
 
@@
 For high-entropy sources of $w$ over the Hamming metric, this bound matches the best information-theoretic security sketches.
-
-%%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
-When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high.
-%The minimum entropy loss for secure sketches has been quantified in past work.
-Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08},
-%%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
-%the entropy loss of a secure sketch that can reconcile $t$ errors
-% %with high probability 
-% is bounded by the redundancy of
-%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
-Constructions of fuzzy extractors that use a secure sketch inherit this bound.
-%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-
-%to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
-This string $\recout$ is  required to have high HILL entropy even conditioned on $s$.
-Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
 
@@
 
-%We show that this relaxation of the security requirement is  useful.
-Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
-%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
-The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
-%\lnote{it would be good to find another application}
-
 In \secref{sec:LWE block fixing sources}, we are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
@@
 However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
-%We ask whether it is possible to avoid this loss by making whole process ``computational.''
+Furthermore, this approach does not allow the use of private randomness; private randomness is a crucial ingredient in our construction.
 We compare the two approaches in \secref{sec:prg based comparison}.
 
-%Authentication generally requires secrets.
-Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
-Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
-%
-%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
-%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
-%It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
-%the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
-%Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.
-This feature is needed because $s$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
-%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.  
-%
-%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
-For example, in the application of secure sketches to fuzzy extractors (whose goal is to reliably produce a uniformly random secret key from a noisy input), the resulting secret key may be too short to be useful if the entropy loss is too high.
-However, because secure sketches are defined as information-theoretic objects, some entropy loss is inherent in any secure sketch construction, because $s$ contains enough information to recover $w$ from any value $w'$ that is close to it.
-%
-%The minimum necessary  entropy loss has been quantified in past work.
-Even if we don't require perfect correctness (i.e., allow $\rec$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
-%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
-%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-%
-%\paragraph {Our Contributions}
-%To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
-%The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-%
-%On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful.
-We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%%Furthermore, we have (asymptotic)~constructions that meet these bounds.
-%
-%On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction.
-The idea is to give up on reconstructing $w$ and, instead, to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
-This string $\recout$ is  required to have high HILL entropy even conditioned on $s$.
-Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-%
-%Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
-%~\ref{thm:lossless secure extractor log})).
-We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
-%
-%We show that this relaxation of the security requirement is  useful.
-Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
-%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
-The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
-%\lnote{it would be good to find another application} 
-%
-%Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
-To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).
-We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-The LWE error vector, in our case, is the input $w$ itself.
-To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
-We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed).
-This relaxation requires new results about the hardness of LWE when samples have a fixed error vector, which may be of independent interest~(\thref{thm:blockLWE}).
 \section{Preliminaries}
 \label{sec:preliminaries}
-For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
+For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
-%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
-%The {\em collision probability} of  $X$ is 
-%$\col(X) = \sum_{x} \Pr[X=x]^2$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
-%We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.
 For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
@@
 al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
-Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.
-can we change this $d$ to $\mathsf{dis}$?}
-
-\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
+Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+
+\begin{definition}
 \label{def:fuzzy extractor}
@@
 Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
-\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
+\begin{definition}
 \label{def:secure sketch}
@@
 An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
-
 \begin{definition}
@@
 
-%In \secref{sec:impossCompSecSketch} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch?
-It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
-%\begin{definition}
-%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
-%\[
-%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
-%\] where the probability is taken over the coins of \sketch and \rec.
-%\end{definition}
-\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
+\begin{lemma}
 \label{lem:fuzzy ext construction}
@@
 The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-%%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
-If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
+If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
 \item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
@@
 \end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
-
-%\bnote{There needs to be more linking language here.}
-%It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).
-In the next section, we show this paradigm is difficult to realize.
-
-%\textbf{Note: }A computational fuzzy extractor could also be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).
-We compare the two approaches in \secref{sec:prg based comparison} after presenting our construction.
-%, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).
-%The cause for the entropy loss in the secure sketch is the additional bits added for error correction.
-In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.
-%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.
-
-%=============================================================
+Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.
+
+\textbf{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.
+In the information-theoretic setting this seemed inherent as the ``correct'' $R$ should be information-theoretically unknown conditioned on $P$.
+However, in the computationally setting this is not true.
+Looking ahead, in our construction $R$ is information-theoretically determined conditioned on $P$~(with high probability over the coins of \gen).
+Our $\rep$ algorithm will never output an incorrect key~(with high probability over the coins of \gen) but may not terminate.
+However, it is not clear this is the desired behavior.
+For this reason, we leave the behavior of \rep ambiguous when $\dis(w, w')>t$.
+
 \section{Impossibility of Computational Secure Sketches}
@@
 
-%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp.
-unpredictability) entropy when given a source with $m$ bits of entropy.
 In particular, for the case of the Hamming metric and inputs that have full entropy, our results are as follows.
@@
 \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  construct sketches with essentially the same information-theoretic security\footnote{The security in  \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  is expressed in terms of entropy of the error rate; recall that $\log B_t(\cdot)\approx H_q(t/n)$, where $n$ is the number of symbols, $q$ is the alphabet size, and $H_q$ is the $q$-ary entropy function.} .
-
 In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
-
-%These results are strongest for high entropy sources.
-The results get weaker as we consider sources with lower starting entropy.
-If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.
 
@@
 
-%\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}
-
 Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.
 Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the sketch-and-extract construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
-%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.
-This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.
-%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
-%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.
-We simply include both of these parameters in the definition.
-We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.
 We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
@@
 We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.
-%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
-%\[
-%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
-%\]
 \end{definition}
-%We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.
-While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.
-\lnote{ do we need this?
-if distance is exactly $t'$, then the point is different as long as $t'>0$.
-So why not just say "exactly $t'$ in the definition?}
-
-%We will concentrate on metrics where the size of each ball is fixed.
-We say a metric space that obeys this property is regular~(using terminology from graph theory).
-This will allow us to show that the neighbor of a uniformly chosen point is also uniformly random.
-%\begin{definition}
-%A metric space $(\mathcal{M},d)$ is \emph{$(t, c)-$distance regular} if for all $x\in \mathcal{M}, |B_t(x)| = c$. 
-%\end{definition}
-%For a distribution $X$ we define the distribution $N_t(X)$ as the process of sampling a random neighbor of a random point in $X$.
-That is $\Pr[N_t(X) = z] = \sum_{x\in X}\Pr[X=x \wedge y \leftarrow B_t(x) \wedge z=y]$.
-%\begin{lemma}\label{lem:uniformNeighbor}
-%Let $(\mathcal{M}, d)$ be a $(t, c)-$distance regular and let $U$ be uniform over $\mathcal{M}$.  Then $U \overset{d}= N_t(U)$.
-%
-%\end{lemma}
-%\begin{proof}
-%Note that $\forall z, \Pr[U = z] =1/|\mathcal{M}|$.  Thus, it suffices to show that $\forall z , \Pr[N_t(U) =z] =1/|\mathcal{M}|$.
-%
-%Fix an arbitrary $z\in \mathcal{M}$.  Then, 
-%\begin{align*}
-%\sum_{x\in U} \Pr[U=x \wedge y\leftarrow B_t(x) \wedge y=z] &=
-%\sum_{x\in U} \Pr[U = x \wedge x\in B_t(z)] \Pr[y\leftarrow B_t(x) \wedge y=z | x\in B_t(z)]\\
-%&=\frac{c}{|\mathcal{M}|} \frac{1}{c} = \frac{1}{\mathcal{M}}.
-%\end{align*}
-%%The uniform distribution over $\mathcal{M}$ is a random bit string of length $n$.
-Let $x\leftarrow \mathcal{M}$, then $\sample (x) = z = x\oplus y$ where $y$ has at weight at least $1$ and at most $t$.
-Since $x$ was uniformly random $x\oplus y$ is uniformly random.
-%\end{proof}
-
-\ignore{
-Finally, we will 
-dealing with an arbitrary secure sketch that only needs to satisfy the correctness property of a secure sketch~(see \defref{def:secure sketch}).  \lnote{why do we need this definition?}
-
-\begin{definition}
-A pair of functions $(\sketch, \rec) $ is a $(s_{rec}, t)$-\emph{recover functionality for a metric space $\mathcal{M}, d$} if $\sketch : \mathcal{M}\rightarrow \{0,1 \}^*$ is a randomized function and $\rec: \mathcal{M}\times \{0, 1\}^*\rightarrow \mathcal{M}$ is a function computable by a circuit of size at most $s_{rec}$, such that $\rec (w', \sketch (w)) = w$ if $\dis(w, w')\leq t$ for all $w, w' \in \mathcal{M}$.
-\end{definition}
-}
-
-\ignore{For any recover functionality, there is an inherent tradeoff between the ability to keep points stationary and to perform error correction.
-
-\begin{theorem}\label{thm:compSketchImpUniform}
-Let $\mathcal{M}, d$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable and $(t, c)$-distance regular.
-Furthermore, let $(\sketch, \rec)$ be any $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.
-Then $H^\hill_{\epsilon, s}( U |\sketch(U))\not \geq \Hoo(U)$ for $s \approx (s_{neigh} + 2s_{rec})$ and $\epsilon=1/2$~(if $s_{neigh}, s_{rec}$ are polynomial so is $s$).
-\end{theorem}
-%\emph{Intuition:  }The goal that a recover functionality cannot be both stable~(maps points to themselves) and correcting~(maps nearby points back to themselves).
-If a recovery functionality is correcting then we can check if the input point maps to itself.
-If a recovery functionality is stable then we can see if recovery succeeds with nearby points.
-
-\begin{proof}
-Let $U_\mathcal{M}$ be the uniform distribution over $\mathcal{M}$ and let $d$ a  metric.
-Furthermore assume $\mathcal{M}$ is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be a $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.
-Let $X\overset{d}= Y\overset{d}= U_\mathcal{M}$ be i.i.d..
-It suffices to construct a distinguisher $D$~(whose size is $s\approx s_{neigh}+2s_{rec}$) such that $\expe[D(X, SS(X))]- \expe[D(Y, SS(X))]\geq \epsilon = 1/2$.
-%Let $q$ be a polynomial.  
-$D$ is defined as follows:
-\begin{enumerate}
-\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$. 
-\item Sample $b\leftarrow \{0,1\}, z'\leftarrow \sample(z)$.
-\item If $b=1$:
-\subitem If $\rec(z', s) = z\wedge \rec(z, s) = z$ output $1$.
-\item If $b=0$:
-\subitem If $\rec(z, s) = z \wedge \rec(z', s)=z$ output $1$.
-\item Output $0$.
-\end{enumerate}
-First note that $D$ is of size $O(s_{neigh}+2s_{rec})$ and thus in polynomial in $s_{sam}, s_{neigh}$.
-It remains to show that $D$ separates $(X,\sketch(X))$ and $(Y,\sketch(X))$.
-We being by noting that on input $(X, \sketch(X)), D$ outputs $1$.
-By \lemref{lem:uniformNeighbor} we have:
-\begin{align*}
-0&=\delta([Y, \sample(Y), \sketch(X)],& &[\sample(Y), Y, \sketch(X)])\\
-&=\delta([Y, \sketch(X), \sample(Y), \sketch(X)],& &[\sample(Y), \sketch(X), Y, \sketch(X)])\\
-&=\delta([\rec(Y,\sketch(X)), \rec(\sample(Y),\sketch(X))],& &[\rec(\sample(Y), \sketch(X)), \rec(Y, \sketch(X))])
-\end{align*}
-Thus, the output of $\rec$ is the same when given $(\sample(Y), Y)$ or $(Y, \sample(Y))$\footnote{This is also true for a stronger class of recover functionalities that is able to keep state between queries.}.
-This means it can properly recover $Y$ with probability at most $1/2$ over the ordering of inputs.
-Thus we have,
-\begin{align*}
-\Pr[D'(X, \sketch(X))=1] - \Pr[D'(Y, \sketch(X))=1] &=\\
-1 - \frac{1}{2}(\Pr[\rec(Y, \sketch(X)) = Y \wedge \rec(\sample(Y),\sketch(X))=Y]&+\\\Pr[\rec(\sample(Y), \sketch(X)) = Y \wedge \rec(Y, \sketch(X)) = Y])&\geq 
-1-\frac{1}{2}\left(1\right) =\frac{1}{2}
-\end{align*}
-
-%\begin{enumerate}
-%\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$.
-%\item Initialize $correct, stable = 0$.
-%\item For $i=1...q$:
-%\subitem $x_i \leftarrow U$, if $\rec(x_i, s) = x_i, stable +=1/q$.
-%\subitem $x_i' \leftarrow \sample (x_i)$, if $\rec(x_i', s) = x_i, correct+=1/q$.
-%\item If $\rec(z, s)\neq z$ output $0$.
-%\item If $stable<1/2$ output $1$
-%\item Else $z'\leftarrow \sample(z)$.
-%\subitem If $\rec(z', s) = z$ output $1$.
-%\subitem Else output $0$.
-%\end{enumerate}
-%
-%We begin by noting that $D$ is of size $O(q(s_{sam}+s_{neigh}+2s_{rec})+2s_{rec}+s_{neigh})$ and thus is polynomial in $s_{sam}, s_{neigh}, s_{rec}$.
-It remains to show that $D$ separates $(X, SS(X))$ and $(Y, SS(X))$ by a noticeable $\epsilon$.
-Let $STABLE = \Pr[\rec(U, \sketch(X)) = U]$.
-We begin by noting that $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-That is, after step (3) $D$ has a good approximation
-%of $STABLE$.  Similarly, let $CORRECT = \Pr[\rec(\sample(U), \sketch(X)) = U]$.  As before $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-%Thus, after step (3), $\Pr[|CORRECT-correct|>\ngl \wedge |STABLE-stable|>\ngl|]<\ngl$.
-We proceed assuming, that $CORRECT$ and $STABLE$ are known exactly at step (4), and note the output of $D$ is negligibly close to the output of a distinguisher that knows $CORRECT$ and $STABLE$ exactly~(we label this distinguisher $D'$).
-%\begin{claim}
-%$CORRECT+STABLE\leq 1$.
-%\end{claim}
-%\begin{proof}
-%\begin{align*}
-%\Pr[\rec(U, \sketch(X) = U] + \Pr[\rec(\sample(U), \sketch(X)) = U]&\leq\\
-%\Pr[\rec(U, \sketch(X) = U]  + \Pr[\rec(Y), \sketch(X)\neq Y] &=1
-%\end{align*}
-%Where the first inequality proceeds because of \lemref{lem:uniformNeighbor} and the fact that \sample never returns itself.
-The equality proceeds as these events as these events are complementary events after renaming.
-%\end{proof}
-%We now show that when $(\sketch, \rec)$ is stable or correcting the distinguisher has nonnegligible advantage:
-%\begin{itemize}
-%\item Case 1: $STABLE<1/2$.
-%\begin{align*}
-%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1] &=\\
-%\Pr[\rec(X, \sketch(X) = X] - \Pr[\rec(Y, \sketch(X) = Y] &\geq
-% 1- 1/2  = 1/2
-%\end{align*} 
-%\item Case 2: $STABLE\geq 1/2, CORRECT \leq 1/2$.
-%\begin{align*}
-%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1]&=\\
-%\Pr[\rec(X, \sketch(X)) = X \wedge \rec(\sample(X), \sketch(X)) = X] &-\\\Pr[\rec(Y, \sketch(X) = Y) \wedge \rec(\sample(Y), \sketch(X)) = Y)]&\geq\\
-%1 - \Pr[\rec(\sample(Y), \sketch(X)) = Y)]= 1-1/2 = 1/2
-%\end{align*}
-%\end{itemize}
-%Thus, in both cases we have $\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1]\geq 1/2$.  As noted above, $CORRECT, STABLE$ are only known approximately and thus:
-%\[
-%\Pr[D(X, \sketch(X) )= 1] - \Pr[D(Y, \sketch(X) )= 1]\geq 
-%\Pr[D'(X, \sketch(X) )= 1] - \Pr[D'(Y, \sketch(X) )= 1] - \ngl \geq 1/2 -\ngl
-%\]
-This completes the proof.
-\end{proof}
-
-This proof relied on two crucial facts: 1) that the neighbor of a uniform point was uniformly distributed 2) for an point uncorrelated with the value of the secure sketch it was impossible to distinguish between a point and its neighbor.
-We can extend this result to distributions other than the uniform distribution but by drawing on more general results from coding theory.
-
-\subsection{Indistinguishable sketches imply information theoretic sketches}
-In this section we show that the results of \thref{thm:compSketchImpUniform} can be extended to whenever $X$ is indistinguishable from a high min-entropy distribution.  }
 
@@
 However, we work with an arbitrary recover functionality that is not necessarily monotone.}.
-
 Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.
@@
 If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
-%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
-If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
 \end{theorem}
-%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.
-In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.
-Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.
-Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g.
-where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).
-However, this is still a meaningful set of error correcting codes.
-A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.
-They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.
-
-%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
+
 For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
@@
 \label{lem:shannon to sketch}
-For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
-%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
-%
-% Define the following procedures
-%\lnote{I think this description is buggy}
-%\begin{center}
-%\begin{tabular}{c|c}
-%\begin{minipage}{3in}
-%\textbf{\sketch}
-%\begin{enumerate}
-%\item Input $w\leftarrow W$.
-%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
-%\item Sample $c\leftarrow \mathcal{C}$.
-%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
-%\item Output $p = x \oplus c, \pi$.
-%\end{enumerate}
-% \end{minipage} &
-%\begin{minipage}{3in}
-%\textbf{\rec}
-%\begin{enumerate}
-%\item Input $(w', p, \pi)$
-%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
-%\item Compute $c' = p \oplus x'$.
-%\item Compute $c = \rec'(c)$.
-%\item Output $p\oplus c$.
-%\\
-%\end{enumerate}
-%\end{minipage} 
-%\end{tabular}
-%\end{center}
-Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
-%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
-%\begin{itemize}
-%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
-%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
-%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
-%\end{itemize}
+For an alphabet $\mathcal{Z}$, let $\mathcal{C}$ over $\mathcal{Z}^n$ be a $(t, \delta)$ Shannon code.
+Then there exists a $(\mathcal{Z}^n, m, m-(n\log|\mathcal{Z}|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$.
 \end{lemma}
-%\begin{construction}
-%Let $\delta >0$ be a parameter.
-%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.
-Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.
-Thefn for $\beta = 2^{-\ell}
-%\end{construction}
 Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
@@
 \label{cor:rec yields sketch}
-Let $Z$ be an alphabet.
-Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+Let $\mathcal{Z}$ be an alphabet.
+Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
+If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
 $4(\epsilon+t\delta)$. 
-%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
 \end{corollary}
-\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
-
-\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |Z|-\tilde{m})-2$ bits of entropy.
-
-%\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.
-Unfortunately, we have lower bounds for the entropy drop for information-theoretic sketches:
-
-%\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
-%\label{prop:lower bound entropy drop}
-%For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.
-Here $h(\cdot)$ is the binary entropy function.
-%\end{proposition}
-
-%Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.
-This entropy drop is tied to the Shannon capacity.
-Furthermore, we have information theoretic constructions that meet these bounds.
-Thus, defining a computational secure sketch using HILL entropy is unlikely to be useful.
-
-%\begin{theorem}
-%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable.
-Furthermore, let $(\sketch, \rec)$ be any $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.
-Let $U$ be the uniform distribution over $\mathcal{M}$.
-If $s_{ball}, s_{rec}, s_{sam}$ are of polynomial size, then $H^\hill_{\epsilon, s}( U |\sketch(U))\not \geq \Hoo(U)$ for polynomial $s$ and noticeable $\epsilon$.
-%\end{theorem}
-%\emph{Intuition:  }We will show that a recover functionality cannot be both stable~(maps points to themselves) and correcting~(maps nearby points back to themselves).
-If a recovery functionality is correcting then we can check if the input point maps to itself.
-If a recovery functionality is stable then we can see if recovery succeeds with nearby points.
-%
-%\begin{proof}
-%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable~(by $\sample$).
-Let $(\sketch, \rec)$ be a $s_{rec}, t$-recover functionality for $\mathcal{M}, d$.
-Let $X, Y, U$ be i.i.d.
-and be the uniform distribution over $\mathcal{M}$.
-By assumption $s_{ball}, s_{sam}, s_{rec}$ be of polynomial size.
-It suffices to construct a polynomial size distinguisher $D$ such that $\expe[D(X, SS(X))]- \expe[D(Y, SS(X)]> \epsilon$ for noticeable $\epsilon$.
-Let $q$ be a polynomial.
-$D$ is defined as follows:
-%
-%\begin{enumerate}
-%\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$.
-%\item Initialize $correct, stable = 0$.
-%\item For $i=1...q$:
-%\subitem $x_i \leftarrow U$, if $\rec(x_i, s) = x_i, stable +=1/q$.
-%\subitem $x_i' \leftarrow \sample (x_i)$, if $\rec(x_i', s) = x_i, correct+=1/q$.
-%\item If $\rec(z, s)\neq z$ output $0$.
-%\item If $stable<2/3$ output $1$
-%\item Else $z'\leftarrow \sample(z)$.
-%\subitem If $\rec(z', s) = z$ output $1$.
-%\subitem Else output $0$.
-%\end{enumerate}
-%
-%We begin by noting that $D$ is of size at most $q(s_{sam}+s_{ball}+2s_{rec})+2s_{rec}+s_{ball}$ and thus is polynomial assuming that $q, s_{sam}, s_{ball}, s_{rec}$ are of polynomial size.
-It remains to show that $D$ separates $X, SS(X)$ and $Y, SS(X)$ by a noticeable $\epsilon$.
-Let $STABLE = \Pr[\rec(U, \sketch(X)) = U]$.
-We begin by noting that $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-That is, after step (3) $D$ has a good approximation
-%of $STABLE$.  Similarly, let $CORRECT = \Pr[\rec(\sample(U), \sketch(X)) = U]$.  As before $\Pr[|correct-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-%
-%\begin{claim}
-%$CORRECT+STABLE\leq 1$.
-%\end{claim}
-%\bnote{finish proof}
-%
-%\end{proof}
+\textbf{Note} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
+
+\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |\mathcal{Z}|-\tilde{m})-2$ bits of entropy.
 
@@
 In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.
-We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax the definition slightly, similarly to the relaxation of HILL entropy described in the previous section).
-
-\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
+We begin by recalling the definition of conditional unpredictability entropy~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}, which captures the notion of ``hard to guess'' (we relax the definition slightly, similarly to the relaxation of HILL entropy described in the previous section).
+
+\begin{definition}
 \label{def:unp entropy}
@@
 We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
-\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
+Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a \emph{reconstructive} extractor~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
 
@@
 
-%This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.
-The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.
-This means we cannot construct a good code out of the points of $Y$.
-\lnote{I find the previous three sentences more confusing than helpful; do we really need them?
-should we reword or remove?} %Our bound is a result of the Hamming bound for the space.
-
 \subsection{Avoiding sketch entropy upper bounds}
@@
 The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  
-%The results get weaker as we consider sources with lower starter entropy.  
 This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed, and thus there is no (computational)~entropy loss.  
-%For example, we can not rule out a computational secure sketch with entropy loss for low entropy sources.
-%This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.  
 This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .
@@
 
-%\subsection{Defining  Computational Fuzzy Conductors}
-%\label{sec:unp secure sketch}
-%In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.
-If, the error correcting algorithm outputs a new random variable, bounds do not apply.
-Instead of building a computational sketch, we will build a computational conductor.
-We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
-%%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
-%%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
-%%\begin{enumerate}
-%%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
-%%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
-%%\end{enumerate}
-%%\end{definition}
-%%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.
-We begin by defining unpredictability entropy:
-%
-%
-%%We now provide a definition of a robust computational sketch using unpredictability entropy:
-%\begin{definition}\label{def:comp secure sketch}
-%A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
-%\begin{enumerate}
-%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
-%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.
-That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
-%If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
-%\end{definition}
-%
-%%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.
-%In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.
-We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
-
 \section{Computational Fuzzy Extractor based on \class{LWE}}
@@
 \begin{construction}
-Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
-Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
-%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$.
-$\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$.
-$m > n$ are parameters to be figured out later.
+Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. 
+Define $\gen, \rep$ as follows:
 \begin{center}
@@
  We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
- %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
 We describe one possible polynomial-time $\decode_t$ (which corrects more errors than is possible by exhaustive search) in \secref{sec:time main construction}.
@@
 If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.
+(A recent result of Brakerski et al.~\cite{brakerski2013classical} shows security of $\LWE$ based on hardness of approximating lattices problems for classical algorithms.
+We have not considered how this result can be integrated into our analysis.)
 
 The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
-%\subsection{LWE with uniform errors}
-%\label{subsec:LWE uniform error}
 Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
@@
 The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
-%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.
-%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
-%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
-%\label{lem:uniform LWE}
-%Let $n$ be a security parameter.
-Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.
-Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.
-Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.
-Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
-%\end{lemma}
-
-%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
 \begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
@@
 \end{lemma}
-
-%\begin{lemma}
-%\label{lem:conversion to unpredictability}
-%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
-%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
-%\end{lemma}
-%\begin{lemma}
-%\label{lem:dmq with unp entropy}
-%Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer.
-Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+\sigma}m$.
-Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+\sigma}m/\rho)$.
-Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.
-Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
-%\[
-%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
-%\]
-%\end{lemma}
-The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} as long as all the parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.
-%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}.
-2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.
-
-%\subsection{Computational Secure Sketch based on \class{LWE}}
-%\label{subsec:fuzzyExtLWE}
-%We now give a formal description of our sketch based on LWE.  We now consider a source $W$~(this fulfills the role of $E$ in standard LWE notation):
-%
-%\begin{construction}[Computation Secure Sketch based on LWE]
-%\label{cons:LWESecureSketch} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers.
-Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+\sigma}m$.
-Let $\decode_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
-Let $W$ be a distribution over $\{0,1\}^{(\log \rho q)\times m}$\,.
-Then the following is a computational secure sketch:%We present the construction in
-%%\begin{figure}
-%%\label{fig:construction figure}
-%%\caption{Computational Secure Sketch based on the Learning with Errors problem}
-%\begin{center}
-%\begin{tabular}{c|c}
-%\begin{minipage}{3in}
-%\textbf{\sketch}
-%\begin{enumerate}
-%\item Input $w\leftarrow W$.
-%\item Sample $\vA\in\Fq^{m\times n}, x\in\Fq^n$ uniformly.
-%\item Output $p = (\vA, \vA x+w)$.\\
-%\end{enumerate}
-% \end{minipage} &
-%\begin{minipage}{3in}
-%\textbf{\rec}
-%\begin{enumerate}
-%\item Input $(w', p)$
-%\item Parse $p$ as $(\vA, \vect{C})$
-%\item Set $x' = \decode_t(\vA, \vect{C}-w') $. 
-%\item Output $w = \vect{C}-\vA x'$.
-%\end{enumerate}
-%\end{minipage} 
-%\end{tabular}
-%\end{center}
-%%\end{figure}
-%%\textbf{\gen}
-%%\begin{enumerate}
-%%\item Input $w\leftarrow W$.
-%%\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
-%%\item Use $w$ as the randomness for the sampling algorithm, \\$\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
-%%\item Output $p = (A, AX+E)$.
-%%\end{enumerate}
-%%
-%%
-%%\textbf{\rep}
-%%\begin{enumerate}
-%%\item Input $(w', p)$
-%%\item Parse $p$ as $(A, C)$
-%%\item Compute $E' \leftarrow \sample (w')$.
-%%\item Set $X' = \decode_t(A, C-E') $. 
-%%\item Output $sam_w = C-AX'$.
-%%\end{enumerate}
-%\end{construction}
+The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} if all parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.
 
@@
 \label{sec:time main construction}
-%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
 \consref{cons:informal construction} is useful only if $\decode_t$ can be efficiently implemented.
@@
 The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
-%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).
-\lnote{can we combine these lemmas into one?
-It's hard for the reader to compare line-by-line to see where the differences are.
-More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
-%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
-%\label{lem:i t constant time}
-%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).
-Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.
-Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
-%\end{lemma}
 \begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
 \label{lem:i t poly time}
-%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
 Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
@@
 \end{lemma}
-
-%\textbf{Problems:} Construction~\ref{cons:LWESecureSketch} does not meet Definition~\ref{def:comp secure sketch}.
-This is because the sampling algorithm may not be invertible.
-Furthermore, in standard $\LWE$ the sampling algorithm is Gaussian and there is no fixed number of bits used to sample error in any dimension.
-Approximating the Gaussian distribution using a fixed number of bits may be possible but there are still two error patterns which require a significantly different number of bits.
-We will address both of these problems by sampling the error from a uniform distribution.
 
@@
 Thus, to achieve a lossless construction we need $k \log q = m\log \rho q$.
-In order to decode a meaningful number of errors we need $m>n>k$.
-However, dimensions of $w$ are sampled with fewer bits than dimensions of $X$.
-That is, $\log \rho q < \log q$.
-Thus, by increasing the size of $q$ we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
+In other words, in order to decode a meaningful number of errors, the vector $w$ is of higher dimension than the vector $X$, but each coordinate of $w$ is sampled using fewer bits than each coordinate of $X$.
+Thus, by increasing the size of $q$~(while keeping $\rho q$ fixed) we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
 The formal statement is below.
-
-%\begin{theorem}
-%\label{thm:lossless secure sketch}
-%Let $n$ be a security parameter and let $t$ be a constant.
-Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.
-Let $W$ be uniform over $\zo^{n(t+1)b}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors, there is a
-%\[
-%(\zo^{n(t+1)b}, |W|,|W|, \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-% for $\epsilon = \ngl(n), s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
-%\end{theorem}
 
@@
 Let $d$ be a positive constant (giving us a tradeoff between running time of $\rep$ and $|w|$).
-Consider the Hamming metric over the alphabet $Z=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
-Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c/d+2)n}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |Z|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
+Consider the Hamming metric over the alphabet $\mathcal{Z}=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
+Let $W$ be uniform over $\mathcal{M}=\mathcal{Z}^m$, where $m={(c/d+2)n}=O(n)$.
+If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |\mathcal{Z}|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
-% for following parameters:
-%\[
-%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
-%\] 
 \end{theorem}
@@
 For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
-%In particular, we describe how to set $q = \poly(n)$.
 \end{proof}
@@
 We can essentially think of $\vA X+W$ as an encryption of $X$ that where decryption works from any close $W'$.
-%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.
 
@@
 (A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; note that LWE-based pseudorandom generators exist~\cite{applebaum2006pseudorandom}.)
-%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.
-This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.
 
@@
 
-%However, the construction of a computational fuzzy extractor by 
-%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
-In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
-The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).
-
 To summarize, the advantage of \consref{cons:informal construction} is that the security of our construction does not depend on the decoding radius $t$.  
@@
 The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$ (but for $n$ and $m$ reduced by the amount of fixed symbols).
-%\vspace{.1in}
 \begin{theorem}
@@
 The proof techniques of Brakerski et al.
-allow removal of $\beta$, improving the parameters of \thref{thm:blockLWE}.
+can be extended to our setting with multiple fixed dimensions, improving the parameters of \thref{thm:blockLWE}~(specifically, removing the need for $\beta$).
 
 \thref{thm:blockLWE} allows us to construct a lossless computational fuzzy extractor from block-fixing sources:
-
-%\begin{theorem}
-%\label{thm:lossless block sketch}
-%Let $n$ be a security parameter and let $t$ be a constant.
-Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.
-Let $W$ be an $\alpha$-symbol fixing source over $\zo^{((t+1)n+\alpha)b}$.
-There is a \lnote{instead of ``there is'' can we actually point to the to construction?}
-%\[
-%(\zo^{((t+1)n+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-% for $s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
-%\end{theorem}
 
@@
 \begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .  
-%Recall that \thref{thm:blockLWE} requires that $q^{-\beta} = \ngl(n)$.
-Since, \lemref{lem:uniform LWE decision} requires that $q = O(n^{3/2})$, the condition of \thref{thm:blockLWE} are satisfied by any  $\beta = \omega(1)$.
 Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see \secref{ssec:block params}. 
@@
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-
 \bnote{Need grants for Leo and Xianrui}
+
 \bibliographystyle{alpha}
@@
 We use $i$ as a index into matrix rows and the error vector and $j$ as an  index into columns and the solution vector.
-
-%It should be clear to the reader where the reduction differs for another block fixing source.\lnote{I don't like the phrasing; maybe we should say that if the blocks are fixed to some non-0 value, the reduction is essentially the same}
 
@@
 \item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
-%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
 \item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
@@
 Since $\vS_T$ is a full rank square matrix and $\gamma_i$ is uniformly and independently generated, that row is also uniform and independent of other entries in $\vA$.
-% In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.
-Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.
-Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.
-Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5.
-For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number.
-Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors.
-Therefore, the entire matrix $\vA$ is a truly random matrix.
-This completes the claim.
 \end{proof}
@@
 Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
-%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
 We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
-%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.
-The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
 Recall the other rows are not modified.  We have the following for $1\leq i\leq m$:
@@
 This completes the proof of the~\lemref{lem:averageToMaximalError}.
-
-%Suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]> 2\epsilon$.  
-%This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.
-Then note that $\Pr[W\in V]> 1/2$ as $W\setminus V$ contains at most $2^{k-1}-1$ points each of which has probability at most $1/2^k$ so $\Pr[W\in (W\setminus V)]\leq (2^{k-1}-1)/2^k < 1/2$.
-Thus,
-%\begin{align*}
-%\Pr_{w\in W}[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]\\
-%&\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
-%\end{align*}
-%% where $\forall d\in D, \Pr[d'\leftarrow \sample(d) \wedge \rec(d') > 2\epsilon$.  In turn this implies that  
-%%\begin{align*}
-%%\Pr_{c\in C}[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]&=\frac{1}{|C|} \sum_{c\in C}  \Pr[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]\\
-%%&\geq \frac{1}{|C|} \sum_{d\in D}  \Pr[ d'\leftarrow \sample (d) \wedge \rec(d') \neq d]\\
-%%&\geq \frac{1}{|C|}\sum_{d\in D} 2\epsilon = \frac{1}{|C|}\left(\frac{|C|}{2}+1\right)2\epsilon = \epsilon + 2\epsilon/|C|> \epsilon
-%%\end{align*}
-%This is a contradiction.  The statement of~\lemref{lem:averageToMaximalError} follows directly.
 \end{proof}
@@
 where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. 
-%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.
-Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.
-This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.
 Define $D$ as:
@@
 \[ \Pr_{x\leftarrow X_y}[x'\leftarrow \neigh(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
-%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
 Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.
@@
 
-\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
+\thref{thm:imp of unp entropy} follows by noting that $\mathcal{Z}^n$ can be sampled in time $n\log |\mathcal{Z}|$ and neighborhood sampled in time $n\log |\mathcal{Z}|$.
 \end{proof}
-
-%\bnote{This is the proof for not relaxed unpredictability entropy}
-%\begin{proof}
-%Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
-Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
-We begin by showing that $Y$ must correctly recover most of the time.
-%\begin{claim}
-%\label{clm:y is recoverable}
-%\begin{align*}
-%\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
-%\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
-%\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
-%\end{align*}
-%\end{claim}
-%\begin{proof}
-%Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
-%\begin{itemize}
-%\item Input $x\in \zo^b, s\in\zo^*$.
-%\item Sample $x'\leftarrow B_t(x)$.
-%\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
-%\end{itemize}
-%Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
-The statement of the claim follows as
-%\begin{align*}
-%\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
-%\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
-%\end{align*}
-%\end{proof}
-%We now consider the experiment $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
-\clref{clm:y is recoverable} says that
-%\[
-% \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
-%\]
-%We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
-Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
-%We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
-%\begin{itemize}
-%\item Input $s\in\zo^*$.
-%\item Sample $x'\leftarrow \zo^b$.
-%\item Output $\rec(x', s)$.
-%\end{itemize}
-%We define by $X$ the random variable corresponding to the sample $x'$ performed by $\decode_t$.
-%We now show that $\mathcal{I}$ predicts $Y$:
-%\begin{align*}
-%2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
-%&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
-%\end{align*}
-%Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
-%\end{proof}
-
-%\subsection{Proof of \lemref{lem:i t constant time}}
-%\label{sec:proof lem i t constant time}
-%\begin{proof} We consider the expected number of iterations in step 2 when $t+1\leq m/n$.
-Steps 3 and 4 can be accomplished in time $n^3\log q +s_{ver}$.
-An iteration of $\decode_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
-That is,
-%\begin{align*}
-%\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq  \prod_{i=0}^{n-1}\left( 1-\frac{m-n}{n(m-i)}\right)\\
-%&\geq \prod_{i=0}^{n-1}\left( 1-\frac{1}{n}\right)\geq \left(1-\frac{1}{n}\right)^n \geq 1/4.
-%\end{align*}
-%Note in the last step we assume that $n\geq 2$.
-The minimum of $(1-1/n)^n$ is achieved at $n=2$ and it quickly converges to $1/e$.
-Thus, the expected number of iterations is at most $4$ giving the stated running time for $\decode_t$.
-%\end{proof}
 
@@
 \end{align*}
-%\xnote{$ m \log 2n^{1/2+\sigma}m = n \log n^f$}
 This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.
@@
 t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-%f \log n &= \frac{m}{n}\log 2n^2m\\
 f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma} m+1}{\log n}
@@
 \end{align*}
-%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+\sigma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+\sigma}}{\log n}$}
 Note that $f$ is at a constant in $n$.
@@
 
-%The output corresponds to stretch~(in computational entropy) of $1/g$.
-%, A linear stretch instead of $m\log (2\rho q +1)= k\log q$.
-%Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
-
 \subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
@@
 Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
-
-\ignore{
-\subsection{Old parameter setting}
-The question then becomes whether there is a setting 
-Our construction has two goals: 1) maximizing correcting capability~(while retaining polynomial time decoding, and 2) maximizing the unpredictability entropy of $W$ conditioned on the construction~($\tilde{m}$ in \defref{def:comp secure sketch}).
-Our parameters will differ significantly depending on what setting of $t$ is used.
-We will consider both settings where $t\leq m/n-2$ and $t\leq c\log n (m/n-2)$.
-Recall these corresponding to Construction~\ref{cons:decoding algorithm} running either in fixed polynomial time or time approximately $n^{2c}$.
-We consider each of these settings:
-
-$\mathbf{t \leq m/n-1}$
-
-We first find the appropriate range of $n$.
-First, we need $n>n_0$ for LWE security.
-Increasing $n$, up to the point when $H_\infty(X)=H_\infty(W)$, i.e., $n\log q = m\log\rho q$, increases the unpredictability entropy of the construction~(see \assref{assume:entropy LWE}).
-However, this decreases the number of errors $t$ we can correct.
-There is no advantage to increasing $n$ further\footnote{We primarily consider the construction with no entropy drop, if a drop is unpredictability entropy is acceptable, more errors can be corrected.
-However, if the remaining unpredictability entropy is worse than a known information theoretic construction~(see~\cite{DBLP:journals/siamcomp/DodisORS08}), an information theoretic construction should be used.
-}.
-
-We first analyze the lossless construction, when  $H_\infty(X)=H_\infty(W)$ and thus $n\log q = m\log\rho q$.
-Substituting $m \ge (t+1)n$ above one has:
-\[
-n \log q  = m \log \rho q \geq (t+1)n \log \rho q
-\]
-Thus, the lossless construction can support settings where $t+1\leq \frac{\log q}{\log \rho q}$.
-In order to apply \lemref{lem:uniform LWE}, we need that $\rho q\geq 2n^2m \geq 2(t+1)n^3$.
-We consider the setting $q = n^d$ for some constant $d$ (larger $q$ is unlikely to improve parameters unless
-%In Appendix~\ref{sec:parameters q expo}, we review parameters where $q=2^n$, these parameters are worse unless 
-lattice problems are hard to approximate within exponential factors.)  
-Dividing the above equations above we have:
-\[
-t+1\leq \frac{\log q}{\log \rho q}\leq \frac{\log q}{\log 2(t+1) n^3}\leq \frac{\log n^d}{\log 2t n^3} \approx d/3
-\]
-(the last step follows because the second-to-last step already implies $t\le d\log n$).
-Thus, we can support a constant $d/3-1$ number of errors where $q = n^d$ is the size of our field.
-Because we need $\rho q\geq 2n^2m \geq 2(t+1)n^3$ (to apply \lemref{lem:uniform LWE}), we require $\rho > n^{3-d}$.
-Thus, our construction is secure if SIVP and GAPSVP are hard within approximation factors of
-\[
-\tilde{O}(n^{5/2}m/\rho) = \tilde{O}\left(\frac{n^{5/2} m }{\rho}\right)
-= \tilde{O}\left(\frac{n^{5/2}t}{n^{3-d}}\right)
-= \tilde{O}\left(n^{d-1/2}m\right)
-\]
-
-%As an example if $\gamma = n^{c}$, this yields:
-%\[
-%t\leq \frac{n}{n + \log n + \log t - \log \gamma} = \frac{n}{n+\log n +\log t  -\log n} = \frac{n}{n + \log t}
-%\]
-%Alternatively, if $\gamma = n^{\log n}$, this yields:
-%\[
-%t\leq \frac{n}{n + \log n + \log t - \log \gamma} = \frac{n}{n+\log n +\log t  -\log^2 n} = \frac{n}{n+\log n - \log^2 n + \log t}
-%\]
-%Thus, as $q$ grows we can support a larger number of errors.
-However, the growth of $q$ with a fixed size $\rho q$ leads to the approximation factor in \lemref{lem:uniform LWE} no longer being a harder problem.
-Thus, $q$ can only be increased while the lattice problems in \lemref{lem:uniform LWE} is still believed to be hard.
-Furthermore, in the decision formulation of \lemref{lem:uniform LWE decision} requires that $q(n) = poly(n)$.
-This means that $t\leq O(\log n)$.
-
-$\mathbf{t\leq c\log n(m/n -1)}$
-
-We repeat the above analysis.  Recall we now consider the case where $m\geq (t+1)n/(c\log n)$.  We seek to satisfy:
-\[
-n\log q = m\log \rho q \geq (t+1)n \log \rho q /(c\log n)
-\]
-Again, we assume that $q = n^d$ for some constant $d$.  Then 
-\[
-t+1\leq \frac{c \log n \log q }{\log \rho q}\leq \frac{cd\log^2 n}{ \log \frac{2(t+1) n^3}{c\log n}}\leq \frac{cd \log^2 n}{3 \log n} \approx \frac{cd \log n}{3}.
-\]
-This gives $\rho > n^{3-d}/\log n$ and security if SVIP and GAPSVP are hard within approximation factors of $\tilde{O}(n^{d-1/2}m/\log n)$.
-
-\textbf{Formulation from $W, t$:}
-
-In a standard application, a source $W$ and number of errors $t$ will be given\footnote{Parameter settings will change the alphabet size and thus might change $t$, we ignore these effects and assume $t$ is given.}.
-Thus, the goal is to maximize security subject to correcting $t$ errors.
-This means the following parameters must be set:
-\begin{itemize}
-\item How large should $X$ be?
-The size of $X$ is the limiting factor for the resulting unpredictability entropy.
-Thus, $n$ should be as large as possible while allowing decoding.
-We must also ensure that $n>n_0$ for security.
-\item How large a field should we operate over?
-This is the parameter $q$.
-Increasing this parameter allows correcting more errors~(subject to the underlying lattice problems still being hard to approximate).
-\item How length block should $W$ be split into?  This is the parameter $\rho q$.  Setting this parameter also sets $m = |W|/\log \rho q$.
-\end{itemize}
-
-Unfortunately, the parameters $m, n$ and depend on each other and cannot be set independently.  As before, we will consider the fixed poly time decoder and variable poly time decoder in turn.
-
-$\mathbf{t\leq (m/n-1)}$
-
-We set parameters in the following order:
-\begin{itemize}
-\item Let $m, n$ be integer solutions to the following equations that maximizes $n$~(if the maximum solution is less than $n_0$, we cannot support a secure construction):
-\begin{align*}
-|W| &= m\log 2n^2m\\
-n&\leq m/(t+1)
-\end{align*}
-We assume that the solution for $m,n$ exists and is tight~(in the sense that $n = m/(t+1)$).
-If not, there is an entropy loss in the construction due to size mismatches~(in the entropy analysis below) and padding~(to ensure that $|W|$ is an integer number of blocks).
-\item Set $\rho q = 2n^2m $.
-\item Set $q = n^{(t+1)\log( 2(t+1)n)/\log n}$.  Note that although $n$ appears in the exponent if $t$ is a fixed constant~(does not depend on $|W|$), this value is $q =\poly(n)$.  
-\end{itemize}  Given these parameters, we can calculate the sizes of $X$ and $W$~(as we show in the \secref{sec:security of LWE cons} $\tilde{m} =|W|$):
-\begin{align*}
-H^{\unp}_{\epsilon, s} ( W | AX+W) &= \min\{ H_\infty(W), H_\infty(E)\}\\
-H_\infty(X) = |X| &= n \log q= \frac{m}{t+1}\log n^{(t+1)\log 2(t+1)n/\log n} \\
-&= \frac{m}{t+1} \frac{(t+1)\log 2(t+1)n}{\log n} \log n = m \log 2(t+1)n^3 \approx m\log 2n^2m\\
-H_\infty(W) = |W| & = m \log \rho q = m \log 2n^2 m\,.
-\end{align*}
-
-$\mathbf{t \leq c\log n(m/n-1)}$
-We set parameters in the following order:
-\begin{itemize}
-\item Let $m, n$ be integer solutions to the following equations that maximizes $n$~(if the maximum solution is less than $n_0$, we cannot support a secure construction):
-\begin{align*}
-|W| & = m\log 2n^2m\\
- \frac{nt}{c\log n} + n&\leq m
-\end{align*}
-We assume that the solution for $m,n$ exists and is tight~(in the sense that $ \frac{nt}{c\log n} + n=m$).
-If not, there is an entropy loss in the construction due to size mismatches~(in the entropy analysis below) and padding~(to ensure that $|W|$ is an integer number of blocks).
-\item Set $\rho q = 2n^2m $.
-\item Set $q = (2n^2m)^{m/n}$.  Note if $t = O(\log n)$, then $m/n = \frac{t}{c\log n} +1 = O(1)$ and thus $q$ is polynomial in $n$.
-\end{itemize}  Given these parameters, we can calculate the sizes of $X$ and $W$~(as we show in the \secref{sec:security of LWE cons} $\tilde{m} =|W|$):
-\begin{align*}
-H^{\unp}_{\epsilon, s} ( W | \vA X+W) &= \min\{ H_\infty(W), H_\infty(E)\}\\
-H_\infty(X) = |X| &= n \log q= n \log (2n^2m)^{m/n} = m \log 2n^2m\\
-H_\infty(W) = |W| & = m \log \rho q = m \log 2n^2 m\,.
-\end{align*}
-
-We'll now consider a formulation for a fixed length biometric and a number of block errors.
-We assume that $n$ is given as a security parameter and thus we ask how many errors can be corrected for a noisy uniform distribution of length $w>>n$.
-We denote the number of errors by $t$~(we'll be able to correct block errors over the alphabet $[-\rho q, \rho q]$).
-Let $n$ be a security parameter and let $W$ be the uniform distribution of length $w>>n$.
-Let $m$ as the minimum integer such that $m\log 4m^2 n\geq w$.
-Set $q = 2^{m/n}4m^2n$.
-Then split $W=( W_1,..., W_m)$ where each $W_i$ is of length $\log 4m^2 n$ bits.
-Then, for $W' =( W_1',.., W_m')$ if  $t = |\{i |  W_i \neq W_i'\}| \leq m/n$ block errors, Construction~\ref{cons:decoding algorithm} allows for decoding in expected polynomial time.
-Furthermore, $H^{\unp}_{\epsilon, s}(W | \vA X+W)\geq |W|$~(stating \lemref{lem:uniform LWE decision} in the language of Assumption~\ref{assume:entropy LWE}).
-
-\begin{theorem}
-\label{thm:security of secure sketch}
-Let $n_0$ be a security parameter and let $W$ be uniform over $\mathcal{M}$ and let $t$ be a constant.  Let $m,n $ be the solution to the following equations that maximizes $n$.
-\begin{align*}
-|W| &= m\log 2n^2m\\
-n&\leq m/t
-\end{align*}
-If $n>n_0$ and $n = m/t$ and \assref{assume:entropy LWE} holds, then for 
-\begin{align*}
-q &= n^{3t\log( \sqrt[3]{2t}n)/\log n}\\
-\rho q &= 2n^2m,
-\end{align*}  Construction~\ref{cons:LWESecureSketch} with uniform error over the interval $[-2n^2m, 2n^2m]$ is a $(\mathcal{M}, |W|, |W|, \epsilon, s, s_{sketch}, s_{rec}, t)$-computational secure sketch for $s = \poly(n), s_{sketch} = O(m\times n )$ and $s_{rec}$ is expected polynomial time.
-\end{theorem}
-
-\bnote{Not sure what to do with this}
-\begin{theorem}
-\label{thm:security of block sketch}
-Let $n_0$ be a security parameter and let $t$ be a constant.
-Let $W\in \{0, 1\}^{(m+\alpha)\times \log 2n^2m}$ be an $\alpha$-symbol fixing source where $m,n $ are the solution to the following equations that maximizes $n$.
-\begin{align*}
-|W| &= (m+\alpha)\log 2n^2m\\
-(n+\alpha)&\leq (m+\alpha)/t
-\end{align*}
-If $n>n_0$ and $n+\alpha = (m+\alpha)/t$ and \assref{assume:entropy LWE} holds, then for 
-\begin{align*}
-q &= n^{3t\log( \sqrt[3]{2t}n)/\log n}\\
-\rho q &= 2n^2m,
-\end{align*}  Construction~\ref{cons:LWESecureSketch} with uniform error over the interval $[-2n^2m, 2n^2m]$ is a $(\mathcal{M}, \Hoo(W), \Hoo(W), \epsilon, s, s_{sketch}, s_{rec}, t)$-computational secure sketch for $s= \poly(n)$,  $s_{sketch} = O(m\times n )$ and $s_{rec}$ is expected polynomial time under .
-\end{theorem}
-
-}
-
-\ignore{
-\section{Fuzzy Extractor Statement of Construction~\ref{cons:LWESecureSketch}}
-\label{sec:fuzzy extractor phrasing}
-In this section we restate Construction~\ref{cons:LWESecureSketch} as a computational fuzzy extractor instead of a computational secure sketch:
-\begin{construction}[Computational Fuzzy Extractor based on LWE] 
-\label{cons:LWEFuzzyExtractor} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers, furthermore let $\chi$ be a distribution $\Fq$ that can be sampled with a fixed number of bits $s_{err}$.
-Let $\decode_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.
-Furthermore, let $\rext$ be a reconstructive extractor.
-Let $W$ be a distribution over $\{0,1\}^{s_{err}\times m}$.
-
-\textbf{\gen}
-\begin{enumerate}
-\item Input $w\leftarrow W$.
-\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
-\item Use $w$ as the randomness for the sampling algorithm, $\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
-\item Sample $seed\leftarrow U$ as required for \rext.  Compute $r\leftarrow \rext(E, seed)$
-\item Set $p = (A, AX+E, seed)$.
-\item Output $(r, p)$.
-\end{enumerate}
-
-\textbf{\rep}
-\begin{enumerate}
-\item Input $(w', p)$
-\item Parse $p$ as $(A, C, seed)$
-\item Compute $E' \leftarrow \sample (w')$.
-\item Set $X' = \decode_t(A, C-E') $. 
-\item Compute $r\leftarrow \rext (C-AX', seed)$.
-\item Output $r$.
-\end{enumerate}
-\end{construction}
-
-\begin{theorem}[Security of Construction~\ref{cons:LWEFuzzyExtractor}]\label{thm:LWEFuzzyExtractor}
-Fix $(n, m, q, \chi)$ such that Assumption~\ref{assume:general LWE} holds for $\mathcal{I}$ of size at most $s$ with success $\epsilon$.
-Furthermore assume that a fixed number of bits $s_{err}$ are necessary to sample from $\chi$.
-Let $\rext: \chi^m \times\{0,1\}^\ell\rightarrow \{0,1\}^{k_{len}}\times \{0,1\}^\ell$ be an extractor with $(\log 1/\epsilon - \log 1/\delta, \delta)$-reconstruction $(\cons,\decons)$.
-Let $\decode_t$ be an inverter as described in Construction~\ref{cons:LWEFuzzyExtractor} of size $s_{\decode_t}$.
-Then Construction~\ref{cons:LWEFuzzyExtractor} is a $(\{0,1\}^{m\times s_{err}}, m\times s_{err}, k_{len}, t, s_{rec}, s/(|\cons|+|\decons|), 5\delta)$ computational fuzzy extractor where $s_{rec, t} = s_{\decode_t}+ |\sample| + O(m\times n\times \log q) + |\rext|$.
-\end{theorem}
-}
-
-\ignore{
-\section{Min-entropy error LWE}
-Throughout this section we will assume that \sample uses $\ell$ bits of randomness to produce the required distribution in a single dimension.
-Usually, this is the normal (Gaussian) distribution with some mean.
-Note that for the uniform distribution sampling requires $\log q$ bits where $q$ is the size of the range.
-By information theory we know that in expectation, the number of random bits is smaller for an distribution that is not uniform, but this provides us no guarantee about the worst case number of bits.
-We will begin with noting a few cases that seem significantly easier to show.
-Recall that the distribution $W$ is drawn from is specified and known by the adversary.
-\begin{itemize}
-\item Case 1: $\Hoo(W)\leq \ell (m- n)$.
-This case is not secure.
-Let $W\in\{0,1\}^{\ell m}$ and we further specify $W=W_1,...,W_m$ where each $W_i\in\{0,1\}^\ell$.
-We then set $W_1,...,W_n$ equal to some fixed value, $0$ without loss of generality, and $W_{n+1},...,W_m$ to the uniform distribution.
-Then it is clear for the first $n$ equations, the adversary is solving a system $Ax=b$ without any error and this can be done in $P$.
-\item Case 2: Full or no entropy.
-As before, let $W\in\{0,1\}^{\ell m}$ and we further specify $W=W_1,...,W_m$ where each $W_i\in\{0,1\}^\ell$.
-We further restrict to the case where each $W_i$ either $W_i\overset{d}=U_\ell$ or $\Hoo(W_i) = 0$.
-Thus, for each dimension either, one of the two occurs: the error is properly generated or the adversary knows the error exactly.
-So, for each dimension, given the $W_i\overset{d}=U_\ell$, the adversary can only guess the correct random variable not better than $2^{\ell}$.
-Similarly, if given the $\Hoo(W_i) = 0$, the adversary can always guess the correct variable.(\xnote{This is trivial, since if we give $\Hoo(W_i) = 0$, we are actually giving the a random variable has probably of 1.})
-
-We are considering the case that the adversary will be given the ensemble $\{W_1,...,W_n\}$, where each $W_i$ has some entropy.
-
-\item Case 3: General case.
-\item \textbf{Hypothetical worry case}  Suppose for convenience we are working with the normal distribution that has variance $\frac{2}{\pi}$ (centered around 0).  That is 
-\[
-\Pr[X=x] = \frac{1}{\sqrt{\frac{2}{\pi}}\sqrt{2\pi}}e^{-\frac{1}{2}{\frac{2}{\pi}x^2}}=\frac{1}{2}e^{-\pi x^2}
-\]
-Thus, $\Pr[X=0] =1/2$.
-One can easily design a procedure $\sample'$ that generates this distribution using a maximum of some number $\ell$ bits.
-Let $w_1,...,w_\ell$ be the bits that $\sample'$ takes as input.
-Then when $w_1=0$ the sampler outputs $0$.
-The generation for other values does not matter (only that generating some value takes $\ell$ bits).
-Thus, to generate $n$ samples we need at most $\ell n$ bits.
-However, there is a distribution with min-entropy $\Hoo(W)=(\ell -1) m$, that produces always produces the all zero error.
-This distribution has the first bit of each $W_i$ 0 and the remaining bits truly random.
-Thus, it seems impossible for our scheme to be secure for an arbitrary procedure \sample, but we will need to specify a specific \sample.
-Another possibility is to use a different distribution that looks like the normai distribution but requires a ``flatter'' number of coins to be used for each distribution.
-Is there a definition of an algorithm that uses the same number of random bits for each invocation?
-Would this be enough to get rid of this problem?
-\end{itemize}
-Questions: 
-\begin{enumerate}
-\item How we sample this error vector $\vect{e}$?  Can we do something other than Gaussian to remove some worries?
-\item Given the two biometric data which have small distance between each other, will we get the small distance between the error vector after sampling?
-\textbf{Solved, each dimension is sampled independently.  Thus, our distance blowup is only as large as the number of bits needed to sample each dimension.}
-\item When is LWE easy and when is LWE hard?  Are we going to be able to create a sufficient gap between these two cases?
-\item Does the parallel sampler of Peikert allow for the distance in two randomness being small, creating small output distance?
-\textbf{Solved, was trying to do the wrong thing.  Just Gaussian in each dimension.}
-\item Does the sampler of Peikert allow for nonuniform input distribution?
-\textbf{Solved, was trying to do the wrong thing (was trying to sample from lattice points, instead of adding noise around a lattice point).}
-\subitem If not how does applying an extractor change the distance of two distributions?
-\item How if it all can this be used concurrently?  Seems very one time right now.
-\item How efficient will our decoding procedure be?  Efficient enough for practical usage?
-\end{enumerate}
-
-\textbf{What security do we need: }
-}
-
-\ignore{
-\section{Robustness of LWE to error with min-entropy}
-\label{sec: lwe min-entropy}
-
-In this section we explore the robustness of the LWE assumption when the errors are drawn from a deficient distribution.
-We provide a short introduction to the Learning with Errors problem in \secref{sec:fuzzyCompLWE}.
-For a more complete introduction see the survey by Regev~\cite{regevLWEsurvey}.
-The tools presented in this section are used to show the security of the computational secure sketch presented \subsecref{subsec:fuzzyExtLWE}.
-This work is also of independent interest and can be viewed in a similar way to the work of Goldwasser et.
-al.~\cite{goldwasserRobustLWE}.
-In their work, they consider the robustness of an LWE instance $A, Ax+e$ where $x$ is sampled from a distribution that has min-entropy but is not uniform.
-They then use this result to show LWE-based cryptosystems are leakage-resilient.
-Our theorem statement will follow a similar structure to the theorem statement of Goldwasser et.
-al.
-so we first present their informal theorem:
-\begin{theorem}~(\cite[Theorem 1 (Informal)]{goldwasserRobustLWE})
-For any super-polynomial modulus $q=q(n)$, any $k\geq \log q$, and any distribution $\mathcal{D}=\{D\}_{n\in\mathbb{N}}$ over $\{0,1\}^n$ with min-entropy $k$ , the (non-standard) LWE assumption, where the secret is drawn from distribution $\mathcal{D},$ follows from the (standard) LWE assumption with secret size $\ell\overset{\Delta}=\frac{k-\omega(\log n)}{\log q}$ (where the ``error rate'' is super-polynomially small and the adversaries run in time $\poly(n)$).
-\end{theorem}
-
-Before considering high entropy error, we must be clear about what this means.
-The $x$ in an LWE instance is sampled uniformly from $\{0,q\}^n$, thus the sampling procedure requires $\lceil \log q\rceil\times n$ bits.
-However, $e$ is sampled from some error distribution $\chi$.
-$\chi$ is normally the normal distribution centered around $0$ with some variance $\sigma^2$ and then rounded to the nearest integer between $[-q/2, q/2]$.
-Sampling from a rounded normal distribution requires a variable number of random bits for each dimension.
-Indeed, using the normal distribution there are events with nonzero but negligible probability.
-These events necessarily take a large number of bits to sample.
-
-\textbf{This is internal discussion and needs to be taken care of before presentation:}  There are two ways to provide these bits: 1) break the random string into chunks where each chunk is as long as the maximum number of random bits needed 2) provide the random bits needed to each dimensions.
-One might hope that this problem is avoided by rounding to the nearest integer, but there is still some weight assigned to integers far from $0$.
-We could consider a distribution whose statistical distance to the normal distance is exponentially small and gives weight 0 to all integers outside some radius.
-
-For the moment we will ignore these problems and assume that a fixed number of bits is used to sample each dimension.
-This would be the case if we substituted the uniform distribution on a significantly smaller domain.
-\bnote{We need to be sure this produces a secure LWE instance}.
-
-Thus, we assume that there exists a $\sample$ that uses $\ell$ bits of randomness to produce an error term in one dimension.  We are now ready to present the LWE assumption:
-\begin{assumption}[Learning with Errors]
-Let $k$ be a security parameter and define $q=\poly(k)$\bnote{Do we want the poly or exponential case?}and $n = \poly( k)$.
-Let $x\overset{\$}\leftarrow \{0,q\}^n$.
-An LWE sample is of the form $(a,b) = (a, a_1x_1+...+a_nx_n+\sample(e) \mod q)$ where $a_1,...,a_n\overset{\$}\leftarrow\{0,q\}^n$ and $e\overset{\$}\leftarrow\{0,1\}^\ell$.
-The $(m,n,q,k)$-LWE assumption is that no algorithm given $m = \poly(k)$ LWE samples running in time $\poly(k)$ can recover $x$ with probability greater than negligible in $k$.
-\end{assumption}
-
-We then achieve our non-standard LWE assumption by sampling $e$ from a high-entropy distribution instead of the uniform distribution.
-
-\subsection{Affine min-entropy distributions}
-In the previous section, we investigated the security of the LWE assumption with deficient distributions.
-Namely, we saw that the LWE assumption for block-fixing sources was implied by the LWE assumption with fewer dimensions and samples.
-We now ask: what other types of min-entropy distributions can be shown to reduce to the LWE assumption?
-Using a reduction to standard LWE seems to require that the errors be considered homomorphically.
-This is because recovering the error terms would break LWE.
-Furthermore, these errors are first put through the \sample procedure, so this needs homomorphic properties as well.
-Thus, the class we can hope for in this reduction is a linear set of errors.
-
-Recall, a function, $f:D^n \mapsto R$, over field $K$ is a \textbf{linear transformation} if $\forall x,y\in D$ and $\forall a, b\in K, f(ax+by) = af(x) + bf(y)$.
-
-We will consider the \textbf{LWE assumption w/ linear sources}.
-That is, we consider an error distribution $E = E_1||...||E_k$ where $\Hoo(E) = qn$ and $E = \mathbf{T}(U_1||...||U_n)$ for rank $n$ matrix $\mathbf{T}: \Fq^n\mapsto \Fq^k$.
-\vspace{.1in}
-\begin{theorem}\label{thm:linearLWE}
-Let $k$ be a security parameter and define $q, n, m = \poly(k)$.
-Let $E$ be a linear source over $\{0,1\}^{\ell(m+\alpha)}$ where $\Hoo(E) \geq m\ell$.
-Then the $(m,n,q,k)$-LWE assumption where \sample is a linear transformation implies the $(m+\alpha, n+\alpha, q, k)$-LWE w/ linear sources assumption.
-\end{theorem}
-\begin{proof}
-The main difference between \thref{thm:blockLWE} and \thref{thm:linearLWE} is how we produce the errors terms.
-We will use the same basic strategy of introducing equations and randomizing, however, the equations will errors will now be involved in the randomization.
-As before, let $\mathcal{A}$ be an algorithm that accepts $m+\alpha$ LWE samples each of length $n+\alpha$ where the errors are generated $(E_1,..., E_{m+\alpha})^T = \mathbf{T} (U_1,..., U_m)^T$ for some matrix $\mathbf{T}$.
-Further, assume that $\mathcal{A}$ returns $x$ with noticeable probability.
-Our algorithm $\mathcal{A'}$ will make a single call to $\mathcal{A}$ and we will focus on properly preparing the LWE w/ linear sources instance.
-We use $A',A,C,D,F,G,b,b'$ with the same meaning as before.
-\end{proof}
-}
-
-\ignore{
-\subsection{LWE search reduction}
-\begin{proof}
-Let $\mathcal{A}$ be an algorithm that accepts $m+\alpha$ LWE samples each of length $n+\alpha$ where $\alpha$ of the equations have a known error (and the remainder of the errors are uniformly generated) and returns $x$ with noticeable probability.
-Denote this probability as $\epsilon$.
-We will show how to convert $\mathcal{A}$ into an algorithm $\mathcal{A'}$ that accepts $m$ LWE samples of length $n$ and returns $x'$ with noticeable probability.
-We begin by making the following assumptions for clarity:
-\begin{itemize}
-\item $\mathcal{A}$ asks for all $m+\alpha$ samples and asks for them simultaneously.  Since $\mathcal{A}$ has no effect on the samples, this does not limit $\mathcal{A}$'s power.
-\item For the known error samples, the added error is $0$.  It is clear in our reduction where the added error would be added, but exposition is clearer without these errors.
-\item The last $\alpha$ samples are the known error samples.  For other positioning of the known error samples, we can provide a permutation from our input, but this form is clearer.
-\end{itemize}
-The algorithm $\mathcal{A'}$ will make a single call to the algorithm $\mathcal{A}$ and thus the entire analysis will be showing that $\mathcal{A'}$ is able to properly prepare the instance that $\mathcal{A}$ is expecting and convert the result of $\mathcal{A}$ into a solution for the input of $\mathcal{A'}$.
-We will use the matrix notation for the remainder of the proof.
-Thus, the job of $\mathcal{A'}$ is to perform the following transformation:
-\begin{align*}
-\begin{array}{c | c}
-\mathcal{A'}\text{ receives:        } & \mathcal{A}\text{ expects: }\\\hline
-\left(A'\right) , b' = A' x' + e' & A = \left( \begin{array}{c | c}C & D \\ \hline F & G\end{array} \right), b=Ax+e
-\end{array}
-\end{align*}
-Where the matrices have the dimensions as shown in \figref{fig:matrixDimension}: 
-\begin{figure}[b]
-\[
-\begin{array}{c | c | c | c | c | c}
-A & A' & C & D & F & G\\\hline
-m\times n & (m+\alpha)\times( n+\alpha) & m\times n & m \times \alpha & \alpha \times n & \alpha \times \alpha
-\end{array}
-\]
-\caption{Dimensions of matrices in reduction.}
-\label{fig:matrixDimension}
-\end{figure}
-Thus, we have two major jobs, produce an augmented matrix $A$ that is a truly random matrix and to produce an augmented $b$ that given a solution for $x$ will yield a solution for $x'$.
-The code of $\mathcal{A'}$ is presented in \figref{fig:imperfectLWEreduction}.
-The main idea is to generate $\alpha$ new LWE samples and use $\alpha$ new variables to exactly solve these equations.
-These last $\alpha$ equations then have no errors and can be used to randomize the instance to produce a random matrix without augmenting the error in the $b$ vector.
-\begin{figure}
-\begin{enumerate}
-\item Input $A', b' = A'x' +e'$.
-\item Randomly generate $F$.
-\item Set $b = (b'_1,..., b'_n, \$, ..., \$)$ that is set the first $n$ values of $b$ equal to $b'$ and randomly generate the remainder.
-\item Initialize $A = \left(\begin{array}{c | c}C = A' & D = \mathbf{0}\\\hline F & G = I\end{array}\right)$.
-\item For $i=1...m+\alpha$, perform the following randomization:\label{step:randomizationSearch}
-\subitem Randomly generate $\gamma_{i,1},.., \gamma_{i,\alpha}$.
-\subitem Set $A_{i, \cdot} = A_{i, \cdot} +\sum_{j=1}^\alpha \gamma_{i,j}A_{m+j, \cdot}$.
-\subitem Set $b_i = b_i +\sum_{j=1}^\alpha \gamma_{i,j} b_j$.
-\item Run $\mathcal{A}$ on input $A, b$.
-\item Receive output $x$ from $\mathcal{A'}$
-\item Output $x' = x_1,..., x_n$.
-\end{enumerate}
-\caption{Code for $\mathcal{A'}$ to generate LWE w/ symbol fixing source from standard LWE instance}
-\label{fig:imperfectLWEreduction}
-\end{figure}
-\begin{claim}\label{cl:randomMatrix}
-The matrix $A$ generated after Step \ref{step:randomizationSearch} is a random matrix.
-\end{claim}
-\begin{proof}
-First, the submatrices $D, G$ are clearly truly random after step \ref{step:randomizationSearch}.
-For the matrix $D, D_{i, j}$ is assigned the value $\gamma_{(i,j-n)}$.
-Similarly, for the matrix $G$, each entry is assigned as $\gamma_{(i-n, j-n)}$.
-This is due to the original construction of the matrix $G$.
-Then before step \ref{step:randomizationSearch} the matrices $C, F$ are random submatrices ($C=A'$ by assumption and $F$ by construction).
-Thus, it remains to show that $C, F$ remain random after step 5.
-We consider a single row vector of $C$.
-The new row vector $C_{(i,\cdot)} = C_{(i,\cdot)} +\sum_{j=1}^\alpha \gamma_{i,j}F_{(j, \cdot)}$.
-That is, $C_{(i,\cdot)}$ is the sum of a random vector and a random linear combination independent vectors.
-That is, $C_{(i,\cdot)}$ is a random vector.
-
-Similarly, consider a single row vector $F$.
-The new row vector $F_{(i,\cdot)} = \sum_{j=1}^\alpha \gamma_{i+n,j}F_{(i,\cdot)}$ is a random linear combination of independent vectors and thus truly random (since all $\gamma$ are chosen independently and randomly).
-\bnote{I feel these claims are obvious but I would like to have a citation.}
-
-Thus, the entire matrix $A=\left(\begin{array}{c | c}C & D \\\hline F & G\end{array}\right)$ is a truly random matrix.  This completes the claim.
-\end{proof}
-\begin{claim}\label{cl:goodLWEinstance}
-The inputs $A, b$ provided to $\mathcal{A}$ is a random LWE w/ symbol fixing sources instance (provided that $A', b'$ was a random instance).
-\end{claim}
-\begin{proof}
-By \clref{cl:randomMatrix} $A$ provided to $\mathcal{A}$ is a truly random matrix.
-Thus, we must show that $b$ is of the proper form.
-That is, we must show there exists an $x$ such that $b_i = A_{(i , \cdot)} x + e_i$ for $i=1,...,m$ and $b_i = A_{(i, \cdot)} x$ for $i=m+1,...,m+\alpha$.
-
-By assumption there exists an $x'$ such that $A'x'+e' = b'$.
-Before step \ref{step:randomizationSearch}, we have added $\alpha$ equations as well as $\alpha$ unknowns.
-This means there no solutions have been eliminated.
-Namely, $x^*_i = x'_i$ for $i=1,...,n$ and $x^*_i = b_i - \sum_{j=1}^m F_{i, j} x_j'$ for $i=n+1,..., n+\alpha$.
-The case where $F$ does not have full row rank is also handled because the $G$ is the identity matrix and thus $F|G$ always has full row rank.
-Furthermore, note that the last $\alpha$ equations have no error.
-Thus, before step \ref{step:randomizationSearch} there exists a solution $x^*$ of the proper form.
-It remains to show that the randomization in step \ref{step:randomizationSearch} retains the solution $x^*$.
-
-The newly randomized system $A,b$ retains the same solution $x^*$  because we are not adding rows that have any error terms.
-More precisely, let $A^*, b^*$ be the system before randomization (where $A^*x^*+e^* = b^*$).
-Then for each row vector
-\begin{align*}
-A_{(i, \cdot)} &= A^*_{(i, \cdot)}+\sum_{j=1}^\alpha \gamma_{i, j} A^*_{(m+j, \cdot)}, \\b_i &= b^*_i + \sum_{j=1}^\alpha \gamma_{i,j}b_j^*.
-\end{align*}
-Thus, we have the following for all $i=1,..., m$:
-\begin{align*}
-A_{(i, \cdot)} x^* +e_i^*&= (A^*_{(i, \cdot)}+\sum_{j=1}^\alpha \gamma_{i, j} A^*_{(m+j, \cdot)})x^*+e_i^*\\
-&= A^*_{(i, \cdot)}x^* + \sum_{j=1}^\alpha \gamma_{i,j} A^*_{(m+j, \cdot)}x^*+e_i^*\\
-&=\left( A^*_{(i, \cdot)}x^* + e_i^*\right)+ \sum_{j=1}^\alpha \gamma_{i,j} A^*_{(m+j, \cdot)}x^* \\
-&= b^*_i + \sum_{j=1}^\alpha \gamma_{i,j}b_j^* = b_i
-\end{align*}
-
-The same equations follow without the term $e_i^*$ for $i=m+1,..., m+\alpha$.  
-Thus, $x^*$ is a solution to the randomized LWE instance as well.
-It remains to show that $x^*$ is a random vector.
-This is clear for $x^*_i, i=1,...,n$.
-For the remaining $x^*_i, i=m+1, ..., m+\alpha$ this follows since $x^*_i = b_i - \sum_{j=1}^m F_{i, j} x_j'$ where $b_i, F_{i, j}$ are randomly and independently chosen.
-This completes the claim.
-\end{proof}
-\begin{claim}
-If $x$ is a ``good'' solution output by $\mathcal{A}$ then $x'_i = x_i$ for $i=1,...,n$.  
-\end{claim}
-This claim follows by the analysis in \clref{cl:goodLWEinstance}.  The added equations and randomization do not affect the solution to the original $A', A'x'+e'$ instance provided.
-\begin{claim}
-$\mathcal{A'}$ outputs a ``good'' solution with probability only negligibly different  than the probability $\mathcal{A}$ outputs a good solution.
-\end{claim}
-The only time that $\mathcal{A'}$ does not produce the correct distribution is when the rows of $F$ are not linearly independent.  However, this occurs with negligible probability~\cite{something}.
-
-Thus, we have constructed an algorithm $\mathcal{A'}$ that is able to recover a secret $x'$ of a standard LWE instance by adding samples  and equations that have no error.
-Notice it was critical to add a variable for each new sample being provided to $\mathcal{A}$.
-Furthermore, adding a degree of freedom for each new sample also allowed for construction of an equation with no error.
-This completes the proof.
-
-\end{proof}
-
-\ignore{
-\section{Parameters for Construction~\ref{cons:LWESecureSketch} when $q=2^n$}
-\label{sec:parameters q expo}
-The results of~\lemref{lem:uniform LWE decision} only support $q = \poly(n)$.  However, the reductions of Peikert may extend~\lemref{lem:uniform LWE decision} to exponential $q$.
-
-$q = O(2^n)$.
-In this setting, we are no longer constrained by field size.
-We need $\rho$ be large enough that the underlying lattice problems are still hard to approximate within a $\tilde{O}(n^{5/2}m/\rho)$ factor.
-Unfortunately, even correcting a constant $c$ number of errors is difficult in this domain.
-Let $\gamma$ be the maximum approximation factor where the underlying lattices problems are still hard.
-Then, $\rho \leq \frac{n^{5/2}m}{\gamma}$.
-To correct $c$ errors we need that $\log q/\log \rho q \geq c$.
-That is,
-\begin{align*}
-c&\leq \frac{\log q}{\log \rho q}\\
-&\leq \frac{n}{\log \frac{n^{5/2}mq}{\gamma}}\\
-&\leq \frac{n}{\log \frac{n^{5/2}m2^n}{\gamma}}\\
-&\leq \frac{n}{n + \log n + \log m - \log \gamma}
-\end{align*}
-Ignoring the $\log n$ and $\log m$ terms this yields that:
-\begin{align*}
-c&\leq \frac{n}{n-\log \gamma}\\
-\frac{n(c-1)}{c}&\leq \log \gamma\\
-2^{n(c-1)/c} &\leq \gamma
-\end{align*}
-Thus, supporting even a constant number of errors for $q=2^n$ requires lattice problems are exponentially hard to approximate, which would be quite surprising.  
-}
-}
 \end{document}

### 2013-09-04 CompFuzzExt-asiacrypt.tex
Asiacrypt version

--- 2013-09-04 trunk/CompFuzzExt.tex
@@
-\documentclass[11pt]{article}
-%\documentclass{llncs}
+%\documentclass[11pt]{article}
+\documentclass{llncs}
 \def\shownotes{1}
 
-\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
-\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
+%\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
+%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
 %\geometry{landscape}                % Activate for for rotated page geometry
@@
 \usepackage{amssymb, amsmath, amsfonts}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage{enumerate}
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{assumption}[theorem]{Assumption}
+%\newtheorem{claim}[theorem]{Claim}
+%\newtheorem{problem}[theorem]{Problem}
+\newtheorem{construction}{Construction}
+%\spn@wtheorem{lemma}{Lemma}{\bfseries}{\itshape}
 
@@
 \newcounter{ectr}
-
-\newenvironment{newitemize}{%
-\begin{list}{\mbox{}\hspace{5pt}$\bullet$\hfill}{\labelwidth=15pt%
-\labelsep=5pt \leftmargin=20pt \topsep=3pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{3pt} }}{\end{list}}
-
-\newenvironment{newenum}{%
-\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=17pt%
-\labelsep=5pt \leftmargin=22pt \topsep=3pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt} }}{\end{list}}
-
-\newenvironment{tiret}{%
-\begin{list}{\hspace{2pt}\rule[0.5ex]{6pt}{1pt}\hfill}{\labelwidth=15pt%
-\labelsep=3pt \leftmargin=22pt \topsep=3pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt}}}{\end{list}}
-
-\newenvironment{blocklist}{\begin{list}{}{\labelwidth=0pt%
-\labelsep=0pt \leftmargin=0pt \topsep=10pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{20pt}}}{\end{list}}
-
-\newenvironment{blocklistindented}{\begin{list}{}{\labelwidth=0pt%
-\labelsep=30pt \leftmargin=30pt\topsep=5pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{10pt}}}{\end{list}}
-
-\newenvironment{onelist}{%
-\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=18pt%
-\labelsep=7pt \leftmargin=25pt \topsep=2pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt} }}{\end{list}}
-
-\newenvironment{twolist}{%
-\begin{list}{{\rm (\arabic{ctr}.\arabic{ectr})}%
-\hfill}{\usecounter{ectr} \labelwidth=26pt%
-\labelsep=7pt \leftmargin=33pt \topsep=2pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{2pt} }}{\end{list}}
-
-\newenvironment{centerlist}{%
-\begin{list}{\mbox{}}{\labelwidth=0pt%
-\labelsep=0pt \leftmargin=0pt \topsep=10pt%
-\setlength{\listparindent}{\saveparindent}%
-\setlength{\parsep}{\saveparskip}%
-\setlength{\itemsep}{10pt} }}{\end{list}}
-
-\newenvironment{newcenter}[1]{\begin{centerlist}\centering%
-\item #1}{\end{centerlist}}
-
-\newenvironment{codecenter}[1]{\begin{small}\begin{centerlist}\centering%
-\item #1}{\end{centerlist}\end{small}}
+%
+%\newenvironment{newitemize}{%
+%\begin{list}{\mbox{}\hspace{5pt}$\bullet$\hfill}{\labelwidth=15pt%
+%\labelsep=5pt \leftmargin=20pt \topsep=3pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{3pt} }}{\end{list}}
+%
+%
+%\newenvironment{newenum}{%
+%\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=17pt%
+%\labelsep=5pt \leftmargin=22pt \topsep=3pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{2pt} }}{\end{list}}
+%
+%\newenvironment{tiret}{%
+%\begin{list}{\hspace{2pt}\rule[0.5ex]{6pt}{1pt}\hfill}{\labelwidth=15pt%
+%\labelsep=3pt \leftmargin=22pt \topsep=3pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{2pt}}}{\end{list}}
+%
+%
+%\newenvironment{blocklist}{\begin{list}{}{\labelwidth=0pt%
+%\labelsep=0pt \leftmargin=0pt \topsep=10pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{20pt}}}{\end{list}}
+%
+%\newenvironment{blocklistindented}{\begin{list}{}{\labelwidth=0pt%
+%\labelsep=30pt \leftmargin=30pt\topsep=5pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{10pt}}}{\end{list}}
+%
+%\newenvironment{onelist}{%
+%\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=18pt%
+%\labelsep=7pt \leftmargin=25pt \topsep=2pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{2pt} }}{\end{list}}
+%
+%\newenvironment{twolist}{%
+%\begin{list}{{\rm (\arabic{ctr}.\arabic{ectr})}%
+%\hfill}{\usecounter{ectr} \labelwidth=26pt%
+%\labelsep=7pt \leftmargin=33pt \topsep=2pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{2pt} }}{\end{list}}
+%
+%\newenvironment{centerlist}{%
+%\begin{list}{\mbox{}}{\labelwidth=0pt%
+%\labelsep=0pt \leftmargin=0pt \topsep=10pt%
+%\setlength{\listparindent}{\saveparindent}%
+%\setlength{\parsep}{\saveparskip}%
+%\setlength{\itemsep}{10pt} }}{\end{list}}
+%
+%\newenvironment{newcenter}[1]{\begin{centerlist}\centering%
+%\item #1}{\end{centerlist}}
+%
+%\newenvironment{codecenter}[1]{\begin{small}\begin{centerlist}\centering%
+%\item #1}{\end{centerlist}\end{small}}
 
@@
 \title{\textbf{Computational Fuzzy Extractors}}
-\author{Benjamin Fuller 
-\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
-~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
-%\author{}
+\author{Benjamin Fuller\inst{1} \and Xianrui Meng\inst{2} \and Leonid Reyzin\inst{2}}
+\authorrunning{B. Fuller \and X. Meng \and L. Reyzin}
+\institute{Boston University and MIT Lincoln Laboratory \and Boston University} 
+\tocauthor{Benjamin Fuller, Xianrui Meng, and Leonid Reyzin (Boston University)}
+
 \begin{document}
@@
 Our construction uses private randomness, which is allowed in the fuzzy extractor setting but not in noiseless randomness extraction.
-Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.
+Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE,regevLWEsurvey} and derive a longer key $r$.
 
@@
 
-\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.
+\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic,barak2011leftover,dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.
 They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.
@@
 \item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
+The \emph{correctness} property guarantees that for all $w, w'$ where $\dis(w, w')\leq t$, if $(R, P)\leftarrow \gen(w)$ then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
 If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
@@
 
-Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.
+Intuitively, HILL entropy is as good as average min-entropy for all computationally bounded observers.
 Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the sketch-and-extract construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
@@
 An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
-We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
+We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in the full version~\cite{fullerMengReyzin2013}):
 \begin{lemma}
@@
 
-We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
+We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in full version~\cite{fullerMengReyzin2013}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
+Let $(\mathcal{M}, \dis)$ be a $(s_{neigh}, t)$-neighborhood samplable metric space.
+Let $(\sketch, \rec)$ be a HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
 Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
@@
 Let  $(W, S)$ be a pair of random variables.
-We say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
+$W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S$, denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
 \[
@@
 
-We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
+A pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
 Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a \emph{reconstructive} extractor~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
@@
 Unfortunately, the conditional unpredictability entropy $\tilde{m}$ must decrease as $t$ increases, as the following theorem states.
-(The proof of the theorem, generalized to more metric spaces, is in \secref{sec:proof of imp unp entropy}.)
+(The proof of the theorem, generalized to more metric spaces, is in the full version~\cite{fullerMengReyzin2013}.)
 
@@
 \label{thm:imp of unp entropy}
-Let $\mathcal{Z}$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{Z}^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq t(|\rec|+n\log |\mathcal{Z}|)$, then $\tilde{m}\leq n\log |\mathcal{Z}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
+Let $\mathcal{Z}$ be an alphabet.
+Let $(\sketch, \rec)$ ben an unpredictability-entropy $(\mathcal{Z}^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$, if $s_{sec} \geq t(|\rec|+n\log |\mathcal{Z}|)$, then $\tilde{m}\leq n\log |\mathcal{Z}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
@@
 \begin{tabular}{c|c}
-\begin{minipage}{3in}
+\begin{minipage}{2.3in}
 \textbf{\gen}
@@
  \end{minipage} &
-\begin{minipage}{3in}
+\begin{minipage}{2.3in}
 \textbf{\rep}
@@
 Intuitively, security comes from the computational hardness of decoding random linear codes with a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.
-Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.
+In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  \[\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon.\]  Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.
 
@@
 \label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a complete description of the $\LWE$ problem and related lattices problems~(which we do not define here) see~\cite{regev2005LWE}.
+The $\LWE$ problem was introduced by Regev \cite{regev2005LWE,regevLWEsurvey} as a generalization of ``learning parity with noise." For a complete description of the $\LWE$ problem and related lattices problems~(which we do not define here) see~\cite{regev2005LWE}.
 We now recall the definition of the decisional version of the problem.
@@
 Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
-The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
+The formal statement is below~(proof in the full version of this work~\cite{fullerMengReyzin2013}):
 \begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
@@
 Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}; efficiency follows by \lemref{lem:i t poly time}.
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
+For a detailed explanation of the various parameters and constraints see the full version of this work\cite{fullerMengReyzin2013}.
 \end{proof}
@@
 \label{sec:prg based comparison}
-As mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
+As mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic,barak2011leftover,dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
 We will call this approach \emph{sketch-and-comp-extract}.
@@
 Then, security of $\distLWE_{n, m, q, \chi'}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi}$.
-We show this stronger version of the theorem in \apref{sec:proof of block theorem}.
+We prove this stronger version of the theorem in the full version of this work~\cite{fullerMengReyzin2013}.
 
@@
 \begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .  
-Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see \secref{ssec:block params}. 
+Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see the full version of this work~\cite{fullerMengReyzin2013}.
 \end{proof}
@@
 We thank Jacob Alperin-Sheriff for pointing out the connection with the work of Brakerski et al.
-The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+
+This work supported in part by National Science Foundation grants 0831281, 1012910, and 1012798.
+The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-\bnote{Need grants for Leo and Xianrui}
-
-\bibliographystyle{alpha}
+\bibliographystyle{splncs03}
 \bibliography{crypto}
@@
 \end{proof}
-
-We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
-\begin{claim}
-\label{cl:full rank matrix}
-Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
-let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha] >  1- q^{-\beta}$.
-\end{claim}
-\begin{proof}
-Let $p_i$ be the probability that the $i$th
-row is linearly dependent on the previous $i-1$ rows. 
-By the union bound, the probability that $\alpha$ rows are linearly dependent is bounded by 
-$\sum_{i=1}^\alpha p_i$.
-Since $i-1$ rows can span a space of size at most $q^{i-1}$, the probability $p_i$ that a randomly chosen $i$th row is in that space is at most $q^{i-1}/q^{\alpha+\beta}$. So
-\begin{align*}
-\Pr[\rank(\vS) < \alpha] &=\sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-= \frac{q^{\alpha}-1}{q-1}\frac{1}{q^{\alpha+\beta} }< q^{-\beta}.
-\end{align*}
-\end{proof}
-
-\section{Proof of Theorem \ref{thm:blockLWE}}
-\label{sec:proof of block theorem}
-
-\begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same.
- In the reduction, the distinguisher is allowed to depend on the source and can know the positions of the fixed blocks and their values.
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
-For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.
-Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.
-We use similar notation for the complement of $T$, denoted $T^c$.
-For a matrix or vector we use $\mathsf{T}$ to denote the transpose.
-We use $i$ as a index into matrix rows and the error vector and $j$ as an  index into columns and the solution vector.
-
-Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.
-Let $\beta$ be such that $q^{-\beta} = \ngl(n)$.
-All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
-Let $\chi'$ be some error distribution over $\Fq^m$ and let $\chi$ over $\Fq^{m+n}$ be defined by sampling $\chi'$ to obtain values on dimensions $1,..., m$ and then appending $\alpha$ 0s.
-
-Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi}$ with advantage $\epsilon>1/\poly(n)$.
-Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ .
-Then
-\[
-|\Pr[D(\vA, \vA X+\chi) = 1] - \Pr[D(\vA, U )=1]|> \epsilon.
-\]
-
-We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
-Let $\vA'$ denote the uniform distribution over $\Fq^{m\times n}$, $X'$ denote the uniform distribution over $\Fq^n$, and $U'$ denote the uniform distribution over $\Fq^{m}$ .
-We will build a distinguisher $D'$ of polynomial size for which
-\begin{align}
-\label{eq:block LWE dist}
-|\Pr[D'(\vA', \vA'X'+\chi') = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
-\end{align}
-$D'$  will make a single call to $D$, so we focus on how to prepare a random block-fixing instance for $D$ from the random instance that $D'$ is given.
-The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
-
-\begin{figure}[p]
-\begin{framed}
-\begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi'$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
-\item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, for uniformly chosen $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
-\item Choose $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ uniformly at random.
-		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
-\item For all $1\le j \le \alpha+\beta$, $j\notin T$:
-\label{step:fill in matrix}
-\subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
-\subitem For $i=1,..., m$:
-\subsubitem Choose $\vQ_{i,j}\overset{\$}\leftarrow \Fq$ uniformly at random.
-\subsubitem Set $b_i^* = b_i^* + \vQ_{i,j} x_{n+j}$.
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
-\item \label{step:randomization}
-For {$i=1,..., m$}:
-\subitem Choose a row vector $\gamma_i \leftarrow \Fq^{1 \times \alpha}$ uniformly at random.
-\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
-\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+\alpha})^{\mathsf{T}}$
-\item For $i=m+1,\dots, m+\alpha$:
-\subitem Set $\va_i \leftarrow \va^*_i$
-\subitem Set $b_i = b_i^*$.
-\item Output $D(\vA, \vb)$. 
-\end{enumerate}
-\end{framed}
-\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-
-The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
-\begin{claim}
-\label{cl:full rank matrix 5.2}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
-\end{claim}
-\begin{proof}
-Direct result of \clref{cl:full rank matrix} because $q^{-\beta} = \ngl(n)$.
-\end{proof}
-The probability that a random $\vS$ is not full rank is $\ngl(n)$ so the distinguisher $D$ must still have an advantage when the matrix $\vS$ is full rank.  That is,
-\[
-|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
-\]
-
-It suffices to show that $D'$ prepares a good instance for $D$ conditioned on $\vS$ being full rank. We show this in the following three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
-\item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
-\item If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then the conditional distribution $\vb\,|\,\vA$ is also uniform.
-\end{enumerate}
-
-\begin{claim}
-\label{cl:randomMatrixDist}
-The matrix $\vA$ is distributed as a uniformly random choice from the set of all matrices whose bottom-right $\alpha\times (\alpha+\beta)$ submatrix $\vS$ satisfies $\rank(\vS) = \alpha$.
-\end{claim}
-\begin{proof}
-The bottom $\alpha$ rows of $\vA$ (namely, $\vR|\vS$) are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
-The top left $m\times n$ quadrant of $\vA$ is also random, because it is produced as a sum of a uniformly random $\vA'$ with some values that are uncorrelated with $\vA'$.
-The submatrix of the top-right $m\times (\alpha+\beta)$ quadrant corresponding to $\vQ_{T^c}$~(recall this is the restriction of $\vQ$ to the columns not in $T$) is also random, because it is initialized with random values to which some uncorrelated values are then added.
-It is important to note that all these values are independent of $\gamma_i$ values.
-
-Thus, we restrict attention to the $m\times \alpha$ submatrix of $\vA$ that corresponds to $\vQ_T$ in $\vA^*$ (note that these values are $0$ in $\vA^*$).
-Consider a particular row $i$.
-That row is computed as $\gamma_i \vS_{T}$.
-Since $\vS_T$ is a full rank square matrix and $\gamma_i$ is uniformly and independently generated, that row is also uniform and independent of other entries in $\vA$.
-\end{proof}
-\begin{claim}
-\label{cl:random ax+e}
-If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$, where
-\begin{itemize}
-\item $e_i = e_i'$ for $1\leq i\leq m$,
-\item $e_i = 0$ for $m<i\leq m+\alpha$,
-\item $x_j = x_j'$ for $1\leq j \leq n$,
-\item and $x_j$ is uniform and independent of $\vA$ and $\ve'$ for $n<j\le n+\alpha+\beta$,
-\end{itemize}
-\end{claim}
-\begin{proof}
-Partially define $\vx$ as $x_j = x_j'$ if $1\leq j \leq n$ and $x_j$ as the value generated in step~\ref{step:fill in matrix} for $j>n $ and $j\not\in T$.
-Define the remaining variables $\vx_T$ as the solution to the following system of equations.
-\begin{eqnarray}
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  \label{eq:x t solution}
-\end{eqnarray}
-A solution $\vx_T$ exists as $\vS_T$ is full rank.
-Moreover, it is uniform and independent of $\vA$ and $\ve$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve$.
-
-We now show that $\vb^* = \vA^* \vx+\ve$.
-All entries in matrix $\vQ$ corresponding to variables in $T$ are set to zero.
-Thus, the values of $\vx^T$ do not affect $b_i^*$ for $1\le i \le m$.
-The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $b_i^*$.
-Thus, for $1 \leq i \le m$, we have $\vb^* = \vA^*\vx+\ve$.
-For $m< i$, this constraint is also satisfied by the values of $\vx_T$ set in Equation~\ref{eq:x t solution}.
-
-Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
-We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
-Recall the other rows are not modified.  We have the following for $1\leq i\leq m$:
-\begin{align*}
-\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
-&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
-\end{align*}
-Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
-\begin{align*}
-(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
-&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
-\\&=  \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
-\end{align*}
-This completes the proof of the claim.
-\end{proof}
-\begin{claim}\label{clm:random b}
-If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then $\vb\,|\,\vA$ is also uniform.
-\end{claim}
-\begin{proof}
-Since $\vR, \vS$, and $\vQ$ are chosen independently of $\vb'$, the distribution $\vb'\,|\,\vA^*$ is uniform.
-Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-Its first $m$ coordinates are  computed by adding the uniform vector $\vb'$ to values that are independent of $\vb^*$, and its remaining $\alpha$ coordinates $b^*_{m+1},\dots,b^*_{m+\alpha}$ are   chosen uniformly.
-Thus $\vb^*\,|\,\vA^*$ is uniform.
-
-Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
-It is independent of $\vb^*$ and $\vA^*$, so $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform.
-Let $\vgamma'=\left(\begin{array}{c | c}\vect{I_m} & \vgamma \\\hline \vect{0} & \vect{I_\alpha}\end{array}\right)$.
-Note that $\vb=\vgamma' \vb^*$.  Since $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform, and $\vgamma'$ is invertible, $\vb\,|\,(\vA^*, \vgamma)$ must also be uniform.
-Since $\vA$ is a deterministic function of $\vA^*$ and $\vgamma$ (assuming Step~\ref{step:find columns} is deterministic---if not, we can fix the coins used), the distribution $\vb\,|\,\vA$ is the same  as $\vb\,|\,(\vA^*, \vgamma)$ and is thus also uniform.
-\end{proof}
-
-Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $D'$ properly prepares the instance thus,
-\begin{align*}
-&\left|\Pr[D'(\vA, \vA X+\chi) = 1] - \Pr[D'(\vA, U) =1] \right|\\
-&\, = \left| \Pr\left[D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
-&\, =\left|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]  \right| \Pr[\rank(\vS) = \alpha] \\
-&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
-\end{align*}
-Where the second line follows because we can detect when $\rank(\vS)<\alpha$ and output a random bit in this case.
-Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
-\end{proof}
-\section{Additional Proofs}
-
-\subsection{Proof of \lemref{lem:averageToMaximalError}}
-\label{sec:proof of average to maximal error}
-\begin{proof}
-Let $C$ be the  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$ such that  $\Hoo(C)\geq k$.  Then for all $t'\le t$
-\[
-\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \neigh (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
-\]
-For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \neigh(c, t') \wedge \rec(c') \neq c]$.  
-Then by Markov's inequality:
-\[
-\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
-\]
-Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.
-Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.
-Since $H_\infty(C)\geq k$, we know $|C'|\geq 2^{k-1}$~(otherwise $\Pr_{c\leftarrow C}[c\in C']=\sum_{c\in C'}\Pr[C=c]$ would be less than $2^{k-1}\frac{1}{2^k} = 1/2$).
-This completes the proof of the~\lemref{lem:averageToMaximalError}.
-\end{proof}
-
-\subsection{Proof of \thref{thm:impSketchArbitraryW}}
-\label{sec:proof of thm sketch implies code}
-\begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
-\[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\le \epsilon\, ,
-\]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. 
-Define $D$ as:
-\begin{enumerate}
-\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{enumerate}
- By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.
-Let $X_y$ denote the random variable $X|Y=y$.
-By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.
-
-Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.
-Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).
-Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).
-Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \neigh(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
-Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.
-The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
-\end{proof}
-
-\subsection{Proof of \thref{thm:imp of unp entropy}}
-\label{sec:proof of imp unp entropy}
-Instead of proving the result just for Hamming metric over $\mathcal{Z}^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
-We now define this second condition:
-\begin{definition}
-A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
-\end{definition}
-
-\begin{theorem}
-Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
-Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least some fixed value $B_t(\cdot)$.
-Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
-\end{theorem}
-\begin{proof}
-Let $(X, Y)$ be two random variables such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq |\mathcal{M}| (1-\epsilon -t\delta) / |B_t(\cdot)|$.
-
-Let $B_t(x)$ denote the random variable representing a random neighbor of distance at most $t$ from $x$ (note that $B_t$ may not be efficiently samplable, because we are assuming only that a neighbor a fixed distance is efficiently samplable).
-We begin by showing that \rec must recover points of $X$.  
-\begin{claim}
-\label{clm:y is recoverable}
-\begin{align*}
-\Pr[\rec(B_t(X), Y) = X]&=\\
-\Pr[(x, y)\leftarrow (X, Y) \wedge x'\leftarrow B_t(x) \wedge \rec(x', y) = x] &\geq 1-\epsilon -t\delta.
-\end{align*}
-\end{claim}
-\begin{proof}
-Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.
-We construct the following distinguisher $D\in\mathcal{D}_{s_{sec}}$ (the distinguisher design is slightly complicated by the fact that we don't know at which particular distance $t'$ the recover procedure is most likely to fail, so we have to try all distances):
-\begin{itemize}
-\item Input $w\in \mathcal{M}, s\in\zo^*$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{itemize}
-First note that $|D| = t( |\rec|+ s_{neigh} )$.
-Since $(\sketch, \rec)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
-If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist at least one $1\leq t'\leq t$ for which $\Pr[\rec(\neigh(X, t'), Y) = X] < 1-\epsilon -t\delta$.
-Then
-\begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(X, Y)=1] &\geq\\
-(1-t\delta) - \Pr[\rec(\neigh(X, t'), Y) = X] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
-\end{align*}
-This is a contradiction and the statement of the claim follows.
-\end{proof}
-
-Now define $\mathcal{I}$ as follows:
-\begin{itemize}
-\item Input $y\in\zo^*$.
-\item Sample $x'\leftarrow \sample$.
-\item Output $\rec(x', y)$.
-\end{itemize}
-Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$. 
-We now show that $\mathcal{I}$ predicts $X$:
-\begin{align*}
-\Pr[\mathcal{I}(Y) = X] & = \\
-&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
-&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[\sample = x' ] \Pr[\rec(x', y) =x]\\
-&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x' \mathrm{ s. t. } \dis(x', x)\le t} \Pr[\sample = x']\Pr[\rec(x', y) =x]\\
-&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\mathrm{ s. t. } \dis(x', x)\le t} \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[B_t(x) = x'] \Pr[\rec(x', y) =x]\\
-&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
-\end{align*}
-(the last step follows by  \clref{clm:y is recoverable}).
-
-\thref{thm:imp of unp entropy} follows by noting that $\mathcal{Z}^n$ can be sampled in time $n\log |\mathcal{Z}|$ and neighborhood sampled in time $n\log |\mathcal{Z}|$.
-\end{proof}
-
-\subsection{Proof of \lemref{lem:i t poly time}}
-\label{sec:proof lem i t poly time}
-\begin{proof}
-Note that $\decode_t$ will stop if $w$ and $w'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
-\begin{align*}
-\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\left(\frac{m}{n}-2\right)\log n}{m-i}\right)\\
-&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
-&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}\,.
-\end{align*}
-(The second-to-last step holds as long as $n\ge 2d\log n$.) Because at each iteration, we select $2n$ rows independently at random, the expected number of iterations is at most $n^{4d}$; each iteration takes $O(n^3)$ operations in $\Fq$, which gives us the expected running time bound.
-
-The probability that $\decode_t$ outputs $\perp$ is bounded by 
-\begin{eqnarray*}
-\Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
-&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&= &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times}]\cdot \Pr[\rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot q^{-n}\\
-& = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
-\end{eqnarray*}
-The third line from the bottom follows from the fact that the locations of the errors are assumed to be independent of the sketch, and therefore independent of the matrix $\vA$.
-The second line from the bottom follows from \clref{cl:full rank matrix} when $\beta = n$; note that, because we use the union bound and evaluate the probability separately for each value of $j$,  we can treat $\vA_{i_1,\dots, i_{2n}}$ as a randomly chosen $2n\times n$ matrix, ignoring the fact that these matrices are correlated.
-
-We claim that if the code generated by $\vA$ 
-has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $\vx'=\vx$.
-Indeed, suppose $\vx'\neq \vx$.
-Since $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $w-w'$, such an $\vx'$ will not pass Step 6.
-
-The probability that the code generated by $\vA$ has distance lower than $2t+1$ is at most $e^{-\Omega(n)}$ (see \corref{cor:code high distance}), the probability of outputting $\perp$ is also $e^{-\Omega(n)}$~(computed above).
-This gives the correctness bound for $\decode_t$.
-\end{proof}
-
-\section{Parameter Settings for \consref{cons:informal construction}}
-\label{sec:parameter settings}
-In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure extractor log} we give a lossless fuzzy extractor from a security parameter $n$ and an error $t$.
-In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
-We begin by reviewing the parameters that make up our construction:
-
-\begin{itemize}
-\item $|W|$: The length of the source.  
-\item $t$: Number of errors that can be supported.  
-\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
-\item $q$: The size of the field.  
-\item $\rho$: The fraction of the field needed for error sampling.  
-\item $m$: The size of each number of samples in the LWE instance.  
-\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
-\end{itemize}
-We will split the source $|W|$ into $m$ blocks each of size $2\rho q+1$~(that is, $|W| = m\log (2\rho q+1)$).
-We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.
-As stated above we have three constraints:
-\begin{itemize}
-\item Maintain security of LWE.
-If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + \sigma} m = \poly(n)$.
-The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.
-We ignore this effect and assume that $\rho q = 2n^{1/2+\sigma}m$.
-\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
-\item Minimize entropy loss of the construction.
-We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.
-We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.
-Substituting, one has $m\log 2\rho q+1 = k \log q$.
-\end{itemize}
-Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
-\begin{align*}
-n_0&< n -k \\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+\sigma}m\\
-m\log (2\rho q +1)&= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
-\end{align*}
-This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma} m+1}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
-Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n -k \\
-m &= \frac{(c/d+2)n \log n}{\log n} = (\frac{c}{d}+2)n\\
-f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma}m+1}{\log n} = \frac{g(c+2d)}{d}\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
-\end{align*}
-Note that $f$ is at a constant in $n$.
-Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= (\frac{c}{d}+2)n\\
-q & = n^f = n^{\frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
-\end{align*}
-
-Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $d<c$~(this also ensures that $m\geq 3n$, as required for \lemref{lem:i t poly time} to hold).
-Since $\rho q = 2n^{1/2+\rho }m = O(n^{5/2})$ in our setting $\rho = O(n^{-1/2})$.
-Thus, for large enough settings of parameters $\rho$ is less than $1/10$ as required by \lemref{lem:uniform LWE decision}.
-
-Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.
-We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).
-The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.
-In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.
-Setting $1<g<2$ achieves an increase in output length~(over the input length of $W$).
-We also (arbitrarily) set $\sigma=1/2$ to simplify the statement of \thref{thm:lossless secure extractor log}, making $\rho q = 2(c/d+2) n^2$.
-
-\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
-\label{ssec:block params}
-We repeat parameter settings for block fixing sources.
-We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.
-We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
-\begin{align*}
-n_0&< n -k  -\alpha -\beta\\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+\sigma}m\\
-m\log (2\rho q+1)&= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k - \alpha -\beta\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
-\end{align*}
-As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k  - \alpha - \beta \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-%f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma} m+1)}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.
-Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n/3 -  \log n\\
-m &= \frac{(c/d+2)n \log n}{ \log n} = (\frac{c}{d}+2)n\\
-f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(3(\frac{c}{d}+2)\right)\frac{\log (4(\frac{c}{d}+2) n^{3/2+\sigma}+1)}{\log n} = O(1)
-\end{align*}
-
-Assuming $n/3-\log(n)> n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= (\frac{c}{d}+2)n\\
-q & = n^f = n^{\frac{m}{n}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
-\end{align*}
-
-As before we arbitrarily set $\sigma = 1/2$, giving $\rho q = 2(\frac{c}{d}+2)n^2$.
-Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
 \end{document}

### 2013-09-04 CompFuzzExt-asiacrypt.tex
Asiacrypt version

@@
 \documentclass{llncs}
-\def\shownotes{1}
+\def\shownotes{0}
 
@@
 
-%\newtheorem{theorem}{Theorem}[section]
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newtheorem{proposition}[theorem]{Proposition}
-%\newtheorem{corollary}[theorem]{Corollary}
-%\newtheorem{definition}[theorem]{Definition}
-%\newtheorem{assumption}[theorem]{Assumption}
-%\newtheorem{claim}[theorem]{Claim}
-%\newtheorem{problem}[theorem]{Problem}
 \newtheorem{construction}{Construction}
-%\spn@wtheorem{lemma}{Lemma}{\bfseries}{\itshape}
-
-\newcounter{ctr}
-\newcounter{savectr}
-\newcounter{ectr}
-%
-%\newenvironment{newitemize}{%
-%\begin{list}{\mbox{}\hspace{5pt}$\bullet$\hfill}{\labelwidth=15pt%
-%\labelsep=5pt \leftmargin=20pt \topsep=3pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{3pt} }}{\end{list}}
-%
-%
-%\newenvironment{newenum}{%
-%\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=17pt%
-%\labelsep=5pt \leftmargin=22pt \topsep=3pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{2pt} }}{\end{list}}
-%
-%\newenvironment{tiret}{%
-%\begin{list}{\hspace{2pt}\rule[0.5ex]{6pt}{1pt}\hfill}{\labelwidth=15pt%
-%\labelsep=3pt \leftmargin=22pt \topsep=3pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{2pt}}}{\end{list}}
-%
-%
-%\newenvironment{blocklist}{\begin{list}{}{\labelwidth=0pt%
-%\labelsep=0pt \leftmargin=0pt \topsep=10pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{20pt}}}{\end{list}}
-%
-%\newenvironment{blocklistindented}{\begin{list}{}{\labelwidth=0pt%
-%\labelsep=30pt \leftmargin=30pt\topsep=5pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{10pt}}}{\end{list}}
-%
-%\newenvironment{onelist}{%
-%\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=18pt%
-%\labelsep=7pt \leftmargin=25pt \topsep=2pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{2pt} }}{\end{list}}
-%
-%\newenvironment{twolist}{%
-%\begin{list}{{\rm (\arabic{ctr}.\arabic{ectr})}%
-%\hfill}{\usecounter{ectr} \labelwidth=26pt%
-%\labelsep=7pt \leftmargin=33pt \topsep=2pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{2pt} }}{\end{list}}
-%
-%\newenvironment{centerlist}{%
-%\begin{list}{\mbox{}}{\labelwidth=0pt%
-%\labelsep=0pt \leftmargin=0pt \topsep=10pt%
-%\setlength{\listparindent}{\saveparindent}%
-%\setlength{\parsep}{\saveparskip}%
-%\setlength{\itemsep}{10pt} }}{\end{list}}
-%
-%\newenvironment{newcenter}[1]{\begin{centerlist}\centering%
-%\item #1}{\end{centerlist}}
-%
-%\newenvironment{codecenter}[1]{\begin{small}\begin{centerlist}\centering%
-%\item #1}{\end{centerlist}\end{small}}
 
@@
 
-\title{\textbf{Computational Fuzzy Extractors}}
+\title{Computational Fuzzy Extractors}
 \author{Benjamin Fuller\inst{1} \and Xianrui Meng\inst{2} \and Leonid Reyzin\inst{2}}
@@
 
- Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
+ Regev~\cite{regev2005LWE} and Peikert~\cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
 Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.

### 2013-09-04 CompFuzzExt.tex
Asiacrypt version

@@
 
-\title{\textbf{Computational Fuzzy Extractors}}
+\title{Computational Fuzzy Extractors}
 \author{Benjamin Fuller 
@@
 Furthermore, this approach does not allow the use of private randomness; private randomness is a crucial ingredient in our construction.
-%We ask whether it is possible to avoid this loss by making whole process ``computational.''
 We compare the two approaches in \secref{sec:prg based comparison}.
 
-%Authentication generally requires secrets.
-Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
-Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
-%
-%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
-%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
-%It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
-%the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
-%Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.
-This feature is needed because $s$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
-%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.  
-%
-%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application.
-For example, in the application of secure sketches to fuzzy extractors (whose goal is to reliably produce a uniformly random secret key from a noisy input), the resulting secret key may be too short to be useful if the entropy loss is too high.
-However, because secure sketches are defined as information-theoretic objects, some entropy loss is inherent in any secure sketch construction, because $s$ contains enough information to recover $w$ from any value $w'$ that is close to it.
-%
-%The minimum necessary  entropy loss has been quantified in past work.
-Even if we don't require perfect correctness (i.e., allow $\rec$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
-%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
-%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
-%
-%\paragraph {Our Contributions}
-%To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
-%The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.
-%
-%On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful.
-We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-%%Furthermore, we have (asymptotic)~constructions that meet these bounds.
-%
-%On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction.
-The idea is to give up on reconstructing $w$ and, instead, to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.
-This string $\recout$ is  required to have high HILL entropy even conditioned on $s$.
-Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
-%
-%Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
-%~\ref{thm:lossless secure extractor log})).
-We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.
-%
-%We show that this relaxation of the security requirement is  useful.
-Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
-%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.
-The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
-%\lnote{it would be good to find another application} 
-%
-%Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.
-To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).
-We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-The LWE error vector, in our case, is the input $w$ itself.
-To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution.
-We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed).
-This relaxation requires new results about the hardness of LWE when samples have a fixed error vector, which may be of independent interest~(\thref{thm:blockLWE}).
 \section{Preliminaries}
@@
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
-%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
-%The {\em collision probability} of  $X$ is 
-%$\col(X) = \sum_{x} \Pr[X=x]^2$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
-%We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.
 For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
@@
 The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-%%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.
 If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
@@
 
-\paragraph{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.
+\textbf{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.
 In the information-theoretic setting this seemed inherent as the ``correct'' $R$ should be information-theoretically unknown conditioned on $P$.
@@
 Looking ahead, in our construction $R$ is information-theoretically determined conditioned on $P$~(with high probability over the coins of \gen).
-Our $\rep$ algorithm will never output an incorrect key but may run for an unbounded time~(with high probability over the coins of \gen).
+Our $\rep$ algorithm will never output an incorrect key~(with high probability over the coins of \gen) but may not terminate.
 However, it is not clear this is the desired behavior.
 For this reason, we leave the behavior of \rep ambiguous when $\dis(w, w')>t$.
-% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).
-
-%\bnote{There needs to be more linking language here.}
-%It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).
-In the next section, we show this paradigm is difficult to realize.
-
-%\textbf{Note: }A computational fuzzy extractor could also be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).
-We compare the two approaches in \secref{sec:prg based comparison} after presenting our construction.
-%, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).
-%The cause for the entropy loss in the secure sketch is the additional bits added for error correction.
-In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.
-%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.
-
-%=============================================================
+
 \section{Impossibility of Computational Secure Sketches}
@@
 \label{lem:shannon to sketch}
-For an alphabet $\mathcal{Z}$, let $\mathcal{C}$ over $\mathcal{Z}^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
-%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
-%
-% Define the following procedures
-%\lnote{I think this description is buggy}
-%\begin{center}
-%\begin{tabular}{c|c}
-%\begin{minipage}{3in}
-%\textbf{\sketch}
-%\begin{enumerate}
-%\item Input $w\leftarrow W$.
-%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
-%\item Sample $c\leftarrow \mathcal{C}$.
-%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
-%\item Output $p = x \oplus c, \pi$.
-%\end{enumerate}
-% \end{minipage} &
-%\begin{minipage}{3in}
-%\textbf{\rec}
-%\begin{enumerate}
-%\item Input $(w', p, \pi)$
-%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
-%\item Compute $c' = p \oplus x'$.
-%\item Compute $c = \rec'(c)$.
-%\item Output $p\oplus c$.
-%\\
-%\end{enumerate}
-%\end{minipage} 
-%\end{tabular}
-%\end{center}
+For an alphabet $\mathcal{Z}$, let $\mathcal{C}$ over $\mathcal{Z}^n$ be a $(t, \delta)$ Shannon code.
 Then there exists a $(\mathcal{Z}^n, m, m-(n\log|\mathcal{Z}|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$.
-%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
-%\begin{itemize}
-%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
-%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
-%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
-%\end{itemize}
 \end{lemma}
-%\begin{construction}
-%Let $\delta >0$ be a parameter.
-%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.
-Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.
-Thefn for $\beta = 2^{-\ell}
-%\end{construction}
 Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
@@
 $4(\epsilon+t\delta)$. 
-%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
 \end{corollary}
-\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
+\textbf{Note} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
 
 \corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |\mathcal{Z}|-\tilde{m})-2$ bits of entropy.
-
-%\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.
-Unfortunately, we have lower bounds for the entropy drop for information-theoretic sketches:
-
-%\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
-%\label{prop:lower bound entropy drop}
-%For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.
-Here $h(\cdot)$ is the binary entropy function.
-%\end{proposition}
-
-%Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.
-This entropy drop is tied to the Shannon capacity.
-Furthermore, we have information theoretic constructions that meet these bounds.
-Thus, defining a computational secure sketch using HILL entropy is unlikely to be useful.
-
-%\begin{theorem}
-%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable.
-Furthermore, let $(\sketch, \rec)$ be any $(s_{rec}, t)$-recover functionality for $\mathcal{M}, d$.
-Let $U$ be the uniform distribution over $\mathcal{M}$.
-If $s_{ball}, s_{rec}, s_{sam}$ are of polynomial size, then $H^\hill_{\epsilon, s}( U |\sketch(U))\not \geq \Hoo(U)$ for polynomial $s$ and noticeable $\epsilon$.
-%\end{theorem}
-%\emph{Intuition:  }We will show that a recover functionality cannot be both stable~(maps points to themselves) and correcting~(maps nearby points back to themselves).
-If a recovery functionality is correcting then we can check if the input point maps to itself.
-If a recovery functionality is stable then we can see if recovery succeeds with nearby points.
-%
-%\begin{proof}
-%Let $\mathcal{M}, d$ be a finite metric space that is $s_{sam}$ efficiently samplable and $s_{ball}, t$ neighborhood efficiently samplable~(by $\sample$).
-Let $(\sketch, \rec)$ be a $s_{rec}, t$-recover functionality for $\mathcal{M}, d$.
-Let $X, Y, U$ be i.i.d.
-and be the uniform distribution over $\mathcal{M}$.
-By assumption $s_{ball}, s_{sam}, s_{rec}$ be of polynomial size.
-It suffices to construct a polynomial size distinguisher $D$ such that $\expe[D(X, SS(X))]- \expe[D(Y, SS(X)]> \epsilon$ for noticeable $\epsilon$.
-Let $q$ be a polynomial.
-$D$ is defined as follows:
-%
-%\begin{enumerate}
-%\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*$.
-%\item Initialize $correct, stable = 0$.
-%\item For $i=1...q$:
-%\subitem $x_i \leftarrow U$, if $\rec(x_i, s) = x_i, stable +=1/q$.
-%\subitem $x_i' \leftarrow \sample (x_i)$, if $\rec(x_i', s) = x_i, correct+=1/q$.
-%\item If $\rec(z, s)\neq z$ output $0$.
-%\item If $stable<2/3$ output $1$
-%\item Else $z'\leftarrow \sample(z)$.
-%\subitem If $\rec(z', s) = z$ output $1$.
-%\subitem Else output $0$.
-%\end{enumerate}
-%
-%We begin by noting that $D$ is of size at most $q(s_{sam}+s_{ball}+2s_{rec})+2s_{rec}+s_{ball}$ and thus is polynomial assuming that $q, s_{sam}, s_{ball}, s_{rec}$ are of polynomial size.
-It remains to show that $D$ separates $X, SS(X)$ and $Y, SS(X)$ by a noticeable $\epsilon$.
-Let $STABLE = \Pr[\rec(U, \sketch(X)) = U]$.
-We begin by noting that $\Pr[|stable-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-That is, after step (3) $D$ has a good approximation
-%of $STABLE$.  Similarly, let $CORRECT = \Pr[\rec(\sample(U), \sketch(X)) = U]$.  As before $\Pr[|correct-STABLE|>\ngl]<\ngl(n)$ assuming enough queries~(\bnote{fill in this information}).
-%
-%\begin{claim}
-%$CORRECT+STABLE\leq 1$.
-%\end{claim}
-%\bnote{finish proof}
-%
-%\end{proof}
 
@@
 The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
-%\subsection{LWE with uniform errors}
-%\label{subsec:LWE uniform error}
 Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
@@
 In other words, in order to decode a meaningful number of errors, the vector $w$ is of higher dimension than the vector $X$, but each coordinate of $w$ is sampled using fewer bits than each coordinate of $X$.
-Thus, by increasing the size of $q$ we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
+Thus, by increasing the size of $q$~(while keeping $\rho q$ fixed) we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
 The formal statement is below.
-
-%\begin{theorem}
-%\label{thm:lossless secure sketch}
-%Let $n$ be a security parameter and let $t$ be a constant.
-Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.
-Let $W$ be uniform over $\zo^{n(t+1)b}$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors, there is a
-%\[
-%(\zo^{n(t+1)b}, |W|,|W|, \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-% for $\epsilon = \ngl(n), s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
-%\end{theorem}
 
@@
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
-% for following parameters:
-%\[
-%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
-%\] 
 \end{theorem}
@@
 Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.
-
-%However, the construction of a computational fuzzy extractor by 
-%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.
-In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.
-The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).
 
@@
 \thref{thm:blockLWE} allows us to construct a lossless computational fuzzy extractor from block-fixing sources:
-
-%\begin{theorem}
-%\label{thm:lossless block sketch}
-%Let $n$ be a security parameter and let $t$ be a constant.
-Consider the Hamming metric with block length $b = \log 2n^3(t+1)$.
-Let $W$ be an $\alpha$-symbol fixing source over $\zo^{((t+1)n+\alpha)b}$.
-There is a \lnote{instead of ``there is'' can we actually point to the to construction?}
-%\[
-%(\zo^{((t+1)n+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
-%\]
-% for $s = \poly(n), s_{sketch} = O(n^3\log n )$ and $s_{rec}= O(n^3 \log n)$.
-%\end{theorem}
 
@@
 We thank Jacob Alperin-Sheriff for pointing out the connection with the work of Brakerski et al.
-The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+
+This work is supported in part by National Science Foundation grants 0831281, 1012910, and 1012798.
+The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
 
-\bnote{Need grants for Leo and Xianrui}
 \bibliographystyle{alpha}
@@
 \end{proof}
-
-%\bnote{This is the proof for not relaxed unpredictability entropy}
-%\begin{proof}
-%Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.
-Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
-We begin by showing that $Y$ must correctly recover most of the time.
-%\begin{claim}
-%\label{clm:y is recoverable}
-%\begin{align*}
-%\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
-%\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
-%\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
-%\end{align*}
-%\end{claim}
-%\begin{proof}
-%Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
-%\begin{itemize}
-%\item Input $x\in \zo^b, s\in\zo^*$.
-%\item Sample $x'\leftarrow B_t(x)$.
-%\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
-%\end{itemize}
-%Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(B_t(W), \sketch(W) = W)  ]\geq 1-\delta$.
-The statement of the claim follows as
-%\begin{align*}
-%\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
-%\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
-%\end{align*}
-%\end{proof}
-%We now consider the experiment $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.
-\clref{clm:y is recoverable} says that
-%\[
-% \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
-%\]
-%We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.
-Thus, for all $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
-%We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
-%\begin{itemize}
-%\item Input $s\in\zo^*$.
-%\item Sample $x'\leftarrow \zo^b$.
-%\item Output $\rec(x', s)$.
-%\end{itemize}
-%We define by $X$ the random variable corresponding to the sample $x'$ performed by $\decode_t$.
-%We now show that $\mathcal{I}$ predicts $Y$:
-%\begin{align*}
-%2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
-%&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
-%&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{2^{-b}}{1/|B_t(\cdot)|} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
-%&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
-%\end{align*}
-%Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
-%\end{proof}
-
-%\subsection{Proof of \lemref{lem:i t constant time}}
-%\label{sec:proof lem i t constant time}
-%\begin{proof} We consider the expected number of iterations in step 2 when $t+1\leq m/n$.
-Steps 3 and 4 can be accomplished in time $n^3\log q +s_{ver}$.
-An iteration of $\decode_t$ succeeds when all selected rows of $\vA, \vect{C}$ have no error.
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.
-That is,
-%\begin{align*}
-%\Pr[i_1,..., i_n\text{ have no errors}]&\geq \prod_{i=0}^{n-1}\left(1 - \frac{t}{m-i}\right)\geq  \prod_{i=0}^{n-1}\left( 1-\frac{m-n}{n(m-i)}\right)\\
-%&\geq \prod_{i=0}^{n-1}\left( 1-\frac{1}{n}\right)\geq \left(1-\frac{1}{n}\right)^n \geq 1/4.
-%\end{align*}
-%Note in the last step we assume that $n\geq 2$.
-The minimum of $(1-1/n)^n$ is achieved at $n=2$ and it quickly converges to $1/e$.
-Thus, the expected number of iterations is at most $4$ giving the stated running time for $\decode_t$.
-%\end{proof}
 

### 2013-09-04 trunk/CompFuzzExt-asiacrypt.tex
Minor edits in both versions

--- 2013-09-04 CompFuzzExt-asiacrypt.tex
@@
 If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.
-Given the hardness of decoding random linear codes~\cite{berlekamp1978}, we do not expect significant improvement in error-tolerance of our construction.
+Given the hardness of decoding random linear codes~\cite{berlekamp1978}, we do not expect significant improvement in the error-tolerance of our construction.
 
@@
 
-We review definitions of Shannon codes~\cite{shannon1949mathematical}:
+We review the definition of a Shannon code~\cite{shannon1949mathematical}:
 \begin{definition}
@@
 We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
-To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
+To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
 \end{definition}
@@
 
-We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in full version~\cite{fullerMengReyzin2013}).
+We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in the full version of this work~\cite{fullerMengReyzin2013}).
 \begin{theorem}\label{thm:impSketchArbitraryW}
@@
 For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
-The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
+The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the symbols of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
 The formal statement of this result  can be expressed in the following Lemma (which is implicit in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}).
@@
 Let $\mathcal{Z}$ be an alphabet.
-Let $(\sketch, \rec)$ ben an unpredictability-entropy $(\mathcal{Z}^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$, if $s_{sec} \geq t(|\rec|+n\log |\mathcal{Z}|)$, then $\tilde{m}\leq n\log |\mathcal{Z}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
+Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{Z}^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$, if $s_{sec} \geq t(|\rec|+n\log |\mathcal{Z}|)$, then $\tilde{m}\leq n\log |\mathcal{Z}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
 \end{theorem}
@@
 The $\LWE$ problem was introduced by Regev \cite{regev2005LWE,regevLWEsurvey} as a generalization of ``learning parity with noise." For a complete description of the $\LWE$ problem and related lattices problems~(which we do not define here) see~\cite{regev2005LWE}.
-We now recall the definition of the decisional version of the problem.
+We now recall the decisional version of the problem.
 
@@
 \end{lemma}
-The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} if all parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.
+The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} when parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.
 
@@
 correcting $O(\log n)$ errors (note that this corresponds to a superpolynomial number of possible error patterns).
-This algorithm is only a proof of concept, and neither the algorithm nor its analysis have been optimized for constants.
+This algorithm is a proof of concept, and neither the algorithm nor its analysis have been optimized for constants.
 An improved decoding algorithm can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
@@
 Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}; efficiency follows by \lemref{lem:i t poly time}.
-For a detailed explanation of the various parameters and constraints see the full version of this work\cite{fullerMengReyzin2013}.
+For a detailed explanation of the various parameters and constraints see the full version of this work~\cite{fullerMengReyzin2013}.
 \end{proof}
@@
 \section*{Acknowledgements}
-The authors are grateful to Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
+The authors are grateful to Jacob Alperin-Sheriff, Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
 In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.
-We thank Jacob Alperin-Sheriff for pointing out the connection with the work of Brakerski et al.
 

### 2013-09-04 trunk/CompFuzzExt.tex
added grants for Leo and Xianrui
Minor edits in both versions

@@
 The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a complete description of the $\LWE$ problem and related lattices problems~(which we do not define here) see~\cite{regev2005LWE}.
-We now recall the definition of the decisional version of the problem.
+We now recall the decisional version of the problem.
 
@@
 \section*{Acknowledgements}
-The authors are grateful to Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
+The authors are grateful to Jacob Alperin-Sheriff, Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
 In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.
-We thank Jacob Alperin-Sheriff for pointing out the connection with the work of Brakerski et al.
-The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+
+This work is supported in part by National Science Foundation grants 0831281, 1012910, and 1012798.
+The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-\bnote{Need grants for Leo and Xianrui}
 

### 2013-12-10 Asiacrypt/CompFuzzExt.tex
Reorganized and adding constant rate work

--- 2013-09-04 trunk/CompFuzzExt.tex
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-For the Hamming metric over $\mathcal{Z}^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose t} (|\mathcal{Z}|-1)^i $.
+For the Hamming metric over $\mathcal{Z}^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.
-We present a simple $\decode_t$ that runs in polynomial time and can correct
-correcting $O(\log n)$ errors (note that this corresponds to a superpolynomial number of possible error patterns).
+We present a simple $\decode_t$ that runs in polynomial time and can correct $O(\log n)$ errors (note that this corresponds to a superpolynomial number of possible error patterns).
 This algorithm is a proof of concept, and neither the algorithm nor its analysis have been optimized for constants.

### 2013-12-10 trunk/constantRate/ConstCompFuzzExt.tex
Reorganized and adding constant rate work

--- 2013-12-10 Asiacrypt/CompFuzzExt.tex
@@
 \newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
-\newcommand{\xnote}[1]{{\authnote{Xianrui}{#1}}}
 
@@
 
-\title{Computational Fuzzy Extractors}
-\author{Benjamin Fuller 
-\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
-~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
-%\author{}
+\title{Constant Rate Computational Fuzzy Extractors}
+\author{Some people}
 \begin{document}
@@
 
-\begin{abstract} 
-Fuzzy extractors derive strong keys from noisy sources.  Their
-security is defined information-theoretically, which limits the length
-of the derived key, sometimes making it too short to be useful. We ask
-whether it is possible to obtain longer keys by considering
-computational security, and show the following.
-
-\begin{itemize}
-\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
-achieved using an information reconciliation component called a ``secure
-sketch.'' The security of this component, which directly affects the
-length of the resulting key, is subject to lower bounds from coding
-theory.  We show that, even when defined computationally, secure
-sketches are still subject to lower bounds from coding theory. Specifically, we consider
-two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy.
-For both cases we show  that computational secure sketches cannot outperform the best information-theoretic secure sketches in the case of high-entropy Hamming metric sources.
-
-\item\textbf{Positive Result:} We show that the negative result can be overcome by
-analyzing computational fuzzy extractors directly.  Namely, we show
-how to build a computational fuzzy extractor whose output key length
-equals the entropy of the source (this is impossible in the
-information-theoretic setting). Our construction is based on the
-hardness of the Learning with Errors (LWE) problem, and is secure when
-the noisy source is uniform or symbol-fixing (that is, each dimension
-is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
-that the decision version of LWE is secure even when a small number of
-dimensions has no error.
-\end{itemize}
-\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, error-correcting codes, computational entropy, randomness extractors.
-\end{abstract}
+%\begin{abstract} 
+%We make computational fuzzy extractors better.
+%\end{abstract}
 
 \section{Introduction}\label{sec:introduction}
+Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} derive stable keys from noisy data.
+They are composed of two algorithms: \gen takes a source value $w_0$, and produces a key $r$ and a public value $p$, and \rep which takes a nearby value $w_1$ and $p$ producing the original key $r$.
+Intuitively, they are two functions: error correction~(to provide the same value with \emph{noisy} readings) and key derivation~(to transform an entropic source into a uniform key).
+Traditionally, these two functions were performed by two separate primitives: a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} and a randomness extractor~\cite{nisan1993randomness}.
 
-Authentication generally requires a secret drawn from some high-entropy source.
-One of the primary building blocks for authentication is reliable key derivation.
-Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
+For a fixed length key, there are two main parameters: the desired error tolerance and the required entropy of the source.
+In the information-theoretic setting these two parameter are at odds.
+Any increase error-tolerance requires a similar increase to the entropy of the source.
+However, this does not need to be the case in the computational setting.
+The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The main difference isa computational fuzzy extractor outputs a pseudorandom key instead of a truly random key.
+Both definitions appear in \secref{sec:preliminaries}.}  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.
+We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.
+\footnote{Security is impossible if all points of the source distribution are close together.
+In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within the error-tolerance.
+This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}
 
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).
-The setting
-consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).
-The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.
-This information allows
-the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
-Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.
-This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
-
-Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.
-The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.
-In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
-A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
-Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.
-
-We ask whether it is possible to obtain longer keys by considering
-computational, rather than information theoretic, security.
-
-\paragraph {Our Negative Results}
-We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called a \emph{secure sketch}.
-A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
-The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.
-This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors produce random strings from strings with conditional min-entropy.
-We call this the \emph{sketch-and-extract} construction.
-
-The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.
-Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-
-Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
-This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
-Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
-For high-entropy sources of $w$ over the Hamming metric, this bound matches the best information-theoretic security sketches.
-
-\paragraph {Our Positive Results}
-
-Both of the above negative results arise because a secure sketch functions like a decoder of an error-correcting code.
-To avoid them, we give up on building computational secure sketches and focus directly on the entropy loss in fuzzy extractors.
-Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.
-
-By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$.
-Our construction is for the Hamming metric and uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.
-First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$ (this idea is similar to the way the code-offset construction is presented in
-\cite{JW99} as  a ``fuzzy commitment'').
-Our construction uses private randomness, which is allowed in the fuzzy extractor setting but not in noiseless randomness extraction.
-Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.
-
-Specifically,  we use the  recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012}, which shows the hardness of decoding random linear codes when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-This allows us to use $w$ as the error vector, assuming it is uniform.
-We also use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009},  which says that LWE has many hardcore bits, to hide $r$.
-
-Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.
-Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor.
-If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.
-Given the hardness of decoding random linear codes~\cite{berlekamp1978}, we do not expect significant improvement in the error-tolerance of our construction.
-
-In \secref{sec:LWE block fixing sources}, we are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
-This relaxation follows from our results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
-
-\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.
-They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.
-One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.
-However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
-Furthermore, this approach does not allow the use of private randomness; private randomness is a crucial ingredient in our construction.
-We compare the two approaches in \secref{sec:prg based comparison}.
+Our construction is based on obfuscation.
+While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we only use the obfuscation of point functions.
+This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
+Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).
+Dodis and Smith constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.
+Unfortunately, our construction is not a noisy point obfuscation and leaks partial information about particular blocks of the source.
 
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-For the Hamming metric over $\mathcal{Z}^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
+We primarily consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
+For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 
-\textbf{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.
-In the information-theoretic setting this seemed inherent as the ``correct'' $R$ should be information-theoretically unknown conditioned on $P$.
-However, in the computationally setting this is not true.
-Looking ahead, in our construction $R$ is information-theoretically determined conditioned on $P$~(with high probability over the coins of \gen).
-Our $\rep$ algorithm will never output an incorrect key~(with high probability over the coins of \gen) but may not terminate.
-However, it is not clear this is the desired behavior.
-For this reason, we leave the behavior of \rep ambiguous when $\dis(w, w')>t$.
+\subsection{Obfuscation}
+The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
+This notion is known to be impossible in a black-box way for all polynomial time programs.
+Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
+Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
 
-\section{Impossibility of Computational Secure Sketches}
-\label{sec:impossCompSecSketch}
-In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.
-We consider two different notions for computational entropy, and for both of them show that corresponding secure sketches are subject to the same upper bounds as those for information-theoretic secure sketches.
-Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help.
+We present the notion of virtual black-box obfuscation with the weakening that the simulator produces an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
 
-In particular, for the case of the Hamming metric and inputs that have full entropy, our results are as follows.
-In  \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-Dodis et al.
-\cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  construct sketches with essentially the same information-theoretic security\footnote{The security in  \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  is expressed in terms of entropy of the error rate; recall that $\log B_t(\cdot)\approx H_q(t/n)$, where $n$ is the number of symbols, $q$ is the alphabet size, and $H_q$ is the $q$-ary entropy function.} .
-In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
+\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  Let $\mathcal{C}$ be a family of polynomial-size circuits.
+A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
+\begin{enumerate}
+\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
+\[
+\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
+\]
+where the probability is taken over the randomness $r$.
+\emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability ver the random coin tosses $r$.
+Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
+\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
+\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
+and for all binary predicates $\pi$, 
+\[
+|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
+\]
+where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
+Furthermore, the.runtime of $A$ and $S$ must be polynomial in the length of their first input.
+\end{enumerate}
+\end{definition}
 
-\subsection{Bounds on Secure Sketches using HILL entropy}
-\label{sec:imp HILL sketch}
-HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
-It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
-Here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}); since we show impossibility even for this weaker definition, impossibility for the stronger definition follows immediately.
+In this work, we will use obfuscation of point-programs, 
+\[
+I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
+\]
+
+We provide the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
+\begin{enumerate}  
+\item Input: string $w\in \zo^n$.
+\item Choose a generator $g\overset{\$}\leftarrow G$
+\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
+\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
+\end{enumerate}
+\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
+Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
+Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
+For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\angle$ are computationally indistinguishable.
+\end{assumption}
+\begin{theorem}~\cite{canetti1997towards}
+The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
+\end{theorem}
+
+As described above there exist other constructions of point function obfuscates under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
+
+Lastly, we will need the notion of composable obfuscation.
+
+\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}].
+A PPT algorithm $\mathcal{O}$ is a $t$-\emph{com posable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
+That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
+\[
+|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
+\]
+where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
+\end{definition}
+
+\section{Supported Sources}
+We now describe a set of high entropy sources appropriate for our construction.
+After giving the description of the distribution, we give examples of distributions that fit in this class and provide additional characterizations.
 
 \begin{definition}
-\label{def:relaxed hill}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon$.
+Let $\mathcal{O}_{w_1,..., w_k}$ be an oracle that return $\mathcal{O}_{w_1,..., w_k}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
+A source $W = W_1||...|W_k$ is a $(q, \alpha, \ell)$-\emph{guessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $S$ of size at least $\ell$ such that
+\[
+\forall i\in S, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.
+However, we can show necessary and sufficient types of sources for a guessable block distribution.
+We begin by defining the entropy jump of a block source which will appear in our characterization.
+
+\begin{definition}
+Let $W = W_1,..., W_k$ be a source under ordering $i_1,..., i_k$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
 \end{definition}
 
-Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.
-Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the sketch-and-extract construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
-We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
-
-Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches).
-For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
-In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.
-
-The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
-In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $X, Y$ such that $\Hav(X | Y)\geq \tilde{m}$ and $(X, Y)$ is computationally indistinguishable from $(W, \sketch(W))$.
-Sample a sketch $s\leftarrow \sketch(W)$.
-We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).
-%So, by indistinguishability, it must also succeed on $Y$.
- Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability, $\rec (x',y) = x$ with high probability.
- This means we can construct a large set $\mathcal{C}$ from the support of $X|y$.
-$\mathcal{C}$ will be an error correcting code and $\rec$ an efficient decoder.
-We can then use standard arguments to turn this code into an information theoretic sketch.
-
-To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
-\begin{definition}
-\label{def:neighborhood samplable}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.
-\end{definition}
-
-We review the definition of a Shannon code~\cite{shannon1949mathematical}:
-\begin{definition}
-\label{def:shannon-code}
-Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
-To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
-\end{definition}
-This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
-For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
-However, we work with an arbitrary recover functionality that is not necessarily monotone.}.
-Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.
-
- \begin{definition}
-Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
-\end{definition}
-An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
-See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.
-An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
-We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
-\begin{lemma}
-\label{lem:averageToMaximalError}
-Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
-There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
-\end{lemma}
-
-We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
-\begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
-If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
-\end{theorem}
-
-For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
-The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the symbols of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
-The formal statement of this result  can be expressed in the following Lemma (which is implicit in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}).
-\begin{lemma}
-\label{lem:shannon to sketch}
-For an alphabet $\mathcal{Z}$, let $\mathcal{C}$ over $\mathcal{Z}^n$ be a $(t, \delta)$ Shannon code.
-Then there exists a $(\mathcal{Z}^n, m, m-(n\log|\mathcal{Z}|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$.
-\end{lemma}
-Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
-\begin{corollary}
-\label{cor:rec yields sketch}
-Let $\mathcal{Z}$ be an alphabet.
-Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-$4(\epsilon+t\delta)$. 
-\end{corollary}
-\textbf{Note} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
-
-\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |\mathcal{Z}|-\tilde{m})-2$ bits of entropy.
-
-\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
-\label{sec:imp unp sketch}
-In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
-However, HILL entropy is a strong notion.
-In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.
-We begin by recalling the definition of conditional unpredictability entropy~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}, which captures the notion of ``hard to guess'' (we relax the definition slightly, similarly to the relaxation of HILL entropy described in the previous section).
-
-\begin{definition}
-\label{def:unp entropy}
-Let  $(W, S)$ be a pair of random variables.
-We say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
-\[
-\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
-.\]
-\end{definition}
-
-We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a \emph{reconstructive} extractor~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
-
-Unfortunately, the conditional unpredictability entropy $\tilde{m}$ must decrease as $t$ increases, as the following theorem states.
-(The proof of the theorem, generalized to more metric spaces, is in \secref{sec:proof of imp unp entropy}.)
-
-\begin{theorem}
-\label{thm:imp of unp entropy}
-Let $\mathcal{Z}$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{Z}^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq t(|\rec|+n\log |\mathcal{Z}|)$, then $\tilde{m}\leq n\log |\mathcal{Z}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
-\end{theorem}
-In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.
-As mentioned at the beginning of~\secref{sec:impossCompSecSketch}, essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the randomized code-offset construction.
-However, it is conceivable that unpredictability entropy secure sketches could achieve lower entropy loss with greater efficiency for some parameter settings.
-
-\subsection{Avoiding sketch entropy upper bounds}
-\label{ssec:avoiding bounds}
-
-The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  
-This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed, and thus there is no (computational)~entropy loss.  
-This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .
-
-Both of lower bounds arise because \rec must function as an error-correcting code for many points of any indistinguishable distribution.
-It may be possible to avoid these bounds if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
-This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.
-Such an algorithm is called a computational fuzzy conductor.
-See~\cite{KanukurthiR09} for the definition of a fuzzy conductor.
-To the best of our knowledge, a computational fuzzy conductor has not been defined in the literature, the natural definition is to replace the pseudorandomness condition in \defref{def:comp fuzzy extractor} with a HILL entropy requirement.
-
-Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).
-It may be possible to achieve significantly better parameters with a construction that is a computational fuzzy conductor~(but not a computational fuzzy extractor) and then applying an extractor.
-We leave this as an open problem.
-
-\section{Computational Fuzzy Extractor based on \class{LWE}}
-\label{sec:fuzzyCompExt}
-
-In this section we describe our main construction.
-Security of our construction depends on the source $W$.
-We first consider  a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.
-Our construction uses the code-offset construction~\cite{JW99}, \cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).
-
-\begin{construction}
-Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. 
-Define $\gen, \rep$ as follows:
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
-\item Sample $\vA\in\Fq^{m\times n}, \vx\in\Fq^n$ uniformly.
-\item Compute $p = (\vA, \vA \vx+w)$, \\\ $r = \vx_{1,...,n/2}$.
-\item Output $(r, p)$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
-\item Parse $p$ as $(\vA, \vect{c})$; let $\vb=\vect{c}-w'$.
-\item Let $x = \decode_t(\vA, \vb)$\\
-\item Output $r = x_{1,...,n/2}$.
-\end{enumerate}
-\end{minipage} 
-\end{tabular}
-\end{center}
-\label{cons:informal construction}
-\end{construction}
-
-Intuitively, security comes from the computational hardness of decoding random linear codes with a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.
-Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.
-
-The rest of this section is devoted to making these intuitive statements precise.
- We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
-We describe one possible polynomial-time $\decode_t$ (which corrects more errors than is possible by exhaustive search) in \secref{sec:time main construction}.
-In \secref{sec:lossless extractor}, we describe parameter settings that allow us to extract as many bits as the input entropy, resulting in a lossless construction.
-In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a sketch-and-extract approach (\lemref{lem:fuzzy ext construction}) instantiated with a computational extractor.
-
-\subsection{Security of \consref{cons:informal construction}}
-\label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a complete description of the $\LWE$ problem and related lattices problems~(which we do not define here) see~\cite{regev2005LWE}.
-We now recall the decisional version of the problem.
-
-\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
-Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime\footnote{%
-Unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding.}.
-%
-Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $X$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
- The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
-$(\vA, \vA X+\chi)$ from
- the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
-
-We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If for any $s_{sec} = \poly(n)$, there exists   $\epsilon  = \ngl(n)$ such that  $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure, then we say  it is \emph{secure}.
-\end{definition}
-
- Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
-Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
-If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.
-(A recent result of Brakerski et al.~\cite{brakerski2013classical} shows security of $\LWE$ based on hardness of approximating lattices problems for classical algorithms.
-We have not considered how this result can be integrated into our analysis.)
-
-The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
-Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
-The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
-This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.
-The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
-\begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
-\label{lem:uniform LWE decision}
-Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer with $m\ge 3n$.
-Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$.
-If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]^m$,  $\distLWE_{n, m, q, \chi}$ is secure.
-\end{lemma}
-
-To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has simultaneously many hardcore bits.
-The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
-We state their result for a general error distribution~(noting that their proof does not depend on the error distribution):
-\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-\label{lem:many hardcore bits}
- If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure, then
-\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,\dots, k}, \vA, \vA X+\chi) , (U, \vA, \vA X+\chi)) \le \epsilon\,,\]
-where $U$ denotes the uniform distribution over $\Fq^k$,  $\vA$ denotes the uniform distribution over $\Fq^{m\times n}$, $X$ denotes the uniform distribution over $\Fq^n$, $X_{1,\dots, k}$ denote the first $k$ coordinates of $x$, and $s_{sec}' \approx s_{sec} - n^3$.
-\end{lemma}
-The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} when parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.
-
-\subsection{Efficiency of \consref{cons:informal construction}}
-\label{sec:time main construction}
-\consref{cons:informal construction} is useful only if $\decode_t$ can be efficiently implemented.
-We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.
-We present a simple $\decode_t$ that runs in polynomial time and can correct $O(\log n)$ errors (note that this corresponds to a superpolynomial number of possible error patterns).
-This algorithm is a proof of concept, and neither the algorithm nor its analysis have been optimized for constants.
-An improved decoding algorithm can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
-
-\begin{construction}
-\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
-\begin{enumerate}
-\item Input $\vA , \vb = \vA \vx + w - w'$
-\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, \vb$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vb_{i_1,...,i_{2n}}$.
-\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
-If no such rows exist, output $\perp$ and stop.
-\item Denote by $\vA', \vb'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vb_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $\vx' = (\vA')^{-1}\vb'$.  
-\item If $\vb- \vA \vx'$ has more than $t$ nonzero coordinates, go to step (2).
-\item Output $\vx'$.
-\end{enumerate}
-\end{construction}
-
-Each step is computable in time $O(n^3)$. 
-For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $w$ and $w'$ agree on those rows).
-If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $\vx'=\vx$, and the algorithm terminates.
-However, we also need to ensure correctness: we need to make sure that if $\vx'\neq \vx$, we detect it in step 6.
-This detection will happen if $\vb-\vA \vx' = \vA (\vx-\vx')+(w-w')$ has more than $t$ nonzero coordinates.
-It suffices to ensure that $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $w-w'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
-
-Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.
-Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
-The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
-\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
-\label{lem:i t poly time}
-Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this expectation is over the choice of random coins of $\decode_t$, regardless of the input, as long as $\dis(w, w')\le t$).
-It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
-\end{lemma}
-
-\subsection{Lossless Computational Fuzzy Extractor}
-\label{sec:lossless extractor}
-We now state a setting of parameters that yields a lossless construction.
-The intuition is as follows.
-We are splitting our source into $m$ blocks each of size $\log \rho q$~(from \lemref{lem:uniform LWE decision}) for a total input entropy of $m\log \rho q$.
-Our key is derived from hardcore bits of $X$: $X_{1,\dots, k}$ and is of size $k \log q$~(from \lemref{lem:many hardcore bits}).
-Thus, to achieve a lossless construction we need $k \log q = m\log \rho q$.
-In other words, in order to decode a meaningful number of errors, the vector $w$ is of higher dimension than the vector $X$, but each coordinate of $w$ is sampled using fewer bits than each coordinate of $X$.
-Thus, by increasing the size of $q$~(while keeping $\rho q$ fixed) we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
-The formal statement is below.
-
-\begin{theorem}
-\label{thm:lossless secure extractor log}
-Let $n$ be a security parameter and let the number of errors $t = c\log n$ for some positive constant $c$.
-Let $d$ be a positive constant (giving us a tradeoff between running time of $\rep$ and $|w|$).
-Consider the Hamming metric over the alphabet $\mathcal{Z}=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
-Let $W$ be uniform over $\mathcal{M}=\mathcal{Z}^m$, where $m={(c/d+2)n}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |\mathcal{Z}|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
-\end{theorem}
+\begin{claim}
+Let $W$ be a $(q, \alpha, \ell)$-guessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
+\end{claim}
 \begin{proof}
-Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}; efficiency follows by \lemref{lem:i t poly time}.
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
+Suppose not, for convenience assume the ordering that violates this condition is $1,..., k$.
+We describe a distribution $W$ where $\forall 1\leq j\leq k-\ell$, $J(j)\leq \log q +\alpha$.
+Define $W$ as follows $W_1 = c_1,...., W_{j-1} = c_{j-1}$ are constants.
 \end{proof}
-
-\thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.
-We can essentially think of $\vA X+W$ as an encryption of $X$ that where decryption works from any close $W'$.
-
-\subsection{Comparison with computational-extractor-based constructions}
-\label{sec:prg based comparison}
-As mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
-We will call this approach \emph{sketch-and-comp-extract}.
-(A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; note that LWE-based pseudorandom generators exist~\cite{applebaum2006pseudorandom}.)
-
-This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.
-However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
-
-In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor.
-Instead, we require that $w$ is not computationally recoverable  given $p$.
-This requirement is weaker---in particular, in our construction, $w$ may have no information-theoretic entropy conditioned on $p$.
-The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$.
-Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.
-
-The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.
-In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes, because decoding algorithms will not reach the information-theoretic decoding radius.
-
-Unfortunately, LWE parameter sizes require relatively long $w$.
-Therefore, in practice, sketch-then-comp-extract will beat our construction  if the computational extractor is instantiated efficiently based on assumptions other than LWE (for example, a cryptographic hash function for an extractor and a block cipher for a PRG).
-However, we believe that our conceptual framework can lead to better constructions.
-Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.
-
-To summarize, the advantage of \consref{cons:informal construction} is that the security of our construction does not depend on the decoding radius $t$.  
-The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.
-We begin to address this second problem in the next section.
-
-\section{Computational Fuzzy Extractor for Nonuniform Sources}
-\label{sec:LWE block fixing sources}
-While showing the security of~\consref{cons:informal construction} for arbitrary high-min-entropy distributions is an open problem, in this section we show it for a particular class of distributions called symbol-fixing.
-First we recall the notion of a symbol fixing source~(from~\cite[Definition 2.3]{KZ07}):
-\begin{definition}
-Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $\mathcal{Z}$.  We say that it is a $(m+
-\alpha, m, |\mathcal{Z}|) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
-Note that $H_\infty(W)=m\log |\mathcal{Z}|$.
-\end{definition}
-
-Symbol-fixing sources are a very structured class of distributions.
-However, extending \consref{cons:informal construction} to such a class is not obvious.
-Although symbol-fixing sources are deterministically extractible~\cite{KZ07}, we cannot first run a deterministic extractor before using \consref{cons:informal construction}.
-This is because we need to preserve distance between $w$ and $w'$ and an extractor must not preserve distance between input points.
-We present an alternative approach, showing security of $\LWE$ directly with symbol-fixing sources.
-
-The following theorem states the main technical result of this section, which is of potential interest outside our specific setting.
-The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$ (but for $n$ and $m$ reduced by the amount of fixed symbols).
-\begin{theorem}
-\label{thm:blockLWE}
-Let $n$ be a security parameter, $m, \alpha$ be polynomial in $n$, and $q=\poly(n)$ be a prime and $\beta\in\mathbb{Z^+}$ be such that $q^{-\beta} = \ngl(n)$. 
-Let $U$ denote the uniform distribution over $\mathcal{Z}^m$ for an alphabet $\mathcal{Z}\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |\mathcal{Z}|)$ symbol fixing source over $\mathcal{Z}^{m+\alpha}$.
-If $\distLWE_{n, m,q, U}$ is secure, then $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ is also secure.
-\end{theorem}
-
-\thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.
-Let $\chi'$ be an arbitrary error distribution.
-Define $\chi$ as the distribution where $m$ dimensions are sampled according to $\chi'$ and the remaining dimensions have some fixed error.
-Then, security of $\distLWE_{n, m, q, \chi'}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi}$.
-We show this stronger version of the theorem in \apref{sec:proof of block theorem}.
-
-The intuition for this result is as follows.
-Providing a single sample with no error ``fixes'' at most a single variable.
-Thus, if there are significantly more variables than samples with no error,  search $\LWE$ should still be hard.
-We are able to show a stronger result that $\distLWE$ is still hard.
-The nontrivial part of the reduction is using the additional $\alpha+ \beta$ variables  to ``explain'' a random value for the last $\alpha$ samples, without knowing the other variables.
-The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
-A similar theorem for the case of a single fixed dimension was shown in concurrent work by Brakerski et al.~\cite[Lemma 4.3]{brakerski2013classical}.
-The proof techniques of Brakerski et al.
-can be extended to our setting with multiple fixed dimensions, improving the parameters of \thref{thm:blockLWE}~(specifically, removing the need for $\beta$).
-
-\thref{thm:blockLWE} allows us to construct a lossless computational fuzzy extractor from block-fixing sources:
-
-\begin{theorem}
-\label{thm:lossless block sketch log}
-Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d\le c$ be a positive constant and consider the Hamming metric over the alphabet $\mathcal{Z}=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
-Let $\mathcal{M} = \mathcal{Z}^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
-Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |\mathcal{Z}|)$-symbol fixing sources.  If GAPSVP and SIVP are hard to approximate within polynomial factors 
-using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
- there exists $\epsilon = \ngl(n)$ 
-such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, m\log |\mathcal{Z}|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
- The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
-\end{theorem}
-
-\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .  
-Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see \secref{ssec:block params}. 
-\end{proof}
-
-\section*{Acknowledgements}
-The authors are grateful to Jacob Alperin-Sheriff, Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
-In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.
-
-This work is supported in part by National Science Foundation grants 0831281, 1012910, and 1012798.
-The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-
 \bibliographystyle{alpha}
 \bibliography{crypto}
-\appendix
-\section{Properties of Random Linear Codes}
-For efficient decoding of \consref{cons:informal construction}, we need the $\LWE$ instance to have high distance with overwhelming probability.
-We will use the $q$-ary entropy function, denoted $H_q(x)$ and defined as $H_q(x) = x\log _q(q-1) - x\log_q x - (1-x)\log_q (1-x)$.
-Note that $H_2(x) = -x\log x - (1-x)\log (1-x)$.
-In the region $[0, \frac{1}{2}]$ for any value $q'\geq q$, $H_{q'}(x)\leq H_{q}(x)$.
-The following theorem is standard in coding theory:
 
-\begin{theorem}~\cite[Theorem 8]{venkatLecture}
-\label{thm:random code good distance}
-For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .
-If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
-\end{theorem}
-Our setting is the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
-\begin{corollary}
-\label{cor:code high distance}
-Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
-Let $q$ be a prime and $\tau = O(\frac{m}{n}\log n )$.
-For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $\tau$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
-\end{corollary}
-\begin{proof}
-Let $c$ be some constant.
-Let $\delta = \tau/m = \frac{c\log n}{n}$.
-We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).
-It suffices to show that for sufficiently large $n$, there exists $\epsilon>0$ where $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.
-For sufficiently large $n$:
-\begin{itemize}
-\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
-\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
-\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.
-\end{proof}
-
-We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
-\begin{claim}
-\label{cl:full rank matrix}
-Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
-let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha] >  1- q^{-\beta}$.
-\end{claim}
-\begin{proof}
-Let $p_i$ be the probability that the $i$th
-row is linearly dependent on the previous $i-1$ rows. 
-By the union bound, the probability that $\alpha$ rows are linearly dependent is bounded by 
-$\sum_{i=1}^\alpha p_i$.
-Since $i-1$ rows can span a space of size at most $q^{i-1}$, the probability $p_i$ that a randomly chosen $i$th row is in that space is at most $q^{i-1}/q^{\alpha+\beta}$. So
-\begin{align*}
-\Pr[\rank(\vS) < \alpha] &=\sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-= \frac{q^{\alpha}-1}{q-1}\frac{1}{q^{\alpha+\beta} }< q^{-\beta}.
-\end{align*}
-\end{proof}
-
-\section{Proof of Theorem \ref{thm:blockLWE}}
-\label{sec:proof of block theorem}
-
-\begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same.
- In the reduction, the distinguisher is allowed to depend on the source and can know the positions of the fixed blocks and their values.
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
-For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.
-Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.
-We use similar notation for the complement of $T$, denoted $T^c$.
-For a matrix or vector we use $\mathsf{T}$ to denote the transpose.
-We use $i$ as a index into matrix rows and the error vector and $j$ as an  index into columns and the solution vector.
-
-Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.
-Let $\beta$ be such that $q^{-\beta} = \ngl(n)$.
-All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
-Let $\chi'$ be some error distribution over $\Fq^m$ and let $\chi$ over $\Fq^{m+n}$ be defined by sampling $\chi'$ to obtain values on dimensions $1,..., m$ and then appending $\alpha$ 0s.
-
-Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi}$ with advantage $\epsilon>1/\poly(n)$.
-Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ .
-Then
-\[
-|\Pr[D(\vA, \vA X+\chi) = 1] - \Pr[D(\vA, U )=1]|> \epsilon.
-\]
-
-We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
-Let $\vA'$ denote the uniform distribution over $\Fq^{m\times n}$, $X'$ denote the uniform distribution over $\Fq^n$, and $U'$ denote the uniform distribution over $\Fq^{m}$ .
-We will build a distinguisher $D'$ of polynomial size for which
-\begin{align}
-\label{eq:block LWE dist}
-|\Pr[D'(\vA', \vA'X'+\chi') = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
-\end{align}
-$D'$  will make a single call to $D$, so we focus on how to prepare a random block-fixing instance for $D$ from the random instance that $D'$ is given.
-The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
-
-\begin{figure}[p]
-\begin{framed}
-\begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi'$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
-\item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, for uniformly chosen $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
-\item Choose $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ uniformly at random.
-		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
-\item For all $1\le j \le \alpha+\beta$, $j\notin T$:
-\label{step:fill in matrix}
-\subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
-\subitem For $i=1,..., m$:
-\subsubitem Choose $\vQ_{i,j}\overset{\$}\leftarrow \Fq$ uniformly at random.
-\subsubitem Set $b_i^* = b_i^* + \vQ_{i,j} x_{n+j}$.
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
-\item \label{step:randomization}
-For {$i=1,..., m$}:
-\subitem Choose a row vector $\gamma_i \leftarrow \Fq^{1 \times \alpha}$ uniformly at random.
-\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
-\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+\alpha})^{\mathsf{T}}$
-\item For $i=m+1,\dots, m+\alpha$:
-\subitem Set $\va_i \leftarrow \va^*_i$
-\subitem Set $b_i = b_i^*$.
-\item Output $D(\vA, \vb)$. 
-\end{enumerate}
-\end{framed}
-\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-
-The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
-\begin{claim}
-\label{cl:full rank matrix 5.2}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
-\end{claim}
-\begin{proof}
-Direct result of \clref{cl:full rank matrix} because $q^{-\beta} = \ngl(n)$.
-\end{proof}
-The probability that a random $\vS$ is not full rank is $\ngl(n)$ so the distinguisher $D$ must still have an advantage when the matrix $\vS$ is full rank.  That is,
-\[
-|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
-\]
-
-It suffices to show that $D'$ prepares a good instance for $D$ conditioned on $\vS$ being full rank. We show this in the following three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
-\item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
-\item If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then the conditional distribution $\vb\,|\,\vA$ is also uniform.
-\end{enumerate}
-
-\begin{claim}
-\label{cl:randomMatrixDist}
-The matrix $\vA$ is distributed as a uniformly random choice from the set of all matrices whose bottom-right $\alpha\times (\alpha+\beta)$ submatrix $\vS$ satisfies $\rank(\vS) = \alpha$.
-\end{claim}
-\begin{proof}
-The bottom $\alpha$ rows of $\vA$ (namely, $\vR|\vS$) are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
-The top left $m\times n$ quadrant of $\vA$ is also random, because it is produced as a sum of a uniformly random $\vA'$ with some values that are uncorrelated with $\vA'$.
-The submatrix of the top-right $m\times (\alpha+\beta)$ quadrant corresponding to $\vQ_{T^c}$~(recall this is the restriction of $\vQ$ to the columns not in $T$) is also random, because it is initialized with random values to which some uncorrelated values are then added.
-It is important to note that all these values are independent of $\gamma_i$ values.
-
-Thus, we restrict attention to the $m\times \alpha$ submatrix of $\vA$ that corresponds to $\vQ_T$ in $\vA^*$ (note that these values are $0$ in $\vA^*$).
-Consider a particular row $i$.
-That row is computed as $\gamma_i \vS_{T}$.
-Since $\vS_T$ is a full rank square matrix and $\gamma_i$ is uniformly and independently generated, that row is also uniform and independent of other entries in $\vA$.
-\end{proof}
-\begin{claim}
-\label{cl:random ax+e}
-If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$, where
-\begin{itemize}
-\item $e_i = e_i'$ for $1\leq i\leq m$,
-\item $e_i = 0$ for $m<i\leq m+\alpha$,
-\item $x_j = x_j'$ for $1\leq j \leq n$,
-\item and $x_j$ is uniform and independent of $\vA$ and $\ve'$ for $n<j\le n+\alpha+\beta$,
-\end{itemize}
-\end{claim}
-\begin{proof}
-Partially define $\vx$ as $x_j = x_j'$ if $1\leq j \leq n$ and $x_j$ as the value generated in step~\ref{step:fill in matrix} for $j>n $ and $j\not\in T$.
-Define the remaining variables $\vx_T$ as the solution to the following system of equations.
-\begin{eqnarray}
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  \label{eq:x t solution}
-\end{eqnarray}
-A solution $\vx_T$ exists as $\vS_T$ is full rank.
-Moreover, it is uniform and independent of $\vA$ and $\ve$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve$.
-
-We now show that $\vb^* = \vA^* \vx+\ve$.
-All entries in matrix $\vQ$ corresponding to variables in $T$ are set to zero.
-Thus, the values of $\vx^T$ do not affect $b_i^*$ for $1\le i \le m$.
-The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $b_i^*$.
-Thus, for $1 \leq i \le m$, we have $\vb^* = \vA^*\vx+\ve$.
-For $m< i$, this constraint is also satisfied by the values of $\vx_T$ set in Equation~\ref{eq:x t solution}.
-
-Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
-We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
-Recall the other rows are not modified.  We have the following for $1\leq i\leq m$:
-\begin{align*}
-\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
-&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
-\end{align*}
-Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
-\begin{align*}
-(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
-&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
-\\&=  \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
-\end{align*}
-This completes the proof of the claim.
-\end{proof}
-\begin{claim}\label{clm:random b}
-If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then $\vb\,|\,\vA$ is also uniform.
-\end{claim}
-\begin{proof}
-Since $\vR, \vS$, and $\vQ$ are chosen independently of $\vb'$, the distribution $\vb'\,|\,\vA^*$ is uniform.
-Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-Its first $m$ coordinates are  computed by adding the uniform vector $\vb'$ to values that are independent of $\vb^*$, and its remaining $\alpha$ coordinates $b^*_{m+1},\dots,b^*_{m+\alpha}$ are   chosen uniformly.
-Thus $\vb^*\,|\,\vA^*$ is uniform.
-
-Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
-It is independent of $\vb^*$ and $\vA^*$, so $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform.
-Let $\vgamma'=\left(\begin{array}{c | c}\vect{I_m} & \vgamma \\\hline \vect{0} & \vect{I_\alpha}\end{array}\right)$.
-Note that $\vb=\vgamma' \vb^*$.  Since $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform, and $\vgamma'$ is invertible, $\vb\,|\,(\vA^*, \vgamma)$ must also be uniform.
-Since $\vA$ is a deterministic function of $\vA^*$ and $\vgamma$ (assuming Step~\ref{step:find columns} is deterministic---if not, we can fix the coins used), the distribution $\vb\,|\,\vA$ is the same  as $\vb\,|\,(\vA^*, \vgamma)$ and is thus also uniform.
-\end{proof}
-
-Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $D'$ properly prepares the instance thus,
-\begin{align*}
-&\left|\Pr[D'(\vA, \vA X+\chi) = 1] - \Pr[D'(\vA, U) =1] \right|\\
-&\, = \left| \Pr\left[D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
-&\, =\left|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]  \right| \Pr[\rank(\vS) = \alpha] \\
-&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
-\end{align*}
-Where the second line follows because we can detect when $\rank(\vS)<\alpha$ and output a random bit in this case.
-Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
-\end{proof}
-\section{Additional Proofs}
-
-\subsection{Proof of \lemref{lem:averageToMaximalError}}
-\label{sec:proof of average to maximal error}
-\begin{proof}
-Let $C$ be the  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$ such that  $\Hoo(C)\geq k$.  Then for all $t'\le t$
-\[
-\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \neigh (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
-\]
-For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \neigh(c, t') \wedge \rec(c') \neq c]$.  
-Then by Markov's inequality:
-\[
-\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
-\]
-Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.
-Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.
-Since $H_\infty(C)\geq k$, we know $|C'|\geq 2^{k-1}$~(otherwise $\Pr_{c\leftarrow C}[c\in C']=\sum_{c\in C'}\Pr[C=c]$ would be less than $2^{k-1}\frac{1}{2^k} = 1/2$).
-This completes the proof of the~\lemref{lem:averageToMaximalError}.
-\end{proof}
-
-\subsection{Proof of \thref{thm:impSketchArbitraryW}}
-\label{sec:proof of thm sketch implies code}
-\begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
-\[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\le \epsilon\, ,
-\]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. 
-Define $D$ as:
-\begin{enumerate}
-\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{enumerate}
- By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.
-Let $X_y$ denote the random variable $X|Y=y$.
-By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.
-
-Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.
-Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).
-Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).
-Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \neigh(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
-Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.
-The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
-\end{proof}
-
-\subsection{Proof of \thref{thm:imp of unp entropy}}
-\label{sec:proof of imp unp entropy}
-Instead of proving the result just for Hamming metric over $\mathcal{Z}^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
-We now define this second condition:
-\begin{definition}
-A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
-\end{definition}
-
-\begin{theorem}
-Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
-Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least some fixed value $B_t(\cdot)$.
-Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
-\end{theorem}
-\begin{proof}
-Let $(X, Y)$ be two random variables such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq |\mathcal{M}| (1-\epsilon -t\delta) / |B_t(\cdot)|$.
-
-Let $B_t(x)$ denote the random variable representing a random neighbor of distance at most $t$ from $x$ (note that $B_t$ may not be efficiently samplable, because we are assuming only that a neighbor a fixed distance is efficiently samplable).
-We begin by showing that \rec must recover points of $X$.  
-\begin{claim}
-\label{clm:y is recoverable}
-\begin{align*}
-\Pr[\rec(B_t(X), Y) = X]&=\\
-\Pr[(x, y)\leftarrow (X, Y) \wedge x'\leftarrow B_t(x) \wedge \rec(x', y) = x] &\geq 1-\epsilon -t\delta.
-\end{align*}
-\end{claim}
-\begin{proof}
-Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.
-We construct the following distinguisher $D\in\mathcal{D}_{s_{sec}}$ (the distinguisher design is slightly complicated by the fact that we don't know at which particular distance $t'$ the recover procedure is most likely to fail, so we have to try all distances):
-\begin{itemize}
-\item Input $w\in \mathcal{M}, s\in\zo^*$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{itemize}
-First note that $|D| = t( |\rec|+ s_{neigh} )$.
-Since $(\sketch, \rec)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
-If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist at least one $1\leq t'\leq t$ for which $\Pr[\rec(\neigh(X, t'), Y) = X] < 1-\epsilon -t\delta$.
-Then
-\begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(X, Y)=1] &\geq\\
-(1-t\delta) - \Pr[\rec(\neigh(X, t'), Y) = X] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
-\end{align*}
-This is a contradiction and the statement of the claim follows.
-\end{proof}
-
-Now define $\mathcal{I}$ as follows:
-\begin{itemize}
-\item Input $y\in\zo^*$.
-\item Sample $x'\leftarrow \sample$.
-\item Output $\rec(x', y)$.
-\end{itemize}
-Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$. 
-We now show that $\mathcal{I}$ predicts $X$:
-\begin{align*}
-\Pr[\mathcal{I}(Y) = X] & = \\
-&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
-&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[\sample = x' ] \Pr[\rec(x', y) =x]\\
-&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x' \mathrm{ s. t. } \dis(x', x)\le t} \Pr[\sample = x']\Pr[\rec(x', y) =x]\\
-&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\mathrm{ s. t. } \dis(x', x)\le t} \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[B_t(x) = x'] \Pr[\rec(x', y) =x]\\
-&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
-\end{align*}
-(the last step follows by  \clref{clm:y is recoverable}).
-
-\thref{thm:imp of unp entropy} follows by noting that $\mathcal{Z}^n$ can be sampled in time $n\log |\mathcal{Z}|$ and neighborhood sampled in time $n\log |\mathcal{Z}|$.
-\end{proof}
-
-\subsection{Proof of \lemref{lem:i t poly time}}
-\label{sec:proof lem i t poly time}
-\begin{proof}
-Note that $\decode_t$ will stop if $w$ and $w'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
-\begin{align*}
-\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\left(\frac{m}{n}-2\right)\log n}{m-i}\right)\\
-&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
-&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}\,.
-\end{align*}
-(The second-to-last step holds as long as $n\ge 2d\log n$.) Because at each iteration, we select $2n$ rows independently at random, the expected number of iterations is at most $n^{4d}$; each iteration takes $O(n^3)$ operations in $\Fq$, which gives us the expected running time bound.
-
-The probability that $\decode_t$ outputs $\perp$ is bounded by 
-\begin{eqnarray*}
-\Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
-&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&= &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times}]\cdot \Pr[\rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot q^{-n}\\
-& = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
-\end{eqnarray*}
-The third line from the bottom follows from the fact that the locations of the errors are assumed to be independent of the sketch, and therefore independent of the matrix $\vA$.
-The second line from the bottom follows from \clref{cl:full rank matrix} when $\beta = n$; note that, because we use the union bound and evaluate the probability separately for each value of $j$,  we can treat $\vA_{i_1,\dots, i_{2n}}$ as a randomly chosen $2n\times n$ matrix, ignoring the fact that these matrices are correlated.
-
-We claim that if the code generated by $\vA$ 
-has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $\vx'=\vx$.
-Indeed, suppose $\vx'\neq \vx$.
-Since $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $w-w'$, such an $\vx'$ will not pass Step 6.
-
-The probability that the code generated by $\vA$ has distance lower than $2t+1$ is at most $e^{-\Omega(n)}$ (see \corref{cor:code high distance}), the probability of outputting $\perp$ is also $e^{-\Omega(n)}$~(computed above).
-This gives the correctness bound for $\decode_t$.
-\end{proof}
-
-\section{Parameter Settings for \consref{cons:informal construction}}
-\label{sec:parameter settings}
-In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure extractor log} we give a lossless fuzzy extractor from a security parameter $n$ and an error $t$.
-In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
-We begin by reviewing the parameters that make up our construction:
-
-\begin{itemize}
-\item $|W|$: The length of the source.  
-\item $t$: Number of errors that can be supported.  
-\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
-\item $q$: The size of the field.  
-\item $\rho$: The fraction of the field needed for error sampling.  
-\item $m$: The size of each number of samples in the LWE instance.  
-\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
-\end{itemize}
-We will split the source $|W|$ into $m$ blocks each of size $2\rho q+1$~(that is, $|W| = m\log (2\rho q+1)$).
-We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.
-As stated above we have three constraints:
-\begin{itemize}
-\item Maintain security of LWE.
-If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + \sigma} m = \poly(n)$.
-The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.
-We ignore this effect and assume that $\rho q = 2n^{1/2+\sigma}m$.
-\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
-\item Minimize entropy loss of the construction.
-We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.
-We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.
-Substituting, one has $m\log 2\rho q+1 = k \log q$.
-\end{itemize}
-Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
-\begin{align*}
-n_0&< n -k \\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+\sigma}m\\
-m\log (2\rho q +1)&= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
-\end{align*}
-This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma} m+1}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
-Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n -k \\
-m &= \frac{(c/d+2)n \log n}{\log n} = (\frac{c}{d}+2)n\\
-f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma}m+1}{\log n} = \frac{g(c+2d)}{d}\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
-\end{align*}
-Note that $f$ is at a constant in $n$.
-Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= (\frac{c}{d}+2)n\\
-q & = n^f = n^{\frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
-\end{align*}
-
-Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $d<c$~(this also ensures that $m\geq 3n$, as required for \lemref{lem:i t poly time} to hold).
-Since $\rho q = 2n^{1/2+\rho }m = O(n^{5/2})$ in our setting $\rho = O(n^{-1/2})$.
-Thus, for large enough settings of parameters $\rho$ is less than $1/10$ as required by \lemref{lem:uniform LWE decision}.
-
-Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.
-We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).
-The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.
-In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.
-Setting $1<g<2$ achieves an increase in output length~(over the input length of $W$).
-We also (arbitrarily) set $\sigma=1/2$ to simplify the statement of \thref{thm:lossless secure extractor log}, making $\rho q = 2(c/d+2) n^2$.
-
-\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
-\label{ssec:block params}
-We repeat parameter settings for block fixing sources.
-We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.
-We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
-\begin{align*}
-n_0&< n -k  -\alpha -\beta\\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+\sigma}m\\
-m\log (2\rho q+1)&= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k - \alpha -\beta\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
-\end{align*}
-As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k  - \alpha - \beta \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-%f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma} m+1)}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.
-Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n/3 -  \log n\\
-m &= \frac{(c/d+2)n \log n}{ \log n} = (\frac{c}{d}+2)n\\
-f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(3(\frac{c}{d}+2)\right)\frac{\log (4(\frac{c}{d}+2) n^{3/2+\sigma}+1)}{\log n} = O(1)
-\end{align*}
-
-Assuming $n/3-\log(n)> n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= (\frac{c}{d}+2)n\\
-q & = n^f = n^{\frac{m}{n}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
-\end{align*}
-
-As before we arbitrarily set $\sigma = 1/2$, giving $\rho q = 2(\frac{c}{d}+2)n^2$.
-Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
 \end{document}

### 2013-12-11 trunk/constantRate/ConstCompFuzzExt.tex
Added construction

@@
 Both definitions appear in \secref{sec:preliminaries}.}  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.
-We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.
-\footnote{Security is impossible if all points of the source distribution are close together.
+We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.
 In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within the error-tolerance.
@@
 Our construction is based on obfuscation.
-While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we only use the obfuscation of point functions.
+While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we use the obfuscation of point functions.
 This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
@@
 Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
-For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\angle$ are computationally indistinguishable.
+For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
 \end{assumption}
@@
 \begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}].
-A PPT algorithm $\mathcal{O}$ is a $t$-\emph{com posable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
+A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
 That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
@@
 \end{definition}
+
+\section{Our Construction}
+
+Before describing our construction, we recall the problem we are trying address.
+The goal is to derive strong keys from noisy sources.
+As discussed in the introduction, the important parameter is the difference between the total entropy and the number of errors being corrected.
+We call this value the entropy gap or $gap= \Hoo(W) - \log|B_t(\cdot)|$.
+The results of Dodis et al.~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08} show that gap is an upper bounded for the length of the derived key.
+
+If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
+Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.
+As described in Fuller, Meng, and Reyzin~\cite{fuller2013computational}, use of a computational fuzzy extractor may allow a construction when $gap = O(\log n)$.
+Their construction is only applicable for high entropy input and yield a result when $gap$ is small.
+We will provide the first construction where $gap$ is negative.
+We first focus on deriving a single key bit in this setting as this is already nontrivial.
+
+\subsection{Single-Bit Construction}
+\begin{construction}
+
+Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.
+Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.
+Let $t$ be the desired error-tolerance and let $C$ be a binary $(\ell, k, t)$-error-correcting code.
+Let $\ext : \zo^n\times \zo^* \rightarrow \zo$ be a $(x, x, x, x)$-extractor.
+We describe $\gen, \rep$ as follows:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_t$
+\item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
+\item For $i=1,..., \ell$:
+\subitem If $c_i = 1$: $p_i = \mathcal{O}(C(w_i))$.
+\subitem If $c_i = 0$: Sample $r_i \leftarrow U_n$.  \\
+\,
+Let $p_i = \mathcal{O}(C(r_i))$.
+\item Let $r = \ext(c, seed)$.
+\item Output $(r, p)$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p, seed)$ 
+\item For $i=1,..., \ell$:
+\subitem If $p_i(w_i') = 1$ set $c_i' = 1$.
+\subitem Else set $c_i' = 0$.
+\item Set $c = \decode$.
+\item Output $r  = \ext (c', seed)$.
+\end{enumerate}
+\vspace{0.45in}
+\end{minipage} 
+\end{tabular}
+\end{center}
+\label{cons:informal construction}
+\end{construction}
+
+\textbf{Notes:}  We make several observations about the above construction:
+\begin{itemize}
+\item Assuming a roughly balanced code $C$~(where on average, half of the bits of a codeword are 0 and half are 1), in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
+As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
+\item There are two possible reasons for a bit of $c_i'$ to be $0$.
+Because the true value was $0$~(there is little chance of $0$ being incorrectly decoded as $1$ assuming $w_i'$ is formed independently of the sketch) and because $w_i \neq w_i'$.
+However if a bit of $c_i'$ is $1$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
+Thus, instead of using a code suited for a binary symmetric channel, a code for the $Z$ channel may be used.
+\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(see~\cite[Section 3.3]{fuller2013computational} for discussion).
+\end{itemize}
 

### 2014-01-06 constantRate/ConstCompFuzzExt.tex
Working on simple case proof

--- 2013-12-11 trunk/constantRate/ConstCompFuzzExt.tex
@@
 
-\section{Our Construction}
+\section{A Constant Rate Computational Fuzzy Extractor}
 
@@
 Let $\ext : \zo^n\times \zo^* \rightarrow \zo$ be a $(x, x, x, x)$-extractor.
+\bnote{fill this in}
 We describe $\gen, \rep$ as follows:
@@
 \begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_t$
+\item \underline{Input}: $w = w_1,..., w_\ell$
 \item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
@@
 
+Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.
+The adversary is provided with equality oracles for each block individually.
+Security rests on an adversaries inability to learn the values using only \emph{adaptive} equality queries.
+We begin with the setting where each block is independent and then move to the setting of correlated blocks.
+
+\begin{lemma}
+Let $n$ be a security parameter.
+Let $W(n) = W = W_1,..., W_t$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.
+Let $t$ be a desired error-tolerance.
+Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.
+%Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}.
+Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.
+\end{lemma}
+\begin{proof}
+Consider a particular block $i$, we measure how an adversaries queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
+Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
+Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
+We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
+The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
+(There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
+There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
+If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
+These responses can be removed as the response is deterministic.
+Let $A'$ represent the sequence with all duplicate queries removed.
+This sequence has at most a single $1$.
+Thus, the total number of possible responses is $q+1$.
+Thus, we have the following,
+\begin{align*}
+\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
+&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
+&=\Hav(W_i |A') \\
+&=\Hoo(W_i) - \log |A'|\\
+&= \omega(\log n) - \log |A'|\\
+&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
+\end{align*}
+Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
+This argument holds for all $i$.  This completes the proof.
+%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).
+Thus,
+%\begin{align*}
+%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
+%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
+%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
+%\end{align*}
+%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).
+Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.
+Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.
+This completes the proof of the lemma.
+\end{proof}
+\begin{lemma}
+For each $c_j$ the adversary knowledge is negligible conditioned on their view.
+\end{lemma}
+
 \section{Supported Sources}

### 2014-01-06 constantRate/ConstCompFuzzExt.tex
Trying to work on proof outline

@@
 We will provide the first construction where $gap$ is negative.
-We first focus on deriving a single key bit in this setting as this is already nontrivial.
+We first introduce the notion of a balanced code:
 
-\subsection{Single-Bit Construction}
+\subsection{First $gap<0$ construction}
 \begin{construction}
@@
 \begin{itemize}
-\item Assuming a roughly balanced code $C$~(where on average, half of the bits of a codeword are 0 and half are 1), in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
+\item Assuming a balanced code $C$~(where on average, half of the bits of a codeword are 0 and half are 1), in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
 As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
@@
 \begin{lemma}
-For each $c_j$ the adversary knowledge is negligible conditioned on their view.
+Let $W$ and $U$ be two distributions of super-logarithmic entropy.
+Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
 \end{lemma}
+\begin{proof}
+It suffices to show that with the probability of all responses being $0$ is overwhelming.
+Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
+\bnote{Finish this proof}
+\end{proof}
 
+\begin{lemma}
+Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
+Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
+\end{lemma}
+\begin{proof}
+\bnote{Do this}
+\end{proof}
+We can extend this lemma to the entire codeword $C$:
+\begin{lemma}
+For all $c_1, c_2 \in C$ we have the following: 
+\[
+\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2) \leq \ngl(n).
+\]
+\end{lemma}
+\begin{lemma}
+If $C$ is a balanced code then, for all $i$, $\Hoo(C_i |View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)}))\geq 1 - \omega(1)(\log n)$.
+\end{lemma}
+\begin{proof}
+From Lemma 3.4\bnote{change to reference}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
+Let $w$ be the exponent of the particular negligible value above~(note $w = \omega(1)$).
+Then we have for $b\in\{0,1\}$
+\begin{align*}
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C_i =b | view ] &\leq 1/2 + \ngl(n)\\
+\end{align*}
+Taking the negative log of each side one has:
+\begin{align*}
+\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
+ &=\\-\log \left(\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\max_{b\in\{0,1\}}\Pr[C_i =b | view ]  \right) &\geq -\log (1/2 + \ngl(n))\\
+&\geq -\log(\frac{1}{2} + \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+2}{2n^{w}}\right)\\
+&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
+&=1-\left(\log (n^w + 2) - \log n^w\right)\\
+&\geq 1- \left(\log (n+1)^w - \log n^w\right)  \\
+&= 1- w\left( \log (n+1) - \log n\right)\\
+&\geq 1 - w*1
+\end{align*}
+\end{proof}
+\begin{lemma}
+$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
+\end{lemma}
+\begin{corollary}
+$\Delta(\ext(C, seed) , U | seed, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)}))\leq \ngl(n)$.
+\end{corollary}
 \section{Supported Sources}

### 2014-01-07 trunk/constantRate/ConstCompFuzzExt.tex
getting proof outline to something reasonable

@@
 They are composed of two algorithms: \gen takes a source value $w_0$, and produces a key $r$ and a public value $p$, and \rep which takes a nearby value $w_1$ and $p$ producing the original key $r$.
-Intuitively, they are two functions: error correction~(to provide the same value with \emph{noisy} readings) and key derivation~(to transform an entropic source into a uniform key).
+Intuitively, they are two functions: information reconciliation~(to provide the same value with \emph{noisy} readings) and key derivation or privacy amplification~(to transform an entropic source into a uniform key).
 Traditionally, these two functions were performed by two separate primitives: a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} and a randomness extractor~\cite{nisan1993randomness}.
@@
 However, this does not need to be the case in the computational setting.
-The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The main difference isa computational fuzzy extractor outputs a pseudorandom key instead of a truly random key.
-Both definitions appear in \secref{sec:preliminaries}.}  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.
+The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The difference is a computational fuzzy extractor outputs a pseudorandom key.
+}  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.
 We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.
-In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within the error-tolerance.
+In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within any error-tolerance region.
 This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}
@@
 
+\textbf{Our Results:} Specifically this paper presents the following:
+\begin{itemize}
+\item The first computational fuzzy extractor that supports a constant fraction of errors.
+\item The first fuzzy extractor where the number of errors corrected is larger than the entropy of the starting distribution.
+\end{itemize}
+\bnote{More details here}
+
+\bnote{Provide an outline of the rest of the paper}
+
 \section{Preliminaries}
@@
 We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
+
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-We primarily consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
+For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
 For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
+However, we will use codes that only correct unidirectional errors~(see \secref{sec:coding theory}).
+
 Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.
 
-\subsection{Fuzzy Extractors and Secure Sketches}
+\subsection{Randomness Extractors and Computational Fuzzy Extractors}
 \label{sec:fuzzy extractors}
 
-We now recall definitions and lemmas from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
+Here we present relevant definitions of fuzzy extractors.
+We focus on the notion of computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
+Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et.
+al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
+The definition of computational fuzzy extractors allows for a small probability of error, as described in~\cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
-
-\begin{definition}
-\label{def:fuzzy extractor}
-An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
-\begin{enumerate}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
-\end{enumerate}
-A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
-\end{definition}
-
-Secure sketches are the main technical tool in the construction of fuzzy extractors.
-Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
-\begin{definition}
-\label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
-\begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
-That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
-\end{definition}
-
-Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
-
-A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
+We will also use the standard notion of an average-case extractor.
 An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
@@
 
-\begin{lemma}
-\label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
+%\begin{definition}
+%\label{def:fuzzy extractor}
+%An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
+%\begin{enumerate}
+%\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
+%\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
+If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
+%\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
+%\end{enumerate}
+%A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
+%\end{definition}
+%
+%Secure sketches are the main technical tool in the construction of fuzzy extractors.
+Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
+%\begin{definition}
+%\label{def:secure sketch}
+%An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+%\begin{enumerate}
+%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
+%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
+The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
+%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
+That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+%\end{enumerate}
+%A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
+%\end{definition}
+%
+
+We now present the definition of a computational fuzzy extractor~(from~\cite{fuller2013computational}):
+
+%A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. 
+%
+%\begin{lemma}
+%\label{lem:fuzzy ext construction}
+%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
-\begin{itemize}
-\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
-\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
-\end{itemize}
-\end{lemma}
-The main parameter we will be concerned with is the entropy loss of the construction.
-In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
-We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
-Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
+%\begin{itemize}
+%\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
+%\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
+%\end{itemize}
+%\end{lemma}
 
@@
 Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.  
+Note that in the above definition of fuzzy extractors, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
+For notational convenience, we the definition of computational fuzzy extractors specifies a general class of sources for which the fuzzy extractor is designed to work, rather than the class of sources that consists of all sources of a given min-entropy $m$~(of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
+
+The question is we ask is for what type of sources can we build fuzzy extractors?
+Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.
+The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t(\cdot)$.
+When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.
+We ask whether security is possible when $gap$ is small or negative.
+%In this paper, we ask whether a smaller entropy loss can be achieved by considering a computational fuzzy extractor with a computational security requirement.
+%We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
+
+As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
+As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch.
+Instead, we will use a computational fuzzy extractor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}):
+
+\begin{definition}
+Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
+A pair of randomized procedures ``generate'' (\gen) and ``reproduce'' (\rep) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties:
+\begin{itemize}
+\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
+\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
+If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.\bnote{need to define conditional HILL entropy}
+\end{itemize}
+\end{definition}
+
+Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor:
+
+\begin{lemma}
+\label{lem:cond and ext}
+Let $\epsilon_{ent} >0$ be a parameter.
+Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.
+Let $\ext:\mathcal{M}_2\times \zo^*\rightarrow \zo^\ell$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.
+Define the $\gen, \rep$:
+\begin{itemize}
+\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \ext(y; x)$,  and output $(r, p)$.
+\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \ext(y; x)$. 
+\end{itemize}
+Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \ell, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
+\end{lemma}
+\begin{proof}
+Result of extractibility of conditional HILL entropy~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}.\bnote{I don't think you need this $\epsilon_{ent}$ should be able to just use average case extractor directly}
+\end{proof}
+
+\subsection{Coding Theory}
+\label{sec:coding theory}
+We introduce some notions from the field of binary error correcting codes.
+Usually the class of errors considered is all points within Hamming distance at most $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but never bit flips from $1\not\rightarrow 0$.
+\begin{definition}
+\label{def:hamming z channel}
+For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
+\end{definition}
+\textbf{Note:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may be exist for these errors.
+
+\begin{definition}
+Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon)$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon$.
+\end{definition}
+
+We need one special property of the code, namely that each output bit is set $1$ with probability $1/2$.
+
+\begin{definition}
+A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
+\end{definition}
+All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
+This is only true as long as $C$ contains no constant bits.
+Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
+For the remainder of this work when we say a code, we assume there are no constant bits.
+
+\begin{lemma}
+Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
+\end{lemma}
+\begin{proof}
+Suppose there is some $i$ that is not equiprobable.
+Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
+First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
+First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
+Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
+Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
+This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
+This completes the proof.
+Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
+This is a contradiction and completes the proof.
+\end{proof}
 
@@
 We will provide the first construction where $gap$ is negative.
-We first focus on deriving a single key bit in this setting as this is already nontrivial.
 
-\subsection{Single-Bit Construction}
+\subsection{First $gap<0$ construction}
 \begin{construction}
-
+\label{cons:first construction}
 Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.
 Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.
-Let $t$ be the desired error-tolerance and let $C$ be a binary $(\ell, k, t)$-error-correcting code.
-Let $\ext : \zo^n\times \zo^* \rightarrow \zo$ be a $(x, x, x, x)$-extractor.
+Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be an output equiprobable $(\neigh_t, \epsilon_{code})$-error-correcting code.
+Let $\ext : \zo^n\times \zo^* \rightarrow \zo^r$ be a $(\tilde{m}, \epsilon_{ext})$-extractor where $\tilde{m}= XXX$.
+\bnote{fill this in}
 We describe $\gen, \rep$ as follows:
@@
 \begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_t$
+\item \underline{Input}: $w = w_1,..., w_\ell$
 \item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
 \item For $i=1,..., \ell$:
-\subitem If $c_i = 1$: $p_i = \mathcal{O}(C(w_i))$.
-\subitem If $c_i = 0$: Sample $r_i \leftarrow U_n$.  \\
+\subitem If $c_i = 0$: $p_i = \mathcal{O}(C(w_i))$.
+\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$.  \\
 \,
@@
 \item For $i=1,..., \ell$:
-\subitem If $p_i(w_i') = 1$ set $c_i' = 1$.
-\subitem Else set $c_i' = 0$.
+\subitem If $p_i(w_i') = 1$ set $c_i' = 0$.
+\subitem Else set $c_i' = 1$.
 \item Set $c = \decode$.
@@
 \begin{itemize}
-\item Assuming a roughly balanced code $C$~(where on average, half of the bits of a codeword are 0 and half are 1), in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
+\item If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
 As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
-\item There are two possible reasons for a bit of $c_i'$ to be $0$.
-Because the true value was $0$~(there is little chance of $0$ being incorrectly decoded as $1$ assuming $w_i'$ is formed independently of the sketch) and because $w_i \neq w_i'$.
-However if a bit of $c_i'$ is $1$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
-Thus, instead of using a code suited for a binary symmetric channel, a code for the $Z$ channel may be used.
+\item There are two possible reasons for a bit of $c_i'$ to be $1$.
+Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.
+However if a bit of $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
+This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
 \item The extractor can be removed from the construction leaving a computational fuzzy conductor~(see~\cite[Section 3.3]{fuller2013computational} for discussion).
@@
 
+Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.
+The adversary is provided with equality oracles for each block individually.
+Security rests on an adversaries inability to learn the values using only \emph{adaptive} equality queries.
+We begin with the setting where each block is independent and then move to the setting of correlated blocks.
+
+\begin{lemma}
+Let $n$ be a security parameter.
+Let $W(n) = W = W_1,..., W_t$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.
+Let $t$ be a desired error-tolerance.
+Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.
+%Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}.
+Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.
+\end{lemma}
+\begin{proof}
+Consider a particular block $i$, we measure how an adversaries queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
+Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
+Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
+We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
+The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
+(There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
+There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
+If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
+These responses can be removed as the response is deterministic.
+Let $A'$ represent the sequence with all duplicate queries removed.
+This sequence has at most a single $1$.
+Thus, the total number of possible responses is $q+1$.
+Thus, we have the following,
+\begin{align*}
+\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
+&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
+&=\Hav(W_i |A') \\
+&=\Hoo(W_i) - \log |A'|\\
+&= \omega(\log n) - \log |A'|\\
+&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
+\end{align*}
+Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
+This argument holds for all $i$.  This completes the proof.
+%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).
+Thus,
+%\begin{align*}
+%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
+%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
+%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
+%\end{align*}
+%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).
+Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.
+Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.
+This completes the proof of the lemma.
+\end{proof}
+\begin{lemma}
+\label{lem:super log insist by equal queries}
+Let $W$ and $U$ be two distributions of super-logarithmic entropy.
+Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+\end{lemma}
+\begin{proof}
+It suffices to show that with the probability of all responses being $0$ is overwhelming.
+Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
+\bnote{Finish this proof}
+\end{proof}
+
+\begin{lemma}
+\label{lem:code bits statistically indist}
+Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
+Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
+\end{lemma}
+\begin{proof}
+\bnote{Do this}
+\end{proof}
+We can extend this lemma to the entire codeword $C$:
+\begin{lemma}
+For all $c_1, c_2 \in C$ we have the following: 
+\[
+\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
+\]
+\end{lemma}
+\begin{lemma}
+If $C$ is output then, for all $i$, $\Hav(C_i |View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)}))\geq 1 - \ngl(n)$.
+\end{lemma}
+\begin{proof}
+Since $C$ is output equiprobable we know that for each $i$, $\Pr[C_i =1 ] = 1/2$.
+Let $w$ be the exponent of the particular negligible value above~(note $w = \omega(1)$).
+For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
+\begin{align*}
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C_i =b | view ] &\leq 1/2 + \ngl(n)\\
+\end{align*}
+If this was not true~(that is in expectation, there was some $b$ that was likely with probability greater than $1/2+1/\poly(n)$), there there would exist an unbounded adversary outputting that $b$, contradicting \lemref{lem:code bits statistically indist}).
+Taking the negative log of each side one has:
+\begin{align*}
+\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
+ &=\\-\log \left(\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\max_{b\in\{0,1\}}\Pr[C_i =b | view ]  \right) &\geq -\log (1/2 + \ngl(n))\\
+&\geq -\log(\frac{1}{2} + \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+2}{2n^{w}}\right)\\
+%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
+&=1-\left(\log (1+\frac{2}{n^w}) \right)\\
+&=1-\frac{1}{\ln 2}\left(\ln (1+\frac{2}{n^w}) \right)\\
+&= 1- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{2}{n^w})^i\right) \\
+&\geq 1 - \frac{1}{\ln 2} \frac{2}{n^w} = 1-\ngl(n)
+\end{align*}
+Here the second to last line is derived using the Taylor expansion for $\ln(1+x)$ and the last line is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive.
+\end{proof}
+By similar reasoning we can extend this lemma to the entire codeword:
+\begin{lemma}
+If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
+\end{lemma}
+%\begin{lemma}
+%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
+%\end{lemma}
+\begin{corollary}
+\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor.
+\end{corollary}
+\begin{proof}
+Result of security of point obfuscation and \lemref{lem:cond and ext}.
+\end{proof}
 \section{Supported Sources}

### 2014-01-07 trunk/constantRate/ConstCompFuzzExt.tex
Working on proof outline

@@
 \newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
+\newcommand{\rnote}[1]{{\authnote{Ran}{#1}}}
+\newcommand{\onote}[1]{{\authnote{Omer}{#1}}}
 
@@
 As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch.
-Instead, we will use a computational fuzzy extractor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}):
+Instead, we will use a computational fuzzy extractor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):
 
@@
 If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.\bnote{need to define conditional HILL entropy}
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
 \end{itemize}
@@
 Let $W(n) = W = W_1,..., W_t$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.
-Let $t$ be a desired error-tolerance.
 Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.
@@
 
+\appendix
+\section{Computational Entropy}
+HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
+It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+
+\begin{definition}
+\label{def:hill ent}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
+\end{definition}
+
 \end{document}

### 2014-01-08 trunk/constantRate/ConstCompFuzzExt.tex
Notation file

@@
 However, this does not need to be the case in the computational setting.
-The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The difference is a computational fuzzy extractor outputs a pseudorandom key.
-}  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.
+The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The only difference between a computational fuzzy extractor and a fuzzy extractor is the key is pseudorandom instead of statistically random.
+}  With computational security, an error tolerance \emph{larger} than the starting entropy may be possible.
 We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.
@@
 This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
-Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).
-Dodis and Smith constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.
-Unfortunately, our construction is not a noisy point obfuscation and leaks partial information about particular blocks of the source.
+
+\textbf{Overview of Construction:}  Consider a source $w = w_1,..., w_\ell$ that is split into blocks.
+We would like to construct tolerate Hamming errors for individual blocks.
+The main idea is for each block, $i$: either the $w_i$ is obfuscated or a random point $r_i$ is obfuscated~(this idea is similar to the construction of digital lockers from point obfuscation).
+Then with a close value $w'$ the recovery value knows where random values were obfuscated and where $w_i$ was obfuscated.
+To tolerate errors, the choice of obfuscating $w_i$ or a random point is made using bits of an error correcting code.
+
+\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).
+Unfortunately, this is not the case.
+Since each block is individual obfuscated, equality of individual blocks is learned~(for sources where not all blocks have high entropy).
+This precludes virtual black-box~(VBB) security where no partial information about the input may be learned.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.
+Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.
 
@@
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-However, we will use codes that only correct unidirectional errors~(see \secref{sec:coding theory}).
+However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
 
@@
 
-Here we present relevant definitions of fuzzy extractors.
-We focus on the notion of computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
+Here we present relevant extractor definitions.
+We start with the standard notion of an average-case extractor.
+An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
+\begin{definition}
+Let $\chi_1$, $\chi_2$ be finite sets.
+A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
+of random variables $X, Y$ over $\chi_1, \chi_2$ such that
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon$.
+\end{definition}
+
+We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
 Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et.
@@
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
-We will also use the standard notion of an average-case extractor.
-An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
-\begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
-U_d \times Y) \le \epsilon$.
-\end{definition}
 
@@
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
+A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
 \begin{itemize}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
+\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
 \item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
@@
 If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
 \end{itemize}
@@
 
-The question is we ask is for what type of sources can we build fuzzy extractors?
+Our main question is: for what type of sources can we build fuzzy extractors?
 Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.
@@
 As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
-As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch.
-Instead, we will use a computational fuzzy extractor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch~\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}.
+Instead, we will use a computational fuzzy conductor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
 We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):
@@
 \begin{definition}
+\label{def:comp fuzzy cond}
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' (\gen) and ``reproduce'' (\rep) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties:
+A pair of randomized procedures ``generate'' (\gen') and ``reproduce'' (\rep') is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
 \begin{itemize}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
+\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
+\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.
+If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
 \item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
@@
 Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.
-Let $\ext:\mathcal{M}_2\times \zo^*\rightarrow \zo^\ell$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.
+Let $\ext:\mathcal{M}_2\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.
 Define the $\gen, \rep$:
@@
 \end{itemize}
-Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \ell, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
+Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
 \end{lemma}
@@
 We introduce some notions from the field of binary error correcting codes.
-Usually the class of errors considered is all points within Hamming distance at most $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but never bit flips from $1\not\rightarrow 0$.
+Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but no bit flips from $1\not\rightarrow 0$.
 \begin{definition}
@@
 All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
-This is only true as long as $C$ contains no constant bits.
+This is true as long as $C$ contains no constant bits.
 Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
@@
 This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
-This completes the proof.
 Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
@@
 
-We present the notion of virtual black-box obfuscation with the weakening that the simulator produces an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
+We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
 
@@
 where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
-Furthermore, the.runtime of $A$ and $S$ must be polynomial in the length of their first input.
+Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
 \end{enumerate}
@@
 \item For $i=1,..., \ell$:
-\subitem If $c_i = 0$: $p_i = \mathcal{O}(C(w_i))$.
-\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$.  \\
-\,
-Let $p_i = \mathcal{O}(C(r_i))$.
+\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
+\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
+\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
 \item Let $r = \ext(c, seed)$.
@@
 This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
-\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(see~\cite[Section 3.3]{fuller2013computational} for discussion).
+\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(\defref{def:comp fuzzy cond}).
 \end{itemize}
 
+\subsection{Security of Construction}
 Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.
@@
 Security rests on an adversaries inability to learn the values using only \emph{adaptive} equality queries.
-We begin with the setting where each block is independent and then move to the setting of correlated blocks.
+For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
 
@@
 \end{proof}
+
+\subsection{Correctness of Construction}
 \section{Supported Sources}

### 2014-01-08 trunk/constantRate/ConstCompFuzzExt.tex
correctness arguments

@@
 \DeclareMathOperator*{\expe}{\mathbb{E}}
+\DeclareMathOperator*{\var}{\text{Var}}
 
@@
 Since $C$ is output equiprobable we know that for each $i$, $\Pr[C_i =1 ] = 1/2$.
-Let $w$ be the exponent of the particular negligible value above~(note $w = \omega(1)$).
+Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
 For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
@@
 %&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
-&=1-\left(\log (1+\frac{2}{n^w}) \right)\\
-&=1-\frac{1}{\ln 2}\left(\ln (1+\frac{2}{n^w}) \right)\\
-&= 1- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{2}{n^w})^i\right) \\
-&\geq 1 - \frac{1}{\ln 2} \frac{2}{n^w} = 1-\ngl(n)
+&=1-\left(\log (1+\frac{2}{n^e}) \right)\\
+&=1-\frac{1}{\ln 2}\left(\ln (1+\frac{2}{n^e}) \right)\\
+&= 1- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{2}{n^e})^i\right) \\
+&\geq 1 - \frac{1}{\ln 2} \frac{2}{n^e} = 1-\ngl(n)
 \end{align*}
@@
 
-\subsection{Correctness of Construction}
+\subsection{Correctness of \consref{cons:first construction}}
+Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
+However, we start by justifying our use of unidirectional codes.
+\begin{lemma}
+\label{lem:no 1 to 0 flips}
+The probability of a single $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $\ngl(n) \leq \ell/2^n$.
+\end{lemma}
+\begin{proof}
+\bnote{we need to come back to this if we use obfuscation with error}
+Recall that $c$ contains at most $\ell$ $1$s.
+Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$.
+Since the $r_i$ are chosen independently, one has,
+\begin{align*}
+\Pr[\text{no $1\rightarrow 0$ flips}] &\geq 1-\Pr[\text{some }r_i = w_i']\\
+&\geq 1-\ell \frac{1}{2^n} = 1-\frac{\poly(n)}{2^n} = \ngl(n)
+\end{align*}
+\end{proof}
+\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
+We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
+Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
+We break the indices of $c = c_1,..., c_\ell$ into two components those where $c_i=1$ and those $c_i = 0$.
+Denote these two components by $c_{I_1}$ and $c_{I_0}$.
+Our goal is to bound how many of the places where $w, w'$ are inserted into $c_{I_0}$.
+Indices $i$,  where $w_i \neq w_i'$ and $c_i = 1$ will be ``corrected'' as $w_i'$ yield $c_i' = 1$ with overwhelming probably~(see \lemref{lem:no 1 to 0 flips}).
+Since $w_{err}$ be set of indices where $w, w'$ differ then for all $j\in w_{err}, \Pr[j\in c_{I_0}] = 1/2$.
+This is a binomial distribution with $p=1/2$ and $n=t$.
+Denote by $X =|\{j | w_j \neq w_j' \wedge j\in c_{I_1}|$.
+Thus, $\expe[X] = t/2$.
+Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
+\begin{align*}
+\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
+\end{align*}
+This leads us to the following lemma:
+\begin{lemma}
+\label{lem:correctness holds}
+If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
+\end{lemma}
+\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
+
 \section{Supported Sources}

### 2014-01-09 constantRate/ConstCompFuzzExt.tex
Adding discussion about limitations of first construction

--- 2014-01-06 constantRate/ConstCompFuzzExt.tex
@@
 
-\title{Constant Rate Computational Fuzzy Extractors}
+\title{Constant Error Rate Computational Fuzzy Extractors}
 \author{Some people}
@@
 However, this does not need to be the case in the computational setting.
-The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The main difference isa computational fuzzy extractor outputs a pseudorandom key instead of a truly random key.
-Both definitions appear in \secref{sec:preliminaries}.}  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.
+The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The only difference between a computational fuzzy extractor and a fuzzy extractor is the key is pseudorandom instead of statistically random.
+}  With computational security, an error tolerance \emph{larger} than the starting entropy may be possible.
 We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.
-In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within the error-tolerance.
+In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within any error-tolerance region.
 This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}
@@
 This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
-Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).
-Dodis and Smith constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.
-Unfortunately, our construction is not a noisy point obfuscation and leaks partial information about particular blocks of the source.
+
+\textbf{Overview of Construction:}  Consider a source $w = w_1,..., w_\ell$ that is split into blocks.
+We would like to construct tolerate Hamming errors for individual blocks.
+The main idea is for each block, $i$: either the $w_i$ is obfuscated or a random point $r_i$ is obfuscated~(this idea is similar to the construction of digital lockers from point obfuscation).
+Then with a close value $w'$ the recovery value knows where random values were obfuscated and where $w_i$ was obfuscated.
+To tolerate errors, the choice of obfuscating $w_i$ or a random point is made using bits of an error correcting code.
+
+\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).
+Unfortunately, this is not the case.
+Since each block is individual obfuscated, equality of individual blocks is learned~(for sources where not all blocks have high entropy).
+This precludes virtual black-box~(VBB) security where no partial information about the input may be learned.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.
+Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.
+
+\textbf{Our Results:} Specifically this paper presents the following:
+\begin{itemize}
+\item The first computational fuzzy extractor that supports a constant fraction of errors.
+\item The first fuzzy extractor where the number of errors corrected is larger than the entropy of the starting distribution.
+\end{itemize}
+\bnote{More details here}
+
+\bnote{Provide an outline of the rest of the paper}
 
@@
 We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
+
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-We primarily consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
+For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
 For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
+However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
+
 Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.
 
-\subsection{Fuzzy Extractors and Secure Sketches}
+\subsection{Randomness Extractors and Computational Fuzzy Extractors}
 \label{sec:fuzzy extractors}
 
-We now recall definitions and lemmas from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
-Let $\mathcal{M}$ be a metric space with distance function $\dis$.
-
-\begin{definition}
-\label{def:fuzzy extractor}
-An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
-\begin{enumerate}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
-\end{enumerate}
-A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
-\end{definition}
-
-Secure sketches are the main technical tool in the construction of fuzzy extractors.
-Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
-\begin{definition}
-\label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
-\begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
-That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
-\end{definition}
-
-Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
-
-A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
+Here we present relevant extractor definitions.
+We start with the standard notion of an average-case extractor.
 An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
@@
 Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
+A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
 of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
 U_d \times Y) \le \epsilon$.
@@
 
-\begin{lemma}
-\label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
+We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
+Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et.
+al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
+The definition of computational fuzzy extractors allows for a small probability of error, as described in~\cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
+Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+
+%\begin{definition}
+%\label{def:fuzzy extractor}
+%An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
+%\begin{enumerate}
+%\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
+%\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
+If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
+%\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
+%\end{enumerate}
+%A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
+%\end{definition}
+%
+%Secure sketches are the main technical tool in the construction of fuzzy extractors.
+Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
+%\begin{definition}
+%\label{def:secure sketch}
+%An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+%\begin{enumerate}
+%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
+%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
+The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
+%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
+That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+%\end{enumerate}
+%A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
+%\end{definition}
+%
+
+We now present the definition of a computational fuzzy extractor~(from~\cite{fuller2013computational}):
+
+%A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. 
+%
+%\begin{lemma}
+%\label{lem:fuzzy ext construction}
+%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
-\begin{itemize}
-\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
-\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
-\end{itemize}
-\end{lemma}
-The main parameter we will be concerned with is the entropy loss of the construction.
-In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
-We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
-Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
+%\begin{itemize}
+%\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
+%\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
+%\end{itemize}
+%\end{lemma}
 
@@
 Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.  
+Note that in the above definition of fuzzy extractors, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
+For notational convenience, we the definition of computational fuzzy extractors specifies a general class of sources for which the fuzzy extractor is designed to work, rather than the class of sources that consists of all sources of a given min-entropy $m$~(of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
+
+Our main question is: for what type of sources can we build fuzzy extractors?
+Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.
+The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t(\cdot)$.
+When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.
+We ask whether security is possible when $gap$ is small or negative.
+%In this paper, we ask whether a smaller entropy loss can be achieved by considering a computational fuzzy extractor with a computational security requirement.
+%We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
+
+As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
+As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch~\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}.
+Instead, we will use a computational fuzzy conductor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):
+
+\begin{definition}
+\label{def:comp fuzzy cond}
+Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
+A pair of randomized procedures ``generate'' (\gen') and ``reproduce'' (\rep') is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
+\begin{itemize}
+\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
+\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.
+If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
+\end{itemize}
+\end{definition}
+
+Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor:
+
+\begin{lemma}
+\label{lem:cond and ext}
+Let $\epsilon_{ent} >0$ be a parameter.
+Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.
+Let $\ext:\mathcal{M}_2\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.
+Define the $\gen, \rep$:
+\begin{itemize}
+\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \ext(y; x)$,  and output $(r, p)$.
+\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \ext(y; x)$. 
+\end{itemize}
+Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
+\end{lemma}
+\begin{proof}
+Result of extractibility of conditional HILL entropy~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}.\bnote{I don't think you need this $\epsilon_{ent}$ should be able to just use average case extractor directly}
+\end{proof}
+
+\subsection{Coding Theory}
+\label{sec:coding theory}
+We introduce some notions from the field of binary error correcting codes.
+Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but no bit flips from $1\not\rightarrow 0$.
+\begin{definition}
+\label{def:hamming z channel}
+For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
+\end{definition}
+\textbf{Note:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may be exist for these errors.
+
+\begin{definition}
+Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon)$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon$.
+\end{definition}
+
+We need one special property of the code, namely that each output bit is set $1$ with probability $1/2$.
+
+\begin{definition}
+A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
+\end{definition}
+All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
+This is true as long as $C$ contains no constant bits.
+Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
+For the remainder of this work when we say a code, we assume there are no constant bits.
+
+\begin{lemma}
+Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
+\end{lemma}
+\begin{proof}
+Suppose there is some $i$ that is not equiprobable.
+Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
+First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
+First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
+Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
+Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
+This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
+Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
+This is a contradiction and completes the proof.
+\end{proof}
 
@@
 We will provide the first construction where $gap$ is negative.
-We first focus on deriving a single key bit in this setting as this is already nontrivial.
 
-\subsection{Single-Bit Construction}
+\subsection{First $gap<0$ construction}
 \begin{construction}
-
+\label{cons:first construction}
 Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.
 Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.
-Let $t$ be the desired error-tolerance and let $C$ be a binary $(\ell, k, t)$-error-correcting code.
-Let $\ext : \zo^n\times \zo^* \rightarrow \zo$ be a $(x, x, x, x)$-extractor.
+Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be an output equiprobable $(\neigh_t, \epsilon_{code})$-error-correcting code.
+Let $\ext : \zo^n\times \zo^* \rightarrow \zo^r$ be a $(\tilde{m}, \epsilon_{ext})$-extractor where $\tilde{m}= XXX$.
 \bnote{fill this in}
@@
 \item For $i=1,..., \ell$:
-\subitem If $c_i = 1$: $p_i = \mathcal{O}(C(w_i))$.
-\subitem If $c_i = 0$: Sample $r_i \leftarrow U_n$.  \\
-\,
-Let $p_i = \mathcal{O}(C(r_i))$.
+\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
+\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
+\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
 \item Let $r = \ext(c, seed)$.
@@
 \begin{itemize}
-\item Assuming a roughly balanced code $C$~(where on average, half of the bits of a codeword are 0 and half are 1), in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
+\item If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
 As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
-\item There are two possible reasons for a bit of $c_i'$ to be $0$.
-Because the true value was $0$~(there is little chance of $0$ being incorrectly decoded as $1$ assuming $w_i'$ is formed independently of the sketch) and because $w_i \neq w_i'$.
-However if a bit of $c_i'$ is $1$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
-Thus, instead of using a code suited for a binary symmetric channel, a code for the $Z$ channel may be used.
-\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(see~\cite[Section 3.3]{fuller2013computational} for discussion).
+\item There are two possible reasons for a bit of $c_i'$ to be $1$.
+Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.
+However if a bit of $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
+This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
+\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(\defref{def:comp fuzzy cond}).
 \end{itemize}
 
+\subsection{Security of Construction}
 Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.
@@
 \begin{lemma}
-For each $c_j$ the adversary knowledge is negligible conditioned on their view.
+\label{lem:super log insist by equal queries}
+Let $W$ and $U$ be two distributions of super-logarithmic entropy.
+Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
 \end{lemma}
+\begin{proof}
+It suffices to show that with the probability of all responses being $0$ is overwhelming.
+Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
+\bnote{Finish this proof}
+\end{proof}
 
-\section{Supported Sources}
+\begin{lemma}
+\label{lem:code bits statistically indist}
+Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
+Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
+\end{lemma}
+\begin{proof}
+\bnote{Do this}
+\end{proof}
+We can extend this lemma to the entire codeword $C$:
+\begin{lemma}
+For all $c_1, c_2 \in C$ we have the following: 
+\[
+\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
+\]
+\end{lemma}
+\begin{lemma}
+If $C$ is output then, for all $i$, $\Hav(C_i |View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)}))\geq 1 - \ngl(n)$.
+\end{lemma}
+\begin{proof}
+Since $C$ is output equiprobable we know that for each $i$, $\Pr[C_i =1 ] = 1/2$.
+Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
+For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
+\begin{align*}
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C_i =b | view ] &\leq 1/2 + \ngl(n)\\
+\end{align*}
+If this was not true~(that is in expectation, there was some $b$ that was likely with probability greater than $1/2+1/\poly(n)$), there there would exist an unbounded adversary outputting that $b$, contradicting \lemref{lem:code bits statistically indist}).
+Taking the negative log of each side one has:
+\begin{align*}
+\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
+ &=\\-\log \left(\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\max_{b\in\{0,1\}}\Pr[C_i =b | view ]  \right) &\geq -\log (1/2 + \ngl(n))\\
+&\geq -\log(\frac{1}{2} + \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+2}{2n^{w}}\right)\\
+%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
+&=1-\left(\log (1+\frac{2}{n^e}) \right)\\
+&=1-\frac{1}{\ln 2}\left(\ln (1+\frac{2}{n^e}) \right)\\
+&= 1- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{2}{n^e})^i\right) \\
+&\geq 1 - \frac{1}{\ln 2} \frac{2}{n^e} = 1-\ngl(n)
+\end{align*}
+Here the second to last line is derived using the Taylor expansion for $\ln(1+x)$ and the last line is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive.
+\end{proof}
+By similar reasoning we can extend this lemma to the entire codeword:
+\begin{lemma}
+If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
+\end{lemma}
+%\begin{lemma}
+%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
+%\end{lemma}
+\begin{corollary}
+\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor.
+\end{corollary}
+\begin{proof}
+Result of security of point obfuscation and \lemref{lem:cond and ext}.
+\end{proof}
+
+\subsection{Correctness of \consref{cons:first construction}}
+Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
+However, we start by justifying our use of unidirectional codes.
+\begin{lemma}
+\label{lem:no 1 to 0 flips}
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/2^n = \ngl(n)$.
+\end{lemma}
+\begin{proof}
+\bnote{we need to come back to this if we use obfuscation with error}
+Recall that $c$ contains at most $\ell$ $1$s.
+Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$.
+Since the $r_i$ are chosen independently, one has,
+\begin{align*}
+\Pr[\text{no $1\rightarrow 0$ flips}] &\geq 1-\Pr[\text{some }r_i = w_i']\\
+&\geq 1-\ell \frac{1}{2^n} = 1-\frac{\poly(n)}{2^n} = \ngl(n)
+\end{align*}
+\end{proof}
+\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
+We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
+Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
+We break the indices of $c = c_1,..., c_\ell$ into two components those where $c_i=1$ and those $c_i = 0$.
+Denote these two components by $c_{I_1}$ and $c_{I_0}$.
+Our goal is to bound how many of the places where $w, w'$ are inserted into $c_{I_0}$.
+Indices $i$,  where $w_i \neq w_i'$ and $c_i = 1$ will be ``corrected'' as $w_i'$ yield $c_i' = 1$ with overwhelming probably~(see \lemref{lem:no 1 to 0 flips}).
+Since $w_{err}$ be set of indices where $w, w'$ differ then for all $j\in w_{err}, \Pr[j\in c_{I_0}] = 1/2$.
+This is a binomial distribution with $p=1/2$ and $n=t$.
+Denote by $X =|\{j | w_j \neq w_j' \wedge j\in c_{I_1}|$.
+Thus, $\expe[X] = t/2$.
+Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
+\begin{align*}
+\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
+\end{align*}
+This leads us to the following lemma:
+\begin{lemma}
+\label{lem:correctness holds}
+If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
+\end{lemma}
+\bnote{This analysis is done assuming that the two sets are the same size.
+Need to worry about variation in the number of $1$s and $0$s in $c$.
+Need to show that for most codes (linear?) the variance in Hamming weight is small.}
+\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
+
+\subsection{Supported Sources}
+\label{sec:supported sources}
+\bnote{need to complete this section and redo the proof in 3.2 with this type of source.}
 We now describe a set of high entropy sources appropriate for our construction.
@@
 \begin{definition}
+\label{def:block guessable}
 Let $\mathcal{O}_{w_1,..., w_k}$ be an oracle that return $\mathcal{O}_{w_1,..., w_k}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
@@
 \end{proof}
+
+\subsection{Discussion}
+Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
+Correction occurs in a small number of dimensions that are allowed to vary completely.
+As described in \secref{sec:supported sources}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
+
+To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet of size $2^n$.  This means that
+\begin{align*}
+\log |B_t(\cdot)| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
+&> \log {\ell \choose t} (2^n-1)^t\\
+&=\Omega(tn) + \log {\ell\choose t}
+% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
+\end{align*}
+We now ask how much entropy is necessary for security?
+The first presented type of source was where each block was independent and had super-logarithmic min-entropy.
+This means that $\Hoo(W) \approx \ell \omega(\log n)$.
+Thus in the setting where $t = \omega(\ell)$ we obtain that
+\[
+gap = \Hoo(W) - \log |B_t(\cdot)| < \ell \omega(\log n) -\left( \omega(\ell n) + \log {\ell \choose t}\right)< 0. 
+\]
+This \consref{cons:first construction} is the first fuzzy extractor with a negative $gap$.\footnote{We can make gap smaller by recalling that note every block must contribute fresh entropy.
+If each block is derived from a single source with super-logarithmic entropy then the starting entropy need only be $\omega(\log n)$.}
+
+\textbf{Note:} If $t = o(\ell)$ then the value of $gap$ is not clear, there are some $\ell$ for which it will be negative.
+However in the setting where $n>>\ell$ and a constant number of errors are being corrected $gap$ may be positive.
+However, we extract from at most $\ell$ bits and thus need $\ell$ to be large enough for reasonable application security.
+Setting $ \ell , t, n$ all of roughly the same size provides a natural balance of parameters.
+
+\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
+The first is that Hamming distance is over an alphabet of exponential size, which precludes use is several major settings.
+The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
+Lastly, we obtain only a single bit from each block of $W_i$, in settings where entropy is at a premium this seems wasteful.
+\section{Second construction}
 \bibliographystyle{alpha}

### 2014-01-09 constantRate/ConstCompFuzzExt.tex
Outline of proof (still need to fill in a lot)

@@
 For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
+Our proof for independent and high entropy blocks is more complicated than necessary, but the structure will hold for the more complicated setting.
+The outline of the proof follows:
+
+\begin{itemize}
+\item Show that conditioned on the adversaries view there is a large set of blocks, $\mathcal{I}$, that still have a super logarithmic entropy.
+\item Show that conditioned on the values of all indices $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$.
+\item For all indices in $\mathcal{I}$, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
+\item Any two codewords, $c_1, c_2$ differing in only these positions are statistically close given the adversaries view.
+\item The set of codewords differing in these positions form a distribution with conditional entropy.  This is sufficient to show
+\end{itemize}
 

### 2014-01-10 trunk/constantRate/ConstCompFuzzExt.tex
Outline of proof (still need to fill in a lot)

@@
 \begin{corollary}
-\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor.
+\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor when $W = W_1,..., W_n$ all $W_i$ are independent and $\Hoo(W_i) = \omega(\log n)$.
 \end{corollary}
@@
 \label{lem:no 1 to 0 flips}
-The probability of a single $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $\ngl(n) \leq \ell/2^n$.
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/2^n = \ngl(n)$.
 \end{lemma}
@@
 \end{lemma}
+\bnote{This analysis is done assuming that the two sets are the same size.
+Need to worry about variation in the number of $1$s and $0$s in $c$.
+Need to show that for most codes (linear?) the variance in Hamming weight is small.}
 \textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
 
-\section{Supported Sources}
+\subsection{Supported Sources}
+\label{sec:supported sources}
+\bnote{need to complete this section and redo the proof in 3.2 with this type of source.}
 We now describe a set of high entropy sources appropriate for our construction.

### 2014-01-10 trunk/constantRate/ConstCompFuzzExt.tex
change composition to comp fuzzy cond and comp extractor.  Worked on intro and abstract

@@
 \newcommand{\ext}{\ensuremath{\mathtt{ext}}}
+\newcommand{\cext}{\ensuremath{\mathtt{cext}}}
 \newcommand{\rext}{\ensuremath{\mathtt{rext}}}
@@
 
-\title{Constant Error Rate Computational Fuzzy Extractors}
-\author{Some people}
+\title{Constant Error Rate Computational Fuzzy Extractors\thanks{The work of B.
+Fuller is sponsored by Assistant Secretary of Defense for Research \& Engineering under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}}
+\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin}
+
 \begin{document}
@@
 
-%\begin{abstract} 
-%We make computational fuzzy extractors better.
-%\end{abstract}
+\begin{abstract} 
+Fuzzy extractors derive strong keys from noisy sources.
+Traditionally, their security is defined information-theoretically.
+Fuzzy extractors have strong bounds on the length of the derived key.
+In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.
+For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation unachievable.
+
+The work of Fuller, Meng, and Reyzin (Asiacrypt 2013), posited these bounds could be overcome by only providing security against computationally-bounded adversaries.
+%They provide a construction of a computational fuzzy extractor that corrects a small number of errors without any loss in key length.
+They show the feasibility of constructing a computational fuzzy extractor that does not suffer from the information-theoretic bounds.
+%Unfortunately, their construction is limited to very high entropy distributions and does not significantly beat information-theoretic bounds.
+In addition, we significantly improve on the allowable error rate and the required entropy rate of each block.
+In particular we construct the following:
+In this work, we provide the first construction of a fuzzy extractor for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.
+
+\textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.
+Let $W = W_1, ..., W_\ell$ be a source composed of blocks over a large alphabet.
+We flip a coin $c_i$ for each block and either obfuscate the block or a random point.
+When a close value $w'$ is input, we can recover most of the coins $c_i$.
+Error-tolerance is achieved by choosing $c = c_1,..., c_\ell$ from an error-correcting code.
+Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).
+Our construction is secure as long as a large number of dimensions are unpredictable given equality queries on individual blocks.
+Our construction provides the following novel features:
+\begin{itemize}
+\item The source entropy is smaller than the log of the number of correctable error patterns.  
+\item Constant error tolerance rate.
+Previous constructions of computational fuzzy extractors corrected a logarithmic fraction of errors.
+(Information-theoretic constructions support a constant fraction of errors but are subject to bounds described above.)
+\item Security for a large class of distributions.
+The main requirement for security is that most blocks have a super-logarithmic amount of entropy.
+Previous computational fuzzy extractors required the source to be essentially uniform.
+\end{itemize}
+\end{abstract}
 
 \section{Introduction}\label{sec:introduction}
+Authentication is a crucial component of system security.
+Reliable key derivation significantly simplifies authentication.
+However many sources with entropy are noisy, providing close values upon subsequent readings~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).
+
 Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} derive stable keys from noisy data.
@@
 
-For a fixed length key, there are two main parameters: the desired error tolerance and the required entropy of the source.
-In the information-theoretic setting these two parameter are at odds.
-Any increase error-tolerance requires a similar increase to the entropy of the source.
+In fuzzy extractors, there are two competing parameters, security and error-tolerance.
+The key should be uniform to an observer but a close  $w_1$ should map to the same key.
+In the information-theoretic realm these two parameters are indeed at odds.
+Let $t$ be the desired error-tolerance and let $|B_t(\cdot)|$ be the size of a Hamming ball of radius $t$.
+Roughly, the length of the key $|r| < \Hoo(W) - \log |B_t(\cdot)|$~(see~\cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions, here we use the sphere packing bound as one bound for the best constructible code).
+For the remainder of this paper, we denote this quantity by $gap = \Hoo(W) - \log |B_t(\cdot)|$.
+
 However, this does not need to be the case in the computational setting.
-The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The only difference between a computational fuzzy extractor and a fuzzy extractor is the key is pseudorandom instead of statistically random.
-}  With computational security, an error tolerance \emph{larger} than the starting entropy may be possible.
-We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.
-In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within any error-tolerance region.
-This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}
+Fuller, Meng, and Reyzin defined computational fuzzy extractors which produce pseudorandom instead of truly random keys~\cite{fuller2013computational}.
+They posit it may be possible to build a computational fuzzy extractor when $gap$ is small or negative.
+We resolve this question and construct a computational fuzzy extractor when $gap<0$.
+This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.
+A necessary condition for security is that a negligible portion of the probability distribution lies within any Hamming ball of radius $t$.
+We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).
 
-Our construction is based on obfuscation.
+In the information-theoretic setting the goal of a fuzzy extractor is to build a key as long as possible.  
+In the computational setting, a key may be expanded once it is long enough to run a pseudorandom generator.
+Thus, our focus is building a reasonable length key for a class of distributions where nothing is possible information-theoretically.
+
+\textbf{Overview of Construction:} The negative results of Fuller, Meng, and Reyzin~\cite{fuller2013computational} show that building a computational fuzzy extractor using a computational secure sketch and a privacy amplification element is unlikely to be fruitful.
+They present two alternatives combining the information-reconciliation and privacy amplification components~(their approach) and using a computational version of a fuzzy conductor~(fuzzy conductors are defined by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+We follow the second approach.
+
+Our construction~(\consref{cons:first construction}) is based on obfuscation.
 While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we use the obfuscation of point functions.
@@
 
-\textbf{Overview of Construction:}  Consider a source $w = w_1,..., w_\ell$ that is split into blocks.
-We would like to construct tolerate Hamming errors for individual blocks.
-The main idea is for each block, $i$: either the $w_i$ is obfuscated or a random point $r_i$ is obfuscated~(this idea is similar to the construction of digital lockers from point obfuscation).
-Then with a close value $w'$ the recovery value knows where random values were obfuscated and where $w_i$ was obfuscated.
-To tolerate errors, the choice of obfuscating $w_i$ or a random point is made using bits of an error correcting code.
+Consider a source $w = w_1,..., w_\ell$ that is split into blocks~(over some large alphabet).
+We would like to tolerate Hamming errors for individual blocks.
+The main idea is for each block $i$ we flip a coin $c_i$ and either obfuscate $w_i$ or a random point $r_i$~(this is similar to the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}).
+With a close value $w'$ the \rec can determine where random values were obfuscated and where $w_i$ was obfuscated~(with some errors).
+Most of the bits $c_i$ are recoverable.
+To tolerate errors we choose the coins $c$ from an appropriate error-correcting code.
+Then, $c$ forms a distribution of high entropy that can be extracted~(either information-theoretically~\cite{nisan1993randomness} or computationally~\cite{DBLP:conf/crypto/Krawczyk10}).
+Note it is hard to recover $w$ from the value $c$.
+As discussed in~\cite[Section 3.3]{fuller2013computational} this is necessary to overcome the information-theoretic lower bounds.
+
+Our construction provides several advantages over previous constructions of computational fuzzy extractors:
+\begin{itemize}
+\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions\footnote{There are artificial examples where no loss in necessary in a fuzzy extractor.
+If $W$ consists of points from an error-correcting code of distance $2t+1$, then no public information is necessary and $gap$ may be negative.
+This violates the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors usually proceeds saying the residual entropy is at least $\Hoo(W)$ less the number of bits needed for error correcting.
+For an arbitrary distribution, this is at least $\log |B_t(\cdot)|$.
+The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions.}.
+\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\log \ell/ \ell)$)
+\item The first computational fuzzy extractor where block are not required to be uniformly distributed.
+Our construction simply requires a large number of blocks that are unguessable given equality queries.
+This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
+\end{itemize}
 
@@
 Unfortunately, this is not the case.
-Since each block is individual obfuscated, equality of individual blocks is learned~(for sources where not all blocks have high entropy).
-This precludes virtual black-box~(VBB) security where no partial information about the input may be learned.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.
+Each block is individual obfuscated, an adversary may ask equality on individual blocks.
+If not all blocks have high entropy this may allow an adversary to learn significant information about the source.
+Thus, our construction is not a virtual black box~(VBB) obfuscation~(where anything learnable by the circuit is simulatable using input/output behavior).
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation when $gap>>0$.
 Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.
 
-\textbf{Our Results:} Specifically this paper presents the following:
-\begin{itemize}
-\item The first computational fuzzy extractor that supports a constant fraction of errors.
-\item The first fuzzy extractor where the number of errors corrected is larger than the entropy of the starting distribution.
-\end{itemize}
-\bnote{More details here}
-
-\bnote{Provide an outline of the rest of the paper}
+\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.
+This means that each block much be drawn from a distribution with super-logarithmic entropy.
+This also means that our distance is computed over a large alphabet~(exponential) in the security parameter.
+Our construction is primarily applicable for burst error-models~\cite{gilbert1960capacity}.
+Constructing a computational fuzzy extractor with the above parameters and a small alphabet is an important open problem.
 
@@
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
+\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
 
@@
 Here we present relevant extractor definitions.
-We start with the standard notion of an average-case extractor.
-An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
-\begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon$.
-\end{definition}
 
@@
 
-Our main question is: for what type of sources can we build fuzzy extractors?
+The work of Fuller, Meng, and Reyzin~\cite{fuller2013computational} presents two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.
+We follow the second approach.
+%Our main question is: for what type of sources can we build fuzzy extractors?
 Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.
@@
 
-As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
+%As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
 As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch~\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}.
 Instead, we will use a computational fuzzy conductor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):
+We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
+\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
+\label{def:hill ent}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
+\end{definition}
 
+We now define the two primitives in this approach: a computational fuzzy conductor and a (computational)~randomness extractor.
+A computational fuzzy conductor is the computational analogue of a fuzzy conductor introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
 \begin{definition}
@@
 
+A computational extractor is the natural adaption of a randomness extractor to the computational setting.
+We use the average case version of the notion introduced by Krawczyk~\cite{krawczyk2010cryptographic}:
+%start with the standard notion of an average-case extractor.
+An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
+\begin{definition}
+Let $\chi_1$, $\chi_2$ be finite sets.
+A function $\cext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, s_{sec}, \epsilon)$-average-case extractor} if for all pairs
+of random variables $X, Y$ over $\chi_1, \chi_2$ such that
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{sec}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon$.
+\end{definition}
+
 Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor:
@@
 \label{lem:cond and ext}
-Let $\epsilon_{ent} >0$ be a parameter.
-Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.
-Let $\ext:\mathcal{M}_2\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.
-Define the $\gen, \rep$:
+Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.
+Let $\cext:\mathcal{M}_2\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, s_{ext}, \epsilon_{ext})$-average case computational extractor.
+Define $\gen, \rep$ as:
 \begin{itemize}
-\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \ext(y; x)$,  and output $(r, p)$.
-\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \ext(y; x)$. 
+\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \cext(y; x)$,  and output $(r, p)$.
+\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \cext(y; x)$. 
 \end{itemize}
-Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
+Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \max\{s_{cond} - |\cext|, s_{ext}\}$.
 \end{lemma}
 \begin{proof}
-Result of extractibility of conditional HILL entropy~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}.\bnote{I don't think you need this $\epsilon_{ent}$ should be able to just use average case extractor directly}
+It suffices to show if there is some distinguisher $D$ of size $s'$ where 
+\[\delta^D((\cext(W; X), U_d, P), (U_\kappa, U_d, P))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D'$ of size $s_{cond}$ where for all $Z$ where $\Hav(Z|P)\geq \tilde{m}$ such that
+ \[
+ \delta^{D'}((Y, P), (Z, P))\geq \epsilon_{cond}.
+ \]
+Let $D$ be such a distinguisher.  That is,
+\[
+\delta^D(\ext(X, U_d)\times U_d \times P, U_\kappa\times U_d\times P)> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D'$ as follows.
+On input $y, p$ sample $x\leftarrow U_d$, compute $r\leftarrow \cext(y, x)$ and output $D(r, x, p)$.
+Note that $|D'| \approx s' + |\cext| = s_{cond}$.
+Then we have the following:
+\begin{align*}
+\delta^{D'}((Y, P), (Z, P))&= \delta^D((\cext(Y, U_d), U_d, P), \cext(Z, U_d), U_d, P)\\
+&\geq \delta^D((\cext(Y, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^D((\cext(Z, U_d), U_d, P), (U_\kappa\times U_d \times P))\\
+&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
+\end{align*}
+Thus $D'$ distinguishes $Y$ from all $Z$ with sufficient conditional min-entropy.  This is a contradiction.
 \end{proof}
@@
 
-\appendix
-\section{Computational Entropy}
-HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
+%\appendix
+%\section{Computational Entropy}
+%HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
 It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
 
-\begin{definition}
-\label{def:hill ent}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
-\end{definition}
-
 \end{document}

### 2014-01-10 constantRate/ConstCompFuzzExt.tex
Revised intro

@@
 
-\title{Constant Error Rate Computational Fuzzy Extractors}
-\author{Some people}
+\title{Constant Error Tolerance Computational Fuzzy Extractors\thanks{The work of B.
+Fuller is sponsored by Assistant Secretary of Defense for Research \& Engineering under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}}
+\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin}
+
 \begin{document}
@@
 
-%\begin{abstract} 
-%We make computational fuzzy extractors better.
-%\end{abstract}
+\begin{abstract} 
+Fuzzy extractors derive strong keys from noisy sources.
+The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly key distributed key.
+Traditionally, their security is defined information-theoretically.
+Fuzzy extractors have upper bounds on the length of the derived key~(Dodis et al., J.
+of Comp 2008).
+In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.
+For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as open problem.
+
+Fuller, Meng, and Reyzin (Asiacrypt 2013) hypothesize that these bounds can be overcome by only providing security against computationally-bounded adversaries.
+%They provide a construction of a computational fuzzy extractor that corrects a small number of errors without any loss in key length.
+%They show the feasibility of constructing a computational fuzzy extractor that does not suffer from the information-theoretic bounds.
+%Unfortunately, their construction is limited to very high entropy distributions and does not significantly beat information-theoretic bounds.
+In addition, we significantly improve on the allowable error rate and the required entropy rate of each block.
+In particular we construct the following:
+In this work, we provide the first construction of a fuzzy extractor for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.
+
+\textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.
+Let $W = W_1, ..., W_\ell$ be a source distribution composed of blocks over a large alphabet, $Z$.
+To obfuscate a sample $w$ drawn from $W$.
+We flip a coin $c_i$ for each block and either obfuscate the block $w_i$ or a random point in $Z$.
+When a close reading $w'$ is given as input, we can recover most of the coins $c_i$.
+Error-tolerance is achieved by sampling $c = c_1,..., c_\ell$ from an error-correcting code.
+Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).
+Security holds as long as a large number of blocks $W_i$ of $W$  are unpredictable given equality queries on individual blocks.
+Our construction provides the following novel features:
+\begin{itemize}
+\item The source entropy is smaller than the log of the number of correctable error patterns.  
+\item Constant error tolerance rate.
+%Previous constructions of computational fuzzy extractors corrected a logarithmic fraction of errors.
+(Information-theoretic constructions support a constant fraction of errors but are subject to bounds described above.)
+\item Security for a large and meaningful class of distributions.
+%The main requirement for security is that most blocks have a super-logarithmic amount of entropy.
+Previous computational fuzzy extractors required the source to be essentially uniform.
+\end{itemize}
+\end{abstract}
 
 \section{Introduction}\label{sec:introduction}
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} derive stable keys from noisy data.
-They are composed of two algorithms: \gen takes a source value $w_0$, and produces a key $r$ and a public value $p$, and \rep which takes a nearby value $w_1$ and $p$ producing the original key $r$.
-Intuitively, they are two functions: information reconciliation~(to provide the same value with \emph{noisy} readings) and key derivation or privacy amplification~(to transform an entropic source into a uniform key).
-Traditionally, these two functions were performed by two separate primitives: a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} and a randomness extractor~\cite{nisan1993randomness}.
+Reliable key derivation is a cornerstone of authentication.
+However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).
+To use noisy physical sources in applications, two problems must be addressed.
+The first is ensuring the same value is obtained from every reading of the source.
+This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).
+The second is converting a source with entropy to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).
+Both of these problems have interactive and non-interactive versions.
+For a single user~(trying to produce the same key from multiple readings of a physical source) the non-interactive versions are appropriate.
+We focus on this setting.
+%If both of these tasks are achieved a noisy physical source can be used like a uniformly random private key.
 
-For a fixed length key, there are two main parameters: the desired error tolerance and the required entropy of the source.
-In the information-theoretic setting these two parameter are at odds.
-Any increase error-tolerance requires a similar increase to the entropy of the source.
+Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} perform both tasks non-interactively.
+They consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public value $p$.
+The second algorithm \rep takes this public value $p$ and a close $w'$ to reproduce the original key $r$.
+Traditionally, a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} performs information-reconciliation and a randomness extractor~\cite{nisan1993randomness} performs privacy amplification.
+
+Unfortunately, fuzzy extractors have not yielded key derivation for all noisy sources.  
+This is because there is tension between security and error-tolerance.
+The key should be uniform to an observer but nearby $w'$ should map to the same key.
+By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.
+In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.
+This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+The length of $r$ is dictated by size of the best code that corrects $t$ errors.
+Error-correcting codes are well studied and we have tight bounds on this quantity.
+% how many codewords may be in a code that corrects $t$ errors.
+
+ Specifically, we consider the Hamming metric.
+For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.
+As we discuss later, it is possible to avoid these losses if the fuzzy extractor has additional knowledge about the distribution.} and logarithm of the number of error patterns to be corrected.
+For the remainder of this paper we denote this quantity by $gap$.
+This represents a real problem as important biometrics~(such as irises~\cite{daugman2004}) have $gap <0$ and information-theoretic fuzzy extractors provide no security.
+
+ %let $|B_t|$ be the number of points within distance $t$.
+The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
+For the remainder of this paper, we denote this quantity by $gap = \Hoo(W) - \log |B_t|$.
+
 However, this does not need to be the case in the computational setting.
-The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The only difference between a computational fuzzy extractor and a fuzzy extractor is the key is pseudorandom instead of statistically random.
-}  With computational security, an error tolerance \emph{larger} than the starting entropy may be possible.
-We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.
-In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within any error-tolerance region.
-This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}
+Fuller, Meng, and Reyzin define computational fuzzy extractors.
+Computational fuzzy extractors produce pseudorandom instead of truly random keys~\cite{fuller2013computational}.
+They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.
+We resolve this question and construct a computational fuzzy extractor when $gap<0$.
+This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.
+A necessary condition for security is that a negligible portion of the probability distribution lies within any Hamming ball of radius $t$.
+We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).
 
-Our construction is based on obfuscation.
-While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we use the obfuscation of point functions.
-This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
+The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.  
+In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
+Thus, our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
 
-\textbf{Overview of Construction:}  Consider a source $w = w_1,..., w_\ell$ that is split into blocks.
-We would like to construct tolerate Hamming errors for individual blocks.
-The main idea is for each block, $i$: either the $w_i$ is obfuscated or a random point $r_i$ is obfuscated~(this idea is similar to the construction of digital lockers from point obfuscation).
-Then with a close value $w'$ the recovery value knows where random values were obfuscated and where $w_i$ was obfuscated.
-To tolerate errors, the choice of obfuscating $w_i$ or a random point is made using bits of an error correcting code.
+\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.
+Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or use a computational version of a fuzzy conductor~(Kanukurthi and Reyzin~\cite{KanukurthiR09} define fuzzy conductors).
+Here, we follow the second approach.
 
-\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).
+Our construction~(\consref{cons:first construction}) is based on obfuscation of point programs.
+A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
+A program is obfuscated if nothing is learnable from the program other than its input and output behavior.
+For a point program, this means hiding all partial information about the point $w$.
+Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
+
+Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).
+We would like to tolerate errors in $t$ individual blocks.
+For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
+With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
+For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.
+Thus, most bits $c_i$ are recoverable.
+To tolerate errors we choose the coins $c$ from an error-correcting code.
+Then, $c$ forms an extractible distribution of high entropy.
+This extraction may be either information-theoretic~\cite{nisan1993randomness} or computation~\cite{DBLP:conf/crypto/Krawczyk10}.
+Note, it is hard to recover $w$ from the value $c$.
+This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.
+
+This construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  
+Our construction provides several advantages over previous constructions of computational fuzzy extractors:
+\begin{itemize}
+\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss in necessary in a fuzzy extractor.
+If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.
+This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.
+For an arbitrary distribution, this is at least $\log |B_t|$.
+The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions~(see \defref{def:block guessable}).}
+\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
+\item The first computational fuzzy extractor where block are not required to be uniformly distributed.
+Our construction simply requires a large number of blocks that are unguessable given equality queries.
+This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
+\end{itemize}
+
+\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.
+This means that blocks much be drawn from distributions with super-logarithmic entropy.
+Furthermore, our distance is Hamming distance over a large alphabet~(exponential in the security parameter).
+Our construction is applicable for burst errors~\cite{gilbert1960capacity}\bnote{explain?}.
+Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
+
+\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a stronger object than a computational fuzzy extractor).
 Unfortunately, this is not the case.
-Since each block is individual obfuscated, equality of individual blocks is learned~(for sources where not all blocks have high entropy).
-This precludes virtual black-box~(VBB) security where no partial information about the input may be learned.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.
+Each block is individually obfuscated, so an adversary may ask equality queries on individual blocks.
+If not all blocks have high entropy an adversary may learn significant information about the source.
+Thus, our construction is not a virtual black box~(VBB) obfuscation~(where anything learnable by the circuit is simulatable using input/output behavior).
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$.
 Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.
-
-\textbf{Our Results:} Specifically this paper presents the following:
-\begin{itemize}
-\item The first computational fuzzy extractor that supports a constant fraction of errors.
-\item The first fuzzy extractor where the number of errors corrected is larger than the entropy of the starting distribution.
-\end{itemize}
-\bnote{More details here}
-
-\bnote{Provide an outline of the rest of the paper}
 
@@
 \label{sec:preliminaries}
-For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
+For a random variable $X = X_1,..., X_\ell$ as the concatenation of $X_i$ where each $X_i$ is over some alphabet $\mathcal{Z}$.
+For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
@@
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
-If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
+If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
 For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
-For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
+For the Hamming metric, $|B_t| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
+Unless otherwise noted logarithms are base $2$.
+%\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
 
@@
 
-\subsection{Randomness Extractors and Computational Fuzzy Extractors}
+\subsection{Coding Theory}
+\label{sec:coding theory}
+We introduce some notions from the field of binary error correcting codes.
+Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel\bnote{cite} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.
+\begin{definition}
+\label{def:hamming z channel}
+For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
+\end{definition}
+\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may exist for this type of error.
+The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).
+
+\begin{definition}
+Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon)$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon$.
+\end{definition}
+
+We need one special property of the code, namely that each output bit is set to $1$ with probability $1/2$.
+
+\begin{definition}
+A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
+\end{definition}
+All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
+This is true as long as $C$ contains no constant bits.
+Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
+For the remainder of this work when we say a code, we assume there are no constant bits.
+
+\begin{lemma}
+\label{lem:linear codes independent}
+Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
+\end{lemma}
+Proof in \apref{sec:proof of linear indep}.
+
+\subsection{Obfuscation}
+Our construction uses virtual black-box obfuscation of point functions.  This is the following family of functions:
+\[
+I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
+\]
+Here we present the virtual black-box definition of obfuscation.
+See \secref{sec:obfuscation} for a more detailed introduction to obfuscation.
+This definition is known to be achievable for point functions under various assumptions~\cite{canetti1997towards, wee2005obfuscating}.
+We also need the obfuscation to be $\ell$-composable~(\defref{def:obf comp}).
+
+We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
+
+\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  
+\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.
+A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
+\begin{enumerate}
+\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
+\[
+\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
+\]
+where the probability is taken over the randomness $r$.
+\emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.
+Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
+\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
+\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
+and for all binary predicates $\pi$, 
+\[
+|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
+\]
+where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
+Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
+\end{enumerate}
+\end{definition}
+
+\section{Computational Fuzzy Extractors}
 \label{sec:fuzzy extractors}
-
-Here we present relevant extractor definitions.
-We start with the standard notion of an average-case extractor.
-An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
-\begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon$.
-\end{definition}
 
@@
 al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
-The definition of computational fuzzy extractors allows for a small probability of error, as described in~\cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
+The definition of computational fuzzy extractors allows for a small probability of error.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
-
 %\begin{definition}
@@
 
-We now present the definition of a computational fuzzy extractor~(from~\cite{fuller2013computational}):
-
 %A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. 
@@
 
-\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
+\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
+\label{def:comp fuzzy extractor}
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
@@
 \end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.  
-Note that in the above definition of fuzzy extractors, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
-For notational convenience, we the definition of computational fuzzy extractors specifies a general class of sources for which the fuzzy extractor is designed to work, rather than the class of sources that consists of all sources of a given min-entropy $m$~(of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
+In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
+The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor is designed to work rather than the family of all sources of a given min-entropy $m$.
+With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary.
 
-Our main question is: for what type of sources can we build fuzzy extractors?
+The work of Fuller, Meng, and Reyzin~\cite{fuller2013computational} presents two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.
+We follow the second approach.
+%Our main question is: for what type of sources can we build fuzzy extractors?
 Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.
-The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t(\cdot)$.
+The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t$.
 When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.
@@
 
-As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
+%As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
 As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch~\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}.
 Instead, we will use a computational fuzzy conductor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):
+We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
+\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
+\label{def:hill ent}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
+\end{definition}
 
+We now define the two primitives for this approach: a computational fuzzy conductor and a (computational)~randomness extractor.
+A computational fuzzy conductor is the computational analogue of a fuzzy conductor introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
 \begin{definition}
@@
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' (\gen') and ``reproduce'' (\rep') is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
 \begin{itemize}
@@
 
-Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor:
+A computational extractor is the natural adaption of a randomness extractor to the computational setting.  We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
+%start with the standard notion of an average-case extractor.
+An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
+\begin{definition}
+Let $\chi$ be a finite set.
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, s_{sec}, \epsilon)$-average-case computational extractor} if for all pairs
+of random variables $X, Y$ over $\zo^\ell, \chi$ such that
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{sec}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon$.
+\end{definition}
+
+Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor~(proof in \secref{sec:cond and cext}):
 
 \begin{lemma}
-\label{lem:cond and ext}
-Let $\epsilon_{ent} >0$ be a parameter.
-Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.
-Let $\ext:\mathcal{M}_2\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.
-Define the $\gen, \rep$:
+\label{lem:cond and cext}
+Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
+Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, s_{ext}, \epsilon_{ext})$-average case computational extractor.
+Define $\gen, \rep$ as:
 \begin{itemize}
-\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \ext(y; x)$,  and output $(r, p)$.
-\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \ext(y; x)$. 
+\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \cext(y; x)$,  and output $(r, p)$.
+\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \cext(y; x)$. 
 \end{itemize}
-Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
+Then $\gen, \rep$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \max\{s_{cond} - |\cext| -d, s_{ext}\}$.
 \end{lemma}
-\begin{proof}
-Result of extractibility of conditional HILL entropy~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}.\bnote{I don't think you need this $\epsilon_{ent}$ should be able to just use average case extractor directly}
-\end{proof}
-
-\subsection{Coding Theory}
-\label{sec:coding theory}
-We introduce some notions from the field of binary error correcting codes.
-Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but no bit flips from $1\not\rightarrow 0$.
-\begin{definition}
-\label{def:hamming z channel}
-For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
-\end{definition}
-\textbf{Note:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may be exist for these errors.
-
-\begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon)$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon$.
-\end{definition}
-
-We need one special property of the code, namely that each output bit is set $1$ with probability $1/2$.
-
-\begin{definition}
-A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
-\end{definition}
-All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
-This is true as long as $C$ contains no constant bits.
-Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
-For the remainder of this work when we say a code, we assume there are no constant bits.
-
-\begin{lemma}
-Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
-\end{lemma}
-\begin{proof}
-Suppose there is some $i$ that is not equiprobable.
-Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
-First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
-First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
-Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
-Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
-This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
-Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
-This is a contradiction and completes the proof.
-\end{proof}
-
-\subsection{Obfuscation}
-The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
-This notion is known to be impossible in a black-box way for all polynomial time programs.
-Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
-Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
-
-We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
-
-\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  Let $\mathcal{C}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
-\begin{enumerate}
-\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
-\[
-\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
-\]
-where the probability is taken over the randomness $r$.
-\emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability ver the random coin tosses $r$.
-Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
-\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
-\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
-and for all binary predicates $\pi$, 
-\[
-|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
-\]
-where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
-Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
-\end{enumerate}
-\end{definition}
-
-In this work, we will use obfuscation of point-programs, 
-\[
-I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
-\]
-
-We provide the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
-\begin{enumerate}  
-\item Input: string $w\in \zo^n$.
-\item Choose a generator $g\overset{\$}\leftarrow G$
-\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
-\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
-\end{enumerate}
-\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
-Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
-Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
-For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
-\end{assumption}
-\begin{theorem}~\cite{canetti1997towards}
-The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
-\end{theorem}
-
-As described above there exist other constructions of point function obfuscates under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
-
-Lastly, we will need the notion of composable obfuscation.
-
-\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}].
-A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
-That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
-\[
-|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
-\]
-where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
-\end{definition}
 
@@
 The goal is to derive strong keys from noisy sources.
-As discussed in the introduction, the important parameter is the difference between the total entropy and the number of errors being corrected.
-We call this value the entropy gap or $gap= \Hoo(W) - \log|B_t(\cdot)|$.
-The results of Dodis et al.~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08} show that gap is an upper bounded for the length of the derived key.
-
-If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
+As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
+In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.
+Thus, we do not providing enough security when $gap<0$ is small.
+Furthermore, we build a computational fuzzy conductor, noting that it can be converted to a computational fuzzy extractor using \lemref{lem:cond and cext}.%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
 Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.
@@
 Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be an output equiprobable $(\neigh_t, \epsilon_{code})$-error-correcting code.
-Let $\ext : \zo^n\times \zo^* \rightarrow \zo^r$ be a $(\tilde{m}, \epsilon_{ext})$-extractor where $\tilde{m}= XXX$.
-\bnote{fill this in}
 We describe $\gen, \rep$ as follows:
@@
 \subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
-\item Let $r = \ext(c, seed)$.
-\item Output $(r, p)$.
+\item Output $(c, p)$.
 \end{enumerate}
@@
 \item Set $c = \decode$.
-\item Output $r  = \ext (c', seed)$.
+\item Output $c$.
 \end{enumerate}
@@
 \begin{corollary}
-\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor.
+\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor when $W = W_1,..., W_n$ all $W_i$ are independent and $\Hoo(W_i) = \omega(\log n)$.
 \end{corollary}
 \begin{proof}
-Result of security of point obfuscation and \lemref{lem:cond and ext}.
+Result of security of point obfuscation and \lemref{lem:cond and cext}.
 \end{proof}
@@
 \subsection{Correctness of \consref{cons:first construction}}
-Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
+We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
+%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
 However, we start by justifying our use of unidirectional codes.
@@
 \end{proof}
-\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
-We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
+
+We now consider the number of possible $0\rightarrow 1$ bit flips in $c$.
+A $0\rightarrow 1$ flip on index $i$ occurs when two conditions are met $w_i\neq w_i'$ and $c_i = 0$.
+Since the first conditioned is only fulfilled at most $t$ times, we have the following lemma:
+
+\begin{lemma}
+Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
+\[
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n}.
+\]
+That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
+\end{lemma}
+
+%\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
+%We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
 Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
@@
 Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
-\begin{align*}
-\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
-\end{align*}
-This leads us to the following lemma:
-\begin{lemma}
-\label{lem:correctness holds}
-If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
-\end{lemma}
-\bnote{This analysis is done assuming that the two sets are the same size.
+%\begin{align*}
+%\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
+%\end{align*}
+%This leads us to the following lemma:
+%\begin{lemma}
+%\label{lem:correctness holds}
+%If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
+%\end{lemma}
+%\bnote{This analysis is done assuming that the two sets are the same size.
 Need to worry about variation in the number of $1$s and $0$s in $c$.
 Need to show that for most codes (linear?) the variance in Hamming weight is small.}
-\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
+%\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
 
@@
 We now describe a set of high entropy sources appropriate for our construction.
+In the proof of security for these sources follows the outline presented \secref{XXXXX}.
 After giving the description of the distribution, we give examples of distributions that fit in this class and provide additional characterizations.
@@
 Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
-Correction occurs in a small number of dimensions that are allowed to vary completely.
+Correction occurs for a small number of dimensions that are allowed to vary completely.
 As described in \secref{sec:supported sources}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
@@
 \begin{align*}
-\log |B_t(\cdot)| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
+\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
 &> \log {\ell \choose t} (2^n-1)^t\\
@@
 \[
-gap = \Hoo(W) - \log |B_t(\cdot)| < \ell \omega(\log n) -\left( \omega(\ell n) + \log {\ell \choose t}\right)< 0. 
+gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \omega(\ell n) + \log {\ell \choose t}\right)< 0. 
 \]
@@
 Lastly, we obtain only a single bit from each block of $W_i$, in settings where entropy is at a premium this seems wasteful.
-\section{Second construction}
 \bibliographystyle{alpha}
@@
 \appendix
-\section{Computational Entropy}
-HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
-It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+\section{Obfuscation}
+\label{sec:obfuscation}
+The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
+This notion is known to be impossible in a black-box way for all polynomial time programs.
+Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
+Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
+The definition of virtual black box obfuscation is presented in \defref{def:obf}.
 
-\begin{definition}
-\label{def:hill ent}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
+In this work, we will use obfuscation of point-programs, 
+\[
+I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
+\]
+
+We present the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
+\begin{enumerate}  
+\item Input: string $w\in \zo^n$.
+\item Choose a generator $g\overset{\$}\leftarrow G$
+\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
+\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
+\end{enumerate}
+\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
+Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
+Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
+For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
+\end{assumption}
+\begin{theorem}~\cite{canetti1997towards}
+The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
+\end{theorem}
+
+As mentioned above there exist other constructions of point function obfuscation under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
+
+Lastly, we will need the notion of composable obfuscation.
+
+\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}]
+\label{def:obf comp}
+A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
+That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
+\[
+|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
+\]
+where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
 \end{definition}
 
+\section{Proof of \lemref{lem:linear codes independent}}
+\label{sec:proof of linear indep}
+\begin{proof}
+Suppose there is some $i$ that is not equiprobable.
+Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
+First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
+First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
+Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
+Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
+This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
+Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
+This is a contradiction and completes the proof.
+\end{proof}
+
+\section{Proof of \lemref{lem:cond and cext}}
+\label{sec:cond and cext}
+\begin{proof}
+It suffices to show if there is some distinguisher $D$ of size $s'$ where 
+\[\delta^D((\cext(W; X), U_d, P), (U_\kappa, U_d, P))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D'$ of size $s_{cond}$ where for all $Z$ where $\Hav(Z|P)\geq \tilde{m}$ such that
+ \[
+ \delta^{D'}((Y, P), (Z, P))\geq \epsilon_{cond}.
+ \]
+Let $D$ be such a distinguisher.  That is,
+\[
+\delta^D(\ext(X, U_d)\times U_d \times P, U_\kappa\times U_d\times P)> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D'$ as follows.
+On input $y, p$ sample $x\leftarrow U_d$, compute $r\leftarrow \cext(y, x)$ and output $D(r, x, p)$.
+Note that $|D'| \approx s' + |\cext| +d= s_{cond}$.
+Then we have the following:
+\begin{align*}
+\delta^{D'}((Y, P), (Z, P))&= \delta^D((\cext(Y, U_d), U_d, P), \cext(Z, U_d), U_d, P)\\
+&\geq \delta^D((\cext(Y, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^D((\cext(Z, U_d), U_d, P), (U_\kappa\times U_d \times P))\\
+&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
+\end{align*}
+Thus $D'$ distinguishes $Y$ from all $Z$ with sufficient conditional min-entropy.  This is a contradiction.
+\end{proof}
+
 \end{document}

### 2014-01-13 trunk/constantRate/ConstCompFuzzExt.tex
Working on proof

@@
 
-\title{Constant Error Rate Computational Fuzzy Extractors\thanks{The work of B.
+\title{Constant Error Tolerance Computational Fuzzy Extractors}
+\author{Ran Canetti \and Benjamin Fuller\footnote{The work of B.
 Fuller is sponsored by Assistant Secretary of Defense for Research \& Engineering under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}}
-\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin}
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
 
@@
 Fuzzy extractors derive strong keys from noisy sources.
+The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly key distributed key.
 Traditionally, their security is defined information-theoretically.
-Fuzzy extractors have strong bounds on the length of the derived key.
+Fuzzy extractors have upper bounds on the length of the derived key~(Dodis et al., J.
+of Comp 2008).
 In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.
-For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation unachievable.
+For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as open problem.
 
-The work of Fuller, Meng, and Reyzin (Asiacrypt 2013), posited these bounds could be overcome by only providing security against computationally-bounded adversaries.
+Fuller, Meng, and Reyzin (Asiacrypt 2013) hypothesize that these bounds can be overcome by only providing security against computationally-bounded adversaries.
 %They provide a construction of a computational fuzzy extractor that corrects a small number of errors without any loss in key length.
-They show the feasibility of constructing a computational fuzzy extractor that does not suffer from the information-theoretic bounds.
+%They show the feasibility of constructing a computational fuzzy extractor that does not suffer from the information-theoretic bounds.
 %Unfortunately, their construction is limited to very high entropy distributions and does not significantly beat information-theoretic bounds.
@@
 \textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.
-Let $W = W_1, ..., W_\ell$ be a source composed of blocks over a large alphabet.
-We flip a coin $c_i$ for each block and either obfuscate the block or a random point.
-When a close value $w'$ is input, we can recover most of the coins $c_i$.
-Error-tolerance is achieved by choosing $c = c_1,..., c_\ell$ from an error-correcting code.
+%Let $W = W_1, ..., W_\ell$ be a source distribution composed of blocks over a large alphabet, $Z$.
+To obfuscate a sample $w$ drawn from $W$.
+We flip a coin $c_i$ for each block and either obfuscate the block $w_i$ or a random point in $Z$.
+When a close reading $w'$ is given as input, we can recover most of the coins $c_i$.
+Error-tolerance is achieved by sampling $c = c_1,..., c_\ell$ from an error-correcting code.
 Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  
-Our construction is secure as long as a large number of dimensions are unpredictable given equality queries on individual blocks.
+%Security holds as long as a large number of blocks $W_i$ of $W$  are unpredictable given equality queries on individual blocks.  
 Our construction provides the following novel features:
@@
 \item Constant error tolerance rate.
-Previous constructions of computational fuzzy extractors corrected a logarithmic fraction of errors.
+%Previous constructions of computational fuzzy extractors corrected a logarithmic fraction of errors.
 (Information-theoretic constructions support a constant fraction of errors but are subject to bounds described above.)
-\item Security for a large class of distributions.
-The main requirement for security is that most blocks have a super-logarithmic amount of entropy.
+\item Security for a large and meaningful class of distributions.
+%The main requirement for security is that most blocks have a super-logarithmic amount of entropy.
 Previous computational fuzzy extractors required the source to be essentially uniform.
@@
 \section{Introduction}\label{sec:introduction}
-Authentication is a crucial component of system security.
-Reliable key derivation significantly simplifies authentication.
-However many sources with entropy are noisy, providing close values upon subsequent readings~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).
+Reliable key derivation is a cornerstone of authentication.
+However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).
+To use noisy physical sources in applications, two problems must be addressed.
+The first is ensuring the same value is obtained from every reading of the source.
+This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).
+The second is converting a source with entropy to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).
+Both of these problems have interactive and non-interactive versions.
+For a single user~(trying to produce the same key from multiple readings of a physical source) non-interactive solutions are appropriate.
+We focus on this setting.
+%If both of these tasks are achieved a noisy physical source can be used like a uniformly random private key.
 
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} derive stable keys from noisy data.
-They are composed of two algorithms: \gen takes a source value $w_0$, and produces a key $r$ and a public value $p$, and \rep which takes a nearby value $w_1$ and $p$ producing the original key $r$.
-Intuitively, they are two functions: information reconciliation~(to provide the same value with \emph{noisy} readings) and key derivation or privacy amplification~(to transform an entropic source into a uniform key).
-Traditionally, these two functions were performed by two separate primitives: a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} and a randomness extractor~\cite{nisan1993randomness}.
+Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} perform both tasks non-interactively.
+They consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public value $p$.
+The second algorithm \rep takes this public value $p$ and a close $w'$ to reproduce the original key $r$.
+Traditionally, a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} performs information-reconciliation and a randomness extractor~\cite{nisan1993randomness} performs privacy amplification.
 
-In fuzzy extractors, there are two competing parameters, security and error-tolerance.
-The key should be uniform to an observer but a close  $w_1$ should map to the same key.
-In the information-theoretic realm these two parameters are indeed at odds.
-Let $t$ be the desired error-tolerance and let $|B_t(\cdot)|$ be the size of a Hamming ball of radius $t$.
-Roughly, the length of the key $|r| < \Hoo(W) - \log |B_t(\cdot)|$~(see~\cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions, here we use the sphere packing bound as one bound for the best constructible code).
-For the remainder of this paper, we denote this quantity by $gap = \Hoo(W) - \log |B_t(\cdot)|$.
+Unfortunately, fuzzy extractors have not yielded key derivation for all noisy sources.  
+This is because there is tension between security and error-tolerance.
+The key should be uniform to an observer but nearby $w'$ should map to the same key.
+By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.
+In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.
+This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+The length of $r$ is dictated by size of the best code that corrects $t$ errors.
+Error-correcting codes are well studied and we have tight bounds on this quantity.
+% how many codewords may be in a code that corrects $t$ errors.
+
+ Specifically, we consider the Hamming metric.
+For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.
+As we discuss later, it is possible to avoid these losses if the fuzzy extractor has additional knowledge about the distribution.} and logarithm of the number of error patterns to be corrected.
+For the remainder of this paper we denote this quantity by $gap$.
+This represents a real problem as important biometrics~(such as irises~\cite{daugman2004}) have $gap <0$ and current fuzzy extractors provide no security guarantee.
+
+ %let $|B_t|$ be the number of points within distance $t$.
+The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
+For the remainder of this paper, we denote this quantity by $gap = \Hoo(W) - \log |B_t|$.
 
 However, this does not need to be the case in the computational setting.
-Fuller, Meng, and Reyzin defined computational fuzzy extractors which produce pseudorandom instead of truly random keys~\cite{fuller2013computational}.
-They posit it may be possible to build a computational fuzzy extractor when $gap$ is small or negative.
+Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.
+Computational fuzzy extractors produce pseudorandom instead of truly random keys.
+They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.
 We resolve this question and construct a computational fuzzy extractor when $gap<0$.
@@
 
-In the information-theoretic setting the goal of a fuzzy extractor is to build a key as long as possible.  
-In the computational setting, a key may be expanded once it is long enough to run a pseudorandom generator.
-Thus, our focus is building a reasonable length key for a class of distributions where nothing is possible information-theoretically.
+The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.  
+In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
+Thus, our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
 
-\textbf{Overview of Construction:} The negative results of Fuller, Meng, and Reyzin~\cite{fuller2013computational} show that building a computational fuzzy extractor using a computational secure sketch and a privacy amplification element is unlikely to be fruitful.
-They present two alternatives combining the information-reconciliation and privacy amplification components~(their approach) and using a computational version of a fuzzy conductor~(fuzzy conductors are defined by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-We follow the second approach.
+\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.
+Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or instead of recovering $w$ produce a new consistent high-entropy secret.
+This is known as a fuzzy conductor~(the entropy is being ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
+Here, we follow the second approach and use a \emph{computational} fuzzy conductor.
 
-Our construction~(\consref{cons:first construction}) is based on obfuscation.
-While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we use the obfuscation of point functions.
-This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
+Our construction~(\consref{cons:first construction}) is based on obfuscation of point programs.
+A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
+Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.
+For a point program, this means hiding all partial information about the point $w$.
+Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
 
-Consider a source $w = w_1,..., w_\ell$ that is split into blocks~(over some large alphabet).
-We would like to tolerate Hamming errors for individual blocks.
-The main idea is for each block $i$ we flip a coin $c_i$ and either obfuscate $w_i$ or a random point $r_i$~(this is similar to the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}).
-With a close value $w'$ the \rec can determine where random values were obfuscated and where $w_i$ was obfuscated~(with some errors).
-Most of the bits $c_i$ are recoverable.
-To tolerate errors we choose the coins $c$ from an appropriate error-correcting code.
-Then, $c$ forms a distribution of high entropy that can be extracted~(either information-theoretically~\cite{nisan1993randomness} or computationally~\cite{DBLP:conf/crypto/Krawczyk10}).
-Note it is hard to recover $w$ from the value $c$.
-As discussed in~\cite[Section 3.3]{fuller2013computational} this is necessary to overcome the information-theoretic lower bounds.
+Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).
+We would like to tolerate errors in $t$ individual blocks.
+For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
+With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
+For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.
+Thus, most bits $c_i$ are recoverable.
+To tolerate errors we choose the coins $c$ from an error-correcting code.
+Then, $c$ forms an distribution of high entropy.
+This construction is conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
+It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.
+Note, it is hard to recover $w$ from the value $c$.
+This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.
 
+This construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  
 Our construction provides several advantages over previous constructions of computational fuzzy extractors:
 \begin{itemize}
-\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions\footnote{There are artificial examples where no loss in necessary in a fuzzy extractor.
-If $W$ consists of points from an error-correcting code of distance $2t+1$, then no public information is necessary and $gap$ may be negative.
-This violates the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors usually proceeds saying the residual entropy is at least $\Hoo(W)$ less the number of bits needed for error correcting.
-For an arbitrary distribution, this is at least $\log |B_t(\cdot)|$.
-The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions.}.
-\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\log \ell/ \ell)$)
+\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss in necessary in a fuzzy extractor.
+If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.
+This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.
+For an arbitrary distribution, this is at least $\log |B_t|$.
+The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions~(see \defref{def:block guessable}).}
+\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
 \item The first computational fuzzy extractor where block are not required to be uniformly distributed.
@@
 
-\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).
+\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.
+This means that blocks much be drawn from distributions with super-logarithmic entropy.
+Furthermore, our distance is Hamming distance over a large alphabet~(super-polynomial in the security parameter).
+Our construction is applicable for physical sources where many bits are expected to run consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
+Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
+
+\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a stronger object than a computational fuzzy extractor).
 Unfortunately, this is not the case.
-Each block is individual obfuscated, an adversary may ask equality on individual blocks.
-If not all blocks have high entropy this may allow an adversary to learn significant information about the source.
+Each block is individually obfuscated, so an adversary may ask equality queries on individual blocks.
+If not all blocks have high entropy an adversary may learn significant information about the source.
 Thus, our construction is not a virtual black box~(VBB) obfuscation~(where anything learnable by the circuit is simulatable using input/output behavior).
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation when $gap>>0$.
-Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.
-
-\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.
-This means that each block much be drawn from a distribution with super-logarithmic entropy.
-This also means that our distance is computed over a large alphabet~(exponential) in the security parameter.
-Our construction is primarily applicable for burst error-models~\cite{gilbert1960capacity}.
-Constructing a computational fuzzy extractor with the above parameters and a small alphabet is an important open problem.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides partial information.
+Constructing VBB obfuscation for sources where $gap <0$.
 
@@
 \label{sec:preliminaries}
-For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
+For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.
+For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
@@
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
-If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
+If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
 For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
-For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
+For the Hamming metric, $|B_t| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
+Unless otherwise noted logarithms are base $2$.
+%\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
 
@@
 
-\subsection{Randomness Extractors and Computational Fuzzy Extractors}
+\subsection{Coding Theory}
+\label{sec:coding theory}
+We introduce some notions from the field of binary error correcting codes.
+Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel\bnote{cite} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.
+\begin{definition}
+\label{def:hamming z channel}
+For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
+\end{definition}
+\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may exist for this type of error.
+The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).
+
+\begin{definition}
+Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon_{code}$.
+\end{definition}
+
+We note that for any code learning a few bits does not inform on the remainder of the bits.
+
+\begin{claim}
+\label{cl:many locations ent}
+Let $C$ be a binary code and let $\mathcal{I}$ be a set of indices of $C$.  Then $\Hav(C | C_\mathcal{I}) = |C| - |\mathcal{I}$.
+\end{claim}
+This claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
+
+%need one special property of the code, namely that each output bit is set to $1$ with probability $1/2$.
+
+\bnote{I don't think we need this!}
+\begin{definition}
+A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
+\end{definition}
+All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
+This is true as long as $C$ contains no constant bits.
+Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
+For the remainder of this work when we say a code, we assume there are no constant bits.
+
+\begin{lemma}
+\label{lem:linear codes independent}
+Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
+\end{lemma}
+Proof in \apref{sec:proof of linear indep}.
+
+\subsection{Obfuscation}
+Our construction uses virtual black-box obfuscation of point functions.  This is the following family of functions:
+\[
+I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
+\]
+Here we present the virtual black-box definition of obfuscation.
+See \secref{sec:obfuscation} for a more detailed introduction to obfuscation.
+This definition is known to be achievable for point functions under various assumptions~\cite{canetti1997towards, wee2005obfuscating}.
+We also need the obfuscation to be $\ell$-composable~(\defref{def:obf comp}).
+
+We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
+
+\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  
+\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.
+A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
+\begin{enumerate}
+\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
+\[
+\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
+\]
+where the probability is taken over the randomness $r$.
+\emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.
+Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
+\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
+\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
+and for all binary predicates $\pi$, 
+\[
+|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
+\]
+where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
+Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
+\end{enumerate}
+\end{definition}
+
+\section{Computational Fuzzy Extractors}
 \label{sec:fuzzy extractors}
 
-Here we present relevant extractor definitions.
-
 We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
-Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et.
+Definitions for information-theoretic fuzzy extractors and a non-interactive information-reconciliation component, known as a secure sketch, can be found in the work of Dodis et.
 al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
-The definition of computational fuzzy extractors allows for a small probability of error, as described in~\cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
+The definition of computational fuzzy extractors allows for a small probability of error.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
-
 %\begin{definition}
@@
 \end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.  
-Note that in the above definition of fuzzy extractors, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
-For notational convenience, we the definition of computational fuzzy extractors specifies a general class of sources for which the fuzzy extractor is designed to work, rather than the class of sources that consists of all sources of a given min-entropy $m$~(of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
+In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
+The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor is designed to work rather than the family of all sources of a given min-entropy $m$.
+With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary.
 
@@
 Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.
-The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t(\cdot)$.
+The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t$.
 When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.
@@
 
-We now define the two primitives in this approach: a computational fuzzy conductor and a (computational)~randomness extractor.
-A computational fuzzy conductor is the computational analogue of a fuzzy conductor introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
+We now define the two primitives for this approach: a computational fuzzy conductor and a (computational)~randomness extractor.
+A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
 \begin{definition}
@@
 
-A computational extractor is the natural adaption of a randomness extractor to the computational setting.
-We use the average case version of the notion introduced by Krawczyk~\cite{krawczyk2010cryptographic}:
+A computational extractor is the natural adaption of a randomness extractor to the computational setting.  We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
 %start with the standard notion of an average-case extractor.
@@
 \begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\cext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, s_{sec}, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
+Let $\chi$ be a finite set.
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, s_{sec}, \epsilon)$-average-case computational extractor} if for all pairs
+of random variables $X, Y$ over $\zo^\ell, \chi$ such that
 $\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{sec}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
@@
 
-Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor:
+Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor~(proof in \secref{sec:cond and cext}):
 
 \begin{lemma}
-\label{lem:cond and ext}
-Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.
-Let $\cext:\mathcal{M}_2\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, s_{ext}, \epsilon_{ext})$-average case computational extractor.
+\label{lem:cond and cext}
+Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
+Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, s_{ext}, \epsilon_{ext})$-average case computational extractor.
 Define $\gen, \rep$ as:
@@
 \end{itemize}
-Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \max\{s_{cond} - |\cext|, s_{ext}\}$.
+Then $\gen, \rep$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \max\{s_{cond} - |\cext| -d, s_{ext}\}$.
 \end{lemma}
-\begin{proof}
-It suffices to show if there is some distinguisher $D$ of size $s'$ where 
-\[\delta^D((\cext(W; X), U_d, P), (U_\kappa, U_d, P))>\epsilon_{cond}+ \epsilon_{ext}\]
- then there is an distinguisher $D'$ of size $s_{cond}$ where for all $Z$ where $\Hav(Z|P)\geq \tilde{m}$ such that
- \[
- \delta^{D'}((Y, P), (Z, P))\geq \epsilon_{cond}.
- \]
-Let $D$ be such a distinguisher.  That is,
-\[
-\delta^D(\ext(X, U_d)\times U_d \times P, U_\kappa\times U_d\times P)> \epsilon_{ext}+\epsilon_{cond}.
-\]
-Then define $D'$ as follows.
-On input $y, p$ sample $x\leftarrow U_d$, compute $r\leftarrow \cext(y, x)$ and output $D(r, x, p)$.
-Note that $|D'| \approx s' + |\cext| = s_{cond}$.
-Then we have the following:
-\begin{align*}
-\delta^{D'}((Y, P), (Z, P))&= \delta^D((\cext(Y, U_d), U_d, P), \cext(Z, U_d), U_d, P)\\
-&\geq \delta^D((\cext(Y, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^D((\cext(Z, U_d), U_d, P), (U_\kappa\times U_d \times P))\\
-&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
-\end{align*}
-Thus $D'$ distinguishes $Y$ from all $Z$ with sufficient conditional min-entropy.  This is a contradiction.
-\end{proof}
-
-\subsection{Coding Theory}
-\label{sec:coding theory}
-We introduce some notions from the field of binary error correcting codes.
-Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but no bit flips from $1\not\rightarrow 0$.
-\begin{definition}
-\label{def:hamming z channel}
-For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
-\end{definition}
-\textbf{Note:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may be exist for these errors.
-
-\begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon)$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon$.
-\end{definition}
-
-We need one special property of the code, namely that each output bit is set $1$ with probability $1/2$.
-
-\begin{definition}
-A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
-\end{definition}
-All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
-This is true as long as $C$ contains no constant bits.
-Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
-For the remainder of this work when we say a code, we assume there are no constant bits.
-
-\begin{lemma}
-Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
-\end{lemma}
-\begin{proof}
-Suppose there is some $i$ that is not equiprobable.
-Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
-First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
-First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
-Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
-Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
-This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
-Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
-This is a contradiction and completes the proof.
-\end{proof}
-
-\subsection{Obfuscation}
-The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
-This notion is known to be impossible in a black-box way for all polynomial time programs.
-Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
-Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
-
-We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
-
-\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  Let $\mathcal{C}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
-\begin{enumerate}
-\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
-\[
-\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
-\]
-where the probability is taken over the randomness $r$.
-\emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability ver the random coin tosses $r$.
-Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
-\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
-\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
-and for all binary predicates $\pi$, 
-\[
-|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
-\]
-where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
-Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
-\end{enumerate}
-\end{definition}
-
-In this work, we will use obfuscation of point-programs, 
-\[
-I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
-\]
-
-We provide the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
-\begin{enumerate}  
-\item Input: string $w\in \zo^n$.
-\item Choose a generator $g\overset{\$}\leftarrow G$
-\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
-\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
-\end{enumerate}
-\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
-Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
-Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
-For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
-\end{assumption}
-\begin{theorem}~\cite{canetti1997towards}
-The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
-\end{theorem}
-
-As described above there exist other constructions of point function obfuscates under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
-
-Lastly, we will need the notion of composable obfuscation.
-
-\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}].
-A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
-That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
-\[
-|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
-\]
-where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
-\end{definition}
 
@@
 The goal is to derive strong keys from noisy sources.
-As discussed in the introduction, the important parameter is the difference between the total entropy and the number of errors being corrected.
-We call this value the entropy gap or $gap= \Hoo(W) - \log|B_t(\cdot)|$.
-The results of Dodis et al.~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08} show that gap is an upper bounded for the length of the derived key.
-
-If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
+As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
+In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.
+Thus, we focus on providing enough security when $gap<0$.
+We build a computational fuzzy conductor, noting that it can be converted to a computational fuzzy extractor using \lemref{lem:cond and cext}.%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
 Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.
@@
 
-\subsection{First $gap<0$ construction}
 \begin{construction}
@@
 Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.
-Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be an output equiprobable $(\neigh_t, \epsilon_{code})$-error-correcting code.
-Let $\ext : \zo^n\times \zo^* \rightarrow \zo^r$ be a $(\tilde{m}, \epsilon_{ext})$-extractor where $\tilde{m}= XXX$.
-\bnote{fill this in}
+Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ %be an output equiprobable
+$(\neigh_t, \epsilon_{code})$-error-correcting code.  
 We describe $\gen, \rep$ as follows:
@@
 \begin{itemize}
-\item If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
+\item The input $w$ is hidden in two different ways.  In locations where $c_i=1$ the block $w_i$ is information-theoretically unknown.
+If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.  
+In locations where $c_i=0$ it is hard to find $w_i$ given the point obfuscation.
 As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
@@
 This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
-\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(\defref{def:comp fuzzy cond}).
 \end{itemize}
@@
 \subsection{Security of Construction}
+\label{sec:sec of construction}
 Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.
 The adversary is provided with equality oracles for each block individually.
-Security rests on an adversaries inability to learn the values using only \emph{adaptive} equality queries.
+Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.
 For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
-Our proof for independent and high entropy blocks is more complicated than necessary, but the structure will hold for the more complicated setting.
-The outline of the proof follows:
+Our proof for independent and high entropy blocks is more complicated than necessary, but the proof structure will hold for the family of sources described in \secref{sec:supported sources}.
+The outline of the proof is to:
 
 \begin{itemize}
-\item Show that conditioned on the adversaries view there is a large set of blocks, $\mathcal{I}$, that still have a super logarithmic entropy.
-\item Show that conditioned on the values of all indices $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$.
-\item For all indices in $\mathcal{I}$, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
-\item Any two codewords, $c_1, c_2$ differing in only these positions are statistically close given the adversaries view.
-\item The set of codewords differing in these positions form a distribution with conditional entropy.  This is sufficient to show
+\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
+\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is still large~(\clref{cl:many locations ent}).
+\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
+\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view.
+\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
+%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
+%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
+%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
+% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
+%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
+\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy).  
 \end{itemize}
@@
 \begin{lemma}
+\label{lem:blocks unguessable after queries}
 Let $n$ be a security parameter.
-Let $W(n) = W = W_1,..., W_t$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.
+Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.
 Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.
 %Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}.
-Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.
+Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \omega(\ell \log n)$.
 \end{lemma}
 \begin{proof}
-Consider a particular block $i$, we measure how an adversaries queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
+Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
 Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
@@
 \end{proof}
+Let $\mathcal{I}$ be the set of all indices $\{1,..., n\}$.
+Then $\Hav(C | C_{\mathcal{I}^c}) = \Hoo(C) = \ell$.
+We know show that all codewords different in only positions of $\mathcal{I}$ are indistinguishable.
 \begin{lemma}
-\label{lem:super log insist by equal queries}
+Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then let $D$ be an unbounded distinguisher 
+\[
+\Pr[D( View(A), C_{\mathcal{I}^c}) =1 | C = c_1] - \Pr[D(View(A), C_{\mathcal{I}^c}) = 1 | C= c_2] < \ngl(n).
+\]
+\end{lemma}
+
+\begin{lemma}
+\bnote{what goes here?}
+Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
+\end{lemma}
+\begin{lemma}
+\label{lem:super log indist by equal queries}
 Let $W$ and $U$ be two distributions of super-logarithmic entropy.
@@
 %\end{lemma}
-\begin{corollary}
-\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor when $W = W_1,..., W_n$ all $W_i$ are independent and $\Hoo(W_i) = \omega(\log n)$.
-\end{corollary}
-\begin{proof}
-Result of security of point obfuscation and \lemref{lem:cond and ext}.
-\end{proof}
 
 \subsection{Correctness of \consref{cons:first construction}}
-Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
+We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
+%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
 However, we start by justifying our use of unidirectional codes.
@@
 \end{proof}
-\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
-We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
+
+We now consider the number of possible $0\rightarrow 1$ bit flips in $c$.
+A $0\rightarrow 1$ flip on index $i$ occurs when two conditions are met $w_i\neq w_i'$ and $c_i = 0$.
+Since the first conditioned is only fulfilled at most $t$ times, we have the following lemma:
+
+\begin{lemma}
+Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
+\[
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n}.
+\]
+That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
+\end{lemma}
+
+\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
+However, this requires a codeword where most codewords have Hamming weight close to $1/2$.
+
+%\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
+%We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
 Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
@@
 Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
-\begin{align*}
-\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
-\end{align*}
-This leads us to the following lemma:
-\begin{lemma}
-\label{lem:correctness holds}
-If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
-\end{lemma}
-\bnote{This analysis is done assuming that the two sets are the same size.
+%\begin{align*}
+%\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
+%\end{align*}
+%This leads us to the following lemma:
+%\begin{lemma}
+%\label{lem:correctness holds}
+%If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
+%\end{lemma}
+%\bnote{This analysis is done assuming that the two sets are the same size.
 Need to worry about variation in the number of $1$s and $0$s in $c$.
 Need to show that for most codes (linear?) the variance in Hamming weight is small.}
-\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
+%\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
+
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for independent sources~(where each block has a super-logarithmic amount of entropy):
+\begin{corollary}
+Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq \omega(\log n)$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = |C| - o(n)$.
+\end{corollary}
+\begin{proof}
+Security is result of arguments in \secref{sec:sec of construction}.  Correctness follows from the arguments above and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
+\end{proof}
 
@@
 \bnote{need to complete this section and redo the proof in 3.2 with this type of source.}
-We now describe a set of high entropy sources appropriate for our construction.
-After giving the description of the distribution, we give examples of distributions that fit in this class and provide additional characterizations.
+
+We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
+We need a distribution where after all of the possible equality queries, a large number of blocks still have super-logarithmic entropy.
 
@@
 \label{def:block guessable}
-Let $\mathcal{O}_{w_1,..., w_k}$ be an oracle that return $\mathcal{O}_{w_1,..., w_k}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
-A source $W = W_1||...|W_k$ is a $(q, \alpha, \ell)$-\emph{guessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $S$ of size at least $\ell$ such that
+Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that
 \[
-\forall i\in S, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
+\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
 \]
 \end{definition}
+As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}.
+
+\begin{theorem}
+Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$.
+Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \log |C| - \beta - o(n)$.
+\end{theorem}
+
+\subsection{Characterizing unguessable block distributions}
 This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.
@@
 
-\subsection{Discussion}
+\subsection{Parameter Discussion}
 Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
-Correction occurs in a small number of dimensions that are allowed to vary completely.
+Correction occurs for a small number of dimensions that are allowed to vary completely.
 As described in \secref{sec:supported sources}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
@@
 
-%\appendix
-%\section{Computational Entropy}
-%HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
-It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
+\appendix
+\section{Obfuscation}
+\label{sec:obfuscation}
+The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
+This notion is known to be impossible in a black-box way for all polynomial time programs.
+Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
+Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
+The definition of virtual black box obfuscation is presented in \defref{def:obf}.
+
+In this work, we will use obfuscation of point-programs, 
+\[
+I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
+\]
+
+We present the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
+\begin{enumerate}  
+\item Input: string $w\in \zo^n$.
+\item Choose a generator $g\overset{\$}\leftarrow G$
+\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
+\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
+\end{enumerate}
+\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
+Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
+Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
+For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
+\end{assumption}
+\begin{theorem}~\cite{canetti1997towards}
+The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
+\end{theorem}
+
+As mentioned above there exist other constructions of point function obfuscation under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
+
+Lastly, we will need the notion of composable obfuscation.
+
+\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}]
+\label{def:obf comp}
+A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
+That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
+\[
+|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
+\]
+where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
+\end{definition}
+
+\section{Proof of \lemref{lem:linear codes independent}}
+\label{sec:proof of linear indep}
+\begin{proof}
+Suppose there is some $i$ that is not equiprobable.
+Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
+First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
+First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
+Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
+Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
+This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
+Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
+This is a contradiction and completes the proof.
+\end{proof}
+
+\section{Proof of \lemref{lem:cond and cext}}
+\label{sec:cond and cext}
+\begin{proof}
+It suffices to show if there is some distinguisher $D$ of size $s'$ where 
+\[\delta^D((\cext(W; X), U_d, P), (U_\kappa, U_d, P))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D'$ of size $s_{cond}$ where for all $Z$ where $\Hav(Z|P)\geq \tilde{m}$ such that
+ \[
+ \delta^{D'}((Y, P), (Z, P))\geq \epsilon_{cond}.
+ \]
+Let $D$ be such a distinguisher.  That is,
+\[
+\delta^D(\ext(X, U_d)\times U_d \times P, U_\kappa\times U_d\times P)> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D'$ as follows.
+On input $y, p$ sample $x\leftarrow U_d$, compute $r\leftarrow \cext(y, x)$ and output $D(r, x, p)$.
+Note that $|D'| \approx s' + |\cext| +d= s_{cond}$.
+Then we have the following:
+\begin{align*}
+\delta^{D'}((Y, P), (Z, P))&= \delta^D((\cext(Y, U_d), U_d, P), \cext(Z, U_d), U_d, P)\\
+&\geq \delta^D((\cext(Y, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^D((\cext(Z, U_d), U_d, P), (U_\kappa\times U_d \times P))\\
+&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
+\end{align*}
+Thus $D'$ distinguishes $Y$ from all $Z$ with sufficient conditional min-entropy.  This is a contradiction.
+\end{proof}
 

### 2014-01-13 trunk/constantRate/ConstCompFuzzExt.tex
Working on proof

@@
 \item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
-\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is still large~(\clref{cl:many locations ent}).
+\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
 \item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
-\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view.
-\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
+\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
+%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
 %\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
@@
 %\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
-\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy).  
+\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
+\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
 \end{itemize}
@@
 \begin{lemma}
-Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then let $D$ be an unbounded distinguisher 
+\label{lem:codewords in I close}
+Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
 \[
-\Pr[D( View(A), C_{\mathcal{I}^c}) =1 | C = c_1] - \Pr[D(View(A), C_{\mathcal{I}^c}) = 1 | C= c_2] < \ngl(n).
+\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < \ngl(n).
 \]
 \end{lemma}
-
+\begin{proof}
+Recall by assumption that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \omega(\log n)$.
+The only information about $C_i$ is contained in the query responses.
+Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with overwhelming probability all responses to $c_i$ are $0$.
+Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $1/\poly(n)$.
+Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is negligible~(occurs with probability at most $q/2^n$).
+Thus, it must occur with $1/\poly(n)$ probability when $c_i=0$.
+When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
+If this occurs with $1/\poly(n)$ probability this violates the super-logarithmic conditional min-entropy condition.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ all distinguishers are negligibly close.
+\end{proof}
+
+%\begin{lemma}
+%\bnote{what goes here?}
+%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
+%\end{lemma}
+%\begin{lemma}
+%\label{lem:super log indist by equal queries}
+%Let $W$ and $U$ be two distributions of super-logarithmic entropy.
+Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%It suffices to show that with the probability of all responses being $0$ is overwhelming.
+Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
+\bnote{Finish this proof}
+%\end{proof}
+
+%\begin{lemma}
+%\label{lem:code bits statistically indist}
+%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
+Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%\bnote{Do this}
+%\end{proof}
+%We can extend this lemma to the entire codeword $C$:
+%\begin{lemma}
+%For all $c_1, c_2 \in C$ we have the following: 
+%\[
+%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
+%\]
+%\end{lemma}
+The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
 \begin{lemma}
-\bnote{what goes here?}
-Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
-\end{lemma}
-\begin{lemma}
-\label{lem:super log indist by equal queries}
-Let $W$ and $U$ be two distributions of super-logarithmic entropy.
-Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$
 \end{lemma}
 \begin{proof}
-It suffices to show that with the probability of all responses being $0$ is overwhelming.
-Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
-\bnote{Finish this proof}
-\end{proof}
-
-\begin{lemma}
-\label{lem:code bits statistically indist}
-Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
-Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
-\end{lemma}
-\begin{proof}
-\bnote{Do this}
-\end{proof}
-We can extend this lemma to the entire codeword $C$:
-\begin{lemma}
-For all $c_1, c_2 \in C$ we have the following: 
-\[
-\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
-\]
-\end{lemma}
-\begin{lemma}
-If $C$ is output then, for all $i$, $\Hav(C_i |View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)}))\geq 1 - \ngl(n)$.
-\end{lemma}
-\begin{proof}
-Since $C$ is output equiprobable we know that for each $i$, $\Pr[C_i =1 ] = 1/2$.
-Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
+Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
+%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
 For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
 \begin{align*}
-\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C_i =b | view ] &\leq 1/2 + \ngl(n)\\
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\
 \end{align*}
-If this was not true~(that is in expectation, there was some $b$ that was likely with probability greater than $1/2+1/\poly(n)$), there there would exist an unbounded adversary outputting that $b$, contradicting \lemref{lem:code bits statistically indist}).
-Taking the negative log of each side one has:
-\begin{align*}
+If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.
+\end{proof}
+\begin{corollary}
+\label{cor:avg min after view}
+$\Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
+\end{corollary}
+\begin{proof}
+Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
+Taking the negative log of the above lemma one has:
+\begin{align}
 \Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
- &=\\-\log \left(\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\max_{b\in\{0,1\}}\Pr[C_i =b | view ]  \right) &\geq -\log (1/2 + \ngl(n))\\
-&\geq -\log(\frac{1}{2} + \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+2}{2n^{w}}\right)\\
+ &=\\-\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\\
+&\geq -\log(P_c+ \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+P_c}{P_c n^{w}}\right)\\
 %&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
-&=1-\left(\log (1+\frac{2}{n^e}) \right)\\
-&=1-\frac{1}{\ln 2}\left(\ln (1+\frac{2}{n^e}) \right)\\
-&= 1- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{2}{n^e})^i\right) \\
-&\geq 1 - \frac{1}{\ln 2} \frac{2}{n^e} = 1-\ngl(n)
-\end{align*}
-Here the second to last line is derived using the Taylor expansion for $\ln(1+x)$ and the last line is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive.
+&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\\
+&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \\
+&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
+&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
+&= |C| - |\mathcal{I}^c| -\ngl(n)\label{eq:min ent}
+\end{align}
+Here the Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
 \end{proof}
-By similar reasoning we can extend this lemma to the entire codeword:
-\begin{lemma}
-If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
-\end{lemma}
+
+%\begin{lemma}
+%\label{lem:obf has hill ent}
+%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.
+Let $ (X, Y)  = (C,
+%\end{proof}
+%By similar reasoning we can extend this lemma to the entire codeword:
+%\begin{lemma}
+%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
+%\end{lemma}
 %\begin{lemma}
@@
 \end{definition}
-As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}.
+As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the rest of the arguments follow the same way).
 

### 2014-01-13 trunk/constantRate/ConstCompFuzzExt.tex
Added notes on problems with the proof

@@
 
- Specifically, we consider the Hamming metric.
+We consider the Hamming metric.
 For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.
@@
 In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
-Thus, our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
+Our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
 
@@
 We would like to tolerate errors in $t$ individual blocks.
-For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
+For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.
+This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
 With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
 For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.
-Thus, most bits $c_i$ are recoverable.
+Thus, most bits of $c_i$ are recoverable.
 To tolerate errors we choose the coins $c$ from an error-correcting code.
 Then, $c$ forms an distribution of high entropy.
-This construction is conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
+This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
 It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.
@@
 This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.
-
-This construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  
+Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+
 Our construction provides several advantages over previous constructions of computational fuzzy extractors:
 \begin{itemize}
-\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss in necessary in a fuzzy extractor.
+\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss is necessary in a fuzzy extractor.
 If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.
 This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.
-For an arbitrary distribution, this is at least $\log |B_t|$.
+For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.
 The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions~(see \defref{def:block guessable}).}
 \item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
-\item The first computational fuzzy extractor where block are not required to be uniformly distributed.
+\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
 Our construction simply requires a large number of blocks that are unguessable given equality queries.
@@
 Furthermore, our distance is Hamming distance over a large alphabet~(super-polynomial in the security parameter).
-Our construction is applicable for physical sources where many bits are expected to run consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
+Our construction is applicable for physical sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
 Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
@@
 Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides partial information.
-Constructing VBB obfuscation for sources where $gap <0$.
+Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
 
@@
 We introduce some notions from the field of binary error correcting codes.
-Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel\bnote{cite} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.
+Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel~\cite{tallini2002capacity} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.
 \begin{definition}
@@
 \end{definition}
-\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may exist for this type of error.
+\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
 The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).
@@
 \label{cl:many locations ent}
-Let $C$ be a binary code and let $\mathcal{I}$ be a set of indices of $C$.  Then $\Hav(C | C_\mathcal{I}) = |C| - |\mathcal{I}$.
+Let $C$ be a binary code and let $\mathcal{I}$ be a set of indices of $C$.  Then $\Hav(C | C_\mathcal{I}) = |C| - |\mathcal{I}|$.
 \end{claim}
@@
 
-\bnote{I don't think we need this!}
-\begin{definition}
-A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
-\end{definition}
-All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
+%\bnote{I don't think we need this!}
+%\begin{definition}
+%A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
+%\end{definition}
+%All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
 This is true as long as $C$ contains no constant bits.
@@
 For the remainder of this work when we say a code, we assume there are no constant bits.
-
-\begin{lemma}
-\label{lem:linear codes independent}
-Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
-\end{lemma}
-Proof in \apref{sec:proof of linear indep}.
+%
+%\begin{lemma}
+%\label{lem:linear codes independent}
+%Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
+%\end{lemma}
+%Proof in \apref{sec:proof of linear indep}.
+%
+%
 
@@
 We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
-Definitions for information-theoretic fuzzy extractors and a non-interactive information-reconciliation component, known as a secure sketch, can be found in the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
+Definitions for information-theoretic fuzzy extractors and a non-interactive information-reconciliation component, known as a secure sketch, can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
 The definition of computational fuzzy extractors allows for a small probability of error.
@@
 We follow the second approach.
-%Our main question is: for what type of sources can we build fuzzy extractors?
-Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.
-The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t$.
-When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.
-We ask whether security is possible when $gap$ is small or negative.
-%In this paper, we ask whether a smaller entropy loss can be achieved by considering a computational fuzzy extractor with a computational security requirement.
-%We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
-
-%As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.
-As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch~\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}.
-Instead, we will use a computational fuzzy conductor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+
+In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.
+Instead of using a fuzzy conductor, we define a computational version.
 We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
@@
 A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+\bnote{depending on what we get from obfuscation may need this to be relaxed HILL entropy.  Would have to redo lemma below, but it is essentially the same.}
 \begin{definition}
@@
 \begin{itemize}
-\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \cext(y; x)$,  and output $(r, p)$.
+\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $r = \cext(y; x)$ and $p = (p', x)$.  Output $(r, p)$.
 \item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \cext(y; x)$. 
@@
 \item The input $w$ is hidden in two different ways.  In locations where $c_i=1$ the block $w_i$ is information-theoretically unknown.
-If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.  
 In locations where $c_i=0$ it is hard to find $w_i$ given the point obfuscation.
 As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
-\item There are two possible reasons for a bit of $c_i'$ to be $1$.
+\item There are two possible reasons for a bit $c_i'$ to be $1$.
 Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.
-However if a bit of $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
+However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
 This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
@@
 \label{sec:sec of construction}
-Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.
+Assuming virtual black-box obfuscation, we argue security in the presence of equality oracles for each block.
 The adversary is provided with equality oracles for each block individually.
@@
 For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
-Our proof for independent and high entropy blocks is more complicated than necessary, but the proof structure will hold for the family of sources described in \secref{sec:supported sources}.
+Our proof for independent and high entropy blocks is more complicated than necessary, but the proof structure holds for the family of sources described in \secref{sec:supported sources}.
 The outline of the proof is to:
@@
 \item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
+\bnote{I think this is wrong as currently written.  We transition from indistinguishability of all pairs to high entropy for the distribution.  This should be true but I think the argument is wrong.}
 \item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
+\bnote{I am having a little trouble formalizing this.  Was hoping for HILL entropy but I don't think that's true.  Will we get relaxed HILL entropy?}
 \end{itemize}
@@
 The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
+\bnote{As stated above I don't think this proof is right?}
 \begin{lemma}
@@
 \label{cor:avg min after view}
-$\Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
+$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
 \end{corollary}
@@
  &=\\-\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\\
-&\geq -\log(P_c+ \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+P_c}{P_c n^{w}}\right)\\
+&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right)\\
 %&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
@@
 \end{align}
+\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}
 Here the Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
@@
 Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq \omega(\log n)$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = |C| - o(n)$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = |C| - o(n)$.\bnote{Why the transition from $\ngl(n)$ to $o(n)$?
+Shouldn't this be $\ngl(n)$?}
 \end{corollary}
@@
 \label{sec:supported sources}
-\bnote{need to complete this section and redo the proof in 3.2 with this type of source.}
+\bnote{need to complete this section and redo the proof in  \secref{sec:sec of construction} with this type of source.}
 
@@
 \end{definition}
-As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the rest of the arguments follow the same way).
+As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
 
@@
 \subsection{Characterizing unguessable block distributions}
+\bnote{This section needs to be finished.  The point is to try and give an idea what the above definition means.  What type of distributions fulfill that definition.}
 This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.
@@
 \begin{claim}
-Let $W$ be a $(q, \alpha, \ell)$-guessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
+Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
 \end{claim}
@@
 \end{proof}
+\bnote{keep working}
 
@@
 \end{align*}
-We now ask how much entropy is necessary for security?
+\bnote{Need a good bound on ${\ell \choose t}$.}
+We now ask how much entropy is necessary for security.
 The first presented type of source was where each block was independent and had super-logarithmic min-entropy.
@@
 \textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
-The first is that Hamming distance is over an alphabet of exponential size, which precludes use is several major settings.
+The first is that Hamming distance is over an alphabet of exponential size, which precludes use in some applications.
 The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
-Lastly, we obtain only a single bit from each block of $W_i$, in settings where entropy is at a premium this seems wasteful.
+Lastly, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
 \bibliographystyle{alpha}
@@
 
-\section{Proof of \lemref{lem:linear codes independent}}
-\label{sec:proof of linear indep}
-\begin{proof}
-Suppose there is some $i$ that is not equiprobable.
+\section{Fuzzy Conductors}
+
+\label{sec:conductors}
+In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.  We first review the definition of a fuzzy conductor from~\cite{KanukurthiR09}:
+\begin{definition}
+A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen) and ``reproduce''~(\rep), with the following properties:
+\begin{enumerate}
+\item The generate procedure $\gen$ on input $w\in \mathcal{M}$ outputs a string $y\in\zo^*$ and a helper string $p\in\zo^*$.
+\item The reproduction procedure $\rep$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\zo^*$ as inputs.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $Y, P$ were generated by $(Y, P)\leftarrow \gen(w)$, then $\rep(w', P) = Y$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
+If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep$.
+\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $Y$ is close to a high entropy distribution $Z$.
+That is, $\exists Z$ with $\Hav(Z | P ) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
+\end{enumerate}
+\end{definition}
+
+We borrow from~\cite{DBLP:journals/siamcomp/DodisORS08} the following notation:
+\begin{itemize}
+\item A $\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ where there is a procedure that corrects $t$ errors.
+\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
+\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
+\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is finding the best $S$ for encoding $2^m$ points.
+\end{itemize}
+
+\begin{lemma}
+The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}-1\leq L(\mathcal{M}, t, m) -\log (1-2\epsilon)$.
+\end{lemma}
+\begin{proof}  Assume $(\gen, \rep)$ is a fuzzy conductor with the parameters stated.
+Let $S$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $S$.
+Define $(Y, P) \leftarrow \gen(W)$.
+Then there must exist a distribution $Z$ with $\Hav(Z|P) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
+By Markov's inequality, there exists some set $S_P$ such that $\Pr[P\in S_p] \geq 1/2$ and $\forall p\in S_P$ one has $\mathbf{SD}(Y | P = p, p ), (Z | P = p, p)<2\epsilon$.
+Now applying Markov's inequality of $\max_{z} \Pr[Z=z | P=p]$, there exists a set $S_P'$ such that $\Pr[P\in S_P']>1/2$, and for all $p\in S_P'$, $\Hoo(Z| P =p ) \geq \tilde{m}-1$.
+Denote by $p^*$ a value in $S_P\cap S_P'$~(on value must exist).
+Then $\mathbf{SD}((Y | P =p^* , p^*), (Z| P = p^*, p^*))\leq 2\epsilon$ and $\Hoo(Z|P=p^*)\geq \tilde{m}-1$.
+Denote by the set $T$ the possible values of $Y$ when $P=p^*$.
+For the statistical distance property to hold, $|T| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
+Associate with every $y\in T$ some $w\in S$ which could have produced $y$ with nonzero probability given $P=p^*$, and call this map $C$.
+$C$ defines an error correcting code.
+
+\end{proof}
+
+%\section{Proof of \lemref{lem:linear codes independent}}
+%\label{sec:proof of linear indep}
+%\begin{proof}
+%Suppose there is some $i$ that is not equiprobable.
 Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
@@
 This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
-Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
+%Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
 This is a contradiction and completes the proof.
-\end{proof}
+%\end{proof}
 

### 2014-01-13 trunk/constantRate/ConstCompFuzzExt.tex
Added notes on problems with the proof

@@
 Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
+
+The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our construction in \secref{sec:construction} and discuss parameters and tradeoffs in \secref{sec:discussion}.
 
@@
 \section{A Constant Rate Computational Fuzzy Extractor}
+\label{sec:construction}
 
@@
 
-\subsection{Parameter Discussion}
+\section{Discussion}
+\label{sec:discussion}
 Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
@@
 &> \log {\ell \choose t} (2^n-1)^t\\
-&=\Omega(tn) + \log {\ell\choose t}
+&=\Theta(tn) + \log {\ell\choose t}
 % \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
@@
 \bnote{Need a good bound on ${\ell \choose t}$.}
-We now ask how much entropy is necessary for security.
-The first presented type of source was where each block was independent and had super-logarithmic min-entropy.
-This means that $\Hoo(W) \approx \ell \omega(\log n)$.
-Thus in the setting where $t = \omega(\ell)$ we obtain that
+We now ask how much entropy is necessary for security.  The type of source we considered was independent blocks each with super-logarithmic min-entropy.  This yields 
 \[
-gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \omega(\ell n) + \log {\ell \choose t}\right)< 0. 
+gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right). 
 \]
-This \consref{cons:first construction} is the first fuzzy extractor with a negative $gap$.\footnote{We can make gap smaller by recalling that note every block must contribute fresh entropy.
-If each block is derived from a single source with super-logarithmic entropy then the starting entropy need only be $\omega(\log n)$.}
-
-\textbf{Note:} If $t = o(\ell)$ then the value of $gap$ is not clear, there are some $\ell$ for which it will be negative.
-However in the setting where $n>>\ell$ and a constant number of errors are being corrected $gap$ may be positive.
-However, we extract from at most $\ell$ bits and thus need $\ell$ to be large enough for reasonable application security.
-Setting $ \ell , t, n$ all of roughly the same size provides a natural balance of parameters.
+When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| - \ngl(n)$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+Thus, \consref{cons:first construction} achieves negative $gap$ when $t = \Theta(\ell)$.
+Furthermore, not every block must contribute entropy, so security is possible when the total starting entropy is $\omega(\log n)$.
+For example, \consref{cons:first construction} is secure when each block is equal and drawn from a distribution of super-logarithmic min-entropy.
+So there are supported sources with negative $gap$ for any value of $t$.
+We achieve $gap<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
+%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
 

### 2014-01-13 constantRate/ConstCompFuzzExt.tex
Added notes on problems with the proof

@@
 
-\title{Constant Error Tolerance Computational Fuzzy Extractors\thanks{The work of B.
+\title{Constant Error Tolerance Computational Fuzzy Extractors}
+\author{Ran Canetti \and Benjamin Fuller\footnote{The work of B.
 Fuller is sponsored by Assistant Secretary of Defense for Research \& Engineering under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}}
-\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin}
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
 
@@
 \textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.
-Let $W = W_1, ..., W_\ell$ be a source distribution composed of blocks over a large alphabet, $Z$.
+%Let $W = W_1, ..., W_\ell$ be a source distribution composed of blocks over a large alphabet, $Z$.
 To obfuscate a sample $w$ drawn from $W$.
@@
 Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  
-Security holds as long as a large number of blocks $W_i$ of $W$  are unpredictable given equality queries on individual blocks.
+%Security holds as long as a large number of blocks $W_i$ of $W$  are unpredictable given equality queries on individual blocks.  
 Our construction provides the following novel features:
@@
 Both of these problems have interactive and non-interactive versions.
-For a single user~(trying to produce the same key from multiple readings of a physical source) the non-interactive versions are appropriate.
+For a single user~(trying to produce the same key from multiple readings of a physical source) non-interactive solutions are appropriate.
 We focus on this setting.
@@
 For the remainder of this paper we denote this quantity by $gap$.
-This represents a real problem as important biometrics~(such as irises~\cite{daugman2004}) have $gap <0$ and information-theoretic fuzzy extractors provide no security.
+This represents a real problem as important biometrics~(such as irises~\cite{daugman2004}) have $gap <0$ and current fuzzy extractors provide no security guarantee.
 
@@
 However, this does not need to be the case in the computational setting.
-Fuller, Meng, and Reyzin define computational fuzzy extractors.
-Computational fuzzy extractors produce pseudorandom instead of truly random keys~\cite{fuller2013computational}.
+Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.
+Computational fuzzy extractors produce pseudorandom instead of truly random keys.
 They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.
@@
 In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
-Thus, our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
+Our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
 
 \textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.
-Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or use a computational version of a fuzzy conductor~(Kanukurthi and Reyzin~\cite{KanukurthiR09} define fuzzy conductors).
-Here, we follow the second approach.
+Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or instead of recovering $w$ produce a new consistent high-entropy secret.
+This is known as a fuzzy conductor~(the entropy is being ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
+Here, we follow the second approach and use a \emph{computational} fuzzy conductor.
 
@@
 A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
-A program is obfuscated if nothing is learnable from the program other than its input and output behavior.
+Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.
 For a point program, this means hiding all partial information about the point $w$.
@@
 We would like to tolerate errors in $t$ individual blocks.
-For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
+For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.
+This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
 With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
 For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.
-Thus, most bits $c_i$ are recoverable.
+Thus, most bits of $c_i$ are recoverable.
 To tolerate errors we choose the coins $c$ from an error-correcting code.
-Then, $c$ forms an extractible distribution of high entropy.
-This extraction may be either information-theoretic~\cite{nisan1993randomness} or computation~\cite{DBLP:conf/crypto/Krawczyk10}.
+Then, $c$ forms an distribution of high entropy.
+This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
+It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.
 Note, it is hard to recover $w$ from the value $c$.
 This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.
-
-This construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  
+Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+
 Our construction provides several advantages over previous constructions of computational fuzzy extractors:
 \begin{itemize}
-\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss in necessary in a fuzzy extractor.
+\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss is necessary in a fuzzy extractor.
 If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.
 This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.
-For an arbitrary distribution, this is at least $\log |B_t|$.
+For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.
 The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions~(see \defref{def:block guessable}).}
 \item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
-\item The first computational fuzzy extractor where block are not required to be uniformly distributed.
+\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
 Our construction simply requires a large number of blocks that are unguessable given equality queries.
@@
 This means that blocks much be drawn from distributions with super-logarithmic entropy.
-Furthermore, our distance is Hamming distance over a large alphabet~(exponential in the security parameter).
-Our construction is applicable for burst errors~\cite{gilbert1960capacity}\bnote{explain?}.
+Furthermore, our distance is Hamming distance over a large alphabet~(super-polynomial in the security parameter).
+Our construction is applicable for physical sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
 Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
@@
 Thus, our construction is not a virtual black box~(VBB) obfuscation~(where anything learnable by the circuit is simulatable using input/output behavior).
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$.
-Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides partial information.
+Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
+
+The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our construction in \secref{sec:construction} and discuss parameters and tradeoffs in \secref{sec:discussion}.
 
@@
 \label{sec:preliminaries}
-For a random variable $X = X_1,..., X_\ell$ as the concatenation of $X_i$ where each $X_i$ is over some alphabet $\mathcal{Z}$.
+For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.
 For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon)$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon$.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon_{code}$.
 \end{definition}
 
-We need one special property of the code, namely that each output bit is set to $1$ with probability $1/2$.
-
-\begin{definition}
-A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
-\end{definition}
-All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
+We note that for any code learning a few bits does not inform on the remainder of the bits.
+
+\begin{claim} 
+\label{cl:many locations ent}
+Let $C$ be a binary code and let $\mathcal{I}$ be a set of indices of $C$.  Then $\Hav(C | C_\mathcal{I}) = |C| - |\mathcal{I}|$.
+\end{claim}
+This claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
+
+%need one special property of the code, namely that each output bit is set to $1$ with probability $1/2$.
+
+%\bnote{I don't think we need this!}
+%\begin{definition}
+%A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
+%\end{definition}
+%All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
 This is true as long as $C$ contains no constant bits.
@@
 We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
-Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
+Definitions for information-theoretic fuzzy extractors and a non-interactive information-reconciliation component, known as a secure sketch, can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
 The definition of computational fuzzy extractors allows for a small probability of error.
@@
 We now define the two primitives for this approach: a computational fuzzy conductor and a (computational)~randomness extractor.
-A computational fuzzy conductor is the computational analogue of a fuzzy conductor introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
+A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+\bnote{depending on what we get from obfuscation may need this to be relaxed HILL entropy.  Would have to redo lemma below, but it is essentially the same.}
 \begin{definition}
@@
 In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.
-Thus, we do not providing enough security when $gap<0$ is small.
-Furthermore, we build a computational fuzzy conductor, noting that it can be converted to a computational fuzzy extractor using \lemref{lem:cond and cext}.%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
+Thus, we focus on providing enough security when $gap<0$.
+We build a computational fuzzy conductor, noting that it can be converted to a computational fuzzy extractor using \lemref{lem:cond and cext}.%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
 Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.
@@
 Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.
-Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be an output equiprobable $(\neigh_t, \epsilon_{code})$-error-correcting code.
+Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ %be an output equiprobable
+$(\neigh_t, \epsilon_{code})$-error-correcting code.  
 We describe $\gen, \rep$ as follows:
@@
 \begin{itemize}
-\item If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.
+\item The input $w$ is hidden in two different ways.  In locations where $c_i=1$ the block $w_i$ is information-theoretically unknown.
+In locations where $c_i=0$ it is hard to find $w_i$ given the point obfuscation.
 As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
-\item There are two possible reasons for a bit of $c_i'$ to be $1$.
+\item There are two possible reasons for a bit $c_i'$ to be $1$.
 Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.
-However if a bit of $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
+However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
 This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
-\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(\defref{def:comp fuzzy cond}).
 \end{itemize}
@@
 \subsection{Security of Construction}
-Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.
+\label{sec:sec of construction}
+Assuming virtual black-box obfuscation, we argue security in the presence of equality oracles for each block.
 The adversary is provided with equality oracles for each block individually.
-Security rests on an adversaries inability to learn the values using only \emph{adaptive} equality queries.
+Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.
 For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
-Our proof for independent and high entropy blocks is more complicated than necessary, but the structure will hold for the more complicated setting.
-The outline of the proof follows:
+Our proof for independent and high entropy blocks is more complicated than necessary, but the proof structure holds for the family of sources described in \secref{sec:supported sources}.
+The outline of the proof is to:
 
 \begin{itemize}
-\item Show that conditioned on the adversaries view there is a large set of blocks, $\mathcal{I}$, that still have a super logarithmic entropy.
-\item Show that conditioned on the values of all indices $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$.
-\item For all indices in $\mathcal{I}$, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
-\item Any two codewords, $c_1, c_2$ differing in only these positions are statistically close given the adversaries view.
-\item The set of codewords differing in these positions form a distribution with conditional entropy.  This is sufficient to show
+\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
+\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
+\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
+\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
+%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
+%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
+%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
+%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
+% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
+%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
+\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
+\bnote{I think this is wrong as currently written.  We transition from indistinguishability of all pairs to high entropy for the distribution.  This should be true but I think the argument is wrong.}
+\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
+\bnote{I am having a little trouble formalizing this.  Was hoping for HILL entropy but I don't think that's true.  Will we get relaxed HILL entropy?}
 \end{itemize}
@@
 \end{proof}
+Let $\mathcal{I}$ be the set of all indices $\{1,..., n\}$.
+Then $\Hav(C | C_{\mathcal{I}^c}) = \Hoo(C) = \ell$.
+We know show that all codewords different in only positions of $\mathcal{I}$ are indistinguishable.
 \begin{lemma}
-\label{lem:super log insist by equal queries}
-Let $W$ and $U$ be two distributions of super-logarithmic entropy.
-Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+\label{lem:codewords in I close}
+Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
+\[
+\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < \ngl(n).
+\]
 \end{lemma}
 \begin{proof}
-It suffices to show that with the probability of all responses being $0$ is overwhelming.
+Recall by assumption that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \omega(\log n)$.
+The only information about $C_i$ is contained in the query responses.
+Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with overwhelming probability all responses to $c_i$ are $0$.
+Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $1/\poly(n)$.
+Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is negligible~(occurs with probability at most $q/2^n$).
+Thus, it must occur with $1/\poly(n)$ probability when $c_i=0$.
+When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
+If this occurs with $1/\poly(n)$ probability this violates the super-logarithmic conditional min-entropy condition.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ all distinguishers are negligibly close.
+\end{proof}
+
+%\begin{lemma}
+%\bnote{what goes here?}
+%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
+%\end{lemma}
+%\begin{lemma}
+%\label{lem:super log indist by equal queries}
+%Let $W$ and $U$ be two distributions of super-logarithmic entropy.
+Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%It suffices to show that with the probability of all responses being $0$ is overwhelming.
 Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
 \bnote{Finish this proof}
-\end{proof}
-
+%\end{proof}
+
+%\begin{lemma}
+%\label{lem:code bits statistically indist}
+%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
+Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%\bnote{Do this}
+%\end{proof}
+%We can extend this lemma to the entire codeword $C$:
+%\begin{lemma}
+%For all $c_1, c_2 \in C$ we have the following: 
+%\[
+%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
+%\]
+%\end{lemma}
+The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
+\bnote{As stated above I don't think this proof is right?}
 \begin{lemma}
-\label{lem:code bits statistically indist}
-Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
-Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
+Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$
 \end{lemma}
 \begin{proof}
-\bnote{Do this}
-\end{proof}
-We can extend this lemma to the entire codeword $C$:
-\begin{lemma}
-For all $c_1, c_2 \in C$ we have the following: 
-\[
-\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
-\]
-\end{lemma}
-\begin{lemma}
-If $C$ is output then, for all $i$, $\Hav(C_i |View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)}))\geq 1 - \ngl(n)$.
-\end{lemma}
-\begin{proof}
-Since $C$ is output equiprobable we know that for each $i$, $\Pr[C_i =1 ] = 1/2$.
-Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
+Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
+%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
 For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
 \begin{align*}
-\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C_i =b | view ] &\leq 1/2 + \ngl(n)\\
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\
 \end{align*}
-If this was not true~(that is in expectation, there was some $b$ that was likely with probability greater than $1/2+1/\poly(n)$), there there would exist an unbounded adversary outputting that $b$, contradicting \lemref{lem:code bits statistically indist}).
-Taking the negative log of each side one has:
-\begin{align*}
+If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.
+\end{proof}
+\begin{corollary}
+\label{cor:avg min after view}
+$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
+\end{corollary}
+\begin{proof}
+Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
+Taking the negative log of the above lemma one has:
+\begin{align}
 \Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
- &=\\-\log \left(\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\max_{b\in\{0,1\}}\Pr[C_i =b | view ]  \right) &\geq -\log (1/2 + \ngl(n))\\
-&\geq -\log(\frac{1}{2} + \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+2}{2n^{w}}\right)\\
+ &=\nonumber \\
+ -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\nonumber \\
+&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right) \nonumber \\
 %&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
-&=1-\left(\log (1+\frac{2}{n^e}) \right)\\
-&=1-\frac{1}{\ln 2}\left(\ln (1+\frac{2}{n^e}) \right)\\
-&= 1- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{2}{n^e})^i\right) \\
-&\geq 1 - \frac{1}{\ln 2} \frac{2}{n^e} = 1-\ngl(n)
-\end{align*}
-Here the second to last line is derived using the Taylor expansion for $\ln(1+x)$ and the last line is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive.
+&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\nonumber \\
+&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \nonumber \\
+&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
+&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
+&= |C| - |\mathcal{I}^c| -\ngl(n) \label{eq:min ent}
+\end{align}
+\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
 \end{proof}
-By similar reasoning we can extend this lemma to the entire codeword:
-\begin{lemma}
-If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
-\end{lemma}
+%\begin{lemma}
+%\label{lem:obf has hill ent}
+%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.
+Let $ (X, Y)  = (C,
+%\end{proof}
+%By similar reasoning we can extend this lemma to the entire codeword:
+%\begin{lemma}
+%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
+%\end{lemma}
 %\begin{lemma}
@@
 %\end{lemma}
-\begin{corollary}
-\consref{cons:first construction} is a $XXXXX$ computational fuzzy extractor when $W = W_1,..., W_n$ all $W_i$ are independent and $\Hoo(W_i) = \omega(\log n)$.
-\end{corollary}
-\begin{proof}
-Result of security of point obfuscation and \lemref{lem:cond and cext}.
-\end{proof}
 
@@
 \end{lemma}
+
+\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
+However, this requires a codeword where most codewords have Hamming weight close to $1/2$.
 
@@
 
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for independent sources~(where each block has a super-logarithmic amount of entropy):
+\begin{corollary}
+Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq \omega(\log n)$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = |C| - o(n)$.\bnote{Why the transition from $\ngl(n)$ to $o(n)$?
+Shouldn't this be $\ngl(n)$?}
+\end{corollary}
+\begin{proof}
+Security is result of arguments in \secref{sec:sec of construction}.  Correctness follows from the arguments above and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
+\end{proof}
+
 \subsection{Supported Sources}
 \label{sec:supported sources}
-\bnote{need to complete this section and redo the proof in 3.2 with this type of source.}
-We now describe a set of high entropy sources appropriate for our construction.
-In the proof of security for these sources follows the outline presented \secref{XXXXX}.
-After giving the description of the distribution, we give examples of distributions that fit in this class and provide additional characterizations.
+\bnote{need to complete this section and redo the proof in  \secref{sec:sec of construction} with this type of source.}
+
+We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
+We need a distribution where after all of the possible equality queries, a large number of blocks still have super-logarithmic entropy.
 
@@
 \label{def:block guessable}
-Let $\mathcal{O}_{w_1,..., w_k}$ be an oracle that return $\mathcal{O}_{w_1,..., w_k}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
-A source $W = W_1||...|W_k$ is a $(q, \alpha, \ell)$-\emph{guessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $S$ of size at least $\ell$ such that
+Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that
 \[
-\forall i\in S, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
+\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
 \]
 \end{definition}
+As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
+
+\begin{theorem}
+Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$.
+Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \log |C| - \beta - o(n)$.
+\end{theorem}
+
+\subsection{Characterizing unguessable block distributions}
+\bnote{This section needs to be finished.  The point is to try and give an idea what the above definition means.  What type of distributions fulfill that definition.}
 This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.
@@
 \end{proof}
-
-\subsection{Discussion}
+\bnote{keep working}
+
+\section{Discussion}
+\label{sec:discussion}
 Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
@@
 &> \log {\ell \choose t} (2^n-1)^t\\
-&=\Omega(tn) + \log {\ell\choose t}
+&=\Theta(tn) + \log {\ell\choose t}
 % \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
 \end{align*}
-We now ask how much entropy is necessary for security?
-The first presented type of source was where each block was independent and had super-logarithmic min-entropy.
-This means that $\Hoo(W) \approx \ell \omega(\log n)$.
-Thus in the setting where $t = \omega(\ell)$ we obtain that
+\bnote{Need a good bound on ${\ell \choose t}$.}
+We now ask how much entropy is necessary for security.  The type of source we considered was independent blocks each with super-logarithmic min-entropy.  This yields 
 \[
-gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \omega(\ell n) + \log {\ell \choose t}\right)< 0. 
+gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right). 
 \]
-This \consref{cons:first construction} is the first fuzzy extractor with a negative $gap$.\footnote{We can make gap smaller by recalling that note every block must contribute fresh entropy.
-If each block is derived from a single source with super-logarithmic entropy then the starting entropy need only be $\omega(\log n)$.}
-
-\textbf{Note:} If $t = o(\ell)$ then the value of $gap$ is not clear, there are some $\ell$ for which it will be negative.
-However in the setting where $n>>\ell$ and a constant number of errors are being corrected $gap$ may be positive.
-However, we extract from at most $\ell$ bits and thus need $\ell$ to be large enough for reasonable application security.
-Setting $ \ell , t, n$ all of roughly the same size provides a natural balance of parameters.
+When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| - \ngl(n)$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+Thus, \consref{cons:first construction} achieves negative $gap$ when $t = \Theta(\ell)$.
+Furthermore, not every block must contribute entropy, so security is possible when the total starting entropy is $\omega(\log n)$.
+For example, \consref{cons:first construction} is secure when each block is equal and drawn from a distribution of super-logarithmic min-entropy.
+So there are supported sources with negative $gap$ for any value of $t$.
+We achieve $gap<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
+%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
 
 \textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
-The first is that Hamming distance is over an alphabet of exponential size, which precludes use is several major settings.
+The first is that Hamming distance is over an alphabet of exponential size, which precludes use in some applications.
 The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
-Lastly, we obtain only a single bit from each block of $W_i$, in settings where entropy is at a premium this seems wasteful.
+Lastly, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
 \bibliographystyle{alpha}

### 2014-01-14 trunk/constantRate/ConstCompFuzzExt.tex
Added notes on problems with the proof

@@
 \title{Constant Error Tolerance Computational Fuzzy Extractors}
-\author{Ran Canetti \and Benjamin Fuller\footnote{The work of B.
-Fuller is sponsored by Assistant Secretary of Defense for Research \& Engineering under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
+\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
+work was sponsored by the Department of the Air Force under Air Force
+Contract
+\#FA8721-05-C-0002.  Opinions,
+interpretations, conclusions and recommendations are those of the author
+and
+are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
 
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', p, seed)$ 
+\item \underline{Input}: $(w', p)$ 
 \item For $i=1,..., \ell$:
@@
 \subitem Else set $c_i' = 1$.
-\item Set $c = \decode$.
+\item Set $c = \decode(c')$.
 \item Output $c$.
 \end{enumerate}
-\vspace{0.45in}
+\vspace{0.15in}
 \end{minipage} 
@@
 \Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
- &=\\-\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\\
-&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right)\\
+ &=\nonumber \\
+ -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\nonumber \\
+&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right) \nonumber \\
 %&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
-&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\\
-&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \\
+&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\nonumber \\
+&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \nonumber \\
 &= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
 &\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
-&= |C| - |\mathcal{I}^c| -\ngl(n)\label{eq:min ent}
+&= |C| - |\mathcal{I}^c| -\ngl(n) \label{eq:min ent}
 \end{align}
-\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}
-Here the Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
+\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
 \end{proof}
-
 %\begin{lemma}

### 2014-01-14 constantRate/ConstCompFuzzExt.tex
Fixing proof about maximal probability outcome

@@
 \item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
-\bnote{I think this is wrong as currently written.  We transition from indistinguishability of all pairs to high entropy for the distribution.  This should be true but I think the argument is wrong.}
 \item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
@@
 The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
-\bnote{As stated above I don't think this proof is right?}
 \begin{lemma}
-Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$
+For all $c\in C|C_{\mathcal{I}^c}$, 
+\[
+\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n).
+\]
 \end{lemma}
 \begin{proof}
-Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
-%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
-For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
+We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
+\[
+\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
+\]
+Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
+Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that there exists some polynomial $1/\poly(n)$ such that 
 \begin{align*}
-\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ \frac{1}{\poly(n)} \\
 \end{align*}
-If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.
+This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $1/\poly(n)$.
+Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.
+This is a contradiction and completes the proof.
 \end{proof}
@@
 \end{align}
-\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
+\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, \omega(1)\}$ since the $\ngl$ term probably dominates the above.
+If we are more precise with the analysis above we can probably make this $\ngl$ more precise and get better bounds.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
 \end{proof}

### 2014-01-14 constantRate/ConstCompFuzzExt.tex
adding a lot on characterizing block sources

@@
 We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
-We need a distribution where after all of the possible equality queries, a large number of blocks still have super-logarithmic entropy.
+We need a distribution where after $q$-equality queries, a large number of blocks still have super-logarithmic entropy.
 
@@
 \begin{theorem}
-Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$.
+Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
 Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
@@
 \subsection{Characterizing unguessable block distributions}
-\bnote{This section needs to be finished.  The point is to try and give an idea what the above definition means.  What type of distributions fulfill that definition.}
-This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.
-However, we can show necessary and sufficient types of sources for a guessable block distribution.
-We begin by defining the entropy jump of a block source which will appear in our characterization.
-
-\begin{definition}
-Let $W = W_1,..., W_k$ be a source under ordering $i_1,..., i_k$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
-\end{definition}
+
+\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
+In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.
+
+The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
+Thus, we begin with the case of independent blocks.
 
 \begin{claim}
-Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
+\label{cl:independent high ent}
+Let $W = W_1,..., W_\ell$ be a source where blocks are independent.
+Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.
+Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
 \end{claim}
 \begin{proof}
-Suppose not, for convenience assume the ordering that violates this condition is $1,..., k$.
-We describe a distribution $W$ where $\forall 1\leq j\leq k-\ell$, $J(j)\leq \log q +\alpha$.
-Define $W$ as follows $W_1 = c_1,...., W_{j-1} = c_{j-1}$ are constants.
+We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.
+It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
+As argued in the proof of \lemref{lem:blocks unguessable after queries}, we can consider the sequence of queries without duplicates~(as duplicate queries provide no additional information and do not increase the number of possible response strings).
+Then there are at most $q+1$ possible response strings~(all strings of Hamming weight at most $1$).
+Then by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have that
+\[
+\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hav(W_i | View(A^{\mathcal{O}_{W}(i, \cdot)})) \geq \Hoo(W_i) -\log (q+1).
+\]
 \end{proof}
-\bnote{keep working}
+In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
+This is a subset of the distributions in \clref{cl:independent high ent}.
+
+We now consider more complicated~(realistic) distributions where blocks are not independent.  We begin with distributions that are block unguessable.
+
+\begin{claim}
+\label{cl:each block from single seed}
+Let $e =\omega(\log n)$ and let $f:\zo^e \rightarrow \zo^{n\times \ell}$ be a function.
+Furthermore, let $f_i$ denote the restriction of $f$'s output to the bits $[i\times n,..., i\times n+n-1]$.
+If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-block unguessable distribution.
+\end{claim}
+\begin{proof}
+Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.
+Consider a query $q_j$ on block $i$, there are two possibilities either $q_j$ is not in the image of $f_i$ on $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
+Thus, a query eliminates at most a single value of $U_e$, this holds for all blocks $i$.
+Then similarly to the proof of \clref{cl:independent high ent}, we can eliminate queries which correspond to the same value of $U_e$.
+Then the possible responses are strings with Hamming weight at most $1$ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
+\end{proof}
+
+Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.
+This claims rests on there being no easy ``entry'' point to the distribution.
+This is not always the case.
+Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.
+
+\begin{claim}
+Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
+There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+\end{claim}
+\begin{proof}
+We present an adversary $A$~(running in polynomial time) that completely determines the value $x$.
+$A$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
+Then $A$ queries on $y_1,..., y_p$ exactly one answer returns $1$.
+Let this value be $y_1^*$ and its preimage $x_1^*$.
+Then $A$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.
+Again, exactly one of these queries returns $1$.
+This process is repeated until all of $x$ is recovered.
+The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
+Once $x$ has been recovered then $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+\end{proof}
+
+The previous example relied on an adversaries ability to completely determine a block from the previous blocks.
+We formalize this notion next.
+We defining the entropy jump of a block source as the remaining entropy when other blocks are known:
+
+\begin{definition}
+Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
+\end{definition}
+
+We now show that there must be a super-logarithmic jump early enough.
+
+\begin{claim}
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $J(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
+\end{claim}
+
+%\begin{claim}
+%Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
+%\end{claim}
+\bnote{I instead of min-entropy here we want support size.  Are we okay with that?  Not sure how this adapts to average min-entropy.}
+\begin{proof}
+For convenience relabel the ordering that violates the condition as $1,..., \ell$.
+We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.
+As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
+Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.
+This process is repeated until $W_{\ell-\beta+1}$ is learned.
+Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct $W_i | W_1,.., W_{i-1}$.
+\end{proof}
 

### 2014-01-14 constantRate/ConstCompFuzzExt.tex
adding a lot on characterizing block sources

@@
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
+Let $|W|$ be the size of the support of $W$ that is $|W| = \{w | \Pr[W=w]>0\}$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
@@
 \begin{definition}
-Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
+Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $J(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
 \end{definition}
@@
 
-%\begin{claim}
-%Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
-%\end{claim}
-\bnote{I instead of min-entropy here we want support size.  Are we okay with that?  Not sure how this adapts to average min-entropy.}
 \begin{proof}
@@
 This process is repeated until $W_{\ell-\beta+1}$ is learned.
-Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct $W_i | W_1,.., W_{i-1}$.
+Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_i | W_1,.., W_{i-1}$.
 \end{proof}

### 2014-01-15 constantRate/ConstCompFuzzExt.tex
fixing proof on remaining entropy after adversary view

@@
 \label{cor:avg min after view}
-$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
+$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \omega(1) \log n\}= \min\{ |C| - |\mathcal{I}^c|,  \omega(1) \log n\}$.
 \end{corollary}
 \begin{proof}
-Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
+%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
 Taking the negative log of the above lemma one has:
@@
  -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\nonumber \\
-&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right) \nonumber \\
-%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
-&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\nonumber \\
-&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \nonumber \\
-&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
-&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
-&= |C| - |\mathcal{I}^c| -\ngl(n) \label{eq:min ent}
+ &\approx \min \{-\log P_c, -\log \ngl(n)\} \\
+ &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \omega(1) \log n\}
+%&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right) \nonumber \\
+%%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
+%&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\nonumber \\
+%&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \nonumber \\
+%&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
+%&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
+%&= |C| - |\mathcal{I}^c| -\ngl(n) \label{eq:min ent}
 \end{align}
-\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, \omega(1)\}$ since the $\ngl$ term probably dominates the above.
-If we are more precise with the analysis above we can probably make this $\ngl$ more precise and get better bounds.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
+\bnote{If we are more precise with the analysis above we can probably make this $\ngl$ more precise and get better bounds.
+For example if each block has linear entropy this should be quite good.
+Also we are doing point wise analysis, can we do better by considering each part of the code?}
 \end{proof}
@@
 Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq \omega(\log n)$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = |C| - o(n)$.\bnote{Why the transition from $\ngl(n)$ to $o(n)$?
-Shouldn't this be $\ngl(n)$?}
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\min\{ |C|, \omega(1)\log n\}$.
 \end{corollary}
@@
 Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \log |C| - \beta - o(n)$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \min\{\log |C| - \beta, \omega(1)\log n\}$.
 \end{theorem}

### 2014-01-15 constantRate/ConstCompFuzzExt.tex
converted proofs away from ngl notation

@@
 For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
+The set of $\mathcal{I}^c$ is the set of all indices not contained in $\mathcal{I}$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
@@
 In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
-The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor is designed to work rather than the family of all sources of a given min-entropy $m$.
+The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
 With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary.
 
-The work of Fuller, Meng, and Reyzin~\cite{fuller2013computational} presents two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.
+Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.
 We follow the second approach.
@@
 Let $n$ be a security parameter.
-Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.
-Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.
+Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = k = \omega(\log n)$.
+Then let $\mathcal{A}$ be an adversary making a polynomial, $q = \poly(n)$, number of oracle equality queries for blocks $i$.
 %Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}.
-Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \omega(\ell \log n)$.
+Then $\forall i, \Hav(W_i | View(A))  = k- \log (q+1)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \ell (k-\log (q+1))$.
 \end{lemma}
@@
 The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
-(There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
+(All the dependence between $W_i$ and the queries is contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
 There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
@@
 &=\Hoo(W_i) - \log |A'|\\
-&= \omega(\log n) - \log |A'|\\
-&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
+&=k - \log |A'|\\
+&=k - \log (q+1)
 \end{align*}
@@
 This argument holds for all $i$.  This completes the proof.
-%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).
-Thus,
-%\begin{align*}
-%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
-%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
-%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
-%\end{align*}
-%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).
-Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.
-Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.
-This completes the proof of the lemma.
 \end{proof}
+
+Denote by $k' = k - \log (q+1)$.
 Let $\mathcal{I}$ be the set of all indices $\{1,..., n\}$.
 Then $\Hav(C | C_{\mathcal{I}^c}) = \Hoo(C) = \ell$.
-We know show that all codewords different in only positions of $\mathcal{I}$ are indistinguishable.
+We now show that codewords that differ only positions of $\mathcal{I}$ are indistinguishable.
 \begin{lemma}
@@
 \[
-\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < \ngl(n).
+\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < 2^{k'+1}.
 \]
@@
 \begin{proof}
-Recall by assumption that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \omega(\log n)$.
+Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq k'$.
 The only information about $C_i$ is contained in the query responses.
-Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with overwhelming probability all responses to $c_i$ are $0$.
-Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $1/\poly(n)$.
-Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is negligible~(occurs with probability at most $q/2^n$).
-Thus, it must occur with $1/\poly(n)$ probability when $c_i=0$.
+Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with probability $1-2^{-k'+1}$ all responses to $c_i$ are $0$.
+Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $>2^{-k'+1}$.
+Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is at most $q/2^n$.
+Thus, it must occur with probability:
+\begin{align*}
+2^{-k'+1}&>\Pr[\text{non zero response location }i]\\
+\Pr[\text{non zero response location }i] &= \Pr[c_i =1]\Pr[\text{non zero response location }i\wedge c_i=1] \\&+ \Pr[c_i=0] \Pr[\text{non zero response location }i \wedge c_i=0]\\
+&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i=0]
+\end{align*}
+Since $n\geq k$ this yields that 
+\begin{align*}
+ \Pr[\text{non zero response location }i \wedge c_i=0] &> 2^{-k+1+\log (q+1)} - 2^{-(n+1) +\log q} \\
+ &\geq 2^{-k+1+\log (q+1)} - 2^{-k +\log (q+1)} \\
+ &\geq 2^{-(k+1) -1+ \log q} = 2^{-k'}.
+ \end{align*}
  When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
-If this occurs with $1/\poly(n)$ probability this violates the super-logarithmic conditional min-entropy condition.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ all distinguishers are negligibly close.
+If this occurs with over $2^{-k'}$ probability this violates the super-logarithmic conditional min-entropy condition.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $2^{-k'+1}$.
 \end{proof}
@@
 \begin{lemma}
+\label{lem:no codeword high prob}
 For all $c\in C|C_{\mathcal{I}^c}$, 
 \[
-\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n).
+\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-k'+1}.
 \]
@@
 Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
-Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that there exists some polynomial $1/\poly(n)$ such that 
+Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
 \begin{align*}
-\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ \frac{1}{\poly(n)} \\
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-k'+1} \\
 \end{align*}
-This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $1/\poly(n)$.
+This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-k'+1}$.
 Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.
@@
 \label{cor:avg min after view}
-$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \omega(1) \log n\}= \min\{ |C| - |\mathcal{I}^c|,  \omega(1) \log n\}$.
+$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), k'-1\} -1= \min\{ |C| - |\mathcal{I}^c|, k'-1\} -1$.
 \end{corollary}
@@
 %Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
-Taking the negative log of the above lemma one has:
-\begin{align}
+Taking the negative log of \lemref{lem:no codeword high prob} one has:
+\begin{align*}
 \Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
- &=\nonumber \\
- -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\nonumber \\
- &\approx \min \{-\log P_c, -\log \ngl(n)\} \\
- &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \omega(1) \log n\}
-%&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right) \nonumber \\
-%%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
-%&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\nonumber \\
-%&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \nonumber \\
-%&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
-%&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
-%&= |C| - |\mathcal{I}^c| -\ngl(n) \label{eq:min ent}
-\end{align}
-\bnote{If we are more precise with the analysis above we can probably make this $\ngl$ more precise and get better bounds.
-For example if each block has linear entropy this should be quite good.
-Also we are doing point wise analysis, can we do better by considering each part of the code?}
+ &= \\
+ -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-k'+1}) \\
+ &\geq \min \{-\log P_c, -\log 2^{-k'+1}\} -1\\
+ &= \min \{ \Hav(C | C_{\mathcal{I}^c}), k'-1\}-1 \\
+ & \min \{ \Hav(C | C_{\mathcal{I}^c}), k-\log(q+1)-1\}-1 
+\end{align*}
 \end{proof}
@@
 \begin{corollary}
-Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq \omega(\log n)$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\min\{ |C|, \omega(1)\log n\}$.
+Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq k= \omega(\log n)$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\min\{ |C|, k - \log s_{sec} -1\}$.
 \end{corollary}
@@
 \begin{theorem}
-Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
+Let $\mathcal{W}$ be a family of $(q, k= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
 Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \min\{\log |C| - \beta, \omega(1)\log n\}$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \min\{\log |C| - \beta, k-\log s_{sec} -1\}$.
 \end{theorem}
@@
 \label{sec:conductors}
-In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.  We first review the definition of a fuzzy conductor from~\cite{KanukurthiR09}:
+Fuzzy extractors are known to have strong upper bounds on remaining entropy based on the best error correcting codes.
+Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
+They suggest these bounds may be avoided by outputting a fresh random variable.
+This is known as a fuzzy conductor~\cite{KanukurthiR09}.
 \begin{definition}
-A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen) and ``reproduce''~(\rep), with the following properties:
+A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
 \begin{enumerate}
-\item The generate procedure $\gen$ on input $w\in \mathcal{M}$ outputs a string $y\in\zo^*$ and a helper string $p\in\zo^*$.
-\item The reproduction procedure $\rep$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\zo^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $Y, P$ were generated by $(Y, P)\leftarrow \gen(w)$, then $\rep(w', P) = Y$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
-If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep$.
+\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $y\in\zo^*$ and a helper string $p\in\zo^*$.
+\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\zo^*$ as inputs.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $Y, P$ were generated by $(Y, P)\leftarrow \gen'(w)$, then $\rep(w', P) = Y$ with probability~(over the coins of $\gen', \rep'$) at least $1-\epsilon$.
+If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
 \item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $Y$ is close to a high entropy distribution $Z$.
@@
 
-We borrow from~\cite{DBLP:journals/siamcomp/DodisORS08} the following notation:
+\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
+This motivates our use of a computational fuzzy conductor in \secref{sec:fuzzy extractors}.
+We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
 \begin{itemize}
-\item A $\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ where there is a procedure that corrects $t$ errors.
-\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
+\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
+%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
 \item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
-\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is finding the best $S$ for encoding $2^m$ points.
+\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
 \end{itemize}
@@
 \begin{lemma}
-The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}-1\leq L(\mathcal{M}, t, m) -\log (1-2\epsilon)$.
+The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
 \end{lemma}
-\begin{proof}  Assume $(\gen, \rep)$ is a fuzzy conductor with the parameters stated.
+\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
 Let $S$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $S$.
-Define $(Y, P) \leftarrow \gen(W)$.
+Define $(Y, P) \leftarrow \gen'(W)$.
 Then there must exist a distribution $Z$ with $\Hav(Z|P) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
@@
 Now applying Markov's inequality of $\max_{z} \Pr[Z=z | P=p]$, there exists a set $S_P'$ such that $\Pr[P\in S_P']>1/2$, and for all $p\in S_P'$, $\Hoo(Z| P =p ) \geq \tilde{m}-1$.
-Denote by $p^*$ a value in $S_P\cap S_P'$~(on value must exist).
+Denote by $p^*$ a value in $S_P\cap S_P'$~(one value must exist).
 Then $\mathbf{SD}((Y | P =p^* , p^*), (Z| P = p^*, p^*))\leq 2\epsilon$ and $\Hoo(Z|P=p^*)\geq \tilde{m}-1$.
@@
 Associate with every $y\in T$ some $w\in S$ which could have produced $y$ with nonzero probability given $P=p^*$, and call this map $C$.
-$C$ defines an error correcting code.
+$C$ defines an error correcting code with the required parameters.
 

### 2014-01-16 constantRate/ConstCompFuzzExt.tex
reorganized with block guessable first

@@
 Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.
-For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
-Our proof for independent and high entropy blocks is more complicated than necessary, but the proof structure holds for the family of sources described in \secref{sec:supported sources}.
-The outline of the proof is to:
+Our construction is secure as long as enough blocks are unpredictable after adaptive queries:
+
+\begin{definition}
+\label{def:block guessable}
+Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that
+\[
+\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+
+\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  The outline of the proof is to:
 
 \begin{itemize}
-\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
-\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
+\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
 \item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
@@
 \end{itemize}
+
+Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
+Then $\Hav(C | C_{\mathcal{I}^c}) \geq |C| - \beta$.
+We now show that codewords that differ only positions of $\mathcal{I}$ are indistinguishable.
+\begin{lemma}
+\label{lem:codewords in I close}
+Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
+\[
+\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < 2^{\alpha+1}.
+\]
+\end{lemma}
+\begin{proof}
+Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \alpha$.
+The only information about $C_i$ is contained in the query responses.
+Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with probability $1-2^{-\alpha+1}$ all responses to $c_i$ are $0$.
+Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $>2^{-\alpha+1}$.
+Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is at most $q/2^n$.
+Thus, it must occur with probability:
+\begin{align*}
+2^{-\alpha+1}&>\Pr[\text{non zero response location }i]\\
+\Pr[\text{non zero response location }i] &= \Pr[c_i =1]\Pr[\text{non zero response location }i\wedge c_i=1] \\&+ \Pr[c_i=0] \Pr[\text{non zero response location }i \wedge c_i=0]\\
+&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i=0]
+\end{align*}
+We now show that $n-\log q \geq \alpha$:
+\begin{claim}
+$n-\log q \geq \alpha$
+\end{claim}
+\begin{proof}
+Consider one particular $i \in \mathcal{I}$.
+It suffices to show that there exists an adversary $A$ making $q$ queries such that the remaining entropy in that block is at most $n-\log (q+1)$.
+Let $W_i$ be a distribution, consider $A$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
+After these queries, Then, the remaining min-entropy is at most:
+\begin{align*}
+\Hav(W_i | View(A)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
+&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
+&=-\log\left( 2^{-n+\log q} \right) = n-\log q
+\end{align*}
+\end{proof}
+
+We then have that:
+\begin{align*}
+ \Pr[\text{non zero response location }i \wedge c_i=0] &> 2(2^{-\alpha} - 2^{-(n+1) +\log q} )\\
+ &\geq 2\times 2^{-\alpha-1}  = 2^{-\alpha}
+ \end{align*}
+ When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
+If this occurs with over $2^{-\alpha}$ probability this violates the super-logarithmic conditional min-entropy condition.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $2^{-\alpha+1}$.
+\end{proof}
+
+%\begin{lemma}
+%\bnote{what goes here?}
+%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
+%\end{lemma}
+%\begin{lemma}
+%\label{lem:super log indist by equal queries}
+%Let $W$ and $U$ be two distributions of super-logarithmic entropy.
+Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%It suffices to show that with the probability of all responses being $0$ is overwhelming.
+Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
+\bnote{Finish this proof}
+%\end{proof}
+
+%\begin{lemma}
+%\label{lem:code bits statistically indist}
+%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
+Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%\bnote{Do this}
+%\end{proof}
+%We can extend this lemma to the entire codeword $C$:
+%\begin{lemma}
+%For all $c_1, c_2 \in C$ we have the following: 
+%\[
+%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
+%\]
+%\end{lemma}
+The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
+\begin{lemma}
+\label{lem:no codeword high prob}
+For all $c\in C|C_{\mathcal{I}^c}$, 
+\[
+\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-(\alpha-1)}.
+\]
+\end{lemma}
+\begin{proof}
+We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
+\[
+\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
+\]
+Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
+Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
+\begin{align*}
+\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-(\alpha-1)} \\
+\end{align*}
+This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-\alpha+1}$.
+Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.
+This is a contradiction and completes the proof.
+\end{proof}
+\begin{corollary}
+\label{cor:avg min after view}
+$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\} -1= \min\{ |C| - |\mathcal{I}^c|, \alpha-1\} -1$.
+\end{corollary}
+\begin{proof}
+%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
+Taking the negative log of \lemref{lem:no codeword high prob} one has:
+\begin{align*}
+\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
+ &= \\
+ -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-\alpha+1}) \\
+ &\geq \min \{-\log P_c, -\log 2^{-\alpha+1}\} -1\\
+ &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\}-1 
+\end{align*}
+\end{proof}
+%\begin{lemma}
+%\label{lem:obf has hill ent}
+%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
+%\end{lemma}
+%\begin{proof}
+%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.
+Let $ (X, Y)  = (C,
+%\end{proof}
+%By similar reasoning we can extend this lemma to the entire codeword:
+%\begin{lemma}
+%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
+%\end{lemma}
+%\begin{lemma}
+%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
+%\end{lemma}
+
+\subsection{Correctness of \consref{cons:first construction}}
+We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
+%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
+However, we start by justifying our use of unidirectional codes.
+\begin{lemma}
+\label{lem:no 1 to 0 flips}
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/2^n = \ngl(n)$.
+\end{lemma}
+\begin{proof}
+\bnote{we need to come back to this if we use obfuscation with error}
+Recall that $c$ contains at most $\ell$ $1$s.
+Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$.
+Since the $r_i$ are chosen independently, one has,
+\begin{align*}
+\Pr[\text{no $1\rightarrow 0$ flips}] &\geq 1-\Pr[\text{some }r_i = w_i']\\
+&\geq 1-\ell \frac{1}{2^n} = 1-\frac{\poly(n)}{2^n} = \ngl(n)
+\end{align*}
+\end{proof}
+
+We now consider the number of possible $0\rightarrow 1$ bit flips in $c$.
+A $0\rightarrow 1$ flip on index $i$ occurs when two conditions are met $w_i\neq w_i'$ and $c_i = 0$.
+Since the first conditioned is only fulfilled at most $t$ times, we have the following lemma:
+
+\begin{lemma}
+Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
+\[
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n}.
+\]
+That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
+\end{lemma}
+
+\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
+However, this requires a codeword where most codewords have Hamming weight close to $1/2$.
+
+%\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
+%We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
+Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
+We break the indices of $c = c_1,..., c_\ell$ into two components those where $c_i=1$ and those $c_i = 0$.
+Denote these two components by $c_{I_1}$ and $c_{I_0}$.
+Our goal is to bound how many of the places where $w, w'$ are inserted into $c_{I_0}$.
+Indices $i$,  where $w_i \neq w_i'$ and $c_i = 1$ will be ``corrected'' as $w_i'$ yield $c_i' = 1$ with overwhelming probably~(see \lemref{lem:no 1 to 0 flips}).
+Since $w_{err}$ be set of indices where $w, w'$ differ then for all $j\in w_{err}, \Pr[j\in c_{I_0}] = 1/2$.
+This is a binomial distribution with $p=1/2$ and $n=t$.
+Denote by $X =|\{j | w_j \neq w_j' \wedge j\in c_{I_1}|$.
+Thus, $\expe[X] = t/2$.
+Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
+%\begin{align*}
+%\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
+%\end{align*}
+%This leads us to the following lemma:
+%\begin{lemma}
+%\label{lem:correctness holds}
+%If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
+%\end{lemma}
+%\bnote{This analysis is done assuming that the two sets are the same size.
+Need to worry about variation in the number of $1$s and $0$s in $c$.
+Need to show that for most codes (linear?) the variance in Hamming weight is small.}
+%\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
+
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for independent sources~(where each block has a super-logarithmic amount of entropy):
+\begin{theorem}
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \min\{\log |C| - \beta, \alpha-\log s_{sec} -1\}-1$.
+\end{theorem}
+\begin{proof}
+Security is result of arguments in \secref{sec:sec of construction}.  Correctness follows from the arguments above and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
+\end{proof}
+
+%\subsection{Supported Sources}
+%\label{sec:supported sources}
+%\bnote{need to complete this section and redo the proof in  \secref{sec:sec of construction} with this type of source.}
+%
+%We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
+We need a distribution where after $q$-equality queries, a large number of blocks still have super-logarithmic entropy.
+%
+%As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
+
+\subsection{Characterizing unguessable block distributions}
+
+\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
+In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.
+
+The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
+Thus, we begin with the case of independent blocks.
 
@@
 
-Denote by $k' = k - \log (q+1)$.
-Let $\mathcal{I}$ be the set of all indices $\{1,..., n\}$.
-Then $\Hav(C | C_{\mathcal{I}^c}) = \Hoo(C) = \ell$.
-We now show that codewords that differ only positions of $\mathcal{I}$ are indistinguishable.
-\begin{lemma}
-\label{lem:codewords in I close}
-Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
-\[
-\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < 2^{k'+1}.
-\]
-\end{lemma}
-\begin{proof}
-Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq k'$.
-The only information about $C_i$ is contained in the query responses.
-Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with probability $1-2^{-k'+1}$ all responses to $c_i$ are $0$.
-Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $>2^{-k'+1}$.
-Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is at most $q/2^n$.
-Thus, it must occur with probability:
-\begin{align*}
-2^{-k'+1}&>\Pr[\text{non zero response location }i]\\
-\Pr[\text{non zero response location }i] &= \Pr[c_i =1]\Pr[\text{non zero response location }i\wedge c_i=1] \\&+ \Pr[c_i=0] \Pr[\text{non zero response location }i \wedge c_i=0]\\
-&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i=0]
-\end{align*}
-Since $n\geq k$ this yields that 
-\begin{align*}
- \Pr[\text{non zero response location }i \wedge c_i=0] &> 2^{-k+1+\log (q+1)} - 2^{-(n+1) +\log q} \\
- &\geq 2^{-k+1+\log (q+1)} - 2^{-k +\log (q+1)} \\
- &\geq 2^{-(k+1) -1+ \log q} = 2^{-k'}.
- \end{align*}
- When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
-If this occurs with over $2^{-k'}$ probability this violates the super-logarithmic conditional min-entropy condition.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $2^{-k'+1}$.
-\end{proof}
-
-%\begin{lemma}
-%\bnote{what goes here?}
-%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
-%\end{lemma}
-%\begin{lemma}
-%\label{lem:super log indist by equal queries}
-%Let $W$ and $U$ be two distributions of super-logarithmic entropy.
-Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
-%\end{lemma}
-%\begin{proof}
-%It suffices to show that with the probability of all responses being $0$ is overwhelming.
-Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
-\bnote{Finish this proof}
-%\end{proof}
-
-%\begin{lemma}
-%\label{lem:code bits statistically indist}
-%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
-Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
-%\end{lemma}
-%\begin{proof}
-%\bnote{Do this}
-%\end{proof}
-%We can extend this lemma to the entire codeword $C$:
-%\begin{lemma}
-%For all $c_1, c_2 \in C$ we have the following: 
-%\[
-%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
-%\]
-%\end{lemma}
-The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
-\begin{lemma}
-\label{lem:no codeword high prob}
-For all $c\in C|C_{\mathcal{I}^c}$, 
-\[
-\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-k'+1}.
-\]
-\end{lemma}
-\begin{proof}
-We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
-\[
-\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
-\]
-Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
-Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
-\begin{align*}
-\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-k'+1} \\
-\end{align*}
-This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-k'+1}$.
-Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.
-This is a contradiction and completes the proof.
-\end{proof}
-\begin{corollary}
-\label{cor:avg min after view}
-$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), k'-1\} -1= \min\{ |C| - |\mathcal{I}^c|, k'-1\} -1$.
-\end{corollary}
-\begin{proof}
-%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
-Taking the negative log of \lemref{lem:no codeword high prob} one has:
-\begin{align*}
-\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
- &= \\
- -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-k'+1}) \\
- &\geq \min \{-\log P_c, -\log 2^{-k'+1}\} -1\\
- &= \min \{ \Hav(C | C_{\mathcal{I}^c}), k'-1\}-1 \\
- & \min \{ \Hav(C | C_{\mathcal{I}^c}), k-\log(q+1)-1\}-1 
-\end{align*}
-\end{proof}
-%\begin{lemma}
-%\label{lem:obf has hill ent}
-%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
-%\end{lemma}
-%\begin{proof}
-%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.
-Let $ (X, Y)  = (C,
-%\end{proof}
-%By similar reasoning we can extend this lemma to the entire codeword:
-%\begin{lemma}
-%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
-%\end{lemma}
-%\begin{lemma}
-%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
-%\end{lemma}
-
-\subsection{Correctness of \consref{cons:first construction}}
-We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
-%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
-However, we start by justifying our use of unidirectional codes.
-\begin{lemma}
-\label{lem:no 1 to 0 flips}
-The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/2^n = \ngl(n)$.
-\end{lemma}
-\begin{proof}
-\bnote{we need to come back to this if we use obfuscation with error}
-Recall that $c$ contains at most $\ell$ $1$s.
-Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$.
-Since the $r_i$ are chosen independently, one has,
-\begin{align*}
-\Pr[\text{no $1\rightarrow 0$ flips}] &\geq 1-\Pr[\text{some }r_i = w_i']\\
-&\geq 1-\ell \frac{1}{2^n} = 1-\frac{\poly(n)}{2^n} = \ngl(n)
-\end{align*}
-\end{proof}
-
-We now consider the number of possible $0\rightarrow 1$ bit flips in $c$.
-A $0\rightarrow 1$ flip on index $i$ occurs when two conditions are met $w_i\neq w_i'$ and $c_i = 0$.
-Since the first conditioned is only fulfilled at most $t$ times, we have the following lemma:
-
-\begin{lemma}
-Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
-\[
-\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n}.
-\]
-That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
-\end{lemma}
-
-\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
-However, this requires a codeword where most codewords have Hamming weight close to $1/2$.
-
-%\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
-%We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
-Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
-We break the indices of $c = c_1,..., c_\ell$ into two components those where $c_i=1$ and those $c_i = 0$.
-Denote these two components by $c_{I_1}$ and $c_{I_0}$.
-Our goal is to bound how many of the places where $w, w'$ are inserted into $c_{I_0}$.
-Indices $i$,  where $w_i \neq w_i'$ and $c_i = 1$ will be ``corrected'' as $w_i'$ yield $c_i' = 1$ with overwhelming probably~(see \lemref{lem:no 1 to 0 flips}).
-Since $w_{err}$ be set of indices where $w, w'$ differ then for all $j\in w_{err}, \Pr[j\in c_{I_0}] = 1/2$.
-This is a binomial distribution with $p=1/2$ and $n=t$.
-Denote by $X =|\{j | w_j \neq w_j' \wedge j\in c_{I_1}|$.
-Thus, $\expe[X] = t/2$.
-Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
-%\begin{align*}
-%\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
-%\end{align*}
-%This leads us to the following lemma:
-%\begin{lemma}
-%\label{lem:correctness holds}
-%If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
-%\end{lemma}
-%\bnote{This analysis is done assuming that the two sets are the same size.
-Need to worry about variation in the number of $1$s and $0$s in $c$.
-Need to show that for most codes (linear?) the variance in Hamming weight is small.}
-%\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
-
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for independent sources~(where each block has a super-logarithmic amount of entropy):
-\begin{corollary}
-Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq k= \omega(\log n)$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\min\{ |C|, k - \log s_{sec} -1\}$.
-\end{corollary}
-\begin{proof}
-Security is result of arguments in \secref{sec:sec of construction}.  Correctness follows from the arguments above and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
-\end{proof}
-
-\subsection{Supported Sources}
-\label{sec:supported sources}
-\bnote{need to complete this section and redo the proof in  \secref{sec:sec of construction} with this type of source.}
-
-We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
-We need a distribution where after $q$-equality queries, a large number of blocks still have super-logarithmic entropy.
-
-\begin{definition}
-\label{def:block guessable}
-Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that
-\[
-\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
-
-\begin{theorem}
-Let $\mathcal{W}$ be a family of $(q, k= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \min\{\log |C| - \beta, k-\log s_{sec} -1\}$.
-\end{theorem}
-
-\subsection{Characterizing unguessable block distributions}
-
-\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
-In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.
-
-The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
-Thus, we begin with the case of independent blocks.
-
 \begin{claim}

### 2014-01-16 constantRate/ConstCompFuzzExt.tex
reorganized with block guessable first

@@
 Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
-Then $\Hav(C | C_{\mathcal{I}^c}) \geq |C| - \beta$.
-We now show that codewords that differ only positions of $\mathcal{I}$ are indistinguishable.
+Then $\Hav(C | C_{\mathcal{I}^c}) \geq |C| - \beta$~(by \clref{cl:many locations ent}).
+We now show that codewords differing in positions of $\mathcal{I}$ are indistinguishable.
 \begin{lemma}
@@
 
-\begin{lemma}
-\label{lem:blocks unguessable after queries}
-Let $n$ be a security parameter.
-Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = k = \omega(\log n)$.
-Then let $\mathcal{A}$ be an adversary making a polynomial, $q = \poly(n)$, number of oracle equality queries for blocks $i$.
-%Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}.
-Then $\forall i, \Hav(W_i | View(A))  = k- \log (q+1)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \ell (k-\log (q+1))$.
-\end{lemma}
-\begin{proof}
-Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
-Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
-Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
-We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
-The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
-(All the dependence between $W_i$ and the queries is contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
-There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
-If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
-These responses can be removed as the response is deterministic.
-Let $A'$ represent the sequence with all duplicate queries removed.
-This sequence has at most a single $1$.
-Thus, the total number of possible responses is $q+1$.
-Thus, we have the following,
-\begin{align*}
-\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
-&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
-&=\Hav(W_i |A') \\
-&=\Hoo(W_i) - \log |A'|\\
-&=k - \log |A'|\\
-&=k - \log (q+1)
-\end{align*}
-Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
-This argument holds for all $i$.  This completes the proof.
-\end{proof}
-
 \begin{claim}
@@
 Let $W = W_1,..., W_\ell$ be a source where blocks are independent.
+Let $\alpha$ be a parameter.
 Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.
@@
 It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
-As argued in the proof of \lemref{lem:blocks unguessable after queries}, we can consider the sequence of queries without duplicates~(as duplicate queries provide no additional information and do not increase the number of possible response strings).
-Then there are at most $q+1$ possible response strings~(all strings of Hamming weight at most $1$).
-Then by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have that
-\[
-\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hav(W_i | View(A^{\mathcal{O}_{W}(i, \cdot)})) \geq \Hoo(W_i) -\log (q+1).
-\]
+Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
+Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
+Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
+We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
+The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
+Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
+There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
+If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
+These responses can be removed as the response is deterministic.
+Let $A'$ represent the sequence with all duplicate queries removed.
+This sequence has at most a single $1$.
+Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).
+Thus, we have the following,
+\begin{align*}
+\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
+&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
+&=\Hav(W_i |A') \\
+&=\Hoo(W_i) - \log |A'|\\
+&=\alpha - \log |A'|\\
+&=\alpha - \log (q+1)
+\end{align*}
+Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
+This argument holds for all $i$.  This completes the proof.
 \end{proof}
@@
 Correction occurs for a small number of dimensions that are allowed to vary completely.
-As described in \secref{sec:supported sources}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
+As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
 

### 2014-01-20 trunk/constantRate/ConstCompFuzzExt.tex
revised proof outline

@@
 For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
+The set of $\mathcal{I}^c$ is the set of all indices not contained in $\mathcal{I}$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
+Let $|W|$ be the size of the support of $W$ that is $|W| = \{w | \Pr[W=w]>0\}$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
@@
 A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-\bnote{depending on what we get from obfuscation may need this to be relaxed HILL entropy.  Would have to redo lemma below, but it is essentially the same.}
 \begin{definition}
@@
 Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.
-For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
-Our proof for independent and high entropy blocks is more complicated than necessary, but the proof structure holds for the family of sources described in \secref{sec:supported sources}.
-The outline of the proof is to:
-
+Our construction is secure as long as enough blocks are unpredictable after adaptive queries:
+
+\begin{definition}
+\label{def:block guessable}
+Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
+\begin{cases}
+1 & w_i = w_i'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that
+\[
+\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+
+%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  
+We now show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
+To show security it is sufficient to show that there exists a distribution $C'$ such that $\Hav(C' | P) \geq k$ and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
+Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
+First note that $\Hav(C' |P) =\Hav(C' | \mathcal{I}^c) =  \Hav|C'| = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).
+It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.
+Define the distribution $X$ as follows:
+\[X_i = 
+\begin{cases}
+W_i & C_i = 0\\
+R_i & C_i = 1.
+\end{cases}\]
+The outline for the rest of the proof is as follows:
 \begin{itemize}
-\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
-\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
-\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
-\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
-%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
-%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
-%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
-%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
-% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
-%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
-\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
-\bnote{I think this is wrong as currently written.  We transition from indistinguishability of all pairs to high entropy for the distribution.  This should be true but I think the argument is wrong.}
-\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
-\bnote{I am having a little trouble formalizing this.  Was hoping for HILL entropy but I don't think that's true.  Will we get relaxed HILL entropy?}
+\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
+\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ cannot distinguish between $C$ and $C'$.
+That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
+This is done in \lemref{lem:sim cannot distinguish}.
+% the following steps:
+%\begin{itemize}
+%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
+%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
+%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
+%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
+%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
+%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
+%\end{itemize}
+\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
 \end{itemize}
 
+Together these arguments allow us to conclude:
+\begin{theorem}
+\label{thm:security of cons}
+Let $\mathcal{O}$ be a virtual black box obfuscator \bnote{fill in parameters for auxiliary and composability} \bnote{need to link parameters for obfuscation and block unguessable} for point programs of hardness $s_{obf}, \epsilon_{obf}$.
+Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + 2^{-(\alpha - 1)}$.
+\end{theorem}
+
+We now prove $S$ cannot distinguish between $C$ and $C'$.  
+Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
+Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
 \begin{lemma}
-\label{lem:blocks unguessable after queries}
-Let $n$ be a security parameter.
-Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.
-Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.
-%Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}.
-Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \omega(\ell \log n)$.
+\label{lem:sim cannot distinguish}
+$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < 2^{-(\alpha+1)}$.
 \end{lemma}
+
 \begin{proof}
-Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
-Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
-Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
-We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
-The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
-(There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
-There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
-If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
-These responses can be removed as the response is deterministic.
-Let $A'$ represent the sequence with all duplicate queries removed.
-This sequence has at most a single $1$.
-Thus, the total number of possible responses is $q+1$.
-Thus, we have the following,
-\begin{align*}
-\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
-&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
-&=\Hav(W_i |A') \\
-&=\Hoo(W_i) - \log |A'|\\
-&= \omega(\log n) - \log |A'|\\
-&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
-\end{align*}
-Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
-This argument holds for all $i$.  This completes the proof.
-%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).
-Thus,
-%\begin{align*}
-%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
-%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
-%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
-%\end{align*}
-%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).
-Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.
-Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.
-This completes the proof of the lemma.
-\end{proof}
-Let $\mathcal{I}$ be the set of all indices $\{1,..., n\}$.
-Then $\Hav(C | C_{\mathcal{I}^c}) = \Hoo(C) = \ell$.
-We know show that all codewords different in only positions of $\mathcal{I}$ are indistinguishable.
+\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is $2^{-(\alpha+1)}$.
 \begin{lemma}
@@
 \[
-\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < \ngl(n).
+\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c_1), S^{\mathcal{O}_X(\cdot, \cdot)}(c_2)) < 2^{-(\alpha+1)}.
 \]
@@
 \begin{proof}
-Recall by assumption that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \omega(\log n)$.
-The only information about $C_i$ is contained in the query responses.
-Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with overwhelming probability all responses to $c_i$ are $0$.
-Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $1/\poly(n)$.
-Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is negligible~(occurs with probability at most $q/2^n$).
-Thus, it must occur with $1/\poly(n)$ probability when $c_i=0$.
+Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
+The only information about the correct value of the codeword is contained in the query responses.
+Let $c^*\in C | C_{\mathcal{I}^c}$ be the value that was used to generate $X$.
+It suffices to show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
+Suppose not, that is suppose, the probability of at least one nonzero response is $> 2^{-(\alpha+1)}$.
+Since $w, w'$ are independent of $p$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$.
+Thus, it must occur with probability:
+\begin{align*}
+2^{-\alpha+1}&>\Pr[\text{non zero response location }i]\\
+\Pr[\text{non zero response location }i] &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1] \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\\
+&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i^*=0]
+\end{align*}
+We now show that $n-\log q \geq \alpha$:
+\begin{claim}
+$n-\log q \geq \alpha$
+\end{claim}
+\begin{proof}
+Consider one particular $i \in \mathcal{I}$.
+It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log (q+1)$.
+Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
+After these queries, Then, the remaining min-entropy is at most:
+\begin{align*}
+\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
+&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
+&=-\log\left( 2^{-n+\log q} \right) = n-\log q
+\end{align*}
+\end{proof}
+
+We then have that:
+\begin{align*}
+ \Pr[\text{non zero response location }i \wedge c_i=0] &> 2(2^{-\alpha} - 2^{-(n+1) +\log q} )\\
+ &\geq 2\times 2^{-\alpha-1}  = 2^{-\alpha}
+ \end{align*}
  When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
-If this occurs with $1/\poly(n)$ probability this violates the super-logarithmic conditional min-entropy condition.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ all distinguishers are negligibly close.
+If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $2^{-\alpha+1}$.
+This concludes the proof of \lemref{lem:codewords in I close}
 \end{proof}
-
+Since point wise the two distributions are close we can conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < 2^{-(\alpha+1)}$.
+This completes the proof of \lemref{lem:sim cannot distinguish}.
+\end{proof}
+
+%The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
 %\begin{lemma}
-%\bnote{what goes here?}
-%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
-%\end{lemma}
-%\begin{lemma}
-%\label{lem:super log indist by equal queries}
-%Let $W$ and $U$ be two distributions of super-logarithmic entropy.
-Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+%\label{lem:no codeword high prob}
+%For all $c\in C|C_{\mathcal{I}^c}$, 
+%\[
+%\expe_{View(S)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(S)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-(\alpha-1)}.
+%\]
 %\end{lemma}
 %\begin{proof}
-%It suffices to show that with the probability of all responses being $0$ is overwhelming.
-Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
-\bnote{Finish this proof}
+%We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
+%\[
+%\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
+%\]
+%Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
+%Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
+%\begin{align*}
+%\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-(\alpha-1)} \\
+%\end{align*}
+%This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-\alpha+1}$.
+Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.
+This is a contradiction and completes the proof.
 %\end{proof}
-
-%\begin{lemma}
-%\label{lem:code bits statistically indist}
-%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
-Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
-%\end{lemma}
+%\begin{corollary}
+%\label{cor:avg min after view}
+%$\Hav(C| View(S))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\} -1= \min\{ |C| - |\mathcal{I}^c|, \alpha-1\} -1$.
+%\end{corollary}
 %\begin{proof}
-%\bnote{Do this}
+%%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
+%Taking the negative log of \lemref{lem:no codeword high prob} one has:
+%\begin{align*}
+%\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
+% &= \\
+% -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-\alpha+1}) \\
+% &\geq \min \{-\log P_c, -\log 2^{-\alpha+1}\} -1\\
+% &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\}-1 
+%\end{align*}
 %\end{proof}
-%We can extend this lemma to the entire codeword $C$:
-%\begin{lemma}
-%For all $c_1, c_2 \in C$ we have the following: 
-%\[
-%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
-%\]
-%\end{lemma}
-The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
-\bnote{As stated above I don't think this proof is right?}
-\begin{lemma}
-Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$
-\end{lemma}
-\begin{proof}
-Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
-%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
-For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$.
-\begin{align*}
-\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\
-\end{align*}
-If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.
-\end{proof}
-\begin{corollary}
-\label{cor:avg min after view}
-$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
-\end{corollary}
-\begin{proof}
-Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
-Taking the negative log of the above lemma one has:
-\begin{align}
-\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
- &=\nonumber \\
- -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\nonumber \\
-&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right) \nonumber \\
-%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
-&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\nonumber \\
-&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \nonumber \\
-&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
-&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
-&= |C| - |\mathcal{I}^c| -\ngl(n) \label{eq:min ent}
-\end{align}
-\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
-\end{proof}
-%\begin{lemma}
-%\label{lem:obf has hill ent}
-%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
-%\end{lemma}
-%\begin{proof}
-%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.
-Let $ (X, Y)  = (C,
-%\end{proof}
-%By similar reasoning we can extend this lemma to the entire codeword:
-%\begin{lemma}
-%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
-%\end{lemma}
-%\begin{lemma}
-%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
-%\end{lemma}
 
@@
 \begin{lemma}
+\label{lem:correct of cons}
 Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
@@
 
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for independent sources~(where each block has a super-logarithmic amount of entropy):
-\begin{corollary}
-Let $\mathcal{W}$ be the family of block distributions where $W_i$ are independent and $\Hoo(W_i) \geq \omega(\log n)$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = |C| - o(n)$.\bnote{Why the transition from $\ngl(n)$ to $o(n)$?
-Shouldn't this be $\ngl(n)$?}
-\end{corollary}
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for block unguessable distributions:
+\begin{theorem}
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+\end{theorem}
 \begin{proof}
-Security is result of arguments in \secref{sec:sec of construction}.  Correctness follows from the arguments above and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
+Security is result of \thref{thm:security of cons}.  Correctness follows from \lemref{lem:correct of cons} and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
 \end{proof}
 
-\subsection{Supported Sources}
-\label{sec:supported sources}
-\bnote{need to complete this section and redo the proof in  \secref{sec:sec of construction} with this type of source.}
-
-We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
-We need a distribution where after all of the possible equality queries, a large number of blocks still have super-logarithmic entropy.
-
-\begin{definition}
-\label{def:block guessable}
-Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that
-\[
-\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
-
-\begin{theorem}
-Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$.
-Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \log |C| - \beta - o(n)$.
-\end{theorem}
+%\subsection{Supported Sources}
+%\label{sec:supported sources}
+%\bnote{need to complete this section and redo the proof in  \secref{sec:sec of construction} with this type of source.}
+%
+%We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
+We need a distribution where after $q$-equality queries, a large number of blocks still have super-logarithmic entropy.
+%
+%As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
 
 \subsection{Characterizing unguessable block distributions}
-\bnote{This section needs to be finished.  The point is to try and give an idea what the above definition means.  What type of distributions fulfill that definition.}
-This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.
-However, we can show necessary and sufficient types of sources for a guessable block distribution.
-We begin by defining the entropy jump of a block source which will appear in our characterization.
-
-\begin{definition}
-Let $W = W_1,..., W_k$ be a source under ordering $i_1,..., i_k$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
-\end{definition}
+
+\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
+In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.
+
+The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
+Thus, we begin with the case of independent blocks.
 
 \begin{claim}
-Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
+\label{cl:independent high ent}
+Let $W = W_1,..., W_\ell$ be a source where blocks are independent.
+Let $\alpha$ be a parameter.
+Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.
+Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
 \end{claim}
 \begin{proof}
-Suppose not, for convenience assume the ordering that violates this condition is $1,..., k$.
-We describe a distribution $W$ where $\forall 1\leq j\leq k-\ell$, $J(j)\leq \log q +\alpha$.
-Define $W$ as follows $W_1 = c_1,...., W_{j-1} = c_{j-1}$ are constants.
+We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.
+It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
+Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
+Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
+Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
+We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
+The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
+Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
+There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
+If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
+These responses can be removed as the response is deterministic.
+Let $A'$ represent the sequence with all duplicate queries removed.
+This sequence has at most a single $1$.
+Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).
+Thus, we have the following,
+\begin{align*}
+\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
+&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
+&=\Hav(W_i |A') \\
+&=\Hoo(W_i) - \log |A'|\\
+&=\alpha - \log |A'|\\
+&=\alpha - \log (q+1)
+\end{align*}
+Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
+This argument holds for all $i$.  This completes the proof.
 \end{proof}
-\bnote{keep working}
+In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
+This is a subset of the distributions in \clref{cl:independent high ent}.
+
+We now consider more complicated~(realistic) distributions where blocks are not independent.  We begin with distributions that are block unguessable.
+
+\begin{claim}
+\label{cl:each block from single seed}
+Let $e =\omega(\log n)$ and let $f:\zo^e \rightarrow \zo^{n\times \ell}$ be a function.
+Furthermore, let $f_i$ denote the restriction of $f$'s output to the bits $[i\times n,..., i\times n+n-1]$.
+If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-block unguessable distribution.
+\end{claim}
+\begin{proof}
+Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.
+Consider a query $q_j$ on block $i$, there are two possibilities either $q_j$ is not in the image of $f_i$ on $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
+Thus, a query eliminates at most a single value of $U_e$, this holds for all blocks $i$.
+Then similarly to the proof of \clref{cl:independent high ent}, we can eliminate queries which correspond to the same value of $U_e$.
+Then the possible responses are strings with Hamming weight at most $1$ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
+\end{proof}
+
+Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.
+This claims rests on there being no easy ``entry'' point to the distribution.
+This is not always the case.
+Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.
+
+\begin{claim}
+Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
+There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+\end{claim}
+\begin{proof}
+We present an adversary $A$~(running in polynomial time) that completely determines the value $x$.
+$A$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
+Then $A$ queries on $y_1,..., y_p$ exactly one answer returns $1$.
+Let this value be $y_1^*$ and its preimage $x_1^*$.
+Then $A$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.
+Again, exactly one of these queries returns $1$.
+This process is repeated until all of $x$ is recovered.
+The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
+Once $x$ has been recovered then $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+\end{proof}
+
+The previous example relied on an adversaries ability to completely determine a block from the previous blocks.
+We formalize this notion next.
+We defining the entropy jump of a block source as the remaining entropy when other blocks are known:
+
+\begin{definition}
+Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $J(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
+\end{definition}
+
+\noindent
+We now show that there must be a super-logarithmic jump early enough.
+
+\begin{claim}
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $J(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
+\end{claim}
+
+\begin{proof}
+For convenience relabel the ordering that violates the condition as $1,..., \ell$.
+We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.
+As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
+Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.
+This process is repeated until $W_{\ell-\beta+1}$ is learned.
+Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_i | W_1,.., W_{i-1}$.
+\end{proof}
 

### 2014-01-21 trunk/constantRate/ConstCompFuzzExt.tex
Cleaned up revised proof of first construction

@@
 Fuzzy extractors derive strong keys from noisy sources.
-The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly key distributed key.
+The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly distributed key.
 Traditionally, their security is defined information-theoretically.
@@
 Fuller, Meng, and Reyzin (Asiacrypt 2013) hypothesize that these bounds can be overcome by only providing security against computationally-bounded adversaries. 
-%They provide a construction of a computational fuzzy extractor that corrects a small number of errors without any loss in key length.
-%They show the feasibility of constructing a computational fuzzy extractor that does not suffer from the information-theoretic bounds.
-%Unfortunately, their construction is limited to very high entropy distributions and does not significantly beat information-theoretic bounds.
-In addition, we significantly improve on the allowable error rate and the required entropy rate of each block.
-In particular we construct the following:
 In this work, we provide the first construction of a fuzzy extractor for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.
@@
 \textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.  
-%Let $W = W_1, ..., W_\ell$ be a source distribution composed of blocks over a large alphabet, $Z$.
-To obfuscate a sample $w$ drawn from $W$.
-We flip a coin $c_i$ for each block and either obfuscate the block $w_i$ or a random point in $Z$.
-When a close reading $w'$ is given as input, we can recover most of the coins $c_i$.
-Error-tolerance is achieved by sampling $c = c_1,..., c_\ell$ from an error-correcting code.
 Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  
-%Security holds as long as a large number of blocks $W_i$ of $W$  are unpredictable given equality queries on individual blocks.  
 Our construction provides the following novel features:
@@
 \item Constant error tolerance rate.  
-%Previous constructions of computational fuzzy extractors corrected a logarithmic fraction of errors.
-(Information-theoretic constructions support a constant fraction of errors but are subject to bounds described above.)
-\item Security for a large and meaningful class of distributions.
-%The main requirement for security is that most blocks have a super-logarithmic amount of entropy.
-Previous computational fuzzy extractors required the source to be essentially uniform.
+\item Security for a large and meaningful class of distributions.  \bnote{this description needs to be better}.
 \end{itemize}
@@
 However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).
-To use noisy physical sources in applications, two problems must be addressed.
+\bnote{add more examples here} To use noisy physical sources in applications, two problems must be addressed.
 The first is ensuring the same value is obtained from every reading of the source.
 This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).
-The second is converting a source with entropy to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).
+The second is converting the entropic source to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).
 Both of these problems have interactive and non-interactive versions.
-For a single user~(trying to produce the same key from multiple readings of a physical source) non-interactive solutions are appropriate.
+For a single user~(trying to produce the same key from multiple readings of a physical source) the non-interactive solutions are appropriate.
 We focus on this setting.
@@
 For the remainder of this paper we denote this quantity by $gap$.
-This represents a real problem as important biometrics~(such as irises~\cite{daugman2004}) have $gap <0$ and current fuzzy extractors provide no security guarantee.
+This represents a real problem, important biometrics, such as irises~\cite{daugman2004}, have $gap <0$ and current fuzzy extractors provide no security guarantee.
 
@@
 
-However, this does not need to be the case in the computational setting.
+This does not need to be the case in the computational setting.
 Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.
@@
 This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.
-A necessary condition for security is that a negligible portion of the probability distribution lies within any Hamming ball of radius $t$.
+A necessary condition for security is that a negligible portion of the source's probability distribution lies within any Hamming ball of radius $t$.
 We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).
@@
 In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
-Our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
+Our focus is on expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
 
 \textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.
-Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or instead of recovering $w$ produce a new consistent high-entropy secret.
-This is known as a fuzzy conductor~(the entropy is being ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
+Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.
+This is known as a fuzzy conductor~(the entropy is ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
 Here, we follow the second approach and use a \emph{computational} fuzzy conductor.
@@
 To tolerate errors we choose the coins $c$ from an error-correcting code.
-Then, $c$ forms an distribution of high entropy.
+The set of possible codewords forms a high entropy distribution.
 This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
@@
 For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.
-The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions~(see \defref{def:block guessable}).}
+The distributions supported by our construction are not error-correcting codes, we require unpredictability in many dimensions~(see \defref{def:block guessable}).}
 \item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
@@
 For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
-The set of $\mathcal{I}^c$ is the set of all indices not contained in $\mathcal{I}$.
+The set $\mathcal{I}^c$ is the complement of $\mathcal{I}$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-Let $|W|$ be the size of the support of $W$ that is $|W| = \{w | \Pr[W=w]>0\}$.
+Let $|W|$ be the size of the support of $W$ that is $|W| = |\{w | \Pr[W=w]>0\}|$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
@@
 For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
-For the Hamming metric, $|B_t| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
+For the Hamming metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).
+Codes where $\log |C| = \Theta(\ell)$ and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
 
@@
 \label{cl:many locations ent}
-Let $C$ be a binary code and let $\mathcal{I}$ be a set of indices of $C$.  Then $\Hav(C | C_\mathcal{I}) = |C| - |\mathcal{I}|$.
+Let $C$ be a binary code and let $\mathcal{I}^c$ be a set of indices of $C$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \log |C| - |\mathcal{I}^c|$.
 \end{claim}
@@
 %\end{definition}
-%All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).
+%All binary linear codes~(without constant bits) are output equiprobable and .
 This is true as long as $C$ contains no constant bits.
@@
 Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
+\bnote{We never need to run our simulator so I think we can use virtual gray-box.}
 \end{enumerate}
@@
 \end{definition}
-In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
+In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness.
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
@@
 In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.
-Instead of using a fuzzy conductor, we define a computational version.
+To overcome these bounds, we use a computational version of a fuzzy conductor.
 We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
@@
 Thus, we focus on providing enough security when $gap<0$.
-We build a computational fuzzy conductor, noting that it can be converted to a computational fuzzy extractor using \lemref{lem:cond and cext}.%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
+We build a computational fuzzy conductor, which can be converted to a computational fuzzy extractor using a computational extractor~(\lemref{lem:cond and cext}).%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
 Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.
@@
 \item \underline{Input}: $w = w_1,..., w_\ell$
-\item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
+\item Sample $c\leftarrow C$.
 \item For $i=1,..., \ell$:
 \subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
-\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
+\subitem Else: Sample $r_i \leftarrow U_n$. 
 \subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
@@
 \item For $i=1,..., \ell$:
-\subitem If $p_i(w_i') = 1$ set $c_i' = 0$.
-\subitem Else set $c_i' = 1$.
+\subitem If $p_i(w_i') = 1$: set $c_i' = 0$.
+\subitem Else: set $c_i' = 1$.
 \item Set $c = \decode(c')$.
@@
 \label{sec:sec of construction}
+\bnote{this paragraph needs to be rewritten}
 Assuming virtual black-box obfuscation, we argue security in the presence of equality oracles for each block.
@@
 %\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  
-We now show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
-To show security it is sufficient to show that there exists a distribution $C'$ such that $\Hav(C' | P) \geq k$ and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
+We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
+To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
 Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
-First note that $\Hav(C' |P) =\Hav(C' | \mathcal{I}^c) =  \Hav|C'| = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).
+First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).
 It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.
@@
 \label{thm:security of cons}
-Let $\mathcal{O}$ be a virtual black box obfuscator \bnote{fill in parameters for auxiliary and composability} \bnote{need to link parameters for obfuscation and block unguessable} for point programs of hardness $s_{obf}, \epsilon_{obf}$.
+Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
 Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
-Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + 2^{-(\alpha - 1)}$.
+Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
 \end{theorem}
 
+\noindent
 We now prove $S$ cannot distinguish between $C$ and $C'$.  
@@
 \label{lem:sim cannot distinguish}
-$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < 2^{-(\alpha+1)}$.
+$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
 \end{lemma}
@@
 \begin{proof}
-\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is $2^{-(\alpha+1)}$.
+\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
 \begin{lemma}
 \label{lem:codewords in I close}
-Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
+Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then, 
 \[
-\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c_1), S^{\mathcal{O}_X(\cdot, \cdot)}(c_2)) < 2^{-(\alpha+1)}.
+\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
 \]
@@
 Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
-The only information about the correct value of the codeword is contained in the query responses.
-Let $c^*\in C | C_{\mathcal{I}^c}$ be the value that was used to generate $X$.
-It suffices to show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
-Suppose not, that is suppose, the probability of at least one nonzero response is $> 2^{-(\alpha+1)}$.
-Since $w, w'$ are independent of $p$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$.
+The only information about the correct value of $c_i^*$ is contained in the query responses.
+When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
+We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
+Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
+Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
 Thus, it must occur with probability:
-\begin{align*}
-2^{-\alpha+1}&>\Pr[\text{non zero response location }i]\\
-\Pr[\text{non zero response location }i] &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1] \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\\
-&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i^*=0]
-\end{align*}
+\begin{align}
+2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
+ &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
+&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
+\end{align}
 We now show that $n-\log q \geq \alpha$:
 \begin{claim}
+\label{cl:ent bounded away from n}
 $n-\log q \geq \alpha$
@@
 \begin{proof}
-Consider one particular $i \in \mathcal{I}$.
-It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log (q+1)$.
+It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.
 Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
-After these queries, Then, the remaining min-entropy is at most:
+After these queries the remaining min-entropy is at most:
 \begin{align*}
@@
 \end{align*}
+This completes the proof of \clref{cl:ent bounded away from n}.
 \end{proof}
-
-We then have that:
+\noindent
+Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
 \begin{align*}
- \Pr[\text{non zero response location }i \wedge c_i=0] &> 2(2^{-\alpha} - 2^{-(n+1) +\log q} )\\
- &\geq 2\times 2^{-\alpha-1}  = 2^{-\alpha}
+ \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
  \end{align*}
@@
 If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $2^{-\alpha+1}$.
+By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
 This concludes the proof of \lemref{lem:codewords in I close}
 \end{proof}
-Since point wise the two distributions are close we can conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < 2^{-(\alpha+1)}$.
+By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
 This completes the proof of \lemref{lem:sim cannot distinguish}.
@@
 \begin{proof}
-Security is result of \thref{thm:security of cons}.  Correctness follows from \lemref{lem:correct of cons} and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
+Security is a result of \thref{thm:security of cons} because $2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}$ is negligible when $\epsilon_{obf} = \ngl(n), \ell = \poly(n)$ and $\alpha =\omega(\log n)$.
+Correctness follows from \lemref{lem:correct of cons} and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
 \end{proof}

### 2014-01-24 constantRate/ConstCompFuzzExt.tex
working on second construction

@@
 Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.
-Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ %be an output equiprobable
+Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
 $(\neigh_t, \epsilon_{code})$-error-correcting code.  
@@
 \end{center}
-\label{cons:informal construction}
 \end{construction}
@@
 \label{def:block guessable}
-Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that
+Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
+\begin{cases}
+1 & w_i = w_i'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that
 \[
@@
 
-\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  The outline of the proof is to:
-
+%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  
+We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
+To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
+Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
+First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).
+It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.
+Define the distribution $X$ as follows:
+\[X_i = 
+\begin{cases}
+W_i & C_i = 0\\
+R_i & C_i = 1.
+\end{cases}\]
+The outline for the rest of the proof is as follows:
 \begin{itemize}
-\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
-\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
-\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
-%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
-%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
-%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
-%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
-% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
-%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
-\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
-\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
-\bnote{I am having a little trouble formalizing this.  Was hoping for HILL entropy but I don't think that's true.  Will we get relaxed HILL entropy?}
+\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
+\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ cannot distinguish between $C$ and $C'$.
+That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
+This is done in \lemref{lem:sim cannot distinguish}.
+% the following steps:
+%\begin{itemize}
+%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
+%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
+%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
+%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
+%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
+%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
+%\end{itemize}
+\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
 \end{itemize}
 
+Together these arguments allow us to conclude:
+\begin{theorem}
+\label{thm:security of cons}
+Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
+Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
+\end{theorem}
+
+\noindent
+We now prove $S$ cannot distinguish between $C$ and $C'$.  
 Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
-Then $\Hav(C | C_{\mathcal{I}^c}) \geq |C| - \beta$~(by \clref{cl:many locations ent}).
-We now show that codewords differing in positions of $\mathcal{I}$ are indistinguishable.
+Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
+\begin{lemma}
+\label{lem:sim cannot distinguish}
+$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
+\end{lemma}
+
+\begin{proof}
+\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
 \begin{lemma}
 \label{lem:codewords in I close}
-Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
+Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then, 
 \[
-\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < 2^{\alpha+1}.
+\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
 \]
@@
 \begin{proof}
-Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \alpha$.
-The only information about $C_i$ is contained in the query responses.
-Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with probability $1-2^{-\alpha+1}$ all responses to $c_i$ are $0$.
-Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $>2^{-\alpha+1}$.
-Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is at most $q/2^n$.
+Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
+The only information about the correct value of $c_i^*$ is contained in the query responses.
+When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
+We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
+Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
+Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
 Thus, it must occur with probability:
-\begin{align*}
-2^{-\alpha+1}&>\Pr[\text{non zero response location }i]\\
-\Pr[\text{non zero response location }i] &= \Pr[c_i =1]\Pr[\text{non zero response location }i\wedge c_i=1] \\&+ \Pr[c_i=0] \Pr[\text{non zero response location }i \wedge c_i=0]\\
-&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i=0]
-\end{align*}
+\begin{align}
+2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
+ &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
+&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
+\end{align}
 We now show that $n-\log q \geq \alpha$:
 \begin{claim}
+\label{cl:ent bounded away from n}
 $n-\log q \geq \alpha$
@@
 \begin{proof}
-Consider one particular $i \in \mathcal{I}$.
-It suffices to show that there exists an adversary $A$ making $q$ queries such that the remaining entropy in that block is at most $n-\log (q+1)$.
-Let $W_i$ be a distribution, consider $A$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
-After these queries, Then, the remaining min-entropy is at most:
+It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.
+Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
+After these queries the remaining min-entropy is at most:
 \begin{align*}
-\Hav(W_i | View(A)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
+\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
 &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
@@
 \end{align*}
+This completes the proof of \clref{cl:ent bounded away from n}.
 \end{proof}
-
-We then have that:
+\noindent
+Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
 \begin{align*}
- \Pr[\text{non zero response location }i \wedge c_i=0] &> 2(2^{-\alpha} - 2^{-(n+1) +\log q} )\\
- &\geq 2\times 2^{-\alpha-1}  = 2^{-\alpha}
+ \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
  \end{align*}
  When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
-If this occurs with over $2^{-\alpha}$ probability this violates the super-logarithmic conditional min-entropy condition.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $2^{-\alpha+1}$.
+If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
+By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
+This concludes the proof of \lemref{lem:codewords in I close}
 \end{proof}
-
+By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
+This completes the proof of \lemref{lem:sim cannot distinguish}.
+\end{proof}
+
+%The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
 %\begin{lemma}
-%\bnote{what goes here?}
-%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
-%\end{lemma}
-%\begin{lemma}
-%\label{lem:super log indist by equal queries}
-%Let $W$ and $U$ be two distributions of super-logarithmic entropy.
-Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
+%\label{lem:no codeword high prob}
+%For all $c\in C|C_{\mathcal{I}^c}$, 
+%\[
+%\expe_{View(S)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(S)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-(\alpha-1)}.
+%\]
 %\end{lemma}
 %\begin{proof}
-%It suffices to show that with the probability of all responses being $0$ is overwhelming.
-Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.
-\bnote{Finish this proof}
-%\end{proof}
-
-%\begin{lemma}
-%\label{lem:code bits statistically indist}
-%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.
-Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
-%\end{lemma}
-%\begin{proof}
-%\bnote{Do this}
-%\end{proof}
-%We can extend this lemma to the entire codeword $C$:
-%\begin{lemma}
-%For all $c_1, c_2 \in C$ we have the following: 
+%We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
 %\[
-%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
+%\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
 %\]
-%\end{lemma}
-The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
-\begin{lemma}
-\label{lem:no codeword high prob}
-For all $c\in C|C_{\mathcal{I}^c}$, 
-\[
-\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-(\alpha-1)}.
-\]
-\end{lemma}
-\begin{proof}
-We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
-\[
-\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
-\]
-Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
-Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
-\begin{align*}
-\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-(\alpha-1)} \\
-\end{align*}
-This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-\alpha+1}$.
+%Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
+%Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
+%\begin{align*}
+%\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-(\alpha-1)} \\
+%\end{align*}
+%This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-\alpha+1}$.
 Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.
 This is a contradiction and completes the proof.
-\end{proof}
-\begin{corollary}
-\label{cor:avg min after view}
-$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\} -1= \min\{ |C| - |\mathcal{I}^c|, \alpha-1\} -1$.
-\end{corollary}
-\begin{proof}
-%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
-Taking the negative log of \lemref{lem:no codeword high prob} one has:
-\begin{align*}
-\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
- &= \\
- -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-\alpha+1}) \\
- &\geq \min \{-\log P_c, -\log 2^{-\alpha+1}\} -1\\
- &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\}-1 
-\end{align*}
-\end{proof}
-%\begin{lemma}
-%\label{lem:obf has hill ent}
-%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
-%\end{lemma}
+%\end{proof}
+%\begin{corollary}
+%\label{cor:avg min after view}
+%$\Hav(C| View(S))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\} -1= \min\{ |C| - |\mathcal{I}^c|, \alpha-1\} -1$.
+%\end{corollary}
 %\begin{proof}
-%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.
-Let $ (X, Y)  = (C,
+%%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
+%Taking the negative log of \lemref{lem:no codeword high prob} one has:
+%\begin{align*}
+%\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
+% &= \\
+% -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-\alpha+1}) \\
+% &\geq \min \{-\log P_c, -\log 2^{-\alpha+1}\} -1\\
+% &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\}-1 
+%\end{align*}
 %\end{proof}
-%By similar reasoning we can extend this lemma to the entire codeword:
-%\begin{lemma}
-%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
-%\end{lemma}
-%\begin{lemma}
-%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
-%\end{lemma}
 
@@
 
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for independent sources~(where each block has a super-logarithmic amount of entropy):
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for block unguessable distributions:
 \begin{theorem}
@@
 Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \min\{\log |C| - \beta, \alpha-\log s_{sec} -1\}-1$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
 \begin{proof}
-Security is result of arguments in \secref{sec:sec of construction}.  Correctness follows from the arguments above and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
+Security is a result of \thref{thm:security of cons} because $2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}$ is negligible when $\epsilon_{obf} = \ngl(n), \ell = \poly(n)$ and $\alpha =\omega(\log n)$.
+Correctness follows from \lemref{lem:correct of cons} and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
 \end{proof}
@@
 \begin{align*}
-\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
+\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
 &=\Hav(W_i | A_{w_1},..., A_{w_q})\\
@@
 
+\noindent
 We now show that there must be a super-logarithmic jump early enough.
@@
 
-\section{Discussion}
+\subsection{Discussion}
 \label{sec:discussion}
@@
 \textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
-The first is that Hamming distance is over an alphabet of exponential size, which precludes use in some applications.
-The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
-Lastly, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
+The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
+Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
+Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications.
+We begin to address this weakness in the next section.
+
+\section{Reducing Alphabet Size}
+\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
+Unfortunately, each block is individually obfuscated causing the blocks to be of super-polynomial size~(our analysis was in the case where the blocks where exponential in the security parameter).
+In this section, we present a generalization of \consref{cons:first construction} where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.
+Unfortunately, obfuscated multiple blocks together decreases the effective error tolerance.
+\begin{construction}
+\label{cons:sampling}
+Let $n$ be a security parameter.
+Let $Z$ be an alphabet where $|Z| = \Omega(n)$, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.
+Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
+Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.
+Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^\eta$.
+Define $\gen, \rep$ as:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\gamma$
+\item Sample $c\leftarrow C$.
+\item For $i=1,..., \ell$:
+\begin{itemize}
+\item Sample $j_{i, 1},..., j_{i, \eta}\overset{\$}\leftarrow \{1,..., \gamma\}$
+\item If $c_i = 0$: 
+\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
+\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
+\subitem Set $p_i = \rho_i, j_{i, 1},..., j_{i, \eta}$.
+\item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
+\subitem Let $p_i = \mathcal{O}(I_{r_i}) j_{i,1},..., j_{i, \eta}$.
+\end{itemize}
+\item Output $(c, p)$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p)$ 
+\item For $i=1,..., \ell$:
+\begin{itemize}
+\item Parse $p_i$ as $\rho_i, j_{i, 1},..., j_{i, \eta}$.
+\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
+\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
+\item Else set $c_i' = 1$.
+\end{itemize}
+\item Set $c = \decode(c')$.
+\item Output $c$.
+\end{enumerate}
+\vspace{0.37in}
+\end{minipage} 
+\end{tabular}
+\end{center}
+\end{construction}
+
+The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.
+In the setting where each symbol of $W$ is long enough for secure obfuscation, \consref{cons:sampling} is essentially the same as \consref{cons:first construction}.
+As before we must show security and correctness of \consref{cons:sampling}.
+For security, the main argument is that each of the $v_i$ created has enough entropy to be unguessable.
+We show this in the setting of block fixing sources~\cite{KZ07}.
+This argument comes from the sampling literature~(used to create locally computable randomness extractors~\cite{lu2002hyper,vadhan2003constructing}).
+For correctness we must show that the probability for each symbol $v_i \neq v_i'$ is a small constant so that $c'$ will be corrected to $c$.
+
+\subsection{Security of \consref{cons:sampling}}
+In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has entropy on its own.
+Consider a source with entropy $\lambda$.
+Then the expected entropy of
+\begin{align*}
+\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
+&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
+\end{align*}
+This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.
+
+\bnote{something something about by sampling theory the prob of this being more than constant from expected value is negligible.}
+\bnote{need to finish this}
+
+\subsection{Correctness of \consref{cons:sampling}}
+The argument that $1\rightarrow 0$ flips are extremely unlikely carries over from \consref{cons:first construction}.
+In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.
+Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.
+Then
+\begin{align*}
+\Pr[v_i = v_i' ] &= \Pr[w_{j_{i,1}} = w_{j_{i,1}}' \wedge ... \wedge w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
+&=\Pr[w_{j_{i,1}} = w_{j_{i,1}}'] \times ... \times \Pr[w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
+&=\left (1-\frac{t}{\gamma}\right)^{\eta}
+\end{align*} 
+This value is $\Theta(1)$ when $t = \Theta(\frac{\gamma }{\eta})$.
+\bnote{finish}
+
+\subsection{Discussion}
+As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
+\begin{align*}
+gap &= \Hoo(W) -\log |B_t| \\
+&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
+&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
+&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
+&= \omega(\frac{\gamma \log n}{\eta})
+\end{align*}
+%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
+\bnote{finish}
 \bibliographystyle{alpha}

### 2014-01-28 trunk/constantRate/ConstCompFuzzExt.tex
Adding outline for sampling construction

@@
 \textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
-The first is that Hamming distance is over an alphabet of exponential size, which precludes use in some applications.
-The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
-Lastly, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
+The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
+Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
+Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications.
+We begin to address this weakness in the next section.
+
+\section{Sample-then-Obfuscate}
+\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
+In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.
+This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.
+Second, it allows us to decrease the size of each block from exponential to a super polynomial $2^{\log^c n}$ for some $c>0$.
+Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
+
+\begin{construction}
+\label{cons:sampling}
+Let $n$ be a security parameter.
+Let $Z$ be an alphabet where $|Z| = \omega(\poly(n))$, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.
+Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
+Let $\sample_\beta(\gamma)$ output a uniform subset of indices of $1,..., \gamma$ of size $\beta$.
+Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.
+Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^\eta$.
+Define $\gen, \rep$ as:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\gamma$
+\item Sample $c\leftarrow C$.
+\item For $i=1,..., \ell$:
+\begin{itemize}
+\item Sample $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_\eta(\gamma)$
+\item If $c_i = 0$: 
+\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
+\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
+\subitem Set $p_i = \rho_i, j_{i, 1},..., j_{i, \eta}$.
+\item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
+\subitem Let $p_i = \mathcal{O}(I_{r_i}) j_{i,1},..., j_{i, \eta}$.
+\end{itemize}
+\item Output $(c, p)$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p)$ 
+\item For $i=1,..., \ell$:
+\begin{itemize}
+\item Parse $p_i$ as $\rho_i, j_{i, 1},..., j_{i, \eta}$.
+\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
+\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
+\item Else set $c_i' = 1$.
+\end{itemize}
+\item Set $c = \decode(c')$.
+\item Output $c$.
+\end{enumerate}
+\vspace{0.37in}
+\end{minipage} 
+\end{tabular}
+\end{center}
+\end{construction}
+
+The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.
+This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
+For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
+There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
+
+As before we must show security and correctness of \consref{cons:sampling}.
+For security, the main argument is that each of the $v_i$ created has enough entropy to be unguessable.
+For correctness we must show that the probability for each symbol $v_i \neq v_i'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.
+
+\subsection{Security of \consref{cons:sampling}}
+In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has entropy on its own.
+From here security follows as the set of $V_1,..., V_\ell$ is a block-unguessable distribution and then overall security follows by \thref{thm:security of cons}.
+Consider a source with entropy $\lambda$.
+Then the expected entropy of
+\begin{align*}
+\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
+&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
+\end{align*}
+This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.
+Note this is independent of how the entropy is distributed between blocks.
+In particular, we make no assumptions about particular blocks being unguessable, only about the overall entropy rate.
+This is a much more natural condition for a source than \defref{def:block guessable}.
+To show security we need the entropy of all $v_i$ to be $\omega(\log n)$ with overwhelming probability.
+This follows by an argument from the locally computable extractor literature.
+
+\begin{theorem}
+\label{th:samp sec}
+Let $n$ be a security parameter and let $Z$ be some super-polynomially size alphabet.  Let $W = W_1,..., W_\gamma$ be a distribution where each $W_i$ is over $Z$.  Let 
+\[
+\Hoo(W) = \omega\left(\frac{\gamma \log n}{\eta}\right),
+\] 
+then for all $i$ and for all values of $j_{1,1},..., j_{\ell, \eta}$ the distribution $\delta(V_i | j_{1,1},..., j_{\ell, \eta} , V'_i ) <\epsilon_{sam}$ where $\Hoo(V_i') = \omega(\log n)$.
+\end{theorem}
+
+\begin{corollary}
+\label{cor:samp unguess}
+Let $n, Z, W$ be as in \thref{th:samp sec}, then for all $j_{1,1},..., j_{\ell, \eta}$, $V | j_{1,1},..., j_{\ell,\eta}$ is $\epsilon_{sam}$ close to a $(\poly(n), \alpha = \omega(\log n), 0)$-block unguessable distribution.
+In particular, If $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = 2\epsilon_{obf} + \ell(\epsilon_{sam} + 2^{-(\alpha-1)})$.
+\end{corollary}
+\begin{proof}
+Direct result of \thref{th:samp sec}, \bnote{need a claim saying if all $W_i$ have entropy, we are block unguessable}, and \thref{thm:security of cons}.
+\end{proof}
+
+\bnote{something something about by sampling theory the prob of this being more than constant from expected value is negligible.}
+\bnote{need to finish this}
+
+\subsection{Correctness of \consref{cons:sampling}}
+The argument that $1\rightarrow 0$ flips are extremely unlikely carries over from \consref{cons:first construction}.
+In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.
+Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.
+Then
+\begin{align*}
+\Pr[v_i = v_i' ] &= \Pr[w_{j_{i,1}} = w_{j_{i,1}}' \wedge ... \wedge w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
+&=\Pr[w_{j_{i,1}} = w_{j_{i,1}}'] \times ... \times \Pr[w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
+&=\left (1-\frac{t}{\gamma}\right)^{\eta}
+\end{align*} 
+This value is $\Theta(1)$ when $t = \Theta(\frac{\gamma }{\eta})$.
+\bnote{finish, Chernoff, not far from expectation.}
+
+\subsection{Discussion}
+\bnote{need to write this once we have parameters in the two sections above.}
+%As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
+%\begin{align*}
+%gap &= \Hoo(W) -\log |B_t| \\
+%&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
+%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
+%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
+%&= \omega(\frac{\gamma \log n}{\eta})
+%\end{align*}
+%%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
+%\bnote{finish}
 \bibliographystyle{alpha}

### 2014-01-29 constantRate/ConstCompFuzzExt.tex
Working on sampler stuff

@@
 
-\section{Reducing Alphabet Size}
+\section{Sample-then-Obfuscate}
 \consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
-Unfortunately, each block is individually obfuscated causing the blocks to be of super-polynomial size~(our analysis was in the case where the blocks where exponential in the security parameter).
-In this section, we present a generalization of \consref{cons:first construction} where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.
-Unfortunately, obfuscated multiple blocks together decreases the effective error tolerance.
+In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.
+This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.
+Second, it allows us to decrease the size of each block from exponential to a super polynomial $2^{\log^c n}$ for some $c>0$.
+Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
+In ordering for sampling to work properly, we need a source that is likely contribute some entropy from a randomly chosen block.
+
+\begin{definition}
+\label{def:unordered source}
+A distribution $W = W_1,..., W_\gamma$ is called a $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}, W_{i+1}=w_{i+1},..., W_\gamma = w_\gamma) \geq \alpha.
+\]
+\end{definition}
+
+\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.
+This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
 \begin{construction}
@@
 Let $n$ be a security parameter.
-Let $Z$ be an alphabet where $|Z| = \Omega(n)$, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.
+Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.
 Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
+Let $\sample_\beta(\gamma)$ output a uniform subset of indices of $1,..., \gamma$ of size $\beta$.
 Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.
-Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^\eta$.
+Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.
 Define $\gen, \rep$ as:
@@
 \begin{itemize}
-\item Sample $j_{i, 1},..., j_{i, \eta}\overset{\$}\leftarrow \{1,..., \gamma\}$
+\item Sample $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_\eta(\gamma)$
 \item If $c_i = 0$: 
@@
 The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.
-In the setting where each symbol of $W$ is long enough for secure obfuscation, \consref{cons:sampling} is essentially the same as \consref{cons:first construction}.
+This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
+For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
+There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
+Our construction uses the na\"{i}ve sampler that takes truly random samples, the analysis is essentially the same for more sophisticated samplers that use fewer random bits.
+Goldreich provides an accessible introduction to samplers~\cite{goldreich1997sample}.
+
 As before we must show security and correctness of \consref{cons:sampling}.
-For security, the main argument is that each of the $v_i$ created has enough entropy to be unguessable.
-We show this in the setting of block fixing sources~\cite{KZ07}.
-This argument comes from the sampling literature~(used to create locally computable randomness extractors~\cite{lu2002hyper,vadhan2003constructing}).
-For correctness we must show that the probability for each symbol $v_i \neq v_i'$ is a small constant so that $c'$ will be corrected to $c$.
+For security, the main argument is that each of the $v_i$ has enough entropy to be unguessable.
+For correctness we must show that the induced error rate in $v$ and $v'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.
 
@@
 In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has entropy on its own.
+This means that  $V_1,..., V_\ell$ is a block-unguessable distribution and security follows by \thref{thm:security of cons}.
 Consider a source with entropy $\lambda$.
-Then the expected entropy of
-\begin{align*}
-\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
-&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
-\end{align*}
-This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.
+The expected number of selected blocks that have entropy at least $\alpha$ is $\frac{\gamma-\beta}{\gamma} \times \beta$.
+A good sampler selects a within a constant fraction of the expected number of these blocks.
+
+\begin{lemma}
+\bnote{write a lemma about this}
+\end{lemma}
+%\begin{align*}
+%\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
+%&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
+%\end{align*}
+%This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.
+Note this is independent of how the entropy is distributed between blocks.
+In particular, we make no assumptions about particular blocks being unguessable, only about the overall entropy rate.
+This is a much more natural condition for a source than \defref{def:block guessable}.
+%To show security we need the entropy of all $v_i$ to be $\omega(\log n)$ with overwhelming probability.  This follows by an argument from the locally computable extractor literature.
+
+\begin{theorem}
+\label{th:samp sec}
+Let $n$ be a security parameter and let $Z$ be some super-polynomially size alphabet.  Let $W = W_1,..., W_\gamma$ be a distribution where each $W_i$ is over $Z$.  Let 
+\[
+\Hoo(W) = \omega\left(\frac{\gamma \log n}{\eta}\right),
+\] 
+then for all $i$ and for all values of $j_{1,1},..., j_{\ell, \eta}$ the distribution $\delta(V_i | j_{1,1},..., j_{\ell, \eta} , V'_i ) <\epsilon_{sam}$ where $\Hoo(V_i') = \omega(\log n)$.\bnote{I think $\epsilon_{sam}$ will be a negligible for resultant entropy of $O(\beta \times \alpha \times (\mathcal{I}-\beta)/\mathcal{I})$.}
+\end{theorem}
+
+\begin{corollary}
+\label{cor:samp unguess}
+Let $n, Z, W$ be as in \thref{th:samp sec}, then for all $j_{1,1},..., j_{\ell, \eta}$, $V | j_{1,1},..., j_{\ell,\eta}$ is $\epsilon_{sam}$ close to a $(\poly(n), \alpha = \omega(\log n), 0)$-block unguessable distribution.
+In particular, If $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = 2\epsilon_{obf} + \ell(\epsilon_{sam} + 2^{-(\alpha-1)})$.
+\end{corollary}
+\begin{proof}
+Direct result of \thref{th:samp sec}, \bnote{need a claim saying if all $W_i$ have entropy, we are block unguessable}, and \thref{thm:security of cons}.
+\end{proof}
 
@@
 This value is $\Theta(1)$ when $t = \Theta(\frac{\gamma }{\eta})$.
-\bnote{finish}
+\bnote{finish, Chernoff, not far from expectation.}
 
 \subsection{Discussion}
-As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
-\begin{align*}
-gap &= \Hoo(W) -\log |B_t| \\
-&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
-&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
-&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
-&= \omega(\frac{\gamma \log n}{\eta})
-\end{align*}
-%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
-\bnote{finish}
+\bnote{need to write this once we have parameters in the two sections above.}
+%As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
+%\begin{align*}
+%gap &= \Hoo(W) -\log |B_t| \\
+%&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
+%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
+%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
+%&= \omega(\frac{\gamma \log n}{\eta})
+%\end{align*}
+%%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
+%\bnote{finish}
 \bibliographystyle{alpha}

### 2014-01-30 constantRate/ConstCompFuzzExt.tex
preliminary proof of security of sampling cons

@@
 
-\section{A Constant Rate Computational Fuzzy Extractor}
+\section{A Constant Error-Tolerance Computational Fuzzy Extractor}
 \label{sec:construction}
@@
 We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
+In \apref{sec:characterize} we provide discussion on the types of sources that satisfy \defref{def:block guessable}.
 To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
@@
 %As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
-
-\subsection{Characterizing unguessable block distributions}
-
-\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
-In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.
-
-The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
-Thus, we begin with the case of independent blocks.
-
-\begin{claim}
-\label{cl:independent high ent}
-Let $W = W_1,..., W_\ell$ be a source where blocks are independent.
-Let $\alpha$ be a parameter.
-Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.
-Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
-\end{claim}
-\begin{proof}
-We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.
-It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
-Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
-Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
-Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
-We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
-The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
-Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
-There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
-If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
-These responses can be removed as the response is deterministic.
-Let $A'$ represent the sequence with all duplicate queries removed.
-This sequence has at most a single $1$.
-Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).
-Thus, we have the following,
-\begin{align*}
-\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
-&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
-&=\Hav(W_i |A') \\
-&=\Hoo(W_i) - \log |A'|\\
-&=\alpha - \log |A'|\\
-&=\alpha - \log (q+1)
-\end{align*}
-Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
-This argument holds for all $i$.  This completes the proof.
-\end{proof}
-In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
-This is a subset of the distributions in \clref{cl:independent high ent}.
-
-We now consider more complicated~(realistic) distributions where blocks are not independent.  We begin with distributions that are block unguessable.
-
-\begin{claim}
-\label{cl:each block from single seed}
-Let $e =\omega(\log n)$ and let $f:\zo^e \rightarrow \zo^{n\times \ell}$ be a function.
-Furthermore, let $f_i$ denote the restriction of $f$'s output to the bits $[i\times n,..., i\times n+n-1]$.
-If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-block unguessable distribution.
-\end{claim}
-\begin{proof}
-Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.
-Consider a query $q_j$ on block $i$, there are two possibilities either $q_j$ is not in the image of $f_i$ on $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
-Thus, a query eliminates at most a single value of $U_e$, this holds for all blocks $i$.
-Then similarly to the proof of \clref{cl:independent high ent}, we can eliminate queries which correspond to the same value of $U_e$.
-Then the possible responses are strings with Hamming weight at most $1$ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
-\end{proof}
-
-Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.
-This claims rests on there being no easy ``entry'' point to the distribution.
-This is not always the case.
-Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.
-
-\begin{claim}
-Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
-There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
-\end{claim}
-\begin{proof}
-We present an adversary $A$~(running in polynomial time) that completely determines the value $x$.
-$A$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
-Then $A$ queries on $y_1,..., y_p$ exactly one answer returns $1$.
-Let this value be $y_1^*$ and its preimage $x_1^*$.
-Then $A$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.
-Again, exactly one of these queries returns $1$.
-This process is repeated until all of $x$ is recovered.
-The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
-Once $x$ has been recovered then $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
-\end{proof}
-
-The previous example relied on an adversaries ability to completely determine a block from the previous blocks.
-We formalize this notion next.
-We defining the entropy jump of a block source as the remaining entropy when other blocks are known:
-
-\begin{definition}
-Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $J(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
-\end{definition}
-
-\noindent
-We now show that there must be a super-logarithmic jump early enough.
-
-\begin{claim}
-Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $J(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
-\end{claim}
-
-\begin{proof}
-For convenience relabel the ordering that violates the condition as $1,..., \ell$.
-We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.
-As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
-Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.
-This process is repeated until $W_{\ell-\beta+1}$ is learned.
-Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_i | W_1,.., W_{i-1}$.
-\end{proof}
 
@@
 \subsection{Security of \consref{cons:sampling}}
-In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has entropy on its own.
-This means that  $V_1,..., V_\ell$ is a block-unguessable distribution and security follows by \thref{thm:security of cons}.
+In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has super-logarithmic entropy on its own.
+This means that  $V_1,..., V_\ell$ is a block-unguessable distribution~(by \clref{cl:all blocks entropy}) and security follows by \thref{thm:security of cons}.
 Consider a source with entropy $\lambda$.
 The expected number of selected blocks that have entropy at least $\alpha$ is $\frac{\gamma-\beta}{\gamma} \times \beta$.
-A good sampler selects a within a constant fraction of the expected number of these blocks.
+A good sampler selects within a constant fraction of the expected number of these blocks.
 
 \begin{lemma}
-\bnote{write a lemma about this}
+\label{lem:sampling works}
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.
+Let $\eta = \Omega(\log n)$.
+Consider some fixed $i$, the distribution $V_{i}, J_{i, 1},..., J_{i, \eta}$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{\beta\times \log \gamma}$ where for all $u\in U_{\beta \times \log \gamma}$ $V' | A=a$, $\Hoo(V' | A=a) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.\bnote{need to come up with the right number of coins for $\sample$}
 \end{lemma}
+\begin{proof}
+By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.
+\bnote{need someone to check parameters, I am fairly sure of the quality of the statement}
+\end{proof}
 %\begin{align*}
@@
 
-\begin{theorem}
-\label{th:samp sec}
-Let $n$ be a security parameter and let $Z$ be some super-polynomially size alphabet.  Let $W = W_1,..., W_\gamma$ be a distribution where each $W_i$ is over $Z$.  Let 
-\[
-\Hoo(W) = \omega\left(\frac{\gamma \log n}{\eta}\right),
-\] 
-then for all $i$ and for all values of $j_{1,1},..., j_{\ell, \eta}$ the distribution $\delta(V_i | j_{1,1},..., j_{\ell, \eta} , V'_i ) <\epsilon_{sam}$ where $\Hoo(V_i') = \omega(\log n)$.\bnote{I think $\epsilon_{sam}$ will be a negligible for resultant entropy of $O(\beta \times \alpha \times (\mathcal{I}-\beta)/\mathcal{I})$.}
-\end{theorem}
+\begin{corollary}
+\label{cor:samp sec}
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.  Let $\eta = \Omega(\log n)$.  
+The distribution $V, J$ is $\epsilon_{sam}(\ell (\ngl(n) +2^{-\Omega(n)})) = \ngl(n)$-close to a distribution $V', U_{\beta\times \ell \times \log \gamma}$ where for $u\in U_{\beta\times \ell\times \log \gamma}$ for all $i$, $\Hoo(V_i' | U_{\beta\times \ell \times \log \gamma}) \geq \alpha'$.
+\end{corollary}
+\begin{proof}
+Union bound over the statistical distance in \lemref{lem:sampling works}.
+\end{proof}
+
+\begin{corollary}
+\label{cor:v are unguessable}
+Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\beta \times \log \gamma}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
+\end{corollary}
+\begin{proof}
+Result of \clref{cl:all blocks entropy}.
+\end{proof}
 
@@
 \label{cor:samp unguess}
-Let $n, Z, W$ be as in \thref{th:samp sec}, then for all $j_{1,1},..., j_{\ell, \eta}$, $V | j_{1,1},..., j_{\ell,\eta}$ is $\epsilon_{sam}$ close to a $(\poly(n), \alpha = \omega(\log n), 0)$-block unguessable distribution.
-In particular, If $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = 2\epsilon_{obf} + \ell(\epsilon_{sam} + 2^{-(\alpha-1)})$.
+Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha-1)}) = \ngl(n)$.
 \end{corollary}
 \begin{proof}
-Direct result of \thref{th:samp sec}, \bnote{need a claim saying if all $W_i$ have entropy, we are block unguessable}, and \thref{thm:security of cons}.
-\end{proof}
-
-\bnote{something something about by sampling theory the prob of this being more than constant from expected value is negligible.}
-\bnote{need to finish this}
+Result of \corref{cor:v are unguessable} and \thref{thm:security of cons}.
+\end{proof}
 
@@
 %\end{proof}
+
+\section{Characterizing unguessable block distributions}
+\label{sec:characterize}
+
+\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
+In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
+The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
+Thus, we begin with the case of independent blocks.
+
+\begin{claim}
+\label{cl:independent high ent}
+Let $W = W_1,..., W_\ell$ be a source where blocks are independent.
+Let $\alpha$ be a parameter.
+Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.
+Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
+\end{claim}
+\begin{proof}
+We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.
+It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
+Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we ignore all other blocks as they are independent).  
+Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
+Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
+We assume a deterministic adversary~(we assume the best coins are in nonuniform advice).
+The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
+Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
+There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
+If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
+These responses can be removed as the response is deterministic.
+Let $A'$ represent the sequence with all duplicate queries removed.
+This sequence has at most a single $1$.
+Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).
+Thus, we have the following,
+\begin{align*}
+\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
+&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
+&=\Hav(W_i |A') \\
+&=\Hoo(W_i) - \log |A'|\\
+&=\alpha - \log |A'|\\
+&=\alpha - \log (q+1)
+\end{align*}
+Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
+This argument holds for all $i$.  This completes the proof.
+\end{proof}
+In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
+\clref{cl:independent high ent} captures this type of distribution.
+We now consider more complicated distributions where blocks are not independent.
+
+\begin{claim}
+\label{cl:each block from single seed}
+Let $e =\omega(\log n)$ and let $f:\zo^e \rightarrow \zo^{n\times \ell}$ be a function.
+Furthermore, let $f_i$ denote the restriction of $f$'s output to the bits $[i\times n,..., i\times n+n-1]$.
+If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-block unguessable distribution.
+\end{claim}
+\begin{proof}
+Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.
+Consider a query $q_j$ on block $i$, there are two possibilities either $q_j$ is not in the image of $f_i$ on $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
+Thus, a query eliminates at most a single value of $U_e$, this holds for all blocks $i$.
+Then similarly to the proof of \clref{cl:independent high ent}, we can eliminate queries which correspond to the same value of $U_e$.
+Then the possible responses are strings with Hamming weight at most $1$ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
+\end{proof}
+
+Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.
+We can prove a similar claim in the case where $f$ is not injectiveall blocks do not a source~(determined by $f$).
+
+\begin{claim}
+\label{cl:all blocks entropy}
+Let $W = W_1,..., W_\ell$ be a source.
+Let $\alpha =\omega(\log n)$ and suppose that for all $i$ $\Hoo(W_i)\geq \alpha$, then for $q = \poly(n)$, $\alpha ' = \omega(\log n)$, $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
+\end{claim}
+\begin{proof}
+Consider a particular block $W_i$, it suffices to show that $\Hav(W_i | Q_1,A_1,..., Q_q, A_q) \geq \omega(\log n)$.  By the definition of conditional min-entropy:
+\begin{align*}
+\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &= -\log (\Pr[\text{some non zero response}] \max_{w\in W_i} \Pr[W_i | \text{non zero response}) \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i| \text{all zero responses}])\\
+&\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}]).
+\end{align*}
+It suffices to show that $\Pr[\text{some non zero response}] = \ngl(n)$ and that $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = \ngl(n)$.  We show each of these is turn.
+
+First note that clearly the 1st query returns $1$ with $2^{-\alpha}$ probability~(due to the min-entropy condition).
+Conditioned on this response being $0$ the probability of all other events increases by at most negligible amount~(the statistical distance between the original distribution and the distribution conditioned on the first response being $0$ is $\ngl(n)$).
+Thus, the total probability of a $1$ is at most:
+\[
+\Pr[\text{some non zero response}] \leq 2^{-\alpha} + (2^{-\alpha}+\ngl(n)) + ... +(2^{-\alpha}+q\times \ngl(n)) = \ngl(n).
+\]
+Now consider $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}]$.  For each zero response, the probability of any $w_i$ increases by at most a negligible amount, this means that 
+\[\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = 2^{-\alpha} + q\times \ngl(n) = \ngl(n).\]
+
+Thus, we have the following:
+\begin{align*}
+\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}])\\
+& \geq -\log (\ngl(n) + (1-\ngl(n))\ngl(n)) = -\log (\ngl(n)) = \omega(\log (n)).
+\end{align*}
+This completes the proof.\bnote{someone check this proof!!!! also make it more precise and better}
+\end{proof}
+
+Claims~\ref{cl:each block from single seed} and~\ref{cl:all blocks entropy} rest on there being no easy ``entry'' point to the distribution.
+This is not always the case.
+Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.
+
+\begin{claim}
+Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
+There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+\end{claim}
+\begin{proof}
+We present an adversary $A$~(running in polynomial time) that completely determines the value $x$.
+$A$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
+Then $A$ queries on $y_1,..., y_p$ exactly one answer returns $1$.
+Let this value be $y_1^*$ and its preimage $x_1^*$.
+Then $A$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.
+Again, exactly one of these queries returns $1$.
+This process is repeated until all of $x$ is recovered.
+The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
+Once $x$ has been recovered then $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+\end{proof}
+
+The previous example relied on an adversaries ability to completely determine a block from the previous blocks.
+We formalize this notion next.
+We defining the entropy jump of a block source as the remaining entropy when other blocks are known:
+
+\begin{definition}
+Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $J(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
+\end{definition}
+
+\noindent
+We now show that there must be a super-logarithmic jump early enough.
+
+\begin{claim}
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $J(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
+\end{claim}
+
+\begin{proof}
+For convenience relabel the ordering that violates the condition as $1,..., \ell$.
+We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.
+As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
+Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.
+This process is repeated until $W_{\ell-\beta+1}$ is learned.
+Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_i | W_1,.., W_{i-1}$.
+\end{proof}
 

### 2014-01-30 constantRate/ConstCompFuzzExt.tex
working on correctness of sampling

@@
 \subsection{Correctness of \consref{cons:sampling}}
-The argument that $1\rightarrow 0$ flips are extremely unlikely carries over from \consref{cons:first construction}.
-In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.
+The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.
+Let $t'$ be the capacity of $C$.
+To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.
+Let $t$ be the number of supported errors between $w$ and $w'$.
+Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
+% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.
 Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.
@@
 \begin{align*}
-\Pr[v_i = v_i' ] &= \Pr[w_{j_{i,1}} = w_{j_{i,1}}' \wedge ... \wedge w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
-&=\Pr[w_{j_{i,1}} = w_{j_{i,1}}'] \times ... \times \Pr[w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
-&=\left (1-\frac{t}{\gamma}\right)^{\eta}
+\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
+&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
+&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
+&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
 \end{align*} 
-This value is $\Theta(1)$ when $t = \Theta(\frac{\gamma }{\eta})$.
+Thus, by setting $c = -\log(1-t')/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
+
 \bnote{finish, Chernoff, not far from expectation.}

### 2014-01-30 constantRate/ConstCompFuzzExt.tex
correctness of sampling construction

@@
 
-Together these arguments allow us to conclude:
+\noindent Together these arguments allow us to conclude:
 \begin{theorem}
@@
 \end{theorem}
-
-\noindent
-We now prove $S$ cannot distinguish between $C$ and $C'$.  
-Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
-Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
-\begin{lemma}
-\label{lem:sim cannot distinguish}
-$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
-\end{lemma}
-
-\begin{proof}
-\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
-\begin{lemma}
-\label{lem:codewords in I close}
-Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then, 
-\[
-\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
-\]
-\end{lemma}
-\begin{proof}
-Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
-The only information about the correct value of $c_i^*$ is contained in the query responses.
-When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
-We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
-Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
-Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
-Thus, it must occur with probability:
-\begin{align}
-2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
- &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
-&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
-\end{align}
-We now show that $n-\log q \geq \alpha$:
-\begin{claim}
-\label{cl:ent bounded away from n}
-$n-\log q \geq \alpha$
-\end{claim}
-\begin{proof}
-It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.
-Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
-After these queries the remaining min-entropy is at most:
-\begin{align*}
-\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
-&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
-&=-\log\left( 2^{-n+\log q} \right) = n-\log q
-\end{align*}
-This completes the proof of \clref{cl:ent bounded away from n}.
-\end{proof}
-\noindent
-Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
-\begin{align*}
- \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
- \end{align*}
- When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
-If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
-This concludes the proof of \lemref{lem:codewords in I close}
-\end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
-This completes the proof of \lemref{lem:sim cannot distinguish}.
-\end{proof}
 
@@
 Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications.
-We begin to address this weakness in the next section.
+We begin to address this weakness in the next section.\bnote{come back to this linking language}
 
@@
 Let $n$ be a security parameter.
-Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.
+Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$ and $\gamma = Omega(n )$.
 Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
@@
 \label{lem:sampling works}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1))$-unordered block source.
 Let $\eta = \Omega(\log n)$.
@@
 \label{cor:samp unguess}
-Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha-1)}) = \ngl(n)$.
+Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
 \end{corollary}
@@
 \end{align*} 
-Thus, by setting $c = -\log(1-t')/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
-
-\bnote{finish, Chernoff, not far from expectation.}
-
-\subsection{Discussion}
-\bnote{need to write this once we have parameters in the two sections above.}
-%As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
-%\begin{align*}
-%gap &= \Hoo(W) -\log |B_t| \\
-%&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
-%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
-%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
-%&= \omega(\frac{\gamma \log n}{\eta})
-%\end{align*}
-%%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
-%\bnote{finish}
+Thus, by setting $c = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
+
+\begin{lemma}
+Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.
+Let $c = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq c(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
+\end{lemma}
+\begin{proof}
+With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.
+As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^c = t'/(2\eta)$.
+By the Chernoff bound, we have
+\begin{align*}
+\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \ell}) 
+\end{align*}
+\end{proof}
+
+\begin{corollary}
+Let $\ell = \omega(\log n)$ and let $C\subset\zo^\ell$ and  be a code that corrects $t' = \Theta(\ell)$ $0\rightarrow 1$ bit errors.  Then when 
+\[
+\dis(w, w')\leq \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
+\] 
+and $(R, P)\leftarrow \gen(w)$, then 
+\[
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\ell}) = 1-\ngl(n).
+\]
+That is, \consref{cons:sampling} is correct with error at most $\ngl(n)$.
+
+\end{corollary}
+\subsection{Discussion of \consref{cons:sampling}}
+We now show that \consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.
+For security of an unordered block source we needed both $\alpha = \Theta(1)$ and $\beta\leq \gamma/2-\Omega(1)$.
+This means that the overall required entropy of $\Hoo(W) = \Theta(\gamma)$.
+We are able to correct $O(\gamma/\eta)$ errors
+This yields:
+\begin{align*}
+gap &= \Hoo(W) -\log |B_t| \\
+&< \Theta(\gamma)- t \log |Z|\\
+&= \Theta(\gamma) - O(\gamma/\eta) \log |Z|\\
+\end{align*}
+That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for any fixed $Z$ we can set $\eta = \omega(\log n)$ and $\eta = o(\log |Z|)$).
+If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $Z$.
 \bibliographystyle{alpha}
@@
 
+\section{Proof of \thref{thm:security of cons}}
+\noindent
+We now prove $S$ cannot distinguish between $C$ and $C'$.  
+Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
+Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
+\begin{lemma}
+\label{lem:sim cannot distinguish}
+$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
+\end{lemma}
+
+\begin{proof}
+\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
+\begin{lemma}
+\label{lem:codewords in I close}
+Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then, 
+\[
+\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
+\]
+\end{lemma}
+\begin{proof}
+Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
+The only information about the correct value of $c_i^*$ is contained in the query responses.
+When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
+We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
+Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
+Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
+Thus, it must occur with probability:
+\begin{align}
+2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
+ &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
+&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
+\end{align}
+We now show that $n-\log q \geq \alpha$:
+\begin{claim}
+\label{cl:ent bounded away from n}
+$n-\log q \geq \alpha$
+\end{claim}
+\begin{proof}
+It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.
+Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
+After these queries the remaining min-entropy is at most:
+\begin{align*}
+\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
+&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
+&=-\log\left( 2^{-n+\log q} \right) = n-\log q
+\end{align*}
+This completes the proof of \clref{cl:ent bounded away from n}.
+\end{proof}
+\noindent
+Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
+\begin{align*}
+ \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
+ \end{align*}
+ When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
+If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
+By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
+This concludes the proof of \lemref{lem:codewords in I close}
+\end{proof}
+By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
+This completes the proof of \lemref{lem:sim cannot distinguish}.
+\end{proof}
+
 \end{document}

### 2014-01-30 trunk/constantRate/ConstCompFuzzExt.tex
cleaning up sampling coins for sampler

--- 2014-01-21 trunk/constantRate/ConstCompFuzzExt.tex
@@
 
-\subsection{Characterizing unguessable block distributions}
+\subsection{Discussion}
+\label{sec:discussion}
+Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
+Correction occurs for a small number of dimensions that are allowed to vary completely.
+As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
+
+To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet of size $2^n$.  This means that
+\begin{align*}
+\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
+&> \log {\ell \choose t} (2^n-1)^t\\
+&=\Theta(tn) + \log {\ell\choose t}
+% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
+\end{align*}
+\bnote{Need a good bound on ${\ell \choose t}$.}
+We now ask how much entropy is necessary for security.  The type of source we considered was independent blocks each with super-logarithmic min-entropy.  This yields 
+\[
+gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right). 
+\]
+When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| - \ngl(n)$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+Thus, \consref{cons:first construction} achieves negative $gap$ when $t = \Theta(\ell)$.
+Furthermore, not every block must contribute entropy, so security is possible when the total starting entropy is $\omega(\log n)$.
+For example, \consref{cons:first construction} is secure when each block is equal and drawn from a distribution of super-logarithmic min-entropy.
+So there are supported sources with negative $gap$ for any value of $t$.
+We achieve $gap<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
+%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
+
+\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
+The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
+Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
+Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications.
+We begin to address this weakness in the next section.\bnote{come back to this linking language}
+
+\section{Sample-then-Obfuscate}
+\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
+In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.
+This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.
+Second, it allows us to decrease the size of each block from exponential to an arbitrary super polynomial.
+Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
+In ordering for sampling to work properly, we need a source that is likely contribute some entropy from a randomly chosen block.
+
+\begin{definition}
+\label{def:unordered source}
+A distribution $W = W_1,..., W_\gamma$ is called a $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}, W_{i+1}=w_{i+1},..., W_\gamma = w_\gamma) \geq \alpha.
+\]
+\end{definition}
+
+\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.
+This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
+We will use an algorithm that draws random samples from block sources.
+Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs $\eta$ random and unique indices of $\{1,..., \gamma\}$ and let $r_{sam}$ the number of required coins for $\sample$.
+\begin{construction}
+\label{cons:sampling}
+Let $n$ be a security parameter.
+Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$ and $\gamma = Omega(n )$.
+Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
+Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.
+Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.
+Define $\gen, \rep$ as:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\gamma$
+\item Sample $c\leftarrow C$.
+\item For $i=1,..., \ell$:
+\begin{itemize}
+\item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
+\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
+\item If $c_i = 0$: 
+\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
+\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
+\subitem Set $p_i = \rho_i, \lambda_i$.
+\item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
+\subitem Let $p_i = \mathcal{O}(I_{r_i}) \lambda_i$.
+\end{itemize}
+\item Output $(c, p)$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p)$ 
+\item For $i=1,..., \ell$:
+\begin{itemize}
+\item Parse $p_i$ as $\rho_i, \lambda_i$.
+\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
+\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
+\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
+\item Else set $c_i' = 1$.
+\end{itemize}
+\item Set $c = \decode(c')$.
+\item Output $c$.
+\end{enumerate}
+\vspace{0.37in}
+\end{minipage} 
+\end{tabular}
+\end{center}
+\end{construction}
+
+The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.
+This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
+For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
+There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
+Our construction uses the na\"{i}ve sampler that takes truly random samples, the analysis is essentially the same for more sophisticated samplers that use fewer random bits.
+Goldreich provides an accessible introduction to samplers~\cite{goldreich1997sample}.
+
+As before we must show security and correctness of \consref{cons:sampling}.
+For security, the main argument is that each of the $v_i$ has enough entropy to be unguessable.
+For correctness we must show that the induced error rate in $v$ and $v'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.
+
+\subsection{Security of \consref{cons:sampling}}
+Consider a source where most blocks have some entropy~(conditioned on the rest).
+In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has super-logarithmic entropy on its own.
+A sampler will select enough good blocks almost all the time, meaning if we take enough samples we obtain a super-logarithmic amount of entropy.
+This means that  $V_1,..., V_\ell$ is a block-unguessable distribution~(by \clref{cl:all blocks entropy}) and security follows by \thref{thm:security of cons}.
+
+\begin{lemma}
+\label{lem:sampling works}
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.
+Let $\eta = \Omega(\log n)$.
+Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
+\end{lemma}
+\begin{proof}
+By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.
+\bnote{need someone to check parameters, I am fairly sure of the quality of the statement}
+\end{proof}
+
+\begin{corollary}
+\label{cor:samp sec}
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.  Let $\eta = \Omega(\log n)$.  
+The distribution $V, \Lambda$ is $\epsilon_{sam}(\ell (\ngl(n) +2^{-\Omega(n)})) = \ngl(n)$-close to a distribution $V', U_{\ell\times r_{sam}}$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
+\end{corollary}
+\begin{proof}
+Union bound over the statistical distance in \lemref{lem:sampling works}.
+\end{proof}
+
+\begin{corollary}
+\label{cor:v are unguessable}
+Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\ell\times r_{sam}}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
+\end{corollary}
+\begin{proof}
+Result of \clref{cl:all blocks entropy}.
+\end{proof}
+
+\begin{corollary}
+\label{cor:samp unguess}
+Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
+\end{corollary}
+\begin{proof}
+Result of \corref{cor:v are unguessable} and \thref{thm:security of cons}.
+\end{proof}
+
+\subsection{Correctness of \consref{cons:sampling}}
+The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.
+Let $t'$ be the capacity of $C$.
+To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.
+Let $t$ be the number of supported errors between $w$ and $w'$.
+Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
+% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.
+Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.
+Then
+\begin{align*}
+\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
+&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
+&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
+&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
+\end{align*} 
+Thus, by setting $c = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
+
+\begin{lemma}
+Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.
+Let $c = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq c(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
+\end{lemma}
+\begin{proof}
+With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.
+As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^c = t'/(2\eta)$.
+By the Chernoff bound, we have
+\begin{align*}
+\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \ell}) 
+\end{align*}
+\end{proof}
+
+\begin{corollary}
+Let $\ell = \omega(\log n)$ and let $C\subset\zo^\ell$ and  be a code that corrects $t' = \Theta(\ell)$ $0\rightarrow 1$ bit errors.  Then when 
+\[
+\dis(w, w')\leq \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
+\] 
+and $(R, P)\leftarrow \gen(w)$, then 
+\[
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\ell}) = 1-\ngl(n).
+\]
+That is, \consref{cons:sampling} is correct with error at most $\ngl(n)$.
+
+\end{corollary}
+\subsection{Discussion of \consref{cons:sampling}}
+We now show that \consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.
+For security of an unordered block source we needed both $\alpha = \Theta(1)$ and $\beta\leq \gamma/2-\Omega(1)$.
+This means that the overall required entropy of $\Hoo(W) = \Theta(\gamma)$.
+We are able to correct $O(\gamma/\eta)$ errors
+This yields:
+\begin{align*}
+gap &= \Hoo(W) -\log |B_t| \\
+&< \Theta(\gamma)- t \log |Z|\\
+&= \Theta(\gamma) - O(\gamma/\eta) \log |Z|\\
+\end{align*}
+That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for any fixed $Z$ we can set $\eta = \omega(\log n)$ and $\eta = o(\log |Z|)$).
+If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $Z$.
+\bibliographystyle{alpha}
+\bibliography{crypto}
+
+\appendix
+\section{Obfuscation}
+\label{sec:obfuscation}
+The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
+This notion is known to be impossible in a black-box way for all polynomial time programs.
+Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
+Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
+The definition of virtual black box obfuscation is presented in \defref{def:obf}.
+
+In this work, we will use obfuscation of point-programs, 
+\[
+I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
+\]
+
+We present the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
+\begin{enumerate}  
+\item Input: string $w\in \zo^n$.
+\item Choose a generator $g\overset{\$}\leftarrow G$
+\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
+\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
+\end{enumerate}
+\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
+Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
+Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
+For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
+\end{assumption}
+\begin{theorem}~\cite{canetti1997towards}
+The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
+\end{theorem}
+
+As mentioned above there exist other constructions of point function obfuscation under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
+
+Lastly, we will need the notion of composable obfuscation.
+
+\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}]
+\label{def:obf comp}
+A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
+That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
+\[
+|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
+\]
+where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
+\end{definition}
+
+\section{Fuzzy Conductors}
+
+\label{sec:conductors}
+Fuzzy extractors are known to have strong upper bounds on remaining entropy based on the best error correcting codes.
+Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
+They suggest these bounds may be avoided by outputting a fresh random variable.
+This is known as a fuzzy conductor~\cite{KanukurthiR09}.
+\begin{definition}
+A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
+\begin{enumerate}
+\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $y\in\zo^*$ and a helper string $p\in\zo^*$.
+\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\zo^*$ as inputs.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $Y, P$ were generated by $(Y, P)\leftarrow \gen'(w)$, then $\rep(w', P) = Y$ with probability~(over the coins of $\gen', \rep'$) at least $1-\epsilon$.
+If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
+\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $Y$ is close to a high entropy distribution $Z$.
+That is, $\exists Z$ with $\Hav(Z | P ) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
+\end{enumerate}
+\end{definition}
+
+\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
+This motivates our use of a computational fuzzy conductor in \secref{sec:fuzzy extractors}.
+We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
+\begin{itemize}
+\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
+%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
+\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
+\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
+\end{itemize}
+
+\begin{lemma}
+The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
+\end{lemma}
+\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
+Let $S$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $S$.
+Define $(Y, P) \leftarrow \gen'(W)$.
+Then there must exist a distribution $Z$ with $\Hav(Z|P) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
+By Markov's inequality, there exists some set $S_P$ such that $\Pr[P\in S_p] \geq 1/2$ and $\forall p\in S_P$ one has $\mathbf{SD}(Y | P = p, p ), (Z | P = p, p)<2\epsilon$.
+Now applying Markov's inequality of $\max_{z} \Pr[Z=z | P=p]$, there exists a set $S_P'$ such that $\Pr[P\in S_P']>1/2$, and for all $p\in S_P'$, $\Hoo(Z| P =p ) \geq \tilde{m}-1$.
+Denote by $p^*$ a value in $S_P\cap S_P'$~(one value must exist).
+Then $\mathbf{SD}((Y | P =p^* , p^*), (Z| P = p^*, p^*))\leq 2\epsilon$ and $\Hoo(Z|P=p^*)\geq \tilde{m}-1$.
+Denote by the set $T$ the possible values of $Y$ when $P=p^*$.
+For the statistical distance property to hold, $|T| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
+Associate with every $y\in T$ some $w\in S$ which could have produced $y$ with nonzero probability given $P=p^*$, and call this map $C$.
+$C$ defines an error correcting code with the required parameters.
+
+\end{proof}
+
+%\section{Proof of \lemref{lem:linear codes independent}}
+%\label{sec:proof of linear indep}
+%\begin{proof}
+%Suppose there is some $i$ that is not equiprobable.
+Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
+First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
+First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
+Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
+Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
+This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
+%Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
+This is a contradiction and completes the proof.
+%\end{proof}
+
+\section{Characterizing unguessable block distributions}
+\label{sec:characterize}
 
 \defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
-In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.
-
-The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
+In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
+The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
 Thus, we begin with the case of independent blocks.
@@
 It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
-Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
+Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we ignore all other blocks as they are independent).  
 Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
 Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
-We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).
+We assume a deterministic adversary~(we assume the best coins are in nonuniform advice).
 The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
@@
 In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
-This is a subset of the distributions in \clref{cl:independent high ent}.
-
-We now consider more complicated~(realistic) distributions where blocks are not independent.  We begin with distributions that are block unguessable.
+\clref{cl:independent high ent} captures this type of distribution.
+We now consider more complicated distributions where blocks are not independent.
 
@@
 Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.
-This claims rests on there being no easy ``entry'' point to the distribution.
+We can prove a similar claim in the case where $f$ is not injectiveall blocks do not a source~(determined by $f$).
+
+\begin{claim}
+\label{cl:all blocks entropy}
+Let $W = W_1,..., W_\ell$ be a source.
+Let $\alpha =\omega(\log n)$ and suppose that for all $i$ $\Hoo(W_i)\geq \alpha$, then for $q = \poly(n)$, $\alpha ' = \omega(\log n)$, $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
+\end{claim}
+\begin{proof}
+Consider a particular block $W_i$, it suffices to show that $\Hav(W_i | Q_1,A_1,..., Q_q, A_q) \geq \omega(\log n)$.  By the definition of conditional min-entropy:
+\begin{align*}
+\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &= -\log (\Pr[\text{some non zero response}] \max_{w\in W_i} \Pr[W_i | \text{non zero response}) \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i| \text{all zero responses}])\\
+&\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}]).
+\end{align*}
+It suffices to show that $\Pr[\text{some non zero response}] = \ngl(n)$ and that $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = \ngl(n)$.  We show each of these is turn.
+
+First note that clearly the 1st query returns $1$ with $2^{-\alpha}$ probability~(due to the min-entropy condition).
+Conditioned on this response being $0$ the probability of all other events increases by at most negligible amount~(the statistical distance between the original distribution and the distribution conditioned on the first response being $0$ is $\ngl(n)$).
+Thus, the total probability of a $1$ is at most:
+\[
+\Pr[\text{some non zero response}] \leq 2^{-\alpha} + (2^{-\alpha}+\ngl(n)) + ... +(2^{-\alpha}+q\times \ngl(n)) = \ngl(n).
+\]
+Now consider $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}]$.  For each zero response, the probability of any $w_i$ increases by at most a negligible amount, this means that 
+\[\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = 2^{-\alpha} + q\times \ngl(n) = \ngl(n).\]
+
+Thus, we have the following:
+\begin{align*}
+\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}])\\
+& \geq -\log (\ngl(n) + (1-\ngl(n))\ngl(n)) = -\log (\ngl(n)) = \omega(\log (n)).
+\end{align*}
+This completes the proof.\bnote{someone check this proof!!!! also make it more precise and better}
+\end{proof}
+
+Claims~\ref{cl:each block from single seed} and~\ref{cl:all blocks entropy} rest on there being no easy ``entry'' point to the distribution.
 This is not always the case.
@@
 \end{proof}
-
-\section{Discussion}
-\label{sec:discussion}
-Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
-Correction occurs for a small number of dimensions that are allowed to vary completely.
-As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
-
-To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet of size $2^n$.  This means that
-\begin{align*}
-\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
-&> \log {\ell \choose t} (2^n-1)^t\\
-&=\Theta(tn) + \log {\ell\choose t}
-% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
-\end{align*}
-\bnote{Need a good bound on ${\ell \choose t}$.}
-We now ask how much entropy is necessary for security.  The type of source we considered was independent blocks each with super-logarithmic min-entropy.  This yields 
-\[
-gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right). 
-\]
-When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| - \ngl(n)$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
-Thus, \consref{cons:first construction} achieves negative $gap$ when $t = \Theta(\ell)$.
-Furthermore, not every block must contribute entropy, so security is possible when the total starting entropy is $\omega(\log n)$.
-For example, \consref{cons:first construction} is secure when each block is equal and drawn from a distribution of super-logarithmic min-entropy.
-So there are supported sources with negative $gap$ for any value of $t$.
-We achieve $gap<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
-%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
-
-\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
-The first is that Hamming distance is over an alphabet of exponential size, which precludes use in some applications.
-The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
-Lastly, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
-\bibliographystyle{alpha}
-\bibliography{crypto}
-
-\appendix
-\section{Obfuscation}
-\label{sec:obfuscation}
-The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
-This notion is known to be impossible in a black-box way for all polynomial time programs.
-Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
-Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
-The definition of virtual black box obfuscation is presented in \defref{def:obf}.
-
-In this work, we will use obfuscation of point-programs, 
-\[
-I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
-\]
-
-We present the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
-\begin{enumerate}  
-\item Input: string $w\in \zo^n$.
-\item Choose a generator $g\overset{\$}\leftarrow G$
-\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
-\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
-\end{enumerate}
-\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
-Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
-Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
-For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
-\end{assumption}
-\begin{theorem}~\cite{canetti1997towards}
-The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
-\end{theorem}
-
-As mentioned above there exist other constructions of point function obfuscation under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
-
-Lastly, we will need the notion of composable obfuscation.
-
-\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}]
-\label{def:obf comp}
-A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
-That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
-\[
-|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
-\]
-where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
-\end{definition}
-
-\section{Fuzzy Conductors}
-
-\label{sec:conductors}
-Fuzzy extractors are known to have strong upper bounds on remaining entropy based on the best error correcting codes.
-Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
-They suggest these bounds may be avoided by outputting a fresh random variable.
-This is known as a fuzzy conductor~\cite{KanukurthiR09}.
-\begin{definition}
-A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
-\begin{enumerate}
-\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $y\in\zo^*$ and a helper string $p\in\zo^*$.
-\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\zo^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $Y, P$ were generated by $(Y, P)\leftarrow \gen'(w)$, then $\rep(w', P) = Y$ with probability~(over the coins of $\gen', \rep'$) at least $1-\epsilon$.
-If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
-\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $Y$ is close to a high entropy distribution $Z$.
-That is, $\exists Z$ with $\Hav(Z | P ) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
-\end{enumerate}
-\end{definition}
-
-\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
-This motivates our use of a computational fuzzy conductor in \secref{sec:fuzzy extractors}.
-We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
-\begin{itemize}
-\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
-%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
-\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
-\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
-\end{itemize}
-
-\begin{lemma}
-The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
-\end{lemma}
-\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
-Let $S$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $S$.
-Define $(Y, P) \leftarrow \gen'(W)$.
-Then there must exist a distribution $Z$ with $\Hav(Z|P) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
-By Markov's inequality, there exists some set $S_P$ such that $\Pr[P\in S_p] \geq 1/2$ and $\forall p\in S_P$ one has $\mathbf{SD}(Y | P = p, p ), (Z | P = p, p)<2\epsilon$.
-Now applying Markov's inequality of $\max_{z} \Pr[Z=z | P=p]$, there exists a set $S_P'$ such that $\Pr[P\in S_P']>1/2$, and for all $p\in S_P'$, $\Hoo(Z| P =p ) \geq \tilde{m}-1$.
-Denote by $p^*$ a value in $S_P\cap S_P'$~(one value must exist).
-Then $\mathbf{SD}((Y | P =p^* , p^*), (Z| P = p^*, p^*))\leq 2\epsilon$ and $\Hoo(Z|P=p^*)\geq \tilde{m}-1$.
-Denote by the set $T$ the possible values of $Y$ when $P=p^*$.
-For the statistical distance property to hold, $|T| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
-Associate with every $y\in T$ some $w\in S$ which could have produced $y$ with nonzero probability given $P=p^*$, and call this map $C$.
-$C$ defines an error correcting code with the required parameters.
-
-\end{proof}
-
-%\section{Proof of \lemref{lem:linear codes independent}}
-%\label{sec:proof of linear indep}
-%\begin{proof}
-%Suppose there is some $i$ that is not equiprobable.
-Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
-First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
-First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
-Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
-Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
-This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
-%Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
-This is a contradiction and completes the proof.
-%\end{proof}
 

### 2014-01-30 trunk/constantRate/ConstCompFuzzExt.tex
Editing up to section 5

@@
 \newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
+\newcommand{\Hfuzz}{\mathrm{H}^{\mathtt{fuzz}}_{t,\infty}}
 \newcommand{\Dom}{\mathsl{Dom}}
@@
 
+\bnote{there are two constructions now}
 \textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.  
@@
 \section{Introduction}\label{sec:introduction}
+\bnote{I want a new name for $gap$!}
 Reliable key derivation is a cornerstone of authentication.
@@
 Both of these problems have interactive and non-interactive versions.
-For a single user~(trying to produce the same key from multiple readings of a physical source) the non-interactive solutions are appropriate.
+For a single user~(trying to produce the same key from multiple readings of a physical source) non-interactive solutions are appropriate.
 We focus on this setting.
@@
 
+\bnote{the whole introduction should be rewritten, doesn't mention second construction.}
 We consider the Hamming metric.
 For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.
-As we discuss later, it is possible to avoid these losses if the fuzzy extractor has additional knowledge about the distribution.} and logarithm of the number of error patterns to be corrected.
+As we discuss later, it is possible to avoid these losses if the fuzzy extractor knows something about the distribution.} and logarithm of the number of error patterns to be corrected.
 For the remainder of this paper we denote this quantity by $gap$.
@@
 In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
-Our focus is on expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
-
+Our focus is on expanding the class of distributions for which we can provide meaningful security.
+
+\bnote{two constructions}
 \textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.
@@
 It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.
-Note, it is hard to recover $w$ from the value $c$.
-This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.
+It is hard to recover $w$ from the value $c$.
+This is necessary to overcome lower bounds on entropy loss~\cite[Section 3.3]{fuller2013computational}.
 Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
@@
 \end{itemize}
+\bnote{compare contrast constructions}
 
@@
 If not all blocks have high entropy an adversary may learn significant information about the source.
-Thus, our construction is not a virtual black box~(VBB) obfuscation~(where anything learnable by the circuit is simulatable using input/output behavior).
+Thus, our construction is not a obfuscation for any reasonable definition.
 Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides partial information.
 Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
-
-The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our construction in \secref{sec:construction} and discuss parameters and tradeoffs in \secref{sec:discussion}.
+\bnote{does second construction get closer to obfuscation?}
+
+The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
 
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
+For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^\ell$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
 For the Hamming metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
@@
 
-Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.
+Usually, we use capitalized letters for random variables and lowercase letters for samples from a random variable.
 
@@
 \]
+\bnote{We need a different name for the circuit, $C$ is our error-correcting code.}
 where the probability is taken over the randomness $r$.
@@
 We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
-Definitions for information-theoretic fuzzy extractors and a non-interactive information-reconciliation component, known as a secure sketch, can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
+Definitions for information-theoretic fuzzy extractors can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
 The definition of computational fuzzy extractors allows for a small probability of error.
@@
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary.
+With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary~(see \apref{sec:minimal conditions} for the precise statement).
 
@@
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(s_{cone}, \epsilon_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
 \begin{itemize}
-\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.
+\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $X\in\{0,1\}^\ell$ and a helper string $SS\in\{0,1\}^*$.
+\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $SS\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', SS) = X] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.
 If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(Y |P)\geq \tilde{m}$.
 \end{itemize}
@@
 Let $\chi$ be a finite set.
-A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, s_{sec}, \epsilon)$-average-case computational extractor} if for all pairs
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, s_{ext}, \epsilon_{ext})$-average-case computational extractor} if for all pairs
 of random variables $X, Y$ over $\zo^\ell, \chi$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{sec}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon$.
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{ext}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon_{ext}$.
 \end{definition}
@@
 \label{lem:cond and cext}
-Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
+Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{cond},\epsilon_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
 Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, s_{ext}, \epsilon_{ext})$-average case computational extractor.
@@
 \begin{itemize}
-\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $r = \cext(y; x)$ and $p = (p', x)$.  Output $(r, p)$.
-\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \cext(y; x)$. 
+\item $\gen(w; seed):$ run $(x, ss)= \gen'(w)$ and set $r = \cext(x; seed)$, $p = (ss, seed)$.  Output $(r, p)$.
+\item $\rep(w, (ss, seed)):$ recover $x = \rec'(w'; p')$ and output $r = \cext(x; seed)$. 
 \end{itemize}
@@
 \label{sec:construction}
-
+\bnote{this needs to be rewritten}
 Before describing our construction, we recall the problem we are trying address.
 The goal is to derive strong keys from noisy sources.
-As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
+As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is  negative.
 In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.
@@
 Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.
-Our construction is secure as long as enough blocks are unpredictable after adaptive queries:
+Our construction is secure as long as enough blocks are unpredictable after adaptive queries~(we discuss minimal conditions for fuzzy extractor security in more depth in \apref{sec:minimal conditions}):
 
@@
 %\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  
-We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
-In \apref{sec:characterize} we provide discussion on the types of sources that satisfy \defref{def:block guessable}.
+We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.  We discuss  block unguessable distributions in \apref{sec:characterize}.
 To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
@@
 \label{thm:security of cons}
-Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
+Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator \bnote{grey box?} with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
 Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
@@
 \label{lem:correct of cons}
-Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
-\[
-\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n}.
+Let $C$ be a $(\neigh_t, \epsilon_{code})$-code.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
+\[
+\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\epsilon_{code}\right).
 \]
@@
 
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for block unguessable distributions:
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for block unguessable distributions:
 \begin{theorem}
@@
 Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 Security is a result of \thref{thm:security of cons} because $2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}$ is negligible when $\epsilon_{obf} = \ngl(n), \ell = \poly(n)$ and $\alpha =\omega(\log n)$.
-Correctness follows from \lemref{lem:correct of cons} and the fact that $C$ is a $(\neigh_t, \epsilon_{code})$-code.
+Correctness follows from \lemref{lem:correct of cons}.
 \end{proof}
@@
 
-To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet of size $2^n$.  This means that
+To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.
+We allow $t$ errors with an alphabet $\mathcal{Z}$ of size $2^n$.
+This means that
 \begin{align*}
-\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
+\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i\\
 &> \log {\ell \choose t} (2^n-1)^t\\
@@
 \end{align*}
-\bnote{Need a good bound on ${\ell \choose t}$.}
-We now ask how much entropy is necessary for security.  The type of source we considered was independent blocks each with super-logarithmic min-entropy.  This yields 
+
+We consider what entropy is necessary for security.
+The simplest type of block unguessable distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
+This yields:
 \[
@@
 \]
-When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| - \ngl(n)$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
 Thus, \consref{cons:first construction} achieves negative $gap$ when $t = \Theta(\ell)$.
-Furthermore, not every block must contribute entropy, so security is possible when the total starting entropy is $\omega(\log n)$.
-For example, \consref{cons:first construction} is secure when each block is equal and drawn from a distribution of super-logarithmic min-entropy.
-So there are supported sources with negative $gap$ for any value of $t$.
 We achieve $gap<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
@@
 \section{Sample-then-Obfuscate}
+\label{sec:sampling}
 \consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
@@
 Let $n$ be a security parameter.
-Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$ and $\gamma = Omega(n )$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = Omega(n)$.
 Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
-Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.
-Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.
+Let $\eta = \omega(\log n)$ be some function such that $\eta \log (\mathcal{Z}) = \omega(\log n)$.
+Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
 Define $\gen, \rep$ as:
@@
 \label{cor:samp unguess}
-Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
+Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
 \end{corollary}
@@
 gap &= \Hoo(W) -\log |B_t| \\
-&< \Theta(\gamma)- t \log |Z|\\
-&= \Theta(\gamma) - O(\gamma/\eta) \log |Z|\\
+&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
+&= \Theta(\gamma) - O(\gamma/\eta) \log |\mathcal{Z}|\\
 \end{align*}
-That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for any fixed $Z$ we can set $\eta = \omega(\log n)$ and $\eta = o(\log |Z|)$).
-If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $Z$.
+That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for any fixed $\mathcal{Z}$ we can set $\eta = \omega(\log n)$ and $\eta = o(\log |\mathcal{Z}|)$).
+If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
 \bibliographystyle{alpha}
@@
 \begin{enumerate}
-\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $y\in\zo^*$ and a helper string $p\in\zo^*$.
-\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\zo^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $Y, P$ were generated by $(Y, P)\leftarrow \gen'(w)$, then $\rep(w', P) = Y$ with probability~(over the coins of $\gen', \rep'$) at least $1-\epsilon$.
+\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
+\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\rep(w', SS) = X$ with probability~(over the coins of $\gen', \rep'$) at least $1-\epsilon$.
 If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
-\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $Y$ is close to a high entropy distribution $Z$.
-That is, $\exists Z$ with $\Hav(Z | P ) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
+\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.
+That is, $\exists Y$ with $\Hav(Y | SS ) \geq \tilde{m}$ such that $\Delta((X, SS), (Y, SS))\leq \epsilon$.
 \end{enumerate}
@@
 \begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
-Let $S$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $S$.
-Define $(Y, P) \leftarrow \gen'(W)$.
-Then there must exist a distribution $Z$ with $\Hav(Z|P) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
-By Markov's inequality, there exists some set $S_P$ such that $\Pr[P\in S_p] \geq 1/2$ and $\forall p\in S_P$ one has $\mathbf{SD}(Y | P = p, p ), (Z | P = p, p)<2\epsilon$.
-Now applying Markov's inequality of $\max_{z} \Pr[Z=z | P=p]$, there exists a set $S_P'$ such that $\Pr[P\in S_P']>1/2$, and for all $p\in S_P'$, $\Hoo(Z| P =p ) \geq \tilde{m}-1$.
-Denote by $p^*$ a value in $S_P\cap S_P'$~(one value must exist).
-Then $\mathbf{SD}((Y | P =p^* , p^*), (Z| P = p^*, p^*))\leq 2\epsilon$ and $\Hoo(Z|P=p^*)\geq \tilde{m}-1$.
-Denote by the set $T$ the possible values of $Y$ when $P=p^*$.
-For the statistical distance property to hold, $|T| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
-Associate with every $y\in T$ some $w\in S$ which could have produced $y$ with nonzero probability given $P=p^*$, and call this map $C$.
+Let $A$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $A$.
+Define $(X,SS) \leftarrow \gen'(W)$.
+Then there must exist a distribution $Y$ with $\Hav(Y|SS) \geq \tilde{m}$ such that $\Delta((X,SS), (Y, SS))\leq \epsilon$.
+By Markov's inequality, there exists some set $B_{SS}$ such that $\Pr[ss\in B_{SS}] \geq 1/2$ and $\forall s\in B_{SS}$ one has $\Delta(X | SS = s, s ), (Y | SS = s, s)<2\epsilon$.
+Now applying Markov's inequality of $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.
+Denote by $s^*$ a value in $B_{SS}\cap B_{SS'}$~(one value must exist).
+Then $\Delta((X | SS =s^* , s^*), (Y| SS = s^*, s^*))\leq 2\epsilon$ and $\Hoo(Y|SS=s^*)\geq \tilde{m}-1$.
+Denote by the set $A'$ the possible values of $X$ when $SS=s^*$.
+For the statistical distance property to hold, $|A'| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
+Associate with every $x\in A'$ some $w\in S$ which could have produced $x$ with nonzero probability given $SS=s^*$, and call this map $C$.
 $C$ defines an error correcting code with the required parameters.
-
-\end{proof}
-
-%\section{Proof of \lemref{lem:linear codes independent}}
-%\label{sec:proof of linear indep}
-%\begin{proof}
-%Suppose there is some $i$ that is not equiprobable.
-Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
-First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
-First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
-Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
-Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
-This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
-%Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
-This is a contradiction and completes the proof.
-%\end{proof}
+\end{proof}
+
+\section{Minimal Conditions for Fuzzy Extractor Security}
+\label{sec:minimal conditions}
+As mentioned in the introduction a necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.
+In the interactive setting using multi-party computation it is possible to achieve security under this condition.
+We codify this notion:
+
+\begin{definition}
+\label{def:fuzzy min-ent}
+A distribution $W$ in a metric space $\mathcal{M}$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) = k$ if the following holds:
+\[
+\forall m\in \mathcal{M} Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+\]
+\end{definition}
+\begin{lemma}
+Let $n$ be a security parameter and let $W$ be a distribution over $\mathcal{M}$  
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) if $\kappa =\omega(\log n)$.
+\end{lemma}
+\begin{proof}
+Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+This means that there exists a point $m\mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
+Consider the following distinguisher $D$:
+\begin{itemize}
+\item On input $r, p$.
+\item If $\rep(m, p) = r$, output $1$.
+\item Else output $0$.
+\end{itemize}
+First note that $|D|$ is of size $\log |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n)$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
+\[
+\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} - \frac{1}{2^{-\kappa}} = 1/\poly(n).
+\]
+\end{proof}
+
+For the Hamming distance having $\Hfuzz(W)\geq \omega(\log n)$ means that there are more entropic dimensions that the desired error-tolerance.
+There are two minimal types of distributions that provide $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).
+The other is that there $t+\omega(\log n)$ blocks that contribute some constant amount of entropy.
+Definitions~\ref{def:block guessable} and~\ref{def:unordered source} are geared towards this type of source, achieving security when the number of entropic blocks is only one greater than the desired error correction is an open problem.
 
@@
 \begin{align*}
-\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &= -\log (\Pr[\text{some non zero response}] \max_{w\in W_i} \Pr[W_i | \text{non zero response}) \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i| \text{all zero responses}])\\
+\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &= -\log (\Pr[\text{some non zero response}] \max_{w\in W_i} \Pr[W_i | \text{non zero response}) \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i| \text{all zero responses}]\\
 &\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}]).
@@
 \begin{proof}
-It suffices to show if there is some distinguisher $D$ of size $s'$ where 
-\[\delta^D((\cext(W; X), U_d, P), (U_\kappa, U_d, P))>\epsilon_{cond}+ \epsilon_{ext}\]
- then there is an distinguisher $D'$ of size $s_{cond}$ where for all $Z$ where $\Hav(Z|P)\geq \tilde{m}$ such that
- \[
- \delta^{D'}((Y, P), (Z, P))\geq \epsilon_{cond}.
- \]
-Let $D$ be such a distinguisher.  That is,
-\[
-\delta^D(\ext(X, U_d)\times U_d \times P, U_\kappa\times U_d\times P)> \epsilon_{ext}+\epsilon_{cond}.
-\]
-Then define $D'$ as follows.
-On input $y, p$ sample $x\leftarrow U_d$, compute $r\leftarrow \cext(y, x)$ and output $D(r, x, p)$.
-Note that $|D'| \approx s' + |\cext| +d= s_{cond}$.
+It suffices to show if there is some distinguisher $D'$ of size $s'$ where 
+\[\delta^{D'}((\cext(X; U_d), U_d, SS), (U_\kappa, U_d, SS))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D$ of size $s_{cond}$ where for all $Y$ where $\Hav(Y|SS) \geq \tilde{m}$ such that
+ \[
+ \delta^{D}((X, SS), (Y, SS))\geq \epsilon_{cond}.
+ \]
+Let $D'$ be such a distinguisher.  That is,
+\[
+\delta^{D'}(\cext(X, U_d)\times U_d \times SS, U_\kappa\times U_d\times SS)> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D$ as follows.
+On input $(y, ss)$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, ss)$.
+Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
 Then we have the following:
 \begin{align*}
-\delta^{D'}((Y, P), (Z, P))&= \delta^D((\cext(Y, U_d), U_d, P), \cext(Z, U_d), U_d, P)\\
-&\geq \delta^D((\cext(Y, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^D((\cext(Z, U_d), U_d, P), (U_\kappa\times U_d \times P))\\
+\delta^{D}((X, SS), (Y, SS))&= \delta^{D'}((\cext(X, U_d), U_d, SS), \cext(Y, U_d), U_d, SS)\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^{D'}((\cext(Y, U_d), U_d, SS), (U_\kappa\times U_d \times SS))\\
 &>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
 \end{align*}
-Thus $D'$ distinguishes $Y$ from all $Z$ with sufficient conditional min-entropy.  This is a contradiction.
+Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
 \end{proof}

### 2014-01-30 trunk/constantRate/ConstCompFuzzExt.tex
editing notation in sec 5

@@
 \item For $i=1,..., \ell$:
-\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
-\subitem Else: Sample $r_i \leftarrow U_n$. 
-\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
+\begin{enumerate}
+\item If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
+\item Else: Sample $r_i \leftarrow U_n$. 
+\subitem Let $p_i = \mathcal{O}(I_{r_i})$.
+\end{enumerate}
 \item Output $(c, p)$.
@@
 \item For $i=1,..., \ell$:
-\subitem If $p_i(w_i') = 1$: set $c_i' = 0$.
-\subitem Else: set $c_i' = 1$.
+\begin{enumerate}
+\item If $p_i(w_i') = 1$: set $c_i' = 0$.
+\item Else: set $c_i' = 1$.
+\end{enumerate}
 \item Set $c = \decode(c')$.
@@
 \consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
-In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.
-This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.
-Second, it allows us to decrease the size of each block from exponential to an arbitrary super polynomial.
+In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
+The main advantage of this approach is it expands the supported sources as no single block must have high entropy.
 Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
+Thus, we have a tradeoff between individually required entropy and supported error tolerance.
 In ordering for sampling to work properly, we need a source that is likely contribute some entropy from a randomly chosen block.
@@
 \label{def:unordered source}
-A distribution $W = W_1,..., W_\gamma$ is called a $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
+A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
 \[
@@
 \defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.
-This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
-We will use an algorithm that draws random samples from block sources.
-Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs $\eta$ random and unique indices of $\{1,..., \gamma\}$ and let $r_{sam}$ the number of required coins for $\sample$.
+This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
+We use an algorithm that draws random samples from block sources.
+Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample$.
 \begin{construction}
@@
 Let $n$ be a security parameter.
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = Omega(n)$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
 Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
-Let $\eta = \omega(\log n)$ be some function such that $\eta \log (\mathcal{Z}) = \omega(\log n)$.
-Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
+Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable obfuscator\bnote{right def?} for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
 Define $\gen, \rep$ as:
@@
 \item For $i=1,..., \ell$:
-\begin{itemize}
+\begin{enumerate}
 \item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
@@
 \subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
-\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
+\subitem Set $\rho_i = \mathcal{O}(I_{v_i})$.
 \subitem Set $p_i = \rho_i, \lambda_i$.
 \item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
-\subitem Let $p_i = \mathcal{O}(I_{r_i}) \lambda_i$.
-\end{itemize}
+\subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
+\end{enumerate}
 \item Output $(c, p)$.
@@
 \item For $i=1,..., \ell$:
-\begin{itemize}
+\begin{enumerate}
 \item Parse $p_i$ as $\rho_i, \lambda_i$.
 \item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
-\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
-\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
+\item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
+\item If $\rho_i(v_i') = 1$ set $c_i' = 0$.
 \item Else set $c_i' = 1$.
-\end{itemize}
+\end{enumerate}
 \item Set $c = \decode(c')$.
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+There is a crucial difference, our use of a computational primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
 In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
-Our construction uses the na\"{i}ve sampler that takes truly random samples, the analysis is essentially the same for more sophisticated samplers that use fewer random bits.
-Goldreich provides an accessible introduction to samplers~\cite{goldreich1997sample}.
-
-As before we must show security and correctness of \consref{cons:sampling}.
-For security, the main argument is that each of the $v_i$ has enough entropy to be unguessable.
-For correctness we must show that the induced error rate in $v$ and $v'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.
+Our construction uses the na\"{i}ve sampler that takes truly random samples, but the public randomness can be substantially decreased by using more sophisticated samplers.
+Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.
+
+As before we show security and correctness of \consref{cons:sampling}.
+For security, we argue that each of the $v_i$ is unguessable.
+For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability) so that $c'$ will be corrected to $c$ with overwhelming probability.
 
 \subsection{Security of \consref{cons:sampling}}
-Consider a source where most blocks have some entropy~(conditioned on the rest).
 In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has super-logarithmic entropy on its own.
@@
 By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.
-\bnote{need someone to check parameters, I am fairly sure of the quality of the statement}
+\bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}
 \end{proof}
@@
 \label{cor:samp sec}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.  Let $\eta = \Omega(\log n)$.  
-The distribution $V, \Lambda$ is $\epsilon_{sam}(\ell (\ngl(n) +2^{-\Omega(n)})) = \ngl(n)$-close to a distribution $V', U_{\ell\times r_{sam}}$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.
+Let $\eta = \Omega(\log n)$.
+Denote by $\epsilon_{sam} = \ngl(n) + 2^{-\Omega(n)} = \ngl(n)$ the value from \lemref{lem:sampling works}.
+Then, the distribution $(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
 \end{corollary}
 \begin{proof}
-Union bound over the statistical distance in \lemref{lem:sampling works}.
+Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
 \end{proof}
@@
 \label{cor:v are unguessable}
+Let $W, V, \Lambda, V', U_{\ell\times r_{sam}}$ be as in \corref{cor:samp sec}.
 Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\ell\times r_{sam}}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
@@
 \label{cor:samp unguess}
-Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
+Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator \bnote{what type of obfuscator?} with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \ell\epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
 \end{corollary}
@@
 Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.
-Let $c = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq c(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
+Let $c = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq c(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\eta})$ where the probability is over the coins of $\gen$.
 \end{lemma}
@@
 \begin{align*}
-\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \ell}) 
+\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \eta}) 
 \end{align*}
@@
 \begin{corollary}
-Let $\ell = \omega(\log n)$ and let $C\subset\zo^\ell$ and  be a code that corrects $t' = \Theta(\ell)$ $0\rightarrow 1$ bit errors.  Then when 
-\[
-\dis(w, w')\leq \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
+Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ and  be a code that corrects $t' = \Theta(\ell)$ $0\rightarrow 1$ bit errors.  Then when 
+\[
+\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
 \] 
@@
 \[
-\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\ell}) = 1-\ngl(n).
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) = 1-\ngl(n).
 \]

### 2014-02-03 trunk/constantRate/ConstCompFuzzExt.tex
notation and Omer notes

@@
 We also need the obfuscation to be $\ell$-composable~(\defref{def:obf comp}).
-
+\onote{if we need it, should put the def here not in the appendix.
+Also say that we need an AI definition}\onote{should discuss assumptions for composable AI point obfuscation.
+Here it make a lot of difference it we can get by with VGB}\onote{might be simpler to just define a set function instead of a point function and skip the composability stuff}
 We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
@@
 \label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
+A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent \onote{remove dependent} auxiliary input if the following conditions are met:
 \begin{enumerate}
@@
 Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
+\onote{consider removing the notions you do not use}
 \item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
+\onote{this follows from the fact that O is PPT}
 \item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
@@
 We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.  We discuss  block unguessable distributions in \apref{sec:characterize}.
-To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
+To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable \onote{fix}.
 Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
 First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).
-It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.
+It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ \onote{is small}.
 Define the distribution $X$ as follows:
@@
 \item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
-\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ cannot distinguish between $C$ and $C'$.
+\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ \onote{fix: making polynomial number of oracle queries to $\mathcal{O}_X$}cannot distinguish between $C$ and $C'$.
 That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
+\onote{sounds like VGB is enough}
 This is done in \lemref{lem:sim cannot distinguish}.
@@
 
-\noindent Together these arguments allow us to conclude:
+\noindent Together these arguments allow us to conclude: \onote{Shouldn't this theorem have a proof? All of these parameter do not seem to follow trivially from the bullet points before.}
 \begin{theorem}

### 2014-02-03 trunk/constantRate/ConstCompFuzzExt.tex
proof of security of construction

@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon_{code}$.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \delta_{code}$.
 \end{definition}
@@
 %\begin{definition}
-%A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
+%A binary $(\neigh_t, \delta_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
 %\end{definition}
@@
 Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
-$(\neigh_t, \epsilon_{code})$-error-correcting code.
+$(\neigh_t, \delta_{code})$-error-correcting code.
 We describe $\gen, \rep$ as follows:
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
 \[
@@
 %\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
-We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.  We discuss  block unguessable distributions in \apref{sec:characterize}.
-To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable \onote{fix}.
-Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
-First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).
-It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ \onote{is small}.
-Define the distribution $X$ as follows:
-\[X_i =
-\begin{cases}
-W_i & C_i = 0\\
-R_i & C_i = 1.
-\end{cases}\]
-The outline for the rest of the proof is as follows:
-\begin{itemize}
-\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
-\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ \onote{fix: making polynomial number of oracle queries to $\mathcal{O}_X$}cannot distinguish between $C$ and $C'$.
-That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
-\onote{sounds like VGB is enough}
-This is done in \lemref{lem:sim cannot distinguish}.
-% the following steps:
-%\begin{itemize}
-%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
-%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
-%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
-%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
-%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).
-%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
-%\end{itemize}
-\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
-\end{itemize}
-
-\noindent Together these arguments allow us to conclude: \onote{Shouldn't this theorem have a proof? All of these parameter do not seem to follow trivially from the bullet points before.}
+We discuss  block unguessable distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for block unguessable distributions:
 \begin{theorem}
 \label{thm:security of cons}
-Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator \bnote{grey box?} with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
+Let $\mathcal{O}$ be an $\ell$-composable virtual gray box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
 Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
@@
 \end{theorem}
+
+We give a brief outline of the proof here, the full proof is in \apref{app:security of main cons}.
+It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
+Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
+We first note that $C'$ has sufficient entropy.
+That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.
+It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
+%Define the distribution $X$ as follows:
+%\[X_i =
+%\begin{cases}
+%W_i & C_i = 0\\
+%R_i & C_i = 1.
+%\end{cases}\]
+The outline for the rest of the proof is as follows:
+\begin{itemize}
+\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}}(C)$.
+\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}}(C) \approx S^{\mathcal{O}}(C')$. 
+\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$.
+\end{itemize}
 
@@
 \label{lem:correct of cons}
-Let $C$ be a $(\neigh_t, \epsilon_{code})$-code.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then
-\[
-\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\epsilon_{code}\right).
+Let $C$ be a $(\neigh_t, \delta_{code})$-code.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then
+\[
+\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\delta_{code}\right).
 \]
@@
 Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$ with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
-Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
+Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \delta_{code})$ code.
 Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable obfuscator\bnote{right def?} for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
@@
 Let $t$ be the number of supported errors between $w$ and $w'$.
+\bnote{should really use something other than $c$ here}
 Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
@@
 Let $\alpha$ be a parameter.
-Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.
+Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of blocks such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.
 Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
@@
 \end{proof}
-In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
+\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
 \clref{cl:independent high ent} captures this type of distribution.
-We now consider more complicated distributions where blocks are not independent.
+
+However, \defref{def:block guessable} captures considerably more distributions.  We now consider more complicated distributions where blocks are not independent.
 
@@
 Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.
-We can prove a similar claim in the case where $f$ is not injectiveall blocks do not a source~(determined by $f$).
+We can prove a slightly weaker claim when the correlation between $W_i$ is arbitrary:
 
@@
 Let $W = W_1,..., W_\ell$ be a source.
-Let $\alpha =\omega(\log n)$ and suppose that for all $i$ $\Hoo(W_i)\geq \alpha$, then for $q = \poly(n)$, $\alpha ' = \omega(\log n)$, $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
+Let $\alpha =\omega(\log n)$ and suppose that for all $i$ $\Hoo(W_i)\geq \alpha$, then for $q = \poly(n)$, there exists a $\alpha ' = \omega(\log n)$ such that $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
 \end{claim}
@@
 \section{Proof of \thref{thm:security of cons}}
-\noindent
+\label{app:security of main cons}
+\begin{proof}
+
+Let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
+Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+Our goal is to how that $H^{\hill}_{\epsilon', s_{obf}}(C|P)\geq |C|- \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
+
+By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.
+Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.
+Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.
+By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.
+Define the distribution $X$ as follows:
+\[X_i =
+\begin{cases}
+W_i & C_i = 0\\
+R_i & C_i = 1.
+\end{cases}\]
+
+Let $D$ be some distinguisher of size at most $s_{obf}$.  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $s_{obf}$ queries) such that
+\begin{align}
+\label{eq:dist before}
+|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{obf}.
+\end{align}
+
 We now prove $S$ cannot distinguish between $C$ and $C'$.
-Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
-Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
 \begin{lemma}
@@
 
+\noindent Now by the security of obfuscation we have that 
+\begin{align}
+\label{eq:dist after}
+|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{obf}.
+\end{align}
+Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
+\begin{align*}
+\delta^{D}(( P, C), (P, C'))&\leq |\expe \expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
+&+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\
+&+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
+&\leq \epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{obf}.
+\end{align*}
+This completes the proof of \thref{thm:security of cons}.
+\end{proof}
+
 \end{document}

### 2014-02-03 trunk/constantRate/ConstCompFuzzExt.tex
cleaning up linking language

@@
 
-We note that for any code learning a few bits does not inform on the remainder of the bits.
+We note that for any code learning a few bits does not inform on the remainder of the bits~(the claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
 
@@
 \end{claim}
-This claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
-
-%need one special property of the code, namely that each output bit is set to $1$ with probability $1/2$.
-
-%\bnote{I don't think we need this!}
-%\begin{definition}
-%A binary $(\neigh_t, \delta_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
-%\end{definition}
-%All binary linear codes~(without constant bits) are output equiprobable and .
-This is true as long as $C$ contains no constant bits.
-Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
-For the remainder of this work when we say a code, we assume there are no constant bits.
-%
-%\begin{lemma}
-%\label{lem:linear codes independent}
-%Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
-%\end{lemma}
-%Proof in \apref{sec:proof of linear indep}.
-%
-%
 
@@
 
-We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
+We focus on computational fuzzy extractors introduced~\cite{fuller2013computational}.
 Definitions for information-theoretic fuzzy extractors can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
@@
 \label{sec:construction}
-\bnote{this needs to be rewritten}
-Before describing our construction, we recall the problem we are trying address.
-The goal is to derive strong keys from noisy sources.
-As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is  negative.
-In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.
-Thus, we focus on providing enough security when $gap<0$.
-We build a computational fuzzy conductor, which can be converted to a computational fuzzy extractor using a computational extractor~(\lemref{lem:cond and cext}).%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
-Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.
-As described in Fuller, Meng, and Reyzin~\cite{fuller2013computational}, use of a computational fuzzy extractor may allow a construction when $gap = O(\log n)$.
-Their construction is only applicable for high entropy input and yield a result when $gap$ is small.
-We will provide the first construction where $gap$ is negative.
+For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.
+Our goal is to derive strong keys when the number of possible error patterns is larger than the starting entropy of source.
+That is we want to provide some security when $0>gap = \Hoo(W) - \log|B_t|$.
+In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
+Thus, we focus on building a computational fuzzy conductor with meaningful output entropy.
+Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
 
@@
 \label{sec:sec of construction}
-\bnote{this paragraph needs to be rewritten}
-Assuming virtual black-box obfuscation, we argue security in the presence of equality oracles for each block.
-The adversary is provided with equality oracles for each block individually.
-Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.
+\consref{cons:first construction} is secure if no distinguisher can tell whether they are working with random obfuscations or obfuscations of $W_i$.
+By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
+This means we can consider what the adversary learns using adaptive equality queries to individual blocks.
 Our construction is secure as long as enough blocks are unpredictable after adaptive queries~(we discuss minimal conditions for fuzzy extractor security in more depth in \apref{sec:minimal conditions}):
@@
 \]
-That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
+That is, \consref{cons:first construction} is correct with error at most $\ell/2^n+\delta_{code}$.
 \end{lemma}
@@
 
-\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
-The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
-Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
-Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications.
-We begin to address this weakness in the next section.\bnote{come back to this linking language}
+\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to \consref{cons:first construction}.
+First, we require blocks to be super-polynomial in size.
+Second, we only obtain a single bit from each block.
+Third, since each block is individually obfuscated, we leak information about individual blocks.
+To compensate for this leakage, we need most blocks to be unguessable given equality queries.
+Our second construction addresses this last weakness.
 
@@
 In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
-The main advantage of this approach is it expands the supported sources as no single block must have high entropy.
+The main advantage of this approach is reduces the required entropy in each block of the source.
 Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
 Thus, we have a tradeoff between individually required entropy and supported error tolerance.
-In ordering for sampling to work properly, we need a source that is likely contribute some entropy from a randomly chosen block.
+In ordering for sampling to work properly, we need a source where most blocks are likely to contribute some entropy.
 
@@
 \defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.
-This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
+This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}).
+An unguessable block distribution is a statement about the average remaining entropy while an unordered block source is a worst case condition.
+However, we achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
 We use an algorithm that draws random samples from block sources.
@@
 \subsection{Security of \consref{cons:sampling}}
+\bnote{this whole chain of arguments needs to be cleaned up}
 In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has super-logarithmic entropy on its own.
@@
 \label{cor:samp unguess}
-Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator \bnote{what type of obfuscator?} with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \ell\epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
+Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual grey box obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
 \end{corollary}
@@
 Let $t$ be the number of supported errors between $w$ and $w'$.
-\bnote{should really use something other than $c$ here}
-Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
-% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.
-Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.
-Then
+Let $\mu$ be a parameter and let $t = \mu(\gamma-\eta)/\eta$, for any  $i$ one has:
 \begin{align*}
 \expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
-&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
-&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
+&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
+&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
+&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu
 \end{align*}
-Thus, by setting $c = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
+Thus, by setting $\mu = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
 
@@
 Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.
-Let $c = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq c(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\eta})$ where the probability is over the coins of $\gen$.
+Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\eta})$ where the probability is over the coins of $\gen$.
 \end{lemma}
@@
 With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.
-As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^c = t'/(2\eta)$.
+As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^\mu = t'/(2\eta)$.
 By the Chernoff bound, we have
 \begin{align*}
-\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \eta})
+\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \eta}).
 \end{align*}
@@
 \begin{corollary}
-Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ and  be a code that corrects $t' = \Theta(\ell)$ $0\rightarrow 1$ bit errors.  Then when
+Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ be a $(\neigh_t, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
 \[
@@
 \[
-\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) = 1-\ngl(n).
-\]
-That is, \consref{cons:sampling} is correct with error at most $\ngl(n)$.
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) -\delta_{code}= 1-\ngl(n).
+\]
+That is, \consref{cons:sampling} is correct with overwhelming probability.
 
@@
 \subsection{Discussion of \consref{cons:sampling}}
-We now show that \consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.
-For security of an unordered block source we needed both $\alpha = \Theta(1)$ and $\beta\leq \gamma/2-\Omega(1)$.
-This means that the overall required entropy of $\Hoo(W) = \Theta(\gamma)$.
-We are able to correct $O(\gamma/\eta)$ errors
+\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.
+The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
+We are able to correct $O(\gamma/\eta)$ errors.
 This yields:
@@
 \end{align*}
-That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for any fixed $\mathcal{Z}$ we can set $\eta = \omega(\log n)$ and $\eta = o(\log |\mathcal{Z}|)$).
+That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
 If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
+However, in this setting $gap =\Omega(\gamma)$ and known constructions of information-theoretic fuzzy extractors suffice in this setting.
 \bibliographystyle{alpha}

### 2014-02-03 constantRate/ConstCompFuzzExt.tex
adding second construction to introduction

--- 2014-01-30 constantRate/ConstCompFuzzExt.tex
@@
 
+\bnote{there are two constructions now}
 \textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.
@@
 This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
-The length of $r$ is dictated by size of the best code that corrects $t$ errors.
+The length of the key $r$ is dictated by size of the best code that corrects $t$ errors.
 Error-correcting codes are well studied and we have tight bounds on this quantity.
@@
 We consider the Hamming metric.
-For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.
-As we discuss later, it is possible to avoid these losses if the fuzzy extractor has additional knowledge about the distribution.} and logarithm of the number of error patterns to be corrected.
+For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected.
 For the remainder of this paper we denote this quantity by $gap$.
-This represents a real problem, important biometrics, such as irises~\cite{daugman2004}, have $gap <0$ and current fuzzy extractors provide no security guarantee.
+This represents a real problem as $gap<0$ for important biometrics and current fuzzy extractors provide no security guarantee~(see \apref{sec:iris no key}).
 
@@
 
-This does not need to be the case in the computational setting.
-Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.
+To achieve security when $gap<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
+However, the tools for constructing information-theoretic fuzzy extractors have not admitted natural and meaningful restrictions.
+Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
 Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.
-We resolve this question and construct a computational fuzzy extractor when $gap<0$.
+Building a computational fuzzy extractor with $gap<0$ may be possible for a broader class of distributions than is possible in the information-theoretic realm.
+
+In this work, we show that constructing a computational fuzzy extractor is possible for a large class of distributions with $gap<0$.  
+%We resolve this question and construct a computational fuzzy extractor when $gap<0$.
 This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.
@@
 We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).
-
-The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.  
-In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
-Our focus is on expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.
-
-\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.
+%The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.
+In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  We focus on providing a reasonable length key when $gap<0$.
+Fuller, Meng, and Reyzin show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
 Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.
@@
 Here, we follow the second approach and use a \emph{computational} fuzzy conductor.
-
-Our construction~(\consref{cons:first construction}) is based on obfuscation of point programs.
+We present two constructions of computational fuzzy conductors for different types of source distributions $W$.
+These constructions may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
+
+Both of constructions are based on the obfuscation of point programs.
 A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
@@
 Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
-
+Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+
+\textbf{\consref{cons:first construction}: }
 Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).
@@
 This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
-It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.
-Note, it is hard to recover $w$ from the value $c$.
-This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.
-Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
-
-Our construction provides several advantages over previous constructions of computational fuzzy extractors:
-\begin{itemize}
-\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss is necessary in a fuzzy extractor.
-If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.
-This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.
-For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.
-The distributions supported by our construction are not error-correcting codes, we require unpredictability in many dimensions~(see \defref{def:block guessable}).}
-\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
-\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
+
+In \consref{cons:first construction}, each block of $W$ is individually obfuscated.
+This has two drawbacks, first an adversary may learn the value of some blocks which may be sensitive information.
+Second, security only holds for sources where a large number of blocks have super-logarithmic entropy~(\defref{def:block guessable}).
+Our second construction addresses these problems.
+
+\textbf{\consref{cons:sampling}: }  
+As before we consider a source $W=W_1,...,W_\ell$ that is split into blocks.  However, instead of obfuscating individually  
+blocks individually, for each bit $c_i$ we randomly select a subset of blocks.
+These blocks are concatenated and obfuscated together.
+By sampling, we can significantly decrease the entropy requirement on individual blocks.
+This paradigm is similar to the \emph{sample-then-extract} paradigm in the locally-computable extractor literature~\cite{lu2002hyper,vadhan2003constructing}.
+For this reason, we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
+
+%Our construction provides several advantages over previous constructions of computational fuzzy extractors:
+%\begin{itemize}
+%\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
+Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
+%\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
 Our construction simply requires a large number of blocks that are unguessable given equality queries.
 This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
-\end{itemize}
-
-\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.
-This means that blocks much be drawn from distributions with super-logarithmic entropy.
-Furthermore, our distance is Hamming distance over a large alphabet~(super-polynomial in the security parameter).
-Our construction is applicable for physical sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
+%\end{itemize}
+
+\textbf{Limitations: } In order to achieve security with $gap<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
+Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
 Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
-
-\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a stronger object than a computational fuzzy extractor).
-Unfortunately, this is not the case.
-Each block is individually obfuscated, so an adversary may ask equality queries on individual blocks.
-If not all blocks have high entropy an adversary may learn significant information about the source.
-Thus, our construction is not a virtual black box~(VBB) obfuscation~(where anything learnable by the circuit is simulatable using input/output behavior).
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides partial information.
+Furthermore, we may leak sensitive information about the underlying source $W$.
+For example, in \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
+Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides all partial information.
 Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
 
-The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our construction in \secref{sec:construction} and discuss parameters and tradeoffs in \secref{sec:discussion}.
+The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
 
@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon_{code}$.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \delta_{code}$.
 \end{definition}
 
-We note that for any code learning a few bits does not inform on the remainder of the bits.
+We note that for any code learning a few bits does not inform on the remainder of the bits~(the claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
 
@@
 \end{claim}
-This claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
-
-%need one special property of the code, namely that each output bit is set to $1$ with probability $1/2$.
-
-%\bnote{I don't think we need this!}
-%\begin{definition}
-%A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
-%\end{definition}
-%All binary linear codes~(without constant bits) are output equiprobable and .
-This is true as long as $C$ contains no constant bits.
-Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.
-For the remainder of this work when we say a code, we assume there are no constant bits.
-%
-%\begin{lemma}
-%\label{lem:linear codes independent}
-%Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
-%\end{lemma}
-%Proof in \apref{sec:proof of linear indep}.
-%
-%
 
@@
 
-We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.
-Definitions for information-theoretic fuzzy extractors and a non-interactive information-reconciliation component, known as a secure sketch, can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
+We focus on computational fuzzy extractors introduced~\cite{fuller2013computational}.
+Definitions for information-theoretic fuzzy extractors can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
 The definition of computational fuzzy extractors allows for a small probability of error.
@@
 \begin{itemize}
-\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $r = \cext(y; x)$ and $p = (p', x)$.  Output $(r, p)$.
-\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \cext(y; x)$. 
+\item $\gen(w; seed):$ run $(x, ss)= \gen'(w)$ and set $r = \cext(x; seed)$, $p = (ss, seed)$.  Output $(r, p)$.
+\item $\rep(w, (ss, seed)):$ recover $x = \rec'(w'; p')$ and output $r = \cext(x; seed)$.
 \end{itemize}
@@
 \label{sec:construction}
-
-Before describing our construction, we recall the problem we are trying address.
-The goal is to derive strong keys from noisy sources.
-As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
-In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.
-Thus, we focus on providing enough security when $gap<0$.
-We build a computational fuzzy conductor, which can be converted to a computational fuzzy extractor using a computational extractor~(\lemref{lem:cond and cext}).%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).
-Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.
-As described in Fuller, Meng, and Reyzin~\cite{fuller2013computational}, use of a computational fuzzy extractor may allow a construction when $gap = O(\log n)$.
-Their construction is only applicable for high entropy input and yield a result when $gap$ is small.
-We will provide the first construction where $gap$ is negative.
+For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.
+Our goal is to derive strong keys when the number of possible error patterns is larger than the starting entropy of source.
+That is we want to provide some security when $0>gap = \Hoo(W) - \log|B_t|$.
+In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
+Thus, we focus on building a computational fuzzy conductor with meaningful output entropy.
+Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
 
@@
 Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
-$(\neigh_t, \epsilon_{code})$-error-correcting code.  
+$(\neigh_t, \delta_{code})$-error-correcting code.
 We describe $\gen, \rep$ as follows:
@@
 \item For $i=1,..., \ell$:
-\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
-\subitem Else: Sample $r_i \leftarrow U_n$. 
-\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
+\begin{enumerate}
+\item If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
+\item Else: Sample $r_i \leftarrow U_n$.
+\subitem Let $p_i = \mathcal{O}(I_{r_i})$.
+\end{enumerate}
 \item Output $(c, p)$.
@@
 \label{sec:sec of construction}
-\bnote{this paragraph needs to be rewritten}
-Assuming virtual black-box obfuscation, we argue security in the presence of equality oracles for each block.
-The adversary is provided with equality oracles for each block individually.
-Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.
-Our construction is secure as long as enough blocks are unpredictable after adaptive queries:
+\consref{cons:first construction} is secure if no distinguisher can tell whether they are working with random obfuscations or obfuscations of $W_i$.
+By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
+This means we can consider what the adversary learns using adaptive equality queries to individual blocks.
+Our construction is secure as long as enough blocks are unpredictable after adaptive queries~(we discuss minimal conditions for fuzzy extractor security in more depth in \apref{sec:minimal conditions}):
 
@@
 %\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
-We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
-In \apref{sec:characterize} we provide discussion on the types of sources that satisfy \defref{def:block guessable}.
-To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.
-Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
-First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).
-It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.
-Define the distribution $X$ as follows:
-\[X_i = 
-\begin{cases}
-W_i & C_i = 0\\
-R_i & C_i = 1.
-\end{cases}\]
-The outline for the rest of the proof is as follows:
-\begin{itemize}
-\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
-\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ cannot distinguish between $C$ and $C'$.
-That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
-This is done in \lemref{lem:sim cannot distinguish}.
-% the following steps:
-%\begin{itemize}
-%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
-%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
-%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
-%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
-%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
-%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
-%\end{itemize}
-\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
-\end{itemize}
-
-Together these arguments allow us to conclude:
+We discuss  block unguessable distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for block unguessable distributions:
 \begin{theorem}
 \label{thm:security of cons}
-Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
+Let $\mathcal{O}$ be an $\ell$-composable virtual gray box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
 Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
@@
 
-\noindent
-We now prove $S$ cannot distinguish between $C$ and $C'$.  
-Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.
-Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
-\begin{lemma}
-\label{lem:sim cannot distinguish}
-$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
-\end{lemma}
-
-\begin{proof}
-\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
-\begin{lemma}
-\label{lem:codewords in I close}
-Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then, 
-\[
-\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
-\]
-\end{lemma}
-\begin{proof}
-Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
-The only information about the correct value of $c_i^*$ is contained in the query responses.
-When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
-We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
-Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
-Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
-Thus, it must occur with probability:
-\begin{align}
-2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
- &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
-&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
-\end{align}
-We now show that $n-\log q \geq \alpha$:
-\begin{claim}
-\label{cl:ent bounded away from n}
-$n-\log q \geq \alpha$
-\end{claim}
-\begin{proof}
-It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.
-Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
-After these queries the remaining min-entropy is at most:
-\begin{align*}
-\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
-&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
-&=-\log\left( 2^{-n+\log q} \right) = n-\log q
-\end{align*}
-This completes the proof of \clref{cl:ent bounded away from n}.
-\end{proof}
-\noindent
-Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
-\begin{align*}
- \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
- \end{align*}
- When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
-If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
-This concludes the proof of \lemref{lem:codewords in I close}
-\end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
-This completes the proof of \lemref{lem:sim cannot distinguish}.
-\end{proof}
+We give a brief outline of the proof here, the full proof is in \apref{app:security of main cons}.
+It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
+Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
+We first note that $C'$ has sufficient entropy.
+That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.
+It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
+%Define the distribution $X$ as follows:
+%\[X_i =
+%\begin{cases}
+%W_i & C_i = 0\\
+%R_i & C_i = 1.
+%\end{cases}\]
+The outline for the rest of the proof is as follows:
+\begin{itemize}
+\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}}(C)$.
+\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}}(C) \approx S^{\mathcal{O}}(C')$. 
+\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$.
+\end{itemize}
 
@@
 \label{lem:correct of cons}
-Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then 
-\[
-\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n}.
-\]
-That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
+Let $C$ be a $(\neigh_t, \delta_{code})$-code.  When $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
+\[
+\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\delta_{code}\right).
+\]
+That is, \consref{cons:first construction} is correct with error at most $\ell/2^n+\delta_{code}$.
 \end{lemma}
@@
 \textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
-However, this requires a codeword where most codewords have Hamming weight close to $1/2$.
+This requires a code where most codewords have Hamming weight close to $1/2$.
 
@@
 
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correctness for block unguessable distributions:
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for block unguessable distributions:
 \begin{theorem}
 Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$ with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 
-\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.
-The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.
-Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
-Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications.
-We begin to address this weakness in the next section.
+\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to \consref{cons:first construction}.
+First, we require blocks to be super-polynomial in size.
+Second, we only obtain a single bit from each block.
+Third, since each block is individually obfuscated, we leak information about individual blocks.
+To compensate for this leakage, we need most blocks to be unguessable given equality queries.
+Our second construction addresses this last weakness.
 
 \section{Sample-then-Obfuscate}
+\label{sec:sampling}
 \consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
-In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.
-This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.
-Second, it allows us to decrease the size of each block from exponential to a super polynomial $2^{\log^c n}$ for some $c>0$.
+In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
+The main advantage of this approach is reduces the required entropy in each block of the source.
 Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
-In ordering for sampling to work properly, we need a source that is likely contribute some entropy from a randomly chosen block.
+Thus, we have a tradeoff between individually required entropy and supported error tolerance.
+In ordering for sampling to work properly, we need a source where most blocks are likely to contribute some entropy.
 
@@
 \defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.
-This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
+This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}).
+An unguessable block distribution is a statement about the average remaining entropy while an unordered block source is a worst case condition.
+However, we achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
+We use an algorithm that draws random samples from block sources.
+Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample$.
 \begin{construction}
@@
 Let $n$ be a security parameter.
-Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.
-Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.
-Let $\sample_\beta(\gamma)$ output a uniform subset of indices of $1,..., \gamma$ of size $\beta$.
-Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.
-Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
+Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \delta_{code})$ code.
+Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable obfuscator\bnote{right def?} for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
 Define $\gen, \rep$ as:
@@
 \item For $i=1,..., \ell$:
-\begin{itemize}
-\item Sample $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_\eta(\gamma)$
+\begin{enumerate}
+\item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
+\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
 \item If $c_i = 0$:
 \subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
-\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
-\subitem Set $p_i = \rho_i, j_{i, 1},..., j_{i, \eta}$.
+\subitem Set $\rho_i = \mathcal{O}(I_{v_i})$.
+\subitem Set $p_i = \rho_i, \lambda_i$.
 \item If $c_i = 1$: Sample $r_i \leftarrow U_n$.
-\subitem Let $p_i = \mathcal{O}(I_{r_i}) j_{i,1},..., j_{i, \eta}$.
-\end{itemize}
+\subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
+\end{enumerate}
 \item Output $(c, p)$.
@@
 \item For $i=1,..., \ell$:
-\begin{itemize}
-\item Parse $p_i$ as $\rho_i, j_{i, 1},..., j_{i, \eta}$.
-\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
-\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
+\begin{enumerate}
+\item Parse $p_i$ as $\rho_i, \lambda_i$.
+\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
+\item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
+\item If $\rho_i(v_i') = 1$ set $c_i' = 0$.
 \item Else set $c_i' = 1$.
-\end{itemize}
+\end{enumerate}
 \item Set $c = \decode(c')$.
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+There is a crucial difference, our use of a computational primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
 In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
-Our construction uses the na\"{i}ve sampler that takes truly random samples, the analysis is essentially the same for more sophisticated samplers that use fewer random bits.
-Goldreich provides an accessible introduction to samplers~\cite{goldreich1997sample}.
-
-As before we must show security and correctness of \consref{cons:sampling}.
-For security, the main argument is that each of the $v_i$ has enough entropy to be unguessable.
-For correctness we must show that the induced error rate in $v$ and $v'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.
+Our construction uses the na\"{i}ve sampler that takes truly random samples, but the public randomness can be substantially decreased by using more sophisticated samplers.
+Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.
+
+As before we show security and correctness of \consref{cons:sampling}.
+For security, we argue that each of the $v_i$ is unguessable.
+For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability) so that $c'$ will be corrected to $c$ with overwhelming probability.
 
 \subsection{Security of \consref{cons:sampling}}
+\bnote{this whole chain of arguments needs to be cleaned up}
 In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has super-logarithmic entropy on its own.
+A sampler will select enough good blocks almost all the time, meaning if we take enough samples we obtain a super-logarithmic amount of entropy.
 This means that  $V_1,..., V_\ell$ is a block-unguessable distribution~(by \clref{cl:all blocks entropy}) and security follows by \thref{thm:security of cons}.
-Consider a source with entropy $\lambda$.
-The expected number of selected blocks that have entropy at least $\alpha$ is $\frac{\gamma-\beta}{\gamma} \times \beta$.
-A good sampler selects within a constant fraction of the expected number of these blocks.
 
@@
 \label{lem:sampling works}
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.
+Let $\eta = \Omega(\log n)$.
+Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
+\end{lemma}
+\begin{proof}
+By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.
+\bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}
+\end{proof}
+
+\begin{corollary}
+\label{cor:samp sec}
 Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.
 Let $\eta = \Omega(\log n)$.
-Consider some fixed $i$, the distribution $V_{i}, J_{i, 1},..., J_{i, \eta}$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{\beta\times \log \gamma}$ where for all $u\in U_{\beta \times \log \gamma}$ $V' | A=a$, $\Hoo(V' | A=a) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.\bnote{need to come up with the right number of coins for $\sample$}
-\end{lemma}
-\begin{proof}
-By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.
-\bnote{need someone to check parameters, I am fairly sure of the quality of the statement}
-\end{proof}
-%\begin{align*}
-%\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
-%&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
-%\end{align*}
-%This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.
-Note this is independent of how the entropy is distributed between blocks.
-In particular, we make no assumptions about particular blocks being unguessable, only about the overall entropy rate.
-This is a much more natural condition for a source than \defref{def:block guessable}.
-%To show security we need the entropy of all $v_i$ to be $\omega(\log n)$ with overwhelming probability.  This follows by an argument from the locally computable extractor literature.
-
-\begin{corollary}
-\label{cor:samp sec}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.  Let $\eta = \Omega(\log n)$.  
-The distribution $V, J$ is $\epsilon_{sam}(\ell (\ngl(n) +2^{-\Omega(n)})) = \ngl(n)$-close to a distribution $V', U_{\beta\times \ell \times \log \gamma}$ where for $u\in U_{\beta\times \ell\times \log \gamma}$ for all $i$, $\Hoo(V_i' | U_{\beta\times \ell \times \log \gamma}) \geq \alpha'$.
+Denote by $\epsilon_{sam} = \ngl(n) + 2^{-\Omega(n)} = \ngl(n)$ the value from \lemref{lem:sampling works}.
+Then, the distribution $(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
 \end{corollary}
 \begin{proof}
-Union bound over the statistical distance in \lemref{lem:sampling works}.
+Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
 \end{proof}
@@
 \label{cor:v are unguessable}
-Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\beta \times \log \gamma}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
+Let $W, V, \Lambda, V', U_{\ell\times r_{sam}}$ be as in \corref{cor:samp sec}.
+Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\ell\times r_{sam}}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
 \end{corollary}
@@
 \label{cor:samp unguess}
-Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha-1)}) = \ngl(n)$.
+Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual grey box obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
 \end{corollary}
@@
 Let $t$ be the number of supported errors between $w$ and $w'$.
-Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
-% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.
-Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.
-Then
+Let $\mu$ be a parameter and let $t = \mu(\gamma-\eta)/\eta$, for any  $i$ one has:
 \begin{align*}
 \expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
-&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
-&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
+&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
+&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
+&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu
 \end{align*}
-Thus, by setting $c = -\log(1-t')/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
-
-\bnote{finish, Chernoff, not far from expectation.}
-
-\subsection{Discussion}
-\bnote{need to write this once we have parameters in the two sections above.}
-%As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
-%\begin{align*}
-%gap &= \Hoo(W) -\log |B_t| \\
-%&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
-%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
-%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
-%&= \omega(\frac{\gamma \log n}{\eta})
-%\end{align*}
-%%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
-%\bnote{finish}
+Thus, by setting $\mu = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
+
+\begin{lemma}
+Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.
+Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\eta})$ where the probability is over the coins of $\gen$.
+\end{lemma}
+\begin{proof}
+With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.
+As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^\mu = t'/(2\eta)$.
+By the Chernoff bound, we have
+\begin{align*}
+\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \eta}).
+\end{align*}
+\end{proof}
+
+\begin{corollary}
+Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ be a $(\neigh_t, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
+\[
+\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
+\]
+and $(R, P)\leftarrow \gen(w)$, then
+\[
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) -\delta_{code}= 1-\ngl(n).
+\]
+That is, \consref{cons:sampling} is correct with overwhelming probability.
+
+\end{corollary}
+\subsection{Discussion of \consref{cons:sampling}}
+\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.
+The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
+We are able to correct $O(\gamma/\eta)$ errors.
+This yields:
+\begin{align*}
+gap &= \Hoo(W) -\log |B_t| \\
+&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
+&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
+\end{align*}
+That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
+If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
+However, in this setting $gap =\Omega(\gamma)$ and known constructions of information-theoretic fuzzy extractors suffice in this setting.
 \bibliographystyle{alpha}
@@
 \begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
-Let $S$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $S$.
-Define $(Y, P) \leftarrow \gen'(W)$.
-Then there must exist a distribution $Z$ with $\Hav(Z|P) \geq \tilde{m}$ such that $\mathbf{SD}((Y, P), (Z, P))\leq \epsilon$.
-By Markov's inequality, there exists some set $S_P$ such that $\Pr[P\in S_p] \geq 1/2$ and $\forall p\in S_P$ one has $\mathbf{SD}(Y | P = p, p ), (Z | P = p, p)<2\epsilon$.
-Now applying Markov's inequality of $\max_{z} \Pr[Z=z | P=p]$, there exists a set $S_P'$ such that $\Pr[P\in S_P']>1/2$, and for all $p\in S_P'$, $\Hoo(Z| P =p ) \geq \tilde{m}-1$.
-Denote by $p^*$ a value in $S_P\cap S_P'$~(one value must exist).
-Then $\mathbf{SD}((Y | P =p^* , p^*), (Z| P = p^*, p^*))\leq 2\epsilon$ and $\Hoo(Z|P=p^*)\geq \tilde{m}-1$.
-Denote by the set $T$ the possible values of $Y$ when $P=p^*$.
-For the statistical distance property to hold, $|T| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
-Associate with every $y\in T$ some $w\in S$ which could have produced $y$ with nonzero probability given $P=p^*$, and call this map $C$.
+Let $A$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $A$.
+Define $(X,SS) \leftarrow \gen'(W)$.
+Then there must exist a distribution $Y$ with $\Hav(Y|SS) \geq \tilde{m}$ such that $\Delta((X,SS), (Y, SS))\leq \epsilon$.
+By Markov's inequality, there exists some set $B_{SS}$ such that $\Pr[ss\in B_{SS}] \geq 1/2$ and $\forall s\in B_{SS}$ one has $\Delta(X | SS = s, s ), (Y | SS = s, s)<2\epsilon$.
+Now applying Markov's inequality of $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.
+Denote by $s^*$ a value in $B_{SS}\cap B_{SS'}$~(one value must exist).
+Then $\Delta((X | SS =s^* , s^*), (Y| SS = s^*, s^*))\leq 2\epsilon$ and $\Hoo(Y|SS=s^*)\geq \tilde{m}-1$.
+Denote by the set $A'$ the possible values of $X$ when $SS=s^*$.
+For the statistical distance property to hold, $|A'| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
+Associate with every $x\in A'$ some $w\in S$ which could have produced $x$ with nonzero probability given $SS=s^*$, and call this map $C$.
 $C$ defines an error correcting code with the required parameters.
-
-\end{proof}
-
-%\section{Proof of \lemref{lem:linear codes independent}}
-%\label{sec:proof of linear indep}
-%\begin{proof}
-%Suppose there is some $i$ that is not equiprobable.
-Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$.
-First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$.
-First suppose that $0<|C_{i_1}| < |C_{i_0}|$.
-Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.
-Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.
-This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.
-%Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.
-This is a contradiction and completes the proof.
-%\end{proof}
+\end{proof}
+
+\section{$gap<0$ for Irises}
+\label{sec:iris no key}
+The iris is the biometric believed to have the most entropy.
+The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
+Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
+The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.
+This transform is designed for the process of identification, achieving the best possible true accept/false accept tradeoff.
+
+The precise number of errors that must be tolerated depends on the desired true accept rate (how often the correct key is produced).
+For a true accept rate of $20\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
+The comparison between the two readings is then made using bits not excluded by either image.
+It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $gap$:
+\begin{align*}
+gap &= \Hoo(W) - \log |B_t|\\
+&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
+\end{align*}
+Irises are believed to be the strongest biometric and reliable key derivation from irises is an open problem.
+
+\section{Minimal Conditions for Fuzzy Extractor Security}
+\label{sec:minimal conditions}
+As mentioned in the introduction a necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.
+In the interactive setting using multi-party computation it is possible to achieve security under this condition.
+We codify this notion:
+
+\begin{definition}
+\label{def:fuzzy min-ent}
+A distribution $W$ in a metric space $\mathcal{M}$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) = k$ if the following holds:
+\[
+\forall m\in \mathcal{M} Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+\]
+\end{definition}
+\begin{lemma}
+Let $n$ be a security parameter and let $W$ be a distribution over $\mathcal{M}$
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) if $\kappa =\omega(\log n)$.
+\end{lemma}
+\begin{proof}
+Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+This means that there exists a point $m\mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
+Consider the following distinguisher $D$:
+\begin{itemize}
+\item On input $r, p$.
+\item If $\rep(m, p) = r$, output $1$.
+\item Else output $0$.
+\end{itemize}
+First note that $|D|$ is of size $\log |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n)$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
+\[
+\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} - \frac{1}{2^{-\kappa}} = 1/\poly(n).
+\]
+\end{proof}
+
+For the Hamming distance having $\Hfuzz(W)\geq \omega(\log n)$ means that there are more entropic dimensions that the desired error-tolerance.
+There are two minimal types of distributions that provide $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).
+The other is that there $t+\omega(\log n)$ blocks that contribute some constant amount of entropy.
+Definitions~\ref{def:block guessable} and~\ref{def:unordered source} are geared towards this type of source, achieving security when the number of entropic blocks is only one greater than the desired error correction is an open problem.
 
@@
 \begin{proof}
-It suffices to show if there is some distinguisher $D$ of size $s'$ where 
-\[\delta^D((\cext(W; X), U_d, P), (U_\kappa, U_d, P))>\epsilon_{cond}+ \epsilon_{ext}\]
- then there is an distinguisher $D'$ of size $s_{cond}$ where for all $Z$ where $\Hav(Z|P)\geq \tilde{m}$ such that
- \[
- \delta^{D'}((Y, P), (Z, P))\geq \epsilon_{cond}.
- \]
-Let $D$ be such a distinguisher.  That is,
-\[
-\delta^D(\ext(X, U_d)\times U_d \times P, U_\kappa\times U_d\times P)> \epsilon_{ext}+\epsilon_{cond}.
-\]
-Then define $D'$ as follows.
-On input $y, p$ sample $x\leftarrow U_d$, compute $r\leftarrow \cext(y, x)$ and output $D(r, x, p)$.
-Note that $|D'| \approx s' + |\cext| +d= s_{cond}$.
+It suffices to show if there is some distinguisher $D'$ of size $s'$ where
+\[\delta^{D'}((\cext(X; U_d), U_d, SS), (U_\kappa, U_d, SS))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D$ of size $s_{cond}$ where for all $Y$ where $\Hav(Y|SS) \geq \tilde{m}$ such that
+ \[
+ \delta^{D}((X, SS), (Y, SS))\geq \epsilon_{cond}.
+ \]
+Let $D'$ be such a distinguisher.  That is,
+\[
+\delta^{D'}(\cext(X, U_d)\times U_d \times SS, U_\kappa\times U_d\times SS)> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D$ as follows.
+On input $(y, ss)$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, ss)$.
+Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
 Then we have the following:
 \begin{align*}
-\delta^{D'}((Y, P), (Z, P))&= \delta^D((\cext(Y, U_d), U_d, P), \cext(Z, U_d), U_d, P)\\
-&\geq \delta^D((\cext(Y, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^D((\cext(Z, U_d), U_d, P), (U_\kappa\times U_d \times P))\\
+\delta^{D}((X, SS), (Y, SS))&= \delta^{D'}((\cext(X, U_d), U_d, SS), \cext(Y, U_d), U_d, SS)\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^{D'}((\cext(Y, U_d), U_d, SS), (U_\kappa\times U_d \times SS))\\
 &>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
 \end{align*}
-Thus $D'$ distinguishes $Y$ from all $Z$ with sufficient conditional min-entropy.  This is a contradiction.
+Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
+\end{proof}
+
+\section{Proof of \thref{thm:security of cons}}
+\label{app:security of main cons}
+\begin{proof}
+
+Let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
+Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+Our goal is to how that $H^{\hill}_{\epsilon', s_{obf}}(C|P)\geq |C|- \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
+
+By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.
+Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.
+Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.
+By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.
+Define the distribution $X$ as follows:
+\[X_i =
+\begin{cases}
+W_i & C_i = 0\\
+R_i & C_i = 1.
+\end{cases}\]
+
+Let $D$ be some distinguisher of size at most $s_{obf}$.  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $s_{obf}$ queries) such that
+\begin{align}
+\label{eq:dist before}
+|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{obf}.
+\end{align}
+
+We now prove $S$ cannot distinguish between $C$ and $C'$.
+\begin{lemma}
+\label{lem:sim cannot distinguish}
+$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
+\end{lemma}
+
+\begin{proof}
+\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
+\begin{lemma}
+\label{lem:codewords in I close}
+Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
+\[
+\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
+\]
+\end{lemma}
+\begin{proof}
+Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
+The only information about the correct value of $c_i^*$ is contained in the query responses.
+When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
+We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
+Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
+Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
+Thus, it must occur with probability:
+\begin{align}
+2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
+ &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
+&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
+\end{align}
+We now show that $n-\log q \geq \alpha$:
+\begin{claim}
+\label{cl:ent bounded away from n}
+$n-\log q \geq \alpha$
+\end{claim}
+\begin{proof}
+It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.
+Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
+After these queries the remaining min-entropy is at most:
+\begin{align*}
+\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
+&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
+&=-\log\left( 2^{-n+\log q} \right) = n-\log q
+\end{align*}
+This completes the proof of \clref{cl:ent bounded away from n}.
+\end{proof}
+\noindent
+Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
+\begin{align*}
+ \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
+ \end{align*}
+ When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
+If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
+By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
+This concludes the proof of \lemref{lem:codewords in I close}
+\end{proof}
+By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
+This completes the proof of \lemref{lem:sim cannot distinguish}.
+\end{proof}
+
+\noindent Now by the security of obfuscation we have that 
+\begin{align}
+\label{eq:dist after}
+|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{obf}.
+\end{align}
+Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
+\begin{align*}
+\delta^{D}(( P, C), (P, C'))&\leq |\expe \expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
+&+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\
+&+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
+&\leq \epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{obf}.
+\end{align*}
+This completes the proof of \thref{thm:security of cons}.
 \end{proof}

### 2014-02-03 trunk/constantRate/ConstCompFuzzExt.tex

@@
 
-\bnote{the whole introduction should be rewritten, doesn't mention second construction.}
 We consider the Hamming metric.
-For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.
-As we discuss later, it is possible to avoid these losses if the fuzzy extractor knows something about the distribution.} and logarithm of the number of error patterns to be corrected.
+For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected.
 For the remainder of this paper we denote this quantity by $gap$.
-This represents a real problem, important biometrics, such as irises~\cite{daugman2004}, have $gap <0$ and current fuzzy extractors provide no security guarantee.
+This represents a real problem as $gap<0$ for important biometrics and current fuzzy extractors provide no security guarantee~(see \apref{sec:iris no key}).
 
@@
 
-This does not need to be the case in the computational setting.
-Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.
+To achieve security when $gap<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
+However, the tools for constructing information-theoretic fuzzy extractors have not admitted natural and meaningful restrictions.
+Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
 Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.
-We resolve this question and construct a computational fuzzy extractor when $gap<0$.
+Building a computational fuzzy extractor with $gap<0$ may be possible for a broader class of distributions than is possible in the information-theoretic realm.
+
+In this work, we show that constructing a computational fuzzy extractor is possible for a large class of distributions with $gap<0$.
+%We resolve this question and construct a computational fuzzy extractor when $gap<0$.
 This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.
@@
 We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).
-
-The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.
-In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.
-Our focus is on expanding the class of distributions for which we can provide meaningful security.
-
-\bnote{two constructions}
-\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.
+%The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.
+In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  We focus on providing a reasonable length key when $gap<0$.
+Fuller, Meng, and Reyzin show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
 Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.
@@
 This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
-It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.
-It is hard to recover $w$ from the value $c$.
-This is necessary to overcome lower bounds on entropy loss~\cite[Section 3.3]{fuller2013computational}.
-Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
-
-Our construction provides several advantages over previous constructions of computational fuzzy extractors:
-\begin{itemize}
-\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss is necessary in a fuzzy extractor.
-If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.
-This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.
-For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.
-The distributions supported by our construction are not error-correcting codes, we require unpredictability in many dimensions~(see \defref{def:block guessable}).}
-\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
-\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
+
+In \consref{cons:first construction}, each block of $W$ is individually obfuscated.
+This has two drawbacks, first an adversary may learn the value of some blocks which may be sensitive information.
+Second, security only holds for sources where a large number of blocks have super-logarithmic entropy~(\defref{def:block guessable}).
+Our second construction addresses these problems.
+
+\textbf{\consref{cons:sampling}: }
+As before we consider a source $W=W_1,...,W_\ell$ that is split into blocks.  However, instead of obfuscating individually
+blocks individually, for each bit $c_i$ we randomly select a subset of blocks.
+These blocks are concatenated and obfuscated together.
+By sampling, we can significantly decrease the entropy requirement on individual blocks.
+This paradigm is similar to the \emph{sample-then-extract} paradigm in the locally-computable extractor literature~\cite{lu2002hyper,vadhan2003constructing}.
+For this reason, we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
+
+%Our construction provides several advantages over previous constructions of computational fuzzy extractors:
+%\begin{itemize}
+%\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
+Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
+%\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
 Our construction simply requires a large number of blocks that are unguessable given equality queries.
 This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
-\end{itemize}
-\bnote{compare contrast constructions}
-
-\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.
-This means that blocks much be drawn from distributions with super-logarithmic entropy.
-Furthermore, our distance is Hamming distance over a large alphabet~(super-polynomial in the security parameter).
-Our construction is applicable for physical sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
+%\end{itemize}
+
+\textbf{Limitations: } In order to achieve security with $gap<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
+Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
 Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
-
-\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a stronger object than a computational fuzzy extractor).
-Unfortunately, this is not the case.
-Each block is individually obfuscated, so an adversary may ask equality queries on individual blocks.
-If not all blocks have high entropy an adversary may learn significant information about the source.
-Thus, our construction is not a obfuscation for any reasonable definition.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides partial information.
+Furthermore, we may leak sensitive information about the underlying source $W$.
+For example, in \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
+Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides all partial information.
 Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
-\bnote{does second construction get closer to obfuscation?}
-
-The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
+
+The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
 
@@
 \label{lem:correct of cons}
-Let $C$ be a $(\neigh_t, \delta_{code})$-code.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then
+Let $C$ be a $(\neigh_t, \delta_{code})$-code.  When $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
 \[
@@
 \[
-\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
+\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
 \]
@@
 &< \Theta(\gamma)- t \log |\mathcal{Z}|\\
-&= \Theta(\gamma) - O(\gamma/\eta) \log |\mathcal{Z}|\\
+&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
 \end{align*}
@@
 \end{proof}
+
+\section{$gap<0$ for Irises}
+\label{sec:iris no key}
+The iris is the biometric believed to have the most entropy.
+The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
+Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
+The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.
+This transform is designed for the process of identification, achieving the best possible true accept/false accept tradeoff.
+
+The precise number of errors that must be tolerated depends on the desired true accept rate (how often the correct key is produced).
+For a true accept rate of $20\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
+The comparison between the two readings is then made using bits not excluded by either image.
+It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $gap$:
+\begin{align*}
+gap &= \Hoo(W) - \log |B_t|\\
+&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
+\end{align*}
+Irises are believed to be the strongest biometric and reliable key derivation from irises is an open problem.
 

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex
editing language in section 5

@@
 
-\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.
-This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}).
-An unguessable block distribution is a statement about the average remaining entropy while an unordered block source is a worst case condition.
-However, we achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.
-We use an algorithm that draws random samples from block sources.
-Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample$.
+\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) where blocks must have entropy conditioned on the value of previous blocks.
+An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).
+An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.
+However, we achieve security for significantly lower entropy levels than were needed for block unguessable distributions.
+
+We use an algorithm that selects a fixed size random subset of $\{1,..., \gamma\}$.
+Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
 \begin{construction}
@@
 Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \delta_{code})$ code.
-Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable obfuscator\bnote{right def?} for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
+Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
 Define $\gen, \rep$ as:
@@
 
-The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.
+The main change in \consref{cons:sampling} is that the obfuscated values are concatenated blocks symbols of $W$.
 This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-There is a crucial difference, our use of a computational primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+There is a crucial difference, our use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
 In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
-Our construction uses the na\"{i}ve sampler that takes truly random samples, but the public randomness can be substantially decreased by using more sophisticated samplers.
+Our construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
 Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.
@@
 \bnote{this whole chain of arguments needs to be cleaned up}
-In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has super-logarithmic entropy on its own.
-A sampler will select enough good blocks almost all the time, meaning if we take enough samples we obtain a super-logarithmic amount of entropy.
-This means that  $V_1,..., V_\ell$ is a block-unguessable distribution~(by \clref{cl:all blocks entropy}) and security follows by \thref{thm:security of cons}.
+\bnote{went through the surrounding text, need to look at all the theorem statements}
+In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $V_i$ has super-logarithmic entropy on its own~(samplers will select ``enough'' of the good blocks of $W$ each time).
+We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
+Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.
+We begin by showing that each $V_i$ is statistically close to a high entropy distribution.
 
@@
 \begin{proof}
-By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.
-\bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}
-\end{proof}
-
+By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.
+\bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.
+too much for a reader to digest.}
+\end{proof}
+
+\noindent
+We can then argue that all $V_i$ simultaneously have individual entropy with good probability:
 \begin{corollary}
@@
 
+In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a block unguessable distribution~\clref{cl:all blocks entropy}.
+This allows us to conclude:
 \begin{corollary}
@@
 \end{corollary}
-\begin{proof}
-Result of \clref{cl:all blocks entropy}.
-\end{proof}
-
+
+Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a block unguessable distribution, \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,..., V_\ell$.
 \begin{corollary}
@@
 The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.
+This probability is at most $\ell/\mathcal{Z}^\eta$.
+We now show that there are few enough $0\rightarrow 1$ flips with overwhelming probability.
 Let $t'$ be the capacity of $C$.
-To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.
-Let $t$ be the number of supported errors between $w$ and $w'$.
-Let $\mu$ be a parameter and let $t = \mu(\gamma-\eta)/\eta$, for any  $i$ one has:
+We show that $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.
+
+We first consider calculate $\expe[\dis(V, V')]$ for some desired error tolerance $t$.
+Let $\mu$ be a parameter, let $t = \mu(\gamma-\eta)/\eta$ and assume that $\dis(w, w')\leq t$, for any  $i$ one has:
 \begin{align*}
@@
 \end{align*}
-Thus, by setting $\mu = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
+Thus, by setting $\mu = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(V, V')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.  \bnote{stopped here.}
 

### 2014-02-04 constantRate/ConstCompFuzzExt.tex
editing section 5.2

@@
 Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
-Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \delta_{code})$ code.
-Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable obfuscator\bnote{right def?} for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
+Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
+Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
 Define $\gen, \rep$ as:
@@
 \subitem Set $p_i = \rho_i, \lambda_i$.
-\item If $c_i = 1$: Sample $r_i \leftarrow U_n$.
+\item If $c_i = 1$: Sample $r_i \leftarrow U_{\mathcal{Z}^{\eta}}$.
 \subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
@@
 The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.
+This probability is at most $\ell/\mathcal{Z}^\eta$.
+We now show that there are few enough $0\rightarrow 1$ flips with overwhelming probability.
 Let $t'$ be the capacity of $C$.
-To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.
-Let $t$ be the number of supported errors between $w$ and $w'$.
-Let $\mu$ be a parameter and let $t = \mu(\gamma-\eta)/\eta$, for any  $i$ one has:
+We show that $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.
+
+\begin{lemma}
+Let $n, W$ be as above and Let $C$ be a code that corrects $t'$ $0\rightarrow 1$ bit errors where $t' =\Theta(\ell)$.
+Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, if $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
+%That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
+\end{lemma}
+
+\begin{proof}
+Let $t$ be as stated in the lemma.
+We first consider calculate $\expe[\dis(V, V')]$ and then show that the distance between $v$ and $v'$ is rarely much more than this value.  
+Let $\mu = -\log(1-t'/(2\ell))/2$ then one has:
 \begin{align*}
@@
 &\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu
+&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
+& = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}
 \end{align*}
-Thus, by setting $\mu = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.
-
-\begin{lemma}
-Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.
-Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\eta})$ where the probability is over the coins of $\gen$.
-\end{lemma}
-\begin{proof}
-With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.
-As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^\mu = t'/(2\eta)$.
-By the Chernoff bound, we have
+
+With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq  t'/(2\ell)$. By the Chernoff bound, we have
 \begin{align*}
-\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \eta}).
+\Pr\left[\frac{1}{\ell} \sum_{i=1}^\ell X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\ell} = O(e^{- \ell}).
 \end{align*}
+Where the last equality holds because $t'/(2\ell) = \Theta(1)$.
 \end{proof}
@@
 \begin{corollary}
-Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ be a $(\neigh_t, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
-\[
-\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
+Let $\eta= \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$ let $C\subset\zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
+\[
+\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
 \]
@@
 \[
-\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) -\delta_{code}= 1-\ngl(n).
+\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
 \]
@@
 If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
-However, in this setting $gap =\Omega(\gamma)$ and known constructions of information-theoretic fuzzy extractors suffice in this setting.
+However, in this setting $gap =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
 \bibliographystyle{alpha}

### 2014-02-04 constantRate/ConstCompFuzzExt.tex
still working on sec 5

@@
 In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.
-For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as open problem.
-
-Fuller, Meng, and Reyzin (Asiacrypt 2013) hypothesize that these bounds can be overcome by only providing security against computationally-bounded adversaries.
-In this work, we provide the first construction of a fuzzy extractor for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.
-
-\bnote{there are two constructions now}
-\textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.
-Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).
-Our construction provides the following novel features:
-\begin{itemize}
-\item The source entropy is smaller than the log of the number of correctable error patterns.
-\item Constant error tolerance rate.
-\item Security for a large and meaningful class of distributions.  \bnote{this description needs to be better}.
-\end{itemize}
+For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as an open problem.
+
+For an arbitrary source it is impossible to provide meaningful security~(even with interaction solutions) when the starting entropy is smaller than the logarithm of the number of error patterns.
+Some restriction on the type of source is necessary.
+Meaningful restrictions (and accompanying constructions) have proved elusive for information-theoretic fuzzy extractors.
+Fuller, Meng, and Reyzin (Asiacrypt 2013) define a computationally-secure version of a fuzzy extractor.  It may be easier to construct computational fuzzy extractors for meaningful sources.
+
+In this work, we construct the first (computational) fuzzy extractors that are secure for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.
+
+\textbf{Constructions:}  We construct computational fuzzy extractors from point function obfuscation.
+Our constructions are inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).
+Our two constructions are similar to spirit but optimize different parameters.
+The first requires individual blocks of the source to have super-logarithmic entropy and corrects a constant fraction of errors.
+The second construction uses sampling to reduce the required entropy of the source.
+Unfortunately, sampling also reduces the effective error tolerance of the construction.
+%The first construction works for high-entropy and high-error sources, while the second construction works for distributions with lower entropy and error.
+\bnote{need something else to say here}
 \end{abstract}
@@
 \begin{theorem}
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
+Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$ with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 \end{corollary}
+
+Combining the last two sections, we have that \consref{cons:sampling} is secure and correct:
+\begin{theorem}
+Let $n$ be a security parameter.
+Let $\mathcal{W}$ be the family of $(\alpha = \omega(1), \beta\leq \gamma(1/2-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
+Let $\eta = \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$.
+Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon = \ngl(n)$ such that \cons{sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ for
+\begin{align*}
+t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
+\tilde{m} &=|C|\\
+\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
+\end{align*}
+\end{theorem}
+
 \subsection{Discussion of \consref{cons:sampling}}

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex
still working on sec 5

@@
 Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
-Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \delta_{code})$ code.
+Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
 Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
@@
 
-We first consider calculate $\expe[\dis(V, V')]$ for some desired error tolerance $t$.
-Let $\mu$ be a parameter, let $t = \mu(\gamma-\eta)/\eta$ and assume that $\dis(w, w')\leq t$, for any  $i$ one has:
+\begin{lemma}
+Let $n, W$ be as above and Let $C$ be a code that corrects $t'$ $0\rightarrow 1$ bit errors where $t' =\Theta(\ell)$.
+Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, if $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
+%That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
+\end{lemma}
+
+\begin{proof}
+Let $t$ be as stated in the lemma.
+We first consider calculate $\expe[\dis(V, V')]$ and then show that the distance between $v$ and $v'$ is rarely much more than this value.  
+Let $\mu = -\log(1-t'/(2\ell))/2$ then one has:
 \begin{align*}
@@
 &\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu
+&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
+& = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}
 \end{align*}
-Thus, by setting $\mu = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(V, V')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.  \bnote{stopped here.}
-
-\begin{lemma}
-Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.
-Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\eta})$ where the probability is over the coins of $\gen$.
-\end{lemma}
-\begin{proof}
-With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.
-As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^\mu = t'/(2\eta)$.
-By the Chernoff bound, we have
+
+With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq  t'/(2\ell)$. By the Chernoff bound, we have
 \begin{align*}
-\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \eta}).
+\Pr\left[\frac{1}{\ell} \sum_{i=1}^\ell X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\ell} = O(e^{- \ell}).
 \end{align*}
+Where the last equality holds because $t'/(2\ell) = \Theta(1)$.
 \end{proof}
@@
 \end{corollary}
+
+Combining the last two sections, we have that \consref{cons:sampling} is secure and correct:
+\begin{theorem}
+Let $n$ be a security parameter.
+Let $\mathcal{W}$ be the family of $(\alpha = \omega(1), \beta\leq \gamma(1/2-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
+Let $\eta = \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$.
+Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ for
+\begin{align*}
+t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
+\tilde{m} &=|C|\\
+\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
+\end{align*}
+\end{theorem}
+
 \subsection{Discussion of \consref{cons:sampling}}

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex

@@
 \subsection{Obfuscation}
-Our construction uses virtual black-box obfuscation of point functions.  This is the following family of functions:
+Our construction uses obfuscation of point functions. This is the following family of functions:
 \[
@@
 \]
-Here we present the virtual black-box definition of obfuscation.
-See \secref{sec:obfuscation} for a more detailed introduction to obfuscation.
-This definition is known to be achievable for point functions under various assumptions~\cite{canetti1997towards, wee2005obfuscating}.
-We also need the obfuscation to be $\ell$-composable~(\defref{def:obf comp}).
-\onote{if we need it, should put the def here not in the appendix.
-Also say that we need an AI definition}\onote{should discuss assumptions for composable AI point obfuscation.
-Here it make a lot of difference it we can get by with VGB}\onote{might be simpler to just define a set function instead of a point function and skip the composability stuff}
-We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
-
-\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}
-\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent \onote{remove dependent} auxiliary input if the following conditions are met:
+The notion of obfuscation required is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
+This notion is weaker then the notion of virtual grey-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time as long as it only makes polynomial number of oracle queries to the point function.
+In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
+Compassable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Difﬁe Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+
+\begin{definition}[$t$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.
+A PPT algorithm $\mathcal{O}$ is a $t$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
 \begin{enumerate}
-\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$,
-\[
-\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
-\]
-\bnote{We need a different name for the circuit, $C$ is our error-correcting code.}
-where the probability is taken over the randomness $r$.
-\emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.
-Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
-\onote{consider removing the notions you do not use}
-\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
-\onote{this follows from the fact that O is PPT}
-\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
-and for all binary predicates $\pi$,
-\[
-|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
-\]
-where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
-Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
-\bnote{We never need to run our simulator so I think we can use virtual gray-box.}
+\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^t \in \mathcal{I}_n$, (where $t=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\[
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^t)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^t|}) = 1] | < \frac{1}{p(n)} \enspace,
+\]
+where $(I^1,\dots,I^t)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
 \end{enumerate}

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex

@@
 \subsection{Obfuscation}
-Our construction uses obfuscation of point functions. This is the following family of functions:
+Our construction uses obfuscation for a family of point function $\mathcal{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
 \[
@@
 \]
-The notion of obfuscation required is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
-This notion is weaker then the notion of virtual grey-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time as long as it only makes polynomial number of oracle queries to the point function.
+The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
+This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time while making at most polynomial number of oracle queries to the function.
 In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
@@
 \begin{enumerate}
-\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$
+\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
 \item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^t \in \mathcal{I}_n$, (where $t=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:

### 2014-02-04 constantRate/ConstCompFuzzExt.tex
changing main proof with cleaned up obf notions

@@
 \subsection{Obfuscation}
-Our construction uses virtual black-box obfuscation of point functions.  This is the following family of functions:
+Our construction uses obfuscation for a family of point function $\mathcal{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
 \[
@@
 \]
-Here we present the virtual black-box definition of obfuscation.
-See \secref{sec:obfuscation} for a more detailed introduction to obfuscation.
-This definition is known to be achievable for point functions under various assumptions~\cite{canetti1997towards, wee2005obfuscating}.
-We also need the obfuscation to be $\ell$-composable~(\defref{def:obf comp}).
-\onote{if we need it, should put the def here not in the appendix.
-Also say that we need an AI definition}\onote{should discuss assumptions for composable AI point obfuscation.
-Here it make a lot of difference it we can get by with VGB}\onote{might be simpler to just define a set function instead of a point function and skip the composability stuff}
-We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.
-
-\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}
-\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent \onote{remove dependent} auxiliary input if the following conditions are met:
+The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
+This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time while making at most polynomial number of oracle queries to the function.
+In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
+Composable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+
+\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.
+A PPT algorithm $\mathcal{O}$ is a $\ell$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
 \begin{enumerate}
-\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$,
-\[
-\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
-\]
-\bnote{We need a different name for the circuit, $C$ is our error-correcting code.}
-where the probability is taken over the randomness $r$.
-\emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.
-Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
-\onote{consider removing the notions you do not use}
-\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
-\onote{this follows from the fact that O is PPT}
-\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
-and for all binary predicates $\pi$,
-\[
-|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
-\]
-where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.
-Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
-\bnote{We never need to run our simulator so I think we can use virtual gray-box.}
+\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathcal{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\[
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
+\]
+where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
 \end{enumerate}
@@
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(s_{cone}, \epsilon_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(s_{cond}, \epsilon_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
 \begin{itemize}
@@
 \item For $i=1,..., \ell$:
-\begin{enumerate}
+\begin{enumerate}[(i)]
 \item If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
@@
 \item For $i=1,..., \ell$:
-\begin{enumerate}
+\begin{enumerate}[(i)]
 \item If $p_i(w_i') = 1$: set $c_i' = 0$.
@@
 \label{thm:security of cons}
-Let $\mathcal{O}$ be an $\ell$-composable virtual gray box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\zo^n$. %that is $(s_{obf}, \epsilon_{obf})$-hard.  
 Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
-Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
+For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
 \end{theorem}
@@
 \begin{proof}
-Security is a result of \thref{thm:security of cons} because $2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}$ is negligible when $\epsilon_{obf} = \ngl(n), \ell = \poly(n)$ and $\alpha =\omega(\log n)$.
-Correctness follows from \lemref{lem:correct of cons}.
+Security is a result of \thref{thm:security of cons}.  Correctness follows from \lemref{lem:correct of cons}.
 \end{proof}
@@
 Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for the family of point functions over $\zo^\eta\times \mathcal{Z}$.
+Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
 Define $\gen, \rep$ as:
@@
 \item For $i=1,..., \ell$:
-\begin{enumerate}
+\begin{enumerate}[(i)]
 \item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
@@
 \item For $i=1,..., \ell$:
-\begin{enumerate}
+\begin{enumerate}[(i)]
 \item Parse $p_i$ as $\rho_i, \lambda_i$.
@@
 \label{cor:samp unguess}
-Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual grey box obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
+Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$, then for every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
+%for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
 \end{corollary}
@@
 Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon = \ngl(n)$ such that \cons{sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ for
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$-hard with error $\delta$ for
 \begin{align*}
@@
 &< \Theta(\gamma)- t \log |\mathcal{Z}|\\
-&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
+&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
 \end{align*}
@@
 \label{sec:minimal conditions}
-As mentioned in the introduction a necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.
-In the interactive setting using multi-party computation it is possible to achieve security under this condition.
-We codify this notion:
+A necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.  We make this intuition formal here:
 
@@
 \begin{lemma}
+\label{lem:fuzz necessary}
 Let $n$ be a security parameter and let $W$ be a distribution over $\mathcal{M}$
@@
 \end{proof}
+
+\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+This means that fuzzy min-entropy is a necessary condition for an interactive solution as well.
+The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
+When $gap<0$ there is some distribution such that $\Hfuzz(W)=0$.
+This means we inherently must talk about the security and errors together.
 
@@
 
-Let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.
-Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
-Our goal is to how that $H^{\hill}_{\epsilon', s_{obf}}(C|P)\geq |C|- \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\zo^n$.
+Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq |C|- \beta$.
+% for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
+Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < |C|-\beta$.
 
@@
 By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.
+Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that 
+\[
+| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
+\]  
 Define the distribution $X$ as follows:
@@
 R_i & C_i = 1.
-\end{cases}\]
-
-Let $D$ be some distinguisher of size at most $s_{obf}$.  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $s_{obf}$ queries) such that
+\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
 \begin{align}
 \label{eq:dist before}
-|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{obf}.
+|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
 \end{align}
-
 We now prove $S$ cannot distinguish between $C$ and $C'$.
@@
 \label{eq:dist after}
-|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{obf}.
+|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 &+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
-&\leq \epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{obf}.
+&\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
+&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
 \end{align*}
-This completes the proof of \thref{thm:security of cons}.
+This is a contradiction and completes the proof of \thref{thm:security of cons}.
 \end{proof}

### 2014-02-04 constantRate/ConstCompFuzzExt.tex
Working on biometric appendix

@@
 \begin{proof}
-\bnote{we need to come back to this if we use obfuscation with error}
 Recall that $c$ contains at most $\ell$ $1$s.
@@
 
-\section{$gap<0$ for Irises}
+\section{Inadequacy of Fuzzy Extractors for Biometrics}
+Fuzzy extractors were developed to derive stable from noisy sources.
+Biometrics represent an important noisy physical source.
+Unlike physical unclonable functions, biometrics are inherently fixed distributions.
+It is not possible to increase their entropy or reduce their error to improve key strength.
+Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).
+The security of the resulting system is usually measured using false accept rate vs.
+false reject rate.
+This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.
+A known false accept rate provides there is no guarantee helper data information-leakage.
+Indeed the helper data may completely reveal the original input.
+In high security applications, this type of analysis is sufficient.
+
 \label{sec:iris no key}
-The iris is the biometric believed to have the most entropy.
+As an example, the iris is the biometric believed to have the most entropy.
 The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.
-This transform is designed for the process of identification, achieving the best possible true accept/false accept tradeoff.
-
-The precise number of errors that must be tolerated depends on the desired true accept rate (how often the correct key is produced).
-For a true accept rate of $20\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
+The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.\footnote{There is considerable subsequent research after the work of Daugman~\cite{daugman2004}.
+These works do not dramatically improve the original results.}
+
+The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
+For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
 The comparison between the two readings is then made using bits not excluded by either image.
@@
 \end{align*}
-Irises are believed to be the strongest biometric and reliable key derivation from irises is an open problem.
-
+Although irises are believed to be the strongest biometric a fuzzy extractor with the above parameters may completely reveal the original value.
+
+%Fingerprints are in a similar situation.  Ratha, Connell, and Bolle estimate that fingerprints contain $82$ bits of entropy~\cite{ratha2003biometrics}.
+%\bnote{Don't know what I want to say about fingerprints right now.  
 \section{Minimal Conditions for Fuzzy Extractor Security}

### 2014-02-04 constantRate/ConstCompFuzzExt.tex
term minimal usable entropy

@@
 \title{Constant Error Tolerance Computational Fuzzy Extractors}
-\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
-work was sponsored by the Department of the Air Force under Air Force
-Contract
-\#FA8721-05-C-0002.  Opinions,
-interpretations, conclusions and recommendations are those of the author
-and
-are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
+%\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
+%work was sponsored by the Department of the Air Force under Air Force
+%Contract
+%\#FA8721-05-C-0002.  Opinions,
+%interpretations, conclusions and recommendations are those of the author
+%and
+%are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
 
@@
 Fuzzy extractors derive strong keys from noisy sources.
-The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly distributed key.
+The goal is to reliably convert a high entropy source~(which may differ on repeated readings) to the same uniformly distributed key.
 Traditionally, their security is defined information-theoretically.
-Fuzzy extractors have upper bounds on the length of the derived key~(Dodis et al., J.
+%Fuzzy extractors have upper bounds on the length of the derived key.
+
+Traditionally, a fuzzy extractor works for any distribution with enough entropy.
+%In this setting, the entropy of the source must be significantly higher than the logarithm of number of error patterns corrected~(Dodis et al., J.
 of Comp 2008).
-In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.
+We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.
+Dodis et al.~(J.
+of Comp.
+2008) show there is some source where the maximum key length cannot exceed the minimum usable entropy.
+Therefore, fuzzy extractors that only consider the input entropy must output a key whose length is at most the minimum usable entropy.
 For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as an open problem.
 
-For an arbitrary source it is impossible to provide meaningful security~(even with interaction solutions) when the starting entropy is smaller than the logarithm of the number of error patterns.
-Some restriction on the type of source is necessary.
+%Traditional fuzzy extractors output a key roughly of length minimum usable entropy.  
+To achieve meaningful security when the minimum usable entropy is negative, some restriction on the source is necessary.
 Meaningful restrictions (and accompanying constructions) have proved elusive for information-theoretic fuzzy extractors.
@@
 
-In this work, we construct the first (computational) fuzzy extractors that are secure for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.
+In this work, we construct the first (computational) fuzzy extractors that are secure for a large class of distributions where the minimum usable entropy is negative.
 
@@
 \section{Introduction}\label{sec:introduction}
-\bnote{I want a new name for $gap$!}
 Reliable key derivation is a cornerstone of authentication.
@@
 We consider the Hamming metric.
-For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected.
-For the remainder of this paper we denote this quantity by $gap$.
-This represents a real problem as $gap<0$ for important biometrics and current fuzzy extractors provide no security guarantee~(see \apref{sec:iris no key}).
+For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected~(and we have constructions of fuzzy extractors that nearly meet this bound).
+For the remainder of this paper we call this difference the minimum usable entropy, denoted $H_{usable}$.
+This represents a practical problem as important biometrics have $H_{usable}<0$~(see \apref{sec:iris no key}).
 
@@
 The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
-For the remainder of this paper, we denote this quantity by $gap = \Hoo(W) - \log |B_t|$.
-
-To achieve security when $gap<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
-However, the tools for constructing information-theoretic fuzzy extractors have not admitted natural and meaningful restrictions.
+For the remainder of this paper, we denote this quantity by $H_{usable} = \Hoo(W) - \log |B_t|$.
+
+To achieve security when $H_{usable}<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
+However, the tools for constructing information-theoretic fuzzy extractors have not produced natural restrictions.
 Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
 Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-Building a computational fuzzy extractor with $gap<0$ may be possible for a broader class of distributions than is possible in the information-theoretic realm.
-
-In this work, we show that constructing a computational fuzzy extractor is possible for a large class of distributions with $gap<0$.
-%We resolve this question and construct a computational fuzzy extractor when $gap<0$.
-This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.
-A necessary condition for security is that a negligible portion of the source's probability distribution lies within any Hamming ball of radius $t$.
-We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).
-%The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.
-In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  We focus on providing a reasonable length key when $gap<0$.
+A computational fuzzy extractor may exist for a larger class of distributions with $H_{usable}<0$ than is possible information-theoretically.
+
+In this work, we construct a computational fuzzy extractor when $H_{usable}<0$ for a large class of distributions.
+In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $H_{usable}<0$.
+
 Fuller, Meng, and Reyzin show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
@@
 We present two constructions of computational fuzzy conductors for different types of source distributions $W$.
-These constructions may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
+These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
 
@@
 %\begin{itemize}
-%\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
+%\item The first computational fuzzy extractor where $H_{usable}$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
 Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
@@
 
-\textbf{Limitations: } In order to achieve security with $gap<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
+\textbf{Limitations: } In order to achieve security with $H_{usable}<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
 Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
@@
 Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides all partial information.
-Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $H_{usable}>>0$ using a information-reconciliation component that hides all partial information.
+Constructing VBB obfuscation for sources where $H_{usable} <0$ is an open problem.
 
@@
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary~(see \apref{sec:minimal conditions} for the precise statement).
+With $H_{usable}<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary~(see \apref{sec:minimal conditions} for the precise statement).
 
@@
 Our goal is to derive strong keys when the number of possible error patterns is larger than the starting entropy of source.
-That is we want to provide some security when $0>gap = \Hoo(W) - \log|B_t|$.
+That is we want to provide some security when $0>H_{usable} = \Hoo(W) - \log|B_t|$.
 In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
@@
 
-To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.
+To show that $H_{usable}$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.
 We allow $t$ errors with an alphabet $\mathcal{Z}$ of size $2^n$.
@@
 \[
-gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
-Thus, \consref{cons:first construction} achieves negative $gap$ when $t = \Theta(\ell)$.
-We achieve $gap<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
+H_{usable} = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
+\]
+When $t =\Theta(\ell)$, then $H_{usable}<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+Thus, \consref{cons:first construction} achieves negative $H_{usable}$ when $t = \Theta(\ell)$.
+We achieve $H_{usable}<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
 %When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
@@
 \label{sec:sampling}
-\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.
+\consref{cons:first construction} is a computational fuzzy extractor with $H_{usable}<0$.
 In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
@@
 \subsection{Discussion of \consref{cons:sampling}}
-\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.
+\consref{cons:sampling} achieves $H_{usable}<0$ for an interesting setting of parameters.
 The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
@@
 \begin{align*}
-gap &= \Hoo(W) -\log |B_t| \\
+H_{usable} &= \Hoo(W) -\log |B_t| \\
 &< \Theta(\gamma)- t \log |\mathcal{Z}|\\
@@
 \end{align*}
-That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
-If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
-However, in this setting $gap =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
+That is, \consref{cons:sampling} achieves $H_{usable}<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
+If we are willing to accept $H_{usable}\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
+However, in this setting $H_{usable} =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
 \bibliographystyle{alpha}
@@
 The comparison between the two readings is then made using bits not excluded by either image.
-It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $gap$:
+It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $H_{usable}$:
 \begin{align*}
-gap &= \Hoo(W) - \log |B_t|\\
+H_{usable} &= \Hoo(W) - \log |B_t|\\
 &= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
@@
 \label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $\mathcal{M}$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) = k$ if the following holds:
-\[
-\forall m\in \mathcal{M} Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+\[
+\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
 \]
@@
 \label{lem:fuzz necessary}
-Let $n$ be a security parameter and let $W$ be a distribution over $\mathcal{M}$
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) if $\kappa =\omega(\log n)$.
+Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
 \end{lemma}
@@
 The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
-When $gap<0$ there is some distribution such that $\Hfuzz(W)=0$.
+When $H_{usable}<0$ there is some distribution such that $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution of all points within distance $t$).
 This means we inherently must talk about the security and errors together.

### 2014-02-04 constantRate/ConstCompFuzzExt.tex
removing obfuscation appendix

@@
 In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
-Composable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
 
@@
 \appendix
-\section{Obfuscation}
-\label{sec:obfuscation}
-The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).
-This notion is known to be impossible in a black-box way for all polynomial time programs.
-Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).
-Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.
-The definition of virtual black box obfuscation is presented in \defref{def:obf}.
-
-In this work, we will use obfuscation of point-programs,
-\[
-I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
-\]
-
-We present the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
-\begin{enumerate}
-\item Input: string $w\in \zo^n$.
-\item Choose a generator $g\overset{\$}\leftarrow G$
-\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
-\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
-\end{enumerate}
-\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.
-Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.
-Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.
-For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
-\end{assumption}
-\begin{theorem}~\cite{canetti1997towards}
-The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
-\end{theorem}
-
-As mentioned above there exist other constructions of point function obfuscation under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.
-
-Lastly, we will need the notion of composable obfuscation.
-
-\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}]
-\label{def:obf comp}
-A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.
-That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
-\[
-|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
-\]
-where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
-\end{definition}
-
 \section{Fuzzy Conductors}

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex
edited E.1 and E.2, working on E.3

@@
 \newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
+\newcommand{\guess}{\mathsf{guess}}
 
@@
 In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
-Compassable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Difﬁe Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
-
-\begin{definition}[$t$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+
+\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
 \label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is a $t$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
+A PPT algorithm $\mathcal{O}$ is a $\ell$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
 \begin{enumerate}
 \item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
-\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^t \in \mathcal{I}_n$, (where $t=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathcal{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
 \[
-|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^t)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^t|}) = 1] | < \frac{1}{p(n)} \enspace,
-\]
-where $(I^1,\dots,I^t)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
+\]
+where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
 \end{enumerate}
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} \lnote{is it ''block unguessable'' or ''unguessable block''?
+the usage is inconsistent}if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
 \[
@@
 Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ for
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$-hard with error $\delta$ for
 \begin{align*}
@@
 \begin{align*}
-gap &= \Hoo(W) -\log |B_t| \\
+H_{usable} &= \Hoo(W) -\log |B_t| \\
 &< \Theta(\gamma)- t \log |\mathcal{Z}|\\
-&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
-\end{align*}
-That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
-If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
-However, in this setting $gap =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
+&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
+\end{align*}
+That is, \consref{cons:sampling} achieves $H_{usable}<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
+If we are willing to accept $H_{usable}\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
+However, in this setting $H_{usable} =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
 \bibliographystyle{alpha}
@@
 
-\section{$gap<0$ for Irises}
+\section{Inadequacy of Fuzzy Extractors for Biometrics}
+Fuzzy extractors were developed to derive stable from noisy sources.
+Biometrics represent an important noisy physical source.
+Unlike physical unclonable functions, biometrics are inherently fixed distributions.
+It is not possible to increase their entropy or reduce their error to improve key strength.
+Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).
+The security of the resulting system is usually measured using false accept rate vs.
+false reject rate.
+This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.
+A known false accept rate provides there is no guarantee helper data information-leakage.
+Indeed the helper data may completely reveal the original input.
+In high security applications, this type of analysis is sufficient.
+
 \label{sec:iris no key}
-The iris is the biometric believed to have the most entropy.
+As an example, the iris is the biometric believed to have the most entropy.
 The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.
-This transform is designed for the process of identification, achieving the best possible true accept/false accept tradeoff.
-
-The precise number of errors that must be tolerated depends on the desired true accept rate (how often the correct key is produced).
-For a true accept rate of $20\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
+The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.\footnote{There is considerable subsequent research after the work of Daugman~\cite{daugman2004}.
+These works do not dramatically improve the original results.}
+
+The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
+For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
 The comparison between the two readings is then made using bits not excluded by either image.
-It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $gap$:
-\begin{align*}
-gap &= \Hoo(W) - \log |B_t|\\
+It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $H_{usable}$:
+\begin{align*}
+H_{usable} &= \Hoo(W) - \log |B_t|\\
 &= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
 \end{align*}
-Irises are believed to be the strongest biometric and reliable key derivation from irises is an open problem.
-
+Although irises are believed to be the strongest biometric a fuzzy extractor with the above parameters may completely reveal the original value.
+
+%Fingerprints are in a similar situation.  Ratha, Connell, and Bolle estimate that fingerprints contain $82$ bits of entropy~\cite{ratha2003biometrics}.
+%\bnote{Don't know what I want to say about fingerprints right now.  
 \section{Minimal Conditions for Fuzzy Extractor Security}
 \label{sec:minimal conditions}
-As mentioned in the introduction a necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.
-In the interactive setting using multi-party computation it is possible to achieve security under this condition.
-We codify this notion:
+A necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.  We make this intuition formal here:
 
@@
 \label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $\mathcal{M}$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) = k$ if the following holds:
+A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
 \[
-\forall m\in \mathcal{M} Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
 \]
@@
 \begin{lemma}
-Let $n$ be a security parameter and let $W$ be a distribution over $\mathcal{M}$
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) if $\kappa =\omega(\log n)$.
+\label{lem:fuzz necessary}
+Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
 \end{lemma}
@@
 
+\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+This means that fuzzy min-entropy is a necessary condition for an interactive solution as well.
+The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
+When $H_{usable}<0$ there is some distribution such that $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution of all points within distance $t$).
+This means we inherently must talk about the security and errors together.
+
 For the Hamming distance having $\Hfuzz(W)\geq \omega(\log n)$ means that there are more entropic dimensions that the desired error-tolerance.
@@
 In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
-The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.
+The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.
 Thus, we begin with the case of independent blocks.
@@
 \label{cl:independent high ent}
-Let $W = W_1,..., W_\ell$ be a source where blocks are independent.
+Let $W = W_1,  ...
+, W_\ell$ be a source in which all blocks $W_i$  are mutually independent.
 Let $\alpha$ be a parameter.
-Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of blocks such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.
-Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
+Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.
+Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
 In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
@@
 \begin{proof}
-We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.
-It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
-Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we ignore all other blocks as they are independent).
-Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.
-Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.
-We assume a deterministic adversary~(we assume the best coins are in nonuniform advice).
-The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.
-Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.
-There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.
-If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.
-These responses can be removed as the response is deterministic.
-Let $A'$ represent the sequence with all duplicate queries removed.
-This sequence has at most a single $1$.
-Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).
+It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log q$.
+We can ignore queries for all blocks but the $i$th, as the blocks are independent.
+Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice).
+Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $\mathcal{A}$ \lnote{is the adversary $S$, $\mathcal{A}$, or $A$?} making $q$  queries about the $i$th block.
+Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed).
+Thus, the total number of possible responses is $q+1$.
 Thus, we have the following,
 \begin{align*}
-\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
-&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
-&=\Hav(W_i |A') \\
-&=\Hoo(W_i) - \log |A'|\\
-&=\alpha - \log |A'|\\
-&=\alpha - \log (q+1)
-\end{align*}
-Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
-This argument holds for all $i$.  This completes the proof.
-\end{proof}
-\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
-\clref{cl:independent high ent} captures this type of distribution.
+\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
+&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
+&=\alpha - \log (q+1)\,,
+\end{align*}
+where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
+\end{proof}
+\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
+\clref{cl:independent high ent} captures, in particular, this class of distributions.
 
@@
 \label{cl:each block from single seed}
-Let $e =\omega(\log n)$ and let $f:\zo^e \rightarrow \zo^{n\times \ell}$ be a function.
-Furthermore, let $f_i$ denote the restriction of $f$'s output to the bits $[i\times n,..., i\times n+n-1]$.
+Let $f:\zo^e \rightarrow \mathcal{Z}^\ell$ be a function.
+Furthermore, let $f_i$ denote the restriction of $f$'s output to its $i$th coordinate.
 If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-block unguessable distribution.
@@
 \begin{proof}
-Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.
-Consider a query $q_j$ on block $i$, there are two possibilities either $q_j$ is not in the image of $f_i$ on $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
-Thus, a query eliminates at most a single value of $U_e$, this holds for all blocks $i$.
-Then similarly to the proof of \clref{cl:independent high ent}, we can eliminate queries which correspond to the same value of $U_e$.
-Then the possible responses are strings with Hamming weight at most $1$ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
-\end{proof}
-
-Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.
-We can prove a slightly weaker claim when the correlation between $W_i$ is arbitrary:
+Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})$.
+Consider a query $q_j$ on block $i$.
+There are two possibilities: either $q_j$ is not in the image of $f_i$,  or $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
+Then (by assuming $A$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.
+Then the possible responses are strings with Hamming weight at most $1$ (like in the
+proof of \clref{cl:independent high ent}),
+ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
+\end{proof}
+
+Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ for which \consref{cons:first construction} is secure.
+For these distributions, all the coordinates are as dependent as possible: one determines all others.
+
+We can prove a slightly weaker claim when the correlation between the coordinates $W_i$ is arbitrary:
 
@@
 Let $W = W_1,..., W_\ell$ be a source.
-Let $\alpha =\omega(\log n)$ and suppose that for all $i$ $\Hoo(W_i)\geq \alpha$, then for $q = \poly(n)$, there exists a $\alpha ' = \omega(\log n)$ such that $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
+Let $\alpha =\omega(\log n)$ and suppose that for all $i$, $\Hoo(W_i)\geq \alpha$.
+Then for $q = \poly(n)$, there exists an $\alpha ' = \omega(\log n)$ such that $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
 \end{claim}
 \begin{proof}
-Consider a particular block $W_i$, it suffices to show that $\Hav(W_i | Q_1,A_1,..., Q_q, A_q) \geq \omega(\log n)$.  By the definition of conditional min-entropy:
+Intuitively, the claim is true because the oracle is negligibly like to return 1 on any query. Formally, we proceed by induction on oracle queries. 
+For a random variable $X$, let $\guess(X) = \max_x \Pr[X=x]$.
+Using the same notation as in the proof of Claim  \clref{cl:independent high ent}),  fix $i$ and $j$. Our inductive hypothesis is
+that $\Hav(W_i | A_1 \dots A_{j-1}) \ge \alpha_{j-1}$, where $\alpha_{j-1}=\omega(\log n)$.
+Recall that $\Hav(W_i | A_1 \dots A_j) =  -\log \expe_{a_1 \dots a_j} \guess (W_i|A_1 \dots, A_j=a_1\dots a_j)$.
+\begin{align*}
+\expe_{a_1 \dots a_j} \guess (W_i|A_1 \dots, A_j=a_1\dots a_j)
+ = {} & \sum_{a_1 \dots a_{j-1}} \guess(W_i |A_1\dots A_j=a_1\dots a_{j-1}0) \Pr[A_1\dots A_j=a_1\dots a_{j-1}0] \\
+&+  \sum_{a_1 \dots a_{j-1}} \guess(W_i | A_1\dots A_j=a_1\dots a_{j-1}1) \Pr [A_1\dots A_j=a_1\dots a_{j-1}1] ) \\
+\end{align*}
+
+We first deal with the second term. 
+\begin{align*}
+\sum_{a_1 \dots a_{j-1}}
+\Pr [A_1\dots A_j=a_1\dots a_{j-1}1] & \le
+\sum_{a_1 \dots a_{j-1}}
+\max_k \guess[W_k | A_1\dots A_{j-1}=a_1\dots a_{j-1}] \cdot \Pr[A_1\dots A_{j-1}=a_1\dots a_{j-1}] 
+\\ & \le
+\sum_k \sum_{a_1\dots a_{j-1}} \guess[W_k | A_1\dots A_{j-1}=a_1\dots a_{j-1}] \cdot \Pr[A_1\dots A_{j-1}=a_1\dots a_{j-1}] \\
+& =
+\sum_k 2^{-\Hav(W_k | A_1\dots A_{j-1})}\\
+&\le k 2^{-\alpha_{j-1}} = \ngl(n)\,.
+\end{align*}
+
+\lnote{working here}
+
+, it suffices to show that $\Hav(W_i | Q_1,A_1,..., Q_q, A_q) \geq \omega(\log n)$.  By the definition of conditional min-entropy:
 \begin{align*}
@@
 &+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
-&\leq \epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{obf}.
-\end{align*}
-This completes the proof of \thref{thm:security of cons}.
+&\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
+&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
+\end{align*}
+This is a contradiction and completes the proof of \thref{thm:security of cons}.
 \end{proof}

### 2014-02-05 constantRate/ConstCompFuzzExt.tex
reorganized edited first three appendices

@@
 \newcommand{\Hfuzz}{\mathrm{H}^{\mathtt{fuzz}}_{t,\infty}}
+\newcommand{\Huse}{\mathrm{H}_{\mathtt{usable}}}
 \newcommand{\Dom}{\mathsl{Dom}}
@@
 Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} perform both tasks non-interactively.
-They consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public value $p$.
-The second algorithm \rep takes this public value $p$ and a close $w'$ to reproduce the original key $r$.
+They consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.
+The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
 Traditionally, a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} performs information-reconciliation and a randomness extractor~\cite{nisan1993randomness} performs privacy amplification.
@@
 For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected~(and we have constructions of fuzzy extractors that nearly meet this bound).
-For the remainder of this paper we call this difference the minimum usable entropy, denoted $H_{usable}$.
-This represents a practical problem as important biometrics have $H_{usable}<0$~(see \apref{sec:iris no key}).
+For the remainder of this paper we call this difference the minimum usable entropy, denoted $\Huse$.
+This represents a practical problem as important biometrics have $\Huse<0$~(see \apref{sec:iris no key}).
 
@@
 The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
-For the remainder of this paper, we denote this quantity by $H_{usable} = \Hoo(W) - \log |B_t|$.
-
-To achieve security when $H_{usable}<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
+For the remainder of this paper, we denote this quantity by $\Huse = \Hoo(W) - \log |B_t|$.
+
+To achieve security when $\Huse<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
 However, the tools for constructing information-theoretic fuzzy extractors have not produced natural restrictions.
@@
 Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-A computational fuzzy extractor may exist for a larger class of distributions with $H_{usable}<0$ than is possible information-theoretically.
-
-In this work, we construct a computational fuzzy extractor when $H_{usable}<0$ for a large class of distributions.
-In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $H_{usable}<0$.
+A computational fuzzy extractor may exist for a larger class of distributions with $\Huse<0$ than is possible information-theoretically.
+
+In this work, we construct a computational fuzzy extractor when $\Huse<0$ for a large class of distributions.
+In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse<0$.
 
@@
 %\begin{itemize}
-%\item The first computational fuzzy extractor where $H_{usable}$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
+%\item The first computational fuzzy extractor where $\Huse$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
 Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
@@
 
-\textbf{Limitations: } In order to achieve security with $H_{usable}<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
+\textbf{Limitations: } In order to achieve security with $\Huse<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
 Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
@@
 Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $H_{usable}>>0$ using a information-reconciliation component that hides all partial information.
-Constructing VBB obfuscation for sources where $H_{usable} <0$ is an open problem.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $\Huse>>0$ using a information-reconciliation component that hides all partial information.
+Constructing VBB obfuscation for sources where $\Huse <0$ is an open problem.
 
@@
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $H_{usable}<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary~(see \apref{sec:minimal conditions} for the precise statement).
+With $\Huse<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary~(see \apref{sec:minimal conditions} for the precise statement).
 
@@
 Our goal is to derive strong keys when the number of possible error patterns is larger than the starting entropy of source.
-That is we want to provide some security when $0>H_{usable} = \Hoo(W) - \log|B_t|$.
+That is we want to provide some security when $0>\Huse = \Hoo(W) - \log|B_t|$.
 In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
@@
 
-To show that $H_{usable}$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.
+To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.
 We allow $t$ errors with an alphabet $\mathcal{Z}$ of size $2^n$.
@@
 \[
-H_{usable} = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$, then $H_{usable}<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
-Thus, \consref{cons:first construction} achieves negative $H_{usable}$ when $t = \Theta(\ell)$.
-We achieve $H_{usable}<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
+\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
+\]
+When $t =\Theta(\ell)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+Thus, \consref{cons:first construction} achieves negative $\Huse$ when $t = \Theta(\ell)$.
+We achieve $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
 %When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
@@
 \label{sec:sampling}
-\consref{cons:first construction} is a computational fuzzy extractor with $H_{usable}<0$.
+\consref{cons:first construction} is a computational fuzzy extractor with $\Huse<0$.
 In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
@@
 \subsection{Discussion of \consref{cons:sampling}}
-\consref{cons:sampling} achieves $H_{usable}<0$ for an interesting setting of parameters.
+\consref{cons:sampling} achieves $\Huse<0$ for an interesting setting of parameters.
 The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
@@
 \begin{align*}
-H_{usable} &= \Hoo(W) -\log |B_t| \\
+\Huse &= \Hoo(W) -\log |B_t| \\
 &< \Theta(\gamma)- t \log |\mathcal{Z}|\\
@@
 \end{align*}
-That is, \consref{cons:sampling} achieves $H_{usable}<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
-If we are willing to accept $H_{usable}\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
-However, in this setting $H_{usable} =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
+That is, \consref{cons:sampling} achieves $\Huse<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
+If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
+However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
 \bibliographystyle{alpha}
@@
 \appendix
+
+\section{Use of Fuzzy Extractors for Biometrics}
+Fuzzy extractors were developed to derive stable from noisy sources.
+Biometrics represent an important noisy physical source.
+Unlike physical unclonable functions, biometrics are fixed distributions.
+Biometrics cannot be redesigned to  increase their entropy or reduce their error rates.
+Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).
+Unfortunately, most work measures system security using false accept rate vs.
+false reject rate.
+This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.
+False accept rate provides no bound on helper data information-leakage.
+Indeed the helper data may completely reveal the original input.
+In high security applications, measuring false accept rate vs.
+false reject rate is insufficient to argue system security.
+
+\label{sec:iris no key}
+As an example, we focus on the human iris.
+The iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
+The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
+Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
+The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.
+There has been considerable research since the work of Daugman~\cite{daugman2004}.
+These works do not dramatically alter the entropy measurement or error rate necessary for a reasonable false reject rate.
+We use the Daugman's parameters for our calculations.
+
+The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
+For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.%\footnote{Daugman  improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
+The comparison between the two readings is then made using bits not excluded by either image.
+It is not clear how to extend into the fuzzy extractor setting.
+Even with the masking vector $\Huse$ is negative for irises.}
+We have the following calculation for $\Huse$:
+\begin{align*}
+\Huse &= \Hoo(W) - \log |B_t|\\
+&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
+\end{align*}
+Thus, if we were to use a fuzzy extractor that worked for all distributions with the same entropy and error characteristics no key is possible~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
+Although irises are believed to be the strongest biometric a fuzzy extractor can provide no security without using some additional property of the iris distribution.
+
+\section{Minimal Conditions for Fuzzy Extractor Security}
+\label{sec:minimal conditions}
+
+A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting any point into the \rep algorithm.
+This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
+We make this intuition formal here:
+
+\begin{definition}
+\label{def:fuzzy min-ent}
+A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+\[
+\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+\]
+\end{definition}
+\begin{lemma}
+\label{lem:fuzz necessary}
+Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
+\end{lemma}
+\begin{proof}
+Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+This means that there exists a point $m\mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
+Consider the following distinguisher $D$:
+\begin{itemize}
+\item On input $r, p$.
+\item If $\rep(m, p) = r$, output $1$.
+\item Else output $0$.
+\end{itemize}
+First note that $|D|$ is of size $\log |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n)$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
+\[
+\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} - \frac{1}{2^{-\kappa}} = 1/\poly(n).
+\]
+\end{proof}
+\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+This means that fuzzy min-entropy is also a necessary condition for interactive solution.
+%The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
+If we wish to support parameter regimes where $\Huse<0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
+Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse<0$.
+This motivates our restriction to meaningful classes of source distributions with $\Huse<0$.
+%This means we inherently must talk about the security and errors together.
+
+In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.
+There are two minimal types of distributions where $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).
+The other is that there $t+\omega(\log n)$ blocks that contribute some entropy~(there is a continuum between these two types).
+Definitions~\ref{def:block guessable} and~\ref{def:unordered source} were developed for these types of sources respectively.
+However, we do not achieve security when $\Hfuzz(W)= \omega(\log n)$ for either definition, this is an open problem.
+
 \section{Fuzzy Conductors}
@@
 \label{sec:conductors}
-Fuzzy extractors are known to have strong upper bounds on remaining entropy based on the best error correcting codes.
+Fuzzy extractors are known to have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
 Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
@@
 \item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\rep(w', SS) = X$ with probability~(over the coins of $\gen', \rep'$) at least $1-\epsilon$.
+The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep(w', SS) = X]\geq 1-\delta$~(over the coins of $\gen', \rep'$).
 If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
@@
 \noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
-This motivates our use of a computational fuzzy conductor in \secref{sec:fuzzy extractors}.
+This motivates our use of a computational fuzzy conductor in \defref{def:comp fuzzy cond}.
 We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
@@
 \end{itemize}
-
+Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.  
 \begin{lemma}
@@
 
-\section{Inadequacy of Fuzzy Extractors for Biometrics}
-Fuzzy extractors were developed to derive stable from noisy sources.
-Biometrics represent an important noisy physical source.
-Unlike physical unclonable functions, biometrics are inherently fixed distributions.
-It is not possible to increase their entropy or reduce their error to improve key strength.
-Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).
-The security of the resulting system is usually measured using false accept rate vs.
-false reject rate.
-This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.
-A known false accept rate provides there is no guarantee helper data information-leakage.
-Indeed the helper data may completely reveal the original input.
-In high security applications, this type of analysis is sufficient.
-
-\label{sec:iris no key}
-As an example, the iris is the biometric believed to have the most entropy.
-The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
-Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.\footnote{There is considerable subsequent research after the work of Daugman~\cite{daugman2004}.
-These works do not dramatically improve the original results.}
-
-The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
-For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
-The comparison between the two readings is then made using bits not excluded by either image.
-It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $H_{usable}$:
-\begin{align*}
-H_{usable} &= \Hoo(W) - \log |B_t|\\
-&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
-\end{align*}
-Although irises are believed to be the strongest biometric a fuzzy extractor with the above parameters may completely reveal the original value.
-
-%Fingerprints are in a similar situation.  Ratha, Connell, and Bolle estimate that fingerprints contain $82$ bits of entropy~\cite{ratha2003biometrics}.
-%\bnote{Don't know what I want to say about fingerprints right now.  
-\section{Minimal Conditions for Fuzzy Extractor Security}
-\label{sec:minimal conditions}
-A necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.  We make this intuition formal here:
-
-\begin{definition}
-\label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
-\[
-\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
-\]
-\end{definition}
-\begin{lemma}
-\label{lem:fuzz necessary}
-Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-\end{lemma}
-\begin{proof}
-Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m\mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
-Consider the following distinguisher $D$:
-\begin{itemize}
-\item On input $r, p$.
-\item If $\rep(m, p) = r$, output $1$.
-\item Else output $0$.
-\end{itemize}
-First note that $|D|$ is of size $\log |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n)$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
-\[
-\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} - \frac{1}{2^{-\kappa}} = 1/\poly(n).
-\]
-\end{proof}
-
-\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
-This means that fuzzy min-entropy is a necessary condition for an interactive solution as well.
-The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
-When $H_{usable}<0$ there is some distribution such that $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution of all points within distance $t$).
-This means we inherently must talk about the security and errors together.
-
-For the Hamming distance having $\Hfuzz(W)\geq \omega(\log n)$ means that there are more entropic dimensions that the desired error-tolerance.
-There are two minimal types of distributions that provide $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).
-The other is that there $t+\omega(\log n)$ blocks that contribute some constant amount of entropy.
-Definitions~\ref{def:block guessable} and~\ref{def:unordered source} are geared towards this type of source, achieving security when the number of entropic blocks is only one greater than the desired error correction is an open problem.
-
 \section{Characterizing unguessable block distributions}

### 2014-02-05 constantRate/ConstCompFuzzExt.tex
editing sections 2 and 3

@@
 Furthermore, we may leak sensitive information about the underlying source $W$.
-For example, in \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
+In \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
 Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
 Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $\Huse>>0$ using a information-reconciliation component that hides all partial information.
-Constructing VBB obfuscation for sources where $\Huse <0$ is an open problem.
+Constructing noisy point obfuscation for all sources remains an open problem.
 
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^\ell$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
+We consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^\ell$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
 For the Hamming metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
@@
 Unless otherwise noted logarithms are base $2$.
-%\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).
-
 Usually, we use capitalized letters for random variables and lowercase letters for samples from a random variable.
@@
 \label{sec:coding theory}
-We introduce some notions from the field of binary error correcting codes.
+We introduce some notions from binary coding theory.
 Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel~\cite{tallini2002capacity} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.
@@
 \end{definition}
-\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
-The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).
-Codes where $\log |C| = \Theta(\ell)$ and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
-These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
 
@@
 
+\textbf{Notes:} 
+Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+ Codes where $\log |C| = \Theta(\ell)$ and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
+The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different.
+See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.
+
 \subsection{Obfuscation}
-Our construction uses obfuscation for a family of point function $\mathcal{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
+Our construction uses obfuscation for a family of point functions $\mathtt{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
 \[
@@
 \begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
-\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is a $\ell$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
+\label{def:obf} Let $\mathtt{I}$ be a family of polynomial-size circuits.
+A PPT algorithm $\mathcal{O}$ is a $\ell$-composable VGB obfuscator for $\mathtt{I}$ with auxiliary-input if the following conditions are met:
 \begin{enumerate}
-\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
-\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathcal{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\item \emph{Functionality:} for every $ I \in \mathtt{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
 \[
@@
 
-We focus on computational fuzzy extractors introduced~\cite{fuller2013computational}.
+In this section we present our paradigm for constructing computational fuzzy extractors.
 Definitions for information-theoretic fuzzy extractors can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
@@
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
-%\begin{definition}
-%\label{def:fuzzy extractor}
-%An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
-%\begin{enumerate}
-%\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
-%\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
-%\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
-%\end{enumerate}
-%A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
-%\end{definition}
-%
-%Secure sketches are the main technical tool in the construction of fuzzy extractors.
-Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
-%\begin{definition}
-%\label{def:secure sketch}
-%An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
-%\begin{enumerate}
-%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
-That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time.
-%\end{definition}
-%
-
-%A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
-%
-%\begin{lemma}
-%\label{lem:fuzzy ext construction}
-%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
-%\begin{itemize}
-%\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
-%\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
-%\end{itemize}
-%\end{lemma}
 
@@
 \end{definition}
-In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness.
+In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness~(this will be crucial in our second construction).
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $\Huse<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary~(see \apref{sec:minimal conditions} for the precise statement).
+With $\Huse<0$ this is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
 
@@
 We follow the second approach.
-
 In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.
@@
 \end{definition}
-
-We now define the two primitives for this approach: a computational fuzzy conductor and a (computational)~randomness extractor.
+We now define a computational fuzzy conductor and a (computational)~randomness extractor.
 A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
@@
 \end{definition}
-
-A computational extractor is the natural adaption of a randomness extractor to the computational setting.  We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
-%start with the standard notion of an average-case extractor.
-An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
+A computational extractor is the adaption of a randomness extractor to the computational setting.  We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
 \begin{definition}
@@
 
-Combining a computational fuzzy conductor and an appropriate randomness extractor yields a computational fuzzy extractor~(proof in \secref{sec:cond and cext}):
+Combining a computational fuzzy conductor and an appropriate computational extractor yields a computational fuzzy extractor~(proof in \apref{sec:cond and cext}):
 
@@
 \end{itemize}
-Then $\gen, \rep$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \max\{s_{cond} - |\cext| -d, s_{ext}\}$.
+Then $\gen, \rep$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
 \end{lemma}
@@
 \subsection{Correctness of \consref{cons:first construction}}
+\label{sec:correct first cons}
 We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
@@
 \subsection{Correctness of \consref{cons:sampling}}
+\label{sec:correct sampling}
 The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.
@@
 \delta^{D}((X, SS), (Y, SS))&= \delta^{D'}((\cext(X, U_d), U_d, SS), \cext(Y, U_d), U_d, SS)\\
-&\geq \delta^{D'}((\cext(X, U_d), U_d, P), (U_\kappa\times U_d \times P)) - \delta^{D'}((\cext(Y, U_d), U_d, SS), (U_\kappa\times U_d \times SS))\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, SS), (U_\kappa\times U_d \times SS)) - \delta^{D'}((\cext(Y, U_d), U_d, SS), (U_\kappa\times U_d \times SS))\\
 &>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
 \end{align*}
-Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
+Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
 \end{proof}

### 2014-02-05 trunk/constantRate/ConstCompFuzzExt.tex
proof of D.3

@@
 Furthermore, we may leak sensitive information about the underlying source $W$.
-For example, in \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
+In \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
 Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $H_{usable}>>0$ using a information-reconciliation component that hides all partial information.
-Constructing VBB obfuscation for sources where $H_{usable} <0$ is an open problem.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $\Huse>>0$ using a information-reconciliation component that hides all partial information.
+Constructing noisy point obfuscation for all sources remains an open problem.
 
@@
 \end{definition}
-In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness.
+In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness~(this will be crucial in our second construction).
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $H_{usable}<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary~(see \apref{sec:minimal conditions} for the precise statement).
+With $\Huse<0$ this is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
 
@@
 Let $W = W_1,..., W_\ell$ be a source.
-Let $\alpha =\omega(\log n)$ and suppose that for all $i$, $\Hoo(W_i)\geq \alpha$.
-Then for $q = \poly(n)$, there exists an $\alpha ' = \omega(\log n)$ such that $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
+Suppose that for all $i$, $\Hoo(W_i)\geq \alpha$, and that $q 2^{-\alpha}\leq1/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is superlogarithmic).
+Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-block unguessable distribution.
 \end{claim}
-\begin{proof}
-Intuitively, the claim is true because the oracle is negligibly like to return 1 on any query. Formally, we proceed by induction on oracle queries. 
-For a random variable $X$, let $\guess(X) = \max_x \Pr[X=x]$.
-Using the same notation as in the proof of Claim  \clref{cl:independent high ent}),  fix $i$ and $j$. Our inductive hypothesis is
-that $\Hav(W_i | A_1 \dots A_{j-1}) \ge \alpha_{j-1}$, where $\alpha_{j-1}=\omega(\log n)$.
-Recall that $\Hav(W_i | A_1 \dots A_j) =  -\log \expe_{a_1 \dots a_j} \guess (W_i|A_1 \dots, A_j=a_1\dots a_j)$.
+
+\begin{proof}
+Intuitively, the claim is true because the oracle is not likely to return 1 on any query. Formally, we proceed by induction on oracle queries,
+using the same notation as in the proof of   \clref{cl:independent high ent}. Our inductive hypothesis is
+that $\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0] \leq (j-1)2^{1-\alpha}$.  If the inductive hypothesis holds, then, for each $i$,  
+\begin{equation}
+\label{eq:cond-entropy}
+\Hoo(W_i | A_1= \dots= A_{j-1}=0) \ge \alpha-1\,.
+\end{equation}
+This is true for $j=1$ by the condition of the theorem. It is true for $j>1$ because, as a consequence of the definition of $\Hoo$,
+for any random variable $X$ and event $E$, $\Hoo(X|E)\ge \Hoo(X)+\log\Pr[E]$; and $(j-1) 2^{1-\alpha}\leq 2 q 2^{-\alpha} \leq 1/2$.  We prove the base case and the inductive step as follows:
 \begin{align*}
-\expe_{a_1 \dots a_j} \guess (W_i|A_1 \dots, A_j=a_1\dots a_j)
- = {} & \sum_{a_1 \dots a_{j-1}} \guess(W_i |A_1\dots A_j=a_1\dots a_{j-1}0) \Pr[A_1\dots A_j=a_1\dots a_{j-1}0] \\
-&+  \sum_{a_1 \dots a_{j-1}} \guess(W_i | A_1\dots A_j=a_1\dots a_{j-1}1) \Pr [A_1\dots A_j=a_1\dots a_{j-1}1] ) \\
+\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0 \vee A_j\neq 0] & = 
+\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0]+\Pr[A_1=\dots = A_{j-1}=0 \wedge A_j=1]\\
+& \le  (j-1)2^{1-\alpha}+\Pr[A_j=1\,|\,A_1=\dots = A_{j-1}=0]\\
+& \le  (j-1)2^{1-\alpha}+\max_k 2^{-\Hoo(W_k | A_1=\dots =A_{j-1}=0)}\\
+& \le  (j-1)2^{1-\alpha}+ 2^{1-\alpha}\\
+& = j 2^{1-\alpha}
 \end{align*}
-
-We first deal with the second term. 
+(where the third line follows by considering that to get $A_j=1$, the adversary needs to guess some $W_k$, and the fourth line follows by \eqref{eq:cond-entropy}).
+Thus, using $j=q+1$ in \eqref{eq:cond-entropy},
+ we know $\Hoo(W_i | A_1= \dots= A_q=0) \ge \alpha-1$.
 \begin{align*}
-\sum_{a_1 \dots a_{j-1}}
-\Pr [A_1\dots A_j=a_1\dots a_{j-1}1] & \le
-\sum_{a_1 \dots a_{j-1}}
-\max_k \guess[W_k | A_1\dots A_{j-1}=a_1\dots a_{j-1}] \cdot \Pr[A_1\dots A_{j-1}=a_1\dots a_{j-1}] 
-\\ & \le
-\sum_k \sum_{a_1\dots a_{j-1}} \guess[W_k | A_1\dots A_{j-1}=a_1\dots a_{j-1}] \cdot \Pr[A_1\dots A_{j-1}=a_1\dots a_{j-1}] \\
-& =
-\sum_k 2^{-\Hav(W_k | A_1\dots A_{j-1})}\\
-&\le k 2^{-\alpha_{j-1}} = \ngl(n)\,.
+\Hav[W_i | A_1,\dots, A_q] &\ge -\log \left( 2^{-\Hoo(W_i | A_1= \dots= A_q=0)}\Pr[A_1=\dots=A_q=0]+1\cdot \Pr[A_1\neq 0 \vee \dots \vee  A_q\neq 0] \right)\\
+& \ge -\log \left(  2^{-\Hoo(W_i | A_1= \dots= A_q=0)}+q2^{1-\alpha} \right)\\
+& \ge -\log   (q+1) 2^{1-\alpha}) = \alpha-1-\log(q+1)\,.
 \end{align*}
-
-\lnote{working here}
-
-, it suffices to show that $\Hav(W_i | Q_1,A_1,..., Q_q, A_q) \geq \omega(\log n)$.  By the definition of conditional min-entropy:
-\begin{align*}
-\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &= -\log (\Pr[\text{some non zero response}] \max_{w\in W_i} \Pr[W_i | \text{non zero response}) \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i| \text{all zero responses}]\\
-&\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}]).
-\end{align*}
-It suffices to show that $\Pr[\text{some non zero response}] = \ngl(n)$ and that $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = \ngl(n)$.  We show each of these is turn.
-
-First note that clearly the 1st query returns $1$ with $2^{-\alpha}$ probability~(due to the min-entropy condition).
-Conditioned on this response being $0$ the probability of all other events increases by at most negligible amount~(the statistical distance between the original distribution and the distribution conditioned on the first response being $0$ is $\ngl(n)$).
-Thus, the total probability of a $1$ is at most:
-\[
-\Pr[\text{some non zero response}] \leq 2^{-\alpha} + (2^{-\alpha}+\ngl(n)) + ... +(2^{-\alpha}+q\times \ngl(n)) = \ngl(n).
-\]
-Now consider $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}]$.  For each zero response, the probability of any $w_i$ increases by at most a negligible amount, this means that
-\[\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = 2^{-\alpha} + q\times \ngl(n) = \ngl(n).\]
-
-Thus, we have the following:
-\begin{align*}
-\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}])\\
-& \geq -\log (\ngl(n) + (1-\ngl(n))\ngl(n)) = -\log (\ngl(n)) = \omega(\log (n)).
-\end{align*}
-This completes the proof.\bnote{someone check this proof!!!! also make it more precise and better}
 \end{proof}

### 2014-02-05 constantRate/ConstCompFuzzExt.tex
Small notational changes

@@
 \end{definition}
-In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness~(this will be crucial in our second construction).
+In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness.
+In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
@@
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(s_{cond}, \epsilon_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
 \begin{itemize}
@@
 Let $\chi$ be a finite set.
-A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, s_{ext}, \epsilon_{ext})$-average-case computational extractor} if for all pairs
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon_{ext}, s_{ext})$-average-case computational extractor} if for all pairs
 of random variables $X, Y$ over $\zo^\ell, \chi$ such that
@@
 \label{lem:cond and cext}
-Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{cond},\epsilon_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
-Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, s_{ext}, \epsilon_{ext})$-average case computational extractor.
-Define $\gen, \rep$ as:
+Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
+Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.
+Define $(\gen, \rep)$ as:
 \begin{itemize}
@@
 \end{itemize}
-Then $\gen, \rep$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
+Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
 \end{lemma}
@@
 \label{sec:construction}
-For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.
-Our goal is to derive strong keys when the number of possible error patterns is larger than the starting entropy of source.
-That is we want to provide some security when $0>\Huse = \Hoo(W) - \log|B_t|$.
+For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.  Our goal is to derive strong keys for a large class of sources where $0>\Huse = \Hoo(W) - \log|B_t|$.
 In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
-Thus, we focus on building a computational fuzzy conductor with meaningful output entropy.
-Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+We focus on building a computational fuzzy conductor with meaningful output entropy.
+Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
 
@@
 \label{cons:first construction}
-Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.
-Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.
+Let $n$ be a security parameter, let $\mathcal{Z}$ be an alphabet with $|\mathcal{Z}| \ge 2^n$ and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $\mathcal{Z}$.
 Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
@@
 \item If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
-\item Else: Sample $r_i \leftarrow U_n$.
+\item Else: Sample $r_i \overset{\$}\leftarrow \mathcal{Z}$.
 \subitem Let $p_i = \mathcal{O}(I_{r_i})$.
@@
 
-\textbf{Notes:}  We make several observations about the above construction:
-\begin{itemize}
-\item The input $w$ is hidden in two different ways.  In locations where $c_i=1$ the block $w_i$ is information-theoretically unknown.
+The input $w$ is hidden in two different ways.  In locations where $c_i=1$ the block $w_i$ is information-theoretically unknown.
 In locations where $c_i=0$ it is hard to find $w_i$ given the point obfuscation.
-As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
-\item There are two possible reasons for a bit $c_i'$ to be $1$.
+%As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
+
+There are two possible reasons for a bit $c_i'$ to be $1$.
 Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.
-However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).
+However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
 This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
-\end{itemize}
 
@@
 \label{thm:security of cons}
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\zo^n$. %that is $(s_{obf}, \epsilon_{obf})$-hard.  
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}$. 
 Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
@@
 \begin{itemize}
-\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}}(C)$.
-\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}}(C) \approx S^{\mathcal{O}}(C')$.
-\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$.
+\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
+\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.
+That is, $\delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
+\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
 \end{itemize}
@@
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 \subitem Set $p_i = \rho_i, \lambda_i$.
-\item If $c_i = 1$: Sample $r_i \leftarrow U_{\mathcal{Z}^{\eta}}$.
+\item If $c_i = 1$: Sample $r_i \overset{\$}\leftarrow \mathcal{Z}^{\eta}$.
 \subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
@@
 Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
-Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$-hard with error $\delta$ for
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
 \begin{align*}

### 2014-02-05 trunk/constantRate/ConstCompFuzzExt.tex
small edits in D

@@
 &> \log {\ell \choose t} (2^n-1)^t\\
-&=\Theta(tn) + \log {\ell\choose t}
+& =\Theta(tn) + \log {\ell\choose t}
 % \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
@@
 Thus, we begin with the case of independent blocks.
+In all of the examples that follow we denote the adversary by $S$ as we need security against the computationally unbounded adversary defined in VGB obfuscation~(\defref{def:obf}).
 
@@
 \begin{proof}
-It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log q$.
+It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
 We can ignore queries for all blocks but the $i$th, as the blocks are independent.
 Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice).
-Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $\mathcal{A}$ \lnote{is the adversary $S$, $\mathcal{A}$, or $A$?} making $q$  queries about the $i$th block.
+Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block.
 Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed).
@@
 \Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
-&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
+&=\Hoo(W_i) - |A_1, \dots, A_q|\\
 &=\alpha - \log (q+1)\,,
@@
 \noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
-\clref{cl:independent high ent} captures, in particular, this class of distributions.
-
-However, \defref{def:block guessable} captures considerably more distributions.  We now consider more complicated distributions where blocks are not independent.
+\clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
+However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.
 
@@
 There are two possibilities: either $q_j$ is not in the image of $f_i$,  or $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
-Then (by assuming $A$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.
+Then (by assuming $S$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.
 Then the possible responses are strings with Hamming weight at most $1$ (like in the
@@
 This is true for $j=1$ by the condition of the theorem. It is true for $j>1$ because, as a consequence of the definition of $\Hoo$,
-for any random variable $X$ and event $E$, $\Hoo(X|E)\ge \Hoo(X)+\log\Pr[E]$; and $(j-1) 2^{1-\alpha}\leq 2 q 2^{-\alpha} \leq 1/2$.  We prove the base case and the inductive step as follows:
+for any random variable $X$ and event $E$, $\Hoo(X|E)\ge \Hoo(X)+\log\Pr[E]$; and $(j-1) 2^{1-\alpha}\leq 2 q 2^{-\alpha} \leq 1/2$.
+
+We now show that $\Pr[A_1\neq 0 \vee \dots \vee A_{j}\neq 0] \leq j2^{1-\alpha}$, assuming that $\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0] \leq (j-1)2^{1-\alpha}$.
 \begin{align*}
@@
 & \le  (j-1)2^{1-\alpha}+\Pr[A_j=1\,|\,A_1=\dots = A_{j-1}=0]\\
-& \le  (j-1)2^{1-\alpha}+\max_k 2^{-\Hoo(W_k | A_1=\dots =A_{j-1}=0)}\\
+& \le  (j-1)2^{1-\alpha}+\max_i 2^{-\Hoo(W_i | A_1=\dots =A_{j-1}=0)}\\
 & \le  (j-1)2^{1-\alpha}+ 2^{1-\alpha}\\
@@
 \end{align*}
-(where the third line follows by considering that to get $A_j=1$, the adversary needs to guess some $W_k$, and the fourth line follows by \eqref{eq:cond-entropy}).
-Thus, using $j=q+1$ in \eqref{eq:cond-entropy},
- we know $\Hoo(W_i | A_1= \dots= A_q=0) \ge \alpha-1$.
+(where the third line follows by considering that to get $A_j=1$, the adversary needs to guess some $W_i$, and the fourth line follows by~\eqref{eq:cond-entropy}).
+Thus, using $j=q+1$ in~\eqref{eq:cond-entropy},
+ we know $\Hoo(W_i | A_1= \dots= A_q=0) \ge \alpha-1$.  Finally this means that
 \begin{align*}
-\Hav[W_i | A_1,\dots, A_q] &\ge -\log \left( 2^{-\Hoo(W_i | A_1= \dots= A_q=0)}\Pr[A_1=\dots=A_q=0]+1\cdot \Pr[A_1\neq 0 \vee \dots \vee  A_q\neq 0] \right)\\
+\Hav(W_i | A_1,\dots, A_q) &\ge -\log \left( 2^{-\Hoo(W_i | A_1= \dots= A_q=0)}\Pr[A_1=\dots=A_q=0]+1\cdot \Pr[A_1\neq 0 \vee \dots \vee  A_q\neq 0] \right)\\
 & \ge -\log \left(  2^{-\Hoo(W_i | A_1= \dots= A_q=0)}+q2^{1-\alpha} \right)\\
-& \ge -\log   (q+1) 2^{1-\alpha}) = \alpha-1-\log(q+1)\,.
+& \ge -\log \left(  (q+1) 2^{1-\alpha}\right) = \alpha-1-\log(q+1)\,.
 \end{align*}

### 2014-02-05 trunk/constantRate/ConstCompFuzzExt.tex
small edits in D

@@
 \begin{theorem}
-Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
+Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\mathcal{Z}^\ell$ for any $q = \poly(n)$.
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 When $t =\Theta(\ell)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
-Thus, \consref{cons:first construction} achieves negative $\Huse$ when $t = \Theta(\ell)$.
-We achieve $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
+Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
+%We achieve security when $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
 %When $ \ell , t, n$ to be the same order provides a natural balance of parameters.

### 2014-02-06 trunk/constantRate/ConstCompFuzzExt.tex
Revised security of second cons argument to be chernoff bound

@@
 Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
+Let $\eta = \omega(\log n) = o(\gamma)$ and let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
 Define $\gen, \rep$ as:
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-There is a crucial difference, our use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+A crucial difference is the use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
 In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
@@
 \subsection{Security of \consref{cons:sampling}}
-\bnote{this whole chain of arguments needs to be cleaned up}
-\bnote{went through the surrounding text, need to look at all the theorem statements}
 In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $V_i$ has super-logarithmic entropy on its own~(samplers will select ``enough'' of the good blocks of $W$ each time).
@@
 
+\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
 \begin{lemma}
 \label{lem:sampling works}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta = \omega(\log n) \le  o(\gamma)$.
+Consider some fixed $i$, there exists a value $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ such that
+\[
+\Pr[\Hoo(V_i | \Lambda) \geq  \omega(\log n) = \alpha'] \geq 1- O(e^{-\eta}).
+\]
+\end{lemma}
+\begin{proof}
+Consider some fixed $i$.  
+For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \gamma(1/2+\Theta(1))$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Since this is a worst case guarantee,
+\[
+\Hoo(V_i |\Lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
+\]
+
+Denote by $X = |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|$.
+We now calculate $\expe[X]$.
+Let $j_1,.., j_\eta$ be the elements selected by sampling algorithm.
+Note that the first element $j_1\in\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
+Consider some choice $j_k$ there are least $\gamma-\beta-k$ samples in $\mathcal{I}$ remaining, so it the $\Pr[j_k\in\mathcal{I}]>(\gamma-\beta-\eta)/\gamma$.
+We can associate with each $j_k$ a Bernoulli random variable $X_i$ with success probability $(\gamma-\beta-\eta)/\gamma$ and note that
+\[
+\expe[X] \geq \eta \expe[X_i] \geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
+\]
+
+Using the Chernoff bound the probability that $X$ is rarely far from its expected value:
+\[
+\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
+\]
+Where the last equality follows because 
+\[
+\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
+\]
+That is $\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \omega(\log n)] \geq 1- O(e^{-\eta})$.
+\end{proof}
+
+%
+%\begin{lemma}
+%
+%Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.
 Let $\eta = \Omega(\log n)$.
 Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
-\end{lemma}
-\begin{proof}
-By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.
+%\end{lemma}
+%\begin{proof}
+%By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.
 \bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.
 too much for a reader to digest.}
-\end{proof}
+%\end{proof}
 
@@
 \label{cor:samp sec}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.
-Let $\eta = \Omega(\log n)$.
-Denote by $\epsilon_{sam} = \ngl(n) + 2^{-\Omega(n)} = \ngl(n)$ the value from \lemref{lem:sampling works}.
-Then, the distribution $(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1-\Theta(1)))$-unordered block source.
+Let $\eta = \omega(\log n) = o(\gamma)$ and let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.
+Then $\Pr[\exists i, \Hoo(V_i | \Lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
+%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
 \end{corollary}
 \begin{proof}
-Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
+Union bound over the probability in \lemref{lem:sampling works}.
+%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
 \end{proof}
@@
 \label{cor:v are unguessable}
-Let $W, V, \Lambda, V', U_{\ell\times r_{sam}}$ be as in \corref{cor:samp sec}.
-Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\ell\times r_{sam}}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
+Let $W, V, \Lambda$ be as in \corref{cor:samp sec}.
+Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-block unguessable distribution.
 \end{corollary}
@@
 \begin{proof}
-Result of \corref{cor:v are unguessable} and \thref{thm:security of cons}.
+Result of \corref{cor:v are unguessable} and \thref{thm:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
 \end{proof}
@@
 Let $\mathcal{W}$ be the family of $(\alpha = \omega(1), \beta\leq \gamma(1/2-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
-Let $\eta = \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$.
+Let $\eta = \omega(\log n) = o(\gamma)$ and $\ell = O(\poly(n)) = \omega(\log n)$.
 Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
Revised security of second cons arg

@@
 Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
+We need a strong version of point obfuscation secure under composition, this is achievable under a particular number-theoretic assumption~\cite{bitansky2010strong}.
 Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
@@
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $\Huse<0$ this is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
+With $\Huse<0$ some restriction is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
+Instead of restricting the class of source distributions~(for which security is achieved), the definition could restrict the error model to errors that are ``likely'' to occur in the source.
+We leave this as an open problem.
 
@@
 
-\section{A Constant Error-Tolerance Computational Fuzzy Extractor}
+\section{A Computational Fuzzy Extractor when $\Huse<0$}
 \label{sec:construction}
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} \lnote{is it ''block unguessable'' or ''unguessable block''?
-the usage is inconsistent}if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
 \[
@@
 %\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
-We discuss  block unguessable distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for block unguessable distributions:
+We discuss unguessable block distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for unguessable block distributions:
 \begin{theorem}
@@
 
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for block unguessable distributions:
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for unguessable block distributions:
 \begin{theorem}
-Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.
+Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\mathcal{Z}^\ell$ for any $q = \poly(n)$.
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 We consider what entropy is necessary for security.
-The simplest type of block unguessable distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
 For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
@@
 An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.
-However, we achieve security for significantly lower entropy levels than were needed for block unguessable distributions.
+However, we achieve security for significantly lower entropy levels than were needed for unguessable block distributions.
 
@@
 
+%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
 \begin{lemma}
 \label{lem:sampling works}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta = \omega(\log n) \le  o(\gamma)$.
+Consider some fixed $i$, there exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that
+\[
+\Pr[\Hoo(V_i | \Lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
+\]
+\end{lemma}
+\begin{proof}
+Consider some fixed $i$.  Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda$ be some particular outcome.
+For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Since this is a worst case guarantee for all $\lambda$,
+\[
+\Hoo(V_i |\lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
+\]
+
+Denote by $X = |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|$.
+We now calculate $\expe[X]$.
+Let $j_1,.., j_\eta$ be the elements selected by sampling algorithm.
+The ``first'' element $j_1$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
+For each selected index $j_k$ there are least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}]>(\gamma-\beta-\eta)/\gamma$.
+We can associate with each $j_k$ a Bernoulli random variable $X_k$ with success probability at least $(\gamma-\beta-\eta)/\gamma$ and note that
+\[
+\expe[X] = \sum_{k=1}^\eta\expe[X_k] \geq \eta \expe[X_\eta]\geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
+\]
+Using the Chernoff bound, $X$ rarely is far from its expected value:
+\[
+\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
+\]
+Where the last equality follows because 
+\[
+\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
+\]
+That is \[
+\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \alpha'] \geq 1- O(e^{-\eta}).
+\]
+\end{proof}
+
+%
+%\begin{lemma}
+%
+%Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.
 Let $\eta = \Omega(\log n)$.
 Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
-\end{lemma}
-\begin{proof}
-By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.
+%\end{lemma}
+%\begin{proof}
+%By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.
 \bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.
 too much for a reader to digest.}
-\end{proof}
+%\end{proof}
 
@@
 \label{cor:samp sec}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.
-Let $\eta = \Omega(\log n)$.
-Denote by $\epsilon_{sam} = \ngl(n) + 2^{-\Omega(n)} = \ngl(n)$ the value from \lemref{lem:sampling works}.
-Then, the distribution $(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1-\Theta(1)))$-unordered block source.
+Let $\eta = \omega(\log n) = o(\gamma)$ and let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.
+Then $\Pr[\exists i, \Hoo(V_i | \Lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
+%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
 \end{corollary}
 \begin{proof}
-Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
-\end{proof}
-
-In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a block unguessable distribution~\clref{cl:all blocks entropy}.
+Union bound over the probability in \lemref{lem:sampling works}.
+%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
+\end{proof}
+
+In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a unguessable block distribution~\clref{cl:all blocks entropy}.
 This allows us to conclude:
@@
 \label{cor:v are unguessable}
-Let $W, V, \Lambda, V', U_{\ell\times r_{sam}}$ be as in \corref{cor:samp sec}.
-Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\ell\times r_{sam}}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
+Let $W, V, \Lambda$ be as in \corref{cor:samp sec}.
+Let $q = \poly(n)$, for $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$ the distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-unguessable block distribution.
 \end{corollary}
 
-Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a block unguessable distribution, \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,..., V_\ell$.
+Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a unguessable block distribution, \consref{cons:sampling} is \consref{cons:first construction} applied to $V_1,..., V_\ell$.
 \begin{corollary}
@@
 Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.
-Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
+Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-unguessable block distribution.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-unguessable block distribution.
 \end{claim}
 \begin{proof}
-It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log q$.
+It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
 We can ignore queries for all blocks but the $i$th, as the blocks are independent.
 Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice).
-Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $\mathcal{A}$ \lnote{is the adversary $S$, $\mathcal{A}$, or $A$?} making $q$  queries about the $i$th block.
+Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block.
 Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed).
@@
 Furthermore, let $f_i$ denote the restriction of $f$'s output to its $i$th coordinate.
-If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-block unguessable distribution.
+If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
 \end{claim}
@@
 Suppose that for all $i$, $\Hoo(W_i)\geq \alpha$, and that $q 2^{-\alpha}\leq1/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is superlogarithmic).
-Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-block unguessable distribution.
+Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block distribution.
 \end{claim}

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
Moved second cons proofs to appendix

@@
 
-We give a brief outline of the proof here, the full proof is in \apref{app:security of main cons}.
+We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
 It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
@@
 Since the $r_i$ are chosen independently, one has,
-\begin{align*}
-\Pr[\text{no $1\rightarrow 0$ flips}] &\geq 1-\Pr[\text{some }r_i = w_i']\\
-&\geq 1-\ell \frac{1}{2^n} = 1-\frac{\poly(n)}{2^n} = \ngl(n)
-\end{align*}
+\[
+\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{2^n}.
+\]
 \end{proof}
@@
 Correction occurs for a small number of dimensions that are allowed to vary completely.
-As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
+As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries.
 
@@
 \]
-When $t =\Theta(\ell)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
-Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
+When $t =\Theta(\ell)$ and the entropy of each block is $o(n)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+%Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
 %We achieve security when $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
@@
 Thus, we have a tradeoff between individually required entropy and supported error tolerance.
-In ordering for sampling to work properly, we need a source where most blocks are likely to contribute some entropy.
+In ordering for sampling to work properly, we need a source where a constant fraction of blocks are likely to contribute some entropy.
 
@@
 An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.
-However, we achieve security for significantly lower entropy levels than were needed for unguessable block distributions.
+However, we achieve security for significantly lower entropy levels than for unguessable block distributions.
 
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is the use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.
+A crucial difference is the use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has individual entropy.
 In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
@@
 Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.
-We begin by showing that each $V_i$ is statistically close to a high entropy distribution.
+We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
 
@@
 \[
-\Pr[\Hoo(V_i | \Lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
+\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
 \]
 \end{lemma}
-\begin{proof}
-Consider some fixed $i$.  Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda$ be some particular outcome.
-For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee for all $\lambda$,
-\[
-\Hoo(V_i |\lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
-\]
-
-Denote by $X = |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|$.
-We now calculate $\expe[X]$.
-Let $j_1,.., j_\eta$ be the elements selected by sampling algorithm.
-The ``first'' element $j_1$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
-For each selected index $j_k$ there are least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}]>(\gamma-\beta-\eta)/\gamma$.
-We can associate with each $j_k$ a Bernoulli random variable $X_k$ with success probability at least $(\gamma-\beta-\eta)/\gamma$ and note that
-\[
-\expe[X] = \sum_{k=1}^\eta\expe[X_k] \geq \eta \expe[X_\eta]\geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
-\]
-Using the Chernoff bound, $X$ rarely is far from its expected value:
-\[
-\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
-\]
-Where the last equality follows because 
-\[
-\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
-\]
-That is \[
-\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \alpha'] \geq 1- O(e^{-\eta}).
-\]
-\end{proof}
-
 %
@@
 Let $\eta = \omega(\log n) = o(\gamma)$ and let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.
-Then $\Pr[\exists i, \Hoo(V_i | \Lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
+Then $\Pr_{\lambda\leftarrow \Lambda}[\exists i, \Hoo(V_i | \Lambda = \lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
 %[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
@@
 Let $t'$ be the capacity of $C$.
-We show that $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.
+We show $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.
+The proof is in \apref{sec:sampling errors}.
 
 \begin{lemma}
+\label{lem:sampling errors}
 Let $n, W$ be as above and Let $C$ be a code that corrects $t'$ $0\rightarrow 1$ bit errors where $t' =\Theta(\ell)$.
@@
 \end{lemma}
-
-\begin{proof}
-Let $t$ be as stated in the lemma.
-We first consider calculate $\expe[\dis(V, V')]$ and then show that the distance between $v$ and $v'$ is rarely much more than this value.
-Let $\mu = -\log(1-t'/(2\ell))/2$ then one has:
-\begin{align*}
-\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
-&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
-& = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}
-\end{align*}
-
-With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq  t'/(2\ell)$. By the Chernoff bound, we have
-\begin{align*}
-\Pr\left[\frac{1}{\ell} \sum_{i=1}^\ell X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\ell} = O(e^{- \ell}).
-\end{align*}
-Where the last equality holds because $t'/(2\ell) = \Theta(1)$.
-\end{proof}
 
@@
 
+\section{Proof of \lemref{lem:sampling works}}
+\label{sec:proof of sampling lemma}
+\begin{proof}
+Consider some fixed $i$.  Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda$ be some particular outcome.
+For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Since this is a worst case guarantee for all $\lambda$,
+\[
+\Hoo(V_i |\lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
+\]
+
+Denote by $X = |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|$.
+We now calculate $\expe[X]$.
+Let $j_1,.., j_\eta$ be the elements selected by sampling algorithm.
+The ``first'' element $j_1$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
+For each selected index $j_k$ there are least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}]>(\gamma-\beta-\eta)/\gamma$.
+We can associate with each $j_k$ a Bernoulli random variable $X_k$ with success probability at least $(\gamma-\beta-\eta)/\gamma$ and note that
+\[
+\expe[X] = \sum_{k=1}^\eta\expe[X_k] \geq \eta \expe[X_\eta]\geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
+\]
+Using the Chernoff bound, $X$ rarely is far from its expected value:
+\[
+\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
+\]
+Where the last equality follows because 
+\[
+\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
+\]
+That is \[
+\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \alpha'] \geq 1- O(e^{-\eta}).
+\]
+\end{proof}
+
+\section{Proof of \lemref{lem:sampling errors}}
+\label{sec:sampling errors}
+
+\begin{proof}
+Let $t$ be as stated in the lemma.
+We first consider calculate $\expe[\dis(V, V')]$ and then show that the distance between $v$ and $v'$ is rarely much more than this value.
+Let $\mu = -\log(1-t'/(2\ell))/2$ then one has:
+\begin{align*}
+\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
+&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
+&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
+&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
+& = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}
+\end{align*}
+
+With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq  t'/(2\ell)$. By the Chernoff bound, we have
+\begin{align*}
+\Pr\left[\frac{1}{\ell} \sum_{i=1}^\ell X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\ell} = O(e^{- \ell}).
+\end{align*}
+Where the last equality holds because $t'/(2\ell) = \Theta(1)$.
+\end{proof}
+
 \end{document}

### 2014-02-06 trunk/constantRate/ConstCompFuzzExt.tex
Small edits to first four sections

@@
 
-Traditionally, a fuzzy extractor works for any distribution with enough entropy.
+Fuzzy extractors work for any distribution with enough entropy.
 %In this setting, the entropy of the source must be significantly higher than the logarithm of number of error patterns corrected~(Dodis et al., J.
@@
 of Comp.
-2008) show there is some source where the maximum key length cannot exceed the minimum usable entropy.
-Therefore, fuzzy extractors that only consider the input entropy must output a key whose length is at most the minimum usable entropy.
-For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as an open problem.
+2008) show there is some source where the key length cannot exceed the minimum usable entropy.
+Therefore, fuzzy extractors that output the same length key for any source with enough entropy cannot output a key longer than the minimum usable entropy.
+For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.
 
@@
 Our constructions are inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  
-Our two constructions are similar to spirit but optimize different parameters.
+\bnote{this whole paragraph needs work} Our two constructions are similar to spirit but optimize different parameters.
 The first requires individual blocks of the source to have super-logarithmic entropy and corrects a constant fraction of errors.
@@
 Both of these problems have interactive and non-interactive versions.
-For a single user~(trying to produce the same key from multiple readings of a physical source) non-interactive solutions are appropriate.
+For a single user trying to produce the same key from multiple readings of a physical source non-interactive solutions are needed.
 We focus on this setting.
@@
 
-Unfortunately, fuzzy extractors have not yielded key derivation for all noisy sources.
-This is because there is tension between security and error-tolerance.
+Fuzzy extractors have not yielded key derivation for all noisy sources.
+There is tension between security and error-tolerance.
 The key should be uniform to an observer but nearby $w'$ should map to the same key.
@@
 To achieve security when $\Huse<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
-However, the tools for constructing information-theoretic fuzzy extractors have not produced natural restrictions.
+However, the tools for constructing information-theoretic fuzzy extractors have not yielded natural restrictions.
 Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
@@
 
-In this work, we construct a computational fuzzy extractor when $\Huse<0$ for a large class of distributions.
+In this work, we construct computational fuzzy extractors when $\Huse<0$ for large classes of distributions.
 In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse<0$.
@@
 With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
-For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.
+For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.
 Thus, most bits of $c_i$ are recoverable.
-To tolerate errors we choose the coins $c$ from an error-correcting code.
+To tolerate errors we sample the coins $c$ from the codewords of an error-correcting code.
 The set of possible codewords forms a high entropy distribution.
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^\ell$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.
+We consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^\ell$ the Hamming distance between $x,y$ is $\dis(x,y) = \{i | x_i \neq y_i\}$.
 For the Hamming metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
@@
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $\Huse<0$ this is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
+With $\Huse<0$ some restriction is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
+Instead of restricting the class of source distributions, the definition could restrict the correctable errors to errors that are ``likely'' to occur in the source.
+We leave this as an open problem.
 
@@
 If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(Y |P)\geq \tilde{m}$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $X$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
 \end{itemize}
@@
 \label{cons:first construction}
-Let $n$ be a security parameter, let $\mathcal{Z}$ be an alphabet with $|\mathcal{Z}| \ge 2^n$ and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $n$ be a security parameter, let $\mathcal{Z}$ be an alphabet with $|\mathcal{Z}| = \omega(\poly(n))$ and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
 Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $\mathcal{Z}$.
@@
 There are two possible reasons for a bit $c_i'$ to be $1$.
-Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.
+Because the true value was $1$ and because $w_i \neq w_i'$.
 However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
@@
 By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-This means we can consider what the adversary learns using adaptive equality queries to individual blocks.
-Our construction is secure as long as enough blocks are unpredictable after adaptive queries~(we discuss minimal conditions for fuzzy extractor security in more depth in \apref{sec:minimal conditions}):
+Our construction is secure as long as enough blocks are unpredictable after adaptive queries:
 
@@
 \item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.
-That is, $\delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
+That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
 \item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
@@
 \label{lem:no 1 to 0 flips}
-The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/2^n = \ngl(n)$.
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
 \end{lemma}
@@
 Recall that $c$ contains at most $\ell$ $1$s.
-Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$.
+Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/|\mathcal{Z}|$.
 Since the $r_i$ are chosen independently, one has,
-\begin{align*}
-\Pr[\text{no $1\rightarrow 0$ flips}] &\geq 1-\Pr[\text{some }r_i = w_i']\\
-&\geq 1-\ell \frac{1}{2^n} = 1-\frac{\poly(n)}{2^n} = \ngl(n)
-\end{align*}
+\[
+\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{|\mathcal{Z}|}.
+\]
 \end{proof}
@@
 \[
-\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\delta_{code}\right).
-\]
-That is, \consref{cons:first construction} is correct with error at most $\ell/2^n+\delta_{code}$.
+\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{|\mathcal{Z}|}+\delta_{code}\right).
+\]
+That is, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|+\delta_{code}$.
 \end{lemma}
 
-\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
+\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+\Omega(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
 This requires a code where most codewords have Hamming weight close to $1/2$.
@@
 
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for block unguessable distributions:
+Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for unguessable block distributions:
 \begin{theorem}
-Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\mathcal{Z}^\ell$ for any $q = \poly(n)$.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$~(over $\mathcal{Z}^\ell$ where $|\mathcal{Z}| = \omega(\poly(n))$).
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 \log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i\\
-&> \log {\ell \choose t} (2^n-1)^t\\
-& =\Theta(tn) + \log {\ell\choose t}
+&> \log {\ell \choose t} (|\mathcal{Z}|-1)^t\\
+& =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
 % \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
@@
 \[
-\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
-Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
+\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
+\]
+When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+%Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
 %We achieve security when $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
@@
 An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.
-However, we achieve security for significantly lower entropy levels than were needed for block unguessable distributions.
+However, we achieve security for significantly lower entropy levels than for unguessable block distributions.
 
@@
 Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.
-We begin by showing that each $V_i$ is statistically close to a high entropy distribution.
-
-\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
+We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
+
+%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
 \begin{lemma}
@@
 Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta = \omega(\log n) \le  o(\gamma)$.
-Consider some fixed $i$, there exists a value $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ such that
-\[
-\Pr[\Hoo(V_i | \Lambda) \geq  \omega(\log n) = \alpha'] \geq 1- O(e^{-\eta}).
+Consider some fixed $i$, there exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that
+\[
+\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
 \]
 \end{lemma}
-\begin{proof}
-Consider some fixed $i$.  
-For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \gamma(1/2+\Theta(1))$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee,
-\[
-\Hoo(V_i |\Lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
-\]
-
-Denote by $X = |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|$.
-We now calculate $\expe[X]$.
-Let $j_1,.., j_\eta$ be the elements selected by sampling algorithm.
-Note that the first element $j_1\in\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
-Consider some choice $j_k$ there are least $\gamma-\beta-k$ samples in $\mathcal{I}$ remaining, so it the $\Pr[j_k\in\mathcal{I}]>(\gamma-\beta-\eta)/\gamma$.
-We can associate with each $j_k$ a Bernoulli random variable $X_i$ with success probability $(\gamma-\beta-\eta)/\gamma$ and note that
-\[
-\expe[X] \geq \eta \expe[X_i] \geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
-\]
-
-Using the Chernoff bound the probability that $X$ is rarely far from its expected value:
-\[
-\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
-\]
-Where the last equality follows because 
-\[
-\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
-\]
-That is $\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \omega(\log n)] \geq 1- O(e^{-\eta})$.
-\end{proof}
-
 %
@@
 
-In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a block unguessable distribution~\clref{cl:all blocks entropy}.
+In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a unguessable block distribution~\clref{cl:all blocks entropy}.
 This allows us to conclude:
@@
 Let $W, V, \Lambda$ be as in \corref{cor:samp sec}.
-Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-block unguessable distribution.
+Let $q = \poly(n)$, for $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$ the distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-unguessable block distribution.
 \end{corollary}
 
-Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a block unguessable distribution, \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,..., V_\ell$.
+Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a unguessable block distribution, \consref{cons:sampling} is \consref{cons:first construction} applied to $V_1,..., V_\ell$.
 \begin{corollary}
@@
 \subsection{Discussion of \consref{cons:sampling}}
-\consref{cons:sampling} achieves $\Huse<0$ for an interesting setting of parameters.
+We now show \consref{cons:sampling} can work for unordered block sources when $\Huse<0$.
 The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
@@
 Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.
-Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
+Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-unguessable block distribution.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-unguessable block distribution.
 \end{claim}
@@
 \label{cl:ent bounded away from n}
-$n-\log q \geq \alpha$
+$\alpha \le n-\log q$
 \end{claim}
 \begin{proof}
-It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.
+It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.
 Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
@@
 \begin{align*}
-\delta^{D}(( P, C), (P, C'))&\leq |\expe \expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
+\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
 &+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\

### 2014-02-06 trunk/constantRate/ConstCompFuzzExt.tex
Small edits to first three appendices

@@
 \section{Use of Fuzzy Extractors for Biometrics}
-Fuzzy extractors were developed to derive stable from noisy sources.
+Fuzzy extractors derive stable from noisy sources.
 Biometrics represent an important noisy physical source.
@@
 This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.
-False accept rate provides no bound on helper data information-leakage.
+False accept rate provides no bound on the information leaked by the helper data.
 Indeed the helper data may completely reveal the original input.
@@
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.
 There has been considerable research since the work of Daugman~\cite{daugman2004}.
-These works do not dramatically alter the entropy measurement or error rate necessary for a reasonable false reject rate.
+However, These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.
 We use the Daugman's parameters for our calculations.
@@
 \end{align*}
-Thus, if we were to use a fuzzy extractor that worked for all distributions with the same entropy and error characteristics no key is possible~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
-Although irises are believed to be the strongest biometric a fuzzy extractor can provide no security without using some additional property of the iris distribution.
+Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
+Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
 
@@
 
-A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting any point into the \rep algorithm.
+A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
 This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
@@
 \end{definition}
+For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
 \begin{lemma}
@@
 Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
 \end{lemma}
@@
 Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m\mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
+This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
 Consider the following distinguisher $D$:
@@
 \end{itemize}
-First note that $|D|$ is of size $\log |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n)$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
-\[
-\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} - \frac{1}{2^{-\kappa}} = 1/\poly(n).
+First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
+Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.
+Thus, when $\kappa = \omega(\log n)$:
+\[
+\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
 \]
@@
 \label{sec:conductors}
-Fuzzy extractors are known to have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
+Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
 Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
@@
 By Markov's inequality, there exists some set $B_{SS}$ such that $\Pr[ss\in B_{SS}] \geq 1/2$ and $\forall s\in B_{SS}$ one has $\Delta(X | SS = s, s ), (Y | SS = s, s)<2\epsilon$.
-Now applying Markov's inequality of $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.
+Now applying Markov's inequality to $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.
 Denote by $s^*$ a value in $B_{SS}\cap B_{SS'}$~(one value must exist).

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
Moved second cons proofs to appendix
Small edits to first three appendices

@@
 With $\Huse<0$ some restriction is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
-Instead of restricting the class of source distributions~(for which security is achieved), the definition could restrict the error model to errors that are ``likely'' to occur in the source.
+Instead of restricting the class of source distributions, the definition could restrict the correctable errors to errors that are ``likely'' to occur in the source.
 We leave this as an open problem.
@@
 Recall that $c$ contains at most $\ell$ $1$s.
-Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$.
+Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/|\mathcal{Z}|$.
 Since the $r_i$ are chosen independently, one has,
 \[
-\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{2^n}.
+\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{|\mathcal{Z}|}.
 \]
@@
 \begin{theorem}
-Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\mathcal{Z}^\ell$ for any $q = \poly(n)$.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$~(over $\mathcal{Z}^\ell$ where $|\mathcal{Z}| = \omega(\poly(n))$).
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
 \end{theorem}
@@
 \[
-\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(n)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
+\]
+When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
 %Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
@@
 \begin{proof}
-\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
+\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
 \begin{lemma}

### 2014-02-06 trunk/constantRate/ConstCompFuzzExt.tex
going through Section 5 and Appendix G

@@
 \label{sec:sampling}
-\consref{cons:first construction} is a computational fuzzy extractor with $\Huse<0$.
+\consref{cons:first construction} is a computational fuzzy extractor \lnote{conductor?} with $\Huse<0$.
 In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
-The main advantage of this approach is reduces the required entropy in each block of the source.
+\lnote{The previous sentence explains how we achieve something without explaining what we achieve or why it improve the prev section.
+We need to rework this paragraph.} The main advantage of this approach is reduces the required entropy in each block of the source.
 Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
@@
 
-\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) where blocks must have entropy conditioned on the value of previous blocks.
+\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), in which blocks must have entropy conditioned on the value of previous blocks.
 An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).
 An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.
-However, we achieve security for significantly lower entropy levels than for unguessable block distributions.
+\lnote{this comparison is unclear to me}  However, we achieve security for significantly lower entropy levels than for unguessable block distributions.
 
@@
 Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
+\lnote{I am not sure spelling out all the parameters in the construction is the right thing to do -- perhaps in the theorem statement is better?} \lnote{we should make a clean statement about what this is a construction of (conductor, not extractor); the parameter should all go there, and not be repeated throughout all the claims}
 \begin{construction}
@@
 Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
-Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta = \omega(\log n) = o(\gamma)$ and let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
+Let $\ell$ be such that $\ell = O(\poly(n))$ and $\ell = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
+Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$ and let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
 Define $\gen, \rep$ as:
@@
 \end{enumerate}
-\item Output $(c, p)$.
+\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
 \end{enumerate}
@@
 
+\lnote{the word sample is kind of overloaded}
+
 The main change in \consref{cons:sampling} is that the obfuscated values are concatenated blocks symbols of $W$.
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is the use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has individual entropy.
-In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.
+A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of $v_i$s.
+
 Our construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
@@
 
-As before we show security and correctness of \consref{cons:sampling}.
-For security, we argue that each of the $v_i$ is unguessable.
-For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability) so that $c'$ will be corrected to $c$ with overwhelming probability.
+We now show security and correctness of \consref{cons:sampling}.
+For security, we argue that each of the $v_i$ values is unguessable.
+For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability), so that $c'$ will be corrected to $c$ with overwhelming probability.
 
 \subsection{Security of \consref{cons:sampling}}
-In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $V_i$ has super-logarithmic entropy on its own~(samplers will select ``enough'' of the good blocks of $W$ each time).
+In order to show security \consref{cons:sampling}, we 
+show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
 We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
-Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.
+Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \thref{thm:security of cons}.
 We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
+Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
+be some particular outcome.
 
@@
 \label{lem:sampling works}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta = \omega(\log n) \le  o(\gamma)$.
-Consider some fixed $i$, there exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that
+Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta =  o(\gamma)$.
+There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
 \[
@@
 Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1-\Theta(1)))$-unordered block source.
-Let $\eta = \omega(\log n) = o(\gamma)$ and let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.
-Then $\Pr_{\lambda\leftarrow \Lambda}[\exists i, \Hoo(V_i | \Lambda = \lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
+Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta =  o(\gamma)$.
+Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.
+Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
 %[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
@@
 
-In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a unguessable block distribution~\clref{cl:all blocks entropy}.
-This allows us to conclude:
+In ~\clref{cl:all blocks entropy} we show that any distribution where each individual block has super-logarithmic min-entropy forms a unguessable block distribution.  This allows us to conclude:
 \begin{corollary}
 \label{cor:v are unguessable}
-Let $W, V, \Lambda$ be as in \corref{cor:samp sec}.
-Let $q = \poly(n)$, for $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$ the distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-unguessable block distribution.
+Let $W, V, \Lambda$ be as in \corref{cor:samp sec}, and
+let $q = \poly(n)$.
+For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$ the distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-unguessable block distribution.
 \end{corollary}
@@
 \label{cor:samp unguess}
-Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$, then for every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
+Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} \lnote{why as in \corref{cor:samp sec} and not in the construction?} and let $\mathcal{O}$ is an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}^\eta$, then for every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
 %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
@@
 Let $W = W_1,..., W_\ell$ be a source.
-Suppose that for all $i$, $\Hoo(W_i)\geq \alpha$, and that $q 2^{-\alpha}\leq1/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is superlogarithmic).
+Suppose that for all $i$, $\Hoo(W_i)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is superlogarithmic).
 Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block distribution.
@@
 \begin{proof}
-Consider some fixed $i$.  Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda$ be some particular outcome.
-For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee for all $\lambda$,
-\[
-\Hoo(V_i |\lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
-\]
-
-Denote by $X = |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|$.
+Consider some fixed $i$.
+For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ \lnote{the definition is stronger and requires a single $\mathcal{I}$ for all $w$} of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $\cal{I}$.
+Namely, Denote by $X |\{j_{i, 1},..., j_{i, \eta}\}\cap \mathcal{I}|$.
+\[
+\Hoo(V_i |\lambda ) \geq \alpha X.
+\]
+\lnote{this needs a proof}
+
 We now calculate $\expe[X]$.
-Let $j_1,.., j_\eta$ be the elements selected by sampling algorithm.
-The ``first'' element $j_1$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
-For each selected index $j_k$ there are least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}]>(\gamma-\beta-\eta)/\gamma$.
+The ``first'' element $j_{i,1}$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
+For each subsequent index $j_{i,k}$ there are at least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}\,|\,j_{i,1}\dots j_{i,k-1}]>(\gamma-\beta-\eta)/\gamma$.
 We can associate with each $j_k$ a Bernoulli random variable $X_k$ with success probability at least $(\gamma-\beta-\eta)/\gamma$ and note that
@@
 \]
-Using the Chernoff bound, $X$ rarely is far from its expected value:
+Using the Chernoff bound \lnote{Chernoff requires independence of $X_i$!}, $X$ rarely is far from its expected value:
 \[

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
Adding citations for hyper geometric

@@
 Our constructions are inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  
-\bnote{this whole paragraph needs work} Our two constructions are similar to spirit but optimize different parameters.
+\bnote{this whole paragraph needs work} Our two constructions are similar in spirit but optimize different parameters.
 The first requires individual blocks of the source to have super-logarithmic entropy and corrects a constant fraction of errors.
@@
 Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $\Huse>>0$ using a information-reconciliation component that hides all partial information.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} achieve a notion of noisy point obfuscation when $\Huse>>0$ using a information-reconciliation component that hides all partial information.
 Constructing noisy point obfuscation for all sources remains an open problem.

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
used hypergeometric tail bound in proof of Lemma 5.3

@@
 Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $\cal{I}$.
-Namely, Denote by $X |\{j_{i, 1},..., j_{i, \eta}\}\cap \mathcal{I}|$.
+Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap \mathcal{I}|$.
 \[
@@
 
-We now calculate $\expe[X]$.
-The ``first'' element $j_{i,1}$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
-For each subsequent index $j_{i,k}$ there are at least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}\,|\,j_{i,1}\dots j_{i,k-1}]>(\gamma-\beta-\eta)/\gamma$.
-We can associate with each $j_k$ a Bernoulli random variable $X_k$ with success probability at least $(\gamma-\beta-\eta)/\gamma$ and note that
-\[
-\expe[X] = \sum_{k=1}^\eta\expe[X_k] \geq \eta \expe[X_\eta]\geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
-\]
-Using the Chernoff bound \lnote{Chernoff requires independence of $X_i$!}, $X$ rarely is far from its expected value:
-\[
-\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
-\]
-Where the last equality follows because 
-\[
-\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
-\]
-That is \[
-\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \alpha'] \geq 1- O(e^{-\eta}).
+We note that $X$ is distributed according to the hypergeometric distribution,
+and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
+Using the tail bounds from~\cite{chvatal1979tail,skala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
+
+Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$, we conclude that 
+ \[
+\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
 \]

### 2014-02-06 trunk/constantRate/ConstCompFuzzExt.tex
Reordered section 4

@@
 \end{definition}
-A computational extractor is the adaption of a randomness extractor to the computational setting.  We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
+A computational extractor is the adaption of a randomness extractor to the computational setting.
+Any information-theoretic randomness extractor is also a computational extractor.
+We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
 \begin{definition}
@@
 
-\section{A Computational Fuzzy Extractor when $\Huse<0$}
+\section{A Computational Fuzzy Conductor when $\Huse<0$}
 \label{sec:construction}
@@
 \label{cons:first construction}
-Let $n$ be a security parameter, let $\mathcal{Z}$ be an alphabet with $|\mathcal{Z}| = \omega(\poly(n))$ and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $\mathcal{Z}$.
-Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
-$(\neigh_t, \delta_{code})$-error-correcting code.
+Let $n$ be a security parameter, let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $\mathcal{O}$ be an obfuscator for the family of point functions $\mathtt{I}_{\mathcal{Z}}$.
+Let  $C\subset \zo^\ell$ be an error-correcting code.
 We describe $\gen, \rep$ as follows:
@@
 The input $w$ is hidden in two different ways.  In locations where $c_i=1$ the block $w_i$ is information-theoretically unknown.
-In locations where $c_i=0$ it is hard to find $w_i$ given the point obfuscation.
-%As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
-
+In locations where $c_i=0$ it is hard to find $w_i$ given access to the point obfuscation.  
 There are two possible reasons for a bit $c_i'$ to be $1$.
 Because the true value was $1$ and because $w_i \neq w_i'$.
-However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
-This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
-
-\subsection{Security of Construction}
-\label{sec:sec of construction}
+However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when $c_i=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
+This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
+
 \consref{cons:first construction} is secure if no distinguisher can tell whether they are working with random obfuscations or obfuscations of $W_i$.
 By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-Our construction is secure as long as enough blocks are unpredictable after adaptive queries:
+More formally, our construction is secure as long as enough blocks are unpredictable after adaptive queries:
 
@@
 
-%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
-We discuss unguessable block distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for unguessable block distributions:
+We discuss unguessable block distributions in \apref{sec:characterize}.
+
 \begin{theorem}
-\label{thm:security of cons}
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}$. 
-Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+\label{thm:main thm first cons}
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_i$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+\end{theorem}
+\begin{proof}
+We argue security in~\lemref{lem:security of cons} and correctness in~\lemref{lem:correct of cons}.
+\end{proof}
+
+\begin{lemma}
+\label{lem:security of cons}
+Let $W, \mathcal{O}, C$ be as in \thref{thm:main thm first cons}.
 For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
-\end{theorem}
+\end{lemma}
 
 We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
+\begin{proof}[Outline]
 It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
@@
 \end{itemize}
-
-%The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
-%\begin{lemma}
-%\label{lem:no codeword high prob}
-%For all $c\in C|C_{\mathcal{I}^c}$,
-%\[
-%\expe_{View(S)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(S)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-(\alpha-1)}.
-%\]
-%\end{lemma}
-%\begin{proof}
-%We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that
-%\[
-%\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
-%\]
-%Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
-%Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that
-%\begin{align*}
-%\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-(\alpha-1)} \\
-%\end{align*}
-%This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-\alpha+1}$.
-Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.
-This is a contradiction and completes the proof.
-%\end{proof}
-%\begin{corollary}
-%\label{cor:avg min after view}
-%$\Hav(C| View(S))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\} -1= \min\{ |C| - |\mathcal{I}^c|, \alpha-1\} -1$.
-%\end{corollary}
-%\begin{proof}
-%%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).
-%Taking the negative log of \lemref{lem:no codeword high prob} one has:
-%\begin{align*}
-%\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
-% &= \\
-% -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-\alpha+1}) \\
-% &\geq \min \{-\log P_c, -\log 2^{-\alpha+1}\} -1\\
-% &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\}-1
-%\end{align*}
-%\end{proof}
-
-\subsection{Correctness of \consref{cons:first construction}}
-\label{sec:correct first cons}
+\end{proof}
+
+We now argue correctness of \consref{cons:first construction}. 
 We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.  
@@
 \label{lem:correct of cons}
-Let $C$ be a $(\neigh_t, \delta_{code})$-code.  When $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
+When $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
 \[
@@
 
-Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for unguessable block distributions:
-\begin{theorem}
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$~(over $\mathcal{Z}^\ell$ where $|\mathcal{Z}| = \omega(\poly(n))$).
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
-\end{theorem}
-\begin{proof}
-Security is a result of \thref{thm:security of cons}.  Correctness follows from \lemref{lem:correct of cons}.
-\end{proof}
-
-%\subsection{Supported Sources}
-%\label{sec:supported sources}
-%\bnote{need to complete this section and redo the proof in  \secref{sec:sec of construction} with this type of source.}
-%
-%We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.
-We need a distribution where after $q$-equality queries, a large number of blocks still have super-logarithmic entropy.
-%
-%As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the remaining arguments follow).
-
 \subsection{Discussion}
@@
 Correction occurs for a small number of dimensions that are allowed to vary completely.
-As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries.
+\consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries.
 
@@
 \label{sec:sampling}
-\consref{cons:first construction} is a computational fuzzy extractor \lnote{conductor?} with $\Huse<0$.
+\consref{cons:first construction} is a computational fuzzy conductor with $\Huse<0$.
 In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
@@
 We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
-Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \thref{thm:security of cons}.
+Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
 We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
@@
 \begin{proof}
-Result of \corref{cor:v are unguessable} and \thref{thm:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
+Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
 \end{proof}
@@
 
-\section{Proof of \thref{thm:security of cons}}
+\section{Proof of \lemref{lem:security of cons}}
 \label{app:security of main cons}
@@
 \end{align*}
-This is a contradiction and completes the proof of \thref{thm:security of cons}.
+This is a contradiction and completes the proof of \lemref{lem:security of cons}.
 \end{proof}
@@
 
-We now calculate $\expe[X]$.
-The ``first'' element $j_{i,1}$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.
-For each subsequent index $j_{i,k}$ there are at least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}\,|\,j_{i,1}\dots j_{i,k-1}]>(\gamma-\beta-\eta)/\gamma$.
-We can associate with each $j_k$ a Bernoulli random variable $X_k$ with success probability at least $(\gamma-\beta-\eta)/\gamma$ and note that
-\[
-\expe[X] = \sum_{k=1}^\eta\expe[X_k] \geq \eta \expe[X_\eta]\geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
-\]
-Using the Chernoff bound \lnote{Chernoff requires independence of $X_i$!}, $X$ rarely is far from its expected value:
-\[
-\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
-\]
-Where the last equality follows because 
-\[
-\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
-\]
-That is \[
-\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \alpha'] \geq 1- O(e^{-\eta}).
+We note that $X$ is distributed according to the hypergeometric distribution,
+and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
+Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
+
+Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$, we conclude that 
+ \[
+\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
 \]

### 2014-02-06 trunk/constantRate/ConstCompFuzzExt.tex
rearranged order of theorems/lemmas

@@
 Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
-Let $\ell$ be such that $\ell = O(\poly(n))$ and $\ell = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$ and let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
+Let $\ell = \omega(\log(n))$ and $\eta = o(\gamma)$ be integer parameters (we will set them later).
+Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
 Define $\gen, \rep$ as:
@@
 
-Our construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
+This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
 Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.
@@
 We now show security and correctness of \consref{cons:sampling}.
-For security, we argue that each of the $v_i$ values is unguessable.
+
+\begin{theorem}
+\label{thm:sampling}
+Let $n$ be a security parameter.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
+Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
+$\ell = \omega(\log n)$.
+Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
+\begin{align*}
+t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
+\tilde{m} &=|C|\\
+\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
+\end{align*}
+\end{theorem}
+
+The next two sections are dedicated to proving this theorem.
+
+ For security we argue that each of the $v_i$ values is unguessable.
 For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability), so that $c'$ will be corrected to $c$ with overwhelming probability.
@@
 \label{lem:sampling works}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta =  o(\gamma)$.
+Let all the variables be as in \thref{thm:sampling}.
 There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
@@
 \label{cor:samp sec}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1-\Theta(1)))$-unordered block source.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta =  o(\gamma)$.
-Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.
+ Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.
 Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
@@
 \label{cor:v are unguessable}
-Let $W, V, \Lambda$ be as in \corref{cor:samp sec}, and
-let $q = \poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$ the distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-unguessable block distribution.
+Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
+Take any $q=\poly(n)$.
+For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
 \end{corollary}
 
-Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a unguessable block distribution, \consref{cons:sampling} is \consref{cons:first construction} applied to $V_1,..., V_\ell$.
+Thus, unless the choice of $\lambda$ is very unlucky,
+\consref{cons:sampling} is \consref{cons:first construction} applied to $V_1,..., V_\ell$. This allows us to conclude the following.
 \begin{corollary}
 \label{cor:samp unguess}
-Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} \lnote{why as in \corref{cor:samp sec} and not in the construction?} and let $\mathcal{O}$ is an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}^\eta$, then for every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
+Let all the variables be as in \thref{thm:sampling}.
+For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
 %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
@@
 \label{sec:correct sampling}
-The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.
+The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.
 This probability is at most $\ell/\mathcal{Z}^\eta$.
-We now show that there are few enough $0\rightarrow 1$ flips with overwhelming probability.
-Let $t'$ be the capacity of $C$.
-We show $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.
+Recall that the code $C$ can correct up to $t'$ flips from $0$ to $1$.
+We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.
 The proof is in \apref{sec:sampling errors}.
@@
 \label{lem:sampling errors}
-Let $n, W$ be as above and Let $C$ be a code that corrects $t'$ $0\rightarrow 1$ bit errors where $t' =\Theta(\ell)$.
-Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, if $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
+Let all the variables be as in \thref{thm:sampling}.
+ Then $\Pr[v'\in\neigh_{t'}(v]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.
 %That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
@@
 \begin{corollary}
-Let $\eta= \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$ let $C\subset\zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
-\[
-\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
-\]
-and $(R, P)\leftarrow \gen(w)$, then
-\[
-\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
+Let all the variables be as in \thref{thm:sampling}.
+When
+\[
+\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
+\]
+and $(c, p)\leftarrow \gen(w)$, then
+\[
+\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
 \]
 That is, \consref{cons:sampling} is correct with overwhelming probability.
-
 \end{corollary}
-
-Combining the last two sections, we have that \consref{cons:sampling} is secure and correct:
-\begin{theorem}
-Let $n$ be a security parameter.
-Let $\mathcal{W}$ be the family of $(\alpha = \omega(1), \beta\leq \gamma(1/2-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
-Let $\eta = \omega(\log n) = o(\gamma)$ and $\ell = O(\poly(n)) = \omega(\log n)$.
-Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
-Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
-\begin{align*}
-t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
-\tilde{m} &=|C|\\
-\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
-\end{align*}
-\end{theorem}
 
@@
 \begin{proof}
-Let $t$ be as stated in the lemma.
-We first consider calculate $\expe[\dis(V, V')]$ and then show that the distance between $v$ and $v'$ is rarely much more than this value.
-Let $\mu = -\log(1-t'/(2\ell))/2$ then one has:
+Define $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$ and note that $t \leq \mu(\gamma - \eta)/\eta$.
+Let
+the Bernoulli random variable $X_i=1$ if and only if $v_i \neq v_i'$, and $X=\sum_{i=1}^{\ell} X_i$. We need to show that $\Pr[X>t']=O(2^{-\ell})$.
+
 \begin{align*}
-\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
+\expe [1-X_i] &=\Pr[w \text{ and } w' \text{ agree on positions } {j_{i,1}},..., j_{i,\eta}]\\
+&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
 &\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
 & = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}

### 2014-02-06 trunk/constantRate/ConstCompFuzzExt.tex
make some notes on the intro

@@
 \section{Introduction}\label{sec:introduction}
+\lnote{What I want to do with this: make it clear that we are not the crazy obfuscation types, but are using something practically achievable; perhaps mention RO; perhaps compare with Dodis' RO analysis (was that for robustness only?); explain that we have two points on an entropy/error tolerance tradeoff; explain how switching to computational makes our construction possible and, in general, why our construction is cool.
+Section titles for 4 and 5!}
 Reliable key derivation is a cornerstone of authentication.
@@
 Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
-\lnote{I am not sure spelling out all the parameters in the construction is the right thing to do -- perhaps in the theorem statement is better?} \lnote{we should make a clean statement about what this is a construction of (conductor, not extractor); the parameter should all go there, and not be repeated throughout all the claims}
+
 \begin{construction}
@@
 Consider some fixed $i$.
-For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ \lnote{the definition is stronger and requires a single $\mathcal{I}$ for all $w$} of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Recall that there a set $\mathcal{I}$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in \mathcal{I}$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
 Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $\cal{I}$.
@@
 \begin{proof}
-Define $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$ and note that $t \leq \mu(\gamma - \eta)/\eta$.
+Define $\mu = -\frac{1}{2}\log(1-t'/(2\ell)) = \Theta(1)$ and note that $t \leq \mu(\gamma - \eta)/\eta$. Since $\eta = \omega(\log n)$, we will assume
+$\eta\ge 2\mu$.
 Let
@@
 &\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
-& = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\left(\frac{1}{2}\right)^2\right)^\mu\\
+& = \left(\frac{1}{2}\right)^{-\log\left(1-\frac{t'}{2\ell}\right)} = 1-\frac{t'}{2\ell}\,.
 \end{align*}
 
-With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq  t'/(2\ell)$. By the Chernoff bound, we have
+Hence, $\expe[X_i]\le t'/(2\ell) = O(1)$, and $\expe[X]\le t'/2$.
+By the Chernoff bound, we have \lnote{this can be tightened}
 \begin{align*}
-\Pr\left[\frac{1}{\ell} \sum_{i=1}^\ell X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\ell} = O(e^{- \ell}).
+\Pr\left[\sum_{i=1}^\ell X_i\geq t'\right]\leq 2e^{-2(t'-\expe[X])^2\ell} \le
+2e^{-2(t'/2)^2\ell} = O(e^{- \ell})\,.
 \end{align*}
-Where the last equality holds because $t'/(2\ell) = \Theta(1)$.
 \end{proof}

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
adding claim on block source entropy

@@
 
-%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
-We discuss unguessable block distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for unguessable block distributions:
+We discuss unguessable block distributions in \apref{sec:characterize}.
+
 \begin{theorem}
-\label{thm:security of cons}
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}$. 
-Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+\label{thm:main thm first cons}
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_i$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+\end{theorem}
+\begin{proof}
+We argue security in~\lemref{lem:security of cons} and correctness in~\lemref{lem:correct of cons}.
+\end{proof}
+
+\begin{lemma}
+\label{lem:security of cons}
+Let all variables be as in \thref{thm:main thm first cons}.
 For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
-\end{theorem}
+\end{lemma}
 
 We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
+\begin{proof}[Outline]
 It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
@@
 \label{lem:no 1 to 0 flips}
+Let all variables be as in \thref{thm:main thm first cons}.  
 The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
@@
 \label{lem:correct of cons}
-Let $C$ be a $(\neigh_t, \delta_{code})$-code.  When $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
+Let all variables be as in \thref{thm:main thm first cons}.  
+For $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
 \[
@@
 \section{Sample-then-Obfuscate}
+\bnote{Reducing required entropy as title?}
 \label{sec:sampling}
-\consref{cons:first construction} is a computational fuzzy extractor \lnote{conductor?} with $\Huse<0$.
-In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
-\lnote{The previous sentence explains how we achieve something without explaining what we achieve or why it improve the prev section.
-We need to rework this paragraph.} The main advantage of this approach is reduces the required entropy in each block of the source.
+\bnote{Leo didn't like this linking.  How about now?}
+\consref{cons:first construction} is a computational fuzzy conductor with $\Huse<0$.
+Unfortunately, \consref{cons:first construction} required most blocks of $W$ to have super-logarithmic min-entropy.
+This may be an unreasonable requirement.
+In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously.
+%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler). 
 Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
-Thus, we have a tradeoff between individually required entropy and supported error tolerance.
-In ordering for sampling to work properly, we need a source where a constant fraction of blocks are likely to contribute some entropy.
+Thus, we have a tradeoff between entropy and error tolerance.
+The main idea is to sample a random subset of blocks $W_{i_1},..., W_{i_\eta}$ and obfuscate the concatenation of these blocks.
+Denote this concatenated value by $V_1$.
+This process is repeated to produce $V_1,..., V_\ell$ and the construction proceeds by either obfuscating $V_i$ or a random point as before.
+For security each value $V_i$ needs to be unguessable.
+This will hold as long as enough blocks we sample contribute some entropy:
 
@@
 Let $n$ be a security parameter.
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
-Let $\ell$ be such that $\ell = O(\poly(n))$ and $\ell = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$ and let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$.
+%and $\gamma = \Omega(n)$.
+Let $\ell = \omega(\log(n))$ and $\eta = o(\gamma)$ be integer parameters (we will set them later).
+Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
+Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions over $\mathtt{I}_{\mathcal{Z}^\eta}$.
 Define $\gen, \rep$ as:
@@
 \item \underline{Input}: $w = w_1,..., w_\gamma$
-\item Sample $c\leftarrow C$.
+\item Select $c\overset{\$}\leftarrow C$.
 \item For $i=1,..., \ell$:
 \begin{enumerate}[(i)]
-\item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
+\item Select $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
 \item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
@@
 \subitem Set $p_i = \rho_i, \lambda_i$.
-\item If $c_i = 1$: Sample $r_i \overset{\$}\leftarrow \mathcal{Z}^{\eta}$.
+\item If $c_i = 1$: Select $r_i \overset{\$}\leftarrow \mathcal{Z}^{\eta}$.
 \subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
@@
 
-\lnote{the word sample is kind of overloaded}
-
-The main change in \consref{cons:sampling} is that the obfuscated values are concatenated blocks symbols of $W$.
+The main change in \consref{cons:sampling} is that the obfuscated values are concatenated symbols of $W$.
 This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of $v_i$s.
-
-Our construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
-Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.
-
-We now show security and correctness of \consref{cons:sampling}.
-For security, we argue that each of the $v_i$ values is unguessable.
+A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of $v_i$s.
+
+This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
+Goldreich provides an introduction to samplers in~\cite{goldreich1997sample}.
+
+\begin{theorem}
+\label{thm:sampling}
+Let $n$ be a security parameter.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
+Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
+$\ell = \omega(\log n)$.
+Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
+\begin{align*}
+t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
+\tilde{m} &=|C|\\
+\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
+\end{align*}
+\end{theorem}
+
+The next two sections are dedicated to proving this theorem.
+ For security we argue that each of the $v_i$ values is unguessable.
 For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability), so that $c'$ will be corrected to $c$ with overwhelming probability.
@@
 \label{lem:sampling works}
-Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta =  o(\gamma)$.
+Let all variables be as in \thref{thm:sampling}.
 There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
@@
 \label{cor:v are unguessable}
-Let $W, V, \Lambda$ be as in \corref{cor:samp sec}, and
-let $q = \poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$ the distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-unguessable block distribution.
+Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
+Take any $q=\poly(n)$.
+For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
 \end{corollary}
 
-Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a unguessable block distribution, \consref{cons:sampling} is \consref{cons:first construction} applied to $V_1,..., V_\ell$.
+Thus, unless the choice of $\lambda$ is very unlucky,
+\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. This allows us to conclude the following.
 \begin{corollary}
 \label{cor:samp unguess}
-Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} \lnote{why as in \corref{cor:samp sec} and not in the construction?} and let $\mathcal{O}$ is an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}^\eta$, then for every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
+Let all the variables be as in \thref{thm:sampling}.
+For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
 %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
@@
 \label{sec:correct sampling}
-The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.
+The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.
 This probability is at most $\ell/\mathcal{Z}^\eta$.
-We now show that there are few enough $0\rightarrow 1$ flips with overwhelming probability.
-Let $t'$ be the capacity of $C$.
-We show $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.
+Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$.
+We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.
 The proof is in \apref{sec:sampling errors}.
@@
 Consider some fixed $i$.
-For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ \lnote{the definition is stronger and requires a single $\mathcal{I}$ for all $w$} of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Recall that there a set $\mathcal{I}$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in \mathcal{I}$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
 Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $\cal{I}$.
 Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap \mathcal{I}|$.
+
+\begin{claim}
 \[
@@
 \]
-\lnote{this needs a proof}
+\end{claim}
+\begin{proof}
+We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda]$.  Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.  Then 
+\begin{align*}
+\max_{v\in V_i}\Pr[V_i = v | \Lambda = \lambda ]&= \max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]\\
+%&=\max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_\eta} = w_{j_\eta} | W_{j_{\eta-1}} =w _{j_{\eta-1}} \wedge ... \wedge W_{j_1} =w_{j_1}]\\
+%&\times \Pr[W_{j_{\eta-1}} = w_{j_{\eta-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
+\end{align*}
+Taking the negative logarithm of both sides we have that 
+\begin{align*}
+\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
+&\ge \sum_{j_k\in \mathcal{I}} \alpha = \alpha X
+\end{align*}
+\end{proof}
 
@@
 and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
-Using the tail bounds from~\cite{chvatal1979tail,skala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
+Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
 
@@
 \begin{proof}
-Let $t$ be as stated in the lemma.
-We first consider calculate $\expe[\dis(V, V')]$ and then show that the distance between $v$ and $v'$ is rarely much more than this value.
-Let $\mu = -\log(1-t'/(2\ell))/2$ then one has:
+Define $\mu = -\frac{1}{2}\log(1-t'/(2\ell)) = \Theta(1)$ and note that $t \leq \mu(\gamma - \eta)/\eta$. Since $\eta = \omega(\log n)$, we will assume
+$\eta\ge 2\mu$.
+Let
+the Bernoulli random variable $X_i=1$ if and only if $v_i \neq v_i'$, and $X=\sum_{i=1}^{\ell} X_i$. We need to show that $\Pr[X>t']=O(2^{-\ell})$.
+
 \begin{align*}
-\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
+\expe [1-X_i] &=\Pr[w \text{ and } w' \text{ agree on positions } {j_{i,1}},..., j_{i,\eta}]\\
+&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
 &\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
-& = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\left(\frac{1}{2}\right)^2\right)^\mu\\
+& = \left(\frac{1}{2}\right)^{-\log\left(1-\frac{t'}{2\ell}\right)} = 1-\frac{t'}{2\ell}\,.
 \end{align*}
 
-With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq  t'/(2\ell)$. By the Chernoff bound, we have
+Hence, $\expe[X_i]\le t'/(2\ell) = O(1)$, and $\expe[X]\le t'/2$.
+By the Chernoff bound, we have \lnote{this can be tightened}
 \begin{align*}
-\Pr\left[\frac{1}{\ell} \sum_{i=1}^\ell X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\ell} = O(e^{- \ell}).
+\Pr\left[\sum_{i=1}^\ell X_i\geq t'\right]\leq 2e^{-2(t'-\expe[X])^2\ell} \le
+2e^{-2(t'/2)^2\ell} = O(e^{- \ell})\,.
 \end{align*}
-Where the last equality holds because $t'/(2\ell) = \Theta(1)$.
 \end{proof}

### 2014-02-07 trunk/constantRate/ConstCompFuzzExt.tex
Small edits

@@
 
-We discuss unguessable block distributions in \apref{sec:characterize}.
+We discuss unguessable block distributions in \apref{sec:characterize}.  \bnote{there should be probably be something here.  block-sources?}
 
@@
 \label{lem:security of cons}
-Let $W, \mathcal{O}, C$ be as in \thref{thm:main thm first cons}.
+Let all variables be as in \thref{thm:main thm first cons}.
 For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
@@
 \end{proof}
-
 We now argue correctness of \consref{cons:first construction}. 
@@
 \label{lem:correct of cons}
-When $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
+Let all variables be as in \thref{thm:main thm first cons}.  
+For $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
 \[
@@
 This requires a code where most codewords have Hamming weight close to $1/2$.
-
-%\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
-%We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
-Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
-We break the indices of $c = c_1,..., c_\ell$ into two components those where $c_i=1$ and those $c_i = 0$.
-Denote these two components by $c_{I_1}$ and $c_{I_0}$.
-Our goal is to bound how many of the places where $w, w'$ are inserted into $c_{I_0}$.
-Indices $i$,  where $w_i \neq w_i'$ and $c_i = 1$ will be ``corrected'' as $w_i'$ yield $c_i' = 1$ with overwhelming probably~(see \lemref{lem:no 1 to 0 flips}).
-Since $w_{err}$ be set of indices where $w, w'$ differ then for all $j\in w_{err}, \Pr[j\in c_{I_0}] = 1/2$.
-This is a binomial distribution with $p=1/2$ and $n=t$.
-Denote by $X =|\{j | w_j \neq w_j' \wedge j\in c_{I_1}|$.
-Thus, $\expe[X] = t/2$.
-Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
-%\begin{align*}
-%\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
-%\end{align*}
-%This leads us to the following lemma:
-%\begin{lemma}
-%\label{lem:correctness holds}
-%If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
-%\end{lemma}
-%\bnote{This analysis is done assuming that the two sets are the same size.
-Need to worry about variation in the number of $1$s and $0$s in $c$.
-Need to show that for most codes (linear?) the variance in Hamming weight is small.}
-%\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
 
@@
 \section{Sample-then-Obfuscate}
+\bnote{Reducing required entropy as title?}
 \label{sec:sampling}
+\bnote{Leo didn't like this linking.  Better?}
 \consref{cons:first construction} is a computational fuzzy conductor with $\Huse<0$.
-In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
-\lnote{The previous sentence explains how we achieve something without explaining what we achieve or why it improve the prev section.
-We need to rework this paragraph.} The main advantage of this approach is reduces the required entropy in each block of the source.
+Unfortunately, \consref{cons:first construction} required most blocks of $W$ to have super-logarithmic min-entropy.
+This may be an unreasonable requirement.
+In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously.
+%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler). 
 Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
-Thus, we have a tradeoff between individually required entropy and supported error tolerance.
-In ordering for sampling to work properly, we need a source where a constant fraction of blocks are likely to contribute some entropy.
+Thus, we have a tradeoff between entropy and error tolerance.
+The main idea is to sample a random subset of blocks $W_{i_1},..., W_{i_\eta}$ and obfuscate the concatenation of these blocks.
+Denote this concatenated value by $V_1$.
+This process is repeated to produce $V_1,..., V_\ell$ and the construction proceeds by either obfuscating $V_i$ or a random point as before.
+For security each value $V_i$ needs to be unguessable.
+This will hold as long as enough blocks we sample contribute some entropy:
 
@@
 Let $n$ be a security parameter.
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$.
+%and $\gamma = \Omega(n)$.
 Let $\ell = \omega(\log(n))$ and $\eta = o(\gamma)$ be integer parameters (we will set them later).
 Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.
+Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions over $\mathtt{I}_{\mathcal{Z}^\eta}$.
 Define $\gen, \rep$ as:
@@
 
-\lnote{the word sample is kind of overloaded}
-
-The main change in \consref{cons:sampling} is that the obfuscated values are concatenated blocks symbols of $W$.
+The main change in \consref{cons:sampling} is that the obfuscated values are concatenated symbols of $W$.
 This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of $v_i$s.
+A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of $v_i$s.
 
 This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
-Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.
-
-We now show security and correctness of \consref{cons:sampling}.
+Goldreich provides an introduction to samplers in~\cite{goldreich1997sample}.
 
@@
 The next two sections are dedicated to proving this theorem.
-
  For security we argue that each of the $v_i$ values is unguessable.
@@
 
-%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
+\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
 \begin{lemma}
 \label{lem:sampling works}
-Let all the variables be as in \thref{thm:sampling}.
+Let all variables be as in \thref{thm:sampling}.
 There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
@@
 \end{lemma}
-%
-%\begin{lemma}
-%
-%Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.
-Let $\eta = \Omega(\log n)$.
-Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
-%\end{lemma}
-%\begin{proof}
-%By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.
-\bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.
-too much for a reader to digest.}
-%\end{proof}
 
@@
 Thus, unless the choice of $\lambda$ is very unlucky,
-\consref{cons:sampling} is \consref{cons:first construction} applied to $V_1,..., V_\ell$. This allows us to conclude the following.
+\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. This allows us to conclude the following.
 \begin{corollary}
@@
 This probability is at most $\ell/\mathcal{Z}^\eta$.
-Recall that the code $C$ can correct up to $t'$ flips from $0$ to $1$.
+Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$.
 We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.
@@
 Let all the variables be as in \thref{thm:sampling}.
- Then $\Pr[v'\in\neigh_{t'}(v]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.
+ Then $\Pr[v'\in\neigh_{t'}(v)]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.
 %That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
@@
 \end{align*}
-That is, \consref{cons:sampling} achieves $\Huse<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.
+That is, \consref{cons:sampling} achieves $\Huse<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
 If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
@@
 \begin{proof}
-Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})$.
+Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.
 Consider a query $q_j$ on block $i$.
@@
 By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
+Recall that $c^*, c'$ match on all indices outside of $\mathcal{I}$.
+Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
 This concludes the proof of \lemref{lem:codewords in I close}
@@
 Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap \mathcal{I}|$.
-\[
-\Hoo(V_i |\lambda ) \geq \alpha X.
-\]
-\lnote{this needs a proof}
+
+\begin{claim}
+\[
+\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
+\]
+\end{claim}
+\begin{proof}
+We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda]$.  Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.  Then 
+\begin{align*}
+\max_{v\in V_i}\Pr[V_i = v | \Lambda = \lambda ]&= \max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]\\
+%&=\max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_\eta} = w_{j_\eta} | W_{j_{\eta-1}} =w _{j_{\eta-1}} \wedge ... \wedge W_{j_1} =w_{j_1}]\\
+%&\times \Pr[W_{j_{\eta-1}} = w_{j_{\eta-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
+\end{align*}
+Taking the negative logarithm of both sides we have that 
+\begin{align*}
+\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
+&\ge \sum_{j_k\in \mathcal{I}} \alpha = \alpha X
+\end{align*}
+\end{proof}
 

### 2014-02-07 trunk/constantRate/ConstCompFuzzExt.tex
Partial block source

@@
 For security each value $V_i$ needs to be unguessable.
-This will hold as long as enough blocks we sample contribute some entropy:
+This will hold as long as enough blocks contribute some entropy:
 
 \begin{definition}
-\label{def:unordered source}
-A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}, W_{i+1}=w_{i+1},..., W_\gamma = w_\gamma) \geq \alpha.
+\label{def:partial source}
+A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}) \geq \alpha.
 \]
@@
 
-\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), in which blocks must have entropy conditioned on the value of previous blocks.
-An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).
-An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.
+\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) as only some blocks are required to have entropy conditioned on the past.
+The need for remaining entropy conditioned on the past is arbitrary.
+The precise requirement is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
+Note a partial block source requires worst case entropy while an unguessable block distribution only requires average conditional entropy.
 \lnote{this comparison is unclear to me}  However, we achieve security for significantly lower entropy levels than for unguessable block distributions.
@@
 Let $n$ be a security parameter.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
 Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
@@
 \subsection{Discussion of \consref{cons:sampling}}
-We now show \consref{cons:sampling} can work for unordered block sources when $\Huse<0$.
-The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
+We now show \consref{cons:sampling} can work for partial block sources when $\Huse<0$.
+The required entropy of  an partial block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
 We are able to correct $O(\gamma/\eta)$ errors.
@@
 The other is that there $t+\omega(\log n)$ blocks that contribute some entropy~(there is a continuum between these two types).
-Definitions~\ref{def:block guessable} and~\ref{def:unordered source} were developed for these types of sources respectively.
+Definitions~\ref{def:block guessable} and~\ref{def:partial source} were developed for these types of sources respectively.
 However, we do not achieve security when $\Hfuzz(W)= \omega(\log n)$ for either definition, this is an open problem.
@@
 \begin{claim}
+\label{cl:vi have entropy}
 \[
@@
 \begin{proof}
-We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda]$.  Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.  Then 
-\begin{align*}
-\max_{v\in V_i}\Pr[V_i = v | \Lambda = \lambda ]&= \max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]\\
-%&=\max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_\eta} = w_{j_\eta} | W_{j_{\eta-1}} =w _{j_{\eta-1}} \wedge ... \wedge W_{j_1} =w_{j_1}]\\
-%&\times \Pr[W_{j_{\eta-1}} = w_{j_{\eta-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
+We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
+Then
+\begin{align*}
+\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
 &= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
@@
 \end{align*}
+This completes the proof of \clref{cl:vi have entropy}.
 \end{proof}
@@
 
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$, we conclude that 
+Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that 
  \[

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
adding claim on block source entropy
Consistency of equality oracle notation

@@
 Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
-We need a strong version of point obfuscation secure under composition, this is achievable under a particular number-theoretic assumption~\cite{bitansky2010strong}.
+We need a strong version of point obfuscation secure under composition, this is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.%, DBLP:conf/innovations/GoldwasserKPV10}.
 Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
@@
 \label{def:block guessable}
-Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
+Let $I_w = (I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(\cdot, \cdot)$ be an oracle that returns \[(I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(i, w_i')=
 \begin{cases}
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
-\[
-\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $I$ making at most $q$ queries
+\[
+\forall i\in \mathcal{I}, \Hav(W_i |View(A^{I_{W}(\cdot, \cdot)}))\geq \alpha.
 \]
@@
 
-%\bnote{even if all $t$ are inserted into the bad block its okay right now.  My goal is to decrease the error tolerance of the code below $t$.}
-%We now turn to the question of how many $0\rightarrow 1$ bits flips occur between $c, c'$.
-Recall that $\dis(w, w')\leq t$ furthermore recall that $w, w'$ are selected independently of the fuzzy extractor, in particular, independently of $c$.
-We break the indices of $c = c_1,..., c_\ell$ into two components those where $c_i=1$ and those $c_i = 0$.
-Denote these two components by $c_{I_1}$ and $c_{I_0}$.
-Our goal is to bound how many of the places where $w, w'$ are inserted into $c_{I_0}$.
-Indices $i$,  where $w_i \neq w_i'$ and $c_i = 1$ will be ``corrected'' as $w_i'$ yield $c_i' = 1$ with overwhelming probably~(see \lemref{lem:no 1 to 0 flips}).
-Since $w_{err}$ be set of indices where $w, w'$ differ then for all $j\in w_{err}, \Pr[j\in c_{I_0}] = 1/2$.
-This is a binomial distribution with $p=1/2$ and $n=t$.
-Denote by $X =|\{j | w_j \neq w_j' \wedge j\in c_{I_1}|$.
-Thus, $\expe[X] = t/2$.
-Using Hoeffding's inequality~\cite{hoeffding1963probability}, one has that
-%\begin{align*}
-%\Pr[X\leq t(1/2+\alpha)] \leq 1-e^{-2\alpha^2 t}
-%\end{align*}
-%This leads us to the following lemma:
-%\begin{lemma}
-%\label{lem:correctness holds}
-%If $t = \omega(\log n)$ and that $\dis(w, w')\leq t$ then for any constant $\alpha>0$, then $\Pr[\dis(c, c')\geq t(1/2+\alpha)] \leq 1-e^{-2\alpha t} = 1-\ngl(n)$.
-%\end{lemma}
-%\bnote{This analysis is done assuming that the two sets are the same size.
-Need to worry about variation in the number of $1$s and $0$s in $c$.
-Need to show that for most codes (linear?) the variance in Hamming weight is small.}
-%\textbf{Note:} If $t = O(\log n)$ the only error tolerance for $C$ that results in decoding with overwhelming probability is $t$.  However, in most use cases, we expect $t=\omega(\log n)$.
-
 \subsection{Discussion}
@@
 \label{sec:sampling}
-\bnote{Leo didn't like this linking.  How about now?}
+\bnote{Leo didn't like this linking.  Better?}
 \consref{cons:first construction} is a computational fuzzy conductor with $\Huse<0$.
@@
 
-%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
+\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
 \begin{lemma}
@@
 Thus, we begin with the case of independent blocks.
-In all of the examples that follow we denote the adversary by $S$ as we need security against the computationally unbounded adversary defined in VGB obfuscation~(\defref{def:obf}).
+In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).
 
@@
 \begin{proof}
-It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
+It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
 We can ignore queries for all blocks but the $i$th, as the blocks are independent.
@@
 \begin{proof}
-Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})$.
+Since $f$ is injective on each block, $\Hav(W_i | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
 Consider a query $q_j$ on block $i$.
@@
 proof of \clref{cl:independent high ent}),
- and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
+ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(S^{I_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
 \end{proof}
@@
 Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
-There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
 \end{claim}
 \begin{proof}
-We present an adversary $A$~(running in polynomial time) that completely determines the value $x$.
-$A$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
-Then $A$ queries on $y_1,..., y_p$ exactly one answer returns $1$.
+We present an adversary $S$~(running in polynomial time) that completely determines the value $x$.
+$S$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
+Then $S$ queries on $y_1,..., y_p$, exactly one answer returns $1$.
 Let this value be $y_1^*$ and its preimage $x_1^*$.
-Then $A$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.
+Then $S$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.
 Again, exactly one of these queries returns $1$.
@@
 The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
-Once $x$ has been recovered then $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
+Once $x$ has been recovered then $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
 \end{proof}
@@
 \label{eq:dist before}
-|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \label{lem:sim cannot distinguish}
-$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
+$\Delta(S^{I_X(\cdot, \cdot)}(C), S^{I_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
 \end{lemma}
@@
 \[
-\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
+\Delta( S^{I_X(\cdot, \cdot)}(c^*), S^{I_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
 \]
@@
 By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
-Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
+Recall that $c^*, c'$ match on all indices outside of $\mathcal{I}$.
+Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
 This concludes the proof of \lemref{lem:codewords in I close}
 \end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
+By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C), S^{I_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
 This completes the proof of \lemref{lem:sim cannot distinguish}.
@@
 \label{eq:dist after}
-|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C')] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \begin{align*}
-\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
-&+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\
-&+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
+\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C)]| \\
+&+|\expe[S^{I_X(\cdot, \cdot)}(C)] - \expe[S^{I_X(\cdot, \cdot)}(C')] |\\
+&+|\expe [S^{I_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
 &\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
@@
 \begin{claim}
-\[
-\Hoo(V_i |\lambda ) \geq \alpha X.
+\label{cl:vi have entropy}
+\[
+\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
 \]
@@
 
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$, we conclude that 
+\bnote{this can also be tightened.}
+Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that 
  \[

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
Consistency of equality oracle notation

@@
 
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\zo^n$.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.
 Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
@@
 \label{eq:dist before}
-|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \label{lem:sim cannot distinguish}
-$\Delta(S^{I_X(\cdot, \cdot)}(C), S^{I_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
+$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
 \end{lemma}
@@
 \[
-\Delta( S^{I_X(\cdot, \cdot)}(c^*), S^{I_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
+\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
 \]
@@
 \end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C), S^{I_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
+By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.
 This completes the proof of \lemref{lem:sim cannot distinguish}.
@@
 \label{eq:dist after}
-|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C')] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \begin{align*}
-\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C)]| \\
-&+|\expe[S^{I_X(\cdot, \cdot)}(C)] - \expe[S^{I_X(\cdot, \cdot)}(C')] |\\
-&+|\expe [S^{I_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
+\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})]| \\
+&+|\expe[S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] - \expe[S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\\
+&+|\expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] - \expe [D(P_1,..., P_\ell, C') ]|\\
 &\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\

### 2014-02-07 trunk/constantRate/ConstCompFuzzExt.tex
working on the intro

@@
 \newcommand{\M}{\mathcal{M}}
+\newcommand{\Vol}{\mathsf{Vol}}
 
@@
 Section titles for 4 and 5!}
-Reliable key derivation is a cornerstone of authentication.
-However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).
-\bnote{add more examples here} To use noisy physical sources in applications, two problems must be addressed.
-The first is ensuring the same value is obtained from every reading of the source.
-This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).
-The second is converting the entropic source to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).
-Both of these problems have interactive and non-interactive versions.
-For a single user trying to produce the same key from multiple readings of a physical source non-interactive solutions are needed.
-We focus on this setting.
-%If both of these tasks are achieved a noisy physical source can be used like a uniformly random private key.
-
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} perform both tasks non-interactively.
-They consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.
+
+\paragraph{Fuzzy Extractors}
+Cryptography relies on secrets for that are read multiple times for key derivation and authentication.
+However, many sources with sufficient secrecy  provide similar but not identical values at each reading~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
+physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical}, 
+and quantum information~\cite{bennett1988privacy}).
+Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
+Both of these problems have interactive and noninteractive versions.
+In this paper, we are interested the noninteractive case, which can be used, in particular, by  a single user trying to produce the same key from multiple readings of a physical source at different times.
+The primitive accomplishing information reconciliation and privacy amplification noninteractively is known as a \emph{fuzzy extractor}; it is defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}
+
+Fuzzy extractors consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.
 The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-Traditionally, a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} performs information-reconciliation and a randomness extractor~\cite{nisan1993randomness} performs privacy amplification.
-
-Fuzzy extractors have not yielded key derivation for all noisy sources.
-There is tension between security and error-tolerance.
-The key should be uniform to an observer but nearby $w'$ should map to the same key.
-By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.
-In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.
-This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
-The length of the key $r$ is dictated by size of the best code that corrects $t$ errors.
-Error-correcting codes are well studied and we have tight bounds on this quantity.
-% how many codewords may be in a code that corrects $t$ errors.
-
-We consider the Hamming metric.
-For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected~(and we have constructions of fuzzy extractors that nearly meet this bound).
-For the remainder of this paper we call this difference the minimum usable entropy, denoted $\Huse$.
-This represents a practical problem as important biometrics have $\Huse<0$~(see \apref{sec:iris no key}).
-
- %let $|B_t|$ be the number of points within distance $t$.
-The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
-For the remainder of this paper, we denote this quantity by $\Huse = \Hoo(W) - \log |B_t|$.
-
-To achieve security when $\Huse<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
-However, the tools for constructing information-theoretic fuzzy extractors have not yielded natural restrictions.
-Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
-Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-A computational fuzzy extractor may exist for a larger class of distributions with $\Huse<0$ than is possible information-theoretically.
-
-In this work, we construct computational fuzzy extractors when $\Huse<0$ for large classes of distributions.
-In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse<0$.
-
-Fuller, Meng, and Reyzin show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.
-This is known as a fuzzy conductor~(the entropy is ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
-Here, we follow the second approach and use a \emph{computational} fuzzy conductor.
-We present two constructions of computational fuzzy conductors for different types of source distributions $W$.
+The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ has sufficient min-entropy $m$.
+The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on strings over some alphabet $\mathcal{Z}$ of length $\ell$).
+
+\paragraph{Limitations of Entropy-Based Approaches}
+Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
+The reason for this tension is quite simple: the adversary who knows $p$ and can guess some $w'$ within distance $t$ of $w$ will be able to easily distinguish $r$ from uniform by running $\rep$ and finding out what $r$ is.
+If $t$ is higher, then $\rep$ tolerates more $w'$ values, so the adversary's job is easier.
+In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then the \emph{entire distribution} of $w$ may have min-entropy $m$ and yet be contained in a single ball, in which case the adversary can simply use the center of the ball as $w'$.
+
+More generally, let $B_t$ denote the number of points in a ball of radius $t$.
+For any $m$ and $t$, one can come up with a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of all points in several nonoverlapping balls of radius $t$ (we need the space to be sufficiently large for the balls to fit).
+We thus call $m-\log B_t$ the \emph{usable} entropy, denoted by $\Huse$.
+The previous paragraph shows that  no fuzzy extractor can handle $\Huse\le 0$ as long as we require it work for \emph{all} distributions of a given min-entropy.
+
+However, some of the distributions with $\Huse\le 0$ are prime candidates use in authentication. \lnote{examples here}. No current fuzzy extractor construction is known to work for them.
+
+\paragraph{Our Contributions}
+We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse<0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
+As already explained above, such constructions cannot work without some restrictions on the distribution.
+The first construction works when every single symbol of $w$ has individual superlogarithmic min-entropy (thus requiring a large alphabet), but allows for arbitrary dependence between symbols (the actual condition is more general and may permit some symbols to have less entropy; see \defref{def:block guessable}).
+
+We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
+However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $O(\ell/\log\ell)$ errors.\lnote{check}.
+
+\paragraph{Our Approach}
+Our constructions are computationally secure.
+Indeed, known techniques for proving information-theoretically secure fuzzy extractors work for all distributions of a given entropy, and thus cannot be used to prove security for some distributions of with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.)
+
+Most known constructions of fuzzy extractors put sufficient information in $p$ to recover $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
+Fuller, Meng, and Reyzin~\cite{fuller2013computational}, in introducing computational fuzzy extractors, show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.
+We take the second approach.
+
+The procedure that takes a high-entropy input to get a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
+Since in our case, the resulting entropy is computational, we define and show two constructions of \emph{computational fuzzy conductors}.
 These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
 
-Both of constructions are based on the obfuscation of point programs.
+Both constructions are based on the obfuscation of point programs~\cite{canetti1997towards}.
 A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
@@
 For a point program, this means hiding all partial information about the point $w$.
-Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
-We need a strong version of point obfuscation secure under composition, this is achievable under a particular number-theoretic assumption~\cite{bitansky2010strong}.
+We need a strong version of point obfuscation, which is secure under composition.  
+However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation.
+In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}; it is may also be reasonable to assume that a cryptographic hash function, such as SHA-2, is a good point obfuscator.
+\lnote{cite anything?} \lnote{where should this fit in:
+it can be achieved under generic cryptographic hardness assumptions~\cite{wee2005obfuscating} -- can the strong variant be achieved by Wee?}
+
 Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+
+\lnote{stopped here}
 
@@
 Constructing noisy point obfuscation for all sources remains an open problem.
+
+The second construction does not require a large alphabet.
+However, because of its lower error tolerance, $\Huse<0$ only for large alphabets (and if $\Huse>0$, then there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
+It would be nice to get information-theoretic security, but current techniques seem to work for all distributions, which we know is impossible.
+
+\lnote{old stuff below}
+
+Fuzzy extractors have not yielded key derivation for all noisy sources.
+There is tension between security and error-tolerance.
+The key should be uniform to an observer but nearby $w'$ should map to the same key.
+By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.
+In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.
+This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+The length of the key $r$ is dictated by size of the best code that corrects $t$ errors.
+Error-correcting codes are well studied and we have tight bounds on this quantity.
+% how many codewords may be in a code that corrects $t$ errors.
+
+We consider the Hamming metric.
+For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected~(and we have constructions of fuzzy extractors that nearly meet this bound).
+For the remainder of this paper we call this difference the minimum usable entropy, denoted $\Huse$.
+This represents a practical problem as important biometrics have $\Huse<0$~(see \apref{sec:iris no key}).
+
+ %let $|B_t|$ be the number of points within distance $t$.
+The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
+For the remainder of this paper, we denote this quantity by $\Huse = \Hoo(W) - \log |B_t|$.
+
+To achieve security when $\Huse<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
+However, the tools for constructing information-theoretic fuzzy extractors have not yielded natural restrictions.
+Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
+Computational fuzzy extractors produce pseudorandom instead of truly random keys.
+A computational fuzzy extractor may exist for a larger class of distributions with $\Huse<0$ than is possible information-theoretically.
+
+In this work, we construct computational fuzzy extractors when $\Huse<0$ for large classes of distributions.
+In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse<0$.
 
@@
 \end{align*}
+\lnote{we should explain what this t means -- the formula is too complex. Also, we seem to require large alphabet size -- is it only because of $\delta$?}
 \end{theorem}
@@
 \begin{proof}
-Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.
+Since $f$ is injective on each block, $\Hav(W_i | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
 Consider a query $q_j$ on block $i$.
@@
 \label{eq:dist before}
-|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \label{lem:sim cannot distinguish}
-$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
+$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
 \end{lemma}
@@
 \[
-\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
+\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
 \]
@@
 \end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.
+By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.
 This completes the proof of \lemref{lem:sim cannot distinguish}.
@@
 \label{eq:dist after}
-|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \begin{align*}
-\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
-&+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\
-&+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
+\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})]| \\
+&+|\expe[S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] - \expe[S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\\
+&+|\expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] - \expe [D(P_1,..., P_\ell, C') ]|\\
 &\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
@@
 
+\bnote{this can also be tightened.}
 Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that 

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
almost done with intro pass

@@
 \section{Introduction}\label{sec:introduction}
-\lnote{What I want to do with this: make it clear that we are not the crazy obfuscation types, but are using something practically achievable; perhaps mention RO; perhaps compare with Dodis' RO analysis (was that for robustness only?); explain that we have two points on an entropy/error tolerance tradeoff; explain how switching to computational makes our construction possible and, in general, why our construction is cool.
-Section titles for 4 and 5!}
-Reliable key derivation is a cornerstone of authentication.
-However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).
-\bnote{add more examples here} To use noisy physical sources in applications, two problems must be addressed.
-The first is ensuring the same value is obtained from every reading of the source.
-This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).
-The second is converting the entropic source to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).
-Both of these problems have interactive and non-interactive versions.
-For a single user trying to produce the same key from multiple readings of a physical source non-interactive solutions are needed.
-We focus on this setting.
-%If both of these tasks are achieved a noisy physical source can be used like a uniformly random private key.
-
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} perform both tasks non-interactively.
-They consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.
+
+\paragraph{Fuzzy Extractors}
+Cryptography relies on secrets for that are read multiple times for key derivation and authentication.
+However, many sources with sufficient randomness  provide similar but not identical values at each reading~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
+physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical}, 
+and quantum information~\cite{bennett1988privacy}).
+Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
+Both of these problems have interactive and noninteractive versions.
+In this paper, we are interested the noninteractive case, which can be used, in particular, by  a single user trying to produce the same key from multiple readings of a physical source at different times.
+The primitive accomplishing information reconciliation and privacy amplification noninteractively is known as a \emph{fuzzy extractor}; it is defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}
+
+Fuzzy extractors consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.
 The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-Traditionally, a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} performs information-reconciliation and a randomness extractor~\cite{nisan1993randomness} performs privacy amplification.
+The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ comes from a high-quality distribution (traditionally, any distribution with sufficient min-entropy $m$).
+The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on strings over some alphabet $\mathcal{Z}$ of length $\ell$).
+
+\paragraph{Limitations of Entropy-Based Approaches}
+Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
+The reason for this tension is quite simple: the adversary who knows $p$ and can guess some $w'$ within distance $t$ of $w$ will be able to easily distinguish $r$ from uniform by running $\rep$ and finding out what $r$ is.
+If $t$ is higher, then $\rep$ tolerates more $w'$ values, so the adversary's job is easier.
+In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then the \emph{entire distribution} of $w$ may have min-entropy $m$ and yet be contained in a single ball, in which case the adversary can simply use the center of the ball as $w'$.
+
+More generally, let $B_t$ denote the number of points in a ball of radius $t$.
+For any $m$ and $t$, one can come up with a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of all points in several nonoverlapping balls of radius $t$ (we need the space to be sufficiently large for the balls to fit).
+We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
+The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-etropy $m$ if  $\Huse\le 0$.
+
+However, some of the distributions with $\Huse\le 0$ are prime candidates use in authentication. \lnote{examples here}. No current fuzzy extractor construction is known to work for them.
+
+\paragraph{Our Contributions}
+We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
+As explained above, such constructions cannot work without some restrictions on the distribution.
+It is secure when symbols in $w$ 
+each have individual superlogarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
+a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
+
+We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
+However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $\ell/\omega(\log\ell)$ errors.
+
+\paragraph{Our Approach}
+Our constructions are computationally secure.
+Indeed, known techniques for proving information-theoretically secure fuzzy extractors work for all distributions of a given entropy, and thus cannot be used to prove security for some distributions  with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.)
+
+Most known constructions of fuzzy extractors put sufficient information in $p$ to recover $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
+Fuller, Meng, and Reyzin~\cite{fuller2013computational}, in introducing computational fuzzy extractors, show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.
+We take the second approach.
+
+Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
+We define and show two constructions of \emph{computational fuzzy conductors}.
+These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
+
+Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.
+A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
+Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.
+For a point program, this means hiding all partial information about the point $w$.
+We need a strong version of point obfuscation, which is secure under composition.  
+However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation.
+In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.
+It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.
+
+Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+Let $w=w_1 \dots w_\ell$, for $w_i\in \mathcal{Z}$.
+In the first construction (\consref{cons:first construction}), for each $i$, $\gen$ flips a coin $c_i$ and either obfuscates $I_{w_i}$ or picks a random point $r_i$ and obfuscates $I_{r_i}$.
+This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
+With a close value $w'$, $\rep$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
+For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.
+Thus, most bits of $c_i$ are recoverable.
+To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code.
+This construction conducts entropy from $w$ to $c$.
+
+Note that obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it converts $w$ to a string of blocks and then applies the first construction.
+Each block is produced by  sampling several coordinates of $w$ and concatenating them.
+This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
+This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
+Note that, unlike in locally computable extractors, we can use the sampler multiple times and not worry about the fact that the same symbols is entering multiple blocks,  because correlations among blocks are not a problem for the first construction.
+Computational, rather than information-theoretic, analysis seems crucial for achieving this property.
+
+\paragraph{Limitations} In order to achieve security with $\Huse\le 0$, our alphabet must be super-polynomial in the security parameter.
+Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
+Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
+Furthermore, we may leak sensitive information about the underlying source $W$.
+In \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
+Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
+Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} achieve a notion of noisy point obfuscation when $\Huse>>0$ using a information-reconciliation component that hides all partial information.
+Constructing noisy point obfuscation for all sources remains an open problem.
+
+The second construction does not require a large alphabet for security.
+However, because of its lower error tolerance, $\Huse \le 0$ only for large alphabets (and if $\Huse>0$, then there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
+It would be nice to get information-theoretic security, but current techniques seem to work for all distributions, which we know is impossible.
+
+\lnote{old stuff below}
 
@@
 For the remainder of this paper we call this difference the minimum usable entropy, denoted $\Huse$.
-This represents a practical problem as important biometrics have $\Huse<0$~(see \apref{sec:iris no key}).
+This represents a practical problem as important biometrics have $\Huse \le 0$~(see \apref{sec:iris no key}).
 
@@
 
-To achieve security when $\Huse<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
+To achieve security when $\Huse \le 0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
 However, the tools for constructing information-theoretic fuzzy extractors have not yielded natural restrictions.
@@
 Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-A computational fuzzy extractor may exist for a larger class of distributions with $\Huse<0$ than is possible information-theoretically.
-
-In this work, we construct computational fuzzy extractors when $\Huse<0$ for large classes of distributions.
-In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse<0$.
-
-Fuller, Meng, and Reyzin show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.
-This is known as a fuzzy conductor~(the entropy is ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.
-Here, we follow the second approach and use a \emph{computational} fuzzy conductor.
-We present two constructions of computational fuzzy conductors for different types of source distributions $W$.
-These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
-
-Both of constructions are based on the obfuscation of point programs.
-A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
-Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.
-For a point program, this means hiding all partial information about the point $w$.
-Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.
-We need a strong version of point obfuscation secure under composition, this is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.%, DBLP:conf/innovations/GoldwasserKPV10}.
-Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
-
-\textbf{\consref{cons:first construction}: }
-Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).
-We would like to tolerate errors in $t$ individual blocks.
-For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.
-This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
-With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
-For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.
-Thus, most bits of $c_i$ are recoverable.
-To tolerate errors we sample the coins $c$ from the codewords of an error-correcting code.
-The set of possible codewords forms a high entropy distribution.
-This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
-
-In \consref{cons:first construction}, each block of $W$ is individually obfuscated.
-This has two drawbacks, first an adversary may learn the value of some blocks which may be sensitive information.
-Second, security only holds for sources where a large number of blocks have super-logarithmic entropy~(\defref{def:block guessable}).
-Our second construction addresses these problems.
-
-\textbf{\consref{cons:sampling}: }
-As before we consider a source $W=W_1,...,W_\ell$ that is split into blocks.  However, instead of obfuscating individually
-blocks individually, for each bit $c_i$ we randomly select a subset of blocks.
-These blocks are concatenated and obfuscated together.
-By sampling, we can significantly decrease the entropy requirement on individual blocks.
-This paradigm is similar to the \emph{sample-then-extract} paradigm in the locally-computable extractor literature~\cite{lu2002hyper,vadhan2003constructing}.
-For this reason, we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-
-%Our construction provides several advantages over previous constructions of computational fuzzy extractors:
-%\begin{itemize}
-%\item The first computational fuzzy extractor where $\Huse$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
-Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
-%\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
-Our construction simply requires a large number of blocks that are unguessable given equality queries.
-This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
-%\end{itemize}
-
-\textbf{Limitations: } In order to achieve security with $\Huse<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
-Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
-Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
-Furthermore, we may leak sensitive information about the underlying source $W$.
-In \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
-Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} achieve a notion of noisy point obfuscation when $\Huse>>0$ using a information-reconciliation component that hides all partial information.
-Constructing noisy point obfuscation for all sources remains an open problem.
+A computational fuzzy extractor may exist for a larger class of distributions with $\Huse\le 0$ than is possible information-theoretically.
+
+In this work, we construct computational fuzzy extractors when $\Huse\le 0$ for large classes of distributions.
+In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse\le 0$.
 
@@
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $\Huse<0$ some restriction is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
+With $\Huse\le 0$ some restriction is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
 Instead of restricting the class of source distributions, the definition could restrict the correctable errors to errors that are ``likely'' to occur in the source.
@@
 
-\section{A Computational Fuzzy Conductor when $\Huse<0$}
+\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}
 \label{sec:construction}
@@
 \]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
 %Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
-%We achieve security when $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
+%We achieve security when $\Huse\le 0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
 %When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
@@
 
-\section{Sample-then-Obfuscate}
-\bnote{Reducing required entropy as title?}
+\section{Trading Errors for Entropy}
 \label{sec:sampling}
-\bnote{Leo didn't like this linking.  Better?}
-\consref{cons:first construction} is a computational fuzzy conductor with $\Huse<0$.
-Unfortunately, \consref{cons:first construction} required most blocks of $W$ to have super-logarithmic min-entropy.
+\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.
+Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.
 This may be an unreasonable requirement.
-In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously.
+In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously, at the price of  decreasing the effective error tolerance.
 %In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler). 
-Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.
-Thus, we have a tradeoff between entropy and error tolerance.
 The main idea is to sample a random subset of blocks $W_{i_1},..., W_{i_\eta}$ and obfuscate the concatenation of these blocks.
@@
 
-\begin{construction}
+\begin{construction}[Sample-then-Obfuscate]
 \label{cons:sampling}
@@
 \subsection{Discussion of \consref{cons:sampling}}
-We now show \consref{cons:sampling} can work for partial block sources when $\Huse<0$.
+We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.
 The required entropy of  an partial block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
@@
 \end{align*}
-That is, \consref{cons:sampling} achieves $\Huse<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
+That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
 If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
@@
 %The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
-If we wish to support parameter regimes where $\Huse<0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
-Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse<0$.
-This motivates our restriction to meaningful classes of source distributions with $\Huse<0$.
+If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
+Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse\le 0$.
+This motivates our restriction to meaningful classes of source distributions with $\Huse\le 0$.
 %This means we inherently must talk about the security and errors together.

### 2014-02-07 trunk/constantRate/ConstCompFuzzExt.tex
finished intro draft

@@
 \section{Introduction}\label{sec:introduction}
-\lnote{What I want to do with this: make it clear that we are not the crazy obfuscation types, but are using something practically achievable; perhaps mention RO; perhaps compare with Dodis' RO analysis (was that for robustness only?); explain that we have two points on an entropy/error tolerance tradeoff; explain how switching to computational makes our construction possible and, in general, why our construction is cool.
-Section titles for 4 and 5!}
 
@@
 Cryptography relies on secrets for that are read multiple times for key derivation and authentication.
-However, many sources with sufficient secrecy  provide similar but not identical values at each reading~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
+However, many sources with sufficient randomness  provide similar but not identical values at each reading~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
 physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical}, 
@@
 The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ has sufficient min-entropy $m$.
+The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ comes from a high-quality distribution (traditionally, any distribution with sufficient min-entropy $m$).
 The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on strings over some alphabet $\mathcal{Z}$ of length $\ell$).
@@
 For any $m$ and $t$, one can come up with a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of all points in several nonoverlapping balls of radius $t$ (we need the space to be sufficiently large for the balls to fit).
-We thus call $m-\log B_t$ the \emph{usable} entropy, denoted by $\Huse$.
-The previous paragraph shows that  no fuzzy extractor can handle $\Huse\le 0$ as long as we require it work for \emph{all} distributions of a given min-entropy.
+We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
+The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-etropy $m$ if  $\Huse\le 0$.
 
@@
 \paragraph{Our Contributions}
-We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse<0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
-As already explained above, such constructions cannot work without some restrictions on the distribution.
-The first construction works when every single symbol of $w$ has individual superlogarithmic min-entropy (thus requiring a large alphabet), but allows for arbitrary dependence between symbols (the actual condition is more general and may permit some symbols to have less entropy; see \defref{def:block guessable}).
+We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
+As explained above, such constructions cannot work without some restrictions on the distribution.
+It is secure when symbols in $w$ 
+each have individual superlogarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
+a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
 
 We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
-However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $O(\ell/\log\ell)$ errors.\lnote{check}.
+However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $\ell/\omega(\log\ell)$ errors.
 
@@
 Our constructions are computationally secure.
-Indeed, known techniques for proving information-theoretically secure fuzzy extractors work for all distributions of a given entropy, and thus cannot be used to prove security for some distributions of with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.)
+Indeed, known techniques for proving information-theoretically secure fuzzy extractors work for all distributions of a given entropy, and thus cannot be used to prove security for some distributions  with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.)
 
@@
 Fuller, Meng, and Reyzin~\cite{fuller2013computational}, in introducing computational fuzzy extractors, show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.
+Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.
 We take the second approach.
 
-The procedure that takes a high-entropy input to get a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
-Since in our case, the resulting entropy is computational, we define and show two constructions of \emph{computational fuzzy conductors}.
+Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
+We define and show two constructions of \emph{computational fuzzy conductors}.
 These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
 
-Both constructions are based on the obfuscation of point programs~\cite{canetti1997towards}.
+Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.
 A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
@@
 We need a strong version of point obfuscation, which is secure under composition.  
-However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation.
-In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}; it is may also be reasonable to assume that a cryptographic hash function, such as SHA-2, is a good point obfuscator.
-\lnote{cite anything?} \lnote{where should this fit in:
-it can be achieved under generic cryptographic hardness assumptions~\cite{wee2005obfuscating} -- can the strong variant be achieved by Wee?}
+However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}.
+In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.
+It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.
 
 Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
-
-\lnote{stopped here}
-
-\textbf{\consref{cons:first construction}: }
-Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).
-We would like to tolerate errors in $t$ individual blocks.
-For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.
+Let $w=w_1 \dots w_\ell$, for $w_i\in \mathcal{Z}$.
+In the first construction (\consref{cons:first construction}), for each $i$, $\gen$ flips a coin $c_i$ and either obfuscates $I_{w_i}$ or picks a random point $r_i$ and obfuscates $I_{r_i}$.
 This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
-With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
+With a close value $w'$, $\rep$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
 For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.
 Thus, most bits of $c_i$ are recoverable.
-To tolerate errors we sample the coins $c$ from the codewords of an error-correcting code.
-The set of possible codewords forms a high entropy distribution.
-This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.
-
-In \consref{cons:first construction}, each block of $W$ is individually obfuscated.
-This has two drawbacks, first an adversary may learn the value of some blocks which may be sensitive information.
-Second, security only holds for sources where a large number of blocks have super-logarithmic entropy~(\defref{def:block guessable}).
-Our second construction addresses these problems.
-
-\textbf{\consref{cons:sampling}: }
-As before we consider a source $W=W_1,...,W_\ell$ that is split into blocks.  However, instead of obfuscating individually
-blocks individually, for each bit $c_i$ we randomly select a subset of blocks.
-These blocks are concatenated and obfuscated together.
-By sampling, we can significantly decrease the entropy requirement on individual blocks.
-This paradigm is similar to the \emph{sample-then-extract} paradigm in the locally-computable extractor literature~\cite{lu2002hyper,vadhan2003constructing}.
-For this reason, we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-
-%Our construction provides several advantages over previous constructions of computational fuzzy extractors:
-%\begin{itemize}
-%\item The first computational fuzzy extractor where $\Huse$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.
-Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
-%\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.
-Our construction simply requires a large number of blocks that are unguessable given equality queries.
-This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
-%\end{itemize}
-
-\textbf{Limitations: } In order to achieve security with $\Huse<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.
-Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
+To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code.
+This construction conducts entropy from $w$ to $c$.
+
+Note that obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it converts $w$ to a string of blocks and then applies the first construction.
+Each block is produced by  sampling several coordinates of $w$ and concatenating them.
+This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
+This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
+Note that, unlike in locally computable extractors, we can use the sampler multiple times and not worry about the fact that the same symbols is entering multiple blocks,  because correlations among blocks are not a problem for the first construction.
+Computational, rather than information-theoretic, analysis seems crucial for achieving this property.
+
+\paragraph{Open Problems}
+Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet}.
+Although the sample-then-obfuscate construction remains secure with a small alphabet, because of its lower error tolerance, $\Huse \le 0$ only for large alphabets (for small alphabets, since $\Huse>0$,  there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
 Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
-Furthermore, we may leak sensitive information about the underlying source $W$.
-In \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
-Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} achieve a notion of noisy point obfuscation when $\Huse>>0$ using a information-reconciliation component that hides all partial information.
-Constructing noisy point obfuscation for all sources remains an open problem.
-
-The second construction does not require a large alphabet.
-However, because of its lower error tolerance, $\Huse<0$ only for large alphabets (and if $\Huse>0$, then there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
-It would be nice to get information-theoretic security, but current techniques seem to work for all distributions, which we know is impossible.
-
-\lnote{old stuff below}
-
-Fuzzy extractors have not yielded key derivation for all noisy sources.
-There is tension between security and error-tolerance.
-The key should be uniform to an observer but nearby $w'$ should map to the same key.
-By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.
-In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.
-This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
-The length of the key $r$ is dictated by size of the best code that corrects $t$ errors.
-Error-correcting codes are well studied and we have tight bounds on this quantity.
-% how many codewords may be in a code that corrects $t$ errors.
-
-We consider the Hamming metric.
-For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected~(and we have constructions of fuzzy extractors that nearly meet this bound).
-For the remainder of this paper we call this difference the minimum usable entropy, denoted $\Huse$.
-This represents a practical problem as important biometrics have $\Huse<0$~(see \apref{sec:iris no key}).
-
- %let $|B_t|$ be the number of points within distance $t$.
-The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
-For the remainder of this paper, we denote this quantity by $\Huse = \Hoo(W) - \log |B_t|$.
-
-To achieve security when $\Huse<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
-However, the tools for constructing information-theoretic fuzzy extractors have not yielded natural restrictions.
-Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
-Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-A computational fuzzy extractor may exist for a larger class of distributions with $\Huse<0$ than is possible information-theoretically.
-
-In this work, we construct computational fuzzy extractors when $\Huse<0$ for large classes of distributions.
-In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse<0$.
-
+
+Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
+The obfuscation is secure as long as $w$ comes from a distribution of sufficient minentropy; in particular, the entropy must be high enough so that $\Huse>0$.
+Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree).
+Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.
+
+\medskip
 The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
moved iris stuff to intro

@@
 \paragraph{Fuzzy Extractors}
-Cryptography relies on secrets for that are read multiple times for key derivation and authentication.
-However, many sources with sufficient randomness  provide similar but not identical values at each reading~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
+Cryptography relies on long-term secrets for key derivation and authentication.
+However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
 physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical}, 
@@
 Both of these problems have interactive and noninteractive versions.
-In this paper, we are interested the noninteractive case, which can be used, in particular, by  a single user trying to produce the same key from multiple readings of a physical source at different times.
-The primitive accomplishing information reconciliation and privacy amplification noninteractively is known as a \emph{fuzzy extractor}; it is defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}
+In this paper, we are interested in the noninteractive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
+ A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification noninteractively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.
 
@@
 The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ comes from a high-quality distribution (traditionally, any distribution with sufficient min-entropy $m$).
-The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on strings over some alphabet $\mathcal{Z}$ of length $\ell$).
+The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\ell$ strings over some alphabet $\mathcal{Z}$).
 
@@
 
-However, some of the distributions with $\Huse\le 0$ are prime candidates use in authentication. \lnote{examples here}. No current fuzzy extractor construction is known to work for them.
+Prime candidate sources for authentication have $\Huse\le 0$.
+As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
+The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.
+Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
+The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
+For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.
+We have the following calculation for $\Huse$:
+\[
+\Huse = \Hoo(W) - \log |B_t|
+= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -414.
+\]
+Note there is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman's work but it affects the quantity not the quality of the above bound.
+No current fuzzy extractor is known to work for irises.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation is $\Huse \approx 44$.}
 
@@
 We need a strong version of point obfuscation, which is secure under composition.  
-However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation.
+However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}.
 In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.
@@
 
-\paragraph{Limitations} In order to achieve security with $\Huse\le 0$, our alphabet must be super-polynomial in the security parameter.
-Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).
+\paragraph{Open Problems}
+Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet.}  Although the sample-then-obfuscate construction remains secure with a small alphabet, because of its lower error tolerance, $\Huse \le 0$ only for large alphabets.
+For small alphabets where $\Huse>0$,  there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
 Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
-Furthermore, we may leak sensitive information about the underlying source $W$.
-In \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.
-Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.
-Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} achieve a notion of noisy point obfuscation when $\Huse>>0$ using a information-reconciliation component that hides all partial information.
-Constructing noisy point obfuscation for all sources remains an open problem.
-
-The second construction does not require a large alphabet for security.
-However, because of its lower error tolerance, $\Huse \le 0$ only for large alphabets (and if $\Huse>0$, then there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
-It would be nice to get information-theoretic security, but current techniques seem to work for all distributions, which we know is impossible.
-
-\lnote{old stuff below}
-
-Fuzzy extractors have not yielded key derivation for all noisy sources.
-There is tension between security and error-tolerance.
-The key should be uniform to an observer but nearby $w'$ should map to the same key.
-By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.
-In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.
-This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
-The length of the key $r$ is dictated by size of the best code that corrects $t$ errors.
-Error-correcting codes are well studied and we have tight bounds on this quantity.
-% how many codewords may be in a code that corrects $t$ errors.
-
-We consider the Hamming metric.
-For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected~(and we have constructions of fuzzy extractors that nearly meet this bound).
-For the remainder of this paper we call this difference the minimum usable entropy, denoted $\Huse$.
-This represents a practical problem as important biometrics have $\Huse \le 0$~(see \apref{sec:iris no key}).
-
- %let $|B_t|$ be the number of points within distance $t$.
-The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).
-For the remainder of this paper, we denote this quantity by $\Huse = \Hoo(W) - \log |B_t|$.
-
-To achieve security when $\Huse \le 0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).
-However, the tools for constructing information-theoretic fuzzy extractors have not yielded natural restrictions.
-Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.
-Computational fuzzy extractors produce pseudorandom instead of truly random keys.
-A computational fuzzy extractor may exist for a larger class of distributions with $\Huse\le 0$ than is possible information-theoretically.
-
-In this work, we construct computational fuzzy extractors when $\Huse\le 0$ for large classes of distributions.
-In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse\le 0$.
-
+
+Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
+The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$.
+Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree).
+Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.
+
+\medskip
 The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
@@
 The iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
+The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
 There has been considerable research since the work of Daugman~\cite{daugman2004}.
-However, These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.
+These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.
 We use the Daugman's parameters for our calculations.
@@
 \Huse &= \Hoo(W) - \log |B_t|\\
-&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
+&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -414.
 \end{align*}

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
minor changes to intro

@@
 \Huse = \Hoo(W) - \log |B_t|
-= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -414.
-\]
-Note there is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman's work but it affects the quantity not the quality of the above bound.
-No current fuzzy extractor is known to work for irises.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation is $\Huse \approx 44$.}
+= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx -707.
+\]
+Note there is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman's, work but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}  No current fuzzy extractor is known to work for irises.
 

### 2014-02-07 trunk/constantRate/ConstCompFuzzExt.tex
notes on introduction

@@
 Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
-The reason for this tension is quite simple: the adversary who knows $p$ and can guess some $w'$ within distance $t$ of $w$ will be able to easily distinguish $r$ from uniform by running $\rep$ and finding out what $r$ is.
-If $t$ is higher, then $\rep$ tolerates more $w'$ values, so the adversary's job is easier.
-In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then the \emph{entire distribution} of $w$ may have min-entropy $m$ and yet be contained in a single ball, in which case the adversary can simply use the center of the ball as $w'$.
+The reason for this tension is simple: if an adversary who knows $p$ can guess some $w'$ within distance $t$ of $w$ they will be able to easily distinguish $r$ from uniform by running $\rep$.
+If $t$ is larger, then $\rep$ tolerates more $w'$ values, so the adversary's job is easier.
+In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then the \emph{entire distribution} of $w$ may have min-entropy $m$ and be contained in a single ball.
+Then the adversary can always produce the key by running $\rep$ with the center of the ball as $w'$.
 
 More generally, let $B_t$ denote the number of points in a ball of radius $t$.
-For any $m$ and $t$, one can come up with a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of all points in several nonoverlapping balls of radius $t$ (we need the space to be sufficiently large for the balls to fit).
+For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several nonoverlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
 We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
@@
 
-However, some of the distributions with $\Huse\le 0$ are prime candidates use in authentication. \lnote{examples here}. No current fuzzy extractor construction is known to work for them.
+Prime candidate sources for authentication have $\Huse\le 0$.
+As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
+The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.
+Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
+Let the outcome of this transform define the distribution $w$.
+The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
+For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.
+We have the following calculation for $\Huse$:
+\[
+\Huse = \Hoo(W) - \log |B_t|
+= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx -707.
+\]
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}  No current fuzzy extractor is known to work for irises.
 
@@
 As explained above, such constructions cannot work without some restrictions on the distribution.
-It is secure when symbols in $w$ 
+Our first construction is secure when symbols in $w$ 
 each have individual superlogarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
@@
 Our constructions are computationally secure.
-Indeed, known techniques for proving information-theoretically secure fuzzy extractors work for all distributions of a given entropy, and thus cannot be used to prove security for some distributions  with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.)
+Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions of a given entropy, and thus cannot be used with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.) \bnote{something about the parenthetical statement I don't like}
 
 Most known constructions of fuzzy extractors put sufficient information in $p$ to recover $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-Fuller, Meng, and Reyzin~\cite{fuller2013computational}, in introducing computational fuzzy extractors, show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Fuller, Meng, and Reyzin~\cite{fuller2013computational} show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
 Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.
@@
 We need a strong version of point obfuscation, which is secure under composition.  
-However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}.
+However, even for this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}.
 In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.
-It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.
+It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.\bnote{ran or omer, is this a reasonable statement?}
 
@@
 
-Note that obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
-We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it converts $w$ to a string of blocks and then applies the first construction.
-Each block is produced by  sampling several coordinates of $w$ and concatenating them.
-This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
+Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}:\bnote{I thought you didn't like this name?} it converts $w$ to a string of blocks and then applies the first construction.
+$\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.\bnote{$w$ isn't converted as there is a reasonable prob that some blocks are not used at all.} This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
 This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
-Note that, unlike in locally computable extractors, we can use the sampler multiple times and not worry about the fact that the same symbols is entering multiple blocks,  because correlations among blocks are not a problem for the first construction.
+Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed for the first construction.
 Computational, rather than information-theoretic, analysis seems crucial for achieving this property.
@@
 \paragraph{Open Problems}
-Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet}.
-Although the sample-then-obfuscate construction remains secure with a small alphabet, because of its lower error tolerance, $\Huse \le 0$ only for large alphabets (for small alphabets, since $\Huse>0$,  there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
-Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
+Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
+However, distributions with $\Huse \le 0$ are supported only for large alphabets.
+For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
+Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.
 
 Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
-The obfuscation is secure as long as $w$ comes from a distribution of sufficient minentropy; in particular, the entropy must be high enough so that $\Huse>0$.
+The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$.
 Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree).
@@
 The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-With $\Huse\le 0$ some restriction is necessary for any meaningful security~(see \apref{sec:minimal conditions}).
+As discussed in the introduction, when $\Huse\le 0$ some restriction on the source is necessary.
 Instead of restricting the class of source distributions, the definition could restrict the correctable errors to errors that are ``likely'' to occur in the source.
@@
 
-\section{Use of Fuzzy Extractors for Biometrics}
-Fuzzy extractors derive stable from noisy sources.
+%\section{Use of Fuzzy Extractors for Biometrics}
+%Fuzzy extractors derive stable from noisy sources.
 Biometrics represent an important noisy physical source.
@@
 false reject rate is insufficient to argue system security.
-
-\label{sec:iris no key}
-As an example, we focus on the human iris.
+%
+%\label{sec:iris no key}
+%As an example, we focus on the human iris.
 The iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.
+The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
 There has been considerable research since the work of Daugman~\cite{daugman2004}.
-However, These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.
+These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.
 We use the Daugman's parameters for our calculations.
-
-The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
+%
+%The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
 For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.%\footnote{Daugman  improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
@@
 Even with the masking vector $\Huse$ is negative for irises.}
-We have the following calculation for $\Huse$:
-\begin{align*}
-\Huse &= \Hoo(W) - \log |B_t|\\
-&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
-\end{align*}
-Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
-Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
-
-\section{Minimal Conditions for Fuzzy Extractor Security}
-\label{sec:minimal conditions}
-
-A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
+%We have the following calculation for $\Huse$:
+%\begin{align*}
+%\Huse &= \Hoo(W) - \log |B_t|\\
+%&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx 707.
+%\end{align*}
+%Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
+%Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
+%
+%\section{Minimal Conditions for Fuzzy Extractor Security}
+%\label{sec:minimal conditions}
+%
+%A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
 This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
 We make this intuition formal here:
-
-\begin{definition}
-\label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
-\[
-\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
-\]
-\end{definition}
-For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
-\begin{lemma}
-\label{lem:fuzz necessary}
-Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-\end{lemma}
-\begin{proof}
-Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+%
+%\begin{definition}
+%\label{def:fuzzy min-ent}
+%A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+%\[
+%\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+%\]
+%\end{definition}
+%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
+%\begin{lemma}
+%\label{lem:fuzz necessary}
+%Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
+%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
+%\end{lemma}
+%\begin{proof}
+%Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
 This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
 Consider the following distinguisher $D$:
-\begin{itemize}
-\item On input $r, p$.
-\item If $\rep(m, p) = r$, output $1$.
-\item Else output $0$.
-\end{itemize}
-First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
+%\begin{itemize}
+%\item On input $r, p$.
+%\item If $\rep(m, p) = r$, output $1$.
+%\item Else output $0$.
+%\end{itemize}
+%First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
 Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.
 Thus, when $\kappa = \omega(\log n)$:
-\[
-\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
-\]
-\end{proof}
-\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+%\[
+%\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
+%\]
+%\end{proof}
+%\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
 This means that fuzzy min-entropy is also a necessary condition for interactive solution.
 %The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
-If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
+%If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
 Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse\le 0$.
 This motivates our restriction to meaningful classes of source distributions with $\Huse\le 0$.
-%This means we inherently must talk about the security and errors together.
-
-In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.
+%%This means we inherently must talk about the security and errors together.  
+%
+%In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.
 There are two minimal types of distributions where $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
cleaning up some notes

@@
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
+Let the outcome of this transform define the distribution $w$.
 The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
@@
 \]
-Note there is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman's, work but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}  No current fuzzy extractor is known to work for irises.
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}  No current fuzzy extractor is known to work for irises.
 
@@
 \paragraph{Open Problems}
-Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet.}  Although the sample-then-obfuscate construction remains secure with a small alphabet, because of its lower error tolerance, $\Huse \le 0$ only for large alphabets.
-For small alphabets where $\Huse>0$,  there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
-Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.
+Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
+However, distributions with $\Huse \le 0$ are supported only for large alphabets.
+For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
+Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.
 
@@
 
-We discuss unguessable block distributions in \apref{sec:characterize}.  \bnote{there should be probably be something here.  block-sources?}
+We discuss unguessable block distributions in \apref{sec:characterize}.
+In particular any source $W$ where for all $i$, $\Hoo(W_i) \geq \omega(\log n)$~(all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
 
@@
 The need for remaining entropy conditioned on the past is arbitrary.
-The precise requirement is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
-Note a partial block source requires worst case entropy while an unguessable block distribution only requires average conditional entropy.
+The actual requirement is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
+%Note a partial block source requires worst case entropy while an unguessable block distribution only requires average conditional entropy.
 \lnote{this comparison is unclear to me}  However, we achieve security for significantly lower entropy levels than for unguessable block distributions.
@@
 \begin{align*}
-t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
+t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
 \tilde{m} &=|C|\\
@@
 \lnote{we should explain what this t means -- the formula is too complex. Also, we seem to require large alphabet size -- is it only because of $\delta$?}
+\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$.}
 \end{theorem}
@@
 false reject rate is insufficient to argue system security.
-
-\label{sec:iris no key}
-As an example, we focus on the human iris.
+%
+%\label{sec:iris no key}
+%As an example, we focus on the human iris.
 The iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
@@
 We use the Daugman's parameters for our calculations.
-
-The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
+%
+%The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
 For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.%\footnote{Daugman  improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
@@
 Even with the masking vector $\Huse$ is negative for irises.}
-We have the following calculation for $\Huse$:
-\begin{align*}
-\Huse &= \Hoo(W) - \log |B_t|\\
-&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -414.
-\end{align*}
-Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
-Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
-
-\section{Minimal Conditions for Fuzzy Extractor Security}
-\label{sec:minimal conditions}
-
-A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
+%We have the following calculation for $\Huse$:
+%\begin{align*}
+%\Huse &= \Hoo(W) - \log |B_t|\\
+%&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx 707.
+%\end{align*}
+%Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
+%Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
+%
+%\section{Minimal Conditions for Fuzzy Extractor Security}
+%\label{sec:minimal conditions}
+%
+%A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
 This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
 We make this intuition formal here:
-
-\begin{definition}
-\label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
-\[
-\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
-\]
-\end{definition}
-For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
-\begin{lemma}
-\label{lem:fuzz necessary}
-Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-\end{lemma}
-\begin{proof}
-Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+%
+%\begin{definition}
+%\label{def:fuzzy min-ent}
+%A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+%\[
+%\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+%\]
+%\end{definition}
+%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
+%\begin{lemma}
+%\label{lem:fuzz necessary}
+%Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
+%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
+%\end{lemma}
+%\begin{proof}
+%Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
 This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
 Consider the following distinguisher $D$:
-\begin{itemize}
-\item On input $r, p$.
-\item If $\rep(m, p) = r$, output $1$.
-\item Else output $0$.
-\end{itemize}
-First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
+%\begin{itemize}
+%\item On input $r, p$.
+%\item If $\rep(m, p) = r$, output $1$.
+%\item Else output $0$.
+%\end{itemize}
+%First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
 Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.
 Thus, when $\kappa = \omega(\log n)$:
-\[
-\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
-\]
-\end{proof}
-\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+%\[
+%\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
+%\]
+%\end{proof}
+%\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
 This means that fuzzy min-entropy is also a necessary condition for interactive solution.
 %The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
-If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
+%If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
 Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse\le 0$.
 This motivates our restriction to meaningful classes of source distributions with $\Huse\le 0$.
-%This means we inherently must talk about the security and errors together.
-
-In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.
+%%This means we inherently must talk about the security and errors together.  
+%
+%In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.
 There are two minimal types of distributions where $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).

### 2014-02-08 constantRate/ConstCompFuzzExt.tex

@@
 For a point program, this means hiding all partial information about the point $w$.
-We need a strong version of point obfuscation, which is secure under composition.  
-However, even for this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}.
-In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.
-It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.\bnote{ran or omer, is this a reasonable statement?}
+We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed.
+While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions.
+Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieve notions of obfuscation seem to be insufficient.
 

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
v1 of the abstract

@@
 
-\title{Constant Error Tolerance Computational Fuzzy Extractors}
+\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
 %\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
@@
 \begin{abstract}
-Fuzzy extractors derive strong keys from noisy sources.
-The goal is to reliably convert a high entropy source~(which may differ on repeated readings) to the same uniformly distributed key.
-Traditionally, their security is defined information-theoretically.
-%Fuzzy extractors have upper bounds on the length of the derived key.
+Fuzzy extractors convert a noisy source of entropy into a consistent uniformly distributed key.
+In the process of eliminating noise, they necessarily lose some of the entropy of the original source.
+We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.
+Unfortunately, this quantity is negative for some sources that are important in practice.
+
+We construct fuzzy extractors that work for distributions in which the minimum usable entropy is \emph{negative}.
+Such constructions must, necessarily, put additional limits on the distribution beyond its starting entropy.
+We show two constructions that have computational security for Hamming distance over large alphabets.
+The first requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+The second requires  a constant fraction  symbols to have a constant amount of entropy conditioned on prior symbols.
+Our constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+
+\iffalse
+For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.
+
+Traditionally, their security is defined information-theoretically.  %Fuzzy extractors have upper bounds on the length of the derived key.
 
@@
 of Comp 2008).
+
 We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.
@@
 Therefore, fuzzy extractors that output the same length key for any source with enough entropy cannot output a key longer than the minimum usable entropy.
-For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.
 
@@
 \bnote{need something else to say here}
+\fi
 \end{abstract}
@@
 There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}  No current fuzzy extractor is known to work for irises.
+\lnote{I want to remove this last sentence because we don't solve this problem}
 
@@
 Our constructions are computationally secure.
-Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions of a given entropy, and thus cannot be used with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.) \bnote{something about the parenthetical statement I don't like}
+Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because then they would prove security, in particular, for the distribution that is contained withing a single ball of radius of $t$).
+\bnote{something about the parenthetical statement I don't like} \lnote{better?}
 
@@
 For a point program, this means hiding all partial information about the point $w$.
-We need a strong version of point obfuscation, which is secure under composition.  
-However, even for this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}.
-In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}.
-It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.\bnote{ran or omer, is this a reasonable statement?}
+We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed.
+While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions.
+Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieved notions of obfuscation seem to be insufficient.
 
@@
 Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
-We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}:\bnote{I thought you didn't like this name?} it converts $w$ to a string of blocks and then applies the first construction.
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}:\bnote{I thought you didn't like this name?}  \lnote{I found a way to work it in that is less self-conscious, so I am ok with it now; in general, I remembered that naming constructions is a good idea} it converts $w$ to a string of blocks and then applies the first construction.
 $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.\bnote{$w$ isn't converted as there is a reasonable prob that some blocks are not used at all.} This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
abstract v2

@@
 \begin{abstract}
-Fuzzy extractors derive strong keys from noisy sources.
-The goal is to reliably convert a high entropy source~(which may differ on repeated readings) to the same uniformly distributed key.
-Traditionally, their security is defined information-theoretically.
-%Fuzzy extractors have upper bounds on the length of the derived key.
+Fuzzy extractors convert a noisy source of entropy into a consistent uniformly distributed key.
+In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns.
+We call what is left after this worst-case loss the \emph{minimum usable entropy}.
+Unfortunately, this quantity is negative for some sources that are important in practice.
+
+We construct fuzzy extractors with computational security that work for distributions in which the minimum usable entropy is negative.
+They correct Hamming errors over a large alphabet.
+In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
+Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+Our second construction requires  a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
+The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+
+\iffalse
+For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.
+
+Traditionally, their security is defined information-theoretically.  %Fuzzy extractors have upper bounds on the length of the derived key.
 
@@
 Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
-We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieve notions of obfuscation seem to be insufficient.
+We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieved notions of obfuscation seem to be insufficient.
 

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
a bit of cleanup in section 2

@@
 
+We note that the problem of fuzzy extractors remains non-trivial even given the recent construction of general purpose indistinguishably obfuscation \cite{GargGH0SW13,PST13}, as the weaker notion of indistinguishably obfuscation seem to be insufficient for our application."
+
 Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
@@
 We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}:\bnote{I thought you didn't like this name?}  \lnote{I found a way to work it in that is less self-conscious, so I am ok with it now; in general, I remembered that naming constructions is a good idea} it converts $w$ to a string of blocks and then applies the first construction.
-$\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.\bnote{$w$ isn't converted as there is a reasonable prob that some blocks are not used at all.} This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
+$\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.\bnote{$w$ isn't converted as there is a reasonable prob that some blocks are not used at all.} \lnote{are you saying conversion must ``use" all input bits or be bijective or something?
+is it just a question of what the word ``convert'' means?} This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
 This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
@@
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-Let $|W|$ be the size of the support of $W$ that is $|W| = |\{w | \Pr[W=w]>0\}|$.
+For a random variable $W$, let $H_0(W)$ \lnote{I decided, after all, that $H_0(W)$ is less ambiguous and probably more commonly used} be the size of the support of $W$,  that is $H_0(W) = |\{w | \Pr[W=w]>0\}|$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
+For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
 We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^\ell$ the Hamming distance between $x,y$ is $\dis(x,y) = \{i | x_i \neq y_i\}$.
-For the Hamming metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\ell$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
+For this metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
 Unless otherwise noted logarithms are base $2$.
-Usually, we use capitalized letters for random variables and lowercase letters for samples from a random variable.
+Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
 
@@
 \label{sec:coding theory}
-We introduce some notions from binary coding theory.
-Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel~\cite{tallini2002capacity} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.
+We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
 \begin{definition}
@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \delta_{code}$.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh_t(c), \Pr[\rec(c') \neq c] \leq \delta_{code}$.
 \end{definition}
 
-We note that for any code learning a few bits does not inform on the remainder of the bits~(the claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
+\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$}
+
+We note that for any code, learning a few bits of a codeword does not inform on the remainder of the bits~(the claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
 
@@
 \label{cl:many locations ent}
-Let $C$ be a binary code and let $\mathcal{I}^c$ be a set of indices of $C$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \log |C| - |\mathcal{I}^c|$.
+Let $C$ be a subset of $\{0,1\}^\ell$ with a uniform distribution, and let $\mathcal{I}\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \log |C| - |\mathcal{I}^c|$.
 \end{claim}
@@
 \textbf{Notes:}
-Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
  Codes where $\log |C| = \Theta(\ell)$ and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
 These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
-The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different.
+The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
 See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.
@@
 The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
-This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time while making at most polynomial number of oracle queries to the function.
+This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at most a polynomial number of oracle queries to the function.
 In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
-Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+They can also be constructed by assuming strong properties of cryptographic hash functions!\cite{canetti1997towards}
 

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
some cleanup in sections 2, 3, 4

@@
 Fuzzy extractors convert a noisy source of entropy into a consistent uniformly distributed key.
-In the process of eliminating noise, they necessarily lose some of the entropy of the original source.
-We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.
+In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns.
+We call what is left after this worst-case loss the \emph{minimum usable entropy}.
 Unfortunately, this quantity is negative for some sources that are important in practice.
 
-We construct fuzzy extractors that work for distributions in which the minimum usable entropy is \emph{negative}.
-Such constructions must, necessarily, put additional limits on the distribution beyond its starting entropy.
-We show two constructions that have computational security for Hamming distance over large alphabets.
-The first requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
-The second requires  a constant fraction  symbols to have a constant amount of entropy conditioned on prior symbols.
-Our constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+We construct fuzzy extractors with computational security that work for distributions in which the minimum usable entropy is negative.
+They correct Hamming errors over a large alphabet.
+In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
+Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+Our second construction requires  a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
+The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
 
@@
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-Let $|W|$ be the size of the support of $W$ that is $|W| = |\{w | \Pr[W=w]>0\}|$.
+For a random variable $W$, let $H_0(W)$ \lnote{I decided, after all, that $H_0(W)$ is less ambiguous and probably more commonly used than $|\cdot |$} be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
+For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
 We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
@@
 \label{cl:many locations ent}
-Let $C$ be a binary code and let $\mathcal{I}^c$ be a set of indices of $C$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \log |C| - |\mathcal{I}^c|$.
+Let $C$ be a subset of $\{0,1\}^\ell$ with a uniform distribution, and let $\mathcal{I}\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{\mathcal{I}^c}) =  H_0(C) - |\mathcal{I}^c|$.
 \end{claim}
@@
 \label{def:obf} Let $\mathtt{I}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is a $\ell$-composable VGB obfuscator for $\mathtt{I}$ with auxiliary-input if the following conditions are met:
+A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}$ with auxiliary-input if the following conditions are met:
 \begin{enumerate}
@@
 \[
-|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
 \]
@@
 \end{definition}
-In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness.
+In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
 In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.
@@
 We follow the second approach.
-In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.
+In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
 To overcome these bounds, we use a computational version of a fuzzy conductor.
@@
 denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
-\end{definition}
+\end{definition} \lnote{I haven't checked this section below this line}
 We now define a computational fuzzy conductor and a (computational)~randomness extractor.
@@
 A computational extractor is the adaption of a randomness extractor to the computational setting.
-Any information-theoretic randomness extractor is also a computational extractor.
+Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained.
 We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
@@
 \label{sec:construction}
-For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.  Our goal is to derive strong keys for a large class of sources where $0>\Huse = \Hoo(W) - \log|B_t|$.
-In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
-We focus on building a computational fuzzy conductor with meaningful output entropy.
-Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.
+Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
+In the computational setting, a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
+We therefore focus on building a computational fuzzy conductor with meaningful output entropy.\lnote{where do we talk about running it multiple times if we don't get enough output from one run?}  Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
 
@@
 \label{cons:first construction}
-Let $n$ be a security parameter, let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $n$ be a security parameter \lnote{it's not clear how this parameter is used in the construction}, let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
 Let $\mathcal{O}$ be an obfuscator for the family of point functions $\mathtt{I}_{\mathcal{Z}}$.
@@
 
-The input $w$ is hidden in two different ways.  In locations where $c_i=1$ the block $w_i$ is information-theoretically unknown.
-In locations where $c_i=0$ it is hard to find $w_i$ given access to the point obfuscation.
-There are two possible reasons for a bit $c_i'$ to be $1$.
-Because the true value was $1$ and because $w_i \neq w_i'$.
-However if a bit $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when $c_i=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
+The input $w$ is hidden in two different ways.  In locations where $c_i=1$, the block $w_i$ is information-theoretically unknown.
+In locations where $c_i=0$, it is hard to find $w_i$ given access to the point obfuscation.
+There are two possible reasons for a bit $c_i'$ to be $1$: because the true value was $1$ and because $w_i \neq w_i'$.
+However, if a bit $c_i'$ is $0$, this likely means that $w_i=w_i'$ because collisions when $c_i=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
 This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
 
-\consref{cons:first construction} is secure if no distinguisher can tell whether they are working with random obfuscations or obfuscations of $W_i$.
+\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_i$.
 By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
small changes to intro

@@
 The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ comes from a high-quality distribution (traditionally, any distribution with sufficient min-entropy $m$).
+The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ comes from a high-quality distribution (traditionally, any distribution with sufficient min-entropy $m$).
 The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\ell$ strings over some alphabet $\mathcal{Z}$).
@@
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-Let the outcome of this transform define the distribution $w$.
+Let the outcome of this transform~(on different irises) define a distribution $w$.
 The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
@@
 \]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}  No current fuzzy extractor is known to work for irises.
-\lnote{I want to remove this last sentence because we don't solve this problem}
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
 
@@
 We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
-As explained above, such constructions cannot work without some restrictions on the distribution.
+As explained above, such constructions cannot work without some restriction on the distribution.
 Our first construction is secure when symbols in $w$
@@
 Our constructions are computationally secure.
-Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because then they would prove security, in particular, for the distribution that is contained withing a single ball of radius of $t$).
-\bnote{something about the parenthetical statement I don't like} \lnote{better?}
-
-Most known constructions of fuzzy extractors put sufficient information in $p$ to recover $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
+Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).
+
+Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
 Fuller, Meng, and Reyzin~\cite{fuller2013computational} show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
@@
 Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
-We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}:\bnote{I thought you didn't like this name?}  \lnote{I found a way to work it in that is less self-conscious, so I am ok with it now; in general, I remembered that naming constructions is a good idea} it converts $w$ to a string of blocks and then applies the first construction.
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it converts $w$ to a string of blocks and then applies the first construction.
 $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.\bnote{$w$ isn't converted as there is a reasonable prob that some blocks are not used at all.} \lnote{are you saying conversion must ``use" all input bits or be bijective or something?
@@
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-For a random variable $W$, let $H_0(W)$ \lnote{I decided, after all, that $H_0(W)$ is less ambiguous and probably more commonly used} be the size of the support of $W$,  that is $H_0(W) = |\{w | \Pr[W=w]>0\}|$.
+For a random variable $W$, let $H_0(W)$ \lnote{I decided, after all, that $H_0(W)$ is less ambiguous and probably more commonly used than $|\cdot |$} be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
@@
 \label{cl:many locations ent}
-Let $C$ be a subset of $\{0,1\}^\ell$ with a uniform distribution, and let $\mathcal{I}\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \log |C| - |\mathcal{I}^c|$.
+Let $C$ be a subset of $\{0,1\}^\ell$ with a uniform distribution, and let $\mathcal{I}\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{\mathcal{I}^c}) =  H_0(C) - |\mathcal{I}^c|$.
 \end{claim}
@@
 This means that
-\begin{align*}
-\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i\\
-&> \log {\ell \choose t} (|\mathcal{Z}|-1)^t\\
-& =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
-% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
-\end{align*}
+\[
+\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
+\]
 
@@
 That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
-If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.
-However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
+If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} can be adapted to a polynomial size alphabet $\mathcal{Z}$ by using a code that corrects Hamming errors~(with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable).
+%However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
 \bibliographystyle{alpha}

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
going through 2, 3, 4

@@
 For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.
-For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
+For a set of indices $\mathcal{I}$ \lnote{I suggest replacing $\mathcal{I}$ with something else, since we use $I$ also in obfuscation and it gets really confusing},  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
 The set $\mathcal{I}^c$ is the complement of $\mathcal{I}$.
@@
 
-\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$}
+\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}
 
@@
 By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-More formally, our construction is secure as long as enough blocks are unpredictable after adaptive queries:
+More formally, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
+This restriction on the distribution is captured in the following definition.
 
@@
 \label{def:block guessable}
-Let $I_w = (I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(\cdot, \cdot)$ be an oracle that returns \[(I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(i, w_i')=
+Let $I_w (\cdot, \cdot)= (I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(\cdot, \cdot)$ \lnote{why do we need such a long oracle name -- it's intimidating.
+Can't we call it just $I_w$?} be an oracle that returns \[I_w(i, w_i')=
 \begin{cases}
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $I$ making at most $q$ queries
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ \lnote{$\mathcal{I}$ confusingly interacts with the oracle name while it has nothing to do with it} of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $I$ making at most $q$ queries
 \[
@@
 \end{definition}
+\lnote{stopped going through section 4 here}
 

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
notational changes

@@
 
-We note that the problem of fuzzy extractors remains non-trivial even given the recent construction of general purpose indistinguishably obfuscation \cite{GargGH0SW13,PST13}, as the weaker notion of indistinguishably obfuscation seem to be insufficient for our application."
+We note that the problem of fuzzy extractors remains non-trivial even given the recent construction of general purpose indistinguishably obfuscation \cite{GargGH0SW13,PST13}, as the weaker notion of indistinguishably obfuscation seems insufficient for our application.\bnote{this sentence needs to be cleaned up} \bnote{what is PST?}
 
@@
 Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
-We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it converts $w$ to a string of blocks and then applies the first construction.
-$\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.\bnote{$w$ isn't converted as there is a reasonable prob that some blocks are not used at all.} \lnote{are you saying conversion must ``use" all input bits or be bijective or something?
-is it just a question of what the word ``convert'' means?} This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into to a string of blocks and then applies the first construction.
+$\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.
+This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
 This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
@@
 For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.
-For a set of indices $\mathcal{I}$ \lnote{I suggest replacing $\mathcal{I}$ with something else, since we use $I$ also in obfuscation and it gets really confusing},  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
-The set $\mathcal{I}^c$ is the complement of $\mathcal{I}$.
+For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
+The set $J^c$ is the complement of $J$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-For a random variable $W$, let $H_0(W)$ \lnote{I decided, after all, that $H_0(W)$ is less ambiguous and probably more commonly used than $|\cdot |$} be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
+For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
@@
 
-\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}
+\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}\bnote{I think so, what would need to change?
+I think we might also be able to deal with just random neighbors?}
 
@@
 \label{cl:many locations ent}
-Let $C$ be a subset of $\{0,1\}^\ell$ with a uniform distribution, and let $\mathcal{I}\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{\mathcal{I}^c}) =  H_0(C) - |\mathcal{I}^c|$.
+Let $C$ be a subset of $\{0,1\}^\ell$ with a uniform distribution, and let $J\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{J^c}) =  H_0(C) - |J^c|$.
 \end{claim}
@@
 
+For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
 \section{Computational Fuzzy Extractors}
@@
 In the computational setting, a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
-We therefore focus on building a computational fuzzy conductor with meaningful output entropy.\lnote{where do we talk about running it multiple times if we don't get enough output from one run?}  Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+We therefore focus on building a computational fuzzy conductor with meaningful output entropy.\lnote{where do we talk about running it multiple times if we don't get enough output from one run?} \bnote{nowhere, it was something I realized yesterday.
+For second construction it doesn't make much sense, just increase $\ell$ has same effect.} Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
 
@@
 \label{def:block guessable}
-Let $I_w (\cdot, \cdot)= (I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(\cdot, \cdot)$ \lnote{why do we need such a long oracle name -- it's intimidating.
-Can't we call it just $I_w$?} be an oracle that returns \[I_w(i, w_i')=
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(i, w_i')=
 \begin{cases}
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ \lnote{$\mathcal{I}$ confusingly interacts with the oracle name while it has nothing to do with it} of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $I$ making at most $q$ queries
-\[
-\forall i\in \mathcal{I}, \Hav(W_i |View(A^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I$ making at most $q$ queries
+\[
+\forall i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
 \]
@@
 It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
-Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.
+Let $J$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.
 We first note that $C'$ has sufficient entropy.
-That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.
+That is, $\Hav(C' |P) =\Hav(C' | C_{J^c} = C'_{J^c}) = |C| - |J^c|$.
 It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
@@
 \end{proof}
-We now argue correctness of \consref{cons:first construction}.
+We now a rgue correctness of \consref{cons:first construction}.
 We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
@@
 \label{def:partial source}
-A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}) \geq \alpha.
+A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall i\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}) \geq \alpha.
 \]
@@
 \end{align*}
-\lnote{we should explain what this t means -- the formula is too complex. Also, we seem to require large alphabet size -- is it only because of $\delta$?}
-\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$.}
+\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
 \end{theorem}
@@
 
-\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
+\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Not for submission.}
 \begin{lemma}
@@
 Let $\alpha$ be a parameter.
-Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.
-Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-unguessable block distribution.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-unguessable block distribution.
+Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in J$, $\Hoo(W_i ) =\alpha $.
+Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |J|)$-unguessable block distribution.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |J|)$-unguessable block distribution.
 \end{claim}
 \begin{proof}
-It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
+It suffices to show that for all $i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
 We can ignore queries for all blocks but the $i$th, as the blocks are independent.
@@
 \begin{definition}
-Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $J(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
+Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $\mathtt{Jump}(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
 \end{definition}
@@
 \begin{claim}
-Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $J(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $\mathtt{Jump}(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
 \end{claim}
@@
 
-By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.
-Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.
-Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.
-By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.
+By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.
+Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.
+Then $C | C_{J^c} \overset{d}=C'$.
+By \clref{cl:many locations ent}, we have that $\Hav(C|C_{J^c} )= |C| -\beta$ and thus $\Hav(C'| C_{J^c}) = |C| -\beta$.
 Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that
@@
 \begin{proof}
-\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
+\noindent It suffices to show that for any two codewords that agree on $J^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
 \begin{lemma}
@@
 \begin{proof}
-Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.
+Recall that for all $i\in J$, $\Hav(W_i | View(S))\geq \alpha$.
 The only information about the correct value of $c_i^*$ is contained in the query responses.
 When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
-We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.
+We now show that for any value of $c^*$ all queries on $i \in J$ return $0$ with probability $1-2^{-\alpha+1}$.
 Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
@@
 If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
-Recall that $c^*, c'$ match on all indices outside of $\mathcal{I}$.
+By the union bound over the indices $i\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+Recall that $c^*, c'$ match on all indices outside of $J$.
 Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
@@
 Consider some fixed $i$.
-Recall that there a set $\mathcal{I}$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in \mathcal{I}$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $\cal{I}$.
-Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap \mathcal{I}|$.
+Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
+Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
 
@@
 \Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
-&\ge \sum_{j_k\in \mathcal{I}} \alpha = \alpha X
+&\ge \sum_{j_k\in J} \alpha = \alpha X
 \end{align*}

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex

@@
 Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
-We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieved notions of obfuscation seem to be insufficient.
-
-We note that the problem of fuzzy extractors remains non-trivial even given the recent construction of general purpose indistinguishably obfuscation \cite{GargGH0SW13,PST13}, as the weaker notion of indistinguishably obfuscation seems insufficient for our application.\bnote{this sentence needs to be cleaned up} \bnote{what is PST?}
+
+We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
+However, currently we do not know if such obfuscation exists.
+Recent works constructed candidates indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
+However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
+The work of \cite{BarakBCKPS13} suggest an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero.
+However, we do not know if these functions include proximity point programs.
 

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
hartley entropy

@@
 For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.
-For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.
-The set $\mathcal{I}^c$ is the complement of $\mathcal{I}$.
+For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
+The set $J^c$ is the complement of $J$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-For a random variable $W$, let $H_0(W)$ \lnote{I decided, after all, that $H_0(W)$ is less ambiguous and probably more commonly used than $|\cdot |$} be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
+For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
@@
 
-\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$}
+\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}\bnote{I think so, what would need to change?
+I think we might also be able to deal with just random neighbors?}
 
@@
 \label{def:block guessable}
-Let $I_w = (I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(\cdot, \cdot)$ be an oracle that returns \[(I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(i, w_i')=
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(i, w_i')=
 \begin{cases}
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $I$ making at most $q$ queries
-\[
-\forall i\in \mathcal{I}, \Hav(W_i |View(A^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I$ making at most $q$ queries
+\[
+\forall i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
 \]
 \end{definition}
+\lnote{stopped going through section 4 here}
 
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of $v_i$s.
+A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of the $v_i$'s.
 
@@
 \Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
-&=\Hoo(W_i) - |A_1, \dots, A_q|\\
+&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
 &=\alpha - \log (q+1)\,,
@@
 If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$.
-Recall that $c^*, c'$ match on all indices outside of $\mathcal{I}$.
+By the union bound over the indices $i\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+Recall that $c^*, c'$ match on all indices outside of $J$.
 Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
-This concludes the proof of \lemref{lem:codewords in I close}
+This concludes the proof of \lemref{lem:codewords in I close}.
 \end{proof}

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
hartley entropy for C

--- 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
@@
 Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
- Codes where $\log |C| = \Theta(\ell)$ and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+ Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
 These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
@@
 Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C)- \beta$.
 \end{theorem}
@@
 Let all variables be as in \thref{thm:main thm first cons}.
-For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
+For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
 \end{lemma}
@@
 We first note that $C'$ has sufficient entropy.
-That is, $\Hav(C' |P) =\Hav(C' | C_{J^c} = C'_{J^c}) = |C| - |J^c|$.
+That is, $\Hav(C' |P) =\Hav(C' | C_{J^c} = C'_{J^c}) = H_0(C) - |J^c|$.
 It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
@@
 \]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
+When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
 %Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
@@
 t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
-\tilde{m} &=|C|\\
+\tilde{m} &=H_0(C)\\
 \delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
@@
 Let all the variables be as in \thref{thm:sampling}.
-For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$.
+For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq H_0(C)$.
 %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
@@
 Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
-Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq |C|- \beta$.
+Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$.
 % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
-Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < |C|-\beta$.
+Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
 
@@
 Then $C | C_{J^c} \overset{d}=C'$.
-By \clref{cl:many locations ent}, we have that $\Hav(C|C_{J^c} )= |C| -\beta$ and thus $\Hav(C'| C_{J^c}) = |C| -\beta$.
+By \clref{cl:many locations ent}, we have that $\Hav(C|C_{J^c} )= H_0(C) -\beta$ and thus $\Hav(C'| C_{J^c}) = H_0(C) -\beta$.
 Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that
@@
 Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
-This concludes the proof of \lemref{lem:codewords in I close}
+This concludes the proof of \lemref{lem:codewords in I close}.
 \end{proof}

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
fixing svn problem adding omer text back

@@
 \end{definition}
-
 For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
did a pass through most of 4 and 5

@@
 \lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}\bnote{I think so, what would need to change?
-I think we might also be able to deal with just random neighbors?}
+I think we might also be able to deal with just random neighbors?}\lnote{I don't see anything that else in the paper would change if we simply changed how probability is taken here (but please check if I am mistaken); I don't think we can deal with random neighbors, since errors in $w'$ translate to code errors, and errors in $w'$ can be adversarial}
 
@@
 \label{def:block guessable}
-Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(i, w_i')=
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
 \begin{cases}
-1 & w_i = w_i'\\
+1 & w_j = w_j'\\
 0 & \text{otherwise}.
@@
 \[
-\forall i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
 \]
@@
 
-We discuss unguessable block distributions in \apref{sec:characterize}.
-In particular any source $W$ where for all $i$, $\Hoo(W_i) \geq \omega(\log n)$~(all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
+We show some examples of unguessable block distributions in \apref{sec:characterize}.
+In particular, any source $W$ where for all $i$, $\Hoo(W_i) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
 
@@
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C)- \beta$.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$ \lnote{and security parameter $n$?}.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C) - \beta$.
 \end{theorem}
@@
 
-We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
+We give a brief outline of the proof here; the proof is in \apref{app:security of main cons}.
 \begin{proof}[Outline]
@@
 Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
-Correction occurs for a small number of dimensions that are allowed to vary completely.
+Correction occurs for a small \lnote{why small?
+constant fraction, right?} number of dimensions that are allowed to vary completely.
 \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries.
+\lnote{has all this already been said in the intro and more formally in she statements of the theorems?
+Do we need to repeat it here?}
 
@@
 
-\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to \consref{cons:first construction}.
+\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
+Do we need it?} There are three major drawbacks to \consref{cons:first construction}.
 First, we require blocks to be super-polynomial in size.
 Second, we only obtain a single bit from each block.
-Third, since each block is individually obfuscated, we leak information about individual blocks.
-To compensate for this leakage, we need most blocks to be unguessable given equality queries.
+Third, since each block is individually obfuscated, we leak information about individual blocks if they can be guessed.
+To compensate for this leakage, we need most\lnote{just some linear fraction, not most, right?
+and, in fact, isn't just one block enough given our repeated use argument which we haven't really made yet?} blocks to be unguessable given equality queries.
 Our second construction addresses this last weakness.
@@
 Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.
-This may be an unreasonable requirement.
 In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously, at the price of  decreasing the effective error tolerance.
 %In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
-The main idea is to sample a random subset of blocks $W_{i_1},..., W_{i_\eta}$ and obfuscate the concatenation of these blocks.
+The main idea is to sample a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscate the concatenation of these blocks.
 Denote this concatenated value by $V_1$.
@@
 \[
-\forall i\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}) \geq \alpha.
+\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
 \]
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of the $v_i$'s.
+A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $v_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of the $v_i$ values.
 
@@
 We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.
-The required entropy of  an partial block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
+The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
 We are able to correct $O(\gamma/\eta)$ errors.
@@
 That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
-If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} can be adapted to a polynomial size alphabet $\mathcal{Z}$ by using a code that corrects Hamming errors~(with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable).
+We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (we need it because with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
 %However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
@@
 Let $W = W_1,  ...
-, W_\ell$ be a source in which all blocks $W_i$  are mutually independent.
+, W_\ell$ be a source in which all blocks $W_j$  are mutually independent.
 Let $\alpha$ be a parameter.
-Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in J$, $\Hoo(W_i ) =\alpha $.
+Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.
 Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |J|)$-unguessable block distribution.
@@
 \begin{proof}
-It suffices to show that for all $i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
-We can ignore queries for all blocks but the $i$th, as the blocks are independent.
+It suffices to show that for all $j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
+We can ignore queries for all blocks but the $j$th, as the blocks are independent.
 Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice).
 Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block.
-Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed).
+Each $A_k$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed).
 Thus, the total number of possible responses is $q+1$.
@@
 \begin{align*}
-\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
-&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
+\Hav(W_j | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
+&=\Hoo(W_j) - |A_1, \dots, A_q|\\
 &=\alpha - \log (q+1)\,,
@@
 Let $f:\zo^e \rightarrow \mathcal{Z}^\ell$ be a function.
-Furthermore, let $f_i$ denote the restriction of $f$'s output to its $i$th coordinate.
-If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
+Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.
+If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
 \end{claim}
 \begin{proof}
-Since $f$ is injective on each block, $\Hav(W_i | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
-Consider a query $q_j$ on block $i$.
-There are two possibilities: either $q_j$ is not in the image of $f_i$,  or $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.
+Since $f$ is injective on each block, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
+Consider a query $q_k$ on block $j$.
+There are two possibilities: either $q_k$ is not in the image of $f_j$,  or $q_k$ can be considered a query on the preimage $f_j^{-1}(q_k)$.
 Then (by assuming $S$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.
@@
 proof of \clref{cl:independent high ent}),
- and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(S^{I_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
+ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $j$, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) \geq \Hoo(W_j) -\log (q+1)$.
 \end{proof}
@@
 
-We can prove a slightly weaker claim when the correlation between the coordinates $W_i$ is arbitrary:
+We can prove a slightly weaker claim when the correlation between the coordinates $W_j$ is arbitrary:
 
@@
 Let $W = W_1,..., W_\ell$ be a source.
-Suppose that for all $i$, $\Hoo(W_i)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is superlogarithmic).
+Suppose that for all $j$, $\Hoo(W_j)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is superlogarithmic).
 Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block distribution.
@@
 using the same notation as in the proof of   \clref{cl:independent high ent}. Our inductive hypothesis is
-that $\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0] \leq (j-1)2^{1-\alpha}$.  If the inductive hypothesis holds, then, for each $i$,
+that $\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0] \leq (k-1)2^{1-\alpha}$.  If the inductive hypothesis holds, then, for each $j$,
 \begin{equation}
 \label{eq:cond-entropy}
-\Hoo(W_i | A_1= \dots= A_{j-1}=0) \ge \alpha-1\,.
+\Hoo(W_j | A_1= \dots= A_{k-1}=0) \ge \alpha-1\,.
 \end{equation}
-This is true for $j=1$ by the condition of the theorem. It is true for $j>1$ because, as a consequence of the definition of $\Hoo$,
-for any random variable $X$ and event $E$, $\Hoo(X|E)\ge \Hoo(X)+\log\Pr[E]$; and $(j-1) 2^{1-\alpha}\leq 2 q 2^{-\alpha} \leq 1/2$.
-
-We now show that $\Pr[A_1\neq 0 \vee \dots \vee A_{j}\neq 0] \leq j2^{1-\alpha}$, assuming that $\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0] \leq (j-1)2^{1-\alpha}$.
+This is true for $k=1$ by the condition of the theorem. It is true for $k>1$ because, as a consequence of the definition of $\Hoo$,
+for any random variable $X$ and event $E$, $\Hoo(X|E)\ge \Hoo(X)+\log\Pr[E]$; and $(k-1) 2^{1-\alpha}\leq 2 q 2^{-\alpha} \leq 1/2$.
+
+We now show that $\Pr[A_1\neq 0 \vee \dots \vee A_{k}\neq 0] \leq k 2^{1-\alpha}$, assuming that $\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0] \leq (k-1)2^{1-\alpha}$.
 \begin{align*}
-\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0 \vee A_j\neq 0] & =
-\Pr[A_1\neq 0 \vee \dots \vee A_{j-1}\neq 0]+\Pr[A_1=\dots = A_{j-1}=0 \wedge A_j=1]\\
-& \le  (j-1)2^{1-\alpha}+\Pr[A_j=1\,|\,A_1=\dots = A_{j-1}=0]\\
-& \le  (j-1)2^{1-\alpha}+\max_i 2^{-\Hoo(W_i | A_1=\dots =A_{j-1}=0)}\\
-& \le  (j-1)2^{1-\alpha}+ 2^{1-\alpha}\\
-& = j 2^{1-\alpha}
+\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0 \vee A_k\neq 0] & =
+\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0]+\Pr[A_1=\dots = A_{k-1}=0 \wedge A_k=1]\\
+& \le  (k-1)2^{1-\alpha}+\Pr[A_k=1\,|\,A_1=\dots = A_{k-1}=0]\\
+& \le  (k-1)2^{1-\alpha}+\max_j 2^{-\Hoo(W_j | A_1=\dots =A_{k-1}=0)}\\
+& \le  (k-1)2^{1-\alpha}+ 2^{1-\alpha}\\
+& = k 2^{1-\alpha}
 \end{align*}
-(where the third line follows by considering that to get $A_j=1$, the adversary needs to guess some $W_i$, and the fourth line follows by~\eqref{eq:cond-entropy}).
-Thus, using $j=q+1$ in~\eqref{eq:cond-entropy},
- we know $\Hoo(W_i | A_1= \dots= A_q=0) \ge \alpha-1$.  Finally this means that
+(where the third line follows by considering that to get $A_k=1$, the adversary needs to guess some $W_j$, and the fourth line follows by~\eqref{eq:cond-entropy}).
+Thus, using $k=q+1$ in~\eqref{eq:cond-entropy},
+ we know $\Hoo(W_j | A_1= \dots= A_q=0) \ge \alpha-1$.  Finally this means that
 \begin{align*}
-\Hav(W_i | A_1,\dots, A_q) &\ge -\log \left( 2^{-\Hoo(W_i | A_1= \dots= A_q=0)}\Pr[A_1=\dots=A_q=0]+1\cdot \Pr[A_1\neq 0 \vee \dots \vee  A_q\neq 0] \right)\\
-& \ge -\log \left(  2^{-\Hoo(W_i | A_1= \dots= A_q=0)}+q2^{1-\alpha} \right)\\
+\Hav(W_j | A_1,\dots, A_q) &\ge -\log \left( 2^{-\Hoo(W_j | A_1= \dots= A_q=0)}\Pr[A_1=\dots=A_q=0]+1\cdot \Pr[A_1\neq 0 \vee \dots \vee  A_q\neq 0] \right)\\
+& \ge -\log \left(  2^{-\Hoo(W_j | A_1= \dots= A_q=0)}+q2^{1-\alpha} \right)\\
 & \ge -\log \left(  (q+1) 2^{1-\alpha}\right) = \alpha-1-\log(q+1)\,.
@@
 \begin{claim}
-Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
+Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
 There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
@@
 This process is repeated until $W_{\ell-\beta+1}$ is learned.
-Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_i | W_1,.., W_{i-1}$.
+Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_j | W_1,.., W_{j-1}$.\lnote{what does this last half-sentence mean}
 \end{proof}
@@
 Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
-
+\lnote{some $i$s should be changed to $j$s below this line, but I ran out of time; will do}
 By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
dealing with notes

@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh_t(c), \Pr[\rec(c') \neq c] \leq \delta_{code}$.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that for all $c\in C, \forall c'\in \neigh_t(c), \Pr[\decode(c') \neq c] \leq \delta_{code}$.
 \end{definition}
@@
 \label{cons:first construction}
-Let $n$ be a security parameter \lnote{it's not clear how this parameter is used in the construction}, let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
 Let $\mathcal{O}$ be an obfuscator for the family of point functions $\mathtt{I}_{\mathcal{Z}}$.
@@
 \label{thm:main thm first cons}
+Let $n$ be a security parameter.
 Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_i$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$ \lnote{and security parameter $n$?}.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.
 Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C) - \beta$.
@@
 
-\subsection{Discussion}
+\subsection{Discussion of \consref{cons:first construction}}
 \label{sec:discussion}
-Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
-Correction occurs for a small \lnote{why small?
-constant fraction, right?} number of dimensions that are allowed to vary completely.
-\consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries.
-\lnote{has all this already been said in the intro and more formally in she statements of the theorems?
-Do we need to repeat it here?}
-
 To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.
@@
 When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
-%Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
-%We achieve security when $\Huse\le 0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
-%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
-
-\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
+
+%\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
 Do we need it?} There are three major drawbacks to \consref{cons:first construction}.
@@
 \label{cons:sampling}
-Let $n$ be a security parameter.
 Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$.
@@
 That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
-We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (we need it because with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
+We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
 %However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
@@
 This process is repeated until $W_{\ell-\beta+1}$ is learned.
-Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_j | W_1,.., W_{j-1}$.\lnote{what does this last half-sentence mean}
+Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to sample from $W_j | W_1,.., W_{j-1}$.
 \end{proof}

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
minor clean up; i->j changes

@@
 Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
-Let $w=w_1 \dots w_\ell$, for $w_i\in \mathcal{Z}$.
-In the first construction (\consref{cons:first construction}), for each $i$, $\gen$ flips a coin $c_i$ and either obfuscates $I_{w_i}$ or picks a random point $r_i$ and obfuscates $I_{r_i}$.
+Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$.
+In the first construction (\consref{cons:first construction}), for each $j$, $\gen$ flips a coin $c_j$ and either obfuscates $I_{w_j}$ or picks a random point $r_j$ and obfuscates $I_{r_j}$.
 This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
-With a close value $w'$, $\rep$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
-For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.
-Thus, most bits of $c_i$ are recoverable.
+With a close value $w'$, $\rep$ then runs the obfuscated program $P_j$ on $w_j'$ and checks whether $P_j(w_j')=1$.
+For most locations $j$, \rep can determine whether $w_j$ or a random value was obfuscated.
+Thus, most bits of $c_j$ are recoverable.
 To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code.
@@
 \label{sec:preliminaries}
-For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.
+For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.
 For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that for all $c\in C, \forall c'\in \neigh_t(c), \Pr[\decode(c') \neq c] \leq \delta_{code}$.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
+} \decode(c') \neq c] \leq \delta_{code}$.
 \end{definition}
-
-\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}\bnote{I think so, what would need to change?
-I think we might also be able to deal with just random neighbors?}\lnote{I don't see anything that else in the paper would change if we simply changed how probability is taken here (but please check if I am mistaken); I don't think we can deal with random neighbors, since errors in $w'$ translate to code errors, and errors in $w'$ can be adversarial}
 
@@
 \item Sample $c\leftarrow C$.
-\item For $i=1,..., \ell$:
+\item For $j=1,..., \ell$:
 \begin{enumerate}[(i)]
-\item If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
-\item Else: Sample $r_i \overset{\$}\leftarrow \mathcal{Z}$.
-\subitem Let $p_i = \mathcal{O}(I_{r_i})$.
+\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
+\item Else: Sample $r_j \overset{\$}\leftarrow \mathcal{Z}$.
+\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
 \end{enumerate}
-\item Output $(c, p)$.
+\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
 \end{enumerate}
@@
 \item \underline{Input}: $(w', p)$
-\item For $i=1,..., \ell$:
+\item For $j=1,..., \ell$:
 \begin{enumerate}[(i)]
-\item If $p_i(w_i') = 1$: set $c_i' = 0$.
-\item Else: set $c_i' = 1$.
+\item If $p_j(w_j') = 1$: set $c_j' = 0$.
+\item Else: set $c_j' = 1$.
 \end{enumerate}
@@
 
-The input $w$ is hidden in two different ways.  In locations where $c_i=1$, the block $w_i$ is information-theoretically unknown.
-In locations where $c_i=0$, it is hard to find $w_i$ given access to the point obfuscation.
-There are two possible reasons for a bit $c_i'$ to be $1$: because the true value was $1$ and because $w_i \neq w_i'$.
-However, if a bit $c_i'$ is $0$, this likely means that $w_i=w_i'$ because collisions when $c_i=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
+The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
+In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
+There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
+However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
 This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
 
-\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_i$.
+\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
 By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
@@
 We show some examples of unguessable block distributions in \apref{sec:characterize}.
-In particular, any source $W$ where for all $i$, $\Hoo(W_i) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
+In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
 
@@
 Let $n$ be a security parameter.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_i$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_j$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
@@
 Recall that $c$ contains at most $\ell$ $1$s.
-Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/|\mathcal{Z}|$.
-Since the $r_i$ are chosen independently, one has,
-\[
-\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{|\mathcal{Z}|}.
+Since $w'$ is chosen independently of the points $r_j$, this probability is the size of each block, that is $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$.
+Since the $r_j$ are chosen independently, one has,
+\[
+\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_j = w_j']\geq 1-\sum_{j=1}^\ell \Pr[r_j = w_j'] \geq 1-\frac{\ell}{|\mathcal{Z}|}.
 \]
@@
 We now consider the number of possible $0\rightarrow 1$ bit flips in $c$.
-A $0\rightarrow 1$ flip on index $i$ occurs when two conditions are met $w_i\neq w_i'$ and $c_i = 0$.
+A $0\rightarrow 1$ flip on index $j$ occurs when two conditions are met $w_j\neq w_j'$ and $c_j = 0$.
 Since the first conditioned is only fulfilled at most $t$ times, we have the following lemma:
@@
 
-\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+\Omega(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
+\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+\Omega(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_j =1$.
 This requires a code where most codewords have Hamming weight close to $1/2$.
@@
 \label{cons:sampling}
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$.
 %and $\gamma = \Omega(n)$.
@@
 Define the distribution $X$ as follows:
-\[X_i =
+\[X_j =
 \begin{cases}
-W_i & C_i = 0\\
-R_i & C_i = 1.
+W_j & C_j = 0\\
+R_j & C_j = 1.
 \end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
@@
 \begin{proof}
-Recall that for all $i\in J$, $\Hav(W_i | View(S))\geq \alpha$.
-The only information about the correct value of $c_i^*$ is contained in the query responses.
+Recall that for all $j\in J$, $\Hav(W_j | View(S))\geq \alpha$.
+The only information about the correct value of $c_j^*$ is contained in the query responses.
 When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
-We now show that for any value of $c^*$ all queries on $i \in J$ return $0$ with probability $1-2^{-\alpha+1}$.
-Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.
-Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
+We now show that for any value of $c^*$ all queries on $j \in J$ return $0$ with probability $1-2^{-\alpha+1}$.
+Suppose not, that is suppose, the probability of at least one nonzero response on index $j$ is $> 2^{-(\alpha+1)}$.
+Since $w, w'$ are independent of $r_j$, the probability of this happening when $c^*_j = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
 Thus, it must occur with probability:
 \begin{align}
-2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
- &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
-&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
+2^{-\alpha+1}&<\Pr[\text{non zero response location }j]\nonumber \\
+ &= \Pr[c_j^* =1]\Pr[\text{non zero response location }j\wedge c_j^*=1]\nonumber \\&+ \Pr[c_j^*=0] \Pr[\text{non zero response location }j \wedge c_j^*=0]\nonumber \\
+&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }j \wedge c_j^*=0] \label{eq:ways to remove ent}
 \end{align}
@@
 It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.
-Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.
+Let $W_j$ be a distribution.
+Consider $S$ that asks the $q$ most likely outcomes.
+The total probability\lnote{what does total probability mean?} of this block\lnote{symbol?} must be at least $2^{-n+\log q}$.
 After these queries the remaining min-entropy is at most:
 \begin{align*}
-\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
+\Hav(W_j | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
 &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
@@
 \begin{align*}
- \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
+ \Pr[\text{non zero response location }j \wedge c_j=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
  \end{align*}
- When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.
+ When there is a $1$ response and $c_j=0$ this means that there is no remaining min-entropy.
 If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-By the union bound over the indices $i\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+By the union bound over the indices $j\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$.
 Recall that $c^*, c'$ match on all indices outside of $J$.

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
minor cleanup

@@
 
-\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) as only some blocks are required to have entropy conditioned on the past.
-The need for remaining entropy conditioned on the past is arbitrary.
-The actual requirement is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
+\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
+The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
 %Note a partial block source requires worst case entropy while an unguessable block distribution only requires average conditional entropy.
@@
 
-We use an algorithm that selects a fixed size random subset of $\{1,..., \gamma\}$.
-Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
+Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.
 
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $v_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of the $v_i$ values.
+A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
 
@@
 \subsection{Discussion of \consref{cons:sampling}}
+\lnote{I need to check this}
 We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.
@@
 \section{Fuzzy Conductors}
-
+\lnote{I need to check this}
 \label{sec:conductors}
@@
 \label{sec:cond and cext}
+\lnote{I need to check this}
 \begin{proof}
@@
 \begin{proof}
-
+\lnote{I need to check this}
 Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.
@@
 Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
-\lnote{some $i$s should be changed to $j$s below this line, but I ran out of time; will do}
 By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
reworded the abstract a bit

@@
 Unfortunately, this quantity is negative for some sources that are important in practice.
-
-We construct fuzzy extractors with computational security that work for distributions in which the minimum usable entropy is negative.
+Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used for such sources.
+
+We construct the first fuzzy extractors that work for a large class of distributions in which the minimum usable entropy is negative.
+Their security is computational.
 They correct Hamming errors over a large alphabet.
 In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
+
 Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
edited obfuscation paragraph

@@
 Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
-We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieved notions of obfuscation seem to be insufficient.
-
-We note that the problem of fuzzy extractors remains non-trivial even given the recent construction of general purpose indistinguishably obfuscation \cite{GargGH0SW13,PST13}, as the weaker notion of indistinguishably obfuscation seems insufficient for our application.\bnote{this sentence needs to be cleaned up} \bnote{what is PST?}
-
-Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
-Let $w=w_1 \dots w_\ell$, for $w_i\in \mathcal{Z}$.
-In the first construction (\consref{cons:first construction}), for each $i$, $\gen$ flips a coin $c_i$ and either obfuscates $I_{w_i}$ or picks a random point $r_i$ and obfuscates $I_{r_i}$.
+
+Both of our constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$.
+In the first construction (\consref{cons:first construction}), for each $j$, $\gen$ flips a coin $c_j$ and either obfuscates $I_{w_j}$ or picks a random point $r_j$ and obfuscates $I_{r_j}$.
 This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
-With a close value $w'$, $\rep$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.
-For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.
-Thus, most bits of $c_i$ are recoverable.
+With a close value $w'$, $\rep$ then runs the obfuscated program $P_j$ on $w_j'$ and checks whether $P_j(w_j')=1$.
+For most locations $j$, \rep can determine whether $w_j$ or a random value was obfuscated.
+Thus, most bits of $c_j$ are recoverable.
 To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code.
@@
 
+\paragraph{On the Relationship to General Obfuscation}
+We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
+However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
+Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
+However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
+The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero.
+However, we do not know if these functions include proximity point programs.
+
 \paragraph{Open Problems}
@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh_t(c), \Pr[\rec(c') \neq c] \leq \delta_{code}$.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
+} \decode(c') \neq c] \leq \delta_{code}$.
 \end{definition}
-
-\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}\bnote{I think so, what would need to change?
-I think we might also be able to deal with just random neighbors?}
 
@@
 
-We discuss unguessable block distributions in \apref{sec:characterize}.
-In particular any source $W$ where for all $i$, $\Hoo(W_i) \geq \omega(\log n)$~(all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
+We show some examples of unguessable block distributions in \apref{sec:characterize}.
+In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
 
@@
 \label{thm:main thm first cons}
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_i$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
+Let $n$ be a security parameter.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_j$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
 Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C)- \beta$.
+Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C) - \beta$.
 \end{theorem}
@@
 
-\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+\Omega(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.
+\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+\Omega(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_j =1$.
 This requires a code where most codewords have Hamming weight close to $1/2$.
 
-\subsection{Discussion}
+\subsection{Discussion of \consref{cons:first construction}}
 \label{sec:discussion}
-Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.
-Correction occurs for a small number of dimensions that are allowed to vary completely.
-\consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries.
-
 To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.
@@
 When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
-%Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.
-%We achieve security when $\Huse\le 0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
-%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
-
-\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to \consref{cons:first construction}.
+
+%\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
+Do we need it?} There are three major drawbacks to \consref{cons:first construction}.
 First, we require blocks to be super-polynomial in size.
 Second, we only obtain a single bit from each block.
-Third, since each block is individually obfuscated, we leak information about individual blocks.
-To compensate for this leakage, we need most blocks to be unguessable given equality queries.
+Third, since each block is individually obfuscated, we leak information about individual blocks if they can be guessed.
+To compensate for this leakage, we need most\lnote{just some linear fraction, not most, right?
+and, in fact, isn't just one block enough given our repeated use argument which we haven't really made yet?} blocks to be unguessable given equality queries.
 Our second construction addresses this last weakness.
@@
 \label{cons:sampling}
-Let $n$ be a security parameter.
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$.
 %and $\gamma = \Omega(n)$.
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of the $v_i$'s.
+A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
 
@@
 \subsection{Discussion of \consref{cons:sampling}}
+\lnote{I need to check this}
 We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.
-The required entropy of  an partial block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.
+The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
 We are able to correct $O(\gamma/\eta)$ errors.
@@
 That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
-If we are willing to accept $\Huse\geq 0$ then \consref{cons:sampling} can be adapted to a polynomial size alphabet $\mathcal{Z}$ by using a code that corrects Hamming errors~(with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable).
+We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
 %However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
@@
 This process is repeated until $W_{\ell-\beta+1}$ is learned.
-Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_i | W_1,.., W_{i-1}$.
+Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to sample from $W_j | W_1,.., W_{j-1}$.
 \end{proof}
@@
 Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
-
 By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
revised claim d.3

@@
 
-We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
-However, currently we do not know if such obfuscation exists.
-Recent works constructed candidates indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
-However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
-The work of \cite{BarakBCKPS13} suggest an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero.
-However, we do not know if these functions include proximity point programs.
-
-Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+Both of our constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
 Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$.
@@
 Computational, rather than information-theoretic, analysis seems crucial for achieving this property.
+
+\paragraph{On the Relationship to General Obfuscation}
+We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
+However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
+Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
+However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
+The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero.
+However, we do not know if these functions include proximity point programs.
 
@@
 Suppose not, that is suppose, the probability of at least one nonzero response on index $j$ is $> 2^{-(\alpha+1)}$.
-Since $w, w'$ are independent of $r_j$, the probability of this happening when $c^*_j = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.
+Since $w, w'$ are independent of $r_j$, the probability of this happening when $c^*_j = 1$ is at most $q/\mathcal{Z}$ or  equivalently $2^{-\log |\mathcal{Z}|+\log q}$.
 Thus, it must occur with probability:
@@
  &= \Pr[c_j^* =1]\Pr[\text{non zero response location }j\wedge c_j^*=1]\nonumber \\&+ \Pr[c_j^*=0] \Pr[\text{non zero response location }j \wedge c_j^*=0]\nonumber \\
-&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }j \wedge c_j^*=0] \label{eq:ways to remove ent}
+&\le 1\times 2^{-\log|\mathcal{Z}|+\log q} + 1\times  \Pr[\text{non zero response location }j \wedge c_j^*=0] \label{eq:ways to remove ent}
 \end{align}
-We now show that $n-\log q \geq \alpha$:
+We now show that for an unguessable block source the remaining entropy $\alpha\leq \log |\mathcal{Z}|-\log q $:
 \begin{claim}
 \label{cl:ent bounded away from n}
-$\alpha \le n-\log q$
+If $W$ is a $(q, \alpha, \beta)$-block unguessable distribution over $\mathcal{Z}$ then $\alpha \le \log |\mathcal{Z}|-\log q$.
 \end{claim}
 \begin{proof}
-It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.
-Let $W_j$ be a distribution.
-Consider $S$ that asks the $q$ most likely outcomes.
-The total probability\lnote{what does total probability mean?} of this block\lnote{symbol?} must be at least $2^{-n+\log q}$.
-After these queries the remaining min-entropy is at most:
+\bnote{Leo I changed some of this under you.  It wasn't clear or probably right as written.}
+\bnote{better name for guess, creativity is running low.}
+Let $W$ be a $(q, \alpha, \beta)$-block unguessable distribution.  Let $J\subset\{1,..., \ell\}$ the set of good indices.
+It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.
+Denote by $guess_{1}, ..., guess_q$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
+Note that $\sum_{i=1}^q \Pr[W_j = guess_i]\geq q/|\mathcal{Z}|$.
+Suppose not, this means that there is some $guess_i$ with probability $\Pr[W_j = guess_i] < 1/|\mathcal{Z}|$.
+Since there are $\mathcal{Z} - q $ remaining possible values of $W_j$ for their total probability to be at least $1-q/|\mathcal{Z}|$ at least of these values has probability at least $1/\mathcal{Z}$.
+This contradicts the statement $guess_1,..., guess_q$ are the most likely values.
+Consider $S$ that queries its oracle on $(j, guess_1),.., (j, guess_q)$.
+Denote by $Guess$ the random variable when $W_j\in \{guess_1,.., guess_q\}$  After these queries the remaining min-entropy is at most:
 \begin{align*}
-\Hav(W_j | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
-&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
-&=-\log\left( 2^{-n+\log q} \right) = n-\log q
+\Hav(W_j | S^{J_W(\cdot, \cdot)}) &=  -\log \left(\Pr[Guess=1]\times 1+ \Pr[Guess=0]\times \max_{w}\Pr[W_j = w|\not Guess =0]\right)\\
+&\leq  -\log \left(\Pr[Guess=1]\times 1\right)\\
+&=-\log\left( \frac{q}{|\mathcal{Z}|} \right) = \log|\mathcal{Z}|-\log q
 \end{align*}
@@
 \begin{align*}
- \Pr[\text{non zero response location }j \wedge c_j=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
+ \Pr[\text{non zero response location }j \wedge c_j=0] &>2^{-\alpha+1} - 2^{-(\log |\mathcal{Z}|-\log q)}=  2^{-\alpha}
  \end{align*}

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
small edits to intro

@@
 Unfortunately, this quantity is negative for some sources that are important in practice.
-Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used for such sources.
+Most known approaches for building fuzzy extractors work in the worst case and cannot be used when the minimum usable entropy is negative.
 
@@
 The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
-
-\iffalse
-For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.
-
-Traditionally, their security is defined information-theoretically.  %Fuzzy extractors have upper bounds on the length of the derived key.
-
-Fuzzy extractors work for any distribution with enough entropy.
-%In this setting, the entropy of the source must be significantly higher than the logarithm of number of error patterns corrected~(Dodis et al., J.
-of Comp 2008).
-
-We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.
-Dodis et al.~(J.
-of Comp.
-2008) show there is some source where the key length cannot exceed the minimum usable entropy.
-Therefore, fuzzy extractors that output the same length key for any source with enough entropy cannot output a key longer than the minimum usable entropy.
-
-%Traditional fuzzy extractors output a key roughly of length minimum usable entropy.
-To achieve meaningful security when the minimum usable entropy is negative, some restriction on the source is necessary.
-Meaningful restrictions (and accompanying constructions) have proved elusive for information-theoretic fuzzy extractors.
-Fuller, Meng, and Reyzin (Asiacrypt 2013) define a computationally-secure version of a fuzzy extractor.  It may be easier to construct computational fuzzy extractors for meaningful sources.
-
-In this work, we construct the first (computational) fuzzy extractors that are secure for a large class of distributions where the minimum usable entropy is negative.
-
-\textbf{Constructions:}  We construct computational fuzzy extractors from point function obfuscation.
-Our constructions are inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).
-\bnote{this whole paragraph needs work} Our two constructions are similar in spirit but optimize different parameters.
-The first requires individual blocks of the source to have super-logarithmic entropy and corrects a constant fraction of errors.
-The second construction uses sampling to reduce the required entropy of the source.
-Unfortunately, sampling also reduces the effective error tolerance of the construction.
-%The first construction works for high-entropy and high-error sources, while the second construction works for distributions with lower entropy and error.
-\bnote{need something else to say here}
-\fi
 \end{abstract}
@@
 Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
-We define and show two constructions of \emph{computational fuzzy conductors}.
+We show two constructions of \emph{computational fuzzy conductors}.
 These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
@@
 Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
-We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into to a string of blocks and then applies the first construction.
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then applies the first construction.
 $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.
@@
 \paragraph{On the Relationship to General Obfuscation}
-We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
+We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
 However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
-Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
+Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
 However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
@@
 
-Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within distance $t$ of $w$.
+Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
 The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$.

### 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
spelling check and notes from outside readers

@@
 \begin{abstract}
-Fuzzy extractors convert a noisy source of entropy into a consistent uniformly distributed key.
+Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.
 In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns.
@@
 The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
-
-\iffalse
-For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.
-
-Traditionally, their security is defined information-theoretically.  %Fuzzy extractors have upper bounds on the length of the derived key.
-
-Fuzzy extractors work for any distribution with enough entropy.
-%In this setting, the entropy of the source must be significantly higher than the logarithm of number of error patterns corrected~(Dodis et al., J.
-of Comp 2008).
-
-We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.
-Dodis et al.~(J.
-of Comp.
-2008) show there is some source where the key length cannot exceed the minimum usable entropy.
-Therefore, fuzzy extractors that output the same length key for any source with enough entropy cannot output a key longer than the minimum usable entropy.
-
-%Traditional fuzzy extractors output a key roughly of length minimum usable entropy.
-To achieve meaningful security when the minimum usable entropy is negative, some restriction on the source is necessary.
-Meaningful restrictions (and accompanying constructions) have proved elusive for information-theoretic fuzzy extractors.
-Fuller, Meng, and Reyzin (Asiacrypt 2013) define a computationally-secure version of a fuzzy extractor.  It may be easier to construct computational fuzzy extractors for meaningful sources.
-
-In this work, we construct the first (computational) fuzzy extractors that are secure for a large class of distributions where the minimum usable entropy is negative.
-
-\textbf{Constructions:}  We construct computational fuzzy extractors from point function obfuscation.
-Our constructions are inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).
-\bnote{this whole paragraph needs work} Our two constructions are similar in spirit but optimize different parameters.
-The first requires individual blocks of the source to have super-logarithmic entropy and corrects a constant fraction of errors.
-The second construction uses sampling to reduce the required entropy of the source.
-Unfortunately, sampling also reduces the effective error tolerance of the construction.
-%The first construction works for high-entropy and high-error sources, while the second construction works for distributions with lower entropy and error.
-\bnote{need something else to say here}
-\fi
+\bnote{more about what we do}
 \end{abstract}
@@
 Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
-Both of these problems have interactive and noninteractive versions.
-In this paper, we are interested in the noninteractive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
- A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification noninteractively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.
+Both of these problems have interactive and non-interactive versions.
+In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
+ A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.
 
@@
 In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then the \emph{entire distribution} of $w$ may have min-entropy $m$ and be contained in a single ball.
-Then the adversary can always produce the key by running $\rep$ with the center of the ball as $w'$.
+Then the adversary can always produce the key by running $\rep$ with the center of the ball as $w'$.\bnote{was told this wasn't clear enough}
 
 More generally, let $B_t$ denote the number of points in a ball of radius $t$.
-For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several nonoverlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
+For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several non-overlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
 We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
-The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-etropy $m$ if  $\Huse\le 0$.
+The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-entropy $m$ if  $\Huse\le 0$.
 
@@
 As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.
+Daugman estimates irises contain $249$ bits of entropy~\cite{daugman2004}.
 Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
@@
 \]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their analysis underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
 
@@
 Our first construction is secure when symbols in $w$
-each have individual superlogarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
+each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
 a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
@@
 Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
-They can also be constructed by assuming strong properties of cryptographic hash functions!\cite{canetti1997towards}
+They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
 
@@
 In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.
-The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
+\bnote{cut the rest of this paragraph?} The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
 As discussed in the introduction, when $\Huse\le 0$ some restriction on the source is necessary.
@@
 \end{proof}
-We now a rgue correctness of \consref{cons:first construction}.
+We now a argue correctness of \consref{cons:first construction}.
 We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
@@
 Let $W = W_1,..., W_\ell$ be a source.
-Suppose that for all $j$, $\Hoo(W_j)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is superlogarithmic).
+Suppose that for all $j$, $\Hoo(W_j)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is super-logarithmic).
 Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block distribution.

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
adding notes from people I had read

@@
 The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+\bnote{more about what we do}
 \end{abstract}
@@
 \paragraph{Limitations of Entropy-Based Approaches}
+\bnote{shorten this heading?}
 Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
@@
 In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then the \emph{entire distribution} of $w$ may have min-entropy $m$ and be contained in a single ball.
-Then the adversary can always produce the key by running $\rep$ with the center of the ball as $w'$.
+Then the adversary can always produce the key by running $\rep$ with the center of the ball as $w'$.\bnote{was told this wasn't clear enough}
 
 More generally, let $B_t$ denote the number of points in a ball of radius $t$.
-For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several nonoverlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
+For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil( 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several non-overlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
 We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
-The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-etropy $m$ if  $\Huse\le 0$.
+The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-entropy $m$ if  $\Huse\le 0$.
+\bnote{is there anyway we can reasonably say what previous works support?}
 

### 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
cleaning up claim d.3

@@
 \bnote{more about what we do}
+
+\textbf{Keywords} Fuzzy extractors, key derivation, error-correcting codes, computational entropy, point obfuscation.
 \end{abstract}
@@
 More generally, let $B_t$ denote the number of points in a ball of radius $t$.
-For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several non-overlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
+For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil( 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several non-overlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
 We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
 The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-entropy $m$ if  $\Huse\le 0$.
+\bnote{is there anyway we can reasonably say what previous works support?}
 
@@
 
-We now consider the number of possible $0\rightarrow 1$ bit flips in $c$.
-A $0\rightarrow 1$ flip on index $j$ occurs when two conditions are met $w_j\neq w_j'$ and $c_j = 0$.
-Since the first conditioned is only fulfilled at most $t$ times, we have the following lemma:
+Since there are most $t$ locations when $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$:
 
@@
 To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
-We allow $t$ errors with an alphabet $\mathcal{Z}$ of size $2^n$.
-This means that
 \[
@@
 \end{definition}
-
 \defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
 The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
-%Note a partial block source requires worst case entropy while an unguessable block distribution only requires average conditional entropy.
-\lnote{this comparison is unclear to me}  However, we achieve security for significantly lower entropy levels than for unguessable block distributions.
-
 Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.
@@
 This yields:
-\begin{align*}
-\Huse &= \Hoo(W) -\log |B_t| \\
-&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
-&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
-\end{align*}
+\[
+\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
+\]
 That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
@@
 \delta^{D}((X, SS), (Y, SS))&= \delta^{D'}((\cext(X, U_d), U_d, SS), \cext(Y, U_d), U_d, SS)\\
-&\geq \delta^{D'}((\cext(X, U_d), U_d, SS), (U_\kappa\times U_d \times SS)) - \delta^{D'}((\cext(Y, U_d), U_d, SS), (U_\kappa\times U_d \times SS))\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, SS), (U_\kappa\times U_d \times SS)) \\
+&- \delta^{D'}((U_\kappa\times U_d \times SS), (\cext(Y, U_d), U_d, SS))\\
 &>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
@@
 \bnote{Leo I changed some of this under you.  It wasn't clear or probably right as written.}
-\bnote{better name for guess, creativity is running low.}
 Let $W$ be a $(q, \alpha, \beta)$-block unguessable distribution.  Let $J\subset\{1,..., \ell\}$ the set of good indices.
 It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.
-Denote by $guess_{1}, ..., guess_q$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
-Note that $\sum_{i=1}^q \Pr[W_j = guess_i]\geq q/|\mathcal{Z}|$.
-Suppose not, this means that there is some $guess_i$ with probability $\Pr[W_j = guess_i] < 1/|\mathcal{Z}|$.
+Denote by $w_{j,1}, ..., w_{j,q}$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
+Then $\sum_{i=1}^q \Pr[W_j = w_{j,i}]\geq q/|\mathcal{Z}|$.
+Suppose not, this means that there is some $w_{j,i}$ with probability $\Pr[W_j = w_{j,i}] < 1/|\mathcal{Z}|$.
 Since there are $\mathcal{Z} - q $ remaining possible values of $W_j$ for their total probability to be at least $1-q/|\mathcal{Z}|$ at least of these values has probability at least $1/\mathcal{Z}$.
-This contradicts the statement $guess_1,..., guess_q$ are the most likely values.
-Consider $S$ that queries its oracle on $(j, guess_1),.., (j, guess_q)$.
-Denote by $Guess$ the random variable when $W_j\in \{guess_1,.., guess_q\}$  After these queries the remaining min-entropy is at most:
+This contradicts the statement $w_{j,1},..., w_{j,q}$ are the most likely values.
+Consider $S$ that queries its oracle on $(j, w_{j,1}),.., (j, w_{j,q})$.
+Denote by $Bad$ the random variable when $W_j\in \{w_{j,1},.., w_{j,q}\}$  After these queries the remaining min-entropy is at most:
 \begin{align*}
-\Hav(W_j | S^{J_W(\cdot, \cdot)}) &=  -\log \left(\Pr[Guess=1]\times 1+ \Pr[Guess=0]\times \max_{w}\Pr[W_j = w|\not Guess =0]\right)\\
-&\leq  -\log \left(\Pr[Guess=1]\times 1\right)\\
+\Hav(W_j | S^{J_W(\cdot, \cdot)}) &=  -\log \left(\Pr[Bad=1]\times 1+ \Pr[Bad=0]\times \max_{w}\Pr[W_j = w| Bad =0]\right)\\
+&\leq  -\log \left(\Pr[Bad=1]\times 1\right)\\
 &=-\log\left( \frac{q}{|\mathcal{Z}|} \right) = \log|\mathcal{Z}|-\log q

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
shortening arguments in section 5

@@
 %\documentclass{llncs}
-\def\shownotes{1}
+\def\shownotes{0}
 
@@
 \noindent
-We can then argue that all $V_i$ simultaneously have individual entropy with good probability:
+We can then argue that all $V_i$ simultaneously have individual entropy with good probability~(by union bound):
 \begin{corollary}
@@
 \end{corollary}
-\begin{proof}
-Union bound over the probability in \lemref{lem:sampling works}.
-%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
-\end{proof}
+%\begin{proof}
+%Union bound over the probability in \lemref{lem:sampling works}.
+%%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
+%\end{proof}
 
@@
 Thus, unless the choice of $\lambda$ is very unlucky,
-\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. This allows us to conclude the following.
+\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. That is, 
 \begin{corollary}
@@
 \end{corollary}
-\begin{proof}
-Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
-\end{proof}
+%\begin{proof}
+%Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
+%\end{proof}
 
@@
 The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.
-This probability is at most $\ell/\mathcal{Z}^\eta$.
 Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$.
@@
 The proof is in \apref{sec:sampling errors}.
+The correctness argument in \thref{thm:sampling} is obtained by subtracting the probability of a single $1\rightarrow 0$ bit flip~($\ell/|\mathcal{Z}|$) and the error of the code~($\delta_{code}$).
 
@@
 
-\begin{corollary}
-Let all the variables be as in \thref{thm:sampling}.
-When
-\[
-\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
-\]
-and $(c, p)\leftarrow \gen(w)$, then
-\[
-\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
-\]
-That is, \consref{cons:sampling} is correct with overwhelming probability.
-\end{corollary}
+%\begin{corollary}
+%Let all the variables be as in \thref{thm:sampling}.
+%When
+%\[
+%\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
+%\]
+%and $(c, p)\leftarrow \gen(w)$, then
+%\[
+%\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
+%\]
+%That is, \consref{cons:sampling} is correct with overwhelming probability.
+%\end{corollary}
 
@@
 \bnote{Leo I changed some of this under you.  It wasn't clear or probably right as written.}
-\bnote{better name for guess, creativity is running low.}
 Let $W$ be a $(q, \alpha, \beta)$-block unguessable distribution.  Let $J\subset\{1,..., \ell\}$ the set of good indices.
 It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.
-Denote by $guess_{1}, ..., guess_q$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
-Note that $\sum_{i=1}^q \Pr[W_j = guess_i]\geq q/|\mathcal{Z}|$.
-Suppose not, this means that there is some $guess_i$ with probability $\Pr[W_j = guess_i] < 1/|\mathcal{Z}|$.
+Let $j\in J$ be some arbitrary element of $J$ and denote by $w_{j,1}, ..., w_{j,q}$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
+Then $\sum_{i=1}^q \Pr[W_j = w_{j,i}]\geq q/|\mathcal{Z}|$.
+Suppose not, this means that there is some $w_{j,i}$ with probability $\Pr[W_j = w_{j,i}] < 1/|\mathcal{Z}|$.
 Since there are $\mathcal{Z} - q $ remaining possible values of $W_j$ for their total probability to be at least $1-q/|\mathcal{Z}|$ at least of these values has probability at least $1/\mathcal{Z}$.
-This contradicts the statement $guess_1,..., guess_q$ are the most likely values.
-Consider $S$ that queries its oracle on $(j, guess_1),.., (j, guess_q)$.
-Denote by $Guess$ the random variable when $W_j\in \{guess_1,.., guess_q\}$  After these queries the remaining min-entropy is at most:
+This contradicts the statement $w_{j,1},..., w_{j,q}$ are the most likely values.
+Consider $S$ that queries its oracle on $(j, w_{j,1}),.., (j, w_{j,q})$.
+Denote by $Bad$ the random variable when $W_j\in \{w_{j,1},.., w_{j,q}\}$  After these queries the remaining min-entropy is at most:
 \begin{align*}
-\Hav(W_j | S^{J_W(\cdot, \cdot)}) &=  -\log \left(\Pr[Guess=1]\times 1+ \Pr[Guess=0]\times \max_{w}\Pr[W_j = w|\not Guess =0]\right)\\
-&\leq  -\log \left(\Pr[Guess=1]\times 1\right)\\
+\Hav(W_j | S^{J_W(\cdot, \cdot)}) &=  -\log \left(\Pr[Bad=1]\times 1+ \Pr[Bad=0]\times \max_{w}\Pr[W_j = w| Bad =0]\right)\\
+&\leq  -\log \left(\Pr[Bad=1]\times 1\right)\\
 &=-\log\left( \frac{q}{|\mathcal{Z}|} \right) = \log|\mathcal{Z}|-\log q

### 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
cleaning up claim d.3
minor edits to intro

@@
 The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
-\bnote{more about what we do}
 
@@
 
-\paragraph{Limitations of Entropy-Based Approaches}
-\bnote{shorten this heading?}
+\paragraph{Limitations of Known Approaches}
+
 Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
-The reason for this tension is simple: if an adversary who knows $p$ can guess some $w'$ within distance $t$ of $w$ they will be able to easily distinguish $r$ from uniform by running $\rep$.
-If $t$ is larger, then $\rep$ tolerates more $w'$ values, so the adversary's job is easier.
-In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then the \emph{entire distribution} of $w$ may have min-entropy $m$ and be contained in a single ball.
-Then the adversary can always produce the key by running $\rep$ with the center of the ball as $w'$.\bnote{was told this wasn't clear enough}
+The reason for this tension is simple: if an adversary who knows $p$ can guess any $w'$ within distance $t$ of $w$, it will be able to easily obtain the true $r$ by running $\rep$.
+%If $t$ is larger, then a single guess for $w'$ may be within distance $t$ of more $w$ values, thus increasing adversarial probability of winning. 
+In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then there exists a distribution of $w$ of min-entropy $m$  \emph{contained entirely in a single ball}.
+For these distributions, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
 
@@
 
+\lnote{restricting errors instead of entropy is another way to get around impossibility}
+
 \medskip
+\lnote{skip if no space}
 The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
@@
 In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.
-\bnote{cut the rest of this paragraph?} The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.
-As discussed in the introduction, when $\Huse\le 0$ some restriction on the source is necessary.
-Instead of restricting the class of source distributions, the definition could restrict the correctable errors to errors that are ``likely'' to occur in the source.
-We leave this as an open problem.
 
@@
 It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.
-Denote by $w_{j,1}, ..., w_{j,q}$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
+Let $j\in J$ be some arbitrary element of $J$ and denote by $w_{j,1}, ..., w_{j,q}$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
 Then $\sum_{i=1}^q \Pr[W_j = w_{j,i}]\geq q/|\mathcal{Z}|$.

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
shortening arguments in section 5
cleaned up sec 3

@@
 %\documentclass{llncs}
-\def\shownotes{0}
+\def\shownotes{1}
 
@@
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s)$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
 \begin{itemize}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
+\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
+\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$, where the probability is over the randomness of $(\gen, \rep)$.
 If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $r$ is pseudorandom conditioned on $p$, that is $\delta^{\mathcal{D}_s}((R, P), (U_\kappa, P))\leq \epsilon$.
 \end{itemize}
@@
 denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
-\end{definition} \lnote{I haven't checked this section below this line}
+\end{definition} 
 We now define a computational fuzzy conductor and a (computational)~randomness extractor.
@@
 \label{def:comp fuzzy cond}
-Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
 \begin{itemize}
-\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $X\in\{0,1\}^\ell$ and a helper string $SS\in\{0,1\}^*$.
-\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $SS\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', SS) = X] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.
-If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $X$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
+\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(R |P)\geq \tilde{m}$.
 \end{itemize}
 \end{definition}
+
+\iffalse
+\begin{definition}
+\label{def:comp fuzzy cond}
+Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties (the first two properties are the same as in \defref{def:comp fuzzy extractor}, with $x$ replacing $r$):
+\begin{itemize}
+\item The generate procedure $\gen$ on input $w\in \mathcal{M}$ outputs a string $x\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
+\item The reproduction procedure $\rep$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(x, p)\leftarrow \gen(w)$, then $\Pr[\rep(w',p) = x] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
+If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.
+That is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
+\end{itemize}
+\end{definition}
+\fi
+
 A computational extractor is the adaption of a randomness extractor to the computational setting.
@@
 A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon_{ext}, s_{ext})$-average-case computational extractor} if for all pairs
-of random variables $X, Y$ over $\zo^\ell, \chi$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{ext}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
+of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{ext}}}((\cext(X; U_d), U_d, Y), U_\kappa\times
 U_d \times Y) \le \epsilon_{ext}$.
@@
 \begin{itemize}
-\item $\gen(w; seed):$ run $(x, ss)= \gen'(w)$ and set $r = \cext(x; seed)$, $p = (ss, seed)$.  Output $(r, p)$.
-\item $\rep(w, (ss, seed)):$ recover $x = \rec'(w'; p')$ and output $r = \cext(x; seed)$.
+\item $\gen(w; seed)$ (where $seed\in \zo^d$): run $(r', p')= \gen'(w)$ and output $r = \cext(r'; seed)$, $p = (p', seed)$. 
+\item $\rep(w', (p', seed)):$ run $r' = \rep'(w'; p')$ and output $r = \cext(r'; seed)$.
 \end{itemize}

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
cleaning up cleanup of section 3

@@
 Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree).
-Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.
+Constructing an efficient obfuscator for proximity queries when $\Huse\le 0$ is an open problem.
 
@@
 \emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
+denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
 \end{definition} 
@@
 \begin{itemize}
-\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(R |P)\geq \tilde{m}$.
+\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
 \end{itemize}
@@
 Let $\chi$ be a finite set.
-A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon_{ext}, s_{ext})$-average-case computational extractor} if for all pairs
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
 of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{ext}}}((\cext(X; U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon_{ext}$.
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon$.
 \end{definition}
@@
 \label{lem:cond and cext}
-Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
+Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
 Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
small changes to 1-2.1

@@
 
-We construct the first fuzzy extractors that work for a large class of distributions in which the minimum usable entropy is negative.
+We construct the first fuzzy extractors that work for a large class of distributions that have negative minimum usable entropy.
 Their security is computational.
@@
 In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then there exists a distribution of $w$ of min-entropy $m$  \emph{contained entirely in a single ball}.
-For these distributions, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
+For this distribution, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
 
@@
 The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-entropy $m$ if  $\Huse\le 0$.
-\bnote{is there anyway we can reasonably say what previous works support?}
 
@@
 \]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their analysis underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
 
@@
 Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-Fuller, Meng, and Reyzin~\cite{fuller2013computational} show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
 Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.
@@
 This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
-Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed for the first construction.
+Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed in the first construction.
 Computational, rather than information-theoretic, analysis seems crucial for achieving this property.
 
-\paragraph{On the Relationship to General Obfuscation}
+\paragraph{Connection to General Obfuscation}
 We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
@@
 \paragraph{Open Problems}
-Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
+Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Codes over large alphabets are often used to correct burst errors~\cite{gilbert1960capacity}.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
 However, distributions with $\Huse \le 0$ are supported only for large alphabets.
@@
 
-\lnote{restricting errors instead of entropy is another way to get around impossibility}
+In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
+An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.
+A meaningful restriction of correctable errors is an open problem.
 
 \medskip
-\lnote{skip if no space}
 The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
@@
 For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
-We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
+We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
 
@@
 \label{cl:many locations ent}
-Let $C$ be a subset of $\{0,1\}^\ell$ with a uniform distribution, and let $J\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{J^c}) =  H_0(C) - |J^c|$.
+Let $C$ be the uniform distribution over a subset of $\{0,1\}^\ell$, and let $J\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{J^c}) =  H_0(C) - |J^c|$.
 \end{claim}

### 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
removing app A

@@
 Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree).
-Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.
-
-\lnote{restricting errors instead of entropy is another way to get around impossibility}
+Constructing an efficient obfuscator for proximity queries when $\Huse\le 0$ is an open problem.
+
+In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
+An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.
+A meaningful restriction of correctable errors is an open problem.
 
 \medskip
-\lnote{skip if no space}
 The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
@@
 We follow the second approach.
-In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
+The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.
+%In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
 To overcome these bounds, we use a computational version of a fuzzy conductor.
@@
 \emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
-\end{definition} \lnote{I haven't checked this section below this line}
+denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
+\end{definition} 
 We now define a computational fuzzy conductor and a (computational)~randomness extractor.
@@
 \label{def:comp fuzzy cond}
-Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
 \begin{itemize}
-\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $X\in\{0,1\}^\ell$ and a helper string $SS\in\{0,1\}^*$.
-\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $SS\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', SS) = X] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.
-If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $X$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
+\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
 \end{itemize}
 \end{definition}
+
+\iffalse
+\begin{definition}
+\label{def:comp fuzzy cond}
+Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties (the first two properties are the same as in \defref{def:comp fuzzy extractor}, with $x$ replacing $r$):
+\begin{itemize}
+\item The generate procedure $\gen$ on input $w\in \mathcal{M}$ outputs a string $x\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
+\item The reproduction procedure $\rep$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
+The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(x, p)\leftarrow \gen(w)$, then $\Pr[\rep(w',p) = x] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
+If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.
+That is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
+\end{itemize}
+\end{definition}
+\fi
+
 A computational extractor is the adaption of a randomness extractor to the computational setting.
@@
 Let $\chi$ be a finite set.
-A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon_{ext}, s_{ext})$-average-case computational extractor} if for all pairs
-of random variables $X, Y$ over $\zo^\ell, \chi$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{ext}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon_{ext}$.
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
+of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon$.
 \end{definition}
@@
 This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
-Goldreich provides an introduction to samplers in~\cite{goldreich1997sample}.
+Goldreich provides an introduction to samplers in~\cite{goldreich2011sample}.
 
@@
 
-\section{Fuzzy Conductors}
-\lnote{I need to check this}
-\label{sec:conductors}
-Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
+%\section{Fuzzy Conductors}
+%\lnote{I need to check this}
+%\label{sec:conductors}
+%Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
 Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
@@
 This is known as a fuzzy conductor~\cite{KanukurthiR09}.
-\begin{definition}
-A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
-\begin{enumerate}
-\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
-\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.
+%\begin{definition}
+%A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
+%\begin{enumerate}
+%\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
+%\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.
 The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep(w', SS) = X]\geq 1-\delta$~(over the coins of $\gen', \rep'$).
 If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
-\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.
+%\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.
 That is, $\exists Y$ with $\Hav(Y | SS ) \geq \tilde{m}$ such that $\Delta((X, SS), (Y, SS))\leq \epsilon$.
-\end{enumerate}
-\end{definition}
-
-\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
+%\end{enumerate}
+%\end{definition}
+%
+%\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
 This motivates our use of a computational fuzzy conductor in \defref{def:comp fuzzy cond}.
-We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
-\begin{itemize}
-\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
-%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
-\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
-\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
-\end{itemize}
-Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.
-\begin{lemma}
-The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
-\end{lemma}
-\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
+%We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
+%\begin{itemize}
+%\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
+%%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
+%\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
+%\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
+%\end{itemize}
+%Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.
+%\begin{lemma}
+%The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
+%\end{lemma}
+%\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
 Let $A$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $A$.
@@
 $C$ defines an error correcting code with the required parameters.
-\end{proof}
+%\end{proof}
 
@@
 
-\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.
-In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
-The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.
-Thus, we begin with the case of independent blocks.
+\defref{def:block guessable} is an inherently adaptive definition and a little unwieldy.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
+The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may reshape the distribution of block $j$.
 In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).
+We first show some sources that are unguessable block distributions~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block distributions~(\secref{sec:negative ex}).
+
+\subsection{Positive Examples}
+\label{sec:positive ex}
+We begin with the case of independent blocks.
 
@@
 We can ignore queries for all blocks but the $j$th, as the blocks are independent.
-Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice).
+Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic ($S$ can calculate the best coins).
 Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block.
@@
 \begin{align*}
-\Hav(W_j | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
+\Hav(W_j | View(S^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
 &=\Hoo(W_j) - |A_1, \dots, A_q|\\
@@
 
-Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ for which \consref{cons:first construction} is secure.
+Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so there is a family of distributions with total entropy $\omega(\log n)$ for which \consref{cons:first construction} is secure.
 For these distributions, all the coordinates are as dependent as possible: one determines all others.
-
 We can prove a slightly weaker claim when the correlation between the coordinates $W_j$ is arbitrary:
@@
 
+\subsection{Negative Examples}
+\label{sec:negative ex}
 Claims~\ref{cl:each block from single seed} and~\ref{cl:all blocks entropy} rest on there being no easy ``entry'' point to the distribution.
@@
 \begin{claim}
-Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
-There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
+Let $p = (\poly(n))$ and let $f_1,..., f_{\ell}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
+There is an adversary making $p\times \ell = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
 \end{claim}
 \begin{proof}
-We present an adversary $S$~(running in polynomial time) that completely determines the value $x$.
+Let $x$ be the true value for $U_{p\times \ell}$.
+We present an adversary $S$ that completely determines $x$.
 $S$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
-Then $S$ queries on $y_1,..., y_p$, exactly one answer returns $1$.
+Then $S$ queries on $(1, y_1),..., (1, y_p)$, exactly one answer returns $1$.
 Let this value be $y_1^*$ and its preimage $x_1^*$.
@@
 Again, exactly one of these queries returns $1$.
-This process is repeated until all of $x$ is recovered.
-The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
+This process is repeated until all of $x$ is recovered~(and thus $w$).
+%The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
 Once $x$ has been recovered then $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
@@
 
-The previous example relied on an adversaries ability to completely determine a block from the previous blocks.
+The previous example relies on an adversaries ability to determine a block from the previous blocks.
 We formalize this notion next.
-We defining the entropy jump of a block source as the remaining entropy when other blocks are known:
+We define the entropy jump of a block source as the remaining entropy when other blocks are known:
 
 \begin{definition}
-Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $\mathtt{Jump}(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
+Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.
+The \emph{jump} of a block $i_j$ is $\mathtt{Jump}(i_j) = \max_{w_{i_1},..., w_{i_{j-1}}} H_0 (W_{i_j} | W_{i_1} = w_{i_1} ,..., W_{i_{j-1}} = w_{i_{j-1}})$.
 \end{definition}
 
-\noindent
-We now show that there must be a super-logarithmic jump early enough.
+If an adversary can learn blocks in succession they can eventually recover the entire secret.
+In order for a distribution to be block unguessable the adversary must get ``stuck'' early enough in their recovery process.
+This translates to having a super-logarithmic jump early enough.
 
 \begin{claim}
-Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $\mathtt{Jump}(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\ell-\beta+1)$, then $W$ is not $(q, 0, \beta)$-unguessable block distribution.
 \end{claim}
@@
 We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.
-As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
-Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.
+As before $S$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
+Then $S$ queries the (at most)~$q/(\ell-\beta+1)$ possible values for $W_2 | W_1$.
 This process is repeated until $W_{\ell-\beta+1}$ is learned.
-Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to sample from $W_j | W_1,.., W_{j-1}$.
-\end{proof}
+\end{proof}
+
+Presenting a sufficient condition for security is more difficult as $S$ may interleave queries to different blocks.
+It seems like the optimum strategy is to focus on a single block at a time but it is unclear how to formalize this intuition.
 

### 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
notational fixes

@@
 
+\bigskip
+
 \textbf{Keywords} Fuzzy extractors, key derivation, error-correcting codes, computational entropy, point obfuscation.
@@
 
-We note that for any code, learning a few bits of a codeword does not inform on the remainder of the bits~(the claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
-
-\begin{claim}
-\label{cl:many locations ent}
-Let $C$ be the uniform distribution over a subset of $\{0,1\}^\ell$, and let $J\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{J^c}) =  H_0(C) - |J^c|$.
-\end{claim}
-
 \textbf{Notes:}
@@
 \subsection{Obfuscation}
-Our construction uses obfuscation for a family of point functions $\mathtt{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
+Our construction uses obfuscation for a family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
 \[
@@
 \begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
-\label{def:obf} Let $\mathtt{I}$ be a family of polynomial-size circuits.
-A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}$ with auxiliary-input if the following conditions are met:
+\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for point functions with auxiliary-input if the following conditions are met:
 \begin{enumerate}
-\item \emph{Functionality:} for every $ I \in \mathtt{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
+\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
 \item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
@@
 Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained.
-We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
+We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
 \begin{definition}
@@
 Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
-In the computational setting, a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).
-We therefore focus on building a computational fuzzy conductor with meaningful output entropy.\lnote{where do we talk about running it multiple times if we don't get enough output from one run?} \bnote{nowhere, it was something I realized yesterday.
-For second construction it doesn't make much sense, just increase $\ell$ has same effect.} Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
 
@@
 Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an obfuscator for the family of point functions $\mathtt{I}_{\mathcal{Z}}$.
+Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
 Let  $C\subset \zo^\ell$ be an error-correcting code.
@@
 \consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
-By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-More formally, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
+By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
+Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
 This restriction on the distribution is captured in the following definition.
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I$ making at most $q$ queries
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
 \[
@@
 \end{definition}
-\lnote{stopped going through section 4 here}
 
@@
 \label{thm:main thm first cons}
-Let $n$ be a security parameter.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_j$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.
-Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C) - \beta$.
+Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
 \end{theorem}
 \begin{proof}
-We argue security in~\lemref{lem:security of cons} and correctness in~\lemref{lem:correct of cons}.
-\end{proof}
+We first argue security in the following Lemma.
 
@@
 Let all variables be as in \thref{thm:main thm first cons}.
-For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
+For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
 \end{lemma}
@@
 It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
-Let $J$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.
-We first note that $C'$ has sufficient entropy.
-That is, $\Hav(C' |P) =\Hav(C' | C_{J^c} = C'_{J^c}) = H_0(C) - |J^c|$.
+Let $J$ be the set of indices that exists according to \defref{def:block guessable}.
+Define the distribution $C'$ as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.
+We first note that $C'$ has sufficient entropy, because $\Hav(C' |P) = \Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - |J^c|$ (the second step is by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
 It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
@@
 \begin{itemize}
-\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
+\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$.
+Since $P$ is a collection of obfuscated programs, there exists a simulator $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
 \item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.
@@
 \end{proof}
-We now a argue correctness of \consref{cons:first construction}.
+We now argue correctness of \consref{cons:first construction}.
 We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
@@
 Let all variables be as in \thref{thm:main thm first cons}.
-The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
 \end{lemma}
 \begin{proof}
-Recall that $c$ contains at most $\ell$ $1$s.
-Since $w'$ is chosen independently of the points $r_j$, this probability is the size of each block, that is $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$.
-Since the $r_j$ are chosen independently, one has,
-\[
-\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_j = w_j']\geq 1-\sum_{j=1}^\ell \Pr[r_j = w_j'] \geq 1-\frac{\ell}{|\mathcal{Z}|}.
-\]
-\end{proof}
-
-Since there are most $t$ locations when $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$:
-
-\begin{lemma}
-\label{lem:correct of cons}
-Let all variables be as in \thref{thm:main thm first cons}.
-For $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
-\[
-\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{|\mathcal{Z}|}+\delta_{code}\right).
-\]
-That is, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|+\delta_{code}$.
-\end{lemma}
-
-\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+\Omega(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_j =1$.
-This requires a code where most codewords have Hamming weight close to $1/2$.
+Consider a coordinate $j$ for which $c_j=1$.
+Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$.
+The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
+\end{proof}
+
+Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
+Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
+\end{proof}
 
@@
 \label{sec:discussion}
+\lnote{I did not check this calculation -- will do}
 To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
@@
 When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
+
+\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
+
+If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
 
@@
 Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions over $\mathtt{I}_{\mathcal{Z}^\eta}$.
-Define $\gen, \rep$ as:
+Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions.  Define $\gen, \rep$ as:
 
@@
 
+\lnote{in prev construction's theorem statement, $\mathcal{Z}$ grows as a function of $n$, and here it doesn't have to, but may.
+Right now the differences between the two theorems are too subtle to notice.
+Make theorem statements similar and highlight the differences.}
 \begin{theorem}
 \label{thm:sampling}
+Let $\mathcal{Z}$ be an alphabet.
 Let $n$ be a security parameter.
@@
 Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
-$\ell = \omega(\log n)$.
-Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
+$\ell = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs. 
   Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
@@
 It suffices to show if there is some distinguisher $D'$ of size $s'$ where
-\[\delta^{D'}((\cext(X; U_d), U_d, SS), (U_\kappa, U_d, SS))>\epsilon_{cond}+ \epsilon_{ext}\]
- then there is an distinguisher $D$ of size $s_{cond}$ where for all $Y$ where $\Hav(Y|SS) \geq \tilde{m}$ such that
- \[
- \delta^{D}((X, SS), (Y, SS))\geq \epsilon_{cond}.
+\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
+ \[
+ \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
  \]
@@
 \[
-\delta^{D'}(\cext(X, U_d)\times U_d \times SS, U_\kappa\times U_d\times SS)> \epsilon_{ext}+\epsilon_{cond}.
+\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
 \]
 Then define $D$ as follows.
-On input $(y, ss)$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, ss)$.
+On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.
 Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
@@
 \begin{align*}
-\delta^{D}((X, SS), (Y, SS))&= \delta^{D'}((\cext(X, U_d), U_d, SS), \cext(Y, U_d), U_d, SS)\\
-&\geq \delta^{D'}((\cext(X, U_d), U_d, SS), (U_\kappa\times U_d \times SS)) \\
-&- \delta^{D'}((U_\kappa\times U_d \times SS), (\cext(Y, U_d), U_d, SS))\\
+\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
+&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
 &>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
@@
 Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.
-Then $C | C_{J^c} \overset{d}=C'$.
-By \clref{cl:many locations ent}, we have that $\Hav(C|C_{J^c} )= H_0(C) -\beta$ and thus $\Hav(C'| C_{J^c}) = H_0(C) -\beta$.
-Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that
+Then
+$\Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - \beta$ (by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
+
+Let $D$ a distinguisher of size at most $s_{sec}$ such that
 \[

### 2014-04-01 constantRate/ConstCompFuzzExt-eprint.tex
Adding presentation for MITRE

--- 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
@@
 \title{Key Derivation From Noisy Sources With More Errors Than Entropy}
-%\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
-%work was sponsored by the Department of the Air Force under Air Force
-%Contract
-%\#FA8721-05-C-0002.  Opinions,
-%interpretations, conclusions and recommendations are those of the author
-%and
-%are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
+\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}.} ~~~~~ Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
+Work done in part while the author was at MIT Lincoln Laboratory.} ~~~~~ Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}.
+} ~~~~~ Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University }
 
@@
 \]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
 
@@
 %However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
+
+\section*{Acknowledgements}
+The authors are grateful to Nir Bitanski, Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.
+
+This work is supported in part by National Science Foundation grants XXXX.
+The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
 \bibliographystyle{alpha}
@@
 However, we do not achieve security when $\Hfuzz(W)= \omega(\log n)$ for either definition, this is an open problem.
-
+%
 %\section{Fuzzy Conductors}

### 2014-04-03 trunk/constantRate/ConstCompFuzzExt-eprint.tex

--- 2014-04-01 constantRate/ConstCompFuzzExt-eprint.tex
@@
 \section*{Acknowledgements}
-The authors are grateful to Nir Bitanski, Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.
+The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.
 
 This work is supported in part by National Science Foundation grants XXXX. 
+Omer Paneth is supported by the Simons award for graduate students in theoretical computer science and an NSF Algorithmic foundations grant 1218461.
 The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.

### 2014-04-14 constantRate/ConstCompFuzzExt-eprint.tex
Grant numbers for eprint

@@
 \title{Key Derivation From Noisy Sources With More Errors Than Entropy}
-\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}.} ~~~~~ Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
-Work done in part while the author was at MIT Lincoln Laboratory.} ~~~~~ Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}.
-} ~~~~~ Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University }
+\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}.
+Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
+Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}.
+Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.
+Boston University.} }
 
@@
 \section*{Acknowledgements}
-The authors are grateful to Nir Bitanski, Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.
-
-This work is supported in part by National Science Foundation grants XXXX.
+The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.
+
+This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, and 1218461. 
+Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.
 The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.

### 2014-04-15 trunk/resuable/resuableCompFuzzExt.tex
reusable paper and crypto review response

--- 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
@@
 
-\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
+\title{Reusable Fuzzy Extractors Against Arbitrary Correlation}
 %\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
@@
 
-\begin{abstract}
-Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.
-In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns.
-We call what is left after this worst-case loss the \emph{minimum usable entropy}.
-Unfortunately, this quantity is negative for some sources that are important in practice.
-Most known approaches for building fuzzy extractors work in the worst case and cannot be used when the minimum usable entropy is negative.
-
-We construct the first fuzzy extractors that work for a large class of distributions that have negative minimum usable entropy.
-Their security is computational.
-They correct Hamming errors over a large alphabet.
-In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
-
-Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
-Our second construction requires  a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
-The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
-
-\bigskip
-
-\textbf{Keywords} Fuzzy extractors, key derivation, error-correcting codes, computational entropy, point obfuscation.
-\end{abstract}
+%\begin{abstract}
+%Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.  
+%
+%\end{abstract}
 
@@
 
+\paragraph{Reusability} Fuzzy extractors should be able to authenticate users to multiple different services/devices.
+That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
+This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
+There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
+Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
+Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
+
 \paragraph{Limitations of Known Approaches}
 
-Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
-The reason for this tension is simple: if an adversary who knows $p$ can guess any $w'$ within distance $t$ of $w$, it will be able to easily obtain the true $r$ by running $\rep$.
-%If $t$ is larger, then a single guess for $w'$ may be within distance $t$ of more $w$ values, thus increasing adversarial probability of winning. 
-In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then there exists a distribution of $w$ of min-entropy $m$  \emph{contained entirely in a single ball}.
-For this distribution, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
+There are two primary questions about the reusability of a fuzzy extractor.
+The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
+Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.
+Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the fuzzy extractor.
+They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
+In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.
 
-More generally, let $B_t$ denote the number of points in a ball of radius $t$.
-For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil( 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several non-overlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
-We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
-The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-entropy $m$ if  $\Huse\le 0$.
-
-Prime candidate sources for authentication have $\Huse\le 0$.
-As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-Daugman estimates irises contain $249$ bits of entropy~\cite{daugman2004}.
-Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-Let the outcome of this transform~(on different irises) define a distribution $w$.
-The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
-For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.
-We have the following calculation for $\Huse$:
-\[
-\Huse = \Hoo(W) - \log |B_t|
-= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx -707.
-\]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
+There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
+The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.fuzzy extractor will only be used a polynomial number of times.
 
 \paragraph{Our Contributions}
-We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
-As explained above, such constructions cannot work without some restriction on the distribution.
-Our first construction is secure when symbols in $w$
-each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
-a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
-
-We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
-However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $\ell/\omega(\log\ell)$ errors.
+We provide the first constructions of reusable fuzzy extractors that allow for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
+Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
+Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
+Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
+In order to provide any meaningful security guarantee, the source distribution must be restricted.
+See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
+\begin{itemize}
+\item Provide an information-theoretic analogue of their construction.  We show a transform from locally computable extractors to fuzzy extractors.
+\item Significantly improve the error tolerance of the \cite[Construction 5.2]{canetti2014key}.
+This also allows the construction to have negative minimum usable, with any super-constant alphabet size~(previously it was any super-polynomial alphabet size.
+This solves the main open problem of~\cite{canetti2014key}.
+\end{itemize}
 
 \paragraph{Our Approach}
-Our constructions are computationally secure.
-Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).
-
-Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.
-We take the second approach.
-
-Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
-We show two constructions of \emph{computational fuzzy conductors}.
-These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
-
-Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.
-A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
-Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.
-For a point program, this means hiding all partial information about the point $w$.
-We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed.
-While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
-For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions.
-Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
-
-Both of our constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
-Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$.
-In the first construction (\consref{cons:first construction}), for each $j$, $\gen$ flips a coin $c_j$ and either obfuscates $I_{w_j}$ or picks a random point $r_j$ and obfuscates $I_{r_j}$.
-This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.
-With a close value $w'$, $\rep$ then runs the obfuscated program $P_j$ on $w_j'$ and checks whether $P_j(w_j')=1$.
-For most locations $j$, \rep can determine whether $w_j$ or a random value was obfuscated.
-Thus, most bits of $c_j$ are recoverable.
-To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code.
-This construction conducts entropy from $w$ to $c$.
-
-Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
-We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then applies the first construction.
-$\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.
-This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
-This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
-Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed in the first construction.
-Computational, rather than information-theoretic, analysis seems crucial for achieving this property.
-
-\paragraph{Connection to General Obfuscation}
-We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
-However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
-Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
-However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
-The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero.
-However, we do not know if these functions include proximity point programs.
-
-\paragraph{Open Problems}
-Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Codes over large alphabets are often used to correct burst errors~\cite{gilbert1960capacity}.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
-However, distributions with $\Huse \le 0$ are supported only for large alphabets.
-For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
-Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.
-
-Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
-The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$.
-Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree).
-Constructing an efficient obfuscator for proximity queries when $\Huse\le 0$ is an open problem.
-
-In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
-An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.
-A meaningful restriction of correctable errors is an open problem.
+Like the work of Canetti et al., our fuzzy extractors are built from point obfuscation.  \bnote{write more here}
 
 \medskip
-The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
+
+The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe reusable fuzzy extractors in \secref{sec:fuzzy extractors}, and present our construction in \secref{sec:construction}.
 
@@
 
-\subsection{Coding Theory}
-\label{sec:coding theory}
-We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
-\begin{definition}
-\label{def:hamming z channel}
-For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
-\end{definition}
-
-\begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+%\subsection{Coding Theory}
+%\label{sec:coding theory}
+%We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
+%\begin{definition}
+%\label{def:hamming z channel}
+%For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
+%\end{definition}
+%
+%\begin{definition}
+%Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
 Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
 } \decode(c') \neq c] \leq \delta_{code}$.
-\end{definition}
-
-\textbf{Notes:}
-Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
-Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+%\end{definition}
+%
+%\textbf{Notes:}
+%Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+%Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
 These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
-The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
+%The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
 See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.
@@
 For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
-\section{Computational Fuzzy Extractors}
+\section{Reusable Fuzzy Extractors}
 \label{sec:fuzzy extractors}
 
-In this section we present our paradigm for constructing computational fuzzy extractors.
+In this section we define reusable fuzzy extractors.
+We weaken the previous definition of Boyen that allowed for arbitrary reusability~\cite[Definitions 6 and 7]{Boyen2004}.
+We will consider a fixed amount of reusability.
+Restricting to limited reuse or a computationally bounded adversary~(that can only interact with a limited number of uses) is necessary to overcome the negative results of Boyen.
+These negative results show that the correlation between $w_1,..., w_q$ must be extremely limited in the unbounded reuse setting.
+
 Definitions for information-theoretic fuzzy extractors can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
@@
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+We begin by reviewing the definition of a computational fuzzy extractor.
+We then consider definitions of reusable fuzzy extractors.
 
@@
 
-Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.
-We follow the second approach.
-The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.
-%In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
-To overcome these bounds, we use a computational version of a fuzzy conductor.
+Our goal for defining outsider security is to allow reusability when each reading comes from an admission distribution.
+There are two possible ways to model the security game, the first is to provide security for joint distributions $W_1,..., W_q$ when each $W_i$ is an admissible distribution.
+A stronger definition uses a multi-stage adversary game where the adversary is allowed to specify the next reading after seeing previous sketches.
+We allow the first stage of the adversary to be unbounded, but restrict the second stage of the adversary when providing computational security.
+Let $A_{sam}, A_{guess}$ be some adversary.
+
+\begin{enumerate}
+%\item[\textbf{Preparation:}] An unbounded $A_{sam}$ specifies to the challenger a distribution $W_1\in\mathcal{M}$.
+We assume there is an efficient procedure to sample from this distribution, but ignore this issue.
+%\item[\textbf{Initialization:}] The challengers samples $w_1\leftarrow W_1$.  The challenger computes $(r_1, p_1)\leftarrow \gen(w_1)$.
+\item[\textbf{Queries:}] For queries $i=1,..., q$, $A_{sam}$ computes $w_i\leftarrow A_{sam}(p_1,..., p_{i-1})$.  The challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
+\item[\textbf{Guessing:}] The adversary outputs $r^*\leftarrow A_{guess}(p_1,..., p_i)$.  The adversary wins if for some $i$, $r^* = r_i$.
+\end{enumerate}
+
+\begin{definition}
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+If for $A_{sam}$ of size at most $s_{sam}$ and $A_{guess}$ of size at most $s_{guess}$.
+For $i=1,..., q$, let $W_{i, p_1,..., p_{i-1}}$ be distribution produced by $A_{sam}(p_1,..., p_{i-1})$.
+We say that $(\gen, \rep)$ is a $(q, \epsilon_{reuse}, s_{sam}, s_{guess})$-reusable fuzzy extractor if $\forall i=1,..., q, \forall p_1,..., p_{i-1}$, $W_{i, p_1,..., p_{i-1}}\in\mathcal{W}$ then $\Pr[\text{exists i}| r^*\leftarrow A_{guess}(p_1,..., p_q) \wedge r^* = r_i] <\epsilon_{reuse}$.
+
+We say that $(\gen, \rep)$ is a reusable fuzzy extractor if it for any $q = \poly(n), s_{guess} = \poly(n)$, there is some $\epsilon = \ngl(n)$ such that $(\gen, \rep)$ is a $(q, \epsilon_{reuse}, \infty, s_{guess})$-reusable fuzzy extractor.
+\end{definition}
+
+\begin{itemize}
+\item In the case where $\gen$ is deterministic we can consider simple consider security to hold for all joint distributions $\forall W_1,..., W_q$ where each $W_i\in\mathcal{W}$.
+We provide an adaptive definition above, the adversary to refine the distribution based on seeing the value of sketch.
+\item We require the adversary to guess one of the output keys $r_i$.
+This is weaker than requiring them to guess a reading $w_i$.
+A successful guess for a reading $w_i$ can be easily transformed to a corresponding key, but the reverse is not necessarily true.
+\item We allow $A_{sam}$ to keep state between queries, in particular they may remember the previously sampled $w_1,..., w_{i-1}$.
+Alternatively, we could have $A_{sam}$ output some state information that is provided in the next queries.
+These two alternatives are equivalent.
+\item The definition of Boyen required the adversary to guess the original reading $w_1$.
+This was necessary as they did not require other readings were admissible distributions.
+To allow arbitrary correlation between readings we must require that they are individually secure.
+\end{itemize}
+
+The work of Canetti et al. shows that a computational fuzzy conductor can be converted to a computational fuzzy extractor using a computational extractor.  We will use the same paradigm here.
+
 We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
@@
 \end{definition} 
-We now define a computational fuzzy conductor and a (computational)~randomness extractor.
-A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-\begin{definition}
+A computational fuzzy conductor is the computational analogue of a fuzzy conductor.
+\begin{definition}~\cite[Definition 3.3]{canetti2014key}
 \label{def:comp fuzzy cond}
@@
 Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained.
-We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
+We provide an average case version of the definition of Krawczyk~\cite{krawczyk2010cryptographic}:
 \begin{definition}
@@
 
-Combining a computational fuzzy conductor and an appropriate computational extractor yields a computational fuzzy extractor~(proof in \apref{sec:cond and cext}):
+Combining a reusable computational fuzzy conductor and an appropriate computational extractor yields a reusable computational fuzzy extractor:
 
+\bnote{write this theorem}
 \begin{lemma}
@@
 
-\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}
+\section{A reusable computational fuzzy extractor for arbitrary correlations}
 \label{sec:construction}
 For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.
-Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
-Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
-
-\begin{construction}
-\label{cons:first construction}
-Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
-Let  $C\subset \zo^\ell$ be an error-correcting code.
-We describe $\gen, \rep$ as follows:
-
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_\ell$
-\item Sample $c\leftarrow C$.
-\item For $j=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
-\item Else: Sample $r_j \overset{\$}\leftarrow \mathcal{Z}$.
-\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
-\end{enumerate}
-\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(w', p)$
-\item For $j=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item If $p_j(w_j') = 1$: set $c_j' = 0$.
-\item Else: set $c_j' = 1$.
-\end{enumerate}
-\item Set $c = \decode(c')$.
-\item Output $c$.
-\end{enumerate}
-\vspace{0.15in}
-\end{minipage}
-\end{tabular}
-\end{center}
-\end{construction}
-
-The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
-In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
-There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
-However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
-This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
-
-\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
-By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
-This restriction on the distribution is captured in the following definition.
 
@@
 
-We show some examples of unguessable block distributions in \apref{sec:characterize}.
-In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
-
-\begin{theorem}
-\label{thm:main thm first cons}
-Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
-\end{theorem}
-\begin{proof}
-We first argue security in the following Lemma.
-
-\begin{lemma}
-\label{lem:security of cons}
-Let all variables be as in \thref{thm:main thm first cons}.
-For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
-\end{lemma}
-
-We give a brief outline of the proof here; the proof is in \apref{app:security of main cons}.
-\begin{proof}[Outline]
-It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
-Let $J$ be the set of indices that exists according to \defref{def:block guessable}.
-Define the distribution $C'$ as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.
-We first note that $C'$ has sufficient entropy, because $\Hav(C' |P) = \Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - |J^c|$ (the second step is by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
-It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
-%Define the distribution $X$ as follows:
-%\[X_i =
-%\begin{cases}
-%W_i & C_i = 0\\
-%R_i & C_i = 1.
-%\end{cases}\]
-The outline for the rest of the proof is as follows:
-\begin{itemize}
-\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$.
-Since $P$ is a collection of obfuscated programs, there exists a simulator $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
-\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.
-That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
-\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
-\end{itemize}
-\end{proof}
-We now argue correctness of \consref{cons:first construction}.
-We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
-%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
-However, we start by justifying our use of unidirectional codes.
-\begin{lemma}
-\label{lem:no 1 to 0 flips}
-Let all variables be as in \thref{thm:main thm first cons}.
-The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
-\end{lemma}
-\begin{proof}
-Consider a coordinate $j$ for which $c_j=1$.
-Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$.
-The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
-\end{proof}
-
-Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
-Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
-\end{proof}
-
-\subsection{Discussion of \consref{cons:first construction}}
-\label{sec:discussion}
-\lnote{I did not check this calculation -- will do}
-To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
-\[
-\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
-\]
-
-We consider what entropy is necessary for security.
-The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
-For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
-This yields:
-\[
-\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
-
-\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
-
-If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
-
-%\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
-Do we need it?} There are three major drawbacks to \consref{cons:first construction}.
-First, we require blocks to be super-polynomial in size.
-Second, we only obtain a single bit from each block.
-Third, since each block is individually obfuscated, we leak information about individual blocks if they can be guessed.
-To compensate for this leakage, we need most\lnote{just some linear fraction, not most, right?
-and, in fact, isn't just one block enough given our repeated use argument which we haven't really made yet?} blocks to be unguessable given equality queries.
-Our second construction addresses this last weakness.
-
-\section{Trading Errors for Entropy}
-\label{sec:sampling}
-\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.
-Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.
-In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously, at the price of  decreasing the effective error tolerance.
-%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
 The main idea is to sample a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscate the concatenation of these blocks.
@@
 
-The main change in \consref{cons:sampling} is that the obfuscated values are concatenated symbols of $W$.
-This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
-For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
-
-This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
-Goldreich provides an introduction to samplers in~\cite{goldreich2011sample}.
-
-\lnote{in prev construction's theorem statement, $\mathcal{Z}$ grows as a function of $n$, and here it doesn't have to, but may.
-Right now the differences between the two theorems are too subtle to notice.
-Make theorem statements similar and highlight the differences.}
-\begin{theorem}
-\label{thm:sampling}
-Let $\mathcal{Z}$ be an alphabet.
-Let $n$ be a security parameter.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
-$\ell = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs. 
-  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
-\begin{align*}
-t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
-\tilde{m} &=H_0(C)\\
-\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
-\end{align*}
-\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
-\end{theorem}
-
-The next two sections are dedicated to proving this theorem.
- For security we argue that each of the $v_i$ values is unguessable.
-For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability), so that $c'$ will be corrected to $c$ with overwhelming probability.
-
-\subsection{Security of \consref{cons:sampling}}
-In order to show security \consref{cons:sampling}, we
-show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
-We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
-Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
-We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
-Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
-be some particular outcome.
-
-\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Not for submission.}
-\begin{lemma}
-\label{lem:sampling works}
-Let all variables be as in \thref{thm:sampling}.
-There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
-\[
-\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
-\]
-\end{lemma}
-
-\noindent
-We can then argue that all $V_i$ simultaneously have individual entropy with good probability~(by union bound):
-\begin{corollary}
-\label{cor:samp sec}
- Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.
-Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
-%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
-\end{corollary}
-%\begin{proof}
-%Union bound over the probability in \lemref{lem:sampling works}.
-%%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
-%\end{proof}
-
-In ~\clref{cl:all blocks entropy} we show that any distribution where each individual block has super-logarithmic min-entropy forms a unguessable block distribution.  This allows us to conclude:
-\begin{corollary}
-\label{cor:v are unguessable}
-Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
-Take any $q=\poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
-\end{corollary}
-
-Thus, unless the choice of $\lambda$ is very unlucky,
-\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. That is, 
-\begin{corollary}
-\label{cor:samp unguess}
-Let all the variables be as in \thref{thm:sampling}.
-For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq H_0(C)$.
-%for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
-\end{corollary}
-%\begin{proof}
-%Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
-%\end{proof}
-
-\subsection{Correctness of \consref{cons:sampling}}
-\label{sec:correct sampling}
-The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.
-Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$.
-We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.
-The proof is in \apref{sec:sampling errors}.
-The correctness argument in \thref{thm:sampling} is obtained by subtracting the probability of a single $1\rightarrow 0$ bit flip~($\ell/|\mathcal{Z}|$) and the error of the code~($\delta_{code}$).
-
-\begin{lemma}
-\label{lem:sampling errors}
-Let all the variables be as in \thref{thm:sampling}.
- Then $\Pr[v'\in\neigh_{t'}(v)]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.
-%That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
-\end{lemma}
-
-%\begin{corollary}
-%Let all the variables be as in \thref{thm:sampling}.
-%When
-%\[
-%\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
-%\]
-%and $(c, p)\leftarrow \gen(w)$, then
-%\[
-%\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
-%\]
-%That is, \consref{cons:sampling} is correct with overwhelming probability.
-%\end{corollary}
-
-\subsection{Discussion of \consref{cons:sampling}}
-\lnote{I need to check this}
-We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.
-The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
-We are able to correct $O(\gamma/\eta)$ errors.
-This yields:
-\[
-\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
-\]
-That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
-We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
-%However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
 \bibliographystyle{alpha}
@@
 
-\appendix
-
-%\section{Use of Fuzzy Extractors for Biometrics}
-%Fuzzy extractors derive stable from noisy sources.
-Biometrics represent an important noisy physical source.
-Unlike physical unclonable functions, biometrics are fixed distributions.
-Biometrics cannot be redesigned to  increase their entropy or reduce their error rates.
-Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).
-Unfortunately, most work measures system security using false accept rate vs.
-false reject rate.
-This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.
-False accept rate provides no bound on the information leaked by the helper data.
-Indeed the helper data may completely reveal the original input.
-In high security applications, measuring false accept rate vs.
-false reject rate is insufficient to argue system security.
-%
-%\label{sec:iris no key}
-%As an example, we focus on the human iris.
-The iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.
-Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-There has been considerable research since the work of Daugman~\cite{daugman2004}.
-These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.
-We use the Daugman's parameters for our calculations.
-%
-%The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
-For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.%\footnote{Daugman  improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
-The comparison between the two readings is then made using bits not excluded by either image.
-It is not clear how to extend into the fuzzy extractor setting.
-Even with the masking vector $\Huse$ is negative for irises.}
-%We have the following calculation for $\Huse$:
-%\begin{align*}
-%\Huse &= \Hoo(W) - \log |B_t|\\
-%&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx 707.
-%\end{align*}
-%Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
-%Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
-%
-%\section{Minimal Conditions for Fuzzy Extractor Security}
-%\label{sec:minimal conditions}
-%
-%A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
-This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
-We make this intuition formal here:
-%
-%\begin{definition}
-%\label{def:fuzzy min-ent}
-%A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
-%\[
-%\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
-%\]
-%\end{definition}
-%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
-%\begin{lemma}
-%\label{lem:fuzz necessary}
-%Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-%\end{lemma}
-%\begin{proof}
-%Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
-Consider the following distinguisher $D$:
-%\begin{itemize}
-%\item On input $r, p$.
-%\item If $\rep(m, p) = r$, output $1$.
-%\item Else output $0$.
-%\end{itemize}
-%First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.
-Thus, when $\kappa = \omega(\log n)$:
-%\[
-%\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
-%\]
-%\end{proof}
-%\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
-This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-%The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
-%If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
-Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse\le 0$.
-This motivates our restriction to meaningful classes of source distributions with $\Huse\le 0$.
-%%This means we inherently must talk about the security and errors together.
-%
-%In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.
-There are two minimal types of distributions where $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).
-The other is that there $t+\omega(\log n)$ blocks that contribute some entropy~(there is a continuum between these two types).
-Definitions~\ref{def:block guessable} and~\ref{def:partial source} were developed for these types of sources respectively.
-However, we do not achieve security when $\Hfuzz(W)= \omega(\log n)$ for either definition, this is an open problem.
-
-%\section{Fuzzy Conductors}
-%\lnote{I need to check this}
-%\label{sec:conductors}
-%Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
-Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
-They suggest these bounds may be avoided by outputting a fresh random variable.
-This is known as a fuzzy conductor~\cite{KanukurthiR09}.
-%\begin{definition}
-%A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
-%\begin{enumerate}
-%\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
-%\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep(w', SS) = X]\geq 1-\delta$~(over the coins of $\gen', \rep'$).
-If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
-%\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.
-That is, $\exists Y$ with $\Hav(Y | SS ) \geq \tilde{m}$ such that $\Delta((X, SS), (Y, SS))\leq \epsilon$.
-%\end{enumerate}
-%\end{definition}
-%
-%\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
-This motivates our use of a computational fuzzy conductor in \defref{def:comp fuzzy cond}.
-%We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
-%\begin{itemize}
-%\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
-%%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
-%\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
-%\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
-%\end{itemize}
-%Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.
-%\begin{lemma}
-%The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
-%\end{lemma}
-%\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
-Let $A$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $A$.
-Define $(X,SS) \leftarrow \gen'(W)$.
-Then there must exist a distribution $Y$ with $\Hav(Y|SS) \geq \tilde{m}$ such that $\Delta((X,SS), (Y, SS))\leq \epsilon$.
-By Markov's inequality, there exists some set $B_{SS}$ such that $\Pr[ss\in B_{SS}] \geq 1/2$ and $\forall s\in B_{SS}$ one has $\Delta(X | SS = s, s ), (Y | SS = s, s)<2\epsilon$.
-Now applying Markov's inequality to $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.
-Denote by $s^*$ a value in $B_{SS}\cap B_{SS'}$~(one value must exist).
-Then $\Delta((X | SS =s^* , s^*), (Y| SS = s^*, s^*))\leq 2\epsilon$ and $\Hoo(Y|SS=s^*)\geq \tilde{m}-1$.
-Denote by the set $A'$ the possible values of $X$ when $SS=s^*$.
-For the statistical distance property to hold, $|A'| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
-Associate with every $x\in A'$ some $w\in S$ which could have produced $x$ with nonzero probability given $SS=s^*$, and call this map $C$.
-$C$ defines an error correcting code with the required parameters.
-%\end{proof}
-
-\section{Characterizing unguessable block distributions}
-\label{sec:characterize}
-
-\defref{def:block guessable} is an inherently adaptive definition and a little unwieldy.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
-The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may reshape the distribution of block $j$.
-In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).
-We first show some sources that are unguessable block distributions~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block distributions~(\secref{sec:negative ex}).
-
-\subsection{Positive Examples}
-\label{sec:positive ex}
-We begin with the case of independent blocks.
-
-\begin{claim}
-\label{cl:independent high ent}
-Let $W = W_1,  ...
-, W_\ell$ be a source in which all blocks $W_j$  are mutually independent.
-Let $\alpha$ be a parameter.
-Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.
-Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |J|)$-unguessable block distribution.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |J|)$-unguessable block distribution.
-\end{claim}
-\begin{proof}
-It suffices to show that for all $j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
-We can ignore queries for all blocks but the $j$th, as the blocks are independent.
-Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic ($S$ can calculate the best coins).
-Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block.
-Each $A_k$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed).
-Thus, the total number of possible responses is $q+1$.
-Thus, we have the following,
-\begin{align*}
-\Hav(W_j | View(S^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
-&=\Hoo(W_j) - |A_1, \dots, A_q|\\
-&=\alpha - \log (q+1)\,,
-\end{align*}
-where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
-\end{proof}
-\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
-\clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
-However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.
-
-\begin{claim}
-\label{cl:each block from single seed}
-Let $f:\zo^e \rightarrow \mathcal{Z}^\ell$ be a function.
-Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.
-If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
-\end{claim}
-\begin{proof}
-Since $f$ is injective on each block, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
-Consider a query $q_k$ on block $j$.
-There are two possibilities: either $q_k$ is not in the image of $f_j$,  or $q_k$ can be considered a query on the preimage $f_j^{-1}(q_k)$.
-Then (by assuming $S$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.
-Then the possible responses are strings with Hamming weight at most $1$ (like in the
-proof of \clref{cl:independent high ent}),
- and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $j$, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) \geq \Hoo(W_j) -\log (q+1)$.
-\end{proof}
-
-Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so there is a family of distributions with total entropy $\omega(\log n)$ for which \consref{cons:first construction} is secure.
-For these distributions, all the coordinates are as dependent as possible: one determines all others.
-We can prove a slightly weaker claim when the correlation between the coordinates $W_j$ is arbitrary:
-
-\begin{claim}
-\label{cl:all blocks entropy}
-Let $W = W_1,..., W_\ell$ be a source.
-Suppose that for all $j$, $\Hoo(W_j)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is super-logarithmic).
-Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block distribution.
-\end{claim}
-
-\begin{proof}
-Intuitively, the claim is true because the oracle is not likely to return 1 on any query. Formally, we proceed by induction on oracle queries,
-using the same notation as in the proof of   \clref{cl:independent high ent}. Our inductive hypothesis is
-that $\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0] \leq (k-1)2^{1-\alpha}$.  If the inductive hypothesis holds, then, for each $j$,
-\begin{equation}
-\label{eq:cond-entropy}
-\Hoo(W_j | A_1= \dots= A_{k-1}=0) \ge \alpha-1\,.
-\end{equation}
-This is true for $k=1$ by the condition of the theorem. It is true for $k>1$ because, as a consequence of the definition of $\Hoo$,
-for any random variable $X$ and event $E$, $\Hoo(X|E)\ge \Hoo(X)+\log\Pr[E]$; and $(k-1) 2^{1-\alpha}\leq 2 q 2^{-\alpha} \leq 1/2$.
-
-We now show that $\Pr[A_1\neq 0 \vee \dots \vee A_{k}\neq 0] \leq k 2^{1-\alpha}$, assuming that $\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0] \leq (k-1)2^{1-\alpha}$.
-\begin{align*}
-\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0 \vee A_k\neq 0] & =
-\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0]+\Pr[A_1=\dots = A_{k-1}=0 \wedge A_k=1]\\
-& \le  (k-1)2^{1-\alpha}+\Pr[A_k=1\,|\,A_1=\dots = A_{k-1}=0]\\
-& \le  (k-1)2^{1-\alpha}+\max_j 2^{-\Hoo(W_j | A_1=\dots =A_{k-1}=0)}\\
-& \le  (k-1)2^{1-\alpha}+ 2^{1-\alpha}\\
-& = k 2^{1-\alpha}
-\end{align*}
-(where the third line follows by considering that to get $A_k=1$, the adversary needs to guess some $W_j$, and the fourth line follows by~\eqref{eq:cond-entropy}).
-Thus, using $k=q+1$ in~\eqref{eq:cond-entropy},
- we know $\Hoo(W_j | A_1= \dots= A_q=0) \ge \alpha-1$.  Finally this means that
-\begin{align*}
-\Hav(W_j | A_1,\dots, A_q) &\ge -\log \left( 2^{-\Hoo(W_j | A_1= \dots= A_q=0)}\Pr[A_1=\dots=A_q=0]+1\cdot \Pr[A_1\neq 0 \vee \dots \vee  A_q\neq 0] \right)\\
-& \ge -\log \left(  2^{-\Hoo(W_j | A_1= \dots= A_q=0)}+q2^{1-\alpha} \right)\\
-& \ge -\log \left(  (q+1) 2^{1-\alpha}\right) = \alpha-1-\log(q+1)\,.
-\end{align*}
-\end{proof}
-
-\subsection{Negative Examples}
-\label{sec:negative ex}
-Claims~\ref{cl:each block from single seed} and~\ref{cl:all blocks entropy} rest on there being no easy ``entry'' point to the distribution.
-This is not always the case.
-Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.
-
-\begin{claim}
-Let $p = (\poly(n))$ and let $f_1,..., f_{\ell}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
-There is an adversary making $p\times \ell = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
-\end{claim}
-\begin{proof}
-Let $x$ be the true value for $U_{p\times \ell}$.
-We present an adversary $S$ that completely determines $x$.
-$S$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.
-Then $S$ queries on $(1, y_1),..., (1, y_p)$, exactly one answer returns $1$.
-Let this value be $y_1^*$ and its preimage $x_1^*$.
-Then $S$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.
-Again, exactly one of these queries returns $1$.
-This process is repeated until all of $x$ is recovered~(and thus $w$).
-%The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
-Once $x$ has been recovered then $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
-\end{proof}
-
-The previous example relies on an adversaries ability to determine a block from the previous blocks.
-We formalize this notion next.
-We define the entropy jump of a block source as the remaining entropy when other blocks are known:
-
-\begin{definition}
-Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.
-The \emph{jump} of a block $i_j$ is $\mathtt{Jump}(i_j) = \max_{w_{i_1},..., w_{i_{j-1}}} H_0 (W_{i_j} | W_{i_1} = w_{i_1} ,..., W_{i_{j-1}} = w_{i_{j-1}})$.
-\end{definition}
-
-If an adversary can learn blocks in succession they can eventually recover the entire secret.
-In order for a distribution to be block unguessable the adversary must get ``stuck'' early enough in their recovery process.
-This translates to having a super-logarithmic jump early enough.
-
-\begin{claim}
-Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\ell-\beta+1)$, then $W$ is not $(q, 0, \beta)$-unguessable block distribution.
-\end{claim}
-
-\begin{proof}
-For convenience relabel the ordering that violates the condition as $1,..., \ell$.
-We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.
-As before $S$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
-Then $S$ queries the (at most)~$q/(\ell-\beta+1)$ possible values for $W_2 | W_1$.
-This process is repeated until $W_{\ell-\beta+1}$ is learned.
-\end{proof}
-
-Presenting a sufficient condition for security is more difficult as $S$ may interleave queries to different blocks.
-It seems like the optimum strategy is to focus on a single block at a time but it is unclear how to formalize this intuition.
-
-\section{Proof of \lemref{lem:cond and cext}}
-\label{sec:cond and cext}
-\lnote{I need to check this}
-\begin{proof}
-It suffices to show if there is some distinguisher $D'$ of size $s'$ where
-\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
- then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
- \[
- \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
- \]
-Let $D'$ be such a distinguisher.  That is,
-\[
-\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
-\]
-Then define $D$ as follows.
-On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.
-Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
-Then we have the following:
-\begin{align*}
-\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
-&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
-&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
-&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
-\end{align*}
-Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
-\end{proof}
-
-\section{Proof of \lemref{lem:security of cons}}
-\label{app:security of main cons}
-\begin{proof}
-\lnote{I need to check this}
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.
-Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
-Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$.
-% for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
-Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
-By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.
-Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.
-Then
-$\Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - \beta$ (by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
-
-Let $D$ a distinguisher of size at most $s_{sec}$ such that
-\[
-| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
-\]
-Define the distribution $X$ as follows:
-\[X_j =
-\begin{cases}
-W_j & C_j = 0\\
-R_j & C_j = 1.
-\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
-\begin{align}
-\label{eq:dist before}
-|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-We now prove $S$ cannot distinguish between $C$ and $C'$.
-\begin{lemma}
-\label{lem:sim cannot distinguish}
-$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
-\end{lemma}
-
-\begin{proof}
-\noindent It suffices to show that for any two codewords that agree on $J^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
-\begin{lemma}
-\label{lem:codewords in I close}
-Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
-\[
-\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
-\]
-\end{lemma}
-\begin{proof}
-Recall that for all $j\in J$, $\Hav(W_j | View(S))\geq \alpha$.
-The only information about the correct value of $c_j^*$ is contained in the query responses.
-When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.
-We now show that for any value of $c^*$ all queries on $j \in J$ return $0$ with probability $1-2^{-\alpha+1}$.
-Suppose not, that is suppose, the probability of at least one nonzero response on index $j$ is $> 2^{-(\alpha+1)}$.
-Since $w, w'$ are independent of $r_j$, the probability of this happening when $c^*_j = 1$ is at most $q/\mathcal{Z}$ or  equivalently $2^{-\log |\mathcal{Z}|+\log q}$.
-Thus, it must occur with probability:
-\begin{align}
-2^{-\alpha+1}&<\Pr[\text{non zero response location }j]\nonumber \\
- &= \Pr[c_j^* =1]\Pr[\text{non zero response location }j\wedge c_j^*=1]\nonumber \\&+ \Pr[c_j^*=0] \Pr[\text{non zero response location }j \wedge c_j^*=0]\nonumber \\
-&\le 1\times 2^{-\log|\mathcal{Z}|+\log q} + 1\times  \Pr[\text{non zero response location }j \wedge c_j^*=0] \label{eq:ways to remove ent}
-\end{align}
-We now show that for an unguessable block source the remaining entropy $\alpha\leq \log |\mathcal{Z}|-\log q $:
-\begin{claim}
-\label{cl:ent bounded away from n}
-If $W$ is a $(q, \alpha, \beta)$-block unguessable distribution over $\mathcal{Z}$ then $\alpha \le \log |\mathcal{Z}|-\log q$.
-\end{claim}
-\begin{proof}
-\bnote{Leo I changed some of this under you.  It wasn't clear or probably right as written.}
-Let $W$ be a $(q, \alpha, \beta)$-block unguessable distribution.  Let $J\subset\{1,..., \ell\}$ the set of good indices.
-It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.
-Let $j\in J$ be some arbitrary element of $J$ and denote by $w_{j,1}, ..., w_{j,q}$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).
-Then $\sum_{i=1}^q \Pr[W_j = w_{j,i}]\geq q/|\mathcal{Z}|$.
-Suppose not, this means that there is some $w_{j,i}$ with probability $\Pr[W_j = w_{j,i}] < 1/|\mathcal{Z}|$.
-Since there are $\mathcal{Z} - q $ remaining possible values of $W_j$ for their total probability to be at least $1-q/|\mathcal{Z}|$ at least of these values has probability at least $1/\mathcal{Z}$.
-This contradicts the statement $w_{j,1},..., w_{j,q}$ are the most likely values.
-Consider $S$ that queries its oracle on $(j, w_{j,1}),.., (j, w_{j,q})$.
-Denote by $Bad$ the random variable when $W_j\in \{w_{j,1},.., w_{j,q}\}$  After these queries the remaining min-entropy is at most:
-\begin{align*}
-\Hav(W_j | S^{J_W(\cdot, \cdot)}) &=  -\log \left(\Pr[Bad=1]\times 1+ \Pr[Bad=0]\times \max_{w}\Pr[W_j = w| Bad =0]\right)\\
-&\leq  -\log \left(\Pr[Bad=1]\times 1\right)\\
-&=-\log\left( \frac{q}{|\mathcal{Z}|} \right) = \log|\mathcal{Z}|-\log q
-\end{align*}
-This completes the proof of \clref{cl:ent bounded away from n}.
-\end{proof}
-\noindent
-Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
-\begin{align*}
- \Pr[\text{non zero response location }j \wedge c_j=0] &>2^{-\alpha+1} - 2^{-(\log |\mathcal{Z}|-\log q)}=  2^{-\alpha}
- \end{align*}
- When there is a $1$ response and $c_j=0$ this means that there is no remaining min-entropy.
-If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-By the union bound over the indices $j\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$.
-Recall that $c^*, c'$ match on all indices outside of $J$.
-Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
-This concludes the proof of \lemref{lem:codewords in I close}.
-\end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.
-This completes the proof of \lemref{lem:sim cannot distinguish}.
-\end{proof}
-
-\noindent Now by the security of obfuscation we have that
-\begin{align}
-\label{eq:dist after}
-|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
-\begin{align*}
-\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})]| \\
-&+|\expe[S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] - \expe[S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\\
-&+|\expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] - \expe [D(P_1,..., P_\ell, C') ]|\\
-&\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
-&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
-\end{align*}
-This is a contradiction and completes the proof of \lemref{lem:security of cons}.
-\end{proof}
-
-\section{Proof of \lemref{lem:sampling works}}
-\label{sec:proof of sampling lemma}
-\begin{proof}
-Consider some fixed $i$.
-Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
-Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
-
-\begin{claim}
-\label{cl:vi have entropy}
-\[
-\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
-\]
-\end{claim}
-\begin{proof}
-Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
-We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
-Then
-\begin{align*}
-\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
-&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
-\end{align*}
-Taking the negative logarithm of both sides we have that
-\begin{align*}
-\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
-&\ge \sum_{j_k\in J} \alpha = \alpha X
-\end{align*}
-This completes the proof of \clref{cl:vi have entropy}.
-\end{proof}
-
-We note that $X$ is distributed according to the hypergeometric distribution,
-and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
-Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
-
-\bnote{this can also be tightened.}
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
- \[
-\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
-\]
-\end{proof}
-
-\section{Proof of \lemref{lem:sampling errors}}
-\label{sec:sampling errors}
-
-\begin{proof}
-Define $\mu = -\frac{1}{2}\log(1-t'/(2\ell)) = \Theta(1)$ and note that $t \leq \mu(\gamma - \eta)/\eta$. Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.
-Let
-the Bernoulli random variable $X_i=1$ if and only if $v_i \neq v_i'$, and $X=\sum_{i=1}^{\ell} X_i$. We need to show that $\Pr[X>t']=O(2^{-\ell})$.
-
-\begin{align*}
-\expe [1-X_i] &=\Pr[w \text{ and } w' \text{ agree on positions } {j_{i,1}},..., j_{i,\eta}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
-&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\left(\frac{1}{2}\right)^2\right)^\mu\\
-& = \left(\frac{1}{2}\right)^{-\log\left(1-\frac{t'}{2\ell}\right)} = 1-\frac{t'}{2\ell}\,.
-\end{align*}
-
-Hence, $\expe[X_i]\le t'/(2\ell) = O(1)$, and $\expe[X]\le t'/2$.
-By the Chernoff bound, we have \lnote{this can be tightened}
-\begin{align*}
-\Pr\left[\sum_{i=1}^\ell X_i\geq t'\right]\leq 2e^{-2(t'-\expe[X])^2\ell} \le
-2e^{-2(t'/2)^2\ell} = O(e^{- \ell})\,.
-\end{align*}
-\end{proof}
-
 \end{document}

### 2014-05-20 trunk/info-bounds/FuzzyExtPossibility.tex
adding info bounds paper

--- 2013-12-10 Asiacrypt/CompFuzzExt.tex
@@
 \documentclass[11pt]{article}
-%\documentclass{llncs}
 \def\shownotes{1}
@@
 \newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
+\newcommand{\Hfuzz}{\mathrm{H}^{\mathtt{fuzz}}_{t,\infty}}
+\newcommand{\Huse}{\mathrm{H}_{\mathtt{usable}}}
 \newcommand{\Dom}{\mathsl{Dom}}
@@
 \newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
-\newcommand{\xnote}[1]{{\authnote{Xianrui}{#1}}}
+\newcommand{\rnote}[1]{{\authnote{Ran}{#1}}}
+\newcommand{\onote}[1]{{\authnote{Omer}{#1}}}
 
@@
 \newcommand{\M}{\mathcal{M}}
+\newcommand{\Vol}{\mathsf{Vol}}
 
-\title{Computational Fuzzy Extractors}
-\author{Benjamin Fuller 
-\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
-~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
-%\author{}
+\title{When are Fuzzy Extractors Possible?}
+
 \begin{document}
@@
 \begin{abstract}
-Fuzzy extractors derive strong keys from noisy sources.  Their
-security is defined information-theoretically, which limits the length
-of the derived key, sometimes making it too short to be useful. We ask
-whether it is possible to obtain longer keys by considering
-computational security, and show the following.
+We characterize when deriving a stable key from a noisy source is possible.
+We use the notation of fuzzy extractors introduced by Dodis et al.
+(Eurocrypt 2004).
+The goal is to produce a strong $key$ from a $w$ drawn from a \emph{strong} distribution $W$ and to produce the same when given a nearby $w'$.
+A fuzzy extractor is split into two algorithms $\gen$ which produces $key$ along with some helper information $p$ and $\rep$ which takes $w'$ and $p$ to reproduce $key$.
+The key must remain strong in the presence of $p$.
+The goal is to produce the correct key whenever $\dis(w, w')\le t$.
 
-\begin{itemize}
-\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
-achieved using an information reconciliation component called a ``secure
-sketch.'' The security of this component, which directly affects the
-length of the resulting key, is subject to lower bounds from coding
-theory.  We show that, even when defined computationally, secure
-sketches are still subject to lower bounds from coding theory. Specifically, we consider
-two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy.
-For both cases we show  that computational secure sketches cannot outperform the best information-theoretic secure sketches in the case of high-entropy Hamming metric sources.
-
-\item\textbf{Positive Result:} We show that the negative result can be overcome by
-analyzing computational fuzzy extractors directly.  Namely, we show
-how to build a computational fuzzy extractor whose output key length
-equals the entropy of the source (this is impossible in the
-information-theoretic setting). Our construction is based on the
-hardness of the Learning with Errors (LWE) problem, and is secure when
-the noisy source is uniform or symbol-fixing (that is, each dimension
-is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
-that the decision version of LWE is secure even when a small number of
-dimensions has no error.
-\end{itemize}
-\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, error-correcting codes, computational entropy, randomness extractors.
+Ideally, key derivation should be possible whenever a negligible portion of $W$ lies within a ball~(arbitrarily centered) of radius $t$.
+We call the maximum overall weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.
+However, current techniques for constructing fuzzy extractors lie far from this necessary condition.
+We investigate whether this is necessary for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).
+Our results are centered on feasibility and our constructions and impossibility results are primarily information-theoretic.
 \end{abstract}
 
-\section{Introduction}\label{sec:introduction}
+\section{Introduction}
+Usually, authentication requires some high quality secret.
+Traditionally, this secret is assumed to have high min-entropy.
+However, many sources with sufficient entropy for authentication present an additional problem of noise.
+That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.
+To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.
 
-Authentication generally requires a secret drawn from some high-entropy source.
-One of the primary building blocks for authentication is reliable key derivation.
-Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).
+This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy}.
+They identify two fundamental tasks in noisy key derivation.
+The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.
+In this work, we consider the non-interaction version of these problems where these tasks are performed non-interactively~(with a single message).
 
-Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).
-The setting
-consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).
-The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.
-This information allows
-the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
-Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.
-This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
+The paradigm for performing noisy key derivation using a single metric is known as fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08}.
+Consider a particular high entropy distribution $W$.
+Our goal is to derive stable keys from $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
+A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes the initial reading $w$ and produces $key$ along with a public helper value $p$.
+The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.
+The $key$ must be strong even to an adversary that has observed $p$~(the problem is trivial if $p$ is private).
 
-Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.
-The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.
-In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.
-A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.
-Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.
+Traditionally, fuzzy extractors are constructed by using a separate information-reconciliation component, known as a secure sketch, that maps $w'$ back to $w$ and a privacy-amplification component, a strong randomness extractor~\cite{nisan1993randomness}, that maps $w$ to a random key.
+These objects can either be information-theoretic or computational.
+The computational versions of these objects are defined in~\cite{krawczyk2010cryptographic} and~\cite{fuller2013computational} respectively.
+Fuller et al.~\cite{fuller2013computational} show that computational secure sketches cannot improve significantly on information-theoretic secure sketches.
 
-We ask whether it is possible to obtain longer keys by considering
-computational, rather than information theoretic, security.
+\textbf{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
+If the error-tolerance allows the entire metric space to authenticate then no security is possible.
+As an example, consider a distribution $W$, where the adversary attempts to learn the key simply by inputting a point to the reproduce function.
+Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
+For a fuzzy extractor to be secure this must occur with negligible probability.
+That is, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
+We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
+Clearly, the fuzzy min-entropy of a distribution must be super-logarithmic for any security.
+Indeed, in the interactive setting this is a sufficient condition as well.
 
-\paragraph {Our Negative Results}
-We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called a \emph{secure sketch}.
-A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.
-The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.
-This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors produce random strings from strings with conditional min-entropy.
-We call this the \emph{sketch-and-extract} construction.
+However, in the one-round setting we are far from achieving security for all distributions with super-logarithmic fuzzy min-entropy.
+Traditional fuzzy extractors and secure sketches incur at entropy loss of the size of the ball to be error-corrected.
+While, this is optimal for the uniform distribution, it seems far from optimal for distributions where points are far apart.
+Indeed, when the goal is provide key derivation from a source that has more errors than entropy, this bound provides no guarantee on the strength of the key.
+The work of Canetti et al.~\cite{canetti2014key} shows it is possible to provide key derivation for some distributions of this type.
+However, their work leaves the question open for a large number of distributions.
+In this work, we attempt to settle this question: for what distributions is noisy key derivation possible and impossible?
+\bnote{come back to this}
 
-The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).
-Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.
-Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
-
-Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.
-This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
-Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.
-For high-entropy sources of $w$ over the Hamming metric, this bound matches the best information-theoretic security sketches.
-
-\paragraph {Our Positive Results}
-
-Both of the above negative results arise because a secure sketch functions like a decoder of an error-correcting code.
-To avoid them, we give up on building computational secure sketches and focus directly on the entropy loss in fuzzy extractors.
-Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.
-
-By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$.
-Our construction is for the Hamming metric and uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.
-First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$ (this idea is similar to the way the code-offset construction is presented in
-\cite{JW99} as  a ``fuzzy commitment'').
-Our construction uses private randomness, which is allowed in the fuzzy extractor setting but not in noiseless randomness extraction.
-Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.
-
-Specifically,  we use the  recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012}, which shows the hardness of decoding random linear codes when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.
-This allows us to use $w$ as the error vector, assuming it is uniform.
-We also use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009},  which says that LWE has many hardcore bits, to hide $r$.
-
-Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.
-Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor.
-If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.
-Given the hardness of decoding random linear codes~\cite{berlekamp1978}, we do not expect significant improvement in the error-tolerance of our construction.
-
-In \secref{sec:LWE block fixing sources}, we are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed).
-This relaxation follows from our results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).
-
-\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.
-They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.
-One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.
-However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.
-Furthermore, this approach does not allow the use of private randomness; private randomness is a crucial ingredient in our construction.
-We compare the two approaches in \secref{sec:prg based comparison}.
+\textbf{Our results:} In this work we show awesome things!\bnote{write}
 
@@
 \label{sec:preliminaries}
-For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.
+For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.
+For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
+The set $J^c$ is the complement of $J$.
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
 and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
+For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.
-We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
+For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
+We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
+
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
-If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.
-For the Hamming metric over $\mathcal{Z}^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.
+If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\ell$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
+For this metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.
+Unless otherwise noted logarithms are base $2$.
+Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
 
-\subsection{Fuzzy Extractors and Secure Sketches}
-\label{sec:fuzzy extractors}
+\section{Fuzzy Extractors}\label{sec:fuzz extractor}
 
@@
 
+Replacing the statistical distance in \defref{def:fuzzy extractor} with a computational distance results in a computational fuzzy extractor~\cite[Definition 2.5]{fuller2013computational}.
+
 Secure sketches are the main technical tool in the construction of fuzzy extractors.
@@
 
-Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
+\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
+Also we do not consider a computational version of secure sketches as Fuller et al.
+showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
 
@@
 \end{lemma}
-The main parameter we will be concerned with is the entropy loss of the construction.
-In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.
-We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
-Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).
 
-\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
-Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
-\begin{itemize}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
-\end{itemize}
-\end{definition}
-Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.
+\subsection{A necessary condition for security}
+\label{sec:minimal conditions}
+We now define fuzzy min-entropy and show that fuzzy extractor security is only possible when the fuzzy min-entropy is super-logarithmic.
 
-\textbf{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.
-In the information-theoretic setting this seemed inherent as the ``correct'' $R$ should be information-theoretically unknown conditioned on $P$.
-However, in the computationally setting this is not true.
-Looking ahead, in our construction $R$ is information-theoretically determined conditioned on $P$~(with high probability over the coins of \gen).
-Our $\rep$ algorithm will never output an incorrect key~(with high probability over the coins of \gen) but may not terminate.
-However, it is not clear this is the desired behavior.
-For this reason, we leave the behavior of \rep ambiguous when $\dis(w, w')>t$.
-
-\section{Impossibility of Computational Secure Sketches}
-\label{sec:impossCompSecSketch}
-In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.
-We consider two different notions for computational entropy, and for both of them show that corresponding secure sketches are subject to the same upper bounds as those for information-theoretic secure sketches.
-Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help.
-
-In particular, for the case of the Hamming metric and inputs that have full entropy, our results are as follows.
-In  \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.
-In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.
-Dodis et al.
-\cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  construct sketches with essentially the same information-theoretic security\footnote{The security in  \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  is expressed in terms of entropy of the error rate; recall that $\log B_t(\cdot)\approx H_q(t/n)$, where $n$ is the number of symbols, $q$ is the alphabet size, and $H_q$ is the $q$-ary entropy function.} .
-In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.
-
-\subsection{Bounds on Secure Sketches using HILL entropy}
-\label{sec:imp HILL sketch}
-HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.
-It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.
-Here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}); since we show impossibility even for this weaker definition, impossibility for the stronger definition follows immediately.
+A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
+This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
+We make this intuition formal here:
 
 \begin{definition}
-\label{def:relaxed hill}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon$.
+\label{def:fuzzy min-ent}
+A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+\[
+\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+\]
 \end{definition}
+For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
+\begin{lemma}
+\label{lem:fuzz necessary}
+Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
+\end{lemma}
+\begin{proof}
+Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
+Consider the following distinguisher $D$:
+\begin{itemize}
+\item On input $r, p$.
+\item If $\rep(m, p) = r$, output $1$.
+\item Else output $0$.
+\end{itemize}
+First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
+Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.
+Thus, when $\kappa = \omega(\log n)$:
+\[
+\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
+\]
+\end{proof}
+\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+This means that fuzzy min-entropy is also a necessary condition for interactive solution.
+In the interactive setting, fuzzy min-entropy is also a sufficient condition using secure two-party computation\bnote{cite something for this}.
+However, in the non-interactive setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.
+We attempt to bridge this gap in this work.
 
-Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.
-Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the sketch-and-extract construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.
-We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.
-
-Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches).
-For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.
-In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.
-
-The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.
-In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $X, Y$ such that $\Hav(X | Y)\geq \tilde{m}$ and $(X, Y)$ is computationally indistinguishable from $(W, \sketch(W))$.
-Sample a sketch $s\leftarrow \sketch(W)$.
-We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).
-%So, by indistinguishability, it must also succeed on $Y$.
- Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability, $\rec (x',y) = x$ with high probability.
- This means we can construct a large set $\mathcal{C}$ from the support of $X|y$.
-$\mathcal{C}$ will be an error correcting code and $\rec$ an efficient decoder.
-We can then use standard arguments to turn this code into an information theoretic sketch.
-
-To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
-\begin{definition}
-\label{def:neighborhood samplable}
-We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.
-\end{definition}
-
-We review the definition of a Shannon code~\cite{shannon1949mathematical}:
-\begin{definition}
-\label{def:shannon-code}
-Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
-To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
-\end{definition}
-This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.
-For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.
-However, we work with an arbitrary recover functionality that is not necessarily monotone.}.
-Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.
+\section{Well-spread distributions}
+We will start with an intuitively simple type of distribution where no results are known.
+Security should be easy when all points of $W$ are far apart.
+Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.
+Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).
+However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.
+We begin by defining a well-spread distribution.
 
 \begin{definition}
-Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+A distribution $W$ is called \emph{$t_{sec}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{sec}$.
 \end{definition}
-An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
-See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.
-An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
-We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
+Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{sec}/2$~(assuming the distribution has super-logarithmic min-entropy).
+Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.
+
 \begin{lemma}
-\label{lem:averageToMaximalError}
-Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
-There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
+Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works only for $W$.
+In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.
+\rec is efficient if there exists efficient decoding for the points in $W$.
+By \lemref{lem:fuzzy ext construction} there also exists a fuzzy extractor.\bnote{fill in the parameters}
 \end{lemma}
 
-We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
-\begin{theorem}\label{thm:impSketchArbitraryW}
-Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.
-Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-Let $s_{rec}$ denote the size of the circuit that computes $\rec$.
-If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
-\end{theorem}
+Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
+Ideally, a secure sketch should be able to recover for any well-spread distribution.
+However, as we show below this is not possible.
 
-For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).
-The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the symbols of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$).
-The formal statement of this result  can be expressed in the following Lemma (which is implicit in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}).
 \begin{lemma}
-\label{lem:shannon to sketch}
-For an alphabet $\mathcal{Z}$, let $\mathcal{C}$ over $\mathcal{Z}^n$ be a $(t, \delta)$ Shannon code.
-Then there exists a $(\mathcal{Z}^n, m, m-(n\log|\mathcal{Z}|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$.
+Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.  Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.  Then $\tilde{m}<....$.
 \end{lemma}
-Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
-\begin{corollary}
-\label{cor:rec yields sketch}
-Let $\mathcal{Z}$ be an alphabet.
-Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-$4(\epsilon+t\delta)$. 
-\end{corollary}
-\textbf{Note} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
-
-\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |\mathcal{Z}|-\tilde{m})-2$ bits of entropy.
-
-\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
-\label{sec:imp unp sketch}
-In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.
-However, HILL entropy is a strong notion.
-In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.
-We begin by recalling the definition of conditional unpredictability entropy~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}, which captures the notion of ``hard to guess'' (we relax the definition slightly, similarly to the relaxation of HILL entropy described in the previous section).
-
-\begin{definition}
-\label{def:unp entropy}
-Let  $(W, S)$ be a pair of random variables.
-We say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
-\[
-\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
-.\]
-\end{definition}
-
-We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.
-Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a \emph{reconstructive} extractor~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).
-
-Unfortunately, the conditional unpredictability entropy $\tilde{m}$ must decrease as $t$ increases, as the following theorem states.
-(The proof of the theorem, generalized to more metric spaces, is in \secref{sec:proof of imp unp entropy}.)
-
-\begin{theorem}
-\label{thm:imp of unp entropy}
-Let $\mathcal{Z}$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{Z}^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq t(|\rec|+n\log |\mathcal{Z}|)$, then $\tilde{m}\leq n\log |\mathcal{Z}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
-\end{theorem}
-In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.
-As mentioned at the beginning of~\secref{sec:impossCompSecSketch}, essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the randomized code-offset construction.
-However, it is conceivable that unpredictability entropy secure sketches could achieve lower entropy loss with greater efficiency for some parameter settings.
-
-\subsection{Avoiding sketch entropy upper bounds}
-\label{ssec:avoiding bounds}
-
-The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  
-This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed, and thus there is no (computational)~entropy loss.  
-This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .
-
-Both of lower bounds arise because \rec must function as an error-correcting code for many points of any indistinguishable distribution.
-It may be possible to avoid these bounds if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.
-This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.
-Such an algorithm is called a computational fuzzy conductor.
-See~\cite{KanukurthiR09} for the definition of a fuzzy conductor.
-To the best of our knowledge, a computational fuzzy conductor has not been defined in the literature, the natural definition is to replace the pseudorandomness condition in \defref{def:comp fuzzy extractor} with a HILL entropy requirement.
-
-Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).
-It may be possible to achieve significantly better parameters with a construction that is a computational fuzzy conductor~(but not a computational fuzzy extractor) and then applying an extractor.
-We leave this as an open problem.
-
-\section{Computational Fuzzy Extractor based on \class{LWE}}
-\label{sec:fuzzyCompExt}
-
-In this section we describe our main construction.
-Security of our construction depends on the source $W$.
-We first consider  a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.
-Our construction uses the code-offset construction~\cite{JW99}, \cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.
-Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).
-
-\begin{construction}
-Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. 
-Define $\gen, \rep$ as follows:
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
-\item Sample $\vA\in\Fq^{m\times n}, \vx\in\Fq^n$ uniformly.
-\item Compute $p = (\vA, \vA \vx+w)$, \\\ $r = \vx_{1,...,n/2}$.
-\item Output $(r, p)$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
-\item Parse $p$ as $(\vA, \vect{c})$; let $\vb=\vect{c}-w'$.
-\item Let $x = \decode_t(\vA, \vb)$\\
-\item Output $r = x_{1,...,n/2}$.
-\end{enumerate}
-\end{minipage} 
-\end{tabular}
-\end{center}
-\label{cons:informal construction}
-\end{construction}
-
-Intuitively, security comes from the computational hardness of decoding random linear codes with a high number of errors (introduced by $w$).  
-In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.
-Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.
-
-The rest of this section is devoted to making these intuitive statements precise.
- We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
-We describe one possible polynomial-time $\decode_t$ (which corrects more errors than is possible by exhaustive search) in \secref{sec:time main construction}.
-In \secref{sec:lossless extractor}, we describe parameter settings that allow us to extract as many bits as the input entropy, resulting in a lossless construction.
-In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a sketch-and-extract approach (\lemref{lem:fuzzy ext construction}) instantiated with a computational extractor.
-
-\subsection{Security of \consref{cons:informal construction}}
-\label{subsec:LWE}
-The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a complete description of the $\LWE$ problem and related lattices problems~(which we do not define here) see~\cite{regev2005LWE}.
-We now recall the decisional version of the problem.
-
-\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
-Let $n$ be a security parameter.  
-Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime\footnote{%
-Unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding.}.
-%
-Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $X$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
- The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
-$(\vA, \vA X+\chi)$ from
- the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.
-
-We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
-If for any $s_{sec} = \poly(n)$, there exists   $\epsilon  = \ngl(n)$ such that  $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure, then we say  it is \emph{secure}.
-\end{definition}
-
- Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
-Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.
-If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.
-(A recent result of Brakerski et al.~\cite{brakerski2013classical} shows security of $\LWE$ based on hardness of approximating lattices problems for classical algorithms.
-We have not considered how this result can be integrated into our analysis.)
-
-The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
-Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$, under the same assumptions, when errors come from the uniform distribution over a small interval\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.
-The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.
-This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.
-The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
-\begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
-\label{lem:uniform LWE decision}
-Let $n$ be a security parameter.
-Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer with $m\ge 3n$.
-Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$.
-If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]^m$,  $\distLWE_{n, m, q, \chi}$ is secure.
-\end{lemma}
-
-To extract pseudorandom bits, we use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has simultaneously many hardcore bits.
-The result says that if $\distLWE_{(n-k, m, q, \chi)}$ is secure then any $k$ variables of $X$ in a $\distLWE_{(n, m, q, \chi)}$ instance are hardcore.
-We state their result for a general error distribution~(noting that their proof does not depend on the error distribution):
-\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
-\label{lem:many hardcore bits}
- If $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ secure, then
-\[\delta^ {\mathcal{D}_{s_{sec'}}} ((X_{1,\dots, k}, \vA, \vA X+\chi) , (U, \vA, \vA X+\chi)) \le \epsilon\,,\]
-where $U$ denotes the uniform distribution over $\Fq^k$,  $\vA$ denotes the uniform distribution over $\Fq^{m\times n}$, $X$ denotes the uniform distribution over $\Fq^n$, $X_{1,\dots, k}$ denote the first $k$ coordinates of $x$, and $s_{sec}' \approx s_{sec} - n^3$.
-\end{lemma}
-The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} when parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.
-
-\subsection{Efficiency of \consref{cons:informal construction}}
-\label{sec:time main construction}
-\consref{cons:informal construction} is useful only if $\decode_t$ can be efficiently implemented.
-We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.
-We present a simple $\decode_t$ that runs in polynomial time and can correct $O(\log n)$ errors (note that this corresponds to a superpolynomial number of possible error patterns).
-This algorithm is a proof of concept, and neither the algorithm nor its analysis have been optimized for constants.
-An improved decoding algorithm can replace our algorithm, which will increase our correcting capability and improve \consref{cons:informal construction}.
-
-\begin{construction}
-\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
-\begin{enumerate}
-\item Input $\vA , \vb = \vA \vx + w - w'$
-\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
-\item Restrict $\vA, \vb$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vb_{i_1,...,i_{2n}}$.
-\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
-If no such rows exist, output $\perp$ and stop.
-\item Denote by $\vA', \vb'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vb_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $\vx' = (\vA')^{-1}\vb'$.  
-\item If $\vb- \vA \vx'$ has more than $t$ nonzero coordinates, go to step (2).
-\item Output $\vx'$.
-\end{enumerate}
-\end{construction}
-
-Each step is computable in time $O(n^3)$. 
-For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $w$ and $w'$ agree on those rows).
-If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $\vx'=\vx$, and the algorithm terminates.
-However, we also need to ensure correctness: we need to make sure that if $\vx'\neq \vx$, we detect it in step 6.
-This detection will happen if $\vb-\vA \vx' = \vA (\vx-\vx')+(w-w')$ has more than $t$ nonzero coordinates.
-It suffices to ensure that $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $w-w'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.
-
-Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.
-Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
-The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
-\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
-\label{lem:i t poly time}
-Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.
-Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this expectation is over the choice of random coins of $\decode_t$, regardless of the input, as long as $\dis(w, w')\le t$).
-It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
-\end{lemma}
-
-\subsection{Lossless Computational Fuzzy Extractor}
-\label{sec:lossless extractor}
-We now state a setting of parameters that yields a lossless construction.
-The intuition is as follows.
-We are splitting our source into $m$ blocks each of size $\log \rho q$~(from \lemref{lem:uniform LWE decision}) for a total input entropy of $m\log \rho q$.
-Our key is derived from hardcore bits of $X$: $X_{1,\dots, k}$ and is of size $k \log q$~(from \lemref{lem:many hardcore bits}).
-Thus, to achieve a lossless construction we need $k \log q = m\log \rho q$.
-In other words, in order to decode a meaningful number of errors, the vector $w$ is of higher dimension than the vector $X$, but each coordinate of $w$ is sampled using fewer bits than each coordinate of $X$.
-Thus, by increasing the size of $q$~(while keeping $\rho q$ fixed) we can set $k\log q = m\log \rho q$, yielding a key of the same size as our source.
-The formal statement is below.
-
-\begin{theorem}
-\label{thm:lossless secure extractor log}
-Let $n$ be a security parameter and let the number of errors $t = c\log n$ for some positive constant $c$.
-Let $d$ be a positive constant (giving us a tradeoff between running time of $\rep$ and $|w|$).
-Consider the Hamming metric over the alphabet $\mathcal{Z}=[-2^{b-1},2^{b-1}]$, where  $b = \log 2(c/d+2) n^2 =O(\log n)$.
-Let $W$ be uniform over $\mathcal{M}=\mathcal{Z}^m$, where $m={(c/d+2)n}=O(n)$.
-If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, m\log |\mathcal{Z}|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
-The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
-\end{theorem}
-\begin{proof}
-Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}; efficiency follows by \lemref{lem:i t poly time}.
-For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.
-\end{proof}
-
-\thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.
-We can essentially think of $\vA X+W$ as an encryption of $X$ that where decryption works from any close $W'$.
-
-\subsection{Comparison with computational-extractor-based constructions}
-\label{sec:prg based comparison}
-As mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.
-We will call this approach \emph{sketch-and-comp-extract}.
-(A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; note that LWE-based pseudorandom generators exist~\cite{applebaum2006pseudorandom}.)
-
-This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.
-However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.
-
-In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor.
-Instead, we require that $w$ is not computationally recoverable  given $p$.
-This requirement is weaker---in particular, in our construction, $w$ may have no information-theoretic entropy conditioned on $p$.
-The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$.
-Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.
-
-The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.
-In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes, because decoding algorithms will not reach the information-theoretic decoding radius.
-
-Unfortunately, LWE parameter sizes require relatively long $w$.
-Therefore, in practice, sketch-then-comp-extract will beat our construction  if the computational extractor is instantiated efficiently based on assumptions other than LWE (for example, a cryptographic hash function for an extractor and a block cipher for a PRG).
-However, we believe that our conceptual framework can lead to better constructions.
-Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.
-
-To summarize, the advantage of \consref{cons:informal construction} is that the security of our construction does not depend on the decoding radius $t$.  
-The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.
-We begin to address this second problem in the next section.
-
-\section{Computational Fuzzy Extractor for Nonuniform Sources}
-\label{sec:LWE block fixing sources}
-While showing the security of~\consref{cons:informal construction} for arbitrary high-min-entropy distributions is an open problem, in this section we show it for a particular class of distributions called symbol-fixing.
-First we recall the notion of a symbol fixing source~(from~\cite[Definition 2.3]{KZ07}):
-\begin{definition}
-Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where each $W_i$ takes values over an alphabet $\mathcal{Z}$.  We say that it is a $(m+
-\alpha, m, |\mathcal{Z}|) $ \emph{symbol fixing source} if for $\alpha$ indices $i_1, \dots, i_\alpha$, the symbols $W_{i_\alpha}$ are fixed, and the remaining $m$  symbols are chosen uniformly at random.
-Note that $H_\infty(W)=m\log |\mathcal{Z}|$.
-\end{definition}
-
-Symbol-fixing sources are a very structured class of distributions.
-However, extending \consref{cons:informal construction} to such a class is not obvious.
-Although symbol-fixing sources are deterministically extractible~\cite{KZ07}, we cannot first run a deterministic extractor before using \consref{cons:informal construction}.
-This is because we need to preserve distance between $w$ and $w'$ and an extractor must not preserve distance between input points.
-We present an alternative approach, showing security of $\LWE$ directly with symbol-fixing sources.
-
-The following theorem states the main technical result of this section, which is of potential interest outside our specific setting.
-The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$ (but for $n$ and $m$ reduced by the amount of fixed symbols).
-\begin{theorem}
-\label{thm:blockLWE}
-Let $n$ be a security parameter, $m, \alpha$ be polynomial in $n$, and $q=\poly(n)$ be a prime and $\beta\in\mathbb{Z^+}$ be such that $q^{-\beta} = \ngl(n)$. 
-Let $U$ denote the uniform distribution over $\mathcal{Z}^m$ for an alphabet $\mathcal{Z}\subset \Fq$, and let $W$ denote an $(m+\alpha, m, |\mathcal{Z}|)$ symbol fixing source over $\mathcal{Z}^{m+\alpha}$.
-If $\distLWE_{n, m,q, U}$ is secure, then $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ is also secure.
-\end{theorem}
-
-\thref{thm:blockLWE} also holds for an arbitrary error distribution~(not just uniform error) in the following sense.
-Let $\chi'$ be an arbitrary error distribution.
-Define $\chi$ as the distribution where $m$ dimensions are sampled according to $\chi'$ and the remaining dimensions have some fixed error.
-Then, security of $\distLWE_{n, m, q, \chi'}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi}$.
-We show this stronger version of the theorem in \apref{sec:proof of block theorem}.
-
-The intuition for this result is as follows.
-Providing a single sample with no error ``fixes'' at most a single variable.
-Thus, if there are significantly more variables than samples with no error,  search $\LWE$ should still be hard.
-We are able to show a stronger result that $\distLWE$ is still hard.
-The nontrivial part of the reduction is using the additional $\alpha+ \beta$ variables  to ``explain'' a random value for the last $\alpha$ samples, without knowing the other variables.
-The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.
-A similar theorem for the case of a single fixed dimension was shown in concurrent work by Brakerski et al.~\cite[Lemma 4.3]{brakerski2013classical}.
-The proof techniques of Brakerski et al.
-can be extended to our setting with multiple fixed dimensions, improving the parameters of \thref{thm:blockLWE}~(specifically, removing the need for $\beta$).
-
-\thref{thm:blockLWE} allows us to construct a lossless computational fuzzy extractor from block-fixing sources:
-
-\begin{theorem}
-\label{thm:lossless block sketch log}
-Let $n$ be a security parameter and let $t = c\log n$ for some positive constant $c$.
-Let $d\le c$ be a positive constant and consider the Hamming metric over the alphabet $\mathcal{Z}=[-2^{b-1},2^{b-1}]$, where $b \approx \log 2(c/d+2)n^2 = O(\log n)$.
-Let $\mathcal{M} = \mathcal{Z}^{m+\alpha}$ where $m= (c/d+2)n=O(n)$ and $\alpha \leq n/3$.
-Let $\mathcal{W}$ be the class of all $(m+\alpha, m, |\mathcal{Z}|)$-symbol fixing sources.  If GAPSVP and SIVP are hard to approximate within polynomial factors 
-using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
- there exists $\epsilon = \ngl(n)$ 
-such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, m\log |\mathcal{Z}|, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
- The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
-\end{theorem}
-
-\begin{proof} Security follows by Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} and  \thref{thm:blockLWE} .  
-Efficiency follows by \lemref{lem:i t poly time}.  For a more detailed explanation of parameters see \secref{ssec:block params}. 
-\end{proof}
-
-\section*{Acknowledgements}
-The authors are grateful to Jacob Alperin-Sheriff, Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.
-In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.
-
-This work is supported in part by National Science Foundation grants 0831281, 1012910, and 1012798.
-The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-
 \bibliographystyle{alpha}
 \bibliography{crypto}
-\appendix
-\section{Properties of Random Linear Codes}
-For efficient decoding of \consref{cons:informal construction}, we need the $\LWE$ instance to have high distance with overwhelming probability.
-We will use the $q$-ary entropy function, denoted $H_q(x)$ and defined as $H_q(x) = x\log _q(q-1) - x\log_q x - (1-x)\log_q (1-x)$.
-Note that $H_2(x) = -x\log x - (1-x)\log (1-x)$.
-In the region $[0, \frac{1}{2}]$ for any value $q'\geq q$, $H_{q'}(x)\leq H_{q}(x)$.
-The following theorem is standard in coding theory:
 
-\begin{theorem}~\cite[Theorem 8]{venkatLecture}
-\label{thm:random code good distance}
-For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .
-If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
-\end{theorem}
-Our setting is the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
-\begin{corollary}
-\label{cor:code high distance}
-Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
-Let $q$ be a prime and $\tau = O(\frac{m}{n}\log n )$.
-For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $\tau$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
-\end{corollary}
-\begin{proof}
-Let $c$ be some constant.
-Let $\delta = \tau/m = \frac{c\log n}{n}$.
-We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).
-It suffices to show that for sufficiently large $n$, there exists $\epsilon>0$ where $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.
-For sufficiently large $n$:
-\begin{itemize}
-\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
-\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
-\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.
-\end{proof}
-
-We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
-\begin{claim}
-\label{cl:full rank matrix}
-Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
-let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha] >  1- q^{-\beta}$.
-\end{claim}
-\begin{proof}
-Let $p_i$ be the probability that the $i$th
-row is linearly dependent on the previous $i-1$ rows. 
-By the union bound, the probability that $\alpha$ rows are linearly dependent is bounded by 
-$\sum_{i=1}^\alpha p_i$.
-Since $i-1$ rows can span a space of size at most $q^{i-1}$, the probability $p_i$ that a randomly chosen $i$th row is in that space is at most $q^{i-1}/q^{\alpha+\beta}$. So
-\begin{align*}
-\Pr[\rank(\vS) < \alpha] &=\sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
-= \frac{q^{\alpha}-1}{q-1}\frac{1}{q^{\alpha+\beta} }< q^{-\beta}.
-\end{align*}
-\end{proof}
-
-\section{Proof of Theorem \ref{thm:blockLWE}}
-\label{sec:proof of block theorem}
-
-\begin{proof}
-We assume that all of the fixed blocks are located at the end and their fixed value is $0$.  If the blocks are fixed to some other value, the reduction is essentially the same.
- In the reduction, the distinguisher is allowed to depend on the source and can know the positions of the fixed blocks and their values.
-For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.
-For a set $T$ of column indices, we denote by $\vA_T$ the restriction of the matrix $\vA$ to the columns contained in $T$.
-Similarly, for a vector $\vx$ we denote by $\vx_T$ the restriction of $\vx$ to the variables contained in $T$.
-We use similar notation for the complement of $T$, denoted $T^c$.
-For a matrix or vector we use $\mathsf{T}$ to denote the transpose.
-We use $i$ as a index into matrix rows and the error vector and $j$ as an  index into columns and the solution vector.
-
-Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.
-Let $\beta$ be such that $q^{-\beta} = \ngl(n)$.
-All operations are computed modulo $q$, and we omit $``\bmod q$'' notation.
-Let $\chi'$ be some error distribution over $\Fq^m$ and let $\chi$ over $\Fq^{m+n}$ be defined by sampling $\chi'$ to obtain values on dimensions $1,..., m$ and then appending $\alpha$ 0s.
-
-Let $D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi}$ with advantage $\epsilon>1/\poly(n)$.
-Let  $\vA$ denote the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $X$ denote the uniform distribution over $\Fq^{(n+\alpha+\beta)}$, and $U$ denote the uniform distribution over $\Fq^{m+\alpha}$ .
-Then
-\[
-|\Pr[D(\vA, \vA X+\chi) = 1] - \Pr[D(\vA, U )=1]|> \epsilon.
-\]
-
-We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.
-Let $\vA'$ denote the uniform distribution over $\Fq^{m\times n}$, $X'$ denote the uniform distribution over $\Fq^n$, and $U'$ denote the uniform distribution over $\Fq^{m}$ .
-We will build a distinguisher $D'$ of polynomial size for which
-\begin{align}
-\label{eq:block LWE dist}
-|\Pr[D'(\vA', \vA'X'+\chi') = 1] - \Pr[D'(\vA', U') =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
-\end{align}
-$D'$  will make a single call to $D$, so we focus on how to prepare a random block-fixing instance for $D$ from the random instance that $D'$ is given.
-The code for $D'$ is given in \figref{fig:perfectLWEreduction}.
-
-\begin{figure}[p]
-\begin{framed}
-\begin{enumerate}
-\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$ for $\ve'\overset{\$} \leftarrow \chi'$ and uniform $\vx'\  \overset{\$} \leftarrow \Fq^n$.
-\item Choose $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$ uniformly at random. Initialize $\vQ \in \Fq^{m\times (\alpha+\beta)}$  to be the zero matrix.
-\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, for uniformly chosen $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
-\item Choose $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ uniformly at random.
-		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
-\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of indices of these columns.\label{step:find columns}
-\item For all $1\le j \le \alpha+\beta$, $j\notin T$:
-\label{step:fill in matrix}
-\subitem Choose $x_{n+j}\overset{\$}\leftarrow \Fq$ uniformly at random.  
-\subitem For $i=1,..., m$:
-\subsubitem Choose $\vQ_{i,j}\overset{\$}\leftarrow \Fq$ uniformly at random.
-\subsubitem Set $b_i^* = b_i^* + \vQ_{i,j} x_{n+j}$.
-\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
-\item \label{step:randomization}
-For {$i=1,..., m$}:
-\subitem Choose a row vector $\gamma_i \leftarrow \Fq^{1 \times \alpha}$ uniformly at random.
-\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
-\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+\alpha})^{\mathsf{T}}$
-\item For $i=m+1,\dots, m+\alpha$:
-\subitem Set $\va_i \leftarrow \va^*_i$
-\subitem Set $b_i = b_i^*$.
-\item Output $D(\vA, \vb)$. 
-\end{enumerate}
-\end{framed}
-\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
-\label{fig:perfectLWEreduction}
-\end{figure}
-
-The distinguisher $D'$ has an advantage when $\vS$ is of rank $\alpha$.  This occurs with overwhelming probability:
-\begin{claim}
-\label{cl:full rank matrix 5.2}
-Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
-\end{claim}
-\begin{proof}
-Direct result of \clref{cl:full rank matrix} because $q^{-\beta} = \ngl(n)$.
-\end{proof}
-The probability that a random $\vS$ is not full rank is $\ngl(n)$ so the distinguisher $D$ must still have an advantage when the matrix $\vS$ is full rank.  That is,
-\[
-|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
-\]
-
-It suffices to show that $D'$ prepares a good instance for $D$ conditioned on $\vS$ being full rank. We show this in the following three claims: 
-\begin{enumerate}
-\item If $\vA'$ is a random matrix then $\vA$ is a random matrix subject to the condition that $\rank(\vS) = \alpha$.
-\item If $\vb' = \vA'\vx'+\ve'$ for uniform $\vA'$ and $\vx'$, then $\exists \vx$~(uniformly distributed and independent of $\vA$ and $\ve'$) such that $\vb = \vA \vx + \ve$, where $\ve_i = \ve_i'$ for $1\leq i\leq m$ and $\ve_i = 0$ otherwise.
-\item If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then the conditional distribution $\vb\,|\,\vA$ is also uniform.
-\end{enumerate}
-
-\begin{claim}
-\label{cl:randomMatrixDist}
-The matrix $\vA$ is distributed as a uniformly random choice from the set of all matrices whose bottom-right $\alpha\times (\alpha+\beta)$ submatrix $\vS$ satisfies $\rank(\vS) = \alpha$.
-\end{claim}
-\begin{proof}
-The bottom $\alpha$ rows of $\vA$ (namely, $\vR|\vS$) are randomly generated~(conditioned on $\rank(\vS) =\alpha$).
-The top left $m\times n$ quadrant of $\vA$ is also random, because it is produced as a sum of a uniformly random $\vA'$ with some values that are uncorrelated with $\vA'$.
-The submatrix of the top-right $m\times (\alpha+\beta)$ quadrant corresponding to $\vQ_{T^c}$~(recall this is the restriction of $\vQ$ to the columns not in $T$) is also random, because it is initialized with random values to which some uncorrelated values are then added.
-It is important to note that all these values are independent of $\gamma_i$ values.
-
-Thus, we restrict attention to the $m\times \alpha$ submatrix of $\vA$ that corresponds to $\vQ_T$ in $\vA^*$ (note that these values are $0$ in $\vA^*$).
-Consider a particular row $i$.
-That row is computed as $\gamma_i \vS_{T}$.
-Since $\vS_T$ is a full rank square matrix and $\gamma_i$ is uniformly and independently generated, that row is also uniform and independent of other entries in $\vA$.
-\end{proof}
-\begin{claim}
-\label{cl:random ax+e}
-If $D'$ is provided with input distributed as $\vA', \vb' = \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$, where
-\begin{itemize}
-\item $e_i = e_i'$ for $1\leq i\leq m$,
-\item $e_i = 0$ for $m<i\leq m+\alpha$,
-\item $x_j = x_j'$ for $1\leq j \leq n$,
-\item and $x_j$ is uniform and independent of $\vA$ and $\ve'$ for $n<j\le n+\alpha+\beta$,
-\end{itemize}
-\end{claim}
-\begin{proof}
-Partially define $\vx$ as $x_j = x_j'$ if $1\leq j \leq n$ and $x_j$ as the value generated in step~\ref{step:fill in matrix} for $j>n $ and $j\not\in T$.
-Define the remaining variables $\vx_T$ as the solution to the following system of equations.
-\begin{eqnarray}
-\vS_T  \vx_T = \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \vx' - \vS_{T^c} \vx_{T^c}  \label{eq:x t solution}
-\end{eqnarray}
-A solution $\vx_T$ exists as $\vS_T$ is full rank.
-Moreover, it is uniform and independent of $\vA$ and $\ve$, because $b^*_{m+1}, \dots, b^*_{m+\alpha}$ are uniform and independent of $\vA$ and $\ve$.
-
-We now show that $\vb^* = \vA^* \vx+\ve$.
-All entries in matrix $\vQ$ corresponding to variables in $T$ are set to zero.
-Thus, the values of $\vx^T$ do not affect $b_i^*$ for $1\le i \le m$.
-The values of $\vx_{T^c}$ are manually set, and $\vQ_{i, j} \vx_{j}$ is added to the corresponding $b_i^*$.
-Thus, for $1 \leq i \le m$, we have $\vb^* = \vA^*\vx+\ve$.
-For $m< i$, this constraint is also satisfied by the values of $\vx_T$ set in Equation~\ref{eq:x t solution}.
-
-Thus, it remains to show that step~\ref{step:randomization} preserves this solution.
-We now show that for all rows $1\leq i\leq m$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
-Recall the other rows are not modified.  We have the following for $1\leq i\leq m$:
-\begin{align*}
-\va_i \vx + e_i &= \left(\va_{i}^*+ \gamma_i(\vR || \vS)\right) \vx + e_i\\
-&=\va_i^* \vx + e_i +\gamma_i(\vR||\vS) \vx\\&= b_i^* + \gamma_i (\vR||\vS)\vx
-\end{align*}
-Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,
-\begin{align*}
-(\vR|| \vS) \vx &= \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}  + \vS_T \vx_T \\
-&=\vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}+  \vS_{T^c} \vx_{T^c}   + \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}  - \vR \begin{pmatrix} \vx_1  \\ \vdots \\\vx_n \end{pmatrix}- \vS_{T^c} \vx_{T^c}
-\\&=  \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
-\end{align*}
-This completes the proof of the claim.
-\end{proof}
-\begin{claim}\label{clm:random b}
-If the conditional distribution $\vb'\,|\,\vA'$ is uniform, then $\vb\,|\,\vA$ is also uniform.
-\end{claim}
-\begin{proof}
-Since $\vR, \vS$, and $\vQ$ are chosen independently of $\vb'$, the distribution $\vb'\,|\,\vA^*$ is uniform.
-Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.
-Its first $m$ coordinates are  computed by adding the uniform vector $\vb'$ to values that are independent of $\vb^*$, and its remaining $\alpha$ coordinates $b^*_{m+1},\dots,b^*_{m+\alpha}$ are   chosen uniformly.
-Thus $\vb^*\,|\,\vA^*$ is uniform.
-
-Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.
-It is independent of $\vb^*$ and $\vA^*$, so $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform.
-Let $\vgamma'=\left(\begin{array}{c | c}\vect{I_m} & \vgamma \\\hline \vect{0} & \vect{I_\alpha}\end{array}\right)$.
-Note that $\vb=\vgamma' \vb^*$.  Since $\vb^*\,|\,(\vA^*, \vgamma)$ is uniform, and $\vgamma'$ is invertible, $\vb\,|\,(\vA^*, \vgamma)$ must also be uniform.
-Since $\vA$ is a deterministic function of $\vA^*$ and $\vgamma$ (assuming Step~\ref{step:find columns} is deterministic---if not, we can fix the coins used), the distribution $\vb\,|\,\vA$ is the same  as $\vb\,|\,(\vA^*, \vgamma)$ and is thus also uniform.
-\end{proof}
-
-Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $D'$ properly prepares the instance thus,
-\begin{align*}
-&\left|\Pr[D'(\vA, \vA X+\chi) = 1] - \Pr[D'(\vA, U) =1] \right|\\
-&\, = \left| \Pr\left[D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
-&\, =\left|\Pr[D(\vA, \vA X+\chi) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, U) =1 | \rank(\vS) = \alpha]  \right| \Pr[\rank(\vS) = \alpha] \\
-&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
-\end{align*}
-Where the second line follows because we can detect when $\rank(\vS)<\alpha$ and output a random bit in this case.
-Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
-\end{proof}
-\section{Additional Proofs}
-
-\subsection{Proof of \lemref{lem:averageToMaximalError}}
-\label{sec:proof of average to maximal error}
-\begin{proof}
-Let $C$ be the  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$ such that  $\Hoo(C)\geq k$.  Then for all $t'\le t$
-\[
-\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \neigh (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
-\]
-For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \neigh(c, t') \wedge \rec(c') \neq c]$.  
-Then by Markov's inequality:
-\[
-\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
-\]
-Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.
-Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.
-Since $H_\infty(C)\geq k$, we know $|C'|\geq 2^{k-1}$~(otherwise $\Pr_{c\leftarrow C}[c\in C']=\sum_{c\in C'}\Pr[C=c]$ would be less than $2^{k-1}\frac{1}{2^k} = 1/2$).
-This completes the proof of the~\lemref{lem:averageToMaximalError}.
-\end{proof}
-
-\subsection{Proof of \thref{thm:impSketchArbitraryW}}
-\label{sec:proof of thm sketch implies code}
-\begin{proof}
-  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
-\[ 
-\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\le \epsilon\, ,
-\]  
-where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. 
-Define $D$ as:
-\begin{enumerate}
-\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{enumerate}
- By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
-$\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.
-Let $X_y$ denote the random variable $X|Y=y$.
-By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.
-
-Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.
-Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).
-Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).
-Thus, for all such that $t', 1\leq t'\leq t$, 
-\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \neigh(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
-Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.
-The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.
-\end{proof}
-
-\subsection{Proof of \thref{thm:imp of unp entropy}}
-\label{sec:proof of imp unp entropy}
-Instead of proving the result just for Hamming metric over $\mathcal{Z}^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.
-We now define this second condition:
-\begin{definition}
-A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
-\end{definition}
-
-\begin{theorem}
-Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.
-Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least some fixed value $B_t(\cdot)$.
-Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.
-If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
-\end{theorem}
-\begin{proof}
-Let $(X, Y)$ be two random variables such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.
-It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq |\mathcal{M}| (1-\epsilon -t\delta) / |B_t(\cdot)|$.
-
-Let $B_t(x)$ denote the random variable representing a random neighbor of distance at most $t$ from $x$ (note that $B_t$ may not be efficiently samplable, because we are assuming only that a neighbor a fixed distance is efficiently samplable).
-We begin by showing that \rec must recover points of $X$.  
-\begin{claim}
-\label{clm:y is recoverable}
-\begin{align*}
-\Pr[\rec(B_t(X), Y) = X]&=\\
-\Pr[(x, y)\leftarrow (X, Y) \wedge x'\leftarrow B_t(x) \wedge \rec(x', y) = x] &\geq 1-\epsilon -t\delta.
-\end{align*}
-\end{claim}
-\begin{proof}
-Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.
-We construct the following distinguisher $D\in\mathcal{D}_{s_{sec}}$ (the distinguisher design is slightly complicated by the fact that we don't know at which particular distance $t'$ the recover procedure is most likely to fail, so we have to try all distances):
-\begin{itemize}
-\item Input $w\in \mathcal{M}, s\in\zo^*$.
-\item For all $1\leq t'\leq t$: 
-\subitem  $w'\leftarrow \neigh(w, t')$.
-\subitem If $\rec(w', z) \neq  w$ output $0$.
-\item Output $1$.
-\end{itemize}
-First note that $|D| = t( |\rec|+ s_{neigh} )$.
-Since $(\sketch, \rec)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.
-If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist at least one $1\leq t'\leq t$ for which $\Pr[\rec(\neigh(X, t'), Y) = X] < 1-\epsilon -t\delta$.
-Then
-\begin{align*}
-\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(X, Y)=1] &\geq\\
-(1-t\delta) - \Pr[\rec(\neigh(X, t'), Y) = X] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
-\end{align*}
-This is a contradiction and the statement of the claim follows.
-\end{proof}
-
-Now define $\mathcal{I}$ as follows:
-\begin{itemize}
-\item Input $y\in\zo^*$.
-\item Sample $x'\leftarrow \sample$.
-\item Output $\rec(x', y)$.
-\end{itemize}
-Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$. 
-We now show that $\mathcal{I}$ predicts $X$:
-\begin{align*}
-\Pr[\mathcal{I}(Y) = X] & = \\
-&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
-&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[\sample = x' ] \Pr[\rec(x', y) =x]\\
-&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x' \mathrm{ s. t. } \dis(x', x)\le t} \Pr[\sample = x']\Pr[\rec(x', y) =x]\\
-&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\mathrm{ s. t. } \dis(x', x)\le t} \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[B_t(x) = x'] \Pr[\rec(x', y) =x]\\
-&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
-\end{align*}
-(the last step follows by  \clref{clm:y is recoverable}).
-
-\thref{thm:imp of unp entropy} follows by noting that $\mathcal{Z}^n$ can be sampled in time $n\log |\mathcal{Z}|$ and neighborhood sampled in time $n\log |\mathcal{Z}|$.
-\end{proof}
-
-\subsection{Proof of \lemref{lem:i t poly time}}
-\label{sec:proof lem i t poly time}
-\begin{proof}
-Note that $\decode_t$ will stop if $w$ and $w'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
-The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
-\begin{align*}
-\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\left(\frac{m}{n}-2\right)\log n}{m-i}\right)\\
-&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
-&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}\,.
-\end{align*}
-(The second-to-last step holds as long as $n\ge 2d\log n$.) Because at each iteration, we select $2n$ rows independently at random, the expected number of iterations is at most $n^{4d}$; each iteration takes $O(n^3)$ operations in $\Fq$, which gives us the expected running time bound.
-
-The probability that $\decode_t$ outputs $\perp$ is bounded by 
-\begin{eqnarray*}
-\Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
-&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&= &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times}]\cdot \Pr[\rank(\vA_{i_1,\dots, i_{2n}})<n]\\
-&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot q^{-n}\\
-& = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
-\end{eqnarray*}
-The third line from the bottom follows from the fact that the locations of the errors are assumed to be independent of the sketch, and therefore independent of the matrix $\vA$.
-The second line from the bottom follows from \clref{cl:full rank matrix} when $\beta = n$; note that, because we use the union bound and evaluate the probability separately for each value of $j$,  we can treat $\vA_{i_1,\dots, i_{2n}}$ as a randomly chosen $2n\times n$ matrix, ignoring the fact that these matrices are correlated.
-
-We claim that if the code generated by $\vA$ 
-has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $\vx'=\vx$.
-Indeed, suppose $\vx'\neq \vx$.
-Since $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $w-w'$, such an $\vx'$ will not pass Step 6.
-
-The probability that the code generated by $\vA$ has distance lower than $2t+1$ is at most $e^{-\Omega(n)}$ (see \corref{cor:code high distance}), the probability of outputting $\perp$ is also $e^{-\Omega(n)}$~(computed above).
-This gives the correctness bound for $\decode_t$.
-\end{proof}
-
-\section{Parameter Settings for \consref{cons:informal construction}}
-\label{sec:parameter settings}
-In this section, we explain the different parameters that go into our construction.
-In \thref{thm:lossless secure extractor log} we give a lossless fuzzy extractor from a security parameter $n$ and an error $t$.
-In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.
-We begin by reviewing the parameters that make up our construction:
-
-\begin{itemize}
-\item $|W|$: The length of the source.  
-\item $t$: Number of errors that can be supported.  
-\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
-\item $q$: The size of the field.  
-\item $\rho$: The fraction of the field needed for error sampling.  
-\item $m$: The size of each number of samples in the LWE instance.  
-\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
-\end{itemize}
-We will split the source $|W|$ into $m$ blocks each of size $2\rho q+1$~(that is, $|W| = m\log (2\rho q+1)$).
-We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.
-As stated above we have three constraints:
-\begin{itemize}
-\item Maintain security of LWE.
-If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + \sigma} m = \poly(n)$.
-The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.
-We ignore this effect and assume that $\rho q = 2n^{1/2+\sigma}m$.
-\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
-\item Minimize entropy loss of the construction.
-We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.
-We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.
-Substituting, one has $m\log 2\rho q+1 = k \log q$.
-\end{itemize}
-Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
-\begin{align*}
-n_0&< n -k \\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+\sigma}m\\
-m\log (2\rho q +1)&= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
-\end{align*}
-This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma} m+1}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.
-Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n -k \\
-m &= \frac{(c/d+2)n \log n}{\log n} = (\frac{c}{d}+2)n\\
-f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma}m+1}{\log n} = \frac{g(c+2d)}{d}\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
-\end{align*}
-Note that $f$ is at a constant in $n$.
-Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= (\frac{c}{d}+2)n\\
-q & = n^f = n^{\frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
-\end{align*}
-
-Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $d<c$~(this also ensures that $m\geq 3n$, as required for \lemref{lem:i t poly time} to hold).
-Since $\rho q = 2n^{1/2+\rho }m = O(n^{5/2})$ in our setting $\rho = O(n^{-1/2})$.
-Thus, for large enough settings of parameters $\rho$ is less than $1/10$ as required by \lemref{lem:uniform LWE decision}.
-
-Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.
-We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).
-The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.
-In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.
-Setting $1<g<2$ achieves an increase in output length~(over the input length of $W$).
-We also (arbitrarily) set $\sigma=1/2$ to simplify the statement of \thref{thm:lossless secure extractor log}, making $\rho q = 2(c/d+2) n^2$.
-
-\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
-\label{ssec:block params}
-We repeat parameter settings for block fixing sources.
-We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.
-We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
-\begin{align*}
-n_0&< n -k  -\alpha -\beta\\
-t&\leq d \log n\left(\frac{m}{n}-2\right)\\
-q &= n^f\\
-\rho q  &= 2n^{1/2+\sigma}m\\
-m\log (2\rho q+1)&= k \log q
-\end{align*}
-Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
-\begin{align*}
-n_0&< n - k - \alpha -\beta\\
-t&\leq d\log n\left(\frac{m}{n}-2\right)\\
-m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
-\end{align*}
-As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.
-However, the last equation may have no solution for $f$ constant.
-Putting the last equation in terms of $f$ one has:
-\begin{align*}
-n_0&< n -k  - \alpha - \beta \\
-t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
-%f \log n &= \frac{m}{n}\log 2n^2m\\
-f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma} m+1)}{\log n}
-\end{align*}
-To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.
-Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
-\begin{align*}
-n_0&< n/3 -  \log n\\
-m &= \frac{(c/d+2)n \log n}{ \log n} = (\frac{c}{d}+2)n\\
-f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(3(\frac{c}{d}+2)\right)\frac{\log (4(\frac{c}{d}+2) n^{3/2+\sigma}+1)}{\log n} = O(1)
-\end{align*}
-
-Assuming $n/3-\log(n)> n_0$ and letting $t= c\log n$ we get the following setting:
-\begin{align*}
-m &= (\frac{c}{d}+2)n\\
-q & = n^f = n^{\frac{m}{n}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
-\rho q &= 2n^{1/2+\sigma}m = 2(\frac{c}{d}+2)n^{3/2+\sigma}
-\end{align*}
-
-As before we arbitrarily set $\sigma = 1/2$, giving $\rho q = 2(\frac{c}{d}+2)n^2$.
-Also, if $c<d$ then we get efficient decoding and $\rho = o(1)$ satisfying the condition of \lemref{lem:uniform LWE decision}.
 \end{document}

### 2014-05-20 trunk/resuable/resuableCompFuzzExt.tex
adding info bounds paper

@@
 \subsection{Obfuscation}
-Our construction uses obfuscation for a family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
+Our construction uses obfuscation for digital lockers $\mathtt{I}_n = \{I_{w, r}\}_{w \in \zo^n, r\in\zo^\kappa}$ defined as follows:
 \[
-I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
-\]
+I_{w, r}(x):\begin{cases} r & x=w\\\perp & \text{otherwise}\end{cases}.
+\].
+
+Digital lockers can be constructed from obfuscations of point functions~\cite{canetti2008obfuscating}.\bnote{need to introduce point functions.}  
 The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
@@
 They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
+A digital locker with output length $\kappa$ can be constructed from a $\kappa+1$ composable point obfuscation.
 
@@
 \end{definition}
-For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
+For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
 \section{Reusable Fuzzy Extractors}
@@
 1 & w_j = w_j'\\
-0 & \text{otherwise}.
+\perp & \text{otherwise}.
 \end{cases}
@@
 \item \underline{Input}: $w = w_1,..., w_\gamma$
-\item Select $c\overset{\$}\leftarrow C$.
+\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
 \item For $i=1,..., \ell$:
@@
 \item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
-\item If $c_i = 0$:
-\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
-\subitem Set $\rho_i = \mathcal{O}(I_{v_i})$.
-\subitem Set $p_i = \rho_i, \lambda_i$.
-\item If $c_i = 1$: Select $r_i \overset{\$}\leftarrow \mathcal{Z}^{\eta}$.
-\subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
+\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
+\item Set $\rho_i = \mathcal{O}(I_{v_i, r_i})$.
+\item Set $p_i = \rho_i, \lambda_i$.
 \end{enumerate}
-\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
+\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
 \end{enumerate}
@@
 \item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
-\item If $\rho_i(v_i') = 1$ set $c_i' = 0$.
-\item Else set $c_i' = 1$.
+\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
 \end{enumerate}
-\item Set $c = \decode(c')$.
-\item Output $c$.
+\item Output $\perp$.
 \end{enumerate}
@@
 
+\textbf{Discussion:} The construction of Canetti et al.~\cite{canetti2014key} encodes the key over a large number of obfuscations.
+To recover their key they must be correct on a large number of obfuscations.
+Instead, we use digital lockers allowing us to encode the entire key in each obfuscation.
+This means for correctness we only need to correctly recover a single obfuscation~(with high probability).
+This allows us to support a significantly higher error rate.
+The tradeoff is requiring higher composability of the point obfuscation.
+The construction of Canetti et al.
+requires order of key length composability~($O(\kappa)$) while we require order of key length times the number of obfuscations produced~($O(\kappa\times \ell)$).
+
+\begin{theorem}
+\label{thm:sampling}
+Let $\mathcal{Z}$ be an alphabet.
+Let $n$ be a security parameter.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma =\Omega(n)$.
+Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$, and let $c> 1$ be a constant and $\ell$ be such that $\ell = n^c$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
+\begin{align*}
+t&\leq -\frac{(c-1)}{2} \frac{(\gamma-\eta)\log n}{\eta} = o(\gamma)\\
+\delta &= e^{-n}
+\end{align*}
+\end{theorem}
+
+We will argue correctness, security, and reusability in turn.
+
+\subsection{Correctness of \consref{cons:sampling}}
+\label{sec:correct sampling}
+We are encoding the entire key in each obfuscation.
+For correctness, at least one of the repeated readings must be correct with overwhelming probability.
+Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.
+For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.
+\bnote{should talk about the obfuscation having some error}
+
+\bnote{can be tightened to $\omega(n^c \log n)$.}
+
+\begin{lemma}
+\label{lem:sampling errors}
+Let all the variables be as in \thref{thm:sampling}.
+ Then $\Pr[\forall i, v_i\neq v_i'] <1 - \ngl(n)$, where the probability is over the coins of $\gen$.  
+\end{lemma}
+\begin{proof}
+Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
+$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.  
+\begin{align*}
+\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
+&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
+\end{align*}
+We then have the probability that all $v_i\neq v_i'$ as:
+\begin{align*}
+\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
+&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
+&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
+\end{align*}
+This completes the proof of \lemref{lem:sampling errors}.
+\end{proof}
+
+\subsection{Security}
+
+\subsection{Reusability}
+
+\bnote{need to prove this new construction is a computational fuzzy conductor}
+
+\bnote{need to prove reusability}
+
 \bibliographystyle{alpha}

### 2014-05-20 trunk/constantRate/ConstCompFuzzExt.tex
Soundtrack to slides
adding super-constant alphabet size to main paper

@@
 Our second construction requires  a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
-The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+\bnote{update}The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
 
@@
 We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
-As explained above, such constructions cannot work without some restriction on the distribution.
+\bnote{need to split out the two constructions} As explained above, such constructions cannot work without some restriction on the distribution.
 Our first construction is secure when symbols in $w$
@@
 These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
+\bnote{first construction is conductor, second is fuzzy extractor}
 
@@
 \paragraph{Connection to General Obfuscation}
-We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
-However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
+We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.\bnote{update with new results} However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
 Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
@@
 For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
-Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.
+Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.  \bnote{Should this just be removed?}
 
@@
 \]
+\bnote{need to introduce digital lockers}
 The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
@@
 Denote this concatenated value by $V_1$.
-This process is repeated to produce $V_1,..., V_\ell$ and the construction proceeds by either obfuscating $V_i$ or a random point as before.
+This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct.
+We first present the necessary definitions and the construction and then compare it to \consref{cons:first construction}.
+% and the construction proceeds by either obfuscating $V_i$ or a random point as before.
 For security each value $V_i$ needs to be unguessable.  
@@
 Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions.  Define $\gen, \rep$ as:
+Let $\eta$ be a parameter, and $\mathcal{O}$ be an obfuscator for the family of digital lockers with $\kappa$-bit outputs.  Define $\gen, \rep$ as:
 
@@
 \item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
-\item If $c_i = 0$:
-\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
-\subitem Set $\rho_i = \mathcal{O}(I_{v_i})$.
-\subitem Set $p_i = \rho_i, \lambda_i$.
-\item If $c_i = 1$: Select $r_i \overset{\$}\leftarrow \mathcal{Z}^{\eta}$.
-\subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
+\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
+\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
+\item Set $p_i = \rho_i, \lambda_i$.
 \end{enumerate}
-\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
+\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
 \end{enumerate}
@@
 
-The main change in \consref{cons:sampling} is that the obfuscated values are concatenated symbols of $W$.
+\noindent
+There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
+\begin{itemize}
+\item Multiple blocks are concatenated together.
+This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.
 This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
+\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.
+This requires the use of digital lockers in place of point obfuscations.
+Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.
+\consref{cons:first construction} only hid part of the key in each obfuscation.
+This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
+\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.
+This construction works for an arbitrary size alphabet.
+We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
+\end{itemize}
+The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.\bnote{reusability}
 
@@
 Let $n$ be a security parameter.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
-$\ell = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs. 
-  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma =\Omega(n)$.
+Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$, and let $c> 1$ be a constant and $\ell$ be such that $\ell = n^c$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
 \begin{align*}
-t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
-\tilde{m} &=H_0(C)\\
-\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
+t&\leq -\frac{(c-1)}{2} \frac{(\gamma-\eta)\log n}{\eta} = o(\gamma)\\
+\delta &= e^{-n}
 \end{align*}
-\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
 \end{theorem}
@@
  For security we argue that each of the $v_i$ values is unguessable.
-For correctness we show that the induced error rate in $v$ and $v'$ is a small constant~(with overwhelming probability), so that $c'$ will be corrected to $c$ with overwhelming probability.
+For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.
 
@@
 We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
-Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
+Then security follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
+Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
+%By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
 We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
@@
 Thus, unless the choice of $\lambda$ is very unlucky,
-\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. That is, 
+\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. That is, \bnote{need to fix this corollary.}
 \begin{corollary}
@@
 Let all the variables be as in \thref{thm:sampling}.
-For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq H_0(C)$.
+For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.% \geq H_0(C)$.
 %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
@@
 \label{sec:correct sampling}
-The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.
-Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$.
-We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.
-The proof is in \apref{sec:sampling errors}.
-The correctness argument in \thref{thm:sampling} is obtained by subtracting the probability of a single $1\rightarrow 0$ bit flip~($\ell/|\mathcal{Z}|$) and the error of the code~($\delta_{code}$).
+\label{sec:correct sampling}
+We are encoding the entire key in each obfuscation.
+For correctness, at least one of the repeated readings must be correct with overwhelming probability.
+Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.
+For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$~(Proof in \apref{sec:sampling errors}) \bnote{should talk about the obfuscation having some error}
 
@@
 Let all the variables be as in \thref{thm:sampling}.
- Then $\Pr[v'\in\neigh_{t'}(v)]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.
-%That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
+ Then $\Pr[\forall i, v_i\neq v_i'] <1 - \ngl(n)$, where the probability is over the coins of $\gen$.  
 \end{lemma}
-
-%\begin{corollary}
-%Let all the variables be as in \thref{thm:sampling}.
-%When
-%\[
-%\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
-%\]
-%and $(c, p)\leftarrow \gen(w)$, then
-%\[
-%\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
-%\]
-%That is, \consref{cons:sampling} is correct with overwhelming probability.
-%\end{corollary}
 
@@
 The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
-We are able to correct $O(\gamma/\eta)$ errors.
+We are able to correct $o(\gamma)$ errors.
 This yields:
 \[
-\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
-\]
-That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
-We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
-%However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
+\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
+\]
+That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super constant.
+We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.
+
+\subsection{Reusability}
+\bnote{write this}
 \bibliographystyle{alpha}
@@
 \label{sec:sampling errors}
-
-\begin{proof}
-Define $\mu = -\frac{1}{2}\log(1-t'/(2\ell)) = \Theta(1)$ and note that $t \leq \mu(\gamma - \eta)/\eta$. Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.
-Let
-the Bernoulli random variable $X_i=1$ if and only if $v_i \neq v_i'$, and $X=\sum_{i=1}^{\ell} X_i$. We need to show that $\Pr[X>t']=O(2^{-\ell})$.
-
+\bnote{can be tightened to $\omega(n^c \log n)$.}
+\begin{proof}
+Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
+$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.  
 \begin{align*}
-\expe [1-X_i] &=\Pr[w \text{ and } w' \text{ agree on positions } {j_{i,1}},..., j_{i,\eta}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
-&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\left(\frac{1}{2}\right)^2\right)^\mu\\
-& = \left(\frac{1}{2}\right)^{-\log\left(1-\frac{t'}{2\ell}\right)} = 1-\frac{t'}{2\ell}\,.
+\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
+&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
 \end{align*}
-
-Hence, $\expe[X_i]\le t'/(2\ell) = O(1)$, and $\expe[X]\le t'/2$.
-By the Chernoff bound, we have \lnote{this can be tightened}
+We then have the probability that all $v_i\neq v_i'$ as:
 \begin{align*}
-\Pr\left[\sum_{i=1}^\ell X_i\geq t'\right]\leq 2e^{-2(t'-\expe[X])^2\ell} \le
-2e^{-2(t'/2)^2\ell} = O(e^{- \ell})\,.
+\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
+&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
+&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
 \end{align*}
+This completes the proof of \lemref{lem:sampling errors}.
 \end{proof}

### 2014-05-20 constantRate/ConstCompFuzzExt.tex
incorporating improvements for resubmission

@@
 Their security is computational.
-They correct Hamming errors over a large alphabet.
 In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
 
-Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+Our first construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+
 Our second construction requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
+It corrects a sub constant fraction of errors and supports super-constant size alphabets.
+In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.
+This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).
+
 The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+
+\bigskip
 
@@
 \]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
 
 \paragraph{Our Contributions}
-We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
-As explained above, such constructions cannot work without some restriction on the distribution.
+We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.
+
 Our first construction is secure when symbols in $w$
@@
 a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
+This construction can correct a constant fraction~($\Theta(\ell)$) of errors.
+However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
 
 We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
-However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $\ell/\omega(\log\ell)$ errors.
+However, this improvement comes at a price to error-tolerance: it tolerates a sub-constant fraction~($o(\ell)$) of errors.
+This second construction comes with an additional feature: reusability.
+Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values~(and maybe some subset of secret keys) where $w_i$ and $w_j$ are close.
+Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.
+We show that for computational adversaries it is possible to significantly expand the allowed correlation between $w_i$ and $w_j$.
+The only condition we need for security is that each marginal $W_i$ is an admissible distribution.
+We do not considering the joint distribution $W_1,..., W_q$.
 
@@
 Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.
-We take the second approach.
+Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
 
 Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
-We show two constructions of \emph{computational fuzzy conductors}.
-These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
+Our first construction is a \emph{computational fuzzy conductors}.
+This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
 
@@
 
-Both of our constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+Both of our constructions use techniques from Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
 Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$.
@@
 Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
-We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then applies the first construction.
+We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then obfuscates each string of blocks.
 $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block.
 This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance.
+We limit the degradation of error-tolerance by using digital lockers in place of point obfuscation~(sufficiently composable point obfuscation implies digital lockers).
 This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.
@@
 \paragraph{Connection to General Obfuscation}
+\bnote{needs to be rewritten}
 We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
@@
 \paragraph{Open Problems}
-Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Codes over large alphabets are often used to correct burst errors~\cite{gilbert1960capacity}.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
+Our first construction achieves a constant fraction error tolerance but at the cost of a large alphabet size.
+Our second construction reduces the alphabet size significantly but only achieves a sub-constant error tolerance.
+It remains an open question to support a constant fraction of errors on a small alphabet.
+More generally, the problem of constructing a secure fuzzy extractor whenever a negligible fraction lies in any ``ball'' remains an open problem.
+%Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Codes over large alphabets are often used to correct burst errors~\cite{gilbert1960capacity}.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
 However, distributions with $\Huse \le 0$ are supported only for large alphabets.
 For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
-Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.
+%Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.  \bnote{Should this just be removed?}
 
@@
 \subsection{Obfuscation}
-Our construction uses obfuscation for a family of point functions $\mathtt{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
+Our constructions will use obfuscation for two types of circuits: point functions and digital lockers. The family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
 \[
 I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
+\]
+and the class of digital lockers is $\mathtt{I}_n = \{I_{w, r}\}_{w \in \zo^n, r\in\zo^\kappa}$ defined as follows:
+\[
+I_{w, r}(x):\begin{cases} r & x=w\\\perp & \text{otherwise}\end{cases}.
 \]
@@
 In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
-Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
 They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
@@
 \end{definition}
-For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
+For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
+When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
 \section{Computational Fuzzy Extractors}
@@
 
-Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.
-We follow the second approach.
-In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
-To overcome these bounds, we use a computational version of a fuzzy conductor.
+Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: using a fuzzy conductor and a privacy amplification component or analyzing the information-reconciliation and privacy amplifications components together  .
+We use each approach~(in \secref{sec:construction} and \secref{sec:sampling} respectively).
+%The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.
+%In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
+We use a computational version of a fuzzy conductor.
 We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
@@
 Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
-Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions over $\mathtt{I}_{\mathcal{Z}^\eta}$.
-Define $\gen, \rep$ as:
+Let $\eta$ be a parameter, and $\mathcal{O}$ be an obfuscator for the family of digital lockers with $\kappa$-bit outputs.  Define $\gen, \rep$ as:
 
@@
 
-The main change in \consref{cons:sampling} is that the obfuscated values are concatenated symbols of $W$.
+\noindent
+There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
+\begin{itemize}
+\item Multiple blocks are concatenated together.
+This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.
 This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
+\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.
+This requires the use of digital lockers in place of point obfuscations.
+Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.
+\consref{cons:first construction} only hid part of the key in each obfuscation.
+This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
+\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.
+This construction works for an arbitrary size alphabet.
+We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
+\end{itemize}
+The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.\bnote{reusability}
 
 This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
-Goldreich provides an introduction to samplers in~\cite{goldreich1997sample}.
-
+Goldreich provides an introduction to samplers in~\cite{goldreich2011sample}.
+
+\lnote{in prev construction's theorem statement, $\mathcal{Z}$ grows as a function of $n$, and here it doesn't have to, but may.
+Right now the differences between the two theorems are too subtle to notice.
+Make theorem statements similar and highlight the differences.}
 \begin{theorem}
 \label{thm:sampling}
+Let $\mathcal{Z}$ be an alphabet.
 Let $n$ be a security parameter.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
-$\ell = \omega(\log n)$.
-Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
-Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma =\Omega(n)$.
+Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$, and let $c> 1$ be a constant and $\ell$ be such that $\ell = n^c$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
+Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
 \begin{align*}
-t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
-\tilde{m} &=H_0(C)\\
-\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
+t&\leq -\frac{(c-1)}{2} \frac{(\gamma-\eta)\log n}{\eta} = o(\gamma)\\
+\delta &= e^{-n}
 \end{align*}
-\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
 \end{theorem}
@@
 
-\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Not for submission.}
 \begin{lemma}
@@
 Thus, unless the choice of $\lambda$ is very unlucky,
-\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. That is, 
-\begin{corollary}
-\label{cor:samp unguess}
+the inputs $V_1,..., V_\ell$ to \consref{cons:sampling} form a block unguessable distribution.
+This is enough to show the probability that adversary sees a output other than $\perp$ from one of the obfuscations is negligible and that the adversary only has information about the key in this case.
+\begin{lemma}[Proof in \apref{sec:sampling unguess}]
+\label{lem:samp unguess}
 Let all the variables be as in \thref{thm:sampling}.
-For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq H_0(C)$.
+For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.% \geq H_0(C)$.
 %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
-\end{corollary}
+\end{lemma}
 %\begin{proof}
@@
 \label{sec:correct sampling}
-The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.
-Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$.
-We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.
-The proof is in \apref{sec:sampling errors}.
-The correctness argument in \thref{thm:sampling} is obtained by subtracting the probability of a single $1\rightarrow 0$ bit flip~($\ell/|\mathcal{Z}|$) and the error of the code~($\delta_{code}$).
-
-\begin{lemma}
+\label{sec:correct sampling}
+We are encoding the entire key in each obfuscation.
+For correctness, at least one of the repeated readings must be correct with overwhelming probability.
+Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.
+For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.
+
+\begin{lemma}[Proof in \apref{sec:sampling errors}]
 \label{lem:sampling errors}
 Let all the variables be as in \thref{thm:sampling}.
- Then $\Pr[v'\in\neigh_{t'}(v)]\geq 1-O(2^{-\ell})$, where the probability is over the coins of $\gen$.
-%That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
+ Then $\Pr[\forall i, v_i\neq v_i'] <1 - \ngl(n)$, where the probability is over the coins of $\gen$.  
 \end{lemma}
-
-%\begin{corollary}
-%Let all the variables be as in \thref{thm:sampling}.
-%When
-%\[
-%\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
-%\]
-%and $(c, p)\leftarrow \gen(w)$, then
-%\[
-%\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
-%\]
-%That is, \consref{cons:sampling} is correct with overwhelming probability.
-%\end{corollary}
 
@@
 The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
-We are able to correct $O(\gamma/\eta)$ errors.
+We are able to correct $o(\gamma)$ errors.
 This yields:
 \[
-\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
-\]
-That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).
-We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
-%However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
+\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
+\]
+That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.
+We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.
+
+\subsection{Reusability}
+\bnote{write this}
 \bibliographystyle{alpha}
@@
 However, we do not achieve security when $\Hfuzz(W)= \omega(\log n)$ for either definition, this is an open problem.
-
-\section{Fuzzy Conductors}
-\lnote{I need to check this}
-\label{sec:conductors}
-Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
+%
+%\section{Fuzzy Conductors}
+%\lnote{I need to check this}
+%\label{sec:conductors}
+%Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
 Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
@@
 $C$ defines an error correcting code with the required parameters.
-\end{proof}
+%\end{proof}
+
+\section{Reusable Fuzzy Extractors}
+\label{sec:reusable}
+
+Fuzzy extractors should authenticate users to multiple different services/devices.
+That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
+This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
+There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
+Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
+Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
+For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.
+
+\paragraph{Previous Results}
+
+There are two primary questions about the reusability of a fuzzy extractor.
+The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
+Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.
+Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
+They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
+In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.
+However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
+
+However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
+There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
+The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.fuzzy extractor will only be used a polynomial number of times.
+
+Instead of restricting the type of correlations, we limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
+We present a simplified non-adaptive definition and note that our results apply equally well to the adaptive definition.
+
+\begin{definition}[Insider Reusable Fuzzy Extractors]
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.
+We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
+\begin{align*}
+\delta^{\mathcal{D}_{s_{sec}}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
+&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
+\end{align*}
+\end{definition}
+
+\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
+%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
+Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
+Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
+In order to provide any meaningful security guarantee, the source distribution must be restricted.
+See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
 
@@
 
+\section{Proof of \lemref{lem:samp unguess}}
+\label{sec:sampling unguess}
+The proof of \lemref{lem:samp unguess} is similar to the proof of \lemref{lem:security of cons}.
+The main difference is the oracle provided to the unbounded simulator $S$.
+Instead repeating the entire proof, we show the following lemma~(analogous to \lemref{lem:codewords in I close}).
+The ``computational'' part of the proof follows similarly by the definition of VGB obfuscation.
+\begin{lemma}
+Let $S$ be an unbounded simulator.
+Let $V$ be a $(q, \alpha = \omega(\log n), 0)$-block unguessable distribution and let $I_{(V, R)}(i, x_i')=\begin{cases} R & v_i = x_i \\ \perp & \text{otherwise}\end{cases}$ be an oracle.
+Let $r^*$ be the true output value in the oracle, then for any $u\in\zo^\kappa$,
+\[
+\Delta(S^{I_{V, R}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{V, R}(\cdot, \cdot)}(u, 1^{\ell \log |Z|}))\le \ell 2^{-\alpha}.
+\]
+\end{lemma}
+\begin{proof}
+Recall that for all $i, \Hav(V_i | View(S))\geq \alpha$.
+The only information about the value of $R$ is contained in query responses.
+When all responses are $\perp$ the view of $S$ is identical when presented with $r^*$ or $u$.
+We now show that for any value of $r^*$ all queries return $\perp$ with probability $1-2^{-\alpha}$.
+Suppose not, that is suppose, the probability of at least one nonzero response for some index $i$ is at least $2^{-a}$.
+When there is a response other than $\perp$ this means that $V_i$ has no remaining entropy.
+If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $F$.
+By union bound over the indices $i$, the total probability of a non-$\perp$ response is at most $\ell 2^{-\alpha}$.
+This concludes the proof.
+\end{proof}
 \section{Proof of \lemref{lem:sampling errors}}
 \label{sec:sampling errors}
-
-\begin{proof}
-Define $\mu = -\frac{1}{2}\log(1-t'/(2\ell)) = \Theta(1)$ and note that $t \leq \mu(\gamma - \eta)/\eta$. Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.
-Let
-the Bernoulli random variable $X_i=1$ if and only if $v_i \neq v_i'$, and $X=\sum_{i=1}^{\ell} X_i$. We need to show that $\Pr[X>t']=O(2^{-\ell})$.
-
+\bnote{can be tightened to $\omega(n^c \log n)$.}
+\begin{proof}
+Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
+$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.  
 \begin{align*}
-\expe [1-X_i] &=\Pr[w \text{ and } w' \text{ agree on positions } {j_{i,1}},..., j_{i,\eta}]\\
-&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
-&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\left(\frac{1}{2}\right)^2\right)^\mu\\
-& = \left(\frac{1}{2}\right)^{-\log\left(1-\frac{t'}{2\ell}\right)} = 1-\frac{t'}{2\ell}\,.
+\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
+&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
 \end{align*}
-
-Hence, $\expe[X_i]\le t'/(2\ell) = O(1)$, and $\expe[X]\le t'/2$.
-By the Chernoff bound, we have \lnote{this can be tightened}
+We then have the probability that all $v_i\neq v_i'$ as:
 \begin{align*}
-\Pr\left[\sum_{i=1}^\ell X_i\geq t'\right]\leq 2e^{-2(t'-\expe[X])^2\ell} \le
-2e^{-2(t'/2)^2\ell} = O(e^{- \ell})\,.
+\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
+&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
+&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
 \end{align*}
+This completes the proof of \lemref{lem:sampling errors}.
 \end{proof}

### 2014-05-20 trunk/constantRate/ConstCompFuzzExt.tex
incorporating improvements for resubmission

@@
 Their security is computational.
-They correct Hamming errors over a large alphabet.
 In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
 
-Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+Our first construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+
 Our second construction requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
-\bnote{update}The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+It corrects a sub constant fraction of errors and supports super-constant size alphabets.
+In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.
+This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).
+
+The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
 
@@
 \paragraph{Our Contributions}
-We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.
-\bnote{need to split out the two constructions} As explained above, such constructions cannot work without some restriction on the distribution.
+We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.
+
 Our first construction is secure when symbols in $w$
@@
 Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.
-We take the second approach.
+Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
 
 Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
-We show two constructions of \emph{computational fuzzy conductors}.
-These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
-\bnote{first construction is conductor, second is fuzzy extractor}
+Our first construction is a \emph{computational fuzzy conductors}.
+This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
 
@@
 \paragraph{Connection to General Obfuscation}
-We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.\bnote{update with new results} However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
+\bnote{needs to be rewritten}
+We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
+However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
 Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
@@
 \paragraph{Open Problems}
-Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Codes over large alphabets are often used to correct burst errors~\cite{gilbert1960capacity}.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
+Our first construction achieves a constant fraction error tolerance but at the cost of a large alphabet size.
+Our second construction reduces the alphabet size significantly but only achieves a sub-constant error tolerance.
+It remains an open question to support a constant fraction of errors on a small alphabet.
+More generally, the problem of constructing a secure fuzzy extractor whenever a negligible fraction lies in any ``ball'' remains an open problem.
+%Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Codes over large alphabets are often used to correct burst errors~\cite{gilbert1960capacity}.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.
 However, distributions with $\Huse \le 0$ are supported only for large alphabets.
 For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
-Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.  \bnote{Should this just be removed?}
+%Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.  \bnote{Should this just be removed?}
 
@@
 \subsection{Obfuscation}
-Our construction uses obfuscation for a family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
+Our constructions will use obfuscation for two types of circuits: point functions and digital lockers. The family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
 \[
@@
 \]
-\bnote{need to introduce digital lockers}
+and the class of digital lockers is $\mathtt{I}_n = \{I_{w, r}\}_{w \in \zo^n, r\in\zo^\kappa}$ defined as follows:
+\[
+I_{w, r}(x):\begin{cases} r & x=w\\\perp & \text{otherwise}\end{cases}.
+\]
 The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
@@
 
-Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.
-We follow the second approach.
-The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.
+Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: using a fuzzy conductor and a privacy amplification component or analyzing the information-reconciliation and privacy amplifications components together  .
+We use each approach~(in \secref{sec:construction} and \secref{sec:sampling} respectively).
+%The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.
 %In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
-To overcome these bounds, we use a computational version of a fuzzy conductor.
+We use a computational version of a fuzzy conductor.
 We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
@@
 \end{itemize}
-The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.\bnote{reusability}
+The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
+Indeed, this is the property that allows this fuzzy extractor to be reusable~(we define reusability in \defref{def:reusable fuzz}).
 
@@
 For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.
+For reusability, we show that \bnote{what?}
 
@@
 Thus, unless the choice of $\lambda$ is very unlucky,
-\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. That is, \bnote{need to fix this corollary.}
-\begin{corollary}
-\label{cor:samp unguess}
+the inputs $V_1,..., V_\ell$ to \consref{cons:sampling} form a block unguessable distribution.
+This is enough to show the probability that adversary sees a output other than $\perp$ from one of the obfuscations is negligible and that the adversary only has information about the key in this case.
+\begin{lemma}[Proof in \apref{sec:sampling unguess}]
+\label{lem:samp unguess}
 Let all the variables be as in \thref{thm:sampling}.
@@
 %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
-\end{corollary}
+\end{lemma}
 %\begin{proof}
@@
 \subsection{Correctness of \consref{cons:sampling}}
-\label{sec:correct sampling}
 \label{sec:correct sampling}
@@
 Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.
-For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$~(Proof in \apref{sec:sampling errors}) \bnote{should talk about the obfuscation having some error}
-
-\begin{lemma}
+For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.
+
+\begin{lemma}[Proof in \apref{sec:sampling errors}]
 \label{lem:sampling errors}
@@
 \end{lemma}
+
+\subsection{Reusability of \consref{cons:sampling}}
+\bnote{write this}
 
@@
 \]
-That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super constant.
+That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.
 We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.
 
-\subsection{Reusability}
-\bnote{write this}
 \bibliographystyle{alpha}
@@
 
+\section{Reusable Fuzzy Extractors}
+\label{sec:reusable}
+
+Fuzzy extractors should authenticate users to multiple different services/devices.
+That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
+This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
+There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
+Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
+Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
+For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.
+
+\paragraph{Previous Results}
+
+There are two primary questions about the reusability of a fuzzy extractor.
+The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
+Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.
+Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
+They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
+In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.
+However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
+
+However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
+There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
+The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.fuzzy extractor will only be used a polynomial number of times.
+
+Instead of restricting the type of correlations, we limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
+We present a simplified non-adaptive definition and note that our results apply equally well to the adaptive definition.
+
+\begin{definition}[Insider Reusable Fuzzy Extractors]
+\label{def:reusable fuzz}
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.
+We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
+\begin{align*}
+\delta^{\mathcal{D}_{s_{sec}}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
+&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
+\end{align*}
+\end{definition}
+
+\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
+%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
+Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
+Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
+In order to provide any meaningful security guarantee, the source distribution must be restricted.
+See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
+
+\begin{theorem}
+
+\end{theorem}
+
 \section{Characterizing unguessable block distributions}
@@
 
+\section{Proof of \lemref{lem:samp unguess}}
+\label{sec:sampling unguess}
+The proof of \lemref{lem:samp unguess} is similar to the proof of \lemref{lem:security of cons}.
+The main difference is the oracle provided to the unbounded simulator $S$.
+Instead repeating the entire proof, we show the following lemma~(analogous to \lemref{lem:codewords in I close}).
+The ``computational'' part of the proof follows similarly by the definition of VGB obfuscation.
+\begin{lemma}
+Let $S$ be an unbounded simulator.
+Let $V$ be a $(q, \alpha = \omega(\log n), 0)$-block unguessable distribution and let $I_{(V, R)}(i, x_i')=\begin{cases} R & v_i = x_i \\ \perp & \text{otherwise}\end{cases}$ be an oracle.
+Let $r^*$ be the true output value in the oracle, then for any $u\in\zo^\kappa$,
+\[
+\Delta(S^{I_{V, R}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{V, R}(\cdot, \cdot)}(u, 1^{\ell \log |Z|}))\le \ell 2^{-\alpha}.
+\]
+\end{lemma}
+\begin{proof}
+Recall that for all $i, \Hav(V_i | View(S))\geq \alpha$.
+The only information about the value of $R$ is contained in query responses.
+When all responses are $\perp$ the view of $S$ is identical when presented with $r^*$ or $u$.
+We now show that for any value of $r^*$ all queries return $\perp$ with probability $1-2^{-\alpha}$.
+Suppose not, that is suppose, the probability of at least one nonzero response for some index $i$ is at least $2^{-a}$.
+When there is a response other than $\perp$ this means that $V_i$ has no remaining entropy.
+If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $F$.
+By union bound over the indices $i$, the total probability of a non-$\perp$ response is at most $\ell 2^{-\alpha}$.
+This concludes the proof.
+\end{proof}
 \section{Proof of \lemref{lem:sampling errors}}

### 2014-05-21 constantRate/ConstCompFuzzExt.tex
moved reusability to main body

@@
 Our second construction requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
-It corrects a sub constant fraction of errors and supports super-constant size alphabets.
+It corrects a sub-constant fraction of errors and supports super-constant size alphabets.
 In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.
@@
 a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
-This construction can correct a constant fraction~($\Theta(\ell)$) of errors.
+This construction can correct a constant fraction of errors~($\Theta(\ell)$).
 However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
 
-We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
-However, this improvement comes at a price to error-tolerance: it tolerates a sub-constant fraction~($o(\ell)$) of errors.
-This second construction comes with an additional feature: reusability.
-Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values~(and maybe some subset of secret keys) where $w_i$ and $w_j$ are close.
-Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.
-We show that for computational adversaries it is possible to significantly expand the allowed correlation between $w_i$ and $w_j$.
-The only condition we need for security is that each marginal $W_i$ is an admissible distribution.
-We do not considering the joint distribution $W_1,..., W_q$.
+We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
+Our second construction supports an arbitrary alphabet size~(though it only achieves $\Huse\le 0$ when the alphabet size is super-constant).
+However, these improvements come at a price to error-tolerance: it tolerates a sub-constant fraction of errors~($o(\ell)$).
+
+The second construction comes with an additional feature: reusability.
+Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.
+The enrolled values $w_i$ and $w_j$ are not assumed to be equal, and so information leakage may add up.
+Indeed, Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.
+Our second construction allows for arbitrary correlation between $w_i$ and $w_j$ against computational adversaries\footnote{Our restriction to computational adversaries implies that the adversary only sees a polynomially bounded number of reuses.
+It remains an open problem to construct a polynomially reusable fuzzy extractor against unbounded adversaries.} as long as each marginal $W_i$ is an admissible distribution.
+%We do not considering the joint distribution $W_1,..., W_q$.
 
@@
 \end{lemma}
+
+\subsection{Reusable Fuzzy Extractors}
+\label{sec:reusable}
+
+Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.
+That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
+This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
+There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
+Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
+Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
+For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.
+
+\paragraph{Previous Results}
+
+There are two primary questions about the reusability of a fuzzy extractor.
+The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
+Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.
+Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
+They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
+In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.
+However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
+
+However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
+There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
+The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.
+
+We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
+We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.
+
+\begin{definition}[Insider Reusable Fuzzy Extractors]
+\label{def:reusable fuzz}
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.
+Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.
+We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
+\begin{align*}
+\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
+&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
+\end{align*}
+\end{definition}
+
+%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
+%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
+Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
+Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
+In order to provide any meaningful security guarantee, the source distribution must be restricted.
+See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
 
@@
 \label{sec:correct sampling}
-\label{sec:correct sampling}
 We are encoding the entire key in each obfuscation.
@@
 
-\subsection{Reusability}
-\bnote{write this}
 \bibliographystyle{alpha}
@@
 
-\section{Reusable Fuzzy Extractors}
-\label{sec:reusable}
-
-Fuzzy extractors should authenticate users to multiple different services/devices.
-That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
-This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
-There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
-Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
-Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
-For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.
-
-\paragraph{Previous Results}
-
-There are two primary questions about the reusability of a fuzzy extractor.
-The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
-Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.
-Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
-They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
-In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.
-However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
-
-However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
-There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
-The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.fuzzy extractor will only be used a polynomial number of times.
-
-Instead of restricting the type of correlations, we limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
-We present a simplified non-adaptive definition and note that our results apply equally well to the adaptive definition.
-
-\begin{definition}[Insider Reusable Fuzzy Extractors]
-Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.
-We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
-\begin{align*}
-\delta^{\mathcal{D}_{s_{sec}}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
-&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
-\end{align*}
-\end{definition}
-
-\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
-%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
-Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
-Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
-In order to provide any meaningful security guarantee, the source distribution must be restricted.
-See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
-
 \section{Characterizing unguessable block distributions}

### 2014-05-30 info-bounds/FuzzyExtPossibility.tex
working on well-spread distribution bounds

--- 2014-05-20 trunk/info-bounds/FuzzyExtPossibility.tex
@@
 \begin{lemma}
-Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works only for $W$.
+Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works for $W$.
 In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.
@@
 Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
-Ideally, a secure sketch should be able to recover for any well-spread distribution.
-However, as we show below this is not possible.
+However, as we show below the above construction does not extend to the setting of all well-spread distributions.
+In particular, any secure sketch must write down a large number of bits~(matching our known constructions of secure sketches).
+However, it is not known if it is necessary to decrease the entropy of the distribution $W$.
 
 \begin{lemma}
-Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.  Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.  Then $\tilde{m}<....$.
+Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.
+Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.
+Then the length of $\sketch$ is at least $\log |B_{t}|$.
 \end{lemma}
+\begin{proof}
+Let $\mathcal{M}$ be a metric space.
+Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions on $\mathcal{M}$.  
+Consider the following experiment:
+\[
+W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{sec}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
+\]
+Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
+Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.
+Now consider the following experiment
+\[
+v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{sec}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
+\]
+Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.
+Then $X\overset{d}= Y$.
+That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.
+Thus, $\Pr[v^* = v] = 1$.
+For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M} - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
+For a secure sketch to lose $\log |B_{t_{sec}}(\cdot)|$ bits of entropy it must write down at least $\log |B_{t_{sec}}(\cdot)|$ bits~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
+Thus, $(\sketch, \rec)$ writes down at least $\log |B_{t_{sec}}|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{sec}}|$ bits on $X$.
+This completes the proof.\bnote{need to deal with the case where the number of bits written by $\sketch$ is variable.}
+\end{proof}
 \bibliographystyle{alpha}

### 2014-06-04 info-bounds/FuzzyExtPossibility.tex
putting in universal hash construction

@@
 \section{Well-spread distributions}
+\subsection{Depends on Distribution}
 We will start with an intuitively simple type of distribution where no results are known.
@@
 \begin{lemma}
+\label{lem:nosketchwellspread}
 Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works for $W$.
@@
 
+\subsection{Works for all well-spread distributions}
 Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
@@
 \end{proof}
+
+\section{Non-well spread distributions}
+\subsection{Dependence on Distributions}
+\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
+secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.
+In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.
+We start by considering distributions that have a fixed number of neighbors for each point.
+
+\begin{definition}
+We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.
+We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
+\end{definition}
+
+\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
+
+We now present an information-theoretic construction for fixed-neighbor distributions.  We first introduce the notion of a pairwise-independent hash:
+
+\begin{definition}
+Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
+\[
+ \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
+\]
+In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
+\end{definition}
+
+We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.
+
+\begin{construction}
+\label{cons:pairwise hash}
+Let $W$ be a $(c, t)$-fixed neighbor distribution over $\mathcal{M}$.
+Let $F :\mathcal{M}\times \mathcal{M}\rightarrow R$ be a pairwise independent hash function.
+We describe $\sketch, \rec$ as follows:
+\begin{itemize}
+\item $\sketch(w)$:
+\subitem Sample $K\leftarrow \mathcal{K}$.
+\subitem Set $p = F(K, w), K$.
+\item $\rec(w', y, K)$:
+\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
+\subitem Output $\perp$.
+\end{itemize}
+\end{construction}
+\begin{lemma}
+\consref{cons:pairwise hash} is a $(\mathcal{M}, m, m - \log |R|, t)$-secure sketch with error $\delta = \frac{c-1}{|R|}$. 
+\end{lemma}
+\begin{proof}
+We first argue security.
+Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
+Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.
+
+We now argue correctness.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is $c$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
+Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
+\begin{align*}
+\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] \le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)]  = \frac{c-1}{|R|}
+\end{align*}
+Where the inequality proceeds by union bound and the equality proceeds by the universality of $F$.  This completes the proof.
+\end{proof}
+\begin{corollary}
+Let $n$ be a security parameter.  
+If $|R| \ge c * n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |c| + \omega(\log n)$ suffices.
+\end{corollary}
+
 \bibliographystyle{alpha}

### 2014-06-04 trunk/info-bounds/FuzzyExtPossibility.tex
putting in universal hash construction

@@
 \[
-\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
+\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
 \]
@@
 \begin{lemma}
-Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works only for $W$.
+\label{lem:nosketchwellspread}
+Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works for $W$.
 In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.
@@
 
+\subsection{Works for all well-spread distributions}
 Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
-Ideally, a secure sketch should be able to recover for any well-spread distribution.
-However, as we show below this is not possible.
+However, as we show below the above construction does not extend to the setting of all well-spread distributions.
+In particular, any secure sketch must write down a large number of bits~(matching our known constructions of secure sketches).
+However, it is not known if it is necessary to decrease the entropy of the distribution $W$.
 
 \begin{lemma}
-Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.  Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.  Then $\tilde{m}<....$.
+Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.
+Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.
+Then the length of $\sketch$ is at least $\log |B_{t}|$.
 \end{lemma}
+\begin{proof}
+Let $\mathcal{M}$ be a metric space.
+Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions on $\mathcal{M}$.  
+Consider the following experiment:
+\[
+W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{sec}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
+\]
+Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
+Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.
+Now consider the following experiment
+\[
+v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{sec}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
+\]
+Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.
+Then $X\overset{d}= Y$.
+That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.
+Thus, $\Pr[v^* = v] = 1$.
+For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M} - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
+For a secure sketch to lose $\log |B_{t_{sec}}(\cdot)|$ bits of entropy it must write down at least $\log |B_{t_{sec}}(\cdot)|$ bits~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
+Thus, $(\sketch, \rec)$ writes down at least $\log |B_{t_{sec}}|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{sec}}|$ bits on $X$.
+This completes the proof.\bnote{need to deal with the case where the number of bits written by $\sketch$ is variable.}
+\end{proof}
+
+\section{Non-well spread distributions}
+\subsection{Dependence on Distributions}
+\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
+secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.
+In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.
+We start by considering distributions that have a fixed number of neighbors for each point.
+
+\begin{definition}
+We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.
+We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
+\end{definition}
+
+\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
+
+We now present an information-theoretic construction for fixed-neighbor distributions.  We first introduce the notion of a pairwise-independent hash:
+
+\begin{definition}
+Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
+\[
+ \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
+\]
+In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
+\end{definition}
+
+We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.
+
+\begin{construction}
+\label{cons:pairwise hash}
+Let $W$ be a $(c, t)$-fixed neighbor distribution over $\mathcal{M}$.
+Let $F :\mathcal{M}\times \mathcal{M}\rightarrow R$ be a pairwise independent hash function.
+We describe $\sketch, \rec$ as follows:
+\begin{itemize}
+\item $\sketch(w)$:
+\subitem Sample $K\leftarrow \mathcal{K}$.
+\subitem Set $p = F(K, w), K$.
+\item $\rec(w', y, K)$:
+\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
+\subitem Output $\perp$.
+\end{itemize}
+\end{construction}
+\begin{lemma}
+\consref{cons:pairwise hash} is a $(\mathcal{M}, m, m - \log |R|, t)$-secure sketch with error $\delta = \frac{c-1}{|R|}$. 
+\end{lemma}
+\begin{proof}
+We first argue security.
+Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
+Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.
+
+We now argue correctness.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is $c$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
+Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
+\begin{align*}
+\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] \le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)]  = \frac{c-1}{|R|}
+\end{align*}
+Where the inequality proceeds by union bound and the equality proceeds by the universality of $F$.  This completes the proof.
+\end{proof}
+\begin{corollary}
+Let $n$ be a security parameter.  
+If $|R| \ge c * n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |c| + \omega(\log n)$ suffices.
+\end{corollary}
+
+Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).
+Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.
+Thus, the remaining entropy for this construction is
+\[
+\Hav(W |\sketch(W)) = \Hoo(W) - \log c - \omega(\log n)
+\]
+For a flat distribution with a fixed number of neighbors, 
+\begin{align*}
+\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
+&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
+&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
+\end{align*}
+Thus, the construction is optimal up to a super-logarithmic factor~(for flat sources with a fixed number of neighbors).
 \bibliographystyle{alpha}

### 2014-06-04 trunk/info-bounds/FuzzyExtPossibility.tex
adding notes about necessary number of sketches for flat distributions

@@
 \]
-In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
+%In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
 \end{definition}
@@
 \end{align*}
-Thus, the construction is optimal up to a super-logarithmic factor~(for flat sources with a fixed number of neighbors).
+Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.
+
+\subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
+We begin by trying to remove the restriction that every point in the metric space has a fixed number of neighbors in a distribution.
+We start with sketches that write down a fixed number of bits~(independent of their input $w$).
+We will show a lower bound on the number of bits that a $\sketch$ algorithm must write down.
+We assume that all coins of $\sketch$ are provided to $\rec$ and that $\rec$ is deterministic~(any coins needed for $\rec$ can be flipped by $\sketch$ in this model).
+
+\begin{lemma}
+Let $W$ be a flat distribution and let $(\sketch, \rec)$ be a secure sketch for $W$.
+Let $W$ be a $(c, t)$-bounded neighbor distribution.
+Let $S_{coin}$ be the number of sketches that can be produced by any fixing of $coin$.
+Then the error $\delta$ of $(\sketch, \rec)$ is at least $\frac{\expe_{coins}L(coins)}{c}$.
+\end{lemma}
+\begin{proof}
+We consider a fixed $w'$ that has $c$ neighbors in the distribution.
+We assume $\rec$ has access to all coins of $\sketch$.
+Furthermore, we assume that $\rec$ is deterministic and that any coins necessary are provided by $\sketch$).
+
+Denote by $S_{coin, R}$ the set of possible sketches for a given set of coins on all values in $R$.
+Furthermore, denote by $S_{coin}$ the set of possible sketches for all values $w$~(for a given value of coin) and note that $S_{coin, R} \subset S_{coin}$.
+Then $\rec(\cdot, w', coin)$ must fail to recover $|R|-|S_{coin, R}|$ fraction of $w\in R$~(recalling that $\rec$ is deterministic for this fixing of $coin$).
+This means that the total number of pairs $(w, coin)$ for which $\rec$ fails to recover is $2^{|coins|}R - \sum_{coins} |S_{coin, R}|$.
+
+This means there must exist some $w$ such that the number of $coin$ values for which $\rec$ fails to recover is 
+\[
+2^{|coin|} - \frac{\sum_{coin} |S_{coin, R}|}{R}.
+\]
+ This means that for this $w$, 
+\[
+\Pr_{coin}[s \leftarrow \sketch(w, coin) \wedge w = \rec(s, w', coin)] < 1- \frac{\expe |S_{coin, R}|}{|R|} = 1-\frac{\expe |S_{coin, R}|}{c} \le 1-\frac{\expe |S_{coin}| }{c}.
+\]
+
+%Consider the function $\rec(w', ss, r)$ where $ss$ is the sketch produced by $\sketch(w)$ and $r$ are the coins used by $\sketch$.  
+\end{proof}
+
+For deterministic sketches:
+\[
+\Hav(W|S ) = -\log \left(\sum_{s\in S} \Pr[S = s] \frac{2^{-\Hoo(W)}}{\Pr[S=s]}\right) = -\log \left(2^{-\Hoo(W)} |S| \right)  = \Hoo(W) - H_0(S).
+\]
 \bibliographystyle{alpha}

### 2014-06-10 constantRate/ConstCompFuzzExt.tex
Adding info-theoretic construction and reusability

@@
 \newcommand{\cext}{\ensuremath{\mathtt{cext}}}
+\newcommand{\cond}{\ensuremath{\mathtt{cond}}}
 \newcommand{\rext}{\ensuremath{\mathtt{rext}}}
@@
 \begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
-\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for point functions with auxiliary-input if the following conditions are met:
+\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
 \begin{enumerate}
@@
 \begin{itemize}
-\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
+\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
 \end{itemize}
@@
 Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.
-That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
+That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
 This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
@@
 The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
-Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.
+Boyen~\cite{Boyen2004} considers fuzzy extractors that are reusable an unbounded number of times.
 Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
-They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
-In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.
+They show in the setting of unbounded reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
+In particular, they show how any information-theoretic fuzzy extractor secure with unbounded reuse can be transformed into their construction.
 However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
@@
 We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
-We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.
+We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
 
@@
 For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.
-For reusability, we show that \bnote{what?}
+Reusability comes essentially for free given a sufficiently composable obfuscation for digital lockers.
+For the sake of clarity we state reusability as a separate theorem~(\thref{thm:reusability}).
 
 \subsection{Security of \consref{cons:sampling}}
+\label{ssec:sec cons sampling}
 In order to show security \consref{cons:sampling}, we
@@
 \subsection{Reusability of \consref{cons:sampling}}
-\bnote{write this}
+The reusability of \consref{cons:sampling} essentially follows from the security of the VGB obfuscator with auxiliary input.
+We consider a bounded $q = \poly(n)$ number of reuses.
+For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator must still be able to simulate.
+Thus, given sufficiently strong reusability we achieve the following stronger result:
+
+\begin{theorem}
+\label{thm:reusability}
+Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
+Then \consref{cons:sampling} is $q$-reusable.
+\end{theorem}
+\begin{proof}
+The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
+\end{proof}
 
@@
 We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.
+However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.
 
@@
 
+\section{An information-theoretic construction with $\Huse\le 0$}
+In this section we show an information-theoretic analogue to \consref{cons:first construction}.
+%This construction can essentially be seen as replacing the computational point obfuscation with information-theoretic randomness extractors.
+Using this weaker object requires us to make a stronger assumption on our starting distribution.
+Furthermore, the important features of \consref{cons:sampling}, $\Huse \le 0$ for a small alphabet and reusability, crucially rely on computational assumptions.
+Achieving these benefits information-theoretically is an open question.
+We will construct an information-theoretic fuzzy conductor which can be converted to a fuzzy extractor using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
+
+The main idea of this construction is to first condense entropy from each block of the source and then apply a standard secure sketch to the extracted information.
+Intuitively, we are then able from a large alphabet while paying entropy loss on the smaller alphabet.
+%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
+We first review some information-theoretic definitions.
+
+\begin{definition}
+\label{def:secure sketch}
+An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+\begin{enumerate}
+\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
+\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
+The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
+\end{definition}
+
+\begin{definition}
+\label{def:conductor}
+A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
+\end{definition}
+
+Note that randomness condensers can be built significantly more efficiently than randomness extractors~(see for example~\cite{dodis2013key}).
+
+\begin{definition}
+\label{def:fuzzy conductor}
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-fuzzy conductor that is $\epsilon$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following condition:
+\begin{itemize}
+\item For any distribution $W\in \mathcal{W}$, the string $r$ has is close to a distribution with average min-entropy conditioned on $P$.
+That is there exists a distribution $Y$ with $\Hav(Y | P)\ge \tilde{m}$ such that $(R ,P)\approx_\epsilon (Y, P)$.
+\end{itemize}
+\end{definition}
+
+\begin{lemma}
+Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
+Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.
+Then the following is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-fuzzy conductor that is $\epsilon \ell$ hard with error $\delta$:
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\ell$
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item Sample $seed_i\leftarrow \zo^d$.
+\item Set $v_i = \cond(w_i, seed_i)$.
+\end{enumerate}
+\item Set $ss \leftarrow \sketch(v_1,..., v_\ell)$.
+\item Set $p = (ss, seed_1,..., seed_\ell)$.
+\item Output $(v, p)$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\ell))$
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item Set $v_i = \cond(w_i, seed_i)$.
+\end{enumerate}
+\item Output $v = \rec(v', ss)$.
+\end{enumerate}
+\vspace{0.7in}
+\end{minipage}
+\end{tabular}
+\end{center}
+\end{lemma}
+\begin{proof}
+Let $W\in \mathcal{W}$.
+It suffices to argue correctness and security.  We first argue correctness.  
+When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.
+Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
+Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.
+
+We now argue security.  Denote by $seed$ the random variable consisting of all $\ell$ seeds and $V$ the entire string of generated $V_1,..., V_\ell$.
+Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.
+We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\ell)\approx (Y, seed_1,.., seed_\ell)$.
+First note since $W$ is $(\alpha, \beta)$-partial block distribution that
+there exists a set of indices $J$ where $|J| \geq \ell - \beta$ such that the following holds:
+\[
+\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\]
+Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$, 
+\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]
+
+%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
+%Then since $W$ is a block-source, 
+%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
+\noindent 
+Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that 
+\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-}) \approx_{\epsilon} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1})\]
+and since $(seed_1,..., seed_{j_1})$ are independent of these values
+\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
+consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
+Applying a deterministic function does not increase statistical distance and thus,
+\begin{align*}
+(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\epsilon} (Z_{j_1}, seed_{j_1},..., seed_1)
+\end{align*}
+
+\noindent
+By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\ell -\beta)$ where 
+\[
+(\cond(W_\ell, seed_\ell), ..., \cond(W_1, seed_1), seed_\ell,..., seed_1) \approx_{\epsilon\ell} (Z, seed_\ell,...,  seed_1).\]
+By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
+%Note that $U_{\mathcal{Y}}^\ell$ is independent of $seed_1,..., seed_\ell$ and so $\Hav(U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p)\ge \tilde{m}$.
+That is, 
+\[
+(V, seed_1,..., seed_\ell, p) \approx_{\epsilon\ell} (U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p).\]  This completes the proof.
+\end{proof}
+
 \section{Proof of \lemref{lem:cond and cext}}

### 2014-06-10 trunk/constantRate/ConstCompFuzzExt.tex
Adding info-theoretic construction and reusability

@@
 \end{lemma}
+
+\subsection{Reusable Fuzzy Extractors}
+\label{sec:reusable}
+
+Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.
+That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
+This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
+There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
+Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
+Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
+For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.
+
+\paragraph{Previous Results}
+
+There are two primary questions about the reusability of a fuzzy extractor.
+The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
+Boyen~\cite{Boyen2004} considers fuzzy extractors that are reusable an unbounded number of times.
+Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
+They show in the setting of unbounded reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
+In particular, they show how any information-theoretic fuzzy extractor secure with unbounded reuse can be transformed into their construction.
+However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
+
+However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
+There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
+The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.
+
+We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
+We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
+
+\begin{definition}[Insider Reusable Fuzzy Extractors]
+\label{def:reusable fuzz}
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.
+Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.
+We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
+\begin{align*}
+\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
+&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
+\end{align*}
+\end{definition}
+
+%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
+%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
+Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
+Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
+In order to provide any meaningful security guarantee, the source distribution must be restricted.
+See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
 
@@
 
-\section{Reusable Fuzzy Extractors}
-\label{sec:reusable}
-
-Fuzzy extractors should authenticate users to multiple different services/devices.
-That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy sources multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
-This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
-There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
-Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
-Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
-For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.
-
-\paragraph{Previous Results}
-
-There are two primary questions about the reusability of a fuzzy extractor.
-The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
-Boyen~\cite{Boyen2004} considers fuzzy extractors that are arbitrarily reusable.
-Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
-They show in the setting of arbitrary reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
-In particular, they show how any information-theoretic fuzzy extractor secure with arbitrary reuse can be transformed into their construction.
-However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
-
-However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
-There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
-The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.fuzzy extractor will only be used a polynomial number of times.
-
-Instead of restricting the type of correlations, we limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
-We present a simplified non-adaptive definition and note that our results apply equally well to the adaptive definition.
-
-\begin{definition}[Insider Reusable Fuzzy Extractors]
-\label{def:reusable fuzz}
-Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.
-We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
-\begin{align*}
-\delta^{\mathcal{D}_{s_{sec}}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
-&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
-\end{align*}
-\end{definition}
-
-\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
-%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
-Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
-Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
-In order to provide any meaningful security guarantee, the source distribution must be restricted.
-See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
-
-\begin{theorem}
-
-\end{theorem}
-
 \section{Characterizing unguessable block distributions}
@@
 
+\section{An information-theoretic construction with $\Huse\le 0$}
+In this section we show an information-theoretic analogue to \consref{cons:first construction}.
+%This construction can essentially be seen as replacing the computational point obfuscation with information-theoretic randomness extractors.
+Using this weaker object requires us to make a stronger assumption on our starting distribution.
+Furthermore, the important features of \consref{cons:sampling}, $\Huse \le 0$ for a small alphabet and reusability, crucially rely on computational assumptions.
+Achieving these benefits information-theoretically is an open question.
+We will construct an information-theoretic fuzzy conductor which can be converted to a fuzzy extractor using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
+
+The main idea of this construction is to first condense entropy from each block of the source and then apply a standard secure sketch to the extracted information.
+Intuitively, we are then able from a large alphabet while paying entropy loss on the smaller alphabet.
+%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
+We first review some information-theoretic definitions.
+
+\begin{definition}
+\label{def:secure sketch}
+An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+\begin{enumerate}
+\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
+\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
+The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
+\end{definition}
+
+\begin{definition}
+\label{def:conductor}
+A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
+\end{definition}
+
+Note that randomness condensers can be built significantly more efficiently than randomness extractors~(see for example~\cite{dodis2013key}).
+
+\begin{definition}
+\label{def:fuzzy conductor}
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-fuzzy conductor that is $\epsilon$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following condition:
+\begin{itemize}
+\item For any distribution $W\in \mathcal{W}$, the string $r$ has is close to a distribution with average min-entropy conditioned on $P$.
+That is there exists a distribution $Y$ with $\Hav(Y | P)\ge \tilde{m}$ such that $(R ,P)\approx_\epsilon (Y, P)$.
+\end{itemize}
+\end{definition}
+
+\begin{lemma}
+Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
+Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.
+Then the following is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-fuzzy conductor that is $\epsilon \ell$ hard with error $\delta$:
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\ell$
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item Sample $seed_i\leftarrow \zo^d$.
+\item Set $v_i = \cond(w_i, seed_i)$.
+\end{enumerate}
+\item Set $ss \leftarrow \sketch(v_1,..., v_\ell)$.
+\item Set $p = (ss, seed_1,..., seed_\ell)$.
+\item Output $(v, p)$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\ell))$
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item Set $v_i = \cond(w_i, seed_i)$.
+\end{enumerate}
+\item Output $v = \rec(v', ss)$.
+\end{enumerate}
+\vspace{0.7in}
+\end{minipage}
+\end{tabular}
+\end{center}
+\end{lemma}
+\begin{proof}
+Let $W\in \mathcal{W}$.
+It suffices to argue correctness and security.  We first argue correctness.  
+When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.
+Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
+Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.
+
+We now argue security.  Denote by $seed$ the random variable consisting of all $\ell$ seeds and $V$ the entire string of generated $V_1,..., V_\ell$.
+Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.
+We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\ell)\approx (Y, seed_1,.., seed_\ell)$.
+First note since $W$ is $(\alpha, \beta)$-partial block distribution that
+there exists a set of indices $J$ where $|J| \geq \ell - \beta$ such that the following holds:
+\[
+\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\]
+Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$, 
+\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]
+
+%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
+%Then since $W$ is a block-source, 
+%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
+\noindent 
+Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that 
+\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-}) \approx_{\epsilon} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1})\]
+and since $(seed_1,..., seed_{j_1})$ are independent of these values
+\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
+consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
+Applying a deterministic function does not increase statistical distance and thus,
+\begin{align*}
+(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\epsilon} (Z_{j_1}, seed_{j_1},..., seed_1)
+\end{align*}
+
+\noindent
+By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\ell -\beta)$ where 
+\[
+(\cond(W_\ell, seed_\ell), ..., \cond(W_1, seed_1), seed_\ell,..., seed_1) \approx_{\epsilon\ell} (Z, seed_\ell,...,  seed_1).\]
+By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
+%Note that $U_{\mathcal{Y}}^\ell$ is independent of $seed_1,..., seed_\ell$ and so $\Hav(U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p)\ge \tilde{m}$.
+That is, 
+\[
+(V, seed_1,..., seed_\ell, p) \approx_{\epsilon\ell} (U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p).\]  This completes the proof.
+\end{proof}
+
+\subsection{Discussion of Information-Theoretic Construction}
+\bnote{write this}
 \section{Proof of \lemref{lem:cond and cext}}

### 2014-06-25 info-bounds/FuzzyExtPossibility.tex
Adding discussion on convex combinations

@@
 
+Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).
+Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.
+Thus, the remaining entropy for this construction is
+\[
+\Hav(W |\sketch(W)) = \Hoo(W) - \log c - \omega(\log n)
+\]
+For a flat distribution with a fixed number of neighbors, 
+\begin{align*}
+\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
+&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
+&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
+\end{align*}
+Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.
+
+\subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
+We begin by trying to remove the restriction that every point in the metric space has a fixed number of neighbors in a distribution.
+We start with sketches that write down a fixed number of bits~(independent of their input $w$).
+We will show a lower bound on the number of bits that a $\sketch$ algorithm must write down.
+We assume that all coins of $\sketch$ are provided to $\rec$ and that $\rec$ is deterministic~(any coins needed for $\rec$ can be flipped by $\sketch$ in this model).
+
+\begin{lemma}
+Let $W$ be a flat distribution and let $(\sketch, \rec)$ be a secure sketch for $W$.
+Let $W$ be a $(c, t)$-bounded neighbor distribution.
+Let $S_{coin}$ be the number of sketches that can be produced by any fixing of $coin$.
+Then the error $\delta$ of $(\sketch, \rec)$ is at least $\frac{\expe_{coins}L(coins)}{c}$.
+\end{lemma}
+\begin{proof}
+We consider a fixed $w'$ that has $c$ neighbors in the distribution.
+We assume $\rec$ has access to all coins of $\sketch$.
+Furthermore, we assume that $\rec$ is deterministic and that any coins necessary are provided by $\sketch$).
+
+Denote by $S_{coin, R}$ the set of possible sketches for a given set of coins on all values in $R$.
+Furthermore, denote by $S_{coin}$ the set of possible sketches for all values $w$~(for a given value of coin) and note that $S_{coin, R} \subset S_{coin}$.
+Then $\rec(\cdot, w', coin)$ must fail to recover $|R|-|S_{coin, R}|$ fraction of $w\in R$~(recalling that $\rec$ is deterministic for this fixing of $coin$).
+This means that the total number of pairs $(w, coin)$ for which $\rec$ fails to recover is $2^{|coins|}R - \sum_{coins} |S_{coin, R}|$.
+
+This means there must exist some $w$ such that the number of $coin$ values for which $\rec$ fails to recover is 
+\[
+2^{|coin|} - \frac{\sum_{coin} |S_{coin, R}|}{R}.
+\]
+ This means that for this $w$, 
+\[
+\Pr_{coin}[s \leftarrow \sketch(w, coin) \wedge w = \rec(s, w', coin)] < 1- \frac{\expe |S_{coin, R}|}{|R|} = 1-\frac{\expe |S_{coin, R}|}{c} \le 1-\frac{\expe |S_{coin}| }{c}.
+\]
+
+%Consider the function $\rec(w', ss, r)$ where $ss$ is the sketch produced by $\sketch(w)$ and $r$ are the coins used by $\sketch$.  
+\end{proof}
+
+For deterministic sketches:
+\[
+\Hav(W|S ) = -\log \left(\sum_{s\in S} \Pr[S = s] \frac{2^{-\Hoo(W)}}{\Pr[S=s]}\right) = -\log \left(2^{-\Hoo(W)} |S| \right)  = \Hoo(W) - H_0(S).
+\]
+
+\bnote{need to extend this to a non-fixed number of bits and randomized.}
+\section{Dealing with non flat distributions}
+The basic hashing approach outlined above does not extend to arbitrary sources.
+The reason is that some balls may have significantly more points but occur with low probability.
+Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with total probability $\Pr[W\in B_1] =2^{-1/2\Hoo(W)}$ and let $B_2$ be a ball with one point with probability $\Pr[W\in B_2] = 2^{-\Hoo(W)}$.
+Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.
+However, this may completely reveal the point in $B_2$.
+
+Dealing with non-flat distributions requires a new strategy.
+Ideally, this strategy should be aware of the density of the current ball, aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
+We present two strategies: leveraging convex combinations, and partitioning the probability space.
+
+\subsection{Leveraging convex combinations?}
+In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+For example, consider the following extension to \consref{cons:pairwise hash}.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$~(a distribution may be an infinite convex combination, we will show this idea does not work even for the case of finite convex combinations).
+For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+
+The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
+Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
+
+In the flat case, we saw it was necessary to write the down number of bits in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(and this is our goal as the adversary can always guess the most likely ball).
+That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+However, in the setting where $W$ is a convex combination of flat sources this does not hold.
+
+Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+Note that the fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that the various $B_i$ do not intersect).
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
+(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+
+Consider an input point $w\in W$.
+One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
+For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
+This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
+Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+In the following discussion, we present a more complicated layering technique that is agnostic to the flat distributions that form the source.
+
+\begin{figure}[h]
+\label{fig:convex comb}
+\centering
+    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+
+\end{figure}
+
+%\begin{centering}
+%\begin{figure}[t]
+%\includegraphics[scale.5*text_width]{convexCombExample}
+%\end{figure}
+%\end{centering}
+
+\section{Examples to Consider}
 \bibliographystyle{alpha}

### 2014-06-30 trunk/info-bounds/FuzzyExtPossibility.tex
layered construction

@@
 \section{Well-spread distributions}
-\subsection{Depends on Distribution}
-We will start with an intuitively simple type of distribution where no results are known.
-Security should be easy when all points of $W$ are far apart.
+In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.
+We begin by considering secure sketches.
+We a call distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
+Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
+Intuitively, no sketch should be necessary for such a distribution.
+However, we show there is a large gap between a secure sketch that works for a particular well-spread distribution and a secure sketch that works for \emph{all} well-spread distributions.
+
+\begin{table}
+\begin{tabular}{l | l | c}
+Upper bound & Depends on Distribution & Works for all Dist\\
+\hline
+Well-spread distribution & $0$ & $\log |B_t|$\\
+Flat distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta)$ &$\log |B_t|$\\
+Arbitrary distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta) + \log \log \mathcal{M}$ & $\log |B_t|$
+\end{tabular}
+\caption{Upper bounds on minimum number of bits that a fuzzy extractor can write down and still have recovery.}
+\label{tab:upper bounds}
+\end{table}
+\subsection{Distribution Dependent Sketches}
+Error-correction should be easy when all points of $W$ are far apart.
 Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.
@@
 \begin{definition}
-A distribution $W$ is called \emph{$t_{sec}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{sec}$.
+A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
 \end{definition}
-Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{sec}/2$~(assuming the distribution has super-logarithmic min-entropy).
+Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
 Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.
@@
 \label{lem:nosketchwellspread}
-Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works for $W$.
+Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.
 In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.
 \rec is efficient if there exists efficient decoding for the points in $W$.
-By \lemref{lem:fuzzy ext construction} there also exists a fuzzy extractor.\bnote{fill in the parameters}
+By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, m,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
 \end{lemma}  
+\begin{proof}
+It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.
+Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.
+Then by the triangle inequality,
+\[
+t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
+This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
+\end{proof}
 
-\subsection{Works for all well-spread distributions}
+\subsection{Distribution Agnostic Sketches}
 Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
 However, as we show below the above construction does not extend to the setting of all well-spread distributions.
-In particular, any secure sketch must write down a large number of bits~(matching our known constructions of secure sketches).
-However, it is not known if it is necessary to decrease the entropy of the distribution $W$.
+In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
+In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
+In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
+
+We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
+It is not known if it is necessary to decrease the entropy of the distribution $W$.
 
 \begin{lemma}
-Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.
-Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.
+Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.
+Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.
 Then the length of $\sketch$ is at least $\log |B_{t}|$.
@@
 Let $\mathcal{M}$ be a metric space.
-Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions on $\mathcal{M}$.  
+Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
 Consider the following experiment:
 \[
-W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{sec}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
+W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
 \]
+That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
 Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
@@
 \[
-v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{sec}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
+v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
 \]
@@
 Thus, $\Pr[v^* = v] = 1$.
-For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M} - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
-For a secure sketch to lose $\log |B_{t_{sec}}(\cdot)|$ bits of entropy it must write down at least $\log |B_{t_{sec}}(\cdot)|$ bits~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
-Thus, $(\sketch, \rec)$ writes down at least $\log |B_{t_{sec}}|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{sec}}|$ bits on $X$.
-This completes the proof.\bnote{need to deal with the case where the number of bits written by $\sketch$ is variable.}
+For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
+For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
+Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.
+This completes the proof.
 \end{proof}
+\noindent
+\textbf{Note:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
+The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).
 
-\section{Non-well spread distributions}
-\subsection{Dependence on Distributions}
+Furthermore, the above lemma easily extends to the setting where the distributions are not well-spread as long as there is an adversary strategy of choosing the input distribution that produces an input to sketch that is identically distributed to the uniform distribution.
+
+\section{Flat spread distributions}
+In the previous section we showed bounds on producing secure sketches and fuzzy extractors for well-spread distributions.
+In this section we further investigate secure sketches where the sketch depends on the input distribution.\footnote{Recall the bound when the sketch does not know the input distribution is $\log |B_t|$ bits and this is constructible for any distribution.}
+
+\subsection{Distribution Dependent Sketches}
+
 \lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
@@
 In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.
-We start by considering distributions that have a fixed number of neighbors for each point.
+We begin by considering flat distributions where the probability of each point in $W$ is the same.
 
 \begin{definition}
-We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.
-We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
+A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in W$, $\Pr[W=w_0] = \Pr[W=w_1]$.  
 \end{definition}
 
-\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
-
-We now present an information-theoretic construction for fixed-neighbor distributions.  We first introduce the notion of a pairwise-independent hash:
+Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme~(\defref{def:fuzzy min-ent}).
+Fuzzy min-entropy is total weight of the maximum probability ball.
+For flat distribution, this is directly correlated to the ball with the largest number of points.
+That is, for a flat distribution
+\begin{align*}
+\Hfuzz(W) &= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} * \Pr[W=w]\\
+&= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} *2^{-\Hoo(W)}\\
+&=\Hoo(W) -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} 
+\end{align*}
+For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
+\begin{align}
+\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
+\end{align}
+%We start by considering distributions that have a fixed number of neighbors for each point.
+%
+%\begin{definition}
+%We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.
+We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
+%\end{definition}
+%
+%\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
+We now present an information-theoretic construction for flat distributions.  We first introduce the notion of a pairwise-independent hash:
 
@@
 \label{cons:pairwise hash}
-Let $W$ be a $(c, t)$-fixed neighbor distribution over $\mathcal{M}$.
-Let $F :\mathcal{M}\times \mathcal{M}\rightarrow R$ be a pairwise independent hash function.
-We describe $\sketch, \rec$ as follows:
+Let $W$ be a flat distribution over $\mathcal{M}$.  Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a pairwise independent hash function.  We describe $\sketch, \rec$ as follows:
 \begin{itemize}
@@
 \begin{lemma}
-\consref{cons:pairwise hash} is a $(\mathcal{M}, m, m - \log |R|, t)$-secure sketch with error $\delta = \frac{c-1}{|R|}$. 
+\consref{cons:pairwise hash} is a $(\mathcal{M}, m, m - \log |R|, t)$-secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
 \end{lemma}
@@
 We now argue correctness.
-Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is $c$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
+Fix some $w, w'$.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
 Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
 \begin{align*}
-\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] \le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)]  = \frac{c-1}{|R|}
+\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} = \frac{|B_{t, max}|-1}{|R|}
 \end{align*}
-Where the inequality proceeds by union bound and the equality proceeds by the universality of $F$.  This completes the proof.
+Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|$.
+This completes the proof.
 \end{proof}
@@
 Let $n$ be a security parameter.  
-If $|R| \ge c * n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |c| + \omega(\log n)$ suffices.
+If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
 \end{corollary}
@@
 \[
-\Hav(W |\sketch(W)) = \Hoo(W) - \log c - \omega(\log n)
+\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
 \]
-For a flat distribution with a fixed number of neighbors, 
+For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
+Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.
+For a flat distribution, this is also the ball with the largest total weight.
+We will see this becomes more difficult as we move to the setting where points have very different probability.
+In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls.
+We will compensate for this problem by writing down a variable number of bits.
+%with a fixed number of neighbors, 
+%\begin{align*}
+%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
+%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
+%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
+%\end{align*}
+%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.
+
+\bnote{need to extend this to a non-fixed number of bits and randomized.}
+\section{Dealing with non flat distributions}
+The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.
+The reason is that some balls may have significantly more points but low overall probability.
+Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.
+Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.
+However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.
+
+Dealing with non-flat distributions requires a new strategy.
+Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
+We first a natural method to leverage convex combinations that does not work\bnote{phrasing}.
+We then show a solution that comes within \bnote{something} of optimal by partitioning the probability space.
+
+\subsection{Leveraging convex combinations?}
+In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+For example, consider the following extension to \consref{cons:pairwise hash}.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, we show it is difficult to leverage convex combinations in the finite setting and handling the infinite case is more difficult.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+
+The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
+Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
+
+In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
+That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+However, in the setting where $W$ is a convex combination of flat sources this does not hold.
+
+Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+This distribution is illustrated in \figref{fig:convex comb}.
+
+The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
+(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+
+Consider an input point $w\in W$.
+One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
+For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
+This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
+Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
+
+\begin{figure}[h]
+
+\centering
+    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+\label{fig:convex comb}    
+\end{figure}
+
+\bnote{remove pagebreak later}
+
+\subsection{Layered Hashing}
+As we saw in the previous section, dealing with non-flat distributions is difficult.
+The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.
+We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.
+Then the hash is applied only considering the maximum weight of the ball containing points at this level.
+Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.
+
+\pagebreak
+
+\begin{construction}
+\label{cons:leveling}
+Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
+Let $\epsilon>0$ be a parameter.
+Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=k,..., n+\log 1/\epsilon$.
+Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.
+We describe $\sketch, \rec$ as follows:
+\begin{itemize}
+\item $\sketch(w)$:
+\subitem If $\Pr[W=w]\le 2^{-n}/\epsilon$
+\begin{itemize}
+\item Set $p=0, w$.
+\end{itemize}
+\subitem Else
+\begin{itemize}
+\item Find $i$ such that $\Pr[W=w]\in L_i$.  
+\item Sample $K\leftarrow \mathcal{K}_i$.
+\item Set $p =1,  i, F_i(K, w), K$.
+\end{itemize}
+\item $\rec(w', y)$:
+\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
+\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
+\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
+\subitem Output $\perp$.
+\end{itemize}
+\end{construction}
+
+Before describing the bounds obtained by \consref{cons:leveling} we will extend our notation for the maximum likelihood ball to the leveled case.
+Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.
+That is,
+\[
+B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
+\]
+\begin{lemma}
+Let $\delta>0$ be an function of $n$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.
+Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log 1/\delta - \log 1/\epsilon -\log n$.\bnote{come back and correct this}
+\end{lemma}
+\begin{proof}
+We begin by arguing correctness.
+Fix some $w, w'$.
+If $\Pr[W=w]\le 2^{-n}\epsilon$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
+Now consider the case when $\Pr[W=w]> 2^{-n}\epsilon$, let $L_i^*$ be the level of $\Pr[W=w]$.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$.
+The size of $W^*$ is at most $B_{t, i, max}$.
+The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).
+Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
+The probability that another element $w^*$ is:
 \begin{align*}
-\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
-&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
-&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
+\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
 \end{align*}
-Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.
+Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
 
+We now argue security.
+First note that the total weight of points whose probability is less than $2^{-n}\epsilon$ is at most $\epsilon$~(there are at most $2^n$ points in the distribution).
+That is, $\sum_{w | \Pr[W=w]\le 2^{-n}\epsilon}\Pr[W = w] \le \epsilon$.
+Let $1_{\text{low prob}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
+Then
+\begin{align*}
+\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low prob}}=1] * 1 + \Pr[1_{\text{low prob}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)\\
+-\log\left( \epsilon + (1-\epsilon)2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
+\end{align*}
+For the remainder of the proof, we seek a bound on $\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\Pr[W=w | \sketch(W)]$.
+We separate out this quantity into levels:
+\begin{align*}
+\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
+&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
+&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
+&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
+&=\frac{ \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|\right)}{\delta}\\
+%&=\delta \sum_{i | k\le i \le n+\log 1/\epsilon} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
+\end{align*}
+Now consider an adversary that receives $i$ as input, in the oracle setting, the best strategy is to guess a point that has the most weight in that layer.
+The success of this adversary is at most $2^{-i}|B_{t,i, max}|$.
+Note there are $n-k+\log 1/\epsilon$ outcomes for $i$ so the overall success of such an adversary is at most $n-k+\log 1/\epsilon$ better than an adversary without such input.
+This allows us to conclude that
+\begin{align*}
+\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \frac{(n-k+\log 1/\epsilon) 2^{-\Hfuzz(W)}}{\delta}.
+\end{align*}
+Combining both cases we have:
+\begin{align*}
+\Hav(W | \sketch(W)) = -\log \left(\epsilon+\frac{(1-\epsilon)(n-k+\log1/\epsilon)2^{-\Hfuzz(W)}}{\delta}\right).
+\end{align*}
+Setting $\epsilon = 2^{-k}$ yields
+\begin{align*}
+\Hav(W | \sketch(W)) &= -\log \left(k+(1-2^{-k})(n)2^{-\Hfuzz(W)/\delta}\right)\\
+&\ge -\log \min\{k, (1-2^{-k}) n2^{-\Hfuzz(W)}/\delta\})-1\\
+&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-k}) - 1\\
+&\ge \Hfuzz(W) - \log n + \log \delta - 2\\
+\end{align*}
+
+\end{proof}
+
+\bibliographystyle{alpha}
+\bibliography{crypto}
+
+\appendix
+\section{Old Proofs}
 \subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
@@
 \]
-\bibliographystyle{alpha}
-\bibliography{crypto}
+
+\section{Examples to Consider}
 

### 2014-07-01 info-bounds/FuzzyExtPossibility.tex
cleaning up yesterday's proof

@@
 \[
-\Hav(W |\sketch(W)) = \Hoo(W) - \log c - \omega(\log n)
+\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
 \]
-For a flat distribution with a fixed number of neighbors, 
+For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
+Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.
+For a flat distribution, this is also the ball with the largest total weight.
+We will see this becomes more difficult as we move to the setting where points have very different probability.
+In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls.
+We will compensate for this problem by writing down a variable number of bits.
+%with a fixed number of neighbors, 
+%\begin{align*}
+%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
+%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
+%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
+%\end{align*}
+%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.
+
+\bnote{need to extend this to a non-fixed number of bits and randomized.}
+\section{Dealing with non flat distributions}
+The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.
+The reason is that some balls may have significantly more points but low overall probability.
+Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.
+Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.
+However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.
+
+Dealing with non-flat distributions requires a new strategy.
+Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
+We first a natural method to leverage convex combinations that does not work\bnote{phrasing}.
+We then show a solution that comes within \bnote{something} of optimal by partitioning the probability space.
+
+\subsection{Leveraging convex combinations?}
+In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+For example, consider the following extension to \consref{cons:pairwise hash}.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, we show it is difficult to leverage convex combinations in the finite setting and handling the infinite case is more difficult.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+
+The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
+Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
+
+In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
+That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+However, in the setting where $W$ is a convex combination of flat sources this does not hold.
+
+Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+This distribution is illustrated in \figref{fig:convex comb}.
+
+The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
+(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+
+Consider an input point $w\in W$.
+One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
+For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
+This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
+Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
+
+\begin{figure}[h]
+
+\centering
+    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+\label{fig:convex comb}    
+\end{figure}
+
+\bnote{remove pagebreak later}
+
+\subsection{Layered Hashing}
+As we saw in the previous section, dealing with non-flat distributions is difficult.
+The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.
+We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.
+Then the hash is applied only considering the maximum weight of the ball containing points at this level.
+Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.
+
+\pagebreak
+
+\begin{construction}
+\label{cons:leveling}
+Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
+Let $\epsilon>0$ be a parameter.
+Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=k,..., n+\log 1/\epsilon$.
+Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.
+We describe $\sketch, \rec$ as follows:
+\begin{itemize}
+\item $\sketch(w)$:
+\subitem If $\Pr[W=w]\le 2^{-n}/\epsilon$
+\begin{itemize}
+\item Set $p=0, w$.
+\end{itemize}
+\subitem Else
+\begin{itemize}
+\item Find $i$ such that $\Pr[W=w]\in L_i$.  
+\item Sample $K\leftarrow \mathcal{K}_i$.
+\item Set $p =1,  i, F_i(K, w), K$.
+\end{itemize}
+\item $\rec(w', y)$:
+\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
+\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
+\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
+\subitem Output $\perp$.
+\end{itemize}
+\end{construction}
+
+Before describing the bounds obtained by \consref{cons:leveling} we will extend our notation for the maximum likelihood ball to the leveled case.
+Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.
+That is,
+\[
+B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
+\]
+\begin{theorem}
+Let $\delta>0$ be an function of $n$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.
+Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+\end{theorem}
+\bnote{right now this is stated without epsilon.  I found the expression to be really gross with $\epsilon$ included.  Thoughts?  I know $\epsilon$ needs to be there because the construction uses it.}
+\begin{proof}
+We begin by arguing correctness.
+Fix some $w, w'$.
+If $\Pr[W=w]\le 2^{-n}\epsilon$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
+Now consider the case when $\Pr[W=w]> 2^{-n}\epsilon$, let $L_i^*$ be the level of $\Pr[W=w]$.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$.
+The size of $W^*$ is at most $B_{t, i, max}$.
+The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).
+Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
+The probability that another element $w^*$ is:
 \begin{align*}
-\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
-&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
-&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
+\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
 \end{align*}
-Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.
+Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
 
+We now argue security.
+First note that the total weight of points whose probability is less than $2^{-n}\epsilon$ is at most $\epsilon$~(there are at most $2^n$ points in the distribution).
+That is, $\sum_{w | \Pr[W=w]\le 2^{-n}\epsilon}\Pr[W = w] \le \epsilon$.
+Let $1_{\text{low prob}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
+Then
+\begin{align*}
+\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low prob}}=1] * 1 + \Pr[1_{\text{low prob}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)\\
+-\log\left( \epsilon + (1-\epsilon)2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
+\end{align*}
+We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
+An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.
+That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+Note there are $n-k+\log 1/\epsilon$ outcomes for $i$ so the overall success of such an adversary is at most $n-k+\log 1/\epsilon$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
+That is,
+\begin{align}
+\expe_{i | k\le i \le n+\log 1/\epsilon}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | k\le i \le n+\log 1/\epsilon}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
+&\le \left(n-k+\log 1/\epsilon\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
+&= \left(n-k+\log 1/\epsilon\right)\Hfuzz(W)\label{eq:link fuzz 3}
+\end{align}
+For the remainder of the proof, we seek a bound on $\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\Pr[W=w | \sketch(W)]$.
+We separate out this quantity into levels:
+\begin{align*}
+\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
+&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
+&\le \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
+&\le \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
+&\le\frac{ \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
+%&=\delta \sum_{i | k\le i \le n+\log 1/\epsilon} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
+%\end{align*}
+%Now consider This allows us to conclude that 
+%\begin{align*}
+%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
+&= \frac{(n-k+\log 1/\epsilon) 2^{-\Hfuzz(W)}}{2\delta}.
+\end{align*}
+Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
+Combining both cases we have:
+\begin{align*}
+\Hav(W | \sketch(W)) = -\log \left(\epsilon+\frac{(1-\epsilon)(n-k+\log1/\epsilon)2^{-\Hfuzz(W)}}{2\delta}\right).
+\end{align*}
+Setting $\epsilon = 2^{-k}$ yields
+\begin{align*}
+\Hav(W | \sketch(W)) &= -\log \left(k+\frac{(1-2^{-k})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
+&\ge -\log \min\{k, \frac{(1-2^{-k}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
+&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-k}) - 2\\
+&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
+\end{align*}
+Where the third line follows from the third because $\Hfuzz(W)\le \Hoo(W) = k$.\bnote{what condition do we need to get rid of $\log (1-2^{-k})$?}
+\end{proof}
+
+\bibliographystyle{alpha}
+\bibliography{crypto}
+
+\appendix
+\section{Old Proofs}
 \subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
@@
 
-\bnote{need to extend this to a non-fixed number of bits and randomized.}
-\section{Dealing with non flat distributions}
-The basic hashing approach outlined above does not extend to arbitrary sources.
-The reason is that some balls may have significantly more points but occur with low probability.
-Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with total probability $\Pr[W\in B_1] =2^{-1/2\Hoo(W)}$ and let $B_2$ be a ball with one point with probability $\Pr[W\in B_2] = 2^{-\Hoo(W)}$.
-Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.
-However, this may completely reveal the point in $B_2$.
-
-Dealing with non-flat distributions requires a new strategy.
-Ideally, this strategy should be aware of the density of the current ball, aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
-We present two strategies: leveraging convex combinations, and partitioning the probability space.
-
-\subsection{Leveraging convex combinations?}
-In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
-For example, consider the following extension to \consref{cons:pairwise hash}.
-Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$~(a distribution may be an infinite convex combination, we will show this idea does not work even for the case of finite convex combinations).
-For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
-
-The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
-Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
-
-In the flat case, we saw it was necessary to write the down number of bits in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(and this is our goal as the adversary can always guess the most likely ball).
-That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
-However, in the setting where $W$ is a convex combination of flat sources this does not hold.
-
-Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
-Note that the fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
-Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that the various $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
-(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
-
-Consider an input point $w\in W$.
-One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
-For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
-This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
-This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
-Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
-In the following discussion, we present a more complicated layering technique that is agnostic to the flat distributions that form the source.
-
-\begin{figure}[h]
-\label{fig:convex comb}
-\centering
-    \includegraphics[width=.9\textwidth]{convexCombExample.png}
-    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
-
-\end{figure}
-
-%\begin{centering}
-%\begin{figure}[t]
-%\includegraphics[scale.5*text_width]{convexCombExample}
-%\end{figure}
-%\end{centering}
-
 \section{Examples to Consider}
-\bibliographystyle{alpha}
-\bibliography{crypto}
 

### 2014-07-02 trunk/info-bounds/FuzzyExtPossibility.tex
minor modifications to level proof

@@
 Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
-Let $\epsilon>0$ be a parameter.
-Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=k,..., n+\log 1/\epsilon$.
+Let $\ell\in\mathbb{Z}^+$ be a parameter.
+Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.
 Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.
@@
 \item $\sketch(w)$:
-\subitem If $\Pr[W=w]\le 2^{-n}/\epsilon$
+\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
 \begin{itemize}
@@
 \]
-\begin{lemma}
+\begin{theorem}
 Let $\delta>0$ be an function of $n$.
 Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.
-Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log 1/\delta - \log 1/\epsilon -\log n$.\bnote{come back and correct this}
-\end{lemma}
+Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+\end{theorem}
+\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
 \begin{proof}
@@
 Fix some $w, w'$.
-If $\Pr[W=w]\le 2^{-n}\epsilon$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
-Now consider the case when $\Pr[W=w]> 2^{-n}\epsilon$, let $L_i^*$ be the level of $\Pr[W=w]$.
+If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
+Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
 Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$.
@@
 We now argue security.
-First note that the total weight of points whose probability is less than $2^{-n}\epsilon$ is at most $\epsilon$~(there are at most $2^n$ points in the distribution).
-That is, $\sum_{w | \Pr[W=w]\le 2^{-n}\epsilon}\Pr[W = w] \le \epsilon$.
+First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).
+That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.
 Let $1_{\text{low prob}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
@@
 \Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low prob}}=1] * 1 + \Pr[1_{\text{low prob}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)\\
--\log\left( \epsilon + (1-\epsilon)2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
+-\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
 \end{align*}
-For the remainder of the proof, we seek a bound on $\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\Pr[W=w | \sketch(W)]$.
+We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
+An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.
+That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+Note there are $n-m+\ell$ outcomes for $i$ so the overall success of such an adversary is at most $n-m+\ell$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
+That is,
+\begin{align}
+\expe_{i | m\le i \le n+\ell}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+\ell}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
+&\le \left(n-m+\ell\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
+&= \left(n-m+\ell\right)\Hfuzz(W)\label{eq:link fuzz 3}
+\end{align}
+For the remainder of the proof, we seek a bound on \[\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].\]
 We separate out this quantity into levels:
 \begin{align*}
-\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
-&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
-&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
-&=\frac{ \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|\right)}{\delta}\\
-%&=\delta \sum_{i | k\le i \le n+\log 1/\epsilon} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
+\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
+&= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
+&\le \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
+&\le \expe_{i | m\le i \le n+\ell} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
+&\le\frac{ \expe_{i | m\le i \le n+\ell} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
+%&=\delta \sum_{i | m\le i \le n+\ell} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
+%\end{align*}
+%Now consider This allows us to conclude that 
+%\begin{align*}
+%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
+&= \frac{(n-m+\ell) 2^{-\Hfuzz(W)}}{2\delta}.
 \end{align*}
-Now consider an adversary that receives $i$ as input, in the oracle setting, the best strategy is to guess a point that has the most weight in that layer.
-The success of this adversary is at most $2^{-i}|B_{t,i, max}|$.
-Note there are $n-k+\log 1/\epsilon$ outcomes for $i$ so the overall success of such an adversary is at most $n-k+\log 1/\epsilon$ better than an adversary without such input.
-This allows us to conclude that
-\begin{align*}
-\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \frac{(n-k+\log 1/\epsilon) 2^{-\Hfuzz(W)}}{\delta}.
-\end{align*}
+Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
 Combining both cases we have:
 \begin{align*}
-\Hav(W | \sketch(W)) = -\log \left(\epsilon+\frac{(1-\epsilon)(n-k+\log1/\epsilon)2^{-\Hfuzz(W)}}{\delta}\right).
+\Hav(W | \sketch(W)) = -\log \left(2^{-\ell}+\frac{(1-2^{-\ell})(n-m+\ell)2^{-\Hfuzz(W)}}{2\delta}\right).
 \end{align*}
-Setting $\epsilon = 2^{-k}$ yields
+Setting $\ell = m$ yields
 \begin{align*}
-\Hav(W | \sketch(W)) &= -\log \left(k+(1-2^{-k})(n)2^{-\Hfuzz(W)/\delta}\right)\\
-&\ge -\log \min\{k, (1-2^{-k}) n2^{-\Hfuzz(W)}/\delta\})-1\\
-&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-k}) - 1\\
-&\ge \Hfuzz(W) - \log n + \log \delta - 2\\
+\Hav(W | \sketch(W)) &= -\log \left(m+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
+&\ge -\log \min\{m, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
+&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
+&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
 \end{align*}
-
+Where the third line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$.
+The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the whole quantity is negative~(and entropy is non-negative).
 \end{proof}

### 2014-07-02 trunk/constantRate/ConstCompFuzzExt-reorg.tex
reorganized version of paper, not sure if awesome

--- 2014-06-10 trunk/constantRate/ConstCompFuzzExt.tex
@@
 \title{Key Derivation From Noisy Sources With More Errors Than Entropy}
-%\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
-%work was sponsored by the Department of the Air Force under Air Force
-%Contract
-%\#FA8721-05-C-0002.  Opinions,
-%interpretations, conclusions and recommendations are those of the author
-%and
-%are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}
+\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
+work was sponsored by the Department of the Air Force under Air Force
+Contract
+\#FA8721-05-C-0002.  Opinions,
+interpretations, conclusions and recommendations are those of the author
+and
+are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
 
@@
 %We do not considering the joint distribution $W_1,..., W_q$.
+
+\begin{table}
+\begin{tabular}{l | l | l | l }
+Construction & Security & Features & Limitations \\
+\hline
+\consref{cons:info theoretic} & Info-theoretic & Exploits distribution & Most symbols must \\
+&&structure & contribute fresh entropy \\\hline
+\consref{cons:sampling} & Computational  & Reusable with arbitrary & Error tolerance is\\
+&&correlation & sub-constant fraction\\\hline
+\consref{cons:first construction} & Computational & Supports distributions  & Super-polynomial \\
+& &  with dependent symbols & size symbols
+\end{tabular}
+\caption{Summary of new constructions.  All constructions support families of distributions with $\Huse \le 0$.}
+\label{tab:upper bounds}
+\end{table}
 
@@
 
-\subsection{Coding Theory}
-\label{sec:coding theory}
-We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
-\begin{definition}
-\label{def:hamming z channel}
-For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
-\end{definition}
-
-\begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
-} \decode(c') \neq c] \leq \delta_{code}$.
-\end{definition}
-
-\textbf{Notes:}
-Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
-Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
-These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
-The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
-See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.
-
-\subsection{Obfuscation}
-Our constructions will use obfuscation for two types of circuits: point functions and digital lockers. The family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
-\[
-I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
-\]
-and the class of digital lockers is $\mathtt{I}_n = \{I_{w, r}\}_{w \in \zo^n, r\in\zo^\kappa}$ defined as follows:
-\[
-I_{w, r}(x):\begin{cases} r & x=w\\\perp & \text{otherwise}\end{cases}.
-\]
-The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
-This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at most a polynomial number of oracle queries to the function.
-In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
-Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
-They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
-
-\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
-\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
-\begin{enumerate}
-\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
-\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
-\[
-|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
-\]
-where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
-\end{enumerate}
-\end{definition}
-For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
-When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
-\section{Computational Fuzzy Extractors}
+\subsection{Fuzzy Extractors}
 \label{sec:fuzzy extractors}
@@
 
-Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: using a fuzzy conductor and a privacy amplification component or analyzing the information-reconciliation and privacy amplifications components together  .
-We use each approach~(in \secref{sec:construction} and \secref{sec:sampling} respectively).
+Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: using a fuzzy conductor and a privacy amplification component or analyzing the information-reconciliation and privacy amplifications components together.
+%We both approaches, \consref{use each approach~(in \secref{sec:construction} and \secref{sec:sampling} respectively).
 %The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.
 %In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
-We use a computational version of a fuzzy conductor.
-We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
+We will use approaches: \consref{cons:info theoretic} and \consref{cons:first construction} use fuzzy conductors and privacy amplification and \consref{cons:sampling} achieves both tasks simultaneously.
+%We use a computational version of a fuzzy conductor.
+We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
 \begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
@@
 \end{definition}
+\noindent \textbf{Note: } Replacing HILL entropy with average min-entropy gives an \emph{information-theoretic fuzzy conductor}.
+We will use this notion for our information-theoretic construction \secref{sec:info theory cons}.
 
@@
 
-\subsection{Reusable Fuzzy Extractors}
+\subsubsection{Information-Theoretic Definitions}
+In this section we review additional definitions that will be used for our information-theoretic construction in \secref{sec:info theory cons}.
+\begin{definition}
+\label{def:secure sketch}
+An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+\begin{enumerate}
+\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
+\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
+The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
+\end{definition}
+
+\begin{definition}
+\label{def:conductor}
+A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
+\end{definition}
+
+\noindent Randomness condensers can be built  more efficiently than randomness extractors~(for example~\cite{dodis2013key}).
+
+%\begin{definition}
+%\label{def:fuzzy conductor}
+%A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-fuzzy conductor that is $\epsilon$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following condition:
+%\begin{itemize}
+%\item For any distribution $W\in \mathcal{W}$, the string $r$ has is close to a distribution with average min-entropy conditioned on $P$.
+That is there exists a distribution $Y$ with $\Hav(Y | P)\ge \tilde{m}$ such that $(R ,P)\approx_\epsilon (Y, P)$.
+%\end{itemize}
+%\end{definition}
+
+\subsubsection{Reusable Fuzzy Extractors}
 \label{sec:reusable}
+\bnote{some of this should probably be moved to the introduction}
 
@@
 
+\subsection{Coding Theory}
+\label{sec:coding theory}
+We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
+\begin{definition}
+\label{def:hamming z channel}
+For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
+\end{definition}
+
+\begin{definition}
+Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
+} \decode(c') \neq c] \leq \delta_{code}$.
+\end{definition}
+
+\textbf{Notes:}
+Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
+The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
+See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.
+
+\subsection{Obfuscation}
+Our constructions will use obfuscation for two types of circuits: point functions and digital lockers. The family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
+\[
+I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
+\]
+and the class of digital lockers is $\mathtt{I}_n = \{I_{w, r}\}_{w \in \zo^n, r\in\zo^\kappa}$ defined as follows:
+\[
+I_{w, r}(x):\begin{cases} r & x=w\\\perp & \text{otherwise}\end{cases}.
+\]
+The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
+This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at most a polynomial number of oracle queries to the function.
+In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
+Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
+
+\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
+\begin{enumerate}
+\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\[
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
+\]
+where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
+\end{enumerate}
+\end{definition}
+For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
+When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
+
 %\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
@@
 
-\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}
-\label{sec:construction}
-For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.
-Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
-Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+\section{An information-theoretic construction with $\Huse\le 0$}
+\label{sec:info theory cons}
+\bnote{needs to be rewritten depending on ordering}
+In this section we show an information-theoretic analogue to \consref{cons:first construction}.
+%This construction can essentially be seen as replacing the computational point obfuscation with information-theoretic randomness extractors.
+Using this weaker object requires us to make a stronger assumption on our starting distribution.
+Furthermore, the important features of \consref{cons:sampling}, $\Huse \le 0$ for a small alphabet and reusability, crucially rely on computational assumptions.
+Achieving these benefits information-theoretically is an open question.
+We will construct an information-theoretic fuzzy conductor which can be converted to a fuzzy extractor using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
+
+The main idea of this construction is to first condense entropy from each block of the source and then apply a secure sketch to the extracted information.
+Intuitively, we are then able from a large alphabet while paying entropy loss on the smaller alphabet.
+%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
 
 \begin{construction}
-\label{cons:first construction}
-Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
-Let  $C\subset \zo^\ell$ be an error-correcting code.
-We describe $\gen, \rep$ as follows:
-
+\label{cons:info theoretic}
+Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.  We describe $\gen, \rep$ as follows:
 \begin{center}
@@
 \item \underline{Input}: $w = w_1,..., w_\ell$
-\item Sample $c\leftarrow C$.
 \item For $j=1,..., \ell$:
 \begin{enumerate}[(i)]
-\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
-\item Else: Sample $r_j \overset{\$}\leftarrow \mathcal{Z}$.
-\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
+\item Sample $seed_i\leftarrow \zo^d$.
+\item Set $v_i = \cond(w_i, seed_i)$.
 \end{enumerate}
-\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
+\item Set $ss \leftarrow \sketch(v_1,..., v_\ell)$.
+\item Set $p = (ss, seed_1,..., seed_\ell)$.
+\item Output $(v, p)$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', p)$
+\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\ell))$
 \item For $j=1,..., \ell$:
 \begin{enumerate}[(i)]
-\item If $p_j(w_j') = 1$: set $c_j' = 0$.
-\item Else: set $c_j' = 1$.
+\item Set $v_i = \cond(w_i, seed_i)$.
 \end{enumerate}
-\item Set $c = \decode(c')$.
-\item Output $c$.
+\item Output $v = \rec(v', ss)$.
 \end{enumerate}
-\vspace{0.15in}
+\vspace{0.7in}
 \end{minipage}
@@
 
-The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
-In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
-There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
-However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
-This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
-
-\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
-By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
-This restriction on the distribution is captured in the following definition.
-
-\begin{definition}
-\label{def:block guessable}
-Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
-\begin{cases}
-1 & w_j = w_j'\\
-0 & \text{otherwise}.
-\end{cases}
-\]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
-\[
-\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-
-We show some examples of unguessable block distributions in \apref{sec:characterize}.
-In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
-
-\begin{theorem}
-\label{thm:main thm first cons}
-Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
-\end{theorem}
-\begin{proof}
-We first argue security in the following Lemma.
-
 \begin{lemma}
-\label{lem:security of cons}
-Let all variables be as in \thref{thm:main thm first cons}.
-For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
+\label{lem:info theory sec}
+Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
+Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.
+Then the following is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-fuzzy conductor that is $\epsilon \ell$ hard with error $\delta$:
+
 \end{lemma}
 
-We give a brief outline of the proof here; the proof is in \apref{app:security of main cons}.
-\begin{proof}[Outline]
-It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
-Let $J$ be the set of indices that exists according to \defref{def:block guessable}.
-Define the distribution $C'$ as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.
-We first note that $C'$ has sufficient entropy, because $\Hav(C' |P) = \Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - |J^c|$ (the second step is by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
-It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
-%Define the distribution $X$ as follows:
-%\[X_i =
-%\begin{cases}
-%W_i & C_i = 0\\
-%R_i & C_i = 1.
-%\end{cases}\]
-The outline for the rest of the proof is as follows:
-\begin{itemize}
-\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$.
-Since $P$ is a collection of obfuscated programs, there exists a simulator $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
-\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.
-That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
-\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
-\end{itemize}
-\end{proof}
-We now argue correctness of \consref{cons:first construction}.
-We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
-%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
-However, we start by justifying our use of unidirectional codes.
-\begin{lemma}
-\label{lem:no 1 to 0 flips}
-Let all variables be as in \thref{thm:main thm first cons}.
-The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
-\end{lemma}
-\begin{proof}
-Consider a coordinate $j$ for which $c_j=1$.
-Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$.
-The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
-\end{proof}
-
-Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
-Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
-\end{proof}
-
-\subsection{Discussion of \consref{cons:first construction}}
-\label{sec:discussion}
-\lnote{I did not check this calculation -- will do}
-To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
-\[
-\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
-\]
-
-We consider what entropy is necessary for security.
-The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
-For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
-This yields:
-\[
-\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
-
-\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
-
-If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
-
-%\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
-Do we need it?} There are three major drawbacks to \consref{cons:first construction}.
-First, we require blocks to be super-polynomial in size.
-Second, we only obtain a single bit from each block.
-Third, since each block is individually obfuscated, we leak information about individual blocks if they can be guessed.
-To compensate for this leakage, we need most\lnote{just some linear fraction, not most, right?
-and, in fact, isn't just one block enough given our repeated use argument which we haven't really made yet?} blocks to be unguessable given equality queries.
-Our second construction addresses this last weakness.
-
-\section{Trading Errors for Entropy}
+\subsection{Discussion of Information-Theoretic Construction}
+\bnote{write this}
+
+\section{Achieving Reusability \& $\Huse\le 0$}
 \label{sec:sampling}
-\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.
+In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with $\Huse \le 0$.
+In this section we show that the addition of computational techniques yields considerable extra power.
+Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.
+This is known to be impossible in the information-theoretic setting.
+%\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.
 Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.
@@
 %In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
+
 The main idea is to sample a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscate the concatenation of these blocks.
 Denote this concatenated value by $V_1$.
-This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct.
-We first present the necessary definitions and the construction and then compare it to \consref{cons:first construction}.
+This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.
+We first present the necessary definitions and the construction.% and then compare it to \consref{cons:first construction}.
 % and the construction proceeds by either obfuscating $V_i$ or a random point as before.
@@
 \noindent
-There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
-\begin{itemize}
-\item Multiple blocks are concatenated together.
+%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
+%\begin{itemize}
+%\item Multiple blocks are concatenated together.
 This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.
@@
 For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.
+%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.
 This requires the use of digital lockers in place of point obfuscations.
@@
 This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
-\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.
+%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.
 This construction works for an arbitrary size alphabet.
 We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
-\end{itemize}
+%\end{itemize}
 The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
@@
 
-\lnote{in prev construction's theorem statement, $\mathcal{Z}$ grows as a function of $n$, and here it doesn't have to, but may.
-Right now the differences between the two theorems are too subtle to notice.
-Make theorem statements similar and highlight the differences.}
 \begin{theorem}
@@
 
-The next two sections are dedicated to proving this theorem.
- For security we argue that each of the $v_i$ values is unguessable.
+Before we show \thref{thm:sampling} we present a simplified construction of \consref{cons:sampling}.
+This construction essentially ignores the sampling step and asks when obfuscation provides security of the obfuscated values $V_1,..., \ell$.
+Our security argument for \consref{cons:sampling} will reduce to this simplified construction.
+After presenting this simplified construction we will return to showing \thref{thm:sampling}.
+
+\subsection{Simplifying \consref{cons:sampling}}
+In this section, we present a simplified version of \consref{cons:sampling}.
+The goal of this construction is to understand the type of sources that \consref{cons:sampling} supports.
+Furthermore, this simplified construction has some advantages over \consref{cons:sampling}.\footnote{For the sake of clarity we defer discussion of \consref{cons:first construction} until \apref{sec:construction}.
+In this section we focus on understand what information is leaked by point obfuscations and digital lockers.}
+%Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
+This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+
+\begin{construction}
+\label{cons:first construction}
+Let $\mathcal{Z}$ be an alphabet and let $V = V_1,..., V_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
+Let  $C\subset \zo^\ell$ be an error-correcting code.
+We describe $\gen, \rep$ as follows:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $v = v_1,..., v_\ell$
+\item Sample $c\leftarrow C$.
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item If $c_j = 0$: $p_j = \mathcal{O}(I_{v_j})$.
+\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
+\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
+\end{enumerate}
+\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(v', p)$
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item If $p_j(v_j') = 1$: set $c_j' = 0$.
+\item Else: set $c_j' = 1$.
+\end{enumerate}
+\item Set $c = \decode(c')$.
+\item Output $c$.
+\end{enumerate}
+\vspace{0.15in}
+\end{minipage}
+\end{tabular}
+\end{center}
+\end{construction}
+
+The input $v$ is hidden in two different ways.  In locations where $c_j=1$, the block $v_j$ is information-theoretically unknown.
+In locations where $c_j=0$, it is hard to find $v_j$ given access to the point obfuscation.
+There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $v_j \neq v_j'$.
+However, if a bit $c_j'$ is $0$, this likely means that $v_j=v_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
+This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
+
+\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $V_j$.
+By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
+Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
+This restriction on the distribution is captured in the following definition.
+
+\begin{definition}
+\label{def:block guessable}
+Let $I_v (\cdot, \cdot)$ be an oracle that returns \[I_v(j, v_j')=
+\begin{cases}
+1 & v_j = v_j'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $V = V_1||...|V_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+\[
+\forall j\in J, \Hav(V_j |View(S^{I_{V}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+
+We show some examples of unguessable block distributions in \apref{sec:characterize}.
+In particular, any source $V$ where for all $j$, $\Hoo(V_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
+
+Intuitively, for a block unguessable distribution, the oracle provided by the obfuscation is not useful.
+Indeed, we can show that \consref{cons:first construction} is a computational fuzzy conductor~(\apref{sec:construction}).
+It is this observation that allows us to show the security of our \emph{sample-then-obfuscate construction}.
+We will show that the output of the sampling part of the algorithm produces a unguessable-block distribution.
+% For security we argue that each of the $v_i$ values is unguessable.
 For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.
@@
 \label{ssec:sec cons sampling}
+We now return to showing \thref{thm:sampling}.  
 In order to show security \consref{cons:sampling}, we
@@
 We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
-Then security follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
+Then security essentially follows from the security of \consref{cons:first construction}.
+%follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
 Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
@@
 However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.
+
+%\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}
 
@@
 
-\section{An information-theoretic construction with $\Huse\le 0$}
-In this section we show an information-theoretic analogue to \consref{cons:first construction}.
-%This construction can essentially be seen as replacing the computational point obfuscation with information-theoretic randomness extractors.
-Using this weaker object requires us to make a stronger assumption on our starting distribution.
-Furthermore, the important features of \consref{cons:sampling}, $\Huse \le 0$ for a small alphabet and reusability, crucially rely on computational assumptions.
-Achieving these benefits information-theoretically is an open question.
-We will construct an information-theoretic fuzzy conductor which can be converted to a fuzzy extractor using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
-
-The main idea of this construction is to first condense entropy from each block of the source and then apply a standard secure sketch to the extracted information.
-Intuitively, we are then able from a large alphabet while paying entropy loss on the smaller alphabet.
-%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
-We first review some information-theoretic definitions.
-
-\begin{definition}
-\label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
-\begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
-\end{definition}
-
-\begin{definition}
-\label{def:conductor}
-A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
-\end{definition}
-
-Note that randomness condensers can be built significantly more efficiently than randomness extractors~(see for example~\cite{dodis2013key}).
-
-\begin{definition}
-\label{def:fuzzy conductor}
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-fuzzy conductor that is $\epsilon$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following condition:
-\begin{itemize}
-\item For any distribution $W\in \mathcal{W}$, the string $r$ has is close to a distribution with average min-entropy conditioned on $P$.
-That is there exists a distribution $Y$ with $\Hav(Y | P)\ge \tilde{m}$ such that $(R ,P)\approx_\epsilon (Y, P)$.
-\end{itemize}
-\end{definition}
-
-\begin{lemma}
-Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
-Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.
-Then the following is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-fuzzy conductor that is $\epsilon \ell$ hard with error $\delta$:
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_\ell$
-\item For $j=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item Sample $seed_i\leftarrow \zo^d$.
-\item Set $v_i = \cond(w_i, seed_i)$.
-\end{enumerate}
-\item Set $ss \leftarrow \sketch(v_1,..., v_\ell)$.
-\item Set $p = (ss, seed_1,..., seed_\ell)$.
-\item Output $(v, p)$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\ell))$
-\item For $j=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item Set $v_i = \cond(w_i, seed_i)$.
-\end{enumerate}
-\item Output $v = \rec(v', ss)$.
-\end{enumerate}
-\vspace{0.7in}
-\end{minipage}
-\end{tabular}
-\end{center}
-\end{lemma}
+\section{Proof of \lemref{lem:cond and cext}}
+\label{sec:cond and cext}
+\lnote{I need to check this}
+\begin{proof}
+It suffices to show if there is some distinguisher $D'$ of size $s'$ where
+\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
+ \[
+ \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
+ \]
+Let $D'$ be such a distinguisher.  That is,
+\[
+\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D$ as follows.
+On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.
+Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
+Then we have the following:
+\begin{align*}
+\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
+&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
+&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
+\end{align*}
+Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
+\end{proof}
+
+\section{Proof of \lemref{lem:info theory sec}}
 \begin{proof}
@@
 
-\subsection{Discussion of Information-Theoretic Construction}
-\bnote{write this}
-\section{Proof of \lemref{lem:cond and cext}}
-\label{sec:cond and cext}
-\lnote{I need to check this}
-\begin{proof}
-It suffices to show if there is some distinguisher $D'$ of size $s'$ where
-\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
- then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
- \[
- \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
- \]
-Let $D'$ be such a distinguisher.  That is,
-\[
-\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
-\]
-Then define $D$ as follows.
-On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.
-Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
-Then we have the following:
-\begin{align*}
-\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
-&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
-&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
-&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
-\end{align*}
-Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
-\end{proof}
-
-\section{Proof of \lemref{lem:security of cons}}
+\section{Analysis of \consref{cons:first construction}}
+\label{sec:construction}
+In this section we present analysis of \consref{cons:first construction}.
+The following theorem states the construction is both correct and secure.
+After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
+\begin{theorem}
+\label{thm:main thm first cons}
+Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
+\end{theorem}
+\begin{proof}
+We first argue security in the following Lemma.
+
+\begin{lemma}
+\label{lem:security of cons}
+Let all variables be as in \thref{thm:main thm first cons}.
+For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
+\end{lemma}
+
+We give a brief outline of the proof here; the proof follows.
+\begin{proof}[Outline]
+It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
+Let $J$ be the set of indices that exists according to \defref{def:block guessable}.
+Define the distribution $C'$ as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.
+We first note that $C'$ has sufficient entropy, because $\Hav(C' |P) = \Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - |J^c|$ (the second step is by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).
+It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
+%Define the distribution $X$ as follows:
+%\[X_i =
+%\begin{cases}
+%W_i & C_i = 0\\
+%R_i & C_i = 1.
+%\end{cases}\]
+The outline for the rest of the proof is as follows:
+\begin{itemize}
+\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$.
+Since $P$ is a collection of obfuscated programs, there exists a simulator $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
+\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.
+That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
+\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
+\end{itemize}
+\end{proof}
+\subsection{Proof of \lemref{lem:security of cons}}
 \label{app:security of main cons}
@@
 
+\subsection{Correctness of \consref{cons:first construction}}
+We now argue correctness of \consref{cons:first construction}.
+We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
+%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.
+However, we start by justifying our use of unidirectional codes.
+\begin{lemma}
+\label{lem:no 1 to 0 flips}
+Let all variables be as in \thref{thm:main thm first cons}.
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
+\end{lemma}
+\begin{proof}
+Consider a coordinate $j$ for which $c_j=1$.
+Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$.
+The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
+\end{proof}
+
+Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
+Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
+\end{proof}
+
+\subsection{Discussion of \consref{cons:first construction}}
+\label{sec:discussion}
+\lnote{I did not check this calculation -- will do}
+To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
+\[
+\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
+\]
+
+We consider what entropy is necessary for security.
+The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
+This yields:
+\[
+\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
+\]
+When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
+
+\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
+
+If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
+
+%\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
+Do we need it?} There are three major drawbacks to \consref{cons:first construction}.
+First, we require blocks to be super-polynomial in size.
+Second, we only obtain a single bit from each block.
+Third, since each block is individually obfuscated, we leak information about individual blocks if they can be guessed.
+To compensate for this leakage, we need most\lnote{just some linear fraction, not most, right?
+and, in fact, isn't just one block enough given our repeated use argument which we haven't really made yet?} blocks to be unguessable given equality queries.
+Our second construction addresses this last weakness.
+
 \section{Proof of \lemref{lem:sampling works}}

### 2014-07-15 info-bounds/FuzzyExtPossibility.tex
editing

@@
 First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.
+Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.
 Thus, when $\kappa = \omega(\log n)$:
@@
 We begin by considering secure sketches.
-We a call distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
+We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
 Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
@@
 \end{tabular}
-\caption{Upper bounds on minimum number of bits that a fuzzy extractor can write down and still have recovery.}
+\caption{Upper bounds on minimum number of bits that a secure sketch can write down and still recovery with overwhelming probability.}
 \label{tab:upper bounds}
 \end{table}
-\subsection{Distribution Dependent Sketches}
+\subsection{Distribution-Dependent Sketches}
 Error-correction should be easy when all points of $W$ are far apart.
@@
 
-\subsection{Distribution Agnostic Sketches}
+\subsection{Distribution-Agnostic Sketches}
 Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
@@
 
+In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
+The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
+We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
+The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
+
 We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
-It is not known if it is necessary to decrease the entropy of the distribution $W$.
 
@@
 Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.
-Then the length of $\sketch$ is at least $\log |B_{t}|$.
+Then the average length of $\sketch$ is at least $\log |B_{t}|$.
 \end{lemma}
+\bnote{what do we mean by average here?
+we mean when receiving a uniform input across the coins.
+Maybe, there are distributions where it writes down a little.
+What's the right thing to say?
+Markov?}
 \begin{proof}
@@
 \noindent
-\textbf{Note:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
+\textbf{Notes:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
 The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).
@@
 
-\section{Flat spread distributions}
+The above lemma only talks about how many bits the algorithms must write down.  It does not say that the entropy of the distribution must decrease~(this is the important question).
+
+\section{Flat distributions}
 In the previous section we showed bounds on producing secure sketches and fuzzy extractors for well-spread distributions.
@@
 
-\subsection{Distribution Dependent Sketches}
+\subsection{Distribution-Dependent Sketches}
 
@@
 
-\bnote{need to extend this to a non-fixed number of bits and randomized.}
-\section{Dealing with non flat distributions}
+\section{Arbitary distributions}
 The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.
@@
 Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
-We first a natural method to leverage convex combinations that does not work\bnote{phrasing}.
-We then show a solution that comes within \bnote{something} of optimal by partitioning the probability space.
+We first consider a mechanism that tries to reduce the arbitrary case to the flat case by selecting a candidate flat distribution.
+Unfortunately, this mechanism does not work as a distribution with high fuzzy min-entropy can be formed as a convex combination of distributions with almost no fuzzy min-entropy~(\secref{sec:convex comb}).
+
+We then show a solution that comes within a super-logarithmic factor of optimal of optimal by partitioning the probability space~(\secref{sec:layered hash}).
 
 \subsection{Leveraging convex combinations?}
+\label{sec:convex comb}
 In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
-For example, consider the following extension to \consref{cons:pairwise hash}.
+For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.
 Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
-However, we show it is difficult to leverage convex combinations in the finite setting and handling the infinite case is more difficult.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
 
@@
 Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+
+\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
+However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
+That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
+
 In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
 
-\begin{figure}[h]
+\begin{figure}[t]
 
@@
 
-\bnote{remove pagebreak later}
-
 \subsection{Layered Hashing}
-As we saw in the previous section, dealing with non-flat distributions is difficult.
+\label{sec:layered hash}
+In the previous section, we saw that sketching non-flat distributions is difficult~(while retaining entropy close to the fuzzy min-entropy).
 The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.
@@
 Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.
-
-\pagebreak
+Naturally, revealing the probability of the original point leaks some information and there is a balance between how much about the probability is revealed to the adversary and how useful it is.
 
@@
 \end{theorem}
-\bnote{right now this is stated without epsilon.  I found the expression to be really gross with $\epsilon$ included.  Thoughts?  I know $\epsilon$ needs to be there because the construction uses it.}
+\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
 \begin{proof}
-We begin by arguing correctness.
-Fix some $w, w'$.
-If $\Pr[W=w]\le 2^{-n}\epsilon$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
-Now consider the case when $\Pr[W=w]> 2^{-n}\epsilon$, let $L_i^*$ be the level of $\Pr[W=w]$.
+\textbf{Correctness:}  We begin by arguing correctness.
+Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions but this is not necessary.}  Fix some $w, w'$.
+If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
+Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
 Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$.
@@
 
+\textbf{Aside:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.
+%We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
+An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.
+That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+Note there are $n-m+\ell$ outcomes for $i$ so the overall success of such an adversary is at most $n-m+\ell$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
+That is,
+\begin{align}
+\expe_{i | m\le i \le n+\ell}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+\ell}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
+&\le \left(n-m+\ell\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
+&= \left(n-m+\ell\right)\Hfuzz(W)\label{eq:link fuzz 3}
+\end{align}
+\textbf{Security:}
 We now argue security.
-First note that the total weight of points whose probability is less than $2^{-n}\epsilon$ is at most $\epsilon$~(there are at most $2^n$ points in the distribution).
-That is, $\sum_{w | \Pr[W=w]\le 2^{-n}\epsilon}\Pr[W = w] \le \epsilon$.
-Let $1_{\text{low prob}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
+First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).
+That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.
+Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
 Then
 \begin{align*}
-\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low prob}}=1] * 1 + \Pr[1_{\text{low prob}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)\\
--\log\left( \epsilon + (1-\epsilon)2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
+\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
+-\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
 \end{align*}
-We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
-An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.
-That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
-Note there are $n-k+\log 1/\epsilon$ outcomes for $i$ so the overall success of such an adversary is at most $n-k+\log 1/\epsilon$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
-That is,
-\begin{align}
-\expe_{i | k\le i \le n+\log 1/\epsilon}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | k\le i \le n+\log 1/\epsilon}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
-&\le \left(n-k+\log 1/\epsilon\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
-&= \left(n-k+\log 1/\epsilon\right)\Hfuzz(W)\label{eq:link fuzz 3}
-\end{align}
-For the remainder of the proof, we seek a bound on $\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\Pr[W=w | \sketch(W)]$.
+For the remainder of the proof, we seek a bound on 
+\[
+2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].
+\]
 We separate out this quantity into levels:
 \begin{align*}
-\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
-&\le \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
-&\le\frac{ \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
-%&=\delta \sum_{i | k\le i \le n+\log 1/\epsilon} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
+\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
+&= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
+&\le \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
+&\le \expe_{i | m\le i \le n+\ell} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
+&\le\frac{ \expe_{i | m\le i \le n+\ell} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
+%&=\delta \sum_{i | m\le i \le n+\ell} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
 %\end{align*}
@@
 %\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
-&= \frac{(n-k+\log 1/\epsilon) 2^{-\Hfuzz(W)}}{2\delta}.
+&= \frac{(n-m+\ell) 2^{-\Hfuzz(W)}}{2\delta}.
 \end{align*}
@@
 \begin{align*}
-\Hav(W | \sketch(W)) = -\log \left(\epsilon+\frac{(1-\epsilon)(n-k+\log1/\epsilon)2^{-\Hfuzz(W)}}{2\delta}\right).
+\Hav(W | \sketch(W)) = -\log \left(2^{-\ell}+\frac{(1-2^{-\ell})(n-m+\ell)2^{-\Hfuzz(W)}}{2\delta}\right).
 \end{align*}
-Setting $\epsilon = 2^{-k}$ yields
+Setting $\ell = m$ yields
 \begin{align*}
-\Hav(W | \sketch(W)) &= -\log \left(k+\frac{(1-2^{-k})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
-&\ge -\log \min\{k, \frac{(1-2^{-k}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
-&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-k}) - 2\\
+\Hav(W | \sketch(W)) &= -\log \left(m+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
+&\ge -\log \min\{m, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
+&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
 &\ge \Hfuzz(W) - \log n + \log \delta - 3\\
 \end{align*}
-Where the third line follows from the third because $\Hfuzz(W)\le \Hoo(W) = k$.\bnote{what condition do we need to get rid of $\log (1-2^{-k})$?}
+Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$.
+The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the whole quantity is negative~(and entropy is non-negative).
 \end{proof}

### 2014-07-18 info-bounds/FuzzyExtPossibility.tex
adding work on distribution agnostic sketches

@@
 We attempt to bridge this gap in this work.
-
-\section{Well-spread distributions}
-In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.
-We begin by considering secure sketches.
-We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
-Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
-Intuitively, no sketch should be necessary for such a distribution.
-However, we show there is a large gap between a secure sketch that works for a particular well-spread distribution and a secure sketch that works for \emph{all} well-spread distributions.
+The summary of our results is in Table~\ref{tab:upper bounds}.
 
@@
 \begin{tabular}{l | l | c}
-Upper bound & Depends on Distribution & Works for all Dist\\
+Lower bounds & Distribution-Dependent & Distribution-Agnostic\\
 \hline
-Well-spread distribution & $0$ & $\log |B_t|$\\
-Flat distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta)$ &$\log |B_t|$\\
-Arbitrary distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta) + \log \log \mathcal{M}$ & $\log |B_t|$
+Well-spread distribution & $\Hfuzz(W)$ & $\log |B_t|$\\
+Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
+Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
 \end{tabular}
-\caption{Upper bounds on minimum number of bits that a secure sketch can write down and still recovery with overwhelming probability.}
+\caption{Residual entropy of secure sketches for complete recovery.}
 \label{tab:upper bounds}
 \end{table}
-\subsection{Distribution-Dependent Sketches}
+\bnote{Fix right side of table}
+We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
+We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
+
+\section{Distribution-Dependent Sketches}
+In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.
+We begin by considering secure sketches.
+We consider the setting where the algorithms have a complete description of the distribution $W$.
+In the next setting we consider the setting where the construction must work for a family of distributions~(we show there is a large gap between these two settings).
+
+\subsection{Well-Spread Distributions}
+We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
+Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
 Error-correction should be easy when all points of $W$ are far apart.
@@
 
-\subsection{Distribution-Agnostic Sketches}
-Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
-However, as we show below the above construction does not extend to the setting of all well-spread distributions.
-In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
-In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
-In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
-
-In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
-The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
-We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
-The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
-
-We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
-
-\begin{lemma}
-Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.
-Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.
-Then the average length of $\sketch$ is at least $\log |B_{t}|$.
-\end{lemma}
-\bnote{what do we mean by average here?
-we mean when receiving a uniform input across the coins.
-Maybe, there are distributions where it writes down a little.
-What's the right thing to say?
-Markov?}
-\begin{proof}
-Let $\mathcal{M}$ be a metric space.
-Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
-Consider the following experiment:
-\[
-W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
-\]
-That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
-Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
-Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.
-Now consider the following experiment
-\[
-v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
-\]
-Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.
-Then $X\overset{d}= Y$.
-That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.
-Thus, $\Pr[v^* = v] = 1$.
-For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
-For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
-Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.
-This completes the proof.
-\end{proof}
-\noindent
-\textbf{Notes:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
-The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).
-
-Furthermore, the above lemma easily extends to the setting where the distributions are not well-spread as long as there is an adversary strategy of choosing the input distribution that produces an input to sketch that is identically distributed to the uniform distribution.
-
-The above lemma only talks about how many bits the algorithms must write down.  It does not say that the entropy of the distribution must decrease~(this is the important question).
-
-\section{Flat distributions}
-In the previous section we showed bounds on producing secure sketches and fuzzy extractors for well-spread distributions.
-In this section we further investigate secure sketches where the sketch depends on the input distribution.\footnote{Recall the bound when the sketch does not know the input distribution is $\log |B_t|$ bits and this is constructible for any distribution.}
-
-\subsection{Distribution-Dependent Sketches}
-
-\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
+\subsection{Flat distributions}
+In the previous section we showed that info-theoretically it is easy to produce a secure sketch and fuzzy extractor for a well-spread distribution when the algorithms are allowed to encode the input distribution $W$.
+%\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
 secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.
@@
 
-Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme~(\defref{def:fuzzy min-ent}).
+Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme (\defref{def:fuzzy min-ent}).
 Fuzzy min-entropy is total weight of the maximum probability ball.
@@
 
-\section{Arbitary distributions}
+\subsection{Arbitary distributions}
 The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.
@@
 
-\subsection{Leveraging convex combinations?}
+\subsubsection{Leveraging convex combinations?}
 \label{sec:convex comb}
@@
 
-\subsection{Layered Hashing}
+\subsubsection{Layered Hashing}
 \label{sec:layered hash}
@@
 
+\section{Distribution-Agnostic Sketches}
+Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
+However, as we show below the above construction does not extend to the setting of all well-spread distributions.
+In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
+In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
+In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
+
+In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
+The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
+We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
+The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
+
+We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
+
+\begin{lemma}
+Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.
+Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.
+Then the average length of $\sketch$ is at least $\log |B_{t}|$.
+\end{lemma}
+\bnote{what do we mean by average here?
+we mean when receiving a uniform input across the coins.
+Maybe, there are distributions where it writes down a little.
+What's the right thing to say?
+Markov?}
+\begin{proof}
+Let $\mathcal{M}$ be a metric space.
+Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
+Consider the following experiment:
+\[
+W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
+\]
+That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
+Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
+Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.
+Now consider the following experiment
+\[
+v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
+\]
+Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.
+Then $X\overset{d}= Y$.
+That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.
+Thus, $\Pr[v^* = v] = 1$.
+For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
+For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
+Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.
+This completes the proof.
+\end{proof}
+\noindent
+\textbf{Notes:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
+The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).
+
+Furthermore, the above lemma easily extends to the setting where the distributions are not well-spread as long as there is an adversary strategy of choosing the input distribution that produces an input to sketch that is identically distributed to the uniform distribution.
+
+The above lemma only talks about how many bits the algorithms must write down.
+It does not say that the entropy of the distribution must decrease~(this is the important question).
+We now proceed to this question.
+
+\subsection{Min-Max to switch quantifiers}
+
+\subsection{Impossibility of info-theoretic sketches for distribution}
+\begin{lemma}
+There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
+\end{lemma}
+
+\begin{corollary}
+This is also impossible for computational sketches that retain hill entropy.
+\end{corollary}
+
+\subsection{Conductors}
+Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
+\begin{lemma}
+Not possible for information-theoretic objects.
+\end{lemma}
 \bibliographystyle{alpha}

### 2014-08-06 info-bounds/FuzzyExtPossibility.tex
revising intro and adding distribution aware notation

@@
 Ideally, key derivation should be possible whenever a negligible portion of $W$ lies within a ball~(arbitrarily centered) of radius $t$.
-We call the maximum overall weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.
-However, current techniques for constructing fuzzy extractors lie far from this necessary condition.
-We investigate whether this is necessary for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).
+We call the maximum weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.
+In interactive information-reconciliation, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+Current techniques for constructing fuzzy extractors lie far from this necessary condition.
+We investigate whether this is inherent for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).
 Our results are centered on feasibility and our constructions and impossibility results are primarily information-theoretic.
+We consider two types of fuzzy extractors and secure sketches.
+The first we call \emph{distribution-aware}, the algorithms know the precise distribution they are trying to correct.
+The second is \emph{distribution-oblivious} where $(\gen, \rep)$ must work for a family of distributions.
+
+\textbf{Distribution-Aware} In the distribution-aware setting we show that whenever the fuzzy min-entropy is super-logarithmic, there exists a secure sketch and fuzzy extractor with super-logarithmic output entropy.
+That is, fuzzy min-entropy is both a necessary and \emph{sufficient} condition for security in this setting.
+
+\textbf{Distribution-Oblivious} The distribution-oblivious situation is more complicated.
+Indeed, there is a significant difference between secure sketches and fuzzy extractors.
+We show that there exist families of distributions where each distribution has fuzzy min-entropy such that any secure sketch is insecure.
+However, it is possible to build a fuzzy extractor for these same family of distributions.
 \end{abstract}
@@
 The computational versions of these objects are defined in~\cite{krawczyk2010cryptographic} and~\cite{fuller2013computational} respectively.
-Fuller et al.~\cite{fuller2013computational} show that computational secure sketches cannot improve significantly on information-theoretic secure sketches.
+Fuller et al.~\cite{fuller2013computational} show that computational secure sketches are unlikely to improve significantly on information-theoretic secure sketches.
 
@@
 For a fuzzy extractor to be secure this must occur with negligible probability.
-That is, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
+That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
+Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
 We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-Clearly, the fuzzy min-entropy of a distribution must be super-logarithmic for any security.
-Indeed, in the interactive setting this is a sufficient condition as well.
+The fuzzy min-entropy of a distribution must be super-logarithmic for any reasonable of either a fuzzy extractor~(\lemref{lem:fuzz necessary}).
 
-However, in the one-round setting we are far from achieving security for all distributions with super-logarithmic fuzzy min-entropy.
+In the more general interactive setting where two parties hold $w$ and $w'$ and wish to agree on a common key, fuzzy min-entropy is both a necessary and sufficient condition~(using two-party computation).
+However, in the one-message setting we are far from achieving security whenever fuzzy min-entropy is high.
+
 Traditional fuzzy extractors and secure sketches incur at entropy loss of the size of the ball to be error-corrected.
-While, this is optimal for the uniform distribution, it seems far from optimal for distributions where points are far apart.
-Indeed, when the goal is provide key derivation from a source that has more errors than entropy, this bound provides no guarantee on the strength of the key.
-The work of Canetti et al.~\cite{canetti2014key} shows it is possible to provide key derivation for some distributions of this type.
-However, their work leaves the question open for a large number of distributions.
-In this work, we attempt to settle this question: for what distributions is noisy key derivation possible and impossible?
-\bnote{come back to this}
+While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
+As an example, many examples that arise in practice there are more error patterns than starting entropy.
+Traditional fuzzy extractors provide no guarantee for sources of this type.
+The work of Canetti et al.~\cite{canetti2014key} shows it is possible to provide build fuzzy extractors for some distributions with this property.
+Their work leaves the question open for a large number of distributions.
+This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}
 
-\textbf{Our results:} In this work we show awesome things!\bnote{write}
+When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
+However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
+This uncertainty is usually expressed by proving the fuzzy extractor works for a class of distributions with some known property~(such as entropy and error levels).
+In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
+We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
 
+\textbf{Our Contributions} We show that for every distribution with super-logarithmic fuzzy min-entropy it is information-theoretically possible to build a secure sketch that retains super-logarithmic min-entropy.
+Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.
+(A key with super-logarithmic entropy can be expanded to arbitrary length using computational techniques.)  For distribution-aware secure sketches and fuzzy extractors, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+The situation is significantly more complicated for distribution-oblivious algorithms.
+Indeed, we show that there natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.
+However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.
+
+\textbf{Note:} Our constructions are information-theoretic and do not run in polynomial time.
+They should primarily be regarded as feasibility results.
+Our negative results apply to algorithms even given arbitrary running time, thus there is clear separation for unbounded running time algorithms.
+It remains as an open question whether our distribution-aware results can be replicated by efficient algorithms.
+This seems unlikely as most  interesting distributions have exponential size description.
+The power of the distribution-aware setting is that the algorithms can access this description.
+It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
+
+\textbf{Open Problems:} We showed that in the distribution-oblivious setting there is a separation between a secure sketch and a fuzzy extractor.
+However, it is still not known if fuzzy extractors can be constructed for any family of distributions.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c }
+& Distribution-Aware & Distribution-Oblivious\\
+\hline
+Secure Sketch & Yes~(\thref{cons:leveling}) & No\\
+\hline
+Fuzzy Extractor & Yes~(\thref{cons:leveling}) & Yes for some families\\
+& & Unknown for arbitrary family
+%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
+%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
+\end{tabular}
+\end{center}
+\caption{Is fuzzy min-entropy sufficient for extraction?}
+\label{tab:main results}
+\end{table}
+
+\bnote{connection to obfuscation}
 \section{Preliminaries}
@@
 
-Replacing the statistical distance in \defref{def:fuzzy extractor} with a computational distance results in a computational fuzzy extractor~\cite[Definition 2.5]{fuller2013computational}.
-
-Secure sketches are the main technical tool in the construction of fuzzy extractors.
+Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distance results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.
+A fuzzy extractor performs two tasks, producing a uniform key and providing error-tolerance.
+Traditional, the uniform key is produced by extraction from the original secret $w$ and the error-tolerance is obtained by using a secure sketch.
 Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
@@
 \textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
-Also we do not consider a computational version of secure sketches as Fuller et al.
+We do not consider a computational version of secure sketches.
+Fuller et al.
 showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
@@
 \label{sec:minimal conditions}
-We now define fuzzy min-entropy and show that fuzzy extractor security is only possible when the fuzzy min-entropy is super-logarithmic.
+Consider the functionality of a fuzzy extractor, the reproduce algorithm produces the same key when provided with a nearby input point.
+In an ideal world, this would be all that is revealed by the reproduce algorithm.
+For the remainder of this work, we compare security with this ideal world.
+This ideal world can be expressed by an adversary providing a ``guess'' point to the algorithm~(and hoping that their guess was closed to the stored point).
+We call the level of security in this setting, fuzzy min-entropy.
+%\todo{doesn't 2PC require assumptions?}
+%We now define fuzzy min-entropy and show that fuzzy extractor security is only possible when the fuzzy min-entropy is super-logarithmic.
 
-A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
+%A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
 This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
@@
 \end{definition}
+
+If an adversary can always obtain the output of a fuzzy extractor by running the reproduce adversary, then there is no hope for security~(independent of the implementation of the fuzzy extractor).
+We make this intuition formal in the following result.
 For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
@@
 Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
+This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
 Consider the following distinguisher $D$:
 \begin{itemize}
-\item On input $r, p$.
-\item If $\rep(m, p) = r$, output $1$.
+\item Input $r, p$.
+\item If $\rep(m^*, p) = r$, output $1$.
 \item Else output $0$.
@@
 This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-In the interactive setting, fuzzy min-entropy is also a sufficient condition using secure two-party computation\bnote{cite something for this}.
-However, in the non-interactive setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.
+As stated above, fuzzy min-entropy is also a sufficient condition for security in the interactive setting.
+However, in the fuzzy extractor~(non-interactive) setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.
 We attempt to bridge this gap in this work.
-The summary of our results is in Table~\ref{tab:upper bounds}.
+
+Before turning to our results we separate between two types of fuzzy extractors and secure sketches.
+The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.
+We call this type of algorithm distribution-oblivious.
+We define a new type of algorithm that called distribution-aware that is allowed to know the precise distribution to be supported.
+We provide a definition for secure sketches~(this definition can easily be extended to fuzzy extractors)
+
+\begin{definition}
+Let $W$ denote a distribution.  A secure sketch, $(\sketch_W, \rec_W)$ is called \emph{distribution-aware} if the correctness and security properties hold for the distribution $W$.  That is, 
+\begin{enumerate}
+\item \emph{Correctness} For all $w\in W$ and for all $w'\in\mathcal{M}$,  if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
+\item \emph{Security} $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+\end{definition}
+Note that correctness is only required to hold for points in the support of the distribution $W$, the algorithms are allowed the description of $W$ and security need only hold for the distribution $W$.
+When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to make use of the (possibly)~exponential size distributions.
+It is not clear how to meaningfully define efficient distribution aware algorithms.
+If the algorithms were required to be efficient, they could only encode a negligible portion of the probability space of $W$, and would have to ``work'' on all distributions $W'$ with the same probability mass function on the encoded space.
+This would make the algorithms a distribution-oblivious fuzzy extractor for all distributions with this property.
+
+We begin with by showing that secure sketches and fuzzy extractors are possible in the distribution aware setting whenever there is super-logarithmic fuzzy min-entropy.
+We then turn to the standard \emph{distribution oblivious} setting.
+
+%The summary of our results is in Table~\ref{tab:upper bounds}.
 
@@
 \begin{tabular}{l | l | c}
-Lower bounds & Distribution-Dependent & Distribution-Agnostic\\
+Lower bounds & Distribution-Dependent & Distribution-Oblivious\\
 \hline
@@
 \bnote{Fix right side of table}
-We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
+\bnote{the table should move.}
+%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
 We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
@@
 \section{Distribution-Dependent Sketches}
-In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.
-We begin by considering secure sketches.
-We consider the setting where the algorithms have a complete description of the distribution $W$.
-In the next setting we consider the setting where the construction must work for a family of distributions~(we show there is a large gap between these two settings).
+In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
+We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.
+We construct secure sketches but all constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.
+In the next section \bnote{what section?} we consider distribution-oblivious algorithms.
 
@@
 Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
-Error-correction should be easy when all points of $W$ are far apart.
-Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.
-Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).
+Error-correction is ``easy'' when all points of $W$ are far apart.
+Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.
+%Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).
 However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.
@@
 Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
-Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.
+Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result can be viewed as saying that well-spread distributions are not interesting in the distribution-aware setting.
+However, we will show that providing secure sketches for well-spread distributions in the distribution-oblivious setting is impossible.}
 
@@
 
+\bnote{stopped here}
 \subsection{Flat distributions}
@@
 \begin{theorem}
+\label{thm:layered hashing}
 Let $\delta>0$ be an function of $n$.

### 2014-08-11 info-bounds/FuzzyExtPossibility.tex
adding min max and starting on hardness of dist agnostic sketching

@@
 
+\newcommand{\Succ}{\mathsf{Succ}}
+\newcommand{\Adv}{\mathbf{Adv}}
+ \newcommand{\Exp}{\mathbf{Exp}}
+
 \title{When are Fuzzy Extractors Possible?}
+\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory.
+Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.
+Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University.
+Work done in part while the author was at Boston University and Harvard University.
+Email: {\tt asmith@psu.edu}.
+}}
 
@@
 \label{sec:preliminaries}
+\bnote{be careful with overloading of $\ell$, both key length and number of levels.}
 For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.
@@
 \[
-\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
+\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
 \]
@@
 If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item \emph{Security} $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+Note correctness is guaranteed only for the support of $W$.
+\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
@@
 Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
-Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
+Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$ & $\log |B_t|$
 \end{tabular}
@@
 We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.
-We construct secure sketches but all constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.
-In the next section \bnote{what section?} we consider distribution-oblivious algorithms.
+We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.
+In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.
 
@@
 
-\bnote{stopped here}
 \subsection{Flat distributions}
-In the previous section we showed that info-theoretically it is easy to produce a secure sketch and fuzzy extractor for a well-spread distribution when the algorithms are allowed to encode the input distribution $W$.
+In the previous section we showed it is easy to produce secure sketch for well-spread distributions in the distribution aware setting.
 %\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
 secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.
-In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.  
-We begin by considering flat distributions where the probability of each point in $W$ is the same.
+In this section, we consider distributions with multiple points in each ball where points have the same probability.
 
@@
 
-Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme (\defref{def:fuzzy min-ent}).
-Fuzzy min-entropy is total weight of the maximum probability ball.
-For flat distribution, this is directly correlated to the ball with the largest number of points.
-That is, for a flat distribution
+Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.
+Fuzzy min-entropy is total weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).
+For flat distributions, this is proportional to the largest number of points in any ball.
+More precisely,
 \begin{align*}
-\Hfuzz(W) &= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} * \Pr[W=w]\\
-&= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} *2^{-\Hoo(W)}\\
-&=\Hoo(W) -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} 
+\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
+&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
+&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
 \end{align*}
@@
 %\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
-We now present an information-theoretic construction for flat distributions.  We first introduce the notion of a pairwise-independent hash:
+We now present a construction for flat distributions.  We use pairwise-independent hashes:
 
@@
 We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.
+The work of Skoric et al.~\cite{skoric2009efficient} use universal hash functions in the setting where there are a polynomial number of possible error patterns.
 
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} = \frac{|B_{t, max}|-1}{|R|}
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
 \end{align*}
-Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|$.
+Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.
 This completes the proof.
@@
 For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
+Furthermore, whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ depending on $\Hfuzz(W)$).
+That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.
 Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.
@@
 We will see this becomes more difficult as we move to the setting where points have very different probability.
-In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls.
+%In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls.
 We will compensate for this problem by writing down a variable number of bits.
@@
 Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
-We first consider a mechanism that tries to reduce the arbitrary case to the flat case by selecting a candidate flat distribution.
-Unfortunately, this mechanism does not work as a distribution with high fuzzy min-entropy can be formed as a convex combination of distributions with almost no fuzzy min-entropy~(\secref{sec:convex comb}).
-
-We then show a solution that comes within a super-logarithmic factor of optimal of optimal by partitioning the probability space~(\secref{sec:layered hash}).
-
-\subsubsection{Leveraging convex combinations?}
-\label{sec:convex comb}
-In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
-For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.
-Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
-However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
-
-The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
-Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
-
-In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
-That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
-However, in the setting where $W$ is a convex combination of flat sources this does not hold.
-
-Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
-This distribution is illustrated in \figref{fig:convex comb}.
-
-The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
-Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
-(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
-
-Consider an input point $w\in W$.
-One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
-For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
-This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
-This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
-Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
-
-\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
-However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
-That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
-
-In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
-
-\begin{figure}[t]
-
-\centering
-    \includegraphics[width=.9\textwidth]{convexCombExample.png}
-    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
-\label{fig:convex comb}    
-\end{figure}
-
-\subsubsection{Layered Hashing}
-\label{sec:layered hash}
-In the previous section, we saw that sketching non-flat distributions is difficult~(while retaining entropy close to the fuzzy min-entropy).
-The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.
-We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.
-Then the hash is applied only considering the maximum weight of the ball containing points at this level.
-Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.
-Naturally, revealing the probability of the original point leaks some information and there is a balance between how much about the probability is revealed to the adversary and how useful it is.
+Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.
+In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
+The main issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
+
+As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
+We address this by describing the probability of the point $w_0\in W$ seen in sketch.
+Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.
+We can think of this construction as dividing the distribution $W$ into probability levels, and each component level is nearly flat.
+As long as levels are large enough, they do not reveal too much information about the stored point $W$.
+Naturally, there is a tradeoff between the number of levels and how useful the level information is to both the \rep algorithm and the adversary.
 
@@
 
-Before describing the bounds obtained by \consref{cons:leveling} we will extend our notation for the maximum likelihood ball to the leveled case.
+\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.
 Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.
@@
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.
 Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
@@
 \textbf{Correctness:}  We begin by arguing correctness.
-Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions but this is not necessary.}  Fix some $w, w'$.
-If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
+Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.
+The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.
+If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.
 Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
 \end{align*}
-Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
-
-\textbf{Aside:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.
+Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
+
+\textbf{Ideal Adversary with access to Level Information:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.
 %We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
@@
 Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$.
-The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the whole quantity is negative~(and entropy is non-negative).
+The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the bound is negative.
 \end{proof}
 
-\section{Distribution-Agnostic Sketches}
-Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
+\begin{corollary}
+Let $n$ be a security parameter and let $\mathcal{M} =\zo^n$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ residual min-entropy and overwhelming correctness.
+Furthermore, there exists a $(\mathcal{M}, \Hoo(W), \ell = \omega(\log n), \epsilon)$ distribution aware fuzzy extractor with $\epsilon = \ngl(n)$) and overwhelming correctness.
+\end{corollary}
+\section{Distribution-Oblivious Sketches}
+\label{sec:dist oblivious}
+
+In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.
+This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.
+In this section we ask if the results can be replicated for a family of distributions.
+Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.
+The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).
+Unfortunately, we show for secure sketches this is not the case.
+That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.
+
+\subsection{A definitional equivalence}
+Before proceeding to our result, we consider the definition of a fuzzy extractor.
+The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
+This can be thought of as a two stage process: 1) the system designer specifies $(\sketch, \rec)$, 2) the adversary specifies a particular member $W\in \mathcal{V}$.
+We will say the system designer wins if the adversary can guess the element in $W$ with low probability, and the adversary wins if the can recover $w\in W$ with noticeable probability.
+That is, we can formulate this process as a standard cryptographic game.
+Let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
+We will formulate this as a two player game.
+
+\begin{center}
+\begin{minipage}{1in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
+$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
+If $W\not\in \mathcal{V}$ return $0$.\\
+If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
+\end{tabbing} \end{minipage} 
+\end{center}
+
+%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
+In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
+
+\begin{center}
+\begin{minipage}{1in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
+$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
+$W \leftarrow \mathcal{W}$\\
+If $W\not\in \mathcal{V}$ return $0$.\\
+If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
+\end{tabbing} \end{minipage} 
+\end{center}
+
+Note the only different between these two games is which player announce their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
+In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
+These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.
+
+\begin{lemma}
+If a fuzzy extractor is secure for all $W\in\mathcal{V}$, then it is secure for all distributions $\mathcal{W}$ over the family $\mathcal{V}$.
+\end{lemma}
+
+Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
+Importantly, the adversary is sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
+We can think of the description of $W$ as side-information or leakage to the adversary.
+The system designer, however never sees the particular outcome $W$.
+This asymmetry will form the basis of our negative results in the next subsection.
+%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
 However, as we show below the above construction does not extend to the setting of all well-spread distributions.
@@
 
-In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
+%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
 The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
@@
 
-We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
-
+%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
+
+\subsection{Impossibility of info-theoretic sketches}
+In the previous section we showed a fuzzy extractor that works for a family of sources must also work for an arbitrary distribution over those sources.
+In addition, the adversary learns the particular source that is being sketched while the system designer does not.
+To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's side information as $Z$.
+Let $\mathbb{F}$ be some field of size $q$.
+Consider the following distributions of the following type $W = w_1,..., w_\ell$ where $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$.
+This type of distribution is a line in space $\mathbb{F}^\ell$.
+Consider $V$ as the uniform distribution over all such $W$.
+Then $V$ is the uniform distribution over $\mathbb{F}^\ell$.
+
+Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
+\begin{lemma}
+There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
+\end{lemma}
+\begin{proof}
+Need to show several things.  
+\begin{itemize}
+\item Each component of the distribution has fuzzy min-entropy.
+\item Any sketch must leak some information about $V$.
+\item The side information can be thought of as a hash function.
+Furthermore, it is independent of the sketch.
+Thus, the sketch and hash are independent information.
+Thus, conditioned on both there is almost no entropy.
+\end{itemize}
+\end{proof}
+
+\bnote{stopped here}
+\begin{lemma}
+There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
+\end{lemma}
+
+\begin{corollary}
+This is also impossible for computational sketches that retain hill entropy.
+\end{corollary}
+
+\subsection{Conductors}
+Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
+\begin{lemma}
+Not possible for information-theoretic objects.
+\end{lemma}
+\bibliographystyle{alpha}
+\bibliography{crypto}
+
+\appendix
+\section{Block Unguessable Distributions}
+\begin{definition}~\cite[Definition 4.2]{canetti2014key}
+\label{def:block guessable}
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
+\begin{cases}
+1 & w_j = w_j'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+\[
+\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+\section{Leveraging convex combinations?}
+\label{sec:convex comb}
+In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+
+The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
+Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
+
+In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
+That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+However, in the setting where $W$ is a convex combination of flat sources this does not hold.
+
+Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+This distribution is illustrated in \figref{fig:convex comb}.
+
+The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
+(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+
+Consider an input point $w\in W$.
+One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
+For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
+This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
+Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+
+\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
+However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
+That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
+
+In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
+
+\begin{figure}[t]
+
+\centering
+    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+\label{fig:convex comb}    
+\end{figure}
+
+\section{Old Proofs}
+\subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
+We begin by trying to remove the restriction that every point in the metric space has a fixed number of neighbors in a distribution.
+We start with sketches that write down a fixed number of bits~(independent of their input $w$).
+We will show a lower bound on the number of bits that a $\sketch$ algorithm must write down.
+We assume that all coins of $\sketch$ are provided to $\rec$ and that $\rec$ is deterministic~(any coins needed for $\rec$ can be flipped by $\sketch$ in this model).
+
+\begin{lemma}
+Let $W$ be a flat distribution and let $(\sketch, \rec)$ be a secure sketch for $W$.
+Let $W$ be a $(c, t)$-bounded neighbor distribution.
+Let $S_{coin}$ be the number of sketches that can be produced by any fixing of $coin$.
+Then the error $\delta$ of $(\sketch, \rec)$ is at least $\frac{\expe_{coins}L(coins)}{c}$.
+\end{lemma}
+\begin{proof}
+We consider a fixed $w'$ that has $c$ neighbors in the distribution.
+We assume $\rec$ has access to all coins of $\sketch$.
+Furthermore, we assume that $\rec$ is deterministic and that any coins necessary are provided by $\sketch$).
+
+Denote by $S_{coin, R}$ the set of possible sketches for a given set of coins on all values in $R$.
+Furthermore, denote by $S_{coin}$ the set of possible sketches for all values $w$~(for a given value of coin) and note that $S_{coin, R} \subset S_{coin}$.
+Then $\rec(\cdot, w', coin)$ must fail to recover $|R|-|S_{coin, R}|$ fraction of $w\in R$~(recalling that $\rec$ is deterministic for this fixing of $coin$).
+This means that the total number of pairs $(w, coin)$ for which $\rec$ fails to recover is $2^{|coins|}R - \sum_{coins} |S_{coin, R}|$.
+
+This means there must exist some $w$ such that the number of $coin$ values for which $\rec$ fails to recover is 
+\[
+2^{|coin|} - \frac{\sum_{coin} |S_{coin, R}|}{R}.
+\]
+ This means that for this $w$, 
+\[
+\Pr_{coin}[s \leftarrow \sketch(w, coin) \wedge w = \rec(s, w', coin)] < 1- \frac{\expe |S_{coin, R}|}{|R|} = 1-\frac{\expe |S_{coin, R}|}{c} \le 1-\frac{\expe |S_{coin}| }{c}.
+\]
+
+%Consider the function $\rec(w', ss, r)$ where $ss$ is the sketch produced by $\sketch(w)$ and $r$ are the coins used by $\sketch$.  
+\end{proof}
+
+For deterministic sketches:
+\[
+\Hav(W|S ) = -\log \left(\sum_{s\in S} \Pr[S = s] \frac{2^{-\Hoo(W)}}{\Pr[S=s]}\right) = -\log \left(2^{-\Hoo(W)} |S| \right)  = \Hoo(W) - H_0(S).
+\]
+
+\subsection{How many bits for distribution oblivious sketch} 
 \begin{lemma}
@@
 
-\subsection{Min-Max to switch quantifiers}
-
-\subsection{Impossibility of info-theoretic sketches for distribution}
-\begin{lemma}
-There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
-\end{lemma}
-
-\begin{corollary}
-This is also impossible for computational sketches that retain hill entropy.
-\end{corollary}
-
-\subsection{Conductors}
-Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
-\begin{lemma}
-Not possible for information-theoretic objects.
-\end{lemma}
-\bibliographystyle{alpha}
-\bibliography{crypto}
-
-\appendix
-\section{Old Proofs}
-\subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
-We begin by trying to remove the restriction that every point in the metric space has a fixed number of neighbors in a distribution.
-We start with sketches that write down a fixed number of bits~(independent of their input $w$).
-We will show a lower bound on the number of bits that a $\sketch$ algorithm must write down.
-We assume that all coins of $\sketch$ are provided to $\rec$ and that $\rec$ is deterministic~(any coins needed for $\rec$ can be flipped by $\sketch$ in this model).
-
-\begin{lemma}
-Let $W$ be a flat distribution and let $(\sketch, \rec)$ be a secure sketch for $W$.
-Let $W$ be a $(c, t)$-bounded neighbor distribution.
-Let $S_{coin}$ be the number of sketches that can be produced by any fixing of $coin$.
-Then the error $\delta$ of $(\sketch, \rec)$ is at least $\frac{\expe_{coins}L(coins)}{c}$.
-\end{lemma}
-\begin{proof}
-We consider a fixed $w'$ that has $c$ neighbors in the distribution.
-We assume $\rec$ has access to all coins of $\sketch$.
-Furthermore, we assume that $\rec$ is deterministic and that any coins necessary are provided by $\sketch$).
-
-Denote by $S_{coin, R}$ the set of possible sketches for a given set of coins on all values in $R$.
-Furthermore, denote by $S_{coin}$ the set of possible sketches for all values $w$~(for a given value of coin) and note that $S_{coin, R} \subset S_{coin}$.
-Then $\rec(\cdot, w', coin)$ must fail to recover $|R|-|S_{coin, R}|$ fraction of $w\in R$~(recalling that $\rec$ is deterministic for this fixing of $coin$).
-This means that the total number of pairs $(w, coin)$ for which $\rec$ fails to recover is $2^{|coins|}R - \sum_{coins} |S_{coin, R}|$.
-
-This means there must exist some $w$ such that the number of $coin$ values for which $\rec$ fails to recover is 
-\[
-2^{|coin|} - \frac{\sum_{coin} |S_{coin, R}|}{R}.
-\]
- This means that for this $w$, 
-\[
-\Pr_{coin}[s \leftarrow \sketch(w, coin) \wedge w = \rec(s, w', coin)] < 1- \frac{\expe |S_{coin, R}|}{|R|} = 1-\frac{\expe |S_{coin, R}|}{c} \le 1-\frac{\expe |S_{coin}| }{c}.
-\]
-
-%Consider the function $\rec(w', ss, r)$ where $ss$ is the sketch produced by $\sketch(w)$ and $r$ are the coins used by $\sketch$.  
-\end{proof}
-
-For deterministic sketches:
-\[
-\Hav(W|S ) = -\log \left(\sum_{s\in S} \Pr[S = s] \frac{2^{-\Hoo(W)}}{\Pr[S=s]}\right) = -\log \left(2^{-\Hoo(W)} |S| \right)  = \Hoo(W) - H_0(S).
-\]
-
 \section{Examples to Consider}

### 2014-08-15 trunk/info-bounds/FuzzyExtPossibility.tex
adding names and affliations

@@
 
+\newcommand{\Succ}{\mathsf{Succ}}
+\newcommand{\Adv}{\mathbf{Adv}}
+ \newcommand{\Exp}{\mathbf{Exp}}
+
 \title{When are Fuzzy Extractors Possible?}
+\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
+work was sponsored by the Department of the Air Force under Air Force
+Contract
+\#FA8721-05-C-0002.  Opinions,
+interpretations, conclusions and recommendations are those of the author
+and
+are not necessarily endorsed by the United States Government.
+Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.
+Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University.
+Work done in part while the author was at Boston University and Harvard University.
+Email: {\tt asmith@psu.edu}.
+}}
 
@@
 For a fuzzy extractor to be secure this must occur with negligible probability.
-That is, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
+That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
+Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
 We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-Clearly, the fuzzy min-entropy of a distribution must be super-logarithmic for any security.
-Indeed, in the interactive setting this is a sufficient condition as well.
+The fuzzy min-entropy of a distribution must be super-logarithmic for any reasonable of either a fuzzy extractor~(\lemref{lem:fuzz necessary}).
 
-However, in the one-round setting we are far from achieving security for all distributions with super-logarithmic fuzzy min-entropy.
+In the more general interactive setting where two parties hold $w$ and $w'$ and wish to agree on a common key, fuzzy min-entropy is both a necessary and sufficient condition~(using two-party computation).
+However, in the one-message setting we are far from achieving security whenever fuzzy min-entropy is high.
+
 Traditional fuzzy extractors and secure sketches incur at entropy loss of the size of the ball to be error-corrected.
-While, this is optimal for the uniform distribution, it seems far from optimal for distributions where points are far apart.
-Indeed, when the goal is provide key derivation from a source that has more errors than entropy, this bound provides no guarantee on the strength of the key.
-The work of Canetti et al.~\cite{canetti2014key} shows it is possible to provide key derivation for some distributions of this type.
-However, their work leaves the question open for a large number of distributions.
-In this work, we attempt to settle this question: for what distributions is noisy key derivation possible and impossible?
-\bnote{come back to this}
+While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
+As an example, many examples that arise in practice there are more error patterns than starting entropy.
+Traditional fuzzy extractors provide no guarantee for sources of this type.
+The work of Canetti et al.~\cite{canetti2014key} shows it is possible to provide build fuzzy extractors for some distributions with this property.
+Their work leaves the question open for a large number of distributions.
+This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}
 
-\textbf{Our results:} In this work we show awesome things!\bnote{write}
+When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
+However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
+This uncertainty is usually expressed by proving the fuzzy extractor works for a class of distributions with some known property~(such as entropy and error levels).
+In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
+We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
 
+\textbf{Our Contributions} We show that for every distribution with super-logarithmic fuzzy min-entropy it is information-theoretically possible to build a secure sketch that retains super-logarithmic min-entropy.
+Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.
+(A key with super-logarithmic entropy can be expanded to arbitrary length using computational techniques.)  For distribution-aware secure sketches and fuzzy extractors, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+The situation is significantly more complicated for distribution-oblivious algorithms.
+Indeed, we show that there natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.
+However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.
+
+\textbf{Note:} Our constructions are information-theoretic and do not run in polynomial time.
+They should primarily be regarded as feasibility results.
+Our negative results apply to algorithms even given arbitrary running time, thus there is clear separation for unbounded running time algorithms.
+It remains as an open question whether our distribution-aware results can be replicated by efficient algorithms.
+This seems unlikely as most  interesting distributions have exponential size description.
+The power of the distribution-aware setting is that the algorithms can access this description.
+It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
+
+\textbf{Open Problems:} We showed that in the distribution-oblivious setting there is a separation between a secure sketch and a fuzzy extractor.
+However, it is still not known if fuzzy extractors can be constructed for any family of distributions.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c }
+& Distribution-Aware & Distribution-Oblivious\\
+\hline
+Secure Sketch & Yes~(\thref{cons:leveling}) & No\\
+\hline
+Fuzzy Extractor & Yes~(\thref{cons:leveling}) & Yes for some families\\
+& & Unknown for arbitrary family
+%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
+%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
+\end{tabular}
+\end{center}
+\caption{Is fuzzy min-entropy sufficient for extraction?}
+\label{tab:main results}
+\end{table}
+
+\bnote{connection to obfuscation}
 \section{Preliminaries}
 \label{sec:preliminaries}
+\bnote{be careful with overloading of $\ell$, both key length and number of levels.}
 For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.
@@
 \[
-\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
+\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
 \]
 \end{definition}
+
+If an adversary can always obtain the output of a fuzzy extractor by running the reproduce adversary, then there is no hope for security~(independent of the implementation of the fuzzy extractor).
+We make this intuition formal in the following result.
 For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
@@
 This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-In the interactive setting, fuzzy min-entropy is also a sufficient condition using secure two-party computation\bnote{cite something for this}.
-However, in the non-interactive setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.
+As stated above, fuzzy min-entropy is also a sufficient condition for security in the interactive setting.
+However, in the fuzzy extractor~(non-interactive) setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.
 We attempt to bridge this gap in this work.
 
-\section{Well-spread distributions}
-In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.
-We begin by considering secure sketches.
-We a call distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
-Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
-Intuitively, no sketch should be necessary for such a distribution.
-However, we show there is a large gap between a secure sketch that works for a particular well-spread distribution and a secure sketch that works for \emph{all} well-spread distributions.
+Before turning to our results we separate between two types of fuzzy extractors and secure sketches.
+The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.
+We call this type of algorithm distribution-oblivious.
+We define a new type of algorithm that called distribution-aware that is allowed to know the precise distribution to be supported.
+We provide a definition for secure sketches~(this definition can easily be extended to fuzzy extractors)
+
+\begin{definition}
+Let $W$ denote a distribution.  A secure sketch, $(\sketch_W, \rec_W)$ is called \emph{distribution-aware} if the correctness and security properties hold for the distribution $W$.  That is, 
+\begin{enumerate}
+\item \emph{Correctness} For all $w\in W$ and for all $w'\in\mathcal{M}$,  if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
+If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
+Note correctness is guaranteed only for the support of $W$.
+\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+\end{definition}
+Note that correctness is only required to hold for points in the support of the distribution $W$, the algorithms are allowed the description of $W$ and security need only hold for the distribution $W$.
+When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to make use of the (possibly)~exponential size distributions.
+It is not clear how to meaningfully define efficient distribution aware algorithms.
+If the algorithms were required to be efficient, they could only encode a negligible portion of the probability space of $W$, and would have to ``work'' on all distributions $W'$ with the same probability mass function on the encoded space.
+This would make the algorithms a distribution-oblivious fuzzy extractor for all distributions with this property.
+
+We begin with by showing that secure sketches and fuzzy extractors are possible in the distribution aware setting whenever there is super-logarithmic fuzzy min-entropy.
+We then turn to the standard \emph{distribution oblivious} setting.
+
+%The summary of our results is in Table~\ref{tab:upper bounds}.
 
@@
 \begin{tabular}{l | l | c}
-Upper bound & Depends on Distribution & Works for all Dist\\
+Lower bounds & Distribution-Dependent & Distribution-Oblivious\\
 \hline
-Well-spread distribution & $0$ & $\log |B_t|$\\
-Flat distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta)$ &$\log |B_t|$\\
-Arbitrary distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta) + \log \log \mathcal{M}$ & $\log |B_t|$
+Well-spread distribution & $\Hfuzz(W)$ & $\log |B_t|$\\
+Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
+Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$ & $\log |B_t|$
 \end{tabular}
-\caption{Upper bounds on minimum number of bits that a fuzzy extractor can write down and still have recovery.}
+\caption{Residual entropy of secure sketches for complete recovery.}
 \label{tab:upper bounds}
 \end{table}
-\subsection{Distribution Dependent Sketches}
-Error-correction should be easy when all points of $W$ are far apart.
-Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.
-Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).
+\bnote{Fix right side of table}
+\bnote{the table should move.}
+%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
+We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
+
+\section{Distribution-Dependent Sketches}
+In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
+We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.
+We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.
+In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.
+
+\subsection{Well-Spread Distributions}
+We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
+Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
+Error-correction is ``easy'' when all points of $W$ are far apart.
+Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.
+%Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).
 However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.
@@
 
-\subsection{Distribution Agnostic Sketches}
-Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
-However, as we show below the above construction does not extend to the setting of all well-spread distributions.
-In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
-In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
-In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
-
-We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
-It is not known if it is necessary to decrease the entropy of the distribution $W$.
-
-\begin{lemma}
-Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.
-Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.
-Then the length of $\sketch$ is at least $\log |B_{t}|$.
-\end{lemma}
-\begin{proof}
-Let $\mathcal{M}$ be a metric space.
-Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
-Consider the following experiment:
-\[
-W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
-\]
-That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
-Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
-Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.
-Now consider the following experiment
-\[
-v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
-\]
-Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.
-Then $X\overset{d}= Y$.
-That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.
-Thus, $\Pr[v^* = v] = 1$.
-For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
-For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
-Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.
-This completes the proof.
-\end{proof}
-\noindent
-\textbf{Note:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
-The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).
-
-Furthermore, the above lemma easily extends to the setting where the distributions are not well-spread as long as there is an adversary strategy of choosing the input distribution that produces an input to sketch that is identically distributed to the uniform distribution.
-
-\section{Flat spread distributions}
-In the previous section we showed bounds on producing secure sketches and fuzzy extractors for well-spread distributions.
-In this section we further investigate secure sketches where the sketch depends on the input distribution.\footnote{Recall the bound when the sketch does not know the input distribution is $\log |B_t|$ bits and this is constructible for any distribution.}
-
-\subsection{Distribution Dependent Sketches}
-
-\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
+\subsection{Flat distributions}
+In the previous section we showed it is easy to produce secure sketch for well-spread distributions in the distribution aware setting.
+%\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
 secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.
-In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.
-We begin by considering flat distributions where the probability of each point in $W$ is the same.
+In this section, we consider distributions with multiple points in each ball where points have the same probability.
 
@@
 
-Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme~(\defref{def:fuzzy min-ent}).
-Fuzzy min-entropy is total weight of the maximum probability ball.
-For flat distribution, this is directly correlated to the ball with the largest number of points.
-That is, for a flat distribution
+Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.
+Fuzzy min-entropy is total weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).
+For flat distributions, this is proportional to the largest number of points in any ball.
+More precisely,
 \begin{align*}
-\Hfuzz(W) &= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} * \Pr[W=w]\\
-&= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} *2^{-\Hoo(W)}\\
-&=\Hoo(W) -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} 
+\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
+&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
+&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
 \end{align*}
@@
 
-\bnote{need to extend this to a non-fixed number of bits and randomized.}
-\section{Dealing with non flat distributions}
+\subsection{Arbitary distributions}
 The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.
@@
 Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
-We first a natural method to leverage convex combinations that does not work\bnote{phrasing}.
-We then show a solution that comes within \bnote{something} of optimal by partitioning the probability space.
+Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.
+In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
+The main issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
 
-\subsection{Leveraging convex combinations?}
-In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
-For example, consider the following extension to \consref{cons:pairwise hash}.
-Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
-However, we show it is difficult to leverage convex combinations in the finite setting and handling the infinite case is more difficult.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
-
-The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
-Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
-
-In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
-That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
-However, in the setting where $W$ is a convex combination of flat sources this does not hold.
-
-Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
-This distribution is illustrated in \figref{fig:convex comb}.
-
-The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
-Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
-(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
-
-Consider an input point $w\in W$.
-One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
-For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
-This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
-This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
-Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
-In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
-
-\begin{figure}[h]
-
-\centering
-    \includegraphics[width=.9\textwidth]{convexCombExample.png}
-    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
-\label{fig:convex comb}    
-\end{figure}
-
-\bnote{remove pagebreak later}
-
-\subsection{Layered Hashing}
-As we saw in the previous section, dealing with non-flat distributions is difficult.
-The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.
-We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.
-Then the hash is applied only considering the maximum weight of the ball containing points at this level.
-Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.
-
-\pagebreak
+As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
+We address this by describing the probability of the point $w_0\in W$ seen in sketch.
+Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.
+We can think of this construction as dividing the distribution $W$ into probability levels, and each component level is nearly flat.
+As long as levels are large enough, they do not reveal too much information about the stored point $W$.
+Naturally, there is a tradeoff between the number of levels and how useful the level information is to both the \rep algorithm and the adversary.
 
@@
 \begin{theorem}
+\label{thm:layered hashing}
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.
 Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
@@
 \begin{proof}
-We begin by arguing correctness.
-Fix some $w, w'$.
-If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.
+\textbf{Correctness:}  We begin by arguing correctness.
+Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.
+The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.
+If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.
 Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
 \end{align*}
-Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
+Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
 
-We now argue security.
-First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).
-That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.
-Let $1_{\text{low prob}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
-Then
-\begin{align*}
-\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low prob}}=1] * 1 + \Pr[1_{\text{low prob}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)\\
--\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
-\end{align*}
-We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
+\textbf{Ideal Adversary with access to Level Information:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.
+%We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
 An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.
@@
 \end{align}
-For the remainder of the proof, we seek a bound on \[\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].\]
+\textbf{Security:}
+We now argue security.
+First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).
+That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.
+Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
+Then
+\begin{align*}
+\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
+-\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
+\end{align*}
+For the remainder of the proof, we seek a bound on 
+\[
+2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].
+\]
 We separate out this quantity into levels:
@@
 \end{align*}
-Where the third line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$.
-The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the whole quantity is negative~(and entropy is non-negative).
+Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$.
+The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the bound is negative.
 \end{proof}
 
+\begin{corollary}
+Let $n$ be a security parameter and let $\mathcal{M} =\zo^n$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ residual min-entropy and overwhelming correctness.
+Furthermore, there exists a $(\mathcal{M}, \Hoo(W), \ell = \omega(\log n), \epsilon)$ distribution aware fuzzy extractor with $\epsilon = \ngl(n)$) and overwhelming correctness.
+\end{corollary}
+\section{Distribution-Oblivious Sketches}
+\label{sec:dist oblivious}
+
+In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.
+This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.
+In this section we ask if the results can be replicated for a family of distributions.
+Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.
+The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).
+Unfortunately, we show for secure sketches this is not the case.
+That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.
+
+\subsection{A definitional equivalence}
+Before proceeding to our result, we consider the definition of a fuzzy extractor.
+The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
+This can be thought of as a two stage process: 1) the system designer specifies $(\sketch, \rec)$, 2) the adversary specifies a particular member $W\in \mathcal{V}$.
+We will say the system designer wins if the adversary can guess the element in $W$ with low probability, and the adversary wins if the can recover $w\in W$ with noticeable probability.
+That is, we can formulate this process as a standard cryptographic game.
+Let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
+We will formulate this as a two player game.
+
+\begin{center}
+\begin{minipage}{1in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
+$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
+If $W\not\in \mathcal{V}$ return $0$.\\
+If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
+\end{tabbing} \end{minipage} 
+\end{center}
+
+%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
+In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
+
+\begin{center}
+\begin{minipage}{1in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
+$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
+$W \leftarrow \mathcal{W}$\\
+If $W\not\in \mathcal{V}$ return $0$.\\
+If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
+\end{tabbing} \end{minipage} 
+\end{center}
+
+Note the only different between these two games is which player announce their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
+In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
+These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.
+
+\begin{lemma}
+If a fuzzy extractor is secure for all $W\in\mathcal{V}$, then it is secure for all distributions $\mathcal{W}$ over the family $\mathcal{V}$.
+\end{lemma}
+
+Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
+Importantly, the adversary is sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
+We can think of the description of $W$ as side-information or leakage to the adversary.
+The system designer, however never sees the particular outcome $W$.
+This asymmetry will form the basis of our negative results in the next subsection.
+%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
+However, as we show below the above construction does not extend to the setting of all well-spread distributions.
+In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
+In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
+In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
+
+%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
+The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
+We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
+The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
+
+%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
+
+\subsection{Impossibility of info-theoretic sketches}
+In the previous section we showed a fuzzy extractor that works for a family of sources must also work for an arbitrary distribution over those sources.
+In addition, the adversary learns the particular source that is being sketched while the system designer does not.
+To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's side information as $Z$.
+Let $\mathbb{F}$ be some field of size $q$.
+Consider the following distributions of the following type $W = w_1,..., w_\ell$ where $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$.
+This type of distribution is a line in space $\mathbb{F}^\ell$.
+Consider $V$ as the uniform distribution over all such $W$.
+Then $V$ is the uniform distribution over $\mathbb{F}^\ell$.
+
+Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
+\begin{lemma}
+There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
+\end{lemma}
+\begin{proof}
+Need to show several things.  
+\begin{itemize}
+\item Each component of the distribution has fuzzy min-entropy.
+\item Any sketch must leak some information about $V$.
+\item The side information can be thought of as a hash function.
+Furthermore, it is independent of the sketch.
+Thus, the sketch and hash are independent information.
+Thus, conditioned on both there is almost no entropy.
+\end{itemize}
+\end{proof}
+
+\bnote{stopped here}
+\begin{lemma}
+There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
+\end{lemma}
+
+\begin{corollary}
+This is also impossible for computational sketches that retain hill entropy.
+\end{corollary}
+
+\subsection{Conductors}
+Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
+\begin{lemma}
+Not possible for information-theoretic objects.
+\end{lemma}
 \bibliographystyle{alpha}
@@
 \appendix
+\section{Block Unguessable Distributions}
+\begin{definition}~\cite[Definition 4.2]{canetti2014key}
+\label{def:block guessable}
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
+\begin{cases}
+1 & w_j = w_j'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+\[
+\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+\section{Leveraging convex combinations?}
+\label{sec:convex comb}
+In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+
+The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
+Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
+
+In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
+That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+However, in the setting where $W$ is a convex combination of flat sources this does not hold.
+
+Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+This distribution is illustrated in \figref{fig:convex comb}.
+
+The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
+(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+
+Consider an input point $w\in W$.
+One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
+For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
+This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
+Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+
+\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
+However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
+That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
+
+In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
+
+\begin{figure}[t]
+
+\centering
+    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+\label{fig:convex comb}    
+\end{figure}
+
 \section{Old Proofs}
@@
 
+\subsection{How many bits for distribution oblivious sketch} 
+\begin{lemma}
+Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.
+Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.
+Then the average length of $\sketch$ is at least $\log |B_{t}|$.
+\end{lemma}
+\bnote{what do we mean by average here?
+we mean when receiving a uniform input across the coins.
+Maybe, there are distributions where it writes down a little.
+What's the right thing to say?
+Markov?}
+\begin{proof}
+Let $\mathcal{M}$ be a metric space.
+Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
+Consider the following experiment:
+\[
+W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
+\]
+That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
+Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
+Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.
+Now consider the following experiment
+\[
+v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
+\]
+Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.
+Then $X\overset{d}= Y$.
+That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.
+Thus, $\Pr[v^* = v] = 1$.
+For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
+For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
+Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.
+This completes the proof.
+\end{proof}
+\noindent
+\textbf{Notes:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
+The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).
+
+Furthermore, the above lemma easily extends to the setting where the distributions are not well-spread as long as there is an adversary strategy of choosing the input distribution that produces an input to sketch that is identically distributed to the uniform distribution.
+
+The above lemma only talks about how many bits the algorithms must write down.
+It does not say that the entropy of the distribution must decrease~(this is the important question).
+We now proceed to this question.
+
 \section{Examples to Consider}

### 2014-08-26 info-bounds/FuzzyExtPossibility.tex
starting proof of affine sources

@@
 \title{When are Fuzzy Extractors Possible?}
-\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory.
+\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
+work was sponsored by the Department of the Air Force under Air Force
+Contract
+\#FA8721-05-C-0002.  Opinions,
+interpretations, conclusions and recommendations are those of the author
+and
+are not necessarily endorsed by the United States Government.
 Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.
@@
 
-\textbf{Our Contributions} We show that for every distribution with super-logarithmic fuzzy min-entropy it is information-theoretically possible to build a secure sketch that retains super-logarithmic min-entropy.
+\textbf{Our Contribution} We show that for every distribution with super-logarithmic fuzzy min-entropy it is information-theoretically possible to build a secure sketch that retains super-logarithmic min-entropy.
 Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.
@@
 The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
-This can be thought of as a two stage process: 1) the system designer specifies $(\sketch, \rec)$, 2) the adversary specifies a particular member $W\in \mathcal{V}$.
-We will say the system designer wins if the adversary can guess the element in $W$ with low probability, and the adversary wins if the can recover $w\in W$ with noticeable probability.
-That is, we can formulate this process as a standard cryptographic game.
-Let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
-We will formulate this as a two player game.
+For clarity we will refer to $\mathcal{V}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular sample taken $w\in W$ as the \emph{outcome}.
+We will add the family $\mathcal{V}$ to the description of a fuzzy extractor where appropriate~(replacing the entropy requirement).
+
+The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
+The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if the can guess $w\in W$ with noticeable probability.
+More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
+We will formulate this as a two player game.\footnote{We denote the outcome of the game as a reward to each player.
+This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
+Later, we will need this game to be zero sum.}
 
@@
 %Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
-In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
+Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
+%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
 
@@
 
-Note the only different between these two games is which player announce their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
+The only difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
 In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
@@
 \begin{lemma}
-If a fuzzy extractor is secure for all $W\in\mathcal{V}$, then it is secure for all distributions $\mathcal{W}$ over the family $\mathcal{V}$.
+\label{lem:quant switch fuzz}
+Let $\mathcal{V}$ be a family of distributions.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor.
+Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
+Then there exists a fuzzy extractor $(\gen', \rep')$ is a $(\mathcal{M}, \mathcal{W}, \ell, t, \epsilon)$-fuzzy extractor.\footnote{Note the other direction of this lemma is true as well.
+If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
 \end{lemma}
 
-Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
-Importantly, the adversary is sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
+Instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
+Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
 We can think of the description of $W$ as side-information or leakage to the adversary.
@@
 This asymmetry will form the basis of our negative results in the next subsection.
+
+\begin{corollary}
+\label{cor:no fuzz for dist}
+Let $\mathcal{V}$ be a family of distributions.
+Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
+If there does not exist a $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor, then there is no $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor.
+\end{corollary}
 %Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
@@
 
+Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for secure sketches as well as fuzzy extractors.
+Additionally we elide the correctness term $\delta$ above, but these generalize the secure sketches and fuzzy extractors with imperfect completeness.
+
 \subsection{Impossibility of info-theoretic sketches}
-In the previous section we showed a fuzzy extractor that works for a family of sources must also work for an arbitrary distribution over those sources.
-In addition, the adversary learns the particular source that is being sketched while the system designer does not.
-To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's side information as $Z$.
-Let $\mathbb{F}$ be some field of size $q$.
-Consider the following distributions of the following type $W = w_1,..., w_\ell$ where $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$.
+In the previous section, we saw that if a fuzzy extractor is secure for a family of sources, for every distribution over those sources there is a secure fuzzy extractor.
+In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
+
+\begin{theorem}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta \le 1/2$ for $\tilde{m} =\omega(1)$.
+%Furthermore, consider $V$ as the uniform distribution over $\mathcal{V}$.
+There is no secure sketch for $\mathcal{
+\end{theorem}
+
+\begin{proof}
+It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
+The adversary sees the information $W$, but the system designer does not.
+We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).
+
+We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.
+We begin by describing our family $\mathcal{V}$.
+$\mathcal{V}$ consists of the set of affine functions from one dimension to $\ell$ dimensions.
+% That is, we project a single point in the field to an arbitrary element in the metric space.
+%In addition, the adversary learns the particular source that is being sketched while the system designer does not.
+To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.
+We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
+Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.
+
+Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\ell$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$ and $a_i\neq 0$.
 This type of distribution is a line in space $\mathbb{F}^\ell$.
-Consider $V$ as the uniform distribution over all such $W$.
-Then $V$ is the uniform distribution over $\mathbb{F}^\ell$.
-
-Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
+Define $V$ as the uniform distribution over all such $W$.
+Fix some $1< t < \ell$.
+It suffices to show the following:
+
+\begin{itemize}
+\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$.
+\item The distribution $V$ is uniform~(from the sketch designers point of view).
+\item For any secure sketch on $V$, $H_0(V | \sketch(V)) \le n -\log |B_t|$.
+\item The information $Z$ is a universal hash of $V$ that is independent of $\sketch(V)$. This suffices to show that $\Hav(V| \sketch(V), Z)$ is very small.
+\end{itemize}
+\begin{proposition} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\end{proposition}
+\begin{proof}
+Consider some fixed $W\in\mathcal{V}$.
+First note that since $w_1$ is uniform in a field of size $\omega(\poly(n))$, the distribution $\Hoo(W) =\omega(\log n)$.
+Recall that $t< \ell$.
+We now show that for any $w, w'\in W$, $\dis(w, w') = \ell$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Fix some $w, w'\in W$.
+Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.
+Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.
+That is, $\dis (w, w')  =\ell$.
+\end{proof}
+
+\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\ell$.
+\end{proposition}
+\begin{proof}
+Consider some $w\in V$.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\ell , b_\ell$.
+The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\ell$ are uniformly random.
+\end{proof}
+\bnote{will need to define average Hartley entropy}
+\bnote{show version without error first?}
+\begin{proposition}
+Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $H_0(V | \sketch(V)) \le n - \log |B_t|+ O(1)$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+Dealing with imperfect correctness makes the bound more complicated.
+In particular, we can only argue about the average remaining support size.}
+\end{proposition}
+\begin{proof}
+By the definition of correctness for $(\sketch, \rec)$, 
+\[
+\forall w, w^*, \Pr_{p\leftarrow \sketch(w)} [\rec(w^*, p) = w] >1-\delta.
+\]
+By the Markov inequality, 
+\[
+\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
+\]
+That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
+
+Outline of what I want to say.
+\begin{itemize}
+\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
+\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
+\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
+\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
+\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
+Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.
+Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).
+\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
+\end{itemize}
+\end{proof}
+
+\bnote{stopped here}
+\end{proof}
 
@@
 
-\bnote{stopped here}
+Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
 \begin{lemma}

### 2014-08-26 trunk/info-bounds/FuzzyExtPossibility.tex
working on impossibility proof

@@
 For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
+We will also use an average case version of this notion~(to the best of our understanding this has not been used before).\bnote{has it?}
+\begin{definition}[Conditional Hartley Entropy]
+\label{def:conditional hartley}
+The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} 2^{-H_0(X | Y=y)})$.
+\end{definition}
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
@@
 The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
-This can be thought of as a two stage process: 1) the system designer specifies $(\sketch, \rec)$, 2) the adversary specifies a particular member $W\in \mathcal{V}$.
-We will say the system designer wins if the adversary can guess the element in $W$ with low probability, and the adversary wins if the can recover $w\in W$ with noticeable probability.
-That is, we can formulate this process as a standard cryptographic game.
-Let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
-We will formulate this as a two player game.
+For clarity we will refer to $\mathcal{V}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular sample taken $w\in W$ as the \emph{outcome}.
+We will add the family $\mathcal{V}$ to the description of a fuzzy extractor where appropriate~(replacing the entropy requirement).
+
+The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
+The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
+More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
+We will formulate this as a two player game.\footnote{We denote the outcome of the game as a reward to each player.
+This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
+This is to apply results from game theory.}
 
@@
 $W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
-If $W\not\in \mathcal{V}$ return $0$.\\
+If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
 If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
@@
 $W \leftarrow \mathcal{W}$\\
-If $W\not\in \mathcal{V}$ return $0$.\\
+If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
 If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
@@
 
-Note the only different between these two games is which player announce their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
+The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
 In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
@@
 \begin{lemma}
-If a fuzzy extractor is secure for all $W\in\mathcal{V}$, then it is secure for all distributions $\mathcal{W}$ over the family $\mathcal{V}$.
+\label{lem:quant switch fuzz}
+Let $\mathcal{V}$ be a family of distributions.
+Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
+Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
+Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-fuzzy extractor.\footnote{The other direction of this lemma is true as well.
+If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
 \end{lemma}
@@
 Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
-Importantly, the adversary is sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
+Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
 We can think of the description of $W$ as side-information or leakage to the adversary.
@@
 This asymmetry will form the basis of our negative results in the next subsection.
+
+\begin{corollary}
+\label{cor:no fuzz for dist}
+Let $\mathcal{V}$ be a family of distributions.
+Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
+If there does not exist a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
+\end{corollary}
 %Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
@@
 
+Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to the case of imperfect correctness.
+
 \subsection{Impossibility of info-theoretic sketches}
-In the previous section we showed a fuzzy extractor that works for a family of sources must also work for an arbitrary distribution over those sources.
-In addition, the adversary learns the particular source that is being sketched while the system designer does not.
-To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's side information as $Z$.
-Let $\mathbb{F}$ be some field of size $q$.
-Consider the following distributions of the following type $W = w_1,..., w_\ell$ where $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$.
+In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.
+In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
+
+\begin{theorem}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta \le 1/2$ for $\tilde{m} =\omega(1)$.
+%Furthermore, consider $V$ as the uniform distribution over $\mathcal{V}$.
+There is no secure sketch for $\mathcal{
+\bnote{what is $t$?}\bnote{finish proof}
+\end{theorem}
+
+\begin{proof}
+\bnote{need to rearrange this proof.}
+It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
+The adversary sees the information $W$, but the system designer does not.
+We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).
+
+We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.
+We begin by describing our family $\mathcal{V}$.
+$\mathcal{V}$ consists of the set of affine functions from one dimension to $\ell$ dimensions.
+% That is, we project a single point in the field to an arbitrary element in the metric space.
+%In addition, the adversary learns the particular source that is being sketched while the system designer does not.
+To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.
+We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
+Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.
+
+Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\ell$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$ and $a_i\neq 0$.
 This type of distribution is a line in space $\mathbb{F}^\ell$.
-Consider $V$ as the uniform distribution over all such $W$.
-Then $V$ is the uniform distribution over $\mathbb{F}^\ell$.
-
-Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
-
+Define $V$ as the uniform distribution over all such $W$.
+Fix some $1< t < \ell$.
+It suffices to show the following:
+
+\begin{itemize}
+\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$.
+\item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
+\item For any secure sketch on $V$, $H_0(V | \sketch(V)) \le n -\log |B_t|$. 
+\item The information $Z$ is a universal hash of $V$ that is independent of $\sketch(V)$. This suffices to show that $\Hav(V| \sketch(V), Z)$ is very small.
+\end{itemize}
+\begin{proposition} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\end{proposition}
+\begin{proof}
+Consider some fixed $W\in\mathcal{V}$.
+The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.
+Recall that $t< \ell$.
+We now show that for any $w, w'\in W$, $\dis(w, w') = \ell$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Fix some $w, w'\in W$.
+Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.
+Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.
+That is, $\dis (w, w')  =\ell$.
+\end{proof}
+
+\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\ell$.
+\end{proposition}
+\begin{proof}
+Consider some $w\in V$.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\ell , b_\ell$.
+The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\ell$ are uniformly random.
+\end{proof}
+\bnote{will need to define average Hartley entropy}
+\bnote{show version without error first?}
+\begin{proposition}
+Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $H_0(V | \sketch(V)) \le (\ell-t) |\mathbb{F}|n +1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+Dealing with imperfect correctness makes the bound more complicated.
+In particular, we can only argue about the average remaining support size.}
+\end{proposition}
+\begin{proof}
+We assume that $\rec$ is deterministic in our analysis.
+Any randomness necessary for the \rec algorithm can be provided by \sketch.
+We will however, not consider these coins in our security analysis.
+
+By the definition of correctness for $(\sketch, \rec)$, 
+\[
+\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+\]
+%For most $p$, $\rec$ works on most neighbors of $w$.  
+Fix some $w$.  
+By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[p\in A_{ss}]\ge 1/2$ and $\forall s\in A_{ss}$, 
+\[
+\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+
+Consider some $p\in A_{ss}$.
+We now show that $H_0(V | p) \le n-\log |B_t|$.
+Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.
+Thus for every value in $V|p$ this is also true.
+This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).
+In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).
+That is $V|p$ is a set with minimum distance at least $t$.
+By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t )|\mathbb{F}|$.
+Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t ) |\mathbb{F}| +1$.
+%By the Markov inequality, 
+%\[
+%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
+%\]
+%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
+%
+%Outline of what I want to say.
+%\begin{itemize}
+%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
+%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
+%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
+%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
+%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
+%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.
+Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).
+%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
+%\end{itemize}
+\end{proof}
+We now define the side information $Z = a_2, b_2, ..., a_\ell, b_\ell$.
+By described above the view of $\sketch, \rec$ is a uniform distribution $V$.
+Thus, the side information $Z$ is independent of $\sketch(V)$.
 \begin{lemma}
-There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
+$\Hav(V| P , Z) = \Theta(1)$
 \end{lemma}
 \begin{proof}
-Need to show several things.  
-\begin{itemize}
-\item Each component of the distribution has fuzzy min-entropy.
-\item Any sketch must leak some information about $V$.
-\item The side information can be thought of as a hash function.
+Consider some fixed $p$.
+If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
+\[
+\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
+\]
+Then by the union bound, 
+\[
+\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
+\]
+\bnote{need to average across $P$}
+\bnote{I'm confused about what we mean by $Z$ being universal here.}
+\bnote{working here!}
+\end{proof}
+%
+%\bnote{stopped here}
+\end{proof}
+
+%\begin{lemma}
+%There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
+%\end{lemma}
+%\begin{proof}
+%Need to show several things.  
+%\begin{itemize}
+%\item Each component of the distribution has fuzzy min-entropy.
+%\item Any sketch must leak some information about $V$.
+%\item The side information can be thought of as a hash function.
 Furthermore, it is independent of the sketch.
@@
 Thus, conditioned on both there is almost no entropy.
-\end{itemize}
-\end{proof}
-
-\bnote{stopped here}
-\begin{lemma}
-There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
-\end{lemma}
+%\end{itemize}
+%\end{proof}
+
+Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
+%\begin{lemma}
+%There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
+%\end{lemma}
 
 \begin{corollary}
-This is also impossible for computational sketches that retain hill entropy.
+This is also impossible for computational sketches that retain hill entropy.\bnote{fill this in, use asiacrypt result.}
 \end{corollary}
 
-\subsection{Conductors}
-Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
-\begin{lemma}
-Not possible for information-theoretic objects.
-\end{lemma}
+%\subsection{Conductors}
+%Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
+%\begin{lemma}
+%Not possible for information-theoretic objects.
+%\end{lemma}
 \bibliographystyle{alpha}
@@
 \appendix
+\section{Coding Theory}
+\begin{definition}
+\label{def:shannon-code}
+Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr_{w' | \dis(w', w)\le t}[\rec(c') \neq c]\le \epsilon$.
+To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
+\end{definition}
+
+ \begin{definition}
+Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
+$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+\end{definition}
+An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
+See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.
+An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
+We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} %(we provide a proof in \secref{sec:proof of average to maximal error}):
+\begin{lemma}
+\label{lem:averageToMaximalError}
+Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
+There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
+\end{lemma}
+
+\bnote{This comes from asiacrypt paper, what to cite?}
 \section{Block Unguessable Distributions}

### 2014-09-09 constantRate/ConstCompFuzzExt-reorg.tex
adding full proof of sampling construction, reorganized

--- 2014-07-02 trunk/constantRate/ConstCompFuzzExt-reorg.tex
@@
 We construct the first fuzzy extractors that work for a large class of distributions that have negative minimum usable entropy.
-Their security is computational.
-In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
-
-Our first construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+We present both information-theoretic and computational constructions.In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
+
+Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a large alphabet.
+In this construction each symbol must contribute fresh entropy.
+We then use computational techniques to obtain two constructions with additional properties.
 
@@
 
-The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
+Our third construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+
+The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
 
@@
 
+\noindent
+For \consref{cons:info theoretic} to be secure we need most blocks to contribute some entropy to the output.  We call this notion a partial block source.
+
+\begin{definition}
+\label{def:partial source}
+A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\]
+\end{definition}
+\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
+The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
+
 \begin{lemma}
@@
 Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
-Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.
-Then the following is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-fuzzy conductor that is $\epsilon \ell$ hard with error $\delta$:
+Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).
 
@@
 In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with $\Huse \le 0$.
-In this section we show that the addition of computational techniques yields considerable extra power.
+In this section we show that computational techniques allow for additional desirable properties.
 Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.
@@
 This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.
-We first present the necessary definitions and the construction.% and then compare it to \consref{cons:first construction}.
-% and the construction proceeds by either obfuscating $V_i$ or a random point as before.
-For security each value $V_i$ needs to be unguessable.  
-This will hold as long as enough blocks contribute some entropy:
-
-\begin{definition}
-\label{def:partial source}
-A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
-\]
-\end{definition}
-\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
-The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
 Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.
@@
 
-Before we show \thref{thm:sampling} we present a simplified construction of \consref{cons:sampling}.
+%Before we show \thref{thm:sampling} we present a simplified construction of \consref{cons:sampling}.
 This construction essentially ignores the sampling step and asks when obfuscation provides security of the obfuscated values $V_1,..., \ell$.
@@
 
-\subsection{Simplifying \consref{cons:sampling}}
-In this section, we present a simplified version of \consref{cons:sampling}.
-The goal of this construction is to understand the type of sources that \consref{cons:sampling} supports.
-Furthermore, this simplified construction has some advantages over \consref{cons:sampling}.\footnote{For the sake of clarity we defer discussion of \consref{cons:first construction} until \apref{sec:construction}.
-In this section we focus on understand what information is leaked by point obfuscations and digital lockers.}
-%Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
-This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
-
-\begin{construction}
-\label{cons:first construction}
-Let $\mathcal{Z}$ be an alphabet and let $V = V_1,..., V_\ell$ be a distribution over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
-Let  $C\subset \zo^\ell$ be an error-correcting code.
-We describe $\gen, \rep$ as follows:
-
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $v = v_1,..., v_\ell$
-\item Sample $c\leftarrow C$.
-\item For $j=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item If $c_j = 0$: $p_j = \mathcal{O}(I_{v_j})$.
-\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
-\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
-\end{enumerate}
-\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(v', p)$
-\item For $j=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item If $p_j(v_j') = 1$: set $c_j' = 0$.
-\item Else: set $c_j' = 1$.
-\end{enumerate}
-\item Set $c = \decode(c')$.
-\item Output $c$.
-\end{enumerate}
-\vspace{0.15in}
-\end{minipage}
-\end{tabular}
-\end{center}
-\end{construction}
-
-The input $v$ is hidden in two different ways.  In locations where $c_j=1$, the block $v_j$ is information-theoretically unknown.
-In locations where $c_j=0$, it is hard to find $v_j$ given access to the point obfuscation.
-There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $v_j \neq v_j'$.
-However, if a bit $c_j'$ is $0$, this likely means that $v_j=v_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
-This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
-
-\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $V_j$.
-By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
-This restriction on the distribution is captured in the following definition.
-
-\begin{definition}
-\label{def:block guessable}
-Let $I_v (\cdot, \cdot)$ be an oracle that returns \[I_v(j, v_j')=
-\begin{cases}
-1 & v_j = v_j'\\
-0 & \text{otherwise}.
-\end{cases}
-\]
-A source $V = V_1||...|V_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
-\[
-\forall j\in J, \Hav(V_j |View(S^{I_{V}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-
-We show some examples of unguessable block distributions in \apref{sec:characterize}.
-In particular, any source $V$ where for all $j$, $\Hoo(V_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
-
-Intuitively, for a block unguessable distribution, the oracle provided by the obfuscation is not useful.
-Indeed, we can show that \consref{cons:first construction} is a computational fuzzy conductor~(\apref{sec:construction}).
-It is this observation that allows us to show the security of our \emph{sample-then-obfuscate construction}.
-We will show that the output of the sampling part of the algorithm produces a unguessable-block distribution.
-% For security we argue that each of the $v_i$ values is unguessable.
-For correctness we show that with overwhelming probability at least of the $v_i$ and $v_i'$ match and allowing the digital locker to be opened and $r$ to be recovered.
-Reusability comes essentially for free given a sufficiently composable obfuscation for digital lockers.
-For the sake of clarity we state reusability as a separate theorem~(\thref{thm:reusability}).
-
 \subsection{Security of \consref{cons:sampling}}
 \label{ssec:sec cons sampling}
-We now return to showing \thref{thm:sampling}.  
+%We now return to showing \thref{thm:sampling}.  
+In this section we briefly describe why \consref{cons:sampling} is secure.  A proof of security appears \apref{sec:analysis sampling}.  
 In order to show security \consref{cons:sampling}, we
 show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
-We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
+Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
+% forms a block-unguessable distribution.
 Then security essentially follows from the security of \consref{cons:first construction}.
 %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
-Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
+%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
 %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
@@
 
-In ~\clref{cl:all blocks entropy} we show that any distribution where each individual block has super-logarithmic min-entropy forms a unguessable block distribution.  This allows us to conclude:
-\begin{corollary}
-\label{cor:v are unguessable}
-Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
-Take any $q=\poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
-\end{corollary}
-
-Thus, unless the choice of $\lambda$ is very unlucky,
-the inputs $V_1,..., V_\ell$ to \consref{cons:sampling} form a block unguessable distribution.
-This is enough to show the probability that adversary sees a output other than $\perp$ from one of the obfuscations is negligible and that the adversary only has information about the key in this case.
-\begin{lemma}[Proof in \apref{sec:sampling unguess}]
+Once all $V_i$ all simultaneously have good entropy, the adversary will never see anything but $\perp$ as an output from the obfuscations~(with overwhelming probability).
+If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.
+
+\begin{lemma}[Proof in \apref{sec:analysis sampling}]
 \label{lem:samp unguess}
@@
 
-\begin{lemma}[Proof in \apref{sec:sampling errors}]
+\begin{lemma}[Proof in \apref{sec:analysis sampling}]
 \label{lem:sampling errors}
@@
 \subsection{Reusability of \consref{cons:sampling}}
-The reusability of \consref{cons:sampling} essentially follows from the security of the VGB obfuscator with auxiliary input.
+The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.
 We consider a bounded $q = \poly(n)$ number of reuses.
@@
 \lnote{I need to check this}
-We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.
+We now show \consref{cons:sampling} supports partial block sources with $\Huse\le 0$.
 The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
@@
 
-%\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}
+\section{Allowing Correlated Symbols}
+In the previous two sections, we presented constructions that supported $\Huse\le 0$ for restricted classes of distributions.
+Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.
+In this section, we present a computational construction that allows for correlation between symbols while still supporting $\Huse \le 0$ and correcting a constant fraction of errors.
+This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+
+\begin{construction}
+\label{cons:first construction}
+Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
+Let  $C\subset \zo^\ell$ be an error-correcting code.
+We describe $\gen, \rep$ as follows:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\ell$
+\item Sample $c\leftarrow C$.
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
+\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
+\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
+\end{enumerate}
+\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p)$
+\item For $j=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item If $p_j(w_j') = 1$: set $c_j' = 0$.
+\item Else: set $c_j' = 1$.
+\end{enumerate}
+\item Set $c = \decode(c')$.
+\item Output $c$.
+\end{enumerate}
+\vspace{0.15in}
+\end{minipage}
+\end{tabular}
+\end{center}
+\end{construction}
+
+The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
+In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
+There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
+However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
+This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
+
+\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
+By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
+Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
+This restriction on the distribution is captured in the following definition.
+
+\begin{definition}
+\label{def:block guessable}
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
+\begin{cases}
+1 & w_j = w_j'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $W = W_1| ...
+|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+\[
+\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+
+We show some examples of unguessable block distributions in \apref{sec:characterize}.
+In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
+The following theorem states the construction is both correct and secure.  %After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
+\begin{theorem}
+\label{thm:main thm first cons}
+Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
+\end{theorem}
+
+\subsection{Discussion of \consref{cons:first construction}}
+\label{sec:discussion}
+\lnote{I did not check this calculation -- will do}
+To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
+\[
+\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
+\]
+
+We consider what entropy is necessary for security.
+The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
+This yields:
+\[
+\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
+\]
+When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
+
+\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
+
+If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
 
@@
 \appendix
-
-%\section{Use of Fuzzy Extractors for Biometrics}
-%Fuzzy extractors derive stable from noisy sources.
-Biometrics represent an important noisy physical source.
-Unlike physical unclonable functions, biometrics are fixed distributions.
-Biometrics cannot be redesigned to  increase their entropy or reduce their error rates.
-Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).
-Unfortunately, most work measures system security using false accept rate vs.
-false reject rate.
-This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.
-False accept rate provides no bound on the information leaked by the helper data.
-Indeed the helper data may completely reveal the original input.
-In high security applications, measuring false accept rate vs.
-false reject rate is insufficient to argue system security.
-%
-%\label{sec:iris no key}
-%As an example, we focus on the human iris.
-The iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-The best estimate for iris entropy is $249$ bits~\cite{daugman2004}.
-Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-There has been considerable research since the work of Daugman~\cite{daugman2004}.
-These works do not dramatically alter the entropy estimate or error rate necessary for a reasonable false reject rate.
-We use the Daugman's parameters for our calculations.
-%
-%The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
-For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.%\footnote{Daugman  improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.
-The comparison between the two readings is then made using bits not excluded by either image.
-It is not clear how to extend into the fuzzy extractor setting.
-Even with the masking vector $\Huse$ is negative for irises.}
-%We have the following calculation for $\Huse$:
-%\begin{align*}
-%\Huse &= \Hoo(W) - \log |B_t|\\
-%&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx 707.
-%\end{align*}
-%Thus, it is impossible to output a key using a fuzzy extractor that outputs the same strength key for all distributions with the same entropy and error tolerance~(see \apref{sec:minimal conditions} for minimal conditions for fuzzy extractor security).
-%Irises are believed to be the strongest biometric but applying current fuzzy extractors to irises yields no meaningful security.
-%
-%\section{Minimal Conditions for Fuzzy Extractor Security}
-%\label{sec:minimal conditions}
-%
-%A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
-This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
-We make this intuition formal here:
-%
-%\begin{definition}
-%\label{def:fuzzy min-ent}
-%A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
-%\[
-%\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
-%\]
-%\end{definition}
-%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
-%\begin{lemma}
-%\label{lem:fuzz necessary}
-%Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-%\end{lemma}
-%\begin{proof}
-%Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.
-Consider the following distinguisher $D$:
-%\begin{itemize}
-%\item On input $r, p$.
-%\item If $\rep(m, p) = r$, output $1$.
-%\item Else output $0$.
-%\end{itemize}
-%First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.
-Thus, when $\kappa = \omega(\log n)$:
-%\[
-%\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
-%\]
-%\end{proof}
-%\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
-This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-%The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.
-%If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).
-Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse\le 0$.
-This motivates our restriction to meaningful classes of source distributions with $\Huse\le 0$.
-%%This means we inherently must talk about the security and errors together.
-%
-%In this work we consider the Hamming distance over some alphabet $\mathcal{Z}$.
-There are two minimal types of distributions where $\Hfuzz(W)\geq \omega(\log n)$, the first is where the $(t+1)$-st least entropic block has super-logarithmic entropy~(the $t$ most entropic blocks are essentially free to the adversary).
-The other is that there $t+\omega(\log n)$ blocks that contribute some entropy~(there is a continuum between these two types).
-Definitions~\ref{def:block guessable} and~\ref{def:partial source} were developed for these types of sources respectively.
-However, we do not achieve security when $\Hfuzz(W)= \omega(\log n)$ for either definition, this is an open problem.
-%
-%\section{Fuzzy Conductors}
-%\lnote{I need to check this}
-%\label{sec:conductors}
-%Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).
-Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.
-They suggest these bounds may be avoided by outputting a fresh random variable.
-This is known as a fuzzy conductor~\cite{KanukurthiR09}.
-%\begin{definition}
-%A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
-%\begin{enumerate}
-%\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
-%\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep(w', SS) = X]\geq 1-\delta$~(over the coins of $\gen', \rep'$).
-If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
-%\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.
-That is, $\exists Y$ with $\Hav(Y | SS ) \geq \tilde{m}$ such that $\Delta((X, SS), (Y, SS))\leq \epsilon$.
-%\end{enumerate}
-%\end{definition}
-%
-%\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.
-This motivates our use of a computational fuzzy conductor in \defref{def:comp fuzzy cond}.
-%We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
-%\begin{itemize}
-%\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
-%%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
-%\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
-%\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
-%\end{itemize}
-%Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.
-%\begin{lemma}
-%The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
-%\end{lemma}
-%\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.
-Let $A$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $A$.
-Define $(X,SS) \leftarrow \gen'(W)$.
-Then there must exist a distribution $Y$ with $\Hav(Y|SS) \geq \tilde{m}$ such that $\Delta((X,SS), (Y, SS))\leq \epsilon$.
-By Markov's inequality, there exists some set $B_{SS}$ such that $\Pr[ss\in B_{SS}] \geq 1/2$ and $\forall s\in B_{SS}$ one has $\Delta(X | SS = s, s ), (Y | SS = s, s)<2\epsilon$.
-Now applying Markov's inequality to $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.
-Denote by $s^*$ a value in $B_{SS}\cap B_{SS'}$~(one value must exist).
-Then $\Delta((X | SS =s^* , s^*), (Y| SS = s^*, s^*))\leq 2\epsilon$ and $\Hoo(Y|SS=s^*)\geq \tilde{m}-1$.
-Denote by the set $A'$ the possible values of $X$ when $SS=s^*$.
-For the statistical distance property to hold, $|A'| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.
-Associate with every $x\in A'$ some $w\in S$ which could have produced $x$ with nonzero probability given $SS=s^*$, and call this map $C$.
-$C$ defines an error correcting code with the required parameters.
-%\end{proof}
 
@@
 
-\section{Proof of \lemref{lem:info theory sec}}
-\begin{proof}
+\section{Analysis of \consref{cons:info theoretic}}
+\begin{proof}[Proof of \lemref{lem:info theory sec}]
 Let $W\in \mathcal{W}$.
@@
 
+\section{Analysis of \consref{cons:sampling}}
+\label{sec:analysis sampling}
+\subsection{Security}
+The proof of security for \consref{cons:sampling} uses the definition of block unguessable distributions~(\defref{def:block guessable}).
+This definition is adaptive and discussed in \apref{sec:characterize}.
+We show the security of \consref{cons:sampling}:
+\begin{itemize}
+\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
+\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
+\item The outputs $V_1,..., V_\ell$ are a block unguessable distribution.  This is made formal in the following corollary:
+\begin{corollary}
+\label{cor:v are unguessable}
+Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
+Take any $q=\poly(n)$.
+For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
+\end{corollary}
+\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable distribution.
+\end{itemize}
+%We now return to showing \thref{thm:sampling}.  
+%In order to show security \consref{cons:sampling}, we
+%show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
+We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
+Then security essentially follows from the security of \consref{cons:first construction}.
+%follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
+%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
+%By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
+%We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
+Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
+%be some particular outcome.
+%
+%Intuitive once all $V_i$ all simultaneously have good entropy, then the obfuscations will never be unlocked.
+%%In ~\clref{cl:all blocks entropy} we show that any distribution where each individual block has super-logarithmic min-entropy forms a unguessable block distribution.
+
+\noindent
+We now present the proofs of Lemmas \ref{lem:sampling works} and \ref{lem:samp unguess}.
+
+\begin{proof}[{\large Proof of \lemref{lem:sampling works}}]
+Consider some fixed $i$.
+Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
+Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
+
+\begin{claim}
+\label{cl:vi have entropy}
+\[
+\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
+\]
+\end{claim}
+\begin{proof}
+Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
+We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
+Then
+\begin{align*}
+\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
+&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
+\end{align*}
+Taking the negative logarithm of both sides we have that
+\begin{align*}
+\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
+&\ge \sum_{j_k\in J} \alpha = \alpha X
+\end{align*}
+This completes the proof of \clref{cl:vi have entropy}.
+\end{proof}
+
+We note that $X$ is distributed according to the hypergeometric distribution,
+and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
+Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
+
+\bnote{this can also be tightened.}
+Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
+ \[
+\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
+\]
+\end{proof}
+
+\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]
+
+\lnote{I need to check this}
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable distribution.
+The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .
+Let $W$ be a $(q, \alpha'' = \omega(\log n), 0)$-unguessable block distribution.
+Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
+
+Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
+Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
+\[
+| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
+\]
+Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
+\[I_{v_1,..., v_\ell, r}(x, j) =
+\begin{cases}
+r & v_i = x\\
+\perp & \text{otherwise.}
+\end{cases}\]  
+By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
+\begin{align}
+\label{eq:dist before}
+|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+\end{align}
+We now prove $S$ cannot distinguish between $R$ and $U$.
+\begin{lemma}
+\label{lem:sim cannot distinguish samp}
+$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
+\end{lemma}
+
+\begin{proof}
+\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
+\begin{lemma}
+\label{lem:codewords in I close samp}
+Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then,
+\[
+\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}.
+\]
+\end{lemma}
+\begin{proof}
+Recall that for all $j$, $\Hav(V_j | View(S))\geq \alpha''$.
+The only information about the correct value of $r$ is contained in the query responses.
+When all responses are $\perp$ the view of $S$ is identical when presented with $r$ or $u$.
+We now show that for any value of $r$ all queries return $\perp$ with probability $1-2^{-\alpha''}$.
+Suppose not, that is suppose, the probability of at least one nonzero response is $> 2^{-(\alpha'')}$.
+
+ When there is a response other than $\perp$ for some $j$ this means that there is no remaining min-entropy in $V_j$.
+If this occurs with over $2^{-\alpha''}$ probability this violates the block unguessability of $V$~(\defref{def:block guessable}).
+By the union bound over the indices $j$ the total probability of a response other than $\perp$ is at most $\ell 2^{-\alpha''}$.
+Thus, for all $r, u$ the statistical distance is at most $\ell 2^{-\alpha''}$.
+This concludes the proof of \lemref{lem:codewords in I close samp}.
+\end{proof}
+By averaging over all points in $\zo^\kappa$ we conclude that 
+\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
+\end{proof}
+
+\noindent Now by the security of obfuscation we have that
+\begin{align}
+\label{eq:dist after}
+|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+\end{align}
+Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
+\begin{align*}
+\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
+&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
+&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
+&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
+&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
+\end{align*}
+This is a contradiction and completes the proof of \lemref{lem:samp unguess}.
+\end{proof}
+
+%\end{proof}
+\subsection{Correctness}
+\label{sec:sampling errors}
+
+%\section{Proof of \lemref{lem:sampling errors}}
+\bnote{can be tightened to $\omega(n^c \log n)$.}
+\begin{proof}[Proof of \lemref{lem:sampling errors}]
+
+Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
+$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.  
+\begin{align*}
+\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
+&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
+\end{align*}
+We then have the probability that all $v_i\neq v_i'$ as:
+\begin{align*}
+\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
+&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
+&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
+\end{align*}
+This completes the proof of \lemref{lem:sampling errors}.
+\end{proof}
+
 \section{Analysis of \consref{cons:first construction}}
 \label{sec:construction}
-In this section we present analysis of \consref{cons:first construction}.
-The following theorem states the construction is both correct and secure.
-After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
-\begin{theorem}
-\label{thm:main thm first cons}
-Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
-\end{theorem}
-\begin{proof}
-We first argue security in the following Lemma.
+\subsection{Security}
+Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.
+However, security is more complicated, the main difficulty is that the definition of block unguessable distributions~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.
+This means we must limit our indistinguishable distribution to blocks that are difficult to guess.
+Security is proved via the following lemma:
 
@@
 We give a brief outline of the proof here; the proof follows.
-\begin{proof}[Outline]
+
+\noindent \textbf{Outline:}  
 It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.
@@
 \end{itemize}
-\end{proof}
-\subsection{Proof of \lemref{lem:security of cons}}
+\begin{proof}[Proof of \lemref{lem:security of cons}]
 \label{app:security of main cons}
-\begin{proof}
+
 \lnote{I need to check this}
@@
 
-\subsection{Correctness of \consref{cons:first construction}}
+\subsection{Correctness}
 We now argue correctness of \consref{cons:first construction}.
@@
 Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
-\end{proof}
-
-\subsection{Discussion of \consref{cons:first construction}}
-\label{sec:discussion}
-\lnote{I did not check this calculation -- will do}
-To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
-\[
-\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
-\]
-
-We consider what entropy is necessary for security.
-The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
-For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
-This yields:
-\[
-\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
-
-\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
-
-If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
-
-%\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block).
-Do we need it?} There are three major drawbacks to \consref{cons:first construction}.
-First, we require blocks to be super-polynomial in size.
-Second, we only obtain a single bit from each block.
-Third, since each block is individually obfuscated, we leak information about individual blocks if they can be guessed.
-To compensate for this leakage, we need most\lnote{just some linear fraction, not most, right?
-and, in fact, isn't just one block enough given our repeated use argument which we haven't really made yet?} blocks to be unguessable given equality queries.
-Our second construction addresses this last weakness.
-
-\section{Proof of \lemref{lem:sampling works}}
-\label{sec:proof of sampling lemma}
-\begin{proof}
-Consider some fixed $i$.
-Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
-Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
-
-\begin{claim}
-\label{cl:vi have entropy}
-\[
-\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
-\]
-\end{claim}
-\begin{proof}
-Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
-We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
-Then
-\begin{align*}
-\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
-&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
-\end{align*}
-Taking the negative logarithm of both sides we have that
-\begin{align*}
-\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
-&\ge \sum_{j_k\in J} \alpha = \alpha X
-\end{align*}
-This completes the proof of \clref{cl:vi have entropy}.
-\end{proof}
-
-We note that $X$ is distributed according to the hypergeometric distribution,
-and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
-Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
-
-\bnote{this can also be tightened.}
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
- \[
-\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
-\]
-\end{proof}
-
-\section{Proof of \lemref{lem:samp unguess}}
-\label{sec:sampling unguess}
-The proof of \lemref{lem:samp unguess} is similar to the proof of \lemref{lem:security of cons}.
-The main difference is the oracle provided to the unbounded simulator $S$.
-Instead repeating the entire proof, we show the following lemma~(analogous to \lemref{lem:codewords in I close}).
-The ``computational'' part of the proof follows similarly by the definition of VGB obfuscation.
-\begin{lemma}
-Let $S$ be an unbounded simulator.
-Let $V$ be a $(q, \alpha = \omega(\log n), 0)$-block unguessable distribution and let $I_{(V, R)}(i, x_i')=\begin{cases} R & v_i = x_i \\ \perp & \text{otherwise}\end{cases}$ be an oracle.
-Let $r^*$ be the true output value in the oracle, then for any $u\in\zo^\kappa$,
-\[
-\Delta(S^{I_{V, R}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{V, R}(\cdot, \cdot)}(u, 1^{\ell \log |Z|}))\le \ell 2^{-\alpha}.
-\]
-\end{lemma}
-\begin{proof}
-Recall that for all $i, \Hav(V_i | View(S))\geq \alpha$.
-The only information about the value of $R$ is contained in query responses.
-When all responses are $\perp$ the view of $S$ is identical when presented with $r^*$ or $u$.
-We now show that for any value of $r^*$ all queries return $\perp$ with probability $1-2^{-\alpha}$.
-Suppose not, that is suppose, the probability of at least one nonzero response for some index $i$ is at least $2^{-a}$.
-When there is a response other than $\perp$ this means that $V_i$ has no remaining entropy.
-If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $F$.
-By union bound over the indices $i$, the total probability of a non-$\perp$ response is at most $\ell 2^{-\alpha}$.
-This concludes the proof.
-\end{proof}
-\section{Proof of \lemref{lem:sampling errors}}
-\label{sec:sampling errors}
-\bnote{can be tightened to $\omega(n^c \log n)$.}
-\begin{proof}
-Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.  
-\begin{align*}
-\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
-&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
-\end{align*}
-We then have the probability that all $v_i\neq v_i'$ as:
-\begin{align*}
-\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
-&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
-&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
-\end{align*}
-This completes the proof of \lemref{lem:sampling errors}.
-\end{proof}
 

### 2014-09-09 trunk/constantRate/ConstCompFuzzExt-reorg.tex
adding full proof of sampling construction, reorganized

@@
 \paragraph{Our Contributions}
-We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.
-
+We provide the first constructions of fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.
+
+\bnote{rewrite this!}
 Our first construction is secure when symbols in $w$
@@
 \paragraph{Our Approach}
+\bnote{rewrite this!}
 Our constructions are computationally secure.

### 2014-09-15 constantRate/ConstCompFuzzExt-reorg.tex
adding analysis of info theoretic construction

@@
 
-The second construction comes with an additional feature: reusability.
+\consref{cons:sampling} comes with an additional feature: reusability.
 Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.
@@
 
-\noindent Randomness condensers can be built  more efficiently than randomness extractors~(for example~\cite{dodis2013key}).
+\noindent Randomness condensers can be built  more efficiently than randomness extractors~(for example~\cite{dodis2014key}).
 
@@
 
-\subsection{Coding Theory}
-\label{sec:coding theory}
-We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
-\begin{definition}
-\label{def:hamming z channel}
-For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
-\end{definition}
-
-\begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
-} \decode(c') \neq c] \leq \delta_{code}$.
-\end{definition}
-
-\textbf{Notes:}
-Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
-Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
-These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
-The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
-See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.
-
 \subsection{Obfuscation}
@@
 
-\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+\begin{definition}[composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
 \label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
@@
 
-\section{An information-theoretic construction with $\Huse\le 0$}
+\section{Supporting more errors than entropy}
 \label{sec:info theory cons}
-\bnote{needs to be rewritten depending on ordering}
-In this section we show an information-theoretic analogue to \consref{cons:first construction}.
-%This construction can essentially be seen as replacing the computational point obfuscation with information-theoretic randomness extractors.
-Using this weaker object requires us to make a stronger assumption on our starting distribution.
-Furthermore, the important features of \consref{cons:sampling}, $\Huse \le 0$ for a small alphabet and reusability, crucially rely on computational assumptions.
-Achieving these benefits information-theoretically is an open question.
-We will construct an information-theoretic fuzzy conductor which can be converted to a fuzzy extractor using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
-
-The main idea of this construction is to first condense entropy from each block of the source and then apply a secure sketch to the extracted information.
-Intuitively, we are then able from a large alphabet while paying entropy loss on the smaller alphabet.
-%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
+In this section we show an information-theoretic fuzzy conductor that supports more errors than entropy.
+Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
+The main idea of this construction is to condense entropy from each block of the source and then apply a secure sketch to the condensed blocks.
+The main idea is to correct errors on a large alphabet~(before condensing) while paying for the error correction on a smaller alphabet~(after condensing).%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
 
@@
 \label{cons:info theoretic}
-Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.  We describe $\gen, \rep$ as follows:
+Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
 \begin{center}
@@
 \begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_\ell$
-\item For $j=1,..., \ell$:
+\item \underline{Input}: $w = w_1,..., w_\gamma$
+\item For $j=1,..., \gamma$:
 \begin{enumerate}[(i)]
@@
 \end{enumerate}
-\item Set $ss \leftarrow \sketch(v_1,..., v_\ell)$.
-\item Set $p = (ss, seed_1,..., seed_\ell)$.
+\item Set $ss \leftarrow \sketch(v_1,..., v_\gamma)$.
+\item Set $p = (ss, seed_1,..., seed_\gamma)$.
 \item Output $(v, p)$.
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\ell))$
-\item For $j=1,..., \ell$:
+\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\gamma))$
+\item For $j=1,..., \gamma$:
 \begin{enumerate}[(i)]
@@
 The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
+This construction is secure and it supports distributions with more errors than entropy~(proof is in~\apref{sec:info theory sec}).
 
@@
 \label{lem:info theory sec}
-Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
-Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).
+Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ wand let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
+Let $(\sketch, \rec)$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).
 
@@
 
-\subsection{Discussion of Information-Theoretic Construction}
-\bnote{write this}
+\subsection{When is $\Huse\le 0$?}
+
+\consref{cons:info theoretic} supports partial block sources with $\Huse\le 0$.
+The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
+The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.
+This means that the input entropy to the secure sketch is $\Theta(\gamma)$.
+Standard secure sketches correct a constant fraction of errors at a entropy loss, yielding $\tilde{m} = \Theta(\gamma)$.
+Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
+More formally:
+\[
+\Huse(W) = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma) \log |\mathcal{Z}| <0
+\]
+That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with $\Huse\le 0$.
+Furthermore, the construction has super-logarithmic output entropy since $\tilde{m} = \Theta(\gamma) = \omega(\log n)$.
 
@@
 %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
-We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
+We begin by showing that each $V_i$ is statistically close to a high entropy distribution.
 Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
@@
 
-\subsection{Discussion of \consref{cons:sampling}}
-\lnote{I need to check this}
-We now show \consref{cons:sampling} supports partial block sources with $\Huse\le 0$.
+\subsection{When is $\Huse\le 0$?}
+\consref{cons:sampling} supports partial block sources with $\Huse\le 0$.
 The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
@@
 This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+Before presenting the construction we provide some definitions from error correcting codes.
+We use slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
+The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.  
+}
+\begin{definition}
+\label{def:hamming z channel}
+For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
+\end{definition}
+
+\begin{definition}
+Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
+} \decode(c') \neq c] \leq \delta_{code}$.
+\end{definition}
 
@@
 
-\subsection{Discussion of \consref{cons:first construction}}
+\subsection{When is $\Huse\le 0$?}
 \label{sec:discussion}
 \lnote{I did not check this calculation -- will do}
-To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
+In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
+We first calculate the size of the Hamming ball.  
 \[
@@
 \]
-
-We consider what entropy is necessary for security.
 The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
@@
 \[
-\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
+\Huse (W) = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
 \]
@@
 \section{Analysis of \consref{cons:info theoretic}}
+\label{sec:info theory sec}
 \begin{proof}[Proof of \lemref{lem:info theory sec}]
@@
 
-We now argue security.  Denote by $seed$ the random variable consisting of all $\ell$ seeds and $V$ the entire string of generated $V_1,..., V_\ell$.
+We now argue security.  Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
 Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.
-We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\ell)\approx (Y, seed_1,.., seed_\ell)$.
+We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
 First note since $W$ is $(\alpha, \beta)$-partial block distribution that
-there exists a set of indices $J$ where $|J| \geq \ell - \beta$ such that the following holds:
+there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
 \[
@@
 \noindent
-By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\ell -\beta)$ where 
-\[
-(\cond(W_\ell, seed_\ell), ..., \cond(W_1, seed_1), seed_\ell,..., seed_1) \approx_{\epsilon\ell} (Z, seed_\ell,...,  seed_1).\]
+By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\gamma -\beta)$ where 
+\[
+(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\epsilon\gamma} (Z, seed_\gamma,...,  seed_1).\]
 By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
-%Note that $U_{\mathcal{Y}}^\ell$ is independent of $seed_1,..., seed_\ell$ and so $\Hav(U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p)\ge \tilde{m}$.
+%Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$.
 That is, 
 \[
-(V, seed_1,..., seed_\ell, p) \approx_{\epsilon\ell} (U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p).\]  This completes the proof.
+(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]  This completes the proof.
 \end{proof}

### 2014-09-15 trunk/constantRate/ConstCompFuzzExt-reorg.tex
modified reusability definition

@@
 We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
-We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
-
-\begin{definition}[Insider Reusable Fuzzy Extractors]
-\label{def:reusable fuzz}
-Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
+%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
+%\begin{definition}[Insider Reusable Fuzzy Extractors]
+%\label{def:reusable fuzz}
+%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
 Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
@@
 We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
-\begin{align*}
-\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
-&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
-\end{align*}
+%\begin{align*}
+%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
+%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
+%\end{align*}
+%\end{definition}
+Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.
+We first present the modified definition and then discuss the differences between our definition and that of Boyen.
+\begin{definition}[Outsider Reusable Fuzzy Extractors]
+\label{def:outsider fuzz ext}
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game~(for each $W_1\in \mathcal{W}$ and for all $i=1,..., q$):
+\begin{itemize}
+\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
+\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
+Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.
+The challenger sets $w_{i+1} = \delta_i(w_1)$.
+\item[Distinguishing] The advantage of $D$ is
+\[
+\epsilon_{sec}\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1] - \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
+\]
+where $u$ is a uniformly random string.
+\end{itemize}
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+We say that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D$ of size at most $s_{sec}$ they win the game with advantage at most $\epsilon_{sec}$.
 \end{definition}
 
-\subsection{Coding Theory}
-\label{sec:coding theory}
-We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
+\paragraph{Adapting the definition of Boyen to the computational setting:} 
+The definition of Boyen considers a single adversary.
+We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
+The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
+However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.
+Our construction satisfies this alternative adaption as well.}
+
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
+This was not allowed in the definition of Boyen as it would make security impossible.
+
+Finally, we allow the distinguishing adversary to see other keys.
+This is strictly stronger than the definition of Boyen.
+However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
+This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
+Our reusable construction~(\consref{cons:sampling}) is not insider secure.
+
+The definition is parameterized by $f_2,..., f_q$.
+This adversary implicitly defines distributions $W_2,..., W_q$~(which depend on $W_1$ and the public values $P_1,...
+P_i$).
+Security seems hopeless if fuzzy extractor is not secure on each of these distributions on their own.
+This is the only requirement we make on these functions.
+We call these types of functions admissible:
+
 \begin{definition}
-\label{def:hamming z channel}
-For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the implicit distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
 \end{definition}
-
-\begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
-} \decode(c') \neq c] \leq \delta_{code}$.
-\end{definition}
-
-\textbf{Notes:}
-Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
-Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
-These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
-The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
-See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.
 
@@
 Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
-Then \consref{cons:sampling} is $q$-reusable.
+For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
 \end{theorem}
@@
 The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
-\end{proof}
-
-\subsection{Discussion of \consref{cons:sampling}}
-\lnote{I need to check this}
-We now show \consref{cons:sampling} supports partial block sources with $\Huse\le 0$.
+The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
+\bnote{almost certainly need to say more here.  expand}
+\end{proof}
+
+\subsection{When is $\Huse\le 0$?}
+\consref{cons:sampling} supports partial block sources with $\Huse\le 0$.
 The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.

### 2014-09-15 trunk/info-bounds/FuzzyExtPossibility.tex
writing down distribution aware impossibility

@@
 For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
-We will also use an average case version of this notion~(to the best of our understanding this has not been used before).\bnote{has it?}
+We will also use an average case version of this notion~(to the best of our understanding this has not been used before):\bnote{has it?}
 \begin{definition}[Conditional Hartley Entropy]
 \label{def:conditional hartley}
-The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} 2^{-H_0(X | Y=y)})$.
+The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
 \end{definition}
@@
 
-\section{Distribution-Dependent Sketches}
+\section{Distribution-Aware  Sketches}
 In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta \le 1/2$ for $\tilde{m} =\omega(1)$.
-%Furthermore, consider $V$ as the uniform distribution over $\mathcal{V}$.
-There is no secure sketch for $\mathcal{
-\bnote{what is $t$?}\bnote{finish proof}
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
+\bnote{finish proof}
 \end{theorem}
@@
 \begin{proof}
-\bnote{need to rearrange this proof.}
 It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
@@
 Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\ell$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$ and $a_i\neq 0$.
-This type of distribution is a line in space $\mathbb{F}^\ell$.
+This type of distribution is an affine line in space $\mathbb{F}^\ell$.
 Define $V$ as the uniform distribution over all such $W$.
-Fix some $1< t < \ell$.
-It suffices to show the following:
+Furthermore, the side information $Z = a_2, b_2, ..., a_\ell, b_\ell$.
+Fix some $4\le t < \ell$.
+We then show the following:
 
 \begin{itemize}
-\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$.
+\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
 \item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
-\item For any secure sketch on $V$, $H_0(V | \sketch(V)) \le n -\log |B_t|$. 
-\item The information $Z$ is a universal hash of $V$ that is independent of $\sketch(V)$. This suffices to show that $\Hav(V| \sketch(V), Z)$ is very small.
+\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\ell-t+1)\log |\mathbb{F}|$. 
+\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
+\item For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.  Thus, $\Hav(V| \sketch(V) , Z)$ is small.
 \end{itemize}
-\begin{proposition} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\begin{proposition} 
+\label{prop:each element good} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
 \end{proposition}
@@
 \end{proof}
-\bnote{will need to define average Hartley entropy}
 \bnote{show version without error first?}
 \begin{proposition}
-Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $H_0(V | \sketch(V)) \le (\ell-t) |\mathbb{F}|n +1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\ell-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
 Dealing with imperfect correctness makes the bound more complicated.
@@
 By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t )|\mathbb{F}|$.
-Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t ) |\mathbb{F}| +1$.
+Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t +1) \log|\mathbb{F}| +1$.
 %By the Markov inequality, 
@@
 \end{proof}
-We now define the side information $Z = a_2, b_2, ..., a_\ell, b_\ell$.
-By described above the view of $\sketch, \rec$ is a uniform distribution $V$.
-Thus, the side information $Z$ is independent of $\sketch(V)$.
+We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.
+
 \begin{lemma}
-$\Hav(V| P , Z) = \Theta(1)$
+$\Hav(V | \sketch(V), Z) \le \Theta(1)$.
 \end{lemma}
 \begin{proof}
-Consider some fixed $p$.
-If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
-\[
-\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
-\]
-Then by the union bound, 
-\[
-\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
-\]
-\bnote{need to average across $P$}
-\bnote{I'm confused about what we mean by $Z$ being universal here.}
-\bnote{working here!}
+Recall that $Z$ consists of $2\ell$ coefficients and there are $(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}$ equally likely values for $Z$.
+ By described above the view of $\sketch, \rec$ is a uniform distribution $V$.
+We know show there are many possible values for $Z$.
+The only information seen by $\sketch$ algorithm is in the point $V=v$.
+The length of this point is $|\mathbb{F}|^\ell$.
+Conditioned on this information there are still many possible values for $Z$.
+That is,
+ \[
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}}{|\mathbb{F}|^\ell}\right) = \log \left( (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\right).
+ \]
+Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+This means that the $\sketch$ algorithm include points for possible $Z$ values~(other than $v$) and these values are disjoint.
+The optimum strategy is to include these values uniformly from different $Z$ values.\bnote{prove this}  This means that
+\begin{align*}
+\Hav(V | \sketch(V), Z) &\le \tilde{H}_0(V | \sketch(V) )- \log H_0(Z | V)\\
+&\le (\ell-t+1)\log |\mathbb{F}|+1 - \log (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\\
+&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-1) \log (|\mathbb{F}|-1)+1\\
+&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-2) \log |\mathbb{F}|+1\\
+&\le \Theta(1)
+\end{align*}
+ Where the last line follows for $t\ge 4$.  The fourth line follows from the third as long as $|\mathbb{F}|????$\bnote{fix this}
  \end{proof}
+%\begin{lemma}
+%$\Hav(V| P , Z) = \Theta(1)$
+%\end{lemma}
+%\begin{proof}
+%Consider some fixed $p$.
+%If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
+%\[
+%\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
+%\]
+%Then by the union bound, 
+%\[
+%\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
+%\]
+%\bnote{need to average across $P$}
+%\bnote{I'm confused about what we mean by $Z$ being universal here.}
+%\bnote{working here!}
+%\end{proof}
 %

### 2014-09-15 constantRate/ConstCompFuzzExt-reorg.tex
working on the intro

@@
 
-Fuzzy extractors consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.
-The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ comes from a high-quality distribution (traditionally, any distribution with sufficient min-entropy $m$).
+Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.
+The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
 The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\ell$ strings over some alphabet $\mathcal{Z}$).
+ The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$.
+This guarantee holds as long as $w$ comes from a high-quality distribution, which
+traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.
+
+\paragraph{Reusable Fuzzy Extractors}
+An additional desirable security property of fuzzy extractors, introduced by Boyen~\cite{Boyen2004}, is called reusability.
+This property is necessary if a user enrolls the same or correlated values multiple times.
+For example, if the source is a biometric reading, the user may have to enroll the same biometric with different organizations (after all, most users have only ten fingers and two irises).
+Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
+Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).
 
@@
 Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
-The reason for this tension is simple: if an adversary who knows $p$ can guess any $w'$ within distance $t$ of $w$, it will be able to easily obtain the true $r$ by running $\rep$.
+The reason for this tension is simple: if an adversary who knows $p$ can guess any $w'$ within distance $t$ of $w$, then it will be able to easily obtain the true $r$ by running $\rep$.
 %If $t$ is larger, then a single guess for $w'$ may be within distance $t$ of more $w$ values, thus increasing adversarial probability of winning. 
@@
 For this distribution, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
-
-More generally, let $B_t$ denote the number of points in a ball of radius $t$.
-For any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil( 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several non-overlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
+Thus, if the security guarantee of a given fuzzy extractor holds for \emph{any} source of a given min-entropy $m$ and the correctness guarantees holds for any $t$ errors, then $m$ must   be greater than $\log B_t$, where $B_t$ denotes the number of points in a ball of radius $t$.
+If a source fails this condition, we will says that it has \emph{more errors than entropy}.
+
+%More generally, for any $m$ and $t$, there is a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil( 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of the uniform distribution over all points in several non-overlapping balls of radius $t$ (the metric space must be large enough for these balls not to intersect).
 We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$.
@@
 
-Prime candidate sources for authentication have $\Huse\le 0$.
+%Prime candidate sources for authentication have $\Huse\le 0$.  
+Unfortunately, prime candidate sources for authentication have more errors than entropy. 
 As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-Daugman estimates irises contain $249$ bits of entropy~\cite{daugman2004}.
-Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-Let the outcome of this transform~(on different irises) define a distribution $w$.
-The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
-For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.
-We have the following calculation for $\Huse$:
-\[
-\Huse = \Hoo(W) - \log |B_t|
-= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx -707.
-\]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
-
-\paragraph{Our Contributions}
-We provide the first constructions of fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.
+Daugman~\cite{daugman2004} designs a transform called IrisCode (using specialized wavelets) to derive a $2048$ bit string from an iris.
+Let the outcome of this transform (on different irises) define a distribution $w$.
+The precise number of errors that must be tolerated depends on the desired false reject rate.
+Even allowing for a false reject rate of up to $80\%$ (i.e., permitting correctness to fail $80\%$ of the time), a $t$ of approximately $205$ is required.
+Thus,
+\[
+\log |B_t|
+= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
+\]
+In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+
+The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
+
+\paragraph{Our Contributions: Handling Sources with More Errors than Entropy}
+We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.
+Our constructions work for Hamming errors for strings $w$ of length $\ell$ over some alphabet $\mathcal{Z}$.
+Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
+
+Our first construction provides information-theoretic security.
+It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols.
+It requires an alphabet size that is super constant in the security parameter.
+\lnote{keep this last sentence?}
+
+We then switch to computational security to obtain constructions with additional features.
+Our second construction works for the same class of distributions as the first, but also provides reusability.
+The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
+We note that such strong reusability was shown to be impossible in information-theoretically secure fuzzy extractors~\cite[Theorem 11]{Boyen2004}.\lnote{really?
+I can't parse his theorem clearly enough} This construction, however, requires that the fraction of errors is sub constant.
+
+\lnote{stopped here}
 
@@
 We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
-\begin{align*}
-\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
-&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
-\end{align*}
+%\begin{align*}
+%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
+%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
+%\end{align*}
+%\end{definition}
+Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.
+We first present the modified definition and then discuss the differences between our definition and that of Boyen.
+\begin{definition}[Outsider Reusable Fuzzy Extractors]
+\label{def:outsider fuzz ext}
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game~(for each $W_1\in \mathcal{W}$ and for all $i=1,..., q$):
+\begin{itemize}
+\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
+\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
+Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.
+The challenger sets $w_{i+1} = \delta_i(w_1)$.
+\item[Distinguishing] The advantage of $D$ is
+\[
+\epsilon_{sec}\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1] - \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
+\]
+where $u$ is a uniformly random string.
+\end{itemize}
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+We say that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D$ of size at most $s_{sec}$ they win the game with advantage at most $\epsilon_{sec}$.
+\end{definition}
+
+\paragraph{Adapting the definition of Boyen to the computational setting:} 
+The definition of Boyen considers a single adversary.
+We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
+The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
+However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.
+Our construction satisfies this alternative adaption as well.}
+
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
+This was not allowed in the definition of Boyen as it would make security impossible.
+
+Finally, we allow the distinguishing adversary to see other keys.
+This is strictly stronger than the definition of Boyen.
+However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
+This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
+Our reusable construction~(\consref{cons:sampling}) is not insider secure.
+
+The definition is parameterized by $f_2,..., f_q$.
+This adversary implicitly defines distributions $W_2,..., W_q$~(which depend on $W_1$ and the public values $P_1,...
+P_i$).
+Security seems hopeless if fuzzy extractor is not secure on each of these distributions on their own.
+This is the only requirement we make on these functions.
+We call these types of functions admissible:
+
+\begin{definition}
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the implicit distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
 \end{definition}
@@
 The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
+The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
+\bnote{almost certainly need to say more here.  expand}
 \end{proof}

### 2014-09-15 trunk/constantRate/ConstCompFuzzExt-reorg.tex
working on intro

@@
 
-Prime candidate sources for authentication have $\Huse\le 0$.
+%Prime candidate sources for authentication have $\Huse\le 0$.  
+Unfortunately, prime candidate sources for authentication have more errors than entropy. 
 As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
-Daugman estimates irises contain $249$ bits of entropy~\cite{daugman2004}.
-Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.
-Let the outcome of this transform~(on different irises) define a distribution $w$.
-The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).
-For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.
-We have the following calculation for $\Huse$:
-\[
-\Huse = \Hoo(W) - \log |B_t|
-= 249 - \log \sum_{i=0}^{205} {2048 \choose i} \approx -707.
-\]
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining} to Daugman but it does not affect $\Huse$ dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
-
-\paragraph{Our Contributions}
-We provide the first constructions of fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.
-
-\bnote{rewrite this!}
-Our first construction is secure when symbols in $w$
+Daugman~\cite{daugman2004} designs a transform called IrisCode (using specialized wavelets) to derive a $2048$ bit string from an iris.
+Let the outcome of this transform (on different irises) define a distribution $w$.
+The precise number of errors that must be tolerated depends on the desired false reject rate.
+Even allowing for a false reject rate of up to $80\%$ (i.e., permitting correctness to fail $80\%$ of the time), a $t$ of approximately $205$ is required.
+Thus,
+\[
+\log |B_t|
+= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
+\]
+In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
+There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+
+The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
+
+\paragraph{Our Contributions: Handling Sources with More Errors than Entropy}
+We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.
+Our constructions work for Hamming errors for strings $w$ of length $\ell$ over some alphabet $\mathcal{Z}$.
+Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
+
+Our first construction provides information-theoretic security.
+It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols.
+It requires an alphabet size that is super constant in the security parameter.
+\lnote{keep this last sentence?}
+
+We then switch to computational security to obtain constructions with additional features.
+Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy.
+However, it provides reusability.
+The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
+We note that such strong reusability was shown to be impossible in information-theoretically secure fuzzy extractors~\cite[Theorem 11]{Boyen2004}.\lnote{really?
+I can't parse his theorem clearly enough} This construction, however, requires that the fraction of errors is subconstant.
+
+Our third construction removes the need for fresh entropy in the symbols. 
+It is secure when symbols in $w$
 each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
 a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
+This construction can correct a constant fraction of errors.
+However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
+
+%\bnote{rewrite this!}
+%Our first construction is secure when symbols in $w$ each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated.
+Moreover, a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
 This construction can correct a constant fraction of errors~($\Theta(\ell)$).
 However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
-
-We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
+%
+%We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
 Our second construction supports an arbitrary alphabet size~(though it only achieves $\Huse\le 0$ when the alphabet size is super-constant).
 However, these improvements come at a price to error-tolerance: it tolerates a sub-constant fraction of errors~($o(\ell)$).
-
-\consref{cons:sampling} comes with an additional feature: reusability.
+%
+%\consref{cons:sampling} comes with an additional feature: reusability.
 Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.

### 2014-09-16 constantRate/ConstCompFuzzExt-reorg.tex
pushing constructions forward

@@
 \title{Key Derivation From Noisy Sources With More Errors Than Entropy}
-\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
-work was sponsored by the Department of the Air Force under Air Force
-Contract
-\#FA8721-05-C-0002.  Opinions,
-interpretations, conclusions and recommendations are those of the author
-and
-are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
+%\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
+%work was sponsored by the Department of the Air Force under Air Force
+%Contract
+%\#FA8721-05-C-0002.  Opinions,
+%interpretations, conclusions and recommendations are those of the author
+%and
+%are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
 
@@
 We then switch to computational security to obtain constructions with additional features.
-Our second construction works for the same class of distributions as the first, but also provides reusability.
+Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy.
+However, it provides reusability.
 The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
 We note that such strong reusability was shown to be impossible in information-theoretically secure fuzzy extractors~\cite[Theorem 11]{Boyen2004}.\lnote{really?
-I can't parse his theorem clearly enough} This construction, however, requires that the fraction of errors is sub constant.
-
-\lnote{stopped here}
-
-\bnote{rewrite this!}
-Our first construction is secure when symbols in $w$
+I can't parse his theorem clearly enough} This construction, however, requires that the fraction of errors is subconstant.
+
+Our third construction removes the need for fresh entropy in the symbols. 
+It is secure when symbols in $w$
 each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
 a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
+This construction can correct a constant fraction of errors.
+However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
+
+%\bnote{rewrite this!}
+%Our first construction is secure when symbols in $w$ each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated.
+Moreover, a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
 This construction can correct a constant fraction of errors~($\Theta(\ell)$).
 However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
-
-We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
+%
+%We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
 Our second construction supports an arbitrary alphabet size~(though it only achieves $\Huse\le 0$ when the alphabet size is super-constant).
 However, these improvements come at a price to error-tolerance: it tolerates a sub-constant fraction of errors~($o(\ell)$).
-
-\consref{cons:sampling} comes with an additional feature: reusability.
+%
+%\consref{cons:sampling} comes with an additional feature: reusability.
 Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.
@@
 \end{tabular}
-\caption{Summary of new constructions.  All constructions support families of distributions with $\Huse \le 0$.}
+\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
 \label{tab:upper bounds}
@@
 
-In this section we present our paradigm for constructing computational fuzzy extractors.
+In this section we define computational fuzzy extractors.
 Definitions for information-theoretic fuzzy extractors can be found in the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.
 The definition of computational fuzzy extractors allows for a small probability of error.
-Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+%Let $\mathcal{M}$ be a metric space with distance function $\dis$.
 
@@
 In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
-In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.
-
-Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: using a fuzzy conductor and a privacy amplification component or analyzing the information-reconciliation and privacy amplifications components together.
-%We both approaches, \consref{use each approach~(in \secref{sec:construction} and \secref{sec:sampling} respectively).
-%The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.
-%In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.
-We will use approaches: \consref{cons:info theoretic} and \consref{cons:first construction} use fuzzy conductors and privacy amplification and \consref{cons:sampling} achieves both tasks simultaneously.
-%We use a computational version of a fuzzy conductor.
-We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
-\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
-\label{def:hill ent}
-Let $(W, S)$ be a pair of random variables.  $W$ has
-\emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
-\end{definition} 
-We now define a computational fuzzy conductor and a (computational)~randomness extractor.
-A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-\begin{definition}
-\label{def:comp fuzzy cond}
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
-\begin{itemize}
-\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
-\end{itemize}
-\end{definition}
-\noindent \textbf{Note: } Replacing HILL entropy with average min-entropy gives an \emph{information-theoretic fuzzy conductor}.
-We will use this notion for our information-theoretic construction \secref{sec:info theory cons}.
-
-\iffalse
-\begin{definition}
-\label{def:comp fuzzy cond}
-Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties (the first two properties are the same as in \defref{def:comp fuzzy extractor}, with $x$ replacing $r$):
-\begin{itemize}
-\item The generate procedure $\gen$ on input $w\in \mathcal{M}$ outputs a string $x\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
-\item The reproduction procedure $\rep$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(x, p)\leftarrow \gen(w)$, then $\Pr[\rep(w',p) = x] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
-If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep$.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.
-That is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
-\end{itemize}
-\end{definition}
-\fi
-
-A computational extractor is the adaption of a randomness extractor to the computational setting.
-Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained.
-We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
-\begin{definition}
-Let $\chi$ be a finite set.
-A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
-of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon$.
-\end{definition}
-
-Combining a computational fuzzy conductor and an appropriate computational extractor yields a computational fuzzy extractor~(proof in \apref{sec:cond and cext}):
-
-\begin{lemma}
-\label{lem:cond and cext}
-Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
-Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.
-Define $(\gen, \rep)$ as:
-\begin{itemize}
-\item $\gen(w; seed)$ (where $seed\in \zo^d$): run $(r', p')= \gen'(w)$ and output $r = \cext(r'; seed)$, $p = (p', seed)$. 
-\item $\rep(w', (p', seed)):$ run $r' = \rep'(w'; p')$ and output $r = \cext(r'; seed)$.
-\end{itemize}
-Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
-\end{lemma}
-
-\subsubsection{Information-Theoretic Definitions}
-In this section we review additional definitions that will be used for our information-theoretic construction in \secref{sec:info theory cons}.
-\begin{definition}
-\label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
-\begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
-\end{definition}
-
-\begin{definition}
-\label{def:conductor}
-A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
-\end{definition}
-
-\noindent Randomness condensers can be built  more efficiently than randomness extractors~(for example~\cite{dodis2014key}).
-
-%\begin{definition}
-%\label{def:fuzzy conductor}
-%A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-fuzzy conductor that is $\epsilon$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following condition:
-%\begin{itemize}
-%\item For any distribution $W\in \mathcal{W}$, the string $r$ has is close to a distribution with average min-entropy conditioned on $P$.
-That is there exists a distribution $Y$ with $\Hav(Y | P)\ge \tilde{m}$ such that $(R ,P)\approx_\epsilon (Y, P)$.
-%\end{itemize}
-%\end{definition}
+In Constructions~\ref{cons:sampling} and~\ref{cons:first construction} it is crucial that $w'$ is chosen independently of the outcome of \gen.
+
+Information-theoretic fuzzy extractors are obtained by replacing computational distance by statistical distance.
+We do make a second definitional modification.
+The standard definition of information-theoretic fuzzy extractors considers $\mathcal{W}$  consisting of all distributions of a given entropy.
+As described in the introduction, it is impossible to provide security for all distributions with more errors than entropy.
+Thus, in both the computational and information-theoretic settings we consider arbitrary families of distributions.
 
@@
 This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
-There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).
-Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.
-Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
-For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.
-
-\paragraph{Previous Results}
+Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).
+Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).
+Boyen constructs a outsider reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
+Boyen also transforms this construction in an insider secure construction using random oracles.
+\paragraph{Previous Negative Results}
 
@@
 Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
-They show in the setting of unbounded reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.
-In particular, they show how any information-theoretic fuzzy extractor secure with unbounded reuse can be transformed into their construction.
-However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
-
-However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
-There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
+They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.
+This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.
+There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
+Their result can be interpreted as saying that reusability is impractical.
+
+However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
+There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
 The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.
@@
 %\end{definition}
-Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.
-We first present the modified definition and then discuss the differences between our definition and that of Boyen.
+Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss definitional differences in \apref{sec:comparing reusability}.
+
 \begin{definition}[Outsider Reusable Fuzzy Extractors]
 \label{def:outsider fuzz ext}
-Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game~(for each $W_1\in \mathcal{W}$ and for all $i=1,..., q$):
-\begin{itemize}
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$ and fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
+\begin{enumerate}%[leftmargin=-.6in]
 \item[Sampling] The challenger samples $w_1\leftarrow W_1$.
@@
 where $u$ is a uniformly random string.
-\end{itemize}
+\end{enumerate}
 Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
@@
 \paragraph{Adapting the definition of Boyen to the computational setting:}
-The definition of Boyen considers a single adversary.
-We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
-The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
-However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.
-Our construction satisfies this alternative adaption as well.}
-
-Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
-This was not allowed in the definition of Boyen as it would make security impossible.
-
-Finally, we allow the distinguishing adversary to see other keys.
-This is strictly stronger than the definition of Boyen.
-However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
-This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
-Our reusable construction~(\consref{cons:sampling}) is not insider secure.
 
@@
 The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}.
-This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at most a polynomial number of oracle queries to the function.
-In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input.
-Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
-They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
-
-\begin{definition}[composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
-\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
-\begin{enumerate}
-\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
-\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
-\[
-|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
-\]
-where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
-\end{enumerate}
-\end{definition}
-For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
-When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
-
-%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
-%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
-Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
-Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
-In order to provide any meaningful security guarantee, the source distribution must be restricted.
-See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
+This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at a polynomial number of oracle queries to the function.
+VGB obfuscators for point functions and digital lockers are constructible from specific number-theoretic assumptions or by strong assumptions on hash functions.
+We provide more details and a formal definition in \apref{sec:obfuscation def}.
 
@@
 \label{sec:info theory cons}
-In this section we show an information-theoretic fuzzy conductor that supports more errors than entropy.
-Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
-The main idea of this construction is to condense entropy from each block of the source and then apply a secure sketch to the condensed blocks.
-The main idea is to correct errors on a large alphabet~(before condensing) while paying for the error correction on a smaller alphabet~(after condensing).%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
+In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy.
+%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
+The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks.
+We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.
+A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.
+Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).
+\begin{definition}
+\label{def:conductor}
+A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
+\end{definition}
+
+The main idea of the construction is that errors are ``corrected'' on the large alphabet~(before condensing) while the entropy loss for the error correction is incurred on a smaller alphabet~(after condensing).
 
@@
 \end{enumerate}
-\item Set $ss \leftarrow \sketch(v_1,..., v_\gamma)$.
-\item Set $p = (ss, seed_1,..., seed_\gamma)$.
-\item Output $(v, p)$.
+\item Set $(r, p') \leftarrow \gen(v_1,..., v_\gamma)$.
+\item Set $p = (p', seed_1,..., seed_\gamma)$.
+\item Output $(r, p)$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\gamma))$
+\item \underline{Input}: $(w', p = (p', seed_1,..., seed_\gamma))$
 \item For $j=1,..., \gamma$:
@@
 \end{enumerate}
-\item Output $v = \rec(v', ss)$.
+\item Output $r = \rep'(v', ss)$.
 \end{enumerate}
@@
 \label{lem:info theory sec}
-Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ wand let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
-Let $(\sketch, \rec)$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).
+%Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-average case randomness conductor.
+Let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.
+Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.
 
@@
 
-\subsection{When is $\Huse\le 0$?}
-
-\consref{cons:info theoretic} supports partial block sources with $\Huse\le 0$.
+\subsection{More errors than entropy}
+
+In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.
 The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
 The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.
-This means that the input entropy to the secure sketch is $\Theta(\gamma)$.
-Standard secure sketches correct a constant fraction of errors at a entropy loss, yielding $\tilde{m} = \Theta(\gamma)$.
+This means that the input entropy to the fuzzy extractor is $\Theta(\gamma)$.
+We assume that the new alphabet $\mathcal{Y}$ is of constant size.
+Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.
 Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
@@
 \[
-\Huse(W) = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma) \log |\mathcal{Z}| <0
-\]
-That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with $\Huse\le 0$.
-Furthermore, the construction has super-logarithmic output entropy since $\tilde{m} = \Theta(\gamma) = \omega(\log n)$.
-
-\section{Achieving Reusability \& $\Huse\le 0$}
+\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) <  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
+\]
+That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.
+
+\section{Adding reusability}
 \label{sec:sampling}
-In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with $\Huse \le 0$.
-In this section we show that computational techniques allow for additional desirable properties.
+In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with more errors than entropy.
 Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.
-This is known to be impossible in the information-theoretic setting.
-%\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.
-Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.
-In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously, at the price of  decreasing the effective error tolerance.
-%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).
-
-The main idea is to sample a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscate the concatenation of these blocks.
+
+The construction samples a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscates the concatenation of these blocks.
 Denote this concatenated value by $V_1$.
@@
 The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
-Indeed, this is the property that allows this fuzzy extractor to be reusable~(we define reusability in \defref{def:reusable fuzz}).
+This is the property that allows reusability.
 
@@
 %We now return to showing \thref{thm:sampling}.  
-In this section we briefly describe why \consref{cons:sampling} is secure.  A proof of security appears \apref{sec:analysis sampling}.  
-In order to show security \consref{cons:sampling}, we
-show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
+In this section we outline security of \consref{cons:sampling}.  A proof of security appears in\apref{sec:analysis sampling}.  
+With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
 Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
@@
 
-Once all $V_i$ all simultaneously have good entropy, the adversary will never see anything but $\perp$ as an output from the obfuscations~(with overwhelming probability).
+Once all $V_i$ all simultaneously have good entropy, the adversary only sees $\perp$ as an output from the obfuscations~(with overwhelming probability).
 If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.
@@
 \label{sec:correct sampling}
-We are encoding the entire key in each obfuscation.
+We encode the entire key in each obfuscation.
 For correctness, at least one of the repeated readings must be correct with overwhelming probability.
@@
 Let all the variables be as in \thref{thm:sampling}.
- Then $\Pr[\forall i, v_i\neq v_i'] <1 - \ngl(n)$, where the probability is over the coins of $\gen$.  
+ Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.  
 \end{lemma}
@@
 We consider a bounded $q = \poly(n)$ number of reuses.
-For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator must still be able to simulate.
-Thus, given sufficiently strong reusability we achieve the following stronger result:
+For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.
+Thus, given sufficiently strong reusability we achieve the following result:
 
@@
 
-\subsection{When is $\Huse\le 0$?}
-\consref{cons:sampling} supports partial block sources with $\Huse\le 0$.
+\subsection{More errors than entropy?}
+In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.
 The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
@@
 \[
-\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
-\]
-That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.
-We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.
-However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.
+\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) < t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  
+\]
+That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.
+We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
+However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.
 
 \section{Allowing Correlated Symbols}
-In the previous two sections, we presented constructions that supported $\Huse\le 0$ for restricted classes of distributions.
+In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.
 Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.
-In this section, we present a computational construction that allows for correlation between symbols while still supporting $\Huse \le 0$ and correcting a constant fraction of errors.
+In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
 This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+
 Before presenting the construction we provide some definitions from error correcting codes.
@@
 
+\bnote{shorten this discussion?}
 The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
@@
 In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
-The following theorem states the construction is both correct and secure.  %After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
+
+Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.
+The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).
+However, we can show that $c$ looks like it has entropy.
+We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
+\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
+\label{def:hill ent}
+Let $(W, S)$ be a pair of random variables.  $W$ has
+\emph{HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
+\end{definition} 
+We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).
+We call this object a computational fuzzy conductor.
+It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+\begin{definition}
+\label{def:comp fuzzy cond}
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
+\begin{itemize}
+\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
+\end{itemize}
+\end{definition}
+Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
+The following theorem states the construction is a computational fuzzy conductor.  %After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
 \begin{theorem}
@@
 
-\subsection{When is $\Huse\le 0$?}
+\subsection{More errors than entropy?}
 \label{sec:discussion}
-\lnote{I did not check this calculation -- will do}
 In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
@@
 \[
-\Huse (W) = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
-\]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
+\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  <\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right) -  \ell \omega(\log n) .
+\]
+When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy.
+Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
 
@@
 
+\section{Further Definitions}
+\subsection{Computational Fuzzy Conductors}
+\label{sec:further defs}
+A computational extractor is the adaption of a randomness extractor to the computational setting.
+Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained.
+We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
+\begin{definition}
+Let $\chi$ be a finite set.
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
+of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon$.
+\end{definition}
+
+Combining a computational fuzzy conductor and an appropriate computational extractor yields a computational fuzzy extractor:
+
+\begin{lemma}
+\label{lem:cond and cext}
+Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
+Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.
+Define $(\gen, \rep)$ as:
+\begin{itemize}
+\item $\gen(w; seed)$ (where $seed\in \zo^d$): run $(r', p')= \gen'(w)$ and output $r = \cext(r'; seed)$, $p = (p', seed)$. 
+\item $\rep(w', (p', seed)):$ run $r' = \rep'(w'; p')$ and output $r = \cext(r'; seed)$.
+\end{itemize}
+Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
+\end{lemma}
+
+\begin{proof}
+It suffices to show if there is some distinguisher $D'$ of size $s'$ where
+\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
+ \[
+ \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
+ \]
+Let $D'$ be such a distinguisher.  That is,
+\[
+\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D$ as follows.
+On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.
+Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
+Then we have the following:
+\begin{align*}
+\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
+&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
+&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
+\end{align*}
+Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
+\end{proof}
+
+\subsection{Adapting Reusability to the Computational Setting}
+\label{sec:comparing reusability}
+
+The definition of Boyen considers a single adversary.
+We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
+The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
+However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.
+Our construction satisfies this alternative adaption as well.}
+
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
+This was not allowed in the definition of Boyen as it would make security impossible.
+
+Finally, we allow the distinguishing adversary to see other keys.
+This is strictly stronger than the definition of Boyen.
+However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
+This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
+Our reusable construction~(\consref{cons:sampling}) is not insider secure.
+
+\subsection{Obfuscation}
+\label{sec:obfuscation def}
+
+In this section, we give a formal definition of the required notion of obfuscation.  
+We require that the obfuscation is composable and secure with respect to auxiliary input.
+Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
+
+\begin{definition}[composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
+\begin{enumerate}
+\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\[
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
+\]
+where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
+\end{enumerate}
+\end{definition}
+For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
+When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
+
+%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
+%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
+Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
+Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
+In order to provide any meaningful security guarantee, the source distribution must be restricted.
+See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
 \section{Characterizing unguessable block distributions}
@@
 
-\section{Proof of \lemref{lem:cond and cext}}
-\label{sec:cond and cext}
-\lnote{I need to check this}
-\begin{proof}
-It suffices to show if there is some distinguisher $D'$ of size $s'$ where
-\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
- then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
- \[
- \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
- \]
-Let $D'$ be such a distinguisher.  That is,
-\[
-\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
-\]
-Then define $D$ as follows.
-On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.
-Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
-Then we have the following:
-\begin{align*}
-\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
-&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
-&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
-&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
-\end{align*}
-Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
-\end{proof}
-
 \section{Analysis of \consref{cons:info theoretic}}
@@
 Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
-Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.
-
-We now argue security.  Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
-Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.
-We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
+Then by correctness of $(\gen', \rep')$, $\Pr[(r, p)\leftarrow \gen'(v) \wedge r'\leftarrow \rep(v',p) \wedge r' = r]\ge 1-\delta$.
+
+We now argue security.
+Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
+To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{text}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
+The lemma then follows by the security of $(\gen', \rep')$.
+
+We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
 First note since $W$ is $(\alpha, \beta)$-partial block distribution that
@@
 Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that 
-\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-}) \approx_{\epsilon} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1})\]
+\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1})\]
 and since $(seed_1,..., seed_{j_1})$ are independent of these values
-\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
+\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
 consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
@@
 \begin{align*}
-(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\epsilon} (Z_{j_1}, seed_{j_1},..., seed_1)
+(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\gamma \epsilon_{cond}} (Z_{j_1}, seed_{j_1},..., seed_1)
 \end{align*}
@@
 \noindent
-By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\gamma -\beta)$ where 
-\[
-(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\epsilon\gamma} (Z, seed_\gamma,...,  seed_1).\]
-By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
+By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \tilde{\alpha}(\gamma -\beta)$ where 
+\[
+(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\gamma \epsilon_{cond}} (Z, seed_\gamma,...,  seed_1).\]
+%By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
 %Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$.
-That is, 
-\[
-(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]  This completes the proof.
+%That is, 
+%\[
+%(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]  
+This completes the proof.
 \end{proof}

### 2014-09-16 trunk/constantRate/ConstCompFuzzExt-reorg.tex
minor updates and bib cleanup

@@
 However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
-Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
+Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{brakerski2014virtual,barak2014protecting} for all programs.
 However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
@@
 \end{definition}
-
-\paragraph{Adapting the definition of Boyen to the computational setting:} 
-The definition of Boyen considers a single adversary.
-We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
-The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
-However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.
-Our construction satisfies this alternative adaption as well.}
-
-Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
-This was not allowed in the definition of Boyen as it would make security impossible.
-
-Finally, we allow the distinguishing adversary to see other keys.
-This is strictly stronger than the definition of Boyen.
-However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
-This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
-Our reusable construction~(\consref{cons:sampling}) is not insider secure.
 
@@
 \label{sec:info theory cons}
-In this section we show an information-theoretic fuzzy conductor that supports more errors than entropy.
-Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
-The main idea of this construction is to condense entropy from each block of the source and then apply a secure sketch to the condensed blocks.
-The main idea is to correct errors on a large alphabet~(before condensing) while paying for the error correction on a smaller alphabet~(after condensing).%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).
+In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy.
+%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
+The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks.
+We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.
+A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.
+Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).
+\begin{definition}
+\label{def:conductor}
+A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
+\end{definition}
+
+The main idea of the construction is that errors are ``corrected'' on the large alphabet~(before condensing) while the entropy loss for the error correction is incurred on a smaller alphabet~(after condensing).
 
@@
 \label{lem:info theory sec}
-Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ wand let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.
-Let $(\sketch, \rec)$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).
+%Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
+Let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
+Most known constructions of fuzzy extractors are average-case fuzzy extractors.
+For simplicity we refer to $\gen', \rep'$ as simply a fuzzy extractor.}  Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.
 
@@
 
+\section{Further Definitions}
+\subsection{Computational Fuzzy Conductors}
+\label{sec:further defs}
+A computational extractor is the adaption of a randomness extractor to the computational setting.
+Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained.
+We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
+\begin{definition}
+A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
+of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon$.
+\end{definition}
+
+Combining a computational fuzzy conductor and a computational extractor yields a computational fuzzy extractor:
+
+\begin{lemma}
+\label{lem:cond and cext}
+Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
+Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.
+Define $(\gen, \rep)$ as:
+\begin{itemize}
+\item $\gen(w; seed)$ (where $seed\in \zo^d$): run $(r', p')= \gen'(w)$ and output $r = \cext(r'; seed)$, $p = (p', seed)$. 
+\item $\rep(w', (p', seed)):$ run $r' = \rep'(w'; p')$ and output $r = \cext(r'; seed)$.
+\end{itemize}
+Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
+\end{lemma}
+
+\begin{proof}
+It suffices to show if there is some distinguisher $D'$ of size $s'$ where
+\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
+ then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
+ \[
+ \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
+ \]
+Let $D'$ be such a distinguisher.  That is,
+\[
+\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
+\]
+Then define $D$ as follows.
+On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.
+Note that $|D| \approx s' + |\cext| +d= s_{cond}$.
+Then we have the following:
+\begin{align*}
+\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
+&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
+&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
+&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
+\end{align*}
+Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
+\end{proof}
+
+\subsection{Adapting Reusability to the Computational Setting}
+\label{sec:comparing reusability}
+
+The definition of Boyen considers a single adversary.
+We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
+The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
+However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.
+Our construction satisfies this alternative adaption as well.}
+
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
+This was not allowed in the definition of Boyen as it would make security impossible.
+
+Finally, we allow the distinguishing adversary to see other keys.
+This is strictly stronger than the definition of Boyen.
+However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
+This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
+Our reusable construction~(\consref{cons:sampling}) is not insider secure.
+
+\subsection{Obfuscation}
+\label{sec:obfuscation def}
+
+In this section, we give a formal definition of the required notion of obfuscation.  
+We require that the obfuscation is composable and secure with respect to auxiliary input.
+Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
+
+\begin{definition}[composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
+\begin{enumerate}
+\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\[
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
+\]
+where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
+\end{enumerate}
+\end{definition}
+For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
+When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
+
+%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.
+%Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.
+Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.
+Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.
+In order to provide any meaningful security guarantee, the source distribution must be restricted.
+See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
 \section{Characterizing unguessable block distributions}
@@
 Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
-Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.
-
-We now argue security.  Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
-Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.
-We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
+Then by correctness of $(\gen', \rep')$, $\Pr[(r, p)\leftarrow \gen'(v) \wedge r'\leftarrow \rep(v',p) \wedge r' = r]\ge 1-\delta$.
+
+We now argue security.
+Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
+To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{text}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
+The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
+Most known constructions are average-case and we omit this notation.}
+
+We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
 First note since $W$ is $(\alpha, \beta)$-partial block distribution that
@@
 Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
-\[I_{v_1,..., v_\ell, r}(x, j) =
+\[I_{v_1,..., v_\ell, r}(x, i) =
 \begin{cases}

### 2014-09-16 trunk/constantRate/ConstCompFuzzExt-reorg.tex
wrote our approach in the intro

@@
 
-\paragraph{Our Contributions: Handling Sources with More Errors than Entropy}
+\paragraph{Our Contributions}
 We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.
@@
 \paragraph{Our Approach}
-\bnote{rewrite this!}
-Our constructions are computationally secure.
+%\bnote{rewrite this!}
+%Our constructions are computationally secure.
 Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).
 
+%Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
+
 Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
-
-Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
+As shown by~\cite{DBLP:journals/siamcomp/DodisORS08}\lnote{specific theorem number} for the information-theoretic case and by \cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} for the computational case, this is unlikely to work for sources with more errors than entropy.
+Thus, we give up on recovering $w$.
+
+Our first construction reduces the alphabet size by hashing each input symbol (which comes from a large alphabet) into a much smaller set, so that the resulting hash value has low entropy deficiency.
+The intuition behind this approach is that it reduces the size of $B_t$ by reducing the alphabet size, but preserves a sufficient portion of the input entropy.
+The resulting string no longer has more errors than entropy.
+ We then apply any information-theoretic fuzzy extractor to the resulting string
+
+Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}.
+Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret.
+The main idea of the construction is to pick a random $r$ and then lock it up in a digital locker that is unlocked by a random subset of the symbols of $w$.
+To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$.
+Reusability follows from composability of obfuscation.
+
+Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
+Of course, hiding an entire $r$ in every locker then becomes too risky, since we do not assume that every symbol has high individual entropy.
+Instead, we hide a single bit per locker (this simplified version of a digital locker is basically point obfuscation).
+To tolerate errors, these bits come from an error correcting code.
+And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.
+
+We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
+We need a strong version of point obfuscation/digital lockers that remains secure even when several obfuscations of correlated points are composed.
+While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions.
+Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+
+%Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
 Our first construction is a \emph{computational fuzzy conductors}.
-This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
-
-Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.
+%This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
+
+%Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.
 A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
@@
 For a point program, this means hiding all partial information about the point $w$.
-We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed.
+%We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed.
 While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
@@
 
-Both of our constructions use techniques from Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
+%Both of our constructions use techniques from Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.
 Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$.
@@
 
-Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
+%Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates).
 We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then obfuscates each string of blocks.
@@
 \paragraph{Connection to General Obfuscation}
-\bnote{needs to be rewritten}
+\bnote{everything below needs to be rewritten}
 We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.

### 2014-09-16 constantRate/ConstCompFuzzExt-reorg.tex
editing intro

@@
 The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\ell$ strings over some alphabet $\mathcal{Z}$).
+The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$).
  The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$.
@@
 For example, if the source is a biometric reading, the user may have to enroll the same biometric with different organizations (after all, most users have only ten fingers and two irises).
-Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
+\bnote{ewww jokes} Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
 Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).
@@
 For this distribution, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
-Thus, if the security guarantee of a given fuzzy extractor holds for \emph{any} source of a given min-entropy $m$ and the correctness guarantees holds for any $t$ errors, then $m$ must   be greater than $\log B_t$, where $B_t$ denotes the number of points in a ball of radius $t$.
+Thus, if the security guarantee of a given fuzzy extractor holds for \emph{any} source of a given min-entropy $m$ and the correctness guarantees holds for any $t$ errors, then $m$ must   be greater than $\log |B_t|$, where $|B_t|$ denotes the number of points in a ball of radius $t$.
 If a source fails this condition, we will says that it has \emph{more errors than entropy}.
@@
 The precise number of errors that must be tolerated depends on the desired false reject rate.
-Even allowing for a false reject rate of up to $80\%$ (i.e., permitting correctness to fail $80\%$ of the time), a $t$ of approximately $205$ is required.
+Even allowing for a false reject rate of up to $80\%$ (i.e., permitting correctness to fail $80\%$ of the time),\bnote{I don't like saying this twice.
+Should either say $20\%$ true accept or correctness around $20\%$} a $t$ of approximately $205$ is required.
 Thus,
@@
 The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
-
-\paragraph{Our Contributions: Handling Sources with More Errors than Entropy}
+\bnote{this should be strengthened.
+move negative results to there.}
+
+\paragraph{Our Contributions}
 We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.
-Our constructions work for Hamming errors for strings $w$ of length $\ell$ over some alphabet $\mathcal{Z}$.
+Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$.
 Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
@@
 \paragraph{Our Approach}
-\bnote{rewrite this!}
-Our constructions are computationally secure.
+%\bnote{rewrite this!}
+%Our constructions are computationally secure.
 Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).
 
+%Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
+
 Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
-
-Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
+As shown by~\cite{DBLP:journals/siamcomp/DodisORS08}\lnote{specific theorem number} for the information-theoretic case and by \cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} for the computational case, this is unlikely to work for sources with more errors than entropy.
+Thus, we give up on recovering $w$.
+\bnote{I'm not sure I buy this argument.
+We have coding bounds, but they don't say that secure sketches won't work.}
+
+Our first construction reduces the alphabet size by hashing each input symbol (which comes from a large alphabet) into a much smaller set, so that the resulting hash value has low entropy deficiency.
+The intuition behind this approach is that it reduces the size of $B_t$ by reducing the alphabet size, but preserves a sufficient portion of the input entropy.
+The resulting string no longer has more errors than entropy.
+ We then apply any information-theoretic fuzzy extractor to the resulting string
+
+Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}.
+Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret.
+The main idea of the construction is to pick a random $r$ and then lock it up in a digital locker that is unlocked by a random subset of the symbols of $w$.
+To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$.
+Reusability follows from composable obfuscation.
+
+Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
+Of course, hiding an entire $r$ in every locker then becomes too risky, since we do not assume that every symbol has high individual entropy.
+Instead, we hide a single bit per locker (this simplified version of a digital locker is basically point obfuscation).
+To tolerate errors, these bits come from an error correcting code.
+And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.
+
+We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
+We need a strong version of point obfuscation/digital lockers that remains secure even when several obfuscations of correlated points are composed.
+While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
+However it is known how to construct composable VGB obfuscation for the class of functions we need.} of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions.
+Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+
+%Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}.
 Our first construction is a \emph{computational fuzzy conductors}.
-This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
-
-Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.
+%This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).
+
+%Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.
 A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.
@@
 \paragraph{Connection to General Obfuscation}
-\bnote{needs to be rewritten}
+\bnote{everything below needs to be rewritten}
 We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
 However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
-Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs.
+Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{brakerski2014virtual,barak2014protecting} for all programs.
 However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
@@
 \label{sec:preliminaries}
-For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.
+For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.
 For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric over vectors in $\mathcal{Z}^\ell$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
-For this metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
+For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
@@
 
-\paragraph{Adapting the definition of Boyen to the computational setting:}
-
 The definition is parameterized by $f_2,..., f_q$.
@@
 \label{def:conductor}
-A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-average case randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
+A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
 \end{definition}
@@
 %Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-average case randomness conductor.
-Let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.
-Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
+Let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
+Most known constructions of fuzzy extractors are average-case fuzzy extractors.
+For simplicity we refer to $\gen', \rep'$ as simply a fuzzy extractor.}  Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.
 
@@
 Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$. 
-%and $\gamma = \Omega(n)$.
-Let $\ell = \omega(\log(n))$ and $\eta = o(\gamma)$ be integer parameters (we will set them later).
-Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
 Let $\eta$ be a parameter, and $\mathcal{O}$ be an obfuscator for the family of digital lockers with $\kappa$-bit outputs.  Define $\gen, \rep$ as:
@@
 
-%Before we show \thref{thm:sampling} we present a simplified construction of \consref{cons:sampling}.
-This construction essentially ignores the sampling step and asks when obfuscation provides security of the obfuscated values $V_1,..., \ell$.
-Our security argument for \consref{cons:sampling} will reduce to this simplified construction.
-After presenting this simplified construction we will return to showing \thref{thm:sampling}.
-
 \subsection{Security of \consref{cons:sampling}}
 \label{ssec:sec cons sampling}
-%We now return to showing \thref{thm:sampling}.  
 In this section we outline security of \consref{cons:sampling}.  A proof of security appears in\apref{sec:analysis sampling}.  
@@
 Before presenting the construction we provide some definitions from error correcting codes.
-We use slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
-Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+We use slightly nonstandard error-correct codes over $\{0,1\}^\gamma$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
 These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
@@
 \label{def:hamming z channel}
-For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
+For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
 \end{definition}
@@
 Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
+Then a set $C$~(over $\zo^\gamma$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
 } \decode(c') \neq c] \leq \delta_{code}$.
@@
 \label{cons:first construction}
-Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.
+Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.
 Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
-Let  $C\subset \zo^\ell$ be an error-correcting code.
+Let  $C\subset \zo^\gamma$ be an error-correcting code.
 We describe $\gen, \rep$ as follows:
@@
 \begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_\ell$
+\item \underline{Input}: $w = w_1,..., w_\gamma$
 \item Sample $c\leftarrow C$.
-\item For $j=1,..., \ell$:
+\item For $j=1,..., \gamma$:
 \begin{enumerate}[(i)]
@@
 \end{enumerate}
-\item Output $(c, p)$, where $p=p_1\dots p_\ell$.
+\item Output $(c, p)$, where $p=p_1\dots p_\gamma$.
 \end{enumerate}
@@
 \item \underline{Input}: $(w', p)$
-\item For $j=1,..., \ell$:
+\item For $j=1,..., \gamma$:
 \begin{enumerate}[(i)]
@@
 A source $W = W_1| ...
-|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
 \[
@@
 \label{thm:main thm first cons}
-Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
+Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.
+Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
 \end{theorem}
@@
 \[
-\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
+\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
 \]
 The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
-For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.
+For this type of source the required entropy is $\Hoo(W) = \gamma\omega(\log n)$.
 This yields:
 \[
-\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  <\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right) -  \ell \omega(\log n) .
-\]
-When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy.
-Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
+\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  <\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
+\]
+When $t =\Theta(\gamma)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy.
+Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\gamma)$).
 
@@
 
-If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
+If $\gamma$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
 
@@
 \begin{definition}
-Let $\chi$ be a finite set.
-A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
-of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
+A function $\cext: \zo^\gamma \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
+of random variables $X, Y$ (with $X$ over $\zo^\gamma$) such that
 $\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
@@
 
-Combining a computational fuzzy conductor and an appropriate computational extractor yields a computational fuzzy extractor:
+Combining a computational fuzzy conductor and a computational extractor yields a computational fuzzy extractor:
 
@@
 \label{lem:cond and cext}
-Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.
-Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.
+Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\gamma$.
+Let $\cext:\zo^\gamma\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.
 Define $(\gen, \rep)$ as:
@@
 \end{definition}
-For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
-When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
+For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\gamma$ is the vector of obfuscated points.
+When we use digital lockers we denote the oracle provided to the simulator as $I_{v, r}(\cdot, \cdot)$ where $v = v_1,..., v_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
 
@@
 Let $W = W_1,  ...
-, W_\ell$ be a source in which all blocks $W_j$  are mutually independent.
+, W_\gamma$ be a source in which all blocks $W_j$  are mutually independent.
 Let $\alpha$ be a parameter.
-Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.
-Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |J|)$-unguessable block distribution.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |J|)$-unguessable block distribution.
+Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.
+Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block distribution.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block distribution.
 \end{claim}
@@
 \label{cl:each block from single seed}
-Let $f:\zo^e \rightarrow \mathcal{Z}^\ell$ be a function.
+Let $f:\zo^e \rightarrow \mathcal{Z}^\gamma$ be a function.
 Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.
@@
 \label{cl:all blocks entropy}
-Let $W = W_1,..., W_\ell$ be a source.
+Let $W = W_1,..., W_\gamma$ be a source.
 Suppose that for all $j$, $\Hoo(W_j)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is super-logarithmic).
@@
 \begin{claim}
-Let $p = (\poly(n))$ and let $f_1,..., f_{\ell}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.
-There is an adversary making $p\times \ell = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
+Let $p = (\poly(n))$ and let $f_1,..., f_{\gamma}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \gamma \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\gamma}), W_2 = f_2(U_{1,..., 2\gamma}),...., W_\gamma = f_\gamma(U)$.
+There is an adversary making $p\times \gamma = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
 \end{claim}
 \begin{proof}
-Let $x$ be the true value for $U_{p\times \ell}$.
+Let $x$ be the true value for $U_{p\times \gamma}$.
 We present an adversary $S$ that completely determines $x$.
@@
 This process is repeated until all of $x$ is recovered~(and thus $w$).
-%The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.
+%The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \gamma)$.
 Once $x$ has been recovered then $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
@@
 \begin{definition}
-Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.
+Let $W = W_1,..., W_\gamma$ be a source under ordering $i_1,..., i_\gamma$.
 The \emph{jump} of a block $i_j$ is $\mathtt{Jump}(i_j) = \max_{w_{i_1},..., w_{i_{j-1}}} H_0 (W_{i_j} | W_{i_1} = w_{i_1} ,..., W_{i_{j-1}} = w_{i_{j-1}})$.
@@
 \begin{claim}
-Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\ell-\beta+1)$, then $W$ is not $(q, 0, \beta)$-unguessable block distribution.
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\gamma$ such that for all $j\le \gamma-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\gamma-\beta+1)$, then $W$ is not $(q, 0, \beta)$-unguessable block distribution.
 \end{claim}
@@
 \begin{proof}
-For convenience relabel the ordering that violates the condition as $1,..., \ell$.
-We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.
-As before $S$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.
-Then $S$ queries the (at most)~$q/(\ell-\beta+1)$ possible values for $W_2 | W_1$.
-This process is repeated until $W_{\ell-\beta+1}$ is learned.
+For convenience relabel the ordering that violates the condition as $1,..., \gamma$.
+We describe an unbounded adversary that determines $W_1,..., W_{\gamma-\beta+1}$.
+As before $S$ queries the $q /\gamma$ possible values for $W_1$ and determines $W_1$.
+Then $S$ queries the (at most)~$q/(\gamma-\beta+1)$ possible values for $W_2 | W_1$.
+This process is repeated until $W_{\gamma-\beta+1}$ is learned.
 \end{proof}
@@
 To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{text}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
-The lemma then follows by the security of $(\gen', \rep')$.
+The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
+Most known constructions are average-case and we omit this notation.}
 
@@
 \end{itemize}
-%We now return to showing \thref{thm:sampling}.  
-%In order to show security \consref{cons:sampling}, we
-%show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
-We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.
-Then security essentially follows from the security of \consref{cons:first construction}.
-%follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
-%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
-%By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
-%We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).
-Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
-%be some particular outcome.
-%
-%Intuitive once all $V_i$ all simultaneously have good entropy, then the obfuscations will never be unlocked.
-%%In ~\clref{cl:all blocks entropy} we show that any distribution where each individual block has super-logarithmic min-entropy forms a unguessable block distribution.
 
@@
 Let all variables be as in \thref{thm:main thm first cons}.
-For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
+For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}( C | P ) \geq H_0(C) - \beta$.
 \end{lemma}
@@
 \lnote{I need to check this}
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.
+Let $\mathcal{O}$ be a $\gamma$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.
 Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
 Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$.
-% for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
+% for $\epsilon' = 2\epsilon_{obf} + (\gamma - \beta)2^{-(\alpha-1)}$.
 Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
@@
 \label{eq:dist before}
-|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\gamma, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|})] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \label{lem:sim cannot distinguish}
-$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
+$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})) \le (\gamma-\beta) 2^{-(\alpha+1)}$.
 \end{lemma}
@@
 \begin{proof}
-\noindent It suffices to show that for any two codewords that agree on $J^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
+\noindent It suffices to show that for any two codewords that agree on $J^c$, the statistical distance is at most $(\gamma-\beta)2^{-(\alpha+1)}$.
 \begin{lemma}
@@
 \[
-\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
+\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\gamma \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\gamma \log |Z|})) \le ( \gamma -\beta) 2^{-(\alpha+1)}.
 \]
@@
 \bnote{Leo I changed some of this under you.  It wasn't clear or probably right as written.}
-Let $W$ be a $(q, \alpha, \beta)$-block unguessable distribution.  Let $J\subset\{1,..., \ell\}$ the set of good indices.
+Let $W$ be a $(q, \alpha, \beta)$-block unguessable distribution.  Let $J\subset\{1,..., \gamma\}$ the set of good indices.
 It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.
@@
 If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
-By the union bound over the indices $j\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$.
+By the union bound over the indices $j\in J$ the total probability of a $1$ in $J$ is at most $(\gamma-\beta)2^{-\alpha+1}$.
 Recall that $c^*, c'$ match on all indices outside of $J$.
-Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.
+Thus, for all $c^*, c'$ the statistical distance is at most $(\gamma- \beta)2^{-\alpha+1}$.
 This concludes the proof of \lemref{lem:codewords in I close}.
 \end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.
+By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})) < (\gamma -\beta)2^{-(\alpha+1)}$.
 This completes the proof of \lemref{lem:sim cannot distinguish}.
@@
 \label{eq:dist after}
-|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+|\expe [D(P_1,..., P_\gamma, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})] |\leq \epsilon_{sec}/3.
 \end{align}
@@
 \begin{align*}
-\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})]| \\
-&+|\expe[S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] - \expe[S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\\
-&+|\expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] - \expe [D(P_1,..., P_\ell, C') ]|\\
-&\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
+\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\gamma, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|})]| \\
+&+|\expe[S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|})] - \expe[S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})] |\\
+&+|\expe [S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})] - \expe [D(P_1,..., P_\gamma, C') ]|\\
+&\leq \epsilon_{sec}/3+ (\gamma-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
 &\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
@@
 Let all variables be as in \thref{thm:main thm first cons}.
-The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \gamma/|\mathcal{Z}| = \ngl(n)$.
 \end{lemma}
@@
 Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$.
-The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
+The lemma follows by the union bound, since there are at most $\gamma$ such coordinates.
 \end{proof}
@@
 Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
-Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
+Therefore, \consref{cons:first construction} is correct with error at most $\gamma/|\mathcal{Z}|$.
 

### 2014-09-16 trunk/info-bounds/FuzzyExtPossibility.tex
writing down distribution aware impossibility
editing intro

@@
 \begin{theorem}
+\label{thm:imposs sketch}
 Let $n$ be a security parameter.
@@
 That is $V|p$ is a set with minimum distance at least $t$.
-By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t )|\mathbb{F}|$.
+By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t+1 )|\mathbb{F}|$.
 Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t +1) \log|\mathbb{F}| +1$.
@@
 \begin{align*}
-\Hav(V | \sketch(V), Z) &\le \tilde{H}_0(V | \sketch(V) )- \log H_0(Z | V)\\
+\tilde{H}_0(V | \sketch(V), Z) &\le \tilde{H}_0(V | \sketch(V) )- \log H_0(Z | V)\\
 &\le (\ell-t+1)\log |\mathbb{F}|+1 - \log (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\\
@@
 \end{align*}
- Where the last line follows for $t\ge 4$.  The fourth line follows from the third as long as $|\mathbb{F}|????$\bnote{fix this}
+ Where the last line follows for $t\ge 4$.  The fourth line follows from the third as long as $|\mathbb{F}|????$\bnote{fix this}\bnote{add more to this}
  \end{proof}
+
+ \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
 %\begin{lemma}
@@
 
-Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
+Canetti et al.~\cite{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
 

### 2014-09-17 trunk/constantRate/ConstCompFuzzExt-reorg.tex
adding reusability citations and intro cleaning

@@
 This property is necessary if a user enrolls the same or correlated values multiple times.
-For example, if the source is a biometric reading, the user may have to enroll the same biometric with different organizations (after all, most users have only ten fingers and two irises).
+For example, if the source is a biometric reading, the user may enroll the same biometric with different organizations.
 Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
 Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).
+Many traditional fuzzy extractors are not reusable~\cite{Boyen2004,simoens2009privacy,blanton2012non,blanton2013analysis}.
 
@@
 Let the outcome of this transform (on different irises) define a distribution $w$.
-The precise number of errors that must be tolerated depends on the desired false reject rate.
-Even allowing for a false reject rate of up to $80\%$ (i.e., permitting correctness to fail $80\%$ of the time), a $t$ of approximately $205$ is required.
+The precise number of errors that must be tolerated depends on the desired correctness.
+For correctness of around $20\%$, a $t$ of approximately $205$ is required.
 Thus,
@@
 The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
+\bnote{this should be strengthened.
+move negative results to there.}
 
@@
 We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.
-Our constructions work for Hamming errors for strings $w$ of length $\ell$ over some alphabet $\mathcal{Z}$.
+Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$.
 Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
@@
 Thus, we give up on recovering $w$.
+\bnote{I'm not sure I buy this argument.
+We have coding bounds, but they don't say that secure sketches won't work.}
 
@@
 Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret.
-The main idea of the construction is to pick a random $r$ and then lock it up in a digital locker that is unlocked by a random subset of the symbols of $w$.
+The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$.
 To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$.
-Reusability follows from composability of obfuscation.
+Reusability follows from composable obfuscation.
 
 Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Of course, hiding an entire $r$ in every locker then becomes too risky, since we do not assume that every symbol has high individual entropy.
-Instead, we hide a single bit per locker (this simplified version of a digital locker is basically point obfuscation).
+Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are easier simpler to construct than digital lockers).
 To tolerate errors, these bits come from an error correcting code.
@@
 We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
-We need a strong version of point obfuscation/digital lockers that remains secure even when several obfuscations of correlated points are composed.
-While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
-For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions.
+We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is 
+%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
+However it is known how to construct composable VGB obfuscation for the class of functions we need.}
+composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}.
 Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
@@
 \paragraph{Connection to General Obfuscation}
-\bnote{everything below needs to be rewritten}
+ \onote{write this!!!}
 We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
@@
 \paragraph{Open Problems}
-Our first construction achieves a constant fraction error tolerance but at the cost of a large alphabet size.
+All of our constructions support more errors than entropy by tolerating errors in a large alphabet and performing error correction over a different smaller alphabet.
+This approach seems limited to larger alphabets~(all of our constructions require a super-constant size alphabet).
+Supporting distributions with more errors than entropy over small alphabets is an important open problem.
+
+%Our first construction achieves a constant fraction error tolerance but at the cost of a large alphabet size.
 Our second construction reduces the alphabet size significantly but only achieves a sub-constant error tolerance.
@@
 
-Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
+%Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
 The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$.
@@
 \medskip
-The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.
+\paragraph{Organization }
+The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.
+Present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.
 
@@
 \label{sec:reusable}
-\bnote{some of this should probably be moved to the introduction}
 
@@
 \label{def:outsider fuzz ext}
-Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$ and fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
+Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
 \begin{enumerate}%[leftmargin=-.6in]
@@
 \item[Distinguishing] The advantage of $D$ is
-\[
-\epsilon_{sec}\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1] - \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
-\]
+\begin{align*}
+\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
+\end{align*}
 where $u$ is a uniformly random string.
 \end{enumerate}
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-We say that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D$ of size at most $s_{sec}$ they win the game with advantage at most $\epsilon_{sec}$.
+$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
 \end{definition}
@@
 \section{Allowing Correlated Symbols}
+\label{sec:cor construction}
 In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.
@@
 Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
-The following theorem states the construction is a computational fuzzy conductor.  %After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
+The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).  
 \begin{theorem}
 \label{thm:main thm first cons}
-Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
+Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.
+Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
 \end{theorem}
@@
 \begin{definition}
-A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
-of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
+A function $\cext: \zo^\gamma \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
+of random variables $X, Y$ (with $X$ over $\zo^\gamma$) such that
 $\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
@@
 \section{Analysis of \consref{cons:first construction}}
-\label{sec:construction}
+\label{sec:construction analysis}
 \subsection{Security}

### 2014-09-17 constantRate/ConstCompFuzzExt-reorg.tex
modifying reusability discussion and abstract

@@
 In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns.
-We call what is left after this worst-case loss the \emph{minimum usable entropy}.
-Unfortunately, this quantity is negative for some sources that are important in practice.
-Most known approaches for building fuzzy extractors work in the worst case and cannot be used when the minimum usable entropy is negative.
-
-We construct the first fuzzy extractors that work for a large class of distributions that have negative minimum usable entropy.
-We present both information-theoretic and computational constructions.In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.
-
-Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a large alphabet.
-In this construction each symbol must contribute fresh entropy.
-We then use computational techniques to obtain two constructions with additional properties.
-
-Our second construction requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
+For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.
+Unfortunately, it is impossible to provide security for all sources with this property.
+Most known approaches for building fuzzy extractors work in the worst case and cannot be used when a source has \emph{more errors than entropy}.
+
+In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.
+Our constructions are for the Hamming metric over symbols of some alphabet $\mathcal{Z}$.
+We present both information-theoretic and computational constructions.
+
+Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a super-constant size alphabet.
+In this construction, each symbol must contribute fresh entropy.
+
+Our second construction provides computational security and supports the same type of sources as the first construction.
+This construction comes with added feature: reusability.
+A reusable fuzzy extractor can be safely reused across multiple noisy readings of the source~(Boyen, CCS 2004).
+Previous reusable fuzzy extractors only provide security when the noise between repeated readings comes from a small and unrealistic class.
+Our construction is secure as long as the fuzzy extractor is secure on each individual reading.
+Unfortunately, this construction only corrects a sub-constant fraction of errors.
+%Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
 It corrects a sub-constant fraction of errors and supports super-constant size alphabets.
@@
 
-Our third construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.
+Our first two constructions require each symbol of the source to contribute fresh entropy.
+Our third construction removes this requirement and allows symbols to be dependent.
+Unfortunately, this change requires a significantly larger alphabet.
 
@@
 This property is necessary if a user enrolls the same or correlated values multiple times.
-For example, if the source is a biometric reading, the user may have to enroll the same biometric with different organizations (after all, most users have only ten fingers and two irises).
-\bnote{ewww jokes} Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
+For example, if the source is a biometric reading, the user may enroll the same biometric with different organizations.
+Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
 Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).
+Many traditional fuzzy extractors are not reusable~\cite{Boyen2004,simoens2009privacy,blanton2012non,blanton2013analysis}.
 
@@
 Let the outcome of this transform (on different irises) define a distribution $w$.
-The precise number of errors that must be tolerated depends on the desired false reject rate.
-Even allowing for a false reject rate of up to $80\%$ (i.e., permitting correctness to fail $80\%$ of the time),\bnote{I don't like saying this twice.
-Should either say $20\%$ true accept or correctness around $20\%$} a $t$ of approximately $205$ is required.
+The precise number of errors that must be tolerated depends on the desired correctness.
+For correctness of around $20\%$, a $t$ of approximately $205$ is required.
 Thus,
@@
 Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret.
-The main idea of the construction is to pick a random $r$ and then lock it up in a digital locker that is unlocked by a random subset of the symbols of $w$.
+The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$.
 To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$.
@@
 Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Of course, hiding an entire $r$ in every locker then becomes too risky, since we do not assume that every symbol has high individual entropy.
-Instead, we hide a single bit per locker (this simplified version of a digital locker is basically point obfuscation).
+Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are easier simpler to construct than digital lockers).
 To tolerate errors, these bits come from an error correcting code.
@@
 We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
-We need a strong version of point obfuscation/digital lockers that remains secure even when several obfuscations of correlated points are composed.
-While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
-However it is known how to construct composable VGB obfuscation for the class of functions we need.} of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
-For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions.
+We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is 
+%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
+However it is known how to construct composable VGB obfuscation for the class of functions we need.}
+composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}.
 Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
@@
 As described in the introduction, it is impossible to provide security for all distributions with more errors than entropy.
-Thus, in both the computational and information-theoretic settings we consider arbitrary families of distributions.
+Thus, in both the computational and information-theoretic settings we consider limited families of distributions.
 
@@
 This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
+There are two primary parameters of the definition: 1) $q$, the reusability of the fuzzy extractor and 2) what class of correlation is allowed between readings $w_i$ and $w_j$.
+
 Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).
 Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).
-Boyen constructs a outsider reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.
-Boyen also transforms this construction in an insider secure construction using random oracles.
-\paragraph{Previous Negative Results}
-
-There are two primary questions about the reusability of a fuzzy extractor.
-The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.
-Boyen~\cite{Boyen2004} considers fuzzy extractors that are reusable an unbounded number of times.
-Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
+Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups.
+Boyen transforms this construction to insider security using random oracles.
+In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.
+Unfortunately, this class of correlation is relatively weak and unrealistic.
+%\paragraph{Previous Negative Results}
+
+Boyen~\cite{Boyen2004} considers information-theoretic fuzzy extractors with unbounded reusability.  
+However, even for this relatively weak class of correlations, Boyen shows that reusability comes at a real cost~\cite[Theorem 11]{Boyen2004}.
+If the correlation between readings contains a set that generates a transitive isometric permutation group, any secure sketch must lose entropy proportional to the number of errors corrected.\footnote{This result strengthens the bounds of~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}, who show this loss is necessary for uniform $W_1$.} This means achieving reusability for sources with more errors than entropy is impossible in this setting.
+%\bnote{old stuff}
+%Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
 They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.
@@
 Their result can be interpreted as saying that reusability is impractical.
-
-However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
+%
+%However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
 There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
@@
 
-We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
+To overcome this result, we consider computationally bounded adversaries.
 %We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
@@
 %\end{definition}
-Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss definitional differences in \apref{sec:comparing reusability}.
+We modify the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss the differences in \apref{sec:comparing reusability}.
 
@@
 
-\bnote{shorten this discussion?}
-The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
-In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
-There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
+%\bnote{shorten this discussion?}
+%The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
+%In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
+%There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
 However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
@@
 Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
-The following theorem states the construction is a computational fuzzy conductor.  %After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
+The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).  
 \begin{theorem}
@@
 
-\section{Further Definitions}
+\section{Definitions}
 \subsection{Computational Fuzzy Conductors}
@@
 
-\subsection{Adapting Reusability to the Computational Setting}
+\subsection{Defining Reusability in the Computational Setting}
 \label{sec:comparing reusability}

### 2014-09-17 trunk/constantRate/ConstCompFuzzExt-reorg.tex
intro fixing

@@
 Thus, if the security guarantee of a given fuzzy extractor holds for \emph{any} source of a given min-entropy $m$ and the correctness guarantees holds for any $t$ errors, then $m$ must   be greater than $\log |B_t|$, where $|B_t|$ denotes the number of points in a ball of radius $t$.
+This condition on the source is necessary regardless of whether the fuzzy extractor is information-theoretic or computational, and extends even to the interactive setting.
 If a source fails this condition, we will says that it has \emph{more errors than entropy}.
@@
 Unfortunately, prime candidate sources for authentication have more errors than entropy. 
-As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
+For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}.
+Physically inclonable functions suffer from similar problems \lnote{ben please fix}
+
+%As an example, the iris is believed to be the best biometric for high security applications~%\cite{prabhakar2003biometric}.
 Daugman~\cite{daugman2004} designs a transform called IrisCode (using specialized wavelets) to derive a $2048$ bit string from an iris.
@@
 Thus,
-\[
-\log |B_t|
-= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
-\]
-In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+%\[
+%\log |B_t|
+%= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
+%\]
+%In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
+%There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
 
@@
 \bnote{this should be strengthened.
-move negative results to there.}
+move negative results to there.} \lnote{waiting for response form Adam}
 
@@
 
-%Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+%Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10].
 Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
@@
 Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-As shown by~\cite{DBLP:journals/siamcomp/DodisORS08}\lnote{specific theorem number} for the information-theoretic case and by \cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} for the computational case, this is unlikely to work for sources with more errors than entropy.
-Thus, we give up on recovering $w$.
-\bnote{I'm not sure I buy this argument.
-We have coding bounds, but they don't say that secure sketches won't work.}
+Unfortunately, the current techniques for building secure sketches do not work for sources with more errors than entropy, because they lose at least $\log |B_t|$ bits of entropy regardless of the source (this loss is necessary when the source is uniform~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}).
+Moreover, relaxing the security definition to computational will not improve this approach~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Thus, we take a different approach and do not attempt to recover $w$.
 
@@
 The resulting string no longer has more errors than entropy.
- We then apply any information-theoretic fuzzy extractor to the resulting string
+ We then apply any information-theoretic fuzzy extractor to the resulting string.
 

### 2014-09-18 info-bounds/FuzzyExtPossibility.tex
adding proof of ss hardness

@@
 For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
+We will also use an average case version of this notion~(to the best of our understanding this has not been used before):\bnote{has it?}
+\begin{definition}[Conditional Hartley Entropy]
+\label{def:conditional hartley}
+The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
+\end{definition}
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
@@
 The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
-The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if the can guess $w\in W$ with noticeable probability.
+The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
 More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
@@
 This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
-Later, we will need this game to be zero sum.}
+This is to apply results from game theory.}
 
@@
 
-The only difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
+The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
 In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
@@
 Let $\mathcal{V}$ be a family of distributions.
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor.
+Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
 Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
-Then there exists a fuzzy extractor $(\gen', \rep')$ is a $(\mathcal{M}, \mathcal{W}, \ell, t, \epsilon)$-fuzzy extractor.\footnote{Note the other direction of this lemma is true as well.
+Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-fuzzy extractor.\footnote{The other direction of this lemma is true as well.
 If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
@@
 
-Instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
+Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
 Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
@@
 Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
-If there does not exist a $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor, then there is no $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor.
+If there does not exist a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
 \end{corollary}
@@
 
-Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for secure sketches as well as fuzzy extractors.
-Additionally we elide the correctness term $\delta$ above, but these generalize the secure sketches and fuzzy extractors with imperfect completeness.
+Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to the case of imperfect correctness.
 
 \subsection{Impossibility of info-theoretic sketches}
-In the previous section, we saw that if a fuzzy extractor is secure for a family of sources, for every distribution over those sources there is a secure fuzzy extractor.
+In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.
 In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
@@
 \begin{theorem}
+\label{thm:imposs sketch}
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta \le 1/2$ for $\tilde{m} =\omega(1)$.
-%Furthermore, consider $V$ as the uniform distribution over $\mathcal{V}$.
-There is no secure sketch for $\mathcal{
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
+\bnote{finish proof}
 \end{theorem}
@@
 Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\ell$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$ and $a_i\neq 0$.
-This type of distribution is a line in space $\mathbb{F}^\ell$.
+This type of distribution is an affine line in space $\mathbb{F}^\ell$.
 Define $V$ as the uniform distribution over all such $W$.
-Fix some $1< t < \ell$.
-It suffices to show the following:
+Furthermore, the side information $Z = a_2, b_2, ..., a_\ell, b_\ell$.
+Fix some $4\le t < \ell$.
+We then show the following:
 
 \begin{itemize}
-\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$.
-\item The distribution $V$ is uniform~(from the sketch designers point of view).
-\item For any secure sketch on $V$, $H_0(V | \sketch(V)) \le n -\log |B_t|$.
-\item The information $Z$ is a universal hash of $V$ that is independent of $\sketch(V)$. This suffices to show that $\Hav(V| \sketch(V), Z)$ is very small.
+\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
+\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\ell-t+1)\log |\mathbb{F}|+1$. 
+\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
+\item For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.  Thus, $\Hav(V| \sketch(V) , Z)$ is small.
 \end{itemize}
-\begin{proposition} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\begin{proposition} 
+\label{prop:each element good} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
 \end{proposition}
@@
 Consider some fixed $W\in\mathcal{V}$.
-First note that since $w_1$ is uniform in a field of size $\omega(\poly(n))$, the distribution $\Hoo(W) =\omega(\log n)$.
+The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.
 Recall that $t< \ell$.
@@
 \end{proof}
-\bnote{will need to define average Hartley entropy}
-\bnote{show version without error first?}
-\begin{proposition}
-Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $H_0(V | \sketch(V)) \le n - \log |B_t|+ O(1)$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+\begin{lemma}
+Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\ell-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
 Dealing with imperfect correctness makes the bound more complicated.
 In particular, we can only argue about the average remaining support size.}
-\end{proposition}
-\begin{proof}
-By the definition of correctness for $(\sketch, \rec)$, 
-\[
-\forall w, w^*, \Pr_{p\leftarrow \sketch(w)} [\rec(w^*, p) = w] >1-\delta.
-\]
-By the Markov inequality, 
-\[
-\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
-\]
-That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
-
-Outline of what I want to say.
-\begin{itemize}
-\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
-\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
-\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
-\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
-\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
-Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.
-Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).
-\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
-\end{itemize}
-\end{proof}
-
-\bnote{stopped here}
-\end{proof}
-
-\begin{lemma}
-There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
 \end{lemma}
 \begin{proof}
-Need to show several things.  
-\begin{itemize}
-\item Each component of the distribution has fuzzy min-entropy.
-\item Any sketch must leak some information about $V$.
-\item The side information can be thought of as a hash function.
+We assume that $\rec$ is deterministic in our analysis.
+Any randomness necessary for the \rec algorithm can be provided by \sketch.
+We will however, not consider these coins in our security analysis.
+
+By the definition of correctness for $(\sketch, \rec)$, 
+\[
+\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+\]
+%For most $p$, $\rec$ works on most neighbors of $w$.  
+Fix some $w$.  
+By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[p\in A_{ss}]\ge 1/2$ and $\forall s\in A_{ss}$, 
+\[
+\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+
+Consider some $p\in A_{ss}$.
+We now show that $H_0(V | p) \le n-\log |B_t|$.
+Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.
+Thus for every value in $V|p$ this is also true.
+This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).
+In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).
+That is $V|p$ is a set with minimum distance at least $t$.
+By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t+1 )|\mathbb{F}|$.
+Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t +1) \log|\mathbb{F}| +1$.
+%By the Markov inequality, 
+%\[
+%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
+%\]
+%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
+%
+%Outline of what I want to say.
+%\begin{itemize}
+%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
+%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
+%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
+%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
+%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
+%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.
+Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).
+%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
+%\end{itemize}
+\end{proof}
+We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.
+
+\begin{lemma}
+$\Hav(V | \sketch(V), Z) \le \Theta(1)$.
+\end{lemma}
+\begin{proof}
+Recall that $Z$ consists of $2\ell$ coefficients and there are $(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}$ equally likely values for $Z$.
+ By described above the view of $\sketch, \rec$ is a uniform distribution $V$.
+We know show there are many possible values for $Z$.
+The only information seen by $\sketch$ algorithm is in the point $V=v$.
+The length of this point is $|\mathbb{F}|^\ell$.
+Conditioned on this information there are still many possible values for $Z$.
+That is,
+ \[
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}}{|\mathbb{F}|^\ell}\right) = \log \left( (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\right).
+ \]
+Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+This means that the $\sketch$ algorithm include points for possible $Z$ values~(other than $v$) and these values are disjoint.
+The optimum strategy is to include these values uniformly from different $Z$ values.
+
+We show this across different sketch values.
+Consider some fixed sketch value $s$ and let $h_s \overset{def}= H_0(V | \sketch(V) = s)$.
+That is, there are $2^{h_s}$ possible values for $V$ conditioned on $\sketch(V) = s$.
+Furthermore, recall that
+\[
+\log \expe_{s\in \sketch(V)} 2^{h_s} = \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \tilde{H}_0(V | \sketch(V)) %\le   (\ell-t+1)\log |\mathbb{F}|+1.
+\]  
+Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.
+Consider these possible values for $Z$ as bins to be filled with the $2^{h_s}$ balls~(possible values of $V | \sketch(V)=s$).
+The average number of balls in each bin is maximized when the bins are filled equally.
+That is, the average number of balls in each bin is bounded by the number of balls divided by the number of bins.
+That is,
+\begin{align*}
+\tilde{H}_0(V |Z  , \sketch(V) = s) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
+&= \log \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \right)
+\end{align*}
+\bnote{should I be writing this as $Z | \sketch(V) =s $?}
+Then averaging over the possible values of $s$, we have the following:
+\begin{align*}
+\tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V | Z, \sketch(V) =s )}\\
+&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \right)\\
+&= \log \frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \expe_{s\in \sketch(V)} 2^{h_s}\\
+&=\log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + \log \expe_{s\in \sketch(V)} 2^{h_s}\\
+&=\log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V))\\ 
+&\le \log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + (\ell-t+1)\log |\mathbb{F}|+1\\
+&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-1) \log (|\mathbb{F}|-1)+1\\
+&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-2) \log |\mathbb{F}|+1\\
+&\le \Theta(1)
+\end{align*}
+ Where the last line follows for $t\ge 4$.  The eighth line follows from the seventh as long as $|\mathbb{F}|????$\bnote{fix this}
+ \end{proof}
+
+ \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
+%\begin{lemma}
+%$\Hav(V| P , Z) = \Theta(1)$
+%\end{lemma}
+%\begin{proof}
+%Consider some fixed $p$.
+%If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
+%\[
+%\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
+%\]
+%Then by the union bound, 
+%\[
+%\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
+%\]
+%\bnote{need to average across $P$}
+%\bnote{I'm confused about what we mean by $Z$ being universal here.}
+%\bnote{working here!}
+%\end{proof}
+%
+%\bnote{stopped here}
+\end{proof}
+
+%\begin{lemma}
+%There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
+%\end{lemma}
+%\begin{proof}
+%Need to show several things.  
+%\begin{itemize}
+%\item Each component of the distribution has fuzzy min-entropy.
+%\item Any sketch must leak some information about $V$.
+%\item The side information can be thought of as a hash function.
 Furthermore, it is independent of the sketch.
@@
 Thus, conditioned on both there is almost no entropy.
-\end{itemize}
-\end{proof}
-
-Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
-
-\begin{lemma}
-There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
-\end{lemma}
+%\end{itemize}
+%\end{proof}
+
+Canetti et al.~\cite{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
+%\begin{lemma}
+%There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
+%\end{lemma}
 
 \begin{corollary}
-This is also impossible for computational sketches that retain hill entropy.
+This is also impossible for computational sketches that retain hill entropy.\bnote{fill this in, use asiacrypt result.}
 \end{corollary}
 
-\subsection{Conductors}
-Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
-\begin{lemma}
-Not possible for information-theoretic objects.
-\end{lemma}
+%\subsection{Conductors}
+%Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
+%\begin{lemma}
+%Not possible for information-theoretic objects.
+%\end{lemma}
 \bibliographystyle{alpha}

### 2014-09-22 constantRate/ConstCompFuzzExt-reorg.tex
minor intro edits

@@
 
-Our second construction provides computational security and supports the same type of sources as the first construction.
-This construction comes with added feature: reusability.
+Our second and third constructions switch to computational security to provide additional features.
+Our second construction supports the same type of sources as the first construction but also provides reusability.
 A reusable fuzzy extractor can be safely reused across multiple noisy readings of the source~(Boyen, CCS 2004).
@@
 Our third construction removes this requirement and allows symbols to be dependent.
-Unfortunately, this change requires a significantly larger alphabet.
+This change requires a significantly larger alphabet.
 
@@
 Unfortunately, prime candidate sources for authentication have more errors than entropy. 
-As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.
+For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}.
+Physical unclonable problems with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.
+
+%As an example, the iris is believed to be the best biometric for high security applications~%\cite{prabhakar2003biometric}.
 Daugman~\cite{daugman2004} designs a transform called IrisCode (using specialized wavelets) to derive a $2048$ bit string from an iris.
@@
 Thus,
-\[
-\log |B_t|
-= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
-\]
-In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
-There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
+%\[
+%\log |B_t|
+%= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
+%\]
+%In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
+%There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}
 
 The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
-\bnote{this should be strengthened.
-move negative results to there.}
+\bnote{negative results stated in our contributions.
+keep there?}
 
@@
 Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
+Table~\ref{tab:upper bounds} summarizes our constructions.
 
@@
 It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols.
-It requires an alphabet size that is super constant in the security parameter.
+%It requires an alphabet size that is super constant in the security parameter.
 \lnote{keep this last sentence?}
 
-We then switch to computational security to obtain constructions with additional features.
-Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy.
-However, it provides reusability.
+We switch to computational security to obtain constructions with additional features.
+Boyen showed information-theoretic reusability fuzzy extractors incur entropy loss proportional to the number of corrected error patterns~\cite[Theorem 11]{Boyen2004}.
+For sources with more errors than entropy, information-theoretic reusability is impossible~(see \secref{sec:reusable} for discussion).
+
+Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy. It provides reusability against \emph{computational} adversaries. 
 The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
-We note that such strong reusability was shown to be impossible in information-theoretically secure fuzzy extractors~\cite[Theorem 11]{Boyen2004}.\lnote{really?
-I can't parse his theorem clearly enough} This construction, however, requires that the fraction of errors is subconstant.
+ This construction, however, requires that the fraction of errors is subconstant. \bnote{reasonable?}
 
@@
 \hline
-\consref{cons:info theoretic} & Info-theoretic & Exploits distribution & Most symbols must \\
-&&structure & contribute fresh entropy \\\hline
-\consref{cons:sampling} & Computational  & Reusable with arbitrary & Error tolerance is\\
-&&correlation & sub-constant fraction\\\hline
-\consref{cons:first construction} & Computational & Supports distributions  & Super-polynomial \\
-& &  with dependent symbols & size symbols
+\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
+&&structure & fresh entropy \\\hline
+\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
+&& & error tolerance\\\hline
+\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
+& &  symbols & size symbols
 \end{tabular}
@@
 The resulting string no longer has more errors than entropy.
- We then apply any information-theoretic fuzzy extractor to the resulting string
-
-Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}.
-Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret.
+ We then apply any information-theoretic fuzzy extractor to the resulting string.
+
+Our second construction, which is computationally secure, is based on obfuscated digital lockers~\cite{canetti2008obfuscating}.
+Digital lockers output a secret value only when given the correct input to ``unlock'' the secret.
+An obfuscated digital locker does not provide information about the locked value or how to unlock it.
 The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$.
 To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$.
-Reusability follows from composable obfuscation.
+We use obfuscation in a way that does not leak partial information; this is crucial to arguing reusability.
 
 Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are easier simpler to construct than digital lockers).
+Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers).
 To tolerate errors, these bits come from an error correcting code.
-And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.
+To ensure an  adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor) from the decoded string.
 
@@
 \paragraph{Open Problems}
-All of our constructions support more errors than entropy by tolerating errors in a large alphabet and performing error correction over a different smaller alphabet.
-This approach seems limited to larger alphabets~(all of our constructions require a super-constant size alphabet).
-Supporting distributions with more errors than entropy over small alphabets is an important open problem.
+All of our constructions support more errors than entropy by using two metrics spaces.
+Errors are tolerated in one metric space and corrected in a second.
+To handle more errors than entropy,  we map to a metric space where multiple error patterns are grouped together.
+All our constructions require the first metric space to have a super-constant size alphabet.
+An alternative approach to the problem may support constant size alphabets.
 
@@
 In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
-An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.
-A meaningful restriction of correctable errors is an open problem.
+An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.%  A meaningful restriction of correctable errors is an open problem.
 
@@
 As described in the introduction, it is impossible to provide security for all distributions with more errors than entropy.
-Thus, in both the computational and information-theoretic settings we consider limited families of distributions.
+In both the computational and information-theoretic settings we consider a family of distributions $\mathcal{W}$.
 
@@
 The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
-\bnote{almost certainly need to say more here.  expand}
+\bnote{say more here?}
 \end{proof}

### 2014-09-22 trunk/constantRate/ConstCompFuzzExt-reorg.tex
minor intro edits

@@
 For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}.
-Physically inclonable functions suffer from similar problems \lnote{ben please fix}
+Physical unclonable problems with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.
 
@@
 The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
-\bnote{this should be strengthened.
-move negative results to there.} \lnote{waiting for response form Adam}
+\bnote{negative results stated in our contributions.
+keep there?}
 
@@
 
-Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}.
-Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret.
+Our second construction, which is computationally secure, is based on obfuscated digital lockers~\cite{canetti2008obfuscating}.
+Digital lockers output a secret value only when given the correct input to ``unlock'' the secret.
+An obfuscated digital locker does not provide information about the locked value or how to unlock it.
 The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$.
 To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$.
-Reusability follows from composable obfuscation.
+We use obfuscation in a way that does not leak partial information; this is crucial to arguing reusability.
 
 Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are easier simpler to construct than digital lockers).
+Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers).
 To tolerate errors, these bits come from an error correcting code.
-And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.
+To ensure an  adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor) from the decoded string.
 
@@
 If $\gamma$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
+
+\section*{Acknowledgements}
+The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, and Mayank Varia for helpful discussions, creative ideas, and important references.
+
+This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, and 1218461. 
+Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.
+The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
 

### 2014-09-22 constantRate/ConstCompFuzzExt-reorg.tex
adding blinding command

@@
 \def\shownotes{1}
+\def\blinded{0}
 
@@
 
+\ifnum\blinded=0
+\newcommand{\blind}[1]{{#1}}
+\else
+\newcommand{\blind}[1]{}
+\def\shownotes{0}
+\fi
+
 \ifnum\shownotes=1
@@
 \fi
+
 \newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
@@
 \title{Key Derivation From Noisy Sources With More Errors Than Entropy}
-%\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
-%work was sponsored by the Department of the Air Force under Air Force
-%Contract
-%\#FA8721-05-C-0002.  Opinions,
-%interpretations, conclusions and recommendations are those of the author
-%and
-%are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
-
+%\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
+\blind{
+\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}.
+Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
+Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}.
+Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.
+Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
+Pennsylvania State University.} }
+}
 \begin{document}
@@
 In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.
-Our constructions are for the Hamming metric over symbols of some alphabet $\mathcal{Z}$.
+Our constructions are for the Hamming metric over symbols of some alphabet .
 We present both information-theoretic and computational constructions.
@@
 
+\blind{
+\section*{Acknowledgements}
+The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, and Mayank Varia for helpful discussions, creative ideas, and important references.
+
+This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, and 1218461. 
+Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.
+The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
+}
 \bibliographystyle{alpha}

### 2014-09-22 trunk/info-bounds/FuzzyExtPossibility.tex
editing and notational fixes

@@
  \documentclass[11pt]{article}
+
 \def\shownotes{1}
+\def\blinded{0}
 
@@
 \fi
+
+\ifnum\blinded=0
+\newcommand{\blind}[1]{{#1}}
+\else
+\newcommand{\blind}[1]{}
+\def\shownotes{0}
+\fi
+
 \newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
 \newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
-\newcommand{\rnote}[1]{{\authnote{Ran}{#1}}}
-\newcommand{\onote}[1]{{\authnote{Omer}{#1}}}
+\newcommand{\anote}[1]{{\authnote{Adam}{#1}}}
 
@@
 \title{When are Fuzzy Extractors Possible?}
+\blind{
 \author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
@@
 }}
-
+}
 \begin{document}
@@
 We call the maximum weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.
-In interactive information-reconciliation, fuzzy min-entropy is both a necessary and sufficient condition for security.
+In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
 
@@
 We investigate whether this is inherent for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).
-Our results are centered on feasibility and our constructions and impossibility results are primarily information-theoretic.
+Our constructions and impossibility results are information-theoretic.
+
 We consider two types of fuzzy extractors and secure sketches.
@@
 
-\textbf{Distribution-Aware} In the distribution-aware setting we show that whenever the fuzzy min-entropy is super-logarithmic, there exists a secure sketch and fuzzy extractor with super-logarithmic output entropy.
+\textbf{Distribution-Aware} Whenever the fuzzy min-entropy is super-logarithmic, there exists a distribution-aware secure sketch and fuzzy extractor with super-logarithmic output entropy.
 That is, fuzzy min-entropy is both a necessary and \emph{sufficient} condition for security in this setting.
@@
 However, it is possible to build a fuzzy extractor for these same family of distributions.
+\bnote{come back to this.}
 \end{abstract}
@@
 
-The paradigm for performing noisy key derivation using a single metric is known as fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08}.
+The paradigm for performing noisy key derivation using a single message is known as fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08}.
 Consider a particular high entropy distribution $W$.
@@
 These objects can either be information-theoretic or computational.
-The computational versions of these objects are defined in~\cite{krawczyk2010cryptographic} and~\cite{fuller2013computational} respectively.
+The computational versions of these objects are defined in~\cite{fuller2013computational} and~\cite{krawczyk2010cryptographic} respectively.
 Fuller et al.~\cite{fuller2013computational} show that computational secure sketches are unlikely to improve significantly on information-theoretic secure sketches.
@@
 \textbf{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
-If the error-tolerance allows the entire metric space to authenticate then no security is possible.
-As an example, consider a distribution $W$, where the adversary attempts to learn the key simply by inputting a point to the reproduce function.
+Fix some distribution $W$.
+The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
 Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For a fuzzy extractor to be secure this must occur with negligible probability.
+For security, this must occur with negligible probability.
 That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
@@
 We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-The fuzzy min-entropy of a distribution must be super-logarithmic for any reasonable of either a fuzzy extractor~(\lemref{lem:fuzz necessary}).
-
-In the more general interactive setting where two parties hold $w$ and $w'$ and wish to agree on a common key, fuzzy min-entropy is both a necessary and sufficient condition~(using two-party computation).
+A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
+
+In the interactive setting where two parties hold $w$ and $w'$ and wish to agree on a common key, fuzzy min-entropy is both a necessary and sufficient condition~(using secure two-party computation). 
 However, in the one-message setting we are far from achieving security whenever fuzzy min-entropy is high.
 
-Traditional fuzzy extractors and secure sketches incur at entropy loss of the size of the ball to be error-corrected.
+Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.
 While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
@@
 Traditional fuzzy extractors provide no guarantee for sources of this type.
-The work of Canetti et al.~\cite{canetti2014key} shows it is possible to provide build fuzzy extractors for some distributions with this property.
-Their work leaves the question open for a large number of distributions.
+The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
 This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}
 
+\paragraph{Codifying distributional uncertainty}
 When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
 However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
-This uncertainty is usually expressed by proving the fuzzy extractor works for a class of distributions with some known property~(such as entropy and error levels).
-In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
+Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
+As long as the distribution falls in this class, security and correctness hold.
+
+To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
+We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
+We call this setting \emph{distribution-oblivious}.
+In the second, we allow the algorithms complete knowledge of the distribution.
+We call this setting \emph{distribution-aware}.
+
+%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
 We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
 
-\textbf{Our Contribution} We show that for every distribution with super-logarithmic fuzzy min-entropy it is information-theoretically possible to build a secure sketch that retains super-logarithmic min-entropy.
+\textbf{Our Contribution} In the \emph{distribution-aware} setting, for every source with super-logarithmic fuzzy min-entropy it is possible to build a secure sketch with super-logarithmic output entropy~(\thref{cons:leveling}).
 Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.
-(A key with super-logarithmic entropy can be expanded to arbitrary length using computational techniques.)  For distribution-aware secure sketches and fuzzy extractors, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-The situation is significantly more complicated for distribution-oblivious algorithms.
-Indeed, we show that there natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.
-However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.
+(A key with super-logarithmic entropy can be expanded to arbitrary length using computational techniques.)  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
 
 \textbf{Note:} Our constructions are information-theoretic and do not run in polynomial time.
-They should primarily be regarded as feasibility results.
-Our negative results apply to algorithms even given arbitrary running time, thus there is clear separation for unbounded running time algorithms.
-It remains as an open question whether our distribution-aware results can be replicated by efficient algorithms.
-This seems unlikely as most  interesting distributions have exponential size description.
+They should be regarded as feasibility results.
+It is unclear how to define distribution-aware efficient algorithms as most distributions have exponential description size.
 The power of the distribution-aware setting is that the algorithms can access this description.
@@
 
-\textbf{Open Problems:} We showed that in the distribution-oblivious setting there is a separation between a secure sketch and a fuzzy extractor.
-However, it is still not known if fuzzy extractors can be constructed for any family of distributions.
+We show that distributional uncertainty is a real drawback to providing security.
+In the standard \emph{distribution-aware} setting, we show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).
+This negative result extends to computational secure sketches~\bnote{cite a corollary}.
+
+%The situation is significantly more complicated for distribution-oblivious algorithms.
+Indeed, we show a natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.
+However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.
+
+\textbf{Open Problem:} The main open problem is whether fuzzy min-entropy is a sufficient condition for constructing a fuzzy extractor in the distribution-oblivious setting.
+We note that it is known how to build a fuzzy extractor for the family of distributions used in our negative result~\cite[Theorem 5.7]{canetti2014key}.
+Furthermore, are computational assumptions necessary?
+\bnote{talk about obfuscation.}
 
@@
 \hline
-Secure Sketch & Yes~(\thref{cons:leveling}) & No\\
+Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
 \hline
-Fuzzy Extractor & Yes~(\thref{cons:leveling}) & Yes for some families\\
-& & Unknown for arbitrary family
+Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & Unknown
 %Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
@@
 
-\bnote{connection to obfuscation}
+\paragraph{Organization} The reminder of the paper is organized as follows.
+In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
+In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
+Finally, in \secref{sec:dist oblivious} we provide negative results for the distribution-oblivious setting.
+
 \section{Preliminaries}
 \label{sec:preliminaries}
-\bnote{be careful with overloading of $\ell$, both key length and number of levels.}
-For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.
+For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.
 For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
 The set $J^c$ is the complement of $J$.
+Unless otherwise noted logarithms are base $2$.
+Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
+
 The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
@@
 For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
-We will also use an average case version of this notion~(to the best of our understanding this has not been used before):\bnote{has it?}
+We will also use an average case version of this notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
 \begin{definition}[Conditional Hartley Entropy]
@@
 We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
+\bnote{there is nothing computational here right now}
 
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric over vectors in $\mathcal{Z}^\ell$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
-For this metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
+For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-Unless otherwise noted logarithms are base $2$.
-Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
-
-\section{Fuzzy Extractors}\label{sec:fuzz extractor}
-
-We now recall definitions and lemmas from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
+For the remainder of this work we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
+
+\subsection{Fuzzy Extractors}\label{sec:fuzz extractor}
+
+We recall definitions and lemmas from the work of Dodis et.
+al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with two changes.
+First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08} and we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
+See~\cite{canetti2014key} for discussion.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
@@
 \label{def:fuzzy extractor}
-An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
+An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
 \begin{enumerate}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.
-The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
+\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
+\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that
+\[
+\forall w, w'\in \mathcal{M}, \dis(w, w')\le t \Rightarrow \Pr[(R, P)\leftarrow \gen(w) \wedge \rep(w', P) =R] \ge 1-\delta
+\]
+where the probability is taken over the coins of $\gen, \rep$.
+\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
 \end{enumerate}
@@
 \label{def:secure sketch}
-An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
 \begin{enumerate}
 \item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.
-The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
+\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
+\[
+ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta
+ \] 
+where the probability is taken over the coins of $\sketch$ and $\rec$.  
+\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
 That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
@@
 \textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
-We do not consider a computational version of secure sketches.
-Fuller et al.
-showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
-
-A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}.
-An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
+
+A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:
+
 \begin{definition}
 Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
+A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
 of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
 U_d \times Y) \le \epsilon$.
@@
 \label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
+Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
 \begin{itemize}
@@
 \label{sec:minimal conditions}
-Consider the functionality of a fuzzy extractor, the reproduce algorithm produces the same key when provided with a nearby input point.
-In an ideal world, this would be all that is revealed by the reproduce algorithm.
-For the remainder of this work, we compare security with this ideal world.
-This ideal world can be expressed by an adversary providing a ``guess'' point to the algorithm~(and hoping that their guess was closed to the stored point).
-We call the level of security in this setting, fuzzy min-entropy.
-%\todo{doesn't 2PC require assumptions?}
-%We now define fuzzy min-entropy and show that fuzzy extractor security is only possible when the fuzzy min-entropy is super-logarithmic.
-
-%A necessary condition for fuzzy extractor security is that an adversary should not be able to learn the key simply by inputting a point into the \rep algorithm.
-This means a negligible portion of the source distribution $W$ lies within any Hamming ball.
-We make this intuition formal here:
+
+In an ideal world, we could provide a reproduce functionality as an oracle.
+In this world, the key is learned if a close point is provided, and no other information is leaked.
+In the rest of this work, we compare security to this ideal world.
+We call this fuzzy min-entropy:
 
@@
 
-If an adversary can always obtain the output of a fuzzy extractor by running the reproduce adversary, then there is no hope for security~(independent of the implementation of the fuzzy extractor).
+If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).
 We make this intuition formal in the following result.
-For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
+For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
 \begin{lemma}
@@
 We attempt to bridge this gap in this work.
-
-Before turning to our results we separate between two types of fuzzy extractors and secure sketches.
+Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
+
+We separate between two types of fuzzy extractors and secure sketches.
 The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.
+This is because we rarely have complete distributions of a physical probability distribution.
 We call this type of algorithm distribution-oblivious.
-We define a new type of algorithm that called distribution-aware that is allowed to know the precise distribution to be supported.
-We provide a definition for secure sketches~(this definition can easily be extended to fuzzy extractors)
+We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.
+We provide a definition for secure sketches~(extendible to fuzzy extractors):
 
 \begin{definition}
-Let $W$ denote a distribution.  A secure sketch, $(\sketch_W, \rec_W)$ is called \emph{distribution-aware} if the correctness and security properties hold for the distribution $W$.  That is, 
+Let $W$ denote a distribution.
+A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.
+That is,
 \begin{enumerate}
-\item \emph{Correctness} For all $w\in W$ and for all $w'\in\mathcal{M}$,  if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.
-If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
-Note correctness is guaranteed only for the support of $W$.
+\item \emph{Correctness} 
+\[
+\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta\]
+ where the probability is taken over the coins of $\sketch$ and $\rec$.  Note correctness is guaranteed only for the support of $W$.
 \item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
@@
 \end{definition}
-Note that correctness is only required to hold for points in the support of the distribution $W$, the algorithms are allowed the description of $W$ and security need only hold for the distribution $W$.
-When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to make use of the (possibly)~exponential size distributions.
-It is not clear how to meaningfully define efficient distribution aware algorithms.
-If the algorithms were required to be efficient, they could only encode a negligible portion of the probability space of $W$, and would have to ``work'' on all distributions $W'$ with the same probability mass function on the encoded space.
-This would make the algorithms a distribution-oblivious fuzzy extractor for all distributions with this property.
-
-We begin with by showing that secure sketches and fuzzy extractors are possible in the distribution aware setting whenever there is super-logarithmic fuzzy min-entropy.
-We then turn to the standard \emph{distribution oblivious} setting.
+Note (\sketch, \rec) know the description of $W$ and security only holds for $W$.
+When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to use the (possibly)~exponential size distributions.
+One possible approach is to allow $(\sketch, \rec)$ an oracle to the probability mass function of $W$.
+Our constructions do not work in this setting.\bnote{why am I talking about this?}
+
+We begin with by showing that fuzzy min-entropy is a sufficient condition in the distribution-aware setting.  We then turn to the standard \emph{distribution oblivious} setting.
 
@@
 \begin{table}
-\begin{tabular}{l | l | c}
-Lower bounds & Distribution-Dependent & Distribution-Oblivious\\
+\begin{tabular}{l | l}
+Lower bounds & Residual Entropy\\
 \hline
-Well-spread distribution & $\Hfuzz(W)$ & $\log |B_t|$\\
-Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
-Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$ & $\log |B_t|$
+Well-spread distribution & $\Hfuzz(W)$ \\
+Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
+Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
 \end{tabular}
-\caption{Residual entropy of secure sketches for complete recovery.}
+\caption{Summary of results for distribution aware setting.  Residual entropy of distribution-aware secure sketches with error $\delta$.}
 \label{tab:upper bounds}
 \end{table}
-\bnote{Fix right side of table}
-\bnote{the table should move.}
 %We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
@@
 \section{Distribution-Aware  Sketches}
+\label{sec:distribution aware}
 In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
@@
 \begin{corollary}
+\label{cor:extension to fuzz ext}
 Let $n$ be a security parameter and let $\mathcal{M} =\zo^n$.
 For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ residual min-entropy and overwhelming correctness.
-Furthermore, there exists a $(\mathcal{M}, \Hoo(W), \ell = \omega(\log n), \epsilon)$ distribution aware fuzzy extractor with $\epsilon = \ngl(n)$) and overwhelming correctness.
+Furthermore, there exists a $(\mathcal{M}, \Hoo(W), \kappa = \omega(\log n), \epsilon)$ distribution aware fuzzy extractor with $\epsilon = \ngl(n)$) and overwhelming correctness.
 \end{corollary}
@@
 We begin by describing our family $\mathcal{V}$.
-$\mathcal{V}$ consists of the set of affine functions from one dimension to $\ell$ dimensions.
+$\mathcal{V}$ consists of the set of affine functions from one dimension to $\gamma$ dimensions.
 % That is, we project a single point in the field to an arbitrary element in the metric space.
@@
 
-Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\ell$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$ and $a_i\neq 0$.
-This type of distribution is an affine line in space $\mathbb{F}^\ell$.
+Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.
+This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
 Define $V$ as the uniform distribution over all such $W$.
-Furthermore, the side information $Z = a_2, b_2, ..., a_\ell, b_\ell$.
-Fix some $4\le t < \ell$.
+Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+Fix some $4\le t < \gamma$.
 We then show the following:
@@
 \item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
-\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\ell-t+1)\log |\mathbb{F}|$. 
+\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\gamma-t+1)\log |\mathbb{F}|+1$. 
 \item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
@@
 The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.
-Recall that $t< \ell$.
-We now show that for any $w, w'\in W$, $\dis(w, w') = \ell$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Recall that $t< \gamma$.
+We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma$ and thus $\Hfuzz(W) = \Hoo(W)$.
 Fix some $w, w'\in W$.
@@
 Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.
-That is, $\dis (w, w')  =\ell$.
+That is, $\dis (w, w')  =\gamma$.
 \end{proof}
 
-\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\ell$.
+\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
 \end{proposition}
@@
 Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\ell , b_\ell$.
-The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\ell$ are uniformly random.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
 \end{proof}
-\bnote{show version without error first?}
-\begin{proposition}
-Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\ell-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+\begin{lemma}
+Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
 Dealing with imperfect correctness makes the bound more complicated.
 In particular, we can only argue about the average remaining support size.}
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 That is $V|p$ is a set with minimum distance at least $t$.
-By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t+1 )|\mathbb{F}|$.
-Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t +1) \log|\mathbb{F}| +1$.
+By the Singleton bound, this implies that $H_0(V | p) \le (\gamma -t+1 )|\mathbb{F}|$.
+Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
 %By the Markov inequality, 
@@
 \begin{proof}
-Recall that $Z$ consists of $2\ell$ coefficients and there are $(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}$ equally likely values for $Z$.
+Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
  By described above the view of $\sketch, \rec$ is a uniform distribution $V$.
@@
 The only information seen by $\sketch$ algorithm is in the point $V=v$.
-The length of this point is $|\mathbb{F}|^\ell$.
+The length of this point is $|\mathbb{F}|^\gamma$.
 Conditioned on this information there are still many possible values for $Z$.
@@
  \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}}{|\mathbb{F}|^\ell}\right) = \log \left( (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\right).
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
  \]
@@
 This means that the $\sketch$ algorithm include points for possible $Z$ values~(other than $v$) and these values are disjoint.
-The optimum strategy is to include these values uniformly from different $Z$ values.\bnote{prove this}  This means that
+The optimum strategy is to include these values uniformly from different $Z$ values.
+
+We show this across different sketch values.
+Consider some fixed sketch value $s$ and let $h_s \overset{def}= H_0(V | \sketch(V) = s)$.
+That is, there are $2^{h_s}$ possible values for $V$ conditioned on $\sketch(V) = s$.
+Furthermore, recall that
+\[
+\log \expe_{s\in \sketch(V)} 2^{h_s} = \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \tilde{H}_0(V | \sketch(V)) %\le   (\gamma-t+1)\log |\mathbb{F}|+1.
+\]  
+Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.
+Consider these possible values for $Z$ as bins to be filled with the $2^{h_s}$ balls~(possible values of $V | \sketch(V)=s$).
+The average number of balls in each bin is maximized when the bins are filled equally.
+That is, the average number of balls in each bin is bounded by the number of balls divided by the number of bins.
+That is,
 \begin{align*}
-\tilde{H}_0(V | \sketch(V), Z) &\le \tilde{H}_0(V | \sketch(V) )- \log H_0(Z | V)\\
-&\le (\ell-t+1)\log |\mathbb{F}|+1 - \log (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\\
-&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-1) \log (|\mathbb{F}|-1)+1\\
-&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-2) \log |\mathbb{F}|+1\\
+\tilde{H}_0(V |Z  , \sketch(V) = s) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
+&= \log \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)
+\end{align*}
+\bnote{should I be writing this as $Z | \sketch(V) =s $?}
+Then averaging over the possible values of $s$, we have the following:
+\begin{align*}
+\tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V | Z, \sketch(V) =s )}\\
+&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)\\
+&= \log \frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\\
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \log \expe_{s\in \sketch(V)} 2^{h_s}\\
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V))\\ 
+&\le \log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + (\gamma-t+1)\log |\mathbb{F}|+1\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+1\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}|+1\\
 &\le \Theta(1)
 \end{align*}
- Where the last line follows for $t\ge 4$.  The fourth line follows from the third as long as $|\mathbb{F}|????$\bnote{fix this}\bnote{add more to this}
+ Where the last line follows for $t\ge 4$.  The eighth line follows from the seventh as long as $|\mathbb{F}|????$\bnote{fix this}
  \end{proof}
@@
 
+\subsection{Computational secure sketches}
+We do not consider a computational version of secure sketches.
+Fuller et al.
+showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+
 \begin{corollary}
@@
 \]
-A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+A source $W = W_1||...|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
 \[
@@
 Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\ell, k\}$ where $\ell$ is the number of distributions $W_1,..., W_\ell$.
-(For our purposes, we can assume that $\ell$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\gamma, k\}$ where $\gamma$ is the number of distributions $W_1,..., W_\gamma$.
+(For our purposes, we can assume that $\gamma$ is quite large and the probability of $w^*$ becomes the dominant factor.)
 
@@
 One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \ell\}$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \gamma\}$.
 For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
 This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
-This is despite the fact $\Hfuzz(W) \approx \min\{\ell, k\}$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\gamma, k\}$.
 Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
@@
     \includegraphics[width=.9\textwidth]{convexCombExample.png}
-    \caption{A convex combination of $W_1,..., W_\ell$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+    \caption{A convex combination of $W_1,..., W_\gamma$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
 \label{fig:convex comb}    

### 2014-09-22 trunk/info-bounds/FuzzyExtPossibility.tex
revisions of distribution aware section

@@
 
-We begin with by showing that fuzzy min-entropy is a sufficient condition in the distribution-aware setting.  We then turn to the standard \emph{distribution oblivious} setting.
-
 %The summary of our results is in Table~\ref{tab:upper bounds}.
@@
 \label{sec:distribution aware}
-In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
+In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors) whenever $\Hfuzz(W)= \omega(\log n)$.
 We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.
@@
 \subsection{Well-Spread Distributions}
+\bnote{is this section useful?}
 We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
@@
 Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
-Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result can be viewed as saying that well-spread distributions are not interesting in the distribution-aware setting.
-However, we will show that providing secure sketches for well-spread distributions in the distribution-oblivious setting is impossible.}
-
+Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.
 \begin{lemma}
 \label{lem:nosketchwellspread}
-Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.
+Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.
 In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.
 \rec is efficient if there exists efficient decoding for the points in $W$.
-By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, m,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
+By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
 \end{lemma}  
@@
 \end{align}
-%We start by considering distributions that have a fixed number of neighbors for each point.
-%
-%\begin{definition}
-%We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.
-We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
-%\end{definition}
-%
-%\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
-We now present a construction for flat distributions.  We use pairwise-independent hashes:
+
+We now present a construction for flat distributions.  We universal hashes:
 
@@
 \]
-%In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
 \end{definition}
 
-We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.
-The work of Skoric et al.~\cite{skoric2009efficient} use universal hash functions in the setting where there are a polynomial number of possible error patterns.
+A sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.
+Skoric et al.
+previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.
 
 \begin{construction}
-\label{cons:pairwise hash}
-Let $W$ be a flat distribution over $\mathcal{M}$.  Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a pairwise independent hash function.  We describe $\sketch, \rec$ as follows:
+\label{cons:universal hash}
+Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  We describe $\sketch, \rec$ as follows:
 \begin{itemize}
@@
 \begin{lemma}
-\consref{cons:pairwise hash} is a $(\mathcal{M}, m, m - \log |R|, t)$-secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
+Let $W$ be a flat distributions with min-entropy $m$.  Then
+\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
 \end{lemma}
@@
 We first argue security.
+Fix some $W\in\mathcal{W}$.
 Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
@@
 Let $n$ be a security parameter.  
-If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
+If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
 \end{corollary}
 
-Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).
-Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.
-Thus, the remaining entropy for this construction is
+Note that \consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
 \[
@@
 For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
-Furthermore, whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ depending on $\Hfuzz(W)$).
-That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.
+The achievable security is proportional to the starting entropy minus the largest number of points in any ball.
+Whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
+%That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.
 Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.
@@
 \subsection{Arbitary distributions}
-The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.
+The hashing approach outlined above~(\consref{cons:universal hash}) does not extend to arbitrary sources.
 The reason is that some balls may have significantly more points but low overall probability.
@@
 \label{cons:leveling}
-Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
+Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.
 Let $\ell\in\mathbb{Z}^+$ be a parameter.
 Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.
-Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.
+Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.
 We describe $\sketch, \rec$ as follows:
@@
 \label{thm:layered hashing}
+Let $W$ be a distribution over $\mathcal{M}$.
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.
-Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.
+Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
 \end{theorem}
@@
 Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$.
-The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the bound is negative.
+The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
 \end{proof}
@@
 \label{cor:extension to fuzz ext}
-Let $n$ be a security parameter and let $\mathcal{M} =\zo^n$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ residual min-entropy and overwhelming correctness.
-Furthermore, there exists a $(\mathcal{M}, \Hoo(W), \kappa = \omega(\log n), \epsilon)$ distribution aware fuzzy extractor with $\epsilon = \ngl(n)$) and overwhelming correctness.
+Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+(Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
 \end{corollary}
+
+\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.
+Going forward we will consider specific metric spaces, namely the Hamming metric.
 \section{Distribution-Oblivious Sketches}
@@
 In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
-For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.
+For example, consider the following hypothetical extension to \consref{cons:universal hash}.
 Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
@@
 Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Furthermore, each of these distributions is flat and thus, \consref{cons:pairwise hash} should apply.
+Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
 

### 2014-09-22 constantRate/ConstCompFuzzExt-reorg.tex
handled reusability in the intro

@@
 However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
-physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
+physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
 and quantum information~\cite{bennett1988privacy}).
@@
 %Prime candidate sources for authentication have $\Huse\le 0$.  
-Unfortunately, prime candidate sources for authentication have more errors than entropy. 
+Unfortunately, sources that have been proposed as prime candidates for authentication have more errors than entropy. 
 For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}.
-Physical unclonable problems with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.
+PUFs with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.
 
@@
 Table~\ref{tab:upper bounds} summarizes our constructions.
+\lnote{Note sure about the first line of this table.
+What does ``exploit distribution structure'' mean?
+Also, can we make it look a bit better?
+Perhaps center.
+Perhaps also remove some lines.
+Perhaps make "main feature" column the same part of speech in each entry.}
 
@@
 We switch to computational security to obtain constructions with additional features.
-Boyen showed information-theoretic reusability fuzzy extractors incur entropy loss proportional to the number of corrected error patterns~\cite[Theorem 11]{Boyen2004}.
-For sources with more errors than entropy, information-theoretic reusability is impossible~(see \secref{sec:reusable} for discussion).
-
-Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy. It provides reusability against \emph{computational} adversaries. 
-The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
- This construction, however, requires that the fraction of errors is subconstant. \bnote{reasonable?}
-
-Our third construction removes the need for fresh entropy in the symbols. 
-It is secure when symbols in $w$
+Our second construction provides reusability (against computationally bounded adversaries).
+Like the first construction,
+it requires that a constant fraction of symbols contribute fresh entropy. However,
+the reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
+The switch to computational security is necessary here: as discussed in \secref{sec:reusable}, it is impossible to obtain such reusability information-theoretically for sources with more errors than entropy.
+This construction requires that the fraction of errors is subconstant.
+
+Our third construction removes the need for fresh entropy in the symbols and allows a constant fraction of symbols of errors, at the cost of requiring a large alphabet size~(super-polynomial in the security parameter).
+It is secure if symbols in $w$
 each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
-a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
-This construction can correct a constant fraction of errors.
-However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
-
+a constant fraction of symbols in $w$ may have little or no entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
 %\bnote{rewrite this!}
@@
 \begin{tabular}{l | l | l | l }
-Construction & Security & Features & Limitations \\
+Construction & Security & Main Feature & Main Limitation \\
 \hline

### 2014-09-23 trunk/constantRate/ConstCompFuzzExt-reorg.tex

@@
 The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$).
+\onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph.
+Consider ignoring them here.}
  The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$.
@@
 %Prime candidate sources for authentication have $\Huse\le 0$.
-Unfortunately, prime candidate sources for authentication have more errors than entropy. 
+Unfortunately, sources that have been proposed as prime candidates for authentication have more errors than entropy.
 For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}.
-Physical unclonable problems with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.
+PUFs with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.
 
@@
 Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$.
-Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
+Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure\onote{consider adding here that the class of sources we can deal with (in all constructions) contains many natural sources (or something along these lines).}.
 Table~\ref{tab:upper bounds} summarizes our constructions.
-
+\lnote{Note sure about the first line of this table.
+What does ``exploit distribution structure'' mean?
+Also, can we make it look a bit better?
+Perhaps center.
+Perhaps also remove some lines.
+Perhaps make "main feature" column the same part of speech in each entry.}
+\onote{The table is confusing to me: all the constructions exploits distribution structure.
+In the second construction most symbols must contribute fresh entropy as well.
+Third construction is also reusable.
+Perhaps there is a better way to organize this information.}
 Our first construction provides information-theoretic security.
@@
 Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers).
+Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers \onote{I would skip this since it does not make the result stronger}).
 To tolerate errors, these bits come from an error correcting code.
@@
 However it is known how to construct composable VGB obfuscation for the class of functions we need.}
-composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong} .
 Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}.
 Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+
+\paragraph{The Required Notion of Obfuscation} \onote{How about this paragraph instead of the one above?} Our constructions are base on obfuscation that is simulation-secure, however, we do not require full-fledged virtual black-box obfuscation \cite{barak2001possibility}.
+Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation\cite{bitansky2010strong}.
+We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
+Composable digital lockers with virtual grey-box security where constructed by Bitanski and Canetti under particular number-theoretic assumptions~\cite{bitansky2010strong}.
 
@@
 
+We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
+
 \paragraph{Connection to General Obfuscation}
- \onote{write this!!!}
-We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
-However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
-Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{brakerski2014virtual,barak2014protecting} for all programs.
-However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
-The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero.
-However, we do not know if these functions include proximity point programs.
+We note that fuzzy extractors for sources with errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}.
+A proximity point program $I_w(x)$ tests if $x$ is within Hamming distance $t$ of $w$.
+Recently, such obfuscation was constructed based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13,BitanskyCKP14}.
+This construction however, is still highly impractical, while the obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
+Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.
 
@@
 
+\blind{
 \section*{Acknowledgements}
@@
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-
+}
 \bibliographystyle{alpha}

### 2014-09-23 trunk/constantRate/ConstCompFuzzExt-reorg.tex
worked on the reusability section

@@
 \begin{abstract}
+\lnote{abstract needs work}
 Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.
@@
 The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
-\bnote{negative results stated in our contributions.
-keep there?}
 
@@
 the reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
-The switch to computational security is necessary here: as discussed in \secref{sec:reusable}, it is impossible to obtain such reusability information-theoretically for sources with more errors than entropy.
 This construction requires that the fraction of errors is subconstant.
@@
 Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-Unfortunately, the current techniques for building secure sketches do not work for sources with more errors than entropy, because they lose at least $\log |B_t|$ bits of entropy regardless of the source (this loss is necessary when the source is uniform~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}).
-Moreover, relaxing the security definition to computational will not improve this approach~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Unfortunately, the current techniques for building secure sketches do not work for sources with more errors than entropy, because they lose at least $\log |B_t|$ bits of entropy regardless of the source.
+Moreover, this loss is necessary when the source is uniform~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} or when reusability against a sufficiently rich class of correlations is desired~\cite[Theorem 11]{Boyen2004}.
+
+Addtionally, relaxing the security definition to computational will not improve this approach~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
 Thus, we take a different approach and do not attempt to recover $w$.
@@
 
-Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.
-That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
-This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
-There are two primary parameters of the definition: 1) $q$, the reusability of the fuzzy extractor and 2) what class of correlation is allowed between readings $w_i$ and $w_j$.
-
+An additional desirable feature of fuzzy extractors is reusability~\cite{Boyen2004}.
+Inuitively, it is the ability to support multiple independent enrollments of the same value, allowing users to reuse the same biometric or PUF, for example, with multiple noncommunicating providers.
+More precisely, the algorithm $\gen$ may be run multiple times on correlated readings $w_1,..., w_q$ of a given source.
+Each time, $\gen$ will produce a different pair of values $(r_1, p_1),..., (r_q, p_q)$.
+Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (even though the reproduction procedure $\rep$ at the $i$th provider obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$).
+Because the multiple providers may not trust each other, a stronger security feature (which we satisfy) ensures that each $r_i$ is secure even when all $r_j$ for $j\neq i$ are also given to the adversary.
+
+ Our ability to construct reusable fuzzy extractors depends on the types of correlations allowed among $w_1, \dots, w_q$.
+Boyen \cite{Boyen2004} showed how to do so when each $w_i$ is a shift of $w_1$ by a value that is oblivious to the value of $w_1$ itself (formally, $w_i$ is a result of a transitive isometry applied to $w_1$).
+Boyen also showed that even for this weak class of correlations, any secure sketch must lose at least $\log |B_t|$ entropy~\cite[Theorem 11]{Boyen2004}.
+
+\lnote{why do we need this outsider/insider distinction here? push everything in this paragraph to the discussion of the definition in the appendix}
 Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).
@@
 
-Boyen~\cite{Boyen2004} considers information-theoretic fuzzy extractors with unbounded reusability.
-However, even for this relatively weak class of correlations, Boyen shows that reusability comes at a real cost~\cite[Theorem 11]{Boyen2004}.
-If the correlation between readings contains a set that generates a transitive isometric permutation group, any secure sketch must lose entropy proportional to the number of errors corrected.\footnote{This result strengthens the bounds of~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}, who show this loss is necessary for uniform $W_1$.} This means achieving reusability for sources with more errors than entropy is impossible in this setting.
 %\bnote{old stuff}
@@
 
-To overcome this result, we consider computationally bounded adversaries.
+%To overcome this result, we consider computationally bounded adversaries.
 %We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
@@
 %\end{definition}
-We modify the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss the differences in \apref{sec:comparing reusability}.
+We modify the definition of Boyen~\cite[Definition 7]{Boyen2004} for the computational setting.
+We discuss the differences between our definition and the definitions in Boyen's work \apref{sec:comparing reusability}.
+\lnote{why do we call it ``outsider''?}
 
@@
 
-Finally, we allow the distinguishing adversary to see other keys.
-This is strictly stronger than the definition of Boyen.
+Finally, we allow the distinguishing adversary to see other keys \lnote{we do?
+then why do we call our definition ``outsider''?}.
+This is strictly stronger than the definition of Boyen \lnote{you mean than the outsider security definition of Boyen?}.
 However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
-This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
-Our reusable construction~(\consref{cons:sampling}) is not insider secure.
+This \lnote{what is ``this''?} is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
+Our reusable construction~(\consref{cons:sampling}) is not insider secure \lnote{according to Boyen's notion, right?
+Why not say ``not robust'' and/or clarify that $r_i$ can leak but $p_i$ cannot be modified.}.
 

### 2014-09-23 trunk/constantRate/ConstCompFuzzExt-reorg.tex
modifying abstract

--- 2014-09-23 trunk/constantRate/ConstCompFuzzExt-reorg.tex
@@
 \begin{abstract}
-Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.
-In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns.
+Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).
+In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns.
 For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.
-Unfortunately, it is impossible to provide security for all sources with this property.
-Most known approaches for building fuzzy extractors work in the worst case and cannot be used when a source has \emph{more errors than entropy}.
-
-In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.
-Our constructions are for the Hamming metric over symbols of some alphabet .
-We present both information-theoretic and computational constructions.
-
-Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a super-constant size alphabet.
-In this construction, each symbol must contribute fresh entropy.
-
-Our second and third constructions switch to computational security to provide additional features.
-Our second construction supports the same type of sources as the first construction but also provides reusability.
-A reusable fuzzy extractor can be safely reused across multiple noisy readings of the source~(Boyen, CCS 2004).
-Previous reusable fuzzy extractors only provide security when the noise between repeated readings comes from a small and unrealistic class.
-Our construction is secure as long as the fuzzy extractor is secure on each individual reading.
-Unfortunately, this construction only corrects a sub-constant fraction of errors.
+Unfortunately, it is impossible to provide security for every source with this property.
+Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.
+
+Fortunately, practical sources contain useful structure.
+In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.
+We show an information-theoretic construction and two computational constructions with added features.  Our constructions are for the Hamming metric over symbols of an alphabet.
+
+\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of Hamming errors over a super-constant size alphabet.
+
+\item \textbf{Computational}
+%By adding computational techniques we obtain constructions with additional features.  
+Our second construction is also secure when each symbol contributes fresh entropy.  
+Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).
+A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.
+Our construction is reusable if each reading is a supported source.
+Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.
+This construction corrects a sub-constant fraction of errors.
 %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
@@
 
-Our first two constructions require each symbol of the source to contribute fresh entropy.
-Our third construction removes this requirement and allows symbols to be dependent.
+Our third construction strengthens the class of supported sources and corrects a constant fraction of errors.
+It is secure when individual symbols have high entropy but may be arbitrarily correlated.
 This change requires a significantly larger alphabet.
@@
 The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
-
-\bigskip
+\end{itemize}
+
+\medskip
 
@@
 Perhaps there is a better way to organize this information.}
+\bnote{these comments are all valid.  I'm not sure what to do about it.  Maybe organize by techniques and then notes (for limitations and features?)}
 Our first construction provides information-theoretic security.
@@
 Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers \onote{I would skip this since it does not make the result stronger}).
+Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker.
 To tolerate errors, these bits come from an error correcting code.
@@
 
-We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
-We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is
-%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
+%We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
+%We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is
+%%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
 However it is known how to construct composable VGB obfuscation for the class of functions we need.}
-composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong} .
+%composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong} .
 Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}.
-Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
-
-\paragraph{The Required Notion of Obfuscation} \onote{How about this paragraph instead of the one above?} Our constructions are base on obfuscation that is simulation-secure, however, we do not require full-fledged virtual black-box obfuscation \cite{barak2001possibility}.
-Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation\cite{bitansky2010strong}.
+%Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+
+\paragraph{The Required Notion of Point Obfuscation} 
+Our constructions use simulation-secure  obfuscation of digital lockers, however, we do not require full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
+Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation~\cite{bitansky2010strong}.
 We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
-Composable digital lockers with virtual grey-box security where constructed by Bitanski and Canetti under particular number-theoretic assumptions~\cite{bitansky2010strong}.
+Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}.
 
@@
 \paragraph{Connection to General Obfuscation}
-We note that fuzzy extractors for sources with errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}.
-A proximity point program $I_w(x)$ tests if $x$ is within Hamming distance $t$ of $w$.
-Recently, such obfuscation was constructed based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13,BitanskyCKP14}.
-This construction however, is still highly impractical, while the obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
+We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}.
+A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$.
+Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
+The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  The obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
 Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.

### 2014-09-23 info-bounds/FuzzyExtPossibility.tex
working on isoparametric inequality proof

@@
 \newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
+\newcommand{\bnd}{\ensuremath{\class{Bnd}}\xspace}
+\newcommand{\inter}{\ensuremath{\class{Inter}}\xspace}
 \newcommand{\zo}{\ensuremath{\{0, 1\}}}
@@
 \end{definition}
-Note that correctness is only required to hold for points in the support of the distribution $W$, the algorithms are allowed the description of $W$ and security need only hold for the distribution $W$.
-When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to make use of the (possibly)~exponential size distributions.
-It is not clear how to meaningfully define efficient distribution aware algorithms.
-If the algorithms were required to be efficient, they could only encode a negligible portion of the probability space of $W$, and would have to ``work'' on all distributions $W'$ with the same probability mass function on the encoded space.
-This would make the algorithms a distribution-oblivious fuzzy extractor for all distributions with this property.
-
-We begin with by showing that secure sketches and fuzzy extractors are possible in the distribution aware setting whenever there is super-logarithmic fuzzy min-entropy.
-We then turn to the standard \emph{distribution oblivious} setting.
+Note (\sketch, \rec) know the description of $W$ and security only holds for $W$.
+When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to use the (possibly)~exponential size distributions.
+One possible approach is to allow $(\sketch, \rec)$ an oracle to the probability mass function of $W$.
+Our constructions do not work in this setting.\bnote{why am I talking about this?}
 
@@
 \section{Distribution-Aware  Sketches}
-In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
+\label{sec:distribution aware}
+In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors) whenever $\Hfuzz(W)= \omega(\log n)$.
 We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.
@@
 \begin{corollary}
-Let $n$ be a security parameter and let $\mathcal{M} =\zo^n$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ residual min-entropy and overwhelming correctness.
-Furthermore, there exists a $(\mathcal{M}, \Hoo(W), \ell = \omega(\log n), \epsilon)$ distribution aware fuzzy extractor with $\epsilon = \ngl(n)$) and overwhelming correctness.
+\label{cor:extension to fuzz ext}
+Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+(Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
 \end{corollary}
+
+\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.
+Going forward we will consider specific metric spaces, namely the Hamming metric.
 \section{Distribution-Oblivious Sketches}
@@
 
-\subsection{Impossibility of info-theoretic sketches}
+\subsection{Fuzzy min-entropy is not sufficient for secure sketches}
 In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.
@@
 \item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
-\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\ell-t+1)\log |\mathbb{F}|+1$. 
+\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\gamma-t+1)\log |\mathbb{F}|+1$. 
 \item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
@@
 Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\ell , b_\ell$.
-The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\ell$ are uniformly random.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
 \end{proof}
 \begin{lemma}
-Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\ell-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
+Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
 Dealing with imperfect correctness makes the bound more complicated.
@@
 Any randomness necessary for the \rec algorithm can be provided by \sketch.
-We will however, not consider these coins in our security analysis.
+We do not consider these coins in our security analysis~(and thus, they can be considered private).
 
@@
 Consider some $p\in A_{ss}$.
-We now show that $H_0(V | p) \le n-\log |B_t|$.
+We now show that $H_0(V | p) \le (\gamma-t+1)\log |\mathbb{F}|$.
 Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.
@@
 \[
-\log \expe_{s\in \sketch(V)} 2^{h_s} = \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \tilde{H}_0(V | \sketch(V)) %\le   (\ell-t+1)\log |\mathbb{F}|+1.
-\]  
-Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.
+\log \expe_{s\in \sketch(V)} 2^{h_s} = \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \tilde{H}_0(V | \sketch(V)) %\le   (\gamma-t+1)\log |\mathbb{F}|+1.
+\]  
+Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.
 Consider these possible values for $Z$ as bins to be filled with the $2^{h_s}$ balls~(possible values of $V | \sketch(V)=s$).
@@
 \tilde{H}_0(V |Z  , \sketch(V) = s) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
-&= \log \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \right)
+&= \log \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)
 \end{align*}
@@
 \tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V | Z, \sketch(V) =s )}\\
-&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \right)\\
-&= \log \frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \expe_{s\in \sketch(V)} 2^{h_s}\\
-&=\log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + \log \expe_{s\in \sketch(V)} 2^{h_s}\\
-&=\log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V))\\ 
-&\le \log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + (\ell-t+1)\log |\mathbb{F}|+1\\
-&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-1) \log (|\mathbb{F}|-1)+1\\
-&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-2) \log |\mathbb{F}|+1\\
+&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)\\
+&= \log \frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\\
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \log \expe_{s\in \sketch(V)} 2^{h_s}\\
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V))\\ 
+&\le \log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + (\gamma-t+1)\log |\mathbb{F}|+1\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+1\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}|+1\\
 &\le \Theta(1)
@@
 
+\subsubsection{Computational secure sketches}
+Fuller et al.
+showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+%This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
+The definitional of Fuller et al. is uses HILL entropy.
+
+HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  Fuller et al.~use a weak version due to Gentry and Wichs~\cite{gentry2011separating}.
+
+\begin{definition}
+\label{def:relaxed hill}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
+\end{definition}
+
+A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $s_{sec}, \epsilon_{sec}$ parameters to the definition, representing the distinguishing circuit).
+By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
+
 \begin{corollary}
-This is also impossible for computational sketches that retain hill entropy.\bnote{fill this in, use asiacrypt result.}
+\label{cor:imposs comp sketch}
+Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
+There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
+If
+\begin{itemize}
+\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
+\item $t\ge 4$,
+\item and $\epsilon + t\delta < 1/16$,
+\end{itemize}
+ then $\tilde{m} =O(1)$.
 \end{corollary}
 
-%\subsection{Conductors}
-%Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
-%\begin{lemma}
-%Not possible for information-theoretic objects.
-%\end{lemma}
+\begin{corollary}
+\label{cor:rec yields sketch}
+Let $\mathcal{Z}$ be an alphabet.
+Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
+If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+$4(\epsilon+t\delta)$. 
+\end{corollary}
+
+\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
+Unpredictable secure sketches is implied by virtual-grey box obfuscation of point functions~\cite{BitanskyCKP14}.
+
+\section{Distribution-Oblivious Fuzzy Extractors}
+In the previous section, we showed a family of distributions that does not admit a secure sketch.
+In this section, we extend this result to fuzzy extractors.
+The main difficulty is showing that fuzzy extractors must cause a significantly entropy drop in $V$.
+This is not true for all metric spaces.
+We begin with the case of perfect correctness in the Hamming metric.
+
+\begin{theorem}
+\label{thm:imposs fuzz ext}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
+\bnote{what is $\epsilon$?
+what are the other parameters?}
+\end{theorem}
+ \bnote{write a proof!}
+\begin{proof}
+The only difference between \thref{thm:imposs fuzz ext} and \thref{thm:imposs sketch} is the functionality required of the algorithms $(\gen, \rep)$.
+Thus, we must prove that a fuzzy extractor must still cause a significant drop in the entropy of $V$:
+
+\begin{lemma}
+Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$ and $\epsilon=$ \bnote{what is this?}.  Then $\tilde{H}_0(V | \gen(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.
+\end{lemma}
+\begin{proof}
+We assume that $\rep$ is deterministic in our analysis.
+Any randomness necessary for the \rep algorithm can be provided by $\gen$.
+We do not consider these coins in our security analysis~(and thus, they can be considered private).
+Denote by $(R, P) \leftarrow \gen(V)$.
+
+%By the definition of correctness for $(\sketch, \rec)$, 
+%\[
+%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+%\]
+%For most $p$, $\rec$ works on most neighbors of $w$.  
+%Fix some $w$.  
+By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
+\[
+(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+\]
+%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+
+Consider some $p^*\in A_{ss}$.
+We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.
+Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p$ is at least $(1-2\epsilon)2^\kappa$.
+Note that, $R|P=p$ is the set of possible keys.
+
+The set of possible keys induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique $Q_{p^*,r}$ such that $\rep(w, p^*) =r$.
+Define two sets, called the boundary and interior respectively: \begin{align*}
+\bnd(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\},\\
+\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\}.
+\end{align*}
+
+Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$, for any $r_1, r_2$, $\inter(Q_{p^*, r_1}) \cap \inter(Q_{p^*, r_2}) =\emptyset$ and the union of all boundaries and interiors is the entire space.
+Furthermore, note that for any $r\in \zo^\kappa$,  $\Pr[V\in Q_{p^*, r}] = \ngl(n).$\bnote{need to fill in this distinguishing argument, note this doesn't need to be the case for all $p^*$ just on average.
+need another markov inequality.}\bnote{what can we say about the relative sizes of these spaces?}
+
+We now consider the distribution of $V | P=p^*$.
+By the functionality of $(\gen, \rep)$, for every $v\in V| P=p^*$, $v\in Int(Q_{p, r})$.
+Furthermore, if $v$ is not in some interior then $v\not \in V | P=p^*$.
+Thus, it suffices to show that $\frac{\sum_{r} |\inter(Q_{p^*, r})|}{\mathcal{M}} = XXX$\bnote{fill this in.}
+
+To show this we any such partitioning of the metric space must have the majority of points lying on the boundary.  This is true for the Hamming metric.
+\begin{lemma}[Isoparametric Inequality]
+\bnote{XXXX}
+\end{lemma}
+\end{proof}
+\end{proof}
+
 \bibliographystyle{alpha}

### 2014-09-24 trunk/info-bounds/FuzzyExtPossibility.tex
working on isoparametric inequality proof

@@
 
-\subsection{Computational secure sketches}
-We do not consider a computational version of secure sketches.
+\subsubsection{Computational secure sketches}
 Fuller et al.
 showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+%This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
+The definitional of Fuller et al. is uses HILL entropy.
+
+HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  Fuller et al.~use a weak version due to Gentry and Wichs~\cite{gentry2011separating}.
+
+\begin{definition}
+\label{def:relaxed hill}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
+\end{definition}
+
+A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $s_{sec}, \epsilon_{sec}$ parameters to the definition, representing the distinguishing circuit).
+By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
 
 \begin{corollary}
-This is also impossible for computational sketches that retain hill entropy.\bnote{fill this in, use asiacrypt result.}
+\label{cor:imposs comp sketch}
+Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
+There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
+If
+\begin{itemize}
+\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
+\item $t\ge 4$,
+\item and $\epsilon + t\delta < 1/16$,
+\end{itemize}
+ then $\tilde{m} =O(1)$.
 \end{corollary}
 
-%\subsection{Conductors}
-%Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
-%\begin{lemma}
-%Not possible for information-theoretic objects.
-%\end{lemma}
+%\begin{corollary}
+%\label{cor:rec yields sketch}
+%Let $\mathcal{Z}$ be an alphabet.
+Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
+%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+%$4(\epsilon+t\delta)$. 
+%\end{corollary}
+
+\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
+Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+
+\section{Distribution-Oblivious Fuzzy Extractors}
+In the previous section, we showed a family of distributions that does not admit a secure sketch.
+In this section, we extend this result to fuzzy extractors.
+The main difficulty is showing that fuzzy extractors must cause a significantly entropy drop in $V$.
+This is not true for all metric spaces.
+We begin with the case of perfect correctness in the Hamming metric.
+
+\begin{theorem}
+\label{thm:imposs fuzz ext}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
+\bnote{what is $\epsilon$?
+what are the other parameters?}
+\end{theorem}
+ \bnote{write a proof!}
+\begin{proof}
+The only difference between \thref{thm:imposs fuzz ext} and \thref{thm:imposs sketch} is the functionality required of the algorithms $(\gen, \rep)$.
+Thus, we must prove that a fuzzy extractor must still cause a significant drop in the entropy of $V$:
+
+\begin{lemma}
+Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$ and $\epsilon=$ \bnote{what is this?}.  Then $\tilde{H}_0(V | \gen(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.
+\end{lemma}
+\begin{proof}
+We assume that $\rep$ is deterministic in our analysis.
+Any randomness necessary for the \rep algorithm can be provided by $\gen$.
+We do not consider these coins in our security analysis~(and thus, they can be considered private).
+Denote by $(R, P) \leftarrow \gen(V)$.
+
+%By the definition of correctness for $(\sketch, \rec)$, 
+%\[
+%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+%\]
+%For most $p$, $\rec$ works on most neighbors of $w$.  
+%Fix some $w$.  
+By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
+\[
+(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+\]
+%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+
+Consider some $p^*\in A_{ss}$.
+We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.
+Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p$ is at least $(1-2\epsilon)2^\kappa$.
+Note that, $R|P=p$ is the set of possible keys.
+
+The set of possible keys induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique $Q_{p^*,r}$ such that $\rep(w, p^*) =r$.
+Define two sets, called the boundary and interior respectively: \begin{align*}
+\bnd(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\},\\
+\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\}.
+\end{align*}
+
+Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$.
+Furthermore, note that for any $r\in \zo^\kappa$,  $ | Q_{p^*, r}| \le (1+\epsilon)2^\kappa.$\bnote{need to fill in this distinguishing argument, note this doesn't need to be the case for all $p^*$ just on average.
+need another markov inequality.}\bnote{what can we say about the relative sizes of these spaces?}
+
+We now consider the distribution of $V | P=p^*$.
+By the functionality of $(\gen, \rep)$, for every $v\in V| P=p^*$, $v\in Int(Q_{p, r})$.
+Furthermore, if $v$ is not in some interior then $v\not \in V | P=p^*$.
+Thus, it suffices to show that $\frac{\sum_{r} |\inter(Q_{p^*, r})|}{\mathcal{M}} = XXX$\bnote{fill this in.}
+
+To show this we any such partitioning of the metric space must have the majority of points lying on the boundary.  This is true for the Hamming metric.
+\begin{lemma}[Isoparametric Inequality]
+\bnote{XXXX}
+\end{lemma}
+\end{proof}
+\end{proof}
+
 \bibliographystyle{alpha}

### 2014-09-24 constantRate/ConstCompFuzzExt-reorg.tex
working on reusability

@@
 \begin{abstract}
-Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.
-In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns.
+\lnote{needs work}
+Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).
+In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns.
 For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.
-Unfortunately, it is impossible to provide security for all sources with this property.
-Most known approaches for building fuzzy extractors work in the worst case and cannot be used when a source has \emph{more errors than entropy}.
-
-In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.
-Our constructions are for the Hamming metric over symbols of some alphabet .
-We present both information-theoretic and computational constructions.
-
-Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a super-constant size alphabet.
-In this construction, each symbol must contribute fresh entropy.
-
-Our second and third constructions switch to computational security to provide additional features.
-Our second construction supports the same type of sources as the first construction but also provides reusability.
-A reusable fuzzy extractor can be safely reused across multiple noisy readings of the source~(Boyen, CCS 2004).
-Previous reusable fuzzy extractors only provide security when the noise between repeated readings comes from a small and unrealistic class.
-Our construction is secure as long as the fuzzy extractor is secure on each individual reading.
-Unfortunately, this construction only corrects a sub-constant fraction of errors.
+Unfortunately, it is impossible to provide security for every source with this property.
+Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.
+
+Fortunately, practical sources contain useful structure.
+In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.
+We show an information-theoretic construction and two computational constructions with added features.  Our constructions are for the Hamming metric over symbols of an alphabet.
+
+\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of Hamming errors over a super-constant size alphabet.
+
+\item \textbf{Computational}
+%By adding computational techniques we obtain constructions with additional features.  
+Our second construction is also secure when each symbol contributes fresh entropy.  
+Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).
+A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.
+Our construction is reusable if each individual reading is a supported source.
+Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.
+This construction corrects a sub-constant fraction of errors.
 %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
@@
 The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$).
+The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space.% (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$).
+\onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph.
+Consider ignoring them here.}
  The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$.
@@
 Table~\ref{tab:upper bounds} summarizes our constructions.
-\lnote{Note sure about the first line of this table.
-What does ``exploit distribution structure'' mean?
-Also, can we make it look a bit better?
-Perhaps center.
-Perhaps also remove some lines.
-Perhaps make "main feature" column the same part of speech in each entry.}
-
+\bnote{table better?}
 Our first construction provides information-theoretic security.
-It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols.
+It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols~(\defref{def:partial source}).
 %It requires an alphabet size that is super constant in the security parameter.
@@
 \begin{table}
-\begin{tabular}{l | l | l | l }
-Construction & Security & Main Feature & Main Limitation \\
+\begin{tabular}{l l l c c}
+Construction & Security & Source Structure & Error-Tolerance & Alphabet Size\\
 \hline
-\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
-&&structure & fresh entropy \\\hline
-\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
-&& & error tolerance\\\hline
-\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
-& &  symbols & size symbols
+\consref{cons:info theoretic} & Info-theoretic  & Partial block source& $\Theta(\gamma)$ & $\omega(1)$ \\
+\consref{cons:sampling} & Reusable Computational & Partial block source& $o(\gamma)$ & $\omega(1)$ \\
+\consref{cons:first construction} & Computational & Unguessable block source & $\Theta(\gamma)$ & $n^{\omega(1)}$
 \end{tabular}
-\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
+\caption{Summary of new constructions.
+All constructions support families of distributions with more errors than entropy.
+Partial blocks sources are defined in \defref{def:partial source} and unguessable block sources are defined in \defref{def:block guessable}.}
 \label{tab:upper bounds}
 \end{table}
+
+%\begin{table}
+%\begin{tabular}{l | l | l | l }
+%Construction & Security & Main Feature  & Main Limitations \\
+%\hline
+%\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
+%&&structure & fresh entropy \\\hline
+%\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
+%&& & error tolerance\\\hline
+%\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
+%& &  symbols & size symbols
+%\end{tabular}
+%\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
+%\label{tab:upper bounds}
+%\end{table}
 
@@
 Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers).
+Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker.
 To tolerate errors, these bits come from an error correcting code.
@@
 
-We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
-We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is 
-%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
+%We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
+%We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is
+%%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
 However it is known how to construct composable VGB obfuscation for the class of functions we need.}
-composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}.
+%composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong} .
 Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}.
-Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+%Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
+
+\paragraph{The Required Notion of Point Obfuscation} 
+Our constructions use simulation-secure  obfuscation of digital lockers, however, we do not require full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
+Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation~\cite{bitansky2010strong}.
+We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
+Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}.
 
@@
 
+We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
+
 \paragraph{Connection to General Obfuscation}
- \onote{write this!!!}
-We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$.
-However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions.
-Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{brakerski2014virtual,barak2014protecting} for all programs.
-However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model.
-The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero.
-However, we do not know if these functions include proximity point programs.
+We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}.
+A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$.
+Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
+The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  The obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
+Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.
 
@@
 
-Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.
-That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
-This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
-There are two primary parameters of the definition: 1) $q$, the reusability of the fuzzy extractor and 2) what class of correlation is allowed between readings $w_i$ and $w_j$.
-
-Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).
-Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).
-Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups.
-Boyen transforms this construction to insider security using random oracles.
-In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.
-Unfortunately, this class of correlation is relatively weak and unrealistic.
+An additional desirable feature of fuzzy extractors is reusability~\cite{Boyen2004}.
+Inuitively, it is the ability to support multiple independent enrollments of the same value, allowing users to reuse the same biometric or PUF, for example, with multiple noncommunicating providers.
+More precisely, the algorithm $\gen$ may be run multiple times on correlated readings $w_1,..., w_q$ of a given source.
+Each time, $\gen$ will produce a different pair of values $(r_1, p_1),..., (r_q, p_q)$.
+Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (even though the reproduction procedure $\rep$ at the $i$th provider obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$).
+Because the multiple providers may not trust each other, a stronger security feature (which we satisfy) ensures that each $r_i$ is secure even when all $r_j$ for $j\neq i$ are also given to the adversary.
+
+ Our ability to construct reusable fuzzy extractors depends on the types of correlations allowed among $w_1, \dots, w_q$.
+Boyen \cite{Boyen2004} showed how to do so when each $w_i$ is a shift of $w_1$ by a value that is oblivious to the value of $w_1$ itself (formally, $w_i$ is a result of a transitive isometry applied to $w_1$).
+Boyen also showed that even for this weak class of correlations, any secure sketch must lose at least $\log |B_t|$ entropy~\cite[Theorem 11]{Boyen2004}.
+
 %\paragraph{Previous Negative Results}
 
-Boyen~\cite{Boyen2004} considers information-theoretic fuzzy extractors with unbounded reusability.  
-However, even for this relatively weak class of correlations, Boyen shows that reusability comes at a real cost~\cite[Theorem 11]{Boyen2004}.
-If the correlation between readings contains a set that generates a transitive isometric permutation group, any secure sketch must lose entropy proportional to the number of errors corrected.\footnote{This result strengthens the bounds of~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}, who show this loss is necessary for uniform $W_1$.} This means achieving reusability for sources with more errors than entropy is impossible in this setting.
 %\bnote{old stuff}
@@
 %\end{definition}
-We modify the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss the differences in \apref{sec:comparing reusability}.
-
-\begin{definition}[Outsider Reusable Fuzzy Extractors]
+We modify the definition of Boyen~\cite[Definition 6]{Boyen2004} for the computational setting.  We discuss the our definition and definitions due to Boyen in \apref{sec:comparing reusability}.
+
+\begin{definition}[Reusable Fuzzy Extractors]
 \label{def:outsider fuzz ext}
@@
 Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
-\begin{enumerate}%[leftmargin=-.6in]
-\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
-\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
+\begin{itemize}%[leftmargin=-.6in]
+\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
+\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
 Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.
 The challenger sets $w_{i+1} = \delta_i(w_1)$.
-\item[Distinguishing] The advantage of $D$ is
+\item \textbf{Distinguishing} The advantage of $D$ is
 \begin{align*}
@@
 where $u$ is a uniformly random string.
-\end{enumerate}
+\end{itemize}
 $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
@@
 A source $W = W_1| ...
-|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block source} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
 \[
@@
 
-We show some examples of unguessable block distributions in \apref{sec:characterize}.
-In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block distribution~(\clref{cl:all blocks entropy}).
+We show some examples of unguessable block sources in \apref{sec:characterize}.
+In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block source~(\clref{cl:all blocks entropy}).
 
@@
 Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
 Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.
@@
 \]
-The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
 For this type of source the required entropy is $\Hoo(W) = \gamma\omega(\log n)$.
@@
 
-\subsection{Defining Reusability in the Computational Setting}
+\subsection{Reusability Fuzzy Extractors}
 \label{sec:comparing reusability}
 
+The goal of a reusable fuzzy extractor is to allow enrollment of a source across multiple services.  A service $i$ sees an reading of the source $w_i$.
+Boyen considers two versions of reusable fuzzy extractors, first where the adversary sees $p_1,..., p_q$~(outsider security~\cite[Definition 6]{Boyen2004}) and tries to learn about the values $w_1,..., w_q$ or the keys $r_1,..., r_q$.
+Second, where the adversary controls some subset of the servers and can key generation on arbitrary $p_i'$~(insider security~\cite[Definition 7]{Boyen2004}).
+This allows the adversary to learn a subset of keys $r_i$~(by performing key generation on the valid $p_i$).
+This definition makes sense when servers are compromised~(after enrollment) and act maliciously.
+
+Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups.
+Boyen transforms this construction to insider security using random oracles.
+%In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.
+
+Insider security strengthens outsider security in two ways.
+First, it allows the adversary to see some subset of keys, second it allows the adversary to perform regeneration on arbitrary $p_i$.
+This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.
+Robust fuzzy extractors provide security against modified $p$.
+In this work, we show reusability when some $r_i$ are observed but do not handle the issue of robustness.
+That is, we assume passive servers.
+Our definition lies between outsider and insider security.
+
+We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
 The definition of Boyen considers a single adversary.
@@
 The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
-However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.
+However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.
 Our construction satisfies this alternative adaption as well.}
-
 Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
@@
 
-Finally, we allow the distinguishing adversary to see other keys.
-This is strictly stronger than the definition of Boyen.
+%Finally, we allow the distinguishing adversary to see other keys \lnote{we do?
+then why do we call our definition ``outsider''?}.
+This is strictly stronger than the definition of Boyen \lnote{you mean than the outsider security definition of Boyen?}.
 However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
-This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
-Our reusable construction~(\consref{cons:sampling}) is not insider secure.
+This \lnote{what is ``this''?} is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
+Our reusable construction~(\consref{cons:sampling}) is not insider secure \lnote{according to Boyen's notion, right?
+Why not say ``not robust'' and/or clarify that $r_i$ can leak but $p_i$ cannot be modified.}.
 
@@
 See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
-\section{Characterizing unguessable block distributions}
+\section{Characterizing unguessable block sources}
 \label{sec:characterize}
@@
 In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).
-We first show some sources that are unguessable block distributions~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block distributions~(\secref{sec:negative ex}).
+We first show some sources that are unguessable block sources~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block sources~(\secref{sec:negative ex}).
 
@@
 Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.
-Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block distribution.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block distribution.
+Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block source.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block source.
 \end{claim}
@@
 Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.
-If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
+If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block source.
 \end{claim}
@@
 Suppose that for all $j$, $\Hoo(W_j)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is super-logarithmic).
-Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block distribution.
+Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block source.
 \end{claim}
@@
 If an adversary can learn blocks in succession they can eventually recover the entire secret.
-In order for a distribution to be block unguessable the adversary must get ``stuck'' early enough in their recovery process.
+In order for a source to be block unguessable the adversary must get ``stuck'' early enough in their recovery process.
 This translates to having a super-logarithmic jump early enough.
@@
 \begin{claim}
-Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\gamma$ such that for all $j\le \gamma-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\gamma-\beta+1)$, then $W$ is not $(q, 0, \beta)$-unguessable block distribution.
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\gamma$ such that for all $j\le \gamma-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\gamma-\beta+1)$, then $W$ is not $(q, 0, \beta)$-unguessable block source.
 \end{claim}
@@
 \subsection{Security}
-The proof of security for \consref{cons:sampling} uses the definition of block unguessable distributions~(\defref{def:block guessable}).
+The proof of security for \consref{cons:sampling} uses the definition of block unguessable sources~(\defref{def:block guessable}).
 This definition is adaptive and discussed in \apref{sec:characterize}.
@@
 \item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
-\item The outputs $V_1,..., V_\ell$ are a block unguessable distribution.  This is made formal in the following corollary:
+\item The outputs $V_1,..., V_\ell$ are a block unguessable source.  This is made formal in the following corollary:
 \begin{corollary}
@@
 Take any $q=\poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
+For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block source.
 \end{corollary}
-\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable distribution.
+\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable source.
 \end{itemize}
@@
 \lnote{I need to check this}
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable distribution.
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable source.
 The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .
-Let $W$ be a $(q, \alpha'' = \omega(\log n), 0)$-unguessable block distribution.
+Let $W$ be a $(q, \alpha'' = \omega(\log n), 0)$-unguessable block source.
 Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
@@
 Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.
-However, security is more complicated, the main difficulty is that the definition of block unguessable distributions~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.
+However, security is more complicated, the main difficulty is that the definition of block unguessable sources~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.
 This means we must limit our indistinguishable distribution to blocks that are difficult to guess.
@@
 Let $\mathcal{O}$ be a $\gamma$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.
-Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.
+Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block source.
 Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$.
@@
 \label{cl:ent bounded away from n}
-If $W$ is a $(q, \alpha, \beta)$-block unguessable distribution over $\mathcal{Z}$ then $\alpha \le \log |\mathcal{Z}|-\log q$.
+If $W$ is a $(q, \alpha, \beta)$-block unguessable source over $\mathcal{Z}$ then $\alpha \le \log |\mathcal{Z}|-\log q$.
 \end{claim}
@@
 \bnote{Leo I changed some of this under you.  It wasn't clear or probably right as written.}
-Let $W$ be a $(q, \alpha, \beta)$-block unguessable distribution.  Let $J\subset\{1,..., \gamma\}$ the set of good indices.
+Let $W$ be a $(q, \alpha, \beta)$-block unguessable source.  Let $J\subset\{1,..., \gamma\}$ the set of good indices.
 It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.

### 2014-09-24 trunk/constantRate/ConstCompFuzzExt-reorg.tex
working on reusability

@@
 \begin{abstract}
+\lnote{needs work}
 Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).
@@
 A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.
-Our construction is reusable if each reading is a supported source.
+Our construction is reusable if each individual reading is a supported source.
 Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.
@@
 The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$).
+The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space.% (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$).
 \onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph.
@@
 Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$.
-Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure\onote{consider adding here that the class of sources we can deal with (in all constructions) contains many natural sources (or something along these lines).}.
+Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
 Table~\ref{tab:upper bounds} summarizes our constructions.
-\lnote{Note sure about the first line of this table.
-What does ``exploit distribution structure'' mean?
-Also, can we make it look a bit better?
-Perhaps center.
-Perhaps also remove some lines.
-Perhaps make "main feature" column the same part of speech in each entry.}
-\onote{The table is confusing to me: all the constructions exploits distribution structure.
-In the second construction most symbols must contribute fresh entropy as well.
-Third construction is also reusable.
-Perhaps there is a better way to organize this information.}
-\bnote{these comments are all valid.  I'm not sure what to do about it.  Maybe organize by techniques and then notes (for limitations and features?)}
+\bnote{table better?}
 Our first construction provides information-theoretic security.
-It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols.
+It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols~(\defref{def:partial source}).
 %It requires an alphabet size that is super constant in the security parameter.
@@
 \begin{table}
-\begin{tabular}{l | l | l | l }
-Construction & Security & Main Feature & Main Limitation \\
+\begin{tabular}{l l l c c}
+ & Security & Source Structure & Error-Tolerance & Alphabet Size\\
 \hline
-\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
-&&structure & fresh entropy \\\hline
-\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
-&& & error tolerance\\\hline
-\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
-& &  symbols & size symbols
+\consref{cons:info theoretic} & Info-theoretic  & Partial block source& $\Theta(\gamma)$ & $\omega(1)$ \\
+\consref{cons:sampling} & Reusable Computational & Partial block source& $o(\gamma)$ & $\omega(1)$ \\
+\consref{cons:first construction} & Computational & Unguessable block source & $\Theta(\gamma)$ & $n^{\omega(1)}$
 \end{tabular}
-\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
+\caption{Summary of new constructions.
+All constructions support families of distributions with more errors than entropy.
+Partial blocks sources are defined in \defref{def:partial source} and unguessable block sources are defined in \defref{def:block guessable}.}
 \label{tab:upper bounds}
 \end{table}
+
+%\begin{table}
+%\begin{tabular}{l | l | l | l }
+%Construction & Security & Main Feature  & Main Limitations \\
+%\hline
+%\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
+%&&structure & fresh entropy \\\hline
+%\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
+%&& & error tolerance\\\hline
+%\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
+%& &  symbols & size symbols
+%\end{tabular}
+%\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
+%\label{tab:upper bounds}
+%\end{table}
 
@@
 
-Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.
-That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.
-This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.
-There are two primary parameters of the definition: 1) $q$, the reusability of the fuzzy extractor and 2) what class of correlation is allowed between readings $w_i$ and $w_j$.
-
-Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).
-Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).
-Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups.
-Boyen transforms this construction to insider security using random oracles.
-In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.
-Unfortunately, this class of correlation is relatively weak and unrealistic.
+An additional desirable feature of fuzzy extractors is reusability~\cite{Boyen2004}.
+Inuitively, it is the ability to support multiple independent enrollments of the same value, allowing users to reuse the same biometric or PUF, for example, with multiple noncommunicating providers.
+More precisely, the algorithm $\gen$ may be run multiple times on correlated readings $w_1,..., w_q$ of a given source.
+Each time, $\gen$ will produce a different pair of values $(r_1, p_1),..., (r_q, p_q)$.
+Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (the reproduction procedure $\rep$ at the $i$th provider still obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$).
+Because the multiple providers may not trust each other, a stronger security feature (which we satisfy) ensures that each $r_i$ is secure even when all $r_j$ for $j\neq i$ are also given to the adversary.
+
+ Our ability to construct reusable fuzzy extractors depends on the types of correlations allowed among $w_1, \dots, w_q$.
+Boyen \cite{Boyen2004} showed how to do so when each $w_i$ is a shift of $w_1$ by a value that is oblivious to the value of $w_1$ itself (formally, $w_i$ is a result of a transitive isometry applied to $w_1$).
+Boyen also showed that even for this weak class of correlations, any secure sketch must lose at least $\log |B_t|$ entropy~\cite[Theorem 11]{Boyen2004}.
+
 %\paragraph{Previous Negative Results}
 
-Boyen~\cite{Boyen2004} considers information-theoretic fuzzy extractors with unbounded reusability.
-However, even for this relatively weak class of correlations, Boyen shows that reusability comes at a real cost~\cite[Theorem 11]{Boyen2004}.
-If the correlation between readings contains a set that generates a transitive isometric permutation group, any secure sketch must lose entropy proportional to the number of errors corrected.\footnote{This result strengthens the bounds of~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}, who show this loss is necessary for uniform $W_1$.} This means achieving reusability for sources with more errors than entropy is impossible in this setting.
 %\bnote{old stuff}
@@
 Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
-\begin{enumerate}%[leftmargin=-.6in]
-\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
-\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
-Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.
-The challenger sets $w_{i+1} = \delta_i(w_1)$.
-\item[Distinguishing] The advantage of $D$ is
+\begin{itemize}%[leftmargin=-.6in]
+\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
+\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
+Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
+\item \textbf{Distinguishing} The advantage of $D$ is
 \begin{align*}
@@
 
-\subsection{Defining Reusability in the Computational Setting}
+\subsection{Reusability Fuzzy Extractors}
 \label{sec:comparing reusability}
 
+The goal of a reusable fuzzy extractor is to allow enrollment of a source across multiple services.  A service $i$ sees an reading of the source $w_i$.
+Boyen considers two versions of reusable fuzzy extractors, first where the adversary sees $p_1,..., p_q$~(outsider security~\cite[Definition 6]{Boyen2004}) and tries to learn about the values $w_1,..., w_q$ or the keys $r_1,..., r_q$.
+Second, where the adversary controls some subset of the servers and can key generation on arbitrary $p_i'$~(insider security~\cite[Definition 7]{Boyen2004}).
+This allows the adversary to learn a subset of keys $r_i$~(by performing key generation on the valid $p_i$).
+This definition makes sense when servers are compromised~(after enrollment) and act maliciously.
+In both definitions, the adversary creates a perturbation function $_i$ after seeing $p_1,..., p_{i-1}$~(and generated keys for outsider security) and the challenger generates $w_i = f_i(w_1)$.
+The definition is parameterized by the class of allowed perturbation functions.
+
+Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the perturbation family is a transitive isometric permutation groups.
+Boyen transforms this construction to insider security using random oracles.
+%In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.
+
+Insider security strengthens outsider security in two ways.
+First, it allows the adversary to see some subset of keys, second it allows the adversary to perform key generation on arbitrary $p_i$.
+This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.
+Robust fuzzy extractors provide security against modified $p$.
+In this work, we show reusability when $r_i$ are observed but do not handle the issue of robustness.
+That is, we assume keys may be exposed but servers keep honest state.
+Our definition lies between outsider and insider security.
+
+We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
 The definition of Boyen considers a single adversary.

### 2014-09-24 constantRate/ConstCompFuzzExt-reorg.tex
trying to improve table

@@
 \begin{table}
-\begin{tabular}{l l l c c}
-Construction & Security & Source Structure & Error-Tolerance & Alphabet Size\\
+{ \centering
+\begin{tabular}{l l l l l}
+ & Security & Source Structure & Error-Tolerance & Alphabet Size\\
 \hline
-\consref{cons:info theoretic} & Info-theoretic  & Partial block source& $\Theta(\gamma)$ & $\omega(1)$ \\
-\consref{cons:sampling} & Reusable Computational & Partial block source& $o(\gamma)$ & $\omega(1)$ \\
-\consref{cons:first construction} & Computational & Unguessable block source & $\Theta(\gamma)$ & $n^{\omega(1)}$
+Cons. \ref{cons:info theoretic} & Info-theoretic  & Most symbols  & Constant fraction & Super constant \\
+& & contribute entropy & &\\\hline
+Cons. \ref{cons:sampling} & Reusable & Most symbols & Sub constant fraction & Super constant \\
+& Computational & contribute entropy & &\\\hline
+Cons. \ref{cons:first construction} & Computational & Symbols correlated  & Constant fraction & Super\\
+& & but hard to guess && polynomial
 \end{tabular}
-\caption{Summary of new constructions.
-All constructions support families of distributions with more errors than entropy.
-Partial blocks sources are defined in \defref{def:partial source} and unguessable block sources are defined in \defref{def:block guessable}.}
+}%end centering
+\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
 \label{tab:upper bounds}
@@
 
+\bnote{can't get this table to center don't know why}
 %\begin{table}
@@
 Each time, $\gen$ will produce a different pair of values $(r_1, p_1),..., (r_q, p_q)$.
-Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (even though the reproduction procedure $\rep$ at the $i$th provider obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$).
+Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (the reproduction procedure $\rep$ at the $i$th provider still obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$).
 Because the multiple providers may not trust each other, a stronger security feature (which we satisfy) ensures that each $r_i$ is secure even when all $r_j$ for $j\neq i$ are also given to the adversary.
@@
 \item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
-Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.
-The challenger sets $w_{i+1} = \delta_i(w_1)$.
+Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
 \item \textbf{Distinguishing} The advantage of $D$ is
@@
 That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.
-We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
+
+\textbf{Note:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
 However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.
@@
 This definition makes sense when servers are compromised~(after enrollment) and act maliciously.
-
-Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups.
+In both definitions, the adversary creates a perturbation function $_i$ after seeing $p_1,..., p_{i-1}$~(and generated keys for outsider security) and the challenger generates $w_i = f_i(w_1)$.
+The definition is parameterized by the class of allowed perturbation functions.
+
+Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the perturbation family is a transitive isometric permutation groups.
 Boyen transforms this construction to insider security using random oracles.
@@
 Insider security strengthens outsider security in two ways.
-First, it allows the adversary to see some subset of keys, second it allows the adversary to perform regeneration on arbitrary $p_i$.
+First, it allows the adversary to see some subset of keys, second it allows the adversary to perform key generation on arbitrary $p_i$.
 This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.
 Robust fuzzy extractors provide security against modified $p$.
-In this work, we show reusability when some $r_i$ are observed but do not handle the issue of robustness.
-That is, we assume passive servers.
+In this work, we show reusability when $r_i$ are observed but do not handle the issue of robustness.
+That is, we assume keys may be exposed but servers keep honest state.
 Our definition lies between outsider and insider security.

### 2014-09-24 info-bounds/FuzzyExtPossibility.tex
stuck on isoperimetric proof

@@
 
-\subsubsection{Computational secure sketches}
+\subsubsection{Extending to Computational secure sketches}
 Fuller et al.
@@
 
-\begin{corollary}
-\label{cor:rec yields sketch}
-Let $\mathcal{Z}$ be an alphabet.
+%\begin{corollary}
+%\label{cor:rec yields sketch}
+%Let $\mathcal{Z}$ be an alphabet.
 Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
-If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-$4(\epsilon+t\delta)$. 
-\end{corollary}
+%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+%$4(\epsilon+t\delta)$. 
+%\end{corollary}
 
 \textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
-Unpredictable secure sketches is implied by virtual-grey box obfuscation of point functions~\cite{BitanskyCKP14}.
+Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
 
@@
 We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.
-Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p$ is at least $(1-2\epsilon)2^\kappa$.
+Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.
 Note that, $R|P=p$ is the set of possible keys.
@@
 
-Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$, for any $r_1, r_2$, $\inter(Q_{p^*, r_1}) \cap \inter(Q_{p^*, r_2}) =\emptyset$ and the union of all boundaries and interiors is the entire space.
-Furthermore, note that for any $r\in \zo^\kappa$,  $\Pr[V\in Q_{p^*, r}] = \ngl(n).$\bnote{need to fill in this distinguishing argument, note this doesn't need to be the case for all $p^*$ just on average.
-need another markov inequality.}\bnote{what can we say about the relative sizes of these spaces?}
+Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$.  We now show $Q$ are small.
+
+\begin{claim} For any $r\in \zo^\kappa$,  $ | Q_{p^*, r}| \le (1+\epsilon)2^\kappa.$
+\end{claim}
+\begin{proof} 
+Recall that for any $r$, $\Pr[U = r] = 1/2^\kappa$.  Since the total statistical distance is $2\epsilon$, 
+\[
+\Pr[R=r] \le 2( 2\epsilon + \Pr[U=r]) = 4\epsilon + 2^{-\kappa+1}.
+\] 
+The distribution $R | P=p^*  \overset{def}= \rep(V | P=p^*, p^*)$.
+Thus, the overall probability $\Pr[V|P=p^* \in Q_{r, P^*}] \le 4\epsilon+2^{-\kappa +1}$.
+\bnote{how to continue from here?
+this doesn't talk about the size of $V|P=p^*$.}
+\end{proof}
 

### 2014-09-25 constantRate/ConstCompFuzzExt-reorg.tex
editing pass through eurocrypt paper

@@
 \lnote{needs work}
-Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).
+Fuzzy extractors convert repeated readings of a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).
 In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns.
@@
 In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.
-We show an information-theoretic construction and two computational constructions with added features.  Our constructions are for the Hamming metric over symbols of an alphabet.
-
-\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of Hamming errors over a super-constant size alphabet.
+We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric.
+
+\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of errors over a super constant size alphabet.
 
@@
 Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.
-This construction corrects a sub-constant fraction of errors.
+This construction corrects a sub-constant fraction of errors over a super constant size alphabet.
 %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
@@
 Cryptography relies on long-term secrets for key derivation and authentication.
-However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
+However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings.
+Prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
 physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
-and quantum information~\cite{bennett1988privacy}).
+and quantum information~\cite{bennett1988privacy}.
 Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
@@
 In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
- A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.
+ A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined in~\cite{DBLP:journals/siamcomp/DodisORS08}.
 
@@
 The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
-The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space.% (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$).
-\onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph.
-Consider ignoring them here.}
+The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space. In this work, we consider the Hamming metric.
  The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$.
@@
 Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$.
-The reason for this tension is simple: if an adversary who knows $p$ can guess any $w'$ within distance $t$ of $w$, then it will be able to easily obtain the true $r$ by running $\rep$.
+The reason for this tension is simple: if an adversary who knows $p$ can guess some $w'$ within distance $t$ of $w$, then it will be able to easily obtain the true $r$ by running $\rep$.
 %If $t$ is larger, then a single guess for $w'$ may be within distance $t$ of more $w$ values, thus increasing adversarial probability of winning.
@@
 Thus, if the security guarantee of a given fuzzy extractor holds for \emph{any} source of a given min-entropy $m$ and the correctness guarantees holds for any $t$ errors, then $m$ must   be greater than $\log |B_t|$, where $|B_t|$ denotes the number of points in a ball of radius $t$.
-This condition on the source is necessary regardless of whether the fuzzy extractor is information-theoretic or computational, and extends even to the interactive setting.
+This condition on the source holds regardless of whether the fuzzy extractor is information-theoretic or computational, and extends even to the interactive setting.
 If a source fails this condition, we will says that it has \emph{more errors than entropy}.
@@
 
-Addtionally, relaxing the security definition to computational will not improve this approach~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
+Additionally, computational definitions of security suffer from similar problems~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
 Thus, we take a different approach and do not attempt to recover $w$.
@@
 The resulting string no longer has more errors than entropy.
- We then apply any information-theoretic fuzzy extractor to the resulting string.
+ We then apply an information-theoretic fuzzy extractor to the resulting string.
 
@@
 
-\paragraph{The Required Notion of Point Obfuscation} 
+\paragraph{The Required Notion of Obfuscation} 
 Our constructions use simulation-secure  obfuscation of digital lockers, however, we do not require full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
@@
 
-We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
-
 \paragraph{Connection to General Obfuscation}
@@
 Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
-The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  The obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
+The construction of Bitansky et al.
+is based on multilinear encoding and is  highly impractical.
+Our constructions use obfuscated digital lockers.
+Obfuscated digital lockers are instantiable under significant weaker assumptions and can be implemented quite efficiently.
+\bnote{we need to say we are weaker than general obfuscation.  happy with this? merged with sentence from above}
 Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.
@@
 \begin{itemize}%[leftmargin=-.6in]
-\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
+\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1, u\leftarrow \zo^\kappa$.
 \item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
@@
 \end{align*}
-where $u$ is a uniformly random string.
 \end{itemize}
@@
 Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the implicit distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
+In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
 \end{definition}
@@
 \end{enumerate}
-\item Set $(r, p') \leftarrow \gen(v_1,..., v_\gamma)$.
+\item Set $(r, p') \leftarrow \gen'(v_1,..., v_\gamma)$.
 \item Set $p = (p', seed_1,..., seed_\gamma)$.
@@
 In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.
-The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
+The structure of a partial block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
+We assume that $\Hoo(W) = \Theta(\gamma)$.
 The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.
@@
 \[
-\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) <  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
+\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) \ge  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
 \]
@@
 %\end{itemize}
-The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
+The use of a computational primitive~(obfuscation of digital lockers) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
 This is the property that allows reusability.
@@
 \label{ssec:sec cons sampling}
-In this section we outline security of \consref{cons:sampling}.  A proof of security appears in\apref{sec:analysis sampling}.
+In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
 With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
@@
 In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.
-The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
+The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
+We assume that $\Hoo(W) = \Theta(\gamma)$.
 We are able to correct $o(\gamma)$ errors.
@@
 \[
-\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) < t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
+\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
 \]
@@
 
-\textbf{Note:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
+\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
 However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.
+
+Furthermore, we showed that \consref{cons:sampling} is secure on partial block sources.
+In fact, it is secure for any source where sampling produces a high entropy string~($\omega(\log n)$) with overwhelming probability.
+For comparison with \consref{cons:info theoretic} we restrict our attention to partial block sources.\bnote{I just added this.
+Okay?}
 
@@
 This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of $r$.
 
 Before presenting the construction we provide some definitions from error correcting codes.
-We use slightly nonstandard error-correct codes over $\{0,1\}^\gamma$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
 Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
@@
 The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
-For this type of source the required entropy is $\Hoo(W) = \gamma\omega(\log n)$.
+For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.
 This yields:
 \[
-\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  <\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
+\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  >\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
 \]
@@
 However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.
-Our construction satisfies this alternative adaption as well.}
-Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.
+\consref{cons:sampling} satisfies this alternative adaption as well.}
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.
 This was not allowed in the definition of Boyen as it would make security impossible.

### 2014-09-26 info-bounds/FuzzyExtPossibility.tex
working on proof for fuzzy ext impossibility

@@
 \newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
-\newcommand{\bnd}{\ensuremath{\class{Bnd}}\xspace}
+\newcommand{\crust}{\ensuremath{\class{Crust}}\xspace}
 \newcommand{\inter}{\ensuremath{\class{Inter}}\xspace}
@@
 \item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
+\item The distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
 \item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\gamma-t+1)\log |\mathbb{F}|+1$. 
@@
 Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
- By described above the view of $\sketch, \rec$ is a uniform distribution $V$.
+ As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.
 We know show there are many possible values for $Z$.
@@
 In this section, we extend this result to fuzzy extractors.
-The main difficulty is showing that fuzzy extractors must cause a significantly entropy drop in $V$.
-This is not true for all metric spaces.
+This result has significantly weaker parameters than the previous result but still demonstrates hard.
+\bnote{write this}
+
 We begin with the case of perfect correctness in the Hamming metric.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon =\ngl( n)$ for $t \approx \kappa $.
 \bnote{what is $\epsilon$?
@@
 \begin{proof}
-The only difference between \thref{thm:imposs fuzz ext} and \thref{thm:imposs sketch} is the functionality required of the algorithms $(\gen, \rep)$.
-Thus, we must prove that a fuzzy extractor must still cause a significant drop in the entropy of $V$:
+Instead of showing the above theorem for an arbitrary length $\kappa$ we assume that the size of $\kappa$ is bounded away from $n$.
+That is, $\kappa = O(n^{1/2})$.
+Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
+
+For this family we construct a different family of distributions $V$.
+This family is closely related to the family we constructed in the previous section \bnote{comparison}.
+However, we consider the binary alphabet.
+Let $\nu = \omega(\log n)$ be some parameter to be determined later\bnote{set this later}.
+We describe a single element $W\in V$.
+For convenience we assume that $n/\nu$ is an integer.
+Let $x_1,..., x_\nu \in \zo^\nu$.
+Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
+Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
+Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
+\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
+b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
+\]
+Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.
+Note, this example is essentially the same family as in the previous example squished to the binary alphabet.
+\bnote{Come back to this explanation.}
+
+We now proceed using the same outline as the previous section\bnote{be more precise}
+\begin{itemize}
+\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item The distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
+\item Show that for most values public values they are many keys that have possible pre images in the metric space.  Furthermore, only a small number of the public values are feasible.
+\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
+\item For most values of possible $Z$ there are many keys that do not receive any weight, thus the output of the fuzzy extractor can be distinguished from uniform.
+\end{itemize}
+
+\begin{proposition} 
+For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\end{proposition}
+\begin{proof}
+Consider some fixed $W\in\mathcal{V}$.
+The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.
+Recall that $t< n/\nu$\bnote{need to say this earlier}.
+We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Fix some $w, w'\in W$.
+Denote by $x, x'$ the values that produce $w, w'$ respectively.
+Clearly, $x\neq x'$.
+Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
+This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
+Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = \omega(\log n)$.
+\end{proof}
+
+\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
+\end{proposition}
+\begin{proof}
+Consider some $w\in V$.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
+\end{proof}
+
+We now proceed to showing the technical portion of the theorem.
+We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
+Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
 
 \begin{lemma}
-Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$ and $\epsilon=$ \bnote{what is this?}.  Then $\tilde{H}_0(V | \gen(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.
+Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.  Let $\nu = \kappa+1$ and $t = n/\nu-1$.  Then $\epsilon = \poly(n)$.\bnote{come back to this statement with precise parameters}
 \end{lemma}
@@
 
-Consider some $p^*\in A_{ss}$.
-We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.
-Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.
-Note that, $R|P=p$ is the set of possible keys.
-
-The set of possible keys induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique $Q_{p^*,r}$ such that $\rep(w, p^*) =r$.
-Define two sets, called the boundary and interior respectively: \begin{align*}
-\bnd(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\},\\
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\}.
+Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
+The distribution $R|P=p^*$ is the set of possible keys.
+The distribution $R|P=p^*$ induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
+Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
+
+Many of these sets must be small.
+That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
+If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.
+This is more points than exist in the metric space.
+
+For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Define two sets, called the interior and crust respectively: \bnote{change term crust?}
+
+\begin{align*}
+\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
+\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
 \end{align*}
 
-Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$.  We now show $Q$ are small.
-
-\begin{claim} For any $r\in \zo^\kappa$,  $ | Q_{p^*, r}| \le (1+\epsilon)2^\kappa.$
-\end{claim}
+Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.
+We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.
+Consider some $r^*\in R_{small}$.
+Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+
+\begin{lemma}
+$|\inter(Q_{p^*, r^*})| \le |B_{n-\kappa -t+2}|$.
+\end{lemma}
 \begin{proof}
-Recall that for any $r$, $\Pr[U = r] = 1/2^\kappa$.  Since the total statistical distance is $2\epsilon$, 
-\[
-\Pr[R=r] \le 2( 2\epsilon + \Pr[U=r]) = 4\epsilon + 2^{-\kappa+1}.
-\] 
-The distribution $R | P=p^*  \overset{def}= \rep(V | P=p^*, p^*)$.
-Thus, the overall probability $\Pr[V|P=p^* \in Q_{r, P^*}] \le 4\epsilon+2^{-\kappa +1}$.
-\bnote{how to continue from here?
-this doesn't talk about the size of $V|P=p^*$.}
+\bnote{deficient sphere/ball?}
+First recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
+We call a set $S$ a \emph{deficient sphere} if there exists a point $x$ and a radius $\beta$ \bnote{check for conflicts with $\beta$} such that $B_{\beta}(x) \subseteq S \subseteq B_{\beta+1}(x)$.
+By the isoperimetric inequality on the Hamming space\bnote{cite!!!!}, there exists a deficient sphere $S_{p^*, r^*}$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
+We now find the radius of $S_{p^*, r^*}$.
+
+Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
+We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
+That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
+Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{do we need to cite something here?}.
+Thus,
+\[n-(\kappa-1) \ge d (\log n - \log d).\]  
+We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.
+
+Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
+That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
+This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
+That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
+And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
+This is a radius of almost $n$}
 \end{proof}
 
-We now consider the distribution of $V | P=p^*$.
-By the functionality of $(\gen, \rep)$, for every $v\in V| P=p^*$, $v\in Int(Q_{p, r})$.
-Furthermore, if $v$ is not in some interior then $v\not \in V | P=p^*$.
-Thus, it suffices to show that $\frac{\sum_{r} |\inter(Q_{p^*, r})|}{\mathcal{M}} = XXX$\bnote{fill this in.}
-
-To show this we any such partitioning of the metric space must have the majority of points lying on the boundary.  This is true for the Hamming metric.
-\begin{lemma}[Isoparametric Inequality]
-\bnote{XXXX}
-\end{lemma}
+We have shown that $|\inter(Q_{p^*, r^*}| \le |B_{n-\kappa -t+2}|$.  Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
+
+To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.
+
+Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^n-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
+ As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
+We know show there are many possible values for $Z |P=p^*$.
+The only information about $Z$ is contained in the point  $V=v$.
+The length of this point is $2^n$.
+Conditioned on this information there are still many possible values for $Z$.
+That is,
+ \[
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n/\nu-1)(\nu -1)}}{2^v} = n -n/\nu - 2\nu +1.
+ \]
+Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+This means that the $\gen$ algorithm may include points for possible $Z$ values into $K_{bad}$~(other than $v$) and these values are disjoint.
+The optimum strategy is to include these values uniformly from different $Z$ values.
+That is,
+\[
+\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | \le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}.
+\]
+
+We now show that $\expe | K_{bad} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
+We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$.  We then have that, 
+\begin{align*}
+\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
+&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
+%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
+\end{align*}
+\bnote{the two combinatorial bounds we are using aren't good enough}
+To show that $\epsilon \ge 1/2$ we have that 
+%\begin{align*}
+%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
+%\end{align*}
+\bnote{why was that sufficient to break security}
+\bnote{still working this isn't complete}
 \end{proof}
 \end{proof}
+
+%\subsection{Contrived Weird Example I'm worried about}
+%\begin{center}
+%\begin{tabular}{c|c}
+%\begin{minipage}{3in}
+%\textbf{\gen}
+%\begin{enumerate}
+%\item \underline{Input}: $w = w_1,..., w_\gamma$
+%\item Sample $pad_1, pad_2 \leftarrow \mathcal{M}$.
+%\item Create random pad $x \leftarrow \zo^\gamma$.
+%\item Set $c \leftarrow Syndrome(w)$.
+%\item Set $r = Ext(w, seed)$, \\$p = \langle w, x\rangle, seed, c, x$.
+%\item If $pad_1 = w \wedge pad_2 =w$:
+%\begin{enumerate}[(i)]
+%\item Set $r=0$, \\
+%$p = \langle w, x\rangle\oplus 1, seed, c, x$.
+%\end{enumerate}
+%\end{enumerate}
+% \end{minipage} &
+%\begin{minipage}{3in}
+%\textbf{\rep}
+%\begin{enumerate}
+%\item \underline{Input}: $(w', p = (b, seed, c, x))$
+%\item Decode $w = Decode(w', c)$.
+%\item 
+%%\begin{enumerate}[(i)]
+%%\end{enumerate}
+%\item Output $r = \rep'(v', ss)$.
+%\end{enumerate}
+%\vspace{0.7in}
+%\end{minipage}
+%\end{tabular}
+%\end{center}
 

### 2014-09-26 constantRate/ConstCompFuzzExt-reorg.tex
abstract and table and distributions for second construction

@@
 Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
-Pennsylvania State University.} }
+Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
+``Privacy Tools'' project.} }
 }
@@
 \begin{abstract}
-\lnote{needs work}
-Fuzzy extractors convert repeated readings of a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).
-In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns.
-For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.
-Unfortunately, it is impossible to provide security for every source with this property.
-Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.
-
-Fortunately, practical sources contain useful structure.
-In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.
-We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric.
+\lnote{Opinions?}
+Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated readings of a noisy source of entropy into the same uniformly distributed key.
+To eliminate noise, they require an initial enrollment phase that takes a reading from the source and produces a nonsecret helper string to be used in subsequent readings.
+This helper string reduces  the entropy of the original source---in the worst case, by as much as the logarithm of the number of tolerated error patterns.
+For many practical sources, reliability demands that the number of tolerated error patterns is large, making this loss greater than the original entropy of the source.
+We say that such sources have \emph{more errors than entropy}.
+Most known approaches for building fuzzy extractors cannot be used for such sources.
+
+%\emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
+% remain secure even when the initial enrollment phase is repeated multiple times on correlated readings, producing multiple helper strings.
+Prior approaches to building reusable fuzzy extractors severely restricted allowed correlations among initial enrollment readings.
+%   
+%We provide constructions of fuzzy extractors for large classes of sources with more errors than entropy.
+We also construct the first reusable fuzzy extractors that has no restrictions on correlations among multiple readings of the source.
+Our constructions exploit the structural properties of a source in addition to its entropy guarantees.
+One is information-theoretic; the other two rely computational assumptions.
+They differ in the types of sources they support.
+
+We provide constructions of fuzzy extractors for large classes of sources with more errors than entropy.
+Our constructions exploit the structural properties of a source in addition to its entropy guarantees.
+Some are made possible by relaxing the security requirement from information-theoretic to computational.
+
+%One is information-theoretic; the other two rely computational assumptions. They differ in the types of sources they support.
+
+\emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
+ remain secure even when the initial enrollment phase is repeated multiple times on correlated readings, producing multiple helper strings.
+By relying on computational security, we construct the first reusable fuzzy extractors that make no assumption about how multiple readings of the source are correlated.
+
+\iffalse
+
+We construct fuzzy extractors for large classes of such sources by exploiting  their structural properties in addition to their entropy guarantees.  
+We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric over a nonbinary alphabet.
+
+The information-theoretic construction supports sources in which most symbols contributes fresh entropy.
+The first computational construction has the additional feature of \emph{reusability}~(Boyen, CCS 2004), allowing multiple correlated
 
@@
 \end{itemize}
+\fi
 
@@
 
-\textbf{Keywords} Fuzzy extractors, key derivation, error-correcting codes, computational entropy, point obfuscation.
+\textbf{Keywords} Fuzzy extractors, reusability, key derivation, error-correcting codes, computational entropy, point obfuscation.
 \end{abstract}
@@
 Table~\ref{tab:upper bounds} summarizes our constructions.
-\bnote{table better?}
 Our first construction provides information-theoretic security.
@@
 
-We switch to computational security to obtain constructions with additional features.
-Our second construction provides reusability (against computationally bounded adversaries).
-Like the first construction,
-it requires that a constant fraction of symbols contribute fresh entropy. However,
-the reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
+We switch to computational security to obtain constructions with additional features. Our second construction provides reusability (against computationally bounded adversaries).  
+The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} comes from an allowed distribution.
+The allowed distributions include those that are supported in the first construction, as well as other distributions, such as those with $k$-wise independence among symbols for superlogarithmic $k$.
 This construction requires that the fraction of errors is subconstant.
@@
 \begin{table}
-{ \centering
+\begin{center}
 \begin{tabular}{l l l l l}
@@
 \hline
-Cons. \ref{cons:info theoretic} & Info-theoretic  & Most symbols  & Constant fraction & Super constant \\
-& & contribute entropy & &\\\hline
+Cons. \ref{cons:info theoretic} & Not reusable  & Most symbols  & Constant fraction & Super constant \\
+&  Info-theoretic & contribute entropy & &\\\hline
 Cons. \ref{cons:sampling} & Reusable & Most symbols & Sub constant fraction & Super constant \\
 & Computational & contribute entropy & &\\\hline
-Cons. \ref{cons:first construction} & Computational & Symbols correlated  & Constant fraction & Super\\
-& & but hard to guess && polynomial
+Cons. \ref{cons:first construction} & Not reusable & Symbols correlated  & Constant fraction & Super polynomial\\
+&  Computational & but hard to guess && 
 \end{tabular}
-}%end centering
+\end{center}
+%end centering
 \caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
@@
 
-\bnote{can't get this table to center don't know why}
 %\begin{table}
@@
 This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
-Goldreich provides an introduction to samplers in~\cite{goldreich2011sample}.
+(See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)
 
@@
 
-Furthermore, we showed that \consref{cons:sampling} is secure on partial block sources.
-In fact, it is secure for any source where sampling produces a high entropy string~($\omega(\log n)$) with overwhelming probability.
-For comparison with \consref{cons:info theoretic} we restrict our attention to partial block sources.\bnote{I just added this.
-Okay?}
+In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.
+However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability.
+For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.
 
@@
 
-This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, and 1218461.
+This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, 1218461, and 1422965.
 Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.

### 2014-09-26 constantRate/ConstCompFuzzExt-reorg.tex
very minor edits

@@
 Our constructions use obfuscated digital lockers.
-Obfuscated digital lockers are instantiable under significant weaker assumptions and can be implemented quite efficiently.
+Obfuscated digital lockers are instantiable under significantly weaker assumptions and can be implemented quite efficiently.
 \bnote{we need to say we are weaker than general obfuscation.  happy with this? merged with sentence from above}
@@
 The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.
-Present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.
+We present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.
 
@@
 Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
+Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $j=1,..., q$:
 \begin{itemize}%[leftmargin=-.6in]
@@
 \begin{align*}
-\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
+\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{j-1}, r_j, r_{j+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{j-1}, u, r_{j+1},..., r_q, p_1,..., p_q)=1].
 \end{align*}
@@
 \section{Definitions}
-\subsection{Computational Fuzzy Conductors}
+\subsection{Computational Fuzzy Conductors and Computational Extractors}
 \label{sec:further defs}
+In this section, we show that a computational fuzzy conductor~\defref{def:comp fuzzy cond} can be transformed to a computational fuzzy extractor~\defref{def:comp fuzzy extractor}.
+The transformation uses a computational extractor.
 A computational extractor is the adaption of a randomness extractor to the computational setting.

### 2014-09-27 constantRate/ConstCompFuzzExt-reorg.tex
minor edits to eurocrypt submission

@@
 Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s)$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
 \begin{itemize}
@@
 If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
-\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $r$ is pseudorandom conditioned on $p$, that is $\delta^{\mathcal{D}_s}((R, P), (U_\kappa, P))\leq \epsilon$.
+\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $r$ is pseudorandom conditioned on $p$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon_{sec}$.
 \end{itemize}
@@
 
-%\paragraph{Previous Negative Results}
-
-%\bnote{old stuff}
-%Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.
-They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.
-This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.
-There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.
-Their result can be interpreted as saying that reusability is impractical.
-%
-%However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.
-There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.
-The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.
-
-%To overcome this result, we consider computationally bounded adversaries.
-%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
-%\begin{definition}[Insider Reusable Fuzzy Extractors]
-%\label{def:reusable fuzz}
-%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.
-Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.
-We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
-%\begin{align*}
-%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
-%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
-%\end{align*}
-%\end{definition}
 We modify the definition of Boyen~\cite[Definition 6]{Boyen2004} for the computational setting.  We discuss the our definition and definitions due to Boyen in \apref{sec:comparing reusability}.
@@
 Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$.
 Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $j=1,..., q$:
@@
 \end{itemize}
-$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
+$(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
 \end{definition}
@@
 \begin{definition}
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$.
 In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
@@
 The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.
-This means that the input entropy to the fuzzy extractor is $\Theta(\gamma)$.
+This means that the input entropy to $(\gen', \rep')$ is $\Theta(\gamma)$.
 We assume that the new alphabet $\mathcal{Y}$ is of constant size.
@@
 \item Select $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
-\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
+\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma,\eta}( \lambda_i)$
 \item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
@@
 Let all the variables be as in \thref{thm:sampling}.
-For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.% \geq H_0(C)$.
-%for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
+For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.
 \end{lemma}
-%\begin{proof}
-%Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
-%\end{proof}
 
@@
 Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
-For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
+For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
 \end{theorem}
@@
 The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
+Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
 \bnote{say more here?}
@@
 This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
-Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of $r$.
+Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.
 
@@
 \emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
+denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
 \end{definition}
@@
 \label{def:comp fuzzy cond}
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
 \begin{itemize}
-\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
+\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
 \end{itemize}
@@
 Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
 \end{theorem}
@@
 \begin{definition}
-A function $\cext: \zo^\gamma \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
+A function $\cext: \zo^\gamma \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon_{sec}, s_{sec})$-average-case computational extractor} if for all pairs
 of random variables $X, Y$ (with $X$ over $\zo^\gamma$) such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon$.
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{sec}}}((\cext(X; U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon_{sec}$.
 \end{definition}
@@
 Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
-To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{text}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
+To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{fext}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
 The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
@@
 
-We give a brief outline of the proof here; the proof follows.
-
-\noindent \textbf{Outline:}
+We give a brief outline of the proof, followed by the proof.
 It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.

### 2014-09-29 trunk/info-bounds/FuzzyExtPossibility.tex
editing through section 4

@@
 The goal is to produce the correct key whenever $\dis(w, w')\le t$.
-
-Ideally, key derivation should be possible whenever a negligible portion of $W$ lies within a ball~(arbitrarily centered) of radius $t$.
-We call the maximum weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.
+\anote{there is a big gap between theory and the needs of practice}
+
+We identify a key quantity of a distribution called \emph{fuzzy min-entropy}.
+Fuzzy min-entropy measures the maximum probability mass of a distribution that lies within a ball of radius $t$ in the metric space.
+Ideally, key derivation should be possible whenever a distribution has fuzzy min-entropy.
 In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
@@
 \section{Introduction}
+\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
+\anote{should our results be seen as justifying the distribution specific approach?}
+\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
 Usually, authentication requires some high quality secret.
 Traditionally, this secret is assumed to have high min-entropy.
-However, many sources with sufficient entropy for authentication present an additional problem of noise.
+However, many sources with sufficient entropy for authentication present an additional problem: noise.
 That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.
@@
 The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.
-In this work, we consider the non-interaction version of these problems where these tasks are performed non-interactively~(with a single message).
-
-The paradigm for performing noisy key derivation using a single message is known as fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08}.
+In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.
+
+A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.
 Consider a particular high entropy distribution $W$.
@@
 The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.
-The $key$ must be strong even to an adversary that has observed $p$~(the problem is trivial if $p$ is private).
+The $key$ should hold even if an adversary has observed $p$~(the problem is trivial if $p$ is private).
+The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.
 
 Traditionally, fuzzy extractors are constructed by using a separate information-reconciliation component, known as a secure sketch, that maps $w'$ back to $w$ and a privacy-amplification component, a strong randomness extractor~\cite{nisan1993randomness}, that maps $w$ to a random key.
-These objects can either be information-theoretic or computational.
-The computational versions of these objects are defined in~\cite{fuller2013computational} and~\cite{krawczyk2010cryptographic} respectively.
-Fuller et al.~\cite{fuller2013computational} show that computational secure sketches are unlikely to improve significantly on information-theoretic secure sketches.
-
-\textbf{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
+A secure sketch consists of a pair of algorithms $\sketch$ takes $w$ and produces a public value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
+The security losses incurred in information-reconciliation~(performed in secure sketches and fuzzy extractors) are larger than losses in privacy amplification.\bnote{should say something here about our understanding of privacy amplification and that extractors are necessary and sufficient} In the following discussion we describe limitations on fuzzy extractors.
+This discussion applies to secure sketches as well.
+\bnote{should say you don't have to build secure sketches}
+
+Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
+Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed and the remainder of the distribution is unknown 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+Usually fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
+
+\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
 Fix some distribution $W$.
@@
 
-In the interactive setting where two parties hold $w$ and $w'$ and wish to agree on a common key, fuzzy min-entropy is both a necessary and sufficient condition~(using secure two-party computation). 
-However, in the one-message setting we are far from achieving security whenever fuzzy min-entropy is high.
+Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
+In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
+If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
+Ideally, the server would keep a ``hashed'' value of $w$.
+This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
+In the one-message setting, we are far from this ideal.
 
 Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.
+This loss is usually linear in the input length of the string.
 While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
@@
 
-\paragraph{Codifying distributional uncertainty}
-When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
+\paragraph{The price of distributional uncertainty}
+As described above, fuzzy extractors are usually built for a family of distributions $\mathcal{W}$.
+This strengthens the security guarantees: security holds as long as $W\in\mathcal{W}$.
+In this work, we show that this uncertainty comes at a significant cost.
+We consider two settings, first where the algorithms $\gen, \rep$ know the entire probability mass function of the distribution $W$.
+We call this setting \emph{distribution aware}.\bnote{prior works on this setting}  The more traditional setting where security holds for a family of distributions $\mathcal{W}$ we call \emph{distribution-oblivious}.
+
+In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.
+A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.
+We ask the question for secure sketches and fuzzy extractors.
+
+%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
 However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
@@
 
-To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
+%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
 We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
@@
 
-\textbf{Our Contribution} In the \emph{distribution-aware} setting, for every source with super-logarithmic fuzzy min-entropy it is possible to build a secure sketch with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.
-(A key with super-logarithmic entropy can be expanded to arbitrary length using computational techniques.)  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-\textbf{Note:} Our constructions are information-theoretic and do not run in polynomial time.
-They should be regarded as feasibility results.
-It is unclear how to define distribution-aware efficient algorithms as most distributions have exponential description size.
+\paragraph{Our Contribution} We first consider the \emph{distribution-aware} setting.
+We show for a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
+Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
+In this work, we consider this minimal goal of a super-logarithmic length key.
+If we require a longer output length this increases the requirement on fuzzy min-entropy.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+Our constructions are primarily feasibility results and do not run in polynomial time.
+In the distribution-aware setting this seems necessary as most distributions have exponential description size.
 The power of the distribution-aware setting is that the algorithms can access this description.
@@
 
+We then show the situation is worse in the distribution-oblivious setting.
 We show that distributional uncertainty is a real drawback to providing security.
-In the standard \emph{distribution-aware} setting, we show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).
-This negative result extends to computational secure sketches~\bnote{cite a corollary}.
-
+We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).
+Using a result of Fuller et al.~\cite{fuller2013computational}, this negative result extends to versions of secure sketches ensure $w$ has  pseudoentropy~(\corref{cor:extension to fuzz ext}).
+Under very strong assumptions, computational secure sketches that provide unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Unpredictability is weaker than pseudoentropy and converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+This negative result is quite strong, it allows the secure sketch to be wrong a $1/4$ of the time and requires the secure sketch to correct a sub constant fraction of errors.
+
+\bnote{add a paragraph here about the negative result for fuzzy extractors}
+\bnote{add a paragraph talking about the computational setting}
 %The situation is significantly more complicated for distribution-oblivious algorithms.
@@
 
-\textbf{Open Problem:} The main open problem is whether fuzzy min-entropy is a sufficient condition for constructing a fuzzy extractor in the distribution-oblivious setting.
-We note that it is known how to build a fuzzy extractor for the family of distributions used in our negative result~\cite[Theorem 5.7]{canetti2014key}.
-Furthermore, are computational assumptions necessary?
-\bnote{talk about obfuscation.}
-
+\paragraph{Our approach} \bnote{say something about our methods.  leveled hashing, distributional uncertainty?}
 \begin{table}
@@
 \hline
-Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & Unknown
+Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})
 %Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
@@
 \end{center}
-\caption{Is fuzzy min-entropy sufficient for extraction?}
+\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  All results are information-theoretic.}
 \label{tab:main results}
@@
 
-\subsection{Fuzzy Extractors}\label{sec:fuzz extractor}
-
-We recall definitions and lemmas from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with two changes.
-First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08} and we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
-See~\cite{canetti2014key} for discussion.
+\subsection{Fuzzy Extractors for families of distributions}\label{sec:fuzz extractor}
+
+In this section, we define of fuzzy extractors and secure sketches.
+Definitions and lemmas are drawn from the work of Dodis et.
+al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.
+First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
+Second in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
+This is a generalization of the definition of Dodis et al.
+which require a fuzzy extractor to work for all distributions of a particular entropy.
+In the \emph{distribution-aware} setting, the algorithms only work for a distribution $W$.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
@@
 
-Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distance results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.
-A fuzzy extractor performs two tasks, producing a uniform key and providing error-tolerance.
-Traditional, the uniform key is produced by extraction from the original secret $w$ and the error-tolerance is obtained by using a secure sketch.
-Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
+Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.
+\bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.
+The canonical construction is called \emph{sketch-and-extract} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
+Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
 \begin{definition}
@@
 \begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
+\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
+\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
 \[
@@
 
-\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
+\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
 
@@
 \end{lemma}
+
+\paragraph{Distribution-aware setting}
+We separate between two types of fuzzy extractors and secure sketches.
+Because we rarely have complete descriptions of a physical probability distribution the standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions $\mathcal{W}$.
+We call this type of algorithm \emph{distribution-oblivious}.
+We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.
+We provide a definition for secure sketches~(extendible to fuzzy extractors):
+
+\begin{definition}
+Let $W$ denote a distribution.
+A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.
+That is,
+\begin{enumerate}
+\item \emph{Correctness} 
+\[
+\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.\]
+Correctness is guaranteed only for the support of $W$.
+\item \emph{Security} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+\end{definition}
+The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
+When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.
+It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.
 
@@
 \end{proof}
-\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
+\lemref{lem:fuzz necessary} still applies.
+This is because $D$ only provides an input to the protocol and looks at the output.
 This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-As stated above, fuzzy min-entropy is also a sufficient condition for security in the interactive setting.
-However, in the fuzzy extractor~(non-interactive) setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.
-We attempt to bridge this gap in this work.
-Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
-
-We separate between two types of fuzzy extractors and secure sketches.
-The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.
-This is because we rarely have complete distributions of a physical probability distribution.
-We call this type of algorithm distribution-oblivious.
-We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.
-We provide a definition for secure sketches~(extendible to fuzzy extractors):
-
-\begin{definition}
-Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.
-That is,
-\begin{enumerate}
-\item \emph{Correctness} 
-\[
-\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta\]
- where the probability is taken over the coins of $\sketch$ and $\rec$.  Note correctness is guaranteed only for the support of $W$.
-\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-\end{definition}
-Note (\sketch, \rec) know the description of $W$ and security only holds for $W$.
-When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to use the (possibly)~exponential size distributions.
-One possible approach is to allow $(\sketch, \rec)$ an oracle to the probability mass function of $W$.
-Our constructions do not work in this setting.\bnote{why am I talking about this?}
-
-%The summary of our results is in Table~\ref{tab:upper bounds}.
-
-\begin{table}
-\begin{tabular}{l | l}
-Lower bounds & Residual Entropy\\
-\hline
-Well-spread distribution & $\Hfuzz(W)$ \\
-Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
-Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
-\end{tabular}
-\caption{Summary of results for distribution aware setting.  Residual entropy of distribution-aware secure sketches with error $\delta$.}
-\label{tab:upper bounds}
-\end{table}
-%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
-We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
+As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.
+
+There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.
+There are also no known impossibility results for distributions with fuzzy min-entropy.
+Thus, the situation for fuzzy extractors is quite unclear.
+As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
+We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.
 
@@
 
+%The summary of our results is in Table~\ref{tab:upper bounds}.
+
+\begin{table}
+\begin{centering}
+\begin{tabular}{l | l}
+Class of Distribution & Residual entropy achieved by construction\\
+\hline
+Well-spread distribution & $\Hfuzz(W)$ \\
+Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
+Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
+\end{tabular}
+\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.
+Here $\delta$ denotes the probability of incorrect reconstruction and $\mathcal{M}$ is the metric space.
+Recall that $\Hfuzz(W)$ is an upper bound for the residual entropy.}
+\label{tab:upper bounds}
+\end{centering}
+\end{table}
+%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
+We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
+
 \subsection{Well-Spread Distributions}
-\bnote{is this section useful?}
+\bnote{can remove this section if we need space}
 We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
@@
 Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
-Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.
+Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.
+However, our negative results for the distribution-oblivious setting will be for families of well-spread distributions.
+This result illustrates how different the distribution-aware and distribution-oblivious settings are.}
 \begin{lemma}
@@
 
-\subsection{Flat distributions}
-In the previous section we showed it is easy to produce secure sketch for well-spread distributions in the distribution aware setting.
+\subsection{Secure Sketches for Flat distributions}
+We showed it is easy to produce secure sketch for well-spread distributions in the distribution aware setting.
 %\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
@@
 \label{cons:universal hash}
-Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  We describe $\sketch, \rec$ as follows:
-\begin{itemize}
-\item $\sketch(w)$:
-\subitem Sample $K\leftarrow \mathcal{K}$.
-\subitem Set $p = F(K, w), K$.
-\item $\rec(w', y, K)$:
-\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
-\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
-\subitem Output $\perp$.
-\end{itemize}
+Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  Let $W$ be a distribution.  We describe $\sketch_W, \rec_W$ as follows:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{$\sketch_W$}
+\begin{enumerate}
+\item \underline{Input}: $w$.
+\item Sample $K\leftarrow \mathcal{K}$.
+\item Set $p = F(K, w), K$.
+\end{enumerate}
+\vspace{.3in}
+\end{minipage} &
+\begin{minipage}{3in}
+\textbf{$\rec_W$}
+\begin{enumerate}
+\item \underline{Input}: $(w', p = y, K)$
+\item Create $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
+\item Output $\perp$.
+\end{enumerate}
+\end{minipage}
+\end{tabular}
+\end{center}
 \end{construction}
+
 \begin{lemma}
@@
 
-\subsection{Arbitary distributions}
-The hashing approach outlined above~(\consref{cons:universal hash}) does not extend to arbitrary sources.
+\subsection{Secure sketches for all distributions with fuzzy min-entropy}
+The hashing approach used for flat~(\consref{cons:universal hash}) does not work for arbitrary sources.
 The reason is that some balls may have significantly more points but low overall probability.
 Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.
-Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.
-However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.
+Then the hashing algorithm writes down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.
+However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.
 
@@
 In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
-The main issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
+The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
 
@@
 Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.
+Let $W$ be a distribution with $\Hfuzz(W)\ge m$.
 Let $\ell\in\mathbb{Z}^+$ be a parameter.
@@
 Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.
-We describe $\sketch, \rec$ as follows:
-\begin{itemize}
-\item $\sketch(w)$:
-\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
-\begin{itemize}
-\item Set $p=0, w$.
-\end{itemize}
-\subitem Else
-\begin{itemize}
+We describe $\sketch_W, \rec_W$ as follows:
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{$\sketch_W$}
+\begin{enumerate}
+\item \underline{Input}: $w$.
+\item If $\Pr[W=w] \le 2^{-(n+\ell)}$. Set $p=0,w$.
+\item Else
+\begin{enumerate}
 \item Find $i$ such that $\Pr[W=w]\in L_i$.
@@
 \item Set $p =1,  i, F_i(K, w), K$.
-\end{itemize}
-\item $\rec(w', y)$:
-\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
-\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
-\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
-\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
-\subitem Output $\perp$.
-\end{itemize}
+\end{enumerate}
+\end{enumerate}
+\vspace{.4in}
+\end{minipage} &
+\begin{minipage}{3in}
+\textbf{$\rec_W$}
+\begin{enumerate}
+\item \underline{Input}: $(w', y)$
+\item If $y_0 = 1$, output $y_{1,..., |y|}$.
+\item Else
+\begin{enumerate}
+\item Parse $(i, z, K) = y_{1,..., |y|}$.
+\item $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\item For $w^*\in W^*$, if $F(K, w^*) = z$, \\ output $w^*$.
+\item Output $\perp$.
+\end{enumerate}
+\end{enumerate}
+\end{minipage}
+\end{tabular}
+\end{center}
 \end{construction}
@@
 Going forward we will consider specific metric spaces, namely the Hamming metric.
-\section{Distribution-Oblivious Sketches}
+\section{Impossibility of Distribution-Oblivious Secure Sketches}
 \label{sec:dist oblivious}
@@
 \subsection{Fuzzy min-entropy is not sufficient for secure sketches}
-In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.
+In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.
 In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
-\bnote{finish proof}
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 3 + (\gamma-1) / \log |\mathbb{F}|$.
 \end{theorem}
@@
 \begin{itemize}
-\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
-\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\gamma-t+1)\log |\mathbb{F}|+1$. 
-\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
+\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
+\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.
+That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
+%   More concretely, conditioned on $V=v$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
 Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.  Thus, $\Hav(V| \sketch(V) , Z)$ is small.
+For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.
+Thus, $\Hav(V| \sketch(V) , Z)$ is small.
 \end{itemize}
@@
 
-\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
+\begin{proposition}
+\label{prop:distribution uniform} $V$ is the uniform distribution over $\mathbb{F}^\gamma$.
 \end{proposition}
@@
 \begin{lemma}
+\label{lem:secure sketch entropy loss}
 Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.
@@
 We do not consider these coins in our security analysis~(and thus, they can be considered private).
-
 By the definition of correctness for $(\sketch, \rec)$, 
 \[
-\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) = w] >1-\delta.
 \]
@@
 Fix some $w$.  
-By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[p\in A_{ss}]\ge 1/2$ and $\forall s\in A_{ss}$, 
+By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[ss\in A_{ss}]\ge 1/2$ and $\forall ss\in A_{ss}$, 
 \[
@@
 
-Consider some $p\in A_{ss}$.
-We now show that $H_0(V | p) \le (\gamma-t+1)\log |\mathbb{F}|$.
+Consider some $ss^*\in A_{ss}$.
+We now show that $H_0(V | \sketch(V) = ss^*) \le (\gamma-t+1)\log |\mathbb{F}|$.
 Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.
-Thus for every value in $V|p$ this is also true.
-This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).
-In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).
-That is $V|p$ is a set with minimum distance at least $t$.
-By the Singleton bound, this implies that $H_0(V | p) \le (\gamma -t+1 )|\mathbb{F}|$.
-Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
+Thus for every value in $V|\sketch(V) = ss^*$ this is also true.
+This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).
+In particular, this implies that for all $w_1, w_2 \in V|\sketch(V)=ss^*$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).
+That is $V|\sketch(V)=ss^*$ is a set with minimum distance at least $t$.
+By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.
+Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
 %By the Markov inequality, 
@@
 \begin{lemma}
+\label{lem:side info determines sketch}
 $\Hav(V | \sketch(V), Z) \le \Theta(1)$.
@@
 
-This means that the $\sketch$ algorithm include points for possible $Z$ values~(other than $v$) and these values are disjoint.
-The optimum strategy is to include these values uniformly from different $Z$ values.
+We now show for any sketch algorithm, for possible values of $Z$ conditioned on $V=v$ there are few points included in the support of $V |\sketch(V)$.
+For any two values of $z_1, z_2$ the distributions $V| Z= z_1$ and $V | Z=z_2$ intersect at most one point.
+The distributions $V | Z=z_1$ and $V| Z=z_2$ for possible $z_1, z_2$~(having seen $v$) overlap only at the point $v$.
+This means for any $v^*\in V| \sketch(V)$ (other than the true $v$) there is at most one $z$ such that $v^*\in V | \sketch(V), Z=z$.
+Thus, we ask The optimum strategy is to include these values uniformly from different $Z$ values.
 
@@
 Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.
-Consider these possible values for $Z$ as bins to be filled with the $2^{h_s}$ balls~(possible values of $V | \sketch(V)=s$).
+Consider these possible values for $Z$ as bins to be filled with the $2^{h_{ss}}$ balls~(possible values of $V | \sketch(V)=ss$).
 The average number of balls in each bin is maximized when the bins are filled equally.
@@
 \begin{align*}
-\tilde{H}_0(V |Z  , \sketch(V) = s) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
-&= \log \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)
+\tilde{H}_0(V |Z  , \sketch(V) = ss) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
+&= \log \left(\frac{2^{h_{ss}}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)
 \end{align*}
-\bnote{should I be writing this as $Z | \sketch(V) =s $?}
 Then averaging over the possible values of $s$, we have the following:
 \begin{align*}
-\tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V | Z, \sketch(V) =s )}\\
+\tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V |  \sketch(V) =ss , (Z| \sketch(V) =ss) )}\\
 &= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)\\
@@
 &\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+1\\
-&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}|+1\\
-&\le \Theta(1)
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (\frac{|\mathbb{F}|}{2})+1\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|) + (\gamma -1)+1\\
+&\le (3-t)\log |\mathbb{F}| + (\gamma -1)+1\\
 \end{align*}
- Where the last line follows for $t\ge 4$.  The eighth line follows from the seventh as long as $|\mathbb{F}|????$\bnote{fix this}
+This value is $\Theta(1)$ if $t\ge 3+ (\gamma-1)/\log | \mathbb{F}|$.
+\bnote{ I feel like this analysis can be tightened up.
+Saying that $\log (|\mathbb{F}| -1 ) \ge \log (|\mathbb{F}|)-1$ seems like a big loss.}
  \end{proof}
-
- \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
-%\begin{lemma}
-%$\Hav(V| P , Z) = \Theta(1)$
-%\end{lemma}
-%\begin{proof}
-%Consider some fixed $p$.
-%If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
-%\[
-%\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
-%\]
-%Then by the union bound, 
-%\[
-%\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
-%\]
-%\bnote{need to average across $P$}
-%\bnote{I'm confused about what we mean by $Z$ being universal here.}
-%\bnote{working here!}
-%\end{proof}
-%
-%\bnote{stopped here}
+\noindent \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
 \end{proof}
 
-%\begin{lemma}
-%There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
-%\end{lemma}
-%\begin{proof}
-%Need to show several things.  
-%\begin{itemize}
-%\item Each component of the distribution has fuzzy min-entropy.
-%\item Any sketch must leak some information about $V$.
-%\item The side information can be thought of as a hash function.
-Furthermore, it is independent of the sketch.
-Thus, the sketch and hash are independent information.
-Thus, conditioned on both there is almost no entropy.
-%\end{itemize}
-%\end{proof}
-
-Canetti et al.~\cite{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
-
-%\begin{lemma}
-%There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
-%\end{lemma}
-
-\subsubsection{Computational secure sketches}
+\subsubsection{Feasibility of Computational secure sketches}
 Fuller et al.
@@
 %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
-The definitional of Fuller et al. is uses HILL entropy.
-
-HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  Fuller et al.~use a weak version due to Gentry and Wichs~\cite{gentry2011separating}.
+The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
 
@@
 
-A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $s_{sec}, \epsilon_{sec}$ parameters to the definition, representing the distinguishing circuit).
+A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ parameters to the definition, representing the distinguishing circuit).
 By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
@@
 \item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-\item $t\ge 4$,
+\item $t\ge 3 + (\gamma-1)/\log |\mathbb{F}|$,
 \item and $\epsilon + t\delta < 1/16$,
@@
 
-\section{Distribution-Oblivious Fuzzy Extractors}
+\section{Impossibility of Distribution-Oblivious Fuzzy Extractors}
 In the previous section, we showed a family of distributions that does not admit a secure sketch.
 In this section, we extend this result to fuzzy extractors.
-The main difficulty is showing that fuzzy extractors must cause a significantly entropy drop in $V$.
-This is not true for all metric spaces.
+This result has significantly weaker parameters than the previous result but still demonstrates hard.
+\bnote{write this}
+
 We begin with the case of perfect correctness in the Hamming metric.
@@
 
-Consider some $p^*\in A_{ss}$.
-We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.
-Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p$ is at least $(1-2\epsilon)2^\kappa$.
-Note that, $R|P=p$ is the set of possible keys.
-
-The set of possible keys induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique $Q_{p^*,r}$ such that $\rep(w, p^*) =r$.
-Define two sets, called the boundary and interior respectively: \begin{align*}
-\bnd(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\},\\
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\}.
+Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
+The distribution $R|P=p^*$ is the set of possible keys.
+The distribution $R|P=p^*$ induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
+Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
+
+Many of these sets must be small.
+That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
+If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.
+This is more points than exist in the metric space.
+
+For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Define two sets, called the interior and crust respectively: \bnote{change term crust?}
+
+\begin{align*}
+\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
+\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
 \end{align*}
 
-Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$.
-Furthermore, note that for any $r\in \zo^\kappa$,  $ | Q_{p^*, r}| \le (1+\epsilon)2^\kappa.$\bnote{need to fill in this distinguishing argument, note this doesn't need to be the case for all $p^*$ just on average.
-need another markov inequality.}\bnote{what can we say about the relative sizes of these spaces?}
-
-We now consider the distribution of $V | P=p^*$.
-By the functionality of $(\gen, \rep)$, for every $v\in V| P=p^*$, $v\in Int(Q_{p, r})$.
-Furthermore, if $v$ is not in some interior then $v\not \in V | P=p^*$.
-Thus, it suffices to show that $\frac{\sum_{r} |\inter(Q_{p^*, r})|}{\mathcal{M}} = XXX$\bnote{fill this in.}
-
-To show this we any such partitioning of the metric space must have the majority of points lying on the boundary.  This is true for the Hamming metric.
-\begin{lemma}[Isoparametric Inequality]
-\bnote{XXXX}
+Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.
+We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.
+Consider some $r^*\in R_{small}$.
+Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+
+\begin{lemma}
+$|\inter(Q_{p^*, r^*})| \le |B_{n-\kappa -t+2}|$.
 \end{lemma}
+\begin{proof}
+\bnote{deficient sphere/ball?}
+First recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
+We call a set $S$ a \emph{deficient sphere} if there exists a point $x$ and a radius $\beta$ \bnote{check for conflicts with $\beta$} such that $B_{\beta}(x) \subseteq S \subseteq B_{\beta+1}(x)$.
+By the isoperimetric inequality on the Hamming space\bnote{cite!!!!}, there exists a deficient sphere $S_{p^*, r^*}$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
+We now find the radius of $S_{p^*, r^*}$.
+
+Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
+We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
+That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
+Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
+do better}.
+Thus,
+\[n-(\kappa-1) \ge d (\log n - \log d).\]  
+We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.
+
+Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
+That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
+This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
+That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
+And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
+This is a radius of almost $n$}
+\end{proof}
+
+We have shown that $|\inter(Q_{p^*, r^*}| \le |B_{n-\kappa -t+2}|$.  Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
+
+To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.
+
+Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^n-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
+ As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
+We know show there are many possible values for $Z |P=p^*$.
+The only information about $Z$ is contained in the point  $V=v$.
+The length of this point is $2^n$.
+Conditioned on this information there are still many possible values for $Z$.
+That is,
+ \[
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n/\nu-1)(\nu -1)}}{2^v} = n -n/\nu - 2\nu +1.
+ \]
+Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+This means that the $\gen$ algorithm may include points for possible $Z$ values into $K_{bad}$~(other than $v$) and these values are disjoint.
+The optimum strategy is to include these values uniformly from different $Z$ values.
+That is,
+\[
+\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | \le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}.
+\]
+
+We now show that $\expe | K_{bad} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
+We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
+\begin{align*}
+\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
+&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
+%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
+\end{align*}
+\bnote{the two combinatorial bounds we are using aren't good enough}
+To show that $\epsilon \ge 1/2$ we have that 
+%\begin{align*}
+%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
+%\end{align*}
+\bnote{why was that sufficient to break security}
+\bnote{still working this isn't complete}
 \end{proof}
 \end{proof}
+
+\textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
+%\subsection{Contrived Weird Example I'm worried about}
+%\begin{center}
+%\begin{tabular}{c|c}
+%\begin{minipage}{3in}
+%\textbf{\gen}
+%\begin{enumerate}
+%\item \underline{Input}: $w = w_1,..., w_\gamma$
+%\item Sample $pad_1, pad_2 \leftarrow \mathcal{M}$.
+%\item Create random pad $x \leftarrow \zo^\gamma$.
+%\item Set $c \leftarrow Syndrome(w)$.
+%\item Set $r = Ext(w, seed)$, \\$p = \langle w, x\rangle, seed, c, x$.
+%\item If $pad_1 = w \wedge pad_2 =w$:
+%\begin{enumerate}[(i)]
+%\item Set $r=0$, \\
+%$p = \langle w, x\rangle\oplus 1, seed, c, x$.
+%\end{enumerate}
+%\end{enumerate}
+% \end{minipage} &
+%\begin{minipage}{3in}
+%\textbf{\rep}
+%\begin{enumerate}
+%\item \underline{Input}: $(w', p = (b, seed, c, x))$
+%\item Decode $w = Decode(w', c)$.
+%\item 
+%%\begin{enumerate}[(i)]
+%%\end{enumerate}
+%\item Output $r = \rep'(v', ss)$.
+%\end{enumerate}
+%\vspace{0.7in}
+%\end{minipage}
+%\end{tabular}
+%\end{center}
 

### 2014-09-29 trunk/info-bounds/FuzzyExtPossibility.tex
moving some proofs to appendix

@@
 \blind{
-\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
-work was sponsored by the Department of the Air Force under Air Force
-Contract
-\#FA8721-05-C-0002.  Opinions,
-interpretations, conclusions and recommendations are those of the author
-and
-are not necessarily endorsed by the United States Government.
+\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
+%The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.
 Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.
@@
 \begin{enumerate}
-\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
-\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that
-\[
-\forall w, w'\in \mathcal{M}, \dis(w, w')\le t \Rightarrow \Pr[(R, P)\leftarrow \gen(w) \wedge \rep(w', P) =R] \ge 1-\delta
-\]
-where the probability is taken over the coins of $\gen, \rep$.
-\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
+\item \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
+\item \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.   
+\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
+\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
 \end{enumerate}
@@
 \bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.
-The canonical construction is called \emph{sketch-and-extract} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
+The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
 Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
@@
 \item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
-\[
- \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta
- \] 
-where the probability is taken over the coins of $\sketch$ and $\rec$.  
-\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
-That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
+\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
+\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \emph{Correctness} 
-\[
-\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.\]
+\item \emph{Correctness:} 
+$
+\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$
 Correctness is guaranteed only for the support of $W$.
-\item \emph{Security} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\item \emph{Security:} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
@@
 \end{lemma}
-\begin{proof}
-Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
-Consider the following distinguisher $D$:
-\begin{itemize}
-\item Input $r, p$.
-\item If $\rep(m^*, p) = r$, output $1$.
-\item Else output $0$.
-\end{itemize}
-First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.
-Thus, when $\kappa = \omega(\log n)$:
-\[
-\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
-\]
-\end{proof}
+
+The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
 Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
 \lemref{lem:fuzz necessary} still applies.  
-This is because $D$ only provides an input to the protocol and looks at the output.
 This means that fuzzy min-entropy is also a necessary condition for interactive solution.
@@
 
-We now present a construction for flat distributions.  We universal hashes:
+\noindent We use universal hashes to construct secure sketches for flat distributions.
+Skoric et al.
+previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.
 
@@
 \end{definition}
-
-A sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.
-Skoric et al.
-previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.
 
@@
 \begin{lemma}
+\label{lem:flat hashing}
 Let $W$ be a flat distributions with min-entropy $m$.  Then
@@
 Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+
+We provide a full proof in \apref{sec:proof of layered hashing}.
+The argument is similar to the proof of \lemref{lem:flat hashing}, however, there is an additional step showing that releasing the probability information is not too harmful.
+Namely, that an adversary with access to the probability information improves their success by a polynomial factor.
+Note we release $n$ levels where $n =\log |\mathcal{M}|$.
+
 \end{theorem}
 \bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
+
+\begin{corollary}
+\label{cor:extension to fuzz ext}
+Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+(Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
+\end{corollary}
+
+\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.
+Going forward we will consider specific metric spaces, namely the Hamming metric.
+\section{Impossibility of Distribution-Oblivious Secure Sketches}
+\label{sec:dist oblivious}
+
+In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.
+This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.
+In this section we ask if the results can be replicated for a family of distributions.
+Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.
+The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).
+Unfortunately, we show for secure sketches this is not the case.
+That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.
+
+\subsection{A definitional equivalence}
+Before proceeding to our result, we consider the definition of a fuzzy extractor.
+The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
+For clarity we will refer to $\mathcal{V}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular sample taken $w\in W$ as the \emph{outcome}.
+We will add the family $\mathcal{V}$ to the description of a fuzzy extractor where appropriate~(replacing the entropy requirement).
+
+The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
+The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
+The minimax theorem says we can reverse which of these actions is announced first.
+That is, the following two player games are equivalent:
+
+%More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
+We provide two formulations of a two player game.\footnote{We denote the outcome of the game as a reward to each player.
+This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
+This is to apply results from game theory.}
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
+$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
+If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
+If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
+Else reward $(-1, 1)$.
+\end{tabbing} 
+\vspace{.065in}
+\end{minipage}  &
+\begin{minipage}{3in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
+$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
+$W \leftarrow \mathcal{W}$\\
+If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
+If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
+Else reward $(-1, 1)$.
+\end{tabbing}
+\end{minipage}
+\end{tabular}
+\end{center}
+
+%\begin{center}
+%\begin{minipage}{1in}
+%\end{center}
+
+%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
+%Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
+%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
+
+%\begin{center}
+%\begin{minipage}{1in}
+% \end{minipage} 
+%\end{center}
+
+The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
+In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
+These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.
+
+\begin{lemma}
+\label{lem:quant switch fuzz}
+Let $\mathcal{V}$ be a family of distributions.
+If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
+Let $V$ be a distribution over elements of $\mathcal{V}$.
+Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
+If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
+\end{lemma}
+
+Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
+Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
+We can think of the description of $W$ as side-information or leakage to the adversary.
+The system designer, however never sees the particular outcome $W$.
+This asymmetry will form the basis of our negative results.
+
+\begin{corollary}
+\label{cor:no fuzz for dist}
+Let $\mathcal{V}$ be a family of distributions.
+Let $V$ be an arbitrary distribution over elements of $\mathcal{V}$.
+If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
+\end{corollary}
+%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
+However, as we show below the above construction does not extend to the setting of all well-spread distributions.
+In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
+In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
+In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
+
+%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
+The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
+We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
+The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
+
+%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
+
+Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
+
+\subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
+In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.
+In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
+
+\begin{theorem}
+\label{thm:imposs sketch}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 3 + (\gamma-1) / \log |\mathbb{F}|$.
+\end{theorem}
+
+\begin{proof}
+It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
+The adversary sees the information $W$, but the system designer does not.
+We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).
+
+We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.
+We begin by describing our family $\mathcal{V}$.
+$\mathcal{V}$ consists of the set of affine functions from one dimension to $\gamma$ dimensions.
+% That is, we project a single point in the field to an arbitrary element in the metric space.
+%In addition, the adversary learns the particular source that is being sketched while the system designer does not.
+To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.
+We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
+Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.
+
+Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.
+This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
+Define $V$ as the uniform distribution over all such $W$.
+Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+Fix some $4\le t < \gamma$.
+We then show the following~(in \apref{sec:proof secure sketch imposs}):
+
+\begin{itemize}
+\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
+\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
+\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.
+That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
+\end{itemize}
+\end{proof}
+\subsubsection{Feasibility of computational secure sketches}
+Fuller et al.
+showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+%This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
+The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
+
+\begin{definition}
+\label{def:relaxed hill}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
+\end{definition}
+
+A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ parameters to the definition, representing the distinguishing circuit).
+By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
+
+\begin{corollary}
+\label{cor:imposs comp sketch}
+Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
+There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
+If
+\begin{itemize}
+\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
+\item $t\ge 3 + (\gamma-1)/\log |\mathbb{F}|$,
+\item and $\epsilon + t\delta < 1/16$,
+\end{itemize}
+ then $\tilde{m} =O(1)$.
+\end{corollary}
+
+%\begin{corollary}
+%\label{cor:rec yields sketch}
+%Let $\mathcal{Z}$ be an alphabet.
+Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
+%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+%$4(\epsilon+t\delta)$. 
+%\end{corollary}
+
+\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
+Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+
+\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
+In the previous section, we showed a family of distributions that does not admit a secure sketch.
+In this section, we extend this result to fuzzy extractors.
+This result has significantly weaker parameters than the previous result but still demonstrates hard.
+\bnote{write this}
+
+We begin with the case of perfect correctness in the Hamming metric.
+
+\begin{theorem}
+\label{thm:imposs fuzz ext}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon =\ngl( n)$ for $t \approx \kappa $.
+\bnote{what is $\epsilon$?
+what are the other parameters?}
+\end{theorem}
+ \bnote{write a proof!}
+\begin{proof}
+Instead of showing the above theorem for an arbitrary length $\kappa$ we assume that the size of $\kappa$ is bounded away from $n$.
+That is, $\kappa = O(n^{1/2})$.
+Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
+
+For this family we construct a different family of distributions $V$.
+This family is closely related to the family we constructed in the previous section \bnote{comparison}.
+However, we consider the binary alphabet.
+Let $\nu = \omega(\log n)$ be some parameter to be determined later\bnote{set this later}.
+We describe a single element $W\in V$.
+For convenience we assume that $n/\nu$ is an integer.
+Let $x_1,..., x_\nu \in \zo^\nu$.
+Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
+Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
+Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
+\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
+b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
+\]
+Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.
+Note, this example is essentially the same family as in the previous example squished to the binary alphabet.
+\bnote{Come back to this explanation.}
+
+We now proceed using the same outline as the previous section\bnote{be more precise}
+\begin{itemize}
+\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item The distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
+\item Show that for most values public values they are many keys that have possible pre images in the metric space.  Furthermore, only a small number of the public values are feasible.
+\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
+\item For most values of possible $Z$ there are many keys that do not receive any weight, thus the output of the fuzzy extractor can be distinguished from uniform.
+\end{itemize}
+
+\begin{proposition} 
+For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\end{proposition}
+\begin{proof}
+Consider some fixed $W\in\mathcal{V}$.
+The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.
+Recall that $t< n/\nu$\bnote{need to say this earlier}.
+We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Fix some $w, w'\in W$.
+Denote by $x, x'$ the values that produce $w, w'$ respectively.
+Clearly, $x\neq x'$.
+Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
+This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
+Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = \omega(\log n)$.
+\end{proof}
+
+\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
+\end{proposition}
+\begin{proof}
+Consider some $w\in V$.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
+\end{proof}
+
+We now proceed to showing the technical portion of the theorem.
+We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
+Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
+
+\begin{lemma}
+Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.  Let $\nu = \kappa+1$ and $t = n/\nu-1$.  Then $\epsilon = \poly(n)$.\bnote{come back to this statement with precise parameters}
+\end{lemma}
+\begin{proof}
+We assume that $\rep$ is deterministic in our analysis.
+Any randomness necessary for the \rep algorithm can be provided by $\gen$.
+We do not consider these coins in our security analysis~(and thus, they can be considered private).
+Denote by $(R, P) \leftarrow \gen(V)$.
+
+%By the definition of correctness for $(\sketch, \rec)$, 
+%\[
+%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+%\]
+%For most $p$, $\rec$ works on most neighbors of $w$.  
+%Fix some $w$.  
+By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
+\[
+(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+\]
+%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+
+Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
+The distribution $R|P=p^*$ is the set of possible keys.
+The distribution $R|P=p^*$ induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
+Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
+
+Many of these sets must be small.
+That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
+If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.
+This is more points than exist in the metric space.
+
+For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Define two sets, called the interior and crust respectively: \bnote{change term crust?}
+
+\begin{align*}
+\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
+\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
+\end{align*}
+
+Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.
+We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.
+Consider some $r^*\in R_{small}$.
+Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+
+\begin{lemma}
+$|\inter(Q_{p^*, r^*})| \le |B_{n-\kappa -t+2}|$.
+\end{lemma}
+\begin{proof}
+\bnote{deficient sphere/ball?}
+First recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
+We call a set $S$ a \emph{deficient sphere} if there exists a point $x$ and a radius $\beta$ \bnote{check for conflicts with $\beta$} such that $B_{\beta}(x) \subseteq S \subseteq B_{\beta+1}(x)$.
+By the isoperimetric inequality on the Hamming space\bnote{cite!!!!}, there exists a deficient sphere $S_{p^*, r^*}$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
+We now find the radius of $S_{p^*, r^*}$.
+
+Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
+We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
+That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
+Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
+do better}.
+Thus,
+\[n-(\kappa-1) \ge d (\log n - \log d).\]  
+We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.
+
+Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
+That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
+This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
+That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
+And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
+This is a radius of almost $n$}
+\end{proof}
+
+We have shown that $|\inter(Q_{p^*, r^*}| \le |B_{n-\kappa -t+2}|$.  Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
+
+To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.
+
+Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^n-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
+ As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
+We know show there are many possible values for $Z |P=p^*$.
+The only information about $Z$ is contained in the point  $V=v$.
+The length of this point is $2^n$.
+Conditioned on this information there are still many possible values for $Z$.
+That is,
+ \[
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n/\nu-1)(\nu -1)}}{2^v} = n -n/\nu - 2\nu +1.
+ \]
+Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+This means that the $\gen$ algorithm may include points for possible $Z$ values into $K_{bad}$~(other than $v$) and these values are disjoint.
+The optimum strategy is to include these values uniformly from different $Z$ values.
+That is,
+\[
+\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | \le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}.
+\]
+
+We now show that $\expe | K_{bad} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
+We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
+\begin{align*}
+\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
+&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
+%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
+\end{align*}
+\bnote{the two combinatorial bounds we are using aren't good enough}
+To show that $\epsilon \ge 1/2$ we have that 
+%\begin{align*}
+%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
+%\end{align*}
+\bnote{why was that sufficient to break security}
+\bnote{still working this isn't complete}
+\end{proof}
+\end{proof}
+
+\textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.
+This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
+\bibliographystyle{alpha}
+\bibliography{crypto}
+
+\appendix
+
+\section{Leveraging convex combinations?}
+\label{sec:convex comb}
+In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+For example, consider the following hypothetical extension to \consref{cons:universal hash}.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+
+The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
+Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
+
+In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
+That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+However, in the setting where $W$ is a convex combination of flat sources this does not hold.
+
+Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+This distribution is illustrated in \figref{fig:convex comb}.
+
+The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\gamma, k\}$ where $\gamma$ is the number of distributions $W_1,..., W_\gamma$.
+(For our purposes, we can assume that $\gamma$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+
+Consider an input point $w\in W$.
+One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \gamma\}$.
+For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
+This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\gamma, k\}$.
+Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+
+\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
+However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
+That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
+
+In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
+
+\begin{figure}[t]
+
+\centering
+    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+    \caption{A convex combination of $W_1,..., W_\gamma$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+\label{fig:convex comb}    
+\end{figure}
+
+\section{Proofs}
+\subsection{Proof of \lemref{lem:fuzz necessary}}
+\label{sec:proof fuzz necessary}
+\begin{proof}
+Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
+Consider the following distinguisher $D$~(note that $D$ only provides an input and looks at the output, thus this distinguisher extends to the interactive setting):
+\begin{itemize}
+\item Input $r, p$.
+\item If $\rep(m^*, p) = r$, output $1$.
+\item Else output $0$.
+\end{itemize}
+First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
+Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.
+Thus, when $\kappa = \omega(\log n)$:
+\[
+\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
+\]
+\end{proof}
+
+\subsection{Proof of \thref{thm:layered hashing}}
+\label{sec:proof of layered hashing}
 \begin{proof}
@@
 
-\begin{corollary}
-\label{cor:extension to fuzz ext}
-Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
-(Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
-\end{corollary}
-
-\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.
-Going forward we will consider specific metric spaces, namely the Hamming metric.
-\section{Impossibility of Distribution-Oblivious Secure Sketches}
-\label{sec:dist oblivious}
-
-In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.
-This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.
-In this section we ask if the results can be replicated for a family of distributions.
-Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.
-The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).
-Unfortunately, we show for secure sketches this is not the case.
-That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.
-
-\subsection{A definitional equivalence}
-Before proceeding to our result, we consider the definition of a fuzzy extractor.
-The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
-For clarity we will refer to $\mathcal{V}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular sample taken $w\in W$ as the \emph{outcome}.
-We will add the family $\mathcal{V}$ to the description of a fuzzy extractor where appropriate~(replacing the entropy requirement).
-
-The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
-The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
-More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
-We will formulate this as a two player game.\footnote{We denote the outcome of the game as a reward to each player.
-This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
-This is to apply results from game theory.}
-
-\begin{center}
-\begin{minipage}{1in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
-$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
-If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
-\end{tabbing} \end{minipage} 
-\end{center}
-
-%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
-Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
-%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
-
-\begin{center}
-\begin{minipage}{1in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
-$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
-$W \leftarrow \mathcal{W}$\\
-If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
-\end{tabbing} \end{minipage} 
-\end{center}
-
-The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
-In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
-These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.
-
-\begin{lemma}
-\label{lem:quant switch fuzz}
-Let $\mathcal{V}$ be a family of distributions.
-Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
-Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
-Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-fuzzy extractor.\footnote{The other direction of this lemma is true as well.
-If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
-\end{lemma}
-
-Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
-Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-We can think of the description of $W$ as side-information or leakage to the adversary.
-The system designer, however never sees the particular outcome $W$.
-This asymmetry will form the basis of our negative results in the next subsection.
-
-\begin{corollary}
-\label{cor:no fuzz for dist}
-Let $\mathcal{V}$ be a family of distributions.
-Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
-If there does not exist a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
-\end{corollary}
-%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
-However, as we show below the above construction does not extend to the setting of all well-spread distributions.
-In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
-In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
-In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
-
-%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
-The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
-We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
-The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
-
-%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
-
-Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to the case of imperfect correctness.
-
-\subsection{Fuzzy min-entropy is not sufficient for secure sketches}
-In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.
-In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
-
-\begin{theorem}
-\label{thm:imposs sketch}
-Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 3 + (\gamma-1) / \log |\mathbb{F}|$.
-\end{theorem}
-
-\begin{proof}
-It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
-The adversary sees the information $W$, but the system designer does not.
-We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).
-
-We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.
-We begin by describing our family $\mathcal{V}$.
-$\mathcal{V}$ consists of the set of affine functions from one dimension to $\gamma$ dimensions.
-% That is, we project a single point in the field to an arbitrary element in the metric space.
-%In addition, the adversary learns the particular source that is being sketched while the system designer does not.
-To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.
-We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
-Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.
-
-Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.
-This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
-Define $V$ as the uniform distribution over all such $W$.
-Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
-Fix some $4\le t < \gamma$.
-We then show the following:
-
-\begin{itemize}
-\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
-\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
-\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.
-That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
-%   More concretely, conditioned on $V=v$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
-Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.
-Thus, $\Hav(V| \sketch(V) , Z)$ is small.
-\end{itemize}
+\section{Proof of \thref{thm:imposs sketch}}
+\label{sec:proof secure sketch imposs}
 \begin{proposition} 
@@
 \noindent \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
-\end{proof}
-
-\subsubsection{Feasibility of Computational secure sketches}
-Fuller et al.
-showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
-%This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
-The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
-
-\begin{definition}
-\label{def:relaxed hill}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
-\end{definition}
-
-A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ parameters to the definition, representing the distinguishing circuit).
-By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
-
-\begin{corollary}
-\label{cor:imposs comp sketch}
-Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
-If
-\begin{itemize}
-\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-\item $t\ge 3 + (\gamma-1)/\log |\mathbb{F}|$,
-\item and $\epsilon + t\delta < 1/16$,
-\end{itemize}
- then $\tilde{m} =O(1)$.
-\end{corollary}
-
-%\begin{corollary}
-%\label{cor:rec yields sketch}
-%Let $\mathcal{Z}$ be an alphabet.
-Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
-%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-%$4(\epsilon+t\delta)$. 
-%\end{corollary}
-
-\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
-Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
-
-\section{Impossibility of Distribution-Oblivious Fuzzy Extractors}
-In the previous section, we showed a family of distributions that does not admit a secure sketch.
-In this section, we extend this result to fuzzy extractors.
-This result has significantly weaker parameters than the previous result but still demonstrates hard.
-\bnote{write this}
-
-We begin with the case of perfect correctness in the Hamming metric.
-
-\begin{theorem}
-\label{thm:imposs fuzz ext}
-Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon =\ngl( n)$ for $t \approx \kappa $.
-\bnote{what is $\epsilon$?
-what are the other parameters?}
-\end{theorem}
- \bnote{write a proof!}
-\begin{proof}
-Instead of showing the above theorem for an arbitrary length $\kappa$ we assume that the size of $\kappa$ is bounded away from $n$.
-That is, $\kappa = O(n^{1/2})$.
-Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
-
-For this family we construct a different family of distributions $V$.
-This family is closely related to the family we constructed in the previous section \bnote{comparison}.
-However, we consider the binary alphabet.
-Let $\nu = \omega(\log n)$ be some parameter to be determined later\bnote{set this later}.
-We describe a single element $W\in V$.
-For convenience we assume that $n/\nu$ is an integer.
-Let $x_1,..., x_\nu \in \zo^\nu$.
-Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
-Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
-Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
-\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
-b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
-\]
-Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.
-Note, this example is essentially the same family as in the previous example squished to the binary alphabet.
-\bnote{Come back to this explanation.}
-
-We now proceed using the same outline as the previous section\bnote{be more precise}
-\begin{itemize}
-\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item The distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
-\item Show that for most values public values they are many keys that have possible pre images in the metric space.  Furthermore, only a small number of the public values are feasible.
-\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
-Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$ there are many keys that do not receive any weight, thus the output of the fuzzy extractor can be distinguished from uniform.
-\end{itemize}
-
-\begin{proposition} 
-For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
-\end{proposition}
-\begin{proof}
-Consider some fixed $W\in\mathcal{V}$.
-The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.
-Recall that $t< n/\nu$\bnote{need to say this earlier}.
-We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
-Fix some $w, w'\in W$.
-Denote by $x, x'$ the values that produce $w, w'$ respectively.
-Clearly, $x\neq x'$.
-Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
-This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
-Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = \omega(\log n)$.
-\end{proof}
-
-\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
-\end{proposition}
-\begin{proof}
-Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
-The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
-\end{proof}
-
-We now proceed to showing the technical portion of the theorem.
-We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
-Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
-
-\begin{lemma}
-Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.  Let $\nu = \kappa+1$ and $t = n/\nu-1$.  Then $\epsilon = \poly(n)$.\bnote{come back to this statement with precise parameters}
-\end{lemma}
-\begin{proof}
-We assume that $\rep$ is deterministic in our analysis.
-Any randomness necessary for the \rep algorithm can be provided by $\gen$.
-We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(R, P) \leftarrow \gen(V)$.
-
-%By the definition of correctness for $(\sketch, \rec)$, 
-%\[
-%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
-%\]
-%For most $p$, $\rec$ works on most neighbors of $w$.  
-%Fix some $w$.  
-By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
-\[
-(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
-\]
-%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
-
-Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
-The distribution $R|P=p^*$ is the set of possible keys.
-The distribution $R|P=p^*$ induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
-Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
-
-Many of these sets must be small.
-That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.
-This is more points than exist in the metric space.
-
-For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Define two sets, called the interior and crust respectively: \bnote{change term crust?}
-
-\begin{align*}
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
-\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
-\end{align*}
-
-Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.
-Consider some $r^*\in R_{small}$.
-Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
-
-\begin{lemma}
-$|\inter(Q_{p^*, r^*})| \le |B_{n-\kappa -t+2}|$.
-\end{lemma}
-\begin{proof}
-\bnote{deficient sphere/ball?}
-First recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
-We call a set $S$ a \emph{deficient sphere} if there exists a point $x$ and a radius $\beta$ \bnote{check for conflicts with $\beta$} such that $B_{\beta}(x) \subseteq S \subseteq B_{\beta+1}(x)$.
-By the isoperimetric inequality on the Hamming space\bnote{cite!!!!}, there exists a deficient sphere $S_{p^*, r^*}$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
-We now find the radius of $S_{p^*, r^*}$.
-
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
-We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
-That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
-Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
-do better}.
-Thus,
-\[n-(\kappa-1) \ge d (\log n - \log d).\]  
-We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.
-
-Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
-That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
-This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
-That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
-And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
-This is a radius of almost $n$}
-\end{proof}
-
-We have shown that $|\inter(Q_{p^*, r^*}| \le |B_{n-\kappa -t+2}|$.  Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
-
-To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.
-
-Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^n-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
- As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
-We know show there are many possible values for $Z |P=p^*$.
-The only information about $Z$ is contained in the point  $V=v$.
-The length of this point is $2^n$.
-Conditioned on this information there are still many possible values for $Z$.
-That is,
- \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n/\nu-1)(\nu -1)}}{2^v} = n -n/\nu - 2\nu +1.
- \]
-Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
-
-This means that the $\gen$ algorithm may include points for possible $Z$ values into $K_{bad}$~(other than $v$) and these values are disjoint.
-The optimum strategy is to include these values uniformly from different $Z$ values.
-That is,
-\[
-\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | \le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}.
-\]
-
-We now show that $\expe | K_{bad} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
-We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
-\begin{align*}
-\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
-&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
-%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
-\end{align*}
-\bnote{the two combinatorial bounds we are using aren't good enough}
-To show that $\epsilon \ge 1/2$ we have that 
-%\begin{align*}
-%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
-%\end{align*}
-\bnote{why was that sufficient to break security}
-\bnote{still working this isn't complete}
-\end{proof}
-\end{proof}
-
-\textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.This result presents a contrast between what is possible for sketches and fuzzy extraction.
-
-%\subsection{Contrived Weird Example I'm worried about}
-%\begin{center}
-%\begin{tabular}{c|c}
-%\begin{minipage}{3in}
-%\textbf{\gen}
-%\begin{enumerate}
-%\item \underline{Input}: $w = w_1,..., w_\gamma$
-%\item Sample $pad_1, pad_2 \leftarrow \mathcal{M}$.
-%\item Create random pad $x \leftarrow \zo^\gamma$.
-%\item Set $c \leftarrow Syndrome(w)$.
-%\item Set $r = Ext(w, seed)$, \\$p = \langle w, x\rangle, seed, c, x$.
-%\item If $pad_1 = w \wedge pad_2 =w$:
-%\begin{enumerate}[(i)]
-%\item Set $r=0$, \\
-%$p = \langle w, x\rangle\oplus 1, seed, c, x$.
-%\end{enumerate}
-%\end{enumerate}
-% \end{minipage} &
-%\begin{minipage}{3in}
-%\textbf{\rep}
-%\begin{enumerate}
-%\item \underline{Input}: $(w', p = (b, seed, c, x))$
-%\item Decode $w = Decode(w', c)$.
-%\item 
-%%\begin{enumerate}[(i)]
-%%\end{enumerate}
-%\item Output $r = \rep'(v', ss)$.
-%\end{enumerate}
-%\vspace{0.7in}
-%\end{minipage}
-%\end{tabular}
-%\end{center}
-
-\bibliographystyle{alpha}
-\bibliography{crypto}
-
-\appendix
-\section{Coding Theory}
-\begin{definition}
-\label{def:shannon-code}
-Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
+
+%\section{Coding Theory}
+%\begin{definition}
+%\label{def:shannon-code}
+%Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
 We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr_{w' | \dis(w', w)\le t}[\rec(c') \neq c]\le \epsilon$.
 To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
-\end{definition}
-
- \begin{definition}
-Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
-\end{definition}
-An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
+%\end{definition}
+%
+%
+% \begin{definition}
+%Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
+%$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+%\end{definition}
+%An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
 See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.
@@
 We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} %(we provide a proof in \secref{sec:proof of average to maximal error}):
-\begin{lemma}
-\label{lem:averageToMaximalError}
-Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
+%\begin{lemma}
+%\label{lem:averageToMaximalError}
+%Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
 There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
-\end{lemma}
-
-\bnote{This comes from asiacrypt paper, what to cite?}
-\section{Block Unguessable Distributions}
-\begin{definition}~\cite[Definition 4.2]{canetti2014key}
-\label{def:block guessable}
-Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
-\begin{cases}
-1 & w_j = w_j'\\
-0 & \text{otherwise}.
-\end{cases}
-\]
-A source $W = W_1||...|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
-\[
-\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-\section{Leveraging convex combinations?}
-\label{sec:convex comb}
-In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
-For example, consider the following hypothetical extension to \consref{cons:universal hash}.
-Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
-However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
-
-The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
-Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
-
-In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
-That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
-However, in the setting where $W$ is a convex combination of flat sources this does not hold.
-
-Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
-This distribution is illustrated in \figref{fig:convex comb}.
-
-The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
-Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\gamma, k\}$ where $\gamma$ is the number of distributions $W_1,..., W_\gamma$.
-(For our purposes, we can assume that $\gamma$ is quite large and the probability of $w^*$ becomes the dominant factor.)
-
-Consider an input point $w\in W$.
-One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \gamma\}$.
-For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
-This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
-This is despite the fact $\Hfuzz(W) \approx \min\{\gamma, k\}$.
-Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
-
-\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
-However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
-That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
-
-In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
-
-\begin{figure}[t]
-
-\centering
-    \includegraphics[width=.9\textwidth]{convexCombExample.png}
-    \caption{A convex combination of $W_1,..., W_\gamma$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
-\label{fig:convex comb}    
-\end{figure}
+%\end{lemma}
+%
+%\bnote{This comes from asiacrypt paper, what to cite?}
+%\section{Block Unguessable Distributions}
+%\begin{definition}~\cite[Definition 4.2]{canetti2014key}
+%\label{def:block guessable}
+%Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
+%\begin{cases}
+%1 & w_j = w_j'\\
+%0 & \text{otherwise}.
+%\end{cases}
+%\]
+%A source $W = W_1||...|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+%\[
+%\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+%\]
+%\end{definition}
 
 \section{Old Proofs}
+\bnote{I don't think we need anything from these sections}
 \subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
@@
 
-\section{Examples to Consider}
-
 \end{document}

### 2014-09-29 info-bounds/FuzzyExtPossibility.tex
working on proof for fuzzy ext impossibility
adding revised proof of fuzzy ext impossibility

@@
 
-Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distance results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.
-A fuzzy extractor performs two tasks, producing a uniform key and providing error-tolerance.
-Traditional, the uniform key is produced by extraction from the original secret $w$ and the error-tolerance is obtained by using a secure sketch.
-Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
+Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.
+\bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.
+The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
+Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
 \begin{definition}
@@
 \begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
-\[
- \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta
- \] 
-where the probability is taken over the coins of $\sketch$ and $\rec$.  
-\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.
-That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
+\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
+\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
+\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
@@
 
+\paragraph{Distribution-aware setting}
+We separate between two types of fuzzy extractors and secure sketches.
+Because we rarely have complete descriptions of a physical probability distribution the standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions $\mathcal{W}$.
+We call this type of algorithm \emph{distribution-oblivious}.
+We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.
+We provide a definition for secure sketches~(extendible to fuzzy extractors):
+
+\begin{definition}
+Let $W$ denote a distribution.
+A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.
+That is,
+\begin{enumerate}
+\item \emph{Correctness:} 
+$
+\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$
+Correctness is guaranteed only for the support of $W$.
+\item \emph{Security:} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\end{enumerate}
+\end{definition}
+The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
+When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.
+It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.
+
 \subsection{A necessary condition for security}
@@
 \end{lemma}
-\begin{proof}
-Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
-Consider the following distinguisher $D$:
-\begin{itemize}
-\item Input $r, p$.
-\item If $\rep(m^*, p) = r$, output $1$.
-\item Else output $0$.
-\end{itemize}
-First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.
-Thus, when $\kappa = \omega(\log n)$:
-\[
-\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
-\]
-\end{proof}
-\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.
+
+The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
+Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
+\lemref{lem:fuzz necessary} still applies.  
 This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-As stated above, fuzzy min-entropy is also a sufficient condition for security in the interactive setting.
-However, in the fuzzy extractor~(non-interactive) setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.
-We attempt to bridge this gap in this work.
-Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
-
-We separate between two types of fuzzy extractors and secure sketches.
-The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.
-This is because we rarely have complete distributions of a physical probability distribution.
-We call this type of algorithm distribution-oblivious.
-We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.
-We provide a definition for secure sketches~(extendible to fuzzy extractors):
-
-\begin{definition}
-Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.
-That is,
-\begin{enumerate}
-\item \emph{Correctness} 
-\[
-\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta\]
- where the probability is taken over the coins of $\sketch$ and $\rec$.  Note correctness is guaranteed only for the support of $W$.
-\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-\end{definition}
-Note (\sketch, \rec) know the description of $W$ and security only holds for $W$.
-When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to use the (possibly)~exponential size distributions.
-One possible approach is to allow $(\sketch, \rec)$ an oracle to the probability mass function of $W$.
-Our constructions do not work in this setting.\bnote{why am I talking about this?}
-
-%The summary of our results is in Table~\ref{tab:upper bounds}.
-
-\begin{table}
-\begin{tabular}{l | l}
-Lower bounds & Residual Entropy\\
-\hline
-Well-spread distribution & $\Hfuzz(W)$ \\
-Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
-Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
-\end{tabular}
-\caption{Summary of results for distribution aware setting.  Residual entropy of distribution-aware secure sketches with error $\delta$.}
-\label{tab:upper bounds}
-\end{table}
-%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
-We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
+As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.
+
+There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.
+There are also no known impossibility results for distributions with fuzzy min-entropy.
+Thus, the situation for fuzzy extractors is quite unclear.
+As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
+We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.
 
@@
 
-A sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.
-Skoric et al.
-previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.
-
 \begin{construction}
 \label{cons:universal hash}
-Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  We describe $\sketch, \rec$ as follows:
-\begin{itemize}
-\item $\sketch(w)$:
-\subitem Sample $K\leftarrow \mathcal{K}$.
-\subitem Set $p = F(K, w), K$.
-\item $\rec(w', y, K)$:
-\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
-\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
-\subitem Output $\perp$.
-\end{itemize}
+Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  Let $W$ be a distribution.  We describe $\sketch_W, \rec_W$ as follows:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{$\sketch_W$}
+\begin{enumerate}
+\item \underline{Input}: $w$.
+\item Sample $K\leftarrow \mathcal{K}$.
+\item Set $p = F(K, w), K$.
+\end{enumerate}
+\vspace{.3in}
+\end{minipage} &
+\begin{minipage}{3in}
+\textbf{$\rec_W$}
+\begin{enumerate}
+\item \underline{Input}: $(w', p = y, K)$
+\item Create $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
+\item Output $\perp$.
+\end{enumerate}
+\end{minipage}
+\end{tabular}
+\end{center}
 \end{construction}
+
 \begin{lemma}
+\label{lem:flat hashing}
 Let $W$ be a flat distributions with min-entropy $m$.  Then
@@
 Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+
+We provide a full proof in \apref{sec:proof of layered hashing}.
+The argument is similar to the proof of \lemref{lem:flat hashing}, however, there is an additional step showing that releasing the probability information is not too harmful.
+Namely, that an adversary with access to the probability information improves their success by a polynomial factor.
+Note we release $n$ levels where $n =\log |\mathcal{M}|$.
+
 \end{theorem}
 \bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
+
+\begin{corollary}
+\label{cor:extension to fuzz ext}
+Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+(Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
+\end{corollary}
+
+\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.
+Going forward we will consider specific metric spaces, namely the Hamming metric.
+\section{Impossibility of Distribution-Oblivious Secure Sketches}
+\label{sec:dist oblivious}
+
+In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.
+This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.
+In this section we ask if the results can be replicated for a family of distributions.
+Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.
+The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).
+Unfortunately, we show for secure sketches this is not the case.
+That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.
+
+\subsection{A definitional equivalence}
+Before proceeding to our result, we consider the definition of a fuzzy extractor.
+The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
+For clarity we will refer to $\mathcal{V}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular sample taken $w\in W$ as the \emph{outcome}.
+We will add the family $\mathcal{V}$ to the description of a fuzzy extractor where appropriate~(replacing the entropy requirement).
+
+The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
+The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
+The minimax theorem says we can reverse which of these actions is announced first.
+That is, the following two player games are equivalent:
+
+%More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
+We provide two formulations of a two player game.\footnote{We denote the outcome of the game as a reward to each player.
+This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
+This is to apply results from game theory.}
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
+$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
+If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
+If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
+Else reward $(-1, 1)$.
+\end{tabbing} 
+\vspace{.065in}
+\end{minipage}  &
+\begin{minipage}{3in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
+$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
+$W \leftarrow \mathcal{W}$\\
+If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
+If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
+Else reward $(-1, 1)$.
+\end{tabbing}
+\end{minipage}
+\end{tabular}
+\end{center}
+
+%\begin{center}
+%\begin{minipage}{1in}
+%\end{center}
+
+%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
+%Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
+%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
+
+%\begin{center}
+%\begin{minipage}{1in}
+% \end{minipage} 
+%\end{center}
+
+The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
+In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
+These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.
+
+\begin{lemma}
+\label{lem:quant switch fuzz}
+Let $\mathcal{V}$ be a family of distributions.
+If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
+Let $V$ be a distribution over elements of $\mathcal{V}$.
+Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
+If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
+\end{lemma}
+
+Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
+Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
+We can think of the description of $W$ as side-information or leakage to the adversary.
+The system designer, however never sees the particular outcome $W$.
+This asymmetry will form the basis of our negative results.
+
+\begin{corollary}
+\label{cor:no fuzz for dist}
+Let $\mathcal{V}$ be a family of distributions.
+Let $V$ be an arbitrary distribution over elements of $\mathcal{V}$.
+If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
+\end{corollary}
+%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
+However, as we show below the above construction does not extend to the setting of all well-spread distributions.
+In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
+In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
+In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
+
+%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
+The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
+We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
+The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
+
+%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
+
+Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
+
+\subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
+In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.
+In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
+
+\begin{theorem}
+\label{thm:imposs sketch}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 3 + (\gamma-1) / \log |\mathbb{F}|$.
+\end{theorem}
+
+\begin{proof}
+It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
+The adversary sees the information $W$, but the system designer does not.
+We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).
+
+We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.
+We begin by describing our family $\mathcal{V}$.
+$\mathcal{V}$ consists of the set of affine functions from one dimension to $\gamma$ dimensions.
+% That is, we project a single point in the field to an arbitrary element in the metric space.
+%In addition, the adversary learns the particular source that is being sketched while the system designer does not.
+To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.
+We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
+Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.
+
+Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.
+This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
+Define $V$ as the uniform distribution over all such $W$.
+Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+Fix some $4\le t < \gamma$.
+We then show the following~(in \apref{sec:proof secure sketch imposs}):
+
+\begin{itemize}
+\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
+\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
+\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.
+That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
+\end{itemize}
+\end{proof}
+\subsubsection{Feasibility of computational secure sketches}
+Fuller et al.
+showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+%This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
+The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
+
+\begin{definition}
+\label{def:relaxed hill}
+Let $(W, S)$ be a pair of random variables.  $W$ has 
+\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
+\end{definition}
+
+A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ parameters to the definition, representing the distinguishing circuit).
+By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
+
+\begin{corollary}
+\label{cor:imposs comp sketch}
+Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
+There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
+If
+\begin{itemize}
+\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
+\item $t\ge 3 + (\gamma-1)/\log |\mathbb{F}|$,
+\item and $\epsilon + t\delta < 1/16$,
+\end{itemize}
+ then $\tilde{m} =O(1)$.
+\end{corollary}
+
+%\begin{corollary}
+%\label{cor:rec yields sketch}
+%Let $\mathcal{Z}$ be an alphabet.
+Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
+%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
+%$4(\epsilon+t\delta)$. 
+%\end{corollary}
+
+\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
+Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+
+\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
+In the previous section, we showed a family of distributions that does not admit a secure sketch.
+In this section, we extend this result to fuzzy extractors.
+This result has significantly weaker parameters than the previous result but still demonstrates hard.
+\bnote{write this}
+
+We begin with the case of perfect correctness in the Hamming metric.
+
+\begin{theorem}
+\label{thm:imposs fuzz ext}
+Let $n$ be a security parameter.
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon \le 1/4 - \Theta(2^{n^{1/3}})$ for $t = \Theta(n^{4/5})$.
+\end{theorem}
+\begin{proof}
+Instead of showing the above theorem for an arbitrary length $\kappa$ we assume that the size of $\kappa$ is bounded away from $n$.
+We assume that $\kappa = \omega(\log n)$ and that $\kappa = o(n^c)$ for any constant $c>0$.
+\bnote{do we actually need this at any point?} Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
+
+Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.
+In particular, we need to assume a larger error tolerance $t=n^{4/5}$.
+This family is closely related to the family we constructed in \thref{thm:imposs sketch}.
+However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.
+Let $\nu = n/t = n^{1/5}$.
+For convenience we assume that $\nu\in\mathbb{Z}^+$.
+We describe a single element $W\in V$.
+Let $x_1,..., x_\nu \in \zo^\nu$.
+Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
+Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
+Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
+\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
+b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
+\]
+Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.
+
+We now proceed using the same outline as the previous section over the binary space.  We use the binary space to exploit the isoperimetric inequality on Hamming space.
+\begin{itemize}
+\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item The distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
+\item Show that for most values public values they are many keys that have possible pre images in the metric space.  Furthermore, only a small number of the public values are feasible.
+\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
+\item For most values of possible $Z$ there are many keys that do not receive any weight, thus the output of the fuzzy extractor can be distinguished from uniform.
+\end{itemize}
+
+\begin{proposition} 
+For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\end{proposition}
+\begin{proof}
+Consider some fixed $W\in\mathcal{V}$.
+The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =n^{1/5}$.
+Recall that $t= n/\nu$.
+We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Fix some $w, w'\in W$.
+Denote by $x, x'$ the values that produce $w, w'$ respectively.
+Clearly, $x\neq x'$.
+Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
+This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
+Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = n^{1/5}$.
+\end{proof}
+
+\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
+\end{proposition}
+\begin{proof}
+Consider some $w\in V$.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
+\end{proof}
+
+We now proceed to showing the technical portion of the theorem.
+We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
+Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
+
+\begin{lemma}
+Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.
+\bnote{do we actually use this anywhere?}There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\Theta(2^{-n^{1/3}})$.
+\end{lemma}
+\begin{proof}
+We assume that $\rep$ is deterministic in our analysis.
+Any randomness necessary for the \rep algorithm can be provided by $\gen$.
+We do not consider these coins in our security analysis~(and thus, they can be considered private).
+Denote by $(R, P) \leftarrow \gen(V)$.
+
+%By the definition of correctness for $(\sketch, \rec)$, 
+%\[
+%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+%\]
+%For most $p$, $\rec$ works on most neighbors of $w$.  
+%Fix some $w$.  
+By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
+\[
+(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+\]
+%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+
+Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
+The distribution $R|P=p^*$ is the set of possible keys.
+The distribution $R|P=p^*$ induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
+Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
+
+Many of these sets must be small.
+That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
+If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.
+This is more points than exist in the metric space.
+
+For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
+We first define the interior of a set:%Define two sets, called the interior and crust respectively: \bnote{change term crust?}
+\begin{align*}
+\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
+%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
+\end{align*}
+
+%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
+We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient sphere:
+\begin{definition}
+A set $S$ is a $\beta$-deficient sphere if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
+\end{definition}
+
+We now proceed to show that the interior of each $Q_{p^*, r^*}$ is small~(using the isoperimetric inequality on the Hamming space):
+%Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+
+\begin{lemma}
+$|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.
+\end{lemma}
+\begin{proof}
+Recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
+By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient sphere $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
+We now find the size of $S_{p^*, r^*}$.
+
+Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
+Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
+This means that $|S_{p^*, r^*}|$ is a deficient sphere of radius at most $n/2-t$.
+Let $X$ denote a uniform string on $\zo^n$.
+We use Hoeffding's inequality~\cite{hoeffding1963probability}:
+
+\begin{align*}
+|S_{p^*, r^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-n^{3/5}} \le 2^{n - n^{3/5}}
+\end{align*}
+
+% That is, We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
+That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
+Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
+do better}.
+Thus,
+%\[n-(\kappa-1) \ge d (\log n - \log d).\]  
+%We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.  
+%
+%Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
+That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
+This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
+That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
+And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
+This is a radius of almost $n$}
+\end{proof}
+
+We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.  %Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
+To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.
+
+Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^t-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
+ As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
+We know show there are many possible values for $Z |P=p^*$.
+The only information about $Z$ is contained in the point  $V=v$.
+The length of this point is $2^n$.
+Conditioned on this information there are still many possible values for $Z$.
+That is,
+ \[
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n-\theta(\nu))}}{2^v} = n -\Theta(\nu).
+ \]
+ \bnote{need to come back to why this is true}
+Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, r^*}$~(other than $v$) and these values are disjoint.
+The optimum strategy is to include these values uniformly from different $Z$ values.
+Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
+Note that $Q_{small} \le 2^{n-n^{1/3}}|R_{small}|$.
+That is, 
+\begin{align*}
+\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-n^{1/3}}|R_{small}|}{2^{n - \theta(\nu)}}\\
+&=\frac{|R_{small}|}{2^{n^{1/3}-\Theta(n^{1/5})}}.
+\end{align*}
+Thus, at most $1/2^{n^{1/3}- \Theta(n^{1/5})}$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $z$.  We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
+\begin{enumerate}
+\item On input $x, z$.
+\item Compute $R_{small}$.  
+\item If $x\not \in R_{small}$ output random bit $b$.
+\item Else compute $V|P=p^* \wedge Z=z$. 
+\item If $Q_{p^*, x} \cap V|P=p^* \wedge Z=z =\emptyset$ output $b=0$.
+\item Else output $b=1$.
+\end{enumerate}
+
+The overall distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise .  The advantage of $D$ is 
+\begin{align*}
+\Pr[D(R, P, Z) = 1] - \Pr[D(U, P, Z) =1]&=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
+&\ge \frac{1}{2}\sum_{p^*\in A_p} \Pr[P=p^*] \Pr[D_{p^*}(R, Z) = 1] - \Pr[D_{p^*}(U, Z)=1]\\
+&\ge \frac{1}{2}\sum_{p^*\in A_p} \Pr[P=p^*] (\Pr[D_{p^*}(R, Z) = 1 | R\in R_{small}] \\&- \Pr[D_{p^*}(U, Z)=1 | R\in R_{small}])\Pr[R\in R_{small}]\\
+&\ge 1/4\sum_{p^* \in A_p} \Pr[P=p^*]\left(1- \Theta(2^{-n^{1/3}})\right) = 1/4-\Theta(2^{-n^{1/3}}).
+\end{align*}
+%We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
+%We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
+%\begin{align*}
+%\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
+%&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
+%%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
+%\end{align*}
+%\bnote{the two combinatorial bounds we are using aren't good enough}
+%To show that $\epsilon \ge 1/2$ we have that 
+%%\begin{align*}
+%%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
+%%\end{align*}
+%\bnote{why was that sufficient to break security}
+%\bnote{still working this isn't complete}
+\end{proof}
+\end{proof}
+
+\textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.
+This result presents a contrast between what is possible for sketches and fuzzy extraction.
+
+\bibliographystyle{alpha}
+\bibliography{crypto}
+
+\appendix
+
+\section{Leveraging convex combinations?}
+\label{sec:convex comb}
+In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+For example, consider the following hypothetical extension to \consref{cons:universal hash}.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+
+The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
+Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
+
+In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
+That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+However, in the setting where $W$ is a convex combination of flat sources this does not hold.
+
+Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+This distribution is illustrated in \figref{fig:convex comb}.
+
+The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\gamma, k\}$ where $\gamma$ is the number of distributions $W_1,..., W_\gamma$.
+(For our purposes, we can assume that $\gamma$ is quite large and the probability of $w^*$ becomes the dominant factor.)
+
+Consider an input point $w\in W$.
+One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \gamma\}$.
+For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
+This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
+This is despite the fact $\Hfuzz(W) \approx \min\{\gamma, k\}$.
+Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
+
+\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
+However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
+That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
+
+In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
+
+\begin{figure}[t]
+
+\centering
+    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+    \caption{A convex combination of $W_1,..., W_\gamma$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+\label{fig:convex comb}    
+\end{figure}
+
+\section{Proofs}
+\subsection{Proof of \lemref{lem:fuzz necessary}}
+\label{sec:proof fuzz necessary}
+\begin{proof}
+Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
+This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
+Consider the following distinguisher $D$~(note that $D$ only provides an input and looks at the output, thus this distinguisher extends to the interactive setting):
+\begin{itemize}
+\item Input $r, p$.
+\item If $\rep(m^*, p) = r$, output $1$.
+\item Else output $0$.
+\end{itemize}
+First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
+Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.
+Thus, when $\kappa = \omega(\log n)$:
+\[
+\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
+\]
+\end{proof}
+
+\subsection{Proof of \thref{thm:layered hashing}}
+\label{sec:proof of layered hashing}
 \begin{proof}
@@
 
-\begin{corollary}
-\label{cor:extension to fuzz ext}
-Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
-(Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
-\end{corollary}
-
-\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.
-Going forward we will consider specific metric spaces, namely the Hamming metric.
-\section{Distribution-Oblivious Sketches}
-\label{sec:dist oblivious}
-
-In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.
-This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.
-In this section we ask if the results can be replicated for a family of distributions.
-Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.
-The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).
-Unfortunately, we show for secure sketches this is not the case.
-That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.
-
-\subsection{A definitional equivalence}
-Before proceeding to our result, we consider the definition of a fuzzy extractor.
-The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
-For clarity we will refer to $\mathcal{V}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular sample taken $w\in W$ as the \emph{outcome}.
-We will add the family $\mathcal{V}$ to the description of a fuzzy extractor where appropriate~(replacing the entropy requirement).
-
-The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
-The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
-More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
-We will formulate this as a two player game.\footnote{We denote the outcome of the game as a reward to each player.
-This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
-This is to apply results from game theory.}
-
-\begin{center}
-\begin{minipage}{1in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
-$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
-If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
-\end{tabbing} \end{minipage} 
-\end{center}
-
-%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
-Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
-%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
-
-\begin{center}
-\begin{minipage}{1in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
-$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
-$W \leftarrow \mathcal{W}$\\
-If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
-\end{tabbing} \end{minipage} 
-\end{center}
-
-The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.
-In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
-These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.
-
-\begin{lemma}
-\label{lem:quant switch fuzz}
-Let $\mathcal{V}$ be a family of distributions.
-Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
-Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
-Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-fuzzy extractor.\footnote{The other direction of this lemma is true as well.
-If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
-\end{lemma}
-
-Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
-Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-We can think of the description of $W$ as side-information or leakage to the adversary.
-The system designer, however never sees the particular outcome $W$.
-This asymmetry will form the basis of our negative results in the next subsection.
-
-\begin{corollary}
-\label{cor:no fuzz for dist}
-Let $\mathcal{V}$ be a family of distributions.
-Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.
-If there does not exist a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
-\end{corollary}
-%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
-However, as we show below the above construction does not extend to the setting of all well-spread distributions.
-In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
-In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
-In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
-
-%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
-The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
-We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
-The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
-
-%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
-
-Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to the case of imperfect correctness.
-
-\subsection{Fuzzy min-entropy is not sufficient for secure sketches}
-In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.
-In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
-
-\begin{theorem}
-\label{thm:imposs sketch}
-Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
-\bnote{finish proof}
-\end{theorem}
-
-\begin{proof}
-It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
-The adversary sees the information $W$, but the system designer does not.
-We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).
-
-We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.
-We begin by describing our family $\mathcal{V}$.
-$\mathcal{V}$ consists of the set of affine functions from one dimension to $\gamma$ dimensions.
-% That is, we project a single point in the field to an arbitrary element in the metric space.
-%In addition, the adversary learns the particular source that is being sketched while the system designer does not.
-To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.
-We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
-Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.
-
-Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.
-This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
-Define $V$ as the uniform distribution over all such $W$.
-Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
-Fix some $4\le t < \gamma$.
-We then show the following:
-
-\begin{itemize}
-\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item The distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
-\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\gamma-t+1)\log |\mathbb{F}|+1$. 
-\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
-Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.  Thus, $\Hav(V| \sketch(V) , Z)$ is small.
-\end{itemize}
+\section{Proof of \thref{thm:imposs sketch}}
+\label{sec:proof secure sketch imposs}
 \begin{proposition} 
@@
 &\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+1\\
-&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}|+1\\
-&\le \Theta(1)
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (\frac{|\mathbb{F}|}{2})+1\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|) + (\gamma -1)+1\\
+&\le (3-t)\log |\mathbb{F}| + (\gamma -1)+1\\
 \end{align*}
- Where the last line follows for $t\ge 4$.  The eighth line follows from the seventh as long as $|\mathbb{F}|????$\bnote{fix this}
+This value is $\Theta(1)$ if $t\ge 3+ (\gamma-1)/\log | \mathbb{F}|$.
+\bnote{ I feel like this analysis can be tightened up.
+Saying that $\log (|\mathbb{F}| -1 ) \ge \log (|\mathbb{F}|)-1$ seems like a big loss.}
  \end{proof}
-
- \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
-%\begin{lemma}
-%$\Hav(V| P , Z) = \Theta(1)$
-%\end{lemma}
-%\begin{proof}
-%Consider some fixed $p$.
-%If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
-%\[
-%\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
-%\]
-%Then by the union bound, 
-%\[
-%\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
-%\]
-%\bnote{need to average across $P$}
-%\bnote{I'm confused about what we mean by $Z$ being universal here.}
-%\bnote{working here!}
-%\end{proof}
-%
-%\bnote{stopped here}
-\end{proof}
-
-%\begin{lemma}
-%There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
-%\end{lemma}
-%\begin{proof}
-%Need to show several things.  
-%\begin{itemize}
-%\item Each component of the distribution has fuzzy min-entropy.
-%\item Any sketch must leak some information about $V$.
-%\item The side information can be thought of as a hash function.
-Furthermore, it is independent of the sketch.
-Thus, the sketch and hash are independent information.
-Thus, conditioned on both there is almost no entropy.
-%\end{itemize}
-%\end{proof}
-
-Canetti et al.~\cite{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
-
-%\begin{lemma}
-%There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
-%\end{lemma}
-
-\subsubsection{Extending to Computational secure sketches}
-Fuller et al.
-showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
-%This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
-The definitional of Fuller et al. is uses HILL entropy.
-
-HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  Fuller et al.~use a weak version due to Gentry and Wichs~\cite{gentry2011separating}.
-
-\begin{definition}
-\label{def:relaxed hill}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
-\end{definition}
-
-A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $s_{sec}, \epsilon_{sec}$ parameters to the definition, representing the distinguishing circuit).
-By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
-
-\begin{corollary}
-\label{cor:imposs comp sketch}
-Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
-If
-\begin{itemize}
-\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-\item $t\ge 4$,
-\item and $\epsilon + t\delta < 1/16$,
-\end{itemize}
- then $\tilde{m} =O(1)$.
-\end{corollary}
-
-%\begin{corollary}
-%\label{cor:rec yields sketch}
-%Let $\mathcal{Z}$ be an alphabet.
-Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
-%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
-%$4(\epsilon+t\delta)$. 
-%\end{corollary}
-
-\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
-Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
-
-\section{Distribution-Oblivious Fuzzy Extractors}
-In the previous section, we showed a family of distributions that does not admit a secure sketch.
-In this section, we extend this result to fuzzy extractors.
-This result has significantly weaker parameters than the previous result but still demonstrates hard.
-\bnote{write this}
-
-We begin with the case of perfect correctness in the Hamming metric.
-
-\begin{theorem}
-\label{thm:imposs fuzz ext}
-Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon =\ngl( n)$ for $t \approx \kappa $.
-\bnote{what is $\epsilon$?
-what are the other parameters?}
-\end{theorem}
- \bnote{write a proof!}
-\begin{proof}
-Instead of showing the above theorem for an arbitrary length $\kappa$ we assume that the size of $\kappa$ is bounded away from $n$.
-That is, $\kappa = O(n^{1/2})$.
-Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
-
-For this family we construct a different family of distributions $V$.
-This family is closely related to the family we constructed in the previous section \bnote{comparison}.
-However, we consider the binary alphabet.
-Let $\nu = \omega(\log n)$ be some parameter to be determined later\bnote{set this later}.
-We describe a single element $W\in V$.
-For convenience we assume that $n/\nu$ is an integer.
-Let $x_1,..., x_\nu \in \zo^\nu$.
-Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
-Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
-Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
-\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
-b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
-\]
-Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.
-Note, this example is essentially the same family as in the previous example squished to the binary alphabet.
-\bnote{Come back to this explanation.}
-
-We now proceed using the same outline as the previous section\bnote{be more precise}
-\begin{itemize}
-\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item The distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
-\item Show that for most values public values they are many keys that have possible pre images in the metric space.  Furthermore, only a small number of the public values are feasible.
-\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
-Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$ there are many keys that do not receive any weight, thus the output of the fuzzy extractor can be distinguished from uniform.
-\end{itemize}
-
-\begin{proposition} 
-For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
-\end{proposition}
-\begin{proof}
-Consider some fixed $W\in\mathcal{V}$.
-The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.
-Recall that $t< n/\nu$\bnote{need to say this earlier}.
-We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
-Fix some $w, w'\in W$.
-Denote by $x, x'$ the values that produce $w, w'$ respectively.
-Clearly, $x\neq x'$.
-Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
-This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
-Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = \omega(\log n)$.
-\end{proof}
-
-\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
-\end{proposition}
-\begin{proof}
-Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
-The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
-\end{proof}
-
-We now proceed to showing the technical portion of the theorem.
-We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
-Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
-
-\begin{lemma}
-Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.  Let $\nu = \kappa+1$ and $t = n/\nu-1$.  Then $\epsilon = \poly(n)$.\bnote{come back to this statement with precise parameters}
-\end{lemma}
-\begin{proof}
-We assume that $\rep$ is deterministic in our analysis.
-Any randomness necessary for the \rep algorithm can be provided by $\gen$.
-We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(R, P) \leftarrow \gen(V)$.
-
-%By the definition of correctness for $(\sketch, \rec)$, 
-%\[
-%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
-%\]
-%For most $p$, $\rec$ works on most neighbors of $w$.  
-%Fix some $w$.  
-By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
-\[
-(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
-\]
-%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
-
-Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
-The distribution $R|P=p^*$ is the set of possible keys.
-The distribution $R|P=p^*$ induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
-Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
-
-Many of these sets must be small.
-That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.
-This is more points than exist in the metric space.
-
-For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Define two sets, called the interior and crust respectively: \bnote{change term crust?}
-
-\begin{align*}
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
-\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
-\end{align*}
-
-Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.
-Consider some $r^*\in R_{small}$.
-Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
-
-\begin{lemma}
-$|\inter(Q_{p^*, r^*})| \le |B_{n-\kappa -t+2}|$.
-\end{lemma}
-\begin{proof}
-\bnote{deficient sphere/ball?}
-First recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
-We call a set $S$ a \emph{deficient sphere} if there exists a point $x$ and a radius $\beta$ \bnote{check for conflicts with $\beta$} such that $B_{\beta}(x) \subseteq S \subseteq B_{\beta+1}(x)$.
-By the isoperimetric inequality on the Hamming space\bnote{cite!!!!}, there exists a deficient sphere $S_{p^*, r^*}$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
-We now find the radius of $S_{p^*, r^*}$.
-
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
-We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
-That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
-Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{do we need to cite something here?}.
-Thus,
-\[n-(\kappa-1) \ge d (\log n - \log d).\]  
-We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.
-
-Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
-That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
-This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
-That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
-And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
-This is a radius of almost $n$}
-\end{proof}
-
-We have shown that $|\inter(Q_{p^*, r^*}| \le |B_{n-\kappa -t+2}|$.  Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
-
-To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.
-
-Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^n-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
- As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
-We know show there are many possible values for $Z |P=p^*$.
-The only information about $Z$ is contained in the point  $V=v$.
-The length of this point is $2^n$.
-Conditioned on this information there are still many possible values for $Z$.
-That is,
- \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n/\nu-1)(\nu -1)}}{2^v} = n -n/\nu - 2\nu +1.
- \]
-Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
-
-This means that the $\gen$ algorithm may include points for possible $Z$ values into $K_{bad}$~(other than $v$) and these values are disjoint.
-The optimum strategy is to include these values uniformly from different $Z$ values.
-That is,
-\[
-\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | \le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}.
-\]
-
-We now show that $\expe | K_{bad} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
-We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$.  We then have that, 
-\begin{align*}
-\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
-&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
-%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
-\end{align*}
-\bnote{the two combinatorial bounds we are using aren't good enough}
-To show that $\epsilon \ge 1/2$ we have that 
-%\begin{align*}
-%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
-%\end{align*}
-\bnote{why was that sufficient to break security}
-\bnote{still working this isn't complete}
-\end{proof}
-\end{proof}
-
-%\subsection{Contrived Weird Example I'm worried about}
-%\begin{center}
-%\begin{tabular}{c|c}
-%\begin{minipage}{3in}
-%\textbf{\gen}
-%\begin{enumerate}
-%\item \underline{Input}: $w = w_1,..., w_\gamma$
-%\item Sample $pad_1, pad_2 \leftarrow \mathcal{M}$.
-%\item Create random pad $x \leftarrow \zo^\gamma$.
-%\item Set $c \leftarrow Syndrome(w)$.
-%\item Set $r = Ext(w, seed)$, \\$p = \langle w, x\rangle, seed, c, x$.
-%\item If $pad_1 = w \wedge pad_2 =w$:
-%\begin{enumerate}[(i)]
-%\item Set $r=0$, \\
-%$p = \langle w, x\rangle\oplus 1, seed, c, x$.
-%\end{enumerate}
-%\end{enumerate}
-% \end{minipage} &
-%\begin{minipage}{3in}
-%\textbf{\rep}
-%\begin{enumerate}
-%\item \underline{Input}: $(w', p = (b, seed, c, x))$
-%\item Decode $w = Decode(w', c)$.
-%\item 
-%%\begin{enumerate}[(i)]
-%%\end{enumerate}
-%\item Output $r = \rep'(v', ss)$.
-%\end{enumerate}
-%\vspace{0.7in}
-%\end{minipage}
-%\end{tabular}
-%\end{center}
-
-\bibliographystyle{alpha}
-\bibliography{crypto}
-
-\appendix
-\section{Coding Theory}
-\begin{definition}
-\label{def:shannon-code}
-Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
+\noindent \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
+
+%\section{Coding Theory}
+%\begin{definition}
+%\label{def:shannon-code}
+%Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
 We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr_{w' | \dis(w', w)\le t}[\rec(c') \neq c]\le \epsilon$.
 To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
-\end{definition}
-
- \begin{definition}
-Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
-\end{definition}
-An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
+%\end{definition}
+%
+%
+% \begin{definition}
+%Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
+%$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+%\end{definition}
+%An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
 See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.

### 2014-09-29 trunk/info-bounds/FuzzyExtPossibility.tex
adding revised proof of fuzzy ext impossibility

@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon =\ngl( n)$ for $t \approx \kappa $.
-\bnote{what is $\epsilon$?
-what are the other parameters?}
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon \le 1/4 - \Theta(2^{n^{1/3}})$ for $t = \Theta(n^{4/5})$.
 \end{theorem}
- \bnote{write a proof!}
 \begin{proof}
 Instead of showing the above theorem for an arbitrary length $\kappa$ we assume that the size of $\kappa$ is bounded away from $n$.
-That is, $\kappa = O(n^{1/2})$.
-Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
-
-For this family we construct a different family of distributions $V$.
-This family is closely related to the family we constructed in the previous section \bnote{comparison}.
-However, we consider the binary alphabet.
-Let $\nu = \omega(\log n)$ be some parameter to be determined later\bnote{set this later}.
+We assume that $\kappa = \omega(\log n)$ and that $\kappa = o(n^c)$ for any constant $c>0$.
+\bnote{do we actually need this at any point?} Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
+
+Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.
+In particular, we need to assume a larger error tolerance $t=n^{4/5}$.
+This family is closely related to the family we constructed in \thref{thm:imposs sketch}.
+However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.
+Let $\nu = n/t = n^{1/5}$.
+For convenience we assume that $\nu\in\mathbb{Z}^+$.
 We describe a single element $W\in V$.
-For convenience we assume that $n/\nu$ is an integer.
 Let $x_1,..., x_\nu \in \zo^\nu$.
@@
 \]
-Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.
-Note, this example is essentially the same family as in the previous example squished to the binary alphabet.
-\bnote{Come back to this explanation.}
-
-We now proceed using the same outline as the previous section\bnote{be more precise}
+Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.
+
+We now proceed using the same outline as the previous section over the binary space.  We use the binary space to exploit the isoperimetric inequality on Hamming space.
 \begin{itemize}
@@
 Consider some fixed $W\in\mathcal{V}$.
-The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.
-Recall that $t< n/\nu$\bnote{need to say this earlier}.
+The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =n^{1/5}$.
+Recall that $t= n/\nu$.
 We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
@@
 This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
-Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = \omega(\log n)$.
+Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = n^{1/5}$.
 \end{proof}
@@
 \begin{lemma}
-Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.  Let $\nu = \kappa+1$ and $t = n/\nu-1$.  Then $\epsilon = \poly(n)$.\bnote{come back to this statement with precise parameters}
+Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.
+\bnote{do we actually use this anywhere?}There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\Theta(2^{-n^{1/3}})$.
 \end{lemma}
@@
 
-For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Define two sets, called the interior and crust respectively: \bnote{change term crust?}
-
+For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
+We first define the interior of a set:%Define two sets, called the interior and crust respectively: \bnote{change term crust?}
 \begin{align*}
 \inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
-\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
+%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
 \end{align*}
 
-Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.
-Consider some $r^*\in R_{small}$.
-Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
+We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient sphere:
+\begin{definition}
+A set $S$ is a $\beta$-deficient ball if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
+\end{definition}
+
+We now proceed to show that the interior of each $Q_{p^*, r^*}$ is small~(using the isoperimetric inequality on the Hamming space):
+%Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
 
 \begin{lemma}
-$|\inter(Q_{p^*, r^*})| \le |B_{n-\kappa -t+2}|$.
+$|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.
 \end{lemma}
 \begin{proof}
-\bnote{deficient sphere/ball?}
-First recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
-We call a set $S$ a \emph{deficient sphere} if there exists a point $x$ and a radius $\beta$ \bnote{check for conflicts with $\beta$} such that $B_{\beta}(x) \subseteq S \subseteq B_{\beta+1}(x)$.
-By the isoperimetric inequality on the Hamming space\bnote{cite!!!!}, there exists a deficient sphere $S_{p^*, r^*}$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
-We now find the radius of $S_{p^*, r^*}$.
+Recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
+By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, r^*}$).
+We now find the size of $S_{p^*, r^*}$.
 
 Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
-We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
+Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
+This means that $|S_{p^*, r^*}|$ is a deficient sphere of radius at most $n/2-t$.
+Let $X$ denote a uniform string on $\zo^n$.
+We use Hoeffding's inequality~\cite{hoeffding1963probability}:
+
+\begin{align*}
+|S_{p^*, r^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-n^{3/5}} \le 2^{n - n^{3/5}}
+\end{align*}
+
+% That is, We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
 That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
@@
 Thus,
-\[n-(\kappa-1) \ge d (\log n - \log d).\]  
-We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.
-
-Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
+%\[n-(\kappa-1) \ge d (\log n - \log d).\]  
+%We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.  
+%
+%Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
 That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
@@
 
-We have shown that $|\inter(Q_{p^*, r^*}| \le |B_{n-\kappa -t+2}|$.  Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
-
+We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.  %Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
 To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.  
-
-Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^n-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
+Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^t-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
  As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
@@
  \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n/\nu-1)(\nu -1)}}{2^v} = n -n/\nu - 2\nu +1.
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n-\theta(\nu))}}{2^v} = n -\Theta(\nu).
  \]
+ \bnote{need to come back to why this is true}
 Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
 
-This means that the $\gen$ algorithm may include points for possible $Z$ values into $K_{bad}$~(other than $v$) and these values are disjoint.
+This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, r^*}$~(other than $v$) and these values are disjoint.
 The optimum strategy is to include these values uniformly from different $Z$ values.
+Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
+Note that $Q_{small} \le 2^{n-n^{1/3}}|R_{small}|$.
 That is, 
-\[
-\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | \le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}.
-\]
-
-We now show that $\expe | K_{bad} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
-We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
 \begin{align*}
-\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
-&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
-%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
+\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-n^{1/3}}|R_{small}|}{2^{n - \theta(\nu)}}\\
+&=\frac{|R_{small}|}{2^{n^{1/3}-\Theta(n^{1/5})}}.
 \end{align*}
-\bnote{the two combinatorial bounds we are using aren't good enough}
-To show that $\epsilon \ge 1/2$ we have that 
+Thus, at most $1/2^{n^{1/3}- \Theta(n^{1/5})}$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $z$.  We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
+\begin{enumerate}
+\item On input $x, z$.
+%\item If $x\not \in R_{small}$ output random bit $b$.
+\item Compute $V|P=p^* \wedge Z=z$. 
+\item If $(Q_{p^*, x} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
+\item Else output $b=1$.
+\end{enumerate}
+
+The distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
+\begin{align*}
+\Pr[D(R, P, Z) = 1] &- \Pr[D(U, P, Z) =1]=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
+&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/2- \Theta(2^{-n^{1/3}})\right) = 1/4-\Theta(2^{-n^{1/3}}).
+\end{align*}
+Where the last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
+%We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
+%We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
 %\begin{align*}
-%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
+%\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
+%&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
+%%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
 %\end{align*}
-\bnote{why was that sufficient to break security}
-\bnote{still working this isn't complete}
+%\bnote{the two combinatorial bounds we are using aren't good enough}
+%To show that $\epsilon \ge 1/2$ we have that 
+%%\begin{align*}
+%%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
+%%\end{align*}
+%\bnote{why was that sufficient to break security}
+%\bnote{still working this isn't complete}
 \end{proof}

### 2014-09-29 info-bounds/FuzzyExtPossibility.tex
moving to k can't be one bit

@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\kappa =\omega(\log n)$ such that $\epsilon \le 1/4 - \Theta(2^{n^{1/3}})$ for $t = \Theta(n^{4/5})$.
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \Theta(2^{n^{1/3}})$ for $t = \Theta(n^{4/5})$.
 \end{theorem}
 \begin{proof}
-Instead of showing the above theorem for an arbitrary length $\kappa$ we assume that the size of $\kappa$ is bounded away from $n$.
-We assume that $\kappa = \omega(\log n)$ and that $\kappa = o(n^c)$ for any constant $c>0$.
-\bnote{do we actually need this at any point?} Note that ruling out a fuzzy extractor with this length key clearly rules out extracting a longer key.
-
 Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.
@@
 
-We now proceed using the same outline as the previous section over the binary space.  We use the binary space to exploit the isoperimetric inequality on Hamming space.
+The proof uses the same basic outline as the previous result.  However, we work over the binary space to exploit the isoperimetric inequality on Hamming space.
 \begin{itemize}
@@
 \item The distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
-\item Show that for most values public values they are many keys that have possible pre images in the metric space.  Furthermore, only a small number of the public values are feasible.
-\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+\item Show that for half the keys have a bounded number of pre images in the metric space.
+Denote this set as $R_{small}$.
+The only viable pre images $v$ in this set are located distance $t$ from the boundary~(that is, $v$ is viable if all points in the metric space within distance $t$ map to the same key).
+This means for every key $r\in R_{small}$ has bounded number of viable points in the metric space: $2^{n-n^{3/5}}$.
+\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
 Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$ there are many keys that do not receive any weight, thus the output of the fuzzy extractor can be distinguished from uniform.
+\item For most values of possible $Z$, the intersection between the viable pre images of $V|P \wedge Z$ and the viable pre images of $R_{small}$ is empty.
+Thus, the output of the fuzzy extractor can be distinguished from uniform.
 \end{itemize}
@@
 \begin{lemma}
-Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$.
-\bnote{do we actually use this anywhere?}There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\Theta(2^{-n^{1/3}})$.
+Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 1$.
+There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\Theta(2^{-n^{1/3}})$.
 \end{lemma}
@@
 That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.
-This is more points than exist in the metric space.
+If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
 
@@
 \begin{definition}
-A set $S$ is a $\beta$-deficient sphere if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
+A set $S$ is a $\beta$-deficient ball if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
 \end{definition}
@@
 Recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient sphere $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient sphere~(and its radius is $t$ larger than $S_{p^*, r^*}$).
+By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, r^*}$).
 We now find the size of $S_{p^*, r^*}$.
 
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
+Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}\leq 2^{1/2}$.
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
@@
 To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.  
-
 Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^t-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
@@
 \item On input $x, z$.
-\item Compute $R_{small}$.  
-\item If $x\not \in R_{small}$ output random bit $b$.
-\item Else compute $V|P=p^* \wedge Z=z$. 
-\item If $Q_{p^*, x} \cap V|P=p^* \wedge Z=z =\emptyset$ output $b=0$.
+%\item If $x\not \in R_{small}$ output random bit $b$.
+\item Compute $V|P=p^* \wedge Z=z$ and $Q_{p^*, x}$. 
+\item If $(Q_{p^*, x} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
 \item Else output $b=1$.
@@
 
-The overall distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise .  The advantage of $D$ is 
+The distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
 \begin{align*}
-\Pr[D(R, P, Z) = 1] - \Pr[D(U, P, Z) =1]&=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
-&\ge \frac{1}{2}\sum_{p^*\in A_p} \Pr[P=p^*] \Pr[D_{p^*}(R, Z) = 1] - \Pr[D_{p^*}(U, Z)=1]\\
-&\ge \frac{1}{2}\sum_{p^*\in A_p} \Pr[P=p^*] (\Pr[D_{p^*}(R, Z) = 1 | R\in R_{small}] \\&- \Pr[D_{p^*}(U, Z)=1 | R\in R_{small}])\Pr[R\in R_{small}]\\
-&\ge 1/4\sum_{p^* \in A_p} \Pr[P=p^*]\left(1- \Theta(2^{-n^{1/3}})\right) = 1/4-\Theta(2^{-n^{1/3}}).
+\Pr[D(R, P, Z) = 1] &- \Pr[D(U, P, Z) =1]=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
+&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/2- \Theta(2^{-n^{1/3}})\right) = 1/4-\Theta(2^{-n^{1/3}}).
 \end{align*}
+The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
 %We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 

### 2014-09-29 info-bounds/FuzzyExtPossibility.tex
wrote a lemma about log (beta-1)

@@
 \end{align*}
-Then averaging over the possible values of $s$, we have the following:
+Then averaging over the possible values of $s$, we have the following as long as $t\ge 4$:
 \begin{align*}
@@
 &\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+1\\
-&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (\frac{|\mathbb{F}|}{2})+1\\
-&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|) + (\gamma -1)+1\\
-&\le (3-t)\log |\mathbb{F}| + (\gamma -1)+1\\
+&< (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}| +1 \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
+&\le (4-t)\log |\mathbb{F}| +1\\
+& <1\,.
 \end{align*}
-This value is $\Theta(1)$ if $t\ge 3+ (\gamma-1)/\log | \mathbb{F}|$.
-\bnote{ I feel like this analysis can be tightened up.
-Saying that $\log (|\mathbb{F}| -1 ) \ge \log (|\mathbb{F}|)-1$ seems like a big loss.}
+\lnote{need for \lemref{lem:log-minus-one}:  $\gamma-1\le |F|$ and $|F|\ge 4$}
+\lnote{change the any needed theorem statements it affects in light of the tightening}
+
+\lnote{this lemma should probably live elsewhere since it is also needed for the FE case}
+\begin{lemma}
+\label{lem:log-minus-one}
+For any real numbers $\alpha \leq \beta$ with $\beta \ge e+1$ (in particular, $b\ge 4$ suffices), the following holds:
+$\alpha \log (\beta-1) > (\alpha-1)\log \beta$. 
+\end{lemma}
+
+\begin{proof}
+Because $\beta-1$ is positive, and $1+x<e^x$ for positive $x$,
+$$1+\frac{1}{\beta-1} < e^{\frac{1}{\beta -1}}\,.$$  Therefore, 
+$$\left(1+\frac{1}{\beta-1}\right)^{\alpha-1} < e^{\frac{\alpha-1}{\beta-1}}\le e < \beta-1$$ (since $\alpha\le \beta$). Multiplying both sides by $(\beta-1)^{\alpha-1}$, we obtain
+$$\beta^{\alpha-1} < (\beta-1)^\alpha\,.$$
+Taking the logarithm of both sides, we get the desired result.
+\end{proof}
+
  \end{proof}

### 2014-09-29 trunk/info-bounds/FuzzyExtPossibility.tex
small changes to fuzzy extractor proof

@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 3 + (\gamma-1) / \log |\mathbb{F}|$.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
 \end{theorem}
@@
 \item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-\item $t\ge 3 + (\gamma-1)/\log |\mathbb{F}|$,
+\item $t\ge 4$,
 \item and $\epsilon + t\delta < 1/16$,
@@
 This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
-Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = n^{1/5}$.
+Thus, $\Hfuzz(W) = \Hoo(W)= n^{1/5}$.
 \end{proof}
@@
 \begin{proof}
-Recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
 By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
@@
 
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}$.
+Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}\leq 2^{1/2}$.
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
@@
 \end{align*}
-
+\bnote{we can push this to $t=n^{2/3+\Theta(1)}$.  Need $t = n^c$ for $2c-1>1/3$ for the second part to go through}
 % That is, We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
@@
  \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n-\theta(\nu))}}{2^v} = n -\Theta(\nu).
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} >\log  \frac{(2^{n/\nu})^{\nu-2}}{2^{\nu}}  \log \frac{2^{(n-2\nu))}}{2^\nu} = n -3\nu.
  \]
- \bnote{need to come back to why this is true}
+ where the inequality follows by \lemref{lem:log-minus-one}.
 Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
@@
 \begin{align*}
-\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-n^{1/3}}|R_{small}|}{2^{n - \theta(\nu)}}\\
-&=\frac{|R_{small}|}{2^{n^{1/3}-\Theta(n^{1/5})}}.
+\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-n^{1/3}}|R_{small}|}{2^{n - 3\nu}}\\
+&=\frac{|R_{small}|}{2^{n^{1/3}-3n^{1/5}}}.
 \end{align*}
-Thus, at most $1/2^{n^{1/3}- \Theta(n^{1/5})}$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $z$.  We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
+Thus, at most $1/2^{n^{1/3}- 3n^{1/5}} = \Theta(2^{-n^{1/3}})$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
+We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
 \begin{enumerate}
@@
 %\item If $x\not \in R_{small}$ output random bit $b$.
-\item Compute $V|P=p^* \wedge Z=z$. 
+\item Compute $V|P=p^* \wedge Z=z$ and $Q_{p^*, x}$. 
 \item If $(Q_{p^*, x} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
@@
 \end{align*}
-Where the last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
+The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
 %We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 

### 2014-09-30 trunk/constantRate/ConstCompFuzzExt-reorg.tex
minor rewording of abstract/intro

@@
 \begin{abstract}
-\lnote{needs work}
-Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).
-In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns.
-For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.
-Unfortunately, it is impossible to provide security for every source with this property.
-Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.
-
-Fortunately, practical sources contain useful structure.
-In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.
-We show an information-theoretic construction and two computational constructions with added features.  Our constructions are for the Hamming metric over symbols of an alphabet.
-
-\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of Hamming errors over a super-constant size alphabet.
+Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
+To eliminate noise, they require an initial enrollment phase that takes the first noisy reading of the secret and produces a nonsecret helper string to be used in subsequent readings.
+This helper string reduces  the entropy of the original secret---in the worst case, by as much as the logarithm of the number of tolerated error patterns.
+For many practical sources of secrets, reliability demands that the number of tolerated error patterns is large, making this loss greater than the original entropy of the secret.
+We say that such sources have \emph{more errors than entropy}.
+Most known approaches for building fuzzy extractors cannot be used for such sources.
+
+%\emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
+% remain secure even when the initial enrollment phase is repeated multiple times on correlated readings, producing multiple helper strings.
+Prior approaches to building reusable fuzzy extractors severely restricted allowed correlations among initial enrollment readings.
+%   
+%We provide constructions of fuzzy extractors for large classes of sources with more errors than entropy.
+We also construct the first reusable fuzzy extractors that has no restrictions on correlations among multiple readings of the source.
+Our constructions exploit the structural properties of a source in addition to its entropy guarantees.
+One is information-theoretic; the other two rely computational assumptions.
+They differ in the types of sources they support.
+
+We provide constructions of fuzzy extractors for large classes of sources with more errors than entropy.
+Our constructions exploit the structural properties of a source in addition to its entropy guarantees.
+Some are made possible by relaxing the security requirement from information-theoretic to computational.
+
+%One is information-theoretic; the other two rely computational assumptions. They differ in the types of sources they support.
+
+\emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
+ remain secure even when the initial enrollment phase is repeated multiple times with the same or correlated secrets, producing multiple helper strings.
+By relying on computational security, we construct the first reusable fuzzy extractors that make no assumption about how multiple readings of the source are correlated.
+
+\iffalse
+
+We construct fuzzy extractors for large classes of such sources by exploiting  their structural properties in addition to their entropy guarantees.  
+We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric over a nonbinary alphabet.
+
+The information-theoretic construction supports sources in which most symbols contributes fresh entropy.
+The first computational construction has the additional feature of \emph{reusability}~(Boyen, CCS 2004), allowing multiple correlated
+
+\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of errors over a super constant size alphabet.
 
@@
 Cryptography relies on long-term secrets for key derivation and authentication.
-However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
+However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings.
+Prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
 physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
-and quantum information~\cite{bennett1988privacy}).
+and quantum information~\cite{bennett1988privacy}.
 Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
 Both of these problems have interactive and non-interactive versions.
-In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
- A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.
+In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple noisy readings of a secret at different times.
+ A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined in~\cite{DBLP:journals/siamcomp/DodisORS08}.
 
@@
 \begin{table}
-\begin{tabular}{l l l c c}
+\begin{center}
+\begin{tabular}{l l l l l}
  & Security & Source Structure & Error-Tolerance & Alphabet Size\\
 \hline
-\consref{cons:info theoretic} & Info-theoretic  & Partial block source& $\Theta(\gamma)$ & $\omega(1)$ \\
-\consref{cons:sampling} & Reusable Computational & Partial block source& $o(\gamma)$ & $\omega(1)$ \\
-\consref{cons:first construction} & Computational & Unguessable block source & $\Theta(\gamma)$ & $n^{\omega(1)}$
+Cons. \ref{cons:info theoretic} & Not reusable  & Most symbols  & Constant fraction & Super constant \\
+&  Info-theoretic & contribute entropy & &\\\hline
+Cons. \ref{cons:sampling} & Reusable & Most symbols & Sub constant fraction & Super constant \\
+& Computational & contribute entropy & &\\\hline
+Cons. \ref{cons:first construction} & Not reusable & Symbols correlated  & Constant fraction & Super polynomial\\
+&  Computational & but hard to guess && 
 \end{tabular}
-\caption{Summary of new constructions.
-All constructions support families of distributions with more errors than entropy.
-Partial blocks sources are defined in \defref{def:partial source} and unguessable block sources are defined in \defref{def:block guessable}.}
+\end{center}
+%end centering
+\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
 \label{tab:upper bounds}
@@
 Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
-The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  The obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
+The construction of Bitansky et al.
+is based on multilinear encoding and is  highly impractical.
+Our constructions use obfuscated digital lockers.
+Obfuscated digital lockers are instantiable under significantly weaker assumptions and can be implemented quite efficiently.
+\bnote{we need to say we are weaker than general obfuscation.  happy with this? merged with sentence from above}
 Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.
@@
 Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$.
+Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $j=1,..., q$:
 \begin{itemize}%[leftmargin=-.6in]
-\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
+\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1, u\leftarrow \zo^\kappa$.
 \item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.
@@
 \begin{align*}
-\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
+\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{j-1}, r_j, r_{j+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{j-1}, u, r_{j+1},..., r_q, p_1,..., p_q)=1].
 \end{align*}
-where $u$ is a uniformly random string.
 \end{itemize}
-$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
+$(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
 \end{definition}
@@
 \begin{definition}
-Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
-In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the implicit distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
+Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$.
+In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
 \end{definition}
@@
 In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.
-The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.
+The structure of a partial block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
+We assume that $\Hoo(W) = \Theta(\gamma)$.
 The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.
-This means that the input entropy to the fuzzy extractor is $\Theta(\gamma)$.
+This means that the input entropy to $(\gen', \rep')$ is $\Theta(\gamma)$.
 We assume that the new alphabet $\mathcal{Y}$ is of constant size.
@@
 \[
-\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) < t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
+\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
 \]
 That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.
-We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
+
+\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
 However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.
+
+In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.
+However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability.
+For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.
 
@@
 This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.
 
 Before presenting the construction we provide some definitions from error correcting codes.
-We use slightly nonstandard error-correct codes over $\{0,1\}^\gamma$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
 Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).

### 2014-09-30 trunk/info-bounds/FuzzyExtPossibility.tex
reorganizing and cleaning up proof

@@
 
-\paragraph{Our Contribution} We first consider the \emph{distribution-aware} setting.
+\paragraph{Positive Results} We first consider the \emph{distribution-aware} setting.
 We show for a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
@@
 
+\paragraph{Negative Results}
 We then show the situation is worse in the distribution-oblivious setting.
 We show that distributional uncertainty is a real drawback to providing security.
-We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).
+We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
+This result is quite strong, it requires the secure sketch to correct only a constant number of errors and allows the secure sketch to be wrong almost a quarter of the time.
+
 Using a result of Fuller et al.~\cite{fuller2013computational}, this negative result extends to versions of secure sketches ensure $w$ has  pseudoentropy~(\corref{cor:extension to fuzz ext}).
@@
 Unpredictability is weaker than pseudoentropy and converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-This negative result is quite strong, it allows the secure sketch to be wrong a $1/4$ of the time and requires the secure sketch to correct a sub constant fraction of errors.
-
-\bnote{add a paragraph here about the negative result for fuzzy extractors}
-\bnote{add a paragraph talking about the computational setting}
+
+We then show a similar result to fuzzy extractors.
+We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
+\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
+(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
+Furthermore, the result only applies for fuzzy extractors with perfect correctness.
+Many but not all fuzzy extractors have perfect correctness.
+
+Computational fuzzy extractors offer more hope for avoiding the impossibility result.
+Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
 %The situation is significantly more complicated for distribution-oblivious algorithms.
@@
 
-\paragraph{Our approach} \bnote{say something about our methods.  leveled hashing, distributional uncertainty?}
+\paragraph{Our approach} \bnote{say something about our methods?}
 \begin{table}
@@
 \end{center}
-\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  All results are information-theoretic.}
+\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
 \label{tab:main results}
@@
 In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
-Finally, in \secref{sec:dist oblivious} we provide negative results for the distribution-oblivious setting.
+In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
 
@@
 For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
-We will also use an average case version of this notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
+We will also use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
 \begin{definition}[Conditional Hartley Entropy]
@@
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
+%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
 We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
 \bnote{there is nothing computational here right now}
-
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
@@
 
-Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.
-\bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.
+\noindent
+Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.
 The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
@@
 
-\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
+\noindent \textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
 
@@
 
-\subsection{A necessary condition for security}
+\subsection{Fuzzy min-entropy: necessary for security}
 \label{sec:minimal conditions}
@@
 \label{sec:distribution aware}
-In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors) whenever $\Hfuzz(W)= \omega(\log n)$.
-We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.
-We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.
-In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.
+In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors using \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
+We first consider distributions where points are far apart, distributions where all points have the same probability, and finally arbitrary distributions.
 
@@
 
-\begin{table}
-\begin{centering}
-\begin{tabular}{l | l}
-Class of Distribution & Residual entropy achieved by construction\\
-\hline
-Well-spread distribution & $\Hfuzz(W)$ \\
-Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
-Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
-\end{tabular}
-\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.
+%\begin{table}
+%\begin{centering}
+%\begin{tabular}{l | l}
+%Class of Distribution & Residual entropy achieved by construction\\
+%\hline
+%Well-spread distribution & $\Hfuzz(W)$ \\
+%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
+%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
+%\end{tabular}
+%\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.
 Here $\delta$ denotes the probability of incorrect reconstruction and $\mathcal{M}$ is the metric space.
 Recall that $\Hfuzz(W)$ is an upper bound for the residual entropy.}
-\label{tab:upper bounds}
-\end{centering}
-\end{table}
+%\label{tab:upper bounds}
+%\end{centering}
+%\end{table}
+%\bnote{I'm not convinced this table is useful}
 %We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
@@
 \begin{lemma}
-\label{lem:flat hashing}
+\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
 Let $W$ be a flat distributions with min-entropy $m$.  Then
@@
 \end{lemma}
-\begin{proof}
-We first argue security.
-Fix some $W\in\mathcal{W}$.
-Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
-Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.
-
-We now argue correctness.
-Fix some $w, w'$.
-Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
-Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
-\begin{align*}
-\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
-\end{align*}
-Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.
-This completes the proof.
-\end{proof}
 \begin{corollary}
@@
 
-Note that \consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
-\[
-\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
-\]
+\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
+$
+\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n).
+$
+
 For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
 The achievable security is proportional to the starting entropy minus the largest number of points in any ball.
-Whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
-%That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.
-Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.
-For a flat distribution, this is also the ball with the largest total weight.
-We will see this becomes more difficult as we move to the setting where points have very different probability.
-%In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls.
-We will compensate for this problem by writing down a variable number of bits.
-%with a fixed number of neighbors, 
-%\begin{align*}
-%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
-%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
-%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
-%\end{align*}
-%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.
+Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
 
@@
 
-Dealing with non-flat distributions requires a new strategy.
-Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.
+Dealing with non-flat distributions requires a new strategy. % The fuzzy extractor must be aware of the density of the current ball.  
 Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.
@@
 Going forward we will consider specific metric spaces, namely the Hamming metric.
-\section{Impossibility of Distribution-Oblivious Secure Sketches}
+\section{Impossibility of $\Hfuzz$ for Distribution-Oblivious Secure Sketches}
 \label{sec:dist oblivious}
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.
 \end{theorem}
@@
 \item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.
-That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
+That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
+\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious secure sketch for the elements of $V$.
 \end{itemize}
@@
 \section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
-In the previous section, we showed a family of distributions that does not admit a secure sketch.
-In this section, we extend this result to fuzzy extractors.
-This result has significantly weaker parameters than the previous result but still demonstrates hard.
-\bnote{write this}
-
-We begin with the case of perfect correctness in the Hamming metric.
+\label{sec:imposs fuzz ext}
+In the previous section, we showed a family of distributions that does not admit a secure sketch.  We extend this result to fuzzy extractors.
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \Theta(2^{n^{1/3}})$ for $t = \Theta(n^{4/5})$.
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
 \end{theorem}
-\begin{proof}
+
+\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.
+The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
+Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
+Obtaining weaker parameters for impossibility of fuzzy extractors makes sense.
+\begin{proof}[Proof Outline]
 Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.
-In particular, we need to assume a larger error tolerance $t=n^{4/5}$.
+In particular, we need to assume a larger error tolerance.
+Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.
+Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
 This family is closely related to the family we constructed in \thref{thm:imposs sketch}.
 However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.
-Let $\nu = n/t = n^{1/5}$.
 For convenience we assume that $\nu\in\mathbb{Z}^+$.
@@
 
-The proof uses the same basic outline as the previous result.  However, we work over the binary space to exploit the isoperimetric inequality on Hamming space.
+We now present an outline for the remainder of the proof~(proofs in \apref{sec:fuzz ext proof}):
 \begin{itemize}
-\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item The distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
+\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
+\item \lemref{lem:fuzz can't get key}: for many values of $Z$, for a large fraction of keys, there are no viable $v\in\mathcal{M}$.  Specifically:
+\begin{itemize}
 \item Show that for half the keys have a bounded number of pre images in the metric space.
@@
 \item For most values of possible $Z$, the intersection between the viable pre images of $V|P \wedge Z$ and the viable pre images of $R_{small}$ is empty.
-Thus, the output of the fuzzy extractor can be distinguished from uniform.
+Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
 \end{itemize}
-
-\begin{proposition} 
-For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
-\end{proposition}
-\begin{proof}
-Consider some fixed $W\in\mathcal{V}$.
-The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =n^{1/5}$.
-Recall that $t= n/\nu$.
-We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
-Fix some $w, w'\in W$.
-Denote by $x, x'$ the values that produce $w, w'$ respectively.
-Clearly, $x\neq x'$.
-Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
-This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
-Thus, $\Hfuzz(W) = \Hoo(W)= n^{1/5}$.
+\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious fuzzy extractor for the elements of $V$.
+\end{itemize}
+
 \end{proof}
 
-\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
-\end{proposition}
-\begin{proof}
-Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
-The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
-\end{proof}
-
-We now proceed to showing the technical portion of the theorem.
-We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
-Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
-
-\begin{lemma}
-Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 1$.
-There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\Theta(2^{-n^{1/3}})$.
-\end{lemma}
-\begin{proof}
-We assume that $\rep$ is deterministic in our analysis.
-Any randomness necessary for the \rep algorithm can be provided by $\gen$.
-We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(R, P) \leftarrow \gen(V)$.
-
-%By the definition of correctness for $(\sketch, \rec)$, 
-%\[
-%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
-%\]
-%For most $p$, $\rec$ works on most neighbors of $w$.  
-%Fix some $w$.  
-By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
-\[
-(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
-\]
-%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
-
-Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
-The distribution $R|P=p^*$ is the set of possible keys.
-The distribution $R|P=p^*$ induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
-Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
-
-Many of these sets must be small.
-That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
-
-For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
-We first define the interior of a set:%Define two sets, called the interior and crust respectively: \bnote{change term crust?}
-\begin{align*}
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
-%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
-\end{align*}
-
-%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient sphere:
-\begin{definition}
-A set $S$ is a $\beta$-deficient ball if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
-\end{definition}
-
-We now proceed to show that the interior of each $Q_{p^*, r^*}$ is small~(using the isoperimetric inequality on the Hamming space):
-%Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
-
-\begin{lemma}
-$|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.
-\end{lemma}
-\begin{proof}
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, r^*}$).
-We now find the size of $S_{p^*, r^*}$.
-
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}\leq 2^{1/2}$.
-Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
-This means that $|S_{p^*, r^*}|$ is a deficient sphere of radius at most $n/2-t$.
-Let $X$ denote a uniform string on $\zo^n$.
-We use Hoeffding's inequality~\cite{hoeffding1963probability}:
-
-\begin{align*}
-|S_{p^*, r^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-n^{3/5}} \le 2^{n - n^{3/5}}
-\end{align*}
-\bnote{we can push this to $t=n^{2/3+\Theta(1)}$.  Need $t = n^c$ for $2c-1>1/3$ for the second part to go through}
-% That is, We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
-That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
-Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
-do better}.
-Thus,
-%\[n-(\kappa-1) \ge d (\log n - \log d).\]  
-%We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.  
-%
-%Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
-That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
-This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
-That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
-And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
-This is a radius of almost $n$}
-\end{proof}
-
-We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.  %Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
-To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.  
-Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^t-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
- As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
-We know show there are many possible values for $Z |P=p^*$.
-The only information about $Z$ is contained in the point  $V=v$.
-The length of this point is $2^n$.
-Conditioned on this information there are still many possible values for $Z$.
-That is,
- \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} >\log  \frac{(2^{n/\nu})^{\nu-2}}{2^{\nu}}  \log \frac{2^{(n-2\nu))}}{2^\nu} = n -3\nu.
- \]
- where the inequality follows by \lemref{lem:log-minus-one}.
-Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
-
-This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, r^*}$~(other than $v$) and these values are disjoint.
-The optimum strategy is to include these values uniformly from different $Z$ values.
-Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
-Note that $Q_{small} \le 2^{n-n^{1/3}}|R_{small}|$.
-That is, 
-\begin{align*}
-\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-n^{1/3}}|R_{small}|}{2^{n - 3\nu}}\\
-&=\frac{|R_{small}|}{2^{n^{1/3}-3n^{1/5}}}.
-\end{align*}
-Thus, at most $1/2^{n^{1/3}- 3n^{1/5}} = \Theta(2^{-n^{1/3}})$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
-We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
-\begin{enumerate}
-\item On input $x, z$.
-%\item If $x\not \in R_{small}$ output random bit $b$.
-\item Compute $V|P=p^* \wedge Z=z$ and $Q_{p^*, x}$. 
-\item If $(Q_{p^*, x} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
-\item Else output $b=1$.
-\end{enumerate}
-
-The distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
-\begin{align*}
-\Pr[D(R, P, Z) = 1] &- \Pr[D(U, P, Z) =1]=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/2- \Theta(2^{-n^{1/3}})\right) = 1/4-\Theta(2^{-n^{1/3}}).
-\end{align*}
-The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
-%We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
-%We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
-%\begin{align*}
-%\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
-%&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
-%%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
-%\end{align*}
-%\bnote{the two combinatorial bounds we are using aren't good enough}
-%To show that $\epsilon \ge 1/2$ we have that 
-%%\begin{align*}
-%%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
-%%\end{align*}
-%\bnote{why was that sufficient to break security}
-%\bnote{still working this isn't complete}
-\end{proof}
-\end{proof}
-
+\noindent
 \textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.
-This result presents a contrast between what is possible for sketches and fuzzy extraction.
+Their construction does not contradict our result because the construction is computationally secure.
+(Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)
 
@@
 \]
+\end{proof}
+
+\subsection{Proof of \lemref{lem:flat hashing}}
+\label{sec:proof of flat hashing}
+\begin{proof}
+We first argue security.
+Fix some $W\in\mathcal{W}$.
+Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
+Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.
+
+We now argue correctness.
+Fix some $w, w'$.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
+Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
+\begin{align*}
+\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
+\end{align*}
+Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.
+This completes the proof.
 \end{proof}
@@
 \lnote{this lemma should probably live elsewhere since it is also needed for the FE case}
+\bnote{fine with it being here as the FE case lives in the appendix too}
 \begin{lemma}
@@
 \noindent \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
+
+\section{Proof of \thref{thm:imposs fuzz ext}}
+\label{sec:fuzz ext proof}
+\begin{proposition} 
+\label{prop:dist fuzzy ent fuzz}
+For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\end{proposition}
+\begin{proof}
+Consider some fixed $W\in\mathcal{V}$.
+The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.
+Recall that $t=o (n/\nu)$.
+We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Fix some $w, w'\in W$.
+Denote by $x, x'$ the values that produce $w, w'$ respectively.
+Clearly, $x\neq x'$.
+Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
+This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
+Thus, $\Hfuzz(W) = \Hoo(W)= \omega(\log n)$.
+\end{proof}
+
+\begin{proposition}\label{prop:dist uniform fuzz}
+$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
+\end{proposition}
+\begin{proof}
+Consider some $w\in V$.
+Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
+\end{proof}
+
+The previous two propositions were similar to the secure sketch case.
+The remainder of the proof is significantly different.
+We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
+Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
+
+\begin{lemma}
+\label{lem:fuzz can't get key}
+Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 1$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\ngl(n)$.
+\end{lemma}
+\begin{proof}
+We assume that $\rep$ is deterministic in our analysis.
+Any randomness necessary for the \rep algorithm can be provided by $\gen$.
+We do not consider these coins in our security analysis~(and thus, they can be considered private).
+Denote by $(R, P) \leftarrow \gen(V)$.
+
+%By the definition of correctness for $(\sketch, \rec)$, 
+%\[
+%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
+%\]
+%For most $p$, $\rec$ works on most neighbors of $w$.  
+%Fix some $w$.  
+By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
+\[
+(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+\]
+%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+
+Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
+The distribution $R|P=p^*$ is the set of possible keys.
+The distribution $R|P=p^*$ induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
+Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
+
+Many of these sets must be small.
+That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
+If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
+
+For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
+We first define the interior of a set:%Define two sets, called the interior and crust respectively: \bnote{change term crust?}
+\begin{align*}
+\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
+%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
+\end{align*}
+
+%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
+We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient sphere:
+\begin{definition}
+A set $S$ is a $\beta$-deficient ball if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
+\end{definition}
+
+We now proceed to show that the interior of each $Q_{p^*, r^*}$ is small~(using the isoperimetric inequality on the Hamming space):
+%Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+
+\begin{lemma}
+$|\inter(Q_{p^*, r^*})| \le 2^{n-4\nu}$.
+\end{lemma}
+\begin{proof}
+By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, r^*}$).
+We now find the size of $S_{p^*, r^*}$.
+
+Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}\leq |\mathcal{M}|/2$.
+Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
+This means that $|S_{p^*, r^*}|$ is a deficient sphere of radius at most $n/2-t$.
+Let $X$ denote a uniform string on $\zo^n$.
+We use Hoeffding's inequality~\cite{hoeffding1963probability}:
+
+\begin{align*}
+|S_{p^*, r^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}
+\end{align*}
+% That is, We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
+That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
+Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
+do better}.
+Thus,
+%\[n-(\kappa-1) \ge d (\log n - \log d).\]  
+%We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.  
+%
+%Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
+That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
+This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
+That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
+And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
+This is a radius of almost $n$}
+\end{proof}
+
+We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-4\nu}$.  %Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
+To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.  
+Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^t-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
+ As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
+We know show there are many possible values for $Z |P=p^*$.
+The only information about $Z$ is contained in the point  $V=v$.
+The length of this point is $2^n$.
+Conditioned on this information there are still many possible values for $Z$.
+That is,
+ \[
+ \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} >\log  \frac{(2^{n/\nu})^{\nu-2}}{2^{\nu}}  \log \frac{2^{(n-2\nu))}}{2^\nu} = n -3\nu.
+ \]
+ where the inequality follows by \lemref{lem:log-minus-one}.
+Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, r^*}$~(other than $v$) and these values are disjoint.
+The optimum strategy is to include these values uniformly from different $Z$ values.
+Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
+Note that $Q_{small} \le 2^{n-n^{1/3}}|R_{small}|$.
+That is, 
+\begin{align*}
+\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}\\
+&=\frac{|R_{small}|}{2^{\nu}}.
+\end{align*}
+Thus, at most $1/2^{\nu} = \ngl(n)$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
+We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
+\begin{enumerate}
+\item On input $x, z$.
+%\item If $x\not \in R_{small}$ output random bit $b$.
+\item Compute $V|P=p^* \wedge Z=z$ and $Q_{p^*, x}$. 
+\item If $(Q_{p^*, x} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
+\item Else output $b=1$.
+\end{enumerate}
+
+The distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
+\begin{align*}
+\Pr[D(R, P, Z) = 1] &- \Pr[D(U, P, Z) =1]=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
+&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/2-\ngl(n)\right) = 1/4-\ngl(n).
+\end{align*}
+The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
+%We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
+%We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
+%\begin{align*}
+%\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
+%&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
+%%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
+%%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
+%\end{align*}
+%\bnote{the two combinatorial bounds we are using aren't good enough}
+%To show that $\epsilon \ge 1/2$ we have that 
+%%\begin{align*}
+%%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
+%%\end{align*}
+%\bnote{why was that sufficient to break security}
+%\bnote{still working this isn't complete}
+
+This completes the proof of \lemref{lem:fuzz can't get key}.
+\end{proof}
 

### 2014-10-01 trunk/constantRate/ConstCompFuzzExt-reorg.tex
added Ran's acks and fixed first sent of intro

@@
 %\documentclass{llncs}
-\def\shownotes{1}
+\def\shownotes{0}
 \def\blinded{0}
@@
 Cryptography relies on long-term secrets for key derivation and authentication.
-However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings.
+However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values of the secret at repeated readings.
 Prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
@@
 The definition is parameterized by $f_2,..., f_q$.
-This adversary implicitly defines distributions $W_2,..., W_q$~(which depend on $W_1$ and the public values $P_1,...
+This adversary implicitly defines distributions $W_2,..., W_q$ (which depend on $W_1$ and the public values $P_1,...
 P_i$).
@@
 
-This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, 1218461, and 1422965.
+Ran Canetti is supported by the NSF MACS project, an NSF Algorithmic foundations grant 1218461, the Check Point Institute for Information Security, and  ISF grant 1523/14.
 Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.
-The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002.
+The work of Benjamin Fuller is sponsored in part by US NSF grants 1012910 and 1012798 and  the United States Air Force under Air Force Contract FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
+Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.
 }

### 2014-10-01 trunk/info-bounds/FuzzyExtPossibility.tex
working on introduction

@@
 \author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
-%The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.
+The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.
 Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.
@@
 \begin{abstract}
-We characterize when deriving a stable key from a noisy source is possible.
-We use the notation of fuzzy extractors introduced by Dodis et al.
-(Eurocrypt 2004).
-The goal is to produce a strong $key$ from a $w$ drawn from a \emph{strong} distribution $W$ and to produce the same when given a nearby $w'$.
-A fuzzy extractor is split into two algorithms $\gen$ which produces $key$ along with some helper information $p$ and $\rep$ which takes $w'$ and $p$ to reproduce $key$.
-The key must remain strong in the presence of $p$.
-The goal is to produce the correct key whenever $\dis(w, w')\le t$.
-\anote{there is a big gap between theory and the needs of practice}
-
-We identify a key quantity of a distribution called \emph{fuzzy min-entropy}.
-Fuzzy min-entropy measures the maximum probability mass of a distribution that lies within a ball of radius $t$ in the metric space.
-Ideally, key derivation should be possible whenever a distribution has fuzzy min-entropy.
+Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
+To help eliminate noise, they produce a non secret helper string.
+This helper value allows the key to be regenerated from a nearby point.
+Known constructions of fuzzy extractors do not provide security for most noisy distributions that occur in practice.
+
+The nonsecret helper string allows an adversary to learn the generated key if they can guess a point close to the original reading.
+A necessary condition to derive keys from a distribution is that no adversary can guess nearby points.
+We call this condition \emph{fuzzy min-entropy}.
 In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Current techniques for constructing fuzzy extractors lie far from this necessary condition.
-We investigate whether this is inherent for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).
-Our constructions and impossibility results are information-theoretic.
-
-We consider two types of fuzzy extractors and secure sketches.
-The first we call \emph{distribution-aware}, the algorithms know the precise distribution they are trying to correct.
-The second is \emph{distribution-oblivious} where $(\gen, \rep)$ must work for a family of distributions.
-
-\textbf{Distribution-Aware} Whenever the fuzzy min-entropy is super-logarithmic, there exists a distribution-aware secure sketch and fuzzy extractor with super-logarithmic output entropy.
-That is, fuzzy min-entropy is both a necessary and \emph{sufficient} condition for security in this setting.
-
-\textbf{Distribution-Oblivious} The distribution-oblivious situation is more complicated.
-Indeed, there is a significant difference between secure sketches and fuzzy extractors.
-We show that there exist families of distributions where each distribution has fuzzy min-entropy such that any secure sketch is insecure.
-However, it is possible to build a fuzzy extractor for these same family of distributions.
-\bnote{come back to this.}
+In this work, we ask whether fuzzy min-entropy is a sufficient condition for security in the fuzzy extractor setting.
+
+A key impediment to providing security is distributional uncertainty.
+We consider two settings, first where the fuzzy extractor knows the precise distribution and second the fuzzy extractor knows the distribution comes from some family.
+We show that fuzzy min-entropy is a sufficient condition in the first setting and insufficient in the second setting.
+That is, there is families of distributions with fuzzy min-entropy that no fuzzy extractor can derive keys from.
+Our results are information-theoretic.
+
+\bnote{keep editing}
 \end{abstract}
@@
 \section{Introduction}
-\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
 \anote{should our results be seen as justifying the distribution specific approach?}
@@
 Traditionally, this secret is assumed to have high min-entropy.
-However, many sources with sufficient entropy for authentication present an additional problem: noise.
+However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
 That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.
@@
 A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.
-Consider a particular high entropy distribution $W$.
-Our goal is to derive stable keys from $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
-A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes the initial reading $w$ and produces $key$ along with a public helper value $p$.
+%Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
+A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.
 The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.
-The $key$ should hold even if an adversary has observed $p$~(the problem is trivial if $p$ is private).
+The $key$ should be uniform even if an adversary has observed $p$.
 The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.
-
-Traditionally, fuzzy extractors are constructed by using a separate information-reconciliation component, known as a secure sketch, that maps $w'$ back to $w$ and a privacy-amplification component, a strong randomness extractor~\cite{nisan1993randomness}, that maps $w$ to a random key.
-A secure sketch consists of a pair of algorithms $\sketch$ takes $w$ and produces a public value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-The security losses incurred in information-reconciliation~(performed in secure sketches and fuzzy extractors) are larger than losses in privacy amplification.\bnote{should say something here about our understanding of privacy amplification and that extractors are necessary and sufficient} In the following discussion we describe limitations on fuzzy extractors.
-This discussion applies to secure sketches as well.
-\bnote{should say you don't have to build secure sketches}
-
-Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed and the remainder of the distribution is unknown 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-Usually fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
+For any security the initial readings must come from a high min-entropy distribution $W$.
+
+Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
+The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
+We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
+Known constructions of fuzzy extractors and secure sketches incur significant losses.
+In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.
+In this work, we ask whether this is inherent.
+We identify a key problem: uncertainty in the distribution of $W$.
 
@@
 The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
-This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}
+This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.
 
 \paragraph{The price of distributional uncertainty}
-As described above, fuzzy extractors are usually built for a family of distributions $\mathcal{W}$.
-This strengthens the security guarantees: security holds as long as $W\in\mathcal{W}$.
+Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
+Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
+
 In this work, we show that this uncertainty comes at a significant cost.
-We consider two settings, first where the algorithms $\gen, \rep$ know the entire probability mass function of the distribution $W$.
-We call this setting \emph{distribution aware}.\bnote{prior works on this setting}  The more traditional setting where security holds for a family of distributions $\mathcal{W}$ we call \emph{distribution-oblivious}.
+We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.
+We call this setting \emph{distribution aware}.
+Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.
+To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
+\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
 
@@
 
-\paragraph{Positive Results} We first consider the \emph{distribution-aware} setting.
-We show for a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
-In this work, we consider this minimal goal of a super-logarithmic length key.
-If we require a longer output length this increases the requirement on fuzzy min-entropy.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Our constructions are primarily feasibility results and do not run in polynomial time.
+\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.  
+We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
+Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
+In this work, we assume the goal is to produce a super-logarithmic length key.
+In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+Our constructions are feasibility results and do not run in polynomial time.
 In the distribution-aware setting this seems necessary as most distributions have exponential description size.
@@
 \paragraph{Negative Results}
-We then show the situation is worse in the distribution-oblivious setting.
-We show that distributional uncertainty is a real drawback to providing security.
+The situation is very different in the distribution-oblivious setting.
 We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
-This result is quite strong, it requires the secure sketch to correct only a constant number of errors and allows the secure sketch to be wrong almost a quarter of the time.
-
-Using a result of Fuller et al.~\cite{fuller2013computational}, this negative result extends to versions of secure sketches ensure $w$ has  pseudoentropy~(\corref{cor:extension to fuzz ext}).
-Under very strong assumptions, computational secure sketches that provide unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Unpredictability is weaker than pseudoentropy and converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
 
@@
 
+Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
+Intuitively, this should be the easiest type of family to perform information-reconciliation.
+In the distribution-aware setting, information-reconciliation requires no information.
+
+\paragraph{Computational security?}
+Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
+Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Semantically secure multi-linear encodings are a very strong assumption and unpredictability is weaker than pseudoentropy.
+Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+
 Computational fuzzy extractors offer more hope for avoiding the impossibility result.
@@
 Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
-%The situation is significantly more complicated for distribution-oblivious algorithms.
-Indeed, we show a natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.
-However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.
+
+\bnote{compare this with universal decoding?}
 
@@
 
-\subsection{Fuzzy min-entropy: necessary for security}
+\subsection{Fuzzy min-entropy: a necessary condition}
 \label{sec:minimal conditions}

### 2014-10-01 trunk/info-bounds/FuzzyExtPossibility.tex
working on our approach

@@
 We ask the question for secure sketches and fuzzy extractors.
-
-%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
-However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
-Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
-As long as the distribution falls in this class, security and correctness hold.
-
-%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
-We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
-We call this setting \emph{distribution-oblivious}.
-In the second, we allow the algorithms complete knowledge of the distribution.
-We call this setting \emph{distribution-aware}.
-
-%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
-We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
-
-\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.  
-We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
-In this work, we assume the goal is to produce a super-logarithmic length key.
-In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Our constructions are feasibility results and do not run in polynomial time.
-In the distribution-aware setting this seems necessary as most distributions have exponential description size.
-The power of the distribution-aware setting is that the algorithms can access this description.
-It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
-
-\paragraph{Negative Results}
-The situation is very different in the distribution-oblivious setting.
-We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
-This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
-
-We then show a similar result to fuzzy extractors.
-We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
-\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
-(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
-Furthermore, the result only applies for fuzzy extractors with perfect correctness.
-Many but not all fuzzy extractors have perfect correctness.
-
-Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
-Intuitively, this should be the easiest type of family to perform information-reconciliation.
-In the distribution-aware setting, information-reconciliation requires no information.
-
-\paragraph{Computational security?}
-Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
-Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Semantically secure multi-linear encodings are a very strong assumption and unpredictability is weaker than pseudoentropy.
-Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-
-Computational fuzzy extractors offer more hope for avoiding the impossibility result.
-Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
-
-\bnote{compare this with universal decoding?}
-
-\paragraph{Our approach} \bnote{say something about our methods?}
+Our results are information-theoretic, we consider the implications of computational security after discussing our results.
+
 \begin{table}
@@
 \end{table}
+
+%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
+However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
+Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
+As long as the distribution falls in this class, security and correctness hold.
+
+%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
+We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
+We call this setting \emph{distribution-oblivious}.
+In the second, we allow the algorithms complete knowledge of the distribution.
+We call this setting \emph{distribution-aware}.
+
+%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
+We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
+
+\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.  
+We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
+Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
+In this work, we assume the goal is to produce a super-logarithmic length key.
+In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+Our constructions are feasibility results and do not run in polynomial time.
+In the distribution-aware setting this seems necessary as most distributions have exponential description size.
+The power of the distribution-aware setting is that the algorithms can access this description.
+It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
+
+\paragraph{Negative Results}
+The situation is very different in the distribution-oblivious setting.
+We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
+This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
+
+We then show a similar result to fuzzy extractors.
+We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
+\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
+(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
+Furthermore, the result only applies for fuzzy extractors with perfect correctness.
+Many but not all fuzzy extractors have perfect correctness.
+
+Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
+Intuitively, this should be the easiest type of family to perform information-reconciliation.
+In the distribution-aware setting, information-reconciliation requires no information.
+
+\paragraph{Computational security?}
+Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
+Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Semantically secure multi-linear encodings are a very strong assumption and unpredictability is weaker than pseudoentropy.
+Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+
+Computational fuzzy extractors offer more hope for avoiding the impossibility result.
+Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
+
+\bnote{compare this with universal decoding?}
+
+\paragraph{Our approach} Our secure sketch in the distribution aware setting relies on two observations.
+First for distributions where every point has roughly the same probability, the fuzzy min-entropy is determined by the ball with the greatest number of points.
+We call this type of distribution \emph{nearly flat}.
+For nearly flat distributions, the goal is to disambiguate any point within a ball of radius $t$.
+A universal hash with output length larger than the size of this ball suffices.
+However, for an arbitrary distribution, we cannot afford to write down information proportion to the ball with the greatest number of points.
+We solve this problem by converting an arbitrary distribution into a number of nearly flat distributions by writing down the probability of our original reading $w$.
+Then in reconstruction we limit ourselves to points of this probability.
+We then show this probability information is not two helpful.
+We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level~(\consref{cons:leveling}).
+
+Our negative results are in the distribution-oblivious setting.
+A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
+However, $\gen$ does not see the distribution $W$, only the sample $w$.
+In our negative results, we construct a family of distributions $\mathcal{W}$ where conditioned on seeing a single point, the support of the remainder of the distribution is uniform.
+Informally, to provide security $\rep(\cdot, p)$ partitions the metric space.
+Each part of this partition maps a single key.
+We can split each part into interiors and boundaries.
+In the Hamming space, the boundary makes up the overwhelming majority of the space.
+Thus, for most distributions $W$ the support of $W$ lies overwhelmingly in the boundary of these parts.
+All points in the boundary can be effectively excluded, reducing the entropy of $W$
+
+\bnote{I'm writing these, very rough draft}
 

### 2014-10-01 trunk/info-bounds/FuzzyExtPossibility.tex
added a bunch of restructuring suggestions for the intro

@@
 To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.
-
-This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy}.
-They identify two fundamental tasks in noisy key derivation.
+\lnote{Why limit to authentication}
+
+ This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}.
+\lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.
 The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.
@@
 For any security the initial readings must come from a high min-entropy distribution $W$.
+
+\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}
 
@@
 
+\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}
+
 Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
@@
 In the one-message setting, we are far from this ideal.
+\lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''?
+Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}
+
+\lnote{I don't think you want to talk about traditional constructions here yet.
+I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}
 
@@
 \paragraph{The price of distributional uncertainty}
+
+\lnote{I think this should be ``Our Contributions'' and go in the following order.
+Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient.
+On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works.
+We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly).
+We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}
+
+The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)
+
 Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
@@
 \paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.
+\lnote{I think this framing gives positive results too much attention.
+As we discussed on Monday, positive results here aren't what we want to emphasize}
 We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
@@
 
-\paragraph{Computational security?}
+\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
 Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.

### 2014-10-01 info-bounds/FuzzyExtPossibility.tex
working to reorganize introduction

@@
 Traditionally, this secret is assumed to have high min-entropy.
-However, many sources with sufficient entropy for authentication present an additional problem: noise.
+However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
 That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.
 To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.
-
-This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy}.
-They identify two fundamental tasks in noisy key derivation.
+\lnote{Why limit to authentication}
+
+ This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}.
+\lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.
 The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.
@@
 A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.
-Consider a particular high entropy distribution $W$.
-Our goal is to derive stable keys from $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
-A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes the initial reading $w$ and produces $key$ along with a public helper value $p$.
+%Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
+A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.
 The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.
-The $key$ should hold even if an adversary has observed $p$~(the problem is trivial if $p$ is private).
+The $key$ should be uniform even if an adversary has observed $p$.
 The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.
-
-Traditionally, fuzzy extractors are constructed by using a separate information-reconciliation component, known as a secure sketch, that maps $w'$ back to $w$ and a privacy-amplification component, a strong randomness extractor~\cite{nisan1993randomness}, that maps $w$ to a random key.
-A secure sketch consists of a pair of algorithms $\sketch$ takes $w$ and produces a public value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-The security losses incurred in information-reconciliation~(performed in secure sketches and fuzzy extractors) are larger than losses in privacy amplification.\bnote{should say something here about our understanding of privacy amplification and that extractors are necessary and sufficient} In the following discussion we describe limitations on fuzzy extractors.
-This discussion applies to secure sketches as well.
-\bnote{should say you don't have to build secure sketches}
-
-Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed and the remainder of the distribution is unknown 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-Usually fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
+For any security the initial readings must come from a high min-entropy distribution $W$.
 
@@
 A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
+We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?
+
+We have evidence for the sufficiency of fuzzy min-entropy.
+In the interactive setting, fuzzy min-entropy is sufficient for both tasks under mild computational assumptions.
+In the non-interactive setting, semantically secure multi-linear maps allow for strong key derivation.
+We provide evidence it is possible under strong assumptions on the knowledge of $W$.
+Thus, one might hope that  information-theoretic fuzzy extraction is possible for all distributions with fuzzy min-entropy.
+
+\paragraph{Main result}
+Our main result is negative~(\thref{thm:imposs sketch}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.
+Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.
+We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.
+Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).
+
+\paragraph{The cost of distributional uncertainty}
+Fuzzy extractors are designed with limited knowledge of the target distribution.
+Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+
+Our negative results show that when the distribution $W$ is sufficiently unknown, fuzzy extractors are impossible.
+To illustrate that distributional uncertainty is the real problem, we define a restricted form of fuzzy extractor that is allowed to know the exact distribution $W$.
+We call this a \emph{distribution-aware} fuzzy extractor.
+In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).
+
+\paragraph{Information-reconciliation in isolation}
+Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
+The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
+We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
+
+A secure sketch performs non-interactive information-reconciliation.
+We show comparable results for secure sketches.
+That is, there is a family of distributions for which no secure sketch in possible.
+Furthermore, secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}).
+\paragraph{Related Settings}
+We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  We first consider the interactive setting.  
+Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
+In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
+If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
+%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
+Ideally, the server would keep a ``hashed'' value of $w$.
+This is  done for noiseless secrets like passwords.}
+In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is \bnote{what?}
+
+\subsection{Old organization}
+
+\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}
+
+Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
+The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
+We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
+Known constructions of fuzzy extractors and secure sketches incur significant losses.
+In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.
+In this work, we ask whether this is inherent.
+We identify a key problem: uncertainty in the distribution of $W$.
+
+\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
+Fix some distribution $W$.
+The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
+Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
+For security, this must occur with negligible probability.
+That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
+Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
+We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
+A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
+
+\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}
 
@@
 The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
-This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}
+This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.
 
 \paragraph{The price of distributional uncertainty}
-As described above, fuzzy extractors are usually built for a family of distributions $\mathcal{W}$.
-This strengthens the security guarantees: security holds as long as $W\in\mathcal{W}$.
+
+\lnote{I think this should be ``Our Contributions'' and go in the following order.
+Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient.
+On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works.
+We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly).
+We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}
+
+The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)
+
+Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
+Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
+
 In this work, we show that this uncertainty comes at a significant cost.
-We consider two settings, first where the algorithms $\gen, \rep$ know the entire probability mass function of the distribution $W$.
-We call this setting \emph{distribution aware}.\bnote{prior works on this setting}  The more traditional setting where security holds for a family of distributions $\mathcal{W}$ we call \emph{distribution-oblivious}.
+We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.
+We call this setting \emph{distribution aware}.
+Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.
+To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
+\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
 
@@
 We ask the question for secure sketches and fuzzy extractors.
+Our results are information-theoretic, we consider the implications of computational security after discussing our results.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c }
+& Distribution-Oblivious & Distribution-Aware\\
+\hline
+Secure Sketch & No~(\thref{thm:imposs sketch}) & Yes~(\thref{cons:leveling})\\
+\hline
+Fuzzy Extractor & No~(\thref{thm:imposs fuzz ext}) & Yes~(\corref{cor:extension to fuzz ext})
+%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
+%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
+\end{tabular}
+\end{center}
+\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
+\label{tab:main results}
+\end{table}
 
@@
 
-\paragraph{Our Contribution} We first consider the \emph{distribution-aware} setting.
-We show for a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
-In this work, we consider this minimal goal of a super-logarithmic length key.
-If we require a longer output length this increases the requirement on fuzzy min-entropy.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Our constructions are primarily feasibility results and do not run in polynomial time.
+\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.
+\lnote{I think this framing gives positive results too much attention.
+As we discussed on Monday, positive results here aren't what we want to emphasize}
+We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
+Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
+In this work, we assume the goal is to produce a super-logarithmic length key.
+In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+Our constructions are feasibility results and do not run in polynomial time.
 In the distribution-aware setting this seems necessary as most distributions have exponential description size.
@@
 
-We then show the situation is worse in the distribution-oblivious setting.
-We show that distributional uncertainty is a real drawback to providing security.
-We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).
-Using a result of Fuller et al.~\cite{fuller2013computational}, this negative result extends to versions of secure sketches ensure $w$ has  pseudoentropy~(\corref{cor:extension to fuzz ext}).
-Under very strong assumptions, computational secure sketches that provide unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Unpredictability is weaker than pseudoentropy and converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-This negative result is quite strong, it allows the secure sketch to be wrong a $1/4$ of the time and requires the secure sketch to correct a sub constant fraction of errors.
-
-\bnote{add a paragraph here about the negative result for fuzzy extractors}
-\bnote{add a paragraph talking about the computational setting}
-%The situation is significantly more complicated for distribution-oblivious algorithms.
-Indeed, we show a natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.
-However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.
-
-\paragraph{Our approach} \bnote{say something about our methods.  leveled hashing, distributional uncertainty?}
-\begin{table}
-\begin{center}
-\begin{tabular}{c | c | c }
-& Distribution-Aware & Distribution-Oblivious\\
-\hline
-Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
-\hline
-Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})
-%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
-%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
-\end{tabular}
-\end{center}
-\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  All results are information-theoretic.}
-\label{tab:main results}
-\end{table}
+\paragraph{Negative Results}
+The situation is very different in the distribution-oblivious setting.
+We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
+This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
+
+We then show a similar result to fuzzy extractors.
+We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
+\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
+(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
+Furthermore, the result only applies for fuzzy extractors with perfect correctness.
+Many but not all fuzzy extractors have perfect correctness.
+
+Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
+Intuitively, this should be the easiest type of family to perform information-reconciliation.
+In the distribution-aware setting, information-reconciliation requires no information.
+
+\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
+Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
+Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Semantically secure multi-linear encodings are a very strong assumption.
+Furthermore, the output is unpredictability~(not pseudoentropic).
+Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+
+Computational fuzzy extractors offer more hope for avoiding the impossibility result.
+Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
+
+\bnote{compare this with universal decoding?}
+
+\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.
+We call this type of distribution nearly flat.
+The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
+Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.
+We use universal hashing to disambiguate points.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).
+We then write down the level and apply the above construction considering only points in that level.
+We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
+
+Our negative results are in the distribution-oblivious setting.
+A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
+However, $\gen$ does not see the distribution $W$, only the sample $w$.
+We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.
+Our family $\mathcal{W}$ is the set of affine lines.
+The value  $p$ partitions the metric space into possible and impossible $w$.
+The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.
+For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.
+This is enough to contradict security for both secure sketches and fuzzy extractors.
+
+\bnote{are these really affine lines?}
+\bnote{I'm writing these, very rough draft}
 
@@
 For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.
-For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
+% For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
 The set $J^c$ is the complement of $J$.
@@
 For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
-We will also use an average case version of this notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
-\begin{definition}[Conditional Hartley Entropy]
-\label{def:conditional hartley}
+We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
+%\begin{definition}[Conditional Hartley Entropy]
+%\label{def:conditional hartley}
 The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
-\end{definition}
+%\end{definition}
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
+%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
 We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
@@
 $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
-For the remainder of this work we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
+Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
 
@@
 First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
-Second in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
+Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
+%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
 This is a generalization of the definition of Dodis et al.
 which require a fuzzy extractor to work for all distributions of a particular entropy.
-In the \emph{distribution-aware} setting, the algorithms only work for a distribution $W$.
+In the \emph{distribution-aware} setting, the algorithms work for a single distribution $W$.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
@@
 \label{def:fuzzy extractor}
-An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
+An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$.
+\gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
+\rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.
+$(\gen, \rep)$ have the following properties:
 \begin{enumerate}
-\item \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
-\item \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.   
 \item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
@@
 
-Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.
-\bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.
-The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
-Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
+\noindent
+Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.
+The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
+Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
 \begin{definition}
 \label{def:secure sketch}
-An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.
+\sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
+\rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.
+$(\sketch, \rec)$ have the following properties:
 \begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
 \item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
@@
 
-\subsection{A necessary condition for security}
+\subsection{Fuzzy min-entropy: a necessary condition}
 \label{sec:minimal conditions}
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 3 + (\gamma-1) / \log |\mathbb{F}|$.
+There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.
 \end{theorem}
@@
 \item For most values of possible $Z$, the intersection between the viable pre images of $V|P \wedge Z$ and the viable pre images of $R_{small}$ is empty.
-Thus, the output of the fuzzy extractor can be distinguished from uniform.
+Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
 \end{itemize}
-
-\begin{proposition} 
-For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
-\end{proposition}
-\begin{proof}
-Consider some fixed $W\in\mathcal{V}$.
-The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =n^{1/5}$.
-Recall that $t= n/\nu$.
-We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
-Fix some $w, w'\in W$.
-Denote by $x, x'$ the values that produce $w, w'$ respectively.
-Clearly, $x\neq x'$.
-Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
-This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
-Thus, $\Hfuzz(W) = \Hoo(W)= 2^\nu = n^{1/5}$.
+\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious fuzzy extractor for the elements of $V$.
+\end{itemize}
+
 \end{proof}
 
-\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
-\end{proposition}
-\begin{proof}
-Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
-The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
-\end{proof}
-
-We now proceed to showing the technical portion of the theorem.
-We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
-Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
-
-\begin{lemma}
-Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 1$.
-There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\Theta(2^{-n^{1/3}})$.
-\end{lemma}
-\begin{proof}
-We assume that $\rep$ is deterministic in our analysis.
-Any randomness necessary for the \rep algorithm can be provided by $\gen$.
-We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(R, P) \leftarrow \gen(V)$.
-
-%By the definition of correctness for $(\sketch, \rec)$, 
-%\[
-%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
-%\]
-%For most $p$, $\rec$ works on most neighbors of $w$.  
-%Fix some $w$.  
-By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
-\[
-(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
-\]
-%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
-
-Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
-The distribution $R|P=p^*$ is the set of possible keys.
-The distribution $R|P=p^*$ induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
-Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
-
-Many of these sets must be small.
-That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
-
-For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
-We first define the interior of a set:%Define two sets, called the interior and crust respectively: \bnote{change term crust?}
-\begin{align*}
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
-%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
-\end{align*}
-
-%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient sphere:
-\begin{definition}
-A set $S$ is a $\beta$-deficient ball if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
-\end{definition}
-
-We now proceed to show that the interior of each $Q_{p^*, r^*}$ is small~(using the isoperimetric inequality on the Hamming space):
-%Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
-
-\begin{lemma}
-$|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.
-\end{lemma}
-\begin{proof}
-Recall that $Q_{p^*, r^*} \le 2^{n-\kappa+1}$.
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, r^*}$).
-We now find the size of $S_{p^*, r^*}$.
-
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}\leq 2^{1/2}$.
-Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
-This means that $|S_{p^*, r^*}|$ is a deficient sphere of radius at most $n/2-t$.
-Let $X$ denote a uniform string on $\zo^n$.
-We use Hoeffding's inequality~\cite{hoeffding1963probability}:
-
-\begin{align*}
-|S_{p^*, r^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-n^{3/5}} \le 2^{n - n^{3/5}}
-\end{align*}
-
-% That is, We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
-That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
-Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
-do better}.
-Thus,
-%\[n-(\kappa-1) \ge d (\log n - \log d).\]  
-%We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.  
-%
-%Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
-That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
-This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
-That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
-And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
-This is a radius of almost $n$}
-\end{proof}
-
-We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-n^{3/5}}$.  %Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
-To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.  
-Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^t-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
- As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
-We know show there are many possible values for $Z |P=p^*$.
-The only information about $Z$ is contained in the point  $V=v$.
-The length of this point is $2^n$.
-Conditioned on this information there are still many possible values for $Z$.
-That is,
- \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \ge \log \frac{2^{(n-\theta(\nu))}}{2^v} = n -\Theta(\nu).
- \]
- \bnote{need to come back to why this is true}
-Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
-
-This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, r^*}$~(other than $v$) and these values are disjoint.
-The optimum strategy is to include these values uniformly from different $Z$ values.
-Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
-Note that $Q_{small} \le 2^{n-n^{1/3}}|R_{small}|$.
-That is, 
-\begin{align*}
-\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-n^{1/3}}|R_{small}|}{2^{n - \theta(\nu)}}\\
-&=\frac{|R_{small}|}{2^{n^{1/3}-\Theta(n^{1/5})}}.
-\end{align*}
-Thus, at most $1/2^{n^{1/3}- \Theta(n^{1/5})}$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $z$.  We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
-\begin{enumerate}
-\item On input $x, z$.
-%\item If $x\not \in R_{small}$ output random bit $b$.
-\item Compute $V|P=p^* \wedge Z=z$ and $Q_{p^*, x}$. 
-\item If $(Q_{p^*, x} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
-\item Else output $b=1$.
-\end{enumerate}
-
-The distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
-\begin{align*}
-\Pr[D(R, P, Z) = 1] &- \Pr[D(U, P, Z) =1]=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/2- \Theta(2^{-n^{1/3}})\right) = 1/4-\Theta(2^{-n^{1/3}}).
-\end{align*}
-The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
-%We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
-%We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
-%\begin{align*}
-%\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
-%&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
-%%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
-%\end{align*}
-%\bnote{the two combinatorial bounds we are using aren't good enough}
-%To show that $\epsilon \ge 1/2$ we have that 
-%%\begin{align*}
-%%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
-%%\end{align*}
-%\bnote{why was that sufficient to break security}
-%\bnote{still working this isn't complete}
-\end{proof}
-\end{proof}
-
+\noindent
 \textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.
-This result presents a contrast between what is possible for sketches and fuzzy extraction.
+Their construction does not contradict our result because the construction is computationally secure.
+(Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)
 

### 2014-10-02 info-bounds/FuzzyExtPossibility.tex
another reorg of the intro

@@
 \newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
+\newcommand{\key}{\ensuremath{\class{key}}\xspace}
 \newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
@@
 \newcommand{\guess}{\mathsf{guess}}
+\newcommand{\eqdef}{\stackrel{\rm def}{=}}
 
@@
 Traditionally, this secret is assumed to have high min-entropy.
-However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
-That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.
+However, many sources of secrets with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
+That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
 To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.
-\lnote{Why limit to authentication}
+\lnote{Why limit to authentication?}
 
@@
 \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.
-The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.
-In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.
-
-A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.
+The first, calledinformation-reconciliation, removes the noise without leaking significant information.
+The second, known as privacy amplification, converts the high entropy secret to a uniform random value.
+In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.
+
+The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.
 %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
-A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.
-The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.
-The $key$ should be uniform even if an adversary has observed $p$.
+A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.
+The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.
 The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.
-For any security the initial readings must come from a high min-entropy distribution $W$.
-
-\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
+
+The security requirement for fuzzy extractors is that they should produce a $key$ should looks uniform to an adversary who has observed $p$.
+Naturally, satisfying this requirement gets harder the easier it is for the adversary to guess some $w'$ within distance $t$ of $w$, because an adversary who is successful at doing so will just obtain $\key$ by running $\rep$.
+
+\paragraph{A New Entropy Notion}
+We introduce a new entropy notion that measures precisely how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$.
+Suppose $w$ is sampled from a distribution $W$.
+To have the maximum chance of success with such a guess $w'$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
+We thus define \emph{fuzzy minentropy} $\Hfuzz(W) \eqdef -\log \max_w' \Pr[W\in B_t(w')]$.
+Observe that, trivially,
+$\Hfuzz(W) \ge \Hoo(w)-\log |B_t(\cdot)|$; this bound is useless (negative) in important practically relevant settings (e.g., iris scans~\cite[Section 5]{blanton2009biometric} and some physical sources~\cite{koeberl2014entropy}) in which entropy is at a premium and the tolerated distance must be high.
+
+Since an adversary who can guess $w'$ can trivially guess $\key$,  $\Hav(\key|p) \le \Hfuzz(W)$, and so at least superlogarithmic fuzzy minentropy is necessary for nontrivial key extraction.
+We now ask whether it also sufficient.
+
+\paragraph{A New Characterization}
+We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ that is at most negligibly far from uniform (\corref{cor:extension to fuzz ext}).
+We thus characterize when fuzzy extractors are possible in terms of our new entropy notion $\Hfuzz$.
+While our constructions are not polynomial-time (because they are dependent on having complete information about $W$), we observe in Section \lnote{ref} that polynomial-time constructions that provide only computational (rather information-theoretic) security are also possible.
+
+This characterization justifies paying attention to $\Hfuzz$ rather than relying on cruder measures such as $\Hoo(w)-\log |B_t(\cdot)|$.
+It is important to note that this characterization allows a fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.
+
+\paragraph{A New Impossibility Result}
+
+However, fuzzy extractor designs are typically not tailored to a particular source, but rather for a family sources (for example, all sources of minentropy at least $k$ with at most $t$ errors).
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+
+We show (\thref{thm:imposs fuzz ext}) that this extra adversarial knowledge can be devastating. 
+Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.
+We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).
+\lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $Hoo$?}
+
+\paragraph{Results on Information Reconciliation}
+Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
+The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
+We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
+
+A secure sketch performs non-interactive information-reconciliation.
+We show comparable results for secure sketches.
+secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible.
+\lnote{something about how for sec sketches results are stronger?}
+
+\paragraph{Related Settings}
+We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  We first consider the interactive setting.  
+Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
+In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
+If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
+%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
+Ideally, the server would keep a ``hashed'' value of $w$.
+This is  done for noiseless secrets like passwords.}
+In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
+The minimal assumption necessary for two party computation is \bnote{what?} \lnote{OT, right?; we can ask Ran about their paper with Tal R.
+or read the paper}
+
+\subsection{Ben's text from Wed afternoon, incorporated into the above}
+
+Intuitively, error-tolerance and key strength are at odds.
 Fix some distribution $W$.
@@
 \paragraph{Main result}
-Our main result is negative~(\thref{thm:imposs sketch}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.
+Our main result is negative~(\thref{thm:imposs fuzz ext}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.
 Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.
@@
 In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).
-
-\paragraph{Information-reconciliation in isolation}
-Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
-The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
-We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-
-A secure sketch performs non-interactive information-reconciliation.
-We show comparable results for secure sketches.
-That is, there is a family of distributions for which no secure sketch in possible.
-Furthermore, secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}).
-\paragraph{Related Settings}
-We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  We first consider the interactive setting.  
-Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
-In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
-If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
-%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
-Ideally, the server would keep a ``hashed'' value of $w$.
-This is  done for noiseless secrets like passwords.}
-In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is \bnote{what?}
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
 \end{theorem}

### 2014-10-02 trunk/info-bounds/FuzzyExtPossibility.tex
pass through introduction

@@
 
-\def\shownotes{1}
+\def\shownotes{0}
 \def\blinded{0}
@@
 \anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
-Usually, authentication requires some high quality secret.
-Traditionally, this secret is assumed to have high min-entropy.
-However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
-That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.
-To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.
-\lnote{Why limit to authentication}
-
- This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}.
-\lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.
-The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.
-In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.
-
-A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.
+Repeatable entropy sources enable applications cryptographic applications such as authentication and key agreement\bnote{more?}.
+However, many entropic sources present a problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
+That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
+To utilize such sources it is often necessary to remove noise, and achieve the same value in subsequent readings.
+\bnote{I tried to remove entropy from this but it needs to be cleaned up}
+
+Bennett, Brassard, and Roberts~\cite{bennett1988privacy} introduced this problem in the interactive setting.
+\lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks.
+The first, called information-reconciliation, removes the noise without leaking significant information.
+The second, known as privacy amplification, converts the high entropy secret to a uniform random value.
+In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.
+
+The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.
 %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
-A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.
-The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.
-The $key$ should be uniform even if an adversary has observed $p$.
+A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.
+The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.
 The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.
-For any security the initial readings must come from a high min-entropy distribution $W$.
-
-\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}
-
+
+The security requirement for fuzzy extractors that is $key$ uniform even to an adversary who has observed $p$.
+Achieving a strong $\key$ is harder as the allowed error tolerance $t$ increases.
+It becomes easier for the adversary to guess a $w'$ within distance $t$ of $w$ and an adversary who guesses a nearby $w'$ can obtain $\key$ by running $\rep$.
+
+\paragraph{A New Entropy Notion}
+We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$.
+Suppose $w$ is sampled from a distribution $W$.
+If the adversary only had access to $\rep$, they would recover $\key$ with maximal probability by guessing $w'$ that maximizes the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
+We  define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_w' \Pr[W\in B_t(w')]$.
+
+An adversary who can guess $w'$ can recover the $\key$, that is, $\Hav(\key|p) \le \Hfuzz(W)$.
+Super-logarithmic fuzzy min-entropy is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}).
+Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  
+Observe that, $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$.
+However, the difference between these quantities is very large for practical settings.
+As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
+We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}
+
+\paragraph{A New Characterization}
+We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
+We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.
+While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather information-theoretic) security are possible in \secref{sec:related settings}.
+
+This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution rather than relying on cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
+It is important to note that this characterization requires the fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.
+
+\paragraph{A New Impossibility Result}
+
+However, fuzzy extractor designs are typically not tailored to a particular source, but rather for a family sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors).
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+
+We showthat this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
+Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.
+We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart.
+\lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.
+
+\paragraph{Results on Information Reconciliation}
 Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
@@
 We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-Known constructions of fuzzy extractors and secure sketches incur significant losses.
-In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.
-In this work, we ask whether this is inherent.
-We identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
-Fix some distribution $W$.
-The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
-Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For security, this must occur with negligible probability.
-That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
-Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
-We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
-
-\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}
-
-Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
-In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
-If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
-Ideally, the server would keep a ``hashed'' value of $w$.
-This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
-In the one-message setting, we are far from this ideal.
-\lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''?
-Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}
-
-\lnote{I don't think you want to talk about traditional constructions here yet.
-I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}
-
-Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.
-This loss is usually linear in the input length of the string.
-While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
-As an example, many examples that arise in practice there are more error patterns than starting entropy.
-Traditional fuzzy extractors provide no guarantee for sources of this type.
-The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
-This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{The price of distributional uncertainty}
-
-\lnote{I think this should be ``Our Contributions'' and go in the following order.
-Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient.
-On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works.
-We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly).
-We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}
-
-The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)
-
-Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
-
-In this work, we show that this uncertainty comes at a significant cost.
-We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.
-We call this setting \emph{distribution aware}.
-Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.
-To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
-\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
-
-In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.
-A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.
-We ask the question for secure sketches and fuzzy extractors.
-Our results are information-theoretic, we consider the implications of computational security after discussing our results.
+
+A secure sketch performs non-interactive information-reconciliation.
+We show comparable results for secure sketches.
+Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}).
+Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.
 
@@
 Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
-%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
-%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
 \end{tabular}
@@
 \end{table}
-
-%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
-However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
-Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
-As long as the distribution falls in this class, security and correctness hold.
-
-%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
-We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
-We call this setting \emph{distribution-oblivious}.
-In the second, we allow the algorithms complete knowledge of the distribution.
-We call this setting \emph{distribution-aware}.
-
-%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
-We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
-
-\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.
-\lnote{I think this framing gives positive results too much attention.
-As we discussed on Monday, positive results here aren't what we want to emphasize}
-We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
-In this work, we assume the goal is to produce a super-logarithmic length key.
-In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Our constructions are feasibility results and do not run in polynomial time.
-In the distribution-aware setting this seems necessary as most distributions have exponential description size.
-The power of the distribution-aware setting is that the algorithms can access this description.
-It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
-
-\paragraph{Negative Results}
-The situation is very different in the distribution-oblivious setting.
-We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
-This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
-
-We then show a similar result to fuzzy extractors.
-We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
-\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
-(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
-Furthermore, the result only applies for fuzzy extractors with perfect correctness.
-Many but not all fuzzy extractors have perfect correctness.
-
-Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
-Intuitively, this should be the easiest type of family to perform information-reconciliation.
-In the distribution-aware setting, information-reconciliation requires no information.
-
-\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
-Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
-Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Semantically secure multi-linear encodings are a very strong assumption and unpredictability is weaker than pseudoentropy.
-Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-
-Computational fuzzy extractors offer more hope for avoiding the impossibility result.
-Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
-
-\bnote{compare this with universal decoding?}
-
-\paragraph{Our approach} Our secure sketch in the distribution aware setting relies on two observations.
-First for distributions where every point has roughly the same probability, the fuzzy min-entropy is determined by the ball with the greatest number of points.
-We call this type of distribution \emph{nearly flat}.
-For nearly flat distributions, the goal is to disambiguate any point within a ball of radius $t$.
-A universal hash with output length larger than the size of this ball suffices.
-However, for an arbitrary distribution, we cannot afford to write down information proportion to the ball with the greatest number of points.
-We solve this problem by converting an arbitrary distribution into a number of nearly flat distributions by writing down the probability of our original reading $w$.
-Then in reconstruction we limit ourselves to points of this probability.
-We then show this probability information is not two helpful.
-We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level~(\consref{cons:leveling}).
+\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.
+We call this type of distribution nearly flat.
+The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
+Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.
+We use universal hashing to disambiguate points.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).
+We then write down the level and apply the above construction considering only points in that level.
+We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
 
@@
 However, $\gen$ does not see the distribution $W$, only the sample $w$.
-In our negative results, we construct a family of distributions $\mathcal{W}$ where conditioned on seeing a single point, the support of the remainder of the distribution is uniform.
-Informally, to provide security $\rep(\cdot, p)$ partitions the metric space.
-Each part of this partition maps a single key.
-We can split each part into interiors and boundaries.
-In the Hamming space, the boundary makes up the overwhelming majority of the space.
-Thus, for most distributions $W$ the support of $W$ lies overwhelmingly in the boundary of these parts.
-All points in the boundary can be effectively excluded, reducing the entropy of $W$
-
+We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.
+Our family $\mathcal{W}$ is the set of affine lines.
+The value  $p$ partitions the metric space into possible and impossible $w$.
+The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.
+For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.
+This is enough to contradict security for both secure sketches and fuzzy extractors.
+
+\bnote{are these really affine lines?}
 \bnote{I'm writing these, very rough draft}
+
+\subsection{Sufficiency of $\Hfuzz$ in related settings}
+\label{sec:related settings}
+We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  
+%We first consider the interactive setting.  
+First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.
+In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.
+We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.
+Our negative result implies that $W|p$ cannot have pseudoentropy~(see \secref{sec:feas comp sec sketch} for discussion).
+
+Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
+Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
+In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
+If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
+%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
+Ideally, the server would keep a ``hashed'' value of $w$.
+This is  done for noiseless secrets like passwords.}
+In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
+The minimal assumption necessary for two party computation is oblivious transfer~\cite{lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R.
+or read the paper}
 
@@
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
+In \secref{sec:distribution aware}, we describe the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
 In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
@@
 For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
-We will also use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
-\begin{definition}[Conditional Hartley Entropy]
-\label{def:conditional hartley}
+We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
+%\begin{definition}[Conditional Hartley Entropy]
+%\label{def:conditional hartley}
 The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
-\end{definition}
+%\end{definition}
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
@@
 \bnote{there is nothing computational here right now}
+
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
@@
 Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.
-The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
-Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
+The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
+Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
 \begin{definition}
 \label{def:secure sketch}
-An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
+An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.
+\sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
+\rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.
+$(\sketch, \rec)$ have the following properties:
 \begin{enumerate}
-\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
-\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
 \item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
@@
 \subsubsection{Feasibility of computational secure sketches}
+\label{sec:feas comp sec sketch}
 Fuller et al.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
+There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
 \end{theorem}
 
-\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.
-The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
-Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
-Obtaining weaker parameters for impossibility of fuzzy extractors makes sense.
 \begin{proof}[Proof Outline]
@@
 \noindent
-\textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.
-Their construction does not contradict our result because the construction is computationally secure.
+\textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.
+We note that the specific family $\mathcal{V}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.
 (Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)
 
+\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.
+The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
+Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
 \bibliographystyle{alpha}
@@
 
+\section{Old intros}
+
+\subsection{Ben's text from Wed afternoon, incorporated into the above}
+
+Intuitively, error-tolerance and key strength are at odds.
+Fix some distribution $W$.
+The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
+Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
+For security, this must occur with negligible probability.
+That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
+Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
+We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
+A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
+We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?
+
+We have evidence for the sufficiency of fuzzy min-entropy.
+In the interactive setting, fuzzy min-entropy is sufficient for both tasks under mild computational assumptions.
+In the non-interactive setting, semantically secure multi-linear maps allow for strong key derivation.
+We provide evidence it is possible under strong assumptions on the knowledge of $W$.
+Thus, one might hope that  information-theoretic fuzzy extraction is possible for all distributions with fuzzy min-entropy.
+
+\paragraph{Main result}
+Our main result is negative~(\thref{thm:imposs fuzz ext}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.
+Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.
+We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.
+Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).
+
+\paragraph{The cost of distributional uncertainty}
+Fuzzy extractors are designed with limited knowledge of the target distribution.
+Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+
+Our negative results show that when the distribution $W$ is sufficiently unknown, fuzzy extractors are impossible.
+To illustrate that distributional uncertainty is the real problem, we define a restricted form of fuzzy extractor that is allowed to know the exact distribution $W$.
+We call this a \emph{distribution-aware} fuzzy extractor.
+In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).
+
+\subsection{Old organization}
+
+\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}
+
+Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
+The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
+We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
+Known constructions of fuzzy extractors and secure sketches incur significant losses.
+In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.
+In this work, we ask whether this is inherent.
+We identify a key problem: uncertainty in the distribution of $W$.
+
+\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
+Fix some distribution $W$.
+The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
+Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
+For security, this must occur with negligible probability.
+That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
+Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
+We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
+A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
+
+\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}
+
+Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
+In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
+If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
+Ideally, the server would keep a ``hashed'' value of $w$.
+This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
+In the one-message setting, we are far from this ideal.
+\lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''?
+Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}
+
+\lnote{I don't think you want to talk about traditional constructions here yet.
+I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}
+
+Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.
+This loss is usually linear in the input length of the string.
+While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
+As an example, many examples that arise in practice there are more error patterns than starting entropy.
+Traditional fuzzy extractors provide no guarantee for sources of this type.
+The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
+This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.
+
+\paragraph{The price of distributional uncertainty}
+
+\lnote{I think this should be ``Our Contributions'' and go in the following order.
+Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient.
+On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works.
+We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly).
+We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}
+
+The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)
+
+Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
+Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
+
+In this work, we show that this uncertainty comes at a significant cost.
+We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.
+We call this setting \emph{distribution aware}.
+Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.
+To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
+\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
+
+In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.
+A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.
+We ask the question for secure sketches and fuzzy extractors.
+Our results are information-theoretic, we consider the implications of computational security after discussing our results.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c }
+& Distribution-Oblivious & Distribution-Aware\\
+\hline
+Secure Sketch & No~(\thref{thm:imposs sketch}) & Yes~(\thref{cons:leveling})\\
+\hline
+Fuzzy Extractor & No~(\thref{thm:imposs fuzz ext}) & Yes~(\corref{cor:extension to fuzz ext})
+%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
+%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
+\end{tabular}
+\end{center}
+\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
+\label{tab:main results}
+\end{table}
+
+%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
+However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
+Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
+As long as the distribution falls in this class, security and correctness hold.
+
+%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
+We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
+We call this setting \emph{distribution-oblivious}.
+In the second, we allow the algorithms complete knowledge of the distribution.
+We call this setting \emph{distribution-aware}.
+
+%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
+We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
+
+\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.
+\lnote{I think this framing gives positive results too much attention.
+As we discussed on Monday, positive results here aren't what we want to emphasize}
+We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
+Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
+In this work, we assume the goal is to produce a super-logarithmic length key.
+In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
+
+Our constructions are feasibility results and do not run in polynomial time.
+In the distribution-aware setting this seems necessary as most distributions have exponential description size.
+The power of the distribution-aware setting is that the algorithms can access this description.
+It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
+
+\paragraph{Negative Results}
+The situation is very different in the distribution-oblivious setting.
+We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
+This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
+
+We then show a similar result to fuzzy extractors.
+We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
+\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
+(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
+Furthermore, the result only applies for fuzzy extractors with perfect correctness.
+Many but not all fuzzy extractors have perfect correctness.
+
+Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
+Intuitively, this should be the easiest type of family to perform information-reconciliation.
+In the distribution-aware setting, information-reconciliation requires no information.
+
+\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
+Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
+Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Semantically secure multi-linear encodings are a very strong assumption.
+Furthermore, the output is unpredictability~(not pseudoentropic).
+Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+
+Computational fuzzy extractors offer more hope for avoiding the impossibility result.
+Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
+Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
+
+\bnote{compare this with universal decoding?}
+
+\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.
+We call this type of distribution nearly flat.
+The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
+Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.
+We use universal hashing to disambiguate points.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).
+We then write down the level and apply the above construction considering only points in that level.
+We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
+
+Our negative results are in the distribution-oblivious setting.
+A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
+However, $\gen$ does not see the distribution $W$, only the sample $w$.
+We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.
+Our family $\mathcal{W}$ is the set of affine lines.
+The value  $p$ partitions the metric space into possible and impossible $w$.
+The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.
+For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.
+This is enough to contradict security for both secure sketches and fuzzy extractors.
+
+\bnote{are these really affine lines?}
+\bnote{I'm writing these, very rough draft}
+
+\paragraph{Organization} The reminder of the paper is organized as follows.
+In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
+In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
+In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
 \section{Leveraging convex combinations?}

### 2014-10-02 trunk/info-bounds/FuzzyExtPossibility.tex
minor notes in the intro

@@
 
-\def\shownotes{0}
+\def\shownotes{1}
 \def\blinded{0}
@@
 Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University.
-Work done in part while the author was at Boston University and Harvard University.
+Work done in part while the author was at Boston University.
 Email: {\tt asmith@psu.edu}.
@@
 
+\newpage
+\tableofcontents\newpage
+
 \section{Introduction}
@@
 \anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
-Repeatable entropy sources enable applications cryptographic applications such as authentication and key agreement\bnote{more?}.
-However, many entropic sources present a problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
+Sources of secret random bits are necessary for most cryptographic applications.
+In many situations, these bits are not explicitly and reliably stored for future use, but are reproduced as a result of some process (such as reading a biometric or a physically unclonable function).
+However, many such sources present a problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
 That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
@@
 
-Bennett, Brassard, and Roberts~\cite{bennett1988privacy} introduced this problem in the interactive setting.
+Bennett, Brassard, and Robert~\cite{bennett1988privacy} introduced this problem in the interactive setting.
 \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks.
@@
 It becomes easier for the adversary to guess a $w'$ within distance $t$ of $w$ and an adversary who guesses a nearby $w'$ can obtain $\key$ by running $\rep$.
+
+\anote{Suggested title: "Fuzzy Minentropy"}
 
@@
 
+\anote{Suggested title: "Characterization  for Distribution-aware Extractability". Emphasize if we know the distribution on $W$}
+
 \paragraph{A New Characterization}
@@
 
+\anote{Suggested title: "Impossibility Results for Distribution-Oblivious Sketches and Extractors".
+Also, "typically fuzzy extractors cannot be tailored".
+Also "for a family of sources" $\to$ "to a family of sources".}
+
 \paragraph{A New Impossibility Result}
@@
 \lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.
+
+\anote{Suggested title: "Results on Information Reconciliation (Secure Sketches)"}
 
@@
 Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
-Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
-\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
+Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
+\[w =  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
 b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
@@
 Consider some fixed $W\in\mathcal{V}$.
-The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.
+The bits $w_{1,..., \nu}$ are uniform, so $\Hoo(W) =\omega(\log n)$.
 Recall that $t=o (n/\nu)$.
@@
 Clearly, $x\neq x'$.
-Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.
-This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.
-Thus, $\Hfuzz(W) = \Hoo(W)= \omega(\log n)$.
+Thus, for any $i$, $a_i x + b_i \neq a_i x' + b_i$.
+This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$.
+That is, at least one of the bits in each block differs between $w$ and $w'$, and so $\dis(w, w') \ge n/\nu$.
+Since no two values in the support of $W$ lie in the same ball of radius $t$, we have $\Hfuzz(W) = \Hoo(W)= \omega(\log n)$.
 \end{proof}

### 2014-10-02 trunk/info-bounds/FuzzyExtPossibility.tex
edits to the intro

@@
 \section{Introduction}
-\anote{should our results be seen as justifying the distribution specific approach?}
-\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
-Sources of secret random bits are necessary for most cryptographic applications.
-In many situations, these bits are not explicitly and reliably stored for future use, but are reproduced as a result of some process (such as reading a biometric or a physically unclonable function).
-However, many such sources present a problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
+Sources of reproducible secret random bits are necessary for many cryptographic applications.
+In many situations, these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
+However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
 That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
-To utilize such sources it is often necessary to remove noise, and achieve the same value in subsequent readings.
-\bnote{I tried to remove entropy from this but it needs to be cleaned up}
-
-Bennett, Brassard, and Robert~\cite{bennett1988privacy} introduced this problem in the interactive setting.
-\lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks.
+To utilize such sources it is often necessary to remove noise, in order to derive the same value in subsequent readings.
+
+The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{Wyner75}.
+Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.
 The first, called information-reconciliation, removes the noise without leaking significant information.
@@
 %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
-A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.
+A fuzzy extractor consists of two algorithms.
+The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.
 The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.
@@
 
-The security requirement for fuzzy extractors that is $key$ uniform even to an adversary who has observed $p$.
-Achieving a strong $\key$ is harder as the allowed error tolerance $t$ increases.
-It becomes easier for the adversary to guess a $w'$ within distance $t$ of $w$ and an adversary who guesses a nearby $w'$ can obtain $\key$ by running $\rep$.
-
-\anote{Suggested title: "Fuzzy Minentropy"}
-
-\paragraph{A New Entropy Notion}
-We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$.
+The security requirement for fuzzy extractors that is $\key$ uniform even to an adversary who has observed $p$.
+This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.
+
+\paragraph{Fuzzy Min-entropy}
+We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$.
 Suppose $w$ is sampled from a distribution $W$.
-If the adversary only had access to $\rep$, they would recover $\key$ with maximal probability by guessing $w'$ that maximizes the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
-We  define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_w' \Pr[W\in B_t(w')]$.
-
-An adversary who can guess $w'$ can recover the $\key$, that is, $\Hav(\key|p) \le \Hfuzz(W)$.
+To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
+We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_w' \Pr[W\in B_t(w')]$.
+
 Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
-Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  
-Observe that, $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$.
-However, the difference between these quantities is very large for practical settings.
+Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  \lnote{know they don't -- that's better than they achieve, because coding is not that good}
+Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.
+However, the lower bound is too imprecise (sometimes even negative) for practical settings.
 As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
@@
 
-\anote{Suggested title: "Characterization  for Distribution-aware Extractability". Emphasize if we know the distribution on $W$}
-
-\paragraph{A New Characterization}
+\paragraph{Characterization  for Distribution-aware Extractability}
 We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}).

### 2014-10-03 info-bounds/FuzzyExtPossibility.tex
working on techniques section

--- 2014-10-01 info-bounds/FuzzyExtPossibility.tex
@@
 \newcommand{\decons}{\ensuremath{\mathtt{decons}}}
+\newcommand{\sd}{\ensuremath{\mathbf{SD}}}
 
@@
 
+\newpage
+\tableofcontents\newpage
+
 \section{Introduction}
-\anote{should our results be seen as justifying the distribution specific approach?}
-\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
-Usually, authentication requires some high quality secret.
-Traditionally, this secret is assumed to have high min-entropy.
-However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
-That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.
-To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.
-\lnote{Why limit to authentication}
-
- This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}.
-\lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.
-The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.
-In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.
-
-A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.
+Sources of reproducible secret random bits are necessary for many cryptographic applications.
+In many situations, these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
+However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
+That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
+To utilize such sources it is often necessary to remove noise, in order to derive the same value in subsequent readings.
+
+The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}.
+Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.
+The first, called information-reconciliation, removes the noise without leaking significant information.
+The second, known as privacy amplification, converts the high entropy secret to a uniform random value.
+In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.
+
+The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.
 %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
-A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.
-The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.
-The $key$ should be uniform even if an adversary has observed $p$.
+A fuzzy extractor consists of two algorithms.
+The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.
+The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.
 The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.
-For any security the initial readings must come from a high min-entropy distribution $W$.
-
-\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
-Fix some distribution $W$.
-The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
-Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For security, this must occur with negligible probability.
-That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
-Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
-We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
-We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?
-
-We have evidence for the sufficiency of fuzzy min-entropy.
-In the interactive setting, fuzzy min-entropy is sufficient for both tasks under mild computational assumptions.
-In the non-interactive setting, semantically secure multi-linear maps allow for strong key derivation.
-We provide evidence it is possible under strong assumptions on the knowledge of $W$.
-Thus, one might hope that  information-theoretic fuzzy extraction is possible for all distributions with fuzzy min-entropy.
-
-\paragraph{Main result}
-Our main result is negative~(\thref{thm:imposs sketch}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.
-Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.
-We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.
-Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).
-
-\paragraph{The cost of distributional uncertainty}
-Fuzzy extractors are designed with limited knowledge of the target distribution.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-
-Our negative results show that when the distribution $W$ is sufficiently unknown, fuzzy extractors are impossible.
-To illustrate that distributional uncertainty is the real problem, we define a restricted form of fuzzy extractor that is allowed to know the exact distribution $W$.
-We call this a \emph{distribution-aware} fuzzy extractor.
-In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).
-
-\paragraph{Information-reconciliation in isolation}
+
+The security requirement for fuzzy extractors that is $\key$ uniform even to an adversary who has observed $p$.
+This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.
+
+\paragraph{Fuzzy Min-entropy}
+We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$.
+Suppose $w$ is sampled from a distribution $W$.
+To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
+We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.
+
+Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
+Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.
+\lnote{know they don't -- that's better than they achieve, because coding is not that good} \bnote{I agree but I didn't know how to introduce this value otherwise.
+Seems like we need a reason to talk about $\Hoo(W) - \log |B_t|$.}
+Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.
+However, the lower bound is too imprecise (sometimes even negative) for practical settings.
+As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
+We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}
+
+\paragraph{Characterization  for Distribution-aware Extractability}
+We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
+We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.
+While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather than information-theoretic) security are possible in \secref{sec:related settings}.
+
+This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution rather than relying on cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
+It is important to note that this characterization requires the fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.
+
+\anote{Suggested title: "Impossibility Results for Distribution-Oblivious Sketches and Extractors".
+Also, "typically fuzzy extractors cannot be tailored".
+Also "for a family of sources" $\to$ "to a family of sources".}
+
+\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
+Typically, fuzzy extractor designs cannot be tailored to a particular source, rather they provide security for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors).
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary know some additional information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+
+We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
+Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.
+We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart.
+\lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.
+
+\paragraph{Results on Information Reconciliation (Secure Sketches)}
 Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
@@
 We show comparable results for secure sketches.
-That is, there is a family of distributions for which no secure sketch in possible.
-Furthermore, secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}).
-\paragraph{Related Settings}
-We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  We first consider the interactive setting.  
+Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}).
+We build our distribution-aware fuzzy extractor by applying a randomness extractor to our distribution-aware secure sketch.
+Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c  l l }
+ & Distribution-Aware & Distribution-Oblivious\\
+\hline
+Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
+\hline
+Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
+\end{tabular}
+\end{center}
+\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
+\label{tab:main results}
+\end{table}
+\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}
+
+\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch using precise knowledge of the distribution $W$.
+We begin with distributions where all points have roughly the same probability.
+We call this type of distribution nearly flat.
+Consider some subsequent reading $w'$.
+At a minimum the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.
+The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
+Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.
+We use universal hashing to disambiguate points.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.
+We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.
+We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
+
+Our negative results are in the distribution-oblivious setting.
+A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
+However, $\gen$ does not see the distribution $W$, only the sample $w$.
+We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.
+Our family $\mathcal{W}$ is the set of affine lines.
+The value $p$ partitions the metric space into regions that produce a consistent value in $\rep$.
+For each of these regions the adversary knows that possible $w$ lie far from the boundary of the region.
+However, in the Hamming space the majority of points lie near the boundary.
+Since the fuzzy extractor does not know the rest of $W$, it must put most points of $W$ near a boundary.
+This means that $W|p$ is small.
+This is enough to break security.
+
+ The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
+The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.
+The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.
+Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.
+
+Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
+
+\bnote{are these really affine lines?}
+\bnote{I'm writing these, very rough draft}
+
+\subsection{Sufficiency of $\Hfuzz$ in related settings}
+\label{sec:related settings}
+We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
+%We first consider the interactive setting.  
+First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.
+In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.
+We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.
+Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).
+
+Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
 Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
@@
 This is  done for noiseless secrets like passwords.}
-In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is \bnote{what?}
-
-\subsection{Old organization}
-
-\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}
-
-Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
-The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
-We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-Known constructions of fuzzy extractors and secure sketches incur significant losses.
-In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.
-In this work, we ask whether this is inherent.
-We identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
-Fix some distribution $W$.
-The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
-Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For security, this must occur with negligible probability.
-That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
-Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
-We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
-
-\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}
-
-Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
-In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
-If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
-Ideally, the server would keep a ``hashed'' value of $w$.
-This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
-In the one-message setting, we are far from this ideal.
-\lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''?
-Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}
-
-\lnote{I don't think you want to talk about traditional constructions here yet.
-I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}
-
-Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.
-This loss is usually linear in the input length of the string.
-While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
-As an example, many examples that arise in practice there are more error patterns than starting entropy.
-Traditional fuzzy extractors provide no guarantee for sources of this type.
-The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
-This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{The price of distributional uncertainty}
-
-\lnote{I think this should be ``Our Contributions'' and go in the following order.
-Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient.
-On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works.
-We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly).
-We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}
-
-The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)
-
-Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
-
-In this work, we show that this uncertainty comes at a significant cost.
-We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.
-We call this setting \emph{distribution aware}.
-Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.
-To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
-\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
-
-In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.
-A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.
-We ask the question for secure sketches and fuzzy extractors.
-Our results are information-theoretic, we consider the implications of computational security after discussing our results.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c | c | c }
-& Distribution-Oblivious & Distribution-Aware\\
-\hline
-Secure Sketch & No~(\thref{thm:imposs sketch}) & Yes~(\thref{cons:leveling})\\
-\hline
-Fuzzy Extractor & No~(\thref{thm:imposs fuzz ext}) & Yes~(\corref{cor:extension to fuzz ext})
-%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
-%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
-\end{tabular}
-\end{center}
-\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
-\label{tab:main results}
-\end{table}
-
-%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
-However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
-Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
-As long as the distribution falls in this class, security and correctness hold.
-
-%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
-We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
-We call this setting \emph{distribution-oblivious}.
-In the second, we allow the algorithms complete knowledge of the distribution.
-We call this setting \emph{distribution-aware}.
-
-%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
-We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
-
-\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.
-\lnote{I think this framing gives positive results too much attention.
-As we discussed on Monday, positive results here aren't what we want to emphasize}
-We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
-In this work, we assume the goal is to produce a super-logarithmic length key.
-In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Our constructions are feasibility results and do not run in polynomial time.
-In the distribution-aware setting this seems necessary as most distributions have exponential description size.
-The power of the distribution-aware setting is that the algorithms can access this description.
-It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
-
-\paragraph{Negative Results}
-The situation is very different in the distribution-oblivious setting.
-We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
-This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
-
-We then show a similar result to fuzzy extractors.
-We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
-\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
-(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
-Furthermore, the result only applies for fuzzy extractors with perfect correctness.
-Many but not all fuzzy extractors have perfect correctness.
-
-Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
-Intuitively, this should be the easiest type of family to perform information-reconciliation.
-In the distribution-aware setting, information-reconciliation requires no information.
-
-\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
-Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
-Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Semantically secure multi-linear encodings are a very strong assumption.
-Furthermore, the output is unpredictability~(not pseudoentropic).
-Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-
-Computational fuzzy extractors offer more hope for avoiding the impossibility result.
-Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
-
-\bnote{compare this with universal decoding?}
-
-\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.
-We call this type of distribution nearly flat.
-The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
-Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.
-We use universal hashing to disambiguate points.
-
-For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).
-We then write down the level and apply the above construction considering only points in that level.
-We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
-
-Our negative results are in the distribution-oblivious setting.
-A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
-However, $\gen$ does not see the distribution $W$, only the sample $w$.
-We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.
-Our family $\mathcal{W}$ is the set of affine lines.
-The value  $p$ partitions the metric space into possible and impossible $w$.
-The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.
-For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.
-This is enough to contradict security for both secure sketches and fuzzy extractors.
-
-\bnote{are these really affine lines?}
-\bnote{I'm writing these, very rough draft}
+In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
+The minimal assumption necessary for two party computation is oblivious transfer~\cite{lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R.
+or read the paper}
 
@@
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
+In \secref{sec:distribution aware}, we construct a distribution-aware fuzzy extractor for all distributions with fuzzy min-entropy.
 In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
@@
 %\end{definition}
-The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
+The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
 %For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
@@
 \item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
-\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
+\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
 \end{enumerate}
@@
 of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
+$\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
 U_d \times Y) \le \epsilon$.
@@
 
-\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
-Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+\textbf{Note:} Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+Our impossibility result says nothing about this weaker form of a secure sketch.
+We do not that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
 
@@
 \end{align*}
-% That is, We now find the maximum radius ball that contains at most $2^{n-(\kappa-1)}$ points.
-That is, $\max \{d\in \mathbb{Z^+}| B_d \le 2^{n-(\kappa-1)}\}$.
-Recall that $2^{n-(\kappa-1)} \ge |B_d| \ge (n/d)^d$\bnote{this bounds sucks!
-do better}.
-Thus,
-%\[n-(\kappa-1) \ge d (\log n - \log d).\]  
-%We first show that $d\le n/2$.  Since $|S_{p^*, r^*} | \le 2^{n-(\kappa-1)}/2^n \le 1/2$, then $d\le \lceil n/2\rceil$.  This is because $\sum_{i=0}^{\lceil n/2 \rceil} {n\choose i} \ge 2^{n-1}$.  
-%
-%Since $d\le 1/2$, $d\le d(\log n - \log d)$ and thus: $d\le n-(\kappa+1)$.
-That is, $S_{p^*, r^*} \cup D$ is a deficient sphere of radius at most $n-(\kappa-1)$.
-This means that $S_{p^*, r^*}$ is a deficient sphere of radius at most $n-(\kappa-1)-t$.
-That is $S_{p^*, r^*}$ is contained in a sphere of radius $n-\kappa-t+2$.
-And thus, $|\inter(Q_{p^*, r^*}|\le |B_{n-\kappa-t+2}|$.\bnote{we need a much better bound here.
-This is a radius of almost $n$}
 \end{proof}
 
-We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-4\nu}$.  %Define the set $K_{bad} = \cup_{r^*\in R_{small}} |Q_{p^*, r^*}|$ and note that $|K_{bad} | \le  |B_{n-\kappa -t+2}||R_{small}|$.
+We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-4\nu}$.  
 To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.  
@@
 The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
-%We now show that $\expe | Q_{p^*, r^*} \cap V | P=p^* \wedge Z=z| \le (1- \epsilon) |R_{small}|$. 
-%We use the combinatorial bound that $|B_d| \le \left(\frac{ne}{d}\right)^d$ \bnote{this bound is terrible!}.  We then have that, 
-%\begin{align*}
-%\expe_z |K_{bad} \cap V | P=p^* \wedge Z=z | &\le \frac{|B_{n-\kappa -t+2}||R_{small}|}{2^{n\nu -n -2\nu +1}}\\
-%&\le  \frac{\left(\frac{ne}{n-\kappa -t+2}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%&\le \frac{2^{3(n-\kappa -t +2)}}{2^{n -n/\nu-2\nu+1}}|R_{small}|
-%%&= \frac{\left(2^{\log n+ \log e - \log (n-\kappa -t+2)}\right)^{n-\kappa -t+2}}{2^{n\nu -n-2\nu+1}}|R_{small}|\\
-%%&=2^{(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n\nu -n 2\nu+1)} |R_{small}|
-%\end{align*}
-%\bnote{the two combinatorial bounds we are using aren't good enough}
-%To show that $\epsilon \ge 1/2$ we have that 
-%%\begin{align*}
-%%(n-\kappa-t+2)(\log n+ \log e - \log (n-\kappa -t+2)) - (n -n/\nu- 2\nu+1) 
-%%\end{align*}
-%\bnote{why was that sufficient to break security}
-%\bnote{still working this isn't complete}
 
@@
 
-%\section{Coding Theory}
-%\begin{definition}
-%\label{def:shannon-code}
-%Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr_{w' | \dis(w', w)\le t}[\rec(c') \neq c]\le \epsilon$.
-To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
-%\end{definition}
-%
-%
-% \begin{definition}
-%Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
-%$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
-%\end{definition}
-%An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.
-See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.
-An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.
-We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} %(we provide a proof in \secref{sec:proof of average to maximal error}):
-%\begin{lemma}
-%\label{lem:averageToMaximalError}
-%Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.
-There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
-%\end{lemma}
-%
-%\bnote{This comes from asiacrypt paper, what to cite?}
-%\section{Block Unguessable Distributions}
-%\begin{definition}~\cite[Definition 4.2]{canetti2014key}
-%\label{def:block guessable}
-%Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
-%\begin{cases}
-%1 & w_j = w_j'\\
-%0 & \text{otherwise}.
-%\end{cases}
-%\]
-%A source $W = W_1||...|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
-%\[
-%\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
-%\]
-%\end{definition}
-
-\section{Old Proofs}
-\bnote{I don't think we need anything from these sections}
-\subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
-We begin by trying to remove the restriction that every point in the metric space has a fixed number of neighbors in a distribution.
-We start with sketches that write down a fixed number of bits~(independent of their input $w$).
-We will show a lower bound on the number of bits that a $\sketch$ algorithm must write down.
-We assume that all coins of $\sketch$ are provided to $\rec$ and that $\rec$ is deterministic~(any coins needed for $\rec$ can be flipped by $\sketch$ in this model).
-
-\begin{lemma}
-Let $W$ be a flat distribution and let $(\sketch, \rec)$ be a secure sketch for $W$.
-Let $W$ be a $(c, t)$-bounded neighbor distribution.
-Let $S_{coin}$ be the number of sketches that can be produced by any fixing of $coin$.
-Then the error $\delta$ of $(\sketch, \rec)$ is at least $\frac{\expe_{coins}L(coins)}{c}$.
-\end{lemma}
-\begin{proof}
-We consider a fixed $w'$ that has $c$ neighbors in the distribution.
-We assume $\rec$ has access to all coins of $\sketch$.
-Furthermore, we assume that $\rec$ is deterministic and that any coins necessary are provided by $\sketch$).
-
-Denote by $S_{coin, R}$ the set of possible sketches for a given set of coins on all values in $R$.
-Furthermore, denote by $S_{coin}$ the set of possible sketches for all values $w$~(for a given value of coin) and note that $S_{coin, R} \subset S_{coin}$.
-Then $\rec(\cdot, w', coin)$ must fail to recover $|R|-|S_{coin, R}|$ fraction of $w\in R$~(recalling that $\rec$ is deterministic for this fixing of $coin$).
-This means that the total number of pairs $(w, coin)$ for which $\rec$ fails to recover is $2^{|coins|}R - \sum_{coins} |S_{coin, R}|$.
-
-This means there must exist some $w$ such that the number of $coin$ values for which $\rec$ fails to recover is 
-\[
-2^{|coin|} - \frac{\sum_{coin} |S_{coin, R}|}{R}.
-\]
- This means that for this $w$, 
-\[
-\Pr_{coin}[s \leftarrow \sketch(w, coin) \wedge w = \rec(s, w', coin)] < 1- \frac{\expe |S_{coin, R}|}{|R|} = 1-\frac{\expe |S_{coin, R}|}{c} \le 1-\frac{\expe |S_{coin}| }{c}.
-\]
-
-%Consider the function $\rec(w', ss, r)$ where $ss$ is the sketch produced by $\sketch(w)$ and $r$ are the coins used by $\sketch$.  
-\end{proof}
-
-For deterministic sketches:
-\[
-\Hav(W|S ) = -\log \left(\sum_{s\in S} \Pr[S = s] \frac{2^{-\Hoo(W)}}{\Pr[S=s]}\right) = -\log \left(2^{-\Hoo(W)} |S| \right)  = \Hoo(W) - H_0(S).
-\]
-
-\subsection{How many bits for distribution oblivious sketch} 
-\begin{lemma}
-Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions.
-Let $t = \lfloor (t_{cor}-1)/2\rfloor$ and let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t )$-secure sketch.
-Then the average length of $\sketch$ is at least $\log |B_{t}|$.
-\end{lemma}
-\bnote{what do we mean by average here?
-we mean when receiving a uniform input across the coins.
-Maybe, there are distributions where it writes down a little.
-What's the right thing to say?
-Markov?}
-\begin{proof}
-Let $\mathcal{M}$ be a metric space.
-Let $\mathcal{W}$ be the set of all $t_{cor}$-well spread distributions on $\mathcal{M}$.  
-Consider the following experiment:
-\[
-W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{cor}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
-\]
-That is, the adversary uniformly samples a well-spread distribution and then a point from the well-spread distribution.  
-Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.
-Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.
-Now consider the following experiment
-\[
-v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{cor}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
-\]
-Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.
-Then $X\overset{d}= Y$.
-That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.
-Thus, $\Pr[v^* = v] = 1$.
-For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M}| - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.
-For a secure sketch to lose $\log |B_t(\cdot)|$ bits of entropy it must write down at least $\log |B_t(\cdot)|$ bits on average~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.
-Thus, $(\sketch, \rec)$ writes down at least $\log |B_t(\cdot)|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{cor}}|$ bits on $X$.
-This completes the proof.
-\end{proof}
-\noindent
-\textbf{Notes:} In the above lemma, the relation between the well-spreadness of the class of distributions and the correctness of the fuzzy extractor is not important and is made to match the relation in \lemref{lem:nosketchwellspread} for convenience.
-The bound is purely derived from the correctness condition, the well-spreadness of the distribution can essentially be arbitrarily replaced~(as long as the maximal distance point from any point in the metric space is the same).
-
-Furthermore, the above lemma easily extends to the setting where the distributions are not well-spread as long as there is an adversary strategy of choosing the input distribution that produces an input to sketch that is identically distributed to the uniform distribution.
-
-The above lemma only talks about how many bits the algorithms must write down.
-It does not say that the entropy of the distribution must decrease~(this is the important question).
-We now proceed to this question.
-
 \end{document}

### 2014-10-03 trunk/info-bounds/FuzzyExtPossibility.tex
editing everything after intro

@@
 
-The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{Wyner75}.
+The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}.
 Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.
@@
 To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
-We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_w' \Pr[W\in B_t(w')]$.
+We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.
 
 Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
-Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  \lnote{know they don't -- that's better than they achieve, because coding is not that good}
+Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.
+\lnote{know they don't -- that's better than they achieve, because coding is not that good} \bnote{I agree but I didn't know how to introduce this value otherwise.
+Seems like we need a reason to talk about $\Hoo(W) - \log |B_t|$.}
 Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.
@@
 We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.
-While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather information-theoretic) security are possible in \secref{sec:related settings}.
+While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather than information-theoretic) security are possible in \secref{sec:related settings}.
 
@@
 
-\paragraph{A New Impossibility Result}
-
-However, fuzzy extractor designs are typically not tailored to a particular source, but rather for a family sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors).
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-
-We showthat this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
+\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
+Typically, fuzzy extractor designs cannot be tailored to a particular source, rather they provide security for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors).
+Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary know some additional information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+
+We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
 Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.
@@
 
-\anote{Suggested title: "Results on Information Reconciliation (Secure Sketches)"}
-
-\paragraph{Results on Information Reconciliation}
+\paragraph{Results on Information Reconciliation (Secure Sketches)}
 Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
@@
 Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}).
+We build our distribution-aware fuzzy extractor by applying a randomness extractor to our distribution-aware secure sketch.
 Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.
@@
 \begin{center}
-\begin{tabular}{c | c | c }
+\begin{tabular}{c  l l }
  & Distribution-Aware & Distribution-Oblivious\\
@@
 \end{table}
-\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.
+\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}
+
+\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.
+We begin with distributions where all points have roughly the same probability.
 We call this type of distribution nearly flat.
+Consider some subsequent reading $w'$.
+To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.
 The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
-Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.
+Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.
 We use universal hashing to disambiguate points.
@@
 For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).
-We then write down the level and apply the above construction considering only points in that level.
-We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.
+We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.
+We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
 
@@
 However, $\gen$ does not see the distribution $W$, only the sample $w$.
-We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.
+This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.
+We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.
 Our family $\mathcal{W}$ is the set of affine lines.
-The value  $p$ partitions the metric space into possible and impossible $w$.
-The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.
-For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.
-This is enough to contradict security for both secure sketches and fuzzy extractors.
+For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.
+For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.
+However, in the Hamming space the majority of points lie near the boundary.
+Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.
+This means that $W|p$ is small.
+This is enough to break security.
+
+ The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
+The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.
+The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.
+Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.
+
+Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
 
@@
 \label{sec:related settings}
-We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  
+We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
 %We first consider the interactive setting.  
@@
 We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.
-Our negative result implies that $W|p$ cannot have pseudoentropy~(see \secref{sec:feas comp sec sketch} for discussion).
+Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).
 
@@
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:distribution aware}, we describe the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
+In \secref{sec:distribution aware}, we construct a distribution-aware fuzzy extractor for all distributions with fuzzy min-entropy.
 In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
@@
 which require a fuzzy extractor to work for all distributions of a particular entropy.
-In the \emph{distribution-aware} setting, the algorithms work for a single distribution $W$.
+We cover the distribution-aware setting in \secref{sec:distribution aware}.
 Let $\mathcal{M}$ be a metric space with distance function $\dis$.
@@
 
-\paragraph{Distribution-aware setting}
-We separate between two types of fuzzy extractors and secure sketches.
-Because we rarely have complete descriptions of a physical probability distribution the standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions $\mathcal{W}$.
-We call this type of algorithm \emph{distribution-oblivious}.
-We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.
+\subsection{Fuzzy min-entropy: a necessary condition}
+\label{sec:minimal conditions}
+
+In an ideal world, we could provide a reproduce functionality as an oracle.
+In this world, the key is learned if a close point is provided, and no other information is leaked.
+In the rest of this work, we compare security to this ideal world.
+We call this fuzzy min-entropy:
+
+\begin{definition}
+\label{def:fuzzy min-ent}
+A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+\[
+\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
+\]
+\end{definition}
+
+If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).
+We make this intuition formal in the following result.
+For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
+\begin{lemma}
+\label{lem:fuzz necessary}
+Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
+\end{lemma}
+
+The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
+Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
+\lemref{lem:fuzz necessary} still applies.  
+This means that fuzzy min-entropy is also a necessary condition for interactive solution.
+As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.
+
+There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.
+There are also no known impossibility results for distributions with fuzzy min-entropy.
+Thus, the situation for fuzzy extractors is quite unclear.
+As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
+We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.
+
+\subsection{Distribution-aware setting}
+\label{sec:distribution aware}
+To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
+We call this type of algorithm \emph{distribution-aware}.
 We provide a definition for secure sketches~(extendible to fuzzy extractors):
@@
 
-\subsection{Fuzzy min-entropy: a necessary condition}
-\label{sec:minimal conditions}
-
-In an ideal world, we could provide a reproduce functionality as an oracle.
-In this world, the key is learned if a close point is provided, and no other information is leaked.
-In the rest of this work, we compare security to this ideal world.
-We call this fuzzy min-entropy:
-
-\begin{definition}
-\label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
-\[
-\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
-\]
-\end{definition}
-
-If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).
-We make this intuition formal in the following result.
-For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
-\begin{lemma}
-\label{lem:fuzz necessary}
-Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-\end{lemma}
-
-The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
-Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
-\lemref{lem:fuzz necessary} still applies.  
-This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.
-
-There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.
-There are also no known impossibility results for distributions with fuzzy min-entropy.
-Thus, the situation for fuzzy extractors is quite unclear.
-As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
-We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.
-
-\section{Distribution-Aware  Sketches}
+\section{Distribution-Aware Information-Reconciliation}
 \label{sec:distribution aware}
-In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors using \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
-We first consider distributions where points are far apart, distributions where all points have the same probability, and finally arbitrary distributions.
+In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
+We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.
 
@@
 
-\subsection{Well-Spread Distributions}
-\bnote{can remove this section if we need space}
-We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
+%\subsection{Well-Spread Distributions}
+%\bnote{can remove this section if we need space}
+%We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
 Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
@@
 However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.
-We begin by defining a well-spread distribution.
-
-\begin{definition}
-A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
-\end{definition}
-Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
+%We begin by defining a well-spread distribution.
+%
+%\begin{definition}
+%A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
+%\end{definition}
+%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
 Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.
@@
 This result illustrates how different the distribution-aware and distribution-oblivious settings are.}
-\begin{lemma}
-\label{lem:nosketchwellspread}
-Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.
+%\begin{lemma}
+%\label{lem:nosketchwellspread}
+%Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.
 In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.
@@
 By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
-\end{lemma}  
-\begin{proof}
-It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.
+%\end{lemma}  
+%\begin{proof}
+%It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.
 Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.
 Then by the triangle inequality,
-\[
-t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
-This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
-\end{proof}
+%\[
+%t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
+%This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
+%\end{proof}
 
 \subsection{Secure Sketches for Flat distributions}
-We showed it is easy to produce secure sketch for well-spread distributions in the distribution aware setting.
-%\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp.
-secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.
 In this section, we consider distributions with multiple points in each ball where points have the same probability.
@@
 
-Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.
-Fuzzy min-entropy is total weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).
+Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.
+Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).
 For flat distributions, this is proportional to the largest number of points in any ball.
@@
 For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
-The achievable security is proportional to the starting entropy minus the largest number of points in any ball.
 Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
@@
 \subsection{Secure sketches for all distributions with fuzzy min-entropy}
-The hashing approach used for flat~(\consref{cons:universal hash}) does not work for arbitrary sources.
+The hashing approach just described does not work for arbitrary sources.
 The reason is that some balls may have significantly more points but low overall probability.
-Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.
-Then the hashing algorithm writes down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.
+Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.
+Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.
 However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.
@@
 As long as levels are large enough, they do not reveal too much information about the stored point $W$.
-Naturally, there is a tradeoff between the number of levels and how useful the level information is to both the \rep algorithm and the adversary.
+Naturally, there is a tradeoff between the number of levels and how useful the level information is to both \rep and the adversary.
 
@@
 Let $\ell\in\mathbb{Z}^+$ be a parameter.
-Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.
+Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell$.
 Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.
@@
 \item \underline{Input}: $w$.
-\item If $\Pr[W=w] \le 2^{-(n+\ell)}$. Set $p=0,w$.
+\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $p=0,w$.
 \item Else
@@
 
-\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.
-Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.
-That is,
-\[
-B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
-\]
 \begin{theorem}
@@
 Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.
-Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
-
-We provide a full proof in \apref{sec:proof of layered hashing}.
-The argument is similar to the proof of \lemref{lem:flat hashing}, however, there is an additional step showing that releasing the probability information is not too harmful.
-Namely, that an adversary with access to the probability information improves their success by a polynomial factor.
-Note we release $n$ levels where $n =\log |\mathcal{M}|$.
+When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
 
 \end{theorem}
-\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
+We provide a proof in \apref{sec:proof of layered hashing}.
+The main idea is to show that an adversary that knows the level of $w$ cannot perform much better than an adversary without this information.
 
@@
 Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution-aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
 (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
@@
 
-\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.
+\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space.
+The relevant parameters were the size of balls and the size of the metric space.
 Going forward we will consider specific metric spaces, namely the Hamming metric.
@@
 
-In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.
-This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.
-In this section we ask if the results can be replicated for a family of distributions.
-Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.
-The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).
-Unfortunately, we show for secure sketches this is not the case.
-That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.
+In the previous section, we showed the sufficient of $\Hfuzz$ for distribution-aware algorithms.
+It is infeasible to assume that $W$ is completely known.
+Traditionally, algorithms only assume that $W$ comes from a family $\mathcal{W}$.
+In this section, we show that uncertainty of the distribution $W$ comes at a real cost.
+We will show a family $\mathcal{W}$~(where each member has fuzzy min-entropy) where any secure sketch for $\mathcal{W}$ leaves almost no entropy.
+A key aspect is formalizing the difference between the views of the fuzzy extractor~(which knows the family $\mathcal{W}$ and the sample $w$) and the view of the adversary~(knows the particular distribution $W$ but not the sample $w$).
 
 \subsection{A definitional equivalence}
-Before proceeding to our result, we consider the definition of a fuzzy extractor.
-The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.
-For clarity we will refer to $\mathcal{V}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular sample taken $w\in W$ as the \emph{outcome}.
-We will add the family $\mathcal{V}$ to the description of a fuzzy extractor where appropriate~(replacing the entropy requirement).
-
-The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.
+\label{sec:def equiv}
+Standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{W}$.
+We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.
+
+The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$.
 The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
-The minimax theorem says we can reverse which of these actions is announced first.
+The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie}.
 That is, the following two player games are equivalent:
@@
 123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
-$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
-If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
+\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
+$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
+If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
 If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
@@
 123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
-$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
-$W \leftarrow \mathcal{W}$\\
-If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
+\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, k)$: \\
+$V \leftarrow \mathcal{A}(\mathcal{W})$\\
+$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
+$W \leftarrow V$\\
+If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
 If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
@@
 
-%\begin{center}
-%\begin{minipage}{1in}
-%\end{center}
-
-%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
-%Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
-%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.
-
-%\begin{center}
-%\begin{minipage}{1in}
-% \end{minipage} 
-%\end{center}
-
-The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
-In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.
-These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.
+$V$ is a distribution over elements of $\mathcal{W}$.
+The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
+In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.
 
@@
 \label{lem:quant switch fuzz}
-Let $\mathcal{V}$ be a family of distributions.
-If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
-Let $V$ be a distribution over elements of $\mathcal{V}$.
+Let $\mathcal{W}$ be a family of distributions.
+If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
+Let $V$ be a distribution over $\mathcal{W}$.
 Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
@@
 
-Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.
+Our negative results will consider an adversary that specifies a distribution $V$ over $\mathcal{W}$.
 Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-We can think of the description of $W$ as side-information or leakage to the adversary.
-The system designer, however never sees the particular outcome $W$.
-This asymmetry will form the basis of our negative results.
+That is, $\sketch, \rec$ sees a distribution $V$ and the adversary seeing some side information $Z$ corresponding to the distribution $W$.
 
@@
 \label{cor:no fuzz for dist}
-Let $\mathcal{V}$ be a family of distributions.
-Let $V$ be an arbitrary distribution over elements of $\mathcal{V}$.
-If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
+Let $\mathcal{W}$ be a family of distributions.
+Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.
+If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
 \end{corollary}
-%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).
-However, as we show below the above construction does not extend to the setting of all well-spread distributions.
-In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.
-In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.
-In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.
-
-%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.
-The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.
-We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.
-The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.
-
-%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).
 
@@
 \subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
-In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.
-In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.
+We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.
+There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.
 \end{theorem}
@@
 \begin{proof}
-It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
-The adversary sees the information $W$, but the system designer does not.
-We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).
-
-We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.
-We begin by describing our family $\mathcal{V}$.
-$\mathcal{V}$ consists of the set of affine functions from one dimension to $\gamma$ dimensions.
-% That is, we project a single point in the field to an arbitrary element in the metric space.
-%In addition, the adversary learns the particular source that is being sketched while the system designer does not.
-To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.
-We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
-Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.
-
-Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.
+We first describe a family $\mathcal{W}$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
+Let $\mathcal{W}$ be the set of all distributions of the form 
+\[W =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} W_1 + \begin{pmatrix} 0  \\ 
+b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
+\]
+where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  
 This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
-Define $V$ as the uniform distribution over all such $W$.
-Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+Define $V$ as the uniform distribution over $\mathcal{W}$.
+The adversary sees $V|Z$, that is, they see the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
 Fix some $4\le t < \gamma$.
@@
 \begin{itemize}
-\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
+\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
 \item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
-\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.
-That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
-\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious secure sketch for the elements of $V$.
+\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
+\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is distribution oblivious secure sketch for the elements of $\mathcal{W}$.
 \end{itemize}
@@
 
-\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).
-Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+\textbf{Note:} Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+Our impossibility result says nothing about this weaker form of a secure sketch.
+We note that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
 
@@
 \begin{proof}
+We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
+\[
+B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
+\]
+
 \textbf{Correctness:}  We begin by arguing correctness.
-Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.
-The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.
-If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.
-Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
+We set $n = \ell$ to be the number of levels.\footnote{This proof can be carried out for an arbitrary $\ell$ but it leads to a more complicated theorem statement.}  Fix some $w, w'$.
+If $\Pr[W=w]\le 2^{-(m+\ell)} = 2^{-(m+n)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.
+Now consider the case when $\Pr[W=w]> 2^{-(m+n)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
 Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$.
@@
 %We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
-An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.
-That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
-Note there are $n-m+\ell$ outcomes for $i$ so the overall success of such an adversary is at most $n-m+\ell$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
+An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that level.
+That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.
+The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+Note there are $n$ outcomes for $i$ so the overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
 That is,
 \begin{align}
-\expe_{i | m\le i \le n+\ell}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+\ell}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
-&\le \left(n-m+\ell\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
-&= \left(n-m+\ell\right)\Hfuzz(W)\label{eq:link fuzz 3}
+\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
+&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
+&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
 \end{align}
@@
 We now argue security.
-First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).
-That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.
+First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).
+That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+m)}}\Pr[W = w] \le 2^{-m}$.
 Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
@@
 \Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
--\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
+-\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
 \end{align*}
@@
 \[
-2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].
+2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+m)}}\Pr[W=w | \sketch(W)].
 \]
@@
 \begin{align*}
-\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
-&\le \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le n+\ell} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
-&\le\frac{ \expe_{i | m\le i \le n+\ell} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
-%&=\delta \sum_{i | m\le i \le n+\ell} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
+\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
+&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
+&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
+&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
+&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
+%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
 %\end{align*}
@@
 %\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
-&= \frac{(n-m+\ell) 2^{-\Hfuzz(W)}}{2\delta}.
+&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
 \end{align*}
@@
 \begin{align*}
-\Hav(W | \sketch(W)) = -\log \left(2^{-\ell}+\frac{(1-2^{-\ell})(n-m+\ell)2^{-\Hfuzz(W)}}{2\delta}\right).
-\end{align*}
-Setting $\ell = m$ yields
-\begin{align*}
-\Hav(W | \sketch(W)) &= -\log \left(m+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
-&\ge -\log \min\{m, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
+\Hav(W | \sketch(W)) &= -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
+&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
 &\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\

### 2014-10-03 info-bounds/FuzzyExtPossibility.tex
more polishing of the intro -- first two pages

@@
 Sources of reproducible secret random bits are necessary for many cryptographic applications.
-In many situations, these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
+In many situations these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
 However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
 That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
-To utilize such sources it is often necessary to remove noise, in order to derive the same value in subsequent readings.
+To utilize such sources, it is often necessary to remove noise, in order to derive the same value in subsequent readings.
 
@@
 Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.
-The first, called information-reconciliation, removes the noise without leaking significant information.
+The first, called information reconciliation, removes the noise without leaking significant information.
 The second, known as privacy amplification, converts the high entropy secret to a uniform random value.
-In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.
-
-The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.
+In this work, we consider the noninteractive version of these problems, in which these tasks are performed together with a single message.
+
+The noninteractive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}, which consists of two algorithms.
 %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.
-A fuzzy extractor consists of two algorithms.
-The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.
+T
+The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces an output $\key$ along with a nonsecret helper value $p$.
 The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.
-The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.
-
-The security requirement for fuzzy extractors that is $\key$ uniform even to an adversary who has observed $p$.
+The correctness guarantee is that the key is reproduced precisely as long as the distance between $w$ and $w'$ is at most $t$.
+
+The security requirement for fuzzy extractors that is $\key$ uniform even to a (computationally unbounded) adversary who has observed $p$.
 This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.
@@
 \paragraph{Fuzzy Min-entropy}
-We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$.
+We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$.
 Suppose $w$ is sampled from a distribution $W$.
-To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
+To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
 We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.
-
-Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
-Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.
-\lnote{know they don't -- that's better than they achieve, because coding is not that good} \bnote{I agree but I didn't know how to introduce this value otherwise.
-Seems like we need a reason to talk about $\Hoo(W) - \log |B_t|$.}
-Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.
-However, the lower bound is too imprecise (sometimes even negative) for practical settings.
-As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
-We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}
-
-\paragraph{Characterization  for Distribution-aware Extractability}
+Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \le \Hfuzz(W) \le \Hoo(W)-\log |B_t(\cdot)|$ with equality when $t=0$.
+
+Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in  \lemref{lem:fuzz necessary}, which formalizes the above intuition). 
+However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance.
+Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
+This question is particularly relevant when the gap between the two sides of the inequality is high.
+As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}.
+We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.
+
+\paragraph{Tight Characterization for the Case of a Known Distribution}
 We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
 We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.
-While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather than information-theoretic) security are possible in \secref{sec:related settings}.
-
-This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution rather than relying on cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
-It is important to note that this characterization requires the fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.
-
-\anote{Suggested title: "Impossibility Results for Distribution-Oblivious Sketches and Extractors".
-Also, "typically fuzzy extractors cannot be tailored".
-Also "for a family of sources" $\to$ "to a family of sources".}
+It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).
+
+This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
 
 \paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
-Typically, fuzzy extractor designs cannot be tailored to a particular source, rather they provide security for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors).
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary know some additional information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
+Assuming full knowledge of a distribution is often unrealistic.
+Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled.
+It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model.
+Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source.
+Existing designs work for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors).
+Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.
 
 We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
-Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.
-We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart.
-\lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.
-
-\paragraph{Results on Information Reconciliation (Secure Sketches)}
-Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
-The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
-We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-
-A secure sketch performs non-interactive information-reconciliation.
-We show comparable results for secure sketches.
-Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}).
-We build our distribution-aware fuzzy extractor by applying a randomness extractor to our distribution-aware secure sketch.
-Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.
-
-\begin{table}
+Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 1-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.
+We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart.
+Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.
+
+\begin{table}[h]
 \begin{center}
 \begin{tabular}{c  l l }
- & Distribution-Aware & Distribution-Oblivious\\
+ & Known Distribution & Family of Distributions\\
 \hline
@@
 \end{table}
-\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}
-
-\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch using precise knowledge of the distribution $W$.
+
+\paragraph{Stronger Results on Information Reconciliation (Secure Sketches)}
+Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$), followed by randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
+The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $\sketch$ to output the original reading $w$.
+
+We show comparable, but stronger, results for secure sketches.
+Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
+(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
+The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
+
+\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.
 We begin with distributions where all points have roughly the same probability.
@@
 Consider some subsequent reading $w'$.
-At a minimum the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.
+To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.
 The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
@@
 However, $\gen$ does not see the distribution $W$, only the sample $w$.
+This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.
 We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.
 Our family $\mathcal{W}$ is the set of affine lines.
-The value $p$ partitions the metric space into regions that produce a consistent value in $\rep$.
-For each of these regions the adversary knows that possible $w$ lie far from the boundary of the region.
+For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.
+For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.
 However, in the Hamming space the majority of points lie near the boundary.
-Since the fuzzy extractor does not know the rest of $W$, it must put most points of $W$ near a boundary.
+Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.
 This means that $W|p$ is small.
@@
 Our impossibility result says nothing about this weaker form of a secure sketch.
-We do not that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+We note that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
 

### 2014-10-03 trunk/info-bounds/FuzzyExtPossibility.tex
change of notation, removing old intros

@@
 \end{table}
-\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}
+
+\paragraph{Stronger Results on Information Reconciliation (Secure Sketches)}
+Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$), followed by randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
+The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $\sketch$ to output the original reading $w$.
+
+We show comparable, but stronger, results for secure sketches.
+Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
+(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
+The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
 
@@
 Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
+There exists a family of distributions $\mathcal{W}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
 If
@@
 \label{sec:imposs fuzz ext}
-In the previous section, we showed a family of distributions that does not admit a secure sketch.  We extend this result to fuzzy extractors.
+In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
+There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
 \end{theorem}
@@
 \begin{proof}[Proof Outline]
-Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.
+Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.
 In particular, we need to assume a larger error tolerance.
@@
 Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
-This family is closely related to the family we constructed in \thref{thm:imposs sketch}.
-However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.
-For convenience we assume that $\nu\in\mathbb{Z}^+$.
-We describe a single element $W\in V$.
+We work over the binary alphabet so we squish affine lines to the binary realm.
 Let $x_1,..., x_\nu \in \zo^\nu$.
@@
 Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
-\[w =  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
+\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
 b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
@@
 Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
-
-We now present an outline for the remainder of the proof~(proofs in \apref{sec:fuzz ext proof}):
+Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/nu}$.
+We now present of the proof~(proofs in \apref{sec:fuzz ext proof}):
 \begin{itemize}
-\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
-\item \lemref{lem:fuzz can't get key}: for many values of $Z$, for a large fraction of keys, there are no viable $v\in\mathcal{M}$.  Specifically:
+\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
+\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half the keys $r\in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  Specifically:
 \begin{itemize}
-\item Show that for half the keys have a bounded number of pre images in the metric space.
-Denote this set as $R_{small}$.
-The only viable pre images $v$ in this set are located distance $t$ from the boundary~(that is, $v$ is viable if all points in the metric space within distance $t$ map to the same key).
-This means for every key $r\in R_{small}$ has bounded number of viable points in the metric space: $2^{n-n^{3/5}}$.
+\item Show that for half the keys have a bounded number of pre images in the metric space.  Denote this set as $R_{small}$.  
+\item Consider some $r\in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
+Consider the set of $V_{r} = \{w | \rep(w, p) = r\}$.
+The only values of $V_r$ that could be the real value of $w$ are distance $t$ from a boundary of $V_r$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $r$).
+We show that most of $V_r$ is near a boundary.
+Harper's theorem says that the boundary of a region is minimized by a ball containing the same number of points~\cite{harper1966optimal} .
+Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.
+Together these two results imply that $V_r$ is small.
 \item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
 Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$, the intersection between the viable pre images of $V|P \wedge Z$ and the viable pre images of $R_{small}$ is empty.
+\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_r$ is empty.
 Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
 \end{itemize}
-\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious fuzzy extractor for the elements of $V$.
+\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is distribution oblivious fuzzy extractor for the elements of $\mathcal{W}$.
 \end{itemize}
@@
 \textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.
-We note that the specific family $\mathcal{V}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.
-(Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)
+We note that the specific family $\mathcal{W}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.
+(Their construction is stated with imperfect correctness.
+A construction with perfect correctness is obtained by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)
 
@@
 Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
+\bnote{improve this}
 \bibliographystyle{alpha}
@@
 
-\section{Old intros}
-
-\subsection{Ben's text from Wed afternoon, incorporated into the above}
-
-Intuitively, error-tolerance and key strength are at odds.
-Fix some distribution $W$.
-The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
-Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For security, this must occur with negligible probability.
-That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
-Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
-We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
-We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?
-
-We have evidence for the sufficiency of fuzzy min-entropy.
-In the interactive setting, fuzzy min-entropy is sufficient for both tasks under mild computational assumptions.
-In the non-interactive setting, semantically secure multi-linear maps allow for strong key derivation.
-We provide evidence it is possible under strong assumptions on the knowledge of $W$.
-Thus, one might hope that  information-theoretic fuzzy extraction is possible for all distributions with fuzzy min-entropy.
-
-\paragraph{Main result}
-Our main result is negative~(\thref{thm:imposs fuzz ext}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.
-Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.
-We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.
-Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).
-
-\paragraph{The cost of distributional uncertainty}
-Fuzzy extractors are designed with limited knowledge of the target distribution.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-
-Our negative results show that when the distribution $W$ is sufficiently unknown, fuzzy extractors are impossible.
-To illustrate that distributional uncertainty is the real problem, we define a restricted form of fuzzy extractor that is allowed to know the exact distribution $W$.
-We call this a \emph{distribution-aware} fuzzy extractor.
-In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).
-
-\subsection{Old organization}
-
-\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}
-
-Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
-The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
-We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-Known constructions of fuzzy extractors and secure sketches incur significant losses.
-In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.
-In this work, we ask whether this is inherent.
-We identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
-Fix some distribution $W$.
-The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
-Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For security, this must occur with negligible probability.
-That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
-Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
-We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
-
-\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}
-
-Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
-In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
-If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
-Ideally, the server would keep a ``hashed'' value of $w$.
-This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
-In the one-message setting, we are far from this ideal.
-\lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''?
-Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}
-
-\lnote{I don't think you want to talk about traditional constructions here yet.
-I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}
-
-Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.
-This loss is usually linear in the input length of the string.
-While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
-As an example, many examples that arise in practice there are more error patterns than starting entropy.
-Traditional fuzzy extractors provide no guarantee for sources of this type.
-The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
-This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{The price of distributional uncertainty}
-
-\lnote{I think this should be ``Our Contributions'' and go in the following order.
-Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient.
-On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works.
-We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly).
-We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}
-
-The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)
-
-Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
-
-In this work, we show that this uncertainty comes at a significant cost.
-We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.
-We call this setting \emph{distribution aware}.
-Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.
-To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
-\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
-
-In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.
-A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.
-We ask the question for secure sketches and fuzzy extractors.
-Our results are information-theoretic, we consider the implications of computational security after discussing our results.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c | c | c }
-& Distribution-Oblivious & Distribution-Aware\\
-\hline
-Secure Sketch & No~(\thref{thm:imposs sketch}) & Yes~(\thref{cons:leveling})\\
-\hline
-Fuzzy Extractor & No~(\thref{thm:imposs fuzz ext}) & Yes~(\corref{cor:extension to fuzz ext})
-%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
-%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
-\end{tabular}
-\end{center}
-\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
-\label{tab:main results}
-\end{table}
-
-%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
-However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
-Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
-As long as the distribution falls in this class, security and correctness hold.
-
-%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
-We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
-We call this setting \emph{distribution-oblivious}.
-In the second, we allow the algorithms complete knowledge of the distribution.
-We call this setting \emph{distribution-aware}.
-
-%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
-We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
-
-\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.
-\lnote{I think this framing gives positive results too much attention.
-As we discussed on Monday, positive results here aren't what we want to emphasize}
-We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
-In this work, we assume the goal is to produce a super-logarithmic length key.
-In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Our constructions are feasibility results and do not run in polynomial time.
-In the distribution-aware setting this seems necessary as most distributions have exponential description size.
-The power of the distribution-aware setting is that the algorithms can access this description.
-It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
-
-\paragraph{Negative Results}
-The situation is very different in the distribution-oblivious setting.
-We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
-This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
-
-We then show a similar result to fuzzy extractors.
-We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
-\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
-(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
-Furthermore, the result only applies for fuzzy extractors with perfect correctness.
-Many but not all fuzzy extractors have perfect correctness.
-
-Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
-Intuitively, this should be the easiest type of family to perform information-reconciliation.
-In the distribution-aware setting, information-reconciliation requires no information.
-
-\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
-Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
-Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Semantically secure multi-linear encodings are a very strong assumption.
-Furthermore, the output is unpredictability~(not pseudoentropic).
-Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-
-Computational fuzzy extractors offer more hope for avoiding the impossibility result.
-Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
-
-\bnote{compare this with universal decoding?}
-
-\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.
-We call this type of distribution nearly flat.
-The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
-Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.
-We use universal hashing to disambiguate points.
-
-For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).
-We then write down the level and apply the above construction considering only points in that level.
-We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
-
-Our negative results are in the distribution-oblivious setting.
-A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
-However, $\gen$ does not see the distribution $W$, only the sample $w$.
-We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.
-Our family $\mathcal{W}$ is the set of affine lines.
-The value  $p$ partitions the metric space into possible and impossible $w$.
-The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.
-For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.
-This is enough to contradict security for both secure sketches and fuzzy extractors.
-
-\bnote{are these really affine lines?}
-\bnote{I'm writing these, very rough draft}
-
-\paragraph{Organization} The reminder of the paper is organized as follows.
-In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
-In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
 \section{Leveraging convex combinations?}
@@
 \label{sec:proof secure sketch imposs}
+The proof of \thref{thm:imposs sketch} uses ideas from coding theory.  We review the definition of a Shannon code: 
+\begin{definition}
+\label{def:shannon-code}
+Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+%To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
+\end{definition}
+
+We now prove item in the outline of \thref{thm:imposs sketch} in turn.
+
 \begin{proposition} 
-\label{prop:each element good} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\label{prop:each element good} For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
 \end{proposition}
 \begin{proof}
-Consider some fixed $W\in\mathcal{V}$.
+Consider some $W\in\mathcal{W}$.
 The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.
@@
 \end{proof}
+
 \begin{lemma}
@@
 Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
-%By the Markov inequality, 
-%\[
-%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
-%\]
-%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
-%
-%Outline of what I want to say.
-%\begin{itemize}
-%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
-%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
-%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
-%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
-%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
-%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.
-Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).
-%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
-%\end{itemize}
 \end{proof}
-We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.
 
@@
 This means for any $v^*\in V| \sketch(V)$ (other than the true $v$) there is at most one $z$ such that $v^*\in V | \sketch(V), Z=z$.
-Thus, we ask The optimum strategy is to include these values uniformly from different $Z$ values.
+Thus, the optimum strategy is to include these values uniformly from different $Z$ values.
 
@@
 \label{prop:dist fuzzy ent fuzz}
-For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
 \end{proposition}
 \begin{proof}
-Consider some fixed $W\in\mathcal{V}$.
+Consider some fixed $W\in\mathcal{W}$.
 The bits $w_{1,..., \nu}$ are uniform, so $\Hoo(W) =\omega(\log n)$.
@@
 %Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient sphere:
+We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient ball:\bnote{use a term other than deficient}
 \begin{definition}
@@
 Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
-Note that $Q_{small} \le 2^{n-n^{1/3}}|R_{small}|$.
+Note that $Q_{small} \le 2^{n-4\nu}|R_{small}|$.
 That is, 

### 2014-10-03 trunk/info-bounds/FuzzyExtPossibility.tex
edited "techniques" in the intro

@@
 
-\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.
-We begin with distributions where all points have roughly the same probability.
-We call this type of distribution nearly flat.
-Consider some subsequent reading $w'$.
-To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.
-The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
-Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.
-We use universal hashing to disambiguate points.
-
-For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.
-We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.
+\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).
+We begin with distributions in which all points in the support have roughly the same probability.
+We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$.
+To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched.
+Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points.
+Thus, our sketch is computed via a universal hash of $w$.
+To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$.
+Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability.
+Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball.
+Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
 We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
 
-Our negative results are in the distribution-oblivious setting.
-A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
-However, $\gen$ does not see the distribution $W$, only the sample $w$.
-This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.
-We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.
+\paragraph{Techniques for Negative Results for Distribution Families}
+Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
+We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
+the adversary knows $W$.
+To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.
+
+Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
+In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$.
+This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.
+
+In the fuzzy extractor case, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$ (preimages of each $\key$ under $\rep(\cdot, p)$).
+For each of these regions, the adversary knows that possible $w$ lie $t$-far from the boundary of the region.
+However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).
+This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, most regions become empty, leaving $\key$ far from uniform.
+
+We note that the use of a high-dimensional Hamming space is important: fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
+
+\lnote{old two pars below this line --- do we need anything?}
+
+We construct a family of distributions $\mathcal{W}$ for which knowing only a single value $w$ leaves the remainder of the support is uniform.
 Our family $\mathcal{W}$ is the set of affine lines.
@@
 Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.
-
-Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
 

### 2014-10-04 info-bounds/FuzzyExtPossibility.tex
working through body of paper

@@
 
-Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in  \lemref{lem:fuzz necessary}, which formalizes the above intuition). 
+Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
 However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance.
@@
 
-\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.
-We begin with distributions where all points have roughly the same probability.
-We call this type of distribution nearly flat.
-Consider some subsequent reading $w'$.
-To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.
-The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
-Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.
-We use universal hashing to disambiguate points.
-
-For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.
-We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.
+\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).
+We begin with distributions in which all points in the support have roughly the same probability.
+We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$.
+To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched.
+Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points.
+Thus, our sketch is computed via a universal hash of $w$.
+To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$.
+Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability.
+Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball.
+Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
 We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
 
-Our negative results are in the distribution-oblivious setting.
-A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
-However, $\gen$ does not see the distribution $W$, only the sample $w$.
-This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.
-We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.
-Our family $\mathcal{W}$ is the set of affine lines.
-For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.
-For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.
-However, in the Hamming space the majority of points lie near the boundary.
-Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.
-This means that $W|p$ is small.
-This is enough to break security.
-
- The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
+\paragraph{Techniques for Negative Results for Distribution Families}
+Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
+We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
+the adversary knows $W$.
+To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.
+
+Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
+In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$.
+This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.
+
+In the fuzzy extractor case, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$ (preimages of each $\key$ under $\rep(\cdot, p)$).
+For each of these regions, the adversary knows that possible $w$ lie $t$-far from the boundary of the region.
+However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).
+This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, most regions become empty, leaving $\key$ far from uniform.
+
 The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.
-The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.
-Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.
-
-Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
-
-\bnote{are these really affine lines?}
-\bnote{I'm writing these, very rough draft}
+The result for fuzzy extractors is more delicate.
+It requires the fuzzy extractor to correct $t = \omega(n^{1/2}\log n)$ errors~(where $n$ is the length of the string) and have perfect correctness.
+Extending this result to imperfect correctness seems challenging and is an interesting open problem.
+This result also relies on the majority of points lying near boundaries of a set.
+Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
 
@@
 In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
-The minimal assumption necessary for two party computation is oblivious transfer~\cite{lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R.
+The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R.
 or read the paper}
@@
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
+For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
 We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
-\bnote{there is nothing computational here right now}
 
@@
 
-In this section, we define of fuzzy extractors and secure sketches.
+In this section, we define fuzzy extractors and secure sketches.
 Definitions and lemmas are drawn from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.
+al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.
 First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
@@
 %\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
-This is a generalization of the definition of Dodis et al.
-which require a fuzzy extractor to work for all distributions of a particular entropy.
-We cover the distribution-aware setting in \secref{sec:distribution aware}.
-Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
+We discuss distribution-aware algorithms in \secref{sec:distribution aware def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.
 
@@
 \end{enumerate}
-A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
 \end{definition}
@@
 \end{enumerate}
-A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
 \end{definition}
 
-\noindent \textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
-
+\noindent In the above definitions, the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.
 A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:
@@
 \begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
+Let $\mathcal{M}$, $\chi$ be finite sets.
+A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
+of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
 $\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
@@
 In an ideal world, we could provide a reproduce functionality as an oracle.
-In this world, the key is learned if a close point is provided, and no other information is leaked.
-In the rest of this work, we compare security to this ideal world.
-We call this fuzzy min-entropy:
+In this world, the key is output if a close point is provided, and no response is provided otherwise.
+We call the performance of an adversary in this ideal world fuzzy min-entropy:
 
@@
 \label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
 \[
-\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
+\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
 \]
@@
 
-If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).
-We make this intuition formal in the following result.
-For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
-\begin{lemma}
-\label{lem:fuzz necessary}
+Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):%If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).
+We make this intuition formal:
+%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
+\begin{proposition}
+\label{prop:fuzz necessary}
 Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-\end{lemma}
-
-The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
-Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
-\lemref{lem:fuzz necessary} still applies.  
-This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.
-
-There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.
-There are also no known impossibility results for distributions with fuzzy min-entropy.
-Thus, the situation for fuzzy extractors is quite unclear.
-As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
-We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.
-
-\subsection{Distribution-aware setting}
-\label{sec:distribution aware}
-To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
-We call this type of algorithm \emph{distribution-aware}.
-We provide a definition for secure sketches~(extendible to fuzzy extractors):
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
+ with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
+\end{proposition}
+
+%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
+%\lemref{lem:fuzz necessary} still applies.  
+\noindent
+There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result)
+Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.
+
+\subsection{Distribution-aware algorithms}
+\label{sec:distribution aware def}
+%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
+We call an algorithm with complete information on the distribution $W$ \emph{distribution-aware}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
 
@@
 Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.
+A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
 That is,
@@
 $
-\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$
+\forall w\in W, \forall w' \in\mathcal{M}| \dis(w,w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
 Correctness is guaranteed only for the support of $W$.
-\item \emph{Security:} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
 \end{definition}
-The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
-When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.
-It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.
-
-\section{Distribution-Aware Information-Reconciliation}
+$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
+We assume distribution-aware algorithms are \emph{inefficient}.
+Finding a natural model of specifying distributions that allows for efficient~(yet generic) distribution-aware constructions of sketches and extractors is an interesting problem.
+
+\section{Sufficiency of $\Hfuzz$ for Distribution-Aware Algorithms}
 \label{sec:distribution aware}
@@
 \end{align*}
-For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
+For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  That is, 
 \begin{align}
@@
 
-\subsection{Secure sketches for all distributions with fuzzy min-entropy}
+\subsection{Secure sketches for all distributions with $\Hfuzz$}
 The hashing approach just described does not work for arbitrary sources.
@@
 Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.
-In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
+However, a distribution with high fuzzy min-entropy may be formed from component distributions with little or no fuzzy min-entropy.
+It is unclear how to leverage the convex combination property in this setting.
+\bnote{I took out the discussion of the appendix, don't know if it helps}%In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
 The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
@@
 
-\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space.
+\noindent
+In our positive results we considered an arbitrary finite metric space.
 The relevant parameters were the size of balls and the size of the metric space.
-Going forward we will consider specific metric spaces, namely the Hamming metric.
+Our negative results are specific to the Hamming metric.
 \section{Impossibility of $\Hfuzz$ for Distribution-Oblivious Secure Sketches}
@@
 \]
-where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  
+where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i, b_i\in\mathbb{F}, a_i\neq 0$.  
 This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
 Define $V$ as the uniform distribution over $\mathcal{W}$.
-The adversary sees $V|Z$, that is, they see the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+The adversary sees $V|Z$.
+$Z$ is the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
 Fix some $4\le t < \gamma$.
@@
 \item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
-\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is distribution oblivious secure sketch for the elements of $\mathcal{W}$.
-\end{itemize}
+\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is distribution oblivious secure sketch for the elements of $\mathcal{W}$.\end{itemize}
 \end{proof}
-\subsubsection{Feasibility of computational secure sketches}
+\subsubsection{Implications for Computational secure sketches}
 \label{sec:feas comp sec sketch}
 Fuller et al.
-showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
 %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
-The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
+The definitional of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
 
@@
 Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
+There exists a family of distributions $\mathcal{W}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
 If
-\begin{itemize}
-\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-\item $t\ge 4$,
-\item and $\epsilon + t\delta < 1/16$,
-\end{itemize}
+$s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
+$t\ge 4$, and 
+ $\epsilon_{sec} + t\delta < 1/16$,
  then $\tilde{m} =O(1)$.
@@
 
-\textbf{Note:} Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
 Our impossibility result says nothing about this weaker form of a secure sketch.
-We note that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+Extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
 
@@
 Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
-
-We now present an outline for the remainder of the proof~(proofs in \apref{sec:fuzz ext proof}):
+Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/nu}$.
+We now present of the proof~(proofs in \apref{sec:fuzz ext proof}):
 \begin{itemize}
-\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
-\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform~(from the fuzzy extractor designer's point of view).  That is $V\overset{d}=U$.
-\item \lemref{lem:fuzz can't get key}: for many values of $Z$, for a large fraction of keys, there are no viable $v\in\mathcal{M}$.  Specifically:
+\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
+\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half the keys $r\in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  Specifically:
 \begin{itemize}
-\item Show that for half the keys have a bounded number of pre images in the metric space.
-Denote this set as $R_{small}$.
-The only viable pre images $v$ in this set are located distance $t$ from the boundary~(that is, $v$ is viable if all points in the metric space within distance $t$ map to the same key).
-This means for every key $r\in R_{small}$ has bounded number of viable points in the metric space: $2^{n-n^{3/5}}$.
+\item Show that for half the keys have a bounded number of pre images in the metric space.  Denote this set as $R_{small}$.  
+\item Consider some $r\in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
+Consider the set of $V_{r} = \{w | \rep(w, p) = r\}$.
+The only values of $V_r$ that could be the real value of $w$ are distance $t$ from a boundary of $V_r$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $r$).
+We show that most of $V_r$ is near a boundary.
+A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short} .
+Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.
+Together these two results imply that $V_r$ is small.
 \item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
 Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$, the intersection between the viable pre images of $V|P \wedge Z$ and the viable pre images of $R_{small}$ is empty.
+\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_r$ is empty.
 Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
 \end{itemize}
-\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious fuzzy extractor for the elements of $V$.
+\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is distribution oblivious fuzzy extractor for the elements of $\mathcal{W}$.
 \end{itemize}
@@
 \textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.
-We note that the specific family $\mathcal{V}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.
-(Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)
+We note that the specific family $\mathcal{W}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors  for this family of distributions when $\mathbb{F}$ is large enough under weaker assumptions.
+(Their construction is stated with imperfect correctness.
+A construction with perfect correctness is obtained by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)
 
 \paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.
-The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
+This result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
 Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
+\bnote{improve this}
 \bibliographystyle{alpha}
@@
 
-\section{Old intros}
-
-\subsection{Ben's text from Wed afternoon, incorporated into the above}
-
-Intuitively, error-tolerance and key strength are at odds.
-Fix some distribution $W$.
-The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
-Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For security, this must occur with negligible probability.
-That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
-Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
-We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
-We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?
-
-We have evidence for the sufficiency of fuzzy min-entropy.
-In the interactive setting, fuzzy min-entropy is sufficient for both tasks under mild computational assumptions.
-In the non-interactive setting, semantically secure multi-linear maps allow for strong key derivation.
-We provide evidence it is possible under strong assumptions on the knowledge of $W$.
-Thus, one might hope that  information-theoretic fuzzy extraction is possible for all distributions with fuzzy min-entropy.
-
-\paragraph{Main result}
-Our main result is negative~(\thref{thm:imposs fuzz ext}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.
-Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.
-We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.
-Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).
-
-\paragraph{The cost of distributional uncertainty}
-Fuzzy extractors are designed with limited knowledge of the target distribution.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-
-Our negative results show that when the distribution $W$ is sufficiently unknown, fuzzy extractors are impossible.
-To illustrate that distributional uncertainty is the real problem, we define a restricted form of fuzzy extractor that is allowed to know the exact distribution $W$.
-We call this a \emph{distribution-aware} fuzzy extractor.
-In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).
-
-\subsection{Old organization}
-
-\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}
-
-Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
-The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.
-We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.
-Known constructions of fuzzy extractors and secure sketches incur significant losses.
-In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.
-In this work, we ask whether this is inherent.
-We identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.
-Fix some distribution $W$.
-The adversary has access to the reproduce function and attempts to learn the key by inputting a point.
-Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.
-For security, this must occur with negligible probability.
-That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.
-Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.
-We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.
-A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).
-
-\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}
-
-Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
-In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
-If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
-Ideally, the server would keep a ``hashed'' value of $w$.
-This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
-In the one-message setting, we are far from this ideal.
-\lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''?
-Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}
-
-\lnote{I don't think you want to talk about traditional constructions here yet.
-I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}
-
-Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.
-This loss is usually linear in the input length of the string.
-While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.
-As an example, many examples that arise in practice there are more error patterns than starting entropy.
-Traditional fuzzy extractors provide no guarantee for sources of this type.
-The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.
-This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.
-
-\paragraph{The price of distributional uncertainty}
-
-\lnote{I think this should be ``Our Contributions'' and go in the following order.
-Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient.
-On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works.
-We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly).
-We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}
-
-The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)
-
-Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.
-Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.
-Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.
-Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.
-
-In this work, we show that this uncertainty comes at a significant cost.
-We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.
-We call this setting \emph{distribution aware}.
-Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.
-To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
-\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
-
-In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.
-A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.
-We ask the question for secure sketches and fuzzy extractors.
-Our results are information-theoretic, we consider the implications of computational security after discussing our results.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c | c | c }
-& Distribution-Oblivious & Distribution-Aware\\
-\hline
-Secure Sketch & No~(\thref{thm:imposs sketch}) & Yes~(\thref{cons:leveling})\\
-\hline
-Fuzzy Extractor & No~(\thref{thm:imposs fuzz ext}) & Yes~(\corref{cor:extension to fuzz ext})
-%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
-%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
-\end{tabular}
-\end{center}
-\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
-\label{tab:main results}
-\end{table}
-
-%When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.
-However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).
-Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).
-As long as the distribution falls in this class, security and correctness hold.
-
-%To characterize key derivation from noisy sources, we consider the effect of this uncertainty.
-We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.
-We call this setting \emph{distribution-oblivious}.
-In the second, we allow the algorithms complete knowledge of the distribution.
-We call this setting \emph{distribution-aware}.
-
-%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.
-We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}
-
-\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.
-\lnote{I think this framing gives positive results too much attention.
-As we discussed on Monday, positive results here aren't what we want to emphasize}
-We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).
-Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.
-In this work, we assume the goal is to produce a super-logarithmic length key.
-In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-
-Our constructions are feasibility results and do not run in polynomial time.
-In the distribution-aware setting this seems necessary as most distributions have exponential description size.
-The power of the distribution-aware setting is that the algorithms can access this description.
-It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.
-
-\paragraph{Negative Results}
-The situation is very different in the distribution-oblivious setting.
-We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).
-This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.
-
-We then show a similar result to fuzzy extractors.
-We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).
-\thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.
-(Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.
-Furthermore, the result only applies for fuzzy extractors with perfect correctness.
-Many but not all fuzzy extractors have perfect correctness.
-
-Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.
-Intuitively, this should be the easiest type of family to perform information-reconciliation.
-In the distribution-aware setting, information-reconciliation requires no information.
-
-\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
-Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.
-Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Semantically secure multi-linear encodings are a very strong assumption.
-Furthermore, the output is unpredictability~(not pseudoentropic).
-Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-
-Computational fuzzy extractors offer more hope for avoiding the impossibility result.
-Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.
-Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
-
-\bnote{compare this with universal decoding?}
-
-\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.
-We call this type of distribution nearly flat.
-The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.
-Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.
-We use universal hashing to disambiguate points.
-
-For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).
-We then write down the level and apply the above construction considering only points in that level.
-We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
-
-Our negative results are in the distribution-oblivious setting.
-A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).
-However, $\gen$ does not see the distribution $W$, only the sample $w$.
-We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.
-Our family $\mathcal{W}$ is the set of affine lines.
-The value  $p$ partitions the metric space into possible and impossible $w$.
-The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.
-For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.
-This is enough to contradict security for both secure sketches and fuzzy extractors.
-
-\bnote{are these really affine lines?}
-\bnote{I'm writing these, very rough draft}
-
-\paragraph{Organization} The reminder of the paper is organized as follows.
-In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.
-In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
-\section{Leveraging convex combinations?}
-\label{sec:convex comb}
-In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+%\section{Leveraging convex combinations?}
+%\label{sec:convex comb}
+%In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
 For example, consider the following hypothetical extension to \consref{cons:universal hash}.
-Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
-However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
-
-The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_\alpha$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, the problem arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+%
+%We now describe a possible modification to the hashing construction.
+Upon receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, write $i$ and perform the sketch as before for distribution $W_i$.
 Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
-
-In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
-That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+Unfortunately, this proposal may remove all entropy.
+%Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
+However, this is not the case.
+%
+%%In the flat case, we used a hash whose length was proportional to the number of points in the largest ball.
+The residual entropy in this case was within a super-logarithmic factor of $\Hfuzz(W)$.
 However, in the setting where $W$ is a convex combination of flat sources this does not hold.
-
-Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+%
+%Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors and $W_i$ contains a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
 This distribution is illustrated in \figref{fig:convex comb}.
-
-The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+%
+%\begin{figure}
+%
+%\centering
+%    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+%    \caption{A convex combination of $W_1,..., W_\alpha$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+%\label{fig:convex comb}    
+%\end{figure}
+%
+%
+%The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
 Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\gamma, k\}$ where $\gamma$ is the number of distributions $W_1,..., W_\gamma$.
-(For our purposes, we can assume that $\gamma$ is quite large and the probability of $w^*$ becomes the dominant factor.)
-
-Consider an input point $w\in W$.
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\alpha, k\}$ where $\alpha$ is the number of distributions $W_1,..., W_\gamma$.
+The value $\alpha$ may be quite large and $k$ may be the dominant factor.
+%
+%Consider an input point $w\in W$.
 One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \gamma\}$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \alpha\}$.
 For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
@@
 Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
-
-\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
-However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
-That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
-
-In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
-
-\begin{figure}[t]
-
-\centering
-    \includegraphics[width=.9\textwidth]{convexCombExample.png}
-    \caption{A convex combination of $W_1,..., W_\gamma$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
-\label{fig:convex comb}    
-\end{figure}
+\bnote{I removed the discussion of convex combs for the submitted version}
 
 \section{Proofs}
-\subsection{Proof of \lemref{lem:fuzz necessary}}
+\subsection{Proof of \propref{prop:fuzz necessary}}
 \label{sec:proof fuzz necessary}
@@
 This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
-Consider the following distinguisher $D$~(note that $D$ only provides an input and looks at the output, thus this distinguisher extends to the interactive setting):
+Consider the following distinguisher $D$:
 \begin{itemize}
@@
 \end{itemize}
-First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.
-Thus, when $\kappa = \omega(\log n)$:
+Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
 \[
@@
 \]
+Note that $D$ only provides an input and looks at the output, thus this distinguisher extends to the interactive setting).
+Also note that $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.
+Thus, $D$ is also a distinguisher in the computational setting.
 \end{proof}
@@
 
-\section{Proof of \thref{thm:imposs sketch}}
+\subsection{Proof of \thref{thm:imposs sketch}}
 \label{sec:proof secure sketch imposs}
+The proof of \thref{thm:imposs sketch} uses the definition of a Shannon code: 
+\begin{definition}
+\label{def:shannon-code}
+Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
+We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+%To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
+\end{definition}
+
+We now prove item in the outline of \thref{thm:imposs sketch} in turn.
+
 \begin{proposition} 
-\label{prop:each element good} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
+\label{prop:each element good} For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
 \end{proposition}
 \begin{proof}
-Consider some fixed $W\in\mathcal{V}$.
+Consider some $W\in\mathcal{W}$.
 The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.
@@
 &< (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}| +1 \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
-&\le (4-t)\log |\mathbb{F}| +1\\
-& <1\,.
+&\le (4-t)\log |\mathbb{F}| +1< 1\,.\\
 \end{align*}
@@
 
-\section{Proof of \thref{thm:imposs fuzz ext}}
+\subsection{Proof of \thref{thm:imposs fuzz ext}}
 \label{sec:fuzz ext proof}
@@
 That is,
- \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} >\log  \frac{(2^{n/\nu})^{\nu-2}}{2^{\nu}}  \log \frac{2^{(n-2\nu))}}{2^\nu} = n -3\nu.
- \]
+ \begin{align*}
+ \forall v, H_0(Z | V=v) &=\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right)\\
+  &= \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \\
+  &>\log  \frac{(2^{n/\nu})^{\nu-2}}{2^{\nu}} \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
+  &=\log \frac{2^{(n-2\nu))}}{2^\nu} = n -3\nu.
+ \end{align*}
  where the inequality follows by \lemref{lem:log-minus-one}.

### 2014-10-04 info-bounds/FuzzyExtPossibility.tex
notation run through

@@
 \newcommand{\key}{\ensuremath{\class{key}}\xspace}
+\newcommand{\Key}{\ensuremath{\class{Key}}\xspace}
+
 \newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
@@
 We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.
-Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \le \Hfuzz(W) \le \Hoo(W)-\log |B_t(\cdot)|$ with equality when $t=0$.
-
-Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
-However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance.
-Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
+Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$ with equality when $t=0$.
+\bnote{I don't follow this equation, equality also for well-spread distributions}
+
+superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
+However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
+Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
 This question is particularly relevant when the gap between the two sides of the inequality is high.
@@
 \paragraph{Tight Characterization for the Case of a Known Distribution}
-We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
+We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
 We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.
@@
 
-This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
+This characterization justifies $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t|$.
 
@@
 Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source.
-Existing designs work for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors).
+Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors).
 Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.
@@
 \end{center}
-\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
+\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
 \label{tab:main results}
@@
 Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
-(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
+(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
 The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
@@
 Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball.
-Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
-
-For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.
+Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.
 We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
@@
 Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
-We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
+We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
 the adversary knows $W$.
@@
 
-The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.
-The result for fuzzy extractors is more delicate.
-It requires the fuzzy extractor to correct $t = \omega(n^{1/2}\log n)$ errors~(where $n$ is the length of the string) and have perfect correctness.
+The result for fuzzy extractors is delicate.
+The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.
 Extending this result to imperfect correctness seems challenging and is an interesting open problem.
-This result also relies on the majority of points lying near boundaries of a set.
+The result also relies on the majority of points lying near boundaries of a set.
 Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
 
-\subsection{Sufficiency of $\Hfuzz$ in related settings}
+\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
 \label{sec:related settings}
@@
 
-Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
+Second, we can weaken the computational assumption necessary for $\Hfuzz(W)$ to be sufficient by moving to an interactive setting.
 Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
@@
 \label{sec:preliminaries}
-For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.
+%For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.
 % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
@@
 
-The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
-and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
+The {\em min-entropy} of $W$ is $\Hoo(W) = -\log(\max_w \Pr[W=w])$,
+and the {\em average (conditional)} min-entropy of $W$ given $P$ is  $\Hav(W|P) = -\log(\expe_{p\in P} \max_{w} \Pr[W=w|P=p])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
+Let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
 We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
@@
 %\label{def:conditional hartley}
-The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
+The conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
 %\end{definition}
+
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
@@
 
-For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
-If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
+For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.
+If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.
 For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.
-$U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
+$U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.
 Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
@@
 An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$.
-\gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
+\gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
 \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.
@@
 \begin{enumerate}
-\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
-\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
+\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = \key] \geq 1-\delta$.
+\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
 \end{enumerate}
@@
 Let $\mathcal{M}$, $\chi$ be finite sets.
-A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
+A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(\tilde{m}, \epsilon)$-average-case extractor} if for all pairs
 of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
+$\tilde{H}_\infty(X|Y) \ge \tilde{m}$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
 U_d \times Y) \le \epsilon$.
@@
 \label{prop:fuzz necessary}
-Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
+Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
 If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
@@
 \noindent
-There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result)
-Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.
+There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
+Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.
 
@@
 $
-\forall w\in W, \forall w' \in\mathcal{M}| \dis(w,w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
+\forall w\in W$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
 Correctness is guaranteed only for the support of $W$.
@@
 
-\section{Sufficiency of $\Hfuzz$ for Distribution-Aware Algorithms}
+\section{Sufficiency of $\Hfuzz(W)$ for Distribution-Aware Algorithms}
 \label{sec:distribution aware}
@@
 %\end{definition}
-%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
+%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has superlogarithmic min-entropy).
 Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.
@@
 \begin{definition}
-Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
+Let $F : \mathcal{K} \times \mathcal{M} \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in \mathcal{M}$:
 \[
@@
 $
-
-For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
-Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
-
-\subsection{Secure sketches for all distributions with $\Hfuzz$}
+For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
+Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a superlogarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
+
+\subsection{Secure sketches for all distributions with $\Hfuzz(W)$}
 The hashing approach just described does not work for arbitrary sources.
 The reason is that some balls may have significantly more points but low overall probability.
-Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.
+Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$ and let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.
 Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.
-However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.
+However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B^1_t$ and the hash completely reveals the point.
 
@@
 As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
-We address this by describing the probability of the point $w_0\in W$ seen in sketch.
+We address this by describing the probability of the point $w\in W$ seen in sketch.
 Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.
@@
 \item Sample $K\leftarrow \mathcal{K}_i$.
-\item Set $p =1,  i, F_i(K, w), K$.
+\item Set $ss =1,  i, F_i(K, w), K$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', y)$
-\item If $y_0 = 1$, output $y_{1,..., |y|}$.
+\item \underline{Input}: $(w', ss)$
+\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
 \item Else
 \begin{enumerate}
-\item Parse $(i, z, K) = y_{1,..., |y|}$.
+\item Parse $(i, y, K) = ss_{1,..., |y|}$.
 \item $W^* = \{w \in W | \dis(w, w')\le t\}$.
@@
 \label{thm:layered hashing}
-Let $W$ be a distribution over $\mathcal{M}$.
+Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.
 Let $\delta>0$ be an function of $n$.
@@
 \label{cor:extension to fuzz ext}
-Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
+Let $\mathcal{M}$ be a metric space where $n = \log |\M|$.
 For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution-aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
@@
 Our negative results are specific to the Hamming metric.
-\section{Impossibility of $\Hfuzz$ for Distribution-Oblivious Secure Sketches}
+\section{Impossibility of $\Hfuzz(W)$ for Distribution-Oblivious Secure Sketches}
 \label{sec:dist oblivious}
@@
 123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
+\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
 $(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
@@
 If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
+If $\Hav(W | \sketch(W))\ge \tilde{m}$ reward $(1, -1)$\\
 Else reward $(-1, 1)$.
@@
 123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, k)$: \\
+\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
 $V \leftarrow \mathcal{A}(\mathcal{W})$\\
@@
 Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-That is, $\sketch, \rec$ sees a distribution $V$ and the adversary seeing some side information $Z$ corresponding to the distribution $W$.
+That is, $(\sketch, \rec)$ sees a distribution $V$ and the adversary seeing some side information $Z$ corresponding to the distribution $W$.
 
@@
 \end{proof}
+\bnote{should note we can decrease field size at the cost of distance.}
 \subsubsection{Implications for Computational secure sketches}
@@
 Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
+\emph{relaxed HILL entropy} at least $\tilde{m}$ conditioned on $S$,
+denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq \tilde{m}$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq \tilde{m}$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
 \end{definition}
@@
 Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
-We work over the binary alphabet so we squish affine lines to the binary realm.
-Let $x_1,..., x_\nu \in \zo^\nu$.
+We work over the binary alphabet so we squish affine lines to the binary alphabet.
+\bnote{better word than squish} Let $x_1,..., x_\nu \in \zo^\nu$.
 Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
@@
 Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
-Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/nu}$.
-We now present of the proof~(proofs in \apref{sec:fuzz ext proof}):
+Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
+We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
 \begin{itemize}
@@
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
-\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half the keys $r\in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  Specifically:
+\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half of the $\key \in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  Specifically:
 \begin{itemize}
-\item Show that for half the keys have a bounded number of pre images in the metric space.  Denote this set as $R_{small}$.  
-\item Consider some $r\in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
-Consider the set of $V_{r} = \{w | \rep(w, p) = r\}$.
-The only values of $V_r$ that could be the real value of $w$ are distance $t$ from a boundary of $V_r$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $r$).
-We show that most of $V_r$ is near a boundary.
+\item Half the keys have at most $2^{\kappa-1}$ pre images in the metric space.  Denote this set as $R_{small}$.  
+\item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
+Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.
+The only values of $V_\key$ that could be the real value of $w$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).
+We show that most of $V_\key$ is near a boundary.
 A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short} .
 Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.
-Together these two results imply that $V_r$ is small.
+Together these two results imply that $V_\key$ is small.
 \item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
 Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_r$ is empty.
+\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ is empty.
 Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
@@
 %\label{sec:convex comb}
+%\bnote{be careful uncommenting this, some notation may be out of date}
 %In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
@@
 %%In the flat case, we used a hash whose length was proportional to the number of points in the largest ball.
-The residual entropy in this case was within a super-logarithmic factor of $\Hfuzz(W)$.
+The residual entropy in this case was within a superlogarithmic factor of $\Hfuzz(W)$.
 However, in the setting where $W$ is a convex combination of flat sources this does not hold.
@@
 
-\section{Proofs}
-\subsection{Proof of \propref{prop:fuzz necessary}}
+\section{Proof of \propref{prop:fuzz necessary}}
 \label{sec:proof fuzz necessary}
@@
 Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
+This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] \geq 1/\poly(n)$.
 Consider the following distinguisher $D$:
@@
 \item Input $r, p$.
-\item If $\rep(m^*, p) = r$, output $1$.
+\item If $\rep(w', p) = r$, output $1$.
 \item Else output $0$.
 \end{itemize}
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
+Clearly, $\Pr[D(\Key, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
 \[
@@
 \]
-Note that $D$ only provides an input and looks at the output, thus this distinguisher extends to the interactive setting).
-Also note that $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.
+Note that $D$ only provides an input and looks at the output, thus it works in the interactive setting.
+Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.
 Thus, $D$ is also a distinguisher in the computational setting.
@@
 
-\subsection{Proof of \lemref{lem:flat hashing}}
+\section{Proof of \lemref{lem:flat hashing}}
 \label{sec:proof of flat hashing}
@@
 Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
-Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.
+Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.
 
@@
 
-\subsection{Proof of \thref{thm:layered hashing}}
+\section{Proof of \thref{thm:layered hashing}}
 \label{sec:proof of layered hashing}
@@
 
+\noindent
 \textbf{Correctness:}  We begin by arguing correctness.
@@
 
-\subsection{Proof of \thref{thm:imposs sketch}}
+\section{Proof of \thref{thm:imposs sketch}}
 \label{sec:proof secure sketch imposs}
@@
 \label{def:shannon-code}
-Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+Let $C$ be a set over space $\mathcal{M}$.
+We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in C$, $\Pr[c'\leftarrow B_t(c) \wedge \rec(c') \neq c]\le \delta$.
 %To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
@@
 
-We now prove item in the outline of \thref{thm:imposs sketch} in turn.
+We now prove item in the outline of \thref{thm:imposs sketch}.
 
@@
 \label{lem:side info determines sketch}
-$\Hav(V | \sketch(V), Z) \le \Theta(1)$.
+$\Hav(V | \sketch(V), Z) <1$.
 \end{lemma}
@@
  As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.
-We know show there are many possible values for $Z$.
+We show having seen $V$ there are many possible values for $Z$~(and the distributions $V|Z$ have disjoint support outside of the observed point).
 The only information seen by $\sketch$ algorithm is in the point $V=v$.
@@
 We now show for any sketch algorithm, for possible values of $Z$ conditioned on $V=v$ there are few points included in the support of $V |\sketch(V)$.
-For any two values of $z_1, z_2$ the distributions $V| Z= z_1$ and $V | Z=z_2$ intersect at most one point.
 The distributions $V | Z=z_1$ and $V| Z=z_2$ for possible $z_1, z_2$~(having seen $v$) overlap only at the point $v$.
@@
 \end{align*}
-Then averaging over the possible values of $s$, we have the following as long as $t\ge 4$:
+Then averaging over the possible values of $s$, we have the following as long as $t\ge 4$~(using  \lemref{lem:log-minus-one}, which appears below):
 \begin{align*}
@@
 \end{align*}
+ \end{proof}
+
 \lnote{need for \lemref{lem:log-minus-one}:  $\gamma-1\le |F|$ and $|F|\ge 4$}
@@
 \label{lem:log-minus-one}
-For any real numbers $\alpha \leq \beta$ with $\beta \ge e+1$ (in particular, $b\ge 4$ suffices), the following holds:
+For any real numbers $\alpha \leq \beta$ with $\beta \ge e+1$ (in particular, $\beta\ge 4$ suffices), the following holds:
 $\alpha \log (\beta-1) > (\alpha-1)\log \beta$. 
@@
 $$\beta^{\alpha-1} < (\beta-1)^\alpha\,.$$
-Taking the logarithm of both sides, we get the desired result.
+Taking the logarithm of both sides yields the statement of the lemma.
 \end{proof}
-
- \end{proof}
-\noindent \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
 
@@
 \begin{proof}
-Consider some $w\in V$.
+Consider some $w\in V$ over $\zo^n$.
 Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
@@
 We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(R, P) \leftarrow \gen(V)$.
+Denote by $(\Key, P) \leftarrow \gen(V)$.
 
@@
 \[
-(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+(\Key |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
 \]
@@
 Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
-The distribution $R|P=p^*$ is the set of possible keys.
-The distribution $R|P=p^*$ induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
-Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
+The distribution $\Key|P=p^*$ is the set of possible keys.
+The distribution $\Key|P=p^*$ induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique value $\key$ such that $\rep(w, p^*) =\key$.
+Denote this partition by $Q_{p^*,\key} = \{w | \rep(w, p^*) = \key\}$.
 
 Many of these sets must be small.
-That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
+That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
+If not, there exists a set of $\key$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
 
@@
 \begin{align*}
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
+\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
 %\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
@@
 %Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient ball:\bnote{use a term other than deficient}
+We now show that for $\key \in R_{small}$ there are few points in $\inter(Q_{p^*, \key })$.
+Consider some $\key^*\in R_{small}$.
+We will use the term deficient ball:\bnote{use a term other than deficient}
 \begin{definition}
@@
 
-We now proceed to show that the interior of each $Q_{p^*, r^*}$ is small~(using the isoperimetric inequality on the Hamming space):
+We now proceed to show that the interior of each $Q_{p^*, \key^*}$ is small:
 %Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
@@
 \begin{lemma}
-$|\inter(Q_{p^*, r^*})| \le 2^{n-4\nu}$.
+$|\inter(Q_{p^*, \key^*})| \le 2^{n-4\nu}$.
 \end{lemma}
 \begin{proof}
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, r^*}$).
-We now find the size of $S_{p^*, r^*}$.
-
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}\leq |\mathcal{M}|/2$.
+By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\beta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, \key^*}$).
+We now find bound the size of $S_{p^*, \key^*}$.
+
+Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-(\kappa-1)}\leq |\mathcal{M}|/2$.
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
-This means that $|S_{p^*, r^*}|$ is a deficient sphere of radius at most $n/2-t$.
+This means that $|S_{p^*, \key^*}|$ is a deficient sphere of radius at most $n/2-t$.
 Let $X$ denote a uniform string on $\zo^n$.
@@
 \begin{align*}
-|S_{p^*, r^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}
+|S_{p^*, \key^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}
 \end{align*}
@@
 
-We have shown that $|\inter(Q_{p^*, r^*})| \le 2^{n-4\nu}$.  
-To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, r^*}$ that do not receive any points.  
-Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^t-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
+We have shown that $|\inter(Q_{p^*, \key^*})| \le 2^{n-4\nu}$.  
+To complete the proof it suffices to show that for most values of the auxiliary information $Z$ there are many parts $Q_{p^*, \key^*}$ that do not receive any points.  
+Recall that $Z$ consists of $2n/\nu$ coefficients and there are $(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}$ equally likely values for $Z$.
  As described above, the view of $\gen, \rep$ is a uniform distribution $V$.
@@
  \end{align*}
- where the inequality follows by \lemref{lem:log-minus-one}.
 Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
 
-This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, r^*}$~(other than $v$) and these values are disjoint.
+This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, \key^*}$~(other than $v$) and these values are disjoint.
 The optimum strategy is to include these values uniformly from different $Z$ values.
-Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
+Consider the set of all preimages of $R_{small}$ denoted $Q_{small} = \cup_{\key\in R_{small}} \inter(Q_{\key, p^*})$.
 Note that $Q_{small} \le 2^{n-4\nu}|R_{small}|$.
-That is, 
+We now show that the intersection between $Q_{\key, p^*}$ is small for most possible values $z$.
 \begin{align*}
-\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}\\
+\expe_z |Q_{small} \cap (V | P=p^* \wedge Z=z) | &\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}\\
 &=\frac{|R_{small}|}{2^{\nu}}.
@@
 \begin{align*}
-\Pr[D(R, P, Z) = 1] &- \Pr[D(U, P, Z) =1]=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
+\Pr[D(\Key, P, Z) = 1] &- \Pr[D(U, P, Z) =1]\\
+&=(\Pr[D(\Key, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
 &\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
@@
 The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
-
 This completes the proof of \lemref{lem:fuzz can't get key}.

### 2014-10-05 info-bounds/FuzzyExtPossibility.tex
run through body of paper

@@
 \blind{
-\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
+\author{
+Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
+Boston University and MIT Lincoln Laboratory.
 The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.
-Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.
-Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University.
-Work done in part while the author was at Boston University.
-Email: {\tt asmith@psu.edu}.
-}}
+Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.
+Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
+Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
+``Privacy Tools'' project.}}
 }
@@
 This helper value allows the key to be regenerated from a nearby point.
-Known constructions of fuzzy extractors do not provide security for most noisy distributions that occur in practice.
-
-The nonsecret helper string allows an adversary to learn the generated key if they can guess a point close to the original reading.
-A necessary condition to derive keys from a distribution is that no adversary can guess nearby points.
-We call this condition \emph{fuzzy min-entropy}.
-In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-In this work, we ask whether fuzzy min-entropy is a sufficient condition for security in the fuzzy extractor setting.
-
-A key impediment to providing security is distributional uncertainty.
-We consider two settings, first where the fuzzy extractor knows the precise distribution and second the fuzzy extractor knows the distribution comes from some family.
-We show that fuzzy min-entropy is a sufficient condition in the first setting and insufficient in the second setting.
-That is, there is families of distributions with fuzzy min-entropy that no fuzzy extractor can derive keys from.
-Our results are information-theoretic.
-
+
+The nonsecret helper string allows an adversary to learn the generated key if they can guess a point nearby to the original reading.
+A necessary condition for key derivation is hardness of guessing nearby points.
+We call the maximum probability mass of nearby points \emph{fuzzy min-entropy}.
+Many practical sources have no known construction of fuzzy extractors but have fuzzy min-entropy.
+There is evidence fuzzy min-entropy is sufficient to construct computational fuzzy extractors.\bnote{how to work in the interactive case?}
+In this work, we ask: \emph{is fuzzy min-entropy sufficient to build an information-theoretic fuzzy extractor?}
+
+We first consider a setting where the fuzzy extractor knows the precise distribution of the physical source.
+In this setting, we construct a fuzzy extractor for any distribution with fuzzy min-entropy.
+
+However, high-entropy distributions can never be fully observed and must be modeled.
+It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary may have a better model.
+Thus, fuzzy extractors are normally built for families of distributions.
+This uncertainty is an impediment to security.
+We show a family of distributions such that no fuzzy extractor can extract a single key bit out for an average member of the family.
+
+\bnote{mention secure sketches?}
 \bnote{keep editing}
+\bnote{nearby or close?  be consistent}
+\bnote{I renamed section titles to get rid of distribution aware and oblivious.  don't quite like them}
 \end{abstract}
@@
 
-The security requirement for fuzzy extractors that is $\key$ uniform even to a (computationally unbounded) adversary who has observed $p$.
+The security requirement for fuzzy extractors is that $\key$ is uniform even to a (computationally unbounded) adversary who has observed $p$.
 This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.
@@
 
-superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
+Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition). 
 However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
@@
 We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
-We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.
+We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.
 It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).
@@
 Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
-(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
+(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.
+its the same corollary}
+
+On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
 The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
@@
 For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
 We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
@@
 \paragraph{Techniques for Negative Results for Distribution Families}
-Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
+We construct a family of distributions $\mathcal{W}$ and prove impossibility for a uniformly random $W\in \mathcal{W}$~(instead of proving impossibility for a worst-case $W$).
 We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
@@
 To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.
+\bnote{this isn't quite accurate, the first coordinate is known.
+you have no info on the rest of the support}
 
 Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
-In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$.
+In the secure sketch case, $ss$ can be used to find fixed points of $\rec(\cdot, ss)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$.
 This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.
@@
 The result also relies on the majority of points lying near boundaries of a set.
-Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
+Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set is not the majority of its area.\bnote{cite cite cite!!!}
 
@@
 \label{sec:related settings}
+\bnote{this needs work}
 We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
@@
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:distribution aware}, we construct a distribution-aware fuzzy extractor for all distributions with fuzzy min-entropy.
-In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
+In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.
+In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results for secure sketches and fuzzy extractors for families of distributions respectively.
 
@@
 The set $J^c$ is the complement of $J$.
+Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
  Unless otherwise noted logarithms are base $2$.
-Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
-
 The {\em min-entropy} of $W$ is $\Hoo(W) = -\log(\max_w \Pr[W=w])$,
@@
 We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
-%\begin{definition}[Conditional Hartley Entropy]
-%\label{def:conditional hartley}
-The conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
-%\end{definition}
+the conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
 
@@
 al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.
-First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
-Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
+First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.
+Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
 %\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
 %This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
-We discuss distribution-aware algorithms in \secref{sec:distribution aware def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+We discuss known distribution algorithms in \secref{sec:known distributions def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.
 
@@
 Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.
-The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
+The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.
 Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
@@
 \begin{enumerate}
-\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
+\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
 \item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
@@
 
-\noindent In the above definitions, the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.
+\noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.
 A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:
@@
 
-In an ideal world, we could provide a reproduce functionality as an oracle.
-In this world, the key is output if a close point is provided, and no response is provided otherwise.
-We call the performance of an adversary in this ideal world fuzzy min-entropy:
+In an ideal world, $p$ is not useful to an adversary.
+The adversary's only attack method is to execute $\rep(\cdot, p)$ on different $w'$.
+In this world, $\rep$ outputs $\key$ if the input is close enough and provides no other  information.
+The security of a fuzzy extractor in this world is the maximum weight of $W$ inside a ball of radius $t$:
 
@@
 \end{definition}
-
-Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):%If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).
-We make this intuition formal:
-%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
+\noindent
+Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
 \begin{proposition}
@@
 There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
-Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.
-
-\subsection{Distribution-aware algorithms}
-\label{sec:distribution aware def}
+Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe the known distribution setting.
+
+\subsection{Known Distribution Algorithms}
+\label{sec:known distributions def}
 %To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
-We call an algorithm with complete information on the distribution $W$ \emph{distribution-aware}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
+We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
 
@@
 Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
+A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
 That is,
@@
 $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
-We assume distribution-aware algorithms are \emph{inefficient}.
-Finding a natural model of specifying distributions that allows for efficient~(yet generic) distribution-aware constructions of sketches and extractors is an interesting problem.
-
-\section{Sufficiency of $\Hfuzz(W)$ for Distribution-Aware Algorithms}
-\label{sec:distribution aware}
-In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
+We assume known distribution algorithms are \emph{inefficient}.
+Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.
+
+\section{Sufficiency of $\Hfuzz(W)$ for Known Distribution Algorithms}
+\label{sec:known distributions}
+In this section, we show it is possible to build known distribution secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
 We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.
-
-%The summary of our results is in Table~\ref{tab:upper bounds}.
-
-%\begin{table}
-%\begin{centering}
-%\begin{tabular}{l | l}
-%Class of Distribution & Residual entropy achieved by construction\\
-%\hline
-%Well-spread distribution & $\Hfuzz(W)$ \\
-%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
-%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
-%\end{tabular}
-%\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.
-Here $\delta$ denotes the probability of incorrect reconstruction and $\mathcal{M}$ is the metric space.
-Recall that $\Hfuzz(W)$ is an upper bound for the residual entropy.}
-%\label{tab:upper bounds}
-%\end{centering}
-%\end{table}
-%\bnote{I'm not convinced this table is useful}
-%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
-We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
-
 %\subsection{Well-Spread Distributions}
@@
 Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.
-However, our negative results for the distribution-oblivious setting will be for families of well-spread distributions.
-This result illustrates how different the distribution-aware and distribution-oblivious settings are.}
+However, our negative results for the family of distributions setting will be for families of well-spread distributions.
+This result illustrates how different the known distribution and family of distributions settings are.}
 %\begin{lemma}
@@
 \subsection{Secure Sketches for Flat distributions}
-In this section, we consider distributions with multiple points in each ball where points have the same probability.
-
+A distribution is flat if all points in its support have the same probability:
 \begin{definition}
@@
 Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.
+We denote the ball with the largest number of points as $B_{t, max}$.
 Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).
@@
 More precisely,
-\begin{align*}
-\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
-&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
-&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
-\end{align*}
-For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  That is, 
 \begin{align}
-\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
+\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \nonumber \\
+&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
+&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)\nonumber \\
+&= \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
 \end{align}
@@
 Skoric et al.
-previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.
+constructed secure sketches from universal hashes to correct a polynomial number of error patterns~\cite{skoric2009efficient}.
 
@@
 \label{cons:universal hash}
-Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  Let $W$ be a distribution.  We describe $\sketch_W, \rec_W$ as follows:
+Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  Let $W$ be a distribution.  Define $\sketch_W, \rec_W$ as:
 
@@
 \label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
-Let $W$ be a flat distributions with min-entropy $m$.  Then
-\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
+Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
+\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
 \end{lemma}
 \begin{corollary}
-Let $n$ be a security parameter.  
-If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
+Let $n = \log |\mathcal{M}|$.
+If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
+That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
 \end{corollary}
 
+\noindent
 \consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
@@
 For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
-Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a superlogarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
+By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.
 
 \subsection{Secure sketches for all distributions with $\Hfuzz(W)$}
-The hashing approach just described does not work for arbitrary sources.
-The reason is that some balls may have significantly more points but low overall probability.
-Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$ and let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.
+The worst-case hashing approach does not work for arbitrary sources.
+The reason is that some balls may have  many points but low total weight.
+Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.
+Let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.
 Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.
-However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B^1_t$ and the hash completely reveals the point.
-
-Dealing with non-flat distributions requires a new strategy. % The fuzzy extractor must be aware of the density of the current ball.  
+However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$ and the hash completely reveals the point.
+
+Dealing with non-flat distributions requires a new strategy. 
 Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.
@@
 It is unclear how to leverage the convex combination property in this setting.
-\bnote{I took out the discussion of the appendix, don't know if it helps}%In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
+\bnote{I took out the appendix on convex combs, didn't think it was helping}%In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
 The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
 
-As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
-We address this by describing the probability of the point $w\in W$ seen in sketch.
-Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.
-We can think of this construction as dividing the distribution $W$ into probability levels, and each component level is nearly flat.
-As long as levels are large enough, they do not reveal too much information about the stored point $W$.
-Naturally, there is a tradeoff between the number of levels and how useful the level information is to both \rep and the adversary.
+The main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
+To overcome this problem, we write the probability of $w\in W$ in the sketch output.
+To ensure this information does not completely reveal $w$ we write down $\lfloor \log \Pr[W=w] \rfloor$.
+We then use a universal hash whose output length is proportional to the number of close points of the same probability as $w$.
+This construction divides the distribution $W$ into probability levels.
+Each level is nearly flat.
 
@@
 Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.
-Let $W$ be a distribution with $\Hfuzz(W)\ge m$.
+Let $W$ be a distribution with $\Hoo(W)= m$.
 Let $\ell\in\mathbb{Z}^+$ be a parameter.
 Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell$.
-Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.
-We describe $\sketch_W, \rec_W$ as follows:
+Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.
+Define $\sketch_W, \rec_W$ as:
 \begin{center}
@@
 Let $\mathcal{M}$ be a metric space where $n = \log |\M|$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution-aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-known distribution secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
 (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
@@
 Our negative results are specific to the Hamming metric.
-\section{Impossibility of $\Hfuzz(W)$ for Distribution-Oblivious Secure Sketches}
-\label{sec:dist oblivious}
-
-In the previous section, we showed the sufficient of $\Hfuzz$ for distribution-aware algorithms.
-It is infeasible to assume that $W$ is completely known.
-Traditionally, algorithms only assume that $W$ comes from a family $\mathcal{W}$.
-In this section, we show that uncertainty of the distribution $W$ comes at a real cost.
+\section{Insufficiency of $\Hfuzz(W)$ to secure sketch from distribution families}
+\label{sec:family of dist}
+
+In the previous section, we showed the sufficiency of $\Hfuzz$ for known distribution algorithms.
+Unfortunately, it is unrealistic to assume that $W$ is completely known.
+Traditionally, algorithms deal with this uncertainty by providing security for a family of distributions $\mathcal{W}$.
+
+In this section, we show uncertainty of $W$ comes at a real cost. 
 We will show a family $\mathcal{W}$~(where each member has fuzzy min-entropy) where any secure sketch for $\mathcal{W}$ leaves almost no entropy.
@@
 \label{sec:def equiv}
-Standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{W}$.
-We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.
+%We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.
 
 The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$.
-The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.
-The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie}.
-That is, the following two player games are equivalent:
+The challenger wins if the adversary cannot guess the outcome of $W$ with high probability, and the adversary wins otherwise.
+Let $V$ is a distribution over elements of $\mathcal{W}$.
+The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces a distribution $V$ instead of a single element $W$.
+That is, the following two player games have the same equilibrium:
 
@@
 
-$V$ is a distribution over elements of $\mathcal{W}$.
-The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
+%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
 In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.
@@
 
-Our negative results will consider an adversary that specifies a distribution $V$ over $\mathcal{W}$.
+In our negative results, the adversary that specifies a distribution $V$ over $\mathcal{W}$.
 Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-That is, $(\sketch, \rec)$ sees a distribution $V$ and the adversary seeing some side information $Z$ corresponding to the distribution $W$.
+An alternate view is that $(\sketch, \rec)$ sees a distribution $V$ while the adversary sees side information $Z$~(corresponding to the distribution $W$).
 
@@
 
-\subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
+\subsection{Insufficiency of $\Hfuzz(W)$ to secure sketch from families of distributions}
 We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.
@@
 Define $V$ as the uniform distribution over $\mathcal{W}$.
-The adversary sees $V|Z$.
+The adversary sees $\sketch(V)$ and $Z$.
 $Z$ is the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+The algorithms $\sketch, \rec$ never see $Z$.
 Fix some $4\le t < \gamma$.
-We then show the following~(in \apref{sec:proof secure sketch imposs}):
+We show the following~(in \apref{sec:proof secure sketch imposs}):
 
@@
 \item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
+Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
 \item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
-\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is distribution oblivious secure sketch for the elements of $\mathcal{W}$.\end{itemize}
+\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is no secure sketch for the family $\mathcal{W}$.\end{itemize}
 \end{proof}
@@
 A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ parameters to the definition, representing the distinguishing circuit).
-By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
+By the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
 
@@
 
-\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
+\section{Insufficiency of $\Hfuzz(W)$ to fuzzy extract from distribution families}
 \label{sec:imposs fuzz ext}
@@
 Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
-We work over the binary alphabet so we squish affine lines to the binary alphabet.
-\bnote{better word than squish} Let $x_1,..., x_\nu \in \zo^\nu$.
-Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
-Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
+
+We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
+Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
 Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
 \[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
-b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
+b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
 \]
+The multiplication is in $\mathbb{F}$.
 Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
@@
 \begin{itemize}
-\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
-\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half of the $\key \in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  Specifically:
+\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half of the $\key \in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  In more detail,
 \begin{itemize}
-\item Half the keys have at most $2^{\kappa-1}$ pre images in the metric space.  Denote this set as $R_{small}$.  
+\item Half the keys have at most $2^{n- (\kappa-1)}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
 \item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
 Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.
-The only values of $V_\key$ that could be the real value of $w$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).
+All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).
 We show that most of $V_\key$ is near a boundary.
@@
 \end{itemize}
-\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is distribution oblivious fuzzy extractor for the elements of $\mathcal{W}$.
+\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is no fuzzy extractor for the family $\mathcal{W}$.
 \end{itemize}
@@
 Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
-\bnote{improve this}
+\bnote{improve this}\bnote{do we need this or is it covered in the intro?}
 \bibliographystyle{alpha}
@@
 
-\subsection{Proof of \thref{thm:imposs fuzz ext}}
+\section{Proof of \thref{thm:imposs fuzz ext}}
 \label{sec:fuzz ext proof}

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
going over proofs, still need fuzzy ext imposs

@@
 \DeclareMathOperator*{\var}{\text{Var}}
+\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 \begin{align}
-\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \nonumber \\
-&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
-&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)\nonumber \\
+\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w')\le t\} \right|* \Pr[W=w]\right) \nonumber \\
+&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w')\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
+&=\Hoo(W) -\log\left( \max_{w' \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w')\le t\} |\right)\nonumber \\
 &= \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
@@
 \end{construction}
+
+\noindent
+We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
+\[
+B_{t, i, max} = \max_{w' \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
+\]
 
@@
 \]
-Note that $D$ only provides an input and looks at the output, thus it works in the interactive setting.
+Note that $D$ only provides an input and looks at the output, thus it extends to an interactive protocol.
 Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.
@@
 Fix some $w, w'$.
-Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
-Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.
+The size of $W^*$ is at most $B_{t, max}$.
+Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
+The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
+The probability that another element $w^*$ collides is:
 \begin{align*}
@@
 \end{align*}
-Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.
+The inequality proceeds by union bound.
+The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t, max}|-1$.
 This completes the proof.
@@
 \begin{proof}
-We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
-\[
-B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
-\]
+Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.
 
 \noindent
-\textbf{Correctness:}  We begin by arguing correctness.
-We set $n = \ell$ to be the number of levels.\footnote{This proof can be carried out for an arbitrary $\ell$ but it leads to a more complicated theorem statement.}  Fix some $w, w'$.
+\textbf{Correctness:}  Fix some $w, w'$.
 If $\Pr[W=w]\le 2^{-(m+\ell)} = 2^{-(m+n)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.
-Now consider the case when $\Pr[W=w]> 2^{-(m+n)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
-Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$.
+When $\Pr[W=w]> 2^{-(m+n)}$ let $L_i^*$ be the level of $\Pr[W=w]$.
+
+Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.
 The size of $W^*$ is at most $B_{t, i, max}$.
 The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).
-Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
-The probability that another element $w^*$ is:
+The probability that another element $w^*$ matches the hash is:
 \begin{align*}
@@
 \end{align*}
-Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.
-
-\textbf{Ideal Adversary with access to Level Information:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.
-%We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.
-An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that level.
-That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.
-The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
-Note there are $n$ outcomes for $i$ so the overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
+The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t, i, max}|$.
+
+\noindent
+\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.
+
+The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.
+The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+There are $n$ outcomes for $i$.
+The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
 That is,
 \begin{align}
-\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
-&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
+\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
+&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
 &= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
@@
 First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).
-That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+m)}}\Pr[W = w] \le 2^{-m}$.
-Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.
+Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
 Then
@@
 \[
-2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+m)}}\Pr[W=w | \sketch(W)].
+2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
 \]
@@
 \end{align*}
-Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
+Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
 Combining both cases we have:
@@
 \label{sec:proof secure sketch imposs}
+Let $c'\leftarrow \neigh_t(c)$ sample a uniform point within distance $t$ of $c$.  
 The proof of \thref{thm:imposs sketch} uses the definition of a Shannon code: 
@@
 Let $C$ be a set over space $\mathcal{M}$.
-We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in C$, $\Pr[c'\leftarrow B_t(c) \wedge \rec(c') \neq c]\le \delta$.
+We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists a procedure $\rec$ such that for all $t'\le t$ and for all $c\in C$, $\Pr[c'\leftarrow \neigh_t(c) \wedge \rec(c') \neq c]\le \delta$.
 %To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
@@
 
+\noindent
 We now prove item in the outline of \thref{thm:imposs sketch}.
@@
 The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.
-Recall that $t< \gamma$.
-We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma$ and thus $\Hfuzz(W) = \Hoo(W)$.
+We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma>t$.
+This shows that $\Hfuzz(W) = \Hoo(W)$.
 Fix some $w, w'\in W$.
@@
 We do not consider these coins in our security analysis~(and thus, they can be considered private).
+\bnote{is this really okay?
+I know its just another markov but it makes me nervous}
 By the definition of correctness for $(\sketch, \rec)$, 
 \[
-\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) = w] >1-\delta.
+\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
 \]
@@
 We now show that $H_0(V | \sketch(V) = ss^*) \le (\gamma-t+1)\log |\mathbb{F}|$.
-Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.
-Thus for every value in $V|\sketch(V) = ss^*$ this is also true.
+For the sketched value $w$, $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.
+
+For every value in $V|\sketch(V) = ss^*$ this is also true.
 This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).
-In particular, this implies that for all $w_1, w_2 \in V|\sketch(V)=ss^*$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).
+This implies that for all $w_1, w_2 \in V|\sketch(V)=ss^*$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).
 That is $V|\sketch(V)=ss^*$ is a set with minimum distance at least $t$.
+
 By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.
@@
  As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.
-We show having seen $V$ there are many possible values for $Z$~(and the distributions $V|Z$ have disjoint support outside of the observed point).
+%Having seen $V$ there are many possible values for $Z$.
+Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.
  The only information seen by $\sketch$ algorithm is in the point $V=v$.
@@
  \]
-Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
-
-We now show for any sketch algorithm, for possible values of $Z$ conditioned on $V=v$ there are few points included in the support of $V |\sketch(V)$.
+Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+We now show for any sketch algorithm there are few possible values of $V|Z$ in the support of $V |\sketch(V)$.
 The distributions $V | Z=z_1$ and $V| Z=z_2$ for possible $z_1, z_2$~(having seen $v$) overlap only at the point $v$.
 This means for any $v^*\in V| \sketch(V)$ (other than the true $v$) there is at most one $z$ such that $v^*\in V | \sketch(V), Z=z$.
-Thus, the optimum strategy is to include these values uniformly from different $Z$ values.
-
+
+The optimum strategy is to include these values uniformly from different $Z$ values.
 We show this across different sketch values.
-Consider some fixed sketch value $s$ and let $h_s \overset{def}= H_0(V | \sketch(V) = s)$.
-That is, there are $2^{h_s}$ possible values for $V$ conditioned on $\sketch(V) = s$.
-Furthermore, recall that
+Consider some fixed sketch value $s$ and let $h_s= H_0(V | \sketch(V) = s)$.
+%That is, there are $2^{h_s}$ possible values for $V$ conditioned on $\sketch(V) = s$.
+Recall that 
 \[
-\log \expe_{s\in \sketch(V)} 2^{h_s} = \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \tilde{H}_0(V | \sketch(V)) %\le   (\gamma-t+1)\log |\mathbb{F}|+1.
+\tilde{H}_0(V | \sketch(V)) =  \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \log \expe_{s\in \sketch(V)} 2^{h_s} %\le   (\gamma-t+1)\log |\mathbb{F}|+1.
 \]  

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
edited the abstract

@@
 Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
-To help eliminate noise, they produce a non secret helper string.
-This helper value allows the key to be regenerated from a nearby point.
-
-The nonsecret helper string allows an adversary to learn the generated key if they can guess a point nearby to the original reading.
-A necessary condition for key derivation is hardness of guessing nearby points.
-We call the maximum probability mass of nearby points \emph{fuzzy min-entropy}.
-Many practical sources have no known construction of fuzzy extractors but have fuzzy min-entropy.
-There is evidence fuzzy min-entropy is sufficient to construct computational fuzzy extractors.\bnote{how to work in the interactive case?}
+After the initial enrollment of a secret, any sufficiently similar value will be converted to the same output key.
+Therefore, a minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret.
+
+We formalize this property of a noisy source of secrets by defining \emph{fuzzy min-entropy}.
+High fuzzy min-entropy is clearly necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
+Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
 In this work, we ask: \emph{is fuzzy min-entropy sufficient to build an information-theoretic fuzzy extractor?}
-
-We first consider a setting where the fuzzy extractor knows the precise distribution of the physical source.
-In this setting, we construct a fuzzy extractor for any distribution with fuzzy min-entropy.
-
-However, high-entropy distributions can never be fully observed and must be modeled.
-It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary may have a better model.
-Thus, fuzzy extractors are normally built for families of distributions.
-This uncertainty is an impediment to security.
-We show a family of distributions such that no fuzzy extractor can extract a single key bit out for an average member of the family.
+%\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
+%\lnote{may be use``analyzing this quantity may be more fruitful than analyzing min-entropy and error-tolerance separately''}
+
+We give a positive answer to this question when the fuzzy extractor knows the precise distribution of the physical source.
+On the other hand, because it is imprudent to assume a precise knowledge of a complicated distribution,  fuzzy extractors are typically expected to work for families of sources.
+We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.
+
+We provide similar results for secure sketches, whose goal is not to derive a key, but to recover the original secret from a nearby one.
 
@@
 \bnote{I renamed section titles to get rid of distribution aware and oblivious.  don't quite like them}
+\lnote{mention computational setting?}
+\lnote{mention the typical analysis that separates min-entropy and error-tolerance?}
 \end{abstract}

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
adding revised proof of lower bounds to appendix

@@
 Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
-To help eliminate noise, they produce a non secret helper string.
-This helper value allows the key to be regenerated from a nearby point.
-Known constructions of fuzzy extractors do not provide security for most noisy distributions that occur in practice.
-
-The nonsecret helper string allows an adversary to learn the generated key if they can guess a point close to the original reading.
-A necessary condition to derive keys from a distribution is that no adversary can guess nearby points.
-We call this condition \emph{fuzzy min-entropy}.
-In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.
-In this work, we ask whether fuzzy min-entropy is a sufficient condition for security in the fuzzy extractor setting.
-
-A key impediment to providing security is distributional uncertainty.
-We consider two settings, first where the fuzzy extractor knows the precise distribution and second the fuzzy extractor knows the distribution comes from some family.
-We show that fuzzy min-entropy is a sufficient condition in the first setting and insufficient in the second setting.
-That is, there is families of distributions with fuzzy min-entropy that no fuzzy extractor can derive keys from.
-Our results are information-theoretic.
-
+After the initial enrollment of a secret, any sufficiently similar value will be converted to the same output key.
+Therefore, a minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret.
+
+We formalize this property of a noisy source of secrets by defining \emph{fuzzy min-entropy}.
+High fuzzy min-entropy is clearly necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
+Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
+In this work, we ask: \emph{is fuzzy min-entropy sufficient to build an information-theoretic fuzzy extractor?}
+%\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
+%\lnote{may be use``analyzing this quantity may be more fruitful than analyzing min-entropy and error-tolerance separately''}
+
+We give a positive answer to this question when the fuzzy extractor knows the precise distribution of the physical source.
+On the other hand, because it is imprudent to assume a precise knowledge of a complicated distribution,  fuzzy extractors are typically expected to work for families of sources.
+We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.
+
+We provide similar results for secure sketches, whose goal is not to derive a key, but to recover the original secret from a nearby one.
+
+\bnote{mention secure sketches?}
 \bnote{keep editing}
+\bnote{nearby or close?  be consistent}
+\bnote{I renamed section titles to get rid of distribution aware and oblivious.  don't quite like them}
+\lnote{mention computational setting?}
+\lnote{mention the typical analysis that separates min-entropy and error-tolerance?}
 \end{abstract}
@@
 We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.
-Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \le \Hfuzz(W) \le \Hoo(W)-\log |B_t(\cdot)|$ with equality when $t=0$.
-
-Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in  \lemref{lem:fuzz necessary}, which formalizes the above intuition). 
-However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance.
-Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
+Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$ with equality when $t=0$.
+\bnote{I don't follow this equation, equality also for well-spread distributions}
+
+Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition). 
+However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
+Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
 This question is particularly relevant when the gap between the two sides of the inequality is high.
@@
 \paragraph{Tight Characterization for the Case of a Known Distribution}
-We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
-We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.
+We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
+We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.
 It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).
 
-This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
+This characterization justifies $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t|$.
 
@@
 We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
-Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 1-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.
+Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.
 We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart.
@@
 Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
-(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
+(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.
+its the same corollary}
+
+On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
 The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
@@
 Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball.
-Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
-
-For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.
-We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
+Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
+
+For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.
+We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
 We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
@@
 \paragraph{Techniques for Negative Results for Distribution Families}
-Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
-We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
+We construct a family of distributions $\mathcal{W}$ and prove impossibility for a uniformly random $W\in \mathcal{W}$~(instead of proving impossibility for a worst-case $W$).
+We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
 the adversary knows $W$.
 To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.
+\bnote{this isn't quite accurate, the first coordinate is known.
+you have no info on the rest of the support}
 
 Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
-In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$.
+In the secure sketch case, $ss$ can be used to find fixed points of $\rec(\cdot, ss)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$.
 This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.
@@
 
-We note that the use of a high-dimensional Hamming space is important: fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}
-
-\lnote{old two pars below this line --- do we need anything?}
-
-We construct a family of distributions $\mathcal{W}$ for which knowing only a single value $w$ leaves the remainder of the support is uniform.
-Our family $\mathcal{W}$ is the set of affine lines.
-For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.
-For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.
-However, in the Hamming space the majority of points lie near the boundary.
-Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.
-This means that $W|p$ is small.
-This is enough to break security.
-
- The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
-The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.
-The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.
-Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.
-
-\bnote{are these really affine lines?}
-\bnote{I'm writing these, very rough draft}
-
-\subsection{Sufficiency of $\Hfuzz$ in related settings}
+The result for fuzzy extractors is delicate.
+The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.
+Extending this result to imperfect correctness seems challenging and is an interesting open problem.
+The result also relies on the majority of points lying near boundaries of a set.
+Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set is not the majority of its area.\bnote{cite cite cite!!!}
+
+\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
 \label{sec:related settings}
+\bnote{this needs work}
 We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
@@
 \label{sec:preliminaries}
-For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.
+%For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.
 % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.
 The set $J^c$ is the complement of $J$.
+Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
  Unless otherwise noted logarithms are base $2$.
-Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
-
-The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
-and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
-For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
+The {\em min-entropy} of $W$ is $\Hoo(W) = -\log(\max_w \Pr[W=w])$,
+and the {\em average (conditional)} min-entropy of $W$ given $P$ is  $\Hav(W|P) = -\log(\expe_{p\in P} \max_{w} \Pr[W=w|P=p])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.
+Let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
 We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
-%\begin{definition}[Conditional Hartley Entropy]
-%\label{def:conditional hartley}
-The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
-%\end{definition}
+the conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
+
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
+For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
 We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
-\bnote{there is nothing computational here right now}
-
-For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.
-If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
+
+For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.
+If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.
 For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.
-$U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
+$U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.
 Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
@@
 
-In this section, we define of fuzzy extractors and secure sketches.
+In this section, we define fuzzy extractors and secure sketches.
 Definitions and lemmas are drawn from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.
-First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.
-Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
+al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.
+First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.
+Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
 %\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
-This is a generalization of the definition of Dodis et al.
-which require a fuzzy extractor to work for all distributions of a particular entropy.
-We cover the distribution-aware setting in \secref{sec:distribution aware}.
-Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
+We discuss known distribution algorithms in \secref{sec:known distributions def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.
 
@@
 \begin{enumerate}
-\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
-\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
+\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = \key] \geq 1-\delta$.
+\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
 \end{enumerate}
-A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
 \end{definition}
@@
 \begin{enumerate}
-\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
+\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
 \item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
-A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
 \end{definition}
 
-\noindent \textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.
-
+\noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.
 A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:
@@
 \begin{definition}
-Let $\chi_1$, $\chi_2$ be finite sets.
-A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
-of random variables $X, Y$ over $\chi_1, \chi_2$ such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
+Let $\mathcal{M}$, $\chi$ be finite sets.
+A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(\tilde{m}, \epsilon)$-average-case extractor} if for all pairs
+of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
+$\tilde{H}_\infty(X|Y) \ge \tilde{m}$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
 U_d \times Y) \le \epsilon$.
@@
 
-In an ideal world, we could provide a reproduce functionality as an oracle.
-In this world, the key is learned if a close point is provided, and no other information is leaked.
-In the rest of this work, we compare security to this ideal world.
-We call this fuzzy min-entropy:
+In an ideal world, $p$ is not useful to an adversary.
+The adversary's only attack method is to execute $\rep(\cdot, p)$ on different $w'$.
+In this world, $\rep$ outputs $\key$ if the input is close enough and provides no other  information.
+The security of a fuzzy extractor in this world is the maximum weight of $W$ inside a ball of radius $t$:
 
@@
 \label{def:fuzzy min-ent}
-A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
+The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
 \[
-\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
+\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
 \]
 \end{definition}
-
-If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).
-We make this intuition formal in the following result.
-For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
-\begin{lemma}
-\label{lem:fuzz necessary}
-Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
-\end{lemma}
-
-The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
-Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
-\lemref{lem:fuzz necessary} still applies.  
-This means that fuzzy min-entropy is also a necessary condition for interactive solution.
-As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.
-
-There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.
-There are also no known impossibility results for distributions with fuzzy min-entropy.
-Thus, the situation for fuzzy extractors is quite unclear.
-As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.
-We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.
-
-\subsection{Distribution-aware setting}
-\label{sec:distribution aware}
-To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
-We call this type of algorithm \emph{distribution-aware}.
-We provide a definition for secure sketches~(extendible to fuzzy extractors):
+\noindent
+Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
+\begin{proposition}
+\label{prop:fuzz necessary}
+Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
+If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
+ with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
+\end{proposition}
+
+%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
+%\lemref{lem:fuzz necessary} still applies.  
+\noindent
+There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
+Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe the known distribution setting.
+
+\subsection{Known Distribution Algorithms}
+\label{sec:known distributions def}
+%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
+We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
 
@@
 Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.
+A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
 That is,
@@
 $
-\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$
+\forall w\in W$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
 Correctness is guaranteed only for the support of $W$.
-\item \emph{Security:} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
 \end{enumerate}
 \end{definition}
-The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
-When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.
-It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.
-
-\section{Distribution-Aware Information-Reconciliation}
-\label{sec:distribution aware}
-In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
+$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
+We assume known distribution algorithms are \emph{inefficient}.
+Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.
+
+\section{Sufficiency of $\Hfuzz(W)$ for Known Distribution Algorithms}
+\label{sec:known distributions}
+In this section, we show it is possible to build known distribution secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
 We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.
-
-%The summary of our results is in Table~\ref{tab:upper bounds}.
-
-%\begin{table}
-%\begin{centering}
-%\begin{tabular}{l | l}
-%Class of Distribution & Residual entropy achieved by construction\\
-%\hline
-%Well-spread distribution & $\Hfuzz(W)$ \\
-%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
-%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
-%\end{tabular}
-%\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.
-Here $\delta$ denotes the probability of incorrect reconstruction and $\mathcal{M}$ is the metric space.
-Recall that $\Hfuzz(W)$ is an upper bound for the residual entropy.}
-%\label{tab:upper bounds}
-%\end{centering}
-%\end{table}
-%\bnote{I'm not convinced this table is useful}
-%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).
-We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.
-
 %\subsection{Well-Spread Distributions}
@@
 %\end{definition}
-%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).
+%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has superlogarithmic min-entropy).
 Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.
-However, our negative results for the distribution-oblivious setting will be for families of well-spread distributions.
-This result illustrates how different the distribution-aware and distribution-oblivious settings are.}
+However, our negative results for the family of distributions setting will be for families of well-spread distributions.
+This result illustrates how different the known distribution and family of distributions settings are.}
 %\begin{lemma}
@@
 More precisely,
-\begin{align*}
-\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
-&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
-&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
-\end{align*}
-For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
 \begin{align}
-\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
+\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w')\le t\} \right|* \Pr[W=w]\right) \nonumber \\
+&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w')\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
+&=\Hoo(W) -\log\left( \max_{w' \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w')\le t\} |\right)\nonumber \\
+&= \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
 \end{align}
@@
 Skoric et al.
-previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.
+constructed secure sketches from universal hashes to correct a polynomial number of error patterns~\cite{skoric2009efficient}.
 
 \begin{definition}
-Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
+Let $F : \mathcal{K} \times \mathcal{M} \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in \mathcal{M}$:
 \[
@@
 $
-
-For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
-Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).
-
-\subsection{Secure sketches for all distributions with fuzzy min-entropy}
-The hashing approach just described does not work for arbitrary sources.
-The reason is that some balls may have significantly more points but low overall probability.
-Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.
+For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
+By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.
+
+\subsection{Secure sketches for all distributions with $\Hfuzz(W)$}
+The worst-case hashing approach does not work for arbitrary sources.
+The reason is that some balls may have  many points but low total weight.
+Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.
+Let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.
 Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.
-However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.
-
-Dealing with non-flat distributions requires a new strategy. % The fuzzy extractor must be aware of the density of the current ball.  
+However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$ and the hash completely reveals the point.
+
+Dealing with non-flat distributions requires a new strategy. 
 Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.
-In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
+However, a distribution with high fuzzy min-entropy may be formed from component distributions with little or no fuzzy min-entropy.
+It is unclear how to leverage the convex combination property in this setting.
+\bnote{I took out the appendix on convex combs, didn't think it was helping}%In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
 The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
 
-As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
-We address this by describing the probability of the point $w_0\in W$ seen in sketch.
-Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.
-We can think of this construction as dividing the distribution $W$ into probability levels, and each component level is nearly flat.
-As long as levels are large enough, they do not reveal too much information about the stored point $W$.
-Naturally, there is a tradeoff between the number of levels and how useful the level information is to both \rep and the adversary.
+The main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
+To overcome this problem, we write the probability of $w\in W$ in the sketch output.
+To ensure this information does not completely reveal $w$ we write down $\lfloor \log \Pr[W=w] \rfloor$.
+We then use a universal hash whose output length is proportional to the number of close points of the same probability as $w$.
+This construction divides the distribution $W$ into probability levels.
+Each level is nearly flat.
 
@@
 
+\noindent
+We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
+\[
+B_{t, i, max} = \max_{w' \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
+\]
+
 \begin{theorem}
 \label{thm:layered hashing}
-Let $W$ be a distribution over $\mathcal{M}$.
+Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.
 Let $\delta>0$ be an function of $n$.
@@
 \label{cor:extension to fuzz ext}
-Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution-aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+Let $\mathcal{M}$ be a metric space where $n = \log |\M|$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-known distribution secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
 (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
@@
 
-\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space.
+\noindent
+In our positive results we considered an arbitrary finite metric space.
 The relevant parameters were the size of balls and the size of the metric space.
-Going forward we will consider specific metric spaces, namely the Hamming metric.
-\section{Impossibility of $\Hfuzz$ for Distribution-Oblivious Secure Sketches}
-\label{sec:dist oblivious}
-
-In the previous section, we showed the sufficient of $\Hfuzz$ for distribution-aware algorithms.
-It is infeasible to assume that $W$ is completely known.
-Traditionally, algorithms only assume that $W$ comes from a family $\mathcal{W}$.
-In this section, we show that uncertainty of the distribution $W$ comes at a real cost.
+Our negative results are specific to the Hamming metric.
+\section{Insufficiency of $\Hfuzz(W)$ to secure sketch from distribution families}
+\label{sec:family of dist}
+
+In the previous section, we showed the sufficiency of $\Hfuzz$ for known distribution algorithms.
+Unfortunately, it is unrealistic to assume that $W$ is completely known.
+Traditionally, algorithms deal with this uncertainty by providing security for a family of distributions $\mathcal{W}$.
+
+In this section, we show uncertainty of $W$ comes at a real cost. 
 We will show a family $\mathcal{W}$~(where each member has fuzzy min-entropy) where any secure sketch for $\mathcal{W}$ leaves almost no entropy.
@@
 
-Our negative results will consider an adversary that specifies a distribution $V$ over $\mathcal{W}$.
+In our negative results, the adversary that specifies a distribution $V$ over $\mathcal{W}$.
 Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-That is, $\sketch, \rec$ sees a distribution $V$ and the adversary seeing some side information $Z$ corresponding to the distribution $W$.
+An alternate view is that $(\sketch, \rec)$ sees a distribution $V$ while the adversary sees side information $Z$~(corresponding to the distribution $W$).
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.
+There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 2$ for $t\ge 4$.
 \end{theorem}
@@
 \]
-where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  
+where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i, b_i\in\mathbb{F}, a_i\neq 0$.  
 This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
 Define $V$ as the uniform distribution over $\mathcal{W}$.
-The adversary sees $V|Z$, that is, they see the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+The adversary sees $\sketch(V)$ and $Z$.
+$Z$ is the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
+The algorithms $\sketch, \rec$ never see $Z$.
 Fix some $4\le t < \gamma$.
-We then show the following~(in \apref{sec:proof secure sketch imposs}):
+We show the following~(in \apref{sec:proof secure sketch imposs}):
 
@@
 \item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
-\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
-\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is distribution oblivious secure sketch for the elements of $\mathcal{W}$.
-\end{itemize}
+Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
+\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
+\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is no secure sketch for the family $\mathcal{W}$.\end{itemize}
 \end{proof}
-\subsubsection{Feasibility of computational secure sketches}
+\bnote{should note we can decrease field size at the cost of distance.}
+\subsubsection{Implications for Computational secure sketches}
 \label{sec:feas comp sec sketch}
 Fuller et al.
-showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
 %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
-The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
+The definitional of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
 
@@
 If
-\begin{itemize}
-\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-\item $t\ge 4$,
-\item and $\epsilon + t\delta < 1/16$,
-\end{itemize}
+$s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
+$t\ge 4$, and 
+ $\epsilon_{sec} + t\delta < 1/16$,
  then $\tilde{m} =O(1)$.
@@
 
-\textbf{Note:} Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
+Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
 Our impossibility result says nothing about this weaker form of a secure sketch.
-We note that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-
-\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
+Extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+
+\section{Insufficiency of $\Hfuzz(W)$ to fuzzy extract from distribution families}
 \label{sec:imposs fuzz ext}
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
+There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 2$ such that $\epsilon \le 1/8 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
 \end{theorem}
@@
 Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
-We work over the binary alphabet so we squish affine lines to the binary realm.
-Let $x_1,..., x_\nu \in \zo^\nu$.
-Let $\mathbb{F}$ denote the field of size $2^{\nu}$.
-Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.
+
+We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
+Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
 Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
 \[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
-b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
+b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
 \]
+The multiplication is in $\mathbb{F}$.
 Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
-Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/nu}$.
-We now present of the proof~(proofs in \apref{sec:fuzz ext proof}):
+Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
+We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
 \begin{itemize}
-\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
-\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half the keys $r\in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  Specifically:
+\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half of the $\key \in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  In more detail,
 \begin{itemize}
-\item Show that for half the keys have a bounded number of pre images in the metric space.  Denote this set as $R_{small}$.  
-\item Consider some $r\in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
-Consider the set of $V_{r} = \{w | \rep(w, p) = r\}$.
-The only values of $V_r$ that could be the real value of $w$ are distance $t$ from a boundary of $V_r$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $r$).
-We show that most of $V_r$ is near a boundary.
-Harper's theorem says that the boundary of a region is minimized by a ball containing the same number of points~\cite{harper1966optimal} .
+\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
+\item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
+Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.
+All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).
+We show that most of $V_\key$ is near a boundary.
+A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short} .
 Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.
-Together these two results imply that $V_r$ is small.
+Together these two results imply that $V_\key$ is small.
 \item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
 Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_r$ is empty.
-Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
+\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).
+Thus, for most values of $Z$, keys lying in $R_{small}$ can be labeled as ``random''.
+%The previous two propositions were similar to the secure sketch counterexample.
+However, the structure on the metric space imposed byThe remainder of the proof is significantly different.
+We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
+Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
 \end{itemize}
-\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is distribution oblivious fuzzy extractor for the elements of $\mathcal{W}$.
+\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is no fuzzy extractor for the family $\mathcal{W}$.
 \end{itemize}
@@
 \textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.
-We note that the specific family $\mathcal{W}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.
+We note that the specific family $\mathcal{W}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors  for this family of distributions when $\mathbb{F}$ is large enough under weaker assumptions.
 (Their construction is stated with imperfect correctness.
@@
 \paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.
-The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
+This result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
 Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
-\bnote{improve this}
+\bnote{improve this}\bnote{do we need this or is it covered in the intro?}
 \bibliographystyle{alpha}
@@
 
-\section{Leveraging convex combinations?}
-\label{sec:convex comb}
-In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
+%\section{Leveraging convex combinations?}
+%\label{sec:convex comb}
+%\bnote{be careful uncommenting this, some notation may be out of date}
+%In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
 For example, consider the following hypothetical extension to \consref{cons:universal hash}.
-Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
-However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
-
-The proposed modification to the construction is as follows, when receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, then write down $i$ and perform the sketch as before for distribution $W_i$.
+Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_\alpha$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
+However, the problem arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
+%
+%We now describe a possible modification to the hashing construction.
+Upon receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, write $i$ and perform the sketch as before for distribution $W_i$.
 Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
-
-In the flat case, we saw it was necessary to write down the number of points in the largest ball, however, the residual entropy in this case was exactly equal to the density of the largest ball~(matching the success of the best adversary that always guesses in this ball).
-That is, the residual entropy $\Hav(W|\sketch(W)) \approx \Hfuzz(W)$.
+Unfortunately, this proposal may remove all entropy.
+%Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
+However, this is not the case.
+%
+%%In the flat case, we used a hash whose length was proportional to the number of points in the largest ball.
+The residual entropy in this case was within a superlogarithmic factor of $\Hfuzz(W)$.
 However, in the setting where $W$ is a convex combination of flat sources this does not hold.
-
-Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors, second let $W_i$ contain a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
+%
+%Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors and $W_i$ contains a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
 This distribution is illustrated in \figref{fig:convex comb}.
-
-The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
+%
+%\begin{figure}
+%
+%\centering
+%    \includegraphics[width=.9\textwidth]{convexCombExample.png}
+%    \caption{A convex combination of $W_1,..., W_\alpha$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
+%\label{fig:convex comb}    
+%\end{figure}
+%
+%
+%The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
 Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\gamma, k\}$ where $\gamma$ is the number of distributions $W_1,..., W_\gamma$.
-(For our purposes, we can assume that $\gamma$ is quite large and the probability of $w^*$ becomes the dominant factor.)
-
-Consider an input point $w\in W$.
+Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\alpha, k\}$ where $\alpha$ is the number of distributions $W_1,..., W_\gamma$.
+The value $\alpha$ may be quite large and $k$ may be the dominant factor.
+%
+%Consider an input point $w\in W$.
 One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \gamma\}$.
+It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \alpha\}$.
 For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
@@
 Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
-
-\textbf{Summary:} The fundamental problem is a distribution $W$ is guaranteed to be a convex combination of flat distributions with the same min-entropy.
-However, the fuzzy min-entropy of these distributions can be arbitrarily separated from the fuzzy min-entropy of $W$.
-That is, $\Hoo(W_i) = \Hoo(W)$ but $\Hfuzz(W_i) << \Hfuzz(W)$.
-
-In the following discussion, we present a more complicated technique that layers the distribution to make it appear flat.
-
-\begin{figure}[t]
-
-\centering
-    \includegraphics[width=.9\textwidth]{convexCombExample.png}
-    \caption{A convex combination of $W_1,..., W_\gamma$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
-\label{fig:convex comb}    
-\end{figure}
-
-\section{Proofs}
-\subsection{Proof of \lemref{lem:fuzz necessary}}
+\bnote{I removed the discussion of convex combs for the submitted version}
+
+\section{Proof of \propref{prop:fuzz necessary}}
 \label{sec:proof fuzz necessary}
@@
 Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.
-Consider the following distinguisher $D$~(note that $D$ only provides an input and looks at the output, thus this distinguisher extends to the interactive setting):
+This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] \geq 1/\poly(n)$.
+Consider the following distinguisher $D$:
 \begin{itemize}
 \item Input $r, p$.
-\item If $\rep(m^*, p) = r$, output $1$.
+\item If $\rep(w', p) = r$, output $1$.
 \item Else output $0$.
 \end{itemize}
-First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.
-Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.
-Thus, when $\kappa = \omega(\log n)$:
+Clearly, $\Pr[D(\Key, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
 \[
@@
 \]
+Note that $D$ only provides an input and looks at the output, thus it extends to an interactive protocol.
+Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.
+Thus, $D$ is also a distinguisher in the computational setting.
 \end{proof}
 
-\subsection{Proof of \lemref{lem:flat hashing}}
+\section{Proof of \lemref{lem:flat hashing}}
 \label{sec:proof of flat hashing}
@@
 
-\subsection{Proof of \thref{thm:layered hashing}}
+\section{Proof of \thref{thm:layered hashing}}
 \label{sec:proof of layered hashing}
 \begin{proof}
-We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
-\[
-B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
-\]
-
-\textbf{Correctness:}  We begin by arguing correctness.
-We set $n = \ell$ to be the number of levels.\footnote{This proof can be carried out for an arbitrary $\ell$ but it leads to a more complicated theorem statement.}  Fix some $w, w'$.
+Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.
+
+\noindent
+\textbf{Correctness:}  Fix some $w, w'$.
 If $\Pr[W=w]\le 2^{-(m+\ell)} = 2^{-(m+n)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.
-Now consider the case when $\Pr[W=w]> 2^{-(m+n)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
-Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$.
+When $\Pr[W=w]> 2^{-(m+n)}$ let $L_i^*$ be the level of $\Pr[W=w]$.
+
+Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.
 The size of $W^*$ is at most $B_{t, i, max}$.
 The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).
-Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
-The probability that another element $w^*$ is:
+The probability that another element $w^*$ matches the hash is:
 \begin{align*}
@@
 \label{sec:proof secure sketch imposs}
-The proof of \thref{thm:imposs sketch} uses ideas from coding theory.  We review the definition of a Shannon code: 
+Let $c'\leftarrow \neigh_t(c)$ sample a uniform point within distance $t$ of $c$.  
+The proof of \thref{thm:imposs sketch} uses the definition of a Shannon code: 
 \begin{definition}
 \label{def:shannon-code}
-Let $\mathcal{C}$ be a set over space $\mathcal{M}$.
-We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
+Let $C$ be a set over space $\mathcal{M}$.
+We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists a procedure $\rec$ such that for all $t'\le t$ and for all $c\in C$, $\Pr[c'\leftarrow \neigh_t(c) \wedge \rec(c') \neq c]\le \delta$.
 %To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
@@
 
-We now prove item in the outline of \thref{thm:imposs sketch} in turn.
+\noindent
+We now prove item in the outline of \thref{thm:imposs sketch}.
 
@@
 \label{lem:side info determines sketch}
-$\Hav(V | \sketch(V), Z) \le \Theta(1)$.
+$\Hav(V | \sketch(V), Z) <2$.
 \end{lemma}
@@
  As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.
-We know show there are many possible values for $Z$.
+%Having seen $V$ there are many possible values for $Z$.
+Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.
  The only information seen by $\sketch$ algorithm is in the point $V=v$.
@@
  \]
-Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
-
-We now show for any sketch algorithm, for possible values of $Z$ conditioned on $V=v$ there are few points included in the support of $V |\sketch(V)$.
-For any two values of $z_1, z_2$ the distributions $V| Z= z_1$ and $V | Z=z_2$ intersect at most one point.
+Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
+
+We now show for any sketch algorithm there are few possible values of $V|Z$ in the support of $V |\sketch(V)$.
 The distributions $V | Z=z_1$ and $V| Z=z_2$ for possible $z_1, z_2$~(having seen $v$) overlap only at the point $v$.
 This means for any $v^*\in V| \sketch(V)$ (other than the true $v$) there is at most one $z$ such that $v^*\in V | \sketch(V), Z=z$.
-Thus, the optimum strategy is to include these values uniformly from different $Z$ values.
-
+
+The optimum strategy is to include these values uniformly from different $Z$ values.
 We show this across different sketch values.
-Consider some fixed sketch value $s$ and let $h_s \overset{def}= H_0(V | \sketch(V) = s)$.
-That is, there are $2^{h_s}$ possible values for $V$ conditioned on $\sketch(V) = s$.
-Furthermore, recall that
+Consider some fixed sketch value $s$ and let $h_s= H_0(V | \sketch(V) = s)$.
+%That is, there are $2^{h_s}$ possible values for $V$ conditioned on $\sketch(V) = s$.
+Recall that 
 \[
-\log \expe_{s\in \sketch(V)} 2^{h_s} = \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \tilde{H}_0(V | \sketch(V)) %\le   (\gamma-t+1)\log |\mathbb{F}|+1.
+\tilde{H}_0(V | \sketch(V)) =  \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \log \expe_{s\in \sketch(V)} 2^{h_s} %\le   (\gamma-t+1)\log |\mathbb{F}|+1.
 \]  
@@
 Consider these possible values for $Z$ as bins to be filled with the $2^{h_{ss}}$ balls~(possible values of $V | \sketch(V)=ss$).
+Each bin receives automatically receives one free point~(all the distributions share $v$).
 The average number of balls in each bin is maximized when the bins are filled equally.
@@
 \begin{align*}
-\tilde{H}_0(V |Z  , \sketch(V) = ss) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
-&= \log \left(\frac{2^{h_{ss}}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)
+\tilde{H}_0(V |Z  , \sketch(V) = ss) &\le \log \left(\frac{\text{\# balls}+\text{\# bins}}{\text{\# bins}}\right)\\
+&= \log \left(\frac{2^{h_{ss}}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} +1 \right)
 \end{align*}
-Then averaging over the possible values of $s$, we have the following as long as $t\ge 4$:
+Then averaging over the possible values of $s$, we have the following as long as $t\ge 4$~(using  \lemref{lem:log-minus-one}, which appears below):
 \begin{align*}
 \tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V |  \sketch(V) =ss , (Z| \sketch(V) =ss) )}\\
-&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)\\
-&= \log \frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\\
-&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \log \expe_{s\in \sketch(V)} 2^{h_s}\\
-&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V))\\ 
-&\le \log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + (\gamma-t+1)\log |\mathbb{F}|+1\\
-&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+1\\
-&< (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}| +1 \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
-&\le (4-t)\log |\mathbb{F}| +1\\
-& <1\,.
+&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} +1\right)\\
+&\le \max\left\{ \log \left(\frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\right)+1, 1\right\}.
 \end{align*}
+Where the inequality follows because $\log x+1 \le \max\{ 1+ \log x,1\}$.
+The left operand to $\max$ is bounded by $2$~(bounded the $\max$ by $2$):
+\begin{align*}
+\log \left(\frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\right)+1
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \log \left(\expe_{s\in \sketch(V)} 2^{h_s}\right) +1\\
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V)) +1 \\ 
+&\le \log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + (\gamma-t+1)\log |\mathbb{F}|+2\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+2\\
+&< (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}| +2 \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
+&\le (4-t)\log |\mathbb{F}| +2< 2\,.
+\end{align*}
+\end{proof}
+
 \lnote{need for \lemref{lem:log-minus-one}:  $\gamma-1\le |F|$ and $|F|\ge 4$}
@@
 \begin{proof}
-Consider some fixed $W\in\mathcal{W}$.
-The bits $w_{1,..., \nu}$ are uniform, so $\Hoo(W) =\omega(\log n)$.
-Recall that $t=o (n/\nu)$.
-We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.
+Consider some fixed $W\in\mathcal{W}$.  The bits $w_{1,..., \nu}$ are uniform, so $\Hoo(W) =\omega(\log n)$.  Recall that $t=o (n/\nu)$. 
+ %We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.  
 Fix some $w, w'\in W$.
@@
 \begin{proof}
-Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
-The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
+Consider some $w\in V$ over $\zo^n$.
+Then $w\leftarrow W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are random.
 \end{proof}
-
-The previous two propositions were similar to the secure sketch case.
-The remainder of the proof is significantly different.
-We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
-Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
 
@@
 \label{lem:fuzz can't get key}
-Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 1$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\ngl(n)$.
+Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\ngl(n)$.
 \end{lemma}
 \begin{proof}
-We assume that $\rep$ is deterministic in our analysis.
+We assume that $\rep$ is deterministic.
 Any randomness necessary for the \rep algorithm can be provided by $\gen$.
 We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(R, P) \leftarrow \gen(V)$.
+Denote by $(\Key, P) \leftarrow \gen(V)$.
 
@@
 Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
-The distribution $R|P=p^*$ is the set of possible keys.
-The distribution $R|P=p^*$ induces a partition on the metric space.
-That is, for every $w\in\mathcal{M}$, there exists a unique value $r$ such that $\rep(w, p^*) =r$.
-Denote this partition by $Q_{p^*,r} = \{w | \rep(w, p^*) = r\}$.
-
-Many of these sets must be small.
-That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $r\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $r$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
-
+The distribution $\Key|P=p^*$ is the set of possible keys.
+The distribution $\Key|P=p^*$ induces a partition on the metric space.
+That is, for every $w\in\mathcal{M}$, there exists a unique value $\key$ such that $\rep(w, p^*) =\key$.
+Denote this partition by $Q_{p^*,\key} = \{w | \rep(w, p^*) = \key\}$.
+
+There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.
+If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
 For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
-We first define the interior of a set:%Define two sets, called the interior and crust respectively: \bnote{change term crust?}
+Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.
+These are the interior of $Q_{p^*, r}$:
 \begin{align*}
-\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\},\\
+\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
 %\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
@@
 %Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We now show that for $r\in R_{small}$ there are few points in $\inter(Q_{p^*, r})$.  Consider some $r^*\in R_{small}$.  We will use the term deficient ball:\bnote{use a term other than deficient}
+We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.
+We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient}
 \begin{definition}
@@
 
-We now proceed to show that the interior of each $Q_{p^*, r^*}$ is small~(using the isoperimetric inequality on the Hamming space):
+Consider some $\key^*\in R_{small}$.  
+We now proceed to show that the interior of each $Q_{p^*, \key^*}$ is small:
 %Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
@@
 \begin{lemma}
-$|\inter(Q_{p^*, r^*})| \le 2^{n-4\nu}$.
+$|\inter(Q_{p^*, \key^*})| \le 2^{n-4\nu}$.
 \end{lemma}
 \begin{proof}
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal})\bnote{better citation?}, there exists a $\beta$-deficient ball $S_{p^*, r^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, r^*}| = |\inter(Q_{p^*, r^*})|$, $|D| = |Q_{p^*, r^*}^\complement|$ and $\forall s\in S_{p^*, r^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, r^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, r^*}$).
-We now find the size of $S_{p^*, r^*}$.
-
-Recall that $|S_{p^*, r^*} \cup D| = |Q_{p^*, r^*} | \le 2^{n-(\kappa-1)}\leq |\mathcal{M}|/2$.
+By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\beta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\beta+t$).
+We now find bound the size of $S_{p^*, \key^*}$.
+
+Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
-This means that $|S_{p^*, r^*}|$ is a deficient sphere of radius at most $n/2-t$.
+This means that $|S_{p^*, \key^*}|$ is a deficient sphere of radius at most $n/2-t$.
 Let $X$ denote a uniform string on $\zo^n$.
@@
 That is,
- \[
- \forall v, H_0(Z | V=v) =\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right) = \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} >\log  \frac{(2^{n/\nu})^{\nu-2}}{2^{\nu}}  \log \frac{2^{(n-2\nu))}}{2^\nu} = n -3\nu.
- \]
- where the inequality follows by \lemref{lem:log-minus-one}.
+ \begin{align*}
+ \forall v, H_0(Z | V=v) &=\log \left(\frac{(2^{n/\nu}-1)^{\nu-1} 2^{n-\nu}}{2^n} \right)\\
+  &= \log \frac{(2^{n/\nu}-1)^{\nu-1}}{2^{\nu}} \\
+  &>\log  \frac{(2^{n/\nu})^{\nu-2}}{2^{\nu}} \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
+  &=\log \frac{2^{(n-2\nu))}}{2^\nu} = n -3\nu.
+ \end{align*}
 Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
 
-This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, r^*}$~(other than $v$) and these values are disjoint.
+This means that the $\gen$ algorithm may include points for possible $Z$ values into parts $Q_{p^*, \key^*}$~(other than $v$) and these values are disjoint.
 The optimum strategy is to include these values uniformly from different $Z$ values.
-Consider the set of $r^*$ with small support, that is $Q_{small} = \cup_{r\in R_{small}} \inter(Q_{r, p^*})$.
+Consider the set of all preimages of $R_{small}$ denoted $Q_{small} = \cup_{\key\in R_{small}} \inter(Q_{\key, p^*})$.
 Note that $Q_{small} \le 2^{n-4\nu}|R_{small}|$.
-That is, 
+We now show that the intersection between $Q_{\key, p^*}$ is small for most possible values $z$.
+As before each bin~(the values of $z$)  receives one ball for free~(the point $v$).
 \begin{align*}
-\expe_z |Q_{small} \cap V | P=p^* \wedge Z=z | &\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}\\
-&=\frac{|R_{small}|}{2^{\nu}}.
+\expe_z |Q_{small} \cap (V | P=p^* \wedge Z=z) | &\le \left(\frac{\text{\# balls}+\text{\# bins}}{\text{\# bins}}\right)\\
+&\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}+1\\
+&=\frac{|R_{small}|}{2^{\nu}}+1
 \end{align*}
-Thus, at most $1/2^{\nu} = \ngl(n)$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
+In expectation across $Z$, 
+\[\frac{\frac{|R_{small}|}{2^{\nu}}+1}{|R_{small}|} \le \frac{1}{2^\nu}+\frac{1}{|R_{small}|} \] fraction of $R_{small}$ receive any support.
+%Thus, at most $1+1/2^{\nu} = \ngl(n)$ keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
 We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
@@
 \begin{align*}
-\Pr[D(R, P, Z) = 1] &- \Pr[D(U, P, Z) =1]=(\Pr[D(R, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
+\Pr[D(\Key, P, Z) = 1] &- \Pr[D(U, P, Z) =1]\\
+&=(\Pr[D(\Key, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
 &\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
 &\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/2-\ngl(n)\right) = 1/4-\ngl(n).
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|R_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in R_{small}]\right) - \Pr[U\not\in R_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in R_{small}] \right)\\
+&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/4-\ngl(n)\right) \ge \frac{1}{8}-\ngl(n).
 \end{align*}
-The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
-
+The sixth line follows since $R_{small} \ge 2^{\kappa-1}\ge 2$.  The eighth line follows because $\Pr[U\in R_{small}]\ge 1/2$.  The last inequality proceeds because $\Pr[P\in A_p]\ge 1/2$.
 This completes the proof of \lemref{lem:fuzz can't get key}.

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
abstract rewording

@@
 Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
-After the initial enrollment of a secret, any sufficiently similar value will be converted to the same output key.
-Therefore, a minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret.
-
-We formalize this property of a noisy source of secrets by defining \emph{fuzzy min-entropy}.
-High fuzzy min-entropy is clearly necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
+A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
+We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
+
+High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
 Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
-In this work, we ask: \emph{is fuzzy min-entropy sufficient to build an information-theoretic fuzzy extractor?}
+In this work, we ask: \emph{is fuzzy min-entropy sufficient to build information-theoretic fuzzy extractors?}
 %\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
@@
 We give a positive answer to this question when the fuzzy extractor knows the precise distribution of the physical source.
-On the other hand, because it is imprudent to assume a precise knowledge of a complicated distribution,  fuzzy extractors are typically expected to work for families of sources.
+On the other hand, because it is imprudent to assume precise knowledge of a complicated distribution,  fuzzy extractors are typically designed to work for families of sources.
 We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.
 
-We provide similar results for secure sketches, whose goal is not to derive a key, but to recover the original secret from a nearby one.
+We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.
 
@@
 We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.
-Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$ with equality when $t=0$.
-\bnote{I don't follow this equation, equality also for well-spread distributions}
+Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.
 
@@
 The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
+
+\subsection{Our Techniques}
 
@@
 
-The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$.
+The security game of a fuzzy extractor for a family of distributions $\mathcal{W}$ can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$.
 The challenger wins if the adversary cannot guess the outcome of $W$ with high probability, and the adversary wins otherwise.
@@
 Let $\mathcal{W}$ be a family of distributions.
-If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
+Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
 Let $V$ be a distribution over $\mathcal{W}$.

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
moving definitional equivalence to appendix

@@
 \newpage
-\tableofcontents\newpage
+%\tableofcontents\newpage
 
@@
 Let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
-We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
-the conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
+We use an average case of remaining support size $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.
 
@@
 \noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.
-A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:
+A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average case randomness extractor}:
 
@@
 Let $\mathcal{M}$, $\chi$ be finite sets.
-A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(\tilde{m}, \epsilon)$-average-case extractor} if for all pairs
+A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(\tilde{m}, \epsilon)$-average case extractor} if for all pairs
 of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
@@
 \label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average-case extractor.
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average case extractor.
 Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
@@
 
-In the previous section, we showed the sufficiency of $\Hfuzz$ for known distribution algorithms.
+In the previous section, we showed the sufficiency of $\Hfuzz(W)$ for known distribution algorithms.
 Unfortunately, it is unrealistic to assume that $W$ is completely known.
@@
 In this section, we show uncertainty of $W$ comes at a real cost.
-We will show a family $\mathcal{W}$~(where each member has fuzzy min-entropy) where any secure sketch for $\mathcal{W}$ leaves almost no entropy.
-A key aspect is formalizing the difference between the views of the fuzzy extractor~(which knows the family $\mathcal{W}$ and the sample $w$) and the view of the adversary~(knows the particular distribution $W$ but not the sample $w$).
-
-\subsection{A definitional equivalence}
-\label{sec:def equiv}
-%We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.
-
-The security game of a fuzzy extractor for a family of distributions $\mathcal{W}$ can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$.
-The challenger wins if the adversary cannot guess the outcome of $W$ with high probability, and the adversary wins otherwise.
-Let $V$ is a distribution over elements of $\mathcal{W}$.
-The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces a distribution $V$ instead of a single element $W$.
-That is, the following two player games have the same equilibrium:
-
-%More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
-We provide two formulations of a two player game.\footnote{We denote the outcome of the game as a reward to each player.
-This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
-This is to apply results from game theory.}
-
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
-$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
-If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge \tilde{m}$ reward $(1, -1)$\\
-Else reward $(-1, 1)$.
-\end{tabbing} 
-\vspace{.065in}
-\end{minipage}  &
-\begin{minipage}{3in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
-$V \leftarrow \mathcal{A}(\mathcal{W})$\\
-$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
-$W \leftarrow V$\\
-If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge \tilde{m}$ reward $(1, -1)$\\
-Else reward $(-1, 1)$.
-\end{tabbing}
-\end{minipage}
-\end{tabular}
-\end{center}
-
-%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
-In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.
-
-\begin{lemma}
-\label{lem:quant switch fuzz}
-Let $\mathcal{W}$ be a family of distributions.
-Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-Let $V$ be a distribution over $\mathcal{W}$.
-Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
-If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
-\end{lemma}
-
-In our negative results, the adversary that specifies a distribution $V$ over $\mathcal{W}$.
-Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-An alternate view is that $(\sketch, \rec)$ sees a distribution $V$ while the adversary sees side information $Z$~(corresponding to the distribution $W$).
-
-\begin{corollary}
-\label{cor:no fuzz for dist}
-Let $\mathcal{W}$ be a family of distributions.
-Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.
-If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-\end{corollary}
-
-Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
-
-\subsection{Insufficiency of $\Hfuzz(W)$ to secure sketch from families of distributions}
+The security game of a fuzzy extractor can be thought of as a three stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary sees $(\sketch, \rec)$ and specifies $W\in \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W))< \tilde{m}$.
+We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W\leftarrow \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W)) < \tilde{m}$.
+
+Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
+Let $Z$ be the description of which $W$ was sampled.
+The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$ where $Z$ is the description of which $W$ was sampled.
+Our results rule out security for an average member of $\mathcal{W}$.
+It may be possible to improve parameters by ruling out only a worst case $W$.
+In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.
+
 We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 2$ for $t\ge 4$.
+There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta <1/4$ and $t\ge 4$ then $\tilde{m}<2$.
+
+Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.  Then, 
+\[
+\Hav(V|\sketch(V), Z)< 2.
+\]
 \end{theorem}
@@
 \begin{proof}
+We prove the stronger average case statement.
 We first describe a family $\mathcal{W}$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
@@
 This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
-Define $V$ as the uniform distribution over $\mathcal{W}$.
+Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.
 The adversary sees $\sketch(V)$ and $Z$.
@@
 \item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
-\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is no secure sketch for the family $\mathcal{W}$.\end{itemize}
+\end{itemize}
 \end{proof}
-\bnote{should note we can decrease field size at the cost of distance.}
+\noindent
+\textbf{Note:} There is tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.
+By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
 \subsubsection{Implications for Computational secure sketches}
@@
  $\epsilon_{sec} + t\delta < 1/16$,
- then $\tilde{m} =O(1)$.
+ then $\tilde{m} <4$.
 \end{corollary}
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 2$ such that $\epsilon \le 1/8 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
+There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$.
+Let $\kappa \ge 2$, $t = \omega(n^{1/2}\log n)$.
+Any $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.
+
+Furthermore, this is true on average.
+Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.
+Let $(\Key, P)\leftarrow \gen(V)$.
+Then,
+\[
+\sd ((\Key,P, Z), (U_\kappa, P, Z))>1/8-\ngl(n).
+\]
+
 \end{theorem}
@@
 \begin{proof}[Proof Outline]
+We prove the stronger average case statement.
+Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
+
 Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
-In particular, we need to assume a larger error tolerance.
-Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.
-Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
-
 We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
@@
 The multiplication is in $\mathbb{F}$.
-Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
-Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
+Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
+Let $\mathcal{W}$ be the set of all such $W$.
+
+ Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.
+The adversary sees $\sketch(V)$ and which distribution was sampled, call this information $Z$.
+$Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
+
 We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
@@
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
-\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half of the $\key \in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  In more detail,
+\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
 \begin{itemize}
@@
 We show that most of $V_\key$ is near a boundary.
-A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short} .
+A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short}.
 Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.
@@
 \item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).
-Thus, for most values of $Z$, keys lying in $R_{small}$ can be labeled as ``random''.
+Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
 %The previous two propositions were similar to the secure sketch counterexample.
@@
 \end{itemize}
-\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is no fuzzy extractor for the family $\mathcal{W}$.
 \end{itemize}
@@
 This result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.
-Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).
-\bnote{improve this}\bnote{do we need this or is it covered in the intro?}
+The secure sketch counter example needs $t=4$ and allows the $\rec$ to be wrong almost $1/4$ of the time.
 \bibliographystyle{alpha}
@@
 
+\section{A Definitional Equivalence}
+\label{sec:def equiv}
+%We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.
+
+As described in \secref{sec:family of dist}, our negative results rule out security for an average member of $\mathcal{W}$.
+It may be possible to significantly improve parameters by only ruling out security for a single member $W$.
+
+Recall the security game of a fuzzy extractor: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$ 3) The challenger wins if $\Hav(W|\sketch(W))\ge \tilde{m}$.
+Instead of just thinking of the uniform distribution over $\mathcal{W}$, consider an arbitrary distribution $V$ over elements of $\mathcal{W}$.
+The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces $V$ instead of a single element $W$.
+That is, the following two player games have the same equilibrium:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
+$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
+If $W\not\in \mathcal{W}$, $\mathcal{C}$ wins.\\
+If $\Hav(W | \sketch(W))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
+Else $\mathcal{A}$ wins.
+\end{tabbing} 
+\vspace{.065in}
+\end{minipage}  &
+\begin{minipage}{3in}
+\begin{tabbing}
+123\=123\=123\=123\=123\=\kill
+\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
+$V \leftarrow \mathcal{A}(\mathcal{W})$\\
+$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
+$W \leftarrow V$\\
+If $W\not\in \mathcal{W}$, $\mathcal{C}$ wins.\\
+If $\Hav(W | \sketch(W))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
+Else $\mathcal{A}$ wins.
+\end{tabbing}
+\end{minipage}
+\end{tabular}
+\end{center}
+
+%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
+In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.
+This means that showing security for a family of distributions $\mathcal{W}$ is equivalent to showing security for all  distributions $V$ when the distribution is known to the algorithms $V$.
+In our negative results, the adversary  uses the uniform distribution $V$ over $\mathcal{W}$.
+However, it may be possible to improve parameters by using a different $V$.
+This would just rule out some member of $\mathcal{W}$ not an average member.
+This is true for fuzzy extractors as well and holds changes in parameters including imperfect correctness.
+
+%Since the distribution used in our negative results was uniform it is stronger, ruling out security for an average $\mathcal{W}$.  However, constructing a nonuniform $V$ may improve these results.
+%\begin{lemma}
+%\label{lem:quant switch fuzz}
+%Let $\mathcal{W}$ be a family of distributions.
+If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
+Let $V$ be a distribution over $\mathcal{W}$.
+Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
+If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
+%\end{lemma}
+
+%\begin{corollary}
+%\label{cor:no fuzz for dist}
+%Let $\mathcal{W}$ be a family of distributions.
+Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.
+If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
+%\end{corollary}
+%
+%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
 \section{Proof of \propref{prop:fuzz necessary}}
@@
 Any randomness necessary for the \rec algorithm can be provided by \sketch.
-We do not consider these coins in our security analysis~(and thus, they can be considered private).
-\bnote{is this really okay?
-I know its just another markov but it makes me nervous}
+This is the same as considering $\rep$ that outputs any coin it flips.
+Since $w, w'$ are independent of $p$ this does not effect correctness.
+Security is defined based on the output of $\rec$ so outputting the coins of $\rep$ does not effect security.
 By the definition of correctness for $(\sketch, \rec)$, 
@@
 \end{align*}
-Where the inequality follows because $\log x+1 \le \max\{ 1+ \log x,1\}$.
+Where the inequality follows because $\log x+1 \le \max\{ 1+ \log x,1\}$ for $x\ge 0$.
 The left operand to $\max$ is bounded by $2$~(bounded the $\max$ by $2$):
@@
 \begin{proof}
-We assume that $\rep$ is deterministic.
-Any randomness necessary for the \rep algorithm can be provided by $\gen$.
-We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(\Key, P) \leftarrow \gen(V)$.
-
-%By the definition of correctness for $(\sketch, \rec)$, 
-%\[
-%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
-%\]
-%For most $p$, $\rec$ works on most neighbors of $w$.  
-%Fix some $w$.  
+As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
 By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
@@
 \begin{align*}
-|S_{p^*, \key^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr[ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}
+|S_{p^*, \key^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr_{X\leftarrow \zo^n} [ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}
 \end{align*}

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
changing notation from balls/bins

@@
 \hline
-Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
+Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})\\
 \hline
@@
 We show comparable, but stronger, results for secure sketches.
-Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
+Namely, we show in \corref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
 (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.
@@
 Our negative results are specific to the Hamming metric.
-\section{Insufficiency of $\Hfuzz(W)$ to secure sketch from distribution families}
+\section{Impossibility of secure sketches for all families with $\Hfuzz$}
 \label{sec:family of dist}
 
-In the previous section, we showed the sufficiency of $\Hfuzz$ for known distribution algorithms.
+In the previous section, we showed the sufficiency of $\Hfuzz(W)$ for known distribution algorithms.
 Unfortunately, it is unrealistic to assume that $W$ is completely known.
@@
 In this section, we show uncertainty of $W$ comes at a real cost.
-We will show a family $\mathcal{W}$~(where each member has fuzzy min-entropy) where any secure sketch for $\mathcal{W}$ leaves almost no entropy.
-A key aspect is formalizing the difference between the views of the fuzzy extractor~(which knows the family $\mathcal{W}$ and the sample $w$) and the view of the adversary~(knows the particular distribution $W$ but not the sample $w$).
-
-\subsection{A definitional equivalence}
-\label{sec:def equiv}
-%We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.
-
-The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$.
-The challenger wins if the adversary cannot guess the outcome of $W$ with high probability, and the adversary wins otherwise.
-Let $V$ is a distribution over elements of $\mathcal{W}$.
-The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces a distribution $V$ instead of a single element $W$.
-That is, the following two player games have the same equilibrium:
-
-%More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively.
-We provide two formulations of a two player game.\footnote{We denote the outcome of the game as a reward to each player.
-This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.
-This is to apply results from game theory.}
-
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
-$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
-If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge \tilde{m}$ reward $(1, -1)$\\
-Else reward $(-1, 1)$.
-\end{tabbing} 
-\vspace{.065in}
-\end{minipage}  &
-\begin{minipage}{3in}
-\begin{tabbing}
-123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
-$V \leftarrow \mathcal{A}(\mathcal{W})$\\
-$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
-$W \leftarrow V$\\
-If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
-If $\Hav(W | \sketch(W))\ge \tilde{m}$ reward $(1, -1)$\\
-Else reward $(-1, 1)$.
-\end{tabbing}
-\end{minipage}
-\end{tabular}
-\end{center}
-
-%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
-In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.
-
-\begin{lemma}
-\label{lem:quant switch fuzz}
-Let $\mathcal{W}$ be a family of distributions.
-If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-Let $V$ be a distribution over $\mathcal{W}$.
-Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
-If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
-\end{lemma}
-
-In our negative results, the adversary that specifies a distribution $V$ over $\mathcal{W}$.
-Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.
-An alternate view is that $(\sketch, \rec)$ sees a distribution $V$ while the adversary sees side information $Z$~(corresponding to the distribution $W$).
-
-\begin{corollary}
-\label{cor:no fuzz for dist}
-Let $\mathcal{W}$ be a family of distributions.
-Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.
-If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-\end{corollary}
-
-Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
-
-\subsection{Insufficiency of $\Hfuzz(W)$ to secure sketch from families of distributions}
+The security game of a fuzzy extractor can be thought of as a three stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary sees $(\sketch, \rec)$ and specifies $W\in \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W))< \tilde{m}$.
+We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W\leftarrow \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W)) < \tilde{m}$.
+
+Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
+Let $Z$ be the description of which $W$ was sampled.
+The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$ where $Z$ is the description of which $W$ was sampled.
+Our results rule out security for an average member of $\mathcal{W}$.
+It may be possible to improve parameters by ruling out only a worst case $W$.
+In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.
+
 We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.
+There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta <1/4$ and $t\ge 4$ then $\tilde{m}<2$.
+
+Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.  Then, 
+\[
+\Hav(V|\sketch(V), Z)< 2.
+\]
 \end{theorem}
@@
 Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
-\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
-\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is no secure sketch for the family $\mathcal{W}$.\end{itemize}
+\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
+\end{itemize}
 \end{proof}
-\bnote{should note we can decrease field size at the cost of distance.}
-\subsubsection{Implications for Computational secure sketches}
+\noindent
+\textbf{Note:} There is tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.
+By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
+\subsection{Implications for Computational secure sketches}
 \label{sec:feas comp sec sketch}
@@
 %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
-The definitional of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
+The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
 
@@
 
-A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ parameters to the definition, representing the distinguishing circuit).
+A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ to the definition, representing the distinguishing circuit).
 By the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
@@
 
-\section{Insufficiency of $\Hfuzz(W)$ to fuzzy extract from distribution families}
+\section{Impossibility of fuzzy extractors for all families with $\Hfuzz$}
 \label{sec:imposs fuzz ext}
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$.
+There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$.
+Let $\kappa \ge 2$, $t = \omega(n^{1/2}\log n)$.
+Any $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.
+
+Furthermore, this is true on average.
+Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.
+Let $(\Key, P)\leftarrow \gen(V)$.
+Then,
+\[
+\sd ((\Key,P, Z), (U_\kappa, P, Z))>1/8-\ngl(n).
+\]
+
 \end{theorem}
@@
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
-\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half of the $\key \in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  In more detail,
+\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
 \begin{itemize}
-\item Half the keys have at most $2^{n- (\kappa-1)}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
+\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
 \item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
@@
 Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
-\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ is empty.
-Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
+\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).
+Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
+%The previous two propositions were similar to the secure sketch counterexample.
+However, the structure on the metric space imposed byThe remainder of the proof is significantly different.
+We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
+Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
 \end{itemize}
-\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is no fuzzy extractor for the family $\mathcal{W}$.
 \end{itemize}
@@
 \label{lem:side info determines sketch}
-$\Hav(V | \sketch(V), Z) <1$.
+$\Hav(V | \sketch(V), Z) <2$.
 \end{lemma}
@@
 Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.
-Consider these possible values for $Z$ as bins to be filled with the $2^{h_{ss}}$ balls~(possible values of $V | \sketch(V)=ss$).
-The average number of balls in each bin is maximized when the bins are filled equally.
-That is, the average number of balls in each bin is bounded by the number of balls divided by the number of bins.
+Consider these possible values for $Z$ as containers to be filled with the $2^{h_{ss}}$ items~(possible values of $V | \sketch(V)=ss$).
+Each container receives automatically receives one free point~(all the distributions share $v$).
+The average number of items in each container is maximized when the containers are filled equally.
+That is, the average number of items in each container is bounded by the number of items divided by the number of container.
 That is,
 \begin{align*}
-\tilde{H}_0(V |Z  , \sketch(V) = ss) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
-&= \log \left(\frac{2^{h_{ss}}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)
+\tilde{H}_0(V |Z  , \sketch(V) = ss) &\le \log \left(\frac{\text{\# items}+\text{\# containers}}{\text{\# containers}}\right)\\
+&= \log \left(\frac{2^{h_{ss}}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} +1 \right)
 \end{align*}
@@
 \tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V |  \sketch(V) =ss , (Z| \sketch(V) =ss) )}\\
-&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \right)\\
-&= \log \frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\\
-&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \log \expe_{s\in \sketch(V)} 2^{h_s}\\
-&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V))\\ 
-&\le \log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + (\gamma-t+1)\log |\mathbb{F}|+1\\
-&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+1\\
-&< (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}| +1 \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
-&\le (4-t)\log |\mathbb{F}| +1< 1\,.\\
+&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} +1\right)\\
+&\le \max\left\{ \log \left(\frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\right)+1, 1\right\}.
+\end{align*}
+Where the inequality follows because $\log x+1 \le \max\{ 1+ \log x,1\}$ for $x\ge 0$.
+The left operand to $\max$ is bounded by $2$~(bounded the $\max$ by $2$):
+\begin{align*}
+\log \left(\frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\right)+1
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \log \left(\expe_{s\in \sketch(V)} 2^{h_s}\right) +1\\
+&=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V)) +1 \\ 
+&\le \log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + (\gamma-t+1)\log |\mathbb{F}|+2\\
+&\le (\gamma-t+2)\log |\mathbb{F}| - (\gamma-1) \log (|\mathbb{F}|-1)+2\\
+&< (\gamma-t+2)\log |\mathbb{F}| - (\gamma-2) \log |\mathbb{F}| +2 \ \ \ \ \mbox{(by \lemref{lem:log-minus-one})}\\
+&\le (4-t)\log |\mathbb{F}| +2< 2\,.
 \end{align*}
@@
 Consider some $w\in V$ over $\zo^n$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
-The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
+Then $w\leftarrow W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are random.
 \end{proof}
-
-The previous two propositions were similar to the secure sketch case.
-The remainder of the proof is significantly different.
-We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
-Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
 
@@
 \label{lem:fuzz can't get key}
-Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 1$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\ngl(n)$.
+Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\ngl(n)$.
 \end{lemma}
 \begin{proof}
-We assume that $\rep$ is deterministic in our analysis.
-Any randomness necessary for the \rep algorithm can be provided by $\gen$.
-We do not consider these coins in our security analysis~(and thus, they can be considered private).
-Denote by $(\Key, P) \leftarrow \gen(V)$.
-
-%By the definition of correctness for $(\sketch, \rec)$, 
-%\[
-%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
-%\]
-%For most $p$, $\rec$ works on most neighbors of $w$.  
-%Fix some $w$.  
+As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
 By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
@@
 
-Many of these sets must be small.
-That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.
-If not, there exists a set of $\key$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.
-
+There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.
+If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
 For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
-We first define the interior of a set:%Define two sets, called the interior and crust respectively: \bnote{change term crust?}
+Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.
+These are the interior of $Q_{p^*, r}$:
 \begin{align*}
@@
 %Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We now show that for $\key \in R_{small}$ there are few points in $\inter(Q_{p^*, \key })$.
-Consider some $\key^*\in R_{small}$.
-We will use the term deficient ball:\bnote{use a term other than deficient}
+We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.
+We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient}
 \begin{definition}
@@
 
+Consider some $\key^*\in R_{small}$.  
 We now proceed to show that the interior of each $Q_{p^*, \key^*}$ is small:
@@
 By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\beta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $t$ larger than $S_{p^*, \key^*}$).
+Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\beta+t$).
 We now find bound the size of $S_{p^*, \key^*}$.
 
-Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-(\kappa-1)}\leq |\mathcal{M}|/2$.
+Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
@@
 We now show that the intersection between $Q_{\key, p^*}$ is small for most possible values $z$.
+As before each container~(the values of $z$)  receives one item for free~(the point $v$).
 \begin{align*}
-\expe_z |Q_{small} \cap (V | P=p^* \wedge Z=z) | &\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}\\
-&=\frac{|R_{small}|}{2^{\nu}}.
+\expe_z |Q_{small} \cap (V | P=p^* \wedge Z=z) | &\le \left(\frac{\text{\# items}+\text{\# containers}}{\text{\# containers}}\right)\\
+&\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}+1\\
+&=\frac{|R_{small}|}{2^{\nu}}+1
 \end{align*}
-Thus, at most $1/2^{\nu} = \ngl(n)$ fraction of keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
+In expectation across $Z$, 
+\[\frac{\frac{|R_{small}|}{2^{\nu}}+1}{|R_{small}|} \le \frac{1}{2^\nu}+\frac{1}{|R_{small}|} \] fraction of $R_{small}$ receive any support.
+%Thus, at most $1+1/2^{\nu} = \ngl(n)$ keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
 We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
@@
 &\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/2-\ngl(n)\right) = 1/4-\ngl(n).
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|R_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in R_{small}]\right) - \Pr[U\not\in R_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in R_{small}] \right)\\
+&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/4-\ngl(n)\right) \ge \frac{1}{8}-\ngl(n).
 \end{align*}
-The fourth line follows since $R_{small} \ge 2^{\kappa-1}$ and thus $\Pr[U\in R_{small}]\ge 1/2$.  The last line follows by recalling that $\Pr[P\in A_p]\ge 1/2$.
+The sixth line follows since $R_{small} \ge 2^{\kappa-1}\ge 2$.  The eighth line follows because $\Pr[U\in R_{small}]\ge 1/2$.  The last inequality proceeds because $\Pr[P\in A_p]\ge 1/2$.
 This completes the proof of \lemref{lem:fuzz can't get key}.

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
edited the low-dim discussion in 1.1 and sufficiency in 1.2

@@
 the adversary knows $W$.
-To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.
-\bnote{this isn't quite accurate, the first coordinate is known.
-you have no info on the rest of the support}
+To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.
 
@@
 The result for fuzzy extractors is delicate.
-The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.
+It uses the fact that $p$ partitions the space into nonoverlapping regions, which is implied by perfect correctness.
 Extending this result to imperfect correctness seems challenging and is an interesting open problem.
-The result also relies on the majority of points lying near boundaries of a set.
-Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set is not the majority of its area.\bnote{cite cite cite!!!}
+It also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.
+This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$.
+(Such a construction would use quantization or tiling, similar to, for example, \cite{CK03,LT03,CZC04,LC06,BDHTV10,VTOSS10}.
+Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted.
+A randomly chosen quantizer could be used to ensure that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)
 
@@
 \label{sec:related settings}
-\bnote{this needs work}
-We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
-%We first consider the interactive setting.  
-First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.
-In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.
-We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.
-Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).
-
-Second, we can weaken the computational assumption necessary for $\Hfuzz(W)$ to be sufficient by moving to an interactive setting.
-Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
-In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
-If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
-%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
-Ideally, the server would keep a ``hashed'' value of $w$.
-This is  done for noiseless secrets like passwords.}
-In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
-The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R.
-or read the paper}
+The security definition of fuzzy extractors and secure sketches can be weakened to require protection only against computationally bounded adversaries~\cite{fuller2013computational}.
+In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
+The construction places into the $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.
+In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency.
+Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).
+
+Furthermore, the functional definition of fuzzy extractors and secure sketches can be weakened to permit interaction between the party having $w$ and the party having $w'$.
+Such a weakening is useful for secure remote authentication~\cite{Boyen05secureremote}.
+When both interaction and computational assumptions are allowed, secure two-party computation can produce a key that will be secure whenever the distribution $W$ has fuzzy min-entropy.
+The two-party computation protocol needs to be secure without assuming authenticated channels; it can be built under the assumptions that collision-resistant hash functions and enhanced trapdoor permutations exist~\cite{DBLP:journals/joc/BarakCLPR11}.
 
@@
 Our negative results are specific to the Hamming metric.
-\section{Insufficiency of $\Hfuzz(W)$ to secure sketch from distribution families}
+\section{Impossibility of secure sketches for all families with $\Hfuzz$}
 \label{sec:family of dist}
@@
 By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
-\subsubsection{Implications for Computational secure sketches}
+\subsection{Implications for Computational secure sketches}
 \label{sec:feas comp sec sketch}
@@
 Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.
-Consider these possible values for $Z$ as bins to be filled with the $2^{h_{ss}}$ balls~(possible values of $V | \sketch(V)=ss$).
-Each bin receives automatically receives one free point~(all the distributions share $v$).
-The average number of balls in each bin is maximized when the bins are filled equally.
-That is, the average number of balls in each bin is bounded by the number of balls divided by the number of bins.
+Consider these possible values for $Z$ as containers to be filled with the $2^{h_{ss}}$ items~(possible values of $V | \sketch(V)=ss$).
+Each container receives automatically receives one free point~(all the distributions share $v$).
+The average number of items in each container is maximized when the containers are filled equally.
+That is, the average number of items in each container is bounded by the number of items divided by the number of container.
 That is,
 \begin{align*}
-\tilde{H}_0(V |Z  , \sketch(V) = ss) &\le \log \left(\frac{\text{\# balls}+\text{\# bins}}{\text{\# bins}}\right)\\
+\tilde{H}_0(V |Z  , \sketch(V) = ss) &\le \log \left(\frac{\text{\# items}+\text{\# containers}}{\text{\# containers}}\right)\\
 &= \log \left(\frac{2^{h_{ss}}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} +1 \right)
@@
 We now show that the intersection between $Q_{\key, p^*}$ is small for most possible values $z$.
-As before each bin~(the values of $z$)  receives one ball for free~(the point $v$).
+As before each container~(the values of $z$)  receives one item for free~(the point $v$).
 \begin{align*}
-\expe_z |Q_{small} \cap (V | P=p^* \wedge Z=z) | &\le \left(\frac{\text{\# balls}+\text{\# bins}}{\text{\# bins}}\right)\\
+\expe_z |Q_{small} \cap (V | P=p^* \wedge Z=z) | &\le \left(\frac{\text{\# items}+\text{\# containers}}{\text{\# containers}}\right)\\
 &\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}+1\\

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
small changes to intro

@@
 In many situations these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
-However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.
+However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,gassend2002silicon,tuyls2006puf,suh2007physical,bennett1988privacy}.
 That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
@@
 The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}.
-Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.
+Bennett, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.
 The first, called information reconciliation, removes the noise without leaking significant information.
@@
 We show comparable, but stronger, results for secure sketches.
-Namely, we show in \corref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known.
-(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.
-its the same corollary}
+Namely, we show in \corref{cor:extension to fuzz ext} that secure sketches are possible if the distribution $W$ is precisely known.
+(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.)
 
@@
 To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched.
-Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points.
+Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points.
 Thus, our sketch is computed via a universal hash of $w$.
@@
 However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).
-This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, most regions become empty, leaving $\key$ far from uniform.
+This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, many regions become empty, leaving $\key$ far from uniform.
 
@@
 Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted.
-A randomly chosen quantizer could be used to ensure that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)
+A randomly chosen quantizer would have the property that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)
 
@@
 \label{sec:related settings}
-The security definition of fuzzy extractors and secure sketches can be weakened to require protection only against computationally bounded adversaries~\cite{fuller2013computational}.
+The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.
 In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
-The construction places into the $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.
+The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.
 In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency.

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
capitalize section headings

@@
 
-\paragraph{Fuzzy Min-entropy}
+\paragraph{Fuzzy Min-Entropy}
 We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$.
@@
 However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).
-This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, most regions become empty, leaving $\key$ far from uniform.
+This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, many regions become empty, leaving $\key$ far from uniform.
 
 The result for fuzzy extractors is delicate.
-The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.
+It uses the fact that $p$ partitions the space into nonoverlapping regions, which is implied by perfect correctness.
 Extending this result to imperfect correctness seems challenging and is an interesting open problem.
-The result also relies on the majority of points lying near boundaries of a set.
-Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set is not the majority of its area.\bnote{cite cite cite!!!}
-
-\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
+It also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.
+This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$.
+(Such a construction would use quantization or tiling, similar to, for example, \cite{CK03,LT03,CZC04,LC06,BDHTV10,VTOSS10}.
+Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted.
+A randomly chosen quantizer would have the property that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)
+
+\subsection{Sufficiency of $\Hfuzz$ in Related Settings}
 \label{sec:related settings}
-\bnote{this needs work}
-We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
-%We first consider the interactive setting.  
-First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.
-In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.
-We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.
-Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).
-
-Second, we can weaken the computational assumption necessary for $\Hfuzz(W)$ to be sufficient by moving to an interactive setting.
-Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.
-In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.
-If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
-%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.
-Ideally, the server would keep a ``hashed'' value of $w$.
-This is  done for noiseless secrets like passwords.}
-In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
-The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R.
-or read the paper}
+The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.
+In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
+The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.
+In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency.
+Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).
+
+Furthermore, the functional definition of fuzzy extractors and secure sketches can be weakened to permit interaction between the party having $w$ and the party having $w'$.
+Such a weakening is useful for secure remote authentication~\cite{Boyen05secureremote}.
+When both interaction and computational assumptions are allowed, secure two-party computation can produce a key that will be secure whenever the distribution $W$ has fuzzy min-entropy.
+The two-party computation protocol needs to be secure without assuming authenticated channels; it can be built under the assumptions that collision-resistant hash functions and enhanced trapdoor permutations exist~\cite{DBLP:journals/joc/BarakCLPR11}.
 
@@
 
-\subsection{Fuzzy Extractors for families of distributions}\label{sec:fuzz extractor}
+\subsection{Fuzzy Extractors for Families of Distributions}\label{sec:fuzz extractor}
 
@@
 
-\subsection{Fuzzy min-entropy: a necessary condition}
+\subsection{Fuzzy min-entropy: a Necessary Condition}
 \label{sec:minimal conditions}
@@
 
-\subsection{Secure Sketches for Flat distributions}
+\subsection{Flat distributions}
 A distribution is flat if all points in its support have the same probability:
@@
 
-\subsection{Secure sketches for all distributions with $\Hfuzz(W)$}
+\subsection{Arbitrary Distributions}
 The worst-case hashing approach does not work for arbitrary sources.
@@
 Our negative results are specific to the Hamming metric.
-\section{Impossibility of secure sketches for all families with $\Hfuzz$}
+\section{Impossibility of Secure Sketches for all Families with $\Hfuzz$}
 \label{sec:family of dist}
@@
 By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
-\subsection{Implications for Computational secure sketches}
+\subsection{Implications for Computational Secure Sketches}
 \label{sec:feas comp sec sketch}
@@
 
-\section{Impossibility of fuzzy extractors for all families with $\Hfuzz$}
+\section{Impossibility of Fuzzy Extractors for all Families with $\Hfuzz$}
 \label{sec:imposs fuzz ext}

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
adam's edits on distribution-aware prior work; leo's edits to def of Hfuzz preamble

@@
 
-This characterization justifies $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t|$.
+A number of previous works in this known-distribution setting have provided efficient algorithms and
+tight bounds for specific distributions---generally the uniform distribution or
+i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
+Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
 
@@
 \paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).
-We begin with distributions in which all points in the support have roughly the same probability.
-We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$.
-To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched.
+We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).
+Consider some subsequent reading $w'$.
+To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched.
 Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points.
@@
 To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$.
-Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability.
+Because the distribution is flat, it is also the ball with the most points of nonzero probability.
 Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball.
@@
 
-\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
+\subsection{Sufficiency of $\Hfuzz$ in Related Settings}
 \label{sec:related settings}
@@
 In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.
-In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results for secure sketches and fuzzy extractors for families of distributions respectively.
+In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.
 
@@
 Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
-
-\subsection{Fuzzy Extractors for families of distributions}\label{sec:fuzz extractor}
+A \emph{negligible} function $\ngl(n)$ is one that decreases faster than any positive inverse polynomial as $n\rightarrow \infty$.
+
+\subsection{Fuzzy Extractors for Families of Distributions}\label{sec:fuzz extractor}
 
@@
 
-\subsection{Fuzzy min-entropy: a necessary condition}
+\subsection{Fuzzy min-entropy: a Necessary Condition}
 \label{sec:minimal conditions}
-
-In an ideal world, $p$ is not useful to an adversary.
-The adversary's only attack method is to execute $\rep(\cdot, p)$ on different $w'$.
-In this world, $\rep$ outputs $\key$ if the input is close enough and provides no other  information.
-The security of a fuzzy extractor in this world is the maximum weight of $W$ inside a ball of radius $t$:
+The value $p$ allows everyone, including the adversary, to find the output of $\rep(\cdot, p)$ on any input $w'$.
+Ideally,  $p$ should not provide any useful information beyond this ability, and the outputs of $\rep$ on inputs that are too distant from $w$ should provide no useful information, either.
+In this ideal scenario, the adversary is limited to trying to guess a $w'$ that is $t$-close to $w$.
+Letting $w'$ be the center of the maximum-weight ball in $W$ would be optimal for the adversary.
+We therefore measure the quality of a source by (the negative logarithm of) this weight.
 

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
minor edits for clarity -- include adding \supp

@@
 \mathchardef\mhyphen="2D
+
+\newcommand{\supp}{\operatorname{supp}}
 
@@
 Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
+A \emph{negligible} function $\ngl(n)$ is one that decreases faster than any positive inverse polynomial as $n\rightarrow \infty$.
 
@@
 \label{sec:minimal conditions}
-
-In an ideal world, $p$ is not useful to an adversary.
-The adversary's only attack method is to execute $\rep(\cdot, p)$ on different $w'$.
-In this world, $\rep$ outputs $\key$ if the input is close enough and provides no other  information.
-The security of a fuzzy extractor in this world is the maximum weight of $W$ inside a ball of radius $t$:
+The value $p$ allows everyone, including the adversary, to find the output of $\rep(\cdot, p)$ on any input $w'$.
+Ideally,  $p$ should not provide any useful information beyond this ability, and the outputs of $\rep$ on inputs that are too distant from $w$ should provide no useful information, either.
+In this ideal scenario, the adversary is limited to trying to guess a $w'$ that is $t$-close to $w$.
+Letting $w'$ be the center of the maximum-weight ball in $W$ would be optimal for the adversary.
+We therefore measure the quality of a source by (the negative logarithm of) this weight.
 
@@
 
-\section{Sufficiency of $\Hfuzz(W)$ for Known Distribution Algorithms}
+\section{Sufficiency of $\Hfuzz(W)$ When the Algorithms Know the Distribution}
 \label{sec:known distributions}
-In this section, we show it is possible to build known distribution secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
+In this section, we show it is possible to build known-distribution secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
 We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.
@@
 \subsection{Flat distributions}
-A distribution is flat if all points in its support have the same probability:
+A distribution is flat if all points in its support have the same probability. Let $\supp(W)$ denote the support of $W$< i.e., the set of points with nonzero probability.
 \begin{definition}
-A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in W$, $\Pr[W=w_0] = \Pr[W=w_1]$.  
+A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in \supp(W)$,  $\Pr[W=w_0] = \Pr[W=w_1]$.  
 \end{definition}
 
-Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.
-We denote the ball with the largest number of points as $B_{t, max}$.
-Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).
-For flat distributions, this is proportional to the largest number of points in any ball.
+Denote the ball of radius $t$ with the largest number of points in the support of $W$ as $B_{t, max}$.
+For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.
 More precisely,
 \begin{align}
-\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w')\le t\} \right|* \Pr[W=w]\right) \nonumber \\
-&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w')\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
-&=\Hoo(W) -\log\left( \max_{w' \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w')\le t\} |\right)\nonumber \\
-&= \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
+\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
+&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
+&=\Hoo(W) -\log\left( \max_{w' \in \mathcal{M}}| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} |\right)\nonumber \\
+&= \Hoo(W) -\log |B_{t, max}\cap \supp(W)|.\label{eq:fuzz for flat}
 \end{align}
@@
 \begin{tabular}{c|c}
-\begin{minipage}{3in}
+\begin{minipage}{2.5in}
 \textbf{$\sketch_W$}
@@
 \end{minipage} &
-\begin{minipage}{3in}
+\begin{minipage}{3.5in}
 \textbf{$\rec_W$}
@@
 \item \underline{Input}: $(w', p = y, K)$
-\item Create $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
 \item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
@@
 If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
-That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
+That is, setting $\log |R| = \log |B_{t, max}\cap\supp(W)| + \omega(\log n)$ suffices.
 \end{corollary}
@@
 $
-\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n).
+\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}\cap\supp(W)| - \omega(\log n).
 $
@@
 \item Parse $(i, y, K) = ss_{1,..., |y|}$.
-\item $W^* = \{w \in W | \dis(w, w')\le t\}$.
+\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
 \item For $w^*\in W^*$, if $F(K, w^*) = z$, \\ output $w^*$.
@@
 \[
-B_{t, i, max} = \max_{w' \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
+B_{t, i, max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
 \]
@@
 Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
-Let $Z$ be the description of which $W$ was sampled.
-The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$ where $Z$ is the description of which $W$ was sampled.
+Let the random variable $Z$ specify which $W$ was sampled.
+The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$.
 Our results rule out security for an average member of $\mathcal{W}$.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta <1/4$ and $t\ge 4$ then $\tilde{m}<2$.
-
-Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.  Then, 
+There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, and yet for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch $(\sketch, \rec)$ with error $\delta <1/4$ and distance $t\ge 4$, the remaining entropy $\tilde{m}<2$.
+
+Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$, and let $Z$ specify which $W$ is sampled.  Then
 \[
@@
 \noindent
-\textbf{Note:} There is tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.
+\textbf{Note:} There is a tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.
 By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}\cap \supp(W)|-1}{|R_i|} = \delta
 \end{align*}
@@
 The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.
-The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}\cap\supp(W)|$ as there at $|B_{t, i, max}\cap\supp(W)|$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
 There are $n$ outcomes for $i$.
@@
 \begin{align}
-\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
+\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}\cap\supp(W)|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
 &\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
@@
 \max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
-&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
+&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{|\sketch(W)|i|}\right)\\
+&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
+&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t, i, max}\cap\supp(W)|/\delta\right)\\
+&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot |B_{t, i, max}\cap \supp(W)|\right)}{2\delta}\\
 %&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
minor edits

@@
 Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
-Let $Z$ be the description of which $W$ was sampled.
-The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$ where $Z$ is the description of which $W$ was sampled.
+Let the random variable $Z$ indicate which $W$ was sampled.
+The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$.
 Our results rule out security for an average member of $\mathcal{W}$.
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta <1/4$ and $t\ge 4$ then $\tilde{m}<2$.
-
-Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.  Then, 
+There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, and yet for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch $(\sketch, \rec)$ with error $\delta <1/4$ and distance $t\ge 4$, the remaining entropy $\tilde{m}<2$.
+
+Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$, and let $Z$ indicate which $W$ is sampled.  Then
 \[
@@
 Our impossibility result says nothing about this weaker form of a secure sketch.
-Extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
+Extraction from unpredictability entropy can be done using an extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}; however, in the computational setting, the obfuscated function can simply hide a randomly generated key, and therefore extraction is not necessary to obtain a fuzzy extractor.
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$.
-Let $\kappa \ge 2$, $t = \omega(n^{1/2}\log n)$.
+There exists a family of distributions $\mathcal{W}$ over $\zo^n$ satisfying the following conditions.
+For each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$.
+Let $\kappa \ge 2$ and $t = \omega(n^{1/2}\log n)$.
 Any $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.
@@
 Furthermore, this is true on average.
-Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.
+Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ indicate which $W$ is sampled.
 Let $(\Key, P)\leftarrow \gen(V)$.
@@
 \[
-\sd ((\Key,P, Z), (U_\kappa, P, Z))>1/8-\ngl(n).
+\sd ((\Key,P, Z), (U_\kappa, P, Z))>1/8-\ngl(n)\,.
 \]
@@
 Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
-We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
+We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).
+\lnote{it would be good to explain why not}  We embed this larger space to the binary Hamming metric.
 Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
@@
  Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.
-The adversary sees $\sketch(V)$ and which distribution was sampled, call this information $Z$.
-$Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
+The adversary sees $\sketch(V)$  and $Z$, where $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
 

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
minor last minute edits

@@
 
-\bnote{mention secure sketches?}
-\bnote{keep editing}
-\bnote{nearby or close?  be consistent}
-\bnote{I renamed section titles to get rid of distribution aware and oblivious.  don't quite like them}
 \lnote{mention computational setting?}
 \lnote{mention the typical analysis that separates min-entropy and error-tolerance?}
+
+\medskip
+\textbf{Keywords:} Fuzzy extractors, secure sketches, information theory, biometric authentication, error-tolerance, key derivation, error-correcting codes.
 \end{abstract}
@@
 
-\subsection{Fuzzy min-entropy: a Necessary Condition}
+\subsection{Fuzzy Min-Entropy: a Necessary Condition}
 \label{sec:minimal conditions}
@@
 $
-\forall w\in W$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
+\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
 Correctness is guaranteed only for the support of $W$.
@@
 
-\subsection{Flat distributions}
-A distribution is flat if all points in its support have the same probability. Let $\supp(W)$ denote the support of $W$< i.e., the set of points with nonzero probability.
+\subsection{Flat Distributions}
+A distribution is flat if all points in its support have the same probability. Let $\supp(W)$ denote the support of $W$, i.e., the set of points with nonzero probability.
 \begin{definition}
@@
 
-Denote the ball of radius $t$ with the largest number of points in the support of $W$ as $B_{t, max}$.
+Denote the ball of radius $t$ with the largest number of points in the support of $W$ as $B_{t,W,max} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.
 For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.
@@
 &= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
-&=\Hoo(W) -\log\left( \max_{w' \in \mathcal{M}}| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} |\right)\nonumber \\
-&= \Hoo(W) -\log |B_{t, max}\cap \supp(W)|.\label{eq:fuzz for flat}
+&= \Hoo(W) -\log |B_{t,W,max}|.\label{eq:fuzz for flat}
 \end{align}
@@
 Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
-\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
+\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t,W,max}|-1}{|R|}$. 
 \end{lemma}
@@
 Let $n = \log |\mathcal{M}|$.
-If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
-That is, setting $\log |R| = \log |B_{t, max}\cap\supp(W)| + \omega(\log n)$ suffices.
+If $|R| \ge |B_{t,W,max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
+That is, setting $\log |R| = \log |B_{t,W,max}| + \omega(\log n)$ suffices.
 \end{corollary}
@@
 $
-\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}\cap\supp(W)| - \omega(\log n).
+\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t,W,max}| - \omega(\log n).
 $
@@
 \item Parse $(i, y, K) = ss_{1,..., |y|}$.
-\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
-\item For $w^*\in W^*$, if $F(K, w^*) = z$, \\ output $w^*$.
+\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
+\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
 \item Output $\perp$.
@@
 \noindent
-We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
+We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t,i,W, max}$ be the ball that contains the most points in $L_i$.  That is,
 \[
-B_{t, i, max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
+B_{t,W_i,max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
 \]
@@
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t,W_i,max}|-1) /\delta$.
 When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
@@
 Our negative results are specific to the Hamming metric.
-\section{Impossibility of Secure Sketches for all Families with $\Hfuzz$}
+\section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
 \label{sec:family of dist}
@@
 Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
-Let the random variable $Z$ specify which $W$ was sampled.
+Let the random variable $Z$ indicate which $W$ was sampled.
 The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$.
@@
 
-Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$, and let $Z$ specify which $W$ is sampled.  Then
+Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$, and let $Z$ indicate which $W$ is sampled.  Then
 \[
@@
 \textbf{Note:} There is a tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.
-By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
+By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.\bnote{it would be nice to say what our counter example says about the binary space.}
 \subsection{Implications for Computational Secure Sketches}
@@
 Our impossibility result says nothing about this weaker form of a secure sketch.
-Extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
-
-\section{Impossibility of Fuzzy Extractors for all Families with $\Hfuzz$}
+Extraction from unpredictability entropy can be done using an extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}; however, in the computational setting, the obfuscated function can simply hide a randomly generated key, and therefore extraction is not necessary to obtain a fuzzy extractor.
+
+\section{Impossibility of Fuzzy Extractors for a Family with $\Hfuzz$}
 \label{sec:imposs fuzz ext}
@@
 Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
-We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
+We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).
+In the binary Hamming space a large fraction of any set of bounded size is the near ``boundary'' of that set.
+This will be important for our proof.
+We will embed the larger alphabet we used into the binary Hamming metric.
 Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
@@
 Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.
-The size of $W^*$ is at most $B_{t, max}$.
+The size of $W^*$ is at most $B_{t,W,max}$.
 Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t,W,max}|-1}{|R|}
 \end{align*}
 The inequality proceeds by union bound.
-The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t, max}|-1$.
+The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t,W,max}|-1$.
 This completes the proof.
@@
 Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.
-The size of $W^*$ is at most $B_{t, i, max}$.
+The size of $W^*$ is at most $B_{t,W_i,max}$.
 The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}\cap \supp(W)|-1}{|R_i|} = \delta
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t,W_i,max}|-1}{|R_i|} = \delta
 \end{align*}
-The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t, i, max}|$.
+The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t,W_i,max}|$.
 
@@
 The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.
-The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}\cap\supp(W)|$ as there at $|B_{t, i, max}\cap\supp(W)|$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,W_i, max}|$ as there at $|B_{t,W_i,max}|$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
 There are $n$ outcomes for $i$.
@@
 \begin{align}
-\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}\cap\supp(W)|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
+\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t,W_i,max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
 &\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
@@
 &\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t, i, max}\cap\supp(W)|/\delta\right)\\
-&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot |B_{t, i, max}\cap \supp(W)|\right)}{2\delta}\\
-%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
+&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t,W_i,max}|/\delta\right)\\
+&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot |B_{t,W_i,max}|\right)}{2\delta}\\
+%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t,W_i,max}|\right)
 %\end{align*}

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
couple last minute modifications

@@
 
-\section{Impossibility of Fuzzy Extractors for all Families with $\Hfuzz$}
+\section{Impossibility of Fuzzy Extractors for a Family with $\Hfuzz$}
 \label{sec:imposs fuzz ext}
@@
 Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
-We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).
-\lnote{it would be good to explain why not}  We embed this larger space to the binary Hamming metric.
+We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).
+A  property of the binary Hamming space is that a large fraction of any set of bounded size is the near ``boundary'' of that set.
+This will be crucial in our proof.
+We will embed the larger alphabet we used into the binary Hamming metric.
 Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
@@
 This would just rule out some member of $\mathcal{W}$ not an average member.
-This is true for fuzzy extractors as well and holds changes in parameters including imperfect correctness.
+This is true for fuzzy extractors as well and is resilient to changes in parameters including imperfect correctness.
 
@@
 \label{lem:fuzz can't get key}
-Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/4-\ngl(n)$.
+Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
 \end{lemma}

### 2014-10-07 info-bounds/FuzzyExtPossibility.tex
changing notation for maximum number of points in a ball

@@
 
-Denote the ball of radius $t$ with the largest number of points in the support of $W$ as $B_{t,W,max} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.
+Denote the largest number of points in a ball of radius $t$ in the support of $W$ as $\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.
 For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.
@@
 &= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
-&= \Hoo(W) -\log |B_{t,W,max}|.\label{eq:fuzz for flat}
+&= \Hoo(W) -\log \beta_{t}.\label{eq:fuzz for flat}
 \end{align}
@@
 Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
-\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t,W,max}|-1}{|R|}$. 
+\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
 \end{lemma}
@@
 Let $n = \log |\mathcal{M}|$.
-If $|R| \ge |B_{t,W,max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
-That is, setting $\log |R| = \log |B_{t,W,max}| + \omega(\log n)$ suffices.
+If $|R| \ge |\beta_{t}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
+That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
 \end{corollary}
@@
 $
-\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t,W,max}| - \omega(\log n).
+\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} - \omega(\log n).
 $
@@
 \noindent
-We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t,i,W, max}$ be the ball that contains the most points in $L_i$.  That is,
+We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
 \[
-B_{t,W_i,max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
+\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
 \]
@@
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t,W_i,max}|-1) /\delta$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.
 When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
@@
 We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).
-In the binary Hamming space a large fraction of any set of bounded size is the near ``boundary'' of that set.
-This will be important for our proof.
+A  property of the binary Hamming space is that a large fraction of any set of bounded size is the near ``boundary'' of that set.
+This will be crucial in our proof.
 We will embed the larger alphabet we used into the binary Hamming metric.
@@
 Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.
-The size of $W^*$ is at most $B_{t,W,max}$.
+The size of $W^*$ is at most $\beta_{t}$.
 Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t,W,max}|-1}{|R|}
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
 \end{align*}
 The inequality proceeds by union bound.
-The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t,W,max}|-1$.
+The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $\beta_{t}-1$.
 This completes the proof.
@@
 Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.
-The size of $W^*$ is at most $B_{t,W_i,max}$.
+The size of $W^*$ is at most $\beta_{t,i}$.
 The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t,W_i,max}|-1}{|R_i|} = \delta
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|} = \delta
 \end{align*}
-The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t,W_i,max}|$.
+The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.
 
@@
 The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.
-The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,W_i, max}|$ as there at $|B_{t,W_i,max}|$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
 There are $n$ outcomes for $i$.
@@
 \begin{align}
-\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t,W_i,max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
+\expe_{i | m\le i \le m+n}2^{-(i+1)}\beta_{t,i}&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
 &\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
@@
 &\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t,W_i,max}|/\delta\right)\\
-&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot |B_{t,W_i,max}|\right)}{2\delta}\\
-%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t,W_i,max}|\right)
+&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*\beta_{t,i}/\delta\right)\\
+&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
+%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
 %\end{align*}
@@
 \label{lem:log-minus-one}
-For any real numbers $\alpha \leq \beta$ with $\beta \ge e+1$ (in particular, $\beta\ge 4$ suffices), the following holds:
-$\alpha \log (\beta-1) > (\alpha-1)\log \beta$. 
+For any real numbers $\alpha \leq \eta$ with $\eta \ge e+1$ (in particular, $\eta\ge 4$ suffices), the following holds:
+$\alpha \log (\eta-1) > (\alpha-1)\log \eta$. 
 \end{lemma}
@@
 \begin{proof}
-Because $\beta-1$ is positive, and $1+x<e^x$ for positive $x$,
-$$1+\frac{1}{\beta-1} < e^{\frac{1}{\beta -1}}\,.$$  Therefore, 
-$$\left(1+\frac{1}{\beta-1}\right)^{\alpha-1} < e^{\frac{\alpha-1}{\beta-1}}\le e < \beta-1$$ (since $\alpha\le \beta$). Multiplying both sides by $(\beta-1)^{\alpha-1}$, we obtain
-$$\beta^{\alpha-1} < (\beta-1)^\alpha\,.$$
+Because $\eta-1$ is positive, and $1+x<e^x$ for positive $x$,
+$$1+\frac{1}{\eta-1} < e^{\frac{1}{\eta -1}}\,.$$  Therefore, 
+$$\left(1+\frac{1}{\eta-1}\right)^{\alpha-1} < e^{\frac{\alpha-1}{\eta-1}}\le e < \eta-1$$ (since $\alpha\le \eta$). Multiplying both sides by $(\eta-1)^{\alpha-1}$, we obtain
+$$\eta^{\alpha-1} < (\eta-1)^\alpha\,.$$
 Taking the logarithm of both sides yields the statement of the lemma.
@@
 \begin{definition}
-A set $S$ is a $\beta$-deficient ball if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
+A set $S$ is a $\eta$-deficient ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
 \end{definition}
@@
 \begin{proof}
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\beta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\beta+t$).
+By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
+Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\eta+t$).
 We now find bound the size of $S_{p^*, \key^*}$.

### 2014-10-07 trunk/info-bounds/FuzzyExtPossibility.tex
moved known distribution case

@@
 
-\subsection{Fuzzy Extractors for Families of Distributions}\label{sec:fuzz extractor}
+\subsection{Fuzzy Extractors and Secure Sketches}\label{sec:fuzz extractor}
 
@@
 %This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
-We discuss known distribution algorithms in \secref{sec:known distributions def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.
+%We discuss known distribution algorithms in \secref{sec:known distributions def}.  
+Let $\mathcal{M}$ be a metric space with distance function $\dis$.
 
@@
 \begin{enumerate}
-\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = \key] \geq 1-\delta$.
+\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
 \item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
@@
 \begin{enumerate}
-\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
+\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
 \item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
@@
 
-\noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.
+\noindent
+In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known in order for the correctness guarantee to hold: correctness holds for any $w'$ with probability $1-\delta$ over the coins of the algorithms, but $w'$ cannot be a function of the output of  $\sketch(w)$.
+
+\paragraph{The Case of Known Distribution}
+If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.
+In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{If we wish to be pedantic and extend correctness to all of $\mathcal{M}$, we can define $\gen$/$\sketch$ to be the identity function on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this will not harm security}.
+
+Note that we have no requirement that the algorithms are compact or efficient, and so the distribution can be fully known to them.
+Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.
+
+\paragraph{From Secure Sketches to Fuzzy Extractors}
 A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average case randomness extractor}:
@@
 There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
-Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe the known distribution setting.
-
-\subsection{Known Distribution Algorithms}
-\label{sec:known distributions def}
+Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy. % We now describe the known distribution setting.
+
+%\subsection{Known Distribution Algorithms}
+%\label{sec:known distributions def}
 %To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
-We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
-
-\begin{definition}
-Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
+%We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
+%
+%\begin{definition}
+%Let $W$ denote a distribution.
+A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution %secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
 That is,
-\begin{enumerate}
-\item \emph{Correctness:} 
-$
-\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
-Correctness is guaranteed only for the support of $W$.
-\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
-\end{enumerate}
-\end{definition}
-$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
+%\begin{enumerate}
+%\item \emph{Correctness:} 
+%$
+%\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
+%Correctness is guaranteed only for the support of $W$.
+%\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
+%\end{enumerate}
+%\end{definition}
+%$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
 We assume known distribution algorithms are \emph{inefficient}.
@@
 
-\begin{definition}
+\begin{definition}[\cite{DBLP:journals/jcss/CarterW79}]
 Let $F : \mathcal{K} \times \mathcal{M} \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in \mathcal{M}$:
@@
 Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
-\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t,W,max}|-1}{|R|}$. 
+\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
 \end{lemma}
@@
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t,W_i,max}|-1) /\delta$.
-When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.
+When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
 
@@
 Let $\mathcal{M}$ be a metric space where $n = \log |\M|$.
-For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-known distribution secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
+For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
 (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)

### 2014-10-07 trunk/info-bounds/FuzzyExtPossibility.tex
minor cleanup of distribution aware setting

@@
 If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.
-In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{If we wish to be pedantic and extend correctness to all of $\mathcal{M}$, we can define $\gen$/$\sketch$ to be the identity function on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this will not harm security}.
+In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not effect security.}.
 

### 2014-10-07 trunk/info-bounds/FuzzyExtPossibility.tex
minor typos

@@
 If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.
-In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not effect security.}.
+In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not affect security.}.
 
@@
 Let $n = \log |\mathcal{M}|$.
-If $|R| \ge |\beta_{t}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
+If $|R| \ge |\beta_{t}|\cdot n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
 That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
@@
 The reason is that some balls may have  many points but low total weight.
-Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.
+For example, let $W$ be a distribution consisting of the following balls.
+Denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.
 Let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.
-Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.
-However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$ and the hash completely reveals the point.
+Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness on $B^1_t$.
+However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$, and the hash completely reveals the point.
 

### 2014-10-27 constantRate/ConstCompFuzzExt-reorg.tex
minor note on code definition

@@
 \begin{abstract}
-\lnote{Opinions?}
-Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated readings of a noisy source of entropy into the same uniformly distributed key.
-To eliminate noise, they require an initial enrollment phase that takes a reading from the source and produces a nonsecret helper string to be used in subsequent readings.
-This helper string reduces  the entropy of the original source---in the worst case, by as much as the logarithm of the number of tolerated error patterns.
-For many practical sources, reliability demands that the number of tolerated error patterns is large, making this loss greater than the original entropy of the source.
+Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
+To eliminate noise, they require an initial enrollment phase that takes the first noisy reading of the secret and produces a nonsecret helper string to be used in subsequent readings.
+This helper string reduces  the entropy of the original secret---in the worst case, by as much as the logarithm of the number of tolerated error patterns.
+For many practical sources of secrets, reliability demands that the number of tolerated error patterns is large, making this loss greater than the original entropy of the secret.
 We say that such sources have \emph{more errors than entropy}.
@@
 \emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
- remain secure even when the initial enrollment phase is repeated multiple times on correlated readings, producing multiple helper strings.
+ remain secure even when the initial enrollment phase is repeated multiple times with the same or correlated secrets, producing multiple helper strings.
 By relying on computational security, we construct the first reusable fuzzy extractors that make no assumption about how multiple readings of the source are correlated.
@@
 Both of these problems have interactive and non-interactive versions.
-In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
+In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple noisy readings of a secret at different times.
  A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined in~\cite{DBLP:journals/siamcomp/DodisORS08}.
@@
 \end{definition}
+\bnote{these are quite strange.  changing them for dissertation.  update if accepted.}
 

### 2014-11-10 trunk/info-bounds/FuzzyExtPossibility.tex
presentation for brown
small typo fix

@@
 \item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
-Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
+Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_2$ have disjoint support outside of $v$.
 \item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).
@@
 Where the inequality follows because $\log x+1 \le \max\{ 1+ \log x,1\}$ for $x\ge 0$.
-The left operand to $\max$ is bounded by $2$~(bounded the $\max$ by $2$):
+The left operand to $\max$ is bounded by $2$~(bounding the $\max$ by $2$):
 \begin{align*}

### 2014-11-24 info-bounds/FuzzyExtPossibility.tex
added references to some info-theoretic two-random variables stuff

@@
 
-\subsection{Sufficiency of $\Hfuzz$ in Related Settings}
+\subsection{Related Settings}
 \label{sec:related settings}
+\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
 The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.
@@
 
-\paragraph{Organization} The reminder of the paper is organized as follows.
+\paragraph{Correlated rather than close readings}
+A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.
+This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.
+
+%The definition of $\Hfuzz$ can be extended to this model (by again thinking of the adversary as choosing the value $w'$ that is most likely to lead to a success).
+
+\paragraph{Organization} The remainder of the paper is organized as follows.
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
@@
 
-\noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.
+\noindent
+In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known in order for the correctness guarantee to hold: correctness holds for any $w'$ with probability $1-\delta$ over the coins of the algorithms, but $w'$ cannot be a function of the output of  $\sketch(w)$.
+
+\paragraph{The Case of Known Distribution}
+If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.
+In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not affect security.}.
+
+Note that we have no requirement that the algorithms are compact or efficient, and so the distribution can be fully known to them.
+Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.
+
+\paragraph{From Secure Sketches to Fuzzy Extractors}
 A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average case randomness extractor}:
@@
 Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
-\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
+\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
 \end{lemma}
@@
 Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.
-When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
 

### 2014-11-24 info-bounds/FuzzyExtPossibility.tex
added acks

@@
 Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
-Boston University and MIT Lincoln Laboratory.
-The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.
+Boston University and MIT Lincoln Laboratory.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.
 Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
@@
 The secure sketch counter example needs $t=4$ and allows the $\rec$ to be wrong almost $1/4$ of the time.
+
+\section*{Acknowledgements}
+The authors are grateful to Gene Itkis and Yevgeniy Dodis for helpful discussions.
+The work of Benjamin Fuller is sponsored in part by US NSF grants 1012910 and 1012798 and  the United States Air Force under Air Force Contract FA8721-05-C-0002.
+Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
+Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.
+
 \bibliographystyle{alpha}

### 2014-11-24 trunk/info-bounds/FuzzyExtPossibility.tex
added funding

@@
 \author{
-Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
-Boston University and MIT Lincoln Laboratory.
-The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.
-Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.
-Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
-Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
-``Privacy Tools'' project.}}
+Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston
+  University and MIT Lincoln Laboratory.}  \and Leonid
+Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.}
+\and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
+  Pennsylvania State University. A.S. is supported NSF awards
+  \#0747294 and \#0941553. This work performed while visiting Boston
+  University's Hariri Institute for Computing.}}
 }

### 2014-12-01 constantRate/ConstCompFuzzExt-reorg.tex
minor typo fixes and grant additions

@@
 \begin{enumerate}[(i)]
-\item Set $v_i = \cond(w_i, seed_i)$.
+\item Set $v_i' = \cond(w_i', seed_i)$.
 \end{enumerate}
-\item Output $r = \rep'(v', ss)$.
+\item Output $r = \rep'(v', p')$.
 \end{enumerate}
@@
 \[
-\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
 \]
@@
 Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
-Let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
+Define $\mathcal{V}$ as the family of all distributions with min-entropy at least $\tilde{\alpha}(\gamma-\beta)$ and let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \mathcal{V}, \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
 Most known constructions of fuzzy extractors are average-case fuzzy extractors.
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', p)$
+\item \underline{Input}: $(w'=w_1',..., w_\gamma', p)$
 \item For $i=1,..., \ell$:
@@
 \item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
-\item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
+\item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
 \item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
@@
  Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.
-Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
+Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \geq 1-\ell\epsilon_{sam}$.
 %[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
@@
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.
+Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.  Adam Smith is supported in part by NSF awards 0747294 and 0941553. 
 }
@@
 Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that
-\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1})\]
+\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-1}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1-1})\]
 and since $(seed_1,..., seed_{j_1})$ are independent of these values

### 2014-12-01 constantRate/eurocryptReviewResponse.txt
first draft of eurocrypt rebuttal

Thank you for the reviews and feedback.  We will incorporate your comments into our work.

Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
A: The second and third construction also secure different types of sources.  The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).  The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).  The third construction allows all blocks to be determined by a single block as long as most blocks are hard to guess.

Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
A: This question is known as a robust fuzzy extractor (Boyen et al., Eurocrypt 2004).  It is a separate question than reusability of a fuzzy extractor. Robust fuzzy extractors are easy in the random oracle model.  In the standard model, constructions are more fragile and utilize one-time MACs (Dodis et al., Crypto 2006).

Q:  I would like to suggest the authors to add some detailed discussion whether the result of this work can be used in general applications, where the condition of a super-constant size of alphabet might does not naturally hold.  Is it a hard challenge to find an alternative of removing this condition? 
Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources
(biometric, PUF examples) where standard fuzzy extractors fail? It would be
great to gain intuition about whether these construction can be improved or
not.
A: The second construction provides reusability regardless of alphabet size.  (It only corrects more errors than entropy on a super-constant size alphabet.)  The constructions support different types of sources, the reusable construction does support a superset of the information-theoretic construction.

Supporting more errors than entropy on a constant size alphabet remains a challenge.  As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors.  This is to avoid stronger lower bounds that arise when working on a single space.  Known techniques for working on a single space recover the original reading (known as a secure sketch) and are subject to stronger negative results.  It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.

We have run some initial experiments and the second construction appears promising for irises where the distance is binary Hamming over 2048 bit strings.  However, there is still considerable work to verify that irises the second construction is secure on irises.  The main work is showing that  sampling producing high entropy strings.  Indeed, the main barrier to applicability is showing that known PUFs and biometrics satisfy the necessary input distribution of our constructions.

Subsequent work (Herder et al., ePrint 2014/938) increased error-tolerance by using confidence information that may be available for some PUFs and biometrics.  It may be possible to incorporate such information to our constructions to improve applicability.

### 2014-12-01 constantRate/eurocryptReviewResponse.txt
MIT CIS talk

@@
 Is it a hard challenge to find an alternative of removing this condition?
-Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources
-(biometric, PUF examples) where standard fuzzy extractors fail? It would be
-great to gain intuition about whether these construction can be improved or
-not.
-A: The second construction provides reusability regardless of alphabet size.
-(It only corrects more errors than entropy on a super-constant size alphabet.)  The constructions support different types of sources, the reusable construction does support a superset of the information-theoretic construction.
+Q: Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?
+It would be great to gain intuition about whether these construction can be improved or not.
+A: Finding "good distributions" that are obtainable in practice and support provable security is an important and fascinating research direction.
+One can view our results as providing a target for biometrics and PUFs.
+Our constructions show promise for two reasons.
+
+First, the second construction provides reusability regardless of alphabet size.
+(It only corrects more errors than entropy on a super-constant size alphabet.)  We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).
+Known fuzzy extractors provide no guarantees for irises.
+However, there is still work to verify that bits sampled from an iris code have high entropy.
+The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions.
+
+Second, the constructions support different types of sources (the second construct does support a superset of the first). This provides multiple options for building a PUF or biometric transform.
 
@@
 This is to avoid stronger lower bounds that arise when working on a single space.
-Known techniques for working on a single space recover the original reading (known as a secure sketch) and are subject to stronger negative results.
+Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.
 It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.
-
-We have run some initial experiments and the second construction appears promising for irises where the distance is binary Hamming over 2048 bit strings.
-However, there is still considerable work to verify that irises the second construction is secure on irises.
-The main work is showing that  sampling producing high entropy strings.
-Indeed, the main barrier to applicability is showing that known PUFs and biometrics satisfy the necessary input distribution of our constructions.
 

### 2014-12-02 trunk/constantRate/eurocryptReviewResponse.txt
edited after Ben's

--- 2014-12-01 constantRate/eurocryptReviewResponse.txt
@@
 Thank you for the reviews and feedback.  We will incorporate your comments into our work.
+We address only the most important comments below.
 
 Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
-A: The second and third construction also secure different types of sources.
+A: The second and third construction not only add reusability--they also handle more interesting sources than the first construction, and thus are interesting even when reusability is not relevant.
 The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).
 The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).
-The third construction allows all blocks to be determined by a single block as long as most blocks are hard to guess.
+The third construction requires most blocks to be hard to guess on their own--but permits, for example, all blocks to be determined by a single one.
 
@@
 It is a separate question than reusability of a fuzzy extractor.
-Robust fuzzy extractors are easy in the random oracle model.
+As Boyen et al.
+show, adding robustness to any fuzzy extractor (including ours) is easy in the random oracle model.
 In the standard model, constructions are more fragile and utilize one-time MACs (Dodis et al., Crypto 2006).
@@
 Q: Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?
-It would be great to gain intuition about whether these construction can be improved or not.
-A: Finding "good distributions" that are obtainable in practice and support provable security is an important and fascinating research direction.
-One can view our results as providing a target for biometrics and PUFs.
-Our constructions show promise for two reasons.
 
-First, the second construction provides reusability regardless of alphabet size.
-(It only corrects more errors than entropy on a super-constant size alphabet.)  We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).
+A: The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions.
+Finding such PUFs and biometric transforms is a fascinating research question that we are currently working on.
+
+One can view our results as providing a target for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired.
+Our constructions show promise for the following reasons:
+
+They support different types of sources. This provides multiple options for building a PUF or a biometric transform.
+
+In particular, the second construction supports sources whose symbols are k-wise independent for a sufficient k.
+This means that even if the resulting string, after all the signal processing, overdefines the original signal (and thus has little entropy relative to its length), our construction may still apply.
+
+Finally, the second construction provides reusability regardless of alphabet size (although the "more errors than entropy" claim holds only for a super-constant size alphabet).
+
+We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).
 Known fuzzy extractors provide no guarantees for irises.
 However, there is still work to verify that bits sampled from an iris code have high entropy.
-The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions.
 
-Second, the constructions support different types of sources (the second construct does support a superset of the first). This provides multiple options for building a PUF or biometric transform.
+Q: It would be great to gain intuition about whether these construction can be improved or not.
 
 Supporting more errors than entropy on a constant size alphabet remains a challenge.
-As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors.
-This is to avoid stronger lower bounds that arise when working on a single space.
-Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.
+As the reviewers note, we crucially make use of two metric spaces: the input metric and a second metric space where we correct errors.
+This is to avoid stronger lower bounds that arise when working on a single space, since known techniques for working on a single space recover the original reading, and are subject to stronger negative results.
 It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.

### 2014-12-02 constantRate/eurocryptReviewResponse.txt
edited one answer to make it more assertive

@@
 Thank you for the reviews and feedback.  We will incorporate your comments into our work.
+We address only the most important comments below.
 
 Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
-A: The second and third construction also secure different types of sources.
+A: The second and third construction not only add reusability--they also handle more interesting sources than the first construction, and thus are interesting even when reusability is not relevant.
 The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).
 The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).
-The third construction allows all blocks to be determined by a single block as long as most blocks are hard to guess.
+The third construction requires most blocks to be hard to guess on their own--but permits, for example, all blocks to be determined by a single one.
 
 Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
-A: This question is known as a robust fuzzy extractor (Boyen et al., Eurocrypt 2004).
-It is a separate question than reusability of a fuzzy extractor.
-Robust fuzzy extractors are easy in the random oracle model.
-In the standard model, constructions are more fragile and utilize one-time MACs (Dodis et al., Crypto 2006).
+A: This question is important, but orthogonal to the challenges addressed by this submission.
+Constructions that can handle malicious manipulation of the helper data are called “robust fuzzy extractors” (Boyen et al., Eurocrypt 2004).
+Boyen et al.
+observed that, in the random oracle model, one can make a fuzzy extractor robust without harming other properties.
+Conversions in the standard model are more delicate (Dodis et al., Crypto 2006).
+Finding robust versions of the constructions in this submission is an interesting question, but lies beyond the scope of this submission.
 

### 2014-12-02 constantRate/eurocryptReviewResponse.txt
pointed out that we work for constant size, too

@@
-Thank you for the reviews and feedback.  We will incorporate your comments into our work.
-We address only the most important comments below.
+Thank you for the feedback, which we will incorporate. We address most salient comments below.
 
-Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
-A: The second and third construction not only add reusability--they also handle more interesting sources than the first construction, and thus are interesting even when reusability is not relevant.
+Q: The second and third construction use obfuscation (for point functions) to add "reusability".
+A: These constructions not only add reusability--they also handle other sources than the first construction, and thus are interesting even when reusability is not relevant.
 The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).
@@
 A: This question is important, but orthogonal to the challenges addressed by this submission.
-Constructions that can handle malicious manipulation of the helper data are called “robust fuzzy extractors” (Boyen et al., Eurocrypt 2004).
-Boyen et al.
-observed that, in the random oracle model, one can make a fuzzy extractor robust without harming other properties.
+Constructions that can handle malicious manipulation of the helper data are called “robust fuzzy extractors”; in the random oracle model, any fuzzy extractor can be made robust without harming other properties (Boyen et al., Eurocrypt 2004).
 Conversions in the standard model are more delicate (Dodis et al., Crypto 2006).
-Finding robust versions of the constructions in this submission is an interesting question, but lies beyond the scope of this submission.
+Finding robust versions of the constructions in this submission without using random oracles is an interesting question, but lies beyond the scope of this submission.
 
-Q:  I would like to suggest the authors to add some detailed discussion whether the result of this work can be used in general applications, where the condition of a super-constant size of alphabet might does not naturally hold.
-Is it a hard challenge to find an alternative of removing this condition?
-Q: Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?
+Q: Is it a hard challenge to find an alternative [for the condition of super-constant size alphabet]?
 
-A: The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions.
-Finding such PUFs and biometric transforms is a fascinating research question that we are currently working on.
+A: Super-constant alphabet is not necessary in the second construction.
+For example, it supports binary sources whose symbols are k-wise independent for a sufficient k (see last sentence of 4.4).
+This means that even if the resulting string, after all the signal processing, overdefines the original signal (and thus has little entropy relative to its length), our construction may still apply.
+This construction may be useful for discretization procedures similar to ones that are used in the IrisCode (which takes the sign of each coordinate of a multidimensional continuous vector).
 
-One can view our results as providing a target for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired.
-Our constructions show promise for the following reasons:
+Q: How do the [constructions] compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?
 
-They support different types of sources. This provides multiple options for building a PUF or a biometric transform.
-
-In particular, the second construction supports sources whose symbols are k-wise independent for a sufficient k.
-This means that even if the resulting string, after all the signal processing, overdefines the original signal (and thus has little entropy relative to its length), our construction may still apply.
-
-Finally, the second construction provides reusability regardless of alphabet size (although the "more errors than entropy" claim holds only for a super-constant size alphabet).
-
-We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).
-Known fuzzy extractors provide no guarantees for irises.
-However, there is still work to verify that bits sampled from an iris code have high entropy.
+A: As we discuss, SOME distributional conditions seem necessary, so it’s a matter of finding the magic spot for which fuzzy extractors exist and realistic sources can satisfy.
+Our work can be seen as providing guidance for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired.
+Since our constructions support different types of sources, they they provide multiple options for building a PUF or a biometric transform.
 
@@
 
-Supporting more errors than entropy on a constant size alphabet remains a challenge.
-As the reviewers note, we crucially make use of two metric spaces: the input metric and a second metric space where we correct errors.
-This is to avoid stronger lower bounds that arise when working on a single space, since known techniques for working on a single space recover the original reading, and are subject to stronger negative results.
-It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.
+A: As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors.
+Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.
 
@@
 It may be possible to incorporate such information to our constructions to improve applicability.
+
+It may also be possible to explore which transformations can be used to change the alphabet and the distribution to get them closer to our conditions.

### 2014-12-02 trunk/constantRate/eurocryptReviewResponse.txt
modified review response

--- 2014-12-01 constantRate/eurocryptReviewResponse.txt
@@
-Thank you for the reviews and feedback.  We will incorporate your comments into our work.
+Thank you for the feedback, which we will incorporate. We address most salient comments below.
 
-Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
-A: The second and third construction also secure different types of sources.
+Q: The second and third construction use obfuscation (for point functions) to add "reusability".
+A: These constructions not only add reusability--they also handle different sources than the first construction, and thus are interesting even when reusability is not relevant.
 The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).
 The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).
-The third construction allows all blocks to be determined by a single block as long as most blocks are hard to guess.
+The third construction requires most blocks to be hard to guess on their own--but permits, for example, all blocks to be determined by a single one.
 
 Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
-A: This question is known as a robust fuzzy extractor (Boyen et al., Eurocrypt 2004).
-It is a separate question than reusability of a fuzzy extractor.
-Robust fuzzy extractors are easy in the random oracle model.
-In the standard model, constructions are more fragile and utilize one-time MACs (Dodis et al., Crypto 2006).
+A: This question is important, but orthogonal to the challenges addressed by this submission.
+Constructions that can handle malicious manipulation of the helper data are called “robust fuzzy extractors”; in the random oracle model, any fuzzy extractor can be made robust without harming other properties (Boyen et al., Eurocrypt 2004).
+Conversions in the standard model are more delicate (Dodis et al., Crypto 2006).
+Finding robust versions of the constructions in this submission without using random oracles is an interesting question, but lies beyond the scope of this submission.
 
-Q:  I would like to suggest the authors to add some detailed discussion whether the result of this work can be used in general applications, where the condition of a super-constant size of alphabet might does not naturally hold.
-Is it a hard challenge to find an alternative of removing this condition?
-Q: Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?
-It would be great to gain intuition about whether these construction can be improved or not.
-A: Finding "good distributions" that are obtainable in practice and support provable security is an important and fascinating research direction.
-One can view our results as providing a target for biometrics and PUFs.
-Our constructions show promise for two reasons.
+Q: Is it a hard challenge to find an alternative [for the condition of super-constant size alphabet]?
 
-First, the second construction provides reusability regardless of alphabet size.
-(It only corrects more errors than entropy on a super-constant size alphabet.)  We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).
-Known fuzzy extractors provide no guarantees for irises.
-However, there is still work to verify that bits sampled from an iris code have high entropy.
-The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions.
+A: As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors.
+Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.
+The two metric space technique is most applicable for super-constant size alphabet.
 
-Second, the constructions support different types of sources (the second construct does support a superset of the first). This provides multiple options for building a PUF or biometric transform.
+However, super-constant alphabet is not necessary in the second construction.
+For example, it supports binary sources whose symbols are k-wise independent for a sufficient k (see last paragraph of 4.4).
 
-Supporting more errors than entropy on a constant size alphabet remains a challenge.
-As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors.
-This is to avoid stronger lower bounds that arise when working on a single space.
-Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.
-It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.
+Q: How do the [constructions] compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?
 
-Subsequent work (Herder et al., ePrint 2014/938) increased error-tolerance by using confidence information that may be available for some PUFs and biometrics.
-It may be possible to incorporate such information to our constructions to improve applicability.
+A: As we discuss, some distributional conditions seem necessary, so it’s a matter of finding a condition where secure fuzzy extractors exist that realistic sources satisfy.
+Our work can be seen as providing guidance for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired.
+Since our constructions support different types of sources, they they provide multiple options for building a PUF or a biometric transform.
+
+For example, the IrisCode transform takes the sign of Gabor filters at nearby locations so the resulting signal is likely redundant.
+This redundancy makes existing constructions fail (as the source is far from uniform).
+However, the produced binary vector may satisfy the k-wise independence condition necessary for the second construction.

### 2014-12-17 trunk/info-bounds/FuzzyExtPossibility.tex
MIT CIS talk
adding discussion of correlated random variables

@@
 \newcommand{\Hfuzz}{\mathrm{H}^{\mathtt{fuzz}}_{t,\infty}}
+\newcommand{\Hcorr}{\mathrm{H}^{\mathtt{corr}}}
 \newcommand{\Huse}{\mathrm{H}_{\mathtt{usable}}}
@@
 \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
-  Pennsylvania State University. A.S. is supported NSF awards
-  \#0747294 and \#0941553. This work performed while visiting Boston
+  Pennsylvania State University. This work performed while visiting Boston
   University's Hariri Institute for Computing.}}
@@
 This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.
+We compare our positive results to these characterizations in \secref{sec:known distributions}.
 
@@
 There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
-Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy. % We now describe the known distribution setting.
-
-%\subsection{Known Distribution Algorithms}
-%\label{sec:known distributions def}
-%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
-%We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
-%
-%\begin{definition}
-%Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution %secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
-That is,
-%\begin{enumerate}
-%\item \emph{Correctness:} 
-%$
-%\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
-%Correctness is guaranteed only for the support of $W$.
-%\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%\end{definition}
-%$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
-We assume known distribution algorithms are \emph{inefficient}.
-Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.
+Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.
+
+\paragraph{Generalizing to correlated random variables}
+Instead of considering $w, w'$ that have bounded distance, we can treat $W, W'$ as a pair of correlated random variables.  
+  Renner and Wolf~\cite{DBLP:conf/asiacrypt/RennerW05} study this setting, firsting consider information-reconciliation and privacy amplification separately.
+They show that $\Hoo(W)$ is a necessary and sufficient condition for privacy amplification.\footnote{The results of Renner and Wolf use smooth notions of entropy.
+A random variable has smooth entropy if it is statistically close to a distribution with true entropy.
+We describe their results in the terminology of non smooth entropy.}  Second, they show that the length of $p$ must grow with the worst case number of possible outcomes for $W$ conditioned on $W'$.\footnote{This result also uses a smooth notion of entropy.
+We describe the non smooth version for simplicity.}  That is, the length of the public value \[|p|\ge \max_{w'\in W} \log |\{w | \Pr[W=w | W'=w']>0\}|.\]
+
+Furthermore, they show there exists a protocol with this length $p$ using optimal encoding functions.
+Intuitively, the public information must describe which possible outcome for $W$ actually occurred.
+This result describes the maximal length of $p$ and does not argue how $p$ effects security.
+It may be possible to construct a $p$ that reduces the entropy of $w$ by less than $\log |p|$.
+In \secref{sec:known distributions}, we will construct schemes with variable length $p$, providing information-reconciliation for distributions where the bounds of Renner and Wolf provide no security guarantees.
+
+Lastly, the work of Renner and Wolf shows characterize when key derivation is possible from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.
+We compare this characterization to fuzzy min-entropy in \secref{sec:known distributions}.
+
+Fuzzy min-entropy can be generalized to this setting.
+Fuzzy extractors consider the worst case $w'$.
+When considering correlated readings, it is natural to treat $W'$ as a random variable:\footnote{Fuzzy extractors are defined to require high probability of correctness for all pairs $w, w'$.
+In the correlated setting, it may make sense to provide an average-case guarantee, where the probability of correctness is also over the draw of $w, w'$.
+Renner and Wolf use a smoothed notion of entropy that removes the $\delta$ fraction of the probability mass of $W=w|W'=w'$ with the most points to improve parameters under such a definition.
+In this work, we consider worst case correctness and use unsmoothed entropy.}
+
+\begin{definition}
+\label{def:cor fuzz min}
+Let $(W, W')$ be a pair of correlated random variables.  The correlated fuzzy min-entropy of $W, W'$ is:
+\[\Hcorr(W, W') = -\log \left( \max_{w'\in \supp(W')}\sum_{w\in W | \Pr[W=w|W'=w']>0} \Pr[W = w] \right).\]
+\end{definition}
+\noindent 
+In \defref{def:fuzzy min-ent}, the sum is implicitly over $W=w|W'=w'$ since we assume any $w'$ within distance $t$ is possible.  
+For now, we consider sufficiency of $\Hfuzz(W)$ for key derivation from noisy sources (\defref{def:fuzzy min-ent}).
+We then consider the implications of our results on the correlated reading setting (\defref{def:cor fuzz min}).
 
@@
 Our negative results are specific to the Hamming metric.
+
+\paragraph{Connection to the characterization of~\cite{DBLP:conf/asiacrypt/RennerW05}}
+Renner and Wolf characterize when it is possible to derive keys from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.
+They consider all possible (randomized) transforms $T, T'$ of $W, W'$ into a new pair of variables $V,V'$.
+They show that \[|\key| \le \sup_{(V, V')\leftarrow (T(W), T'(W))}\left(  \Hoo(V | T') - \log \max_{v'\in V'} |\{v| \Pr[V=v|T' \wedge V'=v']>0\}|\right).\]  Furthermore, they show that there is a transformation that achieves a key of nearly this length.
+The result is nonconstructive as there is no guidance on how to find the transforms $T, T'$.
+Since there is no known bound on the length of $T, T'$ it is not clear how to search the transform space even with unlimited time.
+\consref{cons:leveling} can be used to derive keys from correlated random variables.  The main change is to define \[W^* = \{w | \Pr[W=w | W'=w'] >0 \wedge \Pr[W=w]\in L_i\}.\]  
+Our result shows if one is satisfied with obtaining a strong key when possible (our protocol has losses of $2\log 1/\epsilon + \log n+\log 1/\delta$), then a protocol is possible (and explicitly constructible) in the original space.
+
 \section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
@@
 Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
-Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.
+Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.  Adam Smith is supported in part by NSF awards 0747294 and 0941553.
 

### 2015-01-05 info-bounds/FuzzyExtPossibility.tex
working on reviewer comments

@@
 \author{
-Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.
-Boston University and MIT Lincoln Laboratory.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.
-Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
-Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
-``Privacy Tools'' project.}}
+Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston
+  University and MIT Lincoln Laboratory.}  \and Leonid
+Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.}
+\and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
+  Pennsylvania State University. This work performed while visiting Boston
+  University's Hariri Institute for Computing.}}
 }
@@
 In this work, we ask: \emph{is fuzzy min-entropy sufficient to build information-theoretic fuzzy extractors?}
+
+\bnote{fuzzy min-entropy measures ideal security ... similar to encryption/etc.}
+\bnote{should introduce the idea of distributional uncertainty...very important for us}
 %\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
@@
 Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.
+\bnote{should note that fuzzy min-entropy is the ideal security, measures how an adversary would do with oracle access, goal is to implement this oracle}
 
@@
 We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.
+\bnote{introduce distributional uncertainty here}
 
@@
 We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
-Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.
-We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart.
-Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.
+Specifically, we show a family of distributions $\mathcal{W}_Z$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.
+We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart.
+Our proof relies on high dimensionality of each $W_z$ and on perfect correctness of the $\rep$ procedure.
 
@@
 
-On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
+On the other hand, there is a family of sources, $\mathcal{W}_Z$, where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
 The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
 
+\bnote{asked to discuss implications of our negative results}
+\bnote{can we reframe the paper as the cost of distributional uncertainty?}
+\bnote{compare to current constructions?}
 \subsection{Our Techniques}
@@
 \paragraph{Techniques for Negative Results for Distribution Families}
-We construct a family of distributions $\mathcal{W}$ and prove impossibility for a uniformly random $W\in \mathcal{W}$~(instead of proving impossibility for a worst-case $W$).
-We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
-the adversary knows $W$.
-To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.
+We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$~(instead of proving impossibility for a worst-case $W_z$).
+We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
+the adversary knows $W_z$.
+To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.
 
@@
 This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.
+We compare our positive results to these characterizations in \apref{sec:corr variables}.
+To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for families of distributions.
 
@@
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.
+In \secref{sec:known distributions}, we construct a fuzzy extractor for each known distribution with fuzzy min-entropy.
 In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.
@@
 The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
-For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
+%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).
 We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
-
 For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.
@@
 \noindent
+\bnote{Should note this is the ideal security of a noisy source, both in the interactive/non-interactive settings}
 Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
@@
 There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
-Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy. % We now describe the known distribution setting.
-
-%\subsection{Known Distribution Algorithms}
-%\label{sec:known distributions def}
-%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.
-%We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
-%
-%\begin{definition}
-%Let $W$ denote a distribution.
-A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution %secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.
-That is,
-%\begin{enumerate}
-%\item \emph{Correctness:} 
-%$
-%\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
-%Correctness is guaranteed only for the support of $W$.
-%\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
-%\end{enumerate}
-%\end{definition}
-%$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.
-We assume known distribution algorithms are \emph{inefficient}.
-Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.
+Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.
+
+\bnote{I feel we can provide a more general results than this one.  Helpful?}
 
@@
 Denote the largest number of points in a ball of radius $t$ in the support of $W$ as $\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.
-For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.
+For flat distributions, the weight of the maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.
 More precisely,
@@
 \item Sample $K\leftarrow \mathcal{K}$.
-\item Set $p = F(K, w), K$.
+\item Set $ss = F(K, w), K$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \underline{Input}: $(w', p = y, K)$
+\item \underline{Input}: $(w', ss =( y, K))$
 \item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
@@
 Let $\ell\in\mathbb{Z}^+$ be a parameter.
-Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell$.
+Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell-1$.
 Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.
@@
 \item \underline{Input}: $w$.
-\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $p=0,w$.
+\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $ss=1,w$.
 \item Else
@@
 \item Sample $K\leftarrow \mathcal{K}_i$.
-\item Set $ss =1,  i, F_i(K, w), K$.
+\item Set $ss =0,  i, F_i(K, w), K$.
 \end{enumerate}
@@
 \noindent
-We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
-\[
-\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
-\]
 
@@
 The main idea is to show that an adversary that knows the level of $w$ cannot perform much better than an adversary without this information.
+\bnote{this sentence isn't helpful, provide better intuition}
 
@@
 Our negative results are specific to the Hamming metric.
+
 \section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
@@
 \appendix
+
+\section{Key Derivation from Correlated Random Variables}
+\label{sec:corr variables}
+
+In this work, we consider two draws from some physical source whose distance was bounded according to some metric space.
+Instead of considering $w, w'$ that have bounded distance, we can treat $W, W'$ as a pair of correlated random variables.  
+  Renner and Wolf~\cite{DBLP:conf/asiacrypt/RennerW05} study this setting, firsting consider information-reconciliation and privacy amplification separately.
+They show that $\Hoo(W)$ is a necessary and sufficient condition for privacy amplification.\footnote{The results of Renner and Wolf use smooth notions of entropy.
+A random variable has smooth entropy if it is statistically close to a distribution with true entropy.
+We describe their results in the terminology of non smooth entropy.}  Second, they show that the length of $p$ must grow with the worst case number of possible outcomes for $W$ conditioned on $W'$.\footnote{This result also uses a smooth notion of entropy.
+We describe the non smooth version for simplicity.}  That is, the length of the public value \[|p|\ge \max_{w'\in W} \log |\{w | \Pr[W=w | W'=w']>0\}|.\]
+
+Furthermore, they show there exists a protocol with this length $p$ using optimal encoding functions.
+Intuitively, the public information must describe which possible outcome for $W$ actually occurred.
+This result describes the maximal length of $p$ and does not argue how $p$ effects security.
+It may be possible to construct a $p$ that reduces the entropy of $w$ by less than $\log |p|$.
+In \secref{sec:known distributions}, we will construct schemes with variable length $p$, providing information-reconciliation for distributions where the bounds of Renner and Wolf provide no security guarantees.
+
+Lastly, the work of Renner and Wolf shows characterize when key derivation is possible from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.
+Fuzzy min-entropy can be generalized to this setting.
+Fuzzy extractors consider the worst case $w'$.
+When considering correlated readings, it is natural to treat $W'$ as a random variable:\footnote{Fuzzy extractors are defined to require high probability of correctness for all pairs $w, w'$.
+In the correlated setting, it may make sense to provide an average-case guarantee, where the probability of correctness is also over the draw of $w, w'$.
+Renner and Wolf use a smoothed notion of entropy that removes the $\delta$ fraction of the probability mass of $W=w|W'=w'$ with the most points to improve parameters under such a definition.
+In this work, we consider worst case correctness and use unsmoothed entropy.}
+
+\begin{definition}
+\label{def:cor fuzz min}
+Let $(W, W')$ be a pair of correlated random variables.  The correlated fuzzy min-entropy of $W, W'$ is:
+\[\Hcorr(W, W') = -\log \left( \max_{w'\in \supp(W')}\sum_{w\in W | \Pr[W=w|W'=w']>0} \Pr[W = w] \right).\]
+\end{definition}
+\noindent 
+In \defref{def:fuzzy min-ent}, the sum is implicitly over $W=w|W'=w'$ since we assume any $w'$ within distance $t$ is possible.  
+In \secref{sec:known distributions} we showed sufficiency  of $\Hfuzz(W)$ for key derivation from noisy sources (\defref{def:fuzzy min-ent}).
+
+\paragraph{Connection to the characterization of~\cite{DBLP:conf/asiacrypt/RennerW05}}
+Renner and Wolf characterize when it is possible to derive keys from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.
+They consider all possible (randomized) transforms $T, T'$ of $W, W'$ into a new pair of variables $V,V'$.
+They show that \[|\key| \le \sup_{(V, V')\leftarrow (T(W), T'(W))}\left(  \Hoo(V | T') - \log \max_{v'\in V'} |\{v| \Pr[V=v|T' \wedge V'=v']>0\}|\right).\]  Furthermore, they show that there is a transformation that achieves a key of nearly this length.
+The result is nonconstructive as there is no guidance on how to find the transforms $T, T'$.
+Since there is no known bound on the length of $T, T'$ it is not clear how to search the transform space even with unlimited time.
+\consref{cons:leveling} can be used to derive keys from correlated random variables.  The main change is to define \[W^* = \{w | \Pr[W=w | W'=w'] >0 \wedge \Pr[W=w]\in L_i\}.\]  
+Our result shows if one is satisfied with obtaining a strong key when possible (our protocol has losses of $2\log 1/\epsilon + \log n+\log 1/\delta$), then a protocol is possible (and explicitly constructible) in the original space.
 
@@
 Thus, $D$ is also a distinguisher in the computational setting.
+\bnote{this should probably be in the body of the paper}
 \end{proof}
@@
 Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.
+We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
+\[
+\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
+\]
 
@@
 \end{align*}
-The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.
+The first inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.
 
@@
 \begin{align*}
-\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
--\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
+\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
+&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
 \end{align*}
@@
 \]
-We separate out this quantity into levels:
+We separate out this quantity into levels:\bnote{we need to talk about K here}
 \begin{align*}
 \max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{|\sketch(W)|i|}\right)\\
 &\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*\beta_{t,i}/\delta\right)\\
+&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
 &\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
@@
 \begin{align*}
-\Hav(W | \sketch(W)) &= -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
+\Hav(W | \sketch(W)) &\ge -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
 &\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
@@
 \end{align*}
+The statement of the lemma follows by noting that for any $X, Y$, $\Hav(X|Y)\le \tilde{H}_0(X|Y)$.
 \end{proof}

### 2015-01-06 trunk/info-bounds/FuzzyExtPossibility.tex
adding reviewer comments

@@
 This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.
-We compare our positive results to these characterizations in \secref{sec:known distributions}.
+We compare our positive results to these characterizations in \apref{sec:corr variables}.
+To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for families of distributions.
 
@@
 
-\paragraph{Generalizing to correlated random variables}
-Instead of considering $w, w'$ that have bounded distance, we can treat $W, W'$ as a pair of correlated random variables.  
-  Renner and Wolf~\cite{DBLP:conf/asiacrypt/RennerW05} study this setting, firsting consider information-reconciliation and privacy amplification separately.
-They show that $\Hoo(W)$ is a necessary and sufficient condition for privacy amplification.\footnote{The results of Renner and Wolf use smooth notions of entropy.
-A random variable has smooth entropy if it is statistically close to a distribution with true entropy.
-We describe their results in the terminology of non smooth entropy.}  Second, they show that the length of $p$ must grow with the worst case number of possible outcomes for $W$ conditioned on $W'$.\footnote{This result also uses a smooth notion of entropy.
-We describe the non smooth version for simplicity.}  That is, the length of the public value \[|p|\ge \max_{w'\in W} \log |\{w | \Pr[W=w | W'=w']>0\}|.\]
-
-Furthermore, they show there exists a protocol with this length $p$ using optimal encoding functions.
-Intuitively, the public information must describe which possible outcome for $W$ actually occurred.
-This result describes the maximal length of $p$ and does not argue how $p$ effects security.
-It may be possible to construct a $p$ that reduces the entropy of $w$ by less than $\log |p|$.
-In \secref{sec:known distributions}, we will construct schemes with variable length $p$, providing information-reconciliation for distributions where the bounds of Renner and Wolf provide no security guarantees.
-
-Lastly, the work of Renner and Wolf shows characterize when key derivation is possible from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.
-We compare this characterization to fuzzy min-entropy in \secref{sec:known distributions}.
-
-Fuzzy min-entropy can be generalized to this setting.
-Fuzzy extractors consider the worst case $w'$.
-When considering correlated readings, it is natural to treat $W'$ as a random variable:\footnote{Fuzzy extractors are defined to require high probability of correctness for all pairs $w, w'$.
-In the correlated setting, it may make sense to provide an average-case guarantee, where the probability of correctness is also over the draw of $w, w'$.
-Renner and Wolf use a smoothed notion of entropy that removes the $\delta$ fraction of the probability mass of $W=w|W'=w'$ with the most points to improve parameters under such a definition.
-In this work, we consider worst case correctness and use unsmoothed entropy.}
-
-\begin{definition}
-\label{def:cor fuzz min}
-Let $(W, W')$ be a pair of correlated random variables.  The correlated fuzzy min-entropy of $W, W'$ is:
-\[\Hcorr(W, W') = -\log \left( \max_{w'\in \supp(W')}\sum_{w\in W | \Pr[W=w|W'=w']>0} \Pr[W = w] \right).\]
-\end{definition}
-\noindent 
-In \defref{def:fuzzy min-ent}, the sum is implicitly over $W=w|W'=w'$ since we assume any $w'$ within distance $t$ is possible.  
-For now, we consider sufficiency of $\Hfuzz(W)$ for key derivation from noisy sources (\defref{def:fuzzy min-ent}).
-We then consider the implications of our results on the correlated reading setting (\defref{def:cor fuzz min}).
+\bnote{I feel we can provide a more general results than this one.  Helpful?}
 
@@
 Our negative results are specific to the Hamming metric.
-
-\paragraph{Connection to the characterization of~\cite{DBLP:conf/asiacrypt/RennerW05}}
-Renner and Wolf characterize when it is possible to derive keys from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.
-They consider all possible (randomized) transforms $T, T'$ of $W, W'$ into a new pair of variables $V,V'$.
-They show that \[|\key| \le \sup_{(V, V')\leftarrow (T(W), T'(W))}\left(  \Hoo(V | T') - \log \max_{v'\in V'} |\{v| \Pr[V=v|T' \wedge V'=v']>0\}|\right).\]  Furthermore, they show that there is a transformation that achieves a key of nearly this length.
-The result is nonconstructive as there is no guidance on how to find the transforms $T, T'$.
-Since there is no known bound on the length of $T, T'$ it is not clear how to search the transform space even with unlimited time.
-\consref{cons:leveling} can be used to derive keys from correlated random variables.  The main change is to define \[W^* = \{w | \Pr[W=w | W'=w'] >0 \wedge \Pr[W=w]\in L_i\}.\]  
-Our result shows if one is satisfied with obtaining a strong key when possible (our protocol has losses of $2\log 1/\epsilon + \log n+\log 1/\delta$), then a protocol is possible (and explicitly constructible) in the original space.
 
@@
 
-The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.
-The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses 
+\[
+w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w')}\Pr[W=w].
+\] 
+The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
 There are $n$ outcomes for $i$.
@@
 \textbf{Security:}
+\bnote{need to clean up this proof}
 We now argue security.
@@
 \]
-We separate out this quantity into levels:
+We separate out this quantity into levels:\bnote{we need to talk about K here}\bnote{we were asked what $\Pr[W=w| \sketch(W)]$ means, to me that's well formed}\bnote{shouldn't there be a term here $\Pr[L_i = i]$?}
 \begin{align*}
-\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{|\sketch(W)|i|}\right)\\
+\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
 &\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*\beta_{t,i}/\delta\right)\\
+&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
 &\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
@@
 Any randomness necessary for the \rec algorithm can be provided by \sketch.
-This is the same as considering $\rep$ that outputs any coin it flips.
-Since $w, w'$ are independent of $p$ this does not effect correctness.
-Security is defined based on the output of $\rec$ so outputting the coins of $\rep$ does not effect security.
+This is the same as considering $\rec$ that outputs any coin it flips.
+Since $w, w'$ are independent of $ss$ this does not effect correctness.
+Security is defined based on the output of $\rec$ so outputting the coins of $\rec$ does not effect security.
 By the definition of correctness for $(\sketch, \rec)$, 
 \[
-\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
+\forall w, w', \dis(w, w') \le t, \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
 \]
@@
 \[
-\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
+\frac{|\{w' | \dis (w', w)\le t \wedge \rec(w', ss) \neq w\}|}{|\{w'|\dis(w', w) \le t\}|}\le 2\delta < 1/2.\]
 
@@
 We now show that $H_0(V | \sketch(V) = ss^*) \le (\gamma-t+1)\log |\mathbb{F}|$.
-For the sketched value $w$, $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.
-
-For every value in $V|\sketch(V) = ss^*$ this is also true.
+For the sketched value $w$, at most a $2\delta$ fraction of nearby $w'$ do not map to $w$.
+Thus, this is also true for every value in $V|\sketch(V) = ss^*$ this is also true.
 This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).
@@
 \end{proof}
-
+\bnote{the reviewer is complaining that $V | \sketch(V)$ is not a distribution.  don't know why}
 \begin{lemma}

### 2015-01-08 trunk/info-bounds/FuzzyExtPossibility.tex
working on new proof outline for leveled hashing

@@
 \item Parse $(i, y, K) = ss_{1,..., |y|}$.
-\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
+\item $W^* = \{w | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
 \item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
@@
 \[
-\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
+\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
 \]
@@
 
+\bnote{new outline to proof. proof to come}
+\begin{enumerate}
+\item show chain rule for fuzzy min-entropy
+\item show that fuzzy min-entropy conditioned on i is related to $\beta_{t, i}$.
+\item show that releasing the sketch only gives delta more than necessary.
+\end{enumerate}
 \noindent
 \textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.
-
-The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses 
+Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
+
+Let $I$ be the random variable describing the level.
+Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]
+
+In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.
+With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.
+That is, the adversary's best guess is:
 \[
-w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w')}\Pr[W=w].
+w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
 \] 
-The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.
 There are $n$ outcomes for $i$.
@@
 \begin{align}
-\expe_{i | m\le i \le m+n}2^{-(i+1)}\beta_{t,i}&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
-&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
-&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
+\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
+%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
+&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
 \end{align}
 \textbf{Security:}
-\bnote{need to clean up this proof}
-We now argue security.
+We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.
+We now argue security of the construction.
 First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).
@@
 Then
+\begin{align}
+\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
+&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
+\end{align}
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$
+
+Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
+All the dependence between $W$ and $K$ is contained in $L_I$.
+That is, $\Hav(W | K_I , L_I) = \Hav(W | L_I)$.
+Let $Y_I$ denote the outcome of the hash function.
+We now consider the remaining average min-entropy when $1_{\text{low}} = 0$:
 \begin{align*}
-\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
+&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
+&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
+&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
+&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
+&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
+&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
 \end{align*}
-For the remainder of the proof, we seek a bound on 
-\[
-2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
-\]
-We separate out this quantity into levels:\bnote{we need to talk about K here}\bnote{we were asked what $\Pr[W=w| \sketch(W)]$ means, to me that's well formed}\bnote{shouldn't there be a term here $\Pr[L_i = i]$?}
+Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
 \begin{align*}

### 2015-01-15 TCC-invited-talk/TCC-talk-abstract.tex
Leo's invited talk at TCC 2015 added

\documentclass{llncs}

\title{Wyner's Wire-Tap Channel, Forty Years Later}
\author{Leonid Reyzin}
\titlerunning{Forty Years of the Wire-Tap Channe;}
\authorrunning{Leonid Reyzin}
\institute{Boston University\\Department of Computer Science\\Boston MA 02215 USA\\\url{http://www.cs.bu.edu/fac/reyzin}} 
\tocauthor{Leonid Reyzin (Boston University)}

\begin{document}
\maketitle

\begin{abstract} 
Wyner's information theory paper "The Wire-Tap Channel" turns forty this year. Its importance is underappreciated in cryptography, where its intellectual progeny includes pseudorandom generators, privacy amplification, information reconciliation, and many flavors of randomness extractors (including plain, strong, fuzzy, robust, and nonmalleable). Focusing mostly on privacy amplification and fuzzy extractors, this talk demonstrates the connection from Wyner's paper to today's research, including work on program obfuscation.
\end{abstract}
\end{document}

### 2015-01-16 info-bounds/FuzzyExtPossibility.tex
working on chain rule for fuzzy min-entropy

@@
 \newcommand{\Hfuzz}{\mathrm{H}^{\mathtt{fuzz}}_{t,\infty}}
+\newcommand{\Hfav}{\tilde{\mathrm{H}}^{\mathtt{fuzz}}_{t,\infty}}
 \newcommand{\Hcorr}{\mathrm{H}^{\mathtt{corr}}}
@@
 Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.
-\bnote{should note that fuzzy min-entropy is the ideal security, measures how an adversary would do with oracle access, goal is to implement this oracle}
-
+
+Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.
 Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).
+Fuzzy min-entropy measures the maximum obtainable key from a noisy distribution.
 However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
 Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
-This question is particularly relevant when the gap between the two sides of the inequality is high.
-As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}.
+This question is particularly relevant when the gap between the two sides of the inequality is high.\footnote{For nearly uniform distributions, $\Hfuzz(W) \approx \Hoo(W)- \log |B_t|$.
+In this setting, standard coding based constructions of fuzzy extractors (instantiated with optimum codes) yield keys of size approximately $\Hfuzz(W)$.}  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}.
 We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.
-\bnote{introduce distributional uncertainty here}
-
-\paragraph{Tight Characterization for the Case of a Known Distribution}
-We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
-We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.
-It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).
-
-A number of previous works in this known-distribution setting have provided efficient algorithms and
-tight bounds for specific distributions---generally the uniform distribution or
-i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
-Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
-
-\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
+
+We answer this question in two important settings.
+An important aspect of a fuzzy extractor is how much it knows about the target distribution $W$.
+In the extreme the fuzzy extractor has a complete description of the probability density function of $W$.
+We call this setting the \emph{known distribution} setting.
+(Previous works have consider
+
 Assuming full knowledge of a distribution is often unrealistic.
@@
 Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors).
-Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.
-
-We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
+Thus, the design is fixed with a partially known distribution, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.
+We call this setting \emph{family of distributions}.
+We ask whether fuzzy min-entropy is sufficient in each of these settings.
+
+\paragraph{Sufficiency of $\Hfuzz(W)$ for a Known Distribution}
+We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
+We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.
+It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).
+
+A number of previous works in this known-distribution setting have provided efficient algorithms and
+tight bounds for specific distributions---generally the uniform distribution or
+i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
+Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
+
+\paragraph{Impossibility of a Fuzzy Extractor for a Family of Distributions}
+Our results are negative when the distribution $W$ is only known to come from a family $\mathcal{W}_Z$ (\thref{thm:imposs fuzz ext}).
 Specifically, we show a family of distributions $\mathcal{W}_Z$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.
@@
 Our proof relies on high dimensionality of each $W_z$ and on perfect correctness of the $\rep$ procedure.
+This result shows that uncertainty in the distribution $W$ is devastating to building a fuzzy extractor.
+This result motivates the further research into physical sources.
+\bnote{come back to this sentence}
 
@@
 \hline
-Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})\\
+Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})\\
 \hline
-Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
+Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})
 \end{tabular}
@@
 We compare our positive results to these characterizations in \apref{sec:corr variables}.
-To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for families of distributions.
+To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for a family of distributions.
 
@@
 
-\subsection{Fuzzy Min-Entropy: a Necessary Condition}
+\subsection{Fuzzy Min-Entropy: suitability of a noisy distribution for key derivation}
 \label{sec:minimal conditions}
@@
 \noindent
-\bnote{Should note this is the ideal security of a noisy source, both in the interactive/non-interactive settings}
-Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
-\begin{proposition}
+Fuzzy min-entropy is a necessary condition for security.
+It measures the advantage provided to the adversary by allowing them to run the $\rep$ functionality.
+Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.
+\begin{proposition}~(proof in \apref{sec:proof fuzz necessary})
 \label{prop:fuzz necessary}
-Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
-If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
- with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
+Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, W, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
+\[
+\epsilon\ge 2^{-m}-\delta -2^{-\kappa}.
+\]
+In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
+%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
+% with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
 \end{proposition}
@@
 %\lemref{lem:fuzz necessary} still applies.  
+The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.
+There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
+Our goal is to provide a superlogarithmic length key whenever a distribution has superlogarithmic fuzzy min-entropy.
+
+\paragraph{Conditional Fuzzy min-entropy}
+In our proofs, we will use a conditional version of fuzzy min-entropy.
+\begin{definition}
+\label{def:cond fuzzy ent}
+The $t$-conditional fuzzy min-entropy of a distribution $W |P$ in a metric space $(\mathcal{M}, \dis)$ is:
+\[
+\Hfav(W|P) = -\log \left( \expe_{p\in P} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w|P=p]\right).
+\]
+\end{definition}
+
 \noindent
-There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
-Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.
-
-\bnote{I feel we can provide a more general results than this one.  Helpful?}
+Fuzzy min-entropy obeys a chain rule:
+\begin{lemma}~(proof in \apref{sec:proof fuzz necessary})
+\label{lem:chain rule fuzz}
+$\Hfav(W|P) \ge \Hfuzz(W) - H_0(P)$.
+\end{lemma}
 
@@
 %Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
-\section{Proof of \propref{prop:fuzz necessary}}
+\section{Fuzzy min-entropy}
 \label{sec:proof fuzz necessary}
-\begin{proof}
-Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.
-This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] \geq 1/\poly(n)$.
+\begin{proof}[Proof of \propref{prop:fuzz necessary}]
+Let $W$ be a distribution where $\Hfuzz(W) = m$.
+This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] = 2^{-m}$.
 Consider the following distinguisher $D$:
@@
 \end{itemize}
-Clearly, $\Pr[D(\Key, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
+Clearly, $\Pr[D(\Key, P) = 1]\geq 2^{-m} - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus,
 \[
-\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
+\sd((R, P), (U_\kappa, P)) \ge \delta^D((R, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
 \]
-Note that $D$ only provides an input and looks at the output, thus it extends to an interactive protocol.
-Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.
-Thus, $D$ is also a distinguisher in the computational setting.
-\bnote{this should probably be in the body of the paper}
+\end{proof}
+
+\begin{proof}[Proof of \lemref{lem:chain rule fuzz}]
+\begin{align*}
+\Hfav(W|P) &= -\log \left( \expe_{p\leftarrow P} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w|P=p] \right)\\
+&= -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w|P=p]\Pr[P=p] \right)\\
+&= -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w \wedge P=p] \right)\\
+&\ge -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w] \right)\\
+&\ge -\log \left( \sum_{p} \max_{w'} \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)\\
+&\ge -\log \left( 2^{H_0(P)} \left(\max_{w'} \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)\right)\\
+&\ge \Hfuzz(W) - H_0(P).
+\end{align*}
 \end{proof}
@@
 
+\bnote{new outline to proof. proof to come}
+\begin{enumerate}
+\item show chain rule for fuzzy min-entropy
+\item show that fuzzy min-entropy conditioned on i is related to $\beta_{t, i}$.
+\item show that releasing the sketch only gives delta more than necessary.
+\end{enumerate}
 \noindent
 \textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.
-
-The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.
-The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.
+Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
+
+Let $I$ be the random variable describing the level.
+Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]
+
+In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.
+With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.
+That is, the adversary's best guess is:
+\[
+w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
+\] 
+The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.
 There are $n$ outcomes for $i$.
@@
 \begin{align}
-\expe_{i | m\le i \le m+n}2^{-(i+1)}\beta_{t,i}&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
-&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
-&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
+\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
+%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
+&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
 \end{align}
 \textbf{Security:}
-We now argue security.
+%We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.  
+We now argue security of the construction.
 First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).
@@
 Then
+\begin{align}
+\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
+&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
+\end{align}
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$
+
+Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
+All the dependence between $W$ and $K$ is contained in $L_I$.
+That is, $\Hav(W | K_I , L_I) = \Hav(W | L_I)$.
+Let $Y_I$ denote the outcome of the hash function.
+We now consider the remaining average min-entropy when $1_{\text{low}} = 0$:
 \begin{align*}
-\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
+&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
+&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
+&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
+&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
+&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
+&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
 \end{align*}
-For the remainder of the proof, we seek a bound on 
-\[
-2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
-\]
-We separate out this quantity into levels:\bnote{we need to talk about K here}
+Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
 \begin{align*}
-\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
+\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
 &\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\

### 2015-01-22 trunk/info-bounds/FuzzyExtPossibility.tex

@@
 \textbf{Security:}
-We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.
+%We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.  
 We now argue security of the construction.
@@
 As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
-By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
+By Markov's inequality, there exists a set $A_{\eps}$ such that $\Pr[p\in A_{\eps}]\ge 1/2$ and $\forall p\in A_{\eps}$, 
 \[
-(\Key |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+(\Key |P =p) \approx_{2\epsilon} (U_\kappa , P =p).
 \]
@@
 \begin{proof}
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\eta+t$).
-We now find bound the size of $S_{p^*, \key^*}$.
+By the isoperimetric inequality on the Hamming space~(we use a version
+due to~\cite[Theorem 1]{frankl1981short}, the original result is due
+to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient
+ball $S_{p^*, \key^*}$ centered at $0^n$ and a deficient ball $D$,
+centered at $1^n$, such that
+$|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*,
+  \key^*}^\complement|$ (where $\cdot^\complement$ denotes the
+complement of a set) and $\forall s\in S_{p^*, \key^*}, d\in D$,
+$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).
+We now bound the size of $S_{p^*, \key^*}$.
 
@@
 \end{align*}
+where the second to last equality follows from the definition of $t$
+(as $4\nu \sqrt{n}$) at the beginning of the proof of Theorem~\ref{thm:imposs fuzz ext}.
 \end{proof}

### 2015-01-30 trunk/info-bounds/FuzzyExtPossibility.tex
incerted some notes

@@
 Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.
-These are the interior of $Q_{p^*, r}$:
+These are the interior of $Q_{p^*, r}$: \lnote{what's $r$?
+in this and previous lines?
+also, I can parse definition of interior below}
 \begin{align*}
@@
 We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.
-We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient}
+We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient} \lnote{how about ``almost ball''}
 \begin{definition}
@@
 complement of a set) and $\forall s\in S_{p^*, \key^*}, d\in D$,
-$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).
+$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).\lnote{Why?}
 We now bound the size of $S_{p^*, \key^*}$.
@@
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
-This means that $|S_{p^*, \key^*}|$ is a deficient sphere of radius at most $n/2-t$.
+This means that $|S_{p^*, \key^*}|$ is a deficient sphere \lnote{ball} of radius at most $n/2-t$.
 Let $X$ denote a uniform string on $\zo^n$.
-We use Hoeffding's inequality~\cite{hoeffding1963probability}:
+We use Hoeffding's inequality~\cite{hoeffding1963probability}: \lnote{should the first $n$ in the line below be $n/2$?}
 

### 2015-01-30 constantRate/ConstCompFuzzExt-crypto.tex
edited intro

--- 2014-12-01 constantRate/ConstCompFuzzExt-reorg.tex
@@
 
-\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
+\title{Fuzzy Extractors From Noisy Sources With More Errors Than Entropy}
 %\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
@@
 
-\paragraph{Our Contributions}
+\paragraph{Our Contributions: Handling More Errors than Entropy}
 We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.
 Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$.
-Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.
-Table~\ref{tab:upper bounds} summarizes our constructions.
-Our first construction provides information-theoretic security.
-It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols~(\defref{def:partial source}).
-%It requires an alphabet size that is super constant in the security parameter.
-\lnote{keep this last sentence?}
-
-We switch to computational security to obtain constructions with additional features. Our second construction provides reusability (against computationally bounded adversaries).  
-The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} comes from an allowed distribution.
-The allowed distributions include those that are supported in the first construction, as well as other distributions, such as those with $k$-wise independence among symbols for superlogarithmic $k$.
-This construction requires that the fraction of errors is subconstant.
-
-Our third construction removes the need for fresh entropy in the symbols and allows a constant fraction of symbols of errors, at the cost of requiring a large alphabet size~(super-polynomial in the security parameter).
-It is secure if symbols in $w$
-each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
-a constant fraction of symbols in $w$ may have little or no entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
-%\bnote{rewrite this!}
-%Our first construction is secure when symbols in $w$ each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated.
-Moreover, a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).
-This construction can correct a constant fraction of errors~($\Theta(\ell)$).
-However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
-%
-%We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
-Our second construction supports an arbitrary alphabet size~(though it only achieves $\Huse\le 0$ when the alphabet size is super-constant).
-However, these improvements come at a price to error-tolerance: it tolerates a sub-constant fraction of errors~($o(\ell)$).
-%
-%\consref{cons:sampling} comes with an additional feature: reusability.
-Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.
-The enrolled values $w_i$ and $w_j$ are not assumed to be equal, and so information leakage may add up.
-Indeed, Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.
-Our second construction allows for arbitrary correlation between $w_i$ and $w_j$ against computational adversaries\footnote{Our restriction to computational adversaries implies that the adversary only sees a polynomially bounded number of reuses.
-It remains an open problem to construct a polynomially reusable fuzzy extractor against unbounded adversaries.} as long as each marginal $W_i$ is an admissible distribution.
-%We do not considering the joint distribution $W_1,..., W_q$.
+Naturally, as argued above, these constructions cannot work for all sources of a given entropy; instead, each construction takes advantage of the specific properties of a source.
+
+Our first construction works for \emph{sources with high-entropy samples}: these are sources for which a randomly sampled substring is likely to have sufficient entropy.
+For example, a source can satisfy this condition if sufficiently many symbols are almost $k$-wise independent for some superlogarithmic $k$.
+This construction uses digital lockers~\cite{canetti2008obfuscating}, which lock up the output $r$ using the sampled substring as the key to the locker.
+Such lockers can be constructed using a salted hash function under appropriate assumptions or, more generally, from point obfuscation.
+
+We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with high-entropy marginals}: sources in which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed.
+In this construction, we use single symbols of $w$ for locking up bits of a secret that we then transform into $r$.
+This construction tolerates more errors than the first construction, but requires higher marginal entropy per symbol than the first construction.
+
+Our third construction provides information-theoretic, rather than computational, security.
+It works for \emph{sparse block sources}, which are sources for which a sufficient fraction of the symbols have entropy conditioned on previous blocks.
+It uses symbols-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.
+
+Our approach in all three constructions is different from most known constructions of fuzzy extractors, which put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}).
+We deliberately do not recover $w$, because known techniques for building secure sketches do not work for sources with more errors than entropy, since they lose at least $\log |B_t|$ bits of entropy regardless of the source .(This loss is necessary when the source is uniform~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} or when reusability against a sufficiently rich class of correlations is desired~\cite[Theorem 11]{Boyen2004}; computational definitions of security suffer from similar problems~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.).
+
+\paragraph{Our Contributions: Reusability}
+Our first construction provides reusability (against computationally bounded adversaries).  
+The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} comes from a source with high-entropy samples.
+This construction is the first to provide reusability for a realistic class of correlated readings.
 
@@
 
-\paragraph{Our Approach}
-%\bnote{rewrite this!}
-%Our constructions are computationally secure.
-Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).
-
-%Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10].
-Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).
-
-Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
-Unfortunately, the current techniques for building secure sketches do not work for sources with more errors than entropy, because they lose at least $\log |B_t|$ bits of entropy regardless of the source.
-Moreover, this loss is necessary when the source is uniform~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} or when reusability against a sufficiently rich class of correlations is desired~\cite[Theorem 11]{Boyen2004}.
-
-Additionally, computational definitions of security suffer from similar problems~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.
-Thus, we take a different approach and do not attempt to recover $w$.
-
-Our first construction reduces the alphabet size by hashing each input symbol (which comes from a large alphabet) into a much smaller set, so that the resulting hash value has low entropy deficiency.
-The intuition behind this approach is that it reduces the size of $B_t$ by reducing the alphabet size, but preserves a sufficient portion of the input entropy.
-The resulting string no longer has more errors than entropy.
- We then apply an information-theoretic fuzzy extractor to the resulting string.
-
-Our second construction, which is computationally secure, is based on obfuscated digital lockers~\cite{canetti2008obfuscating}.
-Digital lockers output a secret value only when given the correct input to ``unlock'' the secret.
-An obfuscated digital locker does not provide information about the locked value or how to unlock it.
-The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$.
-To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$.
-We use obfuscation in a way that does not leak partial information; this is crucial to arguing reusability.
-
-Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$.
-Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker.
-To tolerate errors, these bits come from an error correcting code.
-To ensure an  adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor) from the decoded string.
-
-%We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
-%We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is
-%%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.
-However it is known how to construct composable VGB obfuscation for the class of functions we need.}
-%composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong} .
-Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}.
-%Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.
-
-\paragraph{The Required Notion of Obfuscation} 
-Our constructions use simulation-secure  obfuscation of digital lockers, however, we do not require full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
+\paragraph{Relation to Obfuscation} 
+Our constructions use simulation-secure obfuscation of digital lockers, which can be achieved by simple efficient constructions using appropriate assumptions on a salted hash function or on a variant of discrete log.
+\lnote{verify that it's DL and not DH and cite!}
+The precise definition of the obfuscation required is not full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
 Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation~\cite{bitansky2010strong}.
 We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
-Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}.
+Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}. \lnote{revise}
 
@@
 
-\paragraph{Connection to General Obfuscation}
-We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}.
+We also note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}.
 A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$.
@@
 \bnote{we need to say we are weaker than general obfuscation.  happy with this? merged with sentence from above}
-Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.
+Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor. \lnote{revise}
 

### 2015-01-31 trunk/constantRate/ConstCompFuzzExt-crypto.tex
editing the intro for the crypto paper

--- 2015-01-30 constantRate/ConstCompFuzzExt-crypto.tex
@@
 %\documentclass{llncs}
-\def\shownotes{0}
+\def\shownotes{1}
 \def\blinded{0}
@@
 
-\paragraph{Reusable Fuzzy Extractors}
-An additional desirable security property of fuzzy extractors, introduced by Boyen~\cite{Boyen2004}, is called reusability.
-This property is necessary if a user enrolls the same or correlated values multiple times.
-For example, if the source is a biometric reading, the user may enroll the same biometric with different organizations.
-Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
-Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).
-Many traditional fuzzy extractors are not reusable~\cite{Boyen2004,simoens2009privacy,blanton2012non,blanton2013analysis}.
-
 \paragraph{Limitations of Known Approaches}
@@
 
-The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
-
 \paragraph{Our Contributions: Handling More Errors than Entropy}
@@
 
-Our first construction works for \emph{sources with high-entropy samples}: these are sources for which a randomly sampled substring is likely to have sufficient entropy.
-For example, a source can satisfy this condition if sufficiently many symbols are almost $k$-wise independent for some superlogarithmic $k$.
+Our first construction works for \emph{sources with high-entropy samples}: these are sources for which a randomly sampled substring of some superlogarithmic length is likely to have superlogarithmic  entropy.
+For example, a source can satisfy this condition if a constant fraction of symbols are almost $k$-wise independent for some superlogarithmic $k$ (note there is no total entropy requirement:  the total entropy of such a source may be not  much greater than the entropy of the sample).
 This construction uses digital lockers~\cite{canetti2008obfuscating}, which lock up the output $r$ using the sampled substring as the key to the locker.
-Such lockers can be constructed using a salted hash function under appropriate assumptions or, more generally, from point obfuscation.
-
-We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with high-entropy marginals}: sources in which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed.
+Such lockers can be constructed using a salted hash function under appropriate assumptions or, more generally, from point obfuscation, as we discuss below.
+
+We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed.
 In this construction, we use single symbols of $w$ for locking up bits of a secret that we then transform into $r$.
-This construction tolerates more errors than the first construction, but requires higher marginal entropy per symbol than the first construction.
+This construction tolerates a higher error rate than the first construction, but over a larger alphabet, where errors may be more likely.
 
 Our third construction provides information-theoretic, rather than computational, security.
-It works for \emph{sparse block sources}, which are sources for which a sufficient fraction of the symbols have entropy conditioned on previous blocks.
+It works for \emph{sparse block sources}.
+These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks.
 It uses symbols-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.
@@
 Our approach in all three constructions is different from most known constructions of fuzzy extractors, which put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}).
-We deliberately do not recover $w$, because known techniques for building secure sketches do not work for sources with more errors than entropy, since they lose at least $\log |B_t|$ bits of entropy regardless of the source .(This loss is necessary when the source is uniform~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} or when reusability against a sufficiently rich class of correlations is desired~\cite[Theorem 11]{Boyen2004}; computational definitions of security suffer from similar problems~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.).
+We deliberately do not recover $w$, because known techniques for building secure sketches do not work for sources with more errors than entropy, since they lose at least $\log |B_t|$ bits of entropy regardless of the source.
+(This loss is necessary when the source is uniform~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} or when reusability against a sufficiently rich class of correlations is desired~\cite[Theorem 11]{Boyen2004}; computational definitions of secure sketches suffer from similar problems~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.)
 
 \paragraph{Our Contributions: Reusability}
+An additional desirable security property of fuzzy extractors, introduced by Boyen~\cite{Boyen2004}, is called reusability.
+This property is necessary if a user enrolls the same or correlated values multiple times.
+For example, if the source is a biometric reading, the user may enroll the same biometric with different organizations.
+Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
+Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).
+Many traditional fuzzy extractors are not reusable~\cite{Boyen2004,simoens2009privacy,blanton2012non,blanton2013analysis}.
+In fact, the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.
+
 Our first construction provides reusability (against computationally bounded adversaries).  
@@
 \begin{tabular}{l l l l l}
- & Security & Source Structure & Error-Tolerance & Alphabet Size\\
+  & Source Structure & Error Rate  & Techniques\\
 \hline
-Cons. \ref{cons:info theoretic} & Not reusable  & Most symbols  & Constant fraction & Super constant \\
-&  Info-theoretic & contribute entropy & &\\\hline
-Cons. \ref{cons:sampling} & Reusable & Most symbols & Sub constant fraction & Super constant \\
-& Computational & contribute entropy & &\\\hline
-Cons. \ref{cons:first construction} & Not reusable & Symbols correlated  & Constant fraction & Super polynomial\\
-&  Computational & but hard to guess && 
-\end{tabular}
+Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-and-obfuscate \\
+Cons. \ref{cons:first construction}  & high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
+Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-and-fuzzy-extract\\
+\hline\end{tabular}
 \end{center}
 %end centering
-\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
+\caption{Summary of new constructions.  }
 \label{tab:upper bounds}
@@
 \paragraph{Relation to Obfuscation} 
-Our constructions use simulation-secure obfuscation of digital lockers, which can be achieved by simple efficient constructions using appropriate assumptions on a salted hash function or on a variant of discrete log.
-\lnote{verify that it's DL and not DH and cite!}
-The precise definition of the obfuscation required is not full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
-Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation~\cite{bitansky2010strong}.
-We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
-Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}. \lnote{revise}
+Our constructions use simulation-secure obfuscation of digital lockers, which can be achieved by simple efficient constructions using a salted hash function or modular exponentiation under appropriate assumptions~\lnote{refs needed?
+especially for salted hash?}
+The precise definition we require is not full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
+Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation, as long as it remains secure even when several digital lockers with correlated keys are composed~\cite{bitansky2010strong}.
 
@@
 A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$.
-Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
-The construction of Bitansky et al.
-is based on multilinear encoding and is  highly impractical.
-Our constructions use obfuscated digital lockers.
-Obfuscated digital lockers are instantiable under significantly weaker assumptions and can be implemented quite efficiently.
-\bnote{we need to say we are weaker than general obfuscation.  happy with this? merged with sentence from above}
-Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor. \lnote{revise}
+Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation for large classes of programs, including proximity point programs, based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
+However, in contrast to obfuscated digital lockers, the  more general construction of Bitansky et al. is based on stronger assumptions and is highly impractical in terms of efficiency.  
+It is not known how to construct \emph{reusable} fuzzy extractors from general obfuscation, because known obfuscation of proximity point programs is not known to be composable.
 
 \paragraph{Open Problems}
+\lnote{can we kill this paragraph? I don't see how it helps our cause. And in any case the grouping construction supports constant size alphabets}
 All of our constructions support more errors than entropy by using two metrics spaces.

### 2015-01-31 constantRate/ConstCompFuzzExt-crypto.tex
added a sentence on active attacks against p

@@
 traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.
-
-\paragraph{Reusable Fuzzy Extractors}
-An additional desirable security property of fuzzy extractors, introduced by Boyen~\cite{Boyen2004}, is called reusability.
-This property is necessary if a user enrolls the same or correlated values multiple times.
-For example, if the source is a biometric reading, the user may enroll the same biometric with different organizations.
-Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$.
-Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).
-Many traditional fuzzy extractors are not reusable~\cite{Boyen2004,simoens2009privacy,blanton2012non,blanton2013analysis}.
+Note that in this paper we consider only passive attacks on $p$; the problem of protecting against modification of $p$ has been addressed in, e.g., \cite{Boyen05secureremote,DKKRS12}, and, in particular, the random-oracle-based techniques of \cite{Boyen05secureremote} can be applied here, as well.
+\lnote{ok sentence?}
 

### 2015-02-04 trunk/constantRate/ConstCompFuzzExt-crypto.tex
minor edits to introduction

@@
 traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.
+Note that in this paper we consider only passive attacks on $p$; the problem of protecting against modification of $p$ has been addressed in, e.g., \cite{Boyen05secureremote,DKKRS12}.
+In particular, the random-oracle-based transform of \cite[Theorem 1]{Boyen05secureremote} can be applied to our constructions.
 
@@
 Our constructions use simulation-secure obfuscation of digital lockers, which can be achieved by simple efficient constructions using a salted hash function or modular exponentiation under appropriate assumptions~\lnote{refs needed?
-especially for salted hash?}
+especially for salted hash?}\bnote{the canetti 98 paper is okay for one time but we need reusability, the mod exp is bitanski canetti }
 The precise definition we require is not full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.

### 2015-02-04 constantRate/ConstCompFuzzExt-crypto.tex
Minor fixes and lnotes

@@
 
-\title{Fuzzy Extractors From Noisy Sources With More Errors Than Entropy}
+\title{Fuzzy Extractors for Noisy Sources with More Errors Than Entropy}
 %\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
@@
 traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.
-Note that in this paper we consider only passive attacks on $p$; the problem of protecting against modification of $p$ has been addressed in, e.g., \cite{Boyen05secureremote,DKKRS12}, and, in particular, the random-oracle-based techniques of \cite{Boyen05secureremote} can be applied here, as well.
-\lnote{ok sentence?}
+Note that in this paper we consider only passive attacks on $p$; the problem of protecting against modification of $p$ has been addressed in, e.g., \cite{Boyen05secureremote,DKKRS12}.
+In particular, the random-oracle-based transform of \cite[Theorem 1]{Boyen05secureremote} can be applied to our constructions.
 
@@
 In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
-An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.%  A meaningful restriction of correctable errors is an open problem.
+An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.
+\lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem.
 

### 2015-02-06 trunk/constantRate/ConstCompFuzzExt-crypto.tex
happy with intro and obfuscation references

@@
 Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$.
-Naturally, as argued above, these constructions cannot work for all sources of a given entropy; instead, each construction takes advantage of the specific properties of a source.
+Naturally, as argued above, these constructions cannot work for all sources of a given entropy and for any $t$ errors.
+In this work, each construction takes advantage of the specific properties of a source, but still works for any $t$ errors.
+(It is an open problem to achieve our goal by restricting the error patterns instead of restricting the source distribution.)
 
@@
 This construction uses digital lockers~\cite{canetti2008obfuscating}, which lock up the output $r$ using the sampled substring as the key to the locker.
-Such lockers can be constructed using a salted hash function under appropriate assumptions or, more generally, from point obfuscation, as we discuss below.
+Such lockers can be constructed very efficiently via a single application of a cryptographic hash function (under appropriate assumptions) or, more generally, from point obfuscation, as we discuss below.
 
@@
 \paragraph{Relation to Obfuscation} 
-Our constructions use simulation-secure obfuscation of digital lockers, which can be achieved by simple efficient constructions using a salted hash function or modular exponentiation under appropriate assumptions~\lnote{refs needed?
-especially for salted hash?}\bnote{the canetti 98 paper is okay for one time but we need reusability, the mod exp is bitanski canetti }
+Our constructions use simulation-secure obfuscation of digital lockers.
 The precise definition we require is not full-fledged virtual black-box obfuscation~\cite{barak2001possibility}.
 Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation, as long as it remains secure even when several digital lockers with correlated keys are composed~\cite{bitansky2010strong}.
+
+The following simple and efficient construction of digital lockers, proposed by Lynn, Prabhakaran, and Sahai~\cite[Section 4]{lynn2004positive}, provides the desired security in the random oracle model of~\cite{DBLP:conf/ccs/BellareR93}.
+Let $H$ be a cryptographic hash function, modeled as a random oracle.
+To lock up a value $y$ using a key $x$, output the pair $r, H(r, x)\oplus (y||0^k)$, where $r$ is a nonce, $||$ denotes concatenation, and $k$ is some security parameter.
+As long as the entropy of $x$ is superlogarithmic, the adversary has negligible probability of finding the correct $x$; and if the adversary doesn't find the correct $x$, then the adversarial knowledge about $x$ and $y$ is not significantly affected by this locker.
+Concatenation with $0^k$ is used to make sure that it is possible to tell (with certainty $1-2^{-k}$) when the correct value is unlocked.
+
+It is seems plausible that in the real world (without random oracles), specific cryptographic hash functions, if used in this construction, will provide the necessary security~\cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}.
+Moreover, Bitansky and Canetti~\cite{bitansky2010strong}, building on the work of~\cite{canetti2008obfuscating,CKVW10}, show how to obtain composable digital lockers based on a strong version of the Decisional Diffie-Hellman assumption without random oracles.
 
@@
 
-\paragraph{Open Problems}
-\lnote{can we kill this paragraph? I don't see how it helps our cause. And in any case the grouping construction supports constant size alphabets}
-All of our constructions support more errors than entropy by using two metrics spaces.
+%\paragraph{Open Problems}
+%\lnote{can we kill this paragraph? I don't see how it helps our cause. And in any case the grouping construction supports constant size alphabets}
+%All of our constructions support more errors than entropy by using two metrics spaces.
 Errors are tolerated in one metric space and corrected in a second.
@@
 
-In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
-An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.%  A meaningful restriction of correctable errors is an open problem.
+%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
+An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.
+\lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem.
+%\fi
 
@@
 We require that the obfuscation is composable and secure with respect to auxiliary input.
-Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
-They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.
+Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} (following \cite{canetti2008obfuscating,CKVW10}) from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+As described in the Introduction, they can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}, \cite[Section 4]{lynn2004positive}, \cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}.
 

### 2015-02-06 constantRate/ConstCompFuzzExt-crypto.tex
in the middle of surgery rearranging sections

@@
 \hline
-Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-and-obfuscate \\
+Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
 Cons. \ref{cons:first construction}  & high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
-Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-and-fuzzy-extract\\
+Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
 \hline\end{tabular}
@@
 
-In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
+%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.
 An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.
 \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem.
+%\fi
 
@@
 
-\section{Supporting more errors than entropy}
-\label{sec:info theory cons}
-In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy.
-%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
-The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks.
-We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.
-A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.
-Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).
-\begin{definition}
-\label{def:conductor}
-A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
-\end{definition}
-
-The main idea of the construction is that errors are ``corrected'' on the large alphabet~(before condensing) while the entropy loss for the error correction is incurred on a smaller alphabet~(after condensing).
-
-\begin{construction}
-\label{cons:info theoretic}
-Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_\gamma$
-\item For $j=1,..., \gamma$:
-\begin{enumerate}[(i)]
-\item Sample $seed_i\leftarrow \zo^d$.
-\item Set $v_i = \cond(w_i, seed_i)$.
-\end{enumerate}
-\item Set $(r, p') \leftarrow \gen'(v_1,..., v_\gamma)$.
-\item Set $p = (p', seed_1,..., seed_\gamma)$.
-\item Output $(r, p)$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(w', p = (p', seed_1,..., seed_\gamma))$
-\item For $j=1,..., \gamma$:
-\begin{enumerate}[(i)]
-\item Set $v_i' = \cond(w_i', seed_i)$.
-\end{enumerate}
-\item Output $r = \rep'(v', p')$.
-\end{enumerate}
-\vspace{0.7in}
-\end{minipage}
-\end{tabular}
-\end{center}
-\end{construction}
-
-\noindent
-For \consref{cons:info theoretic} to be secure we need most blocks to contribute some entropy to the output.  We call this notion a partial block source.
-
-\begin{definition}
-\label{def:partial source}
-A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
-\]
-\end{definition}
-\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
-The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
-This construction is secure and it supports distributions with more errors than entropy~(proof is in~\apref{sec:info theory sec}).
-
-\begin{lemma}
-\label{lem:info theory sec}
-%Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
-Define $\mathcal{V}$ as the family of all distributions with min-entropy at least $\tilde{\alpha}(\gamma-\beta)$ and let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \mathcal{V}, \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
-Most known constructions of fuzzy extractors are average-case fuzzy extractors.
-For simplicity we refer to $\gen', \rep'$ as simply a fuzzy extractor.}  Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.
-
-\end{lemma}
-
-\subsection{More errors than entropy}
-
-In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.
-The structure of a partial block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
-We assume that $\Hoo(W) = \Theta(\gamma)$.
-The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.
-This means that the input entropy to $(\gen', \rep')$ is $\Theta(\gamma)$.
-We assume that the new alphabet $\mathcal{Y}$ is of constant size.
-Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.
-Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
-More formally:
-\[
-\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) \ge  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
-\]
-That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.
-
-\section{Adding reusability}
+\section{Reusable Construction for Sources with High-Entropy Samples}
 \label{sec:sampling}
-In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with more errors than entropy.
-Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.
-
-The construction samples a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscates the concatenation of these blocks.
-Denote this concatenated value by $V_1$.
-This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.
-Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.
+Let $w$ be a string of symbols (over an arbitrary alphabet) $w=w_1\dots w_\gamma$.
+The construction first chooses a random fuzzy extractor output $r$.
+It then samples a random subset of blocks $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$.
+This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
+Let $\sample_{\gamma, \eta}(\cdot)$ denote an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.
 
@@
 %\end{itemize}
-The use of a computational primitive~(obfuscation of digital lockers) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
-This is the property that allows reusability.
-
-This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
+The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.
+
+This construction can use the na\"{i}ve sampler that takes truly random samples.
+If desired, public randomness may be substantially decreased by using more sophisticated samplers.
 (See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)
@@
 
-\section{Allowing Correlated Symbols}
+\section{Construction for Sources with High-Entropy Marginals}
+
 \label{sec:cor construction}
@@
 
+\section{Information-Theoretic Construction for Sparse Block Sources}
+\label{sec:info theory cons}
+In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy for sparse block sources.
+%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
+The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks.
+We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.
+A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.
+Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).
+\begin{definition}
+\label{def:conductor}
+A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
+\end{definition}
+
+The main idea of the construction is that errors are ``corrected'' on the large alphabet~(before condensing) while the entropy loss for the error correction is incurred on a smaller alphabet~(after condensing).
+
+\begin{construction}
+\label{cons:info theoretic}
+Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\gamma$
+\item For $j=1,..., \gamma$:
+\begin{enumerate}[(i)]
+\item Sample $seed_i\leftarrow \zo^d$.
+\item Set $v_i = \cond(w_i, seed_i)$.
+\end{enumerate}
+\item Set $(r, p') \leftarrow \gen'(v_1,..., v_\gamma)$.
+\item Set $p = (p', seed_1,..., seed_\gamma)$.
+\item Output $(r, p)$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p = (p', seed_1,..., seed_\gamma))$
+\item For $j=1,..., \gamma$:
+\begin{enumerate}[(i)]
+\item Set $v_i' = \cond(w_i', seed_i)$.
+\end{enumerate}
+\item Output $r = \rep'(v', p')$.
+\end{enumerate}
+\vspace{0.7in}
+\end{minipage}
+\end{tabular}
+\end{center}
+\end{construction}
+
+\noindent
+For \consref{cons:info theoretic} to be secure we need most blocks to contribute some entropy to the output.  We call this notion a partial block source.
+
+\begin{definition}
+\label{def:partial source}
+A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\]
+\end{definition}
+\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
+The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
+This construction is secure and it supports distributions with more errors than entropy~(proof is in~\apref{sec:info theory sec}).
+
+\begin{lemma}
+\label{lem:info theory sec}
+%Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
+Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
+Define $\mathcal{V}$ as the family of all distributions with min-entropy at least $\tilde{\alpha}(\gamma-\beta)$ and let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \mathcal{V}, \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
+Most known constructions of fuzzy extractors are average-case fuzzy extractors.
+For simplicity we refer to $\gen', \rep'$ as simply a fuzzy extractor.}  Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.
+
+\end{lemma}
+
+\subsection{More errors than entropy}
+
+In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.
+The structure of a partial block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
+We assume that $\Hoo(W) = \Theta(\gamma)$.
+The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.
+This means that the input entropy to $(\gen', \rep')$ is $\Theta(\gamma)$.
+We assume that the new alphabet $\mathcal{Y}$ is of constant size.
+Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.
+Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
+More formally:
+\[
+\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) \ge  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
+\]
+That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.
+
 \blind{
@@
 Let $\alpha$ be a parameter.
-Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.
+Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) \ge \alpha $.
 Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block source.
@@
 \end{cases}\]
-By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
+By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $g$ queries) such that
 \begin{align}

### 2015-02-09 info-bounds/FuzzyExtPossibility.tex
working on proof of leveled hashing

@@
 \noindent
+
+Before proving security of \consref{cons:leveling} we extend the notation to the maximum likelihood ball containing points of a given probability.
+Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.
+That is,
+\[
+\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
+\]
 
@@
 Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.
-We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
-\[
-\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
-\]
-
-\noindent
-\textbf{Correctness:}  Fix some $w, w'$.
+
+\paragraph{Correctness:}  Fix some $w, w'$.
 If $\Pr[W=w]\le 2^{-(m+\ell)} = 2^{-(m+n)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.
@@
 The first inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.
+
+\paragraph{Security:}
+We now argue security of the construction.
+First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).
+Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
+Then
+\begin{align}
+\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
+&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
+\end{align}
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$
+
+We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  Let $I$ be the random variable of the level information.
+\begin{claim}
+$\Hoo(W | I=i ) -\log \beta_{t, i} \ge \Hfuzz(W | I =i ) \ge \Hoo(W | I =i ) -\log \beta_{t, i}-1$.
+\end{claim}
+\begin{proof}
+We show the left inequality first.
+\begin{align*}
+\Hfuzz(W|I=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | I=i]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
+&= (m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
+&=(m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
+&=(m+i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)\\
+&= m+i-\log \beta_{t, i}.
+\end{align*}
+We now show the right inequality.
+\end{proof}
 
@@
 %We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.
-We now argue security of the construction.
-First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).
-Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
-Then
-\begin{align}
-\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
-&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
-\end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$
 
@@
 As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
-By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
+By Markov's inequality, there exists a set $A_{\epsilon}$ such that $\Pr[p\in A_{\epsilon}]\ge 1/2$ and $\forall p\in A_{\epsilon}$, 
 \[
-(\Key |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
+(\Key |P =p) \approx_{2\epsilon} (U_\kappa , P =p).
 \]
@@
 \begin{proof}
-By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).
-Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\eta+t$).
-We now find bound the size of $S_{p^*, \key^*}$.
+By the isoperimetric inequality on the Hamming space~(we use a version
+due to~\cite[Theorem 1]{frankl1981short}, the original result is due
+to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient
+ball $S_{p^*, \key^*}$ centered at $0^n$ and a deficient ball $D$,
+centered at $1^n$, such that
+$|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*,
+  \key^*}^\complement|$ (where $\cdot^\complement$ denotes the
+complement of a set) and $\forall s\in S_{p^*, \key^*}, d\in D$,
+$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).\lnote{Why?}
+We now bound the size of $S_{p^*, \key^*}$.
 

### 2015-02-09 trunk/info-bounds/FuzzyExtPossibility.tex
proof outline for leveled hashing

@@
 We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
-
-High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
+Fuzzy min-entropy measures the success of the adversary when provided with the functionality of the fuzzy extractor.
+It measures the \emph{ideal} security of a distribution.
+
+High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required (assuming the existence of semantically-secure graded encodings).
 Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
-In this work, we ask: \emph{is fuzzy min-entropy sufficient to build information-theoretic fuzzy extractors?}
-
-\bnote{fuzzy min-entropy measures ideal security ... similar to encryption/etc.}
-\bnote{should introduce the idea of distributional uncertainty...very important for us}
-%\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
-%\lnote{may be use``analyzing this quantity may be more fruitful than analyzing min-entropy and error-tolerance separately''}
-
-We give a positive answer to this question when the fuzzy extractor knows the precise distribution of the physical source.
-On the other hand, because it is imprudent to assume precise knowledge of a complicated distribution,  fuzzy extractors are typically designed to work for families of sources.
+The challenge is to design information-theoretic fuzzy extractors whose security (almost) matches the fuzzy min-entropy of a distribution.
+
+In this work, we ask whether this challenge is inherent.
+ We provide two main technical results.
+\begin{itemize}
+\item \textbf{Sufficiency of fuzzy min-entropy:}  It is possible to build a fuzzy extractor for any \emph{precisely known} physical source.
+This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.
+Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.
+\item \textbf{Cost of distributional uncertainty:}  High entropy distributions can never be fully observed and must be modeled.
+An adversary may have a better model than the fuzzy extractor designer.
+To compensate, fuzzy extractors are typically designed to work for families of physical sources.
 We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.
-
+This result justifies further study of physical sources to increase the fidelity of our models.
+\end{itemize}
 We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.
-
-\lnote{mention computational setting?}
-\lnote{mention the typical analysis that separates min-entropy and error-tolerance?}
+Our results are information-theoretic, but we discuss implications for the computational setting.
 
@@
 
-\bnote{new outline to proof. proof to come}
-\begin{enumerate}
-\item show chain rule for fuzzy min-entropy
-\item show that fuzzy min-entropy conditioned on i is related to $\beta_{t, i}$.
-\item show that releasing the sketch only gives delta more than necessary.
-\end{enumerate}
-\noindent
-\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.
-Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
-
-Let $I$ be the random variable describing the level.
-Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]
-
-In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.
-With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.
-That is, the adversary's best guess is:
-\[
-w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
-\] 
-The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.
-There are $n$ outcomes for $i$.
-The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
-That is,
-\begin{align}
-\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
-%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
-&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
-\end{align}
-\textbf{Security:}
-%We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.  
+\paragraph{Security:}
 We now argue security of the construction.
@@
 \end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$
-
-Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
-All the dependence between $W$ and $K$ is contained in $L_I$.
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notation clarity).
+
+\begin{align}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}=0} \wedge I=i}) \right)\nonumber\\
+&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}=0} \wedge I=i)}\right)\nonumber\\
+&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}=0} \wedge I=i)}\right)\nonumber\\
+&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
+&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
+&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
+&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
+\end{align}
+
+We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  
+\pagebreak
+\begin{claim}
+\label{cl:fuzz proportional beta}
+$\Hoo(W | I=i ) -\log \beta_{t, i} \ge \Hfuzz(W | I =i )-1$.\bnote{this is where I'm stuck right now.
+We started with a nearly flat distribution which would allow us to prove this.
+When we condition on $I=i$ it doesn't need to be nearly flat.}
+\end{claim}
+\begin{proof}
+\begin{align*}
+\Hfuzz(W|I=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | I=i]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
+&= (m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
+&=(m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
+&=(m+i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)\\
+&= m+i-\log \beta_{t, i}.
+\end{align*}
+\bnote{this proof doesn't follow.}
+\end{proof}
+
+\noindent
+Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
+\begin{align*}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}})-1}\right) -\log 1/\delta \\
+&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log 1/\delta \\
+&=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log 1/\delta \\
+&\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log 1/\delta.
+\end{align*}
+Where the last line follows by \lemref{lem:chain rule fuzz}.\bnote{need to get rid of low prob here}
+
+%\bnote{old proof stuff}
+%\noindent
+%\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.
+Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
+%
+%Let $I$ be the random variable describing the level.
+Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]
+%
+%In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.
+With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.
+That is, the adversary's best guess is:
+%\[
+%w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
+%\] 
+%The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.
+There are $n$ outcomes for $i$.
+The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
+That is,
+%\begin{align}
+%\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
+%%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
+%&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
+%\end{align}
+%\textbf{Security:}
+%%We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.  
+%
+%Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
+%All the dependence between $W$ and $K$ is contained in $L_I$.
 That is, $\Hav(W | K_I , L_I) = \Hav(W | L_I)$.
@@
 We now consider the remaining average min-entropy when $1_{\text{low}} = 0$:
-\begin{align*}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
-&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
-&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
-&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
-&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
-&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
-&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
-\end{align*}
-Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
-\begin{align*}
-\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
-&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
-%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
+%\begin{align*}
+%\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
+%&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
+%&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
+%&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
+%&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
+%&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
+%&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
 %\end{align*}
-%Now consider This allows us to conclude that 
+%Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
 %\begin{align*}
-%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
-&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
-\end{align*}
-Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
+%\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
+%&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
+%&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
+%&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
+%%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
+%%\end{align*}
+%%Now consider This allows us to conclude that 
+%%\begin{align*}
+%%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
+%&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
+%\end{align*}
+%Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
 Combining both cases we have:
@@
 As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
-By Markov's inequality, there exists a set $A_{\eps}$ such that $\Pr[p\in A_{\eps}]\ge 1/2$ and $\forall p\in A_{\eps}$, 
+By Markov's inequality, there exists a set $A_{\epsilon}$ such that $\Pr[p\in A_{\epsilon}]\ge 1/2$ and $\forall p\in A_{\epsilon}$, 
 \[

### 2015-02-09 info-bounds/FuzzyExtPossibility.tex
revised proof leveled hashing

@@
 Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.
-\begin{proposition}~(proof in \apref{sec:proof fuzz necessary})
+All proofs for statements in this section can be found in \apref{sec:proof fuzz necessary}.
+\begin{proposition}
 \label{prop:fuzz necessary}
@@
 Our goal is to provide a superlogarithmic length key whenever a distribution has superlogarithmic fuzzy min-entropy. 
+Fuzzy min-entropy obeys some natural entropy properties:
+\begin{lemma}
+\label{lem:conditional fuzz rule}
+$\Hfuzz(W|P=p) \ge \Hfuzz(W) + \log \Pr[P=p]$.
+\end{lemma}
 
@@
 \noindent
-Fuzzy min-entropy obeys a chain rule:
-\begin{lemma}~(proof in \apref{sec:proof fuzz necessary})
+
+\begin{lemma}
 \label{lem:chain rule fuzz}
@@
 \end{proof}
+\begin{proof}[Proof of \lemref{lem:conditional fuzz rule}]
+\begin{align*}
+\Hfuzz(W | P=p) &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \Pr[W=w | P=p] \right)\\
+ &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
+ &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
+ &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
+ &= \Hfuzz(W) - \log \frac{1}{\Pr[P=p]}.
+\end{align*}
+\end{proof}
 
@@
 \end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$
-
-We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  Let $I$ be the random variable of the level information.
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notation clarity).
+
+\begin{align}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge I=i}) \right)\nonumber\\
+&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
+&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
+&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
+&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
+&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
+&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
+\end{align}
+
+\noindent
+We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  
 \begin{claim}
-$\Hoo(W | I=i ) -\log \beta_{t, i} \ge \Hfuzz(W | I =i ) \ge \Hoo(W | I =i ) -\log \beta_{t, i}-1$.
+\label{cl:fuzz proportional beta}
+\[\Hoo(W | 1_{\text{low}} =0 \wedge J=j ) -\log \beta_{t, i} \ge \Hfuzz(W | J=j \wedge 1_{\text{low}}=0)+1.\]
 \end{claim}
 \begin{proof}
-We show the left inequality first.
+For convenience denote by $J=j$ the random variable $1_{\text{low}}=0 \wedge I=i$. 
 \begin{align*}
-\Hfuzz(W|I=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | I=i]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
-&= (m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
-&=(m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
-&=(m+i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)\\
-&= m+i-\log \beta_{t, i}.
+\Hfuzz(W|J=j) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | J=j]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \min_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \max_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)+1\\
+&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-\Hoo(W|J=j)}\right) \right)+1\\
+&= \Hoo(W|J=j)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 1\right) \right)+1\\
+&=\Hoo(W|J=j)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
+&=\Hoo(W|J=j)+1-\log \beta_{t, i}.
 \end{align*}
-We now show the right inequality.
-\end{proof}
-
-\bnote{new outline to proof. proof to come}
-\begin{enumerate}
-\item show chain rule for fuzzy min-entropy
-\item show that fuzzy min-entropy conditioned on i is related to $\beta_{t, i}$.
-\item show that releasing the sketch only gives delta more than necessary.
-\end{enumerate}
+Where the third line follows by \clref{cl:nearly flat after conditioning}, which follows.  This completes the proof of \clref{cl:fuzz proportional beta}.
+\end{proof}
+
+\begin{claim}
+\label{cl:nearly flat after conditioning}
+Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.
+Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
+\end{claim}
+\begin{proof}
+\begin{align*}
+\Pr[W=w_1 | J=j] &=&\frac{\Pr[W=w_1\wedge J=j] }{\Pr[J=j]}
+&=& \frac{\Pr[W=w_1]}{\Pr[J=j]}\\
+&\ge& \frac{\Pr[W=w_2]}{2 \Pr[J=j]}
+&=& \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
+&=&\frac{\Pr[W=w_2]}{2}.
+\end{align*}
+Where the first and last equality follow by Bayes' rule.
+The second and fourth equality follow by noting that $\Pr[W=w \wedge J=j] = \Pr[W=w]$ for all $w\in L_i$.
+The inequality proceeds by assumption.
+This completes the proof of \clref{cl:nearly flat after conditioning}.
+\end{proof}
+
 \noindent 
-\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.
-Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
-
-Let $I$ be the random variable describing the level.
-Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]
-
-In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.
-With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.
-That is, the adversary's best guess is:
-\[
-w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
-\] 
-The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.
-There are $n$ outcomes for $i$.
-The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
-That is,
-\begin{align}
-\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
-%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
-&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
-\end{align}
-\textbf{Security:}
-%We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.
-
-Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
-All the dependence between $W$ and $K$ is contained in $L_I$.
-That is, $\Hav(W | K_I , L_I) = \Hav(W | L_I)$.
-Let $Y_I$ denote the outcome of the hash function.
-We now consider the remaining average min-entropy when $1_{\text{low}} = 0$:
+We now return to the proof of \lemref{lem:flat hashing}. Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
 \begin{align*}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
-&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
-&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
-&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
-&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
-&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
-&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
+&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
+&=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log \frac{1}{\delta} \\
+&\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log \frac{1}{\delta}\\
+&\ge\Hfuzz(W)-1-\log n -\log \frac{1}{\delta} - \log (1-2^{-m})
 \end{align*}
-Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
+Where the second-to-last line follows by \lemref{lem:chain rule fuzz}.  The last line follows by \lemref{lem:conditional fuzz rule} and by noting that $\Pr[1_{\text{low}}=0] \ge 1/(1-2^{-m})$.
+Returning to equation \ref{eq:min-entropy} one has:
 \begin{align*}
-\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
-&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
-&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
-%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
-%\end{align*}
-%Now consider This allows us to conclude that 
-%\begin{align*}
-%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
-&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
+\Hav(W | \sketch(W)) &\ge -\log\left( 2^{-m} + (1-2^{-m}) 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)\\
+&\ge -\log \left(2^{-m}+2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\right)\\
+&\ge -\log \min\{2^{-m}, 2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\}-1\\
+&\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  -2\log (1-2^{-m}) \\
+&\ge \Hfuzz(W) - 3- \log n - \log 1/\delta
 \end{align*}
-Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
-Combining both cases we have:
-\begin{align*}
-\Hav(W | \sketch(W)) &\ge -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
-&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
-&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
-&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
-\end{align*}
-Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$.
-The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
+Where the fourth line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$.
+The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \le 1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
 \end{proof}

### 2015-02-09 trunk/info-bounds/FuzzyExtPossibility.tex
revised proof leveled hashing

@@
 Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.
-When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 4$.
 
@@
 We provide a proof in \apref{sec:proof of layered hashing}.
-The main idea is to show that an adversary that knows the level of $w$ cannot perform much better than an adversary without this information.
-\bnote{this sentence isn't helpful, provide better intuition}
+The main idea is that providing the level information makes the distribution look nearly flat~(the probability of points differs by at most a factor of two).
+We can apply similar techniques to \lemref{lem:flat hashing} to show security for each nearly flat distribution.
+Then, we show that providing the level information does not hurt security too much.
 
@@
 \end{proof}
+\begin{proof}[Proof of \lemref{lem:conditional fuzz rule}]
+\begin{align*}
+\Hfuzz(W | P=p) &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \Pr[W=w | P=p] \right)\\
+ &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
+ &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
+ &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
+ &= \Hfuzz(W) + \log \Pr[P=p].
+\end{align*}
+\end{proof}
 
@@
 \end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notation clarity).
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notational clarity).
 
 \begin{align}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}=0} \wedge I=i}) \right)\nonumber\\
-&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}=0} \wedge I=i)}\right)\nonumber\\
-&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}=0} \wedge I=i)}\right)\nonumber\\
-&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
-&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
-&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
-&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}=0} \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge I=i}) \right)\nonumber\\
+&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
+&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
+&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
+&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
+&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
+&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
 \end{align}
 
+\noindent
+The third line follows because the only dependence between $\mathcal{K}_i$ and $W$ is in $i$.
+The fourth line follows by \cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
 We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.
-\pagebreak
 \begin{claim}
 \label{cl:fuzz proportional beta}
-$\Hoo(W | I=i ) -\log \beta_{t, i} \ge \Hfuzz(W | I =i )-1$.\bnote{this is where I'm stuck right now.
-We started with a nearly flat distribution which would allow us to prove this.
-When we condition on $I=i$ it doesn't need to be nearly flat.}
+\[\Hoo(W | 1_{\text{low}} =0 \wedge J=j ) -\log \beta_{t, i} \ge \Hfuzz(W | J=j \wedge 1_{\text{low}}=0)-1.\]
+\end{claim}
+\begin{proof}
+For convenience denote by $J=j$ the random variable $1_{\text{low}}=0 \wedge I=i$. 
+\begin{align*}
+\Hfuzz(W|J=j) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | J=j]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \min_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \max_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)+1\\
+&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-\Hoo(W|J=j)}\right) \right)+1\\
+&= \Hoo(W|J=j)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 1\right) \right)+1\\
+&=\Hoo(W|J=j)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
+&=\Hoo(W|J=j)+1-\log \beta_{t, i}.
+\end{align*}
+Where the third line follows by \clref{cl:nearly flat after conditioning}, which follow the body of the proof.  This completes the proof of \clref{cl:fuzz proportional beta}.
+\end{proof}
+
+\noindent 
+We now return to the proof of \thref{thm:layered hashing}. Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
+\begin{align*}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
+&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
+&=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log \frac{1}{\delta} \\
+&\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log \frac{1}{\delta}\\
+&\ge\Hfuzz(W)-1-\log n -\log \frac{1}{\delta} - \log (1-2^{-m})
+\end{align*}
+Where the second-to-last line follows by \lemref{lem:chain rule fuzz}.  The last line follows by \lemref{lem:conditional fuzz rule} and by noting that $\Pr[1_{\text{low}}=0] \ge 1/(1-2^{-m})$.
+Returning to equation \ref{eq:min-entropy} one has:
+\begin{align*}
+\Hav(W | \sketch(W)) &\ge -\log\left( 2^{-m} + (1-2^{-m}) 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)\\
+&\ge -\log \left(2^{-m}+2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\right)\\
+&\ge -\log \min\{2^{-m}, 2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\}-1\\
+&\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  -2\log (1-2^{-m}) \\
+&\ge \Hfuzz(W) - 4- \log n - \log 1/\delta
+\end{align*}
+Where the fourth line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$.
+The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \le 1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
+\end{proof}
+
+\begin{claim}
+\label{cl:nearly flat after conditioning}
+Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.
+Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
 \end{claim}
@@
 \begin{align*}
-\Hfuzz(W|I=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | I=i]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
-&= (m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
-&=(m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
-&=(m+i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)\\
-&= m+i-\log \beta_{t, i}.
+\Pr[W=w_1 | J=j] &=\frac{\Pr[W=w_1\wedge J=j] }{\Pr[J=j]}\\
+&= \frac{\Pr[W=w_1]}{\Pr[J=j]}\\
+&\ge \frac{\Pr[W=w_2]}{2 \Pr[J=j]}\\
+&= \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
+&=\frac{\Pr[W=w_2]}{2}.
 \end{align*}
-\bnote{this proof doesn't follow.}
-\end{proof}
-
-\noindent
-Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
-\begin{align*}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}})-1}\right) -\log 1/\delta \\
-&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log 1/\delta \\
-&=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log 1/\delta \\
-&\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log 1/\delta.
-\end{align*}
-Where the last line follows by \lemref{lem:chain rule fuzz}.\bnote{need to get rid of low prob here}
-
-%\bnote{old proof stuff}
-%\noindent
-%\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.
-Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.
-%
-%Let $I$ be the random variable describing the level.
-Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]
-%
-%In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.
-With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.
-That is, the adversary's best guess is:
-%\[
-%w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
-%\] 
-%The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.
-There are $n$ outcomes for $i$.
-The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).
-That is,
-%\begin{align}
-%\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
-%%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
-%&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
-%\end{align}
-%\textbf{Security:}
-%%We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.  
-%
-%Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
-%All the dependence between $W$ and $K$ is contained in $L_I$.
-That is, $\Hav(W | K_I , L_I) = \Hav(W | L_I)$.
-Let $Y_I$ denote the outcome of the hash function.
-We now consider the remaining average min-entropy when $1_{\text{low}} = 0$:
-%\begin{align*}
-%\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
-%&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
-%&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
-%&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
-%&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
-%&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
-%&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
-%\end{align*}
-%Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
-%\begin{align*}
-%\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
-%&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
-%&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
-%&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
-%%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
-%%\end{align*}
-%%Now consider This allows us to conclude that 
-%%\begin{align*}
-%%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
-%&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
-%\end{align*}
-%Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
-Combining both cases we have:
-\begin{align*}
-\Hav(W | \sketch(W)) &\ge -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
-&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
-&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
-&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
-\end{align*}
-Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$.
-The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
+Where the first and last equality follow by Bayes' rule.
+The second and fourth equality follow by noting that $\Pr[W=w \wedge J=j] = \Pr[W=w \wedge 1_{\text{low}}=0 \wedge I=i] = \Pr[W=w]$ for all $w\in L_i$.
+The inequality proceeds by assumption.
+This completes the proof of \clref{cl:nearly flat after conditioning}.
 \end{proof}

### 2015-02-09 trunk/info-bounds/FuzzyExtPossibility.tex
cleaning up proof of negatie results

@@
 We prove the stronger average case statement.
-Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
+Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}+1$ and note that $n/\nu >t$.
 
@@
 \begin{itemize}
-\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
-\item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
+\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $\Key_{small}$.  
+\item Consider some $\key \in \Key_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
 Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.
@@
 \label{sec:proof fuzz necessary}
+In this section, we provide proofs of the items in \secref{sec:minimal conditions}.  
 \begin{proof}[Proof of \propref{prop:fuzz necessary}]
@@
 \begin{itemize}
-\item Input $r, p$.
-\item If $\rep(w', p) = r$, output $1$.
+\item Input $\key, p$.
+\item If $\rep(w', p) = \key$, output $1$.
 \item Else output $0$.
@@
 \[
-\sd((R, P), (U_\kappa, P)) \ge \delta^D((R, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
+\sd((\Key, P), (U_\kappa, P)) \ge \delta^D((\Key, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
 \]
+This completes the proof of \propref{prop:fuzz necessary}.
 \end{proof}
@@
  &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
- &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
+% &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
  &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
@@
 \end{align*}
+This completes the proof of \lemref{lem:conditional fuzz rule}.
 \end{proof}
@@
 \end{align*}
+This completes the proof of \lemref{lem:chain rule fuzz}.
 \end{proof}
@@
 \end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notational clarity).
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $L_I$ be the random variable of the level information (in what follows, $L_I$ takes values between $m$ and $m+n$, where possible we omit this for notational clarity).
 
 \begin{align}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge I=i}) \right)\nonumber\\
-&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
-&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
-&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
-&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
-&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
-&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge L_I =i }) \right)\nonumber\\
+&=-\log \left( \expe_{i} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
+&=-\log \left( \expe_{i} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
+&\ge-\log \left( \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
+&\ge-\log \left(\frac{1}{\delta} \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
+&\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
+&\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
 \end{align}
@@
 We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.
+For convenience denote by $J \overset{def}= (L_I \wedge 1_{\text{low}}=0)$.
+That is, $\Pr[J=i] \overset{def}= \Pr[1_{\text{low}}=0 \wedge L_I=i$].
 \begin{claim}
 \label{cl:fuzz proportional beta}
-\[\Hoo(W | 1_{\text{low}} =0 \wedge J=j ) -\log \beta_{t, i} \ge \Hfuzz(W | J=j \wedge 1_{\text{low}}=0)-1.\]
+$\Hoo(W |   J=i ) -\log \beta_{t, i} \ge \Hfuzz(W | J=i)-1.$
 \end{claim}
 \begin{proof}
-For convenience denote by $J=j$ the random variable $1_{\text{low}}=0 \wedge I=i$. 
 \begin{align*}
-\Hfuzz(W|J=j) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | J=j]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \min_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \max_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)+1\\
-&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-\Hoo(W|J=j)}\right) \right)+1\\
-&= \Hoo(W|J=j)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 1\right) \right)+1\\
-&=\Hoo(W|J=j)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
-&=\Hoo(W|J=j)+1-\log \beta_{t, i}.
+\Hfuzz(W|J=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \Pr[W=w | J=i]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t}\left( \min_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \left(\max_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)+1\\
+&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 2^{-\Hoo(W|J=i)}\right) \right)+1\\
+&= \Hoo(W|J=i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 1\right) \right)+1\\
+&=\Hoo(W|J=i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
+&=\Hoo(W|J=i)+1-\log \beta_{t, i}.
 \end{align*}
-Where the third line follows by \clref{cl:nearly flat after conditioning}, which follow the body of the proof.  This completes the proof of \clref{cl:fuzz proportional beta}.
+Where the third line follows by \lemref{lem:nearly flat after conditioning}, which follows the proof of \thref{thm:layered hashing}.  This completes the proof of \clref{cl:fuzz proportional beta}.
 \end{proof}
@@
 \begin{align*}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
-&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
+&=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
 &=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log \frac{1}{\delta} \\
@@
 
-\begin{claim}
-\label{cl:nearly flat after conditioning}
+\begin{lemma}
+\label{lem:nearly flat after conditioning}
 Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.
 Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
-\end{claim}
+\end{lemma}
 \begin{proof}
@@
 &= \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
-&=\frac{\Pr[W=w_2]}{2}.
+&=\frac{\Pr[W=w_2 | J=j]}{2}.
 \end{align*}
@@
 The inequality proceeds by assumption.
-This completes the proof of \clref{cl:nearly flat after conditioning}.
+This completes the proof of \lemref{lem:nearly flat after conditioning}.
 \end{proof}
@@
 \label{lem:fuzz can't get key}
-Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
+Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(\Key, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
 \end{lemma}
@@
 
-Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
+Consider some $p^*\in A_{p}$.  
 The distribution $\Key|P=p^*$ is the set of possible keys.
@@
 
-There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.
+There exists a set $\Key_{small}$  where $|\Key_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in \Key_{small}$,  $|Q_{p^*, \key}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.
 If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
-For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
+For the remainder of the proof we restrict ourselves to elements in $\Key_{small}$.
 Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.
-These are the interior of $Q_{p^*, r}$: \lnote{what's $r$?
-in this and previous lines?
-also, I can parse definition of interior below}
+These are points where all points within distance $t$ map to the same key.
+We call this set the interior of $Q_{p^*, \key}$:
 \begin{align*}
-\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
+\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge (\forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key)\},\\
 %\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
 \end{align*}
-
-%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.
-We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient} \lnote{how about ``almost ball''}
+ The isoperimetric inequality says $\inter(Q_{p^*, \key})$ must be of bounded size.
+This statement use the sets which are nearly balls in the Hamming space\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.
+We use the term near ball for emphasis.}:
 \begin{definition}
-A set $S$ is a $\eta$-deficient ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
+A set $S$ is a $\eta$-near ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
 \end{definition}
-
-Consider some $\key^*\in R_{small}$.  
-We now proceed to show that the interior of each $Q_{p^*, \key^*}$ is small:
-%Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+\noindent
+We now show for any $\key^*$, $\inter(Q_{p^*, \key^*})$ is small:
 
@@
 due to~\cite[Theorem 1]{frankl1981short}, the original result is due
-to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient
-ball $S_{p^*, \key^*}$ centered at $0^n$ and a deficient ball $D$,
+to Harper~\cite{harper1966optimal}), there exists a $\eta$-near
+ball $S_{p^*, \key^*}$ centered at $0^n$ and a near ball $D$,
 centered at $1^n$, such that
@@
 complement of a set) and $\forall s\in S_{p^*, \key^*}, d\in D$,
-$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).\lnote{Why?}
+$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).
+Since $S_{p^*, \key^*}$ is a near ball and the set $D^\complement$ contains all points of distance less than $t$ from $S_{p^*, \key^*}$.
+Thus, the set $S_{p^*, \key^*} \cup D^\complement$ contains a near ball of radius is $\eta+t-1$).
 We now bound the size of $S_{p^*, \key^*}$.
 
-Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.
+Recall that $|S_{p^*, \key^*} \cup D^\complement| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
-This means that $|S_{p^*, \key^*}|$ is a deficient sphere \lnote{ball} of radius at most $n/2-t$.
+This means that $|S_{p^*, \key^*}|$ is a near ball of radius at most $n/2-t+1$.
 Let $X$ denote a uniform string on $\zo^n$.
-We use Hoeffding's inequality~\cite{hoeffding1963probability}: \lnote{should the first $n$ in the line below be $n/2$?}
+We use Hoeffding's inequality~\cite{hoeffding1963probability}:
 
 \begin{align*}
-|S_{p^*, \key^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr_{X\leftarrow \zo^n} [ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}
+|S_{p^*, \key^*}| &\le \{ x | \dis (x, 0)\le \frac{n}{2}-t+1\}\\&= 2^n \Pr_{X\leftarrow \zo^n} [ wt(X) \le (\frac{1}{2}-\frac{t-1}{n})n] \\
+&\le 2^n e^{-n (((t-1)/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}.
 \end{align*}
 where the second to last equality follows from the definition of $t$
-(as $4\nu \sqrt{n}$) at the beginning of the proof of Theorem~\ref{thm:imposs fuzz ext}.
+(as $4\nu \sqrt{n}+1$) at the beginning of the proof of Theorem~\ref{thm:imposs fuzz ext}.
 \end{proof}
@@
 The optimum strategy is to include these values uniformly from different $Z$ values.
-Consider the set of all preimages of $R_{small}$ denoted $Q_{small} = \cup_{\key\in R_{small}} \inter(Q_{\key, p^*})$.
-Note that $Q_{small} \le 2^{n-4\nu}|R_{small}|$.
+Consider the set of all preimages of $\Key_{small}$ denoted $Q_{small} = \cup_{\key\in \Key_{small}} \inter(Q_{\key, p^*})$.
+Note that $Q_{small} \le 2^{n-4\nu}|\Key_{small}|$.
 We now show that the intersection between $Q_{\key, p^*}$ is small for most possible values $z$.
@@
 \expe_z |Q_{small} \cap (V | P=p^* \wedge Z=z) | &\le \left(\frac{\text{\# items}+\text{\# containers}}{\text{\# containers}}\right)\\
-&\le \frac{2^{n-4\nu}|R_{small}|}{2^{n - 3\nu}}+1\\
-&=\frac{|R_{small}|}{2^{\nu}}+1
+&\le \frac{2^{n-4\nu}|\Key_{small}|}{2^{n - 3\nu}}+1\\
+&=\frac{|\Key_{small}|}{2^{\nu}}+1
 \end{align*}
 In expectation across $Z$, 
-\[\frac{\frac{|R_{small}|}{2^{\nu}}+1}{|R_{small}|} \le \frac{1}{2^\nu}+\frac{1}{|R_{small}|} \] fraction of $R_{small}$ receive any support.
-%Thus, at most $1+1/2^{\nu} = \ngl(n)$ keys in $R_{small}$ have any support  conditioned on $p^*$ and $Z$~(note this is an expectation across the values of $Z$).
+\[\frac{\frac{|\Key_{small}|}{2^{\nu}}+1}{|\Key_{small}|} \le \frac{1}{2^\nu}+\frac{1}{|\Key_{small}|} \] fraction of $\Key_{small}$ receive any support.  
 We now present a distinguisher $D_{p^*}$ for a particular $p^*$:
 \begin{enumerate}
-\item On input $x, z$.
+\item On input $\key, z$.
 %\item If $x\not \in R_{small}$ output random bit $b$.
-\item Compute $V|P=p^* \wedge Z=z$ and $Q_{p^*, x}$. 
-\item If $(Q_{p^*, x} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
+\item Compute $V|P=p^* \wedge Z=z$ and $Q_{p^*, \key}$. 
+\item If $(Q_{p^*, \key} \cap V|P=p^* \wedge Z=z) =\emptyset$ output $b=0$.
 \item Else output $b=1$.
@@
 
-The distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
+The distinguisher $D(\key, p, z)$ is formed by calling $D_p(\key, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
 \begin{align*}
@@
 &\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|R_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in R_{small}]\right) - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in R_{small}] \right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in \Key_{small}]\Pr[U\in \Key_{small}] - \Pr[U\not\in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|\Key_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in \Key_{small}]\right) - \Pr[U\not\in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in \Key_{small}] \right)\\
 &\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/4-\ngl(n)\right) \ge \frac{1}{8}-\ngl(n).
 \end{align*}
-The sixth line follows since $R_{small} \ge 2^{\kappa-1}\ge 2$.  The eighth line follows because $\Pr[U\in R_{small}]\ge 1/2$.  The last inequality proceeds because $\Pr[P\in A_p]\ge 1/2$.
+The sixth line follows since $\Key_{small} \ge 2^{\kappa-1}\ge 2$.  The eighth line follows because $\Pr[U\in \Key_{small}]\ge 1/2$.  The last inequality proceeds because $\Pr[P\in A_p]\ge 1/2$.
 This completes the proof of \lemref{lem:fuzz can't get key}.

### 2015-02-10 trunk/info-bounds/FuzzyExtPossibility.tex
revisions in body on notation and theme

@@
 We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
-Fuzzy min-entropy measures the success of the adversary when provided with the functionality of the fuzzy extractor.
-It measures the \emph{ideal} security of a distribution.
-
-High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required (assuming the existence of semantically-secure graded encodings).
+Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor and thus the \emph{ideal} security possible from a noisy distribution.
+
+High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
 Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
 The challenge is to design information-theoretic fuzzy extractors whose security (almost) matches the fuzzy min-entropy of a distribution.
-
 In this work, we ask whether this challenge is inherent.
@@
 \begin{itemize}
-\item \textbf{Sufficiency of fuzzy min-entropy:}  It is possible to build a fuzzy extractor for any \emph{precisely known} physical source.
+\item \textbf{Sufficiency of fuzzy min-entropy:}  We construct a fuzzy extractor for each physical source with fuzzy min-entropy.
 This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.
 Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.
-\item \textbf{Cost of distributional uncertainty:}  High entropy distributions can never be fully observed and must be modeled.
+The constructed fuzzy extractor must \emph{precisely know} the distribution of the noisy source.
+\item \textbf{Cost of distributional uncertainty:}  High entropy sources can never be fully observed and must be modeled.
 An adversary may have a better model than the fuzzy extractor designer.
@@
 We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.
-This result justifies further study of physical sources to increase the fidelity of our models.
+This result emphasizes the importance of high fidelity models of high entropy sources.
 \end{itemize}
@@
 Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.
+It can be thought of as measuring the ideal security of a noisy source of entropy when used for key derivation.
+This is similar to how security is measured for program obfuscation~\cite{barak2001possibility}, we discuss the connection to program obfuscation in \secref{sec:related settings}.
 Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).
-Fuzzy min-entropy measures the maximum obtainable key from a noisy distribution.
+
 However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
@@
 We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.
-
-We answer this question in two important settings.
-An important aspect of a fuzzy extractor is how much it knows about the target distribution $W$.
-In the extreme the fuzzy extractor has a complete description of the probability density function of $W$.
-We call this setting the \emph{known distribution} setting.
-(Previous works have consider
-
-Assuming full knowledge of a distribution is often unrealistic.
+We provide an answer in two settings.
+
+\paragraph{Sufficiency of $\Hfuzz(W)$ for a Precisely Known Distribution}
+Ideally, a fuzzy extractor has \emph{precise knowledge} of the probability distribution function of $W$.
+We call this  the \emph{precise knowledge} setting.
+In this setting, we show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
+Our construction crucially utilizes the probability distribution function of $W$ and, in particular, is not polynomial time.
+This result shows that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor of a distribution $W$.
+
+A number of previous works in the precise knowledge setting have provided efficient algorithms and
+tight bounds for specific distributions---generally the uniform distribution or
+i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
+Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
+
+\paragraph{The Challenge of Precisely Knowing a High Entropy Distribution}
+Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic.
 Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled.
@@
 Thus, the design is fixed with a partially known distribution, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.
-We call this setting \emph{family of distributions}.
+We call this setting \emph{distributional uncertainty}.
 We ask whether fuzzy min-entropy is sufficient in each of these settings.
 
-\paragraph{Sufficiency of $\Hfuzz(W)$ for a Known Distribution}
-We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
-We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.
-It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).
-
-A number of previous works in this known-distribution setting have provided efficient algorithms and
-tight bounds for specific distributions---generally the uniform distribution or
-i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
-Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
-
-\paragraph{Impossibility of a Fuzzy Extractor for a Family of Distributions}
-Our results are negative when the distribution $W$ is only known to come from a family $\mathcal{W}_Z$ (\thref{thm:imposs fuzz ext}).
-Specifically, we show a family of distributions $\mathcal{W}_Z$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.
+\paragraph{The Cost of Distributional Uncertainty}
+When the distribution is $W$ is uncertain, our results are negative.   In this setting, $W$ is only known to be in family of distributions $\mathcal{W}_Z$.
+We construct a family $\mathcal{W}_Z$ where not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.
 We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart.
@@
 This result shows that uncertainty in the distribution $W$ is devastating to building a fuzzy extractor.
-This result motivates the further research into physical sources.
-\bnote{come back to this sentence}
+In particular, our positive results (\corref{cor:extension to fuzz ext}) show it is possible to build a fuzzy extractor for each $W_z$, but no construction can simultaneously secure the whole family.
+Our result motivates further research into high fidelity descriptions of noisy physical sources.
 
@@
 \begin{tabular}{c  l l }
- & Known Distribution & Family of Distributions\\
+ & Precise Knowledge & Distributional Uncertainty\\
 \hline
@@
 
-\bnote{asked to discuss implications of our negative results}
-\bnote{can we reframe the paper as the cost of distributional uncertainty?}
 \bnote{compare to current constructions?}
@@
 
-\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).
+\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).
 We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).
@@
 We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.
-We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.
-
-\paragraph{Techniques for Negative Results for Distribution Families}
-We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$~(instead of proving impossibility for a worst-case $W_z$).
+We call this construction \emph{leveled hashing}~(\consref{cons:leveling}).
+
+\paragraph{Techniques for Negative Results for Distributional Uncertainty}
+We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$.
 We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
@@
 Extending this result to imperfect correctness seems challenging and is an interesting open problem.
-It also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.
+Our result also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.
 This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$.
@@
 The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.
-In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
+In this computational setting, a single fuzzy extractor (or secure sketch) can simultaneously secure all possible distributions by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
 The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.
-In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency.
-Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).
+This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.
+The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).
+Extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.}
 
@@
 We compare our positive results to these characterizations in \apref{sec:corr variables}.
-To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for a family of distributions.
+To the best of our knowledge, prior results on correlated random variables are in the precise knowledge setting, we are unaware of works that consider implications of distributional uncertainty.
 
@@
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:known distributions}, we construct a fuzzy extractor for each known distribution with fuzzy min-entropy.
-In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.
+In \secref{sec:known distributions}, we construct a fuzzy extractor in the precise knowledge setting.
+In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we construct families of distributions that no secure sketches and fuzzy extractors can secure, respectively~(the distributional uncertainty setting).
 
@@
 In this section, we define fuzzy extractors and secure sketches.
-Definitions and lemmas are drawn from the work of Dodis et.
-al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.
-First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.
-Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
+Definitions and lemmas are drawn from the work of Dodis et al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.
+First, we allow for error as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.
+Second, in the \emph{distributional uncertainty} setting we consider a general family $\mathcal{W}_Z$ of distributions instead of families containing all distributions of a given min-entropy.
 %\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
@@
 \label{def:fuzzy extractor}
-An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$.
+An $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$.
 \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
@@
 \item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
-\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
+\item \emph{Security:} for any distribution $W_z\in\mathcal{W}_Z$, if $(\Key,P)\leftarrow\gen (W_z)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
 \end{enumerate}
@@
 \label{def:secure sketch}
-An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.
+An $(\mathcal{M},\mathcal{W}_Z, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.
 \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
@@
 \item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
-\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
+\item \emph{Security}: for any distribution $W_z\in\mathcal{W}_Z$, $\Hav(W_z|\sketch(W_z))\geq \tilde{m}$.
 \end{enumerate}
@@
 
-\paragraph{The Case of Known Distribution}
-If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.
+\paragraph{The Case of a Precisely Known Distribution}
+If in the above definitions we take $\mathcal{W}_Z$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{precisely known distribution}.
 In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not affect security.}.
@@
 \label{lem:fuzzy ext construction}
-Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average case extractor.
-Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
+Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average case extractor.
+Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
 \begin{itemize}
@@
 Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.
-All proofs for statements in this section can be found in \apref{sec:proof fuzz necessary}.
+We defer proofs of statements in this section to \apref{sec:proof fuzz necessary}.
 \begin{proposition}
 \label{prop:fuzz necessary}
-Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, W, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
+Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \{W\}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
 \[
@@
 In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
-%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
-% with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
 \end{proposition}
@@
 The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.
-There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
-Our goal is to provide a superlogarithmic length key whenever a distribution has superlogarithmic fuzzy min-entropy. 
-Fuzzy min-entropy obeys some natural entropy properties:
+Fuzzy min-entropy represents an upper bound on the security from a noisy source.
+In the \secref{sec:related settings} computational setting there is evidence it may be possible to (nearly) achieve this upper bound.
+However, in the information-theoretic setting there are many distributions with fuzzy min-entropy with no known fuzzy extractor~(or corresponding impossibility result).
+We know show some properties of fuzzy min-entropy.
 \begin{lemma}
@@
 
-\section{Sufficiency of $\Hfuzz(W)$ When the Algorithms Know the Distribution}
+\section{Sufficiency of $\Hfuzz(W)$ in the Precise Knowledge Setting}
 \label{sec:known distributions}
-In this section, we show it is possible to build known-distribution secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
-We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.
-%\subsection{Well-Spread Distributions}
-%\bnote{can remove this section if we need space}
-%We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.
-Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.
-Error-correction is ``easy'' when all points of $W$ are far apart.
-Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.
-%Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).
-However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.
-%We begin by defining a well-spread distribution.
-%
-%\begin{definition}
-%A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
-%\end{definition}
-%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has superlogarithmic min-entropy).
-Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.
-However, our negative results for the family of distributions setting will be for families of well-spread distributions.
-This result illustrates how different the known distribution and family of distributions settings are.}
-%\begin{lemma}
-%\label{lem:nosketchwellspread}
-%Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.
-In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.
-\rec is efficient if there exists efficient decoding for the points in $W$.
-By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
-%\end{lemma}  
-%\begin{proof}
-%It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.
-Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.
-Then by the triangle inequality,
-%\[
-%t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
-%This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
-%\end{proof}
+In this section, we show it is possible to build secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) given precise knowledge of a distribution $W$ whenever $\Hfuzz(W)= \omega(\log n)$.
+We first consider flat distributions and then turn to arbitrary distributions.
 
@@
 
-Denote the largest number of points in a ball of radius $t$ in the support of $W$ as $\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.
-For flat distributions, the weight of the maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.
-More precisely,
+Denote the largest number of points in a ball of radius $t$ in the support of $W$ as \[\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|.\]   For flat distributions, this quantity defines the fuzzy min-entropy,
 \begin{align}
@@
 \noindent
-\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
-$
-\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} - \omega(\log n).
-$
+\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.
+The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$.
 For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).
@@
 \subsection{Arbitrary Distributions}
-The worst-case hashing approach does not work for arbitrary sources.
+The hashing approach used in the previous subsection does not work for arbitrary sources.
 The reason is that some balls may have  many points but low total weight.
@@
 It is unclear how to leverage the convex combination property in this setting.
-\bnote{I took out the appendix on convex combs, didn't think it was helping}%In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.
-The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.
 
@@
 To overcome this problem, we write the probability of $w\in W$ in the sketch output.
-To ensure this information does not completely reveal $w$ we write down $\lfloor \log \Pr[W=w] \rfloor$.
-We then use a universal hash whose output length is proportional to the number of close points of the same probability as $w$.
-This construction divides the distribution $W$ into probability levels.
-Each level is nearly flat.
+To ensure this information does not completely reveal $w$ we write down only the approximate probability of the outcome $w$.
+We then use a universal hash whose output length is proportional to the maximum number of points of the same approximate probability in any ball.
 
@@
 \noindent
-
-Before proving security of \consref{cons:leveling} we extend the notation to the maximum likelihood ball containing points of a given probability.
-Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.
-That is,
+To set parameters, we restrict our notation of the maximum likelihood ball to points of a given probability.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
 \[
@@
 \end{theorem}
+\noindent
 We provide a proof in \apref{sec:proof of layered hashing}.
@@
 \label{cor:extension to fuzz ext}
-Let $\mathcal{M}$ be a metric space where $n = \log |\M|$.
+Let $\mathcal{M}$ be a sequence of metric space parameterized by $n$ where $n = \log |\M|$.
 For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.
@@
 
-\noindent
-In our positive results we considered an arbitrary finite metric space.
-The relevant parameters were the size of balls and the size of the metric space.
-Our negative results are specific to the Hamming metric.
-
 \section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
@@
 
-In the previous section, we showed the sufficiency of $\Hfuzz(W)$ for known distribution algorithms.
-Unfortunately, it is unrealistic to assume that $W$ is completely known.
-Traditionally, algorithms deal with this uncertainty by providing security for a family of distributions $\mathcal{W}$.
-
-In this section, we show uncertainty of $W$ comes at a real cost.
-The security game of a fuzzy extractor can be thought of as a three stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary sees $(\sketch, \rec)$ and specifies $W\in \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W))< \tilde{m}$.
-We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W\leftarrow \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W)) < \tilde{m}$.
-
-Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.
-Let the random variable $Z$ indicate which $W$ was sampled.
-The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$.
-Our results rule out security for an average member of $\mathcal{W}$.
+In the previous section, we showed the sufficiency of $\Hfuzz(W)$ when the distribution was precisely known.
+It may be infeasible to completely characterize a high entropy distribution $W$.
+Traditionally, algorithms deal with this \emph{distributional uncertainty} by providing security for a family of distributions $\mathcal{W}_Z$.
+
+In this section, we show distributional uncertainty of $W$ comes at a real cost.
+The security game of a fuzzy extractor can be thought of as a three stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary sees $(\sketch, \rec)$ and specifies $W_z\in \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z))< \tilde{m}$.
+
+We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z)) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}$.
 It may be possible to improve parameters by ruling out only a worst case $W$.
-In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.
-
-We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.
+In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.}
+
+Let $V$ be the process of uniformly sampling $W_z\leftarrow \mathcal{W}_Z$ and then sampling $w\leftarrow W_z$.
+Let the random variable $Z$ the outcome of sampling $W_z\leftarrow \mathcal{W}_Z$.
+The view of the challenger is $V$, while the view of the adversary is $\sketch(V)$ and $Z$.
+We now show a family of distributions $\mathcal{W}_Z$ that does not admit a secure sketch.
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, and yet for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch $(\sketch, \rec)$ with error $\delta <1/4$ and distance $t\ge 4$, the remaining entropy $\tilde{m}<2$.
-
-Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$, and let $Z$ indicate which $W$ is sampled.  Then
+There exists a family of distributions $\mathcal{W}_Z$ such that for each element $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z)= \omega(\log n)$, and yet for any $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-secure sketch $(\sketch, \rec)$ with error $\delta <1/4$ and distance $t\ge 4$, $\tilde{m}<2$.
+
+Furthermore, this is true on average.  Let $V$ be process of sampling $W_z\leftarrow \mathcal{W}_Z$ and sampling $w\leftarrow W_z$.  Then
 \[
@@
 We prove the stronger average case statement.
-We first describe a family $\mathcal{W}$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
-Let $\mathcal{W}$ be the set of all distributions of the form 
-\[W =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} W_1 + \begin{pmatrix} 0  \\ 
+We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
+Let $\mathcal{W}_Z$ be the set of all distributions of the form 
+\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} w_1 + \begin{pmatrix} 0  \\ 
 b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
 \]
-where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i, b_i\in\mathbb{F}, a_i\neq 0$.  
-This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
-Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.
-The adversary sees $\sketch(V)$ and $Z$.
-$Z$ is the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
-The algorithms $\sketch, \rec$ never see $Z$.
+The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) and the distribution is sampled by sampling $w_1$.
+Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$.
+The algorithm $\sketch, \rec$ never see $Z$ only the outcome of $v\leftarrow V$.
 Fix some $4\le t < \gamma$.
@@
 \begin{itemize}
-\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:each element good}: for all $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z) = \omega (\log n)$. 
 \item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
 \item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
-Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
-\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
+Here we show the minimum distance between points of $V|\sketch(V)$ is at least $t$.
+\item \lemref{lem:side info determines sketch}:  $\tilde{H}_0(V | \sketch(V), Z) < 2$.
 \end{itemize}
@@
 Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{W}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
+There exists a family of distributions $\mathcal{W}_Z$ over $\mathcal{M}$ such that for each element $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
 If
@@
 
+\noindent
 Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.
@@
 \label{sec:imposs fuzz ext}
-In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.
+In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide an analogous result for fuzzy extractors.
 
@@
 Let $n$ be a security parameter.
-There exists a family of distributions $\mathcal{W}$ over $\zo^n$ satisfying the following conditions.
-For each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$.
+There exists a family of distributions $\mathcal{W}_Z$ over $\zo^n$ satisfying the following conditions.
+For each element $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z)= \omega(\log n)$.
 Let $\kappa \ge 2$ and $t = \omega(n^{1/2}\log n)$.
-Any $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.
-
-Furthermore, this is true on average.
-Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ indicate which $W$ is sampled.
-Let $(\Key, P)\leftarrow \gen(V)$.
-Then,
+Any $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.
+
+Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W_z\leftarrow \mathcal{W}_Z$ and sampling $w\leftarrow W_z$.  Let $(\Key, P)\leftarrow \gen(V)$.  Then, 
 \[
@@
 
-Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
+Our counterexample uses a slightly different family of distributions $\mathcal{W}_Z$ than the counterexample for secure sketches.  
 We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).
@@
 This will be crucial in our proof.
-We will embed the larger alphabet we used into the binary Hamming metric.
+We will embed the larger alphabet in the secure sketch counterexample into the binary Hamming metric.
 Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
@@
 \]
-The multiplication is in $\mathbb{F}$.
-Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
-Let $\mathcal{W}$ be the set of all such $W$.
-
- Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.
-The adversary sees $\sketch(V)$  and $Z$, where $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
-
-We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
+The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.  
+A particular distribution $W_z$ is then the uniform distribution over choices of $x$.
+ Define $V$ as the process of uniformly choosing $W_z\leftarrow \mathcal{W}_Z$ and then sampling from $w\leftarrow W_z$.
+The adversary sees $\sketch(V)$  and $Z$.
+We then show the following~(proofs in \apref{sec:fuzz ext proof}):
 \begin{itemize}
-\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:dist fuzzy ent fuzz}: for all $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z) = \omega (\log n)$. 
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
@@
 Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.
-Together these two results imply that $V_\key$ is small.
-\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
-Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_2$ have disjoint support outside of $v$.
+The number of $w$ that could produce $\key$ is small.
+\item There are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).
+Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_2$ have disjoint support outside of a single point $w$.
 \item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).
 Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
-%The previous two propositions were similar to the secure sketch counterexample.
-However, the structure on the metric space imposed byThe remainder of the proof is significantly different.
-We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.
-Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
 \end{itemize}
@@
 \textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.
-We note that the specific family $\mathcal{W}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors  for this family of distributions when $\mathbb{F}$ is large enough under weaker assumptions.
+We note that the specific family $\mathcal{W}_Z$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors  for this family of distributions when $\mathbb{F}$ is large enough under weaker assumptions.
 (Their construction is stated with imperfect correctness.
@@
 By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.
-Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
+Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|\sketch(V)) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
 \end{proof}

### 2015-02-10 trunk/info-bounds/FuzzyExtPossibility.tex
revising proofs with new notation

@@
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = \beta_{t,i} /\delta$.
 When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 4$.
@@
 \]
-The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) and the distribution is sampled by sampling $w_1$.
+The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) for arbitrary $b_i$ and $a_i\neq 0$.
+The outcome $w\leftarrow W_z$ is sampled by sampling $w_1$ and computing $w$.
 Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$.
@@
 \]
-The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.  
-A particular distribution $W_z$ is then the uniform distribution over choices of $x$.
+The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$ for arbitrary $b_i$ and $a_i\neq 0$.  
+A particular distribution $W_z$ is the uniform distribution over choices of $x$.
  Define $V$ as the process of uniformly choosing $W_z\leftarrow \mathcal{W}_Z$ and then sampling from $w\leftarrow W_z$.
@@
 
-%\section{Leveraging convex combinations?}
-%\label{sec:convex comb}
-%\bnote{be careful uncommenting this, some notation may be out of date}
-%In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.
-For example, consider the following hypothetical extension to \consref{cons:universal hash}.
-Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_\alpha$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.
-However, the problem arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
-%
-%We now describe a possible modification to the hashing construction.
-Upon receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, write $i$ and perform the sketch as before for distribution $W_i$.
-Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.
-Unfortunately, this proposal may remove all entropy.
-%Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.
-However, this is not the case.
-%
-%%In the flat case, we used a hash whose length was proportional to the number of points in the largest ball.
-The residual entropy in this case was within a superlogarithmic factor of $\Hfuzz(W)$.
-However, in the setting where $W$ is a convex combination of flat sources this does not hold.
-%
-%Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors and $W_i$ contains a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.
-This distribution is illustrated in \figref{fig:convex comb}.
-%
-%\begin{figure}
-%
-%\centering
-%    \includegraphics[width=.9\textwidth]{convexCombExample.png}
-%    \caption{A convex combination of $W_1,..., W_\alpha$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
-%\label{fig:convex comb}    
-%\end{figure}
-%
-%
-%The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.
-Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).
-Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\alpha, k\}$ where $\alpha$ is the number of distributions $W_1,..., W_\gamma$.
-The value $\alpha$ may be quite large and $k$ may be the dominant factor.
-%
-%Consider an input point $w\in W$.
-One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.
-It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \alpha\}$.
-For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.
-This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.
-This is despite the fact $\Hfuzz(W) \approx \min\{\gamma, k\}$.
-Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.
-\bnote{I removed the discussion of convex combs for the submitted version}
-
 \section{A Definitional Equivalence}
 \label{sec:def equiv}
-%We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.
-
-As described in \secref{sec:family of dist}, our negative results rule out security for an average member of $\mathcal{W}$.
-It may be possible to significantly improve parameters by only ruling out security for a single member $W$.
-
-Recall the security game of a fuzzy extractor: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$ 3) The challenger wins if $\Hav(W|\sketch(W))\ge \tilde{m}$.
-Instead of just thinking of the uniform distribution over $\mathcal{W}$, consider an arbitrary distribution $V$ over elements of $\mathcal{W}$.
-The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces $V$ instead of a single element $W$.
+
+As described in \secref{sec:family of dist}, our negative results rule out security for an average member of $\mathcal{W}_Z$.
+It may be possible to significantly improve parameters by only ruling out security for a single member $W_z$.
+
+Recall the security game of a fuzzy extractor: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W_z\in \mathcal{W}_Z$ 3) The challenger wins if $\Hav(W_z|\sketch(W_z))\ge \tilde{m}$.
+Instead of just thinking of the uniform distribution over $\mathcal{W}_Z$, consider an arbitrary distribution $V$ over elements of $\mathcal{W}_Z$.
+The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces $V$ instead of a single element $W_z$.
 That is, the following two player games have the same equilibrium:
@@
 123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
-$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
-$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
-If $W\not\in \mathcal{W}$, $\mathcal{C}$ wins.\\
-If $\Hav(W | \sketch(W))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
+\textbf{Experiment} $\Exp^{\mathcal{W}_Z}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
+$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W}_Z)$\\
+$W_z \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
+If $W_z\not\in \mathcal{W}_Z$, $\mathcal{C}$ wins.\\
+If $\Hav(W_z | \sketch(W_z))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
 Else $\mathcal{A}$ wins.
@@
 123\=123\=123\=123\=123\=\kill
-\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
-$V \leftarrow \mathcal{A}(\mathcal{W})$\\
-$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
-$W \leftarrow V$\\
-If $W\not\in \mathcal{W}$, $\mathcal{C}$ wins.\\
-If $\Hav(W | \sketch(W))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
+\textbf{Experiment} $\Exp^{\mathcal{W}_Z}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
+$V \leftarrow \mathcal{A}(\mathcal{W}_Z)$\\
+$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W}_Z)$\\
+$W_z \leftarrow V$\\
+If $\Hav(W_z | \sketch(W_z))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
 Else $\mathcal{A}$ wins.
@@
 
-%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
-In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.
-This means that showing security for a family of distributions $\mathcal{W}$ is equivalent to showing security for all  distributions $V$ when the distribution is known to the algorithms $V$.
-In our negative results, the adversary  uses the uniform distribution $V$ over $\mathcal{W}$.
+\noindent
+This means that showing security for a family of distributions $\mathcal{W}_Z$ is equivalent to showing security for all distributions $V$ when the distribution is known to the algorithms $(\sketch, \rec)$.
+In our negative results, the adversary uses the uniform distribution over $\mathcal{W}_Z$.
 However, it may be possible to improve parameters by using a different $V$.
-This would just rule out some member of $\mathcal{W}$ not an average member.
-This is true for fuzzy extractors as well and is resilient to changes in parameters including imperfect correctness.
-
-%Since the distribution used in our negative results was uniform it is stronger, ruling out security for an average $\mathcal{W}$.  However, constructing a nonuniform $V$ may improve these results.
-%\begin{lemma}
-%\label{lem:quant switch fuzz}
-%Let $\mathcal{W}$ be a family of distributions.
-If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-Let $V$ be a distribution over $\mathcal{W}$.
-Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
-If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
-%\end{lemma}
-
-%\begin{corollary}
-%\label{cor:no fuzz for dist}
-%Let $\mathcal{W}$ be a family of distributions.
-Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.
-If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-%\end{corollary}
-%
-%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
+
 \section{Fuzzy min-entropy}
 \label{sec:proof fuzz necessary}
-In this section, we provide proofs of the items in \secref{sec:minimal conditions}.  
+In this section, we provide proofs of statements in \secref{sec:minimal conditions}.  
 \begin{proof}[Proof of \propref{prop:fuzz necessary}]
@@
 \Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|} = \delta
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|}\le \frac{\beta_{t, i}}{|R_i|} = \delta
 \end{align*}
@@
 \begin{proposition} 
-\label{prop:each element good} For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
+\label{prop:each element good} For each $W_z\in\mathcal{W}_Z$, $\Hfuzz(W_z) = \omega(\log n)$.
 \end{proposition}
 \begin{proof}
-Consider some $W\in\mathcal{W}$.
-The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.
-We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma>t$.
-This shows that $\Hfuzz(W) = \Hoo(W)$.
-Fix some $w, w'\in W$.
+Consider some $W_z\in\mathcal{W}_Z$.
+The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W_z) \ge \omega(\log n)$.
+We now show that for any $w, w'\in W_z$, $\dis(w, w') = \gamma>t$.
+This shows that $\Hfuzz(W_z) = \Hoo(W_z)$.
+Fix some $w, w'\in W_z$.
 Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.
@@
 Consider some $w\in V$.
-Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
-The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
+Then $w$ was drawn from an intermediate distribution $W_z$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly distributed.
 \end{proof}
@@
  As described above, the view of $\sketch, \rec$ is a uniform distribution $V$. 
-%Having seen $V$ there are many possible values for $Z$.
-Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.
- The only information seen by $\sketch$ algorithm is in the point $V=v$.
-The length of this point is $|\mathbb{F}|^\gamma$.
-Conditioned on this information there are still many possible values for $Z$.
-That is,
+The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
  \[
@@
 \end{align*}
-Then averaging over the possible values of $s$, we have the following as long as $t\ge 4$~(using  \lemref{lem:log-minus-one}, which appears below):
+Then averaging over the possible values of $s$, we have the following as long as $t\ge 4$:
 \begin{align*}
@@
 \end{align*}
-Where the inequality follows because $\log x+1 \le \max\{ 1+ \log x,1\}$ for $x\ge 0$.
-The left operand to $\max$ is bounded by $2$~(bounding the $\max$ by $2$):
+Where the inequality follows because $\log (x+1) \le \max\{ \log x+ 1,1\}$ for $x\ge 0$.
+The left operand to $\max$ is bounded by $2$~(bounding the $\max$ by $2$).  This argument uses a technical lemma that appears directly after (\lemref{lem:log-minus-one}).
 \begin{align*}
@@
 
-\lnote{this lemma should probably live elsewhere since it is also needed for the FE case}
-\bnote{fine with it being here as the FE case lives in the appendix too}
 \begin{lemma}
@@
 \label{prop:dist fuzzy ent fuzz}
-For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
+For each $W_z\in\mathcal{W}_Z$, $\Hfuzz(W_z) = \omega(\log n)$.
 \end{proposition}
 \begin{proof}
-Consider some fixed $W\in\mathcal{W}$.  The bits $w_{1,..., \nu}$ are uniform, so $\Hoo(W) =\omega(\log n)$.  Recall that $t=o (n/\nu)$. 
+Consider some fixed $W_z\in\mathcal{W}_Z$.  The bits $w_{1,..., \nu} =x$ are uniform, so $\Hoo(W_z) =\omega(\log n)$.  Recall that $t=o (n/\nu)$. 
  %We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.  
-Fix some $w, w'\in W$.
+Fix some $w, w'\in W_z$.
 Denote by $x, x'$ the values that produce $w, w'$ respectively.
@@
 That is, at least one of the bits in each block differs between $w$ and $w'$, and so $\dis(w, w') \ge n/\nu$.
-Since no two values in the support of $W$ lie in the same ball of radius $t$, we have $\Hfuzz(W) = \Hoo(W)= \omega(\log n)$.
+Since no two values in the support of $W_z$ lie in the same ball of radius $t$, we have $\Hfuzz(W_z) = \Hoo(W_z)= \omega(\log n)$.
 \end{proof}
@@
 Consider some $w\in V$ over $\zo^n$.
-Then $w\leftarrow W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.
+Then $w\leftarrow W_z$ for coefficients $z=a_2, b_2, ..., a_\gamma , b_\gamma$.
 The value $w_{1,...,\nu} =x $ is uniformly random and $w_{i\nu+1,...,(i+1)\nu}$ are uniformly random since $b_2,..., b_\gamma$ are random.
@@
 
-Consider some $p^*\in A_{p}$.  
+Consider some $p^*\in A_{\epsilon}$.  
 The distribution $\Key|P=p^*$ is the set of possible keys.
@@
 
-The distinguisher $D(\key, p, z)$ is formed by calling $D_p(\key, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
+The distinguisher $D(\key, p, z)$ is formed by calling $D_p(\key, z)$ when $p\in A_{\epsilon}$ and outputting a random bit otherwise.  The advantage of $D$ is 
 \begin{align*}
 \Pr[D(\Key, P, Z) = 1] &- \Pr[D(U, P, Z) =1]\\
-&=(\Pr[D(\Key, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in \Key_{small}]\Pr[U\in \Key_{small}] - \Pr[U\not\in \Key_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|\Key_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in \Key_{small}]\right) - \Pr[U\not\in \Key_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in \Key_{small}] \right)\\
-&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/4-\ngl(n)\right) \ge \frac{1}{8}-\ngl(n).
-\end{align*}
-The sixth line follows since $\Key_{small} \ge 2^{\kappa-1}\ge 2$.  The eighth line follows because $\Pr[U\in \Key_{small}]\ge 1/2$.  The last inequality proceeds because $\Pr[P\in A_p]\ge 1/2$.
+&=(\Pr[D(\Key, P, Z) = 1| P\in A_{\epsilon}] - \Pr[D(U, P, Z) =1 | P\in A_{\epsilon}])\Pr[P\in A_{\epsilon}]\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in \Key_{small}]\Pr[U\in \Key_{small}] - \Pr[U\not\in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|\Key_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in \Key_{small}]\right) - \Pr[U\not\in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in \Key_{small}] \right)\\
+&\ge \sum_{p^* \in A_{\epsilon}} \Pr[P=p^*]\left(1/4-\ngl(n)\right) \ge \frac{1}{8}-\ngl(n).
+\end{align*}
+The sixth line follows since $\Key_{small} \ge 2^{\kappa-1}\ge 2$.
+The eighth line follows because $\Pr[U\in \Key_{small}]\ge 1/2$.
+The last inequality proceeds because $\Pr[P\in A_{\epsilon}]\ge 1/2$.
 This completes the proof of \lemref{lem:fuzz can't get key}.

### 2015-02-10 trunk/constantRate/ConstCompFuzzExt-crypto.tex
things are in the right order. Fixed up the proof and theorem statement of construction for high-entropy samples

@@
 \newcommand{\Vol}{\mathsf{Vol}}
+\newcommand{\subsetEntropy}{\alpha}
 
@@
 
-We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed.
+We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with sparse high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed.
 In this construction, we use single symbols of $w$ for locking up bits of a secret that we then transform into $r$.
@@
 \hline
-Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-and-obfuscate \\
-Cons. \ref{cons:first construction}  & high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
-Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-and-fuzzy-extract\\
+Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
+Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
+Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
 \hline\end{tabular}
@@
 
-\section{Supporting more errors than entropy}
+\section{Reusable Construction for Sources with High-Entropy Samples}
+\label{sec:sampling}
+
+\paragraph{Sources with High-Entropy Samples}
+Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$.
+For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(w_{j_1}, \dots, w_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
+This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
+However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.
+
+A distribution obtained by applying short-output condensers multiple times to a single sample from a high-entropy source (e.g., via random projections) will have this property, because the outputs of the condensers will be contain fresh entropy as long as the total amount of entropy in the source is not exceeded
+(by a simple conditional entropy argument---each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as fresh entropy remains conditioned on the previous elements).
+
+\paragraph{The Construction}
+The construction first chooses a random $r$ to be used as the output of the fuzzy extractor.
+It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers.
+See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
+The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.
+Composability also allows reusability.
+
+\begin{construction}[Sample-then-Obfuscate]
+\label{cons:sampling}
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples, where each $W_j$ is over $\mathcal{Z}$.
+Let $\ell$ be a parameter, to be determined later.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for the family of digital lockers with $\kappa$-bit outputs. Define $\gen, \rep$ as:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\gamma$
+\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
+\item For $i=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item Choose uniformly random distinct $1\le j_{i, 1},..., j_{i, \eta}\le \gamma$
+\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
+\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
+\item Set $p_i = \rho_i, (j_{i, 1},..., j_{i, \eta})$.
+\end{enumerate}
+\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w'=w_1',..., w_\gamma', p = p_1\dots p_\ell)$
+\item For $i=1,..., \ell$:
+\begin{enumerate}[(i)]
+\item Parse $p_i$ as $\rho_i, (j_{i, 1},..., j_{i, \eta})$.
+\item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
+\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
+\end{enumerate}
+\item Output $\perp$.
+\end{enumerate}
+\vspace{0.37in}
+\end{minipage}
+\end{tabular}
+\end{center}
+\end{construction}
+
+\noindent
+%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
+%\begin{itemize}
+%\item Multiple blocks are concatenated together.
+This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.
+This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
+For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
+%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.
+This requires the use of digital lockers in place of point obfuscations.
+Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.
+\consref{cons:first construction} only hid part of the key in each obfuscation.
+This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
+%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.
+This construction works for an arbitrary size alphabet.
+We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
+%\end{itemize}
+
+\begin{theorem}
+\label{thm:sampling}
+Let $n$ be a security parameter, $\mathcal{Z}$ be an alphabet, and $\gamma, \subsetEntropy$, and $t$ be functions of $n$, as follows.
+Let $\mathcal{W}$ be a family of sources over $\mathcal{Z}^\gamma$ with $(\eta, \subsetEntropy)$ high-entropy samples for $\subsetEntropy = \omega(\log n)$.
+Let $t$ be such that $\left(1-\frac{t}{\gamma-\eta}\right)^\eta>1/p(n)$ for some positive polynomial $p$.
+Then it there exists $\ell = \poly(n)$ such that for any
+$s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $\left (\epsilon_{sec}, s_{sec}\right)$-hard with negligible error.
+\end{theorem}
+
+ Correctness follows immediately: for any given $i$, the probability that $v'_i=v_i$ is at least $1/p(n)$.
+By choosing $\ell$ sufficiently bigger than $1/p(n)$, we guarantee that for at least one $i$,  $v'_i=v_i$ with all but negligible probability
+(indeed, because the $\ell$ samples are independent, the probability this does not happen is at most $(1-1/p(n))^\ell \le e^{-\ell/p(n)}$, using $1+x \le e^x$).
+
+Security follows from obfuscation and is analyzed in \apref{sec:analysis sampling}.
+
+\paragraph{Any sublinear error-rate can be supported if most symbols in a sample contribute entropy.}
+The requirement on $t$ can be expressed as $\eta \log  \left(1-\frac{t }{\gamma-\eta}\right) = O (\log n)$. Using $\ln (1+x)\approx x$ and relying on $O$ to absorb any 
+constant factor involved in this approximation and the switch from $\ln$ to $\log$, we get $\eta \frac{t }{\gamma-\eta} = O(\log n)$. If $t$ is sublinear in $\gamma$
+ (and $\eta$ is no more than a constant fraction of $\gamma$), then $t/(\gamma-\eta)$ is subconstant, and therefore it is possible to satisfy this requirement on $t$ while simultaneously maintaining $\eta = \omega (\log n)$, which implies $\subsetEntropy = \omega(\log n)$ as long as most symbols in a sample of size $\eta$ contribute a constant amount of entropy each.
+
+\paragraph{More Errors than Entropy?}
+The amount of entropy in $W$ need not exceed $\subsetEntropy$---thus, it can be as low as $\omega(\log n)$.
+Assuming $\gamma = n$, the number $t$ of errors may be any function in $o(n)$, and thus $\log |B_t| \ge t \log |Z|$ may far exceed $\Hoo(W)$.
+
+\iffalse 
+\subsection{Security of \consref{cons:sampling}}
+\label{ssec:sec cons sampling}
+In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
+With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
+Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
+% forms a block-unguessable distribution.
+Then security essentially follows from the security of \consref{cons:first construction}.
+%follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
+%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
+%By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
+We begin by showing that each $V_i$ is statistically close to a high entropy distribution.
+Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
+be some particular outcome.
+
+\begin{lemma}
+\label{lem:sampling works}
+Let all variables be as in \thref{thm:sampling}.
+There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
+\[
+\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
+\]
+\end{lemma}
+
+\noindent
+We can then argue that all $V_i$ simultaneously have individual entropy with good probability~(by union bound):
+\begin{corollary}
+\label{cor:samp sec}
+ Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.
+Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \geq 1-\ell\epsilon_{sam}$.
+%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
+\end{corollary}
+%\begin{proof}
+%Union bound over the probability in \lemref{lem:sampling works}.
+%%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
+%\end{proof}
+
+Once all $V_i$ all simultaneously have good entropy, the adversary only sees $\perp$ as an output from the obfuscations~(with overwhelming probability).
+If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.
+
+\begin{lemma}[Proof in \apref{sec:analysis sampling}]
+\label{lem:samp unguess}
+Let all the variables be as in \thref{thm:sampling}.
+For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.
+\end{lemma}
+
+\subsection{Correctness of \consref{cons:sampling}}
+\label{sec:correct sampling}
+We encode the entire key in each obfuscation.
+For correctness, at least one of the repeated readings must be correct with overwhelming probability.
+Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.
+For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.
+
+\begin{lemma}[Proof in \apref{sec:analysis sampling}]
+\label{lem:sampling errors}
+Let all the variables be as in \thref{thm:sampling}.
+ Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.
+\end{lemma}
+\fi
+
+\subsection{Reusability of \consref{cons:sampling}}
+\lnote{haven't looked at this---may need work}
+The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.
+We consider a bounded $q = \poly(n)$ number of reuses.
+For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.
+Thus, given sufficiently strong reusability we achieve the following result:
+
+\begin{theorem}
+\label{thm:reusability}
+Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
+For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
+\end{theorem}
+\begin{proof}
+The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
+The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
+Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
+\bnote{say more here?}
+\end{proof}
+
+\iffalse
+\subsection{More errors than entropy?}
+In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.
+The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
+We assume that $\Hoo(W) = \Theta(\gamma)$.
+We are able to correct $o(\gamma)$ errors.
+This yields:
+\[
+\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
+\]
+That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.
+
+\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
+However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.
+
+In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.
+However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability.
+For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.
+
+\fi
+
+\section{Construction for Sources with Sparse High-Entropy Marginals}
+\label{sec:cor construction}
+\lnote{stopped here; also need to reorder appendices}
+In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.
+Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.
+In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
+This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
+Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.
+
+Before presenting the construction we provide some definitions from error correcting codes.
+We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
+Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
+These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
+The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
+}
+\begin{definition}
+\label{def:hamming z channel}
+For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
+\end{definition}
+
+\begin{definition}
+Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
+Then a set $C$~(over $\zo^\gamma$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
+} \decode(c') \neq c] \leq \delta_{code}$.
+\end{definition}
+\bnote{these are quite strange.  changing them for dissertation.  update if accepted.}
+
+\begin{construction}
+\label{cons:first construction}
+Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.
+Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
+Let  $C\subset \zo^\gamma$ be an error-correcting code.
+We describe $\gen, \rep$ as follows:
+
+\begin{center}
+\begin{tabular}{c|c}
+\begin{minipage}{3in}
+\textbf{\gen}
+\begin{enumerate}
+\item \underline{Input}: $w = w_1,..., w_\gamma$
+\item Sample $c\leftarrow C$.
+\item For $j=1,..., \gamma$:
+\begin{enumerate}[(i)]
+\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
+\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
+\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
+\end{enumerate}
+\item Output $(c, p)$, where $p=p_1\dots p_\gamma$.
+\end{enumerate}
+ \end{minipage} &
+\begin{minipage}{3in}
+\textbf{\rep}
+\begin{enumerate}
+\item \underline{Input}: $(w', p)$
+\item For $j=1,..., \gamma$:
+\begin{enumerate}[(i)]
+\item If $p_j(w_j') = 1$: set $c_j' = 0$.
+\item Else: set $c_j' = 1$.
+\end{enumerate}
+\item Set $c = \decode(c')$.
+\item Output $c$.
+\end{enumerate}
+\vspace{0.15in}
+\end{minipage}
+\end{tabular}
+\end{center}
+\end{construction}
+
+%\bnote{shorten this discussion?}
+%The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
+%In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
+%There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
+However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
+This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
+
+\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
+By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
+Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
+This restriction on the distribution is captured in the following definition.
+
+\begin{definition}
+\label{def:block guessable}
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
+\begin{cases}
+1 & w_j = w_j'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $W = W_1| ...
+|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block source} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+\[
+\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+
+We show some examples of unguessable block sources in \apref{sec:characterize}.
+In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block source~(\clref{cl:all blocks entropy}).
+
+Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.
+The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).
+However, we can show that $c$ looks like it has entropy.
+We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
+\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
+\label{def:hill ent}
+Let $(W, S)$ be a pair of random variables.  $W$ has
+\emph{HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
+\end{definition}
+We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).
+We call this object a computational fuzzy conductor.
+It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+\begin{definition}
+\label{def:comp fuzzy cond}
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
+\begin{itemize}
+\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
+\end{itemize}
+\end{definition}
+Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
+The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
+\begin{theorem}
+\label{thm:main thm first cons}
+Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
+Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.
+Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
+\end{theorem}
+
+\subsection{More errors than entropy?}
+\label{sec:discussion}
+In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
+We first calculate the size of the Hamming ball.
+\[
+\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
+\]
+The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.
+This yields:
+\[
+\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  >\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
+\]
+When $t =\Theta(\gamma)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy.
+Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\gamma)$).
+
+\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
+
+If $\gamma$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
+
+\section{Information-Theoretic Construction for Sparse Block Sources}
 \label{sec:info theory cons}
-In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy.
+In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy for sparse block sources.
 %Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
@@
 
-\section{Adding reusability}
-\label{sec:sampling}
-In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with more errors than entropy.
-Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.
-
-The construction samples a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscates the concatenation of these blocks.
-Denote this concatenated value by $V_1$.
-This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.
-Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.
-
-\begin{construction}[Sample-then-Obfuscate]
-\label{cons:sampling}
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$.
-Let $\eta$ be a parameter, and $\mathcal{O}$ be an obfuscator for the family of digital lockers with $\kappa$-bit outputs.  Define $\gen, \rep$ as:
-
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_\gamma$
-\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
-\item For $i=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item Select $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
-\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma,\eta}( \lambda_i)$
-\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
-\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
-\item Set $p_i = \rho_i, \lambda_i$.
-\end{enumerate}
-\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(w'=w_1',..., w_\gamma', p)$
-\item For $i=1,..., \ell$:
-\begin{enumerate}[(i)]
-\item Parse $p_i$ as $\rho_i, \lambda_i$.
-\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
-\item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
-\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
-\end{enumerate}
-\item Output $\perp$.
-\end{enumerate}
-\vspace{0.37in}
-\end{minipage}
-\end{tabular}
-\end{center}
-\end{construction}
-
-\noindent
-%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
-%\begin{itemize}
-%\item Multiple blocks are concatenated together.
-This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.
-This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.
-For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
-%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.
-This requires the use of digital lockers in place of point obfuscations.
-Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.
-\consref{cons:first construction} only hid part of the key in each obfuscation.
-This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
-%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.
-This construction works for an arbitrary size alphabet.
-We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
-%\end{itemize}
-The use of a computational primitive~(obfuscation of digital lockers) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.
-This is the property that allows reusability.
-
-This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.
-(See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)
-
-\begin{theorem}
-\label{thm:sampling}
-Let $\mathcal{Z}$ be an alphabet.
-Let $n$ be a security parameter.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma =\Omega(n)$.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$, and let $c> 1$ be a constant and $\ell$ be such that $\ell = n^c$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
-Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
-\begin{align*}
-t&\leq -\frac{(c-1)}{2} \frac{(\gamma-\eta)\log n}{\eta} = o(\gamma)\\
-\delta &= e^{-n}
-\end{align*}
-\end{theorem}
-
-\subsection{Security of \consref{cons:sampling}}
-\label{ssec:sec cons sampling}
-In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
-With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
-Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
-% forms a block-unguessable distribution.
-Then security essentially follows from the security of \consref{cons:first construction}.
-%follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
-%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
-%By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
-We begin by showing that each $V_i$ is statistically close to a high entropy distribution.
-Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
-be some particular outcome.
-
-\begin{lemma}
-\label{lem:sampling works}
-Let all variables be as in \thref{thm:sampling}.
-There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
-\[
-\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
-\]
-\end{lemma}
-
-\noindent
-We can then argue that all $V_i$ simultaneously have individual entropy with good probability~(by union bound):
-\begin{corollary}
-\label{cor:samp sec}
- Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.
-Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \geq 1-\ell\epsilon_{sam}$.
-%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
-\end{corollary}
-%\begin{proof}
-%Union bound over the probability in \lemref{lem:sampling works}.
-%%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
-%\end{proof}
-
-Once all $V_i$ all simultaneously have good entropy, the adversary only sees $\perp$ as an output from the obfuscations~(with overwhelming probability).
-If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.
-
-\begin{lemma}[Proof in \apref{sec:analysis sampling}]
-\label{lem:samp unguess}
-Let all the variables be as in \thref{thm:sampling}.
-For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.
-\end{lemma}
-
-\subsection{Correctness of \consref{cons:sampling}}
-\label{sec:correct sampling}
-We encode the entire key in each obfuscation.
-For correctness, at least one of the repeated readings must be correct with overwhelming probability.
-Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.
-For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.
-
-\begin{lemma}[Proof in \apref{sec:analysis sampling}]
-\label{lem:sampling errors}
-Let all the variables be as in \thref{thm:sampling}.
- Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.
-\end{lemma}
-
-\subsection{Reusability of \consref{cons:sampling}}
-The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.
-We consider a bounded $q = \poly(n)$ number of reuses.
-For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.
-Thus, given sufficiently strong reusability we achieve the following result:
-
-\begin{theorem}
-\label{thm:reusability}
-Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
-For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
-\end{theorem}
-\begin{proof}
-The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
-The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
-Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
-\bnote{say more here?}
-\end{proof}
-
-\subsection{More errors than entropy?}
-In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.
-The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
-We assume that $\Hoo(W) = \Theta(\gamma)$.
-We are able to correct $o(\gamma)$ errors.
-This yields:
-\[
-\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
-\]
-That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.
-
-\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
-However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.
-
-In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.
-However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability.
-For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.
-
-\section{Allowing Correlated Symbols}
-\label{sec:cor construction}
-In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.
-Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.
-In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
-This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
-Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.
-
-Before presenting the construction we provide some definitions from error correcting codes.
-We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
-Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).
-These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
-The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
-}
-\begin{definition}
-\label{def:hamming z channel}
-For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
-\end{definition}
-
-\begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\gamma$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
-} \decode(c') \neq c] \leq \delta_{code}$.
-\end{definition}
-\bnote{these are quite strange.  changing them for dissertation.  update if accepted.}
-
-\begin{construction}
-\label{cons:first construction}
-Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.
-Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
-Let  $C\subset \zo^\gamma$ be an error-correcting code.
-We describe $\gen, \rep$ as follows:
-
-\begin{center}
-\begin{tabular}{c|c}
-\begin{minipage}{3in}
-\textbf{\gen}
-\begin{enumerate}
-\item \underline{Input}: $w = w_1,..., w_\gamma$
-\item Sample $c\leftarrow C$.
-\item For $j=1,..., \gamma$:
-\begin{enumerate}[(i)]
-\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
-\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
-\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
-\end{enumerate}
-\item Output $(c, p)$, where $p=p_1\dots p_\gamma$.
-\end{enumerate}
- \end{minipage} &
-\begin{minipage}{3in}
-\textbf{\rep}
-\begin{enumerate}
-\item \underline{Input}: $(w', p)$
-\item For $j=1,..., \gamma$:
-\begin{enumerate}[(i)]
-\item If $p_j(w_j') = 1$: set $c_j' = 0$.
-\item Else: set $c_j' = 1$.
-\end{enumerate}
-\item Set $c = \decode(c')$.
-\item Output $c$.
-\end{enumerate}
-\vspace{0.15in}
-\end{minipage}
-\end{tabular}
-\end{center}
-\end{construction}
-
-%\bnote{shorten this discussion?}
-%The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
-%In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
-%There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.
-However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).
-This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.
-
-\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
-By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
-This restriction on the distribution is captured in the following definition.
-
-\begin{definition}
-\label{def:block guessable}
-Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
-\begin{cases}
-1 & w_j = w_j'\\
-0 & \text{otherwise}.
-\end{cases}
-\]
-A source $W = W_1| ...
-|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block source} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
-\[
-\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-
-We show some examples of unguessable block sources in \apref{sec:characterize}.
-In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block source~(\clref{cl:all blocks entropy}).
-
-Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.
-The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).
-However, we can show that $c$ looks like it has entropy.
-We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
-\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
-\label{def:hill ent}
-Let $(W, S)$ be a pair of random variables.  $W$ has
-\emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
-\end{definition}
-We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).
-We call this object a computational fuzzy conductor.
-It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-\begin{definition}
-\label{def:comp fuzzy cond}
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
-\begin{itemize}
-\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
-\end{itemize}
-\end{definition}
-Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
-The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
-\begin{theorem}
-\label{thm:main thm first cons}
-Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.
-Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
-\end{theorem}
-
-\subsection{More errors than entropy?}
-\label{sec:discussion}
-In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
-We first calculate the size of the Hamming ball.
-\[
-\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
-\]
-The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
-For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.
-This yields:
-\[
-\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  >\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
-\]
-When $t =\Theta(\gamma)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy.
-Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\gamma)$).
-
-\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.
-
-If $\gamma$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.
-
 \blind{
@@
 \begin{enumerate}
-\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
+\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.\lnote{imperfect correctness allowed?
+It's need for the RO construction.}
 \item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
@@
 When we use digital lockers we denote the oracle provided to the simulator as $I_{v, r}(\cdot, \cdot)$ where $v = v_1,..., v_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
+\lnote{I am confused here -- need to understand this notation and check if we use it.}
 
@@
 See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
-\section{Characterizing unguessable block sources}
+
+\section{Proof of Security of \consref{cons:sampling}}
+\label{sec:analysis sampling}
+\iffalse
+\subsection{Security}
+The proof of security for \consref{cons:sampling} uses the definition of block unguessable sources~(\defref{def:block guessable}).
+This definition is adaptive and discussed in \apref{sec:characterize}.
+We show the security of \consref{cons:sampling}:
+\begin{itemize}
+\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
+\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
+\item The outputs $V_1,..., V_\ell$ are a block unguessable source.  This is made formal in the following corollary:
+\begin{corollary}
+\label{cor:v are unguessable}
+Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
+Take any $q=\poly(n)$.
+For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block source.
+\end{corollary}
+\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable source.
+\end{itemize}
+
+\noindent
+We now present the proofs of Lemmas \ref{lem:sampling works} and \ref{lem:samp unguess}.
+
+\begin{proof}[{\large Proof of \lemref{lem:sampling works}}]
+Consider some fixed $i$.
+Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
+Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
+Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
+
+\begin{claim}
+\label{cl:vi have entropy}
+\[
+\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
+\]
+\end{claim}
+\begin{proof}
+Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
+We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
+Then
+\begin{align*}
+\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
+&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
+&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
+\end{align*}
+Taking the negative logarithm of both sides we have that
+\begin{align*}
+\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
+&\ge \sum_{j_k\in J} \alpha = \alpha X
+\end{align*}
+This completes the proof of \clref{cl:vi have entropy}.
+\end{proof}
+
+We note that $X$ is distributed according to the hypergeometric distribution,
+and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
+Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
+
+\bnote{this can also be tightened.}
+Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
+ \[
+\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
+\]
+\end{proof}
+
+\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]
+\fi
+
+\lnote{I need to check this}
+Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable source.
+The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .
+Let $W$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples.
+Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
+
+Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
+Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
+\[
+| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
+\]
+Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
+\[I_{v_1,..., v_\ell, r}(x, i) =
+\begin{cases}
+r & v_i = x\\
+\perp & \text{otherwise.}
+\end{cases}\]
+By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $g$ queries) such that
+\begin{align}
+\label{eq:dist before}
+|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+\end{align}
+\lnote{why $\log |Z|$? and where did the randomness used to sample go?}
+
+We now prove $S$ cannot distinguish between $R$ and $U$.
+\begin{lemma}
+\label{lem:sim cannot distinguish samp}
+$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
+\end{lemma}
+
+\begin{proof}
+\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
+\begin{lemma}
+\label{lem:codewords in I close samp}
+Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then, \lnote{perhaps this can be tightened}
+\[
+\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le q(q+1) 2^{-\subsetEntropy}.
+\]
+\end{lemma}
+\begin{proof}
+The only information about whether the value is $r$ or $u$ is contained in the query responses.
+First, modify $S$ slightly to quit immediately if it gets a response not equal to $\perp$ (such $S$ is equally successful at distinguishing between $r$ and $u$, because the first non-$\perp$ response suffices).
+There are $q+1$ possible values for $View(S)$ on a given input ($q$ of those views consist of some number of $\perp$ responses followed by the first non-$\perp$ response, and the one view has all $q$ responses equal to $\perp$) .
+By \lnote{cite chain rule lemma here!}, $\Hav(V_j | View(S))) \ge \subsetEntropy - \log(q+1)$ \lnote{add the randomness used to sample into here}.
+Therefore, at each query, the probability that $S$ gets non-$\perp$ answer (equivalently, guesses $V_j$) is at most $(q+1)2^{-\subsetEntropy}$.
+Since there are $q$ queries, the result follows by the union bound.
+ This concludes the proof of \lemref{lem:codewords in I close samp}.
+\end{proof}
+By averaging over all points in $\zo^\kappa$ we conclude that
+\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
+\end{proof}
+
+\noindent Now by the security of obfuscation we have that
+\begin{align}
+\label{eq:dist after}
+|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+\end{align}
+Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
+\begin{align*}
+\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
+&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
+&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
+&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
+&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
+\end{align*}
+This is a contradiction and completes the proof.% of \lemref{lem:samp unguess}.
+%\end{proof}
+
+%\end{proof}
+\iffalse
+\subsection{Correctness}
+\label{sec:sampling errors}
+
+%\section{Proof of \lemref{lem:sampling errors}}
+\bnote{can be tightened to $\omega(n^c \log n)$.}
+\begin{proof}[Proof of \lemref{lem:sampling errors}]
+
+Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.
+Denote by $\mu = -\frac{(c-1)\log n}{2}$ and note that $t\leq \mu(\gamma-\eta)/\eta$.
+Since $\eta = \omega(\log n)$, we will assume
+$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.
+\begin{align*}
+\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
+&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
+&= \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
+&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
+&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
+\end{align*}
+We then have the probability that all $v_i\neq v_i'$ as:
+\begin{align*}
+\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell
+=\left( 1- \frac{1}{n^{c-1}}\right)^\ell \le \left(e^{- \frac{1}{n^{c-1}}} \right)^{\ell}
+= \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}
+\end{align*}
+(using $1+x\le e^x$). This completes the proof of \lemref{lem:sampling errors}.
+\end{proof}
+\fi
+
+\section{Analysis of \consref{cons:first construction}}
+\label{sec:construction analysis}
+
+\subsection{Characterizing sources with sparse high-entropy marginals}
 \label{sec:characterize}
@@
 
-\subsection{Positive Examples}
+\subsubsection{Positive Examples}
 \label{sec:positive ex}
@@
 
-\subsection{Negative Examples}
+\subsubsection{Negative Examples}
 \label{sec:negative ex}
@@
 
-\section{Analysis of \consref{cons:info theoretic}}
-\label{sec:info theory sec}
-\begin{proof}[Proof of \lemref{lem:info theory sec}]
-Let $W\in \mathcal{W}$.
-It suffices to argue correctness and security.  We first argue correctness.
-When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.
-Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
-Then by correctness of $(\gen', \rep')$, $\Pr[(r, p)\leftarrow \gen'(v) \wedge r'\leftarrow \rep(v',p) \wedge r' = r]\ge 1-\delta$.
-
-We now argue security.
-Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
-To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{fext}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
-The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
-Most known constructions are average-case and we omit this notation.}
-
-We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
-First note since $W$ is $(\alpha, \beta)$-partial block distribution that
-there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
-\]
-Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$,
-\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]
-
-%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
-%Then since $W$ is a block-source,
-%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
-\noindent
-Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that
-\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-1}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1-1})\]
-and since $(seed_1,..., seed_{j_1})$ are independent of these values
-\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
-consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
-Applying a deterministic function does not increase statistical distance and thus,
-\begin{align*}
-(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\gamma \epsilon_{cond}} (Z_{j_1}, seed_{j_1},..., seed_1)
-\end{align*}
-
-\noindent
-By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \tilde{\alpha}(\gamma -\beta)$ where
-\[
-(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\gamma \epsilon_{cond}} (Z, seed_\gamma,...,  seed_1).\]
-%By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
-%Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$.
-%That is,
-%\[
-%(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]
-This completes the proof.
-\end{proof}
-
-\section{Analysis of \consref{cons:sampling}}
-\label{sec:analysis sampling}
-\subsection{Security}
-The proof of security for \consref{cons:sampling} uses the definition of block unguessable sources~(\defref{def:block guessable}).
-This definition is adaptive and discussed in \apref{sec:characterize}.
-We show the security of \consref{cons:sampling}:
-\begin{itemize}
-\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
-\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
-\item The outputs $V_1,..., V_\ell$ are a block unguessable source.  This is made formal in the following corollary:
-\begin{corollary}
-\label{cor:v are unguessable}
-Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
-Take any $q=\poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block source.
-\end{corollary}
-\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable source.
-\end{itemize}
-
-\noindent
-We now present the proofs of Lemmas \ref{lem:sampling works} and \ref{lem:samp unguess}.
-
-\begin{proof}[{\large Proof of \lemref{lem:sampling works}}]
-Consider some fixed $i$.
-Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
-Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
-
-\begin{claim}
-\label{cl:vi have entropy}
-\[
-\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
-\]
-\end{claim}
-\begin{proof}
-Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
-We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
-Then
-\begin{align*}
-\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
-&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
-\end{align*}
-Taking the negative logarithm of both sides we have that
-\begin{align*}
-\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
-&\ge \sum_{j_k\in J} \alpha = \alpha X
-\end{align*}
-This completes the proof of \clref{cl:vi have entropy}.
-\end{proof}
-
-We note that $X$ is distributed according to the hypergeometric distribution,
-and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
-Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
-
-\bnote{this can also be tightened.}
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
- \[
-\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
-\]
-\end{proof}
-
-\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]
-
-\lnote{I need to check this}
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable source.
-The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .
-Let $W$ be a $(q, \alpha'' = \omega(\log n), 0)$-unguessable block source.
-Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
-
-Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
-Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
-\[
-| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
-\]
-Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
-\[I_{v_1,..., v_\ell, r}(x, i) =
-\begin{cases}
-r & v_i = x\\
-\perp & \text{otherwise.}
-\end{cases}\]
-By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
-\begin{align}
-\label{eq:dist before}
-|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-We now prove $S$ cannot distinguish between $R$ and $U$.
-\begin{lemma}
-\label{lem:sim cannot distinguish samp}
-$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
-\end{lemma}
-
-\begin{proof}
-\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
-\begin{lemma}
-\label{lem:codewords in I close samp}
-Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then,
-\[
-\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}.
-\]
-\end{lemma}
-\begin{proof}
-Recall that for all $j$, $\Hav(V_j | View(S))\geq \alpha''$.
-The only information about the correct value of $r$ is contained in the query responses.
-When all responses are $\perp$ the view of $S$ is identical when presented with $r$ or $u$.
-We now show that for any value of $r$ all queries return $\perp$ with probability $1-2^{-\alpha''}$.
-Suppose not, that is suppose, the probability of at least one nonzero response is $> 2^{-(\alpha'')}$.
-
- When there is a response other than $\perp$ for some $j$ this means that there is no remaining min-entropy in $V_j$.
-If this occurs with over $2^{-\alpha''}$ probability this violates the block unguessability of $V$~(\defref{def:block guessable}).
-By the union bound over the indices $j$ the total probability of a response other than $\perp$ is at most $\ell 2^{-\alpha''}$.
-Thus, for all $r, u$ the statistical distance is at most $\ell 2^{-\alpha''}$.
-This concludes the proof of \lemref{lem:codewords in I close samp}.
-\end{proof}
-By averaging over all points in $\zo^\kappa$ we conclude that
-\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
-\end{proof}
-
-\noindent Now by the security of obfuscation we have that
-\begin{align}
-\label{eq:dist after}
-|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
-\begin{align*}
-\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
-&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
-&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
-&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
-&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
-\end{align*}
-This is a contradiction and completes the proof of \lemref{lem:samp unguess}.
-\end{proof}
-
-%\end{proof}
-\subsection{Correctness}
-\label{sec:sampling errors}
-
-%\section{Proof of \lemref{lem:sampling errors}}
-\bnote{can be tightened to $\omega(n^c \log n)$.}
-\begin{proof}[Proof of \lemref{lem:sampling errors}]
-
-Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.
-\begin{align*}
-\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
-&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
-\end{align*}
-We then have the probability that all $v_i\neq v_i'$ as:
-\begin{align*}
-\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
-&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
-&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
-\end{align*}
-This completes the proof of \lemref{lem:sampling errors}.
-\end{proof}
-
-\section{Analysis of \consref{cons:first construction}}
-\label{sec:construction analysis}
 \subsection{Security}
@@
 
+\section{Analysis of \consref{cons:info theoretic}}
+\label{sec:info theory sec}
+\begin{proof}[Proof of \lemref{lem:info theory sec}]
+Let $W\in \mathcal{W}$.
+It suffices to argue correctness and security.  We first argue correctness.
+When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.
+Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
+Then by correctness of $(\gen', \rep')$, $\Pr[(r, p)\leftarrow \gen'(v) \wedge r'\leftarrow \rep(v',p) \wedge r' = r]\ge 1-\delta$.
+
+We now argue security.
+Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
+To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{fext}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
+The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
+Most known constructions are average-case and we omit this notation.}
+
+We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
+First note since $W$ is $(\alpha, \beta)$-partial block distribution that
+there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\]
+Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$,
+\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]
+
+%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
+%Then since $W$ is a block-source,
+%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
+\noindent
+Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that
+\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-1}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1-1})\]
+and since $(seed_1,..., seed_{j_1})$ are independent of these values
+\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
+consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
+Applying a deterministic function does not increase statistical distance and thus,
+\begin{align*}
+(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\gamma \epsilon_{cond}} (Z_{j_1}, seed_{j_1},..., seed_1)
+\end{align*}
+
+\noindent
+By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \tilde{\alpha}(\gamma -\beta)$ where
+\[
+(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\gamma \epsilon_{cond}} (Z, seed_\gamma,...,  seed_1).\]
+%By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
+%Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$.
+%That is,
+%\[
+%(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]
+This completes the proof.
+\end{proof}
+
 \end{document}

### 2015-02-10 info-bounds/FuzzyExtPossibility.tex
minor edits to intro

@@
 We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
-Fuzzy min-entropy measures the success of the adversary when provided with the functionality of the fuzzy extractor.
-It measures the \emph{ideal} security of a distribution.
-
-High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required (assuming the existence of semantically-secure graded encodings).
+Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.
+
+High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
 Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
-The challenge is to design information-theoretic fuzzy extractors whose security (almost) matches the fuzzy min-entropy of a distribution.
-
 In this work, we ask whether this challenge is inherent.
- We provide two main technical results.
+We show the following:
 \begin{itemize}
-\item \textbf{Sufficiency of fuzzy min-entropy:}  It is possible to build a fuzzy extractor for any \emph{precisely known} physical source.
+\item \textbf{Sufficiency of fuzzy min-entropy:}  We construct a fuzzy extractor for each physical source with fuzzy min-entropy.
 This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.
 Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.
-\item \textbf{Cost of distributional uncertainty:}  High entropy distributions can never be fully observed and must be modeled.
+The constructed fuzzy extractor must \emph{precisely know} the distribution of the noisy source.
+\item \textbf{Cost of distributional uncertainty:}  High entropy sources can never be fully observed and must be modeled.
 An adversary may have a better model than the fuzzy extractor designer.
 To compensate, fuzzy extractors are typically designed to work for families of physical sources.
-We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.
-This result justifies further study of physical sources to increase the fidelity of our models.
+We build a family of high fuzzy min-entropy sources which no fuzzy extractor can secure.
+This result emphasizes the importance of high fidelity models of high entropy sources.
 \end{itemize}
@@
 \end{abstract}
-
-\newpage
-%\tableofcontents\newpage
 
@@
 The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.
-The correctness guarantee is that the key is reproduced precisely as long as the distance between $w$ and $w'$ is at most $t$.
+The correctness guarantee is that the key is reproduced precisely when the distance between $w$ and $w'$ is at most $t$.
 
@@
 Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.
+Fuzzy min-entropy measures the ideal security of a noisy source of entropy when used for key derivation, similar to distributional notions of program obfuscation~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05}---we discuss the connection in \secref{sec:related settings}.
 Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).
-Fuzzy min-entropy measures the maximum obtainable key from a noisy distribution.
+
 However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
@@
 We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.
-
-We answer this question in two important settings.
-An important aspect of a fuzzy extractor is how much it knows about the target distribution $W$.
-In the extreme the fuzzy extractor has a complete description of the probability density function of $W$.
-We call this setting the \emph{known distribution} setting.
-(Previous works have consider
-
-Assuming full knowledge of a distribution is often unrealistic.
+We provide an answer in two settings.
+
+\paragraph{Sufficiency of $\Hfuzz(W)$ for a Precisely Known Distribution}
+Ideally, a fuzzy extractor has \emph{precise knowledge} of the probability distribution function of $W$.
+We call this  the \emph{precise knowledge} setting.
+In this setting, we show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
+Our construction crucially utilizes the probability distribution function of $W$ and, in particular, is not polynomial time.
+This result shows that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor of a distribution $W$.
+
+A number of previous works in the precise knowledge setting have provided efficient algorithms and
+tight bounds for specific distributions---generally the uniform distribution or
+i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
+Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
+
+\paragraph{The Challenge of Precisely Distributional Knowledge}
+Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic.
 Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled.
@@
 Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors).
-Thus, the design is fixed with a partially known distribution, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.
-We call this setting \emph{family of distributions}.
-We ask whether fuzzy min-entropy is sufficient in each of these settings.
-
-\paragraph{Sufficiency of $\Hfuzz(W)$ for a Known Distribution}
-We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
-We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.
-It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).
-
-A number of previous works in this known-distribution setting have provided efficient algorithms and
-tight bounds for specific distributions---generally the uniform distribution or
-i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
-Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
-
-\paragraph{Impossibility of a Fuzzy Extractor for a Family of Distributions}
-Our results are negative when the distribution $W$ is only known to come from a family $\mathcal{W}_Z$ (\thref{thm:imposs fuzz ext}).
-Specifically, we show a family of distributions $\mathcal{W}_Z$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.
+Thus, the design is fixed with a partially known distribution, and the adversary may know more about the distribution than the designer of the fuzzy extractor.
+We call this the \emph{distributional uncertainty} setting.
+
+\paragraph{The Cost of Distributional Uncertainty}
+When the distribution is $W$ is uncertain, our results are negative.   In this setting, $W$ is known to be an element of a family of distributions $\mathcal{W}_Z$.
+We construct a family $\mathcal{W}_Z$ where not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.
 We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart.
@@
 This result shows that uncertainty in the distribution $W$ is devastating to building a fuzzy extractor.
-This result motivates the further research into physical sources.
-\bnote{come back to this sentence}
+In particular, our positive results (\corref{cor:extension to fuzz ext}) show it is possible to build a fuzzy extractor for each $W_z$, but no construction can simultaneously secure the whole family.
+Our result motivates further research into high fidelity descriptions of noisy sources.
 
@@
 \end{center}
-\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
+\caption{Is fuzzy min-entropy sufficient to extract an information-theoretic superlogarithmic length key?}
 \label{tab:main results}
@@
 
-\bnote{asked to discuss implications of our negative results}
-\bnote{can we reframe the paper as the cost of distributional uncertainty?}
-\bnote{compare to current constructions?}
+\paragraph{Interpreting our Results}
+Our results show that fuzzy min-entropy is sufficient for noisy key derivation if the distribution is precisely known but insufficient if the distribution is only known to come from a family.
+A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.
+Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.
+This impossibility can be overcome by the use of a short seed of uniform randomness.
+We must find an analogous relaxation to derive keys from noisy sources.
+One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.
+
 \subsection{Our Techniques}
 
-\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).
+\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).
 We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).
@@
 
-Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
+An adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
 In the secure sketch case, $ss$ can be used to find fixed points of $\rec(\cdot, ss)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$.
@@
 The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.
-In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
-The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.
-In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency.
-Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).
+In this computational setting, a single fuzzy extractor (or secure sketch) can simultaneously secure all possible distributions by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
+The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).}  This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.
+The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability.
+Thus, extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.
 
@@
 We compare our positive results to these characterizations in \apref{sec:corr variables}.
-To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for a family of distributions.
-
-%The definition of $\Hfuzz$ can be extended to this model (by again thinking of the adversary as choosing the value $w'$ that is most likely to lead to a success).
+To the best of our knowledge, prior results on correlated random variables are in the precise knowledge setting, we are unaware of works that consider the cost of distributional uncertainty.
 
@@
 Let $\delta>0$ be an function of $n$.
-Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.
-When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
+Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = \beta_{t,i} /\delta$.
+When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 4$.
 
 \end{theorem}
+\noindent
 We provide a proof in \apref{sec:proof of layered hashing}.
-The main idea is to show that an adversary that knows the level of $w$ cannot perform much better than an adversary without this information.
-\bnote{this sentence isn't helpful, provide better intuition}
+The main idea is that providing the level information makes the distribution look nearly flat~(the probability of points differs by at most a factor of two).
+We can apply similar techniques to \lemref{lem:flat hashing} to show security for each nearly flat distribution.
+Then, we show that providing the level information does not hurt security too much.
 
@@
 We prove the stronger average case statement.
-We first describe a family $\mathcal{W}$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
-Let $\mathcal{W}$ be the set of all distributions of the form 
-\[W =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} W_1 + \begin{pmatrix} 0  \\ 
+We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
+Let $\mathcal{W}_Z$ be the set of all distributions of the form 
+\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} w_1 + \begin{pmatrix} 0  \\ 
 b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
 \]
-where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i, b_i\in\mathbb{F}, a_i\neq 0$.  
-This type of distribution is an affine line in space $\mathbb{F}^\gamma$.
-Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.
-The adversary sees $\sketch(V)$ and $Z$.
-$Z$ is the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$.
-The algorithms $\sketch, \rec$ never see $Z$.
+The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) for arbitrary $b_i$ and $a_i\neq 0$.
+The outcome $w\leftarrow W_z$ is sampled by sampling $w_1$ and computing $w$.
+Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$.
+The algorithm $\sketch, \rec$ never see $Z$ only the outcome of $v\leftarrow V$.
 Fix some $4\le t < \gamma$.
@@
 We prove the stronger average case statement.
-Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.
-
-Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
+Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}+1$ and note that $n/\nu >t$.
+
+Our counterexample uses a slightly different family of distributions $\mathcal{W}_Z$ than the counterexample for secure sketches.  
 We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).
@@
 \]
-The multiplication is in $\mathbb{F}$.
-Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
-Let $\mathcal{W}$ be the set of all such $W$.
-
- Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.
-The adversary sees $\sketch(V)$  and $Z$, where $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
-
-We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
+The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$ for arbitrary $b_i$ and $a_i\neq 0$.  
+A particular distribution $W_z$ is the uniform distribution over choices of $x$.
+ Define $V$ as the process of uniformly choosing $W_z\leftarrow \mathcal{W}_Z$ and then sampling from $w\leftarrow W_z$.
+The adversary sees $\sketch(V)$  and $Z$.
+We then show the following~(proofs in \apref{sec:fuzz ext proof}):
 \begin{itemize}
-\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
+\item \propref{prop:dist fuzzy ent fuzz}: for all $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z) = \omega (\log n)$. 
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
@@
 
-%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.
-In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.
-This means that showing security for a family of distributions $\mathcal{W}$ is equivalent to showing security for all  distributions $V$ when the distribution is known to the algorithms $V$.
-In our negative results, the adversary  uses the uniform distribution $V$ over $\mathcal{W}$.
+\noindent
+This means that showing security for a family of distributions $\mathcal{W}_Z$ is equivalent to showing security for all distributions $V$ when the distribution is known to the algorithms $(\sketch, \rec)$.
+In our negative results, the adversary uses the uniform distribution over $\mathcal{W}_Z$.
 However, it may be possible to improve parameters by using a different $V$.
-This would just rule out some member of $\mathcal{W}$ not an average member.
-This is true for fuzzy extractors as well and is resilient to changes in parameters including imperfect correctness.
-
-%Since the distribution used in our negative results was uniform it is stronger, ruling out security for an average $\mathcal{W}$.  However, constructing a nonuniform $V$ may improve these results.
-%\begin{lemma}
-%\label{lem:quant switch fuzz}
-%Let $\mathcal{W}$ be a family of distributions.
-If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-Let $V$ be a distribution over $\mathcal{W}$.
-Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.
-If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
-%\end{lemma}
-
-%\begin{corollary}
-%\label{cor:no fuzz for dist}
-%Let $\mathcal{W}$ be a family of distributions.
-Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.
-If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
-%\end{corollary}
-%
-%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
+
 \section{Fuzzy min-entropy}
 \label{sec:proof fuzz necessary}
+In this section, we provide proofs of statements in \secref{sec:minimal conditions}.  
 \begin{proof}[Proof of \propref{prop:fuzz necessary}]
@@
  &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
- &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
+% &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
  &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
- &= \Hfuzz(W) - \log \frac{1}{\Pr[P=p]}.
-\end{align*}
+ &= \Hfuzz(W) + \log \Pr[P=p].
+\end{align*}
+This completes the proof of \lemref{lem:conditional fuzz rule}.
 \end{proof}
@@
 \end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notation clarity).
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $L_I$ be the random variable of the level information (in what follows, $L_I$ takes values between $m$ and $m+n$, where possible we omit this for notational clarity).
 
 \begin{align}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge I=i}) \right)\nonumber\\
-&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
-&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
-&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
-&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
-&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
-&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge L_I =i }) \right)\nonumber\\
+&=-\log \left( \expe_{i} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
+&=-\log \left( \expe_{i} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
+&\ge-\log \left( \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
+&\ge-\log \left(\frac{1}{\delta} \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
+&\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
+&\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
 \end{align}
@@
 \noindent
+The third line follows because the only dependence between $\mathcal{K}_i$ and $W$ is in $i$.
+The fourth line follows by \cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
 We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.
+For convenience denote by $J \overset{def}= (L_I \wedge 1_{\text{low}}=0)$.
+That is, $\Pr[J=i] \overset{def}= \Pr[1_{\text{low}}=0 \wedge L_I=i$].
 \begin{claim}
 \label{cl:fuzz proportional beta}
-\[\Hoo(W | 1_{\text{low}} =0 \wedge J=j ) -\log \beta_{t, i} \ge \Hfuzz(W | J=j \wedge 1_{\text{low}}=0)+1.\]
+$\Hoo(W |   J=i ) -\log \beta_{t, i} \ge \Hfuzz(W | J=i)-1.$
 \end{claim}
 \begin{proof}
-For convenience denote by $J=j$ the random variable $1_{\text{low}}=0 \wedge I=i$. 
-\begin{align*}
-\Hfuzz(W|J=j) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | J=j]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \min_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \max_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)+1\\
-&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-\Hoo(W|J=j)}\right) \right)+1\\
-&= \Hoo(W|J=j)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 1\right) \right)+1\\
-&=\Hoo(W|J=j)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
-&=\Hoo(W|J=j)+1-\log \beta_{t, i}.
-\end{align*}
-Where the third line follows by \clref{cl:nearly flat after conditioning}, which follows.  This completes the proof of \clref{cl:fuzz proportional beta}.
-\end{proof}
-
-\begin{claim}
-\label{cl:nearly flat after conditioning}
-Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.
-Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
-\end{claim}
-\begin{proof}
-\begin{align*}
-\Pr[W=w_1 | J=j] &=&\frac{\Pr[W=w_1\wedge J=j] }{\Pr[J=j]}
-&=& \frac{\Pr[W=w_1]}{\Pr[J=j]}\\
-&\ge& \frac{\Pr[W=w_2]}{2 \Pr[J=j]}
-&=& \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
-&=&\frac{\Pr[W=w_2]}{2}.
-\end{align*}
-Where the first and last equality follow by Bayes' rule.
-The second and fourth equality follow by noting that $\Pr[W=w \wedge J=j] = \Pr[W=w]$ for all $w\in L_i$.
-The inequality proceeds by assumption.
-This completes the proof of \clref{cl:nearly flat after conditioning}.
-\end{proof}
-
-\noindent 
-We now return to the proof of \lemref{lem:flat hashing}. Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
-\begin{align*}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
-&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
+\begin{align*}
+\Hfuzz(W|J=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \Pr[W=w | J=i]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t}\left( \min_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \left(\max_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)+1\\
+&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 2^{-\Hoo(W|J=i)}\right) \right)+1\\
+&= \Hoo(W|J=i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 1\right) \right)+1\\
+&=\Hoo(W|J=i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
+&=\Hoo(W|J=i)+1-\log \beta_{t, i}.
+\end{align*}
+Where the third line follows by \lemref{lem:nearly flat after conditioning}, which follows the proof of \thref{thm:layered hashing}.  This completes the proof of \clref{cl:fuzz proportional beta}.
+\end{proof}
+
+\noindent 
+We now return to the proof of \thref{thm:layered hashing}. Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
+\begin{align*}
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
+&=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
 &=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log \frac{1}{\delta} \\
@@
 &\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  -2\log (1-2^{-m}) \\
-&\ge \Hfuzz(W) - 3- \log n - \log 1/\delta
+&\ge \Hfuzz(W) - 4- \log n - \log 1/\delta
 \end{align*}
@@
 The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \le 1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
+\end{proof}
+
+\begin{lemma}
+\label{lem:nearly flat after conditioning}
+Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.
+Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
+\end{lemma}
+\begin{proof}
+\begin{align*}
+\Pr[W=w_1 | J=j] &=\frac{\Pr[W=w_1\wedge J=j] }{\Pr[J=j]}\\
+&= \frac{\Pr[W=w_1]}{\Pr[J=j]}\\
+&\ge \frac{\Pr[W=w_2]}{2 \Pr[J=j]}\\
+&= \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
+&=\frac{\Pr[W=w_2 | J=j]}{2}.
+\end{align*}
+Where the first and last equality follow by Bayes' rule.
+The second and fourth equality follow by noting that $\Pr[W=w \wedge J=j] = \Pr[W=w \wedge 1_{\text{low}}=0 \wedge I=i] = \Pr[W=w]$ for all $w\in L_i$.
+The inequality proceeds by assumption.
+This completes the proof of \lemref{lem:nearly flat after conditioning}.
 \end{proof}
@@
 
-Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
+Consider some $p^*\in A_{\epsilon}$.  
 The distribution $\Key|P=p^*$ is the set of possible keys.
@@
 
-There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.
+There exists a set $\Key_{small}$  where $|\Key_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in \Key_{small}$,  $|Q_{p^*, \key}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.
 If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
-For the remainder of the proof we restrict ourselves to elements in $R_{small}$.
+For the remainder of the proof we restrict ourselves to elements in $\Key_{small}$.
 Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.
-These are the interior of $Q_{p^*, r}$: \lnote{what's $r$?
-in this and previous lines?
-also, I can parse definition of interior below}
-\begin{align*}
-\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
+These are points where all points within distance $t$ map to the same key.
+We call this set the interior of $Q_{p^*, \key}$:
+\begin{align*}
+\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge (\forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key)\},\\
 %\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
 \end{align*}
-
-%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
-We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.
-We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient} \lnote{how about ``almost ball''}
+ The isoperimetric inequality says $\inter(Q_{p^*, \key})$ must be of bounded size.
+This statement use the sets which are nearly balls in the Hamming space\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.
+We use the term near ball for emphasis.}:
 \begin{definition}
-A set $S$ is a $\eta$-deficient ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
+A set $S$ is a $\eta$-near ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
 \end{definition}
-
-Consider some $\key^*\in R_{small}$.  
-We now proceed to show that the interior of each $Q_{p^*, \key^*}$ is small:
-%Recall that $B_{n-\kappa-t}$ denotes the ball of radius $n-\kappa -t$.
+\noindent
+We now show for any $\key^*$, $\inter(Q_{p^*, \key^*})$ is small:
 
@@
 complement of a set) and $\forall s\in S_{p^*, \key^*}, d\in D$,
-$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).\lnote{Why?}
+$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).
+Since $S_{p^*, \key^*}$ is a near ball and the set $D^\complement$ contains all points of distance less than $t$ from $S_{p^*, \key^*}$.
+Thus, the set $S_{p^*, \key^*} \cup D^\complement$ contains a near ball of radius is $\eta+t-1$).
 We now bound the size of $S_{p^*, \key^*}$.
 
-Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.
+Recall that $|S_{p^*, \key^*} \cup D^\complement| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.
 Since this set contains less than half the points in the metric space we know its radius at most $n/2$.
-This means that $|S_{p^*, \key^*}|$ is a deficient sphere \lnote{ball} of radius at most $n/2-t$.
+This means that $|S_{p^*, \key^*}|$ is a near ball of radius at most $n/2-t+1$.
 Let $X$ denote a uniform string on $\zo^n$.
-We use Hoeffding's inequality~\cite{hoeffding1963probability}: \lnote{should the first $n$ in the line below be $n/2$?}
-
-\begin{align*}
-|S_{p^*, \key^*}| \le \{ x | \dis (x, 0)\le n-t\} &= 2^n \Pr_{X\leftarrow \zo^n} [ wt(X) \le (1/2-t/n)n] \le 2^n e^{-n ((t/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}
+We use Hoeffding's inequality~\cite{hoeffding1963probability}:
+
+\begin{align*}
+|S_{p^*, \key^*}| &\le \{ x | \dis (x, 0)\le \frac{n}{2}-t+1\}\\&= 2^n \Pr_{X\leftarrow \zo^n} [ wt(X) \le (\frac{1}{2}-\frac{t-1}{n})n] \\
+&\le 2^n e^{-n (((t-1)/n)^2)} = 2^n e^{-4\nu} \le 2^{n - 4\nu}.
 \end{align*}
 where the second to last equality follows from the definition of $t$
-(as $4\nu \sqrt{n}$) at the beginning of the proof of Theorem~\ref{thm:imposs fuzz ext}.
+(as $4\nu \sqrt{n}+1$) at the beginning of the proof of Theorem~\ref{thm:imposs fuzz ext}.
 \end{proof}
@@
 
-The distinguisher $D(x, p, z)$ is formed by calling $D_p(x, z)$ when $p\in A_p$ and outputting a random bit otherwise.  The advantage of $D$ is 
+The distinguisher $D(\key, p, z)$ is formed by calling $D_p(\key, z)$ when $p\in A_{\epsilon}$ and outputting a random bit otherwise.  The advantage of $D$ is 
 \begin{align*}
 \Pr[D(\Key, P, Z) = 1] &- \Pr[D(U, P, Z) =1]\\
-&=(\Pr[D(\Key, P, Z) = 1| P\in A_p] - \Pr[D(U, P, Z) =1 | P\in A_p])\Pr[P\in A_p]\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in R_{small}]\Pr[U\in R_{small}] - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|R_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in R_{small}]\right) - \Pr[U\not\in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in R_{small}] - \Pr[U\not \in R_{small}]\right)\\
-&\ge \sum_{p^*\in A_p} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in R_{small}] \right)\\
-&\ge \sum_{p^* \in A_p} \Pr[P=p^*]\left(1/4-\ngl(n)\right) \ge \frac{1}{8}-\ngl(n).
-\end{align*}
-The sixth line follows since $R_{small} \ge 2^{\kappa-1}\ge 2$.  The eighth line follows because $\Pr[U\in R_{small}]\ge 1/2$.  The last inequality proceeds because $\Pr[P\in A_p]\ge 1/2$.
+&=(\Pr[D(\Key, P, Z) = 1| P\in A_{\epsilon}] - \Pr[D(U, P, Z) =1 | P\in A_{\epsilon}])\Pr[P\in A_{\epsilon}]\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in \Key_{small}]\Pr[U\in \Key_{small}] - \Pr[U\not\in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|\Key_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in \Key_{small}]\right) - \Pr[U\not\in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -1+\frac{1}{2}\Pr[U\in \Key_{small}] \right)\\
+&\ge \sum_{p^* \in A_{\epsilon}} \Pr[P=p^*]\left(1/4-\ngl(n)\right) \ge \frac{1}{8}-\ngl(n).
+\end{align*}
+The sixth line follows since $\Key_{small} \ge 2^{\kappa-1}\ge 2$.
+The eighth line follows because $\Pr[U\in \Key_{small}]\ge 1/2$.
+The last inequality proceeds because $\Pr[P\in A_{\epsilon}]\ge 1/2$.
 This completes the proof of \lemref{lem:fuzz can't get key}.

### 2015-02-10 constantRate/ConstCompFuzzExt-crypto.tex
small edits to proof of 3.6
gone through section 3

@@
 Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
-Cons. \ref{cons:first construction}  & high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
+Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
 Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
@@
 \label{sec:sampling}
-Let $w$ be a string of symbols (over an arbitrary alphabet) $w=w_1\dots w_\gamma$.
-The construction first chooses a random fuzzy extractor output $r$.
-It then samples a random subset of blocks $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$.
-This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
-Let $\sample_{\gamma, \eta}(\cdot)$ denote an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.
+
+\paragraph{Sources with High-Entropy Samples}
+Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$.
+For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(w_{j_1}, \dots, w_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
+This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
+However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.
+
+A distribution obtained by applying short-output condensers multiple times to a single sample from a high-entropy source (e.g., via random projections) will have this property, because the outputs of the condensers will be contain fresh entropy as long as the total amount of entropy in the source is not exceeded
+(by a simple conditional entropy argument---each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as fresh entropy remains conditioned on the previous elements).
+
+\paragraph{The Construction}
+The construction first chooses a random $r$ to be used as the output of the fuzzy extractor.
+It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers.
+See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
+The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.
+Composability also allows reusability.
 
@@
 \label{cons:sampling}
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$.
-Let $\eta$ be a parameter, and $\mathcal{O}$ be an obfuscator for the family of digital lockers with $\kappa$-bit outputs.  Define $\gen, \rep$ as:
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples, where each $W_j$ is over $\mathcal{Z}$.
+Let $\ell$ be a parameter, to be determined later.
+Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for the family of digital lockers with $\kappa$-bit outputs. Define $\gen, \rep$ as:
 
@@
 \begin{enumerate}[(i)]
-\item Select $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
-\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma,\eta}( \lambda_i)$
+\item Choose uniformly random distinct $1\le j_{i, 1},..., j_{i, \eta}\le \gamma$
 \item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
 \item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
-\item Set $p_i = \rho_i, \lambda_i$.
+\item Set $p_i = \rho_i, (j_{i, 1},..., j_{i, \eta})$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \underline{Input}: $(w'=w_1',..., w_\gamma', p)$
+\item \underline{Input}: $(w'=w_1',..., w_\gamma', p = p_1\dots p_\ell)$
 \item For $i=1,..., \ell$:
 \begin{enumerate}[(i)]
-\item Parse $p_i$ as $\rho_i, \lambda_i$.
-\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
+\item Parse $p_i$ as $\rho_i, (j_{i, 1},..., j_{i, \eta})$.
 \item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
@@
 %\end{itemize}
-The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.
-
-This construction can use the na\"{i}ve sampler that takes truly random samples.
-If desired, public randomness may be substantially decreased by using more sophisticated samplers.
-(See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)
 
@@
 \label{thm:sampling}
-Let $\mathcal{Z}$ be an alphabet.
-Let $n$ be a security parameter.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma =\Omega(n)$.
-Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$, and let $c> 1$ be a constant and $\ell$ be such that $\ell = n^c$.
-Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
-Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
-\begin{align*}
-t&\leq -\frac{(c-1)}{2} \frac{(\gamma-\eta)\log n}{\eta} = o(\gamma)\\
-\delta &= e^{-n}
-\end{align*}
+Let $n$ be a security parameter, $\mathcal{Z}$ be an alphabet, and $\gamma, \subsetEntropy$, and $t$ be functions of $n$, as follows.
+Let $\mathcal{W}$ be a family of sources over $\mathcal{Z}^\gamma$ with $(\eta, \subsetEntropy)$ high-entropy samples for $\subsetEntropy = \omega(\log n)$.
+Let $t$ be such that $\left(1-\frac{t}{\gamma-\eta}\right)^\eta>1/p(n)$ for some positive polynomial $p$.
+Then it there exists $\ell = \poly(n)$ such that for any
+$s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $\left (\epsilon_{sec}, s_{sec}\right)$-hard with negligible error.
 \end{theorem}
 
+ Correctness follows immediately: for any given $i$, the probability that $v'_i=v_i$ is at least $1/p(n)$.
+By choosing $\ell$ sufficiently bigger than $1/p(n)$, we guarantee that for at least one $i$,  $v'_i=v_i$ with all but negligible probability
+(indeed, because the $\ell$ samples are independent, the probability this does not happen is at most $(1-1/p(n))^\ell \le e^{-\ell/p(n)}$, using $1+x \le e^x$).
+
+Security follows from obfuscation and is analyzed in \apref{sec:analysis sampling}.
+
+\paragraph{Any sublinear error-rate can be supported if most symbols in a sample contribute entropy.}
+The requirement on $t$ can be expressed as $\eta \log  \left(1-\frac{t }{\gamma-\eta}\right) = O (\log n)$. Using $\ln (1+x)\approx x$ and relying on $O$ to absorb any 
+constant factor involved in this approximation and the switch from $\ln$ to $\log$, we get $\eta \frac{t }{\gamma-\eta} = O(\log n)$. If $t$ is sublinear in $\gamma$
+ (and $\eta$ is no more than a constant fraction of $\gamma$), then $t/(\gamma-\eta)$ is subconstant, and therefore it is possible to satisfy this requirement on $t$ while simultaneously maintaining $\eta = \omega (\log n)$, which implies $\subsetEntropy = \omega(\log n)$ as long as most symbols in a sample of size $\eta$ contribute a constant amount of entropy each.
+
+\paragraph{More Errors than Entropy?}
+The amount of entropy in $W$ need not exceed $\subsetEntropy$---thus, it can be as low as $\omega(\log n)$.
+Assuming $\gamma = n$, the number $t$ of errors may be any function in $o(n)$, and thus $\log |B_t| \ge t \log |Z|$ may far exceed $\Hoo(W)$.
+
+\iffalse 
 \subsection{Security of \consref{cons:sampling}}
@@
 \end{lemma}
+\fi
 
@@
 The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.
-We consider a bounded $q = \poly(n)$ number of reuses.
-For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.
+Consider any $q = \poly(n)$ number of reuses.
+For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary.
+The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\label{thm:sampling} in \apref{sec:analysis sampling} (note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$).
+
   Thus, given sufficiently strong reusability we achieve the following result:
@@
 \label{thm:reusability}
-Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
+Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ is an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
 For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
 \end{theorem}
-\begin{proof}
-The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
-The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
-Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
-\bnote{say more here?}
-\end{proof}
-
+
+\iffalse
 \subsection{More errors than entropy?}
@@
 
-\section{Construction for Sources with High-Entropy Marginals}
-
+\fi
+
+\section{Construction for Sources with Sparse High-Entropy Marginals}
 \label{sec:cor construction}
+\lnote{stopped here; also need to reorder appendices}
 In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.
@@
 
-\section{Analysis of \consref{cons:info theoretic}}
-\label{sec:info theory sec}
-\begin{proof}[Proof of \lemref{lem:info theory sec}]
-Let $W\in \mathcal{W}$.
-It suffices to argue correctness and security.  We first argue correctness.
-When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.
-Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
-Then by correctness of $(\gen', \rep')$, $\Pr[(r, p)\leftarrow \gen'(v) \wedge r'\leftarrow \rep(v',p) \wedge r' = r]\ge 1-\delta$.
-
-We now argue security.
-Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
-To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{fext}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
-The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
-Most known constructions are average-case and we omit this notation.}
-
-We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
-First note since $W$ is $(\alpha, \beta)$-partial block distribution that
-there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
-\]
-Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$,
-\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]
-
-%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
-%Then since $W$ is a block-source,
-%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
-\noindent
-Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that
-\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-1}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1-1})\]
-and since $(seed_1,..., seed_{j_1})$ are independent of these values
-\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
-consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
-Applying a deterministic function does not increase statistical distance and thus,
-\begin{align*}
-(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\gamma \epsilon_{cond}} (Z_{j_1}, seed_{j_1},..., seed_1)
-\end{align*}
-
-\noindent
-By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \tilde{\alpha}(\gamma -\beta)$ where
-\[
-(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\gamma \epsilon_{cond}} (Z, seed_\gamma,...,  seed_1).\]
-%By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
-%Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$.
-%That is,
-%\[
-%(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]
-This completes the proof.
-\end{proof}
-
-\section{Analysis of \consref{cons:sampling}}
-\label{sec:analysis sampling}
-\subsection{Security}
-The proof of security for \consref{cons:sampling} uses the definition of block unguessable sources~(\defref{def:block guessable}).
-This definition is adaptive and discussed in \apref{sec:characterize}.
-We show the security of \consref{cons:sampling}:
-\begin{itemize}
-\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
-\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
-\item The outputs $V_1,..., V_\ell$ are a block unguessable source.  This is made formal in the following corollary:
-\begin{corollary}
-\label{cor:v are unguessable}
-Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
-Take any $q=\poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block source.
-\end{corollary}
-\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable source.
-\end{itemize}
-
-\noindent
-We now present the proofs of Lemmas \ref{lem:sampling works} and \ref{lem:samp unguess}.
-
-\begin{proof}[{\large Proof of \lemref{lem:sampling works}}]
-Consider some fixed $i$.
-Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
-Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
-
-\begin{claim}
-\label{cl:vi have entropy}
-\[
-\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
-\]
-\end{claim}
-\begin{proof}
-Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
-We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
-Then
-\begin{align*}
-\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
-&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
-\end{align*}
-Taking the negative logarithm of both sides we have that
-\begin{align*}
-\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
-&\ge \sum_{j_k\in J} \alpha = \alpha X
-\end{align*}
-This completes the proof of \clref{cl:vi have entropy}.
-\end{proof}
-
-We note that $X$ is distributed according to the hypergeometric distribution,
-and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
-Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
-
-\bnote{this can also be tightened.}
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
- \[
-\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
-\]
-\end{proof}
-
-\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]
-
-\lnote{I need to check this}
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable source.
-The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .
-Let $W$ be a $(q, \alpha'' = \omega(\log n), 0)$-unguessable block source.
-Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
-
-Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
-Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
-\[
-| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
-\]
-Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
-\[I_{v_1,..., v_\ell, r}(x, i) =
-\begin{cases}
-r & v_i = x\\
-\perp & \text{otherwise.}
-\end{cases}\]
-By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $g$ queries) such that
-\begin{align}
-\label{eq:dist before}
-|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-We now prove $S$ cannot distinguish between $R$ and $U$.
-\begin{lemma}
-\label{lem:sim cannot distinguish samp}
-$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
-\end{lemma}
-
-\begin{proof}
-\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
-\begin{lemma}
-\label{lem:codewords in I close samp}
-Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then,
-\[
-\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}.
-\]
-\end{lemma}
-\begin{proof}
-Recall that for all $j$, $\Hav(V_j | View(S))\geq \alpha''$.
-The only information about the correct value of $r$ is contained in the query responses.
-When all responses are $\perp$ the view of $S$ is identical when presented with $r$ or $u$.
-We now show that for any value of $r$ all queries return $\perp$ with probability $1-2^{-\alpha''}$.
-Suppose not, that is suppose, the probability of at least one nonzero response is $> 2^{-(\alpha'')}$.
-
- When there is a response other than $\perp$ for some $j$ this means that there is no remaining min-entropy in $V_j$.
-If this occurs with over $2^{-\alpha''}$ probability this violates the block unguessability of $V$~(\defref{def:block guessable}).
-By the union bound over the indices $j$ the total probability of a response other than $\perp$ is at most $\ell 2^{-\alpha''}$.
-Thus, for all $r, u$ the statistical distance is at most $\ell 2^{-\alpha''}$.
-This concludes the proof of \lemref{lem:codewords in I close samp}.
-\end{proof}
-By averaging over all points in $\zo^\kappa$ we conclude that
-\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
-\end{proof}
-
-\noindent Now by the security of obfuscation we have that
-\begin{align}
-\label{eq:dist after}
-|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
-\begin{align*}
-\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
-&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
-&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
-&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
-&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
-\end{align*}
-This is a contradiction and completes the proof of \lemref{lem:samp unguess}.
-\end{proof}
-
-%\end{proof}
-\subsection{Correctness}
-\label{sec:sampling errors}
-
-%\section{Proof of \lemref{lem:sampling errors}}
-\bnote{can be tightened to $\omega(n^c \log n)$.}
-\begin{proof}[Proof of \lemref{lem:sampling errors}]
-
-Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.
-\begin{align*}
-\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
-&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
-\end{align*}
-We then have the probability that all $v_i\neq v_i'$ as:
-\begin{align*}
-\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
-&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
-&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
-\end{align*}
-This completes the proof of \lemref{lem:sampling errors}.
-\end{proof}
-
-\section{Analysis of \consref{cons:first construction}}
-\label{sec:construction analysis}
 \subsection{Security}

### 2015-02-10 trunk/constantRate/ConstCompFuzzExt-crypto.tex
minor edits and notation change from dissertation

@@
 \newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
+\newcommand{\error}{\ensuremath{\class{Err}}\xspace}
+\newcommand{\weight}{\ensuremath{\class{Wgt}}\xspace}
 \newcommand{\dis}{\ensuremath{\mathsf{dis}}}
@@
 These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks.
-It uses symbols-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.
+It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.
 
@@
 %end centering
-\caption{Summary of new constructions.  }
+\caption{Summary of new constructions.
+\consref{cons:sampling} supports the widest class of sources.
+The sources supported by the other sources are subsets of high-entropy samples.
+\consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
 \label{tab:upper bounds}
@@
 %\fi
-
-\medskip
 \paragraph{Organization }
@@
 The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$, where the probability is over the randomness of $(\gen, \rep)$.
-If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
 \item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $r$ is pseudorandom conditioned on $p$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon_{sec}$.
@@
 Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$.
-For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(w_{j_1}, \dots, w_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
+For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
 This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
@@
 \subsection{Reusability of \consref{cons:sampling}}
-\lnote{haven't looked at this---may need work}
 The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.
-We consider a bounded $q = \poly(n)$ number of reuses.
-For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.
+Consider any $q = \poly(n)$ number of reuses.
+For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary.
+The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\label{thm:sampling} in \apref{sec:analysis sampling} (note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$).
+
   Thus, given sufficiently strong reusability we achieve the following result:
@@
 \label{thm:reusability}
-Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
+Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ is an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.
 For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
 \end{theorem}
-\begin{proof}
-The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
-The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
-Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
-\bnote{say more here?}
-\end{proof}
 
@@
 \label{def:hamming z channel}
-For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
+Let $e, c\in \zo^\gamma$ be vectors.  Let $x = \error(c, e)$ be defined as follows
+\[x_i = \begin{cases} 1 & c_i=1 \vee e_i=1\\
+0& \text{ otherwise}.\end{cases}\]
 \end{definition}
@@
 \begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\gamma$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
-} \decode(c') \neq c] \leq \delta_{code}$.
+A set $C$~(over $\zo^\gamma$) is a $(t, \delta_{code})$-Z code if there exists an efficient procedure $\decode$ such that \[\forall e \in \zo^\gamma | \weight(e)\le t, \Pr_{c\in C}[\decode(\error(c,e)) \neq c] \leq \delta_{code}.\]
 \end{definition}
-\bnote{these are quite strange.  changing them for dissertation.  update if accepted.}
 
@@
 Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.
-Let  $C\subset \zo^\gamma$ be an error-correcting code.
+Let  $C\subset \zo^\gamma$ be $(t, \delta_{code})$-Z code.
 We describe $\gen, \rep$ as follows:
@@
 Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.
+Furthermore, let $C$ be a $(t, \delta_{code})$-Z code over $\mathcal{Z}^\gamma$.
 Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
@@
 The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
-However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.
-\consref{cons:sampling} satisfies this alternative adaption as well.}
-Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.
-This was not allowed in the definition of Boyen as it would make security impossible.
+However, to provide meaningful security in the computational setting, we cannot have communication between $f_2,..., f_q$ and $D$.
+This is because $f_2,..., f_q$ are computationally unbounded and thus could break any security that only holds against computationally bounded adversaries.
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.\footnote{An alternative would be to have a single computationally bounded adversary that provides perturbation functions but does not see the original reading $w_1$ as in the definition of Boyen.
+\consref{cons:sampling} satisfies this alternative adaption as well.}  This was not allowed in the definition of Boyen as it would make security impossible.
 

### 2015-02-10 trunk/info-bounds/FuzzyExtPossibility.tex
minor edits from reviewer comments

@@
 We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
-Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor and thus the \emph{ideal} security possible from a noisy distribution.
+Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.
 
@@
 Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
-The challenge is to design information-theoretic fuzzy extractors whose security (almost) matches the fuzzy min-entropy of a distribution.
 In this work, we ask whether this challenge is inherent.
- We provide two main technical results.
+We show the following:
 \begin{itemize}
@@
 To compensate, fuzzy extractors are typically designed to work for families of physical sources.
-We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.
+We build a family of high fuzzy min-entropy sources which no fuzzy extractor can secure.
 This result emphasizes the importance of high fidelity models of high entropy sources.
@@
 Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.
-It can be thought of as measuring the ideal security of a noisy source of entropy when used for key derivation.
-This is similar to how security is measured for program obfuscation~\cite{barak2001possibility}, we discuss the connection to program obfuscation in \secref{sec:related settings}.
+Fuzzy min-entropy measures the ideal security of a noisy source of entropy when used for key derivation, similar to distributional notions of program obfuscation~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05}---we discuss the connection in \secref{sec:related settings}.
 Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).
@@
 
-\paragraph{The Challenge of Precisely Knowing a High Entropy Distribution}
+\paragraph{The Challenge of Precisely Distributional Knowledge}
 Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic.
@@
 Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors).
-Thus, the design is fixed with a partially known distribution, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.
-We call this setting \emph{distributional uncertainty}.
-We ask whether fuzzy min-entropy is sufficient in each of these settings.
+Thus, the design is fixed with a partially known distribution, and the adversary may know more about the distribution than the designer of the fuzzy extractor.
+We call this the \emph{distributional uncertainty} setting.
 
 \paragraph{The Cost of Distributional Uncertainty}
-When the distribution is $W$ is uncertain, our results are negative.   In this setting, $W$ is only known to be in family of distributions $\mathcal{W}_Z$.
+When the distribution is $W$ is uncertain, our results are negative.   In this setting, $W$ is known to be an element of a family of distributions $\mathcal{W}_Z$.
 We construct a family $\mathcal{W}_Z$ where not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.
@@
 In particular, our positive results (\corref{cor:extension to fuzz ext}) show it is possible to build a fuzzy extractor for each $W_z$, but no construction can simultaneously secure the whole family.
-Our result motivates further research into high fidelity descriptions of noisy physical sources.
+Our result motivates further research into high fidelity descriptions of noisy sources.
 
@@
 
-\bnote{compare to current constructions?}
+\paragraph{Interpreting our Results}
+Our results show that fuzzy min-entropy is sufficient for noisy key derivation if the distribution is precisely known but insufficient if the distribution is only known to come from a family.
+A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.
+Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.
+This impossibility can be overcome by the use of a short seed of uniform randomness.
+We must find an analogous relaxation to derive keys from noisy sources.
+One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.
+
 \subsection{Our Techniques}
@@
 In this computational setting, a single fuzzy extractor (or secure sketch) can simultaneously secure all possible distributions by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}.
-The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.
-This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.
-The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).
-Extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.}
+The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).}  This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.
+The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability.
+Thus, extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.
 
@@
 We compare our positive results to these characterizations in \apref{sec:corr variables}.
-To the best of our knowledge, prior results on correlated random variables are in the precise knowledge setting, we are unaware of works that consider implications of distributional uncertainty.
-
-%The definition of $\Hfuzz$ can be extended to this model (by again thinking of the adversary as choosing the value $w'$ that is most likely to lead to a success).
+To the best of our knowledge, prior results on correlated random variables are in the precise knowledge setting, we are unaware of works that consider the cost of distributional uncertainty.
 
@@
 If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = |\{i | w_i \neq w'_i\}|$ where $\mathcal{Z}$ is some alphabet.
 For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.
@@
 Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{W}_Z$ over $\mathcal{M}$ such that for each element $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
-If
+There exists a family of distributions $\mathcal{W}_Z$ over $\mathcal{M}$ such that for each element $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z)= \omega(\log n)$ such that for any $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$, if
 $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 

### 2015-02-10 trunk/constantRate/ConstCompFuzzExt-crypto.tex
did a full pass through all the sections

@@
 
-\iffalse
-
-We construct fuzzy extractors for large classes of such sources by exploiting  their structural properties in addition to their entropy guarantees.  
-We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric over a nonbinary alphabet.
-
-The information-theoretic construction supports sources in which most symbols contributes fresh entropy.
-The first computational construction has the additional feature of \emph{reusability}~(Boyen, CCS 2004), allowing multiple correlated
-
-\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of errors over a super constant size alphabet.
-
-\item \textbf{Computational}
-%By adding computational techniques we obtain constructions with additional features.  
-Our second construction is also secure when each symbol contributes fresh entropy.  
-Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).
-A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.
-Our construction is reusable if each individual reading is a supported source.
-Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.
-This construction corrects a sub-constant fraction of errors over a super constant size alphabet.
-%Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
-It corrects a sub-constant fraction of errors and supports super-constant size alphabets.
-In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.
-This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).
-
-Our third construction strengthens the class of supported sources and corrects a constant fraction of errors.
-It is secure when individual symbols have high entropy but may be arbitrarily correlated.
-This change requires a significantly larger alphabet.
-
-The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
-\end{itemize}
-\fi
-
 \medskip
@@
 It works for \emph{sparse block sources}.
-These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks.
+These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous symbols.
 It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.
@@
 \caption{Summary of new constructions.
-\consref{cons:sampling} supports the widest class of sources.
-The sources supported by the other sources are subsets of high-entropy samples.
+\consref{cons:sampling} supports the widest class of sources, including sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.
 \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
@@
 %\fi
-\paragraph{Organization }
-The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.
-We present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.
 
@@
 Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$.
-For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
+For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if $\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
 This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
@@
 
-A distribution obtained by applying short-output condensers multiple times to a single sample from a high-entropy source (e.g., via random projections) will have this property, because the outputs of the condensers will be contain fresh entropy as long as the total amount of entropy in the source is not exceeded
-(by a simple conditional entropy argument---each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as fresh entropy remains conditioned on the previous elements).
-
-\paragraph{The Construction}
+Such sources $W$ can arise naturally as a result of signal processing and discretization.
+For example, suppose we start with a high-entropy reading $x$ of some physical source, and obtain each symbol $w_i$ by applying a short-output condenser (e.g., a random projection followed by discretization) to $x$.
+Each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as there remains entropy in $x$ conditioned on the previous elements (by a simple conditional entropy argument).
+
+\paragraph{The Sample-then-Obfuscate Construction}
 The construction first chooses a random $r$ to be used as the output of the fuzzy extractor.
 It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers.
-See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
+See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce some number $\ell$ of digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
 The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.
@@
 \label{cons:sampling}
-Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples, where each $W_j$ is over $\mathcal{Z}$.
+Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $\subsetEntropy$-entropy $\eta$-samples, where each $W_j$ is over $\mathcal{Z}$.
 Let $\ell$ be a parameter, to be determined later.
@@
 \label{thm:sampling}
-Let $n$ be a security parameter, $\mathcal{Z}$ be an alphabet, and $\gamma, \subsetEntropy$, and $t$ be functions of $n$, as follows.
-Let $\mathcal{W}$ be a family of sources over $\mathcal{Z}^\gamma$ with $(\eta, \subsetEntropy)$ high-entropy samples for $\subsetEntropy = \omega(\log n)$.
+Let $n$ be a security parameter, $\mathcal{Z}$ be a constant-size alphabet, and $\gamma, \subsetEntropy$, and $t$ be functions of $n$, as follows.
+Let $\mathcal{W}$ be a family of sources over $\mathcal{Z}^\gamma$ with $\alpha$-entropy $\eta$-samples for $\subsetEntropy = \omega(\log n)$.
 Let $t$ be such that $\left(1-\frac{t}{\gamma-\eta}\right)^\eta>1/p(n)$ for some positive polynomial $p$.
-Then it there exists $\ell = \poly(n)$ such that for any
+Then there exists $\ell = \poly(n)$ such that for any
 $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $\left (\epsilon_{sec}, s_{sec}\right)$-hard with negligible error.
@@
 \paragraph{Any sublinear error-rate can be supported if most symbols in a sample contribute entropy.}
-The requirement on $t$ can be expressed as $\eta \log  \left(1-\frac{t }{\gamma-\eta}\right) = O (\log n)$. Using $\ln (1+x)\approx x$ and relying on $O$ to absorb any 
+The requirement on $t$ can be expressed (by taking the negative logarithm of both sides) as $\eta \log  \left(1-\frac{t }{\gamma-\eta}\right) = O (\log n)$.
+Using $\ln (1+x)\approx x$ and relying on $O$ to absorb any
 constant factor involved in this approximation and the switch from $\ln$ to $\log$, we get $\eta \frac{t }{\gamma-\eta} = O(\log n)$. If $t$ is sublinear in $\gamma$
@@
 Assuming $\gamma = n$, the number $t$ of errors may be any function in $o(n)$, and thus $\log |B_t| \ge t \log |Z|$ may far exceed $\Hoo(W)$.
-
-\iffalse 
-\subsection{Security of \consref{cons:sampling}}
-\label{ssec:sec cons sampling}
-In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
-With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.
-Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
-% forms a block-unguessable distribution.
-Then security essentially follows from the security of \consref{cons:first construction}.
-%follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
-%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.
-%By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
-We begin by showing that each $V_i$ is statistically close to a high entropy distribution.
-Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
-be some particular outcome.
-
-\begin{lemma}
-\label{lem:sampling works}
-Let all variables be as in \thref{thm:sampling}.
-There exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that for each $i$,
-\[
-\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
-\]
-\end{lemma}
-
-\noindent
-We can then argue that all $V_i$ simultaneously have individual entropy with good probability~(by union bound):
-\begin{corollary}
-\label{cor:samp sec}
- Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.
-Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \geq 1-\ell\epsilon_{sam}$.
-%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
-\end{corollary}
-%\begin{proof}
-%Union bound over the probability in \lemref{lem:sampling works}.
-%%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
-%\end{proof}
-
-Once all $V_i$ all simultaneously have good entropy, the adversary only sees $\perp$ as an output from the obfuscations~(with overwhelming probability).
-If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.
-
-\begin{lemma}[Proof in \apref{sec:analysis sampling}]
-\label{lem:samp unguess}
-Let all the variables be as in \thref{thm:sampling}.
-For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_{\kappa}, P))< \epsilon_{sec}$.
-\end{lemma}
-
-\subsection{Correctness of \consref{cons:sampling}}
-\label{sec:correct sampling}
-We encode the entire key in each obfuscation.
-For correctness, at least one of the repeated readings must be correct with overwhelming probability.
-Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.
-For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.
-
-\begin{lemma}[Proof in \apref{sec:analysis sampling}]
-\label{lem:sampling errors}
-Let all the variables be as in \thref{thm:sampling}.
- Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.
-\end{lemma}
-\fi
 
@@
 For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary.
-The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\label{thm:sampling} in \apref{sec:analysis sampling} (note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$).
-
-  Thus, given sufficiently strong reusability we achieve the following result:
+The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\ref{thm:sampling} in \apref{sec:analysis sampling}.
+Note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows the $i$th reading of $w$ to be chosen depending on public values $p_1,..., p_{i-1}$, as required by definition of reusability.
+
+  Thus we achieve the following result:
 
@@
 
-\iffalse
-\subsection{More errors than entropy?}
-In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.
-The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
-We assume that $\Hoo(W) = \Theta(\gamma)$.
-We are able to correct $o(\gamma)$ errors.
-This yields:
-\[
-\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
-\]
-That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.
-
-\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.
-However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.
-
-In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.
-However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability.
-For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.
-
-\fi
-
 \section{Construction for Sources with Sparse High-Entropy Marginals}
 \label{sec:cor construction}
-\lnote{stopped here; also need to reorder appendices}
-In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.
-Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.
-In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
+In this section, we consider an alternative construction that is particularly well suited to sources over large alphabets.
+It requires enough symbols individually to contain sufficient entropy, but does not require independence of symbols, or even ``fresh'' entropy from them.
+Unlike the previous construction, it tolerates a linear fraction of errors.
+However, it cannot work for small alphabets, and is not reusable.
+
+\paragraph{Sources with Sparse High-Entropy Marginals} This construction works for distributions $W=W_1, ...
+,W_\gamma$ over $\mathcal{Z}^\gamma $ in which enough symbols $W_j$ are unpredictable even after adaptive queries to equality oracles for other symbols.
+This quality of a distribution is captured in the following definition.
+
+\begin{definition}
+\label{def:block guessable}
+Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
+\begin{cases}
+1 & w_j = w_j'\\
+0 & \text{otherwise}.
+\end{cases}
+\]
+A source $W = W_1, ...
+,W_\gamma$ has $\beta$-sparse $\alpha$-entropy $q$-marginals if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
+\[
+\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
+\]
+\end{definition}
+
+We show some examples of such sources in \apref{sec:characterize}.
+In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all symbols may arbitrarily correlated) is a source with sparse high-entropy marginals~(\clref{cl:all blocks entropy}).
+
+\paragraph{The Error-Correct-and-Obfuscate Construction}
 This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.
@@
 
+As presented, \consref{cons:first construction} is not yet a computational fuzzy extractor.
+The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).
+However, we can show that $c$ looks like it has entropy to a computationally bounded adversary who knows $p$.
+Applying a randomness extractor with outputs over $\zo^\kappa$ (technically, an average-case computational randomness extractor) to $c$, and adding the extractor seed to $p$, will give us the desired fuzzy extractor.
+See \apref{sec:further defs} for the formal details.
+
 \consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
 By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
-This restriction on the distribution is captured in the following definition.
-
-\begin{definition}
-\label{def:block guessable}
-Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
-\begin{cases}
-1 & w_j = w_j'\\
-0 & \text{otherwise}.
-\end{cases}
-\]
-A source $W = W_1| ...
-|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block source} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
-\[
-\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-
-We show some examples of unguessable block sources in \apref{sec:characterize}.
-In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block source~(\clref{cl:all blocks entropy}).
-
-Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.
-The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).
-However, we can show that $c$ looks like it has entropy.
-We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
-\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
-\label{def:hill ent}
-Let $(W, S)$ be a pair of random variables.  $W$ has
-\emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
-\end{definition}
-We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).
-We call this object a computational fuzzy conductor.
-It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-\begin{definition}
-\label{def:comp fuzzy cond}
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
-\begin{itemize}
-\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
-\end{itemize}
-\end{definition}
-Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
-The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
+Therefore, our construction is secure as long as enough symbols are unpredictable even after adaptive queries to equality oracles for individual symbols, which is exactly the property satisfied by sources with sparse high-entropy marginals.
+
+The following theorem formalizes this intuition~(proof in \apref{sec:construction analysis}).
 \begin{theorem}
@@
 Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
+Let $\mathcal{W}$ be a family of sources with $\beta$-sparse $\alpha=\omega(\log n)$-entropy $q$-marginals over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
 Furthermore, let $C$ be a $(t, \delta_{code})$-Z code over $\mathcal{Z}^\gamma$.
 Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction}, followed by a $\kappa$-bit randomness extractor, is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
 \end{theorem}
 
-\subsection{More errors than entropy?}
+\paragraph{More Errors than Entropy?}
 \label{sec:discussion}
@@
 \]
-The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+The simplest type of a source with high-entropy marginals is where each symbol is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
 For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.
@@
 \label{sec:info theory cons}
-In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy for sparse block sources.
-%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
-The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks.
+The construction in this section has information-theoretic security, in contrast to only computational security of the previous two constructions.
+It requires less entropy from each symbol than the previous construction; however, it places more stringent independence requirements on the symbols.
+It tolerates a linear number of errors.
+
+\paragraph{Sparse Block Sources}
+This construction works for sources $W=W_1, ...
+,W_\gamma$ over $\mathcal{Z}^\gamma $ in which enough symbols $W_j$ contribute fresh entropy conditioned on previous symbols.
+We call this such sources \emph{sparse block sources}, weakening the notion of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), which require every symbol to contribute fresh entropy.
+
+\begin{definition}
+\label{def:partial source}
+A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-sparse block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\]
+\end{definition}
+The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, is possible to consider a sparse reverse block source~\cite{vadhan2003constructing}).
+
+\paragraph{The Condense-then-Fuzzy-Extract Construction}
+The construction first condenses entropy from each symbol of the source and then applies a fuzzy extractor to the condensed symbols.
 We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.
@@
 \noindent
-For \consref{cons:info theoretic} to be secure we need most blocks to contribute some entropy to the output.  We call this notion a partial block source.
-
-\begin{definition}
-\label{def:partial source}
-A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
-\]
-\end{definition}
-\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
-The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
-This construction is secure and it supports distributions with more errors than entropy~(proof is in~\apref{sec:info theory sec}).
-
-\begin{lemma}
-\label{lem:info theory sec}
+The following theorem shows the security of this construction (proof is in~\apref{sec:info theory sec}).
+
+\begin{theorem}
+\label{thm:info theory sec}
 %Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
+Let $\mathcal{W}$ be a family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-sparse block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
 Define $\mathcal{V}$ as the family of all distributions with min-entropy at least $\tilde{\alpha}(\gamma-\beta)$ and let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \mathcal{V}, \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
@@
 For simplicity we refer to $\gen', \rep'$ as simply a fuzzy extractor.}  Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.
-
-\end{lemma}
-
-\subsection{More errors than entropy}
-
-In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.
-The structure of a partial block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
+\end{theorem}
+
+\paragraph{More errors than entropy}
+
+We now show that \consref{cons:info theoretic} supports sparse block sources with more errors than entropy.
+The structure of a sparse block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.
 We assume that $\Hoo(W) = \Theta(\gamma)$.
@@
 \label{sec:further defs}
-In this section, we show that a computational fuzzy conductor~\defref{def:comp fuzzy cond} can be transformed to a computational fuzzy extractor~\defref{def:comp fuzzy extractor}.
+
+We first define a slightly weaker object than a computational fuzzy extractor: it outputs a key with computational entropy~(instead of a pseudorandom key).  
+We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+
+Before defining this object, we define conditional computational (``HILL''~\cite{DBLP:journals/siamcomp/HastadILL99}) entropy.
+
+\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
+\label{def:hill ent}
+Let $(W, S)$ be a pair of random variables.  $W$ has
+\emph{HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
+\end{definition}
+
+\begin{definition}
+\label{def:comp fuzzy cond}
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
+\begin{itemize}
+\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
+\end{itemize}
+\end{definition}
+
+Computational fuzzy conductors can be converted to computational fuzzy extractors (\defref{def:comp fuzzy extractor}) using standard techniques, as follows.
 The transformation uses a computational extractor.
@@
 
-\subsection{Reusability Fuzzy Extractors}
+\subsection{Reusability of Fuzzy Extractors}
 \label{sec:comparing reusability}
@@
 Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.\footnote{An alternative would be to have a single computationally bounded adversary that provides perturbation functions but does not see the original reading $w_1$ as in the definition of Boyen.
-\consref{cons:sampling} satisfies this alternative adaption as well.}  This was not allowed in the definition of Boyen as it would make security impossible.
+\consref{cons:sampling} also satisfies this alternative adaption of Boyen's definition.}  This was not allowed in the definition of Boyen, because the adversary was not split-state, and so giving $w_1$ to the adversary would make security impossible.
 
@@
 Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} (following \cite{canetti2008obfuscating,CKVW10}) from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
-As described in the Introduction, they can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}, \cite[Section 4]{lynn2004positive}, \cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}.
+As described in the Introduction, they can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}, \cite[Section 4]{lynn2004positive}, \cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis} (such a construction results in an obfuscated function that, at a few hard-to-find-inputs, differs from the original function; this change does not materially affect our results).
 
@@
 \end{definition}
-For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\gamma$ is the vector of obfuscated points.
-When we use digital lockers we denote the oracle provided to the simulator as $I_{v, r}(\cdot, \cdot)$ where $v = v_1,..., v_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
-\lnote{I am confused here -- need to understand this notation and check if we use it.}
+For notational convenience, when we use point function obfuscation, we denote the oracle $(I^1,\dots,I^\ell)$ provided to the simulator in the above definition as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\gamma$ is the vector of obfuscated points.
+When we use digital lockers, we denote the oracle  $(I^1,\dots,I^\ell)$ provided to the simulator as $I_{v, r}(\cdot, \cdot)$ where $v = v_1,..., v_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
 
@@
 \label{sec:analysis sampling}
-\iffalse
-\subsection{Security}
-The proof of security for \consref{cons:sampling} uses the definition of block unguessable sources~(\defref{def:block guessable}).
-This definition is adaptive and discussed in \apref{sec:characterize}.
-We show the security of \consref{cons:sampling}:
-\begin{itemize}
-\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
-\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
-\item The outputs $V_1,..., V_\ell$ are a block unguessable source.  This is made formal in the following corollary:
-\begin{corollary}
-\label{cor:v are unguessable}
-Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
-Take any $q=\poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block source.
-\end{corollary}
-\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable source.
-\end{itemize}
-
-\noindent
-We now present the proofs of Lemmas \ref{lem:sampling works} and \ref{lem:samp unguess}.
-
-\begin{proof}[{\large Proof of \lemref{lem:sampling works}}]
-Consider some fixed $i$.
-Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
-Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
-
-\begin{claim}
-\label{cl:vi have entropy}
+ Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
+Let $D$ be a distinguisher of size at most $s_{sec}$.
+We want to bound
 \[
-\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
+| \expe[D(R, P)] - \expe[D(U, P)]|
 \]
-\end{claim}
-\begin{proof}
-Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
-We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
-Then
-\begin{align*}
-\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
-&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
-\end{align*}
-Taking the negative logarithm of both sides we have that
-\begin{align*}
-\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
-&\ge \sum_{j_k\in J} \alpha = \alpha X
-\end{align*}
-This completes the proof of \clref{cl:vi have entropy}.
-\end{proof}
-
-We note that $X$ is distributed according to the hypergeometric distribution,
-and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
-Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
-
-\bnote{this can also be tightened.}
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
- \[
-\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
-\]
-\end{proof}
-
-\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]
-\fi
-
-\lnote{I need to check this}
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable source.
-The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .
-Let $W$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples.
-Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
-
-Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
-Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
-\[
-| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
-\]
+by a negligible function.
+
 Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
@@
 \end{cases}\]
-By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $g$ queries) such that
+By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q\le s_{sec}$ queries) such that
 \begin{align}
 \label{eq:dist before}
-|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+\left|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ik}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) \right|  \leq\ngl(n).
 \end{align}
-\lnote{why $\log |Z|$? and where did the randomness used to sample go?}
-
-We now prove $S$ cannot distinguish between $R$ and $U$.
+
+The same is true if we replaced $R$ above by and independent uniform random variable $U$ over $\zo^\kappa$. 
+We now prove the following lemma, which shows that $S$ cannot distinguish between $R$ and $U$.
+
 \begin{lemma}
 \label{lem:sim cannot distinguish samp}
-$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
+Let $U$ denote the uniform distribution over $\zo^\kappa$. Then
+\begin{align}
+\label{eq:sim cannot distinguish samp}
+\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
+- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
+\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right| \le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
+\end{align}
 \end{lemma}
@@
 \begin{proof}
-\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
-\begin{lemma}
-\label{lem:codewords in I close samp}
-Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then, \lnote{perhaps this can be tightened}
-\[
-\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le q(q+1) 2^{-\subsetEntropy}.
-\]
-\end{lemma}
-\begin{proof}
-The only information about whether the value is $r$ or $u$ is contained in the query responses.
+Fix any $u\in \zo^\kappa$ (the lemma will follow by averaging over all $u$). Let $r$ be the correct value of $R$.
+The only information about whether the value is $r$ or $u$ can obtained by $S$ through the query responses.
 First, modify $S$ slightly to quit immediately if it gets a response not equal to $\perp$ (such $S$ is equally successful at distinguishing between $r$ and $u$, because the first non-$\perp$ response suffices).
-There are $q+1$ possible values for $View(S)$ on a given input ($q$ of those views consist of some number of $\perp$ responses followed by the first non-$\perp$ response, and the one view has all $q$ responses equal to $\perp$) .
-By \lnote{cite chain rule lemma here!}, $\Hav(V_j | View(S))) \ge \subsetEntropy - \log(q+1)$ \lnote{add the randomness used to sample into here}.
-Therefore, at each query, the probability that $S$ gets non-$\perp$ answer (equivalently, guesses $V_j$) is at most $(q+1)2^{-\subsetEntropy}$.
-Since there are $q$ queries, the result follows by the union bound.
- This concludes the proof of \lemref{lem:codewords in I close samp}.
+There are $q+1$ possible values for the view of $S$ on a given input ($q$ of those views consist of some number of $\perp$ responses followed by the first non-$\perp$ response, and one view has all $q$ responses equal to $\perp$) .
+By \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(V_i | View(S), \{j_{ik}\}) \ge \Hav(V_j | \{j_{ik}\}) - \log (q+1) \ge \subsetEntropy - \log(q+1)$.
+Therefore, at each query, the probability that $S$ gets a non-$\perp$ answer (equivalently, guesses $V_i$) is at most $(q+1)2^{-\subsetEntropy}$.
+Since there are $q$ queries of $S$, the result of \lemref{lem:sim cannot distinguish samp} follows by the union bound.
+Note that  $q(q+1)/2^\subsetEntropy$ is negligible, because $q$ is polynomial and $\subsetEntropy=\omega(\log n)$.
 \end{proof}
-By averaging over all points in $\zo^\kappa$ we conclude that
-\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
-\end{proof}
-
-\noindent Now by the security of obfuscation we have that
-\begin{align}
-\label{eq:dist after}
-|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
-\begin{align*}
-\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
-&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
-&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
-&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
-&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
-\end{align*}
-This is a contradiction and completes the proof.% of \lemref{lem:samp unguess}.
-%\end{proof}
-
-%\end{proof}
-\iffalse
-\subsection{Correctness}
-\label{sec:sampling errors}
-
-%\section{Proof of \lemref{lem:sampling errors}}
-\bnote{can be tightened to $\omega(n^c \log n)$.}
-\begin{proof}[Proof of \lemref{lem:sampling errors}]
-
-Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.
-Denote by $\mu = -\frac{(c-1)\log n}{2}$ and note that $t\leq \mu(\gamma-\eta)/\eta$.
-Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.
-\begin{align*}
-\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
-&= \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
-&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
-\end{align*}
-We then have the probability that all $v_i\neq v_i'$ as:
-\begin{align*}
-\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell
-=\left( 1- \frac{1}{n^{c-1}}\right)^\ell \le \left(e^{- \frac{1}{n^{c-1}}} \right)^{\ell}
-= \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}
-\end{align*}
-(using $1+x\le e^x$). This completes the proof of \lemref{lem:sampling errors}.
-\end{proof}
-\fi
-
-\section{Analysis of \consref{cons:first construction}}
+
+Adding together Equation~\ref{eq:dist before}, Equation~\ref{eq:sim cannot distinguish samp}, and Equation~\ref{eq:dist before} in which $R$ is replaced with $U$, we obtain the desired result by the triangle inequality.\section{Analysis of \consref{cons:first construction}}
 \label{sec:construction analysis}
@@
 \defref{def:block guessable} is an inherently adaptive definition and a little unwieldy.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
-The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may reshape the distribution of block $j$.
+The majority of the difficulty in characterizing \defref{def:block guessable} is that different symbols may be dependent, so an equality query on symbol $i$ may reshape the distribution of symbol $j$.
 In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).
-We first show some sources that are unguessable block sources~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block sources~(\secref{sec:negative ex}).
+We first show some sources that have sparse high-entropy marginals~(\secref{sec:positive ex}) and then show sources with high overall entropy that do not have sparse high-entropy marginals~(\secref{sec:negative ex}).
 
@@
 \label{sec:positive ex}
-We begin with the case of independent blocks.
+We begin with the case of independent symbols.
 
@@
 Let $W = W_1,  ...
-, W_\gamma$ be a source in which all blocks $W_j$  are mutually independent.
+, W_\gamma$ be a source in which all symbols $W_j$  are mutually independent.
 Let $\alpha$ be a parameter.
-Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) \ge \alpha $.
-Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block source.
-In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block source.
+Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) \ge \alpha$.
+Then for any $q$, $W$ is a source with $(\gamma - |J|)$-sparse $(\alpha - \log (q+1))$-entropy $q$-marginals.
+In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then  $W$ is a source with $(\gamma - |J|)$-sparse $\omega(\log n)$-entropy $q$-marginals.
 \end{claim}
@@
 It suffices to show that for all $j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
-We can ignore queries for all blocks but the $j$th, as the blocks are independent.
+We can ignore queries for all symbols but the $j$th, as the symbols are independent.
 Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic ($S$ can calculate the best coins).
-Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block.
+Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th symbol.
 Each $A_k$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed).
@@
 \end{proof}
-\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
+\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for symbol-fixing sources, where each symbol is either uniform or a fixed symbol~(symbol-fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).
 \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
-However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.
+However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where symbols are not independent.
 
@@
 Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.
-If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block source.
+If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a source with  $0$-sparse $(e - \log (q+1))$-entropy $q$-marginals.
 \end{claim}
 \begin{proof}
-Since $f$ is injective on each block, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
-Consider a query $q_k$ on block $j$.
+Since $f$ is injective on each symbol, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
+Consider a query $q_k$ on symbol $j$.
 There are two possibilities: either $q_k$ is not in the image of $f_j$,  or $q_k$ can be considered a query on the preimage $f_j^{-1}(q_k)$.
@@
 Suppose that for all $j$, $\Hoo(W_j)\geq \alpha$, and that $q \le 2^{\alpha}/4$ (this holds asymptotically, in particular, if $q$ is polynomial and $\alpha$ is super-logarithmic).
-Then  $W$ is a $(q, \alpha-1-\log(q+1), 0)$-unguessable block source.
+Then  $W$ is a source with $0$-sparse $(\alpha-1-\log(q+1))$-entropy $q$-marginals.
 \end{claim}
@@
 This is not always the case.
-Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.
+Indeed it is possible for some symbols to have very high entropy but lose all of it after equality queries.
 
 \begin{claim}
-Let $p = (\poly(n))$ and let $f_1,..., f_{\gamma}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \gamma \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\gamma}), W_2 = f_2(U_{1,..., 2\gamma}),...., W_\gamma = f_\gamma(U)$.
+Let $p = (\poly(n))$ and let $f_1,..., f_{\gamma}$ be injective functions where $f_j:\zo^{j\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \gamma \times \log p$, that is the source has a small number of symbols.}  Then define the distribution $W_1 = f_1(U_{1,...,\gamma}), W_2 = f_2(U_{1,..., 2\gamma}),...., W_\gamma = f_\gamma(U)$.
 There is an adversary making $p\times \gamma = \poly(n)$ queries such that $\Hav(W | View(S^{I_W(\cdot, \cdot)})) = 0$.
@@
 
-The previous example relies on an adversaries ability to determine a block from the previous blocks.
+The previous example relies on an adversary's ability to determine a symbol from the previous symbols.
 We formalize this notion next.
-We define the entropy jump of a block source as the remaining entropy when other blocks are known:
+We define the entropy jump of a source as the remaining entropy of a symbol when previous symbols are known:
 
@@
 Let $W = W_1,..., W_\gamma$ be a source under ordering $i_1,..., i_\gamma$.
-The \emph{jump} of a block $i_j$ is $\mathtt{Jump}(i_j) = \max_{w_{i_1},..., w_{i_{j-1}}} H_0 (W_{i_j} | W_{i_1} = w_{i_1} ,..., W_{i_{j-1}} = w_{i_{j-1}})$.
+The \emph{jump} of a symbol $i_j$ is $\mathtt{Jump}(i_j) = \max_{w_{i_1},..., w_{i_{j-1}}} H_0 (W_{i_j} | W_{i_1} = w_{i_1} ,..., W_{i_{j-1}} = w_{i_{j-1}})$.
 \end{definition}
 
-If an adversary can learn blocks in succession they can eventually recover the entire secret.
-In order for a source to be block unguessable the adversary must get ``stuck'' early enough in their recovery process.
+An adversary who can learn symbols in succession  can eventually recover the entire secret.
+In order for a source to have sparse high-entropy marginals, the adversary must get ``stuck'' early enough in this recovery process.
 This translates to having a super-logarithmic jump early enough.
@@
 \begin{claim}
-Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\gamma$ such that for all $j\le \gamma-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\gamma-\beta+1)$, then $W$ is not $(q, 0, \beta)$-unguessable block source.
+Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\gamma$ such that for all $j\le \gamma-\beta +1$, $\mathtt{Jump}(i_j) = \log q /(\gamma-\beta+1)$, then $W$ is not a  source with $\beta$-sparse high-entropy $q$-marginals.
 \end{claim}
@@
 For convenience relabel the ordering that violates the condition as $1,..., \gamma$.
-We describe an unbounded adversary that determines $W_1,..., W_{\gamma-\beta+1}$.
+We describe an unbounded adversary $S$ that determines $W_1,..., W_{\gamma-\beta+1}$.
 As before $S$ queries the $q /\gamma$ possible values for $W_1$ and determines $W_1$.
@@
 
-Presenting a sufficient condition for security is more difficult as $S$ may interleave queries to different blocks.
-It seems like the optimum strategy is to focus on a single block at a time but it is unclear how to formalize this intuition.
+Presenting a sufficient condition for security is more difficult as $S$ may interleave queries to different symbols.
+It seems like the optimum strategy for $S$ is to focus on a single symbol at a time, but it is unclear how to formalize this intuition.
 
 \subsection{Security}
-Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.
-However, security is more complicated, the main difficulty is that the definition of block unguessable sources~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.
-This means we must limit our indistinguishable distribution to blocks that are difficult to guess.
+It suffices to prove that \consref{cons:first construction} is a  $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor, i.e., that $C$ has HILL entropy $H_0(C)-\beta$ conditioned on $P$.
+The final extraction step will convert it to a computational fuzzy extractor~(see \apref{sec:further defs}).
+
+Security proof of \consref{cons:first construction} is similar to the security proof of \consref{cons:sampling}.
+However, it is made more complicated by the fact that the definition of sources with sparse high-entropy marginals~(\defref{def:block guessable}) allows for certain weak symbols that can easily be guessed.
+This means we must limit our indistinguishable distribution to symbols that are difficult to guess.
 Security is proved via the following lemma:
@@
 \lnote{I need to check this}
-Let $\mathcal{O}$ be a $\gamma$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.
-Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block source.
  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$.
@@
 Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
-By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.
+By \defref{def:block guessable} there exists a set of indices $J$ such that all symbols within $J$ are unguessable.
 Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.
@@
 We now show that for any value of $c^*$ all queries on $j \in J$ return $0$ with probability $1-2^{-\alpha+1}$.
-Suppose not, that is suppose, the probability of at least one nonzero response on index $j$ is $> 2^{-(\alpha+1)}$.
+Suppose not.
+That is, suppose the probability of at least one nonzero response on index $j$ is $> 2^{-(\alpha+1)}$.
 Since $w, w'$ are independent of $r_j$, the probability of this happening when $c^*_j = 1$ is at most $q/\mathcal{Z}$ or  equivalently $2^{-\log |\mathcal{Z}|+\log q}$.
@@
 \end{align}
-We now show that for an unguessable block source the remaining entropy $\alpha\leq \log |\mathcal{Z}|-\log q $:
+We now show that for  $\alpha\leq \log |\mathcal{Z}|-\log q $:
 \begin{claim}
 \label{cl:ent bounded away from n}
-If $W$ is a $(q, \alpha, \beta)$-block unguessable source over $\mathcal{Z}$ then $\alpha \le \log |\mathcal{Z}|-\log q$.
+If $W$ is a source with $\beta$-sparse $\alpha$-entropy $q$-marginals over $\mathcal{Z}$, then $\alpha \le \log |\mathcal{Z}|-\log q$.
 \end{claim}
 \begin{proof}
-\bnote{Leo I changed some of this under you.  It wasn't clear or probably right as written.}
-Let $W$ be a $(q, \alpha, \beta)$-block unguessable source.  Let $J\subset\{1,..., \gamma\}$ the set of good indices.
+ Let $J\subset\{1,..., \gamma\}$ the set of good indices.
 It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.
@@
 Then $\sum_{i=1}^q \Pr[W_j = w_{j,i}]\geq q/|\mathcal{Z}|$.
-Suppose not, this means that there is some $w_{j,i}$ with probability $\Pr[W_j = w_{j,i}] < 1/|\mathcal{Z}|$.
+Suppose not.
+This means that there is some $w_{j,i}$ with probability $\Pr[W_j = w_{j,i}] < 1/|\mathcal{Z}|$.
 Since there are $\mathcal{Z} - q $ remaining possible values of $W_j$ for their total probability to be at least $1-q/|\mathcal{Z}|$ at least of these values has probability at least $1/\mathcal{Z}$.
@@
  When there is a $1$ response and $c_j=0$ this means that there is no remaining min-entropy.
-If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).
+If this occurs with over $2^{-\alpha}$ probability this violates the condition on $W$ (\defref{def:block guessable}).
 By the union bound over the indices $j\in J$ the total probability of a $1$ in $J$ is at most $(\gamma-\beta)2^{-\alpha+1}$.
@@
 Let all variables be as in \thref{thm:main thm first cons}.
-The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \gamma/|\mathcal{Z}| = \ngl(n)$.
+The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random symbol being interpreted as the obfuscation of the point) is $ \le \gamma/|\mathcal{Z}| = \ngl(n)$.
 \end{lemma}
@@
 \label{sec:info theory sec}
-\begin{proof}[Proof of \lemref{lem:info theory sec}]
+\begin{proof}[Proof of Theorem~\ref{thm:info theory sec}]
 Let $W\in \mathcal{W}$.
@@
 We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
-First note since $W$ is $(\alpha, \beta)$-partial block distribution that
+First note since $W$ is $(\alpha, \beta)$ sparse block source that
 there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:

### 2015-02-10 trunk/constantRate/ConstCompFuzzExt-crypto.tex
got main body into lncs format, still working on appendices

@@
+\def\shownotes{0}
+\def\blinded{1}
+\def\lncs{1}
+
+\ifnum\lncs=0
 	\documentclass[11pt]{article}
-%\documentclass{llncs}
-\def\shownotes{1}
-\def\blinded{0}
-
 	\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
@@
 	%\usepackage[parfill]{parskip}
+	\usepackage{amsthm}
+	\newtheorem{theorem}{Theorem}[section]
+	\newtheorem{lemma}[theorem]{Lemma}
+	\newtheorem{proposition}[theorem]{Proposition}
+	\newtheorem{corollary}[theorem]{Corollary}
+	\newtheorem{definition}[theorem]{Definition}
+	\newtheorem{assumption}[theorem]{Assumption}
+	\newtheorem{claim}[theorem]{Claim}
+	\newtheorem{problem}[theorem]{Problem}
+	\newtheorem{construction}[theorem]{Construction}
+
+\else
+	\documentclass[runningheads]{../Asiacrypt/llncs}
+	\newtheorem{construction}{Construction}
+\fi
+
 \usepackage{graphicx}
 \usepackage{amssymb, amsmath, amsfonts}
-\usepackage{amsthm}
 \usepackage{enumerate}
@@
 \newcommand{\distLWE}{\ensuremath{\class{dist\mbox{-}LWE}}}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
 
@@
 
-\title{Fuzzy Extractors for Noisy Sources with More Errors Than Entropy}
+\title{Fuzzy Extractors for Noisy Sources \\with More Errors Than Entropy}
 %\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
@@
 
+\ifnum\lncs=1\medskip\fi
+
 %\emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
@@
 %One is information-theoretic; the other two rely computational assumptions. They differ in the types of sources they support.
+\ifnum\lncs=1\medskip\fi
 
@@
 physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
-and quantum information~\cite{bennett1988privacy}.
+and quantum information \cite{bennett1988privacy}.
 Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
@@
 
+\begin{table}
+\begin{center}
+\ifnum\lncs=0
+\begin{tabular}{l l l l l}
+  & Source Structure & Error Rate  & Techniques\\
+\hline
+Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
+Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
+Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
+\end{tabular}
+\else
+\begin{tabular}{l l l l l}
+  & Source Structure & Error Rate  & Techniques\\
+\hline \vspace{-3mm} \\
+Construction \ref{cons:sampling} & high-entropy & any subconstant \ \ &  Sample-then-obfuscate \\
+\ \ (reusable)& \ \ samples\\ \vspace{-3mm} \\
+Construction \ref{cons:first construction}  & sparse high-entropy \ \  & constant &  Error-correct-and-obfuscate\\
+& \ \ marginals\\ \vspace{-3mm} \\
+Construction \ref{cons:info theoretic}   & sparse block source  & constant & Condense-then-fuzzy-extract\\
+\ \ (info-theoretic)\\
+\hline\end{tabular}
+\fi
+\end{center}
+%end centering
+\caption{Summary of new constructions.
+\consref{cons:sampling} supports the widest class of sources, including sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.
+\consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
+\label{tab:upper bounds}
+\end{table}
+
 \paragraph{Our Contributions: Handling More Errors than Entropy}
@@
 This construction is the first to provide reusability for a realistic class of correlated readings.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l l l l l}
-  & Source Structure & Error Rate  & Techniques\\
-\hline
-Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
-Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
-Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
-\hline\end{tabular}
-\end{center}
-%end centering
-\caption{Summary of new constructions.
-\consref{cons:sampling} supports the widest class of sources, including sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.
-\consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
-\label{tab:upper bounds}
-\end{table}
 
@@
 Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$.
-For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if $\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
+For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if
+\ifnum\lncs=0
+$\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ 
+\else
+\[
+\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy
+\]
+\fi
+for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
 This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
@@
 \begin{tabular}{c|c}
+\ifnum\lncs=0
 \begin{minipage}{3in}
+\else
+\begin{minipage}{2.3in}
+\fi
 \textbf{\gen}
@@
 \end{enumerate}
- \end{minipage} &
+ \end{minipage}\ \  &
+\ifnum\lncs=0
 \begin{minipage}{3in}
-\textbf{\rep}
+\else
+\begin{minipage}{2.2in}
+\fi
+\ \ \textbf{\rep}
 \begin{enumerate}
@@
 \end{enumerate}
-\vspace{0.37in}
+\ifnum\lncs=0
+\vspace{0.6in}
+\fi
 \end{minipage}
@@
 
-\begin{construction}
+\begin{construction}[Error-Correct-and-Obfuscate]
 \label{cons:first construction}
@@
 \begin{tabular}{c|c}
+\ifnum\lncs=0
 \begin{minipage}{3in}
+\else
+\begin{minipage}{2.25in}
+\fi
 \textbf{\gen}
@@
 \end{enumerate}
- \end{minipage} &
+ \end{minipage} \ \ &
+\ifnum\lncs=0
 \begin{minipage}{3in}
-\textbf{\rep}
+\else
+\begin{minipage}{2.25in}
+\fi
+\ \ \textbf{\rep}
 \begin{enumerate}
@@
 
+\noindent
 As presented, \consref{cons:first construction} is not yet a computational fuzzy extractor.
@@
 \[
-\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
+\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}\,.
 \]
@@
 \end{enumerate}
- \end{minipage} &
+ \end{minipage} & \ \ 
+\ifnum\lncs=0
 \begin{minipage}{3in}
-\textbf{\rep}
+\else
+\begin{minipage}{2.25in}
+\fi
+\ \ \textbf{\rep}
 \begin{enumerate}
@@
 \end{enumerate}
+\ifnum\lncs=0
 	\vspace{0.7in}
+\else
+	\vspace{0.15in}
+\fi
 \end{minipage}
@@
 
-Before defining this object, we define conditional computational (``HILL''~\cite{DBLP:journals/siamcomp/HastadILL99}) entropy.
+Before defining this object, we define conditional computational (``HILL'' \cite{DBLP:journals/siamcomp/HastadILL99}) entropy.
 
@@
 \emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
+denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S), \allowbreak (X,S))\leq \epsilon_{sec}$.
 \end{definition}
@@
 of random variables $X, Y$ (with $X$ over $\zo^\gamma$) such that
-$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{sec}}}((\cext(X; U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon_{sec}$.
+$\tilde{H}_\infty(X|Y) \ge m$, we have 
+\ifnum\lncs=0
+$
+\else
+\[
+\fi
+\delta^{\mathcal{D}_{s_{sec}}}((\cext(X; U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon_{sec}
+\ifnum\lncs=0
+$.
+\else
+\,.\]
+\fi
 \end{definition}
@@
 \item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\ifnum\lncs=0
 \[
@@
 \]
+\else
+\begin{align*}
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1]   - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | \\ < \frac{1}{p(n)} \enspace,
+\end{align*}
+\fi
 where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
@@
 Let $U$ denote the uniform distribution over $\zo^\kappa$. Then
+\ifnum\lncs=0
 \begin{align}
+\else
+\begin{eqnarray}
+\lefteqn{
+\fi
+\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
+\ifnum\lncs=1
+\right.} \nonumber \\
+& & \left.
+\fi
+- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
+\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right|
+ \le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
 \label{eq:sim cannot distinguish samp}
-\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
-- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
-\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right| \le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
+\ifnum\lncs=0
 \end{align}
+\else
+\end{eqnarray}
+\fi
 \end{lemma}
@@
 \end{proof}
-By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})) < (\gamma -\beta)2^{-(\alpha+1)}$.
+By averaging over all points in $C'$ we conclude that 
+\[
+\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})) < (\gamma -\beta)2^{-(\alpha+1)}\,.
+\]
 This completes the proof of \lemref{lem:sim cannot distinguish}.

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
put tcc rejection in crypto format

--- 2015-02-10 trunk/info-bounds/FuzzyExtPossibility.tex
@@
-\documentclass[11pt]{article}
-
+\documentclass{llncs}
+% \documentclass{llncs}
 \def\shownotes{1}
-\def\blinded{0}
-
-\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
-\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
+\def\blinded{1}
+
+%\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
+%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
 %\geometry{landscape}                % Activate for for rotated page geometry
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{definition}[theorem]{Definition}
 \newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{problem}[theorem]{Problem}
+%\newtheorem{claim}[theorem]{Claim}
+%\newtheorem{problem}[theorem]{Problem}
 \newtheorem{construction}[theorem]{Construction}
@@
 In many situations these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
-However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,gassend2002silicon,tuyls2006puf,suh2007physical,bennett1988privacy}.
+However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake}, \cite{monrose2002password,pappu2002physical,gassend2002silicon,tuyls2006puf,suh2007physical,bennett1988privacy}.
 That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.
@@
 tight bounds for specific distributions---generally the uniform distribution or
-i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
+i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining}, \cite{DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
 Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
@@
 In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.
-In \secref{sec:known distributions}, we construct a fuzzy extractor in the precise knowledge setting.
+In Section \ref{sec:known distributions}, we construct a fuzzy extractor in the precise knowledge setting.
 In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we construct families of distributions that no secure sketches and fuzzy extractors can secure, respectively~(the distributional uncertainty setting).
@@
 \begin{enumerate}
-\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
+\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then 
+\[\Pr[\rep(w', p) = \key] \geq 1-\delta.\]
 \item \emph{Security:} for any distribution $W_z\in\mathcal{W}_Z$, if $(\Key,P)\leftarrow\gen (W_z)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
@@
 \begin{enumerate}
-\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
+\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then \[\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.\]
 \item \emph{Security}: for any distribution $W_z\in\mathcal{W}_Z$, $\Hav(W_z|\sketch(W_z))\geq \tilde{m}$.
@@
 of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
-$\tilde{H}_\infty(X|Y) \ge \tilde{m}$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
-U_d \times Y) \le \epsilon$.
+$\tilde{H}_\infty(X|Y) \ge \tilde{m}$, we have \[\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
+U_d \times Y) \le \epsilon.\]
 \end{definition}
@@
 \begin{itemize}
-\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
+\item $\gen(w):$ sample $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, output $(r,p)$.
 \item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
@@
 Fuzzy min-entropy is a necessary condition for security.
-It measures the advantage provided to the adversary by allowing them to run the $\rep$ functionality.
+It measures the functionality provided to the adversary by providing $\rep$~(since $p$ is public).
 Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.
@@
 Fuzzy min-entropy represents an upper bound on the security from a noisy source.
-In the \secref{sec:related settings} computational setting there is evidence it may be possible to (nearly) achieve this upper bound.
+There is evidence it may be possible to (nearly) achieve this upper bound in the computational setting (see \secref{sec:related settings}).
 However, in the information-theoretic setting there are many distributions with fuzzy min-entropy with no known fuzzy extractor~(or corresponding impossibility result).
-We know show some properties of fuzzy min-entropy.
+We now show some properties of fuzzy min-entropy.
 \begin{lemma}
@@
 \label{sec:known distributions}
-In this section, we show it is possible to build secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) given precise knowledge of a distribution $W$ whenever $\Hfuzz(W)= \omega(\log n)$.
-We first consider flat distributions and then turn to arbitrary distributions.
+In this section, we build a secure sketch~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) for each distribution $W$ with $\Hfuzz(W) = \omega(\log n)$~(using precise knowledge of $W$).
+We begin with flat distributions and then turn to arbitrary distributions.
 
@@
 
+\noindent
 Denote the largest number of points in a ball of radius $t$ in the support of $W$ as \[\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|.\]   For flat distributions, this quantity defines the fuzzy min-entropy,
 \begin{align}
-\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
+\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right| \Pr[W=w]\right) \nonumber \\
 &= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
@@
 \begin{tabular}{c|c}
-\begin{minipage}{2.5in}
+\begin{minipage}{1.8in}
 \textbf{$\sketch_W$}
@@
 \label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
-Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
+Let $W$ be a flat with $\Hoo(W)\ge m$.  Then
 \consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
 \end{lemma}
-\begin{corollary}
-Let $n = \log |\mathcal{M}|$.
-If $|R| \ge |\beta_{t}|\cdot n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
-That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
-\end{corollary}
-
-\noindent
-\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.
+%\noindent
+%\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.
 The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$.
@@
 \item \underline{Input}: $w$.
-\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $ss=1,w$.
+\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. \\
+Set $ss=1,w$.
 \item Else
 \begin{enumerate}
-\item Find $i$ such that $\Pr[W=w]\in L_i$.
+\item Find $i$ such that \\$\Pr[W=w]\in L_i$.
 \item Sample $K\leftarrow \mathcal{K}_i$.
@@
 \item $W^* = \{w | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
-\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
+\item For $w^*\in W^*$, \\if $F_i(K, w^*) = z$, \\ output $w^*$.
 \item Output $\perp$.
@@
 The main idea is that providing the level information makes the distribution look nearly flat~(the probability of points differs by at most a factor of two).
-We can apply similar techniques to \lemref{lem:flat hashing} to show security for each nearly flat distribution.
+We can apply  techniques from \lemref{lem:flat hashing} to show security for each nearly flat distribution.
 Then, we show that providing the level information does not hurt security too much.
@@
 
-We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z)) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}$.
+We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary randomly samples $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z ) ) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}$.
 It may be possible to improve parameters by ruling out only a worst case $W$.
@@
 Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$.
-The algorithm $\sketch, \rec$ never see $Z$ only the outcome of $v\leftarrow V$.
+The algorithm $\sketch, \rec$ never see $Z$ only $ V$.
 Fix some $4\le t < \gamma$.
@@
 \textbf{Note:} There is a tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.
-By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.\bnote{it would be nice to say what our counter example says about the binary space.}
+By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
 \subsection{Implications for Computational Secure Sketches}
 \label{sec:feas comp sec sketch}
-Fuller et al.
-showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
-%This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.
-The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
+Fuller et al.~show that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.
+The definition of Fuller et al.~uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
 
@@
 \label{def:relaxed hill}
-Let $(W, S)$ be a pair of random variables.  $W$ has 
-\emph{relaxed HILL entropy} at least $\tilde{m}$ conditioned on $S$,
-denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq \tilde{m}$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq \tilde{m}$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
+$W|S$ has \emph{relaxed HILL entropy},
+denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq \tilde{m}$, if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq \tilde{m}$ and \[\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}.\]
 \end{definition}
 
-A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ to the definition, representing the distinguishing circuit).
+%A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ to the definition, representing the distinguishing circuit).
+\noindent
 By the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
@@
 Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{W}_Z$ over $\mathcal{M}$ such that for each element $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z)= \omega(\log n)$ such that for any $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$, if
-$s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-$t\ge 4$, and 
- $\epsilon_{sec} + t\delta < 1/16$,
- then $\tilde{m} <4$.
+There exists a family of distributions $\mathcal{W}_Z$ over $\mathcal{M}$ such that for each element $W_z\in \mathcal{W}_Z$, $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-secure sketch $(\sketch, \rec)$ with error $\delta$, then \[H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W | \sketch(W), Z)<4.\]
+if 
+$t \ge 4$, $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, and  $\epsilon_{sec} + t\delta < 1/16$.
 \end{corollary}
@@
 Our impossibility result says nothing about this weaker form of a secure sketch.
-Extraction from unpredictability entropy can be done using an extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}; however, in the computational setting, the obfuscated function can simply hide a randomly generated key, and therefore extraction is not necessary to obtain a fuzzy extractor.
+Extraction from unpredictability entropy can be done using an extractor with a reconstruction property~\cite{barak-computational,DBLP:conf/eurocrypt/HsiaoLR07}; however, in the computational setting, the obfuscated function can simply hide a randomly generated key, and therefore extraction is not necessary to obtain a fuzzy extractor.
 
@@
 \]
-The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$ for arbitrary $b_i$ and $a_i\neq 0$.  
-A particular distribution $W_z$ is the uniform distribution over choices of $x$.
+The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is indexed by $a_2,..., a_{n/\nu}$ and $b_2,..., b_{n/\nu}$ for arbitrary $b_i$ and $a_i\neq 0$.  
+A particular distribution $W_z$ is the uniform distribution over choices of $x$~(for a fixed $a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$).
  Define $V$ as the process of uniformly choosing $W_z\leftarrow \mathcal{W}_Z$ and then sampling from $w\leftarrow W_z$.
@@
 Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.  Adam Smith is supported in part by NSF awards 0747294 and 0941553.
+}
 
@@
 They consider all possible (randomized) transforms $T, T'$ of $W, W'$ into a new pair of variables $V,V'$.
-They show that \[|\key| \le \sup_{(V, V')\leftarrow (T(W), T'(W))}\left(  \Hoo(V | T') - \log \max_{v'\in V'} |\{v| \Pr[V=v|T' \wedge V'=v']>0\}|\right).\]  Furthermore, they show that there is a transformation that achieves a key of nearly this length.
+They show that
+\begin{align*}
+|&\key|\le\\ &\sup_{(V, V')\leftarrow (T(W), T'(W))}\left(  \Hoo(V | T') - \log \max_{v'\in V'} |\{v| \Pr[V=v|T' \wedge V'=v']>0\}|\right).
+\end{align*}
+\noindent
+Furthermore, they show that there is a transformation that achieves a key of nearly this length.
 The result is nonconstructive as there is no guidance on how to find the transforms $T, T'$.
@@
 
+\noindent
 We now argue correctness.
@@
 \begin{align*}
-\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+\Pr[\exists w^* \in W^* |w^* \neq w &\wedge F(K, w^*) = F(K, w)] \\&\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
  &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
@@
 \begin{align*}
-\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+\Pr[\exists w^* \in W^* |w^* \neq w &\wedge F(K, w^*) = F(K, w)]\\ &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
  &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|}\le \frac{\beta_{t, i}}{|R_i|} = \delta
@@
 \end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $L_I$ be the random variable of the level information (in what follows, $L_I$ takes values between $m$ and $m+n$, where possible we omit this for notational clarity).
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $L_I$ be the random variable of the level information (in what follows, $L_I$ takes values between $m$ and $m+n$, where possible we omit the range of $i$ for notational clarity).
 
@@
 \begin{align*}
-\Hfuzz(W|J=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \Pr[W=w | J=i]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t}\left( \min_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \left(\max_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)+1\\
-&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 2^{-\Hoo(W|J=i)}\right) \right)+1\\
-&= \Hoo(W|J=i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 1\right) \right)+1\\
-&=\Hoo(W|J=i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
+&\Hfuzz(W|J=i) =\\&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}} \Pr[W=w | J=i]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}}\left( \min_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}} \left(\max_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)+1\\
+&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}} 2^{-\Hoo(W|J=i)}\right) \right)+1\\
+&= \Hoo(W|J=i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i\\ \wedge \dis(w, w')\le t}} 1\right) \right)+1\\
+&=\Hoo(W|J=i)\\&-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
 &=\Hoo(W|J=i)+1-\log \beta_{t, i}.
@@
 \end{proof}
-\bnote{the reviewer is complaining that $V | \sketch(V)$ is not a distribution.  don't know why}
 \begin{lemma}
@@
 \begin{align*}
-\log \left(\frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\right)+1
+\log &\left(\frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\gamma-1}} \expe_{s\in \sketch(V)} 2^{h_s}\right)+1\\
 &=\log |\mathbb{F}| - (\gamma -1)\log (|\mathbb{F}|-1) + \log \left(\expe_{s\in \sketch(V)} 2^{h_s}\right) +1\\
@@
 \end{proof}
-
-\lnote{need for \lemref{lem:log-minus-one}:  $\gamma-1\le |F|$ and $|F|\ge 4$}
-\lnote{change the any needed theorem statements it affects in light of the tightening}
 
@@
 \begin{align*}
-\Pr[D(\Key, P, Z) = 1] &- \Pr[D(U, P, Z) =1]\\
+\Pr[&D(\Key, P, Z) = 1] - \Pr[D(U, P, Z) =1]\\
 &=(\Pr[D(\Key, P, Z) = 1| P\in A_{\epsilon}] - \Pr[D(U, P, Z) =1 | P\in A_{\epsilon}])\Pr[P\in A_{\epsilon}]\\
 &\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1 - \Pr[D_{p^*}(U, Z)=1]\right)\\
-&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \Pr[D_{p^*}(U, Z)=1 | U\in \Key_{small}]\Pr[U\in \Key_{small}] - \Pr[U\not\in \Key_{small}]\right)\\
-&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \left(\left(\frac{1}{|\Key_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in \Key_{small}]\right) - \Pr[U\not\in \Key_{small}]\right)\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] (1- \Pr[D_{p^*}(U, Z)=1 | U\in \Key_{small}]\Pr[U\in \Key_{small}] \\&- \Pr[U\not\in \Key_{small}])\\
+&\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] (1- \left(\left(\frac{1}{|\Key_{small}|}+\frac{1}{2^\nu}\right)\Pr[U\in \Key_{small}]\right) \\&- \Pr[U\not\in \Key_{small}])\\
 &\ge \sum_{p^*\in A_{\epsilon}} \Pr[P=p^*] \left(1- \frac{1}{2^{\nu}} -\frac{1}{2}\Pr[U\in \Key_{small}] - \Pr[U\not \in \Key_{small}]\right)\\

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
put tcc rejection in crypto format

@@
-\documentclass{llncs}
-% \documentclass{llncs}
-\def\shownotes{1}
+\def\shownotes{0}
 \def\blinded{1}
-
-%\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
-%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
+\def\lncs{1}
+
+\ifnum\lncs=0
+	\documentclass[11pt]{article}
+	\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
+	\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
 	%\geometry{landscape}                % Activate for for rotated page geometry
 	%\usepackage[parfill]{parskip}
+	\usepackage{amsthm}
+	\newtheorem{theorem}{Theorem}[section]
+	\newtheorem{lemma}[theorem]{Lemma}
+	\newtheorem{proposition}[theorem]{Proposition}
+	\newtheorem{corollary}[theorem]{Corollary}
+	\newtheorem{definition}[theorem]{Definition}
+	\newtheorem{assumption}[theorem]{Assumption}
+	\newtheorem{claim}[theorem]{Claim}
+	\newtheorem{problem}[theorem]{Problem}
+	\newtheorem{construction}[theorem]{Construction}
+
+\else
+	\documentclass[runningheads]{llncs}
+	\newtheorem{construction}{Construction}
+\fi
+
 \usepackage{graphicx}
@@
 %\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
+%\newtheorem{construction}[theorem]{Construction}
 
@@
 \label{lem:fuzz can't get key}
-Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(\Key, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
+Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information theoretic distinguisher between $(\Key, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
 \end{lemma}

### 2015-02-11 trunk/constantRate/ConstCompFuzzExt-crypto.tex
minor edits to grammar

@@
 \caption{Summary of new constructions.
-\consref{cons:sampling} supports the widest class of sources, including sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.
+\consref{cons:sampling} supports the widest class of sources, including the sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.
 \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
@@
 We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with sparse high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed.
-In this construction, we use single symbols of $w$ for locking up bits of a secret that we then transform into $r$.
+In this construction, we use single symbols of $w$ to lock up bits of a secret that we then transform into $r$.
 This construction tolerates a higher error rate than the first construction, but over a larger alphabet, where errors may be more likely.
@@
 These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous symbols.
-It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.
+It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies a standard fuzzy extractor to the resulting string.
 
@@
 If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.
-We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.
+We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = |\{i | x_i \neq y_i\}|$.
 For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.
@@
 for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
-This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
+\bnote{there is no probabilistic guarantee here} This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
 However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.
@@
 We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-
 Before defining this object, we define conditional computational (``HILL'' \cite{DBLP:journals/siamcomp/HastadILL99}) entropy.

### 2015-02-11 constantRate/ConstCompFuzzExt-crypto.tex
put into Springer style

@@
 	%\usepackage[parfill]{parskip}
+	\usepackage{amsthm}
+	\newtheorem{theorem}{Theorem}[section]
+	\newtheorem{lemma}[theorem]{Lemma}
+	\newtheorem{proposition}[theorem]{Proposition}
+	\newtheorem{corollary}[theorem]{Corollary}
+	\newtheorem{definition}[theorem]{Definition}
+	\newtheorem{assumption}[theorem]{Assumption}
+	\newtheorem{claim}[theorem]{Claim}
+	\newtheorem{problem}[theorem]{Problem}
+	\newtheorem{construction}[theorem]{Construction}
+
+\else
+	\documentclass[runningheads]{../Asiacrypt/llncs}
+	\newtheorem{construction}{Construction}
+	\renewcommand{\paragraph}[1]{\subsubsection{#1}}
+\fi
+
 \usepackage{graphicx}
 \usepackage{amssymb, amsmath, amsfonts}
-\usepackage{amsthm}
 \usepackage{enumerate}
@@
 By relying on computational security, we construct the first reusable fuzzy extractors that make no assumption about how multiple readings of the source are correlated.
-
-\iffalse
-
-We construct fuzzy extractors for large classes of such sources by exploiting  their structural properties in addition to their entropy guarantees.  
-We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric over a nonbinary alphabet.
-
-The information-theoretic construction supports sources in which most symbols contributes fresh entropy.
-The first computational construction has the additional feature of \emph{reusability}~(Boyen, CCS 2004), allowing multiple correlated
-
-\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of errors over a super constant size alphabet.
-
-\item \textbf{Computational}
-%By adding computational techniques we obtain constructions with additional features.  
-Our second construction is also secure when each symbol contributes fresh entropy.  
-Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).
-A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.
-Our construction is reusable if each individual reading is a supported source.
-Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.
-This construction corrects a sub-constant fraction of errors over a super constant size alphabet.
-%Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols.
-It corrects a sub-constant fraction of errors and supports super-constant size alphabets.
-In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.
-This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).
-
-Our third construction strengthens the class of supported sources and corrects a constant fraction of errors.
-It is secure when individual symbols have high entropy but may be arbitrarily correlated.
-This change requires a significantly larger alphabet.
-
-The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
-\end{itemize}
-\fi
 
@@
 
+\begin{table}
+\begin{center}
+\ifnum\lncs=0
+\begin{tabular}{l l l l l}
+  & Source Structure & Error Rate  & Techniques\\
+\hline
+Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
+Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
+Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
+\end{tabular}
+\else
+\begin{tabular}{l l l l l}
+  & Source Structure & Error Rate  & Techniques\\
+\hline \vspace{-3mm} \\
+Construction \ref{cons:sampling} & high-entropy & any subconstant \ \ &  Sample-then-obfuscate \\
+\ \ (reusable)& \ \ samples\\ \vspace{-3mm} \\
+Construction \ref{cons:first construction}  & sparse high-entropy \ \  & constant &  Error-correct-and-obfuscate\\
+& \ \ marginals\\ \vspace{-3mm} \\
+Construction \ref{cons:info theoretic}   & sparse block source  & constant & Condense-then-fuzzy-extract\\
+\ \ (info-theoretic)\\
+\hline\end{tabular}
+\fi
+\end{center}
+%end centering
+\caption{Summary of new constructions.
+\consref{cons:sampling} supports the widest class of sources, including the sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.
+\consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
+\label{tab:upper bounds}
+\end{table}
+
 \paragraph{Our Contributions: Handling More Errors than Entropy}
@@
 It works for \emph{sparse block sources}.
-These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks.
-It uses symbols-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.
+These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous symbols.
+It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies a standard fuzzy extractor to the resulting string.
 
@@
 This construction is the first to provide reusability for a realistic class of correlated readings.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l l l l l}
-  & Source Structure & Error Rate  & Techniques\\
-\hline
-Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
-Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
-Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
-\hline\end{tabular}
-\end{center}
-%end centering
-\caption{Summary of new constructions.  }
-\label{tab:upper bounds}
-\end{table}
 
@@
 
-It is seems plausible that in the real world (without random oracles), specific cryptographic hash functions, if used in this construction, will provide the necessary security~\cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}.
+It is seems plausible that in the standard model (without random oracles), specific cryptographic hash functions, if used in this construction, will provide the necessary security~\cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}.
 Moreover, Bitansky and Canetti~\cite{bitansky2010strong}, building on the work of~\cite{canetti2008obfuscating,CKVW10}, show how to obtain composable digital lockers based on a strong version of the Decisional Diffie-Hellman assumption without random oracles.
@@
 %\fi
-
-\medskip
-\paragraph{Organization }
-The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.
-We present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.
 
@@
 Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$.
-For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(w_{j_1}, \dots, w_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
+For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if
+\ifnum\lncs=0
+$\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ 
+\else
+\[
+\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy
+\]
+\fi
+for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$.
 This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$.
-However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.
-
-A distribution obtained by applying short-output condensers multiple times to a single sample from a high-entropy source (e.g., via random projections) will have this property, because the outputs of the condensers will be contain fresh entropy as long as the total amount of entropy in the source is not exceeded
-(by a simple conditional entropy argument---each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as fresh entropy remains conditioned on the previous elements).
-
-\paragraph{The Construction}
+However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate (since the property has to hold only on  average for random $j_1, \dots, j_\eta$, a sufficiently small fraction of low-entropy symbols in $W$ can be tolerated).
+
+Such sources $W$ can arise naturally as a result of signal processing and discretization.
+For example, suppose we start with a high-entropy reading $x$ of some physical source, and obtain each symbol $w_i$ by applying a short-output condenser (e.g., a random projection followed by discretization) to $x$.
+Each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as there remains entropy in $x$ conditioned on the previous elements (by a simple conditional entropy argument).
+
+\paragraph{The Sample-then-Obfuscate Construction}
 The construction first chooses a random $r$ to be used as the output of the fuzzy extractor.
 It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers.
-See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
+See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce some number $\ell$ of digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively.
 The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.
@@
 \begin{definition}
-Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.
-Then a set $C$~(over $\zo^\gamma$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t.
-} \decode(c') \neq c] \leq \delta_{code}$.
+A set $C$~(over $\zo^\gamma$) is a $(t, \delta_{code})$-Z code if there exists an efficient procedure $\decode$ such that \[\forall e \in \zo^\gamma | \weight(e)\le t, \Pr_{c\in C}[\decode(\error(c,e)) \neq c] \leq \delta_{code}.\]
 \end{definition}
-\bnote{these are quite strange.  changing them for dissertation.  update if accepted.}
-
-\begin{construction}
+
+\begin{construction}[Error-Correct-and-Obfuscate]
 \label{cons:first construction}
@@
 
+\noindent
+As presented, \consref{cons:first construction} is not yet a computational fuzzy extractor.
+The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).
+However, we can show that $c$ looks like it has entropy to a computationally bounded adversary who knows $p$.
+Applying a randomness extractor with outputs over $\zo^\kappa$ (technically, an average-case computational randomness extractor) to $c$, and adding the extractor seed to $p$, will give us the desired fuzzy extractor.
+See \apref{sec:further defs} for the formal details.
+
 \consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.
 By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.
-Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols.
-This restriction on the distribution is captured in the following definition.
-
-\begin{definition}
-\label{def:block guessable}
-Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
-\begin{cases}
-1 & w_j = w_j'\\
-0 & \text{otherwise}.
-\end{cases}
-\]
-A source $W = W_1| ...
-|W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block source} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
-\[
-\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
-\]
-\end{definition}
-
-We show some examples of unguessable block sources in \apref{sec:characterize}.
-In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block source~(\clref{cl:all blocks entropy}).
-
-Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.
-The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).
-However, we can show that $c$ looks like it has entropy.
-We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
-\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
-\label{def:hill ent}
-Let $(W, S)$ be a pair of random variables.  $W$ has
-\emph{HILL entropy} at least $k$ conditioned on $S$,
-denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
-\end{definition}
-We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).
-We call this object a computational fuzzy conductor.
-It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-\begin{definition}
-\label{def:comp fuzzy cond}
-A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
-\begin{itemize}
-\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
-\end{itemize}
-\end{definition}
-Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
-The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
+Therefore, our construction is secure as long as enough symbols are unpredictable even after adaptive queries to equality oracles for individual symbols, which is exactly the property satisfied by sources with sparse high-entropy marginals.
+
+The following theorem formalizes this intuition~(proof in \apref{sec:construction analysis}).
 \begin{theorem}
@@
 Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
-Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
-Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.
+Let $\mathcal{W}$ be a family of sources with $\beta$-sparse $\alpha=\omega(\log n)$-entropy $q$-marginals over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.
+Furthermore, let $C$ be a $(t, \delta_{code})$-Z code over $\mathcal{Z}^\gamma$.
 Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs.
-Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
+Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction}, followed by a $\kappa$-bit randomness extractor, is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
 \end{theorem}
 
-\subsection{More errors than entropy?}
+\paragraph{More Errors than Entropy?}
 \label{sec:discussion}
@@
 \[
-\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
+\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}\,.
 \]
-The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
+The simplest type of a source with high-entropy marginals is where each symbol is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).
 For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.
@@
 \noindent
-For \consref{cons:info theoretic} to be secure we need most blocks to contribute some entropy to the output.  We call this notion a partial block source.
-
-\begin{definition}
-\label{def:partial source}
-A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
-\]
-\end{definition}
-\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.
-The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).
-This construction is secure and it supports distributions with more errors than entropy~(proof is in~\apref{sec:info theory sec}).
-
-\begin{lemma}
-\label{lem:info theory sec}
+The following theorem shows the security of this construction (proof is in \apref{sec:info theory sec}).
+
+\begin{theorem}
+\label{thm:info theory sec}
 %Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
-Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
+Let $\mathcal{W}$ be a family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-sparse block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.
 Define $\mathcal{V}$ as the family of all distributions with min-entropy at least $\tilde{\alpha}(\gamma-\beta)$ and let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \mathcal{V}, \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).
@@
 \label{sec:further defs}
-In this section, we show that a computational fuzzy conductor~\defref{def:comp fuzzy cond} can be transformed to a computational fuzzy extractor~\defref{def:comp fuzzy extractor}.
+
+We first define a slightly weaker object than a computational fuzzy extractor: it outputs a key with computational entropy~(instead of a pseudorandom key).  
+We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
+Before defining this object, we define conditional computational (``HILL'' \cite{DBLP:journals/siamcomp/HastadILL99}) entropy.
+
+\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
+\label{def:hill ent}
+Let $(W, S)$ be a pair of random variables.  $W$ has
+\emph{HILL entropy} at least $k$ conditioned on $S$,
+denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S), \allowbreak (X,S))\leq \epsilon_{sec}$.
+\end{definition}
+
+\begin{definition}
+\label{def:comp fuzzy cond}
+A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
+\begin{itemize}
+\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
+\end{itemize}
+\end{definition}
+
+Computational fuzzy conductors can be converted to computational fuzzy extractors (\defref{def:comp fuzzy extractor}) using standard techniques, as follows.
 The transformation uses a computational extractor.
@@
 The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
-However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.
-\consref{cons:sampling} satisfies this alternative adaption as well.}
-Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.
-This was not allowed in the definition of Boyen as it would make security impossible.
+However, to provide meaningful security in the computational setting, we cannot have communication between $f_2,..., f_q$ and $D$.
+This is because $f_2,..., f_q$ are computationally unbounded and thus could break any security that only holds against computationally bounded adversaries.
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.\footnote{An alternative would be to have a single computationally bounded adversary that provides perturbation functions but does not see the original reading $w_1$ as in the definition of Boyen.
+\consref{cons:sampling} also satisfies this alternative adaption of Boyen's definition.}  This was not allowed in the definition of Boyen, because the adversary was not split-state, and so giving $w_1$ to the adversary would make security impossible.
 
@@
 \label{sec:analysis sampling}
-\iffalse
-\subsection{Security}
-The proof of security for \consref{cons:sampling} uses the definition of block unguessable sources~(\defref{def:block guessable}).
-This definition is adaptive and discussed in \apref{sec:characterize}.
-We show the security of \consref{cons:sampling}:
-\begin{itemize}
-\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
-\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
-\item The outputs $V_1,..., V_\ell$ are a block unguessable source.  This is made formal in the following corollary:
-\begin{corollary}
-\label{cor:v are unguessable}
-Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}.
-Take any $q=\poly(n)$.
-For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block source.
-\end{corollary}
-\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable source.
-\end{itemize}
-
-\noindent
-We now present the proofs of Lemmas \ref{lem:sampling works} and \ref{lem:samp unguess}.
-
-\begin{proof}[{\large Proof of \lemref{lem:sampling works}}]
-Consider some fixed $i$.
-Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.
-Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$.
-Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.
-
-\begin{claim}
-\label{cl:vi have entropy}
-\[
-\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
+ Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
+Let $D$ be a distinguisher of size at most $s_{sec}$.
+We want to bound
+\[
+| \expe[D(R, P)] - \expe[D(U, P)]|
 \]
-\end{claim}
-\begin{proof}
-Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.
-We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.
-Then
-\begin{align*}
-\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
-&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
-&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
-\end{align*}
-Taking the negative logarithm of both sides we have that
-\begin{align*}
-\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
-&\ge \sum_{j_k\in J} \alpha = \alpha X
-\end{align*}
-This completes the proof of \clref{cl:vi have entropy}.
-\end{proof}
-
-We note that $X$ is distributed according to the hypergeometric distribution,
-and that $\expe[X]=\eta(\gamma-\beta)/\gamma$.
-Using the tail bounds from~\cite{chvatal1979tail,scala2009hypergeometric}, we can conclude that $\Pr[X\le \expe[X]/2]\le e^{-2((\gamma-\beta)/2\gamma)^2 \eta}=O(e^{-\eta})$.
-
-\bnote{this can also be tightened.}
-Thus, setting $\alpha'=\frac{\alpha \eta(\gamma-\beta)}{2\gamma}$ and applying \clref{cl:vi have entropy}, we conclude that
- \[
-\Pr[\Hoo(V_i ) \geq \alpha'] \geq 1- O(e^{-\eta}).
-\]
-\end{proof}
-
-\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]
-\fi
-
-\lnote{I need to check this}
-Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable source.
-The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .
-Let $W$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples.
-Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
-
-Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
-Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
-\[
-| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
-\]
+by a negligible function.
+
 Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
@@
 \end{cases}\]
-By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $g$ queries) such that
+By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q\le s_{sec}$ queries) such that
 \begin{align}
-\label{eq:dist before}
-|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
+\label{eq:dist before sampling}
+\left|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ik}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) \right|  \leq\ngl(n).
 \end{align}
-\lnote{why $\log |Z|$? and where did the randomness used to sample go?}
-
-We now prove $S$ cannot distinguish between $R$ and $U$.
+
+The same is true if we replaced $R$ above by and independent uniform random variable $U$ over $\zo^\kappa$. 
+We now prove the following lemma, which shows that $S$ cannot distinguish between $R$ and $U$.
+
 \begin{lemma}
 \label{lem:sim cannot distinguish samp}
-$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
+Let $U$ denote the uniform distribution over $\zo^\kappa$. Then
+\ifnum\lncs=0
+\begin{align}
+\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
+- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
+\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right|
+\le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
+\label{eq:sim cannot distinguish samp}
+\end{align}
+\else
+\begin{eqnarray}
+\lefteqn{
+\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
+\right.} \nonumber \\
+& & \left.
+- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
+\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right|
+\le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
+\label{eq:sim cannot distinguish samp}
+\end{eqnarray}
+\fi
+
 \end{lemma}
@@
 \begin{proof}
-\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
-\begin{lemma}
-\label{lem:codewords in I close samp}
-Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then, \lnote{perhaps this can be tightened}
-\[
-\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le q(q+1) 2^{-\subsetEntropy}.
-\]
-\end{lemma}
-\begin{proof}
-The only information about whether the value is $r$ or $u$ is contained in the query responses.
+Fix any $u\in \zo^\kappa$ (the lemma will follow by averaging over all $u$). Let $r$ be the correct value of $R$.
+The only information about whether the value is $r$ or $u$ can obtained by $S$ through the query responses.
 First, modify $S$ slightly to quit immediately if it gets a response not equal to $\perp$ (such $S$ is equally successful at distinguishing between $r$ and $u$, because the first non-$\perp$ response suffices).
-There are $q+1$ possible values for $View(S)$ on a given input ($q$ of those views consist of some number of $\perp$ responses followed by the first non-$\perp$ response, and the one view has all $q$ responses equal to $\perp$) .
-By \lnote{cite chain rule lemma here!}, $\Hav(V_j | View(S))) \ge \subsetEntropy - \log(q+1)$ \lnote{add the randomness used to sample into here}.
-Therefore, at each query, the probability that $S$ gets non-$\perp$ answer (equivalently, guesses $V_j$) is at most $(q+1)2^{-\subsetEntropy}$.
-Since there are $q$ queries, the result follows by the union bound.
- This concludes the proof of \lemref{lem:codewords in I close samp}.
+There are $q+1$ possible values for the view of $S$ on a given input ($q$ of those views consist of some number of $\perp$ responses followed by the first non-$\perp$ response, and one view has all $q$ responses equal to $\perp$) .
+By \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(V_i | View(S), \{j_{ik}\}) \ge \Hav(V_j | \{j_{ik}\}) - \log (q+1) \ge \subsetEntropy - \log(q+1)$.
+Therefore, at each query, the probability that $S$ gets a non-$\perp$ answer (equivalently, guesses $V_i$) is at most $(q+1)2^{-\subsetEntropy}$.
+Since there are $q$ queries of $S$, the result of \lemref{lem:sim cannot distinguish samp} follows by the union bound.
+Note that  $q(q+1)/2^\subsetEntropy$ is negligible, because $q$ is polynomial and $\subsetEntropy=\omega(\log n)$.
 \end{proof}
-By averaging over all points in $\zo^\kappa$ we conclude that
-\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
-\end{proof}
-
-\noindent Now by the security of obfuscation we have that
-\begin{align}
-\label{eq:dist after}
-|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
-\end{align}
-Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
-\begin{align*}
-\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
-&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
-&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
-&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
-&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
-\end{align*}
-This is a contradiction and completes the proof.% of \lemref{lem:samp unguess}.
-%\end{proof}
-
-%\end{proof}
-\iffalse
-\subsection{Correctness}
-\label{sec:sampling errors}
-
-%\section{Proof of \lemref{lem:sampling errors}}
-\bnote{can be tightened to $\omega(n^c \log n)$.}
-\begin{proof}[Proof of \lemref{lem:sampling errors}]
-
-Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.
-Denote by $\mu = -\frac{(c-1)\log n}{2}$ and note that $t\leq \mu(\gamma-\eta)/\eta$.
-Since $\eta = \omega(\log n)$, we will assume
-$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.
-\begin{align*}
-\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
-&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-j}\right)\\
-&= \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
-&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
-&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
-\end{align*}
-We then have the probability that all $v_i\neq v_i'$ as:
-\begin{align*}
-\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell
-=\left( 1- \frac{1}{n^{c-1}}\right)^\ell \le \left(e^{- \frac{1}{n^{c-1}}} \right)^{\ell}
-= \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}
-\end{align*}
-(using $1+x\le e^x$). This completes the proof of \lemref{lem:sampling errors}.
-\end{proof}
-\fi
-
-\section{Analysis of \consref{cons:first construction}}
+
+Adding together Equation~\ref{eq:dist before sampling}, Equation~\ref{eq:sim cannot distinguish samp}, and Equation~\ref{eq:dist before sampling} in which $R$ is replaced with $U$, we obtain the desired result by the triangle inequality.\section{Analysis of \consref{cons:first construction}}
 \label{sec:construction analysis}
@@
 \defref{def:block guessable} is an inherently adaptive definition and a little unwieldy.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
-The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may reshape the distribution of block $j$.
+The majority of the difficulty in characterizing \defref{def:block guessable} is that different symbols may be dependent, so an equality query on symbol $i$ may reshape the distribution of symbol $j$.
 In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).
-We first show some sources that are unguessable block sources~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block sources~(\secref{sec:negative ex}).
+We first show some sources that have sparse high-entropy marginals
+\ifnum\lncs=0
+(\secref{sec:positive ex})
+\fi
+and then show sources with high overall entropy that do not have sparse high-entropy marginals
+\ifnum\lncs=0
+(\secref{sec:negative ex}).
+\fi
 
@@
 Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.
-If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block source.
+If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a source with  $0$-sparse $(e - \log (q+1))$-entropy $q$-marginals.
 \end{claim}
 \begin{proof}
-Since $f$ is injective on each block, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.
-Consider a query $q_k$ on block $j$.
+Since $f$ is injective on each symbol, 
+\ifnum\lncs=0
+$
+\else
+\[
+\fi
+\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))
+\ifnum\lncs=0
+$.  
+\else
+\,.\]
+\fi
+Consider a query $q_k$ on symbol $j$.
 There are two possibilities: either $q_k$ is not in the image of $f_j$,  or $q_k$ can be considered a query on the preimage $f_j^{-1}(q_k)$.
@@
 \Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0 \vee A_k\neq 0] & = 
-\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0]+\Pr[A_1=\dots = A_{k-1}=0 \wedge A_k=1]\\
-& \le  (k-1)2^{1-\alpha}+\Pr[A_k=1\,|\,A_1=\dots = A_{k-1}=0]\\
+\Pr[A_1\neq 0 \vee \dots \vee A_{k-1}\neq 0] \\
+&\ \ \ \ +\Pr[A_1=\dots = A_{k-1}=0 \wedge A_k=1]\\
+& \le  (k-1)2^{1-\alpha}\\
+& \ \ \ \ +\Pr[A_k=1\,|\,A_1=\dots = A_{k-1}=0]\\
 & \le  (k-1)2^{1-\alpha}+\max_j 2^{-\Hoo(W_j | A_1=\dots =A_{k-1}=0)}\\
@@
  we know $\Hoo(W_j | A_1= \dots= A_q=0) \ge \alpha-1$.  Finally this means that
+
+\ifnum\lncs=0
 \begin{align*}
@@
 \end{align*}
+\else
+\begin{align*}
+\Hav(W_j | A_1,\dots, A_q) &\ge -\log ( 2^{-\Hoo(W_j | A_1= \dots= A_q=0)}\Pr[A_1=\dots=A_q=0]\\ &\ \ \ \ \ \ \ \ \ \ \ \  +1\cdot \Pr[A_1\neq 0 \vee \dots \vee  A_q\neq 0] )\\
+& \ge -\log \left(  2^{-\Hoo(W_j | A_1= \dots= A_q=0)}+q2^{1-\alpha} \right)\\
+& \ge -\log \left(  (q+1) 2^{1-\alpha}\right) = \alpha-1-\log(q+1)\,.
+\end{align*}
+\fi
+
 \end{proof}
@@
 \begin{align}
-\label{eq:dist before}
+\label{eq:dist before marginals}
 |\expe [D(P_1,..., P_\gamma, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\gamma \log |Z|})] |\leq \epsilon_{sec}/3.
@@
 \begin{align}
-\label{eq:dist after}
+\label{eq:dist after marginals}
 |\expe [D(P_1,..., P_\gamma, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C', 1^{\gamma \log |Z|})] |\leq \epsilon_{sec}/3.
 \end{align}
-Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
+Combining Equations~\ref{eq:dist before marginals} and~\ref{eq:dist after marginals} and \lemref{lem:sim cannot distinguish}, we have
 \begin{align*}
@@
 and since $(seed_1,..., seed_{j_1})$ are independent of these values
-\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\]
-consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
+\ifnum\lncs=0
+\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\,.\]
+\else
+\begin{align*}
+(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}}\\ (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\,.
+\end{align*}
+\fi
+Consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
 Applying a deterministic function does not increase statistical distance and thus,

### 2015-02-11 trunk/constantRate/ConstCompFuzzExt-crypto-full.tex
adding version for crypto with appendices pulled forward

--- 2015-02-11 constantRate/ConstCompFuzzExt-crypto.tex
@@
 
-\subsubsection{Reusable Fuzzy Extractors}
+\subsection{Reusable Fuzzy Extractors}
 \label{sec:reusable}
@@
 
-We modify the definition of Boyen~\cite[Definition 6]{Boyen2004} for the computational setting.  We discuss the our definition and definitions due to Boyen in \apref{sec:comparing reusability}.
+We modify the definition of Boyen~\cite[Definition 6]{Boyen2004} for the computational setting.  We first present our definition and then compare to the definitions of Boyen.
 
@@
 
+\paragraph{Comparison with the definition of Boyen}
+Boyen considers two versions of reusable fuzzy extractors, first where the adversary sees $p_1,..., p_q$~(outsider security~\cite[Definition 6]{Boyen2004}) and tries to learn about the values $w_1,..., w_q$ or the keys $r_1,..., r_q$.
+Second, where the adversary controls some subset of the servers and can key generation on arbitrary $p_i'$~(insider security~\cite[Definition 7]{Boyen2004}).
+This allows the adversary to learn a subset of keys $r_i$~(by performing key generation on the valid $p_i$).
+This definition makes sense when servers are compromised~(after enrollment) and act maliciously.
+In both definitions, the adversary creates a perturbation function $f_i$ after seeing $p_1,..., p_{i-1}$~(and generated keys for outsider security) and the challenger generates $w_i = f_i(w_1)$.
+The definition is parameterized by the class of allowed perturbation functions.
+
+Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the perturbation family is a transitive isometric permutation groups.
+Boyen transforms this construction to insider security using random oracles.
+%In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.
+
+Insider security strengthens outsider security in two ways.
+First, it allows the adversary to see some subset of keys, second it allows the adversary to perform key generation on arbitrary $p_i$.
+This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.
+Robust fuzzy extractors provide security against modified $p$.
+In this work, we show reusability when $r_i$ are observed but do not handle the issue of robustness.
+That is, we assume keys may be exposed but servers keep honest state.
+Our definition lies between outsider and insider security.
+
+The definition of Boyen considers a single adversary.
+\defref{def:outsider fuzz ext} splits the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
+The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
+However, to provide meaningful security in the computational setting, we cannot have communication between $f_2,..., f_q$ and $D$.
+This is because $f_2,..., f_q$ are computationally unbounded and thus could break any security that only holds against computationally bounded adversaries.
+Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.\footnote{An alternative would be to have a single computationally bounded adversary that provides perturbation functions but does not see the original reading $w_1$ as in the definition of Boyen.
+\consref{cons:sampling} also satisfies this alternative adaption of Boyen's definition.}  This was not allowed in the definition of Boyen, because the adversary was not split-state, and so giving $w_1$ to the adversary would make security impossible.
+
+%Finally, we allow the distinguishing adversary to see other keys \lnote{we do?
+then why do we call our definition ``outsider''?}.
+This is strictly stronger than the definition of Boyen \lnote{you mean than the outsider security definition of Boyen?}.
+However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
+This \lnote{what is ``this''?} is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
+Our reusable construction~(\consref{cons:sampling}) is not insider secure \lnote{according to Boyen's notion, right?
+Why not say ``not robust'' and/or clarify that $r_i$ can leak but $p_i$ cannot be modified.}.
 \subsection{Obfuscation}
@@
 This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at a polynomial number of oracle queries to the function.
-VGB obfuscators for point functions and digital lockers are constructible from specific number-theoretic assumptions or by strong assumptions on hash functions.
-We provide more details and a formal definition in \apref{sec:obfuscation def}.
+In addition, we require that the obfuscation is composable and secure with respect to auxiliary input.
+
+Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} (following \cite{canetti2008obfuscating,CKVW10}) from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
+As described in the Introduction, they can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}, \cite[Section 4]{lynn2004positive}, \cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis} (such a construction results in an obfuscated function that, at a few hard-to-find-inputs, differs from the original function; this change does not materially affect our results).
+
+\begin{definition}[composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
+\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
+\begin{enumerate}
+\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.\lnote{imperfect correctness allowed?
+It's need for the RO construction.}
+\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
+\ifnum\lncs=0
+\[
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
+\]
+\else
+\begin{align*}
+|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1]   - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | \\ < \frac{1}{p(n)} \enspace,
+\end{align*}
+\fi
+where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
+\end{enumerate}
+\end{definition}
+For notational convenience, when we use point function obfuscation, we denote the oracle $(I^1,\dots,I^\ell)$ provided to the simulator in the above definition as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\gamma$ is the vector of obfuscated points.
+When we use digital lockers, we denote the oracle  $(I^1,\dots,I^\ell)$ provided to the simulator as $I_{v, r}(\cdot, \cdot)$ where $v = v_1,..., v_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
 
@@
 
- Correctness follows immediately: for any given $i$, the probability that $v'_i=v_i$ is at least $1/p(n)$.
+\begin{proof} It suffices to argue correctness and security.
+
+\textbf{Correctness:} Correctness follows immediately: for any given $i$, the probability that $v'_i=v_i$ is at least $1/p(n)$.
 By choosing $\ell$ sufficiently bigger than $1/p(n)$, we guarantee that for at least one $i$,  $v'_i=v_i$ with all but negligible probability
@@
 
-Security follows from obfuscation and is analyzed in \apref{sec:analysis sampling}.
+\textbf{Security:}
+We now argue security.
+ Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
+Let $D$ be a distinguisher of size at most $s_{sec}$.
+We want to bound
+\[
+| \expe[D(R, P)] - \expe[D(U, P)]|
+\]
+by a negligible function.
+
+Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
+\[I_{v_1,..., v_\ell, r}(x, i) =
+\begin{cases}
+r & v_i = x\\
+\perp & \text{otherwise.}
+\end{cases}\]
+By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q\le s_{sec}$ queries) such that
+\begin{align}
+\label{eq:dist before sampling}
+\left|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ik}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) \right|  \leq\ngl(n).
+\end{align}
+
+The same is true if we replaced $R$ above by and independent uniform random variable $U$ over $\zo^\kappa$. 
+We now prove the following lemma, which shows that $S$ cannot distinguish between $R$ and $U$.
+
+\begin{lemma}
+\label{lem:sim cannot distinguish samp}
+Let $U$ denote the uniform distribution over $\zo^\kappa$. Then
+\ifnum\lncs=0
+\begin{align}
+\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
+- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
+\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right|
+\le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
+\label{eq:sim cannot distinguish samp}
+\end{align}
+\else
+\begin{eqnarray}
+\lefteqn{
+\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
+\right.} \nonumber \\
+& & \left.
+- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
+\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right|
+\le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
+\label{eq:sim cannot distinguish samp}
+\end{eqnarray}
+\fi
+
+\end{lemma}
+
+\begin{proof}
+Fix any $u\in \zo^\kappa$ (the lemma will follow by averaging over all $u$). Let $r$ be the correct value of $R$.
+The only information about whether the value is $r$ or $u$ can obtained by $S$ through the query responses.
+First, modify $S$ slightly to quit immediately if it gets a response not equal to $\perp$ (such $S$ is equally successful at distinguishing between $r$ and $u$, because the first non-$\perp$ response suffices).
+There are $q+1$ possible values for the view of $S$ on a given input ($q$ of those views consist of some number of $\perp$ responses followed by the first non-$\perp$ response, and one view has all $q$ responses equal to $\perp$) .
+By \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(V_i | View(S), \{j_{ik}\}) \ge \Hav(V_j | \{j_{ik}\}) - \log (q+1) \ge \subsetEntropy - \log(q+1)$.
+Therefore, at each query, the probability that $S$ gets a non-$\perp$ answer (equivalently, guesses $V_i$) is at most $(q+1)2^{-\subsetEntropy}$.
+Since there are $q$ queries of $S$, the result of \lemref{lem:sim cannot distinguish samp} follows by the union bound.
+Note that  $q(q+1)/2^\subsetEntropy$ is negligible, because $q$ is polynomial and $\subsetEntropy=\omega(\log n)$.
+\end{proof}
+
+Adding together Equation~\ref{eq:dist before sampling}, Equation~\ref{eq:sim cannot distinguish samp}, and Equation~\ref{eq:dist before sampling} in which $R$ is replaced with $U$, we obtain the desired result by the triangle inequality.
+This completes the proof of \thref{thm:sampling}.
+\end{proof}
 
@@
 For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary.
-The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\ref{thm:sampling} in \apref{sec:analysis sampling}.
+The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\ref{thm:sampling} above.
 Note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows the $i$th reading of $w$ to be chosen depending on public values $p_1,..., p_{i-1}$, as required by definition of reusability.
@@
 \noindent
-The following theorem shows the security of this construction (proof is in \apref{sec:info theory sec}).
+The following theorem shows the security of this construction.
 
@@
 \end{theorem}
+\begin{proof}
+Let $W\in \mathcal{W}$.
+It suffices to argue correctness and security.  We first argue correctness.
+
+\textbf{Correctness:}
+When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.
+Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
+Then by correctness of $(\gen', \rep')$, $\Pr[(r, p)\leftarrow \gen'(v) \wedge r'\leftarrow \rep(v',p) \wedge r' = r]\ge 1-\delta$.
+
+\textbf{Security:}
+We now argue security.
+Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
+To show that \[R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{fext}} U | P, seed,\] it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
+The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
+Most known constructions are average-case and we omit this notation.}
+
+We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
+First note since $W$ is $(\alpha, \beta)$ sparse block source that
+there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
+\[
+\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
+\]
+Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$,
+\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]
+
+%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
+%Then since $W$ is a block-source,
+%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
+\noindent
+Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that
+\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-1}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1-1})\]
+and since $(seed_1,..., seed_{j_1})$ are independent of these values
+\ifnum\lncs=0
+\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\,.\]
+\else
+\begin{align*}
+(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}}\\ (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\,.
+\end{align*}
+\fi
+Consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
+Applying a deterministic function does not increase statistical distance and thus,
+\begin{align*}
+(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\gamma \epsilon_{cond}} (Z_{j_1}, seed_{j_1},..., seed_1)
+\end{align*}
+
+\noindent
+By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \tilde{\alpha}(\gamma -\beta)$ where
+\[
+(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\gamma \epsilon_{cond}} (Z, seed_\gamma,...,  seed_1).\]
+%By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
+%Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$.
+%That is,
+%\[
+%(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]
+
+This completes the proof of \thref{thm:info theory sec}
+\end{proof}
 
@@
 We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
-Before defining this object, we define conditional computational (``HILL'' \cite{DBLP:journals/siamcomp/HastadILL99}) entropy.
+Before defining this object, we define conditional computational ``HILL'' (\cite{DBLP:journals/siamcomp/HastadILL99}) entropy.
 
@@
 
-\subsection{Reusability of Fuzzy Extractors}
-\label{sec:comparing reusability}
-
-The goal of a reusable fuzzy extractor is to allow enrollment of a source across multiple services.  A service $i$ sees an reading of the source $w_i$.
-Boyen considers two versions of reusable fuzzy extractors, first where the adversary sees $p_1,..., p_q$~(outsider security~\cite[Definition 6]{Boyen2004}) and tries to learn about the values $w_1,..., w_q$ or the keys $r_1,..., r_q$.
-Second, where the adversary controls some subset of the servers and can key generation on arbitrary $p_i'$~(insider security~\cite[Definition 7]{Boyen2004}).
-This allows the adversary to learn a subset of keys $r_i$~(by performing key generation on the valid $p_i$).
-This definition makes sense when servers are compromised~(after enrollment) and act maliciously.
-In both definitions, the adversary creates a perturbation function $_i$ after seeing $p_1,..., p_{i-1}$~(and generated keys for outsider security) and the challenger generates $w_i = f_i(w_1)$.
-The definition is parameterized by the class of allowed perturbation functions.
-
-Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the perturbation family is a transitive isometric permutation groups.
-Boyen transforms this construction to insider security using random oracles.
-%In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.
-
-Insider security strengthens outsider security in two ways.
-First, it allows the adversary to see some subset of keys, second it allows the adversary to perform key generation on arbitrary $p_i$.
-This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.
-Robust fuzzy extractors provide security against modified $p$.
-In this work, we show reusability when $r_i$ are observed but do not handle the issue of robustness.
-That is, we assume keys may be exposed but servers keep honest state.
-Our definition lies between outsider and insider security.
-
-We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
-The definition of Boyen considers a single adversary.
-We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.
-The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.
-However, to provide meaningful security in the computational setting, we cannot have communication between $f_2,..., f_q$ and $D$.
-This is because $f_2,..., f_q$ are computationally unbounded and thus could break any security that only holds against computationally bounded adversaries.
-Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.\footnote{An alternative would be to have a single computationally bounded adversary that provides perturbation functions but does not see the original reading $w_1$ as in the definition of Boyen.
-\consref{cons:sampling} also satisfies this alternative adaption of Boyen's definition.}  This was not allowed in the definition of Boyen, because the adversary was not split-state, and so giving $w_1$ to the adversary would make security impossible.
-
-%Finally, we allow the distinguishing adversary to see other keys \lnote{we do?
-then why do we call our definition ``outsider''?}.
-This is strictly stronger than the definition of Boyen \lnote{you mean than the outsider security definition of Boyen?}.
-However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.
-This \lnote{what is ``this''?} is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.
-Our reusable construction~(\consref{cons:sampling}) is not insider secure \lnote{according to Boyen's notion, right?
-Why not say ``not robust'' and/or clarify that $r_i$ can leak but $p_i$ cannot be modified.}.
-
-\subsection{Obfuscation}
-\label{sec:obfuscation def}
-
-In this section, we give a formal definition of the required notion of obfuscation.
-We require that the obfuscation is composable and secure with respect to auxiliary input.
-Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} (following \cite{canetti2008obfuscating,CKVW10}) from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.
-As described in the Introduction, they can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}, \cite[Section 4]{lynn2004positive}, \cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis} (such a construction results in an obfuscated function that, at a few hard-to-find-inputs, differs from the original function; this change does not materially affect our results).
-
-\begin{definition}[composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
-\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
-\begin{enumerate}
-\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.\lnote{imperfect correctness allowed?
-It's need for the RO construction.}
-\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
-\ifnum\lncs=0
-\[
-|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
-\]
-\else
-\begin{align*}
-|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1]   - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | \\ < \frac{1}{p(n)} \enspace,
-\end{align*}
-\fi
-where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
-\end{enumerate}
-\end{definition}
-For notational convenience, when we use point function obfuscation, we denote the oracle $(I^1,\dots,I^\ell)$ provided to the simulator in the above definition as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\gamma$ is the vector of obfuscated points.
-When we use digital lockers, we denote the oracle  $(I^1,\dots,I^\ell)$ provided to the simulator as $I_{v, r}(\cdot, \cdot)$ where $v = v_1,..., v_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).
+%\subsection{Reusability of Fuzzy Extractors}
+%\label{sec:comparing reusability}
+
+%\subsection{Obfuscation}
+%\label{sec:obfuscation def}
 
@@
 
-\section{Proof of Security of \consref{cons:sampling}}
-\label{sec:analysis sampling}
- Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.
-Let $D$ be a distinguisher of size at most $s_{sec}$.
-We want to bound
-\[
-| \expe[D(R, P)] - \expe[D(U, P)]|
-\]
-by a negligible function.
-
-Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
-\[I_{v_1,..., v_\ell, r}(x, i) =
-\begin{cases}
-r & v_i = x\\
-\perp & \text{otherwise.}
-\end{cases}\]
-By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q\le s_{sec}$ queries) such that
-\begin{align}
-\label{eq:dist before sampling}
-\left|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ik}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) \right|  \leq\ngl(n).
-\end{align}
-
-The same is true if we replaced $R$ above by and independent uniform random variable $U$ over $\zo^\kappa$. 
-We now prove the following lemma, which shows that $S$ cannot distinguish between $R$ and $U$.
-
-\begin{lemma}
-\label{lem:sim cannot distinguish samp}
-Let $U$ denote the uniform distribution over $\zo^\kappa$. Then
-\ifnum\lncs=0
-\begin{align}
-\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
-- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
-\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right|
-\le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
-\label{eq:sim cannot distinguish samp}
-\end{align}
-\else
-\begin{eqnarray}
-\lefteqn{
-\left| \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)} \left (R, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right) 
-\right.} \nonumber \\
-& & \left.
-- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}  
-\left (U, \{j_{ij}\}, 1^{\ell (\kappa+\eta\log |\mathcal Z|)} \right)\right|
-\le \frac{q(q+1)}{2^\subsetEntropy} \le \ngl(n)\,.
-\label{eq:sim cannot distinguish samp}
-\end{eqnarray}
-\fi
-
-\end{lemma}
-
-\begin{proof}
-Fix any $u\in \zo^\kappa$ (the lemma will follow by averaging over all $u$). Let $r$ be the correct value of $R$.
-The only information about whether the value is $r$ or $u$ can obtained by $S$ through the query responses.
-First, modify $S$ slightly to quit immediately if it gets a response not equal to $\perp$ (such $S$ is equally successful at distinguishing between $r$ and $u$, because the first non-$\perp$ response suffices).
-There are $q+1$ possible values for the view of $S$ on a given input ($q$ of those views consist of some number of $\perp$ responses followed by the first non-$\perp$ response, and one view has all $q$ responses equal to $\perp$) .
-By \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(V_i | View(S), \{j_{ik}\}) \ge \Hav(V_j | \{j_{ik}\}) - \log (q+1) \ge \subsetEntropy - \log(q+1)$.
-Therefore, at each query, the probability that $S$ gets a non-$\perp$ answer (equivalently, guesses $V_i$) is at most $(q+1)2^{-\subsetEntropy}$.
-Since there are $q$ queries of $S$, the result of \lemref{lem:sim cannot distinguish samp} follows by the union bound.
-Note that  $q(q+1)/2^\subsetEntropy$ is negligible, because $q$ is polynomial and $\subsetEntropy=\omega(\log n)$.
-\end{proof}
-
-Adding together Equation~\ref{eq:dist before sampling}, Equation~\ref{eq:sim cannot distinguish samp}, and Equation~\ref{eq:dist before sampling} in which $R$ is replaced with $U$, we obtain the desired result by the triangle inequality.\section{Analysis of \consref{cons:first construction}}
+%\section{Proof of Security of \consref{cons:sampling}}
+%\label{sec:analysis sampling}
+
+\section{Analysis of \consref{cons:first construction}}
 \label{sec:construction analysis}
@@
 
-\section{Analysis of \consref{cons:info theoretic}}
-\label{sec:info theory sec}
-\begin{proof}[Proof of Theorem~\ref{thm:info theory sec}]
-Let $W\in \mathcal{W}$.
-It suffices to argue correctness and security.  We first argue correctness.
-When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.
-Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.
-Then by correctness of $(\gen', \rep')$, $\Pr[(r, p)\leftarrow \gen'(v) \wedge r'\leftarrow \rep(v',p) \wedge r' = r]\ge 1-\delta$.
-
-We now argue security.
-Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
-To show that $R | P, seed \approx_{\gamma \epsilon_{cond} + \epsilon_{fext}} U | P, seed$, it suffices to show that $\Hav(V | seed)$ is $\gamma \epsilon_{cond}$ close to a distribution with average min-entropy $\tilde{\alpha}(\gamma - \beta)$.
-The lemma then follows by the security of $(\gen', \rep')$.\footnote{Note, again, that $(\gen', \rep')$ must be an average-case fuzzy extractor.
-Most known constructions are average-case and we omit this notation.}
-
-We now argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}(\gamma - \beta)$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.
-First note since $W$ is $(\alpha, \beta)$ sparse block source that
-there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
-\[
-\forall j\in J, \forall w_1,..., w_{j-1} \in W_1,..., W_{j-1}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
-\]
-Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$,
-\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]
-
-%\[(\ext (W_1, seed_1), seed_1) \approx_{\epsilon} (U_{\mathcal{Y}}, seed_1)\]
-%Then since $W$ is a block-source,
-%\[ \forall w_1\in W_1, \Hoo(W_2 | w_1)\ge k.\]
-\noindent
-Thus, there exists a distribution $Y_{j_1}$ with $\Hav(Y_{j_1} | seed_{j_1}) \ge \tilde{\alpha}$ such that
-\[(\cond (W_{j_1}, seed_{j_1}), seed_{j_1}, W_1,..., W_{j_1-1}) \approx_{\epsilon_{cond}} (Y_{j_1}, seed_{j_1}, W_1,..., W_{j_1-1})\]
-and since $(seed_1,..., seed_{j_1})$ are independent of these values
-\ifnum\lncs=0
-\[(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}} (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\,.\]
-\else
-\begin{align*}
-(\cond (W_{j_1},seed_{j_1}), W_{j_1-1},..., W_1, seed_{j_1}, ..., seed_{1}) \approx_{\epsilon_{cond}}\\ (Y_{j_1}, W_{j_1-1},..., W_1, seed_{j_1}, , ...,  seed_{1})\,.
-\end{align*}
-\fi
-Consider the random variable $Z_{j_1} =( Y_{j_1}, \cond(W_{j_1-1},seed_{j_1-1}),..., \cond(W_{1}, seed_{1}))$ and note that \[\Hav(Z_{j_1} | seed_1,...,seed_{j_1})\ge \alpha'.\]
-Applying a deterministic function does not increase statistical distance and thus,
-\begin{align*}
-(\cond (W_{j_1}, seed_{j_1}), \cond(W_{j_1-1}, seed_{j_1-1}),..., \cond(W_1, seed_1), seed_{j_1},..., seed_{1}) \\\approx_{\gamma \epsilon_{cond}} (Z_{j_1}, seed_{j_1},..., seed_1)
-\end{align*}
-
-\noindent
-By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \tilde{\alpha}(\gamma -\beta)$ where
-\[
-(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\gamma \epsilon_{cond}} (Z, seed_\gamma,...,  seed_1).\]
-%By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.
-%Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$.
-%That is,
-%\[
-%(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]
-This completes the proof.
-\end{proof}
-
 \end{document}

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex

@@
 }
+\author{}\institute{}
 \begin{document}
@@
 \begin{abstract}
-Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
-A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
+Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy
+readings of a high-entropy secret into the same uniformly distributed
+key. A minimum condition for the security of the key is the hardness
+of guessing a value that is similar to the secret, because the fuzzy
+extractor converts such a guess to the key.
+
 We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
 Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.
-
-High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
-Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
-In this work, we ask whether this challenge is inherent.
-We show the following:
-\begin{itemize}
-\item \textbf{Sufficiency of fuzzy min-entropy:}  We construct a fuzzy extractor for each physical source with fuzzy min-entropy.
-This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.
-Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.
-The constructed fuzzy extractor must \emph{precisely know} the distribution of the noisy source.
-\item \textbf{Cost of distributional uncertainty:}  High entropy sources can never be fully observed and must be modeled.
-An adversary may have a better model than the fuzzy extractor designer.
-To compensate, fuzzy extractors are typically designed to work for families of physical sources.
-We build a family of high fuzzy min-entropy sources which no fuzzy extractor can secure.
-This result emphasizes the importance of high fidelity models of high entropy sources.
-\end{itemize}
-We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.
+High fuzzy min-entropy is necessary for the existence of a fuzzy
+extractor. 
+% ; moreover, there is evidence that it may be sufficient when only computational security is required.
+
+We ask: \emph{is high fuzzy min-entropy a
+  sufficient condition for noise-tolerant extraction?}
+If only computational security is required, recent progress on program
+obfuscation gives evidence that fuzzy
+min-entropy is indeed sufficient. In contrast,
+information-theoretic fuzzy extractors are not known for many
+practically relevant sources of high fuzzy min-entropy.
+
+In this paper,
+show that fuzzy min-entropy is also sufficient for
+information-theoretically secure fuzzy extraction. For every source
+distribution $W$ for which security is possible in an ideal world with
+access only to the extractor functionality, we give a secure fuzzy
+extractor.
+
+Our construction relies on the extractor knowing the precise
+distribution of the source $W$.  A more ambitious goal is to design a
+single extractor that works for all possible sources.  We show that
+this more ambitious goal is impossible: we give a family of sources
+with high fuzzy min-entropy for which no single fuzzy extractor is
+secure.  This result emphasizes the importance of accurate models
+of high entropy sources.
+
+% \begin{itemize}
+% \item \textbf{Sufficiency of fuzzy min-entropy:} We show that for each
+%   source with nontrivial (that is, $\omega(\log n)$) fuzzy min-entropy,
+%   there is an infor\-mation-theoretic fuzzy extractor that reliably
+%   extracts a key of length roughly the fuzzy min-entropy.  This result
+%   justifies fuzzy min-entropy as the ``right'' measure of the quality
+%   of a noisy distribution for key derivation. Previous results
+%   considered the entropy and error tolerance of a source separately;
+%   consequently, for many sources with high fuzzy min-entropy, existing
+%   constructions did not lead to secure fuzzy extractors.
+
+%   Our construction works for every source, but requires
+%   \emph{precise knowledge} of the distribution of the source.
+
+% \item \textbf{Cost of distributional uncertainty:} A more ambitious
+%   goal is to design a single extractor that works for all possible
+%   sources.
+
+% High entropy
+%   sources can never be fully observed by sampling, and so some
+%   modeling assumptions must be used.
+
+% Moreover,  An
+%   adversary may have a better model than the fuzzy extractor designer.
+%   To compensate, fuzzy extractors are typically designed to work for
+%   families of physical sources. We build a family of high fuzzy
+%   min-entropy sources which no fuzzy extractor can secure.  This
+%   result emphasizes the importance of high fidelity models of high
+%   entropy sources.
+% \end{itemize}
+% We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.
 Our results are information-theoretic, but we discuss implications for the computational setting.
@@
 \paragraph{Fuzzy Min-Entropy}
-We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$.
+We introduce a new entropy notion that precisely measures how hard it
+is for the adversary to guess a value within distance $t$ of the
+original reading $w$. 
 Suppose $w$ is sampled from a distribution $W$.
@@
 
-Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.
-Fuzzy min-entropy measures the ideal security of a noisy source of entropy when used for key derivation, similar to distributional notions of program obfuscation~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05}---we discuss the connection in \secref{sec:related settings}.
-Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).
-
-However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
+% Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  
+Fuzzy min-entropy measures the ideal security of a noisy source of
+entropy when used for key derivation, similar to distributional
+notions of program obfuscation
+(e.g.,~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05};
+see \secref{sec:related settings} for discussion).  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary}).
+
+However, existing constructions do not measure their security in terms
+of fuzzy min-entropy; instead, their security is shown to be
+$\Hoo(W)$ minus some loss, for error-tolerance, that is at least $\log |B_t|$.
 Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
@@
 \paragraph{Sufficiency of $\Hfuzz(W)$ for a Precisely Known Distribution}
-Ideally, a fuzzy extractor has \emph{precise knowledge} of the probability distribution function of $W$.
-We call this  the \emph{precise knowledge} setting.
-In this setting, we show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}).
-Our construction crucially utilizes the probability distribution function of $W$ and, in particular, is not polynomial time.
-This result shows that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor of a distribution $W$.
+Ideally, a fuzzy extractor has \emph{precise knowledge} of the
+probability distribution function of $W$.  We call this  the
+\emph{precise knowledge} setting.  In this setting, we show that for
+every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to
+construct a fuzzy extractor with a superlogarithmic length $\key$
+(\corref{cor:extension to fuzz ext}). Our construction crucially
+utilizes the probability distribution function of $W$ and, in
+particular, is not polynomial time.  This result shows that
+$\Hfuzz(W)$ is a necessary and sufficient condition for building a
+fuzzy extractor for a given distribution $W$.
 
@@
 
-\paragraph{The Challenge of Precisely Distributional Knowledge}
-Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic.
+\paragraph{The Challenge of Precise Distributional Knowledge}
+Assuming precise knowledge of a distribution $W$ may be unrealistic.
 Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled.
@@
 
-We show comparable, but stronger, results for secure sketches.
+For secure sketches, we show results that are similar to but
+stronger than our results for fuzzy extractor.
 Namely, we show in \corref{cor:extension to fuzz ext} that secure sketches are possible if the distribution $W$ is precisely known.

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
minor abstract edits

@@
 We ask: \emph{is high fuzzy min-entropy a
-  sufficient condition for noise-tolerant extraction?}
+  sufficient condition for noise-tolerant key extraction?}
 If only computational security is required, recent progress on program
@@
 
-In this paper,
-show that fuzzy min-entropy is also sufficient for
+In this paper, we show that fuzzy min-entropy is also sufficient for
 information-theoretically secure fuzzy extraction. For every source
-distribution $W$ for which security is possible in an ideal world with
-access only to the extractor functionality, we give a secure fuzzy
+distribution $W$ for which security is possible we give a secure fuzzy
 extractor.
 
-Our construction relies on the extractor knowing the precise
+Our construction relies on the fuzzy extractor knowing the precise
 distribution of the source $W$.  A more ambitious goal is to design a

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
modifications to techniques discussion and removal of Interpreting Our Results

@@
 
-On the other hand, there is a family of sources, $\mathcal{W}_Z$, where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
-The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
-
-\paragraph{Interpreting our Results}
-Our results show that fuzzy min-entropy is sufficient for noisy key derivation if the distribution is precisely known but insufficient if the distribution is only known to come from a family.
-A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.
+On the other hand, there is a family of sources, $\mathcal{W}_Z$,
+where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for
+which no secure sketch correcting even a few errors is
+possible~(\thref{thm:imposs sketch}). The impossibility result applies
+even when $\rec$ is allowed to be incorrect with probability up to
+$1/4$ (in contrast to our fuzzy extractor impossibility result, which
+requires perfect reconstruction).
+
+% \paragraph{Interpreting our Results}
+% Our results show that fuzzy min-entropy is necessary and sufficient for noisy key
+% derivation if the distribution is precisely known. We give evidence
+% that fuzzy min-entropy alone is not sufficient when the exact
+% distribution is uncertain.  
+%  % but insufficient if the distribution is only known to come from a
+%  % family. 
+%  A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.
 Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.
 This impossibility can be overcome by the use of a short seed of uniform randomness.
-We must find an analogous relaxation to derive keys from noisy sources.
+% We must find an analogous relaxation to derive keys from noisy sources.
 One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.
@@
 
-\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).
-We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).
-Consider some subsequent reading $w'$.
-To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched.
-Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points.
-Thus, our sketch is computed via a universal hash of $w$.
-To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$.
-Because the distribution is flat, it is also the ball with the most points of nonzero probability.
-Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball.
-Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
+\paragraph{Techniques for Positive Results for a Precisely Known
+  Distribution} 
+We now explain how to construct a secure sketch for a precisely known
+distribution $W$ with fuzzy min-entropy (we already explained how to
+construct a fuzzy extractor from it).  We begin with distributions in
+which all points in the support have the same probability (so-called
+``flat'' distributions).  Consider some subsequent reading $w'$. To
+achieve correctness, the sketch algorithm must disambiguate which
+point $w\in W$ within distance $t$ of $w'$ was
+sketched. Disambiguating multiple points can be accomplished by
+universal hashing, as long as the size of hash output space is
+slightly greater than the number of possible points. Thus, our sketch
+is computed via a universal hash of $w$. To determine the length of
+that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
+$t$. Because the distribution is flat, $B^*$ is also the ball with the
+most points of nonzero probability. Thus, the length of the sketch
+needs to be slightly greater than the logarithm of the number of
+non-zero probability point in $B^*$. Since $\Hfuzz(W)$ is
+determined by the weight of that ball, the number of points cannot be
+too high and there will be entropy left after the sketch is published.
+%
+This remaining entropy is sufficient for extracting a key.
 
@@
 We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
-the adversary knows $W_z$.
-To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.
+the adversary knows $W_z$.   To exploit the asymmetry, we construct
+$\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the
+outcome $z$) reduces the distribution to a single affine line, but
+conditioning on \emph{only} $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.
 

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex

@@
 non-zero probability point in $B^*$. Since $\Hfuzz(W)$ is
-determined by the weight of that ball, the number of points cannot be
+determined by the weight of $B^*$, the number of points cannot be
 too high and there will be entropy left after the sketch is published.

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
minor edits to TCC rejection

@@
 
+\smallskip
 We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
@@
 extractor. 
-% ; moreover, there is evidence that it may be sufficient when only computational security is required.
+\smallskip
 
 We ask: \emph{is high fuzzy min-entropy a
-  sufficient condition for noise-tolerant key extraction?}
+  sufficient condition for key extraction from noisy sources?}
 If only computational security is required, recent progress on program
@@
 practically relevant sources of high fuzzy min-entropy. 
+\smallskip
 
@@
 
+\smallskip
 Our construction relies on the fuzzy extractor knowing the precise
@@
 (e.g.,~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05};
-see \secref{sec:related settings} for discussion).  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary}).
+see \secref{sec:related settings} for discussion).  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(Proposition \ref{prop:fuzz necessary}).
 
@@
 needs to be slightly greater than the logarithm of the number of
-non-zero probability point in $B^*$. Since $\Hfuzz(W)$ is
+non-zero probability points in $B^*$. Since $\Hfuzz(W)$ is
 determined by the weight of $B^*$, the number of points cannot be
@@
 %
-This remaining entropy is sufficient for extracting a key.
+This remaining entropy suffices to extract a key.
 
@@
 \begin{lemma}
-\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
+\label{lem:flat hashing}
 Let $W$ be a flat with $\Hoo(W)\ge m$.  Then
@@
 \end{lemma}
+\begin{proof}
+We first argue security.
+Fix some $W\in\mathcal{W}$.
+Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
+Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.
+
+\noindent
+We now argue correctness.
+Fix some $w, w'$.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.
+The size of $W^*$ is at most $\beta_{t}$.
+Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
+The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
+The probability that another element $w^*$ collides is:
+\begin{align*}
+\Pr[\exists w^* \in W^* |w^* \neq w &\wedge F(K, w^*) = F(K, w)] \\&\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
+\end{align*}
+The inequality proceeds by union bound.
+The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $\beta_{t}-1$.
+This completes the proof.
+\end{proof}
+
 %\noindent
@@
 
-\section{Proof of \lemref{lem:flat hashing}}
-\label{sec:proof of flat hashing}
-\begin{proof}
-We first argue security.
-Fix some $W\in\mathcal{W}$.
-Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
-Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.
-
-\noindent
-We now argue correctness.
-Fix some $w, w'$.
-Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.
-The size of $W^*$ is at most $\beta_{t}$.
-Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
-The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
-The probability that another element $w^*$ collides is:
-\begin{align*}
-\Pr[\exists w^* \in W^* |w^* \neq w &\wedge F(K, w^*) = F(K, w)] \\&\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
-\end{align*}
-The inequality proceeds by union bound.
-The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $\beta_{t}-1$.
-This completes the proof.
-\end{proof}
+%\section{Proof of \lemref{lem:flat hashing}}
+%\label{sec:proof of flat hashing}
 

### 2015-02-24 info-bounds/FuzzyExtPossibility.tex
revising for eprint

@@
+\def\shownotes{0}
+\def\blinded{0}
+\def\lncs{0}
+
+\ifnum\lncs=0
 	\documentclass[11pt]{article}
-
-\def\shownotes{1}
-\def\blinded{0}
-
 	\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
@@
 	%\usepackage[parfill]{parskip}
+	\usepackage{amsthm}
+	\newtheorem{theorem}{Theorem}[section]
+	\newtheorem{lemma}[theorem]{Lemma}
+	\newtheorem{proposition}[theorem]{Proposition}
+	\newtheorem{corollary}[theorem]{Corollary}
+	\newtheorem{definition}[theorem]{Definition}
+	\newtheorem{assumption}[theorem]{Assumption}
+	\newtheorem{claim}[theorem]{Claim}
+	\newtheorem{problem}[theorem]{Problem}
+	\newtheorem{construction}[theorem]{Construction}
+
+\else
+	\documentclass[runningheads]{llncs}
+	\newtheorem{construction}{Construction}
+\fi
+
 \usepackage{graphicx}
 \usepackage{amssymb, amsmath, amsfonts}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage{enumerate}
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{claim}[theorem]{Claim}
+%\newtheorem{problem}[theorem]{Problem}
+%\newtheorem{construction}[theorem]{Construction}
 
@@
 }
+%\author{}\institute{}
 \begin{document}
@@
 \begin{abstract}
-Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key.
-A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
+Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy
+readings of a high-entropy secret into the same uniformly distributed
+key. A minimum condition for the security of the key is the hardness
+of guessing a value that is similar to the secret, because the fuzzy
+extractor converts such a guess to the key.
+
+\smallskip
 We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.
 Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.
-
-High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required.
-Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy.
-In this work, we ask whether this challenge is inherent.
-We show the following:
-\begin{itemize}
-\item \textbf{Sufficiency of fuzzy min-entropy:}  We construct a fuzzy extractor for each physical source with fuzzy min-entropy.
-This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.
-Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.
-The constructed fuzzy extractor must \emph{precisely know} the distribution of the noisy source.
-\item \textbf{Cost of distributional uncertainty:}  High entropy sources can never be fully observed and must be modeled.
-An adversary may have a better model than the fuzzy extractor designer.
-To compensate, fuzzy extractors are typically designed to work for families of physical sources.
-We build a family of high fuzzy min-entropy sources which no fuzzy extractor can secure.
-This result emphasizes the importance of high fidelity models of high entropy sources.
-\end{itemize}
-We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.
+High fuzzy min-entropy is necessary for the existence of a fuzzy
+extractor. 
+\smallskip
+
+We ask: \emph{is high fuzzy min-entropy a
+  sufficient condition for key extraction from noisy sources?}
+If only computational security is required, recent progress on program
+obfuscation gives evidence that fuzzy
+min-entropy is indeed sufficient. In contrast,
+information-theoretic fuzzy extractors are not known for many
+practically relevant sources of high fuzzy min-entropy. 
+\smallskip
+
+In this paper, we show that fuzzy min-entropy is also sufficient for
+information-theoretically secure fuzzy extraction. For every source
+distribution $W$ for which security is possible we give a secure fuzzy
+extractor.
+
+\smallskip
+Our construction relies on the fuzzy extractor knowing the precise
+distribution of the source $W$.  A more ambitious goal is to design a
+single extractor that works for all possible sources.  We show that
+this more ambitious goal is impossible: we give a family of sources
+with high fuzzy min-entropy for which no single fuzzy extractor is
+secure.  This result emphasizes the importance of accurate models
+of high entropy sources.
+
+% \begin{itemize}
+% \item \textbf{Sufficiency of fuzzy min-entropy:} We show that for each
+%   source with nontrivial (that is, $\omega(\log n)$) fuzzy min-entropy,
+%   there is an infor\-mation-theoretic fuzzy extractor that reliably
+%   extracts a key of length roughly the fuzzy min-entropy.  This result
+%   justifies fuzzy min-entropy as the ``right'' measure of the quality
+%   of a noisy distribution for key derivation. Previous results
+%   considered the entropy and error tolerance of a source separately;
+%   consequently, for many sources with high fuzzy min-entropy, existing
+%   constructions did not lead to secure fuzzy extractors.
+
+%   Our construction works for every source, but requires
+%   \emph{precise knowledge} of the distribution of the source.
+
+% \item \textbf{Cost of distributional uncertainty:} A more ambitious
+%   goal is to design a single extractor that works for all possible
+%   sources.
+
+% High entropy
+%   sources can never be fully observed by sampling, and so some
+%   modeling assumptions must be used.
+
+% Moreover,  An
+%   adversary may have a better model than the fuzzy extractor designer.
+%   To compensate, fuzzy extractors are typically designed to work for
+%   families of physical sources. We build a family of high fuzzy
+%   min-entropy sources which no fuzzy extractor can secure.  This
+%   result emphasizes the importance of high fidelity models of high
+%   entropy sources.
+% \end{itemize}
+% We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.
 Our results are information-theoretic, but we discuss implications for the computational setting.
@@
 The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.
-The correctness guarantee is that the key is reproduced precisely when the distance between $w$ and $w'$ is at most $t$.
+The correctness guarantee is that the \key is reproduced precisely when the distance between $w$ and $w'$ is at most $t$.
 
@@
 
-Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.
-Fuzzy min-entropy measures the ideal security of a noisy source of entropy when used for key derivation, similar to distributional notions of program obfuscation~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05}---we discuss the connection in \secref{sec:related settings}.
-Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).
-
-However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance.
+% Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  
+Fuzzy min-entropy measures the ideal security of a noisy source of
+entropy when used for key derivation, similar to distributional
+notions of program obfuscation
+(e.g.,~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05};
+see \secref{sec:related settings} for discussion).  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(Proposition \ref{prop:fuzz necessary}).
+
+However, existing constructions do not measure their security in terms
+of fuzzy min-entropy; instead, their security is shown to be
+$\Hoo(W)$ minus some loss, for error-tolerance, that is at least $\log |B_t|$.
 Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary.
@@
 tight bounds for specific distributions---generally the uniform distribution or
-i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
+i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining}, \cite{DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
 Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.
 
-\paragraph{The Challenge of Precisely Distributional Knowledge}
-Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic.
+\paragraph{The Challenge of Precise Distributional Knowledge}
+Assuming precise knowledge of a distribution $W$ may be unrealistic.
 Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled.
@@
 Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$), followed by randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.
-The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $\sketch$ to output the original reading $w$.
-
-We show comparable, but stronger, results for secure sketches.
+The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $ss$ to output the original reading $w$.
+
+For secure sketches, we show results that are similar to but
+stronger than our results for fuzzy extractors.
 Namely, we show in \corref{cor:extension to fuzz ext} that secure sketches are possible if the distribution $W$ is precisely known.
-(In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.)
-
-On the other hand, there is a family of sources, $\mathcal{W}_Z$, where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}).
-The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).
-
-\paragraph{Interpreting our Results}
-Our results show that fuzzy min-entropy is sufficient for noisy key derivation if the distribution is precisely known but insufficient if the distribution is only known to come from a family.
-A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.
+(In fact, we obtain our fuzzy extractors for the case of a precisely known distribution from this result by applying a randomness extractor.)
+
+On the other hand, there is a family of sources, $\mathcal{W}_Z$,
+where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for
+which no secure sketch correcting even a few errors is
+possible~(\thref{thm:imposs sketch}). The impossibility result applies
+even when $\rec$ is allowed to be incorrect with probability up to
+$1/4$ (in contrast to our fuzzy extractor impossibility result, which
+requires perfect reconstruction).
+
+% \paragraph{Interpreting our Results}
+% Our results show that fuzzy min-entropy is necessary and sufficient for noisy key
+% derivation if the distribution is precisely known. We give evidence
+% that fuzzy min-entropy alone is not sufficient when the exact
+% distribution is uncertain.  
+%  % but insufficient if the distribution is only known to come from a
+%  % family. 
+%  A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.
 Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.
 This impossibility can be overcome by the use of a short seed of uniform randomness.
-We must find an analogous relaxation to derive keys from noisy sources.
+% We must find an analogous relaxation to derive keys from noisy sources.
 One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.
@@
 
-\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).
-We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).
-Consider some subsequent reading $w'$.
-To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched.
-Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points.
-Thus, our sketch is computed via a universal hash of $w$.
-To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$.
-Because the distribution is flat, it is also the ball with the most points of nonzero probability.
-Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball.
-Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.
+\paragraph{Techniques for Positive Results for a Precisely Known
+  Distribution} 
+We now explain how to construct a secure sketch for a precisely known
+distribution $W$ with fuzzy min-entropy (we already explained how to
+construct a fuzzy extractor from it).  We begin with distributions in
+which all points in the support have the same probability (so-called
+``flat'' distributions).  Consider some subsequent reading $w'$. To
+achieve correctness, the sketch algorithm must disambiguate which
+point $w\in W$ within distance $t$ of $w'$ was
+sketched. Disambiguating multiple points can be accomplished by
+universal hashing, as long as the size of hash output space is
+slightly greater than the number of possible points. Thus, our sketch
+is computed via a universal hash of $w$. To determine the length of
+that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
+$t$. Because the distribution is flat, $B^*$ is also the ball with the
+most points of nonzero probability. Thus, the length of the sketch
+needs to be slightly greater than the logarithm of the number of
+non-zero probability points in $B^*$. Since $\Hfuzz(W)$ is
+determined by the weight of $B^*$, the number of points cannot be
+too high and there will be remaining entropy after the sketch is published.
+This remaining entropy suffices to extract a key.
 
@@
 The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).}  This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.
-The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability.
-Thus, extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.
+This is true for the set of distributions  with fuzzy min-entropy~(and only those distributions).
+Thus, extending our negative result to the computational setting would rule out the existence of virtual grey-box obfuscation for all circuits.
 
@@
 When both interaction and computational assumptions are allowed, secure two-party computation can produce a key that will be secure whenever the distribution $W$ has fuzzy min-entropy.
-The two-party computation protocol needs to be secure without assuming authenticated channels; it can be built under the assumptions that collision-resistant hash functions and enhanced trapdoor permutations exist~\cite{DBLP:journals/joc/BarakCLPR11}.
+The two-party computation protocol needs to be secure without assuming authenticated channels; it can be assuming the existence of collision-resistant hash functions and enhanced trapdoor permutations~\cite{DBLP:journals/joc/BarakCLPR11}.
 
@@
 Note that we have no requirement that the algorithms are compact or efficient, and so the distribution can be fully known to them.
-Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.
+Finding a natural model of specifying distributions that allows for efficient~(yet generic) constructions of sketches and extractors for a precisely known distribution is an interesting problem.
 
@@
 \begin{lemma}
-\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
-Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
+\label{lem:flat hashing}
+Let $W$ be a flat with $\Hoo(W)\ge m$.  Then
 \consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
 \end{lemma}
-\begin{corollary}
-Let $n = \log |\mathcal{M}|$.
-If $|R| \ge |\beta_{t}|\cdot n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.
-That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
-\end{corollary}
-
-\noindent
-\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.
+\begin{proof}
+We first argue security.
+Fix some $W\in\mathcal{W}$.
+Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
+Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.
+
+\noindent
+We now argue correctness.
+Fix some $w, w'$.
+Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.
+The size of $W^*$ is at most $\beta_{t}$.
+Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
+The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
+The probability that another element $w^*$ collides is:
+\begin{align*}
+\Pr[\exists w^* \in W^* |w^* \neq w &\wedge F(K, w^*) = F(K, w)] \\&\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+ &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
+\end{align*}
+The inequality proceeds by union bound.
+The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $\beta_{t}-1$.
+This completes the proof.
+\end{proof}
+
+%\noindent
+%\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.
 The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$.
@@
 
-We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z)) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}$.
-It may be possible to improve parameters by ruling out only a worst case $W$.
-In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.}
+We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary randomly samples $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z ) ) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}_Z$.
+It may be possible to improve parameters by ruling out only a worst case $W_z$.
+In \apref{sec:def equiv}, we show that providing security for the set of distributions $\mathcal{W}_Z$ is equivalent to providing security for all distributions $Z$ over that family.}
 
 Let $V$ be the process of uniformly sampling $W_z\leftarrow \mathcal{W}_Z$ and then sampling $w\leftarrow W_z$.
-Let the random variable $Z$ the outcome of sampling $W_z\leftarrow \mathcal{W}_Z$.
+Let the random variable $Z$ represent the process of sampling $W_z\leftarrow \mathcal{W}_Z$.
 The view of the challenger is $V$, while the view of the adversary is $\sketch(V)$ and $Z$.
@@
 We prove the stronger average case statement.
-We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
+We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be a field where of size $|\mathbb{F}| =\omega(\poly(n))$.  
 Let $\mathcal{W}_Z$ be the set of all distributions of the form 
@@
 \]
-The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) for arbitrary $b_i$ and $a_i\neq 0$.
+The family is defined by the parameters $z = a_2,.., a_\gamma, b_2,..., b_\gamma$ (seen by the adversary) where $a_i\neq 0$.
 The outcome $w\leftarrow W_z$ is sampled by sampling $w_1$ and computing $w$.
 Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$.
-The algorithm $\sketch, \rec$ never see $Z$ only the outcome of $v\leftarrow V$.
+The algorithm $\sketch, \rec$ never see $Z$ only $ V$.
 Fix some $4\le t < \gamma$.
@@
 Here we show the minimum distance between points of $V|\sketch(V)$ is at least $t$.
-\item \lemref{lem:side info determines sketch}:  $\tilde{H}_0(V | \sketch(V), Z) < 2$.
+\item \lemref{lem:side info determines sketch}:  $\tilde{H}_0(V | \sketch(V), Z) < 2$ and thus $\Hav(V | \sketch(V) <2$.
 \end{itemize}
@@
 Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.
-There exists a family of distributions $\mathcal{W}_Z$ over $\mathcal{M}$ such that for each element $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.
-If
-$s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
-$t\ge 4$, and 
- $\epsilon_{sec} + t\delta < 1/16$,
- then $\tilde{m} <4$.
+There exists a family of distributions $\mathcal{W}_Z$ over $\mathcal{M}$ such that for each element $W_z\in \mathcal{W}_Z$, $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-secure sketch $(\sketch, \rec)$ with error $\delta$, then \[H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W | \sketch(W), Z)<4.\]
+if 
+$t \ge 4$, $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, and  $\epsilon_{sec} + t\delta < 1/16$.
 \end{corollary}
@@
 \]
-The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$ for arbitrary $b_i$ and $a_i\neq 0$.  
-A particular distribution $W_z$ is the uniform distribution over choices of $x$.
+The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is indexed by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$ where $a_i\neq 0$.  
+%A particular distribution $W_z$ is the uniform distribution over choices of $x$~(for a fixed $a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$).
  Define $V$ as the process of uniformly choosing $W_z\leftarrow \mathcal{W}_Z$ and then sampling from $w\leftarrow W_z$.
@@
 \item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
-\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
+\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys are not possible.  In more detail,
 \begin{itemize}
@@
 \textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.
-We note that the specific family $\mathcal{W}_Z$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors  for this family of distributions when $\mathbb{F}$ is large enough under weaker assumptions.
+For the specific family $\mathcal{W}_Z$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors  for this family of distributions when $\mathbb{F}$ is large enough under weaker assumptions.
 (Their construction is stated with imperfect correctness.
@@
 It may be possible to construct a $p$ that reduces the entropy of $w$ by less than $\log |p|$.
-In \secref{sec:known distributions}, we will construct schemes with variable length $p$, providing information-reconciliation for distributions where the bounds of Renner and Wolf provide no security guarantees.
+In \secref{sec:known distributions}, we construct schemes with variable length $p$, providing information-reconciliation for distributions where the bounds of Renner and Wolf provide no security guarantees.
 
@@
 
-\section{Proof of \lemref{lem:flat hashing}}
-\label{sec:proof of flat hashing}
-\begin{proof}
-We first argue security.
-Fix some $W\in\mathcal{W}$.
-Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.
-Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.
-
-We now argue correctness.
-Fix some $w, w'$.
-Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.
-The size of $W^*$ is at most $\beta_{t}$.
-Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.
-The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.
-The probability that another element $w^*$ collides is:
-\begin{align*}
-\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
- &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
-\end{align*}
-The inequality proceeds by union bound.
-The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $\beta_{t}-1$.
-This completes the proof.
-\end{proof}
+%\section{Proof of \lemref{lem:flat hashing}}
+%\label{sec:proof of flat hashing}
 
@@
 \begin{align*}
-\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
+\Pr[\exists w^* \in W^* |w^* \neq w &\wedge F_i(K, w^*) = F_i(K, w)]\\ &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F_i(K, w^*) = F_i(K, w)] \\
  &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|}\le \frac{\beta_{t, i}}{|R_i|} = \delta
 \end{align*}
-The first inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.
+The first inequality is by union bound. The first equality follows from the universality of $F_i$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.
 
@@
 \end{align}
-For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $L_I$ be the random variable of the level information (in what follows, $L_I$ takes values between $m$ and $m+n$, where possible we omit this for notational clarity).
+For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $L_I$ be the random variable of the level information (in what follows, $L_I$ takes values between $m$ and $m+n$, where possible we omit the range of $i$ for notational clarity).
 
 \begin{align}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge L_I =i }) \right)\nonumber\\
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge L_I =i )} \right)\nonumber\\
 &=-\log \left( \expe_{i} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
 &=-\log \left( \expe_{i} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
-&\ge-\log \left( \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
-&\ge-\log \left(\frac{1}{\delta} \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
-&\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
+&\ge-\log \left( \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}) +\log \delta)}\right)\nonumber\\
+&\ge-\log \left(\frac{1}{\delta} \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}))}\right)\nonumber\\
 &\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
@@
 \begin{align*}
-\Hfuzz(W|J=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \Pr[W=w | J=i]\right) \right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t}\left( \min_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)\\
-&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \left(\max_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)+1\\
-&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 2^{-\Hoo(W|J=i)}\right) \right)+1\\
-&= \Hoo(W|J=i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 1\right) \right)+1\\
-&=\Hoo(W|J=i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
+&\Hfuzz(W|J=i) =\\&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}} \Pr[W=w | J=i]\right) \right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}}\left( \min_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)\\
+&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}} \left(\max_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)+1\\
+&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i \\\wedge \dis(w, w')\le t}} 2^{-\Hoo(W|J=i)}\right) \right)+1\\
+&= \Hoo(W|J=i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{\substack{w\in W | \Pr[W=w]\in L_i\\ \wedge \dis(w, w')\le t}} 1\right) \right)+1\\
+&=\Hoo(W|J=i)\\&-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
 &=\Hoo(W|J=i)+1-\log \beta_{t, i}.
 \end{align*}
-Where the third line follows by \lemref{lem:nearly flat after conditioning}, which follows the proof of \thref{thm:layered hashing}.  This completes the proof of \clref{cl:fuzz proportional beta}.
+Where the fourth line follows by \lemref{lem:nearly flat after conditioning}, which follows the proof of \thref{thm:layered hashing}.  This completes the proof of \clref{cl:fuzz proportional beta}.
 \end{proof}
@@
 \begin{align*}
-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
+\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &\ge -\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
 &=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
@@
 &\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log \frac{1}{\delta}\\
-&\ge\Hfuzz(W)-1-\log n -\log \frac{1}{\delta} - \log (1-2^{-m})
-\end{align*}
-Where the second-to-last line follows by \lemref{lem:chain rule fuzz}.  The last line follows by \lemref{lem:conditional fuzz rule} and by noting that $\Pr[1_{\text{low}}=0] \ge 1/(1-2^{-m})$.
+&\ge\Hfuzz(W)-1-\log n -\log \frac{1}{\delta} + \log (1-2^{-m})
+\end{align*}
+Where the second-to-last line follows by \lemref{lem:chain rule fuzz}.  The last line follows by \lemref{lem:conditional fuzz rule} and by noting that $\Pr[1_{\text{low}}=0] \ge (1-2^{-m})$.
 Returning to equation \ref{eq:min-entropy} one has:
@@
 \Hav(W | \sketch(W)) &\ge -\log\left( 2^{-m} + (1-2^{-m}) 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)\\
-&\ge -\log \left(2^{-m}+2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\right)\\
-&\ge -\log \min\{2^{-m}, 2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\}-1\\
-&\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  -2\log (1-2^{-m}) \\
+&\ge -\log \left(2^{-m}+2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta+2\log (1-2^{-m}) )}\right)\\
+&\ge -\log \min\{2^{-m}, 2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta+2\log (1-2^{-m}) )}\}-1\\
+&\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  +2\log (1-2^{-m}) \\
 &\ge \Hfuzz(W) - 4- \log n - \log 1/\delta
@@
 Where the fourth line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$.
-The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \le 1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
+The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \ge -1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
 \end{proof}
@@
 \label{lem:nearly flat after conditioning}
-Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.
-Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
+Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]/2$.
+Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2.$
 \end{lemma}
@@
 Let $C$ be a set over space $\mathcal{M}$.
-We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists a procedure $\rec$ such that for all $t'\le t$ and for all $c\in C$, $\Pr[c'\leftarrow \neigh_t(c) \wedge \rec(c') \neq c]\le \delta$.
+We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists a procedure $\rec$ such that for all $c\in C$, $\Pr[c'\leftarrow \neigh_t(c) \wedge \rec(c') \neq c]\le \delta$.
 %To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
@@
 Since $w, w'$ are independent of $ss$ this does not effect correctness.
-Security is defined based on the output of $\rec$ so outputting the coins of $\rec$ does not effect security.
+Security is defined based on the output of $\sketch$ so outputting the coins of $\rec$ does not effect security.
 By the definition of correctness for $(\sketch, \rec)$, 
 \[
-\forall w, w', \dis(w, w') \le t, \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
+\forall w, w', \dis(w, w') \le t, \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < \delta.
 \]
@@
 \[
-\frac{|\{w' | \dis (w', w)\le t \wedge \rec(w', ss) \neq w\}|}{|\{w'|\dis(w', w) \le t\}|}\le 2\delta < 1/2.\]
+\frac{|\{w' | \dis (w', w)\le t \wedge \rec(w', ss) \neq w\}|}{|\{w'|\dis(w', w) \le t\}|}\le 2\delta.\]
 
@@
 For the sketched value $w$, at most a $2\delta$ fraction of nearby $w'$ do not map to $w$.
-Thus, this is also true for every value in $V|\sketch(V) = ss^*$ this is also true.
+Thus, this is also true for every value in $V|\sketch(V) = ss^*$.
 This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).
@@
 \end{proof}
-\bnote{the reviewer is complaining that $V | \sketch(V)$ is not a distribution.  don't know why}
 \begin{lemma}
 \label{lem:side info determines sketch}
-$\Hav(V | \sketch(V), Z) <2$.
+$\tilde{H}_0(V | \sketch(V), Z) <2$ and thus $\Hav(V | \sketch(V), Z) <2$.
 \end{lemma}
@@
 Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
- As described above, the view of $\sketch, \rec$ is a uniform distribution $V$. 
+ As described above, the view of $\sketch$ is a uniform distribution $V$. 
 The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
@@
 \end{align*}
-The statement of the lemma follows by noting that for any $X, Y$, $\Hav(X|Y)\le \tilde{H}_0(X|Y)$.
-\end{proof}
-
-\lnote{need for \lemref{lem:log-minus-one}:  $\gamma-1\le |F|$ and $|F|\ge 4$}
-\lnote{change the any needed theorem statements it affects in light of the tightening}
+\end{proof}
 
@@
 This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$.
-That is, at least one of the bits in each block differs between $w$ and $w'$, and so $\dis(w, w') \ge n/\nu$.
+That is, at least one of the bits in each block differs between $w$ and $w'$, and so $\dis(w, w') \ge n/\nu>t$.
 Since no two values in the support of $W_z$ lie in the same ball of radius $t$, we have $\Hfuzz(W_z) = \Hoo(W_z)= \omega(\log n)$.
@@
 \[
-(\Key |P =p) \approx_{2\epsilon} (U_\kappa , P =p).
+(\Key |P =p, P=p) \approx_{2\epsilon} (U_\kappa , P =p).
 \]
